### 2014-06-23 Report/decomposition_solutions.tex
Git repository for Journal - 1

This section addresses the distributed precoder designs for the proposed \ac{JSFRA} scheme. The formulation in \eqref{eqn-9} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}. In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are considered. In particular, the \ac{PD} and the \ac{ADMM} based \ac{DD} approaches are addressed.

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\set{\mc{B} \backslash \{b\}}} and \me{\bar{\mc{U}}_b} represents the set \me{\set{\mc{U} \backslash \mc{U}_b}}. The centralized problem defined by \eqref{eqn-9} can be equivalently written as
\begin{IEEEeqnarray}{rCl} \label{eqn-decent-1}
\underset{\substack{t_{l,k,n},\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber,
\end{IEEEeqnarray}
where \me{\tilde{\mbf{v}}_b} denote the vector of of weighted queue deviation corresponding to the users \me{k \in \mc{U}_b}.

Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized} and \cite{kaleva2013primal}, the interference constraint given by \eqref{eqn-9.1c} can be expressed by grouping the interference contribution from each \acp{BS} in the system as
\begin{IEEEeqnarray}{RCL}
\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \underbrace{\sum_{b \in \bar{\mc{B}}_{b_k}} \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}_{\text{neighboring \acp{BS} interference}} \; + \; N_0, \forall k \in \mc{U}.
\label{eqn-decent-2}
\end{IEEEeqnarray}
In \eqref{eqn-decent-2}, the neighboring \acp{BS} signals can be written explicitly using the relaxed expression as
\begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0, \IEEEyessubnumber \label{eqn-decent-3a}
\end{IEEEeqnarray}
where \me{\zeta_{l,k,n,b}}, which is the total interference caused by the \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
\begin{equation}
\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
\end{equation}

The expression in \eqref{eqn-decent-3} can be solved either by primal or by dual decomposition based on the usage of the coupling variable \me{\zeta_{l,k,n,b}} in the optimization problem. In both approaches, the distributed problem is solved by a two level optimization approach in which the local problems are solved at the \ac{BS} level and the master problem controls the variables involved in each local problem \cite{palomar2006tutorial}.

### 2014-06-23 Report/dual_algorithm.tex
Git repository for Journal - 1

In this section, we discuss the alternative approach of decentralizing the precoder design problem using the dual decomposition approach. It differs from the primal approach by fixing the interference price instead of fixing the interference level, which is the case in the primal design. As in the primal approach, in order to decentralize the precoder design problem, the interference terms present in the \ac{SINR} expression \eqref{eq:SINR} using the precoders of the neighbouring \acp{BS} \me{\tilde{\mc{B}}_b} are to be decoupled from the \ac{BS} \me{b}.

In contrast to the primal approach, which decouples the interference by a fixed threshold level as in \eqref{eq-primal-constr}, the dual decomposition decouples the interference by fixing the interference price for all \ac{BS} \me{b} to a user \me{k \in \tilde{\mc{U}_b}} at each iteration. The interference constraint limit as in primal approach is given by
\begin{equation}
\sum_{\pr{k} \in \mc{U}_b} \text{tr} \left ( \mvec{w}{l,k,n}^H \mvec{H}{b,k,n} \mvec{M}{\pr{k},n} \mvec{M}{\pr{k},n}^H \mvec{H}{b,k,n}^H \mvec{w}{l,k,n} \, \right ) \leq \zeta_{l,b,k,n}, \forall k \notin \mc{U}_b
\end{equation}
In order to relax the interference constraint, the dual decomposition approach replaces the interference threshold level \me{\zeta_{l,b,k,n}} by a local copy \me{\zeta^{(b)}_{l,b,k,n}} for each \ac{BS} \me{b \in \mc{B}}. The additional constraint relating the local interference copies to the global interference thresholds are added as
\begin{IEEEeqnarray}{rCl}\label{eq-dual-constr}
\zeta_{l,b,k,n} & \geq & \sum_{\pr{k} \in \mc{U}_b} \text{tr} \left ( \mvec{w}{l,k,n}^H \mvec{H}{b,k,n} \mvec{M}{\pr{k},n} \mvec{M}{\pr{k},n}^H \mvec{H}{b,k,n}^H \mvec{w}{l,k,n} \, \right ), \forall k \notin \mc{U}_b \IEEEyessubnumber \\
\zeta^{(b)}_{l,b,k,n} & = & \zeta_{l,b,k,n}, \forall b. \IEEEyessubnumber \label{eqn-dual-x}
\end{IEEEeqnarray}

The equivalent problem with the local interference variable is written as
\begin{IEEEeqnarray}{rCl}\label{dual-problem}
\underset{\substack{\mvec{m}{l,k,n},p_{l,k,n},\\q_{l,k,n},\beta_{l,k,n},\mbfa{\zeta}^{(b)}}}{\text{minimize}} & \quad & \| \tilde{\mbf{v}}_{b} \|_q \IEEEyessubnumber \\
\text{subject to} & \quad & \bar{\gamma}_{l,k,n} \leq \dfrac{p_{l,k,n}^2 + q_{l,k,n}^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-dual-1} \\
& \quad & N_0 + \rho_{l,k,n} + \sum_{\pr{b} \in \tilde{\mc{B}}_{b}} \zeta^{(b)}_{l,\pr{b},k,n} \leq \beta_{l,k,n} \IEEEyessubnumber \label{eqn-dual-2} \\
& \quad & \eqref{eqn-4.3}, \eqref{eqn-8}, \text{ and } \eqref{eq-dual-constr}, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\bar{\gamma}_{l,k,n}} is given by
\begin{equation}\label{eq:SINR-dual}
\bar{\gamma}_{l,k,n} = \frac{\left | \mvec{w}{l,k,n}^H \mvec{H}{b,k,n} \mvec{m}{l,k,n} \right |^2}{\displaystyle \sum_{\pr{b} \in \tilde{\mc{B}}_{b} } \zeta^{(b)}_{l,\pr{b},k,n} + \rho_{l,k,n} + N_0},
\end{equation}
where \me{p_{l,k,n}, q_{l,k,n}, \bar{\gamma}_{l,k,n}}, and \me{\rho_{l,k,n}} are as defined in \eqref{eqn-wsrm-expr}, \eqref{eq:SINR-dual} and \eqref{eqn-rho} respectively. In order to obtain the distributed algorithm, dual decomposition approach \cite{tolli2011decentralized}, \cite{palomar2006tutorial} is used for the equality constraint given by \eqref{eqn-dual-x}.

### 2014-06-23 Report/dual_approach.tex
Git repository for Journal - 1

In contrast to the \acl{PD} problem, the \acf{DD} performs the distributed precoder design by relaxing the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{tolli2011decentralized,palomar2006tutorial}. In order to decouple the problem \eqref{eqn-decent-1}, the global coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the local copies at each \ac{BS} \me{b} denoted by \me{\zeta^{\set{b}}_{l,k,n,b}, \fall b\in \mc{B}}, which is then used in the problem as an optimization variable.

Let  \me{\mbfa{\zeta}^{\set{b_k}}} be the locally maintained vector formed by stacking the interference entries relevant to the \ac{BS} \me{b_k}. Let \me{\mbfa{\zeta}} be the complete interference entries of all \acp{BS} in the set \me{\mc{B}} stacked as a vector as
\begin{IEEEeqnarray}{rCl}
\mbfa{\zeta} &=& \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1},  \right. \nonumber \\
&\quad& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \IEEEyessubnumber \\
n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\mbfa{\zeta}(b_k)} denote the entries corresponding to the \ac{BS} \me{b_k} and the vector \me{\mbfa{\nu}^{\set{b_k}}} stacks the dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)}. The equality constraint for the local and the global interference vector \me{\zeta^{\set{b_k}}_{l,k,n,b} = \zeta_{l,k,n,b}, \fall b \in \bar{\mc{B}}_{b_k}, k \in \mc{U}} and \me{\forall k \in \bar{\mc{U}}_{b_k}, b=b_k} is relaxed by the partial Lagrangian in the objective as
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-2} \label{eqn-dual-1}
\underset{\substack{\gamma_{l,k,n}, \nu^{\set{b_k}}_{l,k,n,b} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}, \zeta^{\set{b_k}}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}}T} \left ( \mbfa{\zeta}^{\set{b_k}} - \mbfa{\zeta}(b_k) \right ) \IEEEyessubnumber \label{eqn-dual-2a} \\
\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{\set{b_k}}_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-dual-1d} \\
&& \zeta^{\set{b_k}}_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-dual-1e} \\
&\quad& \mbfa{\nu}^{\set{b_k}} \in \mathbb{R}^{n_{b_k}}_+, \; \eqref{eqn-8} \; \text{and} \; \eqref{eqn-primal-1c}. \IEEEyessubnumber \label{eqn-dual-1f}
\end{IEEEeqnarray}
It can be seen from the objective \eqref{eqn-dual-2a} that the global interference \me{\mbfa{\zeta}(b_k)} can be dropped from the objective \eqref{eqn-dual-2a} without affecting the optimal solution, since it is constant for the subproblems.

Now, the problem defined in \eqref{eqn-dual-2} can be decoupled to solve for the precoders at each \ac{BS} by using interference vector \me{\mbfa{\zeta}^{\set{b_k}}} as a optimization variable for the fixed interference price (dual variable) \me{\mbfa{\nu}^{\set{b_k}}}. The convergence of the problem with the objective function \eqref{eqn-dual-2} is slower due to the linear penalty term for the interference assumptions at each \ac{BS}, thereby providing more emphasis only when the interference deviation is significantly large.

In order to bound the interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} and \me{\zeta^{\set{b}}_{l,k,n,b}} between the \acp{BS} \me{b_k} and \me{b}, adding a scaled quadratic penalty of the interference deviation provides better convergence properties without affecting the optimal solution \cite{bertsekas1999nonlinear,boyd2011distributed}. At the optimal point, the actual and the assumed (local) interference values are equal, thereby providing no contribution to the objective. This way of adding a scaled quadratic penalty term in the objective function is known as \ac{ADMM} method for solving the \acl{DD} problem. In addition to the faster convergence, it also identifies the optimal step size for the dual variable update. It can be shown that the optimal step size is equal to the scaling factor \me{\rho} used for the penalty term in the objective function \cite{bertsekas1999nonlinear,boyd2011distributed}. Now, the subproblem at each \ac{BS}, obtained via \ac{ADMM} decomposition, is given by
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \zeta^{\set{b_k}(i)}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}(i)}T} \mbfa{\zeta}^{\set{b_k}(i)} + \frac{\rho}{2} \left \| \, \mbfa{\zeta}^{(i)}(b_k) - \mbfa{\zeta}^{\set{b_k}(i)} \, \right \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
\text{subject to} & \quad & \eqref{eqn-dual-1d} - \eqref{eqn-dual-1f} \IEEEyessubnumber \label{eqn-dual-3b},
\end{IEEEeqnarray}
where \me{(i)} represents the current iteration counter or information exchange counter and \me{\mbfa{\zeta}^{(i)}} denotes the updated interference level obtained from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.

Once the subproblems are solved at each \ac{BS}, the update for the global interference vector and the dual variables can be performed at the \acp{BS} locally by exchanging the local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}. Since the entries in \me{\mbfa{\zeta}^{(i)}} relates exactly two \acp{BS} only, each entry in the \me{\mbfa{\zeta}^{(i)}} can be updated using a function operating on the local copies from the corresponding \acp{BS}. For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i-1)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by the \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b}}. It can be updated by either using
\begin{subeqnarray}
\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} &=& \zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} \, \text{(or)}\slabel{zeta_update-1} \\
\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} &=& \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ), \slabel{zeta_update-2}
\end{subeqnarray}
as discussed briefly in \cite{tolli2011decentralized}. The dual variable entries in the vector \me{\mbfa{\nu}^{\set{b_k}}}, which is the stacked dual variables corresponding to the interference equality constraint at the \ac{BS} \me{b_k}, are updated using the subgradient as
\begin{equation}\label{dual-sg-update}
\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i-1)}_{l,k,n,b} - \zeta^{\set{b}(i-1)}_{l,k,n,b} \right ), \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}.
\end{equation}

The \ac{ADMM} approach uses the quadratic penalty term in the objective for better convergence properties compared to the plain \ac{DD} scheme. The addition of the quadratic term in the objective translates the objective function into a strict convex function. The subproblem defined by \eqref{eqn-dual-3} is convex and the objective has the convex function, therefore the convergence is guaranteed as discussed in \cite{scutari,boyd2011distributed}. The algorithmic representation of the \ac{ADMM} based approach for decentralization is given in Algorithm \ref{algo-3}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
 initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
        exchange \me{\mbfa{\zeta}^{\set{b}(j)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
		update the dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update} \;
        update the interference vector \me{\mbfa{\zeta}^{\set{b}(j+1)}} using \eqref{zeta_update-1} or \eqref{zeta_update-2} \;
		\me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the transmit and the receive precoders \me{\mbf{M}_{k,n}} and \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{\ac{ADMM} based decentralized \acs{JSFRA} scheme}
  \label{algo-3}
\end{algorithm}

### 2014-06-23 Report/icassp_2014_Modified.tex
Git repository for Journal - 1

\documentclass[journal]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{graphicx,acronym}
\usepackage[ruled]{algorithm2e}
\usepackage{subeqnarray,multirow,cite,array}
\usepackage{color}

\acrodef{MSE}{mean squared error}
\acrodef{BC}{broadcast channel}
\acrodef{MC}{multi-cell}
\acrodef{BS}{base station}
\acrodef{MIMO}{multiple-input multiple-output}
\acrodef{SISO}{single-input single-output}
\acrodef{MU}{multi-user}
\acrodef{MU-MIMO}{\acl{MU} \acl{MIMO}}
\acrodef{OFDM}{orthogonal frequency division multiplexing}
\acrodef{WSRM}{weighted sum rate maximization}
\acrodef{QoS}{quality of service}
\acrodef{SCA}{successive convex approximation}
\acrodef{SNR}{signal-to-noise ratio}
\acrodef{MMSE}{minimum \acl{MSE}}
\acrodef{SIR}{signal-to-interference ratio}
\acrodef{SINR}{signal-to-interference-plus-noise ratio}
\acrodef{Q-WSRM}{queue \acl{WSRM}}
\acrodef{QM}{queue minimizing}
\acrodef{SRA}{spatial resource allocation}
\acrodef{JSFRA}{joint space-frequency resource allocation}
\acrodef{WMMSE}{weighted \acl{MMSE}}
\acrodef{KKT}{Karush-Kuhn-Tucker}
\acrodef{GP}{geometric programming}
\acrodef{SOC}{second-order cone}
\acrodef{BCDM}{block coordinate descent method}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\me}[1]{\( #1 \)}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\fall}{\; \forall \;}
\newcommand{\set}[1]{\left \lbrace #1 \right \rbrace }
\newcommand{\mvec}[2]{\mathbf{#1}_{#2}}

\graphicspath{{./../Figures/}}
\DeclareGraphicsExtensions{.eps}

\title{Queue Aware Precoder Design for Space Frequency Resource Allocation}
\author{{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti}
{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
University of Oulu, Oulu, FI-90014\\
Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
}

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\acresetall

\acresetall
\section{conclusions}\label{sec-5}
In this paper, we proposed algorithms to minimize the number of queued packets in a coordinated manner by designing the precoders jointly across the space-frequency dimension for a multi-cell \ac{MU-MIMO} system. The proposed \ac{QM} \ac{JSFRA} scheme adopting the \ac{SCA} technique models the nonconvex constraint as a convex constraint in an iterative manner to design the precoders for the \ac{QM} objective. The \ac{JSFRA} scheme provides better convergence and performance over the traditional per sub-channel \ac{Q-WSRM} approach with the proper queue updates. The impact of varying the exponent used in the objective were also studied with the number of packets remained after the scheduling instant. The decentralized version, which provides independent precoder design with the minimal information exchange will be addressed in our future work.

\section*{Acknowledgement}
This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Siemens Networks, Xilinx Ireland, Renesas Mobile Europe, Academy of Finland.

\vfill
\bibliographystyle{./../Styles/IEEEtran}
\bibliography{./../Library/kirja_survey}

\end{document}

### 2014-06-23 Report/ieee_journal.tex
Git repository for Journal - 1

\documentclass[10pt,letterpaper,journal,onecolumn]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{graphicx,acronym}
\usepackage[ruled]{algorithm2e}
\usepackage{caption,subcaption}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e}

\graphicspath{{./../Figures/}}
\DeclareGraphicsExtensions{.eps}

\input{shortcuts}
\input{acronyms}

\doublespacing

%\title{Queue Aware Precoder Design for Space Frequency Resource Allocation}
%\author{{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti}
%\IEEE{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
%University of Oulu, Oulu, FI-90014\\
%Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
%}

\begin{document}

\begin{abstract}
%\input{abstract}
\end{abstract}

\section{Introduction} \label{sec-1}
%\input{introduction}

\section{System Model and Problem Formulation} 
\subsection{System Model} \label{sec-2}
\input{system_model}
\subsection{Problem Formulation} \label{sec-3.2}
\input{problem_formulation}

\section{Queue Minimizing Precoder Designs} \label{sec-3}
\input{queue_minimizing_intro}

\subsection{Queue Weighted Sum Rate Maximization (\acs{Q-WSRM}) Formulation} \label{sec-3.1}
\input{joint_wsrm_formulation}

\subsection{\ac{JSFRA} scheme via Successive Convex Approximation (\acs{SCA})}
\input{wsrm_formulation}

\subsection{\ac{JSFRA} scheme via MSE reformulation} \label{sec-3.3}
\input{mse_formulation}

\subsection{Reduced Complexity Resource Allocation (Per Sub-Channel Resource Allocation)} \label{sec-3.4}
\input{sub_channel_wsrm}

\section{Distributed Solutions} \label{sec-4}

\input{decomposition_solutions}

\subsection{Primal Decomposition Approach} \label{sec-4.1}

\input{primal_approach}
%\input{primal_algorithm}

\subsection{\ac{ADMM} approach} \label{sec-4.2}

\input{dual_approach}
%\input{dual_algorithm}

\subsection{Distributed MSE Formulation} \label{sec-4.3}

\input{kkt_mse_approach}

\section{Simulation Results} \label{sec-5}
\subsection{Centralized Solutions}
\input{simulation_results}

\subsection{Distributed Solutions}
\input{simulation_distributed}

\section*{Acknowledgment}
This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Renesas Mobile Europe, Academy of Finland.

\section{Conclusions}

\appendices

\section{\ac{KKT} expressions for the Distributed MSE Formulation} \label{a-1}
\input{kkt_appendix}

\bibliographystyle{./../Styles/IEEEtran}
\bibliography{./../Library/kirja_survey}

\end{document}

### 2014-06-23 Report/introduction.tex
Git repository for Journal - 1

We consider the problem of resource allocation for a multi-cell \ac{MU-MIMO} transmission over an \ac{OFDM} system with the objective of minimizing the total number of backlogged packets of all users at a given instant. The available space and frequency resources in the considered system are shared among the users by \ac{BS} cooperation in order to minimize the number of packets waiting for transmission from each \ac{BS} to the respective users. In this paper, beamforming technique is utilized at \acp{BS} and linear single-user detection is employed at each receiver, i.e., the inter-user interference is treated as background noise. The queue minimizing network optimization objective is used to design beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets. To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in queues prior to transmission, and, hence, to avoid packet drops as an indirect objective.

Many existing beamformer designs for similar system models addresses the problem of \ac{WSRM} objective. By adjusting the weights properly, we can use the \ac{WSRM} schemes to achieve other performance measures. For example, if the weight of each user is set to be inversely proportional to his/her data rate, a \ac{WSRM} scheme can maintain fairness among users. Similarly, the \ac{WSRM} schemes can be used to solve the design problem considered in this paper. Specifically, to find a rate vector that minimizes the number of queued packets, we should assign weights based on the current queue size of users. More explicitly, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function depending on it \cite{neely2010stochastic}, where the \ac{Q-WSRM} scheme is the outcome of minimizing the Lyapunov drift between the current and the future queue states.

The topic of \ac{MIMO} \ac{BC} precoder design has been studied extensively with different performance criteria in the literature. For the problem of \ac{WSRM} utility, due to the nonconvex nature of the linear \ac{MIMO} \ac{BC} precoder design, \cite{christensen2008weighted,wmmse_shi} addressed the problem using a reformulation via \ac{MMSE}, casting the problem as a convex one for  fixed receivers. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders. Then the problem is solved using an alternating optimization method, i.e., finding a set of variables while the remaining others are fixed. The \ac{WSRM} problem using an alternative \ac{MMSE} reformulation along with the additional rate constraints is considered in \cite{kaleva2013primal}. A fast converging algorithm for the \ac{WSRM} problem is proposed in \cite{tran2012fast} using a surrogate for a convex program at each iteration.

Earlier work on the queue minimization problem was addressed in the survey paper \cite{berry2004cross} and in particular \cite{qps_cioffi}, where the problem of optimal power allocation is considered to minimize the number of backlogged packets via \acl{GP} formulation. Since the problem considered in \cite{qps_cioffi} assumes multi-user \ac{OFDM} model without multi-antenna support, the queue minimizing scheduling reduces to the problem of optimal power allocation.

In this paper, we consider the problem of designing the precoders for a \ac{MU-MIMO} \ac{OFDM} scenario jointly across space-frequency dimension to minimize the number of queued packets associated with the users. We compare the performance of the proposed \ac{QM} \ac{JSFRA} scheme over the \ac{Q-WSRM} scheme performed over each sub-channel, where the weights are updated after each sub-channel with the unserved packets. We show that the \ac{JSFRA} scheme provides better performance over the sub-channel wise resource allocation technique like \ac{Q-WSRM} scheme.

### 2014-06-23 Report/joint_wsrm_formulation.tex
Git repository for Journal - 1

The \ac{WSRM} technique is predominantly used to design the precoders for the \ac{MIMO} \ac{BC} channels to maximize the weighted sum throughput in the downlink direction. The weights are used to provide different priorities to the users based on their requirements and \ac{QoS} criterion. Since the objective of this work is mainly concerned with the reduction of the number of queued packets, we use the length of the queued packets for each user as the respective weights. Using the length of the queued packets as the corresponding weights is obtained from the well known algorithm, called the \textit{backpreassure algorithm}, which is used to decide the routing decisions for each node in the network to efficiently send the packets to the desired destination with minimal packet drops and delay. The backpreassure algorithm is the outcome of minimizing the Lyapunov drift conditioned over the current queue states \me{\mbf{Q}(i - 1)}, where \me{\mbf{Q}} is the vector formed by stacking the number of queued packets of each user in the system. Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift is given by \cite{georgiadis2006resource,neely2010stochastic}
\begin{equation}
L(i) = \frac{1}{2} \, \| \mbf{Q}(i) \|^2_2 = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k(i)^2.
\end{equation}
The conditional Lyapunov drift is given by taking expectation over all channel realizations as
\begin{equation}
\Delta(i) = \mathrm{E}_H \left [ L(i) - L(i - 1) | \mbf{Q}(i - 1) \right ],
\label{eqn-3.1.0}
\end{equation}
since the transmission depends on the channel condition. Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression can be upper bounded by
\begin{equation}
\Delta(i)\leq \sum_{k \in \mc{U}} \, \mathrm{E}_H \left [ \mbf{Q}(i-1) \left ( \mbf{\lambda}(i) - \mbf{t}(i) \right ) | \mbf{Q}(i-1) \right ] + \mathrm{E}_H \left [ \mbf{\lambda}^2(i-1) \right ] + \mathrm{E} \left [ \mbf{t}^2(i-1) \right ],
\end{equation}
where \me{\mbf{\lambda}} and \me{\mbf{t}} are the stacked arrivals and transmissions of all users. Since the expectation is conditioned over \me{\mbf{Q}(i-1)} and the second order statistics of the arrivals and the transmissions are bounded \cite{neely2010stochastic}, the drift minimization solution is given as
\begin{equation}
\underset{\mbf{t}(i)}{\text{minimize}} \sum_{k \in \mc{U}} \, Q_k(i-1) \: t_k(i).
\label{backpreassure}
\end{equation}

Now from \eqref{backpreassure}, the optimization variables \me{\mbf{t}(i)}, which is the vectorized transmission rates, are to be identified for each user for the current slot \me{i}. Since the current system can exploit both space and frequency resources through \ac{MIMO} \ac{OFDM} model, the transmission rates \me{\mbf{t}(i)} for the current instant can be controlled using the transmit precoders \me{\mbf{M}_{k,n}} designed for each user over each sub-channel resource. Since the decision variables \me{\mbf{t}(i)} depends on the queue state at \me{\mbf{Q}(i - 1)}, we drop the time variable \me{i} for the easy representation. The above problem defined in \eqref{backpreassure} can be rewritten to include the space-frequency allocation variable, namely \me{\mbf{M}_{k,n}}, as
\begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
\text{subject to.} & \quad & t_{l,k,n} \leq \log_2(1+\gamma_{l,k,n}) \IEEEyessubnumber \label{eqn-3.1.2} \\
& \quad &\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-3.1.3} \\
& \quad & \sum_{n=1}^N \sum_{l = 1}^L t_{l,k,n} \leq Q_k, \fall k \in \mc{U} \IEEEyessubnumber \label{eqn-3.1.4}
\end{IEEEeqnarray}
where \eqref{eqn-3.1.4} is due to the \me{[x]^+} operation in \eqref{eqn-2a} and \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}. By using the number of queued packets as the weights, the resources can be allocated to the user with the more number of backlogged packets, which essentially does the allocation in a greedy manner. As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as
\begin{IEEEeqnarray}{rCl}\label{gen_sum}
\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \IEEEyessubnumber \\
\text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.2}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4}. \IEEEyessubnumber
\end{IEEEeqnarray}

The problem defined in \eqref{gen_sum} provides an efficient queue minimizing approach as compared to \eqref{q_gen_sum}, since the resource allocation is driven by the channel conditions as compared to the number of queued packets in the problem defined in \eqref{q_gen_sum}. In both formulations, the resources allocated to the users are limited by the backlogged packets \eqref{eqn-3.1.4}, thereby handling the problem of over allocation. The resource allocation constraint in \eqref{eqn-3.1.4} renders the problem difficult to be solved by the iterative algorithm to design the precoders, which will be discussed later.

### 2014-06-23 Report/kkt_mse_approach.tex
Git repository for Journal - 1

So far, we have discussed the problem of minimizing the number of backlogged packets at the \acp{BS} using the precoders by formulating it as an optimization problem, which can be handled by the existing solvers CVX \cite{grant2008cvx}. In this section, we provide an iterative precoder design for the \ac{JSFRA} formulation approached via \ac{MSE} reformulation as discussed in \ref{sec-3.3}. Even though the \ac{JSFRA} scheme using \ac{SCA} approach and the \ac{MSE} reformulation approach obtained the solutions by relaxing the nonconvex constraints by the half spaces, the structure of the \ac{MSE} reformulation problem allows us to decouple the problem readily without further approximations.

In order to come up with the iterative solution, we need to find the \ac{KKT} equations for the the \ac{MSE} reformulation problem defined in \eqref{eqn-mse-2}. It can be seen that the objective function \eqref{eqn-mse-2.1} has the norm function, which requires the sum of absolute values of the vector entries raised to the power \me{q}. Since the absolute of a function is not differentiable, the problem is usually solved by the subgradient approach. Since the subgradients are not unique and the selection of a subgradient and a step size are not guaranteed to be optimal, in this approach, we drop the absolute value operation for the queue deviation function so as to obtain a unique supporting vector. It is valid in the following special cases without affecting the optimal solution
\begin{itemize}
\item when the exponent \me{q} is odd and \me{q > 1} or,
\item when the number of backlogged packets for each user is larger than the available resources for the transmission \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
\end{itemize}
The first condition is from the fact that the differential of a function with power \me{q} leaves the power to \me{q-1}, which helps us to drop the absolute value condition when \me{q-1} is even. This condition cannot be applied for \me{q=1} since the rate constraint is eliminated by the differential operation.

By removing the absolute value operator from \eqref{eqn-mse-2}, the problem can be rewritten as
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \alpha_{l,k,n},\delta_{b}, \sigma_{l,k,n}}}{\text{minimize}} &\quad& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \left ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \quad & \nonumber \\
\alpha_{l,k,n} : & \quad & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \quad & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} = t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}. The equality condition is used for \eqref{kkt-mse-1.2} and \eqref{kkt-mse-1.3}, since the variables \me{\epsilon_{l,k,n}} and \me{t_{l,k,n}} are used for the corresponding expressions on the other side.

Now the Lagrangian of the problem expressed in \eqref{kkt-mse-1}, with the corresponding dual variables, is used obtain the \ac{KKT} expressions by partially differentiating with respect to the variables \me{t_{l,k,n}}, \me{\epsilon_{l,k,n}}, \me{m_{l,k,n}}, \me{w_{l,k,n}} and the dual variables \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b}. Since the problem of precoder design using \ac{MSE} reformulation is solved by the iterative method, we use the iteration index \me{i} in the superscript to represent the variables at the respective iteration instants. The discussions on the \ac{KKT} expressions are provided in the  Appendix \ref{a-1}. Upon solving the \ac{KKT} expressions, we obtain the following iterative solution with the variables update as
\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
\alpha^{(i)}_{l,k,n} &=& \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.1} \\
\sigma_{l,k,n}^{(i)} &=& \dfrac{q \left [ a_k \, \left (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i-1)} \right )^{(q-1)} \right ]}{\log(2)} \IEEEyessubnumber \label{kkt-mse-4.2} \\
\mvec{m}{l,k,n}^{(i)} &=& \left ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \right )^{-1} \alpha^{(i)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
\mvec{w}{l,k,n}^{(i)} &=& \left ( \sum_{(x,y) \neq (l,k)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i-1)} \mvec{m}{x,y,n}^{\herm \, (i-1)} \mvec{H}{b_{y},k,n}^\herm + \mathbf{I}_{N_R} \right ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i-1)}. \IEEEyessubnumber \label{kkt-mse-4.6}
\end{IEEEeqnarray}

The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the \ac{MSE} variables \me{\epsilon_{l,k,n}^{(0)}} and the throughput variables \me{t_{l,k,n}^{(0)}} randomly. It can be initiated by solving \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} for a random transmit precoders \me{\mbf{M}_{k,n}} satisfying \eqref{kkt-mse-1.4}. It can be noted that the proposed iterative algorithm converges faster than the \acl{PD} and the \ac{ADMM} based \acl{DD} scheme, since the later schemes are based on the subgradient approach and the former one achieves the \ac{KKT} points at each iteration. In \eqref{kkt-mse-4}, all expressions provide the closed form solution for the respective variables except the transmit precoders in \eqref{kkt-mse-4.3}, which depends on the variable \me{\delta_b}. It can be seen that the variable \me{\delta_b} are associated only to the \ac{BS} \me{b}, which can be efficiently solved by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}. After each iteration instant, the transmit and the receive precoders are exchanged across the coordinating \acp{BS} in \me{\mc{B}} in order to reach the optimal point in the next iteration.

The receive beamformers from the users can be informed to the coordinating \acp{BS} by using the precoded uplink pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\mvec{W}{k,n}} evaluated at the receivers. Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\mvec{W}{k,n}^{\herm \, (i-1)} \mvec{H}{b,k,n}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS} \cite{komulainen2013effective}. The algorithmic representation of the \ac{KKT} based scheme is shown in Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1} and the transmit precoders \me{\mbf{m}^{(0)}_{l,k,n}} randomly satisfying the total power constraint \eqref{kkt-mse-1.4}}
 \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly, \me{\mvec{w}{l,k,n}^{(0)}} with \eqref{kkt-mse-4.6} and \me{{t}_{l,k,n}^{(0)}} using \eqref{kkt-mse-4.5}}
 set the maximum iteration counter \me{I_{\max}} to a valid number \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2} \;
	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} with \me{\delta_b} using \eqref{kkt-mse-4.3} by the bisection method satisfying \eqref{kkt-mse-1.4} \;
	update the \ac{MSE} variable \me{\epsilon_{l,k,n}^{(i)}} and the throughput variable \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} \;
	evaluate the receive beamforming vector \me{\mvec{W}{k,n}} by \eqref{kkt-mse-4.6} \;
	exchange the transmit and the receive precoders \me{\mvec{M}{k,n}^{(i)}, \mvec{W}{k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
	$i = i + 1$ \;
  }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
  \label{algo-4}
\end{algorithm}

### 2014-06-23 Report/mse_formulation.tex
Git repository for Journal - 1

In this section, we provide an alternative formulation for the \ac{QM} \ac{JSFRA} scheme using the \ac{MSE} equivalence with the capacity as in \cite{wmmse_shi,kaleva2012weighted} for the \ac{WSRM} problem. The proposed formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} expression for decoding the transmitted symbols using \ac{MMSE} receivers and \me{C} being the capacity of the system. Using the \ac{MSE} relation, \eqref{eqn-6} is written as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\text{minimize} &\quad& \|  \tilde{\mbf{v}}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
&\quad& \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{\mvec{t}{l,k,n}} using the the \ac{MSE} relation.

The \ac{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the set defined by the constraint \eqref{eqn-mse-1.2}. In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}. The first order Taylor approximation around a fixed \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} for \eqref{eqn-mse-1.2} is given by
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}.
\label{mse-lin}
\end{IEEEeqnarray}

Now, using the above approximation for the rate constraint, the optimization problem is solved for the optimal precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}}. Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}. The optimization problem can be given as
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
\text{minimize} &\quad& \|  \tilde{\mbf{v}}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
\end{IEEEeqnarray}
The algorithmic representation is similar to Algorithm \ref{algo-1}, with \eqref{eqn-9} is replaced by \eqref{eqn-mse-2}. The convergence of the \ac{MSE} reformulation algorithm follows the similar comments drawn in \cite{christensen2008weighted,wmmse_shi}. Since at each \ac{KKT} point, the gradient of the original problem and the \ac{MSE} reformulation problem are made equal by the weights in the \ac{MSE} reformulation, the problem is guaranteed to converge to the optimal solution by following the same stationary \ac{KKT} points.

### 2014-06-23 Report/primal_algorithm.tex
Git repository for Journal - 1

The primal decomposition approach is modeled by having a master controller, which controls the resources allocated to each \acp{BS} based on which the optimization is carried out locally at each \ac{BS}. In this scheme, the problem described in \eqref{eqn-9} is decomposed in a way that the precoders intended for the users associated with each \ac{BS} are designed locally with the additional constraint on the interference caused by the transmission to the neighbouring \ac{BS} users. The interference thresholds are set by the centralized controller for each data stream of the users in the system, which needs to be satisfied by the neighbouring \acp{BS} while designing the precoders.

Let \me{\tilde{\mc{B}}_{b}} represent the coordinating \acp{BS} set \me{\{\mc{B} \backslash b \}}. In order to design the precoders for the users \me{\mc{U}_b} belonging to the \ac{BS} \me{b} locally, the precoders related to the neighbouring users \me{\pr{k} \notin \mc{U}_b} are to be removed from the \ac{SINR} expression \eqref{eq:SINR}. To decouple the precoder design, the total interference caused by a \ac{BS} \me{\pr{b} \in \tilde{\mc{B}}_b} is replaced by a fixed interference level \me{\chi_{l,\pr{b},k,n}} associated with the \me{\ith{l}} spatial stream of the user \me{k \in \mc{U}_b}. The interference constraint used in the precoder design problem of the \ac{BS} \me{b} is given by
\begin{equation}
\sum_{\pr{k} \in \mc{U}_b} \text{tr} \left ( \mvec{w}{l,k,n}^H \mvec{H}{b,k,n} \mvec{M}{\pr{k},n} \mvec{M}{\pr{k},n}^H \mvec{H}{b,k,n}^H \mvec{w}{l,k,n} \, \right ) \leq \chi_{l,b,k,n}, \forall k \notin \mc{U}_b
\label{eq-primal-constr}
\end{equation}
Now, the \ac{SINR} expression for the spatial stream \me{l} of a user \me{k \in \mc{U}_b} is given by
\begin{equation}\label{eq:SINR-primal}
\bar{\gamma}_{l,k,n} = \frac{\left | \mvec{w}{l,k,n}^H \mvec{H}{b,k,n} \mvec{m}{l,k,n} \right |^2}{\displaystyle \sum_{\pr{b} \in \tilde{\mc{B}}_{b} } \chi_{l,\pr{b},k,n} + \rho_{l,k,n} + N_0} \leq \gamma_{l,k,n},
\end{equation}
where the inter-cell interference component \me{\rho_{l,k,n}} is given by
\begin{equation}
\rho_{l,k,n} = \sum_{\substack{\pr{l} = 1 ,\\ \pr{l} \neq l}}^L \left | \mvec{w}{l,k,n}^H \mvec{H}{b,k,n} \mvec{m}{\pr{l},k,n} \right |^2 + \sum_{\pr{k} \in \{\mc{U}_{b} \backslash k \}} \sum_{\pr{l}=1}^L \left | \mvec{w}{l,k,n}^H \mvec{H}{b,k,n} \mvec{m}{\pr{l},\pr{k},n} \right |^2.
\label{eqn-rho}
\end{equation}

In order to decouple the precoder design, \acp{BS} use the fixed interference levels set by the centralized controller in the \ac{SINR} expression \eqref{eq:SINR-primal} and additional interference constraints to limit the interference caused by the \ac{BS} \me{b} to the neighbouring users \me{\pr{k} \notin \mc{U}_b} is given by \eqref{eq-primal-constr}. Using the above constraints and approximations, the precoder design problem for a \ac{BS} \me{b} using the fixed interference level is given by
\begin{IEEEeqnarray}{rCl}\label{primal-problem}
\underset{\substack{\mvec{m}{l,k,n},p_{l,k,n},\\q_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} & \quad & \| \tilde{\mbf{v}}_{b} \|_q \IEEEyessubnumber \\
\text{subject to} & \quad & \bar{\gamma}_{l,k,n} \leq \dfrac{p_{l,k,n}^2 + q_{l,k,n}^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-sg-b} \\
& \quad & N_0 + \rho_{l,k,n} + \sum_{\pr{b} \in \tilde{\mc{B}}_{b}} \chi_{l,\pr{b},k,n} \leq \beta_{l,k,n} \IEEEyessubnumber \label{eqn-sg-d} \\
& \quad & \eqref{eqn-4.3}, \eqref{eqn-8}, \text{ and } \eqref{eq-primal-constr}, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{p_{l,k,n}, q_{l,k,n}, \bar{\gamma}_{l,k,n}}, and \me{\rho_{l,k,n}} are as defined in \eqref{eqn-wsrm-expr}, \eqref{eq:SINR-primal} and \eqref{eqn-rho} respectively. The weighted deviation vector \me{\tilde{\mbf{v}}_{b}} stack the weighted deviation metric of users belonging to the \ac{BS} \me{b} as the component elements as discussed earlier.

The local optimization problem solved at the \acp{BS} are coordinated by exchanging minimal information through the backhaul link across the coordinating \acp{BS} to design the optimum set of precoders at each \ac{BS}. The master problem, which determines the interference level for each \ac{BS} is obtained by solving the subgradient of the original problem \cite{palomar2006tutorial} and \cite{pennanen2011decentralized}. In order to obtain the dual variables corresponding to the coupling constraints, partial Lagrangian of the decentralized problem involving the coupling variable \me{\chi_{l,b,\pr{k},n}} is solved. The Lagrangian of the problem outlined in \eqref{primal-problem} is given by
\begin{IEEEeqnarray}{rCl}\label{lagr-primal}
\underset{\substack{\mvec{m}{l,k,n},p_{l,k,n},\\q_{l,k,n},\beta_{l,k,n},\mbfa{\mu}^{(b)}}}{\text{minimize}} &\quad& \|\tilde{\mbf{v}}_{b}\|_q + \sum_{k \in \mc{U}_{b}} \sum_{l = 1}^L \mu^{(b)}_{l,k,n} \left ( \beta_{l,k,n} - N_0 - \rho_{l,k,n} - \sum_{\pr{b} \in \tilde{\mc{B}}_{b}} \chi_{l,\pr{b},k,n} \right ) \nonumber \\
&\quad& + \sum_{\pr{k} \notin \mc{U}_b} \sum_{\pr{l} = 1}^L \mu^{(b)}_{\pr{l},\pr{k},n} \left ( \chi_{\pr{l},b,\pr{k},n} - \sum_{k \in \mc{U}_{b}} \text{tr} \left ( \mvec{w}{\pr{l},\pr{k},n}^H \mvec{H}{b,\pr{k},n} \mvec{M}{k,n} \mvec{M}{k,n}^H \mvec{H}{b,\pr{k},n}^H \mvec{w}{\pr{l},\pr{k},n} \, \right ) \right ) \IEEEyessubnumber \\
\text{subject to}&\quad& \eqref{eqn-4.3}, \eqref{eqn-8}, \text{and} \, \eqref{eqn-sg-b} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\mu^{(b)}_{l,k,n}} represent the dual variable for the constraint \eqref{eqn-sg-d} and \me{\mu^{(b)}_{\pr{l},\pr{k},n}} denote the dual variable for the constraint \eqref{eq-primal-constr} respectively. In order to solve the master problem, the dual variables of the \acp{BS}, which are linked by the interference constraint, need to be exchanged between the \acp{BS} \me{b} and \me{\pr{b}} only. For example, in order to find the interference threshold \me{\chi_{l,\pr{b},k,n}} for the \me{\ith{(i+1)}} iteration, the dual variables and the interference threshold levels of the \me{\ith{(i)}} iteration are exchanged to update \me{\chi_{l,\pr{b},k,n}}. The subgradient update for \me{\chi_{l,\pr{b},k,n}} is given by
\begin{equation}
\chi_{l,\pr{b},k,n}(i + 1) = \left [ \; \chi_{l,\pr{b},k,n}(i) - \sigma(i) \, s^{(\pr{b})}_{l,k,n}(i) \; \right ]^+, \; \forall \pr{b} \in \mc{B}, \forall k \notin \mc{U}_{b}
\label{eqn-primal-sg}
\end{equation}
where \me{\sigma} is the positive step-size which determines the convergence behaviour, and \me{s^{(\pr{b})}_{l,k,n}} is the global subgradient evaluated at the point \me{\chi_{l,\pr{b},k,n}}. Since the inter-cell interference term \me{\chi_{l,\pr{b},k,n}} couples exactly two \acp{BS}, \me{b} and \me{\pr{b}}, the global subgradient can be expressed as \me{s^{(\pr{b})}_{l,k,n}(i) = \mu^{(b)}_{l,k,n}(i) - \mu^{(\pr{b})}_{l,k,n}(i), \, \forall \pr{b} \in \tilde{\mc{B}}_b, \forall k \notin \mc{U}_{b}}.

\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\chi_{l,b,k,n} \forall b \in \mc{B}, \forall k \in \tilde{\mc{U}}_{b_k}, \forall l,n} \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{(b)}_{l,k,n}} using \eqref{lagr-primal} \;
        update \me{\chi_{l,b,k,n}} using \eqref{eqn-primal-sg} \;
        \me{j = j + 1} \;
    }
    update \me{\tilde{\mbf{u}}_{l,k,n}} with the current update of \me{{\mbf{u}}_{l,k,n}} using \eqref{eqn-8}\;
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    $i = i + 1$ \;
  }
 \caption{Algorithm of \acs{JSFRA} Primal scheme}
  \label{algo-2}
\end{algorithm}

### 2014-06-23 Report/primal_approach.tex
Git repository for Journal - 1

The centralized problem described in \eqref{eqn-decent-1} can be solved in a distributed approach using the \ac{PD} method. The decentralized approach decomposes the centralized problem as a two level optimization problem in which the multiple sub problems are coordinated using a master problem. The coordination of the multiple subproblems can be carried out by exchanging the information across the coordinating \acp{BS} in \me{\mc{B}} via backhaul. The distributed solution is achieved by fixing the interference level \me{\zeta_{l,k,n,b}, \forall k \in \mc{U}_{b_k}} from the \acp{BS} \me{b \in \bar{\mc{B}}_{b_k}} so as to decouple the variables \me{\zeta_{l,k,n,b}} \cite{pennanen2011decentralized,bertsekas1999nonlinear}. Now, the subproblems are governed by the master problem by updating the interference thresholds at each iteration using the subgradients.

As discussed in Section \ref{sec-4}, the constraint involving the coupling variables \eqref{eqn-9.1c} can be relaxed using the equivalent formulation in \eqref{eqn-decent-3}. Now, the subproblem for the \ac{BS} \me{b_k \in \mc{B}} can be obtained by grouping the terms relevant to the \ac{BS} \me{b_k} as
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-1}
\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \IEEEyessubnumber \label{eqn-primal-1a} \\
\text{subject to}&\quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_{b_k}} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \IEEEyessubnumber \label{eqn-primal-1c} \\
&& \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-primal-1d} \\
&& \zeta_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-primal-1e} \\
 & \quad & \text{and} \; \eqref{eqn-8} \IEEEyessubnumber,
\end{IEEEeqnarray}
where \me{\zeta_{\pr{l},\pr{k},n,{b_k}}} corresponds to the fixed maximum interference caused by the transmission from the \ac{BS} \me{b_k} to the \me{\ith{\pr{l}}} spatial stream of the \me{\ith{\pr{k}}} user. Let \me{\mbfa{\zeta}^{\set{b_k}}} be the vector representing the fixed interference levels relevant to the \ac{BS} \me{b_k} in a fully connected network (in practice it will be less), which is given by
\begin{IEEEeqnarray}{RCL} \label{eqn-primal-2}
\mbfa{\zeta}_{k,n,b} &=& \left [ \; \zeta_{1,k,n,b}, \dotsc, \zeta_{L,k,n,b} \; \right ] \IEEEyessubnumber \\
\mbfa{\zeta}^{\set{b_k}}_n &=& \left [ \; \mbfa{\zeta}_{\mc{U}_{b_k}(1),n,\bar{\mc{B}}_{b_k}(1)}, \dotsc, \mbfa{\zeta}_{\mc{U}_{b_k}(1),n,\bar{\mc{B}}_{b_k}(|\bar{\mc{B}}_{b_k}|)}, \right . \nonumber \\
&& \left . \dotsc, \mbfa{\zeta}_{\mc{U}_{b_k}(|\mc{U}_{b_k}|),n,\bar{\mc{B}}_{b_k}(|\bar{\mc{B}}_{b_k}|)}, \dotsc, \mbfa{\zeta}_{\bar{\mc{U}}_{b_k}(1),n,b_k}, \dotsc, \mbfa{\zeta}_{\bar{\mc{U}}_{b_k}(|\bar{\mc{U}}_{b_k}|),n,b_k} \; \right  ] \IEEEyessubnumber \\
\mbfa{\zeta}^{\set{b_k}} &=& \left [ \; \mbfa{\zeta}^{(b_k)}_1, \dotsc, \mbfa{\zeta}^{(b_k)}_N \; \right ], \IEEEyessubnumber
\end{IEEEeqnarray}
where the length of the vector \me{\mbfa{\zeta}^{\set{b_k}}} is
\begin{equation}
n_{b_k} = | \mbfa{\zeta}^{\set{b_k}} | = \left ( |\bar{\mc{B}}_{b_k}| |\mc{U}_{b_k}| + |\bar{\mc{U}}_{b_k}|\right ) L N
\label{primal-vec-len}
\end{equation}

The problem defined in \eqref{eqn-primal-1} is already decoupled across the \acp{BS} by fixing the inter-cell interference vector \eqref{eqn-primal-2} for all \acp{BS}. For a fixed interference threshold \me{\mbfa{\zeta}^{\set{b}}}, the precoders are designed using \eqref{eqn-primal-1}. The local subproblem \eqref{eqn-primal-1} solved at each \ac{BS} are coordinated by the master problem, which updates the interference thresholds \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}} for the next iteration. The master and the subproblems follows the classical \ac{BCDM} approach to achieve the optimal solution by alternating the variable set while keeping other set constant in an iterative manner. The master problem controlling multiple subproblems is given by
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-3}
\underset{\mbfa{\zeta}}{\text{minimize}} & \quad & \sum_{b \in \mc{B}} \alpha^{\star}_b (\mbfa{\zeta}^{\set{b}}) \IEEEyessubnumber \\
\text{subject to} & \quad & \mbfa{\zeta}^{\set{b}} \in \mathbb{R}_+^{n_b}, \forall b \in \mc{B}, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\alpha^{\star}_b (\mbfa{\zeta}^{\set{b}})} denotes the optimal solution for \eqref{eqn-primal-1} with the previous value of \me{\mbfa{\zeta}^{(i-1)}}, where \me{\mbfa{\zeta}} is the global interference vector formed by stacking the interference vector associated with each \ac{BS} as \me{\mbfa{\zeta} = \left [ \mbfa{\zeta}^{\set{\mc{B}(0)}}, \mbfa{\zeta}^{\set{\mc{B}(1)}}, \ldots, \mbfa{\zeta}^{\set{\mc{B}(|\mc{B}|)}}\right ]}.

The master problem to find the optimal \me{\mbfa{\zeta}^{\set{b_k}(i)}, \forall b_k \in \mc{B}} is given by the following subgradient method \cite{bertsekas1999nonlinear} as
\begin{equation} \label{primal-sg-update}
\zeta^{\set{b_k}(i)}_{l,k,n,b} = \left [\zeta_{l,k,n,b}^{\set{b_k}(i-1)} - \rho \, s_{l,k,n,b}^{\set{b_k}(i-1)} \right ]^+, \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_b,
\end{equation}
where \me{i} is the iteration index, \me{\rho} is the positive step size, and \me{s^{\set{b_k}(i-1)}_{l,k,n,b}} is the subgradient of the problem defined in \eqref{eqn-primal-3} evaluated at \me{\zeta^{(i-1)}_{l,k,n,b}}. To find the subgradient \me{s^{\set{b_k}(i-1)}_{l,k,n,b}}, the dual variables corresponding to the interference constraints are required, which can be obtained by forming the Lagrangian of the primal problem \eqref{eqn-primal-2} as
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-4}
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \mu^{\set{b_k}}_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \nonumber + \left ( \beta_{l,k,n} - \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \right . \nonumber \\
&& \left . \quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{(i-1)}_{l,k,n,b} \; + \; N_0 \right ) \, \mu^{\set{b_k}}_{l,k,n}  \nonumber \\
&& + \quad \left ( \zeta^{(i-1)}_{\pr{l},\pr{k},n,{b_k}} - \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2 \right ) \, \mu^{\set{b_k}}_{\pr{l},\pr{k},n} , \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \\
\text{subject to} &\quad& \eqref{eqn-primal-1c} \; \text{and} \; \eqref{eqn-8} \IEEEyessubnumber.
\end{IEEEeqnarray}
Now the primal and the dual variables \me{\mu^{\set{b_k}}_{l,k,n}} and \me{\mu^{\set{b_k}}_{\pr{l},\pr{k},n}} corresponding to the constraints \eqref{eqn-primal-1d} and \eqref{eqn-primal-1e} are obtained by solving \eqref{eqn-primal-4}.

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}.

Once the interference vector converges \me{\mbfa{\zeta}^{\set{i}} \approx \mbfa{\zeta}^{\set{i-1}}} or iterated for certain times, say, \me{J_{\max}}, the \ac{SCA} update is performed by exchanging the transmit and the receive precoders to update the respective variables \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}}. The \ac{SCA} update can also be performed until convergence or for certain threshold \me{I_{\max}}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}. In this case, we perform \ac{SCA} and the receiver update at the same instant compared with the update of the recieve beamformers after the \ac{SCA} convergence. The approach followed in the algorithm provides the same solution as that of the separate update, since the receive beamformers are optimal for the given transmit precoders.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-4} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the transmit and the receive precoders \me{\mbf{M}_{k,n}} and \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{\ac{PD} based decentralized \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}

### 2014-06-23 Report/problem_formulation.tex
Git repository for Journal - 1

In order to minimize the number of queued packets at the \acp{BS}, the precoders \me{\mbf{M}_{k,n}} are designed to distribute the resources in an efficient manner to the users by utilizing both spatial and frequency dimension. The problem defined in \eqref{q_gen_sum} raises a question, namely, the linearity of the weights used in the objective function. It can also be a quadratic function, providing more emphasis on the users with large number queued packets as compared to the users with the small queue sizes or some other function of \me{\mbf{Q}}. In order to answer this question, we discuss the \ac{JSFRA} problem formulation, which restricts the solution only to the power functions. For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the packets available at the transmitter. As a result, the number of backlogged packets remaining in the system is given by
\begin{equation}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0 \fall k \in \mathcal{U}.
\label{eqn-4.2}
\end{equation}

The precoder design problem can be given minimizing the absolute value of the deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as
\me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}. The exponent \me{q} plays a vital role in the final allocation, which will be discussed later. Now, the problem of weighted queued packet minimization formulated as a $q$-norm minimization, is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-3}
\underset{\substack{\mvec{m}{l,k,n},\\\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
\end{IEEEeqnarray}
where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, and \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission. It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users. The expression for \me{t_{l,k,n}} is due to the assumption of Gaussian signaling, so that the maximum achievable rate is \me{\log_2(1 + \gamma_{l,k,n})} for a given \ac{SINR} \me{\gamma_{l,k,n}}. In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels. The proposed solution presented in this section also applies to the sub-channel power constraint by replacing \eqref{eqn-4.3} by corresponding formulations. Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{q}-norm in the objective of \eqref{eqn-3}. As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}. Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}. Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained. We comment on the choice of  the norm \me{q} on the objective as below \cite{berry2004cross,qps_cioffi}.
\begin{itemize}
\item With \me{q = 1}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions. As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{Q-WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
\item With \me{q = 2}, the objective prioritizes users with higher queued packets before considering the users with a smaller number of backlogged packets. This is ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
\item With \(q = \infty \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
\end{itemize}

### 2014-06-23 Report/queue_minimizing_intro.tex
Git repository for Journal - 1

In this section, we discuss the precoder design solutions for the problem stated in Section \ref{sec-3.2}. To begin with, we discuss the existing solution and its extension to solve the current problem of resource allocation over multiple sub-channels. Then, we provide two different approaches to solve the \ac{JSFRA} precoder design problem to minimize the total number of backlogged packets. At the end of the section, we discuss a low complex solution for the \ac{JSFRA} problem by limiting the precoder design over each sub-channel at a given instant.

In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is highly difficult due to the non-convex nature of the problem. In addition to that, the objective of minimizing the number of the queued packets over the spatial and the sub-channel dimensions adds further complexity to the existing problem. Since the scheduling of users in each sub-channel can be made by allocating zero transmit power over certain sub-channels, the solutions provided in the paper performs both precoder design and the scheduling of users in a joint manner.

### 2014-06-23 Report/simulation_distributed.tex
Git repository for Journal - 1

In this section, we discuss the simulation performances of the algorithms briefed in Section \ref{sec-3} and \ref{sec-4}. The comparison studies are made using the queue deviation and sum rate convergence of the algorithms discussed so far using different system models. The distributed algorithms for the \ac{JSFRA} scheme and the equivalent \ac{MSE} representation are compared using the excess backlogged packets present after the current iteration instant.

Fig. \ref{fig-d-1} demonstrates the performance of the distributed algorithms in an \ac{OFDM} framework modeled with \me{N = 5} sub-channels with \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas. Each \ac{BS} serves \me{|\mc{U}_b| = 4, \forall b \in \{1,2\}} users in a coordinated manner so as to minimize the interference caused to the neighboring \ac{BS} users. Fig. \ref{fig-d-1.1} shows the total number of backlogged packets at the end of each iteration and Fig. \ref{fig-d-1.2} plots the total rate achieved by various algorithms at each iteration. As discussed earlier in the distributed section, the rate of convergence of any distributed algorithm depends on the proper choice of a step size. In particular, the primal decomposition method is more susceptible to the choice of the step size compared to the \ac{ADMM} approach. Since the primal decomposition iterates at each instant by fixing the interference thresholds, it may lead to infeasible solutions if the initial interference values are not feasible and also with the updated interference value as in \eqref{primal-sg-update}.

Fig. \ref{fig-d-1} also compares the performance of the iterative algorithm for \ac{JSFRA} scheme via \ac{MSE} reformulation using the \ac{KKT} conditions discussed in Section \ref{sec-4.3}. The performance is inferior compared to the other algorithms due to the violation in the assumptions made in the algorithm design \textit{i.e}, \me{Q_k \gg t_k}. Since in this case, we are comparing the \me{q = 1} case, the queue condition \me{Q_k \gg t_k} needs to be satisfied in order to remove the absolute operator from the expression in \eqref{eqn-9.1a} to form \eqref{kkt-mse-1.1}. The total number of backlogged packets after the each iteration reduces monotonically in all cases and converges to the points closer to the centralized solution \me{\chi = 33} bits. As seen in Fig. \ref{fig-d-1}, the \ac{ADMM} approach provides better convergence compared to the primal approach in the initial phase due to the quadratic penalty term included in the objective, which gets pronounced initially due to the large deviation between the assumed and the actual interference across the coordinating \acp{BS}.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{NewFigures/distribute_queue-1}
\caption{Queue deviation}
\label{fig-d-1.1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{NewFigures/distribute_sum_rate-1}
\caption{Sum rate performance}
\label{fig-d-1.2}
\end{subfigure}
\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,12,1 \rbrace} model}
\label{fig-d-1}
\end{figure*}

In Fig. \ref{fig-d-2}, the total backlogged packets and the sum throughput offered to minimize the number of queued packets for \me{K = 12} users across \me{N = 5} sub-channels are plotted for the analysis. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users mounted with \me{N_R = 2} antennas respectively. The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{\mathbb{U}(0,-6)} dB independently. The sum rate and queue minimizing behavior follows similar pattern as in Fig. \ref{fig-d-1} for \me{N_B = 2} \acp{BS} scenario.

Fig. \ref{fig-d-2} demonstrates the convergence behavior of the different distributed algorithms discussed so far. It can be seen from Fig. \ref{fig-d-2}, that the distributed algorithms depend on the step size used in the subgradient update procedure. The primal decomposition algorithm, which distributes the precoder design by fixing the interference thresholds at each iteration, converges to the optimal resource allocations gradually as compared to the \ac{ADMM} based dual approach. The \ac{ADMM} scheme depends on the step size for the convergence, where the larger step size makes the algorithm to reach the optimal point quickly but takes more iterations to converge. The choice of \me{I_{\max}}, which denotes the maximum \ac{SCA} iterations, and the \me{J_{\max}}, which denotes the subgradient convergence limit, are fixed at \me{100} and \me{8} respectively. The information exchange is made at each instant and the performances are evaluated as if the actual transmission is happened with the precoders \me{\mvec{m}{l,k,n}^{(i)}} designed at the \me{\ith{i}} instant in a distributed manner. In this paper, we assume that the actual transmission will happen at the end of the precoder convergence or when the maximum number of iterations reached.

The performance of the joint \ac{Q-WSRM} scheme discussed in the Section \ref{sec-3.1} performs slightly worse than (\me{\approx \, 2} bits) the \ac{JSFRA} scheme in reducing the number of queued packets, even though the performance were similar in Table \ref{tbl-1}. As stated earlier, the joint \ac{Q-WSRM} scheme and the \ac{JSFRA} scheme with the exponent \me{q = 1} performs the same when the number of queued packets are identical for all the users. In this case, the joint \ac{Q-WSRM} becomes the sum rate maximization problem which is equivalent to the greedy \me{q=1} \ac{JSFRA} scheme. In the current scenario, since the number of queued packets are different for the users, the performance of the \ac{JSFRA} scheme is better due to its greedy resource allocation. It can be seen from Fig. \ref{fig-d-2}, that the \ac{KKT} based approach provides inferior result in the queue minimization perspective as compared with the sum rate plot. The performance degradation is due to the unconstrained rate increase for the users beyond their actual number of queued packets available to transmit. Since the objective uses the norm-\me{1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user. The number of queued packets are initialized in a way to analyze the effect of the unconstrained behavior in the \ac{KKT} scheme.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_queue_plot_1}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_sum_rate_plot_1}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,3,12,2 \rbrace} model}
\label{fig-d-2}
\end{figure*}

The performance of the \ac{MSE}-\ac{KKT} scheme is shown in comparison with the other schemes discussed so far in Fig. \ref{fig-d-3}. It can be seen that the \ac{KKT} based approach performs similar to the optimization problem given in \eqref{eqn-9}, which is solved using the solver \cite{grant2008cvx}. In the two norm case, the objective is differentiable and hence can be differentiable for any number of queued packets as compared to the one norm case requiring larger queue sizes in order to drop the absolute function occurring in the norm function. The performance of the closed form solution using the \ac{KKT} solution achieves similar performance without allocating rates beyond the available queued packets. In order to bring out the performance difference, one norm objective plot is also provided in Fig. \ref{fig-d-3} providing better reduction in the number of queued packets in the current transmission slot.
Fig. \ref{fig-d-3}
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{queues_6_3_12}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{rate_6_3_12}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
\label{fig-d-3}
\end{figure*}

### 2014-06-23 Report/simulation_results.tex
Git repository for Journal - 1

In this section, we discuss the performance of the above mentioned algorithms in different scenarios on minimizing the number of queued packets at the transmitter. To begin with, we consider a single cell \ac{SISO} system operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter is kept as \me{Q_k = 6} bits. With these assumptions, the resources allocated for the users on each sub-channel by various algorithms are listed in Table \ref{tbl-1}.

Table \ref{tbl-1} shows the channel seen by the users over each sub-channel followed by the rates allocated over each sub-channel by three different algorithms, joint \ac{Q-WSRM} allocation without the maximum rate constraints \eqref{eqn-3.1.4}, \ac{JSFRA} scheme and the band-wise \ac{Q-WSRM} scheme. Since the total allowed transmission constraint is present only on the \ac{JSFRA} scheme, the total number of packets remained after the current transmission slot is minimum for the \ac{JSFRA} scheme with \me{1.14} bits, where \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}. The precoder design for the optimal allocation in band-wise \ac{Q-WSRM} depends on the order of selecting the sub-channels, which leads to an exhaustive search. In this scenario, the formulation in \eqref{q_gen_sum} and \eqref{gen_sum} performs the same as compared to the \ac{JSFRA} scheme, \textit{i.e}, with the maximum rate constraints, the joint \ac{Q-WSRM} scheme performs the same as the \ac{JSFRA} scheme.

\begin{table*}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|*{14}{c|}}
\hline
\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Joint Q-WSRM w/o} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{WSRM band} \\
\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Queue constraints \eqref{eqn-3.1.4}} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
\cline{3-14}
 && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
\hline
\me{1} & \me{6} & \me{2.26} &  \me{0.69}  &  \me{0.73} & \me{0} &  \me{0}  &  \me{0} & \me{5.56} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{2.68} \\
\me{2} & \me{6} & \me{0.53} &  \me{1.93}  &  \me{1.40} & \me{0} &  \me{5.29}  &  \me{0} & \me{0} &  \me{5.33}  &  \me{0} & \me{0} &  \me{5.26}  &  \me{0} \\
\me{3} & \me{6} & \me{2.45} &  \me{1.31}  &  \me{2.42} & \me{5.84} &  \me{0}  &  \me{5.95} & \me{0} &  \me{0}  &  \me{5.95} & \me{5.93} &  \me{0}  &  \me{0} \\
\hline
\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{6.70} bits} & \multicolumn{3}{c|}{\me{1.14} bits} & \multicolumn{3}{c|}{\me{4.11} bits} \\
\hline
\end{tabular}
\caption{Sub channel wise allocation for a scheduling instant}
\label{tbl-1}
\end{table*}

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{K = 8} users with \me{N_R} antennas each. The users are assumed to be at the cell-edge with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-3} dB and each \ac{BS} are associated with \me{|\mc{U}_b|} users respectively.

\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=1.0\textwidth]{NewFigures/centralized-1a}
\caption{\me{4 \times 1} system}
\label{fig-1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=1.0\textwidth]{NewFigures/centralized-2a}
\caption{\me{4 \times 2} system}
\label{fig-2}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K \rbrace = \lbrace 3,2,8 \rbrace} model}
\end{figure*}

Fig. \ref{fig-1} shows the performance of the above discussed schemes for a single receive antenna system. The figure compares the total number of \ac{SCA} iterations required by the \ac{JSFRA}, \ac{JSFRA} with sum power constraint, \ac{SRA} and \ac{Q-WSRM} schemes to achieve the optimal resource allocation to minimize the number of backlogged packets during the given scheduling instant. The convergence of the proposed \ac{JSFRA} is much quicker compared to the band-wise allocation schemes like the \ac{Q-WSRM} and the \ac{SRA} schemes. The waterfall like behavior for the band-wise allocation schemes suggests the rapid convergence when there is a band switch over, \textit{i.e}, when the queues are updated from the earlier sub-channels to find the precoders for the current sub-channel. The convergence at each sub-channel is iterated for the accuracy of \me{\approx 10^{-4}} or for a predetermined count \me{I_{\max}}, which creates the flat region between each waterfall behavior. The backlogged bits and the iteration count by various schemes at the convergence point are marked in the figures using data tips.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|c|*{8}{c}|c|}
\hline
\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
\hline
\me{1} & 12.0 &  6.15 &  5.32 & 12.0 &  6.95 & 11.1 & 11.9 & 10.8 & 19.71 \\
\me{2} & 11.9 & 7.3 & 5.9 & 10.1 & 9.19 & 10.1 & 10.8 & 10.3 & 20.48 \\
\me{\infty} & 9.15 & 9.15 & 9.15 & 9.15 & 9.16 & 9.15 & 9.15 & 9.15 & 22.75 \\
\hline
\end{tabular}
\caption{Queue information for \me{N=5} sub-channels}
\label{tbl-3}
\end{table}

Fig. \ref{fig-2} compares the convergence behavior of the precoder designs, which allocates the space-frequency resources to the users to minimize the number of backlogged packets. Different values for the exponent \me{q} are compared in Table \ref{tbl-3} for the system configuration \me{\{N_B,K,N_T,N_R\}= \{2,8,4,1\}}. The number of backlogged packets at each user before the current scheduling is fixed to be \me{12} bits. It is evident that the exponent \me{q=1} shows the greedy resource allocation in comparison with the fair scheduling achieved using \me{q=\infty}. The \me{q=\infty} norm does the fair scheduling even the path loss experienced by the users are different. It tries to minimize the variance across the backlogged packets of each user present in the system.

### 2014-06-23 Report/sub_channel_wsrm.tex
Git repository for Journal - 1

In this method, titled as \acf{QM} \ac{SRA} scheme, we limit the resource allocation over the spatial dimension only by performing \ac{JSFRA} design over each sub-channel in an instant. This scheme can be considered in a system employing the \ac{FFR} like power restrictions on certain sub-channels. It can also be used to reduce the problem dimension by limiting the allocation over the spatial dimension only. It is well suited for the persistent scheduling like schemes, where certain sub-channels are dedicated to only certain users. Imposing the user restrictions in the \ac{JSFRA} scheme adds a non-convex constraint which will be difficult to solve.

For a scheduling slot, the precoders are designed over each sub-channel in a sequential manner with the corresponding user queues are updated with the total transmission allocations made in the previous sub-channels on the same slot.

The queue update is common for \ac{SRA} and band-wise \ac{Q-WSRM} schemes, and the queue length controls the design of precoders for the allocation of spatial resources for each sub-channel. The queues are updated before designing the precoders for each sub-channel \me{n} as
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\label{eqn-weight}
\end{equation}
where \me{Q_k} is given by \eqref{eqn-2a} for the user \me{k}. The weight for the sub-channel \me{n} is given by \eqref{eqn-weight}, which uses the allotted transmission bits \me{t_{l,k,j}} evaluated from the earlier sub-channels \me{j < n}. The \ac{QM} \ac{SRA} scheme depends on the permutation pattern of the sub-channel selection order for the precoder design and the performance.

### 2014-06-23 Report/system_model.tex
Git repository for Journal - 1

We consider a downlink \ac{MIMO} \ac{BC} scenario in an \ac{OFDM} framework with \me{N} sub-channels and \me{N_B} \acp{BS} each equipped with \me{N_T} transmit antennas, serving \me{K} users each with \me{N_R} receive antennas. The set of users associated with \ac{BS} \me{b} is denoted by \me{\mathcal{U}_b} and the set \me{\mathcal{U}} represents all users in the system, i.e., \me{\mathcal{U} =\underset{b\in \mathcal{B}}{\cup }\mathcal{U}_b}, where the set \me{\mathcal{B}} holds the coordinating \acp{BS}. The serving \ac{BS} of user \me{k} is denoted by \me{b_k\in \mathcal{B}}. We denote by \me{\mathcal{C} = \set{1,2,\dotsc,N}} the set of all sub-channel indices available in the system.

In this paper we adopt linear beamforming technique at \acp{BS}. Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with the beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} for transmission.   In order to detect  multiple spatial streams at the receiver, a receive beamforming vector \me{\mvec{w}{l,k,n}} is employed at each user. Consequently, the received signal of the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n^\mathrm{th}} at user $k$ is given by
\begin{equation}\label{eqn-1}
y_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
\end{equation}
where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} with rank \me{L = \min(N_R,N_T)} is the channel between the \ac{BS} \me{b} and  user \me{k} on the sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream. Assuming  \me{||\mvec{w}{l,k,n}||_{2}^{2} = 1} and independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
\end{equation}
With the infinite buffer model assumption, let \me{Q_k} be the number of backlogged packets which are destined for the user \me{k} at a given scheduling instant. The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets or bits arriving for the user \me{k} at the \me{{i}^\mathrm{th}} instant. The total number of queued packets at the \me{{i}^\mathrm{th}} instant for the user \me{k} depend on the fresh arrivals at the \me{{i}^\mathrm{th}} instant and the total number of backlogged packets \me{Q_k(i-1)} as given by
\begin{equation}
Q_k(i) = \Big [ Q_k(i-1) - t_k(i-1) \Big ]^+ + \lambda_k(i),
\label{eqn-2a}
\end{equation}
where \me{t_k} denote the transmissions in bits and \me{[x]^+ = \max{ \lbrace x,0  \rbrace}}. The total number of transmitted bits for the user \me{k} is given by \me{t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i)},
where \me{t_{l,k,n}} is the total number of bits that can be transmitted over \me{l^\mathrm{th}} spatial stream and on \me{n^\mathrm{th}} sub-channel at the \me{i^\mathrm{th}} instant. Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-06-23 Report/wsrm_formulation.tex
Git repository for Journal - 1

We present an iterative algorithm to solve \eqref{eqn-3} locally based on the idea of alternating optimization and successive convex approximation.  For this purpose, from \eqref{eq:SINR}, we can explicitly reformulate \eqref{eqn-3} as
\begin{IEEEeqnarray}{RCL}\label{eqn-6}
\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
\text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}),\IEEEyessubnumber \label{eqn-6.2} \\
  & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-6.3} \\
  & \quad &\eqref{eqn-4.3} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\beta_{l,k,n}} denotes the total interference seen by the \me{l^\mathrm{th}} stream of the user \me{k} on the \me{n^\mathrm{th}} sub-channel and let \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} be the vector which needs to be identified for the optimal allocation. In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}. However, this step is without loss of optimality leads to the same solution, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}. Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the interference seen by the user \me{k \in \mathcal{U}_b}. The problem in \eqref{eqn-6} is known to be NP-hard even for the single antenna case \cite{wmmse_shi,kaleva2013primal}. The reformulation in \eqref{eqn-6} allows a tractable solution as presented below. First, we note that the constraints \eqref{eqn-4.3} are convex with involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. Towards this end, we resort to the traditional coordinate descent technique by fixing the transmit beamformers, and find the optimal linear receivers. The optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t the \me{\mbf{w}_{l,k,n}}, and the closed form solution is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-10}
\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}, \IEEEyessubnumber \\
\mvec{R}{l,k,n} &=& \displaystyle \sum_{(j,i) \neq (l,k)} \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + \mathbf{I}_{N_R}, \IEEEyessubnumber
\end{IEEEeqnarray}
which is the \ac{MMSE} receive beamformers \cite{christensen2008weighted,wmmse_shi,kaleva2013primal}.

The problem now is to find optimal transmit beamformers for a given set of linear receivers which is a challenging task. We note that for fixed $\mvec{w}{l,k,n}$, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}. To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by the series of convex constraints. Note that the function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}} since it is in fact the ratio between a quadratic form (of \me{\mvec{m}{l,k,n}}) over an affine function (of \me{\beta_{l,k,n}}) \cite{boyd2004convex}. According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure. Since \me{f(\tilde{\mbf{u}}_{l,k,n})} is convex, a concave approximation of \eqref{eqn-6.2} can be easily found by considering the first order approximation of \me{f(\tilde{\mbf{u}}_{l,k,n})} around the current operation point. For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
\begin{subeqnarray} \label{eqn-wsrm-expr}
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}},
\end{subeqnarray}
and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}. Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables. In CVX \cite{grant2008cvx}, we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `expression' qualifier. Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively. Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint
\begin{equation}
\label{eqn-8}
2 \dfrac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \dfrac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \dfrac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \dfrac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
\end{equation}
In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
\begin{IEEEeqnarray}{rCl}\label{eqn-9}
\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
& \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}.
\end{IEEEeqnarray}

The proposed algorithm is referred as \ac{QM} \ac{JSFRA} scheme with a sum power constraint which is outlined in Algorithm \ref{algo-1}. The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached. Instead of initializing \me{\tilde{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{\tilde{\mbf{u}}_{l,k,n}} in an efficient manner as briefed in Algorithm \ref{algo-1}. In Algorithm \ref{algo-1}, the \ac{SCA} iterations are carried until convergence or for maximum of \me{I_{\max}} iterations for the optimal \me{\mbf{w}_{l,k,n}} receive beamformers and the outer iterations are for the convergence of the number of queued bits, which is limited by the maximum of \me{J_{\max}} iterations.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}}\;
 \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
 \Repeat{\ac{SCA} convergence or \me{i \geq I_{\max}}}{
 solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9} \;
 update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,n}} obtained from the previous step \;
 $i = i + 1$ \;
 }
 update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
 $j = j + 1$ \;
 }
 \caption{Algorithm of \acs{JSFRA} scheme}
 \label{algo-1}
\end{algorithm}

In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which basically means that we do not solve the problem exactly. According to the traditional \ac{BCDM}, we need to solve a sub problem when fixing a set of variables to the global optimum to ensure the convergence to a stationary point. If we just approximate the objective, then the convergence is guaranteed \cite{razaviyayn2013unified}. In our case, we solve the sub problem inexactly, so the convergence proof of \ac{BCDM} does not apply to our problem. Recall that \cite{wmmse_shi} only approximates the non-convex objective in each iteration. In this problem, we used alternating optimization with \ac{SCA} method, which provides monotonic convergence since the objective is improved at each step \textit{i.e} \me{f^{(i)} \geq f^{(i+1)}}, assuming \me{f^{(i)}} is the objective function at the \me{i^\mathrm{th}} \ac{SCA} iteration. In a single receive antenna case, the proposed solution is guaranteed to converge to a \ac{KKT} point as discussed in \cite{tran2012fast}.

### 2014-06-26 Report/joint_wsrm_formulation.tex
ver_0.0.1

@@
 The backpreassure algorithm is the outcome of minimizing the Lyapunov drift conditioned over the current queue states \me{\mbf{Q}(i - 1)}, where \me{\mbf{Q}} is the vector formed by stacking the number of queued packets of each user in the system.
-Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift is given by \cite{georgiadis2006resource,neely2010stochastic}
+Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift conditioned over different channel realizations is given by \cite{georgiadis2006resource,neely2010stochastic}
+\begin{equation} \label{eqn-3.1.0}
+\Delta(i) = \frac{1}{2} \, \sum_{k \in \mc{U}} \, \mathrm{E}_H \Big{[}  \left ( Q_k(i)^2 - Q_k(i-1)^2 \right ) \vert \, \mbf{Q}(i - 1) \Big{]}.
+\end{equation}
+Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression can be upper bounded by
 \begin{equation}
-L(i) = \frac{1}{2} \, \| \mbf{Q}(i) \|^2_2 = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k(i)^2.
+\Delta(i)\leq \mathrm{E}_H \Big{[} \mbf{Q}(i-1) \left \lbrace \mbfa{\lambda}(i) - \mbf{t}(i) \right \rbrace | \mbf{Q}(i-1) \Big{]} + \mathrm{E}_H \left [ \mbfa{\lambda}^2(i-1) \right ] + \mathrm{E}_H \left [ \mbf{t}^2(i-1) \right ],
 \end{equation}
-The conditional Lyapunov drift is given by taking expectation over all channel realizations as
-\begin{equation}
-\Delta(i) = \mathrm{E}_H \left [ L(i) - L(i - 1) | \mbf{Q}(i - 1) \right ],
-\label{eqn-3.1.0}
-\end{equation}
-since the transmission depends on the channel condition. Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression can be upper bounded by
-\begin{equation}
-\Delta(i)\leq \sum_{k \in \mc{U}} \, \mathrm{E}_H \left [ \mbf{Q}(i-1) \left ( \mbf{\lambda}(i) - \mbf{t}(i) \right ) | \mbf{Q}(i-1) \right ] + \mathrm{E}_H \left [ \mbf{\lambda}^2(i-1) \right ] + \mathrm{E} \left [ \mbf{t}^2(i-1) \right ],
-\end{equation}
-where \me{\mbf{\lambda}} and \me{\mbf{t}} are the stacked arrivals and transmissions of all users.
+where \me{\mbfa{\lambda}} and \me{\mbf{t}} are the stacked arrivals and transmissions of all users.
 Since the expectation is conditioned over \me{\mbf{Q}(i-1)} and the second order statistics of the arrivals and the transmissions are bounded \cite{neely2010stochastic}, the drift minimization solution is given as

### 2014-06-26 Report/problem_formulation.tex
ver_0.0.1

@@
 In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels.
-The proposed solution presented in this section also applies to the sub-channel power constraint by replacing \eqref{eqn-4.3} by corresponding formulations.
-Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{q}-norm in the objective of \eqref{eqn-3}.
-As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
-Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}.
-Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained.
-We comment on the choice of  the norm \me{q} on the objective as below \cite{berry2004cross,qps_cioffi}.
-\begin{itemize}
-\item With \me{q = 1}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
-As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{Q-WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
-\item With \me{q = 2}, the objective prioritizes users with higher queued packets before considering the users with a smaller number of backlogged packets.
-This is ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
-\item With \(q = \infty \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
-\end{itemize}

### 2014-06-26 Report/wsrm_formulation.tex
ver_0.0.1

@@
+The proposed solution presented in this section also applies to the sub-channel power constraint by replacing \eqref{eqn-4.3} by corresponding formulations.
+Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{q}-norm in the objective of \eqref{eqn-3}.
+As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
+Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}.
+Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained.
+We comment on the choice of  the norm \me{q} on the objective as below \cite{berry2004cross,qps_cioffi}.
+\begin{itemize}
+\item With \me{q = 1}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
+As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{Q-WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
+\item With \me{q = 2}, the objective prioritizes users with higher queued packets before considering the users with a smaller number of backlogged packets.
+This is ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
+\item With \(q = \infty \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
+\end{itemize}
+
 We present an iterative algorithm to solve \eqref{eqn-3} locally based on the idea of alternating optimization and successive convex approximation.

### 2014-07-01 Report/joint_wsrm_formulation.tex
Updated ver_1

@@
 The backpreassure algorithm is the outcome of minimizing the Lyapunov drift conditioned over the current queue states \me{\mbf{Q}(i - 1)}, where \me{\mbf{Q}} is the vector formed by stacking the number of queued packets of each user in the system.
-Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift conditioned over different channel realizations is given by \cite{georgiadis2006resource,neely2010stochastic}
+Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift conditioned over different channel realizations is given by
 \begin{equation} \label{eqn-3.1.0}
-\Delta(i) = \frac{1}{2} \, \sum_{k \in \mc{U}} \, \mathrm{E}_H \Big{[}  \left ( Q_k(i)^2 - Q_k(i-1)^2 \right ) \vert \, \mbf{Q}(i - 1) \Big{]}.
+\Delta(i) = \frac{1}{2} \, \sum_{k \in \mc{U}} \, \mathrm{E} \Big{[}  \left ( Q_k(i)^2 - Q_k(i-1)^2 \right ) \vert \, \mbf{Q}(i - 1) \Big{]},
 \end{equation}
-Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression can be upper bounded by
+where the expectation is taken over all possible control decisions made in accordance to the channel under consideration to minimize the total backlogged packets at a given instant.
+Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression is given by
 \begin{equation}
-\Delta(i)\leq \mathrm{E}_H \Big{[} \mbf{Q}(i-1) \left \lbrace \mbfa{\lambda}(i) - \mbf{t}(i) \right \rbrace | \mbf{Q}(i-1) \Big{]} + \mathrm{E}_H \left [ \mbfa{\lambda}^2(i-1) \right ] + \mathrm{E}_H \left [ \mbf{t}^2(i-1) \right ],
+\Delta(i) \leq \mathrm{E} \Big{[} \mbf{Q}(i-1) \left \lbrace \mbfa{\lambda}(i) - \mbf{t}(i) \right \rbrace | \mbf{Q}(i-1) \Big{]} + \frac{1}{2} \,\mathrm{E} \left [ \mbfa{\lambda}^2(i) | \mbf{Q}(i-1) \right ] + \frac{1}{2} \,\mathrm{E} \left [ \mbf{t}^2(i) | \mbf{Q}(i-1) \right ],
+\label{drift-exp}
 \end{equation}
-where \me{\mbfa{\lambda}} and \me{\mbf{t}} are the stacked arrivals and transmissions of all users.
-Since the expectation is conditioned over \me{\mbf{Q}(i-1)} and the second order statistics of the arrivals and the transmissions are bounded \cite{neely2010stochastic}, the drift minimization solution is given as
+where \me{\mbfa{\lambda}} and \me{\mbf{t}} are the vectors formed by stacking the arrival and transmission of all users in the system and the inequality is due to the upper bound\footnote{\me{\left ( \max{\Big [ \mbf{Q}(i-1) - \mbf{t}(i),0 \Big ] } + \mbfa{\lambda}(i) \right )^2 \leq \mbf{Q}^2(i-1) + \mbf{t}^2(i) + \mbfa{\lambda}^2(i) + 2 \, \mbf{Q}(i-1) \left ( \mbfa{\lambda}(i) - \mbf{t}(i) \right ) }}.
+
+The first term in \eqref{drift-exp} can be neglected from the optimization, since the arrivals are independent of the current queue state following \me{\mathrm{E} [ \mbf{Q}(i-1) \mbfa{\lambda}(i) | \mbf{Q}(i-1)] = \mbf{Q}(i-1)\mathrm{E} [\mbfa{\lambda}(i)] = \mbf{Q}(i-1)\mbf{A}(i)}.
+In the backpreassure algorithm, discussed in \cite{georgiadis2006resource,neely2010stochastic}, the second order terms are bounded by a constant \me{B}, \textit{i.e}, \me{\mathrm{E} \left [ \mbfa{\lambda}^2(i) | \mbf{Q}(i-1) \right ] + \mathrm{E} \left [ \mbf{t}^2(i) | \mbf{Q}(i-1) \right ] \leq B}.
+With this approximation, the resulting problem can be represented as
 \begin{equation}
@@
 \end{equation}
-
+In \eqref{backpreassure}, the expectation operator is dropped since it is maximized by maximizing the function inside it.
 Now from \eqref{backpreassure}, the optimization variables \me{\mbf{t}(i)}, which is the vectorized transmission rates, are to be identified for each user for the current slot \me{i}.
@@
 
-The problem defined in \eqref{gen_sum} provides an efficient queue minimizing approach as compared to \eqref{q_gen_sum}, since the resource allocation is driven by the channel conditions as compared to the number of queued packets in the problem defined in \eqref{q_gen_sum}.
-In both formulations, the resources allocated to the users are limited by the backlogged packets \eqref{eqn-3.1.4}, thereby handling the problem of over allocation.
-The resource allocation constraint in \eqref{eqn-3.1.4} renders the problem difficult to be solved by the iterative algorithm to design the precoders, which will be discussed later.
+The problem defined in \eqref{gen_sum} provides an efficient queue minimizing approach as compared to \eqref{q_gen_sum}, since the resource allocation is driven by the channel conditions as compared to the number of queued packets as in \eqref{q_gen_sum}.
+It is to be noted that in both formulations, the resources allocated to the users are limited by the backlogged packets \eqref{eqn-3.1.4}, thereby handling the problem of over allocation explicitly with an additional rate constraint.

### 2014-07-01 Report/mse_formulation.tex
Updated ver_1

@@
 The proposed formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} expression for decoding the transmitted symbols using \ac{MMSE} receivers and \me{C} being the capacity of the system.
-Using the \ac{MSE} relation, \eqref{eqn-6} is written as
+Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.
+Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
 \begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
-\text{minimize} &\quad& \|  \tilde{\mbf{v}}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
+\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
 \text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
@@
 \end{IEEEeqnarray}
-where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{\mvec{t}{l,k,n}} using the the \ac{MSE} relation.
+where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the the \ac{MSE} relation.
 
@@
 \begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
-\text{minimize} &\quad& \|  \tilde{\mbf{v}}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
+\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
 \text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
@@
 \end{IEEEeqnarray}
-The algorithmic representation is similar to Algorithm \ref{algo-1}, with \eqref{eqn-9} is replaced by \eqref{eqn-mse-2}.
+
+\subsubsection*{Convergence}
 The convergence of the \ac{MSE} reformulation algorithm follows the similar comments drawn in \cite{christensen2008weighted,wmmse_shi}.
-Since at each \ac{KKT} point, the gradient of the original problem and the \ac{MSE} reformulation problem are made equal by the weights in the \ac{MSE} reformulation, the problem is guaranteed to converge to the optimal solution by following the same stationary \ac{KKT} points.
+Since at each \ac{KKT} point, the gradient of the original problem and the \ac{MSE} reformulation problem are made equal by the weights used in the \ac{MSE} reformulation, the problem is guaranteed to converge to the optimal solution by following the same stationary \ac{KKT} points.

### 2014-07-01 Report/problem_formulation.tex
Updated ver_1

--- 2014-06-23 Report/problem_formulation.tex
@@
-In order to minimize the number of queued packets at the \acp{BS}, the precoders \me{\mbf{M}_{k,n}} are designed to distribute the resources in an efficient manner to the users by utilizing both spatial and frequency dimension.
-The problem defined in \eqref{q_gen_sum} raises a question, namely, the linearity of the weights used in the objective function.
-It can also be a quadratic function, providing more emphasis on the users with large number queued packets as compared to the users with the small queue sizes or some other function of \me{\mbf{Q}}.
-In order to answer this question, we discuss the \ac{JSFRA} problem formulation, which restricts the solution only to the power functions.
-For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the packets available at the transmitter.
-As a result, the number of backlogged packets remaining in the system is given by
-\begin{equation}
-v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0 \fall k \in \mathcal{U}.
-\label{eqn-4.2}
+The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant term.
+It can be seen that \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{q=2} as
+\begin{equation}\label{pf-1}
+\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2.
 \end{equation}
+It can seen that \eqref{pf-1} is equivalent to the \eqref{backpreassure} algorithm when we ignore the second order terms from \eqref{pf-1}.
+It can be seen that by dropping the second order term from the \ac{Q-WSRM} formulation, we require an explicit rate constraint \eqref{eqn-3.1.4} to limit the allocations beyond the respective user requirements.
+In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself.
+Since the objective is to minimize the number of queued packets, the sub-channels are coupled in this formulation as compared to the traditional \ac{WSRM} objective eventhough the interference from the adjacent sub-channels are zero (due to the \ac{OFDM} scheme).
+The queue deviation objective provides an alternate and more complete way to perform the resource allocation as compared to the \eqref{q_gen_sum} approach.
 
-The precoder design problem can be given minimizing the absolute value of the deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as
-\me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}.
-The exponent \me{q} plays a vital role in the final allocation, which will be discussed later.
-Now, the problem of weighted queued packet minimization formulated as a $q$-norm minimization, is given by
-\begin{IEEEeqnarray}{rCl}\label{eqn-3}
-\underset{\substack{\mvec{m}{l,k,n},\\\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
-\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
-\end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, and \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission.
-It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users.
-The expression for \me{t_{l,k,n}} is due to the assumption of Gaussian signaling, so that the maximum achievable rate is \me{\log_2(1 + \gamma_{l,k,n})} for a given \ac{SINR} \me{\gamma_{l,k,n}}.
-In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels.
-The proposed solution presented in this section also applies to the sub-channel power constraint by replacing \eqref{eqn-4.3} by corresponding formulations.
 Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{q}-norm in the objective of \eqref{eqn-3}.
@@
 \item With \me{q = 1}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
-As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{Q-WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
-\item With \me{q = 2}, the objective prioritizes users with higher queued packets before considering the users with a smaller number of backlogged packets.
-This is ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
+As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
+\item With \me{q = 2}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
+For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
 \item With \(q = \infty \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.

### 2014-07-01 Report/problem_formulation_intro.tex
Updated ver_1

In this paper, we address the problem of resource allocation across the \ac{MIMO} \ac{OFDM} framework, which are shared by the users served by multiple \acp{BS}. In order to minimize the queued packets, the precoders are to be designed in a way to overcome the problem of allocating the resources more than required. In order to satisfy this constraint, we use the queue deviation as the utility function as compared to the traditional \ac{WSRM} objective discussed extensively in the literature \cite{christensen2008weighted,wmmse_shi}. For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the packets available at the transmitter. As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
\begin{equation}
v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0 \fall k \in \mathcal{U},
\label{eqn-4.2}
\end{equation}
where the expression \me{t_{l,k,n}} is replaced by maximum achievable rate by using the Gaussian signaling, which is equal to \me{\log_2(1 + \gamma_{l,k,n})} for a given \ac{SINR}. The above positivity constraint need to be satisified by \me{v_k} to avoid the excessive allocation of the resources.

The precoder design problem can be given minimizing the absolute value of the deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as \me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}. The exponent \me{q} plays a vital role in the final allocation, which will be discussed later. Now, the problem of weighted queued packet minimization formulated as a $q$-norm minimization, is given by
\begin{IEEEeqnarray}{rCl}\label{eqn-3}
\underset{\substack{\mvec{m}{l,k,n},\\\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
\end{IEEEeqnarray}
where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, and \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission. It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users. In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels. Before discussing the formulation in detail, we first discuss the existing algorithm to solve the current issue of minimizing the number of backlogged packets at the transmitter.

### 2014-07-01 Report/wsrm_formulation.tex
Updated ver_1

--- 2014-06-23 Report/wsrm_formulation.tex
@@
-We present an iterative algorithm to solve \eqref{eqn-3} locally based on the idea of alternating optimization and successive convex approximation.
-For this purpose, from \eqref{eq:SINR}, we can explicitly reformulate \eqref{eqn-3} as
+In this approach, we present an iterative algorithm to solve \eqref{eqn-3} locally based on the idea of alternating optimization and successive convex approximation.
+Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
 \begin{IEEEeqnarray}{RCL}\label{eqn-6}
-\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
+\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
 \text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}),\IEEEyessubnumber \label{eqn-6.2} \\
@@
 \mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}, \IEEEyessubnumber \\
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{(j,i) \neq (l,k)} \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + \mathbf{I}_{N_R}, \IEEEyessubnumber
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + \mathbf{I}_{N_R}, \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
-In CVX \cite{grant2008cvx}, we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `expression' qualifier.
+In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.
 Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively.
@@
 
+\subsubsection*{Convergence}
+
 In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which basically means that we do not solve the problem exactly.
@@
 In our case, we solve the sub problem inexactly, so the convergence proof of \ac{BCDM} does not apply to our problem.
-Recall that \cite{wmmse_shi} only approximates the non-convex objective in each iteration.
 In this problem, we used alternating optimization with \ac{SCA} method, which provides monotonic convergence since the objective is improved at each step \textit{i.e} \me{f^{(i)} \geq f^{(i+1)}}, assuming \me{f^{(i)}} is the objective function at the \me{i^\mathrm{th}} \ac{SCA} iteration.
-In a single receive antenna case, the proposed solution is guaranteed to converge to a \ac{KKT} point as discussed in \cite{tran2012fast}.
+For a fixed receive beamformers, the problem is guaranteed to converge to a \ac{KKT} point at each \ac{SCA} iteration as discussed in \cite{tran2012fast}.
+Now, by alternating the transmit and the receive precoders, we perform \ac{BCDM}, which provides monotonic convergence of the objective.
+Since the \ac{SCA} method is also considered in our problem, the convergence is not straight forward.
+We can only speculate the convergence based on the monotonicity of the objective values.
+Since receive beamformers are based on the \ac{MMSE} objective, it improves the objective value for each update, providing a monotonic increase in the objective value.

### 2014-07-02 Report/decomposition_solutions.tex
Updated on 16.47:Jul-2

@@
 This section addresses the distributed precoder designs for the proposed \ac{JSFRA} scheme.
-The formulation in \eqref{eqn-9} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
+The formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
 In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are considered.
@@
 
-To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\set{\mc{B} \backslash \{b\}}} and \me{\bar{\mc{U}}_b} represents the set \me{\set{\mc{U} \backslash \mc{U}_b}}.
-The centralized problem defined by \eqref{eqn-9} can be equivalently written as
+To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
+The centralized problem\footnote{\eqref{eqn-9} for the \ac{SCA} approach and \eqref{eqn-mse-2} for \ac{MSE} reformulation approach} can be equivalently written as
 \begin{IEEEeqnarray}{rCl} \label{eqn-decent-1}
-\underset{\substack{t_{l,k,n},\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
+\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
 \text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber,
@@
 
-Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized} and \cite{kaleva2013primal}, the interference constraint given by \eqref{eqn-9.1c} can be expressed by grouping the interference contribution from each \acp{BS} in the system as
-\begin{IEEEeqnarray}{RCL}
-\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \underbrace{\sum_{b \in \bar{\mc{B}}_{b_k}} \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}_{\text{neighboring \acp{BS} interference}} \; + \; N_0, \forall k \in \mc{U}.
-\label{eqn-decent-2}
-\end{IEEEeqnarray}
-In \eqref{eqn-decent-2}, the neighboring \acp{BS} signals can be written explicitly using the relaxed expression as
+Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint\footnote{coupling constraint in \ac{MSE} scheme is given by  \eqref{eqn-mse-2.3}} given by \eqref{eqn-9.1c} can be expressed by grouping the interference contribution from each \acp{BS} in the system as
 \begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
 \beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0, \IEEEyessubnumber \label{eqn-decent-3a}
+&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0, \label{eqn-decent-3a}
 \end{IEEEeqnarray}
@@
 
-The expression in \eqref{eqn-decent-3} can be solved either by primal or by dual decomposition based on the usage of the coupling variable \me{\zeta_{l,k,n,b}} in the optimization problem.
-In both approaches, the distributed problem is solved by a two level optimization approach in which the local problems are solved at the \ac{BS} level and the master problem controls the variables involved in each local problem \cite{palomar2006tutorial}.
+The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the interference caused by the transmission from \ac{BS} \me{b} to the user \me{\ith{k}} corresponding data stream.
+In order the solve for the global optimal precoders, we need to find the optimal coupling variables \me{\zeta_{l,k,n,b}} by either using \ac{PD} or by using \ac{DD} method.
+In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} scheme and \eqref{eqn-mse-2.3} for the \ac{MSE} relaxation scheme are decoupled to perform the distributed precoder design problem.

### 2014-07-02 Report/mse_formulation.tex
Updated on 16.47:Jul-2

@@
 
-The \ac{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the set defined by the constraint \eqref{eqn-mse-1.2}.
+The \ac{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the constraint \eqref{eqn-mse-1.2}.
 In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}.
@@
 Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}.
-The optimization problem can be given as
+The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
 \begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
-\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
+\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
 \text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
@@
 \subsubsection*{Convergence}
-The convergence of the \ac{MSE} reformulation algorithm follows the similar comments drawn in \cite{christensen2008weighted,wmmse_shi}.
-Since at each \ac{KKT} point, the gradient of the original problem and the \ac{MSE} reformulation problem are made equal by the weights used in the \ac{MSE} reformulation, the problem is guaranteed to converge to the optimal solution by following the same stationary \ac{KKT} points.
+The convergence of the \ac{MSE} reformulation approach follows the same arguments detailed in \cite{wmmse_shi,christensen2008weighted}.
+Since the transmit precoders are obtained by minimizing the weighted \ac{MSE} criterion, it converges to the stationary \ac{KKT} point at each iteration.
+The receiver updates are made based on the \ac{MMSE} criterion, it provides the optimal receive beamformers for the given transmit precoders.
+Alternating between these two precoder designs guarantees the monotonicity of the objective function used in the problem \eqref{eqn-mse-2}.
+The \ac{MSE} relaxation method converges to the same stationary \ac{KKT} point as of the original \ac{WSRM} problem by making the graidents equal.

### 2014-07-02 Report/primal_approach.tex
Updated on 16.47:Jul-2

@@
-The centralized problem described in \eqref{eqn-decent-1} can be solved in a distributed approach using the \ac{PD} method.
-The decentralized approach decomposes the centralized problem as a two level optimization problem in which the multiple sub problems are coordinated using a master problem.
-The coordination of the multiple subproblems can be carried out by exchanging the information across the coordinating \acp{BS} in \me{\mc{B}} via backhaul.
-The distributed solution is achieved by fixing the interference level \me{\zeta_{l,k,n,b}, \forall k \in \mc{U}_{b_k}} from the \acp{BS} \me{b \in \bar{\mc{B}}_{b_k}} so as to decouple the variables \me{\zeta_{l,k,n,b}} \cite{pennanen2011decentralized,bertsekas1999nonlinear}.
-Now, the subproblems are governed by the master problem by updating the interference thresholds at each iteration using the subgradients.
+The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}.
+Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3a}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration and is carried out until convergence.
+The primal approach is discussed extensively for the \ac{WSRM} problem in \cite{pennanen2011decentralized} and much of the current work follows the same.
+Much of the details are provided in the Appendix \ref{a-2}.
 
-As discussed in Section \ref{sec-4}, the constraint involving the coupling variables \eqref{eqn-9.1c} can be relaxed using the equivalent formulation in \eqref{eqn-decent-3}.
-Now, the subproblem for the \ac{BS} \me{b_k \in \mc{B}} can be obtained by grouping the terms relevant to the \ac{BS} \me{b_k} as
-\begin{IEEEeqnarray}{rCl} \label{eqn-primal-1}
-\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \IEEEyessubnumber \label{eqn-primal-1a} \\
-\text{subject to}&\quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_{b_k}} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \IEEEyessubnumber \label{eqn-primal-1c} \\
-&& \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-primal-1d} \\
-&& \zeta_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-primal-1e} \\
- & \quad & \text{and} \; \eqref{eqn-8} \IEEEyessubnumber,
-\end{IEEEeqnarray}
-where \me{\zeta_{\pr{l},\pr{k},n,{b_k}}} corresponds to the fixed maximum interference caused by the transmission from the \ac{BS} \me{b_k} to the \me{\ith{\pr{l}}} spatial stream of the \me{\ith{\pr{k}}} user.
-Let \me{\mbfa{\zeta}^{\set{b_k}}} be the vector representing the fixed interference levels relevant to the \ac{BS} \me{b_k} in a fully connected network (in practice it will be less), which is given by
-\begin{IEEEeqnarray}{RCL} \label{eqn-primal-2}
-\mbfa{\zeta}_{k,n,b} &=& \left [ \; \zeta_{1,k,n,b}, \dotsc, \zeta_{L,k,n,b} \; \right ] \IEEEyessubnumber \\
-\mbfa{\zeta}^{\set{b_k}}_n &=& \left [ \; \mbfa{\zeta}_{\mc{U}_{b_k}(1),n,\bar{\mc{B}}_{b_k}(1)}, \dotsc, \mbfa{\zeta}_{\mc{U}_{b_k}(1),n,\bar{\mc{B}}_{b_k}(|\bar{\mc{B}}_{b_k}|)}, \right .
-\nonumber \\
-&& \left .
-\dotsc, \mbfa{\zeta}_{\mc{U}_{b_k}(|\mc{U}_{b_k}|),n,\bar{\mc{B}}_{b_k}(|\bar{\mc{B}}_{b_k}|)}, \dotsc, \mbfa{\zeta}_{\bar{\mc{U}}_{b_k}(1),n,b_k}, \dotsc, \mbfa{\zeta}_{\bar{\mc{U}}_{b_k}(|\bar{\mc{U}}_{b_k}|),n,b_k} \; \right  ] \IEEEyessubnumber \\
-\mbfa{\zeta}^{\set{b_k}} &=& \left [ \; \mbfa{\zeta}^{(b_k)}_1, \dotsc, \mbfa{\zeta}^{(b_k)}_N \; \right ], \IEEEyessubnumber
-\end{IEEEeqnarray}
-where the length of the vector \me{\mbfa{\zeta}^{\set{b_k}}} is
-\begin{equation}
-n_{b_k} = | \mbfa{\zeta}^{\set{b_k}} | = \left ( |\bar{\mc{B}}_{b_k}| |\mc{U}_{b_k}| + |\bar{\mc{U}}_{b_k}|\right ) L N
-\label{primal-vec-len}
-\end{equation}
-
-The problem defined in \eqref{eqn-primal-1} is already decoupled across the \acp{BS} by fixing the inter-cell interference vector \eqref{eqn-primal-2} for all \acp{BS}.
-For a fixed interference threshold \me{\mbfa{\zeta}^{\set{b}}}, the precoders are designed using \eqref{eqn-primal-1}.
-The local subproblem \eqref{eqn-primal-1} solved at each \ac{BS} are coordinated by the master problem, which updates the interference thresholds \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}} for the next iteration.
-The master and the subproblems follows the classical \ac{BCDM} approach to achieve the optimal solution by alternating the variable set while keeping other set constant in an iterative manner.
-The master problem controlling multiple subproblems is given by
-\begin{IEEEeqnarray}{rCl} \label{eqn-primal-3}
-\underset{\mbfa{\zeta}}{\text{minimize}} & \quad & \sum_{b \in \mc{B}} \alpha^{\star}_b (\mbfa{\zeta}^{\set{b}}) \IEEEyessubnumber \\
-\text{subject to} & \quad & \mbfa{\zeta}^{\set{b}} \in \mathbb{R}_+^{n_b}, \forall b \in \mc{B}, \IEEEyessubnumber
-\end{IEEEeqnarray}
-where \me{\alpha^{\star}_b (\mbfa{\zeta}^{\set{b}})} denotes the optimal solution for \eqref{eqn-primal-1} with the previous value of \me{\mbfa{\zeta}^{(i-1)}}, where \me{\mbfa{\zeta}} is the global interference vector formed by stacking the interference vector associated with each \ac{BS} as \me{\mbfa{\zeta} = \left [ \mbfa{\zeta}^{\set{\mc{B}(0)}}, \mbfa{\zeta}^{\set{\mc{B}(1)}}, \ldots, \mbfa{\zeta}^{\set{\mc{B}(|\mc{B}|)}}\right ]}.
-
-The master problem to find the optimal \me{\mbfa{\zeta}^{\set{b_k}(i)}, \forall b_k \in \mc{B}} is given by the following subgradient method \cite{bertsekas1999nonlinear} as
-\begin{equation} \label{primal-sg-update}
-\zeta^{\set{b_k}(i)}_{l,k,n,b} = \left [\zeta_{l,k,n,b}^{\set{b_k}(i-1)} - \rho \, s_{l,k,n,b}^{\set{b_k}(i-1)} \right ]^+, \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_b,
-\end{equation}
-where \me{i} is the iteration index, \me{\rho} is the positive step size, and \me{s^{\set{b_k}(i-1)}_{l,k,n,b}} is the subgradient of the problem defined in \eqref{eqn-primal-3} evaluated at \me{\zeta^{(i-1)}_{l,k,n,b}}.
-To find the subgradient \me{s^{\set{b_k}(i-1)}_{l,k,n,b}}, the dual variables corresponding to the interference constraints are required, which can be obtained by forming the Lagrangian of the primal problem \eqref{eqn-primal-2} as
-\begin{IEEEeqnarray}{rCl} \label{eqn-primal-4}
-\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \mu^{\set{b_k}}_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \nonumber + \left ( \beta_{l,k,n} - \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \right .
-\nonumber \\
-&& \left .
-\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{(i-1)}_{l,k,n,b} \; + \; N_0 \right ) \, \mu^{\set{b_k}}_{l,k,n}  \nonumber \\
-&& + \quad \left ( \zeta^{(i-1)}_{\pr{l},\pr{k},n,{b_k}} - \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2 \right ) \, \mu^{\set{b_k}}_{\pr{l},\pr{k},n} , \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \\
-\text{subject to} &\quad& \eqref{eqn-primal-1c} \; \text{and} \; \eqref{eqn-8} \IEEEyessubnumber.
-\end{IEEEeqnarray}
-Now the primal and the dual variables \me{\mu^{\set{b_k}}_{l,k,n}} and \me{\mu^{\set{b_k}}_{\pr{l},\pr{k},n}} corresponding to the constraints \eqref{eqn-primal-1d} and \eqref{eqn-primal-1e} are obtained by solving \eqref{eqn-primal-4}.
-
-To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner.
-Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}.
-With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}.
-
-Once the interference vector converges \me{\mbfa{\zeta}^{\set{i}} \approx \mbfa{\zeta}^{\set{i-1}}} or iterated for certain times, say, \me{J_{\max}}, the \ac{SCA} update is performed by exchanging the transmit and the receive precoders to update the respective variables \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}}.
-The \ac{SCA} update can also be performed until convergence or for certain threshold \me{I_{\max}}.
-The algorithmic representation of the \ac{PD} approach is detailed in Algorithm.
-\ref{algo-2}.
-In this case, we perform \ac{SCA} and the receiver update at the same instant compared with the update of the recieve beamformers after the \ac{SCA} convergence.
-The approach followed in the algorithm provides the same solution as that of the separate update, since the receive beamformers are optimal for the given transmit precoders.
-\begin{algorithm}
- \SetAlgoLined
- \DontPrintSemicolon
- \BlankLine
- \SetKwInput{KwInit}{Initialize}
- \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
- \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
- update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
- initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
- for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
- \Repeat{convergence or \me{i \geq I_{\max}}}{
-    initialize \me{j=0} \;
-    \Repeat{convergence or \me{j \geq J_{\max}}}{
-        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-4} \;
-        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
-        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
-        \me{j = j + 1} \;
-    }
-    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
-    exchange the transmit and the receive precoders \me{\mbf{M}_{k,n}} and \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
-    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
-    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
-    $i = i + 1$ \;
-  }
- \caption{\ac{PD} based decentralized \acs{JSFRA} scheme}
-  \label{algo-2}
-\end{algorithm}
+\subsubsection*{Convergence}
+The convergence of the primal is similar to that of the centralized problem if the interference variables \me{\zeta_{l,k,n,b}} are allowed to converge to the optimal values.
+But in practice, we can limit the number of exchanges to \me{J_{\max}} after which \ac{SCA} update is performed until convergence or for \me{I_{\max}} times.
+The update of \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} can be made in conjunction with the receiver update \me{\mvec{W}{k,n}}.
+The receiver update can be made by using the precoded pilot transmission from each user as in \cite{komulainen2013effective}.

### 2014-07-02 Report/primal_approach_appendix.tex
Updated on 16.47:Jul-2

By fixing the interference values \me{\zeta_{\pr{l},\pr{k},n,{b_k}}} corresponding to the interference from the \ac{BS} \me{b_k}, the constraint involving the coupling variables \eqref{eqn-9.1c} can be relaxed using the equivalent formulation in \eqref{eqn-decent-3}. Now, the subproblem for the \ac{BS} \me{b_k \in \mc{B}} can be obtained by grouping the terms relevant to the \ac{BS} \me{b_k} as
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-1}
\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \IEEEyessubnumber \label{eqn-primal-1a} \\
\text{subject to}&\quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_{b_k}} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \IEEEyessubnumber \label{eqn-primal-1c} \\
&& \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-primal-1d} \\
&& \zeta_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-primal-1e} \\
 & \quad & \text{and} \; \eqref{eqn-8} \IEEEyessubnumber,
\end{IEEEeqnarray}

Let \me{\mbfa{\zeta}^{\set{b_k}}} be the vector representing the fixed interference levels relevant to the \ac{BS} \me{b_k} in a fully connected network\footnote{in practice it will be less due to the path loss}, which is given by
\begin{IEEEeqnarray}{RCL} \label{eqn-primal-2}
\mbfa{\zeta}_{k,n,b} &=& \left [ \; \zeta_{1,k,n,b}, \dotsc, \zeta_{L,k,n,b} \; \right ] \IEEEyessubnumber \\
\mbfa{\zeta}^{\set{b_k}}_n &=& \left [ \; \mbfa{\zeta}_{\mc{U}_{b_k}(1),n,\bar{\mc{B}}_{b_k}(1)}, \dotsc, \mbfa{\zeta}_{\mc{U}_{b_k}(1),n,\bar{\mc{B}}_{b_k}(|\bar{\mc{B}}_{b_k}|)}, \right . \nonumber \\
&& \left . \dotsc, \mbfa{\zeta}_{\mc{U}_{b_k}(|\mc{U}_{b_k}|),n,\bar{\mc{B}}_{b_k}(|\bar{\mc{B}}_{b_k}|)}, \dotsc, \mbfa{\zeta}_{\bar{\mc{U}}_{b_k}(1),n,b_k}, \dotsc, \mbfa{\zeta}_{\bar{\mc{U}}_{b_k}(|\bar{\mc{U}}_{b_k}|),n,b_k} \; \right  ] \IEEEyessubnumber \\
\mbfa{\zeta}^{\set{b_k}} &=& \left [ \; \mbfa{\zeta}^{(b_k)}_1, \dotsc, \mbfa{\zeta}^{(b_k)}_N \; \right ], \IEEEyessubnumber
\end{IEEEeqnarray}
where the length of the vector \me{\mbfa{\zeta}^{\set{b_k}}} is
\begin{equation}
n_{b_k} = | \mbfa{\zeta}^{\set{b_k}} | = \left ( |\bar{\mc{B}}_{b_k}| |\mc{U}_{b_k}| + |\bar{\mc{U}}_{b_k}|\right ) L N
\label{primal-vec-len}
\end{equation}

The local subproblem \eqref{eqn-primal-1} solved at each \ac{BS} are coordinated by the master problem, which updates the interference thresholds \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}} for the next iteration. The master problem controlling multiple subproblems is given by
\begin{IEEEeqnarray}{rCl} \label{eqn-primal-3}
\underset{\mbfa{\zeta}}{\text{minimize}} & \quad & \sum_{b \in \mc{B}} \alpha^{\star}_b (\mbfa{\zeta}^{\set{b}}) \IEEEyessubnumber \\
\text{subject to} & \quad & \mbfa{\zeta}^{\set{b}} \in \mathbb{R}_+^{n_b}, \forall b \in \mc{B}, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\alpha^{\star}_b (\mbfa{\zeta}^{\set{b}})} denotes the optimal solution for \eqref{eqn-primal-1} with the previous value of \me{\mbfa{\zeta}^{(i-1)}}, where \me{\mbfa{\zeta}} is the global interference vector formed by stacking the interference vector associated with each \ac{BS} as \me{\mbfa{\zeta} = \left [ \mbfa{\zeta}^{\set{\mc{B}(0)}}, \mbfa{\zeta}^{\set{\mc{B}(1)}}, \ldots, \mbfa{\zeta}^{\set{\mc{B}(|\mc{B}|)}}\right ]}.

The master problem to find the optimal \me{\mbfa{\zeta}^{\set{b_k}(i)}, \forall b_k \in \mc{B}} is given by the following subgradient method \cite{bertsekas1999nonlinear} as
\begin{equation} \label{primal-sg-update}
\zeta^{\set{b_k}(i)}_{l,k,n,b} = \left [\zeta_{l,k,n,b}^{\set{b_k}(i-1)} - \rho \, s_{l,k,n,b}^{\set{b_k}(i-1)} \right ]^+, \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_b,
\end{equation}
where \me{i} is the iteration index, \me{\rho} is the positive step size, and \me{s^{\set{b_k}(i-1)}_{l,k,n,b}} is the subgradient of the problem defined in \eqref{eqn-primal-3} evaluated at \me{\zeta^{(i-1)}_{l,k,n,b}}. To find the subgradient \me{s^{\set{b_k}(i-1)}_{l,k,n,b}}, the dual variables corresponding to the interference constraints are required, which can be obtained by forming the dual problem of \eqref{eqn-primal-2} as discussed in \cite{pennanen2011decentralized}. Now the primal and the dual variables \me{\mu^{\set{b_k}}_{l,k,n}} and \me{\mu^{\set{b_k}}_{\pr{l},\pr{k},n}} corresponding to the constraints \eqref{eqn-primal-1d} and \eqref{eqn-primal-1e} can be obtained from the solvers, which solves the dual problem as well.

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-2} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the transmit and the receive precoders \me{\mbf{M}_{k,n}} and \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{\ac{PD} based decentralized \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}

### 2014-07-02 Report/problem_formulation_intro.tex
Updated on 16.47:Jul-2

@@
 \begin{IEEEeqnarray}{rCl}\label{eqn-3}
-\underset{\substack{\mvec{m}{l,k,n},\\\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
+\underset{\substack{\mvec{m}{l,k,n},\\\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
 \text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
 \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, and \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively.
 It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users.

### 2014-07-02 Report/sub_channel_wsrm.tex
Updated on 16.47:Jul-2

@@
-In this method, titled as \acf{QM} \ac{SRA} scheme, we limit the resource allocation over the spatial dimension only by performing \ac{JSFRA} design over each sub-channel in an instant.
-This scheme can be considered in a system employing the \ac{FFR} like power restrictions on certain sub-channels.
-It can also be used to reduce the problem dimension by limiting the allocation over the spatial dimension only.
-It is well suited for the persistent scheduling like schemes, where certain sub-channels are dedicated to only certain users.
-Imposing the user restrictions in the \ac{JSFRA} scheme adds a non-convex constraint which will be difficult to solve.
+The complexity involved in the \ac{JSFRA} scheme scales up significantly based on the sub-channel over which the decision has to be made.
+Not only the complexity, but also the convergence speed depends on the size  and the number of decision variables involved in the optimization problem.
+In order to reduce the complexity involved in the \ac{JSFRA} scheme, we provide an alternative sub-optimal solution, where the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits into consideration.
+It provides an alternative way to the parallel sub-channel wise precoder update using the decomposition techniques discussed in \cite{palomar2006tutorial,boyd2011distributed}.
 
-For a scheduling slot, the precoders are designed over each sub-channel in a sequential manner with the corresponding user queues are updated with the total transmission allocations made in the previous sub-channels on the same slot.
-
-The queue update is common for \ac{SRA} and band-wise \ac{Q-WSRM} schemes, and the queue length controls the design of precoders for the allocation of spatial resources for each sub-channel.
-The queues are updated before designing the precoders for each sub-channel \me{n} as
+The proposed \acf{QM} \ac{SRA} scheme decouples the fixing the power across each sub-channel to a constant value as compared to the global power constraint defined by \eqref{eqn-4.3}.
+In contrast to the decomposition based approach for sub-channel wise resource allocation, this method requires the update on the number of queued bits before each sub-channel level optimization.
+In this approach, the number of queued bits are updated by the difference between the total number of queued bits during the current slot and the total number of bits that are guaranteed by the earlier sub-channel wise allocations in the same slot as
 \begin{equation}
@@
 \end{equation}
-where \me{Q_k} is given by \eqref{eqn-2a} for the user \me{k}.
-The weight for the sub-channel \me{n} is given by \eqref{eqn-weight}, which uses the allotted transmission bits \me{t_{l,k,j}} evaluated from the earlier sub-channels \me{j < n}.
-The \ac{QM} \ac{SRA} scheme depends on the permutation pattern of the sub-channel selection order for the precoder design and the performance.
+where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}.
+In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,j}} is the rate or guaranteed bits allocated over the sub-channel \me{j}.
+The current scheme is very sensitive to the order in which the sub-channels are selected for the optimization problem.

### 2014-07-03 Report/dual_approach.tex
17.28:00 Jul-03-2014

@@
 Let  \me{\mbfa{\zeta}^{\set{b_k}}} be the locally maintained vector formed by stacking the interference entries relevant to the \ac{BS} \me{b_k}.
-Let \me{\mbfa{\zeta}} be the complete interference entries of all \acp{BS} in the set \me{\mc{B}} stacked as a vector as
+Let \me{\mbfa{\zeta}} be the global interference entries of all \acp{BS} in the set \me{\mc{B}} stacked as a vector as
 \begin{IEEEeqnarray}{rCl}
@@
 It can be seen from the objective \eqref{eqn-dual-2a} that the global interference \me{\mbfa{\zeta}(b_k)} can be dropped from the objective \eqref{eqn-dual-2a} without affecting the optimal solution, since it is constant for the subproblems.
+The problem defined in \eqref{eqn-dual-2} can be decoupled to solve for the precoders at each \ac{BS} by using interference vector \me{\mbfa{\zeta}^{\set{b_k}}} as an optimization variable for the fixed interference price (dual variable) \me{\mbfa{\nu}^{\set{b_k}}}.
+In the current work, we consider the robust counterpart of the \acl{DD} scheme, namely \ac{ADMM} approach, which doesn't require any assumptions on the convexity of the functions for convergence \cite{boyd2011distributed}.
 
-Now, the problem defined in \eqref{eqn-dual-2} can be decoupled to solve for the precoders at each \ac{BS} by using interference vector \me{\mbfa{\zeta}^{\set{b_k}}} as a optimization variable for the fixed interference price (dual variable) \me{\mbfa{\nu}^{\set{b_k}}}.
-The convergence of the problem with the objective function \eqref{eqn-dual-2} is slower due to the linear penalty term for the interference assumptions at each \ac{BS}, thereby providing more emphasis only when the interference deviation is significantly large.
-
-In order to bound the interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} and \me{\zeta^{\set{b}}_{l,k,n,b}} between the \acp{BS} \me{b_k} and \me{b}, adding a scaled quadratic penalty of the interference deviation provides better convergence properties without affecting the optimal solution \cite{bertsekas1999nonlinear,boyd2011distributed}.
-At the optimal point, the actual and the assumed (local) interference values are equal, thereby providing no contribution to the objective.
-This way of adding a scaled quadratic penalty term in the objective function is known as \ac{ADMM} method for solving the \acl{DD} problem.
-In addition to the faster convergence, it also identifies the optimal step size for the dual variable update.
+In order to bound the interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} and \me{\zeta^{\set{b}}_{l,k,n,b}} between the \acp{BS} \me{b_k} and \me{b}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation to the objective function \cite{bertsekas1999nonlinear,boyd2011distributed}.
+At the optimal point, the actual and the assumed (local) interference values will be equal and provides no contribution to the objective function.
 It can be shown that the optimal step size is equal to the scaling factor \me{\rho} used for the penalty term in the objective function \cite{bertsekas1999nonlinear,boyd2011distributed}.
-Now, the subproblem at each \ac{BS}, obtained via \ac{ADMM} decomposition, is given by
+Now, the subproblem at each \ac{BS} for the \me{\ith{i}} iteration is give by
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \zeta^{\set{b_k}(i)}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}(i)}T} \mbfa{\zeta}^{\set{b_k}(i)} + \frac{\rho}{2} \left \| \, \mbfa{\zeta}^{(i)}(b_k) - \mbfa{\zeta}^{\set{b_k}(i)} \, \right \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \zeta^{\set{b_k}(i)}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}(i)}T} \mbfa{\zeta}^{\set{b_k}(i)} + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i)}(b_k)}_{\text{global iterate}} - \underbrace{\mbfa{\zeta}^{\set{b_k}(i)}}_{\text{local iterate}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
 \text{subject to} & \quad & \eqref{eqn-dual-1d} - \eqref{eqn-dual-1f} \IEEEyessubnumber \label{eqn-dual-3b},
 \end{IEEEeqnarray}
-where \me{(i)} represents the current iteration counter or information exchange counter and \me{\mbfa{\zeta}^{(i)}} denotes the updated interference level obtained from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.
+where \me{(i)} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.
 
-Once the subproblems are solved at each \ac{BS}, the update for the global interference vector and the dual variables can be performed at the \acp{BS} locally by exchanging the local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}.
-Since the entries in \me{\mbfa{\zeta}^{(i)}} relates exactly two \acp{BS} only, each entry in the \me{\mbfa{\zeta}^{(i)}} can be updated using a function operating on the local copies from the corresponding \acp{BS}.
-For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i-1)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by the \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b}}.
-It can be updated by either using
-\begin{subeqnarray}
-\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} &=& \zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} \, \text{(or)}\slabel{zeta_update-1} \\
-\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} &=& \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ), \slabel{zeta_update-2}
-\end{subeqnarray}
-as discussed briefly in \cite{tolli2011decentralized}.
+Once the local problems are solved at each \ac{BS}, the update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} can be performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}.
+Since the entries in \me{\mbfa{\zeta}^{(i)}} relates exactly two \acp{BS} only, each entry in the \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS} only.
+For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i-1)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by the \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b}} as
+\begin{equation}
+\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
+\label{zeta_update}
+\end{equation}
 The dual variable entries in the vector \me{\mbfa{\nu}^{\set{b_k}}}, which is the stacked dual variables corresponding to the interference equality constraint at the \ac{BS} \me{b_k}, are updated using the subgradient as
@@
 
-The \ac{ADMM} approach uses the quadratic penalty term in the objective for better convergence properties compared to the plain \ac{DD} scheme.
-The addition of the quadratic term in the objective translates the objective function into a strict convex function.
-The subproblem defined by \eqref{eqn-dual-3} is convex and the objective has the convex function, therefore the convergence is guaranteed as discussed in \cite{scutari,boyd2011distributed}.
+\subsubsection*{Convergence}
+The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to the optimal value for a fixed \ac{SCA} point.
+Since subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to the optimal value \cite{boyd2011distributed} for a given \ac{SCA} point.
+The receive beamformers are updated at each \ac{SCA} update provides monotonic increase in the objective function, since the \ac{MMSE} receive beamformers are optimal for the fixed transmit precoders obtained by solving the subproblems until convergence.
 The algorithmic representation of the \ac{ADMM} based approach for decentralization is given in Algorithm \ref{algo-3}.
@@
  update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
- initialize the interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
+ initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
  initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
@@
 		update the dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update} \;
-        update the interference vector \me{\mbfa{\zeta}^{\set{b}(j+1)}} using \eqref{zeta_update-1} or \eqref{zeta_update-2} \;
+        update the global interference vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update} \;
 		\me{j = j + 1} \;
@@
     update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
-    exchange the transmit and the receive precoders \me{\mbf{M}_{k,n}} and \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
+    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
     update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
@@
   }
- \caption{\ac{ADMM} based decentralized \acs{JSFRA} scheme}
+ \caption{Decentralization via \ac{ADMM} for \acs{JSFRA} scheme}
   \label{algo-3}

### 2014-07-03 Report/kkt_mse_approach.tex
17.28:00 Jul-03-2014

@@
-So far, we have discussed the problem of minimizing the number of backlogged packets at the \acp{BS} using the precoders by formulating it as an optimization problem, which can be handled by the existing solvers CVX \cite{grant2008cvx}.
+In general, the distributed approaches presented in the earlier sections can be used to perform the precoder design problem in a decentralized way.
+One significant issue remains in both \acl{PD} and \ac{ADMM} apporaches is the update of the coupling variable.
+In both the methods, the coupling variables are updated by using the subgradients, which depends on the choice of the step size used for each update.
+In order to avoid the use of subgradient update for the coupling variables, the \ac{MSE} reformulation approach can be considered by solving the \ac{KKT} equations.
+Initial work on this approach is discussed extensively in \cite{wmmse_shi} for the \ac{WSRM} problem and \cite{kaleva2012weighted} considered the \ac{WSRM} problem with the additional \ac{QoS} constraints like minimum guaranteed rate requirements.
+
+When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which then makes the problem difficult to solve in an iterative manner.
+But, in our formulation, since the rate constraint imposed by the number of queued packets waiting for the transmission in in the objective function, it provides an efficient apporach to solve the problem with the rate constraints.
 In this section, we provide an iterative precoder design for the \ac{JSFRA} formulation approached via \ac{MSE} reformulation as discussed in \ref{sec-3.3}.
@@
 \begin{itemize}
-\item when the exponent \me{q} is odd and \me{q > 1} or,
+\item when the exponent \me{q} is even or,
 \item when the number of backlogged packets for each user is larger than the available resources for the transmission \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
 \end{itemize}
-The first condition is from the fact that the differential of a function with power \me{q} leaves the power to \me{q-1}, which helps us to drop the absolute value condition when \me{q-1} is even.
-This condition cannot be applied for \me{q=1} since the rate constraint is eliminated by the differential operation.
+The first condition is required for the iterative design, since the objective function needs to be differentiable to find the \ac{KKT} equations.
+So, when the exponent \me{q} is even, the absolute operator can be dropped from the objective function without any change in the optimal solution for any number of queued packets.
 
@@
 \begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
-\underset{\substack{t_{l,k,n},\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \alpha_{l,k,n},\delta_{b}, \sigma_{l,k,n}}}{\text{minimize}} &\quad& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \left ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
-\text{subject to} & \quad & \nonumber \\
-\alpha_{l,k,n} : & \quad & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
-\sigma_{l,k,n} : & \quad & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} = t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
-\delta_b : & \quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
+\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \alpha_{l,k,n}, \\ \delta_{b},\sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \left ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
+\text{subject to} & \hspace{0.5cm} & \nonumber \\
+\alpha_{l,k,n} : & \hspace{0.5cm} & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \\ \nonumber
+&\hspace{0.5cm}& \quad {} + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
+\sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} = t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
+\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 \begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
-\alpha^{(i)}_{l,k,n} &=& \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.1} \\
-\sigma_{l,k,n}^{(i)} &=& \dfrac{q \left [ a_k \, \left (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i-1)} \right )^{(q-1)} \right ]}{\log(2)} \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\alpha^{(i)}_{l,k,n} &=& \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.1} \\
+\sigma_{l,k,n}^{(i)} &=& \dfrac{q \left [ a_k \, \left (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i-1)} \right )^{(q-1)} \right ]}{\log(2)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
 \mvec{m}{l,k,n}^{(i)} &=& \left ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \right )^{-1} \alpha^{(i)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \\ \nonumber
+&+& \quad  N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2,\quad \forall k \in \mc{U}, \forall n \in \mc{C} \IEEEyessubnumber \label{kkt-mse-4.4} \\
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \sum_{(x,y) \neq (l,k)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i-1)} \mvec{m}{x,y,n}^{\herm \, (i-1)} \mvec{H}{b_{y},k,n}^\herm + \mathbf{I}_{N_R} \right ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i-1)}.
-\IEEEyessubnumber \label{kkt-mse-4.6}
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \sum_{(x,y) \neq (l,k)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i-1)} \mvec{m}{x,y,n}^{\herm \, (i-1)} \mvec{H}{b_{y},k,n}^\herm + \mathbf{I}_{N_R} \right ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i-1)}, \IEEEyessubnumber \label{kkt-mse-4.6}
 \end{IEEEeqnarray}
+\me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}}.
 
@@
 It can be initiated by solving \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} for a random transmit precoders \me{\mbf{M}_{k,n}} satisfying \eqref{kkt-mse-1.4}.
-It can be noted that the proposed iterative algorithm converges faster than the \acl{PD} and the \ac{ADMM} based \acl{DD} scheme, since the later schemes are based on the subgradient approach and the former one achieves the \ac{KKT} points at each iteration.
+It can be noted that the proposed iterative algorithm converges faster than the \acl{PD} and the \ac{ADMM} approach\footnote{from our simulations}, since the later schemes are based on the subgradient approach and the former one achieves the \ac{KKT} points at each iteration.
 In \eqref{kkt-mse-4}, all expressions provide the closed form solution for the respective variables except the transmit precoders in \eqref{kkt-mse-4.3}, which depends on the variable \me{\delta_b}.
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=1} and the transmit precoders \me{\mbf{m}^{(0)}_{l,k,n}} randomly satisfying the total power constraint \eqref{kkt-mse-1.4}}
+ \KwInit{\me{i=1} and the transmit precoders \me{\mbf{m}^{(0)}_{l,k,n}} randomly satisfying the power constraint \eqref{kkt-mse-1.4}}
  \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly, \me{\mvec{w}{l,k,n}^{(0)}} with \eqref{kkt-mse-4.6} and \me{{t}_{l,k,n}^{(0)}} using \eqref{kkt-mse-4.5}}

### 2014-07-03 Report/primal_approach_appendix.tex
17.28:00 Jul-03-2014

@@
     update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
-    exchange the transmit and the receive precoders \me{\mbf{M}_{k,n}} and \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
+    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
     update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
@@
   }
- \caption{\ac{PD} based decentralized \acs{JSFRA} scheme}
+ \caption{Decentralization via Primal Decomposition for \acs{JSFRA} scheme}
   \label{algo-2}

### 2014-07-03 Report/joint_wsrm_formulation.tex
Updated on 16.47:Jul-2
Satya corrections !

@@
 The \ac{WSRM} technique is predominantly used to design the precoders for the \ac{MIMO} \ac{BC} channels to maximize the weighted sum throughput in the downlink direction.
-The weights are used to provide different priorities to the users based on their requirements and \ac{QoS} criterion.
-Since the objective of this work is mainly concerned with the reduction of the number of queued packets, we use the length of the queued packets for each user as the respective weights.
-Using the length of the queued packets as the corresponding weights is obtained from the well known algorithm, called the \textit{backpreassure algorithm}, which is used to decide the routing decisions for each node in the network to efficiently send the packets to the desired destination with minimal packet drops and delay.
-The backpreassure algorithm is the outcome of minimizing the Lyapunov drift conditioned over the current queue states \me{\mbf{Q}(i - 1)}, where \me{\mbf{Q}} is the vector formed by stacking the number of queued packets of each user in the system.
-Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift conditioned over different channel realizations is given by
+The weights are used to provide different priorities to the users based on the respective \ac{QoS} criterion.
+Since the objective of this work is concerned with the reduction of the number of queued packets, we use the total number of the queued packets for each user as the respective weights.
+Using the size of the queued packets as the corresponding weights is obtained from the well known algorithm, called the \textit{backpreassure algorithm}, which is used to decide the routing decisions for each node in the network to efficiently send the packets to the desired destination with minimal packet drops and delay.
+The backpreassure algorithm is the outcome of minimizing the Lyapunov drift \cite{neely2010stochastic} conditioned over the current queue states \me{\mbf{Q}(i - 1)}, where \me{\mbf{Q}} is the vector formed by stacking the number of queued packets of each user in the system.
+Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift conditioned over the current queue state is given by
 \begin{equation} \label{eqn-3.1.0}
@@
 \end{equation}
-where the expectation is taken over all possible control decisions made in accordance to the channel under consideration to minimize the total backlogged packets at a given instant.
+where the expectation is taken over all possible control\footnote{transmission rates} decisions made in accordance to the channel under consideration to minimize the total backlogged packets at a given instant.
 Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression is given by
@@
 \end{equation}
-where \me{\mbfa{\lambda}} and \me{\mbf{t}} are the vectors formed by stacking the arrival and transmission of all users in the system and the inequality is due to the upper bound\footnote{\me{\left ( \max{\Big [ \mbf{Q}(i-1) - \mbf{t}(i),0 \Big ] } + \mbfa{\lambda}(i) \right )^2 \leq \mbf{Q}^2(i-1) + \mbf{t}^2(i) + \mbfa{\lambda}^2(i) + 2 \, \mbf{Q}(i-1) \left ( \mbfa{\lambda}(i) - \mbf{t}(i) \right ) }}.
+where \me{\mbfa{\lambda}} and \me{\mbf{t}} are the vectors formed by stacking the arrival and transmission of all users in the system and the inequality provides the upper bound\footnote{\me{\left ( \max{\Big [ \mbf{Q}(i-1) - \mbf{t}(i),0 \Big ] } + \mbfa{\lambda}(i) \right )^2 \leq \mbf{Q}^2(i-1) + \mbf{t}^2(i) + \mbfa{\lambda}^2(i) + 2 \, \mbf{Q}(i-1) \left ( \mbfa{\lambda}(i) - \mbf{t}(i) \right ) }} for the Lyapunov drift.
 
@@
 \begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
-\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
+\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n},\mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
 \text{subject to.} & \quad & t_{l,k,n} \leq \log_2(1+\gamma_{l,k,n}) \IEEEyessubnumber \label{eqn-3.1.2} \\
@@
 \begin{IEEEeqnarray}{rCl}\label{gen_sum}
-\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \IEEEyessubnumber \\
+\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n},\mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \IEEEyessubnumber \\
 \text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.2}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4}. \IEEEyessubnumber

### 2014-07-03 Report/problem_formulation_intro.tex
Satya corrections !

@@
 \begin{equation}
-v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0 \fall k \in \mathcal{U},
+v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0 \fall k \in \mathcal{U}.
 \label{eqn-4.2}
 \end{equation}
-where the expression \me{t_{l,k,n}} is replaced by maximum achievable rate by using the Gaussian signaling, which is equal to \me{\log_2(1 + \gamma_{l,k,n})} for a given \ac{SINR}.
 The above positivity constraint need to be satisified by \me{v_k} to avoid the excessive allocation of the resources.

### 2014-07-03 Report/system_model.tex
Updated ver_1
Satya corrections !

@@
 In order to detect  multiple spatial streams at the receiver, a receive beamforming vector \me{\mvec{w}{l,k,n}} is employed at each user.
-Consequently, the received signal of the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n^\mathrm{th}} at user $k$ is given by
+Consequently, the received data symbol corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n^\mathrm{th}} at user $k$ is given by
 \begin{equation}\label{eqn-1}
-y_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
+\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
 \end{equation}
@@
 \end{equation}
-where \me{t_k} denote the transmissions in bits and \me{[x]^+ = \max{ \lbrace x,0  \rbrace}}.
-The total number of transmitted bits for the user \me{k} is given by \me{t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i)},
-where \me{t_{l,k,n}} is the total number of bits that can be transmitted over \me{l^\mathrm{th}} spatial stream and on \me{n^\mathrm{th}} sub-channel at the \me{i^\mathrm{th}} instant.
+where \me{[x]^+ = \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the transmission in bits for user \me{k}. For \ac{MIMO} \ac{OFDM} system,
+\begin{equation}
+t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i),
+\end{equation}
+where \me{t_{l,k,n} = \log_2(1 + \gamma_{l,k,n})} corresponds to the maximum rate achieved by Gaussian signaling on \me{l^\mathrm{th}} spatial stream and over \me{n^\mathrm{th}} sub-channel for the \ac{SINR} of \me{\gamma_{l,k,n}}.
 Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-07-03 Report/joint_wsrm_formulation.tex
Update at home

@@
-The \ac{WSRM} technique is predominantly used to design the precoders for the \ac{MIMO} \ac{BC} channels to maximize the weighted sum throughput in the downlink direction.
-The weights are used to provide different priorities to the users based on the respective \ac{QoS} criterion.
-Since the objective of this work is concerned with the reduction of the number of queued packets, we use the total number of the queued packets for each user as the respective weights.
+The \ac{WSRM} technique is predominantly used to design the precoders for the \ac{MIMO} \ac{BC} scheme to maximize the weighted sum throughput for all users.
+The weights provide different priorities to the users based on their respective \ac{QoS} requirements.
+Since the objective of the current work is to reduce the total number of backlogged packets, the weights should be a function of the user queue sizes.
+
+the reduction of the number of queued packets, we use the total number of the queued packets for each user as the respective weights.
 Using the size of the queued packets as the corresponding weights is obtained from the well known algorithm, called the \textit{backpreassure algorithm}, which is used to decide the routing decisions for each node in the network to efficiently send the packets to the desired destination with minimal packet drops and delay.

### 2014-07-03 Report/problem_formulation_intro.tex
Update at home

@@
-In this paper, we address the problem of resource allocation across the \ac{MIMO} \ac{OFDM} framework, which are shared by the users served by multiple \acp{BS}.
-In order to minimize the queued packets, the precoders are to be designed in a way to overcome the problem of allocating the resources more than required.
-In order to satisfy this constraint, we use the queue deviation as the utility function as compared to the traditional \ac{WSRM} objective discussed extensively in the literature \cite{christensen2008weighted,wmmse_shi}.
-For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the packets available at the transmitter.
+In this paper, we address the problem of resource allocation across the \ac{MIMO} \ac{OFDM} framework, which are contended by the users served by multiple \acp{BS}.
+In order to minimize the number of queued packets, the precoders are designed to utilize the available space-frequency resources efficiently by limiting the over utilization of the same.
+In order to achieve this, we use the queue deviation utility as compared to the traditional \ac{WSRM} objective discussed extensively in the literature \cite{christensen2008weighted,wmmse_shi}.
+For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
 As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
@@
 
-The precoder design problem can be given minimizing the absolute value of the deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as \me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}.
-The exponent \me{q} plays a vital role in the final allocation, which will be discussed later.
-Now, the problem of weighted queued packet minimization formulated as a $q$-norm minimization, is given by
+The objective function for the precoder design problem is given by minimizing the absolute value of the queue deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as \me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}.
+With this objective, the problem of weighted queued packet minimization is given by the $q$-norm minimization as
 \begin{IEEEeqnarray}{rCl}\label{eqn-3}
-\underset{\substack{\mvec{m}{l,k,n},\\\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
+\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n}\\\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
 \text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
@@
 In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels.
-Before discussing the formulation in detail, we first discuss the existing algorithm to solve the current issue of minimizing the number of backlogged packets at the transmitter.
+Before discussing the solutions in detail, we discuss the existing algorithm to solve the issue of minimizing the number of backlogged packets with additional constraints required by problem.

### 2014-07-03 Report/queue_minimizing_intro.tex
Updated ver_1
Update at home

@@
-In this section, we discuss the precoder design solutions for the problem stated in Section \ref{sec-3.2}.
-To begin with, we discuss the existing solution and its extension to solve the current problem of resource allocation over multiple sub-channels.
-Then, we provide two different approaches to solve the \ac{JSFRA} precoder design problem to minimize the total number of backlogged packets.
-At the end of the section, we discuss a low complex solution for the \ac{JSFRA} problem by limiting the precoder design over each sub-channel at a given instant.
+% To begin with, we discuss the existing solution and its extension to solve the problem of resource allocation over multiple sub-channels.
+Then, we provide two approaches to solve the \ac{JSFRA} precoder design problem to minimize the total number of backlogged packets.
+At the end, we discuss a low complex solution for the \ac{JSFRA} problem by limiting the precoder design over each sub-channel at a given instant.
 
-In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is highly difficult due to the non-convex nature of the problem.
+In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is highly difficult due to the combinatorial and the non-convex nature of the problem.
 In addition to that, the objective of minimizing the number of the queued packets over the spatial and the sub-channel dimensions adds further complexity to the existing problem.

### 2014-07-03 Report/system_model.tex
Update at home

@@
 The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets or bits arriving for the user \me{k} at the \me{{i}^\mathrm{th}} instant.
-The total number of queued packets at the \me{{i}^\mathrm{th}} instant for the user \me{k} depend on the fresh arrivals at the \me{{i}^\mathrm{th}} instant and the total number of backlogged packets \me{Q_k(i-1)} as given by
+The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, represented by \me{Q_k(i+1)}, follows
 \begin{equation}
-Q_k(i) = \Big [ Q_k(i-1) - t_k(i-1) \Big ]^+ + \lambda_k(i),
+Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i),
 \label{eqn-2a}
 \end{equation}
-where \me{[x]^+ = \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the transmission in bits for user \me{k}. For \ac{MIMO} \ac{OFDM} system,
+where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the transmission in bits for user \me{k}. For a \ac{MIMO} \ac{OFDM} system,
 \begin{equation}
@@
 \end{equation}
-where \me{t_{l,k,n} = \log_2(1 + \gamma_{l,k,n})} corresponds to the maximum rate achieved by Gaussian signaling on \me{l^\mathrm{th}} spatial stream and over \me{n^\mathrm{th}} sub-channel for the \ac{SINR} of \me{\gamma_{l,k,n}}.
+where \me{t_{l,k,n}} denotes the transmitted bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
+The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{\log_2(1 + \gamma_{l,k,n})}\footnote{assuming Gaussian signaling} for a given \ac{SINR} of \me{\gamma_{l,k,n}}.
 Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-07-04 Report/joint_wsrm_formulation.tex
16.48 Jul 4 2014

--- 2014-07-03 Report/joint_wsrm_formulation.tex
@@
-The \ac{WSRM} technique is predominantly used to design the precoders for the \ac{MIMO} \ac{BC} channels to maximize the weighted sum throughput in the downlink direction.
-The weights are used to provide different priorities to the users based on the respective \ac{QoS} criterion.
-Since the objective of this work is concerned with the reduction of the number of queued packets, we use the total number of the queued packets for each user as the respective weights.
-Using the size of the queued packets as the corresponding weights is obtained from the well known algorithm, called the \textit{backpreassure algorithm}, which is used to decide the routing decisions for each node in the network to efficiently send the packets to the desired destination with minimal packet drops and delay.
-The backpreassure algorithm is the outcome of minimizing the Lyapunov drift \cite{neely2010stochastic} conditioned over the current queue states \me{\mbf{Q}(i - 1)}, where \me{\mbf{Q}} is the vector formed by stacking the number of queued packets of each user in the system.
-Assuming the queue length grows according to \eqref{eqn-2a} for all the users, the Lyapunov drift conditioned over the current queue state is given by
-\begin{equation} \label{eqn-3.1.0}
-\Delta(i) = \frac{1}{2} \, \sum_{k \in \mc{U}} \, \mathrm{E} \Big{[}  \left ( Q_k(i)^2 - Q_k(i-1)^2 \right ) \vert \, \mbf{Q}(i - 1) \Big{]},
+The queue minimizing algorithms are discussed extensively in the networking literature for providing congestion-free routing between any two nodes\footnote{refers to routers or PC's} in the network.
+It is achieved by finding a control policy considering the differential backlogs of the packets present in the source and the destination node, where control policy refers to the resource or rate allocation strategy.
+The control policy satisfying the condition is known as \emph{backpreassure algorithm}, discussed extensively in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
+The algorithm assumes the physical layer rate as a fixed entity due to the wired infrastructure.
+In order to use the algorithm in the wireless network, the user rate variable \me{t_{k}} should be modeled in accordance with the wireless backbone network.
+
+The \ac{Q-WSRM} scheme is formulated by extending the \emph{backpreassure algorithm} for the \ac{MIMO} \ac{OFDM} network, where multiple \acp{BS} acts like a source nodes and the user terminals as a receiver nodes.
+The user rate variables \me{t_k} are obtained by the design of the transmit and the receive precoders to maximize the weighted sum rate.
+The weights used in the precoder design algorithm should be a function of the number of backlogged packets corresponding to each user.
+In order find the weights, following the approach in \cite{neely2010stochastic}, we bound the Lyapunov function\footnote{\me{\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q^2_k(i)}} drift as
+\begin{IEEEeqnarray}{rCl}
+\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} &=& \frac{1}{2} \left [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \right ] \IEEEyessubnumber \label{eqn-3.1.0} \\
+&\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) }, \IEEEyessubnumber \label{drift-exp}
+\end{IEEEeqnarray}
+where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and the inequality is due to the upper bound
+\begin{equation}
+\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
 \end{equation}
-where the expectation is taken over all possible control\footnote{transmission rates} decisions made in accordance to the channel under consideration to minimize the total backlogged packets at a given instant.
-Now, by substituting \eqref{eqn-2a} in \eqref{eqn-3.1.0}, the resulting expression is given by
+Now the conditional Lyapunov drift for the instant \me{i} is given by
+\begin{IEEEeqnarray}{rCl}
+\Delta(\mbf{Q}(i)) &\triangleq& \mathbb{E} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+ &\leq& \mathbb{E} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) + \mathbb{E}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \IEEEyessubnumber
+\end{IEEEeqnarray}
+where the expectation depends on the control decisions made for the transmission variables \me{t_k} and the second term on the r.h.s is due to i.i.d assumption on the arrivals.
+We can bound the first term on the r.h.s by a constant \me{B} for all possible control actions taken for a given channel condition \cite{neely2010stochastic}, the resulting problem can be given as
 \begin{equation}
-\Delta(i) \leq \mathrm{E} \Big{[} \mbf{Q}(i-1) \left \lbrace \mbfa{\lambda}(i) - \mbf{t}(i) \right \rbrace | \mbf{Q}(i-1) \Big{]} + \frac{1}{2} \,\mathrm{E} \left [ \mbfa{\lambda}^2(i) | \mbf{Q}(i-1) \right ] + \frac{1}{2} \,\mathrm{E} \left [ \mbf{t}^2(i) | \mbf{Q}(i-1) \right ],
-\label{drift-exp}
-\end{equation}
-where \me{\mbfa{\lambda}} and \me{\mbf{t}} are the vectors formed by stacking the arrival and transmission of all users in the system and the inequality provides the upper bound\footnote{\me{\left ( \max{\Big [ \mbf{Q}(i-1) - \mbf{t}(i),0 \Big ] } + \mbfa{\lambda}(i) \right )^2 \leq \mbf{Q}^2(i-1) + \mbf{t}^2(i) + \mbfa{\lambda}^2(i) + 2 \, \mbf{Q}(i-1) \left ( \mbfa{\lambda}(i) - \mbf{t}(i) \right ) }} for the Lyapunov drift.
-
-The first term in \eqref{drift-exp} can be neglected from the optimization, since the arrivals are independent of the current queue state following \me{\mathrm{E} [ \mbf{Q}(i-1) \mbfa{\lambda}(i) | \mbf{Q}(i-1)] = \mbf{Q}(i-1)\mathrm{E} [\mbfa{\lambda}(i)] = \mbf{Q}(i-1)\mbf{A}(i)}.
-In the backpreassure algorithm, discussed in \cite{georgiadis2006resource,neely2010stochastic}, the second order terms are bounded by a constant \me{B}, \textit{i.e}, \me{\mathrm{E} \left [ \mbfa{\lambda}^2(i) | \mbf{Q}(i-1) \right ] + \mathrm{E} \left [ \mbf{t}^2(i) | \mbf{Q}(i-1) \right ] \leq B}.
-With this approximation, the resulting problem can be represented as
-\begin{equation}
-\underset{\mbf{t}(i)}{\text{minimize}} \sum_{k \in \mc{U}} \, Q_k(i-1) \: t_k(i).
+\underset{t_k}{\text{maximize}} \quad \sum_{k \in \mc{U}} \, Q_k(i) \, t_k(i),
 \label{backpreassure}
 \end{equation}
-In \eqref{backpreassure}, the expectation operator is dropped since it is maximized by maximizing the function inside it.
-Now from \eqref{backpreassure}, the optimization variables \me{\mbf{t}(i)}, which is the vectorized transmission rates, are to be identified for each user for the current slot \me{i}.
-Since the current system can exploit both space and frequency resources through \ac{MIMO} \ac{OFDM} model, the transmission rates \me{\mbf{t}(i)} for the current instant can be controlled using the transmit precoders \me{\mbf{M}_{k,n}} designed for each user over each sub-channel resource.
-Since the decision variables \me{\mbf{t}(i)} depends on the queue state at \me{\mbf{Q}(i - 1)}, we drop the time variable \me{i} for the easy representation.
-The above problem defined in \eqref{backpreassure} can be rewritten to include the space-frequency allocation variable, namely \me{\mbf{M}_{k,n}}, as
+where the expectation operator is dropped since it is maximized by maximizing the function inside in an opportunistic manner.
+
+Now the problem in \eqref{backpreassure} looks similar to the \ac{WSRM} problem if the weights are replaced by the number of backlogged packets corresponding to the users.
+The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
+In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}.
+With this, the \ac{Q-WSRM} problem for a wireless system is given by
 \begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
@@
 \end{IEEEeqnarray}
-where \eqref{eqn-3.1.4} is due to the \me{[x]^+} operation in \eqref{eqn-2a} and \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}.
+where the precoders are associated with the \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}.
 By using the number of queued packets as the weights, the resources can be allocated to the user with the more number of backlogged packets, which essentially does the allocation in a greedy manner.

### 2014-07-04 Report/kkt_mse_approach.tex
16.48 Jul 4 2014

@@
-In general, the distributed approaches presented in the earlier sections can be used to perform the precoder design problem in a decentralized way.
-One significant issue remains in both \acl{PD} and \ac{ADMM} apporaches is the update of the coupling variable.
-In both the methods, the coupling variables are updated by using the subgradients, which depends on the choice of the step size used for each update.
-In order to avoid the use of subgradient update for the coupling variables, the \ac{MSE} reformulation approach can be considered by solving the \ac{KKT} equations.
-Initial work on this approach is discussed extensively in \cite{wmmse_shi} for the \ac{WSRM} problem and \cite{kaleva2012weighted} considered the \ac{WSRM} problem with the additional \ac{QoS} constraints like minimum guaranteed rate requirements.
+In general, the distributed approaches presented in the earlier sections can be used to design the precoders in a decentralized way.
+The main issue affecting the convergence of the algorithm in both \acl{PD} and \ac{ADMM} apporaches is the update of the coupling variables using the step size.
+In order to avoid the use of subgradient update, the \ac{MSE} reformulation method is considered is studied extensively in the literature, such as, \cite{wmmse_shi} for the \ac{WSRM} problem and \cite{kaleva2012weighted} considered the \ac{WSRM} problem with the additional \ac{QoS} constraints like minimum guaranteed rate requirements.
 

### 2014-07-04 Report/problem_formulation_intro.tex
16.48 Jul 4 2014

@@
-In this paper, we address the problem of resource allocation across the \ac{MIMO} \ac{OFDM} framework, which are contended by the users served by multiple \acp{BS}.
+In this paper, we address the problem of resource allocation across the \ac{MIMO} \ac{OFDM} framework, in which the resources are contended by the \acp{BS} to empty the respective user queued packets.
 In order to minimize the number of queued packets, the precoders are designed to utilize the available space-frequency resources efficiently by limiting the over utilization of the same.
-In order to achieve this, we use the queue deviation utility as compared to the traditional \ac{WSRM} objective discussed extensively in the literature \cite{christensen2008weighted,wmmse_shi}.
+To achieve this, we use the queue deviation utility as compared to the traditional \ac{WSRM} objective discussed extensively in the literature \cite{christensen2008weighted,wmmse_shi}.
 For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
@@
 The objective function for the precoder design problem is given by minimizing the absolute value of the queue deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as \me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}.
-With this objective, the problem of weighted queued packet minimization is given by the $q$-norm minimization as
+With this objective, the problem of weighted queued packet minimization is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-3}
@@
 In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels.
-Before discussing the solutions in detail, we discuss the existing algorithm to solve the issue of minimizing the number of backlogged packets with additional constraints required by problem.
+Before discussing the proposed solutions, we consider the existing algorithm to solve the issue of minimizing the number of backlogged packets with additional constraints required by problem.

### 2014-07-04 Report/system_model.tex
16.48 Jul 4 2014

@@
 where \me{t_{l,k,n}} denotes the transmitted bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{\log_2(1 + \gamma_{l,k,n})}\footnote{assuming Gaussian signaling} for a given \ac{SINR} of \me{\gamma_{l,k,n}}.
+The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{\log_2(1 + \gamma_{l,k,n})}\footnote{assuming Gaussian signaling} for the \ac{SINR} of \me{\gamma_{l,k,n}}.
 Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-07-09 Report/dual_approach.tex
tempversion

@@
 \end{IEEEeqnarray}
-It can be seen from the objective \eqref{eqn-dual-2a} that the global interference \me{\mbfa{\zeta}(b_k)} can be dropped from the objective \eqref{eqn-dual-2a} without affecting the optimal solution, since it is constant for the subproblems.
+In \eqref{eqn-dual-2a}, the global interference variable \me{\mbfa{\zeta}(b_k)} is dropped without affecting the optimal solution, since it is fixed for a given iteration.
 The problem defined in \eqref{eqn-dual-2} can be decoupled to solve for the precoders at each \ac{BS} by using interference vector \me{\mbfa{\zeta}^{\set{b_k}}} as an optimization variable for the fixed interference price (dual variable) \me{\mbfa{\nu}^{\set{b_k}}}.

### 2014-07-09 Report/kkt_mse_approach.tex
tempversion

@@
 
-When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which then makes the problem difficult to solve in an iterative manner.
-But, in our formulation, since the rate constraint imposed by the number of queued packets waiting for the transmission in in the objective function, it provides an efficient apporach to solve the problem with the rate constraints.
-In this section, we provide an iterative precoder design for the \ac{JSFRA} formulation approached via \ac{MSE} reformulation as discussed in \ref{sec-3.3}.
-Even though the \ac{JSFRA} scheme using \ac{SCA} approach and the \ac{MSE} reformulation approach obtained the solutions by relaxing the nonconvex constraints by the half spaces, the structure of the \ac{MSE} reformulation problem allows us to decouple the problem readily without further approximations.
-
-In order to come up with the iterative solution, we need to find the \ac{KKT} equations for the the \ac{MSE} reformulation problem defined in \eqref{eqn-mse-2}.
-It can be seen that the objective function \eqref{eqn-mse-2.1} has the norm function, which requires the sum of absolute values of the vector entries raised to the power \me{q}.
+When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which makes the problem difficult to solve in an iterative approach.
+But, in the current method, the rate constraints imposed by the number of queued packets are implicitly present in the objective function, it eliminates the need of an additional rate constraints.
+The current formulation uses the \ac{MSE} approach to obtain the iterative algorithm for special scenarios due to the absolute operator in the objective function.
 Since the absolute of a function is not differentiable, the problem is usually solved by the subgradient approach.
-Since the subgradients are not unique and the selection of a subgradient and a step size are not guaranteed to be optimal, in this approach, we drop the absolute value operation for the queue deviation function so as to obtain a unique supporting vector.
-It is valid in the following special cases without affecting the optimal solution
+In order to solve the problem using the closed form equations, we drop the absolute value operator in the objective to obtain the differentiable equivalent.
+It is valid for the following two special cases, namely,
 \begin{itemize}

### 2014-07-10 Report/joint_wsrm_formulation.tex
modified for KKT MMSE

@@
-The queue minimizing algorithms are discussed extensively in the networking literature for providing congestion-free routing between any two nodes\footnote{refers to routers or PC's} in the network.
+The queue minimizing algorithms are discussed extensively in the networking literature for providing congestion-free routing between any two nodes\footnote{routers or user terminals} in the network.
 It is achieved by finding a control policy considering the differential backlogs of the packets present in the source and the destination node, where control policy refers to the resource or rate allocation strategy.
@@
 
-The \ac{Q-WSRM} scheme is formulated by extending the \emph{backpreassure algorithm} for the \ac{MIMO} \ac{OFDM} network, where multiple \acp{BS} acts like a source nodes and the user terminals as a receiver nodes.
+The \ac{Q-WSRM} scheme is formulated by extending the \emph{backpreassure algorithm} for the \ac{MIMO} \ac{OFDM} network, where multiple \acp{BS} act like a source nodes and the user terminals as a receiver nodes.
 The user rate variables \me{t_k} are obtained by the design of the transmit and the receive precoders to maximize the weighted sum rate.
 The weights used in the precoder design algorithm should be a function of the number of backlogged packets corresponding to each user.
-In order find the weights, following the approach in \cite{neely2010stochastic}, we bound the Lyapunov function\footnote{\me{\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q^2_k(i)}} drift as
-\begin{IEEEeqnarray}{rCl}
+In order to find the weights, we adopt the Lyapunov drift minimization as discussed in \cite{neely2010stochastic}, where the Lyapunov function is given by the squared sum of the number backlogged packets as
+\begin{equation}
+\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k(i),
+\end{equation}
+where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot.
+The Lyapunov function provides a measure of congestion in the system, as discussed in \cite[Ch.
+3]{neely2010stochastic}.
+Now the Lyapunov function drift is given by
+\begin{IEEEeqnarray}{rCl}\label{eqn-3.1}
 \mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} &=& \frac{1}{2} \left [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \right ] \IEEEyessubnumber \label{eqn-3.1.0} \\
@@
 \end{IEEEeqnarray}
-where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and the inequality is due to the upper bound
+where the inequality is due to the upper bound
 \begin{equation}
@@
 \end{equation}
-Now the conditional Lyapunov drift for the instant \me{i} is given by
+In order to minimize the number of backlogged packets at each instant, minimization of the Lyapunov drift \eqref{eqn-3.1} is carried over all possible control decisions in the form of transmission rates \me{t_k} to users in the system.
+The Lyapunov drift conditioned on the current backlogged packets \me{\mbfa{Q}(i)} is given by
 \begin{IEEEeqnarray}{rCl}
-\Delta(\mbf{Q}(i)) &\triangleq& \mathbb{E} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+\underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
  &\leq& \mathbb{E} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) + \mathbb{E}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \IEEEyessubnumber
 \end{IEEEeqnarray}
-where the expectation depends on the control decisions made for the transmission variables \me{t_k} and the second term on the r.h.s is due to i.i.d assumption on the arrivals.
+where the second term on the r.h.s is due to i.i.d assumption on the arrivals.
 We can bound the first term on the r.h.s by a constant \me{B} for all possible control actions taken for a given channel condition \cite{neely2010stochastic}, the resulting problem can be given as

### 2014-07-10 Report/kkt_mse_approach.tex
modified for KKT MMSE

@@
 &\hspace{0.5cm}& \quad {} + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
-\sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} = t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
+\sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \geq t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
 \delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
@@
 
-Now the Lagrangian of the problem expressed in \eqref{kkt-mse-1}, with the corresponding dual variables, is used obtain the \ac{KKT} expressions by partially differentiating with respect to the variables \me{t_{l,k,n}}, \me{\epsilon_{l,k,n}}, \me{m_{l,k,n}}, \me{w_{l,k,n}} and the dual variables \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b}.
-Since the problem of precoder design using \ac{MSE} reformulation is solved by the iterative method, we use the iteration index \me{i} in the superscript to represent the variables at the respective iteration instants.
-The discussions on the \ac{KKT} expressions are provided in the  Appendix \ref{a-1}.
-Upon solving the \ac{KKT} expressions, we obtain the following iterative solution with the variables update as
+Now the Lagrangian of the problem expressed in \eqref{kkt-mse-1}, with the corresponding dual variables, is used obtain the \ac{KKT} expressions by partially differentiating with respect to the primal variables \me{t_{l,k,n}}, \me{\epsilon_{l,k,n}}, \me{m_{l,k,n}}, \me{w_{l,k,n}} and the dual variables \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b}.
+Since the precoder design is solved in an iterative fashion, the superscript \me{(i)} denotes the iteration instants.
+The detailed \ac{KKT} expressions are provided in the  Appendix \ref{a-1}.
+Upon solving the \ac{KKT} expressions, we obtain the following iterative solution as
 \begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
-\alpha^{(i)}_{l,k,n} &=& \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.1} \\
-\sigma_{l,k,n}^{(i)} &=& \dfrac{q \left [ a_k \, \left (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i-1)} \right )^{(q-1)} \right ]}{\log(2)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
-\mvec{m}{l,k,n}^{(i)} &=& \left ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \right )^{-1} \alpha^{(i)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \\ \nonumber
-&+& \quad  N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2,\quad \forall k \in \mc{U}, \forall n \in \mc{C} \IEEEyessubnumber \label{kkt-mse-4.4} \\
+\mvec{m}{l,k,n}^{(i)} &=& \left ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \right )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \right ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}, \IEEEyessubnumber \label{kkt-mse-4.6} \\
+\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2, \IEEEyessubnumber \label{kkt-mse-4.4} \\
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \sum_{(x,y) \neq (l,k)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i-1)} \mvec{m}{x,y,n}^{\herm \, (i-1)} \mvec{H}{b_{y},k,n}^\herm + \mathbf{I}_{N_R} \right ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i-1)}, \IEEEyessubnumber \label{kkt-mse-4.6}
+\sigma_{l,k,n}^{(i)} &=& q \,a_k \, \log_2(e)  \, \left (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \right )^{(q-1)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \frac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ), \IEEEyessubnumber \label{kkt-mse-4.1}
 \end{IEEEeqnarray}
 \me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}}.
+The dual variable \me{\alpha^{(i)}} is updated with the memory to avoid any oscillations due to the over allocation of the resources.
+The step size \me{\rho} is used to reduce the effect on the precoder designs on the excess allocations.
 
-The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the \ac{MSE} variables \me{\epsilon_{l,k,n}^{(0)}} and the throughput variables \me{t_{l,k,n}^{(0)}} randomly.
-It can be initiated by solving \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} for a random transmit precoders \me{\mbf{M}_{k,n}} satisfying \eqref{kkt-mse-1.4}.
-It can be noted that the proposed iterative algorithm converges faster than the \acl{PD} and the \ac{ADMM} approach\footnote{from our simulations}, since the later schemes are based on the subgradient approach and the former one achieves the \ac{KKT} points at each iteration.
-In \eqref{kkt-mse-4}, all expressions provide the closed form solution for the respective variables except the transmit precoders in \eqref{kkt-mse-4.3}, which depends on the variable \me{\delta_b}.
-It can be seen that the variable \me{\delta_b} are associated only to the \ac{BS} \me{b}, which can be efficiently solved by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
-After each iteration instant, the transmit and the receive precoders are exchanged across the coordinating \acp{BS} in \me{\mc{B}} in order to reach the optimal point in the next iteration.
+The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors.
+The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to provide equal priorities to all streams.
+With the initial values, the closed form solutions mentioned in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to certain accuracy.
+In \eqref{kkt-mse-4}, all expressions are provided in a closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depends on the \ac{BS} specific dual variable \me{\delta_b}.
+It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
+After each iteration instant, the transmit and the receive precoders are exchanged across the coordinating \acp{BS} in \me{\mc{B}} to obtain the next operating point.
 

### 2014-07-10 Report/mse_formulation.tex
modified for KKT MMSE

@@
-In this section, we provide an alternative formulation for the \ac{QM} \ac{JSFRA} scheme using the \ac{MSE} equivalence with the capacity as in \cite{wmmse_shi,kaleva2012weighted} for the \ac{WSRM} problem.
-The proposed formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} expression for decoding the transmitted symbols using \ac{MMSE} receivers and \me{C} being the capacity of the system.
+In this section, we use an alternative formulation for the \acl{QM} \ac{JSFRA} scheme using the \ac{MSE} equivalence with the capacity as in \cite{christensen2008weighted,wmmse_shi} for the \ac{WSRM} problem.
+The proposed formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )} \cite{viswanath1999optimal,mse_duality}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} expression for decoding the transmitted symbols using \ac{MMSE} receivers and \me{C} being the capacity of the system.
 Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.

### 2014-07-10 Report/problem_formulation.tex
modified for KKT MMSE

@@
-The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant term.
-It can be seen that \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{q=2} as
+The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant value.
+Eq.
+\eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{q=2} as
 \begin{equation}\label{pf-1}
@@
 \end{equation}
-It can seen that \eqref{pf-1} is equivalent to the \eqref{backpreassure} algorithm when we ignore the second order terms from \eqref{pf-1}.
-It can be seen that by dropping the second order term from the \ac{Q-WSRM} formulation, we require an explicit rate constraint \eqref{eqn-3.1.4} to limit the allocations beyond the respective user requirements.
+It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure} when we ignore the second order terms from \eqref{pf-1}.
+Limiting \me{t_k^2} by a constant value, imposes the additional rate constraint \eqref{eqn-3.1.4} in the \ac{Q-WSRM} formulation to avoid the resource wastage in the form of over allocation.
 In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself.
-Since the objective is to minimize the number of queued packets, the sub-channels are coupled in this formulation as compared to the traditional \ac{WSRM} objective eventhough the interference from the adjacent sub-channels are zero (due to the \ac{OFDM} scheme).
-The queue deviation objective provides an alternate and more complete way to perform the resource allocation as compared to the \eqref{q_gen_sum} approach.
+In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achive an efficient allocation by identifying the optimal space-frequency resource for each user in the system.
+The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \eqref{q_gen_sum} approach.
 
-Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{q}-norm in the objective of \eqref{eqn-3}.
+Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}.
 As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
@@
 Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained.
-We comment on the choice of  the norm \me{q} on the objective as below \cite{berry2004cross,qps_cioffi}.
+We comment on the choice of  the \me{\ell_q} on the objective as below \cite{berry2004cross,qps_cioffi}.
 \begin{itemize}

### 2014-07-10 Report/simulation_distributed.tex
ver_0.0.1
16.48 Jul 4 2014
modified for KKT MMSE

@@
 \end{subfigure}
-\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,12,1 \rbrace} model}
+\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
 \label{fig-d-1}
@@
 The performance degradation is due to the unconstrained rate increase for the users beyond their actual number of queued packets available to transmit.
-Since the objective uses the norm-\me{1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user.
+Since the objective uses the \me{\ell_1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user.
 The number of queued packets are initialized in a way to analyze the effect of the unconstrained behavior in the \ac{KKT} scheme.
@@
 It can be seen that the \ac{KKT} based approach performs similar to the optimization problem given in \eqref{eqn-9}, which is solved using the solver \cite{grant2008cvx}.
-In the two norm case, the objective is differentiable and hence can be differentiable for any number of queued packets as compared to the one norm case requiring larger queue sizes in order to drop the absolute function occurring in the norm function.
+In the \me{\ell_2} case, the objective is differentiable and hence can be differentiable for any number of queued packets as compared to the \me{\ell_1} case requiring larger queue sizes in order to drop the absolute function occurring in the norm operator.
 The performance of the closed form solution using the \ac{KKT} solution achieves similar performance without allocating rates beyond the available queued packets.
-In order to bring out the performance difference, one norm objective plot is also provided in Fig.
+In order to bring out the performance difference, \me{\ell_1} objective plot is also provided in Fig.
 \ref{fig-d-3} providing better reduction in the number of queued packets in the current transmission slot.
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{queues_6_3_12}
+\includegraphics[width=\textwidth]{fig-7}
 \caption{Queue deviation}
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{rate_6_3_12}
+\includegraphics[width=\textwidth]{fig-8}
 \caption{Sum rate performance}
 \end{subfigure}
-\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
+%\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
+\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}
 \label{fig-d-3}

### 2014-07-10 Report/system_model.tex
modified for KKT MMSE

@@
 where \me{t_{l,k,n}} denotes the transmitted bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{\log_2(1 + \gamma_{l,k,n})}\footnote{assuming Gaussian signaling} for the \ac{SINR} of \me{\gamma_{l,k,n}}.
+The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{\log_2(1 + \gamma_{l,k,n})}\footnote{Gaussian signaling assumption} for the \ac{SINR} of \me{\gamma_{l,k,n}}.
 Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-07-10 Report/wsrm_formulation.tex
Updated on 16.47:Jul-2
modified for KKT MMSE

@@
 \begin{IEEEeqnarray}{rCl}\label{eqn-9}
-\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
+\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
 \text{subject to} & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
@@
 
-The proposed algorithm is referred as \ac{QM} \ac{JSFRA} scheme with a sum power constraint which is outlined in Algorithm \ref{algo-1}.
+The proposed algorithm is referred as \ac{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint which is outlined in Algorithm \ref{algo-1}.
 The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
@@
 In this problem, we used alternating optimization with \ac{SCA} method, which provides monotonic convergence since the objective is improved at each step \textit{i.e} \me{f^{(i)} \geq f^{(i+1)}}, assuming \me{f^{(i)}} is the objective function at the \me{i^\mathrm{th}} \ac{SCA} iteration.
-For a fixed receive beamformers, the problem is guaranteed to converge to a \ac{KKT} point at each \ac{SCA} iteration as discussed in \cite{tran2012fast}.
+For a fixed receive beamformers, the problem is guaranteed to converge to a \ac{KKT} point at each \ac{SCA} points as discussed in \cite{marks1978technical}.
 Now, by alternating the transmit and the receive precoders, we perform \ac{BCDM}, which provides monotonic convergence of the objective.

### 2014-07-11 Report/dual_approach.tex
Updated MSE KKT

@@
-In contrast to the \acl{PD} problem, the \acf{DD} performs the distributed precoder design by relaxing the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{tolli2011decentralized,palomar2006tutorial}.
-In order to decouple the problem \eqref{eqn-decent-1}, the global coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the local copies at each \ac{BS} \me{b} denoted by \me{\zeta^{\set{b}}_{l,k,n,b}, \fall b\in \mc{B}}, which is then used in the problem as an optimization variable.
-
-Let  \me{\mbfa{\zeta}^{\set{b_k}}} be the locally maintained vector formed by stacking the interference entries relevant to the \ac{BS} \me{b_k}.
-Let \me{\mbfa{\zeta}} be the global interference entries of all \acp{BS} in the set \me{\mc{B}} stacked as a vector as
+In contrast to the \acl{PD} problem, the \acf{DD} relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
+In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution.
+Now the sub problems are coupled by the global consensus vector \me{\mbfa{\zeta}} maintaining the complete stacked  interference profile of all users in the system as
 \begin{IEEEeqnarray}{rCl}
@@
 &\quad& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \IEEEyessubnumber \\
-n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |, \IEEEyessubnumber
+n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
 \end{IEEEeqnarray}
-where \me{\mbfa{\zeta}(b_k)} denote the entries corresponding to the \ac{BS} \me{b_k} and the vector \me{\mbfa{\nu}^{\set{b_k}}} stacks the dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)}.
-The equality constraint for the local and the global interference vector \me{\zeta^{\set{b_k}}_{l,k,n,b} = \zeta_{l,k,n,b}, \fall b \in \bar{\mc{B}}_{b_k}, k \in \mc{U}} and \me{\forall k \in \bar{\mc{U}}_{b_k}, b=b_k} is relaxed by the partial Lagrangian in the objective as
+
+Let \me{\mbfa{\zeta}(b_k)} denotes the consensus entries corresponding to the \ac{BS} \me{b_k}.
+Let \me{\mbfa{\nu}^{\set{b_k}}} represents the stacked dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} used in the subproblems.
+The equality constraint for the local and the consensus interference vector \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} present in each subproblem is relaxed by the taking the partial Lagrangian for the constraint as
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-2} \label{eqn-dual-1}
@@
 \end{IEEEeqnarray}
-In \eqref{eqn-dual-2a}, the global interference variable \me{\mbfa{\zeta}(b_k)} is dropped without affecting the optimal solution, since it is fixed for a given iteration.
-The problem defined in \eqref{eqn-dual-2} can be decoupled to solve for the precoders at each \ac{BS} by using interference vector \me{\mbfa{\zeta}^{\set{b_k}}} as an optimization variable for the fixed interference price (dual variable) \me{\mbfa{\nu}^{\set{b_k}}}.
-In the current work, we consider the robust counterpart of the \acl{DD} scheme, namely \ac{ADMM} approach, which doesn't require any assumptions on the convexity of the functions for convergence \cite{boyd2011distributed}.
+The global interference variable \me{\mbfa{\zeta}(b_k)} in \eqref{eqn-dual-2a} can be dropped without affecting the optimal solution, since it is fixed for a given iteration.
+Instead of solving the dual decomposition problem defined in \eqref{eqn-dual-2}, we consider the \ac{ADMM} scheme which has better convergence properties as discussed in \cite{bertsekas1999nonlinear,boyd2011distributed}.
 
-In order to bound the interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} and \me{\zeta^{\set{b}}_{l,k,n,b}} between the \acp{BS} \me{b_k} and \me{b}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation to the objective function \cite{bertsekas1999nonlinear,boyd2011distributed}.
-At the optimal point, the actual and the assumed (local) interference values will be equal and provides no contribution to the objective function.
-It can be shown that the optimal step size is equal to the scaling factor \me{\rho} used for the penalty term in the objective function \cite{bertsekas1999nonlinear,boyd2011distributed}.
+In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} at the \acp{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} to the objective function.
+At optimality, the locally assumed and the consensus interference values will be equal,  providing no contribution to the objective function.
+The optimal step size use to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed}.
 Now, the subproblem at each \ac{BS} for the \me{\ith{i}} iteration is give by
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \zeta^{\set{b_k}(i)}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}(i)}T} \mbfa{\zeta}^{\set{b_k}(i)} + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i)}(b_k)}_{\text{global iterate}} - \underbrace{\mbfa{\zeta}^{\set{b_k}(i)}}_{\text{local iterate}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \zeta^{\set{b_k}(i)}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}(i-1)}T} \mbfa{\zeta}^{\set{b_k}(i)} + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i-1)}(b_k)}_{\text{consensus values}} - \underbrace{\mbfa{\zeta}^{\set{b_k}(i)}}_{\text{local values}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
 \text{subject to} & \quad & \eqref{eqn-dual-1d} - \eqref{eqn-dual-1f} \IEEEyessubnumber \label{eqn-dual-3b},
 \end{IEEEeqnarray}
-where \me{(i)} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.
+where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i-1)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.
 
-Once the local problems are solved at each \ac{BS}, the update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} can be performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}.
+Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}.
 Since the entries in \me{\mbfa{\zeta}^{(i)}} relates exactly two \acp{BS} only, each entry in the \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS} only.
-For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i-1)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by the \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b}} as
+For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by the \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
 \begin{equation}
-\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i-1)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
+\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
 \label{zeta_update}
@@
 \begin{equation}\label{dual-sg-update}
-\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i-1)}_{l,k,n,b} - \zeta^{\set{b}(i-1)}_{l,k,n,b} \right ), \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}.
+\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ), \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}.
 \end{equation}

### 2014-07-11 Report/kkt_mse_approach.tex
Updated MSE KKT

@@
-In general, the distributed approaches presented in the earlier sections can be used to design the precoders in a decentralized way.
-The main issue affecting the convergence of the algorithm in both \acl{PD} and \ac{ADMM} apporaches is the update of the coupling variables using the step size.
-In order to avoid the use of subgradient update, the \ac{MSE} reformulation method is considered is studied extensively in the literature, such as, \cite{wmmse_shi} for the \ac{WSRM} problem and \cite{kaleva2012weighted} considered the \ac{WSRM} problem with the additional \ac{QoS} constraints like minimum guaranteed rate requirements.
+The distributed solutions via primal and \ac{ADMM} approaches depend on the subgradient update by using a step size parameter for the coupling variables, which affects the speed of convergence to the optimal value.
+In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by solving the \ac{KKT} conditions.
+Simimar work has been considered for the \ac{WSRM} problem with the rate constraints in \cite{kaleva2012weighted}.
+When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which makes the problem difficult to solve in an iterative approach as in \cite{kaleva2012weighted}.
 
-When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which makes the problem difficult to solve in an iterative approach.
-But, in the current method, the rate constraints imposed by the number of queued packets are implicitly present in the objective function, it eliminates the need of an additional rate constraints.
-The current formulation uses the \ac{MSE} approach to obtain the iterative algorithm for special scenarios due to the absolute operator in the objective function.
-Since the absolute of a function is not differentiable, the problem is usually solved by the subgradient approach.
-In order to solve the problem using the closed form equations, we drop the absolute value operator in the objective to obtain the differentiable equivalent.
-It is valid for the following two special cases, namely,
+Even though the rate constraints are implicitly present in the objective function, we cannot formulate the \ac{KKT} conditions readily due to the non-differentiable objective function.
+The non-differentiability of the objective function is due to the absolute operator present in the norm function.
+In order to make the objective function differentiable, we consider the following case for which the absolute operator can be ignored without affecting the optimal solution, namely,
 \begin{itemize}
 \item when the exponent \me{q} is even or,
-\item when the number of backlogged packets for each user is larger than the available resources for the transmission \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
+\item when the number of backlogged packets of each user is large enough \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator.
 \end{itemize}
-The first condition is required for the iterative design, since the objective function needs to be differentiable to find the \ac{KKT} equations.
-So, when the exponent \me{q} is even, the absolute operator can be dropped from the objective function without any change in the optimal solution for any number of queued packets.
 
-By removing the absolute value operator from \eqref{eqn-mse-2}, the problem can be rewritten as
+With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
 \begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
-\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \alpha_{l,k,n}, \\ \delta_{b},\sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \left ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
+\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \alpha_{l,k,n}, \\ \delta_{b},\sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
@@
 where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.
-The equality condition is used for \eqref{kkt-mse-1.2} and \eqref{kkt-mse-1.3}, since the variables \me{\epsilon_{l,k,n}} and \me{t_{l,k,n}} are used for the corresponding expressions on the other side.
+The equality of \eqref{kkt-mse-1.2} is due to the equivalence of the \ac{MSE} expression with the transmit and the receive precoders.
 
-Now the Lagrangian of the problem expressed in \eqref{kkt-mse-1}, with the corresponding dual variables, is used obtain the \ac{KKT} expressions by partially differentiating with respect to the primal variables \me{t_{l,k,n}}, \me{\epsilon_{l,k,n}}, \me{m_{l,k,n}}, \me{w_{l,k,n}} and the dual variables \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b}.
-Since the precoder design is solved in an iterative fashion, the superscript \me{(i)} denotes the iteration instants.
-The detailed \ac{KKT} expressions are provided in the  Appendix \ref{a-1}.
-Upon solving the \ac{KKT} expressions, we obtain the following iterative solution as
+By forming the Lagrangian of \eqref{kkt-mse-1} with the corresponding dual variables as shown in \eqref{kkt-mse-1}, we can obtain the \ac{KKT} expressions by differentiating with respect to the variables present in the problem as detailed in Appendix \ref{a-1}.
+Upon solving the \ac{KKT} expressions, the iterative solution \me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}} is given by
 \begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
-\mvec{m}{l,k,n}^{(i)} &=& \left ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \right )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \right ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}, \IEEEyessubnumber \label{kkt-mse-4.6} \\
+\mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
+\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}, \IEEEyessubnumber \label{kkt-mse-4.6} \\
 \epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2, \IEEEyessubnumber \label{kkt-mse-4.4} \\
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\sigma_{l,k,n}^{(i)} &=& q \,a_k \, \log_2(e)  \, \left (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \right )^{(q-1)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
-\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \frac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ), \IEEEyessubnumber \label{kkt-mse-4.1}
+\sigma_{l,k,n}^{(i)} &=& q \,a_k \, \log_2(e)  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \Big ( \rfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \Big ). \IEEEyessubnumber \label{kkt-mse-4.1}
 \end{IEEEeqnarray}
-\me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}}.
-The dual variable \me{\alpha^{(i)}} is updated with the memory to avoid any oscillations due to the over allocation of the resources.
-The step size \me{\rho} is used to reduce the effect on the precoder designs on the excess allocations.
+The dual variable \me{\alpha^{(i)}} is updated with memory as in \eqref{kkt-mse-4.1} to avoid abrupt oscillations due to \me{\sigma < 0} from \eqref{kkt-mse-4.2} when \me{Q_k < \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
+The parameter \me{\rho \in [0,1]} provides a linear combination of the previous to the current value of the dual variable, dictating system reaction for the excess allocation.
 
@@
 The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to provide equal priorities to all streams.
-With the initial values, the closed form solutions mentioned in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to certain accuracy.
-In \eqref{kkt-mse-4}, all expressions are provided in a closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depends on the \ac{BS} specific dual variable \me{\delta_b}.
+Now, the closed form expressions in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to a certain accuracy.
+In \eqref{kkt-mse-4}, all expressions are in closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depends on the \ac{BS} specific dual variable \me{\delta_b}.
 It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=1} and the transmit precoders \me{\mbf{m}^{(0)}_{l,k,n}} randomly satisfying the power constraint \eqref{kkt-mse-1.4}}
- \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly, \me{\mvec{w}{l,k,n}^{(0)}} with \eqref{kkt-mse-4.6} and \me{{t}_{l,k,n}^{(0)}} using \eqref{kkt-mse-4.5}}
+ \KwInit{\me{i=1} and the receive beamformers \me{\mbf{w}^{(0)}_{l,k,n}} randomly}
+ \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
  set the maximum iteration counter \me{I_{\max}} to a valid number \;
@@
  \Repeat{convergence or \me{i \geq I_{\max}}}{
+	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} with \me{\delta_b} using \eqref{kkt-mse-4.3} by the bisection method satisfying \eqref{kkt-mse-1.4} \;
+	evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(i)}} by \eqref{kkt-mse-4.6} \;
+	update the \ac{MSE} variable \me{\epsilon_{l,k,n}^{(i)}} and the throughput variable \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} \;
 	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2} \;
-	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} with \me{\delta_b} using \eqref{kkt-mse-4.3} by the bisection method satisfying \eqref{kkt-mse-1.4} \;
-	update the \ac{MSE} variable \me{\epsilon_{l,k,n}^{(i)}} and the throughput variable \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} \;
-	evaluate the receive beamforming vector \me{\mvec{W}{k,n}} by \eqref{kkt-mse-4.6} \;
 	exchange the transmit and the receive precoders \me{\mvec{M}{k,n}^{(i)}, \mvec{W}{k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} \;

### 2014-07-14 Report/dual_approach.tex
updated kkt,wsrm,admm,primal

@@
 \text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{\set{b_k}}_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-dual-1d} \\
+&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{\set{b_k}}_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-dual-1d} \\
 && \zeta^{\set{b_k}}_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-dual-1e} \\

### 2014-07-14 Report/ieee_journal.tex
ver_0.0.1
Updated ver_1
Updated on 16.47:Jul-2
17.28:00 Jul-03-2014
Update at home
updated kkt,wsrm,admm,primal

@@
-\documentclass[10pt,letterpaper,journal,onecolumn]{./../Styles/IEEEtran}
+\documentclass[11pt,draftcls,onecolumn]{./../Styles/IEEEtran}
 
@@
 \usepackage{caption,subcaption}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e}
+\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools}
 
-\graphicspath{{./../Figures/}}
+\graphicspath{{./../Figures/}{./../Figures/Linux/}}
 \DeclareGraphicsExtensions{.eps}
@@
 \subsection{Problem Formulation} \label{sec-3.2}
-\input{problem_formulation}
+\input{problem_formulation_intro}
 
@@
 
-\subsection{\ac{JSFRA} scheme via Successive Convex Approximation (\acs{SCA})}
+\subsection{\acs{JSFRA} scheme via Successive Convex Approximation (\acs{SCA})}
+\input{problem_formulation}
 \input{wsrm_formulation}
@@
 
+\section{\acl{PD} approach} \label{a-2}
+\input{primal_approach_appendix}
+
 \section{\ac{KKT} expressions for the Distributed MSE Formulation} \label{a-1}

### 2014-07-14 Report/joint_wsrm_formulation.tex
updated kkt,wsrm,admm,primal

@@
 The algorithm assumes the physical layer rate as a fixed entity due to the wired infrastructure.
-In order to use the algorithm in the wireless network, the user rate variable \me{t_{k}} should be modeled in accordance with the wireless backbone network.
+In order to use the algorithm in the wireless network, the user rate variable \me{t_{k}} should be modeled in accordance with the wireless network.
 
-The \ac{Q-WSRM} scheme is formulated by extending the \emph{backpreassure algorithm} for the \ac{MIMO} \ac{OFDM} network, where multiple \acp{BS} act like a source nodes and the user terminals as a receiver nodes.
+The \ac{Q-WSRM} scheme is formulated by extending the \emph{backpreassure algorithm}\footnote{even though, the algorithm's objective is to provide congestion free transmission, we use this scheme for the comparison purpose} for the \ac{MIMO} \ac{OFDM} network, where multiple \acp{BS} acts like a source nodes and the user terminals as a receiver nodes.
 The user rate variables \me{t_k} are obtained by the design of the transmit and the receive precoders to maximize the weighted sum rate.

### 2014-07-14 Report/mse_formulation.tex
updated kkt,wsrm,admm,primal

--- 2014-07-02 Report/mse_formulation.tex
@@
-In this section, we provide an alternative formulation for the \ac{QM} \ac{JSFRA} scheme using the \ac{MSE} equivalence with the capacity as in \cite{wmmse_shi,kaleva2012weighted} for the \ac{WSRM} problem.
-The proposed formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} expression for decoding the transmitted symbols using \ac{MMSE} receivers and \me{C} being the capacity of the system.
+In this section, we present an alternative formulation for the \acl{QM} \ac{JSFRA} scheme by using the \ac{MSE} equivalence with the capacity as in \cite{christensen2008weighted,wmmse_shi} for the \ac{WSRM} problem.
+The current formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )} \cite{viswanath1999optimal,mse_duality}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} for decoding the transmitted symbols using the \ac{MMSE} receivers and \me{C} is the maximum achievable capacity for a given \ac{SINR} of \me{\gamma}.
 Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.
 Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
-\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
-\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
-\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
-& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
-&\quad& \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
+\begin{IEEEeqnarray}{LL}\label{eqn-mse-1}
+\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
+\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
+ & \quad \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
+& \quad \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
 \end{IEEEeqnarray}
@@
 \text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
-& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(j,i) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
+& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
 \end{IEEEeqnarray}

### 2014-07-14 Report/primal_approach_appendix.tex
updated kkt,wsrm,admm,primal

@@
 && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0 \IEEEyessubnumber \label{eqn-primal-1d} \\
+&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-primal-1d} \\
 && \zeta_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-primal-1e} \\

### 2014-07-14 Report/problem_formulation.tex
updated kkt,wsrm,admm,primal

@@
 Eq.
-\eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{q=2} as
+\eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
 \begin{equation}\label{pf-1}
@@
 Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained.
-We comment on the choice of  the \me{\ell_q} on the objective as below \cite{berry2004cross,qps_cioffi}.
+The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
 \begin{itemize}
-\item With \me{q = 1}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
+\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
 As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
-\item With \me{q = 2}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
+\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
 For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
-\item With \(q = \infty \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
+\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
 \end{itemize}

### 2014-07-14 Report/sub_channel_wsrm.tex
updated kkt,wsrm,admm,primal

@@
-The complexity involved in the \ac{JSFRA} scheme scales up significantly based on the sub-channel over which the decision has to be made.
-Not only the complexity, but also the convergence speed depends on the size  and the number of decision variables involved in the optimization problem.
-In order to reduce the complexity involved in the \ac{JSFRA} scheme, we provide an alternative sub-optimal solution, where the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits into consideration.
-It provides an alternative way to the parallel sub-channel wise precoder update using the decomposition techniques discussed in \cite{palomar2006tutorial,boyd2011distributed}.
+The complexity involved in the \ac{JSFRA} scheme scales significantly with the increase in the number of sub-channels considered in the formulation.
+In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size.
+In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the reamining number of queued bits in the formulation.
+It provides a sub-optimal solution to the optimal way of distributing the sub-channel wise precoder design via primal/dual decomposition methods discussed in \cite{palomar2006tutorial,boyd2011distributed}.
 
-The proposed \acf{QM} \ac{SRA} scheme decouples the fixing the power across each sub-channel to a constant value as compared to the global power constraint defined by \eqref{eqn-4.3}.
-In contrast to the decomposition based approach for sub-channel wise resource allocation, this method requires the update on the number of queued bits before each sub-channel level optimization.
-In this approach, the number of queued bits are updated by the difference between the total number of queued bits during the current slot and the total number of bits that are guaranteed by the earlier sub-channel wise allocations in the same slot as
+The proposed \acf{QM} \ac{SRA} scheme decouples the problem by fixing the power across each sub-channel to a constant value as compared to the global power constraint defined by \eqref{eqn-4.3}.
+In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel level optimization.
+The number of queued bits for each user are updated by the difference between the total number of queued bits during the current slot to the total number of bits that are guaranteed by the earlier sub-channel wise allocations in the same slot as
 \begin{equation}

### 2014-07-14 Report/wsrm_formulation.tex
updated kkt,wsrm,admm,primal

@@
 \text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}),\IEEEyessubnumber \label{eqn-6.2} \\
-  & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-6.3} \\
+  & \quad & \beta_{l,k,n} \geq  N_0 \|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-6.3} \\
   & \quad &\eqref{eqn-4.3} \IEEEyessubnumber
@@
 \mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}, \IEEEyessubnumber \\
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + \mathbf{I}_{N_R}, \IEEEyessubnumber
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R}, \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 \underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
+\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0\|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
 & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\

### 2014-07-15 Report/introduction.tex
updated intro

@@
-We consider the problem of resource allocation for a multi-cell \ac{MU-MIMO} transmission over an \ac{OFDM} system with the objective of minimizing the total number of backlogged packets of all users at a given instant.
-The available space and frequency resources in the considered system are shared among the users by \ac{BS} cooperation in order to minimize the number of packets waiting for transmission from each \ac{BS} to the respective users.
-In this paper, beamforming technique is utilized at \acp{BS} and linear single-user detection is employed at each receiver, i.e., the inter-user interference is treated as background noise.
+The last mile wireless connectivity poses significant bottleneck in the overall data traffic in the interconnected networks.
+The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which is proportional to the battery drain.
+In order to over come the receiver complexity, \ac{OFDM} based transmissions are introduced for the wideband transmissions.
+To improve the data rate, multiple antennas are installed at the \ac{BS} and at the user terminals to avail the additional freedom in the form of spatial dimension.
+The inclusion of \ac{MIMO} technique in the wireless network provides increased data rate or lower outage for the same transmission power and the channel use.
+
+In a network with multiple \acp{BS} serving multiple users (\acs{MU}), the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
+These available packets are transmitted over the shared wireless resources in an efficient manner with the various system constraints.
+In this work, we consider the user allocation over the space-frequency resources provided by the \ac{MU-MIMO} \ac{OFDM} framework in the downlink broadcast transmission to reduce the number of queued packets corresponding to the users at the \acp{BS}.
+Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, the problem can be considered as a resource allocation to minimize the number of backlogged packets at the \acp{BS}.
+
+In general, the resource allocation problems are solved by assigning a binary variable to each user indicating the presence or the absence on a particular resource.
+In contrast to that, we use the transmit beamformers, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource.
+The purpose of using the transmit beamformers for the scheduling is two fold.
+Firstly, it determines the transmission rate on a certain resource and secondly, by making the transmit beamformer to be a zero vector, the corresponding user will not be scheduled on a certain resource.
 The queue minimizing network optimization objective is used to design beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
@@
 
-Many existing beamformer designs for similar system models addresses the problem of \ac{WSRM} objective.
+The queue minimizing precoder designs are nothing but the \ac{WSRM} problem with the additional rate constraint determined by the number of backlogged packets for each user in the system.
+The topic of \ac{MIMO} \ac{BC} precoder design has been studied extensively with different performance criteria in the literature.
+Due to the nonconvex nature of the linear \ac{MIMO} \ac{BC} precoder design problem, it is solved by the sequence of approximated convex problems.
+In \cite{sin_algorithm}, the \ac{MIMO} rate expression is linearized around a fixed point in order to solve the \ac{DC} problem as a concave maximization problem in an iterative manner.
+Similar approach of solving the \ac{WSRM} problem via arithmetic-geometric inequality is proposed in \cite{tran2012fast}, providing better convergence rate compared to the former.
+
+The relation between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} are also used to solve the \ac{WSRM} objective.
+In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MMSE}, casting the problem as a convex one for fixed \ac{MMSE} receivers.
+In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders.
+Then the problem is solved using an alternating optimization method, i.e., finding a set of variables while the remaining others are fixed.
+Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} objective are solved via \ac{MSE} reformulation in \cite{kaleva2013primal}.
+
+The problem of precoder design for the \ac{MIMO} \ac{BC} system are solved either by using the centralized controller or at each \ac{BS} independently by exchanging limited information via backhaul.
+The distributed approaches are performed using the primal or by the dual decomposition.
+In primal decomposition, the coupling interference variables are fixed for each \ac{BS} wise subproblems and solved for the optimal precoders.
+The fixed interference are then updated by using the subgradients as discussed in \cite{pennanen2011decentralized}.
+The dual approach controls the distributed subproblems by fixing the interference price for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
+
 By adjusting the weights properly, we can use the \ac{WSRM} schemes to achieve other performance measures.
@@
 Specifically, to find a rate vector that minimizes the number of queued packets, we should assign weights based on the current queue size of users.
-More explicitly, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function depending on it \cite{neely2010stochastic}, where the \ac{Q-WSRM} scheme is the outcome of minimizing the Lyapunov drift between the current and the future queue states.
-
-The topic of \ac{MIMO} \ac{BC} precoder design has been studied extensively with different performance criteria in the literature.
-For the problem of \ac{WSRM} utility, due to the nonconvex nature of the linear \ac{MIMO} \ac{BC} precoder design, \cite{christensen2008weighted,wmmse_shi} addressed the problem using a reformulation via \ac{MMSE}, casting the problem as a convex one for  fixed receivers.
-In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders.
-Then the problem is solved using an alternating optimization method, i.e., finding a set of variables while the remaining others are fixed.
-The \ac{WSRM} problem using an alternative \ac{MMSE} reformulation along with the additional rate constraints is considered in \cite{kaleva2013primal}.
-A fast converging algorithm for the \ac{WSRM} problem is proposed in \cite{tran2012fast} using a surrogate for a convex program at each iteration.
+The queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function depending on it \cite{tassiulas,neely2010stochastic}, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states.
+Similar algorithms are discussed in the networking literature as the backpreassure algorithm, where the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
 
@@
 Since the problem considered in \cite{qps_cioffi} assumes multi-user \ac{OFDM} model without multi-antenna support, the queue minimizing scheduling reduces to the problem of optimal power allocation.
+In the context of the wireless networks, the backpreassure algorithm has been extended by formulating the wireless transmission rate as a \ac{MIMO} \ac{BC} optimization problem by using the corresponding user queues as the weight for the associated rate \cite{weeraddana2011resource}.
 
-In this paper, we consider the problem of designing the precoders for a \ac{MU-MIMO} \ac{OFDM} scenario jointly across space-frequency dimension to minimize the number of queued packets associated with the users.
-We compare the performance of the proposed \ac{QM} \ac{JSFRA} scheme over the \ac{Q-WSRM} scheme performed over each sub-channel, where the weights are updated after each sub-channel with the unserved packets.
-We show that the \ac{JSFRA} scheme provides better performance over the sub-channel wise resource allocation technique like \ac{Q-WSRM} scheme.
+In the traditional \ac{WSRM} formulation, the precoders are designed for the sub-channels independently due to the interference-free \ac{OFDM} transmission.
+In this work, since the objective is to identify the transmission rates for all the users across the space-frequency resources, the precoders are to be designed jointly across the space-frequency dimension.
+In order minimize the number of queued packets at the \acp{BS}, the precoders are designed by the proposed \ac{JSFRA} formulation with two different approaches in a centralized manner.
+We also propose the distributed approaches for the centralized problem for designing the precoders independently across the \acp{BS} with the limited information exchange.
+
+The outline of this paper is as follows.
+In Section \ref{sec-2-3.2}, we propose the system model and the problem formulation for the current queue minimizing precoder design.
+Existing and the proposed precoder designs for the queue minimizing objective is discussed elaborately in Section \ref{sec-3}.
+The distributed solutions are outlined in Section \ref{sec-4} followed by the simulation results for both centralized and the distributed algorithms are provided in Section \ref{sec-5}.
+Conclusions are drawn in Section \ref{sec-6}.

### 2014-07-15 Report/mse_formulation.tex
updated intro

@@
-In this section, we present an alternative formulation for the \acl{QM} \ac{JSFRA} scheme by using the \ac{MSE} equivalence with the capacity as in \cite{christensen2008weighted,wmmse_shi} for the \ac{WSRM} problem.
-The current formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )} \cite{viswanath1999optimal,mse_duality}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} for decoding the transmitted symbols using the \ac{MMSE} receivers and \me{C} is the maximum achievable capacity for a given \ac{SINR} of \me{\gamma}.
+In this section, we present an alternative approach for solving the \acl{QM} \ac{JSFRA} problem by using the \ac{MSE} equivalence with the the achievable capacity presented in \cite{viswanath1999optimal,mse_duality}.
+It is given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon(\gamma)} \right )}, where \me{\epsilon(\gamma) = {1} / {(1 + \gamma)}} is the \ac{MSE} for decoding the transmitted symbol at the reciever employing the \ac{MMSE} equalizer and \me{C(\gamma)} is the achievable capacity for the \ac{SINR} of \me{\gamma}.
+Using this equivalence, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \ac{MU-MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}.
+In the current approach, we use this relation between the \ac{MSE} and the achievable capacity to solve the \ac{JSFRA} problem by employing \ac{MMSE} receivers.
+
 Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.

### 2014-07-15 Report/simulation_distributed.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>
updated intro

@@
 In this section, we discuss the simulation performances of the algorithms briefed in Section \ref{sec-3} and \ref{sec-4}.
-The comparison studies are made using the queue deviation and sum rate convergence of the algorithms discussed so far using different system models.
-The distributed algorithms for the \ac{JSFRA} scheme and the equivalent \ac{MSE} representation are compared using the excess backlogged packets present after the current iteration instant.
+The comparison studies are made using the queue deviation and sum rate convergence using various system models.
+The distributed algorithms for the \ac{JSFRA} scheme and the equivalent \ac{MSE} representation are compared using the excess backlogged packets present after each \ac{SCA} update.
 
 Fig.
-\ref{fig-d-1} demonstrates the performance of the distributed algorithms in an \ac{OFDM} framework modeled with \me{N = 5} sub-channels with \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas.
-Each \ac{BS} serves \me{|\mc{U}_b| = 4, \forall b \in \{1,2\}} users in a coordinated manner so as to minimize the interference caused to the neighboring \ac{BS} users.
+\ref{fig-d-1} demonstrates the performance of the distributed algorithms in an \ac{OFDM} framework modeled with \me{N = 3} sub-channels with \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas.
+Each \ac{BS} serves \me{|\mc{U}_b| = 4, \forall b \in \{1,2\}} users in a coordinated manner to reduce the number of backlogged packets at each \ac{BS}.
 Fig.
-\ref{fig-d-1.1} shows the total number of backlogged packets at the end of each iteration and Fig.
-\ref{fig-d-1.2} plots the total rate achieved by various algorithms at each iteration.
-As discussed earlier in the distributed section, the rate of convergence of any distributed algorithm depends on the proper choice of a step size.
-In particular, the primal decomposition method is more susceptible to the choice of the step size compared to the \ac{ADMM} approach.
-Since the primal decomposition iterates at each instant by fixing the interference thresholds, it may lead to infeasible solutions if the initial interference values are not feasible and also with the updated interference value as in \eqref{primal-sg-update}.
+\ref{fig-d-1.1} shows the total number of backlogged packets  and Fig.
+\ref{fig-d-1.2} plots the total rate achieved by different algorithms after each \ac{SCA} update.
+As pointed out earlier, the distributed algorithms are very much dependent on the choice of the step size used to update the subgradients.
+In particular, the primal decomposition is more susceptible to the step size as compared to the \ac{ADMM} approach, since interference values are fixed for each primal exchange, it may lead to infeasible solutions if the initial or any intermediate update on the interference determined by \eqref{primal-sg-update} are not in the valid range.
 
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\columnwidth]{NewFigures/distribute_queue-1}
+\includegraphics[width=\columnwidth]{fig-3}
 \caption{Queue deviation}
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\columnwidth]{NewFigures/distribute_sum_rate-1}
+\includegraphics[width=\columnwidth]{fig-4}
 \caption{Sum rate performance}
@@
 \end{subfigure}
-\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
+\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} model}
 \label{fig-d-1}
@@
 \end{subfigure}
-\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,3,12,2 \rbrace} model}
+\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 2,3,9,2 \rbrace} model}
 \label{fig-d-2}

### 2014-07-17 Report/introduction.tex
phase-1

@@
 In order minimize the number of queued packets at the \acp{BS}, the precoders are designed by the proposed \ac{JSFRA} formulation with two different approaches in a centralized manner.
-We also propose the distributed approaches for the centralized problem for designing the precoders independently across the \acp{BS} with the limited information exchange.
+We also propose distributed approaches for the centralized problem for designing the precoders independently across the \acp{BS} with the limited information exchange.
 

### 2014-07-17 Report/simulation_distributed.tex
phase-1

@@
-In this section, we discuss the simulation performances of the algorithms briefed in Section \ref{sec-3} and \ref{sec-4}.
-The comparison studies are made using the queue deviation and sum rate convergence using various system models.
-The distributed algorithms for the \ac{JSFRA} scheme and the equivalent \ac{MSE} representation are compared using the excess backlogged packets present after each \ac{SCA} update.
-
+The performance of the distributed algorithms are studied in this section by comparing with the centralized algorithms.
+The total number of queued packets after the current allocation and the total sum rate achieved by the network are used as the performance measures.
 Fig.
-\ref{fig-d-1} demonstrates the performance of the distributed algorithms in an \ac{OFDM} framework modeled with \me{N = 3} sub-channels with \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas.
-Each \ac{BS} serves \me{|\mc{U}_b| = 4, \forall b \in \{1,2\}} users in a coordinated manner to reduce the number of backlogged packets at each \ac{BS}.
+\ref{fig-d-1} shows the performance of the algorithms for the system configuration represented by \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at each \ac{BS}.
+Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}.
 Fig.
@@
 \ref{fig-d-1.2} plots the total rate achieved by different algorithms after each \ac{SCA} update.
-As pointed out earlier, the distributed algorithms are very much dependent on the choice of the step size used to update the subgradients.
-In particular, the primal decomposition is more susceptible to the step size as compared to the \ac{ADMM} approach, since interference values are fixed for each primal exchange, it may lead to infeasible solutions if the initial or any intermediate update on the interference determined by \eqref{primal-sg-update} are not in the valid range.
+As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the choice of the step size used in the subgradient update.
+Since the interference values are fixed for local subproblem in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update using \eqref{primal-sg-update} is not valid.
 
-Fig.
-\ref{fig-d-1} also compares the performance of the iterative algorithm for \ac{JSFRA} scheme via \ac{MSE} reformulation using the \ac{KKT} conditions discussed in Section \ref{sec-4.3}.
-The performance is inferior compared to the other algorithms due to the violation in the assumptions made in the algorithm design \textit{i.e}, \me{Q_k \gg t_k}.
-Since in this case, we are comparing the \me{q = 1} case, the queue condition \me{Q_k \gg t_k} needs to be satisfied in order to remove the absolute operator from the expression in \eqref{eqn-9.1a} to form \eqref{kkt-mse-1.1}.
-The total number of backlogged packets after the each iteration reduces monotonically in all cases and converges to the points closer to the centralized solution \me{\chi = 33} bits.
-As seen in Fig.
-\ref{fig-d-1}, the \ac{ADMM} approach provides better convergence compared to the primal approach in the initial phase due to the quadratic penalty term included in the objective, which gets pronounced initially due to the large deviation between the assumed and the actual interference across the coordinating \acp{BS}.
+The Fig.
+\ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions of the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} update points.
+In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations by exchanging either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme.
+It can be seen from Fig.
+\ref{fig-d-1} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
+The plot also includes the \ac{Q-WSRM} which performs similar to the other centralized schemes discussed in this paper.
 \begin{figure*}
@@
 In Fig.
-\ref{fig-d-2}, the total backlogged packets and the sum throughput offered to minimize the number of queued packets for \me{K = 12} users across \me{N = 5} sub-channels are plotted for the analysis.
-The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users mounted with \me{N_R = 2} antennas respectively.
-The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{\mathbb{U}(0,-6)} dB independently.
-The sum rate and queue minimizing behavior follows similar pattern as in Fig.
-\ref{fig-d-1} for \me{N_B = 2} \acp{BS} scenario.
+\ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels.
+The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively.
+The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{\mathbb{U}(0,-6)} dB.
+The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.
 
 Fig.
-\ref{fig-d-2} demonstrates the convergence behavior of the different distributed algorithms discussed so far.
-It can be seen from Fig.
-\ref{fig-d-2}, that the distributed algorithms depend on the step size used in the subgradient update procedure.
-The primal decomposition algorithm, which distributes the precoder design by fixing the interference thresholds at each iteration, converges to the optimal resource allocations gradually as compared to the \ac{ADMM} based dual approach.
-The \ac{ADMM} scheme depends on the step size for the convergence, where the larger step size makes the algorithm to reach the optimal point quickly but takes more iterations to converge.
-The choice of \me{I_{\max}}, which denotes the maximum \ac{SCA} iterations, and the \me{J_{\max}}, which denotes the subgradient convergence limit, are fixed at \me{100} and \me{8} respectively.
-The information exchange is made at each instant and the performances are evaluated as if the actual transmission is happened with the precoders \me{\mvec{m}{l,k,n}^{(i)}} designed at the \me{\ith{i}} instant in a distributed manner.
-In this paper, we assume that the actual transmission will happen at the end of the precoder convergence or when the maximum number of iterations reached.
-
-The performance of the joint \ac{Q-WSRM} scheme discussed in the Section \ref{sec-3.1} performs slightly worse than (\me{\approx \, 2} bits) the \ac{JSFRA} scheme in reducing the number of queued packets, even though the performance were similar in Table \ref{tbl-1}.
-As stated earlier, the joint \ac{Q-WSRM} scheme and the \ac{JSFRA} scheme with the exponent \me{q = 1} performs the same when the number of queued packets are identical for all the users.
-In this case, the joint \ac{Q-WSRM} becomes the sum rate maximization problem which is equivalent to the greedy \me{q=1} \ac{JSFRA} scheme.
-In the current scenario, since the number of queued packets are different for the users, the performance of the \ac{JSFRA} scheme is better due to its greedy resource allocation.
-It can be seen from Fig.
-\ref{fig-d-2}, that the \ac{KKT} based approach provides inferior result in the queue minimization perspective as compared with the sum rate plot.
-The performance degradation is due to the unconstrained rate increase for the users beyond their actual number of queued packets available to transmit.
-Since the objective uses the \me{\ell_1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user.
-The number of queued packets are initialized in a way to analyze the effect of the unconstrained behavior in the \ac{KKT} scheme.
+\ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update.
+In case of the distributed algorithms, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations.
+In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformer \me{\mvec{W}{k,n}} update at the same instant.
+The data tips are used to highlight the convergent points of various algorithms.
+The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes.
+It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
 \begin{figure*}
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{NewFigures/distributed_queue_plot_1}
+\includegraphics[width=\textwidth]{fig-5}
 \caption{Queue deviation}
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{NewFigures/distributed_sum_rate_plot_1}
+\includegraphics[width=\textwidth]{fig-6}
 \caption{Sum rate performance}
 \end{subfigure}
-\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 2,3,9,2 \rbrace} model}
+\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
 \label{fig-d-2}
@@
 
-The performance of the \ac{MSE}-\ac{KKT} scheme is shown in comparison with the other schemes discussed so far in Fig.
+The performance of the \ac{MSE}-\ac{KKT} scheme discussed in Section \ref{sec-4.3} is presented in Fig.
 \ref{fig-d-3}.
-It can be seen that the \ac{KKT} based approach performs similar to the optimization problem given in \eqref{eqn-9}, which is solved using the solver \cite{grant2008cvx}.
-In the \me{\ell_2} case, the objective is differentiable and hence can be differentiable for any number of queued packets as compared to the \me{\ell_1} case requiring larger queue sizes in order to drop the absolute function occurring in the norm operator.
-The performance of the closed form solution using the \ac{KKT} solution achieves similar performance without allocating rates beyond the available queued packets.
-In order to bring out the performance difference, \me{\ell_1} objective plot is also provided in Fig.
-\ref{fig-d-3} providing better reduction in the number of queued packets in the current transmission slot.
-Fig. \ref{fig-d-3}
+It compares the \ac{JSFRA} scheme with \me{\ell_1} and \me{\ell_2} norm cases in addition to the \ac{Q-WSRM} scheme.
+We compare the performance of the \ac{MSE}-\ac{KKT} scheme for the exponents \me{q=1} and \me{q=2}.
+The performance of the \me{\ell_1} \ac{JSFRA} scheme performs the best over other algorithms in minimizing the total number of queued bits after the current allocation due to its greedy approach.
+The inclusion of the additional second order rate term in \eqref{pf-1}, the \me{\ell_2} \ac{JSFRA} scheme achieves different performance than the \ac{Q-WSRM} scheme as shown in Fig.
+\ref{fig-d-3}.
+
+It can be seen from Fig.
+\ref{fig-d-3.2}, that the sum rate of the \me{q=1} \ac{KKT} approach outperforms other schemes in spite of Fig.
+\ref{fig-d-3.1} showing inferior queue minimizing performance.
+This due to the lack of the rate bounding constraint \eqref{kkt-mse-4.2}, which is simply given by \me{\sigma_{l,k,n}^{(i)} = \frac{a_k}{\log(2)}} providing no control for the excess allocations.
+For \me{q=2}, when the allocated rate exceeds the available queued bits, \me{\sigma_{l,k,n}^{(i)}} will be negative, thereby reducing \eqref{kkt-mse-4.1} as \me{\alpha_{l,k,n}^{(i)} < \alpha_{l,k,n}^{(i-1)}} to reduce the priority for the corresponding user in the next iteration.
+The performance of the closed form solution using the \ac{KKT} solution performs similar to the centralized schemes with \me{q=2} by limiting the rates beyond the available queued packets.
 \begin{figure*}
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{fig-7}
+\includegraphics[width=\textwidth]{fig-9}
 \caption{Queue deviation}
+\label{fig-d-3.1}
 \end{subfigure}
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{fig-8}
+\includegraphics[width=\textwidth]{fig-10}
 \caption{Sum rate performance}
+\label{fig-d-3.2}
 \end{subfigure}
 %\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
+%\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}
 \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}

### 2014-07-17 Report/simulation_results.tex
ver_0.0.1
modified for KKT MMSE
phase-1

@@
-In this section, we discuss the performance of the above mentioned algorithms in different scenarios on minimizing the number of queued packets at the transmitter.
-To begin with, we consider a single cell \ac{SISO} system operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
-The number of packets waiting at the transmitter is kept as \me{Q_k = 6} bits.
-With these assumptions, the resources allocated for the users on each sub-channel by various algorithms are listed in Table \ref{tbl-1}.
+This section discusses the performance of the centralized algorithms discussed in Section \ref{sec-3} for a few system configurations.
+To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
+The number of packets waiting at the transmitter for each user is given by \me{Q_k = 5,8} and \me{6} bits respectively.
+With this configuration, the resources allocated for the users on each sub-channel by various algorithms are listed in Table \ref{tbl-1}.
 
-Table \ref{tbl-1} shows the channel seen by the users over each sub-channel followed by the rates allocated over each sub-channel by three different algorithms, joint \ac{Q-WSRM} allocation without the maximum rate constraints \eqref{eqn-3.1.4}, \ac{JSFRA} scheme and the band-wise \ac{Q-WSRM} scheme.
-Since the total allowed transmission constraint is present only on the \ac{JSFRA} scheme, the total number of packets remained after the current transmission slot is minimum for the \ac{JSFRA} scheme with \me{1.14} bits, where \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
-The precoder design for the optimal allocation in band-wise \ac{Q-WSRM} depends on the order of selecting the sub-channels, which leads to an exhaustive search.
-In this scenario, the formulation in \eqref{q_gen_sum} and \eqref{gen_sum} performs the same as compared to the \ac{JSFRA} scheme, \textit{i.e}, with the maximum rate constraints, the joint \ac{Q-WSRM} scheme performs the same as the \ac{JSFRA} scheme.
-
+Table \ref{tbl-1} lists the sub-channel wise channel seen by the users followed by the assigned rates over each sub-channel by three different algorithms, \ac{Q-WSRM} allocation, \ac{JSFRA} scheme and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} precoder design proposed in \cite{wmmse_shi}.
+The performance metric used for the comparison of different algorithms is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
+It can be seen from Table \ref{tbl-1}, that the \ac{Q-WSRM} scheme provides more priority to the third user with \me{Q_{3} = 6} bits compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel.
+Int contrast to the \ac{Q-WSRM} scheme, the \ac{JSFRA} scheme assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
 \begin{table*}
@@
 \hline
-\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Joint Q-WSRM w/o} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{WSRM band} \\
-\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Queue constraints \eqref{eqn-3.1.4}} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
+\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRM approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
+\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(\emph{backpreassure} algorithm)} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
 \cline{3-14}
@@
 \hline
-\me{1} & \me{6} & \me{2.26} &  \me{0.69}  &  \me{0.73} & \me{0} &  \me{0}  &  \me{0} & \me{5.56} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{2.68} \\
-\me{2} & \me{6} & \me{0.53} &  \me{1.93}  &  \me{1.40} & \me{0} &  \me{5.29}  &  \me{0} & \me{0} &  \me{5.33}  &  \me{0} & \me{0} &  \me{5.26}  &  \me{0} \\
-\me{3} & \me{6} & \me{2.45} &  \me{1.31}  &  \me{2.42} & \me{5.84} &  \me{0}  &  \me{5.95} & \me{0} &  \me{0}  &  \me{5.95} & \me{5.93} &  \me{0}  &  \me{0} \\
+\me{1} & \me{5} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.91} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
+\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.46}  &  \me{3.54} & \me{0} &  \me{4.36}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
+\me{3} & \me{6} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{5.72} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{5.79} & \me{5.81} &  \me{0}  &  \me{0} \\
 \hline
-\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{6.70} bits} & \multicolumn{3}{c|}{\me{1.14} bits} & \multicolumn{3}{c|}{\me{4.11} bits} \\
+\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{5.28} bits} & \multicolumn{3}{c|}{\me{3.91} bits} & \multicolumn{3}{c|}{\me{5.28} bits} \\
 \hline
@@
 
-In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{K = 8} users with \me{N_R} antennas each.
-The users are assumed to be at the cell-edge with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-3} dB and each \ac{BS} are associated with \me{|\mc{U}_b|} users respectively.
-
+In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
+The users are located with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-6} dB, thereby simulating a realistic scenario.
+Fig.
+\ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system.
+It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRM} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
 \begin{figure*}
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=1.0\textwidth]{NewFigures/centralized-1a}
+\includegraphics[width=1.0\textwidth]{fig-1-1}
 \caption{\me{4 \times 1} system}
@@
 \begin{subfigure}{0.49\textwidth}
-\includegraphics[width=1.0\textwidth]{NewFigures/centralized-2a}
+\includegraphics[width=1.0\textwidth]{fig-2-1}
 \caption{\me{4 \times 2} system}
@@
 \end{subfigure}
-\caption{Convergence plot for \me{\lbrace N,N_B,K \rbrace = \lbrace 3,2,8 \rbrace} model}
+\caption{Convergence plot for \me{\lbrace N,N_B,K \rbrace = \lbrace 3,3,9 \rbrace} model}
 \end{figure*}
 
+In the sub-channel wise allocations, where the total transmit power is shared equally among the sub-channels, the precoders are designed for each sub-channels independently.
+In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels.
+At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random inital point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders.
+The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig.
+\ref{fig-1} for the discussed centralized schemes and the convergence point are marked with the data tips.
 Fig.
-\ref{fig-1} shows the performance of the above discussed schemes for a single receive antenna system.
-The figure compares the total number of \ac{SCA} iterations required by the \ac{JSFRA}, \ac{JSFRA} with sum power constraint, \ac{SRA} and \ac{Q-WSRM} schemes to achieve the optimal resource allocation to minimize the number of backlogged packets during the given scheduling instant.
-The convergence of the proposed \ac{JSFRA} is much quicker compared to the band-wise allocation schemes like the \ac{Q-WSRM} and the \ac{SRA} schemes.
-The waterfall like behavior for the band-wise allocation schemes suggests the rapid convergence when there is a band switch over, \textit{i.e}, when the queues are updated from the earlier sub-channels to find the precoders for the current sub-channel.
-The convergence at each sub-channel is iterated for the accuracy of \me{\approx 10^{-4}} or for a predetermined count \me{I_{\max}}, which creates the flat region between each waterfall behavior.
-The backlogged bits and the iteration count by various schemes at the convergence point are marked in the figures using data tips.
+\ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas.
 \begin{table}
@@
 \hline
-\me{1} & 12.0 &  6.15 &  5.32 & 12.0 &  6.95 & 11.1 & 11.9 & 10.8 & 19.71 \\
-\me{2} & 11.9 & 7.3 & 5.9 & 10.1 & 9.19 & 10.1 & 10.8 & 10.3 & 20.48 \\
-\me{\infty} & 9.15 & 9.15 & 9.15 & 9.15 & 9.16 & 9.15 & 9.15 & 9.15 & 22.75 \\
+\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
+\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
+\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
 \hline
+\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\    
+\cline{1-9}
 \end{tabular}
-\caption{Queue information for \me{N=5} sub-channels}
+\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
 \label{tbl-3}
@@
 
-Fig.
-\ref{fig-2} compares the convergence behavior of the precoder designs, which allocates the space-frequency resources to the users to minimize the number of backlogged packets.
-Different values for the exponent \me{q} are compared in Table \ref{tbl-3} for the system configuration \me{\{N_B,K,N_T,N_R\}= \{2,8,4,1\}}.
-The number of backlogged packets at each user before the current scheduling is fixed to be \me{12} bits.
-It is evident that the exponent \me{q=1} shows the greedy resource allocation in comparison with the fair scheduling achieved using \me{q=\infty}.
-The \me{q=\infty} norm does the fair scheduling even the path loss experienced by the users are different.
-It tries to minimize the variance across the backlogged packets of each user present in the system.
+The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Table \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas.
+The configuration is mentioned in the caption of Table \ref{tbl-3} along with the number of queued bits for each user.
+It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits.
+The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets \me{\chi_k = 3.58} bits.
+The \me{\ell_{\infty}} norm provides the fair allocation by making the queued deviation equal for all the users after the current allocation irrespective of their channel gains.

### 2014-07-20 Report/dual_approach.tex
Corrections after first reading

@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-2} \label{eqn-dual-1}
-\underset{\substack{\gamma_{l,k,n}, \nu^{\set{b_k}}_{l,k,n,b} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}, \zeta^{\set{b_k}}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}}T} \left ( \mbfa{\zeta}^{\set{b_k}} - \mbfa{\zeta}(b_k) \right ) \IEEEyessubnumber \label{eqn-dual-2a} \\
+\underset{\substack{\gamma_{l,k,n}, \nu^{\set{b_k}}_{l,k,n,b},\mvec{W}{k,n} \\ \mvec{M}{k,n}, \beta_{l,k,n}, \zeta^{\set{b_k}}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}}T} \left ( \mbfa{\zeta}^{\set{b_k}} - \mbfa{\zeta}(b_k) \right ) \IEEEyessubnumber \label{eqn-dual-2a} \\
 \text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
@@
 
-In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} at the \acp{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} to the objective function.
+In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} at the \acp{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} in the objective function.
 At optimality, the locally assumed and the consensus interference values will be equal,  providing no contribution to the objective function.
-The optimal step size use to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed}.
-Now, the subproblem at each \ac{BS} for the \me{\ith{i}} iteration is give by
+The optimal step size used to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed}.
+Now, the subproblem at each \ac{BS} for the \me{\ith{i}} iteration is given by
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \zeta^{\set{b_k}(i)}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}(i-1)}T} \mbfa{\zeta}^{\set{b_k}(i)} + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i-1)}(b_k)}_{\text{consensus values}} - \underbrace{\mbfa{\zeta}^{\set{b_k}(i)}}_{\text{local values}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{M}{k,n},\mvec{W}{k,n} \\ \beta_{l,k,n}, \zeta^{\set{b_k}(i)}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}(i-1)}T} \mbfa{\zeta}^{\set{b_k}(i)} + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i-1)}(b_k)}_{\text{consensus values}} - \underbrace{\mbfa{\zeta}^{\set{b_k}(i)}}_{\text{local values}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
 \text{subject to} & \quad & \eqref{eqn-dual-1d} - \eqref{eqn-dual-1f} \IEEEyessubnumber \label{eqn-dual-3b},

### 2014-07-20 Report/introduction.tex
Corrections after first reading

@@
-The last mile wireless connectivity poses significant bottleneck in the overall data traffic in the interconnected networks.
-The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which is proportional to the battery drain.
+The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks.
+The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which is proportional to the mobile battery drain.
 In order to over come the receiver complexity, \ac{OFDM} based transmissions are introduced for the wideband transmissions.
@@
 In a network with multiple \acp{BS} serving multiple users (\acs{MU}), the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
-These available packets are transmitted over the shared wireless resources in an efficient manner with the various system constraints.
+These available packets are transmitted over the shared wireless resources in an efficient manner by including the system limitations and constraints.
 In this work, we consider the user allocation over the space-frequency resources provided by the \ac{MU-MIMO} \ac{OFDM} framework in the downlink broadcast transmission to reduce the number of queued packets corresponding to the users at the \acp{BS}.
@@
 Firstly, it determines the transmission rate on a certain resource and secondly, by making the transmit beamformer to be a zero vector, the corresponding user will not be scheduled on a certain resource.
-The queue minimizing network optimization objective is used to design beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
-To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in queues prior to transmission, and, hence, to avoid packet drops as an indirect objective.
+The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
+To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in the queues prior to the transmission, and, hence, to avoid packet drops as an indirect objective.
 
@@
 The topic of \ac{MIMO} \ac{BC} precoder design has been studied extensively with different performance criteria in the literature.
-Due to the nonconvex nature of the linear \ac{MIMO} \ac{BC} precoder design problem, it is solved by the sequence of approximated convex problems.
+Due to the nonconvex nature of the linear \ac{MIMO} \ac{BC} precoder design problem, it is usually solved by the sequence of approximated convex problems.
 In \cite{sin_algorithm}, the \ac{MIMO} rate expression is linearized around a fixed point in order to solve the \ac{DC} problem as a concave maximization problem in an iterative manner.
@@
 The relation between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} are also used to solve the \ac{WSRM} objective.
-In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MMSE}, casting the problem as a convex one for fixed \ac{MMSE} receivers.
+In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed \ac{MMSE} receivers.
 In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders.
@@
 In Section \ref{sec-2-3.2}, we propose the system model and the problem formulation for the current queue minimizing precoder design.
-Existing and the proposed precoder designs for the queue minimizing objective is discussed elaborately in Section \ref{sec-3}.
+Existing and the proposed precoder designs for the queue minimizing objective are discussed elaborately in Section \ref{sec-3}.
 The distributed solutions are outlined in Section \ref{sec-4} followed by the simulation results for both centralized and the distributed algorithms are provided in Section \ref{sec-5}.

### 2014-07-20 Report/joint_wsrm_formulation.tex
Corrections after first reading

--- 2014-07-10 Report/joint_wsrm_formulation.tex
@@
-The queue minimizing algorithms are discussed extensively in the networking literature for providing congestion-free routing between any two nodes\footnote{routers or user terminals} in the network.
-It is achieved by finding a control policy considering the differential backlogs of the packets present in the source and the destination node, where control policy refers to the resource or rate allocation strategy.
-The control policy satisfying the condition is known as \emph{backpreassure algorithm}, discussed extensively in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
-The algorithm assumes the physical layer rate as a fixed entity due to the wired infrastructure.
-In order to use the algorithm in the wireless network, the user rate variable \me{t_{k}} should be modeled in accordance with the wireless backbone network.
+The queue minimizing algorithms are discussed extensively in the networking literature for providing a congestion-free routing between any two nodes\footnote{routers or user terminals} in the network.
+One such algorithm used extensively is the \emph{backpreassure algorithm}, discussed in detail in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
+The algorithm determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes.
+Even though the algorithm is primarily designed for the wired infrastructure, it can be extended to the wireless networks by designing the user rate variable \me{t_k} in accordance to the wireless network.
 
-The \ac{Q-WSRM} scheme is formulated by extending the \emph{backpreassure algorithm} for the \ac{MIMO} \ac{OFDM} network, where multiple \acp{BS} act like a source nodes and the user terminals as a receiver nodes.
-The user rate variables \me{t_k} are obtained by the design of the transmit and the receive precoders to maximize the weighted sum rate.
+The \ac{Q-WSRM} formulation extends the \emph{backpreassure algorithm} to the \ac{MIMO} \ac{OFDM} framework, in which the multiple \acp{BS} acts as the source nodes and the user terminals as the receiver nodes.
+The control policy in the form of transmit precoders are designed with the objective of minimizing the number of queued packets waiting at the \acp{BS}.
 The weights used in the precoder design algorithm should be a function of the number of backlogged packets corresponding to each user.

### 2014-07-20 Report/kkt_mse_approach.tex
updated kkt,wsrm,admm,primal
Corrections after first reading

@@
 In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by solving the \ac{KKT} conditions.
-Simimar work has been considered for the \ac{WSRM} problem with the rate constraints in \cite{kaleva2012weighted}.
-When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which makes the problem difficult to solve in an iterative approach as in \cite{kaleva2012weighted}.
+Similar work has been considered for the \ac{WSRM} problem with the rate constraints in \cite{kaleva2012weighted}.
+When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} includes a nonconvex constraint, which makes the problem difficult to solve in an iterative approach as in \cite{kaleva2012weighted}.
 
@@
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
-\alpha_{l,k,n} : & \hspace{0.5cm} & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \\ \nonumber
+\alpha_{l,k,n} : & \hspace{0.5cm} & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \\ \nonumber
 &\hspace{0.5cm}& \quad {} + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
@@
 \mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}, \IEEEyessubnumber \label{kkt-mse-4.6} \\
-\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2, \IEEEyessubnumber \label{kkt-mse-4.4} \\
+\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2, \IEEEyessubnumber \label{kkt-mse-4.4} \\
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\sigma_{l,k,n}^{(i)} &=& q \,a_k \, \log_2(e)  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\sigma_{l,k,n}^{(i)} &=& \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
 \alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \Big ( \rfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \Big ). \IEEEyessubnumber \label{kkt-mse-4.1}

### 2014-07-20 Report/mse_formulation.tex
Corrections after first reading

@@
 Using this equivalence, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \ac{MU-MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}.
-In the current approach, we use this relation between the \ac{MSE} and the achievable capacity to solve the \ac{JSFRA} problem by employing \ac{MMSE} receivers.
+In this, we use the relation between the \ac{MSE} and the achievable capacity to solve the \ac{JSFRA} problem by employing \ac{MMSE} receivers.
 
@@
 
-The \ac{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the constraint \eqref{eqn-mse-1.2}.
+The \acl{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the constraint \eqref{eqn-mse-1.2}.
 In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}.

### 2014-07-20 Report/problem_formulation.tex
Corrections after first reading

@@
 \end{equation}
-It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure} when we ignore the second order terms from \eqref{pf-1}.
-Limiting \me{t_k^2} by a constant value, imposes the additional rate constraint \eqref{eqn-3.1.4} in the \ac{Q-WSRM} formulation to avoid the resource wastage in the form of over allocation.
+It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure} if the second order terms are ignored.
+Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over allocation.
 In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself.
 In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achive an efficient allocation by identifying the optimal space-frequency resource for each user in the system.
-The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \eqref{q_gen_sum} approach.
+The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \ac{Q-WSRM} approach.
 

### 2014-07-20 Report/problem_formulation_intro.tex
Corrections after first reading

@@
-In this paper, we address the problem of resource allocation across the \ac{MIMO} \ac{OFDM} framework, in which the resources are contended by the \acp{BS} to empty the respective user queued packets.
+We address the problem of resource allocation across the \ac{MIMO} \ac{OFDM} framework, in which the resources are contended by the \acp{BS} to empty the respective user queued packets.
 In order to minimize the number of queued packets, the precoders are designed to utilize the available space-frequency resources efficiently by limiting the over utilization of the same.
@@
 \end{equation}
-The above positivity constraint need to be satisified by \me{v_k} to avoid the excessive allocation of the resources.
+The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.
 

### 2014-07-20 Report/queue_minimizing_intro.tex
Corrections after first reading

@@
 
-In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is highly difficult due to the combinatorial and the non-convex nature of the problem.
+In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is highly difficult due to the combinatorial and the nonconvex nature of the problem.
 In addition to that, the objective of minimizing the number of the queued packets over the spatial and the sub-channel dimensions adds further complexity to the existing problem.

### 2014-07-20 Report/simulation_distributed.tex
Corrections after first reading

@@
 In case of the distributed algorithms, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations.
-In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformer \me{\mvec{W}{k,n}} update at the same instant.
+In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant.
 The data tips are used to highlight the convergent points of various algorithms.
@@
 \end{subfigure}
-%\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
-%\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}
 \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}

### 2014-07-20 Report/simulation_results.tex
Corrections after first reading

@@
 In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels.
-At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random inital point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders.
+At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random initial point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders.
 The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig.

### 2014-07-20 Report/sub_channel_wsrm.tex
Corrections after first reading

@@
 The proposed \acf{QM} \ac{SRA} scheme decouples the problem by fixing the power across each sub-channel to a constant value as compared to the global power constraint defined by \eqref{eqn-4.3}.
-In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel level optimization.
-The number of queued bits for each user are updated by the difference between the total number of queued bits during the current slot to the total number of bits that are guaranteed by the earlier sub-channel wise allocations in the same slot as
+In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization.
+The number of queued bits for each user are updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
 \begin{equation}

### 2014-08-04 Report/introduction.tex
temp updates

@@
 The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks.
-The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which is proportional to the mobile battery drain.
-In order to over come the receiver complexity, \ac{OFDM} based transmissions are introduced for the wideband transmissions.
-To improve the data rate, multiple antennas are installed at the \ac{BS} and at the user terminals to avail the additional freedom in the form of spatial dimension.
-The inclusion of \ac{MIMO} technique in the wireless network provides increased data rate or lower outage for the same transmission power and the channel use.
+The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which are proportional to the mobile battery drain.
+In order to overcome the receiver complexity, \ac{OFDM} based transmissions are introduced for the wideband transmissions.
+To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension.
+The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
 
 In a network with multiple \acp{BS} serving multiple users (\acs{MU}), the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
-These available packets are transmitted over the shared wireless resources in an efficient manner by including the system limitations and constraints.
-In this work, we consider the user allocation over the space-frequency resources provided by the \ac{MU-MIMO} \ac{OFDM} framework in the downlink broadcast transmission to reduce the number of queued packets corresponding to the users at the \acp{BS}.
-Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, the problem can be considered as a resource allocation to minimize the number of backlogged packets at the \acp{BS}.
+These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints.
+In this work, we consider the problem of transmit design over the space-frequency resources provided by a \ac{MU-MIMO} \ac{OFDM} framework in the downlink broadcast transmission to minimize the number of queued packets.
+Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation to minimize the total number of backlogged packets of all \acp{BS}.
 
@@
 Firstly, it determines the transmission rate on a certain resource and secondly, by making the transmit beamformer to be a zero vector, the corresponding user will not be scheduled on a certain resource.
+
+In order to reduce the complexity involved in the precoder design problem, linear precoding are assumed at the \acp{BS} and linear detection is used at users.
 The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
@@
 
-The queue minimizing precoder designs are nothing but the \ac{WSRM} problem with the additional rate constraint determined by the number of backlogged packets for each user in the system.
-The topic of \ac{MIMO} \ac{BC} precoder design has been studied extensively with different performance criteria in the literature.
-Due to the nonconvex nature of the linear \ac{MIMO} \ac{BC} precoder design problem, it is usually solved by the sequence of approximated convex problems.
-In \cite{sin_algorithm}, the \ac{MIMO} rate expression is linearized around a fixed point in order to solve the \ac{DC} problem as a concave maximization problem in an iterative manner.
-Similar approach of solving the \ac{WSRM} problem via arithmetic-geometric inequality is proposed in \cite{tran2012fast}, providing better convergence rate compared to the former.
+The queue minimizing precoder designs are closely related to the \ac{WSRM} problem with additional rate constraints determined by the number of backlogged packets for each user in the system (see Section \ref{sec-3} for further discussions).
+The topics on \ac{MIMO} \ac{BC} precoder design have been studied extensively with different performance criteria in the literature.
+Due to the nonconvex nature of most, if not all, linear \ac{MIMO} \ac{BC} precoder design problems, the \ac{SCA} method has gradually become a powerful tool to deal with these problems.
+For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around an operating point in order to solve the \ac{WSRM} problem in an iterative manner.
+Similar approach of solving the \ac{WSRM} problem via arithmetic-geometric inequality is proposed in \cite{tran2012fast}.
 
-The relation between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} are also used to solve the \ac{WSRM} objective.
+The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} is also used to solve the \ac{WSRM} problem.
 In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed \ac{MMSE} receivers.
@@
 Then the problem is solved using an alternating optimization method, i.e., finding a set of variables while the remaining others are fixed.
-Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} objective are solved via \ac{MSE} reformulation in \cite{kaleva2013primal}.
+Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem are solved via \ac{MSE} reformulation in \cite{kaleva2013primal}.
 
-The problem of precoder design for the \ac{MIMO} \ac{BC} system are solved either by using the centralized controller or at each \ac{BS} independently by exchanging limited information via backhaul.
-The distributed approaches are performed using the primal or by the dual decomposition.
-In primal decomposition, the coupling interference variables are fixed for each \ac{BS} wise subproblems and solved for the optimal precoders.
-The fixed interference are then updated by using the subgradients as discussed in \cite{pennanen2011decentralized}.
-The dual approach controls the distributed subproblems by fixing the interference price for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
+The problem of precoder design for the \ac{MIMO} \ac{BC} system are solved either by using a centralized controller or by using decentralized algorithms where each BS handles their own problems and exchange limited information via backhaul.
+The distributed approaches are based on the primal or dual decomposition \cite{palomar2006tutorial,boyd2011distributed}.
+In primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders.
+The fixed interference are then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}.
+The dual approach controls the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
 
-By adjusting the weights properly, we can use the \ac{WSRM} schemes to achieve other performance measures.
-For example, if the weight of each user is set to be inversely proportional to his/her data rate, a \ac{WSRM} scheme can maintain fairness among users.
-Similarly, the \ac{WSRM} schemes can be used to solve the design problem considered in this paper.
-Specifically, to find a rate vector that minimizes the number of queued packets, we should assign weights based on the current queue size of users.
-The queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function depending on it \cite{tassiulas,neely2010stochastic}, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states.
-Similar algorithms are discussed in the networking literature as the backpreassure algorithm, where the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
+By adjusting the weights properly, we can find arbitrary rate-tuple in the rate region of the system that maximizes other performance measures by solving the resulting WSRM problem.
+For example, if the weight of each user is set to be inversely proportional to his/her data rate, the corresponding problem guarantees fairness among users.
+As an approximate method, we may assign weights based on the current queue size of users.
+More specifically, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function of it,  which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}.
+In the backpreassure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
 
-Earlier work on the queue minimization problem was addressed in the survey paper \cite{berry2004cross} and in particular \cite{qps_cioffi}, where the problem of optimal power allocation is considered to minimize the number of backlogged packets via \acl{GP} formulation.
-Since the problem considered in \cite{qps_cioffi} assumes multi-user \ac{OFDM} model without multi-antenna support, the queue minimizing scheduling reduces to the problem of optimal power allocation.
-In the context of the wireless networks, the backpreassure algorithm has been extended by formulating the wireless transmission rate as a \ac{MIMO} \ac{BC} optimization problem by using the corresponding user queues as the weight for the associated rate \cite{weeraddana2011resource}.
+Earlier studies on the queue minimization problem was summarized in the survey paper \cite{berry2004cross}.
+In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} by geometric programming formulations.
+Since the problem considered in \cite{qps_cioffi} assumed single antenna transmitters and receivers, the queue minimizing problem reduces to the one of optimal power allocation.
+In the context of wireless networks, the backpreassure algorithm mentioned above was extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.
 
-In the traditional \ac{WSRM} formulation, the precoders are designed for the sub-channels independently due to the interference-free \ac{OFDM} transmission.
-In this work, since the objective is to identify the transmission rates for all the users across the space-frequency resources, the precoders are to be designed jointly across the space-frequency dimension.
-In order minimize the number of queued packets at the \acp{BS}, the precoders are designed by the proposed \ac{JSFRA} formulation with two different approaches in a centralized manner.
-We also propose distributed approaches for the centralized problem for designing the precoders independently across the \acp{BS} with the limited information exchange.
+In this paper, we consider the problem of precoder design across the space-frequency resources to minimize the total number of queued packets of all \acp{BS}.
+For this highly nonconvex problem, we first propose two centralized methods.
+In the first method, we relax the nonconvex constraint by the first order taylor approximation around an operating point, which is updated in an iterative manner until convergence or to a certain accuracy.
+In the second method, we reformulate the \ac{JSFRA} problem using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders.
+For distributed implementation, we further proposed decentralized approaches based on primal and \ac{ADMM} scheme to identify the precoders independently across the \acp{BS} by exchanging limited information via backhaul.
+We also proposed an iterative algorithm by solving the \ac{KKT} equations, which can be implemented easily in a distributed manner.
 
-The outline of this paper is as follows.
-In Section \ref{sec-2-3.2}, we propose the system model and the problem formulation for the current queue minimizing precoder design.
-Existing and the proposed precoder designs for the queue minimizing objective are discussed elaborately in Section \ref{sec-3}.
-The distributed solutions are outlined in Section \ref{sec-4} followed by the simulation results for both centralized and the distributed algorithms are provided in Section \ref{sec-5}.
+The remainder of this paper is as follows.
+In Section \ref{sec-2-3.2}, we introduce the system model and the problem formulation for the queue minimizing precoder design.
+Existing and the proposed precoder designs for the \ac{JSFRA} problem are presented in Section \ref{sec-3}.
+The distributed solutions are provided in Section \ref{sec-4} followed by the simulation results in Section \ref{sec-5}.
 Conclusions are drawn in Section \ref{sec-6}.

### 2014-08-04 Report/joint_wsrm_formulation.tex
temp updates

@@
-The queue minimizing algorithms are discussed extensively in the networking literature for providing a congestion-free routing between any two nodes\footnote{routers or user terminals} in the network.
-One such algorithm used extensively is the \emph{backpreassure algorithm}, discussed in detail in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
+The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network.\footnote{routers or user terminals} One such algorithm  is the \emph{backpreassure algorithm}, discussed in detail in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
 The algorithm determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes.
@@
 The Lyapunov drift conditioned on the current backlogged packets \me{\mbfa{Q}(i)} is given by
-\begin{IEEEeqnarray}{rCl}
+\begin{IEEEeqnarray}{rCl} \label{backpreassure-approx}
 \underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
@@
 where the second term on the r.h.s is due to i.i.d assumption on the arrivals.
-We can bound the first term on the r.h.s by a constant \me{B} for all possible control actions taken for a given channel condition \cite{neely2010stochastic}, the resulting problem can be given as
-\begin{equation}
-\underset{t_k}{\text{maximize}} \quad \sum_{k \in \mc{U}} \, Q_k(i) \, t_k(i),
-\label{backpreassure}
-\end{equation}
-where the expectation operator is dropped since it is maximized by maximizing the function inside in an opportunistic manner.
+We can bound the first term on the r.h.s by a constant \me{B} for all possible control actions taken for a given channel condition \cite{neely2010stochastic}.
 
-Now the problem in \eqref{backpreassure} looks similar to the \ac{WSRM} problem if the weights are replaced by the number of backlogged packets corresponding to the users.
+Now the expression in \eqref{backpreassure-approx} looks similar to the \ac{WSRM} problem if the weights are replaced by the number of backlogged packets corresponding to the users.
 The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
@@
 \begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
-\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n},\mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
-\text{subject to.} & \quad & t_{l,k,n} \leq \log_2(1+\gamma_{l,k,n}) \IEEEyessubnumber \label{eqn-3.1.2} \\
-& \quad &\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-3.1.3} \\
-& \quad & \sum_{n=1}^N \sum_{l = 1}^L t_{l,k,n} \leq Q_k, \fall k \in \mc{U} \IEEEyessubnumber \label{eqn-3.1.4}
+\underset{\substack{\mvec{M}{k,n}, \mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
+\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-3.1.3} \\
+& \quad & \sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U} \IEEEyessubnumber \label{eqn-3.1.4}
 \end{IEEEeqnarray}
@@
 By using the number of queued packets as the weights, the resources can be allocated to the user with the more number of backlogged packets, which essentially does the allocation in a greedy manner.
+
 As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as
 \begin{IEEEeqnarray}{rCl}\label{gen_sum}
-\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n} \\ t_{l,k,n},\mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n} \IEEEyessubnumber \\
-\text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.2}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4}. \IEEEyessubnumber
+\underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \IEEEyessubnumber \\
+\text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4}. \IEEEyessubnumber
 \end{IEEEeqnarray}
-
-The problem defined in \eqref{gen_sum} provides an efficient queue minimizing approach as compared to \eqref{q_gen_sum}, since the resource allocation is driven by the channel conditions as compared to the number of queued packets as in \eqref{q_gen_sum}.
-It is to be noted that in both formulations, the resources allocated to the users are limited by the backlogged packets \eqref{eqn-3.1.4}, thereby handling the problem of over allocation explicitly with an additional rate constraint.
+The problem defined in \eqref{gen_sum} provides a greedy queue minimizing approach as compared to \eqref{q_gen_sum}, since the resource allocation is driven by the channel conditions in comparison with the number of queued packets as in \eqref{q_gen_sum}.
+Note that in both formulations, the resources allocated to the users are limited by the backlogged packets with an explicit rate constraint defined by \eqref{eqn-3.1.4}.

### 2014-08-04 Report/problem_formulation.tex
temp updates

@@
 \end{equation}
-It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure} if the second order terms are ignored.
+It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure-approx} if the second order terms are ignored.
 Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over allocation.
@@
 The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \ac{Q-WSRM} approach.
-
-Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}.
-As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
-Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}.
-Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained.
-The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
-\begin{itemize}
-\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
-As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
-\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
-For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
-\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
-\end{itemize}

### 2014-08-04 Report/problem_formulation_intro.tex
temp updates

@@
-We address the problem of resource allocation across the \ac{MIMO} \ac{OFDM} framework, in which the resources are contended by the \acp{BS} to empty the respective user queued packets.
-In order to minimize the number of queued packets, the precoders are designed to utilize the available space-frequency resources efficiently by limiting the over utilization of the same.
-To achieve this, we use the queue deviation utility as compared to the traditional \ac{WSRM} objective discussed extensively in the literature \cite{christensen2008weighted,wmmse_shi}.
-For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
-As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
+To minimize the total number of backlogged packets, we consider minimizing \me{\ell_{q}}-norm of all the queue deviation given by
 \begin{equation}
-v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0 \fall k \in \mathcal{U}.
+v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}).
 \label{eqn-4.2}
 \end{equation}
-The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.
-
-The objective function for the precoder design problem is given by minimizing the absolute value of the queue deviation in \eqref{eqn-4.2} raised to the exponent \me{q} as \me{\text{minimize} \: \sum_{k \in \mc{U}} \, | v_k |^q}.
-With this objective, the problem of weighted queued packet minimization is given by
+Explicitly, the considered problem is given by \me{\sum_{k \in \mc{U}} \, | v_k |^q}. With this objective, the problem of weighted queued packet minimization is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-3}
-\underset{\substack{\mvec{M}{k,n},\gamma_{l,k,n}\\\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
+\underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
 \text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
@@
 Before discussing the proposed solutions, we consider the existing algorithm to solve the issue of minimizing the number of backlogged packets with additional constraints required by problem.
+
+For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
+As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
+\begin{equation}
+v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0.
+\end{equation}
+The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.
+
+Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}.
+As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
+Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}.
+Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained.
+The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
+\begin{itemize}
+\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
+As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
+\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
+For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
+\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
+\end{itemize}

### 2014-08-04 Report/system_model.tex
updated kkt,wsrm,admm,primal
Corrections after first reading
temp updates

--- 2014-07-04 Report/system_model.tex
@@
 We consider a downlink \ac{MIMO} \ac{BC} scenario in an \ac{OFDM} framework with \me{N} sub-channels and \me{N_B} \acp{BS} each equipped with \me{N_T} transmit antennas, serving \me{K} users each with \me{N_R} receive antennas.
-The set of users associated with \ac{BS} \me{b} is denoted by \me{\mathcal{U}_b} and the set \me{\mathcal{U}} represents all users in the system, i.e., \me{\mathcal{U} =\underset{b\in \mathcal{B}}{\cup }\mathcal{U}_b}, where the set \me{\mathcal{B}} holds the coordinating \acp{BS}.
-The serving \ac{BS} of user \me{k} is denoted by \me{b_k\in \mathcal{B}}.
+The set of users associated with \ac{BS} \me{b} is denoted by \me{\mathcal{U}_b} and the set \me{\mathcal{U}} represents all users in the system, i.e., \me{\mathcal{U} =\underset{b\in \mathcal{B}}{\cup }\mathcal{U}_b}, where \me{\mathcal{B}} is the set of all coordinating \acp{BS}.
+Data for user \me{k} is transmitted from only one \ac{BS} which is denoted by \me{b_k\in \mathcal{B}}.
 We denote by \me{\mathcal{C} = \set{1,2,\dotsc,N}} the set of all sub-channel indices available in the system.
@@
 In this paper we adopt linear beamforming technique at \acp{BS}.
-Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with the beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} for transmission.
+Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with the beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted.
 In order to detect  multiple spatial streams at the receiver, a receive beamforming vector \me{\mvec{w}{l,k,n}} is employed at each user.
-Consequently, the received data symbol corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n^\mathrm{th}} at user $k$ is given by
+Consequently, the received data symbol corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
 \begin{equation}\label{eqn-1}
@@
 \end{equation}
-where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} with rank \me{L = \min(N_R,N_T)} is the channel between the \ac{BS} \me{b} and  user \me{k} on the sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
-Assuming  \me{||\mvec{w}{l,k,n}||_{2}^{2} = 1} and independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
+where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
+In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams.
+Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
 \begin{equation}\label{eq:SINR}
-\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
+\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
 \end{equation}
-With the infinite buffer model assumption, let \me{Q_k} be the number of backlogged packets which are destined for the user \me{k} at a given scheduling instant.
+Let \me{Q_k} be the number of backlogged packets which are destined for the user \me{k} at a given scheduling instant.
 The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets or bits arriving for the user \me{k} at the \me{{i}^\mathrm{th}} instant.
-The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, represented by \me{Q_k(i+1)}, follows
+The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, represented by \me{Q_k(i+1)}, is given by
 \begin{equation}
-Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i),
+Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i)
 \label{eqn-2a}
@@
 \begin{equation}
-t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i),
+t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i)
 \end{equation}
 where \me{t_{l,k,n}} denotes the transmitted bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{\log_2(1 + \gamma_{l,k,n})}\footnote{assuming Gaussian signaling} for the \ac{SINR} of \me{\gamma_{l,k,n}}.
-Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.
+The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} of \me{\gamma_{l,k,n}}.\footnote{This can be achieved by Gaussian signaling} Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-08-04 Report/wsrm_formulation.tex
temp updates

@@
 \underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
-\text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}),\IEEEyessubnumber \label{eqn-6.2} \\
+\text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\left | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n} \right |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}),\IEEEyessubnumber \label{eqn-6.2} \\
   & \quad & \beta_{l,k,n} \geq  N_0 \|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-6.3} \\
-  & \quad &\eqref{eqn-4.3} \IEEEyessubnumber
+  & \quad &\eqref{eqn-4.3}, \IEEEyessubnumber
 \end{IEEEeqnarray}
-where \me{\beta_{l,k,n}} denotes the total interference seen by the \me{l^\mathrm{th}} stream of the user \me{k} on the \me{n^\mathrm{th}} sub-channel and let \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} be the vector which needs to be identified for the optimal allocation.
+where \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} be the vector which needs to be identified for the optimal allocation.
 In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}.
 However, this step is without loss of optimality leads to the same solution, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}.
-Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the interference seen by the user \me{k \in \mathcal{U}_b}.
+Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by the user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}.
 The problem in \eqref{eqn-6} is known to be NP-hard even for the single antenna case \cite{wmmse_shi,kaleva2013primal}.
@@
 Towards this end, we resort to the traditional coordinate descent technique by fixing the transmit beamformers, and find the optimal linear receivers.
-The optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t the \me{\mbf{w}_{l,k,n}}, and the closed form solution is given by
+Recall the original coordinate descent method assumes that the optimization variables belong to disjoint sets (Cartesian product of sets, to be precise) \cite{xu2013block}.
+The optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t the \me{\mbf{w}_{l,k,n}}.
+In order to reduce the complexity involved in the receiver design, we use the \ac{MMSE} receiver \cite{christensen2008weighted,wmmse_shi}, given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-10}
 \mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}, \IEEEyessubnumber \\
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R}, \IEEEyessubnumber
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R}. \IEEEyessubnumber
 \end{IEEEeqnarray}
-which is the \ac{MMSE} receive beamformers \cite{christensen2008weighted,wmmse_shi,kaleva2013primal}.
 
@@
  \SetKwInput{KwInit}{Initialize}
- \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
- \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
- update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}}\;
+ \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}.
+ \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}.
+ \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}.
+ update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}}.\;
  \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
@@
  solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9} \;
- update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,n}} obtained from the previous step \;
- $i = i + 1$ \;
+ update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,n}} obtained from the previous step.
+\;
+ $i = i + 1$. \;
  }
- update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
- $j = j + 1$ \;
+ update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
+ $j = j + 1$. \;
  }

### 2014-08-05 Report/dual_approach.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>

@@
-In contrast to the \acl{PD} problem, the \acf{DD} relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
+In this section, we discuss the \ac{ADMM} decomposition method, which is basically based on the \acf{DD}, but shows better convergence properties.
+In contrast to the \acl{PD} problem, the \acf{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
 In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution.
@@
 &\quad& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \IEEEyessubnumber \\
-n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
+n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right | \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 Let \me{\mbfa{\nu}^{\set{b_k}}} represents the stacked dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} used in the subproblems.
-The equality constraint for the local and the consensus interference vector \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} present in each subproblem is relaxed by the taking the partial Lagrangian for the constraint as
-\begin{IEEEeqnarray}{rCl} \label{eqn-dual-2} \label{eqn-dual-1}
-\underset{\substack{\gamma_{l,k,n}, \nu^{\set{b_k}}_{l,k,n,b},\mvec{W}{k,n} \\ \mvec{M}{k,n}, \beta_{l,k,n}, \zeta^{\set{b_k}}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}}T} \left ( \mbfa{\zeta}^{\set{b_k}} - \mbfa{\zeta}(b_k) \right ) \IEEEyessubnumber \label{eqn-dual-2a} \\
-\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&&\quad + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b_k},k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta^{\set{b_k}}_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-dual-1d} \\
-&& \zeta^{\set{b_k}}_{\pr{l},\pr{k},n,{b_k}} \geq \sum_{k \in \mc{U}_b} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b_k,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b_k}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-dual-1e} \\
-&\quad& \mbfa{\nu}^{\set{b_k}} \in \mathbb{R}^{n_{b_k}}_+, \; \eqref{eqn-8} \; \text{and} \; \eqref{eqn-primal-1c}. \IEEEyessubnumber \label{eqn-dual-1f}
-\end{IEEEeqnarray}
-The global interference variable \me{\mbfa{\zeta}(b_k)} in \eqref{eqn-dual-2a} can be dropped without affecting the optimal solution, since it is fixed for a given iteration.
-Instead of solving the dual decomposition problem defined in \eqref{eqn-dual-2}, we consider the \ac{ADMM} scheme which has better convergence properties as discussed in \cite{bertsekas1999nonlinear,boyd2011distributed}.
-
 In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} at the \acp{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} in the objective function.
 At optimality, the locally assumed and the consensus interference values will be equal,  providing no contribution to the objective function.
-The optimal step size used to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed}.
-Now, the subproblem at each \ac{BS} for the \me{\ith{i}} iteration is given by
+The optimal step size used to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed,bertsekas1999nonlinear}.
+The equality constraint for the local and the consensus interference vector \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} present in each subproblem is relaxed by the taking the partial Lagrangian.
+Now, the subproblem at the \ac{BS} \me{b} for the \me{\ith{i}} iteration is given by
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{M}{k,n},\mvec{W}{k,n} \\ \beta_{l,k,n}, \zeta^{\set{b_k}(i)}_{l,k,n,b}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q + \mbfa{\nu}^{{\set{b_k}(i-1)}T} \mbfa{\zeta}^{\set{b_k}(i)} + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i-1)}(b_k)}_{\text{consensus values}} - \underbrace{\mbfa{\zeta}^{\set{b_k}(i)}}_{\text{local values}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
-\text{subject to} & \quad & \eqref{eqn-dual-1d} - \eqref{eqn-dual-1f} \IEEEyessubnumber \label{eqn-dual-3b},
+\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} - \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{locals}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
+\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
+&& \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-dual-1d} \\
+&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-dual-1e} \\
+&\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-primal-1c} \IEEEyessubnumber \label{eqn-dual-1f}
 \end{IEEEeqnarray}
@@
 
+Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}.
 Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}.
@@
 \begin{equation}
-\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
+\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right )
 \label{zeta_update}
@@
 \begin{equation}\label{dual-sg-update}
-\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ), \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}.
+\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ), \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}
 \end{equation}

### 2014-08-05 Report/ieee_journal.tex
updated intro
temp updates
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>

@@
 
+\acused{MU-MIMO}
+
 \begin{abstract}
@@
 \section{Introduction} \label{sec-1}
-%\input{introduction}
+\input{introduction}
 
-\section{System Model and Problem Formulation}
+\section{System Model and Problem Formulation} \label{sec-2-3.2}
 \subsection{System Model} \label{sec-2}
@@
 
-\section{Queue Minimizing Precoder Designs} \label{sec-3}
+\section{Proposed Queue Minimizing Precoder Designs} \label{sec-3}
 \input{queue_minimizing_intro}
@@
 
-\subsection{\acs{JSFRA} scheme via Successive Convex Approximation (\acs{SCA})}
+\subsection{\acs{JSFRA} scheme via Successive Convex Approximation (\acs{SCA})} \label{sec-3.2.1}
 \input{problem_formulation}
@@
 
-\subsection{Primal Decomposition Approach} \label{sec-4.1}
+\subsection{Decomposition based Approaches}
+
+\subsubsection{Primal Decomposition Approach} \label{sec-4.1}
 
@@
 
-\subsection{\ac{ADMM} approach} \label{sec-4.2}
+\subsubsection{\ac{ADMM} approach} \label{sec-4.2}
 
@@
 
-\subsection{Distributed MSE Formulation} \label{sec-4.3}
+\subsection{Decomposition by solving \ac{KKT} equations} \label{sec-4.3}
 
@@
 
-\section{Conclusions}
+\section{Conclusions} \label{sec-6}
 

### 2014-08-05 Report/kkt_mse_approach.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>

@@
 \begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
-\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \alpha_{l,k,n}, \\ \delta_{b},\sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
+\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
-\alpha_{l,k,n} : & \hspace{0.5cm} & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \\ \nonumber
-&\hspace{0.5cm}& \quad {} + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
+\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 \\ \nonumber
+&\hspace{0.5cm}& \qquad {} \qquad {} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
 \sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \geq t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
-\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
+\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 \mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}, \IEEEyessubnumber \label{kkt-mse-4.6} \\
-\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2, \IEEEyessubnumber \label{kkt-mse-4.4} \\
-t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\sigma_{l,k,n}^{(i)} &=& \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
-\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \Big ( \rfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \Big ). \IEEEyessubnumber \label{kkt-mse-4.1}
+\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
+\sigma_{l,k,n}^{(i)} &=& \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}  \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \frac{\left [ \sigma_{l,k,n}^{(i)} \right ]^+}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
+\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
 \end{IEEEeqnarray}
@@
 
-The receive beamformers from the users can be informed to the coordinating \acp{BS} by using the precoded uplink pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\mvec{W}{k,n}} evaluated at the receivers.
-Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\mvec{W}{k,n}^{\herm \, (i-1)} \mvec{H}{b,k,n}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS} \cite{komulainen2013effective}.
+The receive beamformers from the users can be informed to the coordinating \acp{BS} by using the precoded uplink pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}} evaluated at the receivers.
+Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\sqrt{\alpha_{l,k,n}^{(i-1)}} \mvec{w}{l,k,n}^{\ast \, (i-1)} \mvec{H}{b,k,n}^{\mathrm{T}}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS} \cite{komulainen2013effective}, \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}.
 The algorithmic representation of the \ac{KKT} based scheme is shown in Algorithm.
@@
  \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
- set the maximum iteration counter \me{I_{\max}} to a valid number \;
- for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
- \Repeat{convergence or \me{i \geq I_{\max}}}{
-	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} with \me{\delta_b} using \eqref{kkt-mse-4.3} by the bisection method satisfying \eqref{kkt-mse-1.4} \;
-	evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(i)}} by \eqref{kkt-mse-4.6} \;
-	update the \ac{MSE} variable \me{\epsilon_{l,k,n}^{(i)}} and the throughput variable \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} \;
-	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2} \;
-	exchange the transmit and the receive precoders \me{\mvec{M}{k,n}^{(i)}, \mvec{W}{k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
-	$i = i + 1$ \;
+ set the maximum iteration counter \me{I_{\max}} to a valid number. \;
+ \Repeat{until convergence or \me{j \geq J_{\max}}}{
+ \lForEach{\ac{BS} \me{b \in \mc{B}}}
+ \Repeat{until convergence or \me{i \geq I_{\max}}}{
+	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is identified by the bisection method satisfying \eqref{kkt-mse-1.4}. \;
+	update the \ac{MSE} \me{\epsilon_{l,k,n}^{(i)}} and the throughput \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}. \;
+	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2}. \;
+	$i = i + 1.$ \;
+  }
+  \me{j = j + 1}. \;
+  evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(i)}} using \eqref{kkt-mse-4.6}. \;
+  exchange the receive precoders \me{\mvec{W}{k,n}^{(i)}} and the dual variables \me{\alpha_{l,k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} using the uplink precoded pilots. \;
   }
@@
 \end{algorithm}
+
+\subsubsection*{Convergence}
+The iterative method presented in Algorithm \ref{algo-4} converges to the stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge.
+The convergence of the dual variable is guaranteed, since the problem is convex once we fix the receive precoders \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}.
+Once the dual variables are converged or iterated to a certain accuracy, the receivers are updated using the \ac{MMSE} objective.
+In this algorithm, when \me{t_k > Q_k},

### 2014-08-05 Report/mse_formulation.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>

@@
-In this section, we present an alternative approach for solving the \acl{QM} \ac{JSFRA} problem by using the \ac{MSE} equivalence with the the achievable capacity presented in \cite{viswanath1999optimal,mse_duality}.
-It is given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon(\gamma)} \right )}, where \me{\epsilon(\gamma) = {1} / {(1 + \gamma)}} is the \ac{MSE} for decoding the transmitted symbol at the reciever employing the \ac{MMSE} equalizer and \me{C(\gamma)} is the achievable capacity for the \ac{SINR} of \me{\gamma}.
-Using this equivalence, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \ac{MU-MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}.
-In this, we use the relation between the \ac{MSE} and the achievable capacity to solve the \ac{JSFRA} problem by employing \ac{MMSE} receivers.
+In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable capacity for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}.
+The \ac{MSE} for the data symbol, represented as \me{\epsilon_{l,k,n}}, is given by
+\begin{subeqnarray} \label{mse-error}
+\epsilon_{l,k,n} &=& \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] \\
+ &=&  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+\end{subeqnarray}
+where \me{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}} denotes the transmit and the receive beamformer and \me{\hat{d}_{l,k,n}} is the received symbol as in \eqref{eqn-1}.
+Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver shown in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
+\begin{equation} \label{eqn-mse-eq}
+\epsilon_{l,k,n} = \dfrac{1}{1 + \gamma_{l,k,n}}
+\end{equation}
+where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}.
+Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \ac{MU-MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}.
 
@@
 \underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
-\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
+\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
  & \quad \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
-& \quad \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
+& \quad \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
 \end{IEEEeqnarray}
@@
 \begin{IEEEeqnarray}{rCl}
-- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}.
+- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}
 \label{mse-lin}
@@
 \text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
-& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}.
+& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}
 \end{IEEEeqnarray}

### 2014-08-05 Report/sub_channel_wsrm.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>

@@
 
-The proposed \acf{QM} \ac{SRA} scheme decouples the problem by fixing the power across each sub-channel to a constant value as compared to the global power constraint defined by \eqref{eqn-4.3}.
+The proposed \acf{QM} \ac{SRA} scheme decouples the problem by fixing the power across each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}.
 In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization.
@@
 The current scheme is very sensitive to the order in which the sub-channels are selected for the optimization problem.
+The algorithmic representation of the \acf{QM} \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
+\begin{algorithm}
+ \SetAlgoLined
+ \DontPrintSemicolon
+ \BlankLine
+ \SetKwInput{KwInit}{Initialize}
+ \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
+ \KwIn{permute \me{\mathcal{C} \rightarrow \tilde{\mathcal{C}}}}
+ \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
+ update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{C}}(n)}. \;
+ \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
+ \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
+ update \me{\mvec{w}{l,k,\hat{n}}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,\hat{n}}}.\;
+ \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
+ \Repeat{\ac{SCA} convergence or \me{i \geq I_{\max}}}{
+ solve for the transmit precoders \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} \;
+ update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,\hat{n}}}, \me{\tilde{q}_{l,k,\hat{n}}} and \me{\tilde{\beta}_{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,\hat{n}}} obtained from the previous step.
+\;
+ $i = i + 1$. \;
+ }
+ update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
+ $j = j + 1$. \;
+ }
+ }
+ \caption{Algorithm of \acs{SRA} scheme}
+ \label{algo-5}
+\end{algorithm}

### 2014-08-05 Report/wsrm_formulation.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>

@@
 \underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
-\text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\left | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n} \right |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}),\IEEEyessubnumber \label{eqn-6.2} \\
-  & \quad & \beta_{l,k,n} \geq  N_0 \|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-6.3} \\
-  & \quad &\eqref{eqn-4.3}, \IEEEyessubnumber
+\text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\left | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n} \right |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \label{eqn-6.2} \\
+  & \quad & \beta_{l,k,n} \geq  N_0 \|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
+  & \quad &\eqref{eqn-4.3} \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-Towards this end, we resort to the traditional coordinate descent technique by fixing the transmit beamformers, and find the optimal linear receivers.
+Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and find the optimal transmit beamformers.
 Recall the original coordinate descent method assumes that the optimization variables belong to disjoint sets (Cartesian product of sets, to be precise) \cite{xu2013block}.
-The optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t the \me{\mbf{w}_{l,k,n}}.
-In order to reduce the complexity involved in the receiver design, we use the \ac{MMSE} receiver \cite{christensen2008weighted,wmmse_shi}, given by
-\begin{IEEEeqnarray}{rCl}\label{eqn-10}
-\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}, \IEEEyessubnumber \\
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R}. \IEEEyessubnumber
-\end{IEEEeqnarray}
 
-The problem now is to find optimal transmit beamformers for a given set of linear receivers which is a challenging task.
-We note that for fixed $\mvec{w}{l,k,n}$, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
+By fixing the receivers, the problem now is to find optimal transmit beamformers for a given set of linear receivers which is a challenging task.
+We note that for fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
 Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}.
@@
 \begin{subeqnarray} \label{eqn-wsrm-expr}
-p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
-q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}},
+p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \\
+q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}
 \end{subeqnarray}
@@
 \label{eqn-8}
-2 \dfrac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \dfrac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \dfrac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \dfrac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
+2 \dfrac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \dfrac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \dfrac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \dfrac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}
 \end{equation}
@@
 \underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0\|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \IEEEyessubnumber \label{eqn-9.1c} \\
-& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
-& \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}.
+\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0\|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-9.1c} \\
+& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
+& \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}
 \end{IEEEeqnarray}
+
+Now, the optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}}, which is given by
+\begin{IEEEeqnarray}{rCl}\label{eqn-9--1}
+\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{w}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
+\text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}
+\end{IEEEeqnarray}
+When the number of queued packets for each user is significantly large, the queue minimizing objective is in fact the sum rate maximization problem.
+Since the optimal receivers for the sum rate maximization problem with the fixed transmit precoders is the \ac{MMSE} receivers, we can use the \ac{MMSE} receiver as the receive beamformers without affecting the optimal solution.
+When the number of queued packets are smaller than the achievable transmission rate of the users, the receiver defined by \eqref{eqn-9--1} provides better solution compared to the \ac{MMSE} based receivers given by
+\begin{IEEEeqnarray}{rCl}\label{eqn-10}
+\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n} \IEEEyessubnumber \\
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber
+\end{IEEEeqnarray}
+For the single receive antenna scenario, the receivers in \eqref{eqn-9--1} and \eqref{eqn-10} achieves the same optimal point, since the \ac{SINR} expression is independent of the receive beamformer.
 
@@
  \SetKwInput{KwInit}{Initialize}
- \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}.
- \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}.
- \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}.
+ \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
+ \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
+ \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
  update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}}.\;
@@
  }
- update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
+ update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
  $j = j + 1$. \;

### 2014-08-06 Report/kkt_mse_approach.tex
Updated KKT MSE and figures

@@
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\sigma_{l,k,n}^{(i)} &=& \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}  \IEEEyessubnumber \label{kkt-mse-4.2} \\
-\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \frac{\left [ \sigma_{l,k,n}^{(i)} \right ]^+}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
+\sigma_{l,k,n}^{(i)} &=& \max{\left (0, \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right )}  \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \rfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
 \mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
@@
 
-The receive beamformers from the users can be informed to the coordinating \acp{BS} by using the precoded uplink pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}} evaluated at the receivers.
-Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\sqrt{\alpha_{l,k,n}^{(i-1)}} \mvec{w}{l,k,n}^{\ast \, (i-1)} \mvec{H}{b,k,n}^{\mathrm{T}}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS} \cite{komulainen2013effective}, \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}.
-The algorithmic representation of the \ac{KKT} based scheme is shown in Algorithm.
+In order to perform the distributed approach, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE}, and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} using the transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}.
+Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using the uplink precoded pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}} evaluated at the receivers.
+Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS}, \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}.
+The algorithmic representation of the distributed \ac{MSE}-\ac{KKT} scheme is shown in Algorithm.
 \ref{algo-4}.
+In this approach, the coordinating \acp{BS} are required to perform short transmissions to update the transmit and the receive beamformers before the actual data transmission.
 \begin{algorithm}
@@
  \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
- set the maximum iteration counter \me{I_{\max}} to a valid number. \;
+ set the maximum iteration counter \me{I_{\max},J_{\max}} to a valid number. \;
  \Repeat{until convergence or \me{j \geq J_{\max}}}{
@@
 	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is identified by the bisection method satisfying \eqref{kkt-mse-1.4}. \;
-	update the \ac{MSE} \me{\epsilon_{l,k,n}^{(i)}} and the throughput \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}. \;
-	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2}. \;
+    update \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at the receivers using the transmit precoders \me{\mvec{M}{k,n}^{(i)}} from all \acp{BS}.
+\;
+    perform precoded uplink pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j)}}. \;
     $i = i + 1.$ \;
   }
+ evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(j+1)}} using \eqref{kkt-mse-4.6}. \;
+ inform \acp{BS} using uplink precoded pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j+1)}}. \;
  \me{j = j + 1}. \;
-  evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(i)}} using \eqref{kkt-mse-4.6}. \;
-  exchange the receive precoders \me{\mvec{W}{k,n}^{(i)}} and the dual variables \me{\alpha_{l,k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} using the uplink precoded pilots. \;
  }
@@
 The iterative method presented in Algorithm \ref{algo-4} converges to the stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge.
-The convergence of the dual variable is guaranteed, since the problem is convex once we fix the receive precoders \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}.
+The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive precoders \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}.
 Once the dual variables are converged or iterated to a certain accuracy, the receivers are updated using the \ac{MMSE} objective.
-In this algorithm, when \me{t_k > Q_k},
+In this algorithm, when \me{t_k > Q_k}, \me{\sigma_{l,k,n}} will be zero (dual feasibility), thereby reducing the priority weights \me{\alpha_{l,k,n}} present in the transmit precoder expression in \eqref{kkt-mse-4.3}.

### 2014-08-06 Report/simulation_intro.tex
Updated KKT MSE and figures

The simulations carried out in this work considered the path loss varying uniformly across all users in the system with the channels drawn from the i.i.d samples. The queues are generated based on the poisson process with the average values specified in each section presented.

### 2014-08-06 Report/kkt_mse_approach.tex
kkt corrections

@@
  \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
+ for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
  set the maximum iteration counter \me{I_{\max},J_{\max}} to a valid number. \;
+ initialize \me{j = 0}. \;
  \Repeat{until convergence or \me{j \geq J_{\max}}}{
- \lForEach{\ac{BS} \me{b \in \mc{B}}}
+ initialize \me{i = 0}. \;
  \Repeat{until convergence or \me{i \geq I_{\max}}}{
@@
     perform precoded uplink pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j)}}. \;
-    $i = i + 1.$ \;
+    \me{i = i + 1} \;
   }

### 2014-08-06 Report/simulation_distributed.tex
kkt corrections

@@
 \ref{fig-d-3.1} showing inferior queue minimizing performance.
-This due to the lack of the rate bounding constraint \eqref{kkt-mse-4.2}, which is simply given by \me{\sigma_{l,k,n}^{(i)} = \frac{a_k}{\log(2)}} providing no control for the excess allocations.
+This due to the lack of the rate bounding constraint \eqref{kkt-mse-4.2}, which is simply given by \me{\sigma_{l,k,n}^{(i)} = \frac{a_k}{\log(2)}}, providing no control for the excess allocations.
 For \me{q=2}, when the allocated rate exceeds the available queued bits, \me{\sigma_{l,k,n}^{(i)}} will be negative, thereby reducing \eqref{kkt-mse-4.1} as \me{\alpha_{l,k,n}^{(i)} < \alpha_{l,k,n}^{(i-1)}} to reduce the priority for the corresponding user in the next iteration.

### 2014-08-07 Report/simulation_distributed.tex
stfloats

@@
 The performance of the distributed algorithms are studied in this section by comparing with the centralized algorithms.
-The total number of queued packets after the current allocation and the total sum rate achieved by the network are used as the performance measures.
+The performance is compared using the total number of backlogged packets after each \ac{SCA} update points.
 Fig.
-\ref{fig-d-1} shows the performance of the algorithms for the system configuration represented by \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at each \ac{BS}.
+\ref{fig-d-1} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}.
 Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}.
-Fig.
-\ref{fig-d-1.1} shows the total number of backlogged packets  and Fig.
-\ref{fig-d-1.2} plots the total rate achieved by different algorithms after each \ac{SCA} update.
 As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the choice of the step size used in the subgradient update.
@@
 The Fig.
-\ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions of the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} update points.
+\ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points.
 In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations by exchanging either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme.
@@
 \ref{fig-d-1} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
-The plot also includes the \ac{Q-WSRM} which performs similar to the other centralized schemes discussed in this paper.
 \begin{figure*}
 \centering
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\columnwidth]{fig-3}
-\caption{Queue deviation}
-\label{fig-d-1.1}
-\end{subfigure}
+\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
+\includegraphics[width=0.48\textwidth]{fig-3}
+\label{fig-d-1}
+}
 \hfill
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\columnwidth]{fig-4}
-\caption{Sum rate performance}
-\label{fig-d-1.2}
-\end{subfigure}
-\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} model}
-\label{fig-d-1}
+\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace}]{
+\includegraphics[width=0.48\textwidth]{fig-5}
+\label{fig-d-2}
+}
+\caption{Number of backlogged packets at each \ac{SCA} points}
+\label{fig-d}
 \end{figure*}
@@
 The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively.
-The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{\mathbb{U}(0,-6)} dB.
+The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{[0,-6]} dB.
 The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.
@@
 It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
-\begin{figure*}
-\centering
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{fig-5}
-\caption{Queue deviation}
-\end{subfigure}
-\hfill
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{fig-6}
-\caption{Sum rate performance}
-\end{subfigure}
-\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
-\label{fig-d-2}
-\end{figure*}
+% \begin{figure*}
+% \centering
+% \begin{subfigure}{0.49\textwidth}
+% \includegraphics[width=\textwidth]{fig-5}
+% \caption{Queue deviation}
+% \end{subfigure}
+% \hfill
+% \begin{subfigure}{0.49\textwidth}
+% \includegraphics[width=\textwidth]{fig-6}
+% \caption{Sum rate performance}
+% \end{subfigure}
+% \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
+% \label{fig-d-2}
+% \end{figure*}
 
@@
 \centering
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{fig-9}
-\caption{Queue deviation}
-\label{fig-d-3.1}
-\end{subfigure}
+\subfloat[][Queue deviation]{
+\includegraphics[width=0.48\textwidth]{fig-9}
+\label{fig-d-3.1}}
 \hfill
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[width=\textwidth]{fig-10}
-\caption{Sum rate performance}
-\label{fig-d-3.2}
-\end{subfigure}
+\subfloat[][Sum rate performance]{
+\includegraphics[width=0.48\textwidth]{fig-10}
+\label{fig-d-3.2}}
 \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}

### 2014-08-09 Report/simulation_distributed.tex
updated figures

@@
 We compare the performance of the \ac{MSE}-\ac{KKT} scheme for the exponents \me{q=1} and \me{q=2}.
-The performance of the \me{\ell_1} \ac{JSFRA} scheme performs the best over other algorithms in minimizing the total number of queued bits after the current allocation due to its greedy approach.
+The performance of the \me{\ell_1} \ac{JSFRA} scheme performs the best over other algorithms in minimizing the total number of queued bits after the current allocation due to the greedy approach of the objective.
 The inclusion of the additional second order rate term in \eqref{pf-1}, the \me{\ell_2} \ac{JSFRA} scheme achieves different performance than the \ac{Q-WSRM} scheme as shown in Fig.
@@
 \subfloat[][Queue deviation]{
-\includegraphics[width=0.48\textwidth]{fig-9}
+\includegraphics[width=0.48\textwidth]{fig-9-2}
 \label{fig-d-3.1}}
@@
 \label{fig-d-3.2}}
-\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}
+\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
 \label{fig-d-3}

### 2014-08-09 Report/simulation_results.tex
stfloats
updated figures

@@
 The number of packets waiting at the transmitter for each user is given by \me{Q_k = 5,8} and \me{6} bits respectively.
-With this configuration, the resources allocated for the users on each sub-channel by various algorithms are listed in Table \ref{tbl-1}.
+With this configuration, the resources allocated for the users on each sub-channel by various algorithms are shown in Fig.
+\ref{tbl-1}.
 
-Table \ref{tbl-1} lists the sub-channel wise channel seen by the users followed by the assigned rates over each sub-channel by three different algorithms, \ac{Q-WSRM} allocation, \ac{JSFRA} scheme and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} precoder design proposed in \cite{wmmse_shi}.
+Fig.
+\ref{tbl-1} plots the sub-channel wise channel seen by the users followed by the assigned rates over each sub-channel by three different algorithms, \ac{Q-WSRM} allocation, \ac{JSFRA} scheme and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} precoder design proposed in \cite{wmmse_shi}.
 The performance metric used for the comparison of different algorithms is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
-It can be seen from Table \ref{tbl-1}, that the \ac{Q-WSRM} scheme provides more priority to the third user with \me{Q_{3} = 6} bits compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel.
+It can be seen from Fig.
+\ref{tbl-1}, that the \ac{Q-WSRM} scheme provides more priority to the third user with \me{Q_{3} = 6} bits compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel.
 Int contrast to the \ac{Q-WSRM} scheme, the \ac{JSFRA} scheme assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
-\begin{table*}
+%\begin{table*}
+%\centering
+%\renewcommand{\arraystretch}{1.25} \scriptsize
+%\begin{tabular}{|*{14}{c|}}
+%\hline
+%\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRM approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
+%\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(\emph{backpreassure} algorithm)} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
+%\cline{3-14}
+% && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
+%\hline
+%\me{1} & \me{5} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.91} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
+%\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.46}  &  \me{3.54} & \me{0} &  \me{4.36}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
+%\me{3} & \me{6} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{5.72} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{5.79} & \me{5.81} &  \me{0}  &  \me{0} \\
+%\hline
+%\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{5.28} bits} & \multicolumn{3}{c|}{\me{3.91} bits} & \multicolumn{3}{c|}{\me{5.28} bits} \\
+%\hline
+%\end{tabular}
+%\caption{Sub channel wise allocation for a scheduling instant}
+%\label{tbl-1}
+%\end{table*}
+\begin{figure}
 \centering
-\renewcommand{\arraystretch}{1.25} \scriptsize
-\begin{tabular}{|*{14}{c|}}
-\hline
-\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRM approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
-\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(\emph{backpreassure} algorithm)} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
-\cline{3-14}
- && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
-\hline
-\me{1} & \me{5} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.91} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
-\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.46}  &  \me{3.54} & \me{0} &  \me{4.36}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
-\me{3} & \me{6} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{5.72} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{5.79} & \me{5.81} &  \me{0}  &  \me{0} \\
-\hline
-\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{5.28} bits} & \multicolumn{3}{c|}{\me{3.91} bits} & \multicolumn{3}{c|}{\me{5.28} bits} \\
-\hline
-\end{tabular}
-\caption{Sub channel wise allocation for a scheduling instant}
+\includegraphics[width=\columnwidth]{tbl-1}
+\caption{Allocation for a \ac{SISO} Model comparing different Algorithms}
 \label{tbl-1}
-\end{table*}
+\end{figure}
 
@@
 \centering
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[width=1.0\textwidth]{fig-1-1}
-\caption{\me{4 \times 1} system}
-\label{fig-1}
-\end{subfigure}
+\subfloat[][\me{N_T \times N_R = 4 \times 1} system]{
+\includegraphics[width=0.48\textwidth]{fig-1-2}
+\label{fig-1}}
 \hfill
-\begin{subfigure}{0.49\textwidth}
-\includegraphics[width=1.0\textwidth]{fig-2-1}
-\caption{\me{4 \times 2} system}
-\label{fig-2}
-\end{subfigure}
-\caption{Convergence plot for \me{\lbrace N,N_B,K \rbrace = \lbrace 3,3,9 \rbrace} model}
+\subfloat[][\me{N_T \times N_R = 4 \times 2} system]{
+\includegraphics[width=0.48\textwidth]{fig-2-1}
+\label{fig-2}}
+\caption{Number of backlogged packets at the \ac{SCA} update points for \me{\lbrace N,N_B,K \rbrace = \lbrace 3,3,9\rbrace} model}
+\label{fig-a}
 \end{figure*}
@@
 \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas.
-\begin{table}
+%\begin{table}
+%\centering
+%\renewcommand{\arraystretch}{1.25} \scriptsize
+%\begin{tabular}{|c|*{8}{c}|c|}
+%\hline
+%\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
+%\hline
+%\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
+%\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
+%\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
+%\hline
+%\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
+%\cline{1-9}
+%\end{tabular}
+%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
+%\label{tbl-3}
+%\end{table}
+\begin{figure}
 \centering
-\renewcommand{\arraystretch}{1.25} \scriptsize
-\begin{tabular}{|c|*{8}{c}|c|}
-\hline
-\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
-\hline
-\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
-\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
-\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
-\hline
-\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\    
-\cline{1-9}
-\end{tabular}
+\includegraphics[width=\columnwidth]{tbl-2}
 \caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
 \label{tbl-3}
-\end{table}
+\end{figure}
 
-The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Table \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas.
-The configuration is mentioned in the caption of Table \ref{tbl-3} along with the number of queued bits for each user.
+The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Fig.
+\ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas.
+The configuration is mentioned in the caption of Fig.
+\ref{tbl-3} along with the number of queued bits for each user.
 It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits.

### 2014-08-11 Report/dual_approach.tex
updated tex

@@
     }
-    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
+    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} by exchanging the recent precoders \me{\mvec{m}{l,k,n}} \;
     exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;

### 2014-08-11 Report/primal_approach_appendix.tex
Corrections after first reading
updated tex

@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-primal-1}
-\underset{\substack{\gamma_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \IEEEyessubnumber \label{eqn-primal-1a} \\
+\underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n} \\ \mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b_k} \|_q \IEEEyessubnumber \label{eqn-primal-1a} \\
 \text{subject to}&\quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_{b_k}} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \IEEEyessubnumber \label{eqn-primal-1c} \\

### 2014-08-11 Report/simulation_distributed.tex
updated tex

@@
 
-The performance of the \ac{MSE}-\ac{KKT} scheme discussed in Section \ref{sec-4.3} is presented in Fig.
-\ref{fig-d-3}.
-It compares the \ac{JSFRA} scheme with \me{\ell_1} and \me{\ell_2} norm cases in addition to the \ac{Q-WSRM} scheme.
-We compare the performance of the \ac{MSE}-\ac{KKT} scheme for the exponents \me{q=1} and \me{q=2}.
-The performance of the \me{\ell_1} \ac{JSFRA} scheme performs the best over other algorithms in minimizing the total number of queued bits after the current allocation due to the greedy approach of the objective.
-The inclusion of the additional second order rate term in \eqref{pf-1}, the \me{\ell_2} \ac{JSFRA} scheme achieves different performance than the \ac{Q-WSRM} scheme as shown in Fig.
-\ref{fig-d-3}.
-
-It can be seen from Fig.
-\ref{fig-d-3.2}, that the sum rate of the \me{q=1} \ac{KKT} approach outperforms other schemes in spite of Fig.
-\ref{fig-d-3.1} showing inferior queue minimizing performance.
-This due to the lack of the rate bounding constraint \eqref{kkt-mse-4.2}, which is simply given by \me{\sigma_{l,k,n}^{(i)} = \frac{a_k}{\log(2)}}, providing no control for the excess allocations.
-For \me{q=2}, when the allocated rate exceeds the available queued bits, \me{\sigma_{l,k,n}^{(i)}} will be negative, thereby reducing \eqref{kkt-mse-4.1} as \me{\alpha_{l,k,n}^{(i)} < \alpha_{l,k,n}^{(i-1)}} to reduce the priority for the corresponding user in the next iteration.
-The performance of the closed form solution using the \ac{KKT} solution performs similar to the centralized schemes with \me{q=2} by limiting the rates beyond the available queued packets.
+Fig.
+\ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions.
+In Fig.
+\ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point.
+Fig.
+\ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective.
+The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches.
+The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}.
+The additional condition can be justified due to the dropping of absolute value operator from the objective.
+It can be seen that the heuristic method is not converged to the optimal point but oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
 \begin{figure*}
@@
 \end{figure*}
+
+The objective values are mentioned in the legend for all the schemes, since the objective of \me{\ell_2} norm is not the same as \me{\ell_1} norm, which is used for the plot.
+The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables are not allowed to converge in between the \ac{SCA} steps in the \ac{KKT} approach.
+In the simulation, we update all the variables at each iteration due to the practical issues in the signaling between the \acp{BS}.
+The figure compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRM} scheme compared to the \me{\ell_2} norm which includes it.
+By dropping the squared rate variable, the \ac{Q-WSRM} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues.
+Contrastingly, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

### 2014-08-11 Report/simulation_results.tex
updated tex

@@
 \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas.
-%\begin{table}
+In this setup, we assume the queue sizes of the users are small enough to bring out the difference between the receiver performances for the \ac{JSFRA} solution discussed in Section \ref{sec-3.2.1}.
+In this scenario, the performance of the \ac{MMSE} receiver is not the same as the optimal receiver when the objective is not equivalent to the \ac{WSRM} approach.
+\begin{table}
+\centering
+\renewcommand{\arraystretch}{1.25} \scriptsize
+\begin{tabular}{|c|*{8}{c}|c|}
+\hline
+\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
+\hline
+\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
+\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
+\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
+\hline
+\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
+\cline{1-9}
+\end{tabular}
+\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
+\label{tbl-3}
+\end{table}
+%\begin{figure}
 %\centering
-%\renewcommand{\arraystretch}{1.25} \scriptsize
-%\begin{tabular}{|c|*{8}{c}|c|}
-%\hline
-%\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
-%\hline
-%\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
-%\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
-%\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
-%\hline
-%\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
-%\cline{1-9}
-%\end{tabular}
+%\includegraphics[width=\columnwidth]{tbl-2}
 %\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
 %\label{tbl-3}
-%\end{table}
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{tbl-2}
-\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
-\label{tbl-3}
-\end{figure}
+%\end{figure}
 
-The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Fig.
+The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Table.
 \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas.
-The configuration is mentioned in the caption of Fig.
+The configuration is mentioned in the caption of Table.
 \ref{tbl-3} along with the number of queued bits for each user.

### 2014-08-12 Report/ieee_journal.tex
Updated KKT MSE and figures
stfloats
updated tex
update

@@
-\documentclass[11pt,draftcls,onecolumn]{./../Styles/IEEEtran}
+\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 \usepackage[ruled]{algorithm2e}
-\usepackage{caption,subcaption}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools}
+\usepackage{subfig,subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools}
 
@@
 
-\subsection{Decomposition by solving \ac{KKT} equations} \label{sec-4.3}
+\subsection{Decomposition using \ac{KKT} equations in \ac{MSE} formulation} \label{sec-4.3}
 
@@
 \section{Simulation Results} \label{sec-5}
+\input{simulation_intro}
+
 \subsection{Centralized Solutions}

### 2014-08-12 Report/wsrm_formulation.tex
update

@@
 \end{IEEEeqnarray}
-When the number of queued packets for each user is significantly large, the queue minimizing objective is in fact the sum rate maximization problem.
-Since the optimal receivers for the sum rate maximization problem with the fixed transmit precoders is the \ac{MMSE} receivers, we can use the \ac{MMSE} receiver as the receive beamformers without affecting the optimal solution.
-When the number of queued packets are smaller than the achievable transmission rate of the users, the receiver defined by \eqref{eqn-9--1} provides better solution compared to the \ac{MMSE} based receivers given by
+Now, solving for the optimal receiver using \ac{KKT} conditions, we obtian the following expression in an iterative manner around the \ac{SCA} point \me{\mbf{\tilde{w}}_{l,k,n}}
+\begin{subeqnarray} \label{opt-rx}
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{(j,i)\neq (l,k)} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \\
+\mvec{w}{l,k,n} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \tilde{\mbf{w}}_{l,k,n} }{\|\tilde{\mbf{w}}_{l,k,n} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right ) \, \mvec{R}{l,k,n}^{-1} \, \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}
+\end{subeqnarray}
+where the fractional term inside the brace is a constant. It can be seen that the optimal receiver expression in \eqref{opt-rx} is the scaled version of the \ac{MMSE} receiver, which is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-10}
@@
 \end{IEEEeqnarray}
-For the single receive antenna scenario, the receivers in \eqref{eqn-9--1} and \eqref{eqn-10} achieves the same optimal point, since the \ac{SINR} expression is independent of the receive beamformer.
 

### 2014-08-13 Report/conclusions.tex
completed_journal

In this work, we presented the \acl{QM} objective to minimize the number of backlogged packets by designing the transmit precoders across the space-frequency dimension in a multi-cell \ac{MU} \ac{MIMO} system. We proposed the \ac{JSFRA} scheme, which adpots the \ac{SCA} technique to model the nonconvex constraint as a convex constraint in an iterative manner to design the precoders for the \acl{QM} objective. We also proposed an alternative approach using the \ac{MSE} relaxation for the same problem when the receive beamformers are based on the \ac{MMSE} receivers. The exponent used in the proposed formulation can be modified to achieve either greedy allocation or equally fair allocation. We also proposed the distributed solutions for the proposed centralized \ac{JSFRA} problem using the \ac{ADMM} method, which has better convergence behaviour compared to the primal decomposition. In addition, we also proposed an iterative algorithm based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme to design the preocders in a distributed manner using the closed form solutions.

### 2014-08-13 Report/simulation_results.tex
completed_journal

@@
 \ref{tbl-1}, that the \ac{Q-WSRM} scheme provides more priority to the third user with \me{Q_{3} = 6} bits compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel.
-Int contrast to the \ac{Q-WSRM} scheme, the \ac{JSFRA} scheme assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
+In contrast to the \ac{Q-WSRM} scheme, the \ac{JSFRA} scheme assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
 %\begin{table*}
@@
 \centering
-\subfloat[][\me{N_T \times N_R = 4 \times 1} system]{
+\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
 \includegraphics[width=0.48\textwidth]{fig-1-2}
@@
 \hfill
-\subfloat[][\me{N_T \times N_R = 4 \times 2} system]{
-\includegraphics[width=0.48\textwidth]{fig-2-1}
+\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,3,9,4,2\rbrace}]{
+\includegraphics[width=0.48\textwidth]{fig-2-2}
 \label{fig-2}}
-\caption{Number of backlogged packets at the \ac{SCA} update points for \me{\lbrace N,N_B,K \rbrace = \lbrace 3,3,9\rbrace} model}
+\caption{Number of backlogged packets at the \ac{SCA} update points}
 \label{fig-a}
@@
 \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas.
-In this setup, we assume the queue sizes of the users are small enough to bring out the difference between the receiver performances for the \ac{JSFRA} solution discussed in Section \ref{sec-3.2.1}.
-In this scenario, the performance of the \ac{MMSE} receiver is not the same as the optimal receiver when the objective is not equivalent to the \ac{WSRM} approach.
+As we can see from Fig.
+\ref{fig-2} that both the optimal and the \ac{MMSE} receiver achieves the same optimal point as compared to the \ac{JSFRA} scheme using \ac{MSE} reformulation.
+In all the schemes, the receive beamformers are updated at the \ac{SCA} update points instead of updating after the \ac{SCA} convergence as in Algorithm.
+\ref{algo-1}.
+Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
 \begin{table}

### 2014-08-13 Report/wsrm_formulation.tex
completed_journal

@@
 \end{IEEEeqnarray}
-Now, solving for the optimal receiver using \ac{KKT} conditions, we obtian the following expression in an iterative manner around the \ac{SCA} point \me{\mbf{\tilde{w}}_{l,k,n}}
+Now, by solving for the optimal receiver using \ac{KKT} conditions, we obtian the following expression for the receive beamformer \me{\mvec{w}{l,k,n}} in an iterative manner as
 \begin{subeqnarray} \label{opt-rx}
 \mvec{R}{l,k,n} &=& \displaystyle \sum_{(j,i)\neq (l,k)} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \\
-\mvec{w}{l,k,n} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \tilde{\mbf{w}}_{l,k,n} }{\|\tilde{\mbf{w}}_{l,k,n} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right ) \, \mvec{R}{l,k,n}^{-1} \, \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right ) \, \mvec{R}{l,k,n}^{-1} \, \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}
 \end{subeqnarray}
-where the fractional term inside the brace is a constant. It can be seen that the optimal receiver expression in \eqref{opt-rx} is the scaled version of the \ac{MMSE} receiver, which is given by
+where \me{\mvec{w}{l,k,n}^{(i-1)}} denotes the receive beamformer found in the earlier iteration, around which the linear relaxation is performed to convexify the problem in \eqref{eqn-9--1}.
+It can be seen that the optimal receiver expression in \eqref{opt-rx} is the scaled version of the \ac{MMSE} receiver, which is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-10}

### 2014-08-13 Report/conclusions.tex
Finalized before reviewing - 2

@@
 In this work, we presented the \acl{QM} objective to minimize the number of backlogged packets by designing the transmit precoders across the space-frequency dimension in a multi-cell \ac{MU} \ac{MIMO} system.
-We proposed the \ac{JSFRA} scheme, which adpots the \ac{SCA} technique to model the nonconvex constraint as a convex constraint in an iterative manner to design the precoders for the \acl{QM} objective.
+We proposed the \ac{JSFRA} scheme, which adopts the \ac{SCA} technique to model the nonconvex constraint as a convex constraint in an iterative manner to design the precoders for the \acl{QM} objective.
 We also proposed an alternative approach using the \ac{MSE} relaxation for the same problem when the receive beamformers are based on the \ac{MMSE} receivers.
@@
 We also proposed the distributed solutions for the proposed centralized \ac{JSFRA} problem using the \ac{ADMM} method, which has better convergence behaviour compared to the primal decomposition.
-In addition, we also proposed an iterative algorithm based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme to design the preocders in a distributed manner using the closed form solutions.
+In addition, we also proposed an iterative algorithm based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme to design the precoders in a distributed manner using the closed form solutions.

### 2014-08-13 Report/introduction.tex
Finalized before reviewing - 2

@@
 The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which are proportional to the mobile battery drain.
-In order to overcome the receiver complexity, \ac{OFDM} based transmissions are introduced for the wideband transmissions.
+In order to overcome the receiver complexity, \ac{OFDM} based transmissions are introduced for the wide band transmissions.
 To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension.
@@
 In the second method, we reformulate the \ac{JSFRA} problem using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders.
-For distributed implementation, we further proposed decentralized approaches based on primal and \ac{ADMM} scheme to identify the precoders independently across the \acp{BS} by exchanging limited information via backhaul.
+For distributed implementation, we further proposed decentralized approaches based on primal and \ac{ADMM} scheme to identify the precoders independently across the \acp{BS} by exchanging limited information via back-haul.
 We also proposed an iterative algorithm by solving the \ac{KKT} equations, which can be implemented easily in a distributed manner.

### 2014-08-13 Report/kkt_mse_approach.tex
Finalized before reviewing - 2

@@
 
-In order to perform the distributed approach, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE}, and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} using the transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}.
-Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using the uplink precoded pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}} evaluated at the receivers.
-Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS}, \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}.
-The algorithmic representation of the distributed \ac{MSE}-\ac{KKT} scheme is shown in Algorithm.
+In order to perform the distributed approach, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE}, and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} using the updated transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}.
+Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using uplink precoded pilots, where the uplink precoder is given by \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}}.
+Upon receiving the uplink precoded pilots at the \ac{BS} \me{b}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be measured and used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}.
+The algorithmic representation of the distributed \ac{MSE}-\ac{KKT} scheme is shown in the Algorithm.
 \ref{algo-4}.
-In this approach, the coordinating \acp{BS} are required to perform short transmissions to update the transmit and the receive beamformers before the actual data transmission.
+In this approach, the coordinating \acp{BS} are required to perform short transmissions to update the transmit and the receive beamformers until convergence or to a certain accuracy before doing the actual data transmission.
 \begin{algorithm}

### 2014-08-13 Report/simulation_distributed.tex
update
Finalized before reviewing - 2

@@
 It can be seen that the heuristic method is not converged to the optimal point but oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
-\begin{figure*}
+\begin{figure}
 \centering
-\subfloat[][Queue deviation]{
-\includegraphics[width=0.48\textwidth]{fig-9-2}
-\label{fig-d-3.1}}
-\hfill
-\subfloat[][Sum rate performance]{
-\includegraphics[width=0.48\textwidth]{fig-10}
-\label{fig-d-3.2}}
+\includegraphics[width=\columnwidth]{fig-9-2}
 \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
-\label{fig-d-3}
-\end{figure*}
+\label{fig-d-3.1}
+\end{figure}
 
@@
 By dropping the squared rate variable, the \ac{Q-WSRM} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues.
-Contrastingly, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.
+On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

### 2014-08-13 Report/wsrm_formulation.tex
Finalized before reviewing - 2

@@
 
-Now, the optimal linear receiver for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} is obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}}, which is given by
+Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl}\label{eqn-9--1}
@@
 \end{IEEEeqnarray}
-Now, by solving for the optimal receiver using \ac{KKT} conditions, we obtian the following expression for the receive beamformer \me{\mvec{w}{l,k,n}} in an iterative manner as
+Solving \eqref{eqn-9--1} using \ac{KKT} conditions, we obtain the following iterative expression for the receive beamformer \me{\mvec{w}{l,k,n}} as
 \begin{subeqnarray} \label{opt-rx}
@@
 \end{subeqnarray}
-where \me{\mvec{w}{l,k,n}^{(i-1)}} denotes the receive beamformer found in the earlier iteration, around which the linear relaxation is performed to convexify the problem in \eqref{eqn-9--1}.
+where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the earlier iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
 It can be seen that the optimal receiver expression in \eqref{opt-rx} is the scaled version of the \ac{MMSE} receiver, which is given by

### 2014-08-13 Report/conclusions.tex
modified for review

@@
 The exponent used in the proposed formulation can be modified to achieve either greedy allocation or equally fair allocation.
-We also proposed the distributed solutions for the proposed centralized \ac{JSFRA} problem using the \ac{ADMM} method, which has better convergence behaviour compared to the primal decomposition.
+We also proposed the distributed solutions for the proposed centralized \ac{JSFRA} problem using the \ac{ADMM} method, which has better convergence behavior compared to the primal decomposition.
 In addition, we also proposed an iterative algorithm based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme to design the precoders in a distributed manner using the closed form solutions.

### 2014-08-13 Report/decomposition_solutions.tex
updated kkt,wsrm,admm,primal
Corrections after first reading
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>
modified for review

@@
 In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are considered.
-In particular, the \ac{PD} and the \ac{ADMM} based \ac{DD} approaches are addressed.
+In particular, the \acl{PD} and the \ac{ADMM} based \acl{DD} approaches are addressed.
 
 To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-The centralized problem\footnote{\eqref{eqn-9} for the \ac{SCA} approach and \eqref{eqn-mse-2} for \ac{MSE} reformulation approach} can be equivalently written as
+In order to study the decomposition based solutions, we consider the solution proposed in the \eqref{eqn-9}, which is based on the Taylor approximation for the nonconvex constraint.
+The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2.3} as well.
+Now, the centralized problem can be equivalently written as
 \begin{IEEEeqnarray}{rCl} \label{eqn-decent-1}
-\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
+\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
 \text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber,
@@
 
-Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint\footnote{coupling constraint in \ac{MSE} scheme is given by  \eqref{eqn-mse-2.3}} given by \eqref{eqn-9.1c} can be expressed by grouping the interference contribution from each \acp{BS} in the system as
+Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-2.3} can be expressed by grouping the interference contribution from each \acp{BS} in the coordinating set \me{\mathrm{B}} as
 \begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
 \beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0, \label{eqn-decent-3a}
+&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2 \label{eqn-decent-3a}
 \end{IEEEeqnarray}
@@
 \begin{equation}
-\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
+\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}
 \end{equation}
@@
 The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the interference caused by the transmission from \ac{BS} \me{b} to the user \me{\ith{k}} corresponding data stream.
-In order the solve for the global optimal precoders, we need to find the optimal coupling variables \me{\zeta_{l,k,n,b}} by either using \ac{PD} or by using \ac{DD} method.
+In order the solve for the global optimal precoders, we need to find the optimal coupling variables \me{\zeta_{l,k,n,b}} by either using \acl{PD} or by using \acl{DD} method.
 In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} scheme and \eqref{eqn-mse-2.3} for the \ac{MSE} relaxation scheme are decoupled to perform the distributed precoder design problem.

### 2014-08-13 Report/dual_approach.tex
modified for review

@@
-In this section, we discuss the \ac{ADMM} decomposition method, which is basically based on the \acf{DD}, but shows better convergence properties.
-In contrast to the \acl{PD} problem, the \acf{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
+In this section, we discuss the \ac{ADMM} decomposition method, which is basically based on the \acl{DD}, but shows better convergence properties.
+In contrast to the \acl{PD} problem, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
 In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution.
@@
  \SetKwInput{KwInit}{Initialize}
- \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
+ \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}

### 2014-08-13 Report/ieee_journal.tex
completed_journal
Finalized before reviewing - 2
modified for review

@@
 \begin{abstract}
-%\input{abstract}
+\input{abstract}
 \end{abstract}
 
+\acresetall
 \section{Introduction} \label{sec-1}
@@
 \section*{Acknowledgment}
-This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Renesas Mobile Europe, Academy of Finland.
+This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
 
+\acresetall
 \section{Conclusions} \label{sec-6}
+\input{conclusions}
 

### 2014-08-13 Report/introduction.tex
modified for review

@@
 These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints.
-In this work, we consider the problem of transmit design over the space-frequency resources provided by a \ac{MU-MIMO} \ac{OFDM} framework in the downlink broadcast transmission to minimize the number of queued packets.
+In this work, we consider the problem of transmit design over the space-frequency resources provided by the \acs{MIMO}-\ac{OFDM} framework in the downlink broadcast transmission to minimize the number of queued packets.
 Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation to minimize the total number of backlogged packets of all \acp{BS}.
@@
 For this highly nonconvex problem, we first propose two centralized methods.
-In the first method, we relax the nonconvex constraint by the first order taylor approximation around an operating point, which is updated in an iterative manner until convergence or to a certain accuracy.
+In the first method, we relax the nonconvex constraint by the first order Taylor approximation around an operating point, which is updated in an iterative manner until convergence or to a certain accuracy.
 In the second method, we reformulate the \ac{JSFRA} problem using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders.

### 2014-08-13 Report/mse_formulation.tex
modified for review

@@
 where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}.
-Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \ac{MU-MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}.
+Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}.
 
@@
 Alternating between these two precoder designs guarantees the monotonicity of the objective function used in the problem \eqref{eqn-mse-2}.
-The \ac{MSE} relaxation method converges to the same stationary \ac{KKT} point as of the original \ac{WSRM} problem by making the graidents equal.
+The \ac{MSE} relaxation method converges to the same stationary \ac{KKT} point as of the original \ac{WSRM} problem by making the gradients equal.

### 2014-08-13 Report/problem_formulation.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>
modified for review

@@
 \begin{equation}\label{pf-1}
-\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2.
+\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2
 \end{equation}
@@
 In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself.
-In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achive an efficient allocation by identifying the optimal space-frequency resource for each user in the system.
+In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system.
 The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \ac{Q-WSRM} approach.

### 2014-08-13 Report/sub_channel_wsrm.tex
modified for review

@@
 In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size.
-In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the reamining number of queued bits in the formulation.
+In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
 It provides a sub-optimal solution to the optimal way of distributing the sub-channel wise precoder design via primal/dual decomposition methods discussed in \cite{palomar2006tutorial,boyd2011distributed}.
@@
  \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
- \KwIn{permute \me{\mathcal{C} \rightarrow \tilde{\mathcal{C}}}}
+ \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
  \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
- update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{C}}(n)}. \;
+ update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}. \;
  \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}

### 2014-08-21 Report/decomposition_solutions.tex
Modifications made for the convergence

@@
 The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the interference caused by the transmission from \ac{BS} \me{b} to the user \me{\ith{k}} corresponding data stream.
-In order the solve for the global optimal precoders, we need to find the optimal coupling variables \me{\zeta_{l,k,n,b}} by either using \acl{PD} or by using \acl{DD} method.
-In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} scheme and \eqref{eqn-mse-2.3} for the \ac{MSE} relaxation scheme are decoupled to perform the distributed precoder design problem.
+In order the solve for the global optimal precoders, we need to find the coupling variables \me{\zeta_{l,k,n,b}} by either \acl{PD} or by \acl{DD} method.
+In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} and \eqref{eqn-mse-2.3} for the \ac{MSE} relaxation schemes are decoupled to perform the distributed precoder design problem.

### 2014-08-21 Report/dual_algorithm.tex
Modifications made for the convergence

@@
 It differs from the primal approach by fixing the interference price instead of fixing the interference level, which is the case in the primal design.
-As in the primal approach, in order to decentralize the precoder design problem, the interference terms present in the \ac{SINR} expression \eqref{eq:SINR} using the precoders of the neighbouring \acp{BS} \me{\tilde{\mc{B}}_b} are to be decoupled from the \ac{BS} \me{b}.
+As in the primal approach, in order to decentralize the precoder design problem, the interference terms present in the \ac{SINR} expression \eqref{eq:SINR} using the precoders of the neighboring \acp{BS} \me{\tilde{\mc{B}}_b} are to be decoupled from the \ac{BS} \me{b}.
 

### 2014-08-21 Report/introduction.tex
Modifications made for the convergence

@@
 
-In order to reduce the complexity involved in the precoder design problem, linear precoding are assumed at the \acp{BS} and linear detection is used at users.
+In order to reduce the complexity involved in the precoder design problem, linear precoding are assumed at the \acp{BS} and detection is used at users.
 The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
@@
 Then the problem is solved using an alternating optimization method, i.e., finding a set of variables while the remaining others are fixed.
+The \ac{MSE} reformulation for the \ac{WSRM} problem is also studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner.
 Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem are solved via \ac{MSE} reformulation in \cite{kaleva2013primal}.
@@
 More specifically, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function of it,  which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}.
-In the backpreassure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
+In the backpressure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
 
@@
 Since the problem considered in \cite{qps_cioffi} assumed single antenna transmitters and receivers, the queue minimizing problem reduces to the one of optimal power allocation.
-In the context of wireless networks, the backpreassure algorithm mentioned above was extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.
+In the context of wireless networks, the backpressure algorithm mentioned above was extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.
 

### 2014-08-21 Report/joint_wsrm_formulation.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>
Modifications made for the convergence

@@
-The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network.\footnote{routers or user terminals} One such algorithm  is the \emph{backpreassure algorithm}, discussed in detail in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
+The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network.\footnote{routers or user terminals} One such algorithm  is the \emph{backpressure algorithm}, discussed in detail in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
 The algorithm determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes.
@@
 
-The \ac{Q-WSRM} formulation extends the \emph{backpreassure algorithm} to the \ac{MIMO} \ac{OFDM} framework, in which the multiple \acp{BS} acts as the source nodes and the user terminals as the receiver nodes.
+The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the \ac{MIMO} \ac{OFDM} framework, in which the multiple \acp{BS} acts as the source nodes and the user terminals as the receiver nodes.
 The control policy in the form of transmit precoders are designed with the objective of minimizing the number of queued packets waiting at the \acp{BS}.
@@
 \begin{equation}
-\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k(i),
+\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k(i)
 \end{equation}
@@
 \mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} &=& \frac{1}{2} \left [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \right ] \IEEEyessubnumber \label{eqn-3.1.0} \\
-&\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) }, \IEEEyessubnumber \label{drift-exp}
+&\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) } \IEEEyessubnumber \label{drift-exp}
 \end{IEEEeqnarray}
@@
 \begin{equation}
-\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
+\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t)
 \end{equation}
@@
 The Lyapunov drift conditioned on the current backlogged packets \me{\mbfa{Q}(i)} is given by
-\begin{IEEEeqnarray}{rCl} \label{backpreassure-approx}
+\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
 \underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
- &\leq& \mathbb{E} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) + \mathbb{E}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \IEEEyessubnumber
+ &\leq& \mathbb{E} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) + \mathbb{E}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 
-Now the expression in \eqref{backpreassure-approx} looks similar to the \ac{WSRM} problem if the weights are replaced by the number of backlogged packets corresponding to the users.
+Now the expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} problem if the weights are replaced by the number of backlogged packets corresponding to the users.
 The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
@@
 \underset{\substack{\mvec{M}{k,n}, \mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
-\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-3.1.3} \\
+\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-3.1.3} \\
 & \quad & \sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U} \IEEEyessubnumber \label{eqn-3.1.4}
@@
 \underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \IEEEyessubnumber \\
-\text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4}. \IEEEyessubnumber
+\text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4} \IEEEyessubnumber
 \end{IEEEeqnarray}

### 2014-08-21 Report/mse_formulation.tex
Modifications made for the convergence

@@
 where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}.
-Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}.
+Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.
 
@@
 \end{IEEEeqnarray}
-where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the the \ac{MSE} relation.
+where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the \ac{MSE} relation.
 
@@
 \subsubsection*{Convergence}
-The convergence of the \ac{MSE} reformulation approach follows the same arguments detailed in \cite{wmmse_shi,christensen2008weighted}.
+The convergence of the \ac{MSE} reformulation approach follows the same arguments detailed in \cite{wmmse_shi,hong2012decomposition}.
 Since the transmit precoders are obtained by minimizing the weighted \ac{MSE} criterion, it converges to the stationary \ac{KKT} point at each iteration.

### 2014-08-21 Report/primal_algorithm.tex
Modifications made for the convergence

@@
 The primal decomposition approach is modeled by having a master controller, which controls the resources allocated to each \acp{BS} based on which the optimization is carried out locally at each \ac{BS}.
-In this scheme, the problem described in \eqref{eqn-9} is decomposed in a way that the precoders intended for the users associated with each \ac{BS} are designed locally with the additional constraint on the interference caused by the transmission to the neighbouring \ac{BS} users.
-The interference thresholds are set by the centralized controller for each data stream of the users in the system, which needs to be satisfied by the neighbouring \acp{BS} while designing the precoders.
+In this scheme, the problem described in \eqref{eqn-9} is decomposed in a way that the precoders intended for the users associated with each \ac{BS} are designed locally with the additional constraint on the interference caused by the transmission to the neighboring \ac{BS} users.
+The interference thresholds are set by the centralized controller for each data stream of the users in the system, which needs to be satisfied by the neighboring \acp{BS} while designing the precoders.
 
@@
 
-In order to decouple the precoder design, \acp{BS} use the fixed interference levels set by the centralized controller in the \ac{SINR} expression \eqref{eq:SINR-primal} and additional interference constraints to limit the interference caused by the \ac{BS} \me{b} to the neighbouring users \me{\pr{k} \notin \mc{U}_b} is given by \eqref{eq-primal-constr}.
+In order to decouple the precoder design, \acp{BS} use the fixed interference levels set by the centralized controller in the \ac{SINR} expression \eqref{eq:SINR-primal} and additional interference constraints to limit the interference caused by the \ac{BS} \me{b} to the neighboring users \me{\pr{k} \notin \mc{U}_b} is given by \eqref{eq-primal-constr}.
 Using the above constraints and approximations, the precoder design problem for a \ac{BS} \me{b} using the fixed interference level is given by
@@
 \end{equation}
-where \me{\sigma} is the positive step-size which determines the convergence behaviour, and \me{s^{(\pr{b})}_{l,k,n}} is the global subgradient evaluated at the point \me{\chi_{l,\pr{b},k,n}}.
+where \me{\sigma} is the positive step-size which determines the convergence behavior, and \me{s^{(\pr{b})}_{l,k,n}} is the global subgradient evaluated at the point \me{\chi_{l,\pr{b},k,n}}.
 Since the inter-cell interference term \me{\chi_{l,\pr{b},k,n}} couples exactly two \acp{BS}, \me{b} and \me{\pr{b}}, the global subgradient can be expressed as \me{s^{(\pr{b})}_{l,k,n}(i) = \mu^{(b)}_{l,k,n}(i) - \mu^{(\pr{b})}_{l,k,n}(i), \, \forall \pr{b} \in \tilde{\mc{B}}_b, \forall k \notin \mc{U}_{b}}.

### 2014-08-21 Report/primal_approach_appendix.tex
modified for review
Modifications made for the convergence

@@
 To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner.
-Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}.
+Once we obtain the dual variables from all the \acp{BS}, subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}.
 With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}.

### 2014-08-21 Report/simulation_intro.tex
Modifications made for the convergence

@@
-The simulations carried out in this work considered the path loss varying uniformly across all users in the system with the channels drawn from the i.i.d samples.
-The queues are generated based on the poisson process with the average values specified in each section presented.
+The simulations carried out in this work considered the path loss varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d} samples.
+The queues are generated based on the Poisson process with the average values specified in each section presented.

### 2014-08-21 Report/sub_channel_wsrm.tex
Modifications made for the convergence

@@
 In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization.
-The number of queued bits for each user are updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
+The total number of queued bits for each user are updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
 \begin{equation}

### 2014-08-21 Report/wsrm_formulation.tex
modified for review
Modifications made for the convergence

@@
 
-The proposed algorithm is referred as \ac{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint which is outlined in Algorithm \ref{algo-1}.
+The proposed algorithm is referred as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint which is outlined in Algorithm \ref{algo-1}.
 The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
@@
 In this problem, we used alternating optimization with \ac{SCA} method, which provides monotonic convergence since the objective is improved at each step \textit{i.e} \me{f^{(i)} \geq f^{(i+1)}}, assuming \me{f^{(i)}} is the objective function at the \me{i^\mathrm{th}} \ac{SCA} iteration.
-For a fixed receive beamformers, the problem is guaranteed to converge to a \ac{KKT} point at each \ac{SCA} points as discussed in \cite{marks1978technical}.
+For a fixed receive beamformers, the problem is guaranteed to converge to a \ac{KKT} point at each \ac{SCA} updates as discussed in \cite{marks1978technical}.
 Now, by alternating the transmit and the receive precoders, we perform \ac{BCDM}, which provides monotonic convergence of the objective.
-Since the \ac{SCA} method is also considered in our problem, the convergence is not straight forward.
-We can only speculate the convergence based on the monotonicity of the objective values.
-Since receive beamformers are based on the \ac{MMSE} objective, it improves the objective value for each update, providing a monotonic increase in the objective value.
+
+The linear approximation majorizes the quadratic-over-linear function in \eqref{eqn-6.2} around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}.
+The constraint approximation satisfies the following conditions as in \cite{marks1978technical}
+\begin{subeqnarray} \label{sca-req}
+	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
+	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
+	\partial f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \partial \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n})
+\end{subeqnarray}
+where \me{\bar{f}(x,x^{(i)})} is the approximate function majorizing \me{\bar{f}(x)} around the point \me{x^{(i)}}.
+At each iteration \me{(i)}, the optimal value \me{x^{\ast}} obtained by solving the approximate problem is a feasible solution to next approximation at \me{(i+1)} iteration by following \eqref{sca-req}.
+Once the problem converged to an optimal point, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}.
+Since the receiver minimizes the objective value for the fixed transmit precoders, the proposed \ac{JSFRA} scheme guarantees to converge to an optimal point.

### 2014-09-09 Report/decomposition_solutions.tex
revision - 1

@@
 In order to study the decomposition based solutions, we consider the solution proposed in the \eqref{eqn-9}, which is based on the Taylor approximation for the nonconvex constraint.
-The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2.3} as well.
-Now, the centralized problem can be equivalently written as
+The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well.
+Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
 \begin{IEEEeqnarray}{rCl} \label{eqn-decent-1}

### 2014-09-09 Report/introduction.tex
revision - 1

@@
 The topics on \ac{MIMO} \ac{BC} precoder design have been studied extensively with different performance criteria in the literature.
-Due to the nonconvex nature of most, if not all, linear \ac{MIMO} \ac{BC} precoder design problems, the \ac{SCA} method has gradually become a powerful tool to deal with these problems.
+Due to the nonconvex nature of the \ac{MIMO} \ac{BC} precoder design problems, the \ac{SCA} method has gradually become a powerful tool to deal with these problems.
 For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around an operating point in order to solve the \ac{WSRM} problem in an iterative manner.
@@
 The \ac{MSE} reformulation for the \ac{WSRM} problem is also studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner.
-Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem are solved via \ac{MSE} reformulation in \cite{kaleva2013primal}.
+Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal}.
 
-The problem of precoder design for the \ac{MIMO} \ac{BC} system are solved either by using a centralized controller or by using decentralized algorithms where each BS handles their own problems and exchange limited information via backhaul.
-The distributed approaches are based on the primal or dual decomposition \cite{palomar2006tutorial,boyd2011distributed}.
-In primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders.
+The problem of precoder design for the \ac{MIMO} \ac{BC} system are solved either by using a centralized controller or by using decentralized algorithms where all \acp{BS} often handles its own problem and exchange limited information via backhaul.
+The distributed approaches are based on primal, dual or \ac{ADMM} decomposition, which are discussed in a detailed manner in \cite{palomar2006tutorial,boyd2011distributed}.
+In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders.
 The fixed interference are then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}.
-The dual approach controls the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
+The dual and \ac{ADMM} approach controls the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
 
 By adjusting the weights properly, we can find arbitrary rate-tuple in the rate region of the system that maximizes other performance measures by solving the resulting WSRM problem.
-For example, if the weight of each user is set to be inversely proportional to his/her data rate, the corresponding problem guarantees fairness among users.
+For example, if the weight of each user is set to be inversely proportional to his/her average data rate, the corresponding problem guarantees fairness on an average among the users.
 As an approximate method, we may assign weights based on the current queue size of users.

### 2014-09-09 Report/joint_wsrm_formulation.tex
revision - 1

@@
 
-The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the \ac{MIMO} \ac{OFDM} framework, in which the multiple \acp{BS} acts as the source nodes and the user terminals as the receiver nodes.
-The control policy in the form of transmit precoders are designed with the objective of minimizing the number of queued packets waiting at the \acp{BS}.
-The weights used in the precoder design algorithm should be a function of the number of backlogged packets corresponding to each user.
-In order to find the weights, we adopt the Lyapunov drift minimization as discussed in \cite{neely2010stochastic}, where the Lyapunov function is given by the squared sum of the number backlogged packets as
+The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the \ac{MIMO}-\ac{OFDM} framework, in which the multiple \acp{BS} acts as the source nodes and the user terminals as the receiver nodes.
+The control policy in the form of transmit precoders are designed to minimize the number of queued packets waiting at the \acp{BS}.
+In order to find the optimal algorithm, we use the Lyapunov function which is predominantly used in the control theory for the system stability.
+Since at each time slot, the system can be described by the channel conditions and the number of backlogged packets of each user, Lyapunov function is used to provide a scalar measure, which grows large when the system moves towards the undesirable state.
+Following the approach in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
 \begin{equation}
@@
 \end{equation}
-where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot.
+where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and \me{\frac{1}{2}} is used for the convenience.
 The Lyapunov function provides a measure of congestion in the system, as discussed in \cite[Ch.
@@
 \end{equation}
-In order to minimize the number of backlogged packets at each instant, minimization of the Lyapunov drift \eqref{eqn-3.1} is carried over all possible control decisions in the form of transmission rates \me{t_k} to users in the system.
+In order to minimize the squared sum at each instant, minimization of the Lyapunov drift \eqref{eqn-3.1} is carried over all possible rate allocations in the form of transmission rates \me{t_k} to users in the system.
 The Lyapunov drift conditioned on the current backlogged packets \me{\mbfa{Q}(i)} is given by
 \begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
-\underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
- &\leq& \mathbb{E} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) + \mathbb{E}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber
+\underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+ &\leq& \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i)  \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber
 \end{IEEEeqnarray}
-where the second term on the r.h.s is due to i.i.d assumption on the arrivals.
-We can bound the first term on the r.h.s by a constant \me{B} for all possible control actions taken for a given channel condition \cite{neely2010stochastic}.
+where the second term on the r.h.s follows from the Poisson arrival process.
+Assuming the second order moments of the transmission rates and the arrival rates are bounded, it can be replaced by a suitable bound \me{B} in order to eliminate from the optimization problem \cite{neely2010stochastic}.
 
-Now the expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} problem if the weights are replaced by the number of backlogged packets corresponding to the users.
+Now the expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the number of backlogged packets corresponding to the users.
 The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
-In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}.
-With this, the \ac{Q-WSRM} problem for a wireless system is given by
+The \ac{Q-WSRM} formulation is given by
 \begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
 	\underset{\substack{\mvec{M}{k,n}, \mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
-\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-3.1.3} \\
-& \quad & \sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U} \IEEEyessubnumber \label{eqn-3.1.4}
+	\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-3.1.3}
+\end{IEEEeqnarray}
+In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}.
+The extended version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system is given by \label{q_gen_sum-1} with the additional constraint
+\begin{IEEEeqnarray}{rCl} \label{eqn-3.1.4}
+\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U}
 \end{IEEEeqnarray}
@@
 \underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \IEEEyessubnumber \\
-\text{subject to.} & \quad & \eqref{eqn-3.1.1}, \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4} \IEEEyessubnumber
+\text{subject to.} & \quad & \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4} \IEEEyessubnumber
 \end{IEEEeqnarray}
-The problem defined in \eqref{gen_sum} provides a greedy queue minimizing approach as compared to \eqref{q_gen_sum}, since the resource allocation is driven by the channel conditions in comparison with the number of queued packets as in \eqref{q_gen_sum}.
-Note that in both formulations, the resources allocated to the users are limited by the backlogged packets with an explicit rate constraint defined by \eqref{eqn-3.1.4}.
+The problem defined in \eqref{gen_sum} provides a greedy queue minimizing approach as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison with the number of queued packets as in \ac{Q-WSRME}.
+Note that in both formulations, the resources allocated to the users are limited by the backlogged packets with an explicit maximum rate constraint defined by \eqref{eqn-3.1.4}.

### 2014-09-09 Report/kkt_mse_approach.tex
modified for review
Modifications made for the convergence
revision - 1

@@
 In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by solving the \ac{KKT} conditions.
-Similar work has been considered for the \ac{WSRM} problem with the rate constraints in \cite{kaleva2012weighted}.
-When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} includes a nonconvex constraint, which makes the problem difficult to solve in an iterative approach as in \cite{kaleva2012weighted}.
+Similar work has been considered for the \ac{WSRM} problem with the minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
+When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} includes a nonconvex constraint, which makes the problem difficult to solve due to the additional nonconvex maximum rate constraint \eqref{eqn-3.1.4} for the \ac{WSRM} problem.
 
@@
 \item when the exponent \me{q} is even or,
-\item when the number of backlogged packets of each user is large enough \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator.
+\item when the number of backlogged packets of each user is large enough \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator and the queues as well.
 \end{itemize}
@@
 \begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
-\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
+\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
-\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 \\ \nonumber
+\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
 &\hspace{0.5cm}& \qquad {} \qquad {} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
@@
 where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.
-The equality of \eqref{kkt-mse-1.2} is due to the equivalence of the \ac{MSE} expression with the transmit and the receive precoders.
 
@@
 \sigma_{l,k,n}^{(i)} &=& \max{\left (0, \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right )}  \IEEEyessubnumber \label{kkt-mse-4.2} \\
-\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \rfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
+\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
 \mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
@@
 It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
-After each iteration instant, the transmit and the receive precoders are exchanged across the coordinating \acp{BS} in \me{\mc{B}} to obtain the next operating point.
+After each iteration instant, the transmit and the receive precoders are updated across the coordinating \acp{BS} in \me{\mc{B}} to obtain the next operating point.
 
@@
 \ref{algo-4}.
-In this approach, the coordinating \acp{BS} are required to perform short transmissions to update the transmit and the receive beamformers until convergence or to a certain accuracy before doing the actual data transmission.
 \begin{algorithm}

### 2014-09-09 Report/mse_formulation.tex
revision - 1

@@
 
-Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.
+Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.
 Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
@@
 
-The \acl{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex due to the constraint \eqref{eqn-mse-1.2}.
+The \acl{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
 In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}.
@@
 
-Now, using the above approximation for the rate constraint, the optimization problem is solved for the optimal precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}}.
-Once the optimal values are available, the local \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} is now updated with the new value \me{\epsilon_{l,k,n}}.
+Now, using the above approximation for the rate constraint, the problem defined by \eqref{eqn-mse-1} can be solved optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}} for the fixed receive beamformers.
+Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}.
 The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as

### 2014-09-09 Report/primal_approach.tex
revision - 1

@@
 Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3a}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration and is carried out until convergence.
-The primal approach is discussed extensively for the \ac{WSRM} problem in \cite{pennanen2011decentralized} and much of the current work follows the same.
+The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows the same.
 Much of the details are provided in the Appendix \ref{a-2}.

### 2014-09-09 Report/problem_formulation.tex
Modifications made for the convergence
revision - 1

@@
 The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant value.
-Eq.
+In fact, Eq.
 \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
@@
 \end{equation}
-It is evident that \eqref{pf-1} is equivalent to \eqref{backpreassure-approx} if the second order terms are ignored.
+It is evident that \eqref{pf-1} is equivalent to \eqref{backpressure-approx} if the second order terms are ignored.
 Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over allocation.
@@
 In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system.
-The queue deviation objective provides an alternate and a more efficient way to perform the resource allocation as compared to the \ac{Q-WSRM} approach.
+The queue deviation objective provides an alternative approach to perform the resource allocation without the additional rate constraints as in \ac{Q-WSRME} approach.

### 2014-09-09 Report/problem_formulation_intro.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>
revision - 1

@@
-To minimize the total number of backlogged packets, we consider minimizing \me{\ell_{q}}-norm of all the queue deviation given by
+To minimize the total number of backlogged packets, we consider minimizing weighted \me{\ell_{q}}-norm of all the queue deviation given by
 \begin{equation}
-v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}).
+v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})
 \label{eqn-4.2}
 \end{equation}
-Explicitly, the considered problem is given by \me{\sum_{k \in \mc{U}} \, | v_k |^q}. With this objective, the problem of weighted queued packet minimization is given by
+Explicitly, the considered problem is given by \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. With this objective, the problem of weighted queued packet minimization is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-3}
 \underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
-\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
+\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-4.3}
 \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\gamma_{l,k,n}} is defined in \eqref{eq:SINR}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively.
-It can be easily extended for user specific streams \me{L_k} instead of using the common \me{L} streams for all users.
-In \eqref{eqn-4.3}, we consider the sum power constraint for each \ac{BS} across all sub-channels.
-Before discussing the proposed solutions, we consider the existing algorithm to solve the issue of minimizing the number of backlogged packets with additional constraints required by problem.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
+In \eqref{eqn-4.3}, we consider a \ac{BS} specific sum power constraint for each \ac{BS} across all sub-channels.
 
-For practical and tractability reasons, we impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
+For practical and tractability reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
 As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
-\begin{equation}
-v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0.
+\begin{equation} \label{rate_constraint_a}
+v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0
 \end{equation}
@@
 
-Before proceeding further, we note that the constraint in \eqref{eqn-4.2} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}.
+Before proceeding further, we note that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}.
 As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.

### 2014-09-09 Report/simulation_distributed.tex
revision - 1

@@
 The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively.
-The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{[0,-6]} dB.
+The users are assumed to be scattered over the cell boundary experiencing the path loss following the uniform distribution between \me{[0,-6]} dB.
 The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.
@@
 The additional condition can be justified due to the dropping of absolute value operator from the objective.
-It can be seen that the heuristic method is not converged to the optimal point but oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
+It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
 \begin{figure}
@@
 The objective values are mentioned in the legend for all the schemes, since the objective of \me{\ell_2} norm is not the same as \me{\ell_1} norm, which is used for the plot.
-The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables are not allowed to converge in between the \ac{SCA} steps in the \ac{KKT} approach.
+The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables \me{\alpha_{l,k,n}} and \me{\sigma_{l,k,n}} are not iterated until convergence between each \ac{SCA} steps in the \ac{KKT} approach.
 In the simulation, we update all the variables at each iteration due to the practical issues in the signaling between the \acp{BS}.
-The figure compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRM} scheme compared to the \me{\ell_2} norm which includes it.
-By dropping the squared rate variable, the \ac{Q-WSRM} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues.
+Fig.
+\ref{fig-d-3.1} also compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRME} scheme compared to the \me{\ell_2} norm which includes it.
+By dropping the squared rate variable, the \ac{Q-WSRME} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues.
 On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

### 2014-09-09 Report/simulation_results.tex
revision - 1

@@
-This section discusses the performance of the centralized algorithms discussed in Section \ref{sec-3} for a few system configurations.
+In this section, we discuss the performance of the centralized algorithms from Section \ref{sec-3} for a few system configurations.
 To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
 The number of packets waiting at the transmitter for each user is given by \me{Q_k = 5,8} and \me{6} bits respectively.
-With this configuration, the resources allocated for the users on each sub-channel by various algorithms are shown in Fig.
-\ref{tbl-1}.
 
@@
 \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system.
-It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRM} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
+It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
 \begin{figure*}
@@
 \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas.
-As we can see from Fig.
-\ref{fig-2} that both the optimal and the \ac{MMSE} receiver achieves the same optimal point as compared to the \ac{JSFRA} scheme using \ac{MSE} reformulation.
 In all the schemes, the receive beamformers are updated at the \ac{SCA} update points instead of updating after the \ac{SCA} convergence as in Algorithm.
@@
 It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits.
-The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets \me{\chi_k = 3.58} bits.
+The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets to be equal for all users to \me{\chi_k = 3.58} bits.
 The \me{\ell_{\infty}} norm provides the fair allocation by making the queued deviation equal for all the users after the current allocation irrespective of their channel gains.

### 2014-09-09 Report/sub_channel_wsrm.tex
revision - 1

@@
 In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
-It provides a sub-optimal solution to the optimal way of distributing the sub-channel wise precoder design via primal/dual decomposition methods discussed in \cite{palomar2006tutorial,boyd2011distributed}.
+The centralized precoder design can also be performed across each sub-channel by using the decomposition methods discussed in \cite{palomar2006tutorial,boyd2011distributed}.
 
-The proposed \acf{QM} \ac{SRA} scheme decouples the problem by fixing the power across each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}.
+The proposed \acl{QM} \ac{SRA} formulation enables us to solve for the transmit precoders of all the users associated with the coordinating \ac{BS} in the set \me{\mathcal{B}} over each sub-channel independently by fixing the transmit power on each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}.
 In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization.
@@
 In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,j}} is the rate or guaranteed bits allocated over the sub-channel \me{j}.
-The current scheme is very sensitive to the order in which the sub-channels are selected for the optimization problem.
-The algorithmic representation of the \acf{QM} \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
+The current scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.
+The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
 \begin{algorithm}

### 2014-09-09 Report/system_model.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>
modified for review
revision - 1

@@
 Data for user \me{k} is transmitted from only one \ac{BS} which is denoted by \me{b_k\in \mathcal{B}}.
-We denote by \me{\mathcal{C} = \set{1,2,\dotsc,N}} the set of all sub-channel indices available in the system.
+We denote by \me{\mathcal{N} = \set{1,2,\dotsc,N}} the set of all sub-channel indices available in the system.
 
@@
 where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
-In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams.
+In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams \footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
 Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
 \begin{equation}\label{eq:SINR}
-\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
+\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}
 \end{equation}
@@
 \end{equation}
-where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the transmission in bits for user \me{k}. For a \ac{MIMO} \ac{OFDM} system,
+where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the transmission in bits for user \me{k}. For a \ac{MIMO}-\ac{OFDM} system,
 \begin{equation}

### 2014-09-09 Report/wsrm_formulation.tex
revision - 1

@@
-In this approach, we present an iterative algorithm to solve \eqref{eqn-3} locally based on the idea of alternating optimization and successive convex approximation.
+In this approach, we present an algorithm to solve \eqref{eqn-3} for the transmit precoders in a centralized way by using the idea of alternating optimization and successive convex approximation.
 Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
@@
 Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by the user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}.
-The problem in \eqref{eqn-6} is known to be NP-hard even for the single antenna case \cite{wmmse_shi,kaleva2013primal}.
+Similar to the \ac{WSRM} problem in \cite{tran2012fast}, the problem can be shown to be NP-hard even for the single antenna case.
 The reformulation in \eqref{eqn-6} allows a tractable solution as presented below.
@@
 
-By fixing the receivers, the problem now is to find optimal transmit beamformers for a given set of linear receivers which is a challenging task.
+By fixing the receivers, the problem now is to find optimal transmit beamformers for a given set of linear receivers which is still a challenging task.
 We note that for fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
@@
 \text{subject to} & \quad & \beta_{l,k,n} \geq  N_0\|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-9.1c} \\
-& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
+& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b}\sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
 & \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}
@@
 
-Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{M}_{i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}} as
+Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl}\label{eqn-9--1}
@@
 \begin{subeqnarray} \label{opt-rx}
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{(j,i)\neq (l,k)} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right ) \, \mvec{R}{l,k,n}^{-1} \, \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}
+\mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{(j,i)\neq (l,k)} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \\
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right ) \, \mvec{\widetilde{R}}{l,k,n}^{-1} \, \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}
 \end{subeqnarray}
@@
 \begin{IEEEeqnarray}{rCl}\label{eqn-10}
-\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n} \IEEEyessubnumber \\
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
+\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n} \IEEEyessubnumber
 \end{IEEEeqnarray}

### 2014-09-10 Report/kkt_mse_approach.tex
finished convergence analysis

@@
 \item when the exponent \me{q} is even or,
-\item when the number of backlogged packets of each user is large enough \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator and the queues as well.
+\item when the number of backlogged packets of each user is large enough, \textit{i.e}, \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator and the queues as well.
 \end{itemize}
@@
 \sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \geq t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
-\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
+\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 \end{IEEEeqnarray}
-The dual variable \me{\alpha^{(i)}} is updated with memory as in \eqref{kkt-mse-4.1} to avoid abrupt oscillations due to \me{\sigma < 0} from \eqref{kkt-mse-4.2} when \me{Q_k < \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
-The parameter \me{\rho \in [0,1]} provides a linear combination of the previous to the current value of the dual variable, dictating system reaction for the excess allocation.
+Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in the expressions in \eqref{kkt-mse-4.1}, one has to be fixed to optimize for the other.
+In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.
+It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduce the transmit precoder weights in \eqref{kkt-mse-4.3}.
+This reduction in the precoder weights forces the allocated rate of the user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.
 

### 2014-09-10 Report/mse_formulation.tex
finished convergence analysis

@@
 \subsubsection*{Convergence}
-The convergence of the \ac{MSE} reformulation approach follows the same arguments detailed in \cite{wmmse_shi,hong2012decomposition}.
+Following the similar argument from Section \ref{sec-3.2.1}, we can see that the \ac{SCA} subproblems converges to a stationary point.
+The transmit precoders obtained by the \ac{MSE} relaxations are unique due to the \ac{MSE} expression in \eqref{eqn-mse-2.3}, since it removes the phase ambiguity due to the real valued expression for the transmit precoders as
+\begin{equation}
+\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+\end{equation}
+where \me{\Im{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace}} is zero due to the real valued \ac{MSE}.
 Since the transmit precoders are obtained by minimizing the weighted \ac{MSE} criterion, it converges to the stationary \ac{KKT} point at each iteration.

### 2014-09-10 Report/wsrm_formulation.tex
finished convergence analysis

@@
 
-In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which basically means that we do not solve the problem exactly.
-According to the traditional \ac{BCDM}, we need to solve a sub problem when fixing a set of variables to the global optimum to ensure the convergence to a stationary point.
-If we just approximate the objective, then the convergence is guaranteed \cite{razaviyayn2013unified}.
-In our case, we solve the sub problem inexactly, so the convergence proof of \ac{BCDM} does not apply to our problem.
-In this problem, we used alternating optimization with \ac{SCA} method, which provides monotonic convergence since the objective is improved at each step \textit{i.e} \me{f^{(i)} \geq f^{(i+1)}}, assuming \me{f^{(i)}} is the objective function at the \me{i^\mathrm{th}} \ac{SCA} iteration.
-For a fixed receive beamformers, the problem is guaranteed to converge to a \ac{KKT} point at each \ac{SCA} updates as discussed in \cite{marks1978technical}.
-Now, by alternating the transmit and the receive precoders, we perform \ac{BCDM}, which provides monotonic convergence of the objective.
-
-The linear approximation majorizes the quadratic-over-linear function in \eqref{eqn-6.2} around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}.
-The constraint approximation satisfies the following conditions as in \cite{marks1978technical}
+In order to prove the convergence of the proposed algorithm, we require the following conditions to be satisfied
+\begin{itemize}
+	\item convergence of the \ac{SCA} subproblem	
+	\item uniqueness of the transmit and the receive beamformers obtained
+	\item monotonic convergence of the objective function
+\end{itemize}
+In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, the linear approximation is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}.
+Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
 \begin{subeqnarray} \label{sca-req}
@@
 \end{subeqnarray}
-where \me{\bar{f}(x,x^{(i)})} is the approximate function majorizing \me{\bar{f}(x)} around the point \me{x^{(i)}}.
-At each iteration \me{(i)}, the optimal value \me{x^{\ast}} obtained by solving the approximate problem is a feasible solution to next approximation at \me{(i+1)} iteration by following \eqref{sca-req}.
+where \me{\bar{f}(x,x^{(i)})} is the approximate function \me{\bar{f}(x)} around the point \me{x^{(i-1)}}.
+At each iteration \me{(i-1)}, the optimal value \me{x^{\ast}} obtained by solving the approximate problem is a feasible solution to next approximation at \me{(i)} iteration by following \eqref{sca-req}.
+It can be easily verified that the optimal point of each \ac{SCA} problem satisfies the \ac{KKT} condition of the original problem, which in fact is the stationary point of the \ac{SCA} subproblem.
+
+The uniqueness of the transmit and the receive beamformers can be justified by forcing one antenna to be real valued to exclude the phase ambiguity arising from the complex precoders.
+The monotonic convergence of the objective function can be justified by the following arguments.
+At each \ac{SCA} iteration, the relaxed subproblem is solved for the optimal transmit precoders to minimize the objective function.
+Since the \ac{SCA} subproblem is relaxed around the \me{\ith{(i-1)}} optimal point for the \me{\ith{(i)}} iteration, the solution of the \me{\ith{(i)}} iteration includes optimal point from the  \me{\ith{(i-1)}} iteration as well.
+Therefore, at each \ac{SCA} iteration, the objective function can either be equal to or smaller than the previous solution, thereby leading to the monotonic convergence of the objective function.
+
 Once the problem converged to an optimal point, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}.

### 2014-09-12 Report/ieee_journal.tex
updated version

@@
-\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[11pt,peerreview,onecolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 
-%\title{Queue Aware Precoder Design for Space Frequency Resource Allocation}
-%\author{{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti}
-%\IEEE{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
-%University of Oulu, Oulu, FI-90014\\
-%Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
-%}
+\title{Traffic aware Resource Allocation for \acs{MIMO}-\acs{OFDM} systems}
+\author{
+	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\
+	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
+		University of Oulu, Oulu, FI-90014\\
+		Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
+}
 
 \begin{document}
+
+\maketitle
 

### 2014-09-12 Report/joint_wsrm_formulation.tex
updated version

@@
 \underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
- &\leq& \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i)  \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber
+ &\leq& \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}.
-The extended version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system is given by \label{q_gen_sum-1} with the additional constraint
+The rate constrained version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system, is given by \label{q_gen_sum-1} with the additional constraint
 \begin{IEEEeqnarray}{rCl} \label{eqn-3.1.4}

### 2014-09-12 Report/kkt_mse_approach.tex
updated version

@@
 \end{IEEEeqnarray}
-Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in the expressions in \eqref{kkt-mse-4.1}, one has to be fixed to optimize for the other.
+Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other.
 In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.

### 2014-09-12 Report/mse_formulation.tex
updated version

@@
 \subsubsection*{Convergence}
-Following the similar argument from Section \ref{sec-3.2.1}, we can see that the \ac{SCA} subproblems converges to a stationary point.
+Following the similar arguments as in  Section \ref{sec-3.2.1}, we can see that the \ac{SCA} subproblems converges to a stationary point.
 The transmit precoders obtained by the \ac{MSE} relaxations are unique due to the \ac{MSE} expression in \eqref{eqn-mse-2.3}, since it removes the phase ambiguity due to the real valued expression for the transmit precoders as
@@
 \end{equation}
-where \me{\Im{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace}} is zero due to the real valued \ac{MSE}.
-Since the transmit precoders are obtained by minimizing the weighted \ac{MSE} criterion, it converges to the stationary \ac{KKT} point at each iteration.
-The receiver updates are made based on the \ac{MMSE} criterion, it provides the optimal receive beamformers for the given transmit precoders.
-Alternating between these two precoder designs guarantees the monotonicity of the objective function used in the problem \eqref{eqn-mse-2}.
-The \ac{MSE} relaxation method converges to the same stationary \ac{KKT} point as of the original \ac{WSRM} problem by making the gradients equal.
+At each \ac{SCA} step, the transmit precoders are obtained uniquely by minimizing the weighted \ac{MSE} criterion due to the convex nature of the relaxed problem.
+Upon finding the optimal transmit precoders, the receive beamformers are updated using the \ac{MMSE} receivers.
+The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders thereby leading to the monotonic convergence of the objective function.
+At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, the objective value can either decrease or stays the same after each iteration.

### 2014-09-12 Report/simulation_results.tex
updated version

@@
 Fig.
-\ref{tbl-1} plots the sub-channel wise channel seen by the users followed by the assigned rates over each sub-channel by three different algorithms, \ac{Q-WSRM} allocation, \ac{JSFRA} scheme and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} precoder design proposed in \cite{wmmse_shi}.
+\ref{tbl-1} plots the sub-channel wise channel seen by the users followed by the assigned rates over each sub-channel by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} precoder design proposed in \cite{wmmse_shi}.
 The performance metric used for the comparison of different algorithms is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
 It can be seen from Fig.
-\ref{tbl-1}, that the \ac{Q-WSRM} scheme provides more priority to the third user with \me{Q_{3} = 6} bits compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel.
-In contrast to the \ac{Q-WSRM} scheme, the \ac{JSFRA} scheme assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
-%\begin{table*}
+\ref{tbl-1}, the \ac{Q-WSRME} scheme provides more priority to the third user with \me{Q_{3} = 6} bits as compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel.
+In contrast to the \ac{Q-WSRME} scheme, the \ac{JSFRA} approach assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
+\begin{table*}
+\centering
+\renewcommand{\arraystretch}{1.25} \scriptsize
+\begin{tabular}{|*{14}{c|}}
+\hline
+\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
+\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \emph{backpreassure})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
+\cline{3-14}
+ && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
+\hline
+\me{1} & \me{5} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.91} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
+\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.46}  &  \me{3.54} & \me{0} &  \me{4.36}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
+\me{3} & \me{6} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{5.72} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{5.79} & \me{5.81} &  \me{0}  &  \me{0} \\
+\hline
+\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{5.28} bits} & \multicolumn{3}{c|}{\me{3.91} bits} & \multicolumn{3}{c|}{\me{5.28} bits} \\
+\hline
+\end{tabular}
+\caption{Sub channel wise allocation for a scheduling instant}
+\label{tbl-1}
+\end{table*}
+%\begin{figure}
 %\centering
-%\renewcommand{\arraystretch}{1.25} \scriptsize
-%\begin{tabular}{|*{14}{c|}}
-%\hline
-%\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRM approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
-%\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(\emph{backpreassure} algorithm)} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
-%\cline{3-14}
-% && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
-%\hline
-%\me{1} & \me{5} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.91} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
-%\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.46}  &  \me{3.54} & \me{0} &  \me{4.36}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
-%\me{3} & \me{6} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{5.72} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{5.79} & \me{5.81} &  \me{0}  &  \me{0} \\
-%\hline
-%\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{5.28} bits} & \multicolumn{3}{c|}{\me{3.91} bits} & \multicolumn{3}{c|}{\me{5.28} bits} \\
-%\hline
-%\end{tabular}
-%\caption{Sub channel wise allocation for a scheduling instant}
+%\includegraphics[width=\columnwidth]{tbl-1}
+%\caption{Allocation for a \ac{SISO} Model comparing different Algorithms}
 %\label{tbl-1}
-%\end{table*}
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{tbl-1}
-\caption{Allocation for a \ac{SISO} Model comparing different Algorithms}
-\label{tbl-1}
-\end{figure}
+%\end{figure}
 

### 2014-09-12 Report/wsrm_formulation.tex
updated version

@@
 \end{itemize}
-In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, the linear approximation is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}.
+In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}.
 Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
@@
 	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
-	\partial f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \partial \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n})
+	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n})
 \end{subeqnarray}
-where \me{\bar{f}(x,x^{(i)})} is the approximate function \me{\bar{f}(x)} around the point \me{x^{(i-1)}}.
-At each iteration \me{(i-1)}, the optimal value \me{x^{\ast}} obtained by solving the approximate problem is a feasible solution to next approximation at \me{(i)} iteration by following \eqref{sca-req}.
-It can be easily verified that the optimal point of each \ac{SCA} problem satisfies the \ac{KKT} condition of the original problem, which in fact is the stationary point of the \ac{SCA} subproblem.
+where \me{\bar{f}(x,x^{(i)})} is the approximate function of \me{f(x)} around the point \me{x^{(i)}}.
+Using the assumptions in \eqref{sca-req}, the global optimal point of the relaxed formulation, which is a convex problem, satisfies the \ac{KKT} conditions of the original nonconvex problem, using \eqref{sca-req}.
+It shows that each relaxed formulation converges to the optimal point.
 
@@
 At each \ac{SCA} iteration, the relaxed subproblem is solved for the optimal transmit precoders to minimize the objective function.
-Since the \ac{SCA} subproblem is relaxed around the \me{\ith{(i-1)}} optimal point for the \me{\ith{(i)}} iteration, the solution of the \me{\ith{(i)}} iteration includes optimal point from the  \me{\ith{(i-1)}} iteration as well.
-Therefore, at each \ac{SCA} iteration, the objective function can either be equal to or smaller than the previous solution, thereby leading to the monotonic convergence of the objective function.
+Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point,\textit{i.e} \me{x^{\ast(i-1)}}, for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
+Therefore, at each \ac{SCA} steps, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.
 
-Once the problem converged to an optimal point, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}.
-Since the receiver minimizes the objective value for the fixed transmit precoders, the proposed \ac{JSFRA} scheme guarantees to converge to an optimal point.
+Once the problem converged to an optimal transmit precoders, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}.
+The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, the proposed \ac{JSFRA} scheme guarantees to converge to an optimal point.

### 2014-09-13 Report/ieee_journal.tex
Included figure with Q-WSRME

@@
-\documentclass[11pt,peerreview,onecolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\
-	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
+	\IEEEauthorblockA{Centre for Wireless Communications (CWC), \\ Department of Communications Engineering (DCE), \\
 		University of Oulu, Oulu, FI-90014\\
@@
 \end{abstract}
+
+\begin{keywords}
+\acs{MIMO}-\acs{OFDM}, weighted sum rate maximization, precoder design, queue driven scheduling and precoder design
+\end{keywords}
 

### 2014-09-13 Report/simulation_results.tex
Included figure with Q-WSRME

@@
 In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
-The users are located with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-6} dB, thereby simulating a realistic scenario.
+The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lower path loss.
 Fig.
@@
 \subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-1-2}
+\includegraphics[width=0.48\textwidth]{fig-1-3}
 \label{fig-1}}

### 2014-09-13 Report/wsrm_formulation.tex
Included figure with Q-WSRME

@@
 \end{subeqnarray}
-where \me{\bar{f}(x,x^{(i)})} is the approximate function of \me{f(x)} around the point \me{x^{(i)}}.
+where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}.
 Using the assumptions in \eqref{sca-req}, the global optimal point of the relaxed formulation, which is a convex problem, satisfies the \ac{KKT} conditions of the original nonconvex problem, using \eqref{sca-req}.
@@
 At each \ac{SCA} iteration, the relaxed subproblem is solved for the optimal transmit precoders to minimize the objective function.
-Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point,\textit{i.e} \me{x^{\ast(i-1)}}, for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
+Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point,\textit{i.e} \me{\mbf{x}^{\ast(i-1)}}, for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
 Therefore, at each \ac{SCA} steps, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.

### 2014-09-15 Report/dual_approach.tex
revision - 1
Final version before revision to all

@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} - \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{locals}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} - \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
 \text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
@@
  initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
- for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
+ \ForEach{\ac{BS} \me{b \in \mc{B}}}{
  \Repeat{convergence or \me{i \geq I_{\max}}}{
@@
   }
+ }
  \caption{Decentralization via \ac{ADMM} for \acs{JSFRA} scheme}

### 2014-09-15 Report/kkt_mse_approach.tex
Final version before revision to all

@@
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
-\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
-&\hspace{0.5cm}& \qquad {} \qquad {} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
-\sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \geq t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
+\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
+\sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
 \delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
@@
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\sigma_{l,k,n}^{(i)} &=& \max{\left (0, \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right )}  \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\sigma_{l,k,n}^{(i)} &=& \max{\left \lbrace 0, \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right \rbrace }  \IEEEyessubnumber \label{kkt-mse-4.2} \\
 \alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
@@
  \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
- for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
+ \ForEach{\ac{BS} \me{b \in \mc{B}}}{
  set the maximum iteration counter \me{I_{\max},J_{\max}} to a valid number. \;
+ initialize \me{i = 0}. \;
+ \Repeat{until convergence or \me{i \geq I_{\max}}}{
  initialize \me{j = 0}. \;
  \Repeat{until convergence or \me{j \geq J_{\max}}}{
- initialize \me{i = 0}. \;
- \Repeat{until convergence or \me{i \geq I_{\max}}}{
 	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is identified by the bisection method satisfying \eqref{kkt-mse-1.4}. \;
@@
     perform precoded uplink pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j)}}. \;
-    \me{i = i + 1} \;
+  \me{j = j + 1}. \;
   }
@@
  inform \acp{BS} using uplink precoded pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j+1)}}. \;
- \me{j = j + 1}. \;
+ \me{i = i + 1} \;
+ }
  }

### 2014-09-15 Report/simulation_results.tex
Final version before revision to all

@@
 In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
-The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lower path loss.
+The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lowest path loss component.
 Fig.
@@
 \hfill
-\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,3,9,4,2\rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-2-2}
+\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
+\includegraphics[width=0.48\textwidth]{fig-2-4}
 \label{fig-2}}
@@
 
-In the sub-channel wise allocations, where the total transmit power is shared equally among the sub-channels, the precoders are designed for each sub-channels independently.
-In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels.
-At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random initial point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders.
-The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig.
-\ref{fig-1} for the discussed centralized schemes and the convergence point are marked with the data tips.
 Fig.
-\ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas.
-In all the schemes, the receive beamformers are updated at the \ac{SCA} update points instead of updating after the \ac{SCA} convergence as in Algorithm.
-\ref{algo-1}.
+\ref{fig-a} compares the performance of the centralized algorithms with the total number of residual bits remaining in the system after the current transmission slot.
+The reduction in the number of queued packets after each \ac{SCA} updates are plotted in the figures.
+It can be seen from Fig.
+\ref{fig-a}, the \ac{Q-WSRM} algorithm is not optimal due to the problem of over allocation when the number of queued packets are small.
+In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over allocation problem.
+It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}.
+It can be seen that all the algorithms are Pareto-optimal and provides different performance based on the weights used to find a point in the rate region.
+
+In the scenario defined by Fig.
+\ref{fig-a}, \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the rate maximization algorithm.
+The performance degradation can be attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
+Fig.
+\ref{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case.
+In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in the Algorithm \ref{algo-1}.
+It is also noted that the performance degradation by performing the group update is very minimal.
 Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.

### 2014-09-15 Report/sub_channel_wsrm.tex
Final version before revision to all

@@
 \begin{equation}
-Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
+Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
 \label{eqn-weight}
@@
 where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}.
-In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,j}} is the rate or guaranteed bits allocated over the sub-channel \me{j}.
+In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}.
 The current scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.
@@
  \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
+ \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
  update \me{\mvec{w}{l,k,\hat{n}}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,\hat{n}}}.\;
- \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
- \Repeat{\ac{SCA} convergence or \me{i \geq I_{\max}}}{
+ \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
+ initialize \me{j = 0}. \;
+ \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
  solve for the transmit precoders \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} \;
@@
 \;
- $i = i + 1$. \;
+ $j = j + 1$. \;
  }
  update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
- $j = j + 1$. \;
+ $i = i + 1$. \;
  }

### 2014-09-15 Report/wsrm_formulation.tex
Final version before revision to all

@@
 Instead of initializing \me{\tilde{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{\tilde{\mbf{u}}_{l,k,n}} in an efficient manner as briefed in Algorithm \ref{algo-1}.
-In Algorithm \ref{algo-1}, the \ac{SCA} iterations are carried until convergence or for maximum of \me{I_{\max}} iterations for the optimal \me{\mbf{w}_{l,k,n}} receive beamformers and the outer iterations are for the convergence of the number of queued bits, which is limited by the maximum of \me{J_{\max}} iterations.
+For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for the predefined iterations, say \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
+Next, the receive beamformers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
+This procedure is carried out until convergence of the queue deviation or for fixed number of iterations defined by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
 \begin{algorithm}
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
+ \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
  update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}}.\;
- \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
- \Repeat{\ac{SCA} convergence or \me{i \geq I_{\max}}}{
+ \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
+ initialize \me{j = 0}. \;
+ \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
  solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9} \;
@@
 \;
- $i = i + 1$. \;
+ $j = j + 1$. \;
  }
  update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
- $j = j + 1$. \;
+ $i = i + 1$. \;
  }

### 2014-09-17 Report/ieee_journal.tex
halfway through double_column

@@
-\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
 
+\usepackage{etoolbox}
 \usepackage{amsmath,amssymb}
@@
 
+\newtoggle{single_column}
+\togglefalse{single_column}
+
+\iftoggle{single_column}{
 	\doublespacing
+}
 
-\title{Traffic aware Resource Allocation for \acs{MIMO}-\acs{OFDM} systems}
+\title{Traffic aware Resource Allocation schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} systems}
 \author{

### 2014-09-17 Report/system_model.tex
halfway through double_column

@@
 Consequently, the received data symbol corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
+\iftoggle{single_column}{
 \begin{equation}\label{eqn-1}
@@
 \end{equation}
+}{
+\begin{multline}\label{eqn-1}
+\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n} \\ 
++ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
+\end{multline}
+}
+
 where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.

### 2014-09-29 Report/dual_approach.tex
Antti Changes included

@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} - \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
 \text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
@@
 && \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-dual-1e} \\
-&\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-primal-1c} \IEEEyessubnumber \label{eqn-dual-1f}
+&\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3} \IEEEyessubnumber \label{eqn-dual-1f}
 \end{IEEEeqnarray}
@@
 \subsubsection*{Convergence}
-The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to the optimal value for a fixed \ac{SCA} point.
-Since subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to the optimal value \cite{boyd2011distributed} for a given \ac{SCA} point.
-The receive beamformers are updated at each \ac{SCA} update provides monotonic increase in the objective function, since the \ac{MMSE} receive beamformers are optimal for the fixed transmit precoders obtained by solving the subproblems until convergence.
+The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point.
+Since subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary value \cite{boyd2011distributed} for the fixed \ac{SCA} point.
+The receive beamformers are updated along with the \ac{SCA} update of the tuple \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}}.
+Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic  increase in the objective function.
 The algorithmic representation of the \ac{ADMM} based approach for decentralization is given in Algorithm \ref{algo-3}.
@@
     }
-    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} by exchanging the recent precoders \me{\mvec{m}{l,k,n}} \;
-    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
+    updated \me{\mvec{W}{k,n}} is notified to all \acp{BS} in \me{\mc{B}} by uplink precoded pilots as in \cite{komulainen2013effective},\;
     update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;

### 2014-09-29 Report/introduction.tex
Antti Changes included

@@
 These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints.
-In this work, we consider the problem of transmit design over the space-frequency resources provided by the \acs{MIMO}-\ac{OFDM} framework in the downlink broadcast transmission to minimize the number of queued packets.
+We consider the problem of transmit design over the space-frequency resources provided by the \acs{MIMO}-\ac{OFDM} framework in the downlink broadcast transmission to minimize the number of queued packets.
 Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation to minimize the total number of backlogged packets of all \acp{BS}.
@@
 
-The queue minimizing precoder designs are closely related to the \ac{WSRM} problem with additional rate constraints determined by the number of backlogged packets for each user in the system (see Section \ref{sec-3} for further discussions).
-The topics on \ac{MIMO} \ac{BC} precoder design have been studied extensively with different performance criteria in the literature.
-Due to the nonconvex nature of the \ac{MIMO} \ac{BC} precoder design problems, the \ac{SCA} method has gradually become a powerful tool to deal with these problems.
+The queue minimizing precoder designs are closely related to the \ac{WSRM} problem with additional rate constraints determined by the number of backlogged packets for each user in the system.
+The topics on \ac{MIMO} \ac{IBC} precoder design have been studied extensively with different performance criteria in the literature.
+Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, the \ac{SCA} method has become a powerful tool to deal with these problems.
 For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around an operating point in order to solve the \ac{WSRM} problem in an iterative manner.
@@
 
-The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} is also used to solve the \ac{WSRM} problem.
-In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed \ac{MMSE} receivers.
+The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} can also be used to solve the \ac{WSRM} problem.
+In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients.
 In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders.
@@
 
-The problem of precoder design for the \ac{MIMO} \ac{BC} system are solved either by using a centralized controller or by using decentralized algorithms where all \acp{BS} often handles its own problem and exchange limited information via backhaul.
+The problem of precoder design for the \ac{MIMO} \ac{IBC} system are solved either by using a centralized controller or by using decentralized algorithms where all \acp{BS} handles their own subproblems and exchange limited information via backhaul.
 The distributed approaches are based on primal, dual or \ac{ADMM} decomposition, which are discussed in a detailed manner in \cite{palomar2006tutorial,boyd2011distributed}.
@@
 
-By adjusting the weights properly, we can find arbitrary rate-tuple in the rate region of the system that maximizes other performance measures by solving the resulting WSRM problem.
+By adjusting the weights in the \ac{WSRM} objective properly, we can find arbitrary rate-tuple in the rate region of the system that maximizes the suitable objective measures.
 For example, if the weight of each user is set to be inversely proportional to his/her average data rate, the corresponding problem guarantees fairness on an average among the users.
@@
 In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} by geometric programming formulations.
-Since the problem considered in \cite{qps_cioffi} assumed single antenna transmitters and receivers, the queue minimizing problem reduces to the one of optimal power allocation.
+Since the problem addressed in \cite{qps_cioffi} assumed single antenna transmitters and receivers, the queue minimizing problem reduces to the one of optimal power allocation.
 In the context of wireless networks, the backpressure algorithm mentioned above was extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.

### 2014-09-29 Report/joint_wsrm_formulation.tex
Antti Changes included

@@
 \begin{equation}
-\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k(i)
+\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i)
 \end{equation}
@@
 \underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
- &\leq& \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber
+ &\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
 \end{IEEEeqnarray}
 where the second term on the r.h.s follows from the Poisson arrival process.
-Assuming the second order moments of the transmission rates and the arrival rates are bounded, it can be replaced by a suitable bound \me{B} in order to eliminate from the optimization problem \cite{neely2010stochastic}.
+Assuming the second order moments of the transmission rates and the arrival rates are bounded, the sum of arrivals and the transmission rates can be replaced by a upper bound \me{B} as in \eqref{backpreassure-approx-1b}, in order to eliminate from the optimization problem \cite{neely2010stochastic}.
+The expectation is performed across all possible arrivals and the transmission rates for the given number of queued packets \me{\mbf{Q}(i)} and the channel state information at the \me{\ith{i}} slot.
 
@@
 The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
-The \ac{Q-WSRM} formulation is given by
+The \ac{Q-WSRM} formulation is given by optimizing each term inside the expectation operator \me{\mbf{E}_{\mbfa{\lambda},\mbf{t}}} in \eqref{backpreassure-approx-1b}, which maximizes the
 \begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
@@
 
-As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as
-\begin{IEEEeqnarray}{rCl}\label{gen_sum}
-\underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \IEEEyessubnumber \\
-\text{subject to.} & \quad & \eqref{eqn-3.1.3} \; \text{and} \; \eqref{eqn-3.1.4} \IEEEyessubnumber
-\end{IEEEeqnarray}
-The problem defined in \eqref{gen_sum} provides a greedy queue minimizing approach as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison with the number of queued packets as in \ac{Q-WSRME}.
+As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}.
+This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison with the number of queued packets as in \ac{Q-WSRME}.
 Note that in both formulations, the resources allocated to the users are limited by the backlogged packets with an explicit maximum rate constraint defined by \eqref{eqn-3.1.4}.

### 2014-09-29 Report/kkt_mse_approach.tex
Antti Changes included

@@
 The distributed solutions via primal and \ac{ADMM} approaches depend on the subgradient update by using a step size parameter for the coupling variables, which affects the speed of convergence to the optimal value.
-In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by solving the \ac{KKT} conditions.
+In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by directly solving the \ac{KKT} conditions.
 Similar work has been considered for the \ac{WSRM} problem with the minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
@@
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\sigma_{l,k,n}^{(i)} &=& \max{\left \lbrace 0, \frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right \rbrace }  \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\sigma_{l,k,n}^{(i)} &=& \left [\frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right ]^+  \IEEEyessubnumber \label{kkt-mse-4.2} \\
 \alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
@@
 In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.
+At each iteration, the dual variable \me{\alpha^{(i)}} is updated linearly from the earlier value \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}.
 It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduce the transmit precoder weights in \eqref{kkt-mse-4.3}.
@@
 \subsubsection*{Convergence}
-The iterative method presented in Algorithm \ref{algo-4} converges to the stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge.
+The iterative method presented in Algorithm \ref{algo-4} converges to the stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}.
 The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive precoders \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}.

### 2014-09-29 Report/mse_formulation.tex
Antti Changes included

@@
 \subsubsection*{Convergence}
-Following the similar arguments as in  Section \ref{sec-3.2.1}, we can see that the \ac{SCA} subproblems converges to a stationary point.
-The transmit precoders obtained by the \ac{MSE} relaxations are unique due to the \ac{MSE} expression in \eqref{eqn-mse-2.3}, since it removes the phase ambiguity due to the real valued expression for the transmit precoders as
+Following the similar arguments as in  Section \ref{sec-3.2.1}, we can see that the \ac{SCA} subproblems converges to a stationary point of the original nonconvex problem at each iteration.
+The uniqueness of the transmit and the receive precoders are justified if the phase ambiguity from the stationary solution is eliminated.
+It can be seen from the \ac{MSE} expression \eqref{eqn-mse-2.3} that the phase rotations are fixed for both transmit and the receive precoders at the stationary point, which is evident from the following reformulation of \eqref{eqn-mse-2.3} as
 \begin{equation}

### 2014-09-29 Report/primal_approach.tex
Antti Changes included

@@
 The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows the same.
-Much of the details are provided in the Appendix \ref{a-2}.
+%Much of the details are provided in the Appendix \ref{a-2}.
 
 \subsubsection*{Convergence}
-The convergence of the primal is similar to that of the centralized problem if the interference variables \me{\zeta_{l,k,n,b}} are allowed to converge to the optimal values.
+The convergence of the primal is similar to that of the centralized problem if the interference variables \me{\zeta_{l,k,n,b}} are allowed to converge to a stationary point.
 But in practice, we can limit the number of exchanges to \me{J_{\max}} after which \ac{SCA} update is performed until convergence or for \me{I_{\max}} times.

### 2014-09-29 Report/problem_formulation.tex
Antti Changes included

@@
 Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over allocation.
-In the current queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself.
+In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself.
+This makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \acp{BS} independently by exchanging minimal information exchange \cite{boyd2011distributed}.
 In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system.

### 2014-09-29 Report/problem_formulation_intro.tex
Antti Changes included

@@
 
-For practical and tractability reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
+For practical reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
 As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
@@
 \item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
-As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem \eqref{gen_sum} when the queue size is large enough for all users.
+As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
 \item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
-For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
+For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
 \item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.

### 2014-09-29 Report/simulation_distributed.tex
Antti Changes included

@@
 Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}.
+The total number of queued packets assumed for both figures is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
 As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the choice of the step size used in the subgradient update.
-Since the interference values are fixed for local subproblem in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update using \eqref{primal-sg-update} is not valid.
+Since the interference values are fixed for local subproblem in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
 
@@
 \ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points.
-In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations by exchanging either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme.
+In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations to exchange either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme.
+In Fig.
+\ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence.
 It can be seen from Fig.
@@
 \subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-3}
+\includegraphics[width=0.48\textwidth]{fig-3-1}
 \label{fig-d-1}
@@
 \subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-5}
+\includegraphics[width=0.48\textwidth]{fig-5-1}
 \label{fig-d-2}
@@
 \ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update.
-In case of the distributed algorithms, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations.
-In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant.
+In case of the distributed approaches, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations.
+In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant, which affects the convergence rate and the stationary point of the final solution.
 The data tips are used to highlight the convergent points of various algorithms.
@@
 \centering
-\includegraphics[width=\columnwidth]{fig-9-2}
+\includegraphics[width=\columnwidth]{fig-9-2-1}
 \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
@@
 The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables \me{\alpha_{l,k,n}} and \me{\sigma_{l,k,n}} are not iterated until convergence between each \ac{SCA} steps in the \ac{KKT} approach.
-In the simulation, we update all the variables at each iteration due to the practical issues in the signaling between the \acp{BS}.
+In the simulation, we update all the variables at once at each iteration, \textit{i.e}, \me{J_{\max} = 1}, which is well justified for the practical implementations due to the signaling overheads.
 Fig.

### 2014-09-29 Report/simulation_results.tex
Antti Changes included

@@
 To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
-The number of packets waiting at the transmitter for each user is given by \me{Q_k = 5,8} and \me{6} bits respectively.
+The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits respectively.
 
-Fig.
-\ref{tbl-1} plots the sub-channel wise channel seen by the users followed by the assigned rates over each sub-channel by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} precoder design proposed in \cite{wmmse_shi}.
-The performance metric used for the comparison of different algorithms is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
-It can be seen from Fig.
-\ref{tbl-1}, the \ac{Q-WSRME} scheme provides more priority to the third user with \me{Q_{3} = 6} bits as compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel.
-In contrast to the \ac{Q-WSRME} scheme, the \ac{JSFRA} approach assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
+Table.
+\ref{tbl-1} outlines the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} design \cite{wmmse_shi}.
+The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
+Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} got scheduled in the first sub-channel due to the better channel condition.
+In contrast to the \ac{Q-WSRME} scheme, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets waiting at the transmitter.
+The rate allocated for \me{\mc{U}(2)} on the second sub-channel is higher in \ac{JSFRA} scheme compared to the other schemes.
+It is due to the efficient allocation of the total power shared across the sub-channels.
 \begin{table*}
@@
 \cline{3-14}
- && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
+ && SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
 \hline
-\me{1} & \me{5} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.91} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
-\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.46}  &  \me{3.54} & \me{0} &  \me{4.36}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
-\me{3} & \me{6} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{5.72} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{5.79} & \me{5.81} &  \me{0}  &  \me{0} \\
+\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
+\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
+\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
 \hline
-\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{5.28} bits} & \multicolumn{3}{c|}{\me{3.91} bits} & \multicolumn{3}{c|}{\me{5.28} bits} \\
+\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
 \hline
@@
 It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
+The total number of queued packets for Fig.
+\ref{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig.
+\ref{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
 \begin{figure*}
@@
 \subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-1-3}
+\includegraphics[width=0.48\textwidth]{fig-1-3-1}
 \label{fig-1}}
@@
 \subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-2-4}
+\includegraphics[width=0.48\textwidth]{fig-2-4-1}
 \label{fig-2}}
@@
 
-Fig.
-\ref{fig-a} compares the performance of the centralized algorithms with the total number of residual bits remaining in the system after the current transmission slot.
-The reduction in the number of queued packets after each \ac{SCA} updates are plotted in the figures.
-It can be seen from Fig.
-\ref{fig-a}, the \ac{Q-WSRM} algorithm is not optimal due to the problem of over allocation when the number of queued packets are small.
+The performance of the centralized algorithms are compared by the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
+\ref{fig-a}.
+The \ac{Q-WSRM} algorithm is not optimal due to the problem of over allocation when the number of queued packets are small, as in Fig.
+\ref{fig-a}.
 In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over allocation problem.

### 2014-09-29 Report/sub_channel_wsrm.tex
Antti Changes included

@@
 In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
-The centralized precoder design can also be performed across each sub-channel by using the decomposition methods discussed in \cite{palomar2006tutorial,boyd2011distributed}.
+It can also be solved efficiently by using the distributed algorithms discussed in \cite{palomar2006tutorial,boyd2011distributed} to perform the precoder design over each sub-channel by relaxing the coupling power variable for each sub-channel.
 
@@
 In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}.
-The current scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.
+However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.
 The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
@@
  \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
- solve for the transmit precoders \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} \;
+ solve for the transmit precoders \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}} \;
  update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,\hat{n}}}, \me{\tilde{q}_{l,k,\hat{n}}} and \me{\tilde{\beta}_{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,\hat{n}}} obtained from the previous step.

### 2014-09-29 Report/system_model.tex
Antti Changes included

@@
-We consider a downlink \ac{MIMO} \ac{BC} scenario in an \ac{OFDM} framework with \me{N} sub-channels and \me{N_B} \acp{BS} each equipped with \me{N_T} transmit antennas, serving \me{K} users each with \me{N_R} receive antennas.
+We consider a downlink \ac{MIMO} \ac{IBC} scenario in an \ac{OFDM} framework with \me{N} sub-channels and \me{N_B} \acp{BS} each equipped with \me{N_T} transmit antennas, serving in total \me{K} users each with \me{N_R} receive antennas.
 The set of users associated with \ac{BS} \me{b} is denoted by \me{\mathcal{U}_b} and the set \me{\mathcal{U}} represents all users in the system, i.e., \me{\mathcal{U} =\underset{b\in \mathcal{B}}{\cup }\mathcal{U}_b}, where \me{\mathcal{B}} is the set of all coordinating \acp{BS}.

### 2014-09-29 Report/wsrm_formulation.tex
Antti Changes included

@@
 In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-However, this step is without loss of optimality leads to the same solution, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}.
+However, this step without loss of optimality leads to the same solution, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}.
 Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by the user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}.
@@
 Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and find the optimal transmit beamformers.
+Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
 Recall the original coordinate descent method assumes that the optimization variables belong to disjoint sets (Cartesian product of sets, to be precise) \cite{xu2013block}.
@@
 where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the earlier iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
-It can be seen that the optimal receiver expression in \eqref{opt-rx} is the scaled version of the \ac{MMSE} receiver, which is given by
+Note that \eqref{opt-rx} is obtained by iterating over the fixed \me{\mvec{w}{l,k,n}^{(i-1)}} at each \ac{SCA} iteration until convergence or for fixed number of iterations.
+It can be seen that the optimal receiver expression in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-10}
@@
 
-In order to prove the convergence of the proposed algorithm, we require the following conditions to be satisfied
+In order to prove the convergence of the proposed algorithm, we require the following conditions to be satisfied \cite{scutari}
 \begin{itemize}
@@
 where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}.
-Using the assumptions in \eqref{sca-req}, the global optimal point of the relaxed formulation, which is a convex problem, satisfies the \ac{KKT} conditions of the original nonconvex problem, using \eqref{sca-req}.
-It shows that each relaxed formulation converges to the optimal point.
+The stationary point of the relaxed formulation, which is a convex problem, satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}.
+It can be seen that the  \ac{SCA} relaxed formulation converges to a local stationary point at each iteration.
 
@@
 The monotonic convergence of the objective function can be justified by the following arguments.
-At each \ac{SCA} iteration, the relaxed subproblem is solved for the optimal transmit precoders to minimize the objective function.
+At each \ac{SCA} iteration, the relaxed subproblem is solved for the locally optimal transmit precoders to minimize the objective function.
 Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point,\textit{i.e} \me{\mbf{x}^{\ast(i-1)}}, for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
@@
 
-Once the problem converged to an optimal transmit precoders, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}.
-The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, the proposed \ac{JSFRA} scheme guarantees to converge to an optimal point.
+Once the problem is converged to a stationary transmit precoders, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}.
+The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, the proposed \ac{JSFRA} scheme guarantees to converge to a stationary point of the original nonconvex problem.

### 2014-09-30 Report/decomposition_solutions.tex
Updated double column

@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-decent-1}
-\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
+\underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
 \text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber,
@@
 Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-2.3} can be expressed by grouping the interference contribution from each \acp{BS} in the coordinating set \me{\mathrm{B}} as
+\iftoggle{single_column}{
 \begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
 \beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2 \label{eqn-decent-3a}
+&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2
 \end{IEEEeqnarray}
+}{
+\begin{multline}\label{eqn-decent-3}
+	\beta_{l,k,n} \geq \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \\
+	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2
+\end{multline}
+}
 where \me{\zeta_{l,k,n,b}}, which is the total interference caused by the \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by

### 2014-09-30 Report/dual_approach.tex
Updated double column

@@
 \mbfa{\zeta} &=& \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1},  \right. \nonumber \\
-&\quad& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \IEEEyessubnumber \\
+&& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
 n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right | \IEEEyessubnumber
@@
 The equality constraint for the local and the consensus interference vector \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} present in each subproblem is relaxed by the taking the partial Lagrangian.
-Now, the subproblem at the \ac{BS} \me{b} for the \me{\ith{i}} iteration is given by
+Now, the subproblem at \ac{BS} \me{b} for the \me{\ith{i}} iteration is given by
+\iftoggle{single_column}{
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
@@
 && \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-dual-1d} \\
-&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{C} \IEEEyessubnumber \label{eqn-dual-1e} \\
+&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
 &\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3} \IEEEyessubnumber \label{eqn-dual-1f}
 \end{IEEEeqnarray}
+}{
+\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
+	\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) \vspace{-0.25cm} \nonumber \\
+	&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \vspace{-0.25cm} \\
+	\text{subject to} &\quad& \nonumber \\
+	\beta_{l,k,n} \geq \sum_{\mathclap{j = 1,j \neq l}}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
+	+ \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\
+	\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
+	&& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3} \IEEEyessubnumber \label{eqn-dual-1f}
+\end{IEEEeqnarray}
+}
 where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i-1)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.
@@
 \end{equation}
-The dual variable entries in the vector \me{\mbfa{\nu}^{\set{b_k}}}, which is the stacked dual variables corresponding to the interference equality constraint at the \ac{BS} \me{b_k}, are updated using the subgradient as
+The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which is the stacked dual variables of the interference equality constraint at the \ac{BS} \me{b_k}, are updated using the subgradient as
 \begin{equation}\label{dual-sg-update}
-\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ), \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}
+\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right )
+%, \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}
 \end{equation}
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
- update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
+ \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
+ update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;
  initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
@@
     \Repeat{convergence or \me{j \geq J_{\max}}}{
-        solve for the transmit precoders \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
-        exchange \me{\mbfa{\zeta}^{\set{b}(j)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
-		update the dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update} \;
-        update the global interference vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update} \;
-		\me{j = j + 1} \;
+        solve for \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
+        exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
+		update dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update}\;
+        update the consensus vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update}\;
+		\me{j = j + 1}\;
     }
-    updated \me{\mvec{W}{k,n}} is notified to all \acp{BS} in \me{\mc{B}} by uplink precoded pilots as in \cite{komulainen2013effective},\;
-    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
-    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
+	downlink transmission from all \acp{BS} to notify the precoders to update \me{\mvec{W}{k,n}} from users\;
+    updated \me{\mvec{W}{k,n}} is notified to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
+    update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
+    update \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} approach \;
     $i = i + 1$ \;

### 2014-09-30 Report/ieee_journal.tex
Antti Changes included
Updated double column

@@
 \usepackage[ruled]{algorithm2e}
-\usepackage{subfig,subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools}
+\usepackage{subfig,subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno}
 
@@
 
-\title{Traffic aware Resource Allocation schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} systems}
+\title{Traffic aware Precoding and Resource Allocation schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} systems}
 \author{
@@
 
-\begin{keywords}
-\acs{MIMO}-\acs{OFDM}, weighted sum rate maximization, precoder design, queue driven scheduling and precoder design
-\end{keywords}
+%\begin{keywords}
+%\acs{MIMO}-\acs{OFDM}, weighted sum rate maximization, precoder design, queue driven scheduling and precoder design
+%\end{keywords}
 
@@
 
-\subsection{\acs{JSFRA} scheme via Successive Convex Approximation (\acs{SCA})} \label{sec-3.2.1}
+\subsection{\acs{JSFRA} scheme via \ac{SCA} approach} \label{sec-3.2.1}
 \input{problem_formulation}
@@
 
-\subsection{\ac{JSFRA} scheme via MSE reformulation} \label{sec-3.3}
+\subsection{\ac{JSFRA} scheme via \ac{MSE} reformulation} \label{sec-3.3}
 \input{mse_formulation}
@@
 
-\section{\acl{PD} approach} \label{a-2}
-\input{primal_approach_appendix}
+%\section{\acl{PD} approach} \label{a-2}
+%\input{primal_approach_appendix}
 

### 2014-09-30 Report/introduction.tex
Updated double column

@@
 The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks.
-The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which are proportional to the mobile battery drain.
-In order to overcome the receiver complexity, \ac{OFDM} based transmissions are introduced for the wide band transmissions.
+The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption.
+In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions.
 To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension.
@@
 
-By adjusting the weights in the \ac{WSRM} objective properly, we can find arbitrary rate-tuple in the rate region of the system that maximizes the suitable objective measures.
+By adjusting the weights in the \ac{WSRM} objective properly, we can find arbitrary rate-tuple in the rate region that maximizes the suitable objective measures.
 For example, if the weight of each user is set to be inversely proportional to his/her average data rate, the corresponding problem guarantees fairness on an average among the users.
@@
 More specifically, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function of it,  which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}.
-In the backpressure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
+In backpressure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
 
 Earlier studies on the queue minimization problem was summarized in the survey paper \cite{berry2004cross}.
-In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} by geometric programming formulations.
-Since the problem addressed in \cite{qps_cioffi} assumed single antenna transmitters and receivers, the queue minimizing problem reduces to the one of optimal power allocation.
+In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} using geometric programming.
+Since the problem addressed in \cite{qps_cioffi} assumed single antenna transmitters and receivers, the queue minimizing problem reduces to the optimal power allocation problem.
 In the context of wireless networks, the backpressure algorithm mentioned above was extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.

### 2014-09-30 Report/joint_wsrm_formulation.tex
Updated double column

@@
 3]{neely2010stochastic}.
-Now the Lyapunov function drift is given by
+The Lyapunov function drift, expressed as \me{\Delta(\mbf{Q}(i)) = \mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)}}, is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-3.1}
-\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} &=& \frac{1}{2} \left [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \right ] \IEEEyessubnumber \label{eqn-3.1.0} \\
+&=&\frac{1}{2} \left [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \right ] \IEEEyessubnumber \label{eqn-3.1.0} \\
 &\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) } \IEEEyessubnumber \label{drift-exp}
@@
 The Lyapunov drift conditioned on the current backlogged packets \me{\mbfa{Q}(i)} is given by
+\iftoggle{single_column}{
 \begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
@@
 \end{IEEEeqnarray}
-where the second term on the r.h.s follows from the Poisson arrival process.
-Assuming the second order moments of the transmission rates and the arrival rates are bounded, the sum of arrivals and the transmission rates can be replaced by a upper bound \me{B} as in \eqref{backpreassure-approx-1b}, in order to eliminate from the optimization problem \cite{neely2010stochastic}.
+}{
+\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
+	\underset{\mbf{t}}{\text{minimize}} && \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
+	&& - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
+\end{IEEEeqnarray}	
+}
+where the second term in \eqref{backpreassure-approx-1b} follows from the Poisson arrival process.
+Assuming the second order moments of the transmissions and the arrival rates are bounded, it can be replaced by a upper bound \me{B} as in \eqref{backpreassure-approx-1b}, in order to eliminate from the optimization problem \cite{neely2010stochastic}.
 The expectation is performed across all possible arrivals and the transmission rates for the given number of queued packets \me{\mbf{Q}(i)} and the channel state information at the \me{\ith{i}} slot.

### 2014-09-30 Report/mse_formulation.tex
Updated double column

@@
 In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable capacity for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}.
-The \ac{MSE} for the data symbol, represented as \me{\epsilon_{l,k,n}}, is given by
-\begin{subeqnarray} \label{mse-error}
-\epsilon_{l,k,n} &=& \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] \\
- &=&  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
-\end{subeqnarray}
+The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
+\iftoggle{single_column}{
+\begin{IEEEeqnarray}{rCl} \label{mse-error}
+	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+\end{IEEEeqnarray}
+}{
+\begin{IEEEeqnarray}{rCl} \label{mse-error}
+ \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \nonumber \\
+ + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+\end{IEEEeqnarray}
+}
 where \me{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}} denotes the transmit and the receive beamformer and \me{\hat{d}_{l,k,n}} is the received symbol as in \eqref{eqn-1}.
@@
 Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
+\iftoggle{single_column}{
+\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
+\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
+\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
+ & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
+& \quad &  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
+\end{IEEEeqnarray}
+}{
 \begin{IEEEeqnarray}{LL}\label{eqn-mse-1}
-\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
-\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
- & \quad \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
-& \quad \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
+	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
+	\text{subject to} & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
+	& \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
+	& \qquad \quad {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
+	&  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
 \end{IEEEeqnarray}
-where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the \ac{MSE} relation.
+}
+where \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the \ac{MSE} relation and \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}}.
 
@@
 In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}.
-The first order Taylor approximation around a fixed \ac{MSE} value \me{\tilde{\epsilon}_{l,k,n}} for \eqref{eqn-mse-1.2} is given by
+The first order approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} for \eqref{eqn-mse-1.2} is given by
 \begin{IEEEeqnarray}{rCl}
@@
 The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
+\iftoggle{single_column}{
 \begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
@@
 \end{IEEEeqnarray}
-
+}{
+\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
+	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
+	\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
+	& \quad & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
+	&\quad& + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n} \eqsub \label{eqn-mse-2.3}
+\end{IEEEeqnarray}
+}
 \subsubsection*{Convergence}
@@
 It can be seen from the \ac{MSE} expression \eqref{eqn-mse-2.3} that the phase rotations are fixed for both transmit and the receive precoders at the stationary point, which is evident from the following reformulation of \eqref{eqn-mse-2.3} as
+\iftoggle{single_column}{
 \begin{equation}
@@
 \end{equation}
+}{
+\begin{multline}
+	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
+	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+\end{multline}
+}
 At each \ac{SCA} step, the transmit precoders are obtained uniquely by minimizing the weighted \ac{MSE} criterion due to the convex nature of the relaxed problem.

### 2014-09-30 Report/primal_approach.tex
Updated double column

@@
 The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}.
-Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3a}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration and is carried out until convergence.
+Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration and is carried out until convergence.
 The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows the same.

### 2014-09-30 Report/problem_formulation_intro.tex
Updated double column

@@
 \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
-In \eqref{eqn-4.3}, we consider a \ac{BS} specific sum power constraint for each \ac{BS} across all sub-channels.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively.\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users} In \eqref{eqn-4.3}, we consider a \ac{BS} specific sum power constraint for each \ac{BS} across all sub-channels.
 
@@
 \begin{itemize}
-\item With \me{\ell_{q = 1}}, the objective results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
+\item \me{\ell_{q = 1}} results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
 As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
-\item With \me{\ell_{q = 2}}, the objective prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
+\item \me{\ell_{q = 2}} prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
 For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
-\item With \(\ell_{q = \infty} \), the objective minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
+\item \(\ell_{q = \infty} \) minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
 \end{itemize}

### 2014-09-30 Report/sub_channel_wsrm.tex
Updated double column

@@
 In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
-It can also be solved efficiently by using the distributed algorithms discussed in \cite{palomar2006tutorial,boyd2011distributed} to perform the precoder design over each sub-channel by relaxing the coupling power variable for each sub-channel.
+The optimal approach is to decompose the problem over each sub-channel with a fixed transmit power constraint for each sub-channel.
+The power allocated for each sub-channel is controlled by a master problem based on different algorithms as discussed in \cite{palomar2006tutorial,boyd2011distributed}.
 
@@
  \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
- update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}. \;
+ update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
  \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
- update \me{\mvec{w}{l,k,\hat{n}}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,\hat{n}}}.\;
+ \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
+ update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
  \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
- initialize \me{j = 0}. \;
+ initialize \me{j = 0}\;
  \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
- solve for the transmit precoders \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}} \;
- update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,\hat{n}}}, \me{\tilde{q}_{l,k,\hat{n}}} and \me{\tilde{\beta}_{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,\hat{n}}} obtained from the previous step.
-\;
- $j = j + 1$. \;
+ solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
+ update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
+ $j = j + 1$\;
  }
- update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
- $i = i + 1$. \;
+ update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
+ $i = i + 1$\;
  }

### 2014-09-30 Report/system_model.tex
Updated double column

@@
 }
-
 where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
-In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams \footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
-Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
+In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams.\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted} Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
 \begin{equation}\label{eq:SINR}

### 2014-09-30 Report/wsrm_formulation.tex
Updated double column

@@
 Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
-\begin{IEEEeqnarray}{RCL}\label{eqn-6}
+\iftoggle{single_column}{
+\begin{IEEEeqnarray}{rCl}\label{eqn-6}
 \underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
-\text{subject to}& \quad &\gamma_{l,k,n} \leq \dfrac{\left | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n} \right |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \label{eqn-6.2} \\
-  & \quad & \beta_{l,k,n} \geq  N_0 \|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
+\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \label{eqn-6.2} \\
+  & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
   & \quad &\eqref{eqn-4.3} \IEEEyessubnumber
 \end{IEEEeqnarray}
-where \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} be the vector which needs to be identified for the optimal allocation.
+}{
+\begin{IEEEeqnarray}{rCl}\label{eqn-6}
+	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
+	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
+	&\quad& \beta_{l,k,n} \geq \tilde{N}_0 + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
+	&\quad& \text{and } \eqref{eqn-4.3} \IEEEyessubnumber
+\end{IEEEeqnarray}
+}
+where \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} be the vector which needs to be identified for the optimal allocation and \me{\tilde{N}_0 = N_0\|\mvec{w}{l,k,n}\|^2} be the effective noise variance.
 In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}.
@@
 Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint
-\begin{equation}
-\label{eqn-8}
-2 \dfrac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \dfrac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \dfrac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \dfrac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}
+\iftoggle{single_column}{
+\begin{equation}\label{eqn-8}
+	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}
 \end{equation}
+}{
+\begin{multline}\label{eqn-8}
+	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) \\
+	 + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}
+\end{multline}
+}
 In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
 \begin{IEEEeqnarray}{rCl}\label{eqn-9}
-\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  N_0\|\mvec{w}{l,k,n}\|^2 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-9.1c} \\
-& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b}\sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
+\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}\\\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
+\text{subject to} & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
+& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
 & \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}
@@
 \begin{IEEEeqnarray}{rCl}\label{eqn-9--1}
-\underset{\substack{\gamma_{l,k,n},p_{l,k,n},q_{l,k,n} \\ \mvec{w}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
+\underset{\substack{\gamma_{l,k,n},\mvec{w}{l,k,n},\\\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
 \text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}
@@
 Solving \eqref{eqn-9--1} using \ac{KKT} conditions, we obtain the following iterative expression for the receive beamformer \me{\mvec{w}{l,k,n}} as
-\begin{subeqnarray} \label{opt-rx}
-\mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{(j,i)\neq (l,k)} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right ) \, \mvec{\widetilde{R}}{l,k,n}^{-1} \, \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}
-\end{subeqnarray}
+\begin{IEEEeqnarray}{rCl} \label{opt-rx}
+\mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace
+\end{IEEEeqnarray}
 where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the earlier iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
@@
 \begin{IEEEeqnarray}{rCl}\label{eqn-10}
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
 \mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n} \IEEEyessubnumber
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
- update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}}.\;
+ \KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{M}}_{k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
+ update \me{\mvec{W}{k,n}} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} using \me{\tilde{\mbf{M}}_{k,n}}\;
  \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
- initialize \me{j = 0}. \;
+ initialize \me{j = 0}\;
  \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
- solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9} \;
- update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,n}} obtained from the previous step.
-\;
- $j = j + 1$. \;
+ solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
+ update the constraint set \eqref{eqn-8} with \me{\tilde{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
+ $j = j + 1$\;
  }
- update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
- $i = i + 1$. \;
+ update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
+ $i = i + 1$\;
  }
@@
 
-In order to prove the convergence of the proposed algorithm, we require the following conditions to be satisfied \cite{scutari}
+In order to prove the convergence of the proposed iterative algorithm, we require the following conditions to be satisfied at each step \cite{scutari}
 \begin{itemize}
 	\item convergence of the \ac{SCA} subproblem	
-	\item uniqueness of the transmit and the receive beamformers obtained
+	\item uniqueness of the transmit and the receive beamformers
 	\item monotonic convergence of the objective function
@@
 where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}.
-The stationary point of the relaxed formulation, which is a convex problem, satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}.
+The stationary point of the relaxed convex problem satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}.
 It can be seen that the  \ac{SCA} relaxed formulation converges to a local stationary point at each iteration.
@@
 Once the problem is converged to a stationary transmit precoders, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}.
-The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, the proposed \ac{JSFRA} scheme guarantees to converge to a stationary point of the original nonconvex problem.
+The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, and hence the proposed \ac{JSFRA} scheme guarantees to converge to a stationary point of the original nonconvex problem.

### 2014-10-01 Report/decomposition_solutions.tex
temporary-commit

@@
 Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
-\begin{IEEEeqnarray}{rCl} \label{eqn-decent-1}
+\begin{IEEEeqnarray}{CCl} \label{eqn-decent-1}
 \underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
@@
 
-Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-2.3} can be expressed by grouping the interference contribution from each \acp{BS} in the coordinating set \me{\mathrm{B}} as
+Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \acp{BS} in the coordinating set \me{\mathrm{B}} as
 \iftoggle{single_column}{
@@
 \begin{multline}\label{eqn-decent-3}
-	\beta_{l,k,n} \geq \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \\
-	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2
+	N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
+	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n}
 \end{multline}
@@
 In order the solve for the global optimal precoders, we need to find the coupling variables \me{\zeta_{l,k,n,b}} by either \acl{PD} or by \acl{DD} method.
-In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} and \eqref{eqn-mse-2.3} for the \ac{MSE} relaxation schemes are decoupled to perform the distributed precoder design problem.
+In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} and \eqref{eqn-mse-1.3} for the \ac{MSE} relaxation schemes are decoupled to perform the distributed precoder design problem.

### 2014-10-01 Report/dual_approach.tex
temporary-commit

@@
 Now the sub problems are coupled by the global consensus vector \me{\mbfa{\zeta}} maintaining the complete stacked  interference profile of all users in the system as
-\begin{IEEEeqnarray}{rCl}
-\mbfa{\zeta} &=& \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1},  \right. \nonumber \\
-&& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
-n_{b_k} &=& |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right | \IEEEyessubnumber
+\begin{IEEEeqnarray}{ll}
+\mbfa{\zeta} &= \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1}, \right. \nonumber \\
+& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
+n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right | \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 && \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-dual-1d} \\
-&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
+&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
 &\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3} \IEEEyessubnumber \label{eqn-dual-1f}
@@
 	+ \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\
-	\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
+	\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
 	&& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3} \IEEEyessubnumber \label{eqn-dual-1f}
@@
 Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic  increase in the objective function.
-The algorithmic representation of the \ac{ADMM} based approach for decentralization is given in Algorithm \ref{algo-3}.
+Algorithm \ref{algo-3} outlines the \ac{ADMM} approach for distributed precoder design.
 \begin{algorithm}
@@
     }
-	downlink transmission from all \acp{BS} to notify the precoders to update \me{\mvec{W}{k,n}} from users\;
-    updated \me{\mvec{W}{k,n}} is notified to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
+	downlink precoded pilot transmission with \me{\mvec{M}{k,n}}\;
+    update \me{\mvec{W}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
     update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
-    update \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} approach \;
+    update \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} with equality for the \ac{MSE} approach \;
     $i = i + 1$ \;
@@
  }
- \caption{Decentralization via \ac{ADMM} for \acs{JSFRA} scheme}
+ \caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
   \label{algo-3}

### 2014-10-01 Report/ieee_journal.tex
temporary-commit

@@
 
+\newtoggle{enable_dist_fig}
 \newtoggle{single_column}
 \togglefalse{single_column}
+\togglefalse{enable_dist_fig}
 
@@
 
-\title{Traffic aware Precoding and Resource Allocation schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} systems}
+\title{Traffic aware Resource Allocation schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} systems}
 \author{
 	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\
-	\IEEEauthorblockA{Centre for Wireless Communications (CWC), \\ Department of Communications Engineering (DCE), \\
+	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
 		University of Oulu, Oulu, FI-90014\\

### 2014-10-01 Report/joint_wsrm_formulation.tex
temporary-commit

@@
 In order to minimize the squared sum at each instant, minimization of the Lyapunov drift \eqref{eqn-3.1} is carried over all possible rate allocations in the form of transmission rates \me{t_k} to users in the system.
-The Lyapunov drift conditioned on the current backlogged packets \me{\mbfa{Q}(i)} is given by
-\iftoggle{single_column}{
+The Lyapunov drift conditioned on the current backlogged packets \me{\mbfa{Q}(i)} is given by \eqref{backpressure-approx},
+%\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
+%	\underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+%	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
+%\end{IEEEeqnarray}
+%\begin{IEEEeqnarray}{CL} \label{backpressure-approx}
+%	& \underset{\mbf{t}}{\text{minimize}} \quad \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+%	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
+%	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
+%\end{IEEEeqnarray}	
+\begin{figure*}
 \begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
-	\underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
-	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
+	\underset{\mbf{t}}{\text{minimize}} &\quad& \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \vspace{-0.25in}\\
+	& \leq & \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} + \overbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}^{\le B}\IEEEyessubnumber \label{backpreassure-approx-1b}
 \end{IEEEeqnarray}	
-}{
-\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
-	\underset{\mbf{t}}{\text{minimize}} && \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
-	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
-	&& - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
-\end{IEEEeqnarray}	
-}
-where the second term in \eqref{backpreassure-approx-1b} follows from the Poisson arrival process.
+\vspace{-0.25in}
+\end{figure*}
+where the first term in \eqref{backpreassure-approx-1b} follows from the Poisson arrival process.
+
 Assuming the second order moments of the transmissions and the arrival rates are bounded, it can be replaced by a upper bound \me{B} as in \eqref{backpreassure-approx-1b}, in order to eliminate from the optimization problem \cite{neely2010stochastic}.

### 2014-10-01 Report/kkt_mse_approach.tex
temporary-commit

@@
 With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
+\iftoggle{single_column}{
 \begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
@@
 \end{IEEEeqnarray}
+}{
+\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
+	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
+	\text{subject to} & \nonumber \\
+	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
+	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
+	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
+	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
+\end{IEEEeqnarray}
+}
 where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.
@@
 Upon solving the \ac{KKT} expressions, the iterative solution \me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}} is given by
+\iftoggle{single_column}{
 \begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
 \mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
-\sigma_{l,k,n}^{(i)} &=& \left [\frac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right ]^+  \IEEEyessubnumber \label{kkt-mse-4.2} \\
-\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
+\sigma_{l,k,n}^{(i)} &=& \left [\tfrac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right ]^+  \IEEEyessubnumber \label{kkt-mse-4.2} \\
+\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
 \mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
 \end{IEEEeqnarray}
-Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other.
+}{
+\begin{IEEEeqnarray}{ll} \label{kkt-mse-4}
+	\mvec{m}{l,k,n}^{(i)} =& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} \nonumber \\
+	& \qquad {} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
+	\epsilon_{l,k,n}^{(i)} =& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \nonumber \\
+	& \qquad{} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+	t_{l,k,n}^{(i)} =&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \tfrac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
+	\sigma_{l,k,n}^{(i)} =& \Big [\tfrac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\Big ]^+  \IEEEyessubnumber \label{kkt-mse-4.2} \\
+	\alpha^{(i)}_{l,k,n} =& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
+	\mvec{w}{l,k,n}^{(i)} =& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm \nonumber \\
+	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
+\end{IEEEeqnarray}
+}
+Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-2.2}, one has to be fixed to optimize for the other.
 In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=1} and the receive beamformers \me{\mbf{w}^{(0)}_{l,k,n}} randomly}
- \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly and the dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}}
+ \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n},\epsilon_{l,k,n}^{(0)}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}}}
  \ForEach{\ac{BS} \me{b \in \mc{B}}}{
- set the maximum iteration counter \me{I_{\max},J_{\max}} to a valid number. \;
- initialize \me{i = 0}. \;
+ initialize \me{i = 0} \;
  \Repeat{until convergence or \me{i \geq I_{\max}}}{
- initialize \me{j = 0}. \;
- \Repeat{until convergence or \me{j \geq J_{\max}}}{
-	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is identified by the bisection method satisfying \eqref{kkt-mse-1.4}. \;
-    update \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at the receivers using the transmit precoders \me{\mvec{M}{k,n}^{(i)}} from all \acp{BS}.
-\;
-    perform precoded uplink pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j)}}. \;
-  \me{j = j + 1}. \;
-  }
- evaluate the receive beamforming vector \me{\mvec{W}{k,n}^{(j+1)}} using \eqref{kkt-mse-4.6}. \;
- inform \acp{BS} using uplink precoded pilot transmission from all users with the precoder \me{\mvec{\tilde{w}}{l,k,n}^{(j+1)}}. \;
+	find \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is obtained by bisection search satisfying \eqref{kkt-mse-1.4} \;
+	update \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at \ac{BS} \me{b} and perform precoded downlink pilot transmission with \me{\mvec{M}{k,n}^{(i)}}\;
+	update \me{\mvec{W}{k,n}^{(i+1)}} using \eqref{kkt-mse-4.6} and notify to all \acp{BS} using uplink precoded pilot with \me{\mvec{\tilde{w}}{l,k,n}^{(i+1)}} as the precoder\;
 	\me{i = i + 1} \;

### 2014-10-01 Report/mse_formulation.tex
temporary-commit

@@
 \begin{IEEEeqnarray}{rCl} \label{mse-error}
-	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
 \end{IEEEeqnarray}
@@
  \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \nonumber \\
- + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+ + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
 \end{IEEEeqnarray}
@@
 }{
-\begin{IEEEeqnarray}{LL}\label{eqn-mse-1}
-	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
-	\text{subject to} & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
-	& \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
-	& \qquad \quad {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
+\begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
+	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
+	\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
+	& \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
+	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
 	&  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
@@
 The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
-\iftoggle{single_column}{
-\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
-\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
-\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
-& \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-2.3}
+\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
+\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
+\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin} \IEEEyessubnumber \label{eqn-mse-2.2}
 \end{IEEEeqnarray}
-}{
-\begin{IEEEeqnarray}{rCl}\label{eqn-mse-2}
-	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
-	\text{subject to} & \quad & \eqref{eqn-4.3}, \: \eqref{mse-lin}  \IEEEyessubnumber \label{eqn-mse-2.2} \\
-	& \quad & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
-	&\quad& + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n} \eqsub \label{eqn-mse-2.3}
-\end{IEEEeqnarray}
-}
 \subsubsection*{Convergence}
@@
 The uniqueness of the transmit and the receive precoders are justified if the phase ambiguity from the stationary solution is eliminated.
-It can be seen from the \ac{MSE} expression \eqref{eqn-mse-2.3} that the phase rotations are fixed for both transmit and the receive precoders at the stationary point, which is evident from the following reformulation of \eqref{eqn-mse-2.3} as
+It can be seen from the \ac{MSE} expression \eqref{eqn-mse-1.3} that the phase rotations are fixed for both transmit and the receive precoders at the stationary point, which is evident from the following reformulation of \eqref{eqn-mse-1.3} as
 \iftoggle{single_column}{

### 2014-10-01 Report/primal_approach.tex
temporary-commit

@@
 The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}.
-Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration and is carried out until convergence.
+Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} in \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration until convergence.
 The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows the same.

### 2014-10-01 Report/simulation_distributed.tex
Updated double column
temporary-commit

@@
-The performance of the distributed algorithms are studied in this section by comparing with the centralized algorithms.
-The performance is compared using the total number of backlogged packets after each \ac{SCA} update points.
+The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points.
 Fig.
-\ref{fig-d-1} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}.
+\ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}.
 Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}.
-The total number of queued packets assumed for both figures is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
-As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the choice of the step size used in the subgradient update.
-Since the interference values are fixed for local subproblem in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
+The total number of queued packets assumed for both figures is \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
+As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update.
+Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
 
 The Fig.
-\ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points.
-In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations to exchange either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme.
+\ref{fig-d} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points.
+In between the \ac{SCA} updates, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables.
 In Fig.
@@
 It can be seen from Fig.
-\ref{fig-d-1} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
+\ref{fig-d} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
+
+\iftoggle{enable_dist_fig}
+{	
+In Fig.
+\ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels.
+The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively.
+The users are assumed to have the path loss following the uniform distribution between \me{[0,-6]} dB from all \acp{BS}.
+The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.
+
+Fig.
+\ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update.
+In case of the distributed approaches, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations.
+In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant, which affects the convergence rate and the stationary point of the final solution.
+The data tips are used to highlight the convergent points of various algorithms.
+The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes.
+It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
 \begin{figure*}
@@
 	\subfloat[][System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-3-1}
+		\includegraphics[width=0.48\textwidth]{fig-3-2}
 		\label{fig-d-1}
@@
 \end{figure*}
-
-In Fig.
-\ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels.
-The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively.
-The users are assumed to be scattered over the cell boundary experiencing the path loss following the uniform distribution between \me{[0,-6]} dB.
-The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.
-
-Fig.
-\ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update.
-In case of the distributed approaches, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations.
-In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformers \me{\mvec{W}{k,n}} update at the same instant, which affects the convergence rate and the stationary point of the final solution.
-The data tips are used to highlight the convergent points of various algorithms.
-The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes.
-It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
 % \begin{figure*}
@@
 % \end{figure*}
-
+}{
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth]{fig-3-2}
+\label{fig-d-1}
+\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}}
+\label{fig-d}
+\end{figure}
+}
 Fig.
@@
 	\centering
-\includegraphics[width=\columnwidth]{fig-9-2-1}
-\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
+	\includegraphics[width=\columnwidth]{fig-9-3}
+	\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
 	\label{fig-d-3.1}

### 2014-10-01 Report/simulation_results.tex
Updated double column
temporary-commit

@@
-In this section, we discuss the performance of the centralized algorithms from Section \ref{sec-3} for a few system configurations.
-To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
-The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits respectively.
-
-Table.
-\ref{tbl-1} outlines the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} design \cite{wmmse_shi}.
-The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
-Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} got scheduled in the first sub-channel due to the better channel condition.
-In contrast to the \ac{Q-WSRME} scheme, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets waiting at the transmitter.
-The rate allocated for \me{\mc{U}(2)} on the second sub-channel is higher in \ac{JSFRA} scheme compared to the other schemes.
-It is due to the efficient allocation of the total power shared across the sub-channels.
 \begin{table*}
@@
 
-In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
+In this section, we discuss the performance of the centralized algorithms from Section \ref{sec-3} for a few system configurations.
+To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
+The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits respectively.
+
+Table.
+\ref{tbl-1} outlines the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} design \cite{wmmse_shi}.
+The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
+Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} got scheduled in the first sub-channel due to the better channel condition.
+In contrast, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets waiting at the transmitter.
+The rate allocated for \me{\mc{U}(2)} on the second sub-channel is higher in \ac{JSFRA} scheme compared to the other schemes.
+It is due to the efficient allocation of the total power shared across the sub-channels.
+
+For the \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
 The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lowest path loss component.
@@
 \subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-1-3-1}
+\includegraphics[width=0.48\textwidth]{fig-1-4}
 \label{fig-1}}
@@
 \subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-2-4-1}
+\includegraphics[width=0.48\textwidth]{fig-2-5}
 \label{fig-2}}
@@
 \begin{table}
-\centering
+\flushleft
 \renewcommand{\arraystretch}{1.25} \scriptsize
@@
 \hline
-\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
-\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
-\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
+\me{1} & 15.0 & 3.95 & 5.26 & 8.95 & 7.0 & 11.9 & 12.0 & 9.7 & 25.15 \\
+\me{2} & 11.2 & 3.9 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.9 & 27.77 \\
+\me{\infty} & 11.4 & 4.4 & 10.4 & 10.4 & 10.4 & 8.4 &  8.4 &  6.4 & 28.68 \\
 \hline
@@
 \end{tabular}
-\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
-\label{tbl-3}
+\caption{Queues for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
+\label{tbl-3} \vspace{-0.5cm}
 \end{table}

### 2014-10-01 Report/sub_channel_wsrm.tex
temporary-commit

@@
 However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.
-The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
-\begin{algorithm}
- \SetAlgoLined
- \DontPrintSemicolon
- \BlankLine
- \SetKwInput{KwInit}{Initialize}
- \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
- \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
- \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
- update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
- \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
- update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
- \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
- initialize \me{j = 0}\;
- \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
- solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
- update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
- $j = j + 1$\;
- }
- update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
- $i = i + 1$\;
- }
- }
- \caption{Algorithm of \acs{SRA} scheme}
- \label{algo-5}
-\end{algorithm}
+%The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
+%\begin{algorithm}
+% \SetAlgoLined
+% \DontPrintSemicolon
+% \BlankLine
+% \SetKwInput{KwInit}{Initialize}
+% \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
+% \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
+% \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
+% update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}\;
+% \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
+% \KwInit{\me{i=0} and \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
+% update \me{\mvec{w}{l,k,\hat{n}}} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} using \eqref{eqn-10} and \eqref{eqn-8}\;
+% \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
+% initialize \me{j = 0}\;
+% \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
+% solve for \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} with per sub-channel power constraint \me{P_{\max,\hat{n}}}\;
+% update the constraint set \eqref{eqn-8} with \me{\tilde{u}_{l,k,\hat{n}}} and \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr}\;
+% $j = j + 1$\;
+% }
+% update \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
+% $i = i + 1$\;
+% }
+% }
+% \caption{Algorithm of \acs{SRA} scheme}
+% \label{algo-5}
+%\end{algorithm}
+%

### 2014-10-01 Report/wsrm_formulation.tex
temporary-commit

@@
 \iftoggle{single_column}{
-\begin{IEEEeqnarray}{rCl}\label{eqn-6}
+\begin{IEEEeqnarray}{CCl}\label{eqn-6}
 \underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
@@
 }{
-\begin{IEEEeqnarray}{rCl}\label{eqn-6}
-	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
+\begin{IEEEeqnarray}{CCl}\label{eqn-6}
+	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
 	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
@@
 Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively.
-Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint
+Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint as
 \iftoggle{single_column}{
@@
 In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
-\begin{IEEEeqnarray}{rCl}\label{eqn-9}
-\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}\\\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \\
+\begin{IEEEeqnarray}{CCl}\label{eqn-9}
+\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},,\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
 \text{subject to} & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
@@
 Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}} as
-\begin{IEEEeqnarray}{rCl}\label{eqn-9--1}
-\underset{\substack{\gamma_{l,k,n},\mvec{w}{l,k,n},\\\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
+\begin{IEEEeqnarray}{CCl}\label{eqn-9--1}
+\underset{\substack{\gamma_{l,k,n},\mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
 \text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}
@@
 \mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \frac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace
 \end{IEEEeqnarray}

### 2014-10-01 Report/dual_approach.tex
temporary_version

@@
 }{
+{\allowdisplaybreaks
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
@@
 	&& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3} \IEEEyessubnumber \label{eqn-dual-1f}
-\end{IEEEeqnarray}
+\end{IEEEeqnarray}}
 }
@@
 \nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right )
-%, \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}
 \end{equation}
-
-\subsubsection*{Convergence}
-The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point.
-Since subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary value \cite{boyd2011distributed} for the fixed \ac{SCA} point.
-The receive beamformers are updated along with the \ac{SCA} update of the tuple \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}}.
-Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic  increase in the objective function.
-Algorithm \ref{algo-3} outlines the \ac{ADMM} approach for distributed precoder design.
+The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
+{\allowdisplaybreaks 
 	\begin{algorithm}
@@
 				update \me{\mvec{W}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
-    update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
-    update \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} with equality for the \ac{MSE} approach \;
+				update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
 				$i = i + 1$ \;
@@
 	\end{algorithm}
+}
+\subsubsection*{Convergence}
+The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point.
+Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value.
+The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}.
+Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.

### 2014-10-01 Report/introduction.tex
temporary-commit
temporary_version

@@
 The \ac{MSE} reformulation for the \ac{WSRM} problem is also studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner.
-Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal}.
+Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
 
@@
 
-The remainder of this paper is as follows.
+The remainder of this paper is organized as follows.
 In Section \ref{sec-2-3.2}, we introduce the system model and the problem formulation for the queue minimizing precoder design.

### 2014-10-01 Report/kkt_mse_approach.tex
temporary_version

@@
 
-By forming the Lagrangian of \eqref{kkt-mse-1} with the corresponding dual variables as shown in \eqref{kkt-mse-1}, we can obtain the \ac{KKT} expressions by differentiating with respect to the variables present in the problem as detailed in Appendix \ref{a-1}.
-Upon solving the \ac{KKT} expressions, the iterative solution \me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}} is given by
+The problem in \eqref{kkt-mse-1} is solved using the\ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables as shown in the Appendix \ref{a-1}.
+Upon solving, we obtain the iterative solution as
 \iftoggle{single_column}{
@@
 }{
+{\allowdisplaybreaks
 \begin{IEEEeqnarray}{ll} \label{kkt-mse-4}
@@
 	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
-\end{IEEEeqnarray}
+\end{IEEEeqnarray}}
 }

### 2014-10-01 Report/mse_formulation.tex
temporary_version

@@
 }{
-\begin{IEEEeqnarray}{rCl} \label{mse-error}
- \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \nonumber \\
+\begin{multline} \label{mse-error}
+ \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
  + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
-\end{IEEEeqnarray}
+\end{multline}
 }
@@
 \begin{equation} \label{eqn-mse-eq}
-\epsilon_{l,k,n} = \dfrac{1}{1 + \gamma_{l,k,n}}
+\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}}
 \end{equation}
@@
 Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.
-Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
+Now, by relaxing the \ac{MSE} in \eqref{mse-error} and the rate  \ac{MSE} equivalence, \eqref{eqn-6} is written as
 \iftoggle{single_column}{
@@
 }{
+{\allowdisplaybreaks
 \begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
@@
 	&  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
-\end{IEEEeqnarray}
+\end{IEEEeqnarray}}
 }
-where \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the \ac{MSE} relation and \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}}.
 
@@
 \subsubsection*{Convergence}
-Following the similar arguments as in  Section \ref{sec-3.2.1}, we can see that the \ac{SCA} subproblems converges to a stationary point of the original nonconvex problem at each iteration.
-The uniqueness of the transmit and the receive precoders are justified if the phase ambiguity from the stationary solution is eliminated.
-It can be seen from the \ac{MSE} expression \eqref{eqn-mse-1.3} that the phase rotations are fixed for both transmit and the receive precoders at the stationary point, which is evident from the following reformulation of \eqref{eqn-mse-1.3} as
+Following the similar approach in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem.
+The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution.
+By reorganizing \eqref{eqn-mse-1.3}
 \iftoggle{single_column}{
@@
 }
-At each \ac{SCA} step, the transmit precoders are obtained uniquely by minimizing the weighted \ac{MSE} criterion due to the convex nature of the relaxed problem.
-Upon finding the optimal transmit precoders, the receive beamformers are updated using the \ac{MMSE} receivers.
-The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders thereby leading to the monotonic convergence of the objective function.
+we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are avoided by the real component in the \ac{MSE} expression.
+
+At each \ac{SCA} step, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem.
+Using the transmit precoders, the receive beamformers are obtained using the \ac{MMSE} receivers.
+The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders, leading to the monotonic convergence of the objective function.
 At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, the objective value can either decrease or stays the same after each iteration.

### 2014-10-01 Report/conclusions.tex
double_ready

@@
-In this work, we presented the \acl{QM} objective to minimize the number of backlogged packets by designing the transmit precoders across the space-frequency dimension in a multi-cell \ac{MU} \ac{MIMO} system.
-We proposed the \ac{JSFRA} scheme, which adopts the \ac{SCA} technique to model the nonconvex constraint as a convex constraint in an iterative manner to design the precoders for the \acl{QM} objective.
-We also proposed an alternative approach using the \ac{MSE} relaxation for the same problem when the receive beamformers are based on the \ac{MMSE} receivers.
-The exponent used in the proposed formulation can be modified to achieve either greedy allocation or equally fair allocation.
-We also proposed the distributed solutions for the proposed centralized \ac{JSFRA} problem using the \ac{ADMM} method, which has better convergence behavior compared to the primal decomposition.
-In addition, we also proposed an iterative algorithm based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme to design the precoders in a distributed manner using the closed form solutions.
+In this paper, we addressed the allocation of space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{OFDM} system.
+The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user can be achieved by a non-zero precoding vector.
+We proposed the \ac{JSFRA} scheme by adopting the \ac{SCA} technique to model the nonconvex constraint as a sequence of convex subsets to design the precoders for minimizing the number of queued packets.
+Additionally, an alternative approach using \ac{MSE} relaxation is also proposed with the same objective by fixing the receivers based on \ac{MSE} minimization.
+We also proposed the distributed solutions for the centralized \ac{JSFRA} problem using \ac{ADMM} and primal decomposition methods.
+Finally, we proposed an iterative algorithm to determine the precoders in a decentralized manner based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme.
+Numerical results shows that the proposed algorithms perform better than the existing approaches.

### 2014-10-01 Report/decomposition_solutions.tex
double_ready

@@
 Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
+{\allowdisplaybreaks
 \begin{IEEEeqnarray}{CCl} \label{eqn-decent-1}
@@
 \text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber,
-\end{IEEEeqnarray}
+\end{IEEEeqnarray}}
 where \me{\tilde{\mbf{v}}_b} denote the vector of of weighted queue deviation corresponding to the users \me{k \in \mc{U}_b}.

### 2014-10-01 Report/introduction.tex
double_ready

@@
-The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks.
+%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks.
 The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption.
@@
 
-In a network with multiple \acp{BS} serving multiple users (\acs{MU}), the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
+In a network with multiple \acp{BS} serving \ac{MU}, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
 These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints.
-We consider the problem of transmit design over the space-frequency resources provided by the \acs{MIMO}-\ac{OFDM} framework in the downlink broadcast transmission to minimize the number of queued packets.
-Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation to minimize the total number of backlogged packets of all \acp{BS}.
+We consider the problem of transmit design over the space-frequency resources provided by the \acs{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets.
+Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.
 
-In general, the resource allocation problems are solved by assigning a binary variable to each user indicating the presence or the absence on a particular resource.
+In general, the resource allocation problems are solved by assigning a binary variable to each user indicating the presence or the absence on a particular resource \cite{admission_control}.
 In contrast to that, we use the transmit beamformers, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource.
@@
 
-In order to reduce the complexity involved in the precoder design problem, linear precoding are assumed at the \acp{BS} and detection is used at users.
-The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
+%The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
 To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in the queues prior to the transmission, and, hence, to avoid packet drops as an indirect objective.
@@
 The topics on \ac{MIMO} \ac{IBC} precoder design have been studied extensively with different performance criteria in the literature.
-Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, the \ac{SCA} method has become a powerful tool to deal with these problems.
+Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, the \ac{SCA} method has become a powerful tool to deal with these problems \cite{bertsekas1999nonlinear}.
 For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around an operating point in order to solve the \ac{WSRM} problem in an iterative manner.
-Similar approach of solving the \ac{WSRM} problem via arithmetic-geometric inequality is proposed in \cite{tran2012fast}.
+Similar approach of solving the \ac{WSRM} problem by using arithmetic-geometric inequality is proposed in \cite{tran2012fast}.
 
@@
 In the context of wireless networks, the backpressure algorithm mentioned above was extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.
+Recently, the precoder design for the video transmission over \ac{MIMO} system is considered in \cite{video_queues}.
+In this design, the \ac{MU}-\ac{MIMO} precoders are designed by the \ac{MSE} reformulation as in \cite{christensen2008weighted} with the higher layer performance objective such as playback interruptions and buffer overflow probabilities.
 
-In this paper, we consider the problem of precoder design across the space-frequency resources to minimize the total number of queued packets of all \acp{BS}.
+In this paper, we consider the problem of precoder design across the space-frequency resources to minimize the total number of queued packets waiting in all \acp{BS}.
 For this highly nonconvex problem, we first propose two centralized methods.
@@
 
-The remainder of this paper is organized as follows.
+The organization of this paper is as follows.
 In Section \ref{sec-2-3.2}, we introduce the system model and the problem formulation for the queue minimizing precoder design.

### 2014-10-01 Report/joint_wsrm_formulation.tex
temporary_version
double_ready

--- 2014-09-30 Report/joint_wsrm_formulation.tex
@@
-The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network.\footnote{routers or user terminals} One such algorithm  is the \emph{backpressure algorithm}, discussed in detail in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
+The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network\footnote{routers or user terminals}.
+One such algorithm  is the \emph{backpressure algorithm}, discussed in detail in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
 The algorithm determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes.
@@
 \begin{IEEEeqnarray}{rCl}\label{eqn-3.1}
-&=&\frac{1}{2} \left [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \right ] \IEEEyessubnumber \label{eqn-3.1.0} \\
+&=&\frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ] \IEEEyessubnumber \label{eqn-3.1.0} \\
 &\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) } \IEEEyessubnumber \label{drift-exp}
@@
 	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
-\end{IEEEeqnarray}
-}{
-\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
-	\underset{\mbf{t}}{\text{minimize}} && \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
-	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
-	&& - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
-\end{IEEEeqnarray}	
-}
-where the second term in \eqref{backpreassure-approx-1b} follows from the Poisson arrival process.
+\end{IEEEeqnarray}}{
+{\allowdisplaybreaks
+\begin{IEEEeqnarray}{CL} \label{backpressure-approx}
+	& \underset{\mbf{t}}{\text{minimize}} \quad \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \Big \lbrace \sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i) \Big \rbrace }_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
+	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace \IEEEyessubnumber \label{backpreassure-approx-1b}
+\end{IEEEeqnarray}}}
+%\begin{figure*}
+%\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
+%	\underset{\mbf{t}}{\text{minimize}} &\quad& \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \vspace{-0.25in}\\
+%	& \leq & \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} + \overbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}^{\le B}\IEEEyessubnumber \label{backpreassure-approx-1b}
+%\end{IEEEeqnarray}	
+%\vspace{-0.25in}
+%\end{figure*}
+where the first term in \eqref{backpreassure-approx-1b} follows from the Poisson arrival process.
+
 Assuming the second order moments of the transmissions and the arrival rates are bounded, it can be replaced by a upper bound \me{B} as in \eqref{backpreassure-approx-1b}, in order to eliminate from the optimization problem \cite{neely2010stochastic}.

### 2014-10-01 Report/mse_formulation.tex
double_ready

@@
 
-The \acl{QM} \ac{JSFRA} problem using alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
-In order to solve this efficiently, we use the \ac{SCA} method as discussed earlier in Section \ref{sec-3.2} by using the linear under estimator for the convex function on the r.h.s of \eqref{eqn-mse-1.2}.
-The first order approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} for \eqref{eqn-mse-1.2} is given by
+The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
+We adopt the \ac{SCA} method as in Section \ref{sec-3.2} to relax the constraint by a sequence of convex subsets using first order approximations around \me{\tilde{\epsilon}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl}

### 2014-10-01 Report/system_model.tex
double_ready

@@
 where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
-In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams.\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted} Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
+In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
+Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
 \begin{equation}\label{eq:SINR}
@@
 where \me{t_{l,k,n}} denotes the transmitted bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} of \me{\gamma_{l,k,n}}.\footnote{This can be achieved by Gaussian signaling} Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.
+The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} of \me{\gamma_{l,k,n}}\footnote{This can be achieved by Gaussian signaling}.
+Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-10-01 Report/wsrm_formulation.tex
temporary_version
double_ready

@@
-In this approach, we present an algorithm to solve \eqref{eqn-3} for the transmit precoders in a centralized way by using the idea of alternating optimization and successive convex approximation.
+In this approach, we present an algorithm to solve \eqref{eqn-3} to obtain the transmit precoders in a centralized manner by using the idea of alternating optimization and successive convex approximation.
 Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
@@
 \begin{IEEEeqnarray}{CCl}\label{eqn-6}
-\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
+\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
 \text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \label{eqn-6.2} \\
@@
 \end{IEEEeqnarray}
-}{
+}{\allowdisplaybreaks
 \begin{IEEEeqnarray}{CCl}\label{eqn-6}
@@
 This procedure is carried out until convergence of the queue deviation or for fixed number of iterations defined by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
+{\allowdisplaybreaks
 \begin{algorithm}
@@
 \end{algorithm}
-
+}
 \subsubsection*{Convergence}

### 2014-10-02 Report/ieee_journal.tex
temporary_version
double_ready
markku_modifications

@@
 
-\title{Traffic aware Resource Allocation schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} systems}
+\title{Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems}
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\
+	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti}
 	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
@@
 
-%\begin{keywords}
-%\acs{MIMO}-\acs{OFDM}, weighted sum rate maximization, precoder design, queue driven scheduling and precoder design
-%\end{keywords}
+\begin{IEEEkeywords}
+\acs{MIMO}-\acs{OFDM}, \acs{IBC}, Precoder design, \acs{WSRM}
+\end{IEEEkeywords}
 
@@
 
-\section{\ac{KKT} expressions for the Distributed MSE Formulation} \label{a-1}
+\section{\ac{KKT} conditions for \ac{MSE} approach} \label{a-1}
 \input{kkt_appendix}

### 2014-10-02 Report/introduction.tex
markku_modifications

@@
 
-In a network with multiple \acp{BS} serving \ac{MU}, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
+In a network with multiple \acp{BS} serving \acp{MU}, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
 These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints.
-We consider the problem of transmit design over the space-frequency resources provided by the \acs{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets.
+We consider the problem of transmit precoder design over the space-frequency resources provided by the \acs{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets.
 Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.
 
-In general, the resource allocation problems are solved by assigning a binary variable to each user indicating the presence or the absence on a particular resource \cite{admission_control}.
-In contrast to that, we use the transmit beamformers, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource.
-The purpose of using the transmit beamformers for the scheduling is two fold.
-Firstly, it determines the transmission rate on a certain resource and secondly, by making the transmit beamformer to be a zero vector, the corresponding user will not be scheduled on a certain resource.
+In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence of a particular resource \cite{admission_control}.
+In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource.
+The purpose is two-fold.
+Firstly, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.
 
@@
 Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, the \ac{SCA} method has become a powerful tool to deal with these problems \cite{bertsekas1999nonlinear}.
-For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around an operating point in order to solve the \ac{WSRM} problem in an iterative manner.
-Similar approach of solving the \ac{WSRM} problem by using arithmetic-geometric inequality is proposed in \cite{tran2012fast}.
+For example, in \cite{sin_algorithm}, the nonconvex part of the objective has been linearized around an operating point in order to solve the \ac{WSRM} problem in an iterative manner.
+Similar approach of solving the \ac{WSRM} problem by using arithmetic-geometric inequality has been proposed in \cite{tran2012fast}.
 
@@
 In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders.
-Then the problem is solved using an alternating optimization method, i.e., finding a set of variables while the remaining others are fixed.
-The \ac{MSE} reformulation for the \ac{WSRM} problem is also studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner.
-Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
+Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the remaining others are fixed.
+The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner.
+Additional rate constraints based on the \ac{QoS} requirements were included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
 
-The problem of precoder design for the \ac{MIMO} \ac{IBC} system are solved either by using a centralized controller or by using decentralized algorithms where all \acp{BS} handles their own subproblems and exchange limited information via backhaul.
-The distributed approaches are based on primal, dual or \ac{ADMM} decomposition, which are discussed in a detailed manner in \cite{palomar2006tutorial,boyd2011distributed}.
+The problem of precoder design for the \ac{MIMO} \ac{IBC} system are solved either by using a centralized controller or by using decentralized algorithms where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with the other \acp{BS} via back-haul.
+The distributed approaches are based on primal, dual or \ac{ADMM} decomposition, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}.
 In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders.
 The fixed interference are then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}.
-The dual and \ac{ADMM} approach controls the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
+The dual and \ac{ADMM} approaches control the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
 
-By adjusting the weights in the \ac{WSRM} objective properly, we can find arbitrary rate-tuple in the rate region that maximizes the suitable objective measures.
-For example, if the weight of each user is set to be inversely proportional to his/her average data rate, the corresponding problem guarantees fairness on an average among the users.
-As an approximate method, we may assign weights based on the current queue size of users.
-More specifically, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function of it,  which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}.
+By adjusting the weights in the \ac{WSRM} objective properly, we can find an arbitrary rate-tuple in the rate region that maximizes the suitable objective measures.
+For example, if the weight of each user is set to be inversely proportional to its average data rate, the corresponding problem guarantees fairness on an average among the users.
+As an approximation, we may assign weights based on the current queue size of the users.
+More specifically, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}.
 In backpressure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
 
-Earlier studies on the queue minimization problem was summarized in the survey paper \cite{berry2004cross}.
+Earlier studies on the queue minimization problem were summarized in the survey paper \cite{berry2004cross}.
 In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} using geometric programming.
@@
 In the second method, we reformulate the \ac{JSFRA} problem using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders.
-For distributed implementation, we further proposed decentralized approaches based on primal and \ac{ADMM} scheme to identify the precoders independently across the \acp{BS} by exchanging limited information via back-haul.
-We also proposed an iterative algorithm by solving the \ac{KKT} equations, which can be implemented easily in a distributed manner.
+For a distributed implementation, we further propose decentralized approaches based on primal and \ac{ADMM} schemes to identify the precoders independently across the \acp{BS} by exchanging limited information via back-haul.
+We also propose an iterative algorithm by solving the \ac{KKT} equations, which can be implemented easily in a distributed manner.
 
@@
 In Section \ref{sec-2-3.2}, we introduce the system model and the problem formulation for the queue minimizing precoder design.
-Existing and the proposed precoder designs for the \ac{JSFRA} problem are presented in Section \ref{sec-3}.
+The existing and the proposed precoder designs for the \ac{JSFRA} problem are presented in Section \ref{sec-3}.
 The distributed solutions are provided in Section \ref{sec-4} followed by the simulation results in Section \ref{sec-5}.

### 2014-10-02 Report/joint_wsrm_formulation.tex
markku_modifications

@@
-The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network\footnote{routers or user terminals}.
-One such algorithm  is the \emph{backpressure algorithm}, discussed in detail in \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
-The algorithm determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes.
+The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network.
+One such algorithm  is the \emph{backpressure algorithm} \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
+It determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes.
 Even though the algorithm is primarily designed for the wired infrastructure, it can be extended to the wireless networks by designing the user rate variable \me{t_k} in accordance to the wireless network.
 
-The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the \ac{MIMO}-\ac{OFDM} framework, in which the multiple \acp{BS} acts as the source nodes and the user terminals as the receiver nodes.
-The control policy in the form of transmit precoders are designed to minimize the number of queued packets waiting at the \acp{BS}.
+The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the \ac{MIMO}-\ac{OFDM} downlink framework, in which the multiple \acp{BS} act as the source nodes and the user terminals as the receiver nodes.
+The control policy in the form of transmit precoders is designed to minimize the number of queued packets waiting at the \acp{BS}.
 In order to find the optimal algorithm, we use the Lyapunov function which is predominantly used in the control theory for the system stability.
-Since at each time slot, the system can be described by the channel conditions and the number of backlogged packets of each user, Lyapunov function is used to provide a scalar measure, which grows large when the system moves towards the undesirable state.
+Since at each time slot, the system can be described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state.
 Following the approach in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
 \begin{equation}
-\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i)
+\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i),
 \end{equation}
@@
 3]{neely2010stochastic}.
-The Lyapunov function drift, expressed as \me{\Delta(\mbf{Q}(i)) = \mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)}}, is given by
+The Lyapunov function drift, expressed as \me{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)}}, is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-3.1}
 &=&\frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ] \IEEEyessubnumber \label{eqn-3.1.0} \\
-&\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) } \IEEEyessubnumber \label{drift-exp}
+&\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) }, \IEEEyessubnumber \label{drift-exp}
 \end{IEEEeqnarray}
@@
 \begin{equation}
-\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t)
+\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
 \end{equation}
-In order to minimize the squared sum at each instant, minimization of the Lyapunov drift \eqref{eqn-3.1} is carried over all possible rate allocations in the form of transmission rates \me{t_k} to users in the system.
-The Lyapunov drift conditioned on the current backlogged packets \me{\mbfa{Q}(i)} is given by
+The total number of backlogged packets at any given instant \me{i} is reduced by minimizing the conditional expectation of the Lyapunov drift expression \eqref{drift-exp} given the current number of queued packets \me{\mbfa{Q}(i)} waiting in the system.
+The expectation is taken over all possible arrival and transmission rates of the users to obtain the optimal rate allocation strategy.
+
+Now, the conditional Lyapunov drift, denoted by \me{\Delta{(\mbfa{Q}(i))}}, is given by
 \iftoggle{single_column}{
@@
 	\underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
-	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} \IEEEyessubnumber \label{backpreassure-approx-1b}
+	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \IEEEyessubnumber \label{backpreassure-approx-1b}
 \end{IEEEeqnarray}}{
@@
 	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \Big \lbrace \sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i) \Big \rbrace }_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
-	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace \IEEEyessubnumber \label{backpreassure-approx-1b}
+	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace, \IEEEyessubnumber \label{backpreassure-approx-1b}
 \end{IEEEeqnarray}}}
@@
 where the first term in \eqref{backpreassure-approx-1b} follows from the Poisson arrival process.
+Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpreassure-approx-1b} by a constant \me{B} that can be eliminated from the optimization problem \cite{neely2010stochastic}.
 
-Assuming the second order moments of the transmissions and the arrival rates are bounded, it can be replaced by a upper bound \me{B} as in \eqref{backpreassure-approx-1b}, in order to eliminate from the optimization problem \cite{neely2010stochastic}.
-The expectation is performed across all possible arrivals and the transmission rates for the given number of queued packets \me{\mbf{Q}(i)} and the channel state information at the \me{\ith{i}} slot.
-
-Now the expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the number of backlogged packets corresponding to the users.
+The expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the number of backlogged packets corresponding to the users.
 The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
-The \ac{Q-WSRM} formulation is given by optimizing each term inside the expectation operator \me{\mbf{E}_{\mbfa{\lambda},\mbf{t}}} in \eqref{backpreassure-approx-1b}, which maximizes the
+Since the expectation can be minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
 \begin{IEEEeqnarray}{rCl} \label{q_gen_sum}

### 2014-10-02 Report/problem_formulation_intro.tex
markku_modifications

@@
-To minimize the total number of backlogged packets, we consider minimizing weighted \me{\ell_{q}}-norm of all the queue deviation given by
+To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation given by
 \begin{equation}
-v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})
+v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}),
 \label{eqn-4.2}
@@
 \underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
-\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-4.3}
+\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
 \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with the user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
 In \eqref{eqn-4.3}, we consider a \ac{BS} specific sum power constraint for each \ac{BS} across all sub-channels.
 
-For practical reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total backlogged packets available at the transmitter.
-As a result, the number of backlogged packets \me{v_k} remaining in the system for the user \me{k} is given by
+For practical reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total number of backlogged packets available at the transmitter.
+As a result, the number of backlogged packets \me{v_k} for user \me{k} remaining in the system is given by
 \begin{equation} \label{rate_constraint_a}
@@
 
-Before proceeding further, we note that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of the \me{\ell_q} in the objective of \eqref{eqn-3}.
-As a proof, suppose that \me{t_k>Q_k} for a certain \me{k} at optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
+Before proceeding further, we show that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of norm \me{\ell_q} in the objective of \eqref{eqn-3}.
+Suppose that \me{t_k>Q_k} for certain \me{k} at the optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
 Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}.
-Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that an optimal solution has been obtained.
-The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as
+Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that the optimal solution has been obtained.
+The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as follows
 \begin{itemize}
-\item \me{\ell_{q = 1}} results in greedy allocation \textit{i.e}, emptying the queue of users with good channel condition before considering the users with worse channel conditions.
+\item \me{\ell_{1}} results in greedy allocation \textit{i.e}, emptying the queue of users with good channel conditions before considering the users with worse channel conditions.
 As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
-\item \me{\ell_{q = 2}} prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
+\item \me{\ell_{2}} prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
 For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
-\item \(\ell_{q = \infty} \) minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
+\item \(\ell_{\infty} \) minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
 \end{itemize}

### 2014-10-02 Report/queue_minimizing_intro.tex
revision - 1
markku_modifications

@@
 In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is highly difficult due to the combinatorial and the nonconvex nature of the problem.
-In addition to that, the objective of minimizing the number of the queued packets over the spatial and the sub-channel dimensions adds further complexity to the existing problem.
-Since the scheduling of users in each sub-channel can be made by allocating zero transmit power over certain sub-channels, the solutions provided in the paper performs both precoder design and the scheduling of users in a joint manner.
+In addition, the objective of minimizing the number of the queued packets over the spatial and the sub-channel dimensions adds further complexity to the existing problem.
+Since the scheduling of users in each sub-channel can be made by allocating zero transmit power over certain sub-channels, our solutions perform joint precoder design and user scheduling.
+Before discussing the proposed solutions, we consider the existing algorithm to minimize the number of backlogged packets with additional constraints required by the problem.

### 2014-10-02 Report/system_model.tex
markku_modifications

@@
 We consider a downlink \ac{MIMO} \ac{IBC} scenario in an \ac{OFDM} framework with \me{N} sub-channels and \me{N_B} \acp{BS} each equipped with \me{N_T} transmit antennas, serving in total \me{K} users each with \me{N_R} receive antennas.
-The set of users associated with \ac{BS} \me{b} is denoted by \me{\mathcal{U}_b} and the set \me{\mathcal{U}} represents all users in the system, i.e., \me{\mathcal{U} =\underset{b\in \mathcal{B}}{\cup }\mathcal{U}_b}, where \me{\mathcal{B}} is the set of all coordinating \acp{BS}.
+The set of users associated with \ac{BS} \me{b} is denoted by \me{\mathcal{U}_b} and the set \me{\mathcal{U}} represents all users in the system, i.e., \me{\mathcal{U} =\underset{b\in \mathcal{B}}{\cup }\mathcal{U}_b}, where \me{\mathcal{B}} is the set of indices of all coordinating \acp{BS}.
 Data for user \me{k} is transmitted from only one \ac{BS} which is denoted by \me{b_k\in \mathcal{B}}.
@@
 
-In this paper we adopt linear beamforming technique at \acp{BS}.
-Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with the beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted.
-In order to detect  multiple spatial streams at the receiver, a receive beamforming vector \me{\mvec{w}{l,k,n}} is employed at each user.
-Consequently, the received data symbol corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
+We adopt linear transmit beamforming technique at \acp{BS}.
+Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted.
+In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user.
+Consequently, the received data symbol estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
 \iftoggle{single_column}{
 \begin{equation}\label{eqn-1}
-\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
+\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n},
 \end{equation}
@@
 \hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n} \\ 
-+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
++ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n},
 \end{multline}
@@
 \begin{equation}\label{eq:SINR}
-\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}
+\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
 \end{equation}
 Let \me{Q_k} be the number of backlogged packets which are destined for the user \me{k} at a given scheduling instant.
-The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets or bits arriving for the user \me{k} at the \me{{i}^\mathrm{th}} instant.
-The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, represented by \me{Q_k(i+1)}, is given by
+The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for the user \me{k} at the \me{{i}^\mathrm{th}} time instant\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar}.
+The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, denoted as \me{Q_k(i+1)}, is given by
 \begin{equation}
-Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i)
+Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i),
 \label{eqn-2a}
 \end{equation}
-where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the transmission in bits for user \me{k}. For a \ac{MIMO}-\ac{OFDM} system,
+where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the number of transmitted packets or bits for user \me{k}. For a \ac{MIMO}-\ac{OFDM} system,
 \begin{equation}
-t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i)
+t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i),
 \end{equation}
-where \me{t_{l,k,n}} denotes the transmitted bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
+where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
 The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} of \me{\gamma_{l,k,n}}\footnote{This can be achieved by Gaussian signaling}.

### 2014-10-07 Report/joint_wsrm_formulation.tex
halfcooked

@@
 
-Now, the conditional Lyapunov drift, denoted by \me{\Delta{(\mbfa{Q}(i))}}, is given by
+Now, the conditional Lyapunov drift, denoted by \me{\Delta{(\mbfa{Q}(i))}}, is given by the infimum over the transmission rate as
 \iftoggle{single_column}{
 \begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
-	\underset{\mbf{t}}{\text{minimize}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
-	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \IEEEyessubnumber \label{backpreassure-approx-1b}
+	\underset{\mbf{t}}{\text{inf}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \eqsub \label{backpressure-approx-1b}
 \end{IEEEeqnarray}}{
@@
 \begin{IEEEeqnarray}{CL} \label{backpressure-approx}
-	& \underset{\mbf{t}}{\text{minimize}} \quad \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+	\underset{\mbf{t}}{\text{inf}} \quad & \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
 	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \Big \lbrace \sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i) \Big \rbrace }_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
-	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace, \IEEEyessubnumber \label{backpreassure-approx-1b}
+	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace, \eqsub \label{backpressure-approx-1b}
 \end{IEEEeqnarray}}}
@@
 %\end{figure*}
-where the first term in \eqref{backpreassure-approx-1b} follows from the Poisson arrival process.
-Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpreassure-approx-1b} by a constant \me{B} that can be eliminated from the optimization problem \cite{neely2010stochastic}.
+where the first term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.
+Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpressure-approx-1b} by a constant \me{B} that can be eliminated from the optimization problem \cite{neely2010stochastic}.
 
@@
 Since the expectation can be minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
-\begin{IEEEeqnarray}{rCl} \label{q_gen_sum}
+\begin{IEEEeqnarray}{LCl} \label{q_gen_sum}
 	\underset{\substack{\mvec{M}{k,n}, \mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
-	\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-3.1.3}
+	\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-3.1.3}
 \end{IEEEeqnarray}
+
 In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}.
@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-3.1.4}
-\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U}
+\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U},
 \end{IEEEeqnarray}

### 2014-10-07 Report/problem_formulation_intro.tex
halfcooked

@@
 \begin{equation}
-v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}),
+v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}).
 \label{eqn-4.2}
 \end{equation}
-Explicitly, the considered problem is given by \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. With this objective, the problem of weighted queued packet minimization is given by
+
+Explicitly, the objective of the problem considered is given by \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. With this objective function, the weighted queued packet minimization formulation is given by
 \begin{IEEEeqnarray}{rCl}\label{eqn-3}
@@
 \begin{equation} \label{rate_constraint_a}
-v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0
+v_k =  Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}) \geq 0.
 \end{equation}

### 2014-10-07 Report/mse_formulation.tex
updated_halfcooked

@@
 \begin{IEEEeqnarray}{rCl} \label{mse-error}
-	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
+	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
 \end{IEEEeqnarray}
@@
  \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
- + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
+ + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
 \end{multline}
@@
 \text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
- & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
+ & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
 & \quad &  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
@@
 	& \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
-	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
+	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
 	&  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
@@
 \begin{equation}
-\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
 \end{equation}
@@
 	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
-	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
 \end{multline}

### 2014-10-08 Report/decomposition_solutions.tex
updated document with thanks and punctuations

@@
 \underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
-\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber,
+\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e}, \IEEEyessubnumber
 \end{IEEEeqnarray}}
@@
 \beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2
-\end{IEEEeqnarray}
-}{
+&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2,
+\end{IEEEeqnarray}}{
 \begin{multline}\label{eqn-decent-3}
 	N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
-	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n}
-\end{multline}
-}
+	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n},
+\end{multline}}
 where \me{\zeta_{l,k,n,b}}, which is the total interference caused by the \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
 \begin{equation}
-\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}
+\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
 \end{equation}

### 2014-10-08 Report/dual_approach.tex
updated document with thanks and punctuations

--- 2014-10-01 Report/dual_approach.tex
@@
 & \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
-n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right | \IEEEyessubnumber
+n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 && \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
-&\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3} \IEEEyessubnumber \label{eqn-dual-1f}
+&\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3}, \IEEEyessubnumber \label{eqn-dual-1f}
 \end{IEEEeqnarray}
-}{
+}{{\allowdisplaybreaks
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
@@
 	\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
-	&& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3} \IEEEyessubnumber \label{eqn-dual-1f}
-\end{IEEEeqnarray}
-}
+	&& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3}, \IEEEyessubnumber \label{eqn-dual-1f}
+\end{IEEEeqnarray}}}
 where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i-1)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.
@@
 \begin{equation}
-\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right )
+\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
 \label{zeta_update}
@@
 \begin{equation}\label{dual-sg-update}
-\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right )
-%, \forall b,b_k \in \mc{B}, \forall k \in \bar{\mc{U}}_{b}
+\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ).
 \end{equation}
-
-\subsubsection*{Convergence}
-The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point.
-Since subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary value \cite{boyd2011distributed} for the fixed \ac{SCA} point.
-The receive beamformers are updated along with the \ac{SCA} update of the tuple \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}}.
-Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic  increase in the objective function.
-Algorithm \ref{algo-3} outlines the \ac{ADMM} approach for distributed precoder design.
+The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
+{\allowdisplaybreaks 
 \begin{algorithm}
@@
 			update \me{\mvec{W}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
-    update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or)\;
-    update \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} with equality for the \ac{MSE} approach \;
+			update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
 			$i = i + 1$ \;
@@
 	\label{algo-3}
-\end{algorithm}
+\end{algorithm}}
+
+\subsubsection*{Convergence}
+The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point.
+Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value.
+The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}.
+Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.

### 2014-10-08 Report/ieee_journal.tex
updated document with thanks and punctuations

@@
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti}
-	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
-		University of Oulu, Oulu, FI-90014\\
-		Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
-}
+	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE} and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
+	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi)}}
 

### 2014-10-08 Report/introduction.tex
updated document with thanks and punctuations

@@
 
-Earlier studies on the queue minimization problem were summarized in the survey paper \cite{berry2004cross}.
+Earlier studies on the queue minimization problem were summarized in the survey paper \cite{berry2004cross,layering_as_opt}.
 In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} using geometric programming.
@@
 For a distributed implementation, we further propose decentralized approaches based on primal and \ac{ADMM} schemes to identify the precoders independently across the \acp{BS} by exchanging limited information via back-haul.
-We also propose an iterative algorithm by solving the \ac{KKT} equations, which can be implemented easily in a distributed manner.
+We also propose an iterative algorithm by solving the \ac{KKT} equations, which can be implemented efficiently in a distributed manner.
 
-The organization of this paper is as follows.
+The paper is organized as follows.
 In Section \ref{sec-2-3.2}, we introduce the system model and the problem formulation for the queue minimizing precoder design.
-The existing and the proposed precoder designs for the \ac{JSFRA} problem are presented in Section \ref{sec-3}.
+The existing and the proposed centralized precoder designs are presented in Section \ref{sec-3}.
 The distributed solutions are provided in Section \ref{sec-4} followed by the simulation results in Section \ref{sec-5}.

### 2014-10-08 Report/joint_wsrm_formulation.tex
updated document with thanks and punctuations

@@
 
-The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the \ac{MIMO}-\ac{OFDM} downlink framework, in which the multiple \acp{BS} act as the source nodes and the user terminals as the receiver nodes.
-The control policy in the form of transmit precoders is designed to minimize the number of queued packets waiting at the \acp{BS}.
-In order to find the optimal algorithm, we use the Lyapunov function which is predominantly used in the control theory for the system stability.
-Since at each time slot, the system can be described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state.
-Following the approach in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
+The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the downlink \ac{MIMO}-\ac{OFDM} framework, in which the multiple \acp{BS} act as the source nodes and the user terminals as the receiver nodes.
+The control policy in the form of transmit precoders aims at minimizing the number of queued packets waiting in the \acp{BS}.
+In order to find the optimal strategy, we resort to the Lyapunov theory, which is predominantly used in the control theory to achieve system stability.
+Since at each time slot, the system is described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state.
+Following similar approach as in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
 \begin{equation}
@@
 \end{equation}
-where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and \me{\frac{1}{2}} is used for the convenience.
-The Lyapunov function provides a measure of congestion in the system, as discussed in \cite[Ch.
+where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and \me{\tfrac{1}{2}} is used for the convenience.
+It provides a scalar measure of congestion present in the system \cite[Ch.
 3]{neely2010stochastic}.
-The Lyapunov function drift, expressed as \me{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)}}, is given by
-\begin{IEEEeqnarray}{rCl}\label{eqn-3.1}
-&=&\frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ] \IEEEyessubnumber \label{eqn-3.1.0} \\
-&\leq& \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) }, \IEEEyessubnumber \label{drift-exp}
-\end{IEEEeqnarray}
-where the inequality is due to the upper bound
+
+The optimal transmission rate vector \me{\mbf{t}} to minimize the total number of backlogged packets in the system is obtained by minimizing the Lyapunov function drift expressed as
+\iftoggle{single_column}{
+\begin{multline}\label{eqn-3.1}
+\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ].
+\end{multline}}{
+\begin{multline}\label{eqn-3.1}
+\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} = \\ \frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ].
+\end{multline}}
+In order to eliminate the nonlinear operator \me{[x]^+}, we bound the expression in \eqref{eqn-3.1} as
+\begin{equation}
+\leq \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) },
+\label{drift-exp}
+\end{equation}
+by using the following inequality 
 \begin{equation}
@@
 \end{IEEEeqnarray}}{
-{\allowdisplaybreaks
 \begin{IEEEeqnarray}{CL} \label{backpressure-approx}
@@
 	& \qquad \qquad {} - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\Big \lbrace \sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i) \Big \rbrace, \eqsub \label{backpressure-approx-1b}
-\end{IEEEeqnarray}}}
-%\begin{figure*}
-%\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
-%	\underset{\mbf{t}}{\text{minimize}} &\quad& \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \vspace{-0.25in}\\
-%	& \leq & \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)} + \overbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}^{\le B}\IEEEyessubnumber \label{backpreassure-approx-1b}
-%\end{IEEEeqnarray}	
-%\vspace{-0.25in}
-%\end{figure*}
+\end{IEEEeqnarray}}
 where the first term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.

### 2014-10-08 Report/kkt_mse_approach.tex
updated_halfcooked
updated document with thanks and punctuations

@@
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
-\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
+\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
 \sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
-\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{kkt-mse-1.4}
+\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
-	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
+	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
 	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
-	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
+	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 \mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
@@
 \alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
-\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
+\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}.
+\IEEEyessubnumber \label{kkt-mse-4.6}
 \end{IEEEeqnarray}
-}{
-{\allowdisplaybreaks
+}{{\allowdisplaybreaks
 \begin{IEEEeqnarray}{ll} \label{kkt-mse-4}
@@
 	\epsilon_{l,k,n}^{(i)} =& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \nonumber \\
-	& \qquad{} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+	& \qquad{} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
 	t_{l,k,n}^{(i)} =&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \tfrac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
@@
 	\mvec{w}{l,k,n}^{(i)} =& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm \nonumber \\
-	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}
-\end{IEEEeqnarray}}
-}
-Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-2.2}, one has to be fixed to optimize for the other.
+	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}. \IEEEyessubnumber \label{kkt-mse-4.6}
+\end{IEEEeqnarray}}}
+Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other.
 In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.

### 2014-10-08 Report/mse_formulation.tex
updated document with thanks and punctuations

@@
 \begin{IEEEeqnarray}{rCl} \label{mse-error}
-	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
+	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
 \end{IEEEeqnarray}
@@
  \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
- + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n}
+ + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
 \end{multline}
@@
 \begin{equation} \label{eqn-mse-eq}
-\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}}
+\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}},
 \end{equation}
@@
  & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
-& \quad &  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
+& \quad &  \text{and} \; \eqref{eqn-4.3}.  \IEEEyessubnumber \label{eqn-mse-1.4}
 \end{IEEEeqnarray}
-}{
-{\allowdisplaybreaks
+}{{\allowdisplaybreaks
 \begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
@@
 	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
-	&  \text{and} \; \eqref{eqn-4.3}  \IEEEyessubnumber \label{eqn-mse-1.4}
-\end{IEEEeqnarray}}
-}
+	&  \text{and} \; \eqref{eqn-4.3}. \IEEEyessubnumber \label{eqn-mse-1.4}
+\end{IEEEeqnarray}}}
 
@@
 \begin{IEEEeqnarray}{rCl}
-- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}
+- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n},
 \label{mse-lin}
@@
 \underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
-\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin} \IEEEyessubnumber \label{eqn-mse-2.2}
+\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
 \end{IEEEeqnarray}
@@
 \begin{equation}
-\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
 \end{equation}
@@
 	\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
-	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2
+	+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
 \end{multline}

### 2014-10-08 Report/system_model.tex
halfcooked
updated document with thanks and punctuations

@@
 \end{equation}
-Let \me{Q_k} be the number of backlogged packets which are destined for the user \me{k} at a given scheduling instant.
+
+Let \me{Q_k} be the number of backlogged packets destined for the user \me{k} at a given scheduling instant.
 The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for the user \me{k} at the \me{{i}^\mathrm{th}} time instant\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar}.
@@
 \end{equation}
-where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the number of transmitted packets or bits for user \me{k}. For a \ac{MIMO}-\ac{OFDM} system,
+where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the number of transmitted packets or bits for user \me{k}.
+At the \me{\ith{i}} instant, transmission rate of the user \me{k} is given by
 \begin{equation}
@@
 where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} of \me{\gamma_{l,k,n}}\footnote{This can be achieved by Gaussian signaling}.
+The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} of \me{\gamma_{l,k,n}}\footnote{Upper bound is achieved by using Gaussian signaling}.
 Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2014-10-08 Report/wsrm_formulation.tex
updated document with thanks and punctuations

@@
   & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
-  & \quad &\eqref{eqn-4.3} \IEEEyessubnumber
+  & \quad &\eqref{eqn-4.3}, \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 	&\quad& \beta_{l,k,n} \geq \tilde{N}_0 + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
-	&\quad& \text{and } \eqref{eqn-4.3} \IEEEyessubnumber
+	&\quad& \text{and } \eqref{eqn-4.3}, \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 \begin{equation}\label{eqn-8}
-	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}
+	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
 \end{equation}
@@
 2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) \\
-+ \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}
++ \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
 \end{multline}
@@
 & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
-& \quad & \text{and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9.1e}
+& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
 \end{IEEEeqnarray}
@@
 \underset{\substack{\gamma_{l,k,n},\mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
-\text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}
+\text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}.
 \end{IEEEeqnarray}
@@
 \mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}, \IEEEyessubnumber \eqspace
 \end{IEEEeqnarray}
@@
 \mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
-\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n} \IEEEyessubnumber
+\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber
 \end{IEEEeqnarray}
@@
 
-In order to prove the convergence of the proposed iterative algorithm, we require the following conditions to be satisfied at each step \cite{scutari}
+In order to prove the convergence of the proposed iterative algorithm, we require the following conditions to be satisfied at each \ac{SCA} iteration \cite{scutari}
 \begin{itemize}
@@
 	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
-	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n})
+	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}),
 \end{subeqnarray}

### 2014-10-08 Report/ieee_journal.tex
cooker-night

--- 2014-10-02 Report/ieee_journal.tex
@@
-\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[11pt,draft,onecolumn,a4paper]{./../Styles/IEEEtran}
 
@@
 \newtoggle{single_column}
-\togglefalse{single_column}
+\toggletrue{single_column}
 \togglefalse{enable_dist_fig}
@@
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti}
-	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
-		University of Oulu, Oulu, FI-90014\\
-		Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
-}
+	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
+	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi)}}
 
@@
 \begin{IEEEkeywords}
-\acs{MIMO}-\acs{OFDM}, \acs{IBC}, Precoder design, \acs{WSRM}
+\acs{MIMO}-\acs{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
 \end{IEEEkeywords}

### 2014-10-08 Report/introduction.tex
cooker-night

@@
 These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints.
-We consider the problem of transmit precoder design over the space-frequency resources provided by the \acs{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets.
+We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets.
 Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.

### 2014-10-08 Report/joint_wsrm_formulation.tex
cooker-night

@@
 
-The optimal transmission rate vector \me{\mbf{t}} to minimize the total number of backlogged packets in the system is obtained by minimizing the Lyapunov function drift expressed as
+To minimize the total number of backlogged packets for an instant \me{i}, the optimal transmission rate of all users are obtained by minimizing the Lyapunov function drift expressed as  
 \iftoggle{single_column}{
-\begin{multline}\label{eqn-3.1}
+\begin{equation}\label{eqn-3.1}
 \mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ].
-\end{multline}}{
+\end{equation}}{
 \begin{multline}\label{eqn-3.1}
@@
 \begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
-	\underset{\mbf{t}}{\text{inf}} && \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+	\underset{\mbf{t}}{\text{inf}} &\quad& \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
 	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \eqsub \label{backpressure-approx-1b}
@@
 \end{IEEEeqnarray}}
-where the first term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.
-Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpressure-approx-1b} by a constant \me{B} that can be eliminated from the optimization problem \cite{neely2010stochastic}.
+where the subscripts \me{\mbf{t}} and \me{\mbfa{\lambda}} represents the vector obtained by stacking the transmission and the arrival rate of all users present in the system.
+Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpressure-approx-1b} by a constant \me{B} in order to  eliminated from the optimization problem \cite{neely2010stochastic}.
+The second term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.
 

### 2014-10-08 Report/mse_formulation.tex
cooker-night

@@
 \iftoggle{single_column}{
-\begin{IEEEeqnarray}{rCl} \label{mse-error}
-	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
-\end{IEEEeqnarray}
+\begin{multline} \label{mse-error}
+	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
+	+ \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
+\end{multline}
 }{
@@
 \text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
- & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
+ & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
 & \quad &  \text{and} \; \eqref{eqn-4.3}.  \IEEEyessubnumber \label{eqn-mse-1.4}

### 2014-10-08 Report/wsrm_formulation.tex
cooker-night

@@
   & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
-  & \quad &\eqref{eqn-4.3}, \IEEEyessubnumber
+  & \quad & \text{and } \eqref{eqn-4.3}, \IEEEyessubnumber
 \end{IEEEeqnarray}

### 2014-10-09 Report/decomposition_solutions.tex
modified with markku input

@@
 To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-In order to study the decomposition based solutions, we consider the solution proposed in the \eqref{eqn-9}, which is based on the Taylor approximation for the nonconvex constraint.
+In order to study the decomposition based solutions, we consider the solution proposed in \eqref{eqn-9}, which is based on the Taylor series approximation for the nonconvex constraint.
 The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well.
@@
 \end{IEEEeqnarray}}
-where \me{\tilde{\mbf{v}}_b} denote the vector of of weighted queue deviation corresponding to the users \me{k \in \mc{U}_b}.
+where \me{\tilde{\mbf{v}}_b} denotes the vector of of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.
 
-Following the similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \acp{BS} in the coordinating set \me{\mathrm{B}} as
+Following the similar approach as that in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in the coordinating set \me{\mathcal{B}} as
 \iftoggle{single_column}{
@@
 \end{multline}}
-where \me{\zeta_{l,k,n,b}}, which is the total interference caused by the \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
+where \me{\zeta_{l,k,n,b}} is the total interference caused by \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
 \begin{equation}
@@
 
-The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the interference caused by the transmission from \ac{BS} \me{b} to the user \me{\ith{k}} corresponding data stream.
-In order the solve for the global optimal precoders, we need to find the coupling variables \me{\zeta_{l,k,n,b}} by either \acl{PD} or by \acl{DD} method.
+The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the total interference caused by the transmission from \ac{BS} \me{b} to the \me{\ith{l}} spatial stream of user \me{k} over the sub-channel \me{n}.
+In order the solve for the global optimal precoders, we need to find the coupling variables \me{\zeta_{l,k,n,b}} by either the primal or \acl{DD} method.
 In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} and \eqref{eqn-mse-1.3} for the \ac{MSE} relaxation schemes are decoupled to perform the distributed precoder design problem.

### 2014-10-09 Report/dual_approach.tex
cooker-night
modified with markku input

@@
-In this section, we discuss the \ac{ADMM} decomposition method, which is basically based on the \acl{DD}, but shows better convergence properties.
+The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties.
 In contrast to the \acl{PD} problem, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
@@
 
-Let \me{\mbfa{\zeta}(b_k)} denotes the consensus entries corresponding to the \ac{BS} \me{b_k}.
-Let \me{\mbfa{\nu}^{\set{b_k}}} represents the stacked dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} used in the subproblems.
-In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} at the \acp{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} in the objective function.
+Let \me{\mbfa{\zeta}(b_k)} denote the consensus entries corresponding to \ac{BS} \me{b_k}.
+Let \me{\mbfa{\nu}^{\set{b_k}}} represent the stacked dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} used in the subproblems.
+In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} in \ac{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} in the objective function.
 At optimality, the locally assumed and the consensus interference values will be equal,  providing no contribution to the objective function.
@@
 Now, the subproblem at \ac{BS} \me{b} for the \me{\ith{i}} iteration is given by
-\iftoggle{single_column}{
+\iftoggle{single_column}{\allowdisplaybreaks
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
@@
 Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}.
-Since the entries in \me{\mbfa{\zeta}^{(i)}} relates exactly two \acp{BS} only, each entry in the \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS} only.
-For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by the \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
+Since the entries in \me{\mbfa{\zeta}^{(i)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}.
+For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
 \begin{equation}
@@
 \end{equation}
-The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which is the stacked dual variables of the interference equality constraint at the \ac{BS} \me{b_k}, are updated using the subgradient as
+The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which includes the stacked dual variables of the interference equality constraint at \ac{BS} \me{b_k}, are updated using the subgradient as
 \begin{equation}\label{dual-sg-update}

### 2014-10-09 Report/ieee_journal.tex
modified with markku input

--- 2014-10-02 Report/ieee_journal.tex
@@
-\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,final,twocolumn,a4paper]{./../Styles/IEEEtran}
 
@@
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti}
-	\IEEEauthorblockA{Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), \\
-		University of Oulu, Oulu, FI-90014\\
-		Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}
-}
+	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
+	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
 
@@
 
-\subsection{\acs{JSFRA} scheme via \ac{SCA} approach} \label{sec-3.2.1}
+\subsection{\acs{JSFRA} Scheme via \ac{SCA} approach} \label{sec-3.2.1}
 \input{problem_formulation}
@@
 
-\subsection{\ac{JSFRA} scheme via \ac{MSE} reformulation} \label{sec-3.3}
+\subsection{\ac{JSFRA} Scheme via \ac{MSE} Reformulation} \label{sec-3.3}
 \input{mse_formulation}
 
-\subsection{Reduced Complexity Resource Allocation (Per Sub-Channel Resource Allocation)} \label{sec-3.4}
+\subsection{Reduced Complexity Resource Allocation} \label{sec-3.4}
 \input{sub_channel_wsrm}
@@
 
-\subsection{Decomposition using \ac{KKT} equations in \ac{MSE} formulation} \label{sec-4.3}
+\subsection{Decomposition Using \ac{KKT} Equations in \ac{MSE} Formulation} \label{sec-4.3}
 
@@
 \input{simulation_distributed}
-
-\section*{Acknowledgment}
-This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
 

### 2014-10-09 Report/introduction.tex
modified with markku input

@@
 
-In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence of a particular resource \cite{admission_control}.
+In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence in a particular resource \cite{admission_control}.
 In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource.

### 2014-10-09 Report/joint_wsrm_formulation.tex
modified with markku input

@@
 \end{equation}
-where \me{\mbf{Q}(i)} denotes the stacked user queues at the \me{\ith{i}} slot and \me{\tfrac{1}{2}} is used for the convenience.
+where \me{\mbf{Q}(i) = \sset{Q_1(i),Q_2(i),\dotsc,Q_K(i)}^\mathrm{T}} and \me{\tfrac{1}{2}} is used for the convenience.
 It provides a scalar measure of congestion present in the system \cite[Ch.
@@
 \end{IEEEeqnarray}}
-where the subscripts \me{\mbf{t}} and \me{\mbfa{\lambda}} represents the vector obtained by stacking the transmission and the arrival rate of all users present in the system.
-Since the transmission and the arrival rates are bounded, we can upper bound the second order moments in the first term of \eqref{backpressure-approx-1b} by a constant \me{B} in order to  eliminated from the optimization problem \cite{neely2010stochastic}.
+where the subscripts \me{\mbf{t}} and \me{\mbfa{\lambda}} represents the vector formed by stacking the transmission and the arrival rate of all users in the system.
+Since the transmission and the arrival rates are bounded, the second order moments in the first term of \eqref{backpressure-approx-1b} can be bounded by a constant \me{B} without affecting the optimal solution of the problem \cite{neely2010stochastic}.
 The second term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.
@@
 \end{IEEEeqnarray}
-where the precoders are associated with the \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}.
-By using the number of queued packets as the weights, the resources can be allocated to the user with the more number of backlogged packets, which essentially does the allocation in a greedy manner.
+where the precoders are associated with \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}.
+By using the number of queued packets as the weights, the resources can be allocated to the user with the more backlogged packets, which essentially does the allocation in a greedy manner.
 
 As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}.
-This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison with the number of queued packets as in \ac{Q-WSRME}.
-Note that in both formulations, the resources allocated to the users are limited by the backlogged packets with an explicit maximum rate constraint defined by \eqref{eqn-3.1.4}.
+This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison to the number of queued packets as in \ac{Q-WSRME}.
+Note that in both formulations, the resources allocated to the users are limited by the number of backlogged packets with an explicit maximum rate constraint defined by \eqref{eqn-3.1.4}.

### 2014-10-09 Report/kkt_mse_approach.tex
cooker-night
modified with markku input

@@
-The distributed solutions via primal and \ac{ADMM} approaches depend on the subgradient update by using a step size parameter for the coupling variables, which affects the speed of convergence to the optimal value.
+The distributed solutions via primal and \ac{ADMM} approaches depend on the subgradient update by using a step size parameter for the coupling variables.
+It affects the speed of convergence to the optimal value.
 In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by directly solving the \ac{KKT} conditions.
@@
 Even though the rate constraints are implicitly present in the objective function, we cannot formulate the \ac{KKT} conditions readily due to the non-differentiable objective function.
-The non-differentiability of the objective function is due to the absolute operator present in the norm function.
+The non-differentiability is due to the absolute operator present in the norm function.
 In order to make the objective function differentiable, we consider the following case for which the absolute operator can be ignored without affecting the optimal solution, namely,
 \begin{itemize}
-\item when the exponent \me{q} is even or,
-\item when the number of backlogged packets of each user is large enough, \textit{i.e}, \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator and the queues as well.
+\item when the exponent \me{q} is even, or
+\item when the number of backlogged packets of each user is large enough, \textit{i.e}, \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator, which means also ignoring the queues in the first place as well.
 \end{itemize}
@@
 With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
-\iftoggle{single_column}{
+\iftoggle{single_column}{\allowdisplaybreaks
 \begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
@@
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
-\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\
+\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
 \sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
@@
 At each iteration, the dual variable \me{\alpha^{(i)}} is updated linearly from the earlier value \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}.
-It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduce the transmit precoder weights in \eqref{kkt-mse-4.3}.
-This reduction in the precoder weights forces the allocated rate of the user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.
+It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduces the transmit precoder weights in \eqref{kkt-mse-4.3}.
+This reduction in the precoder weights forces the allocated rate of user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.
 
@@
 Now, the closed form expressions in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to a certain accuracy.
-In \eqref{kkt-mse-4}, all expressions are in closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depends on the \ac{BS} specific dual variable \me{\delta_b}.
+In \eqref{kkt-mse-4}, all expressions are in a closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depend on the \ac{BS} specific dual variable \me{\delta_b}.
 It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
@@
 
-In order to perform the distributed approach, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE}, and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} using the updated transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}.
-Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using uplink precoded pilots, where the uplink precoder is given by \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}}.
+In order to find the distributed solution, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE} and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} and the updated transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}.
+Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using the uplink precoded pilots, where the uplink precoder is \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}}.
 Upon receiving the uplink precoded pilots at the \ac{BS} \me{b}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be measured and used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}.

### 2014-10-09 Report/mse_formulation.tex
modified with markku input

@@
-In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable capacity for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}.
+In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}.
 The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
@@
 }
-where \me{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}} denotes the transmit and the receive beamformer and \me{\hat{d}_{l,k,n}} is the received symbol as in \eqref{eqn-1}.
-Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver shown in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
+where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol.
+Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
 \begin{equation} \label{eqn-mse-eq}
@@
 
-Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.
-Now, by relaxing the \ac{MSE} in \eqref{mse-error} and the rate  \ac{MSE} equivalence, \eqref{eqn-6} is written as
+Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.
+By using the relaxed \ac{MSE} expression in \eqref{mse-error}, the problem in \eqref{eqn-3} can be expressed as
 \iftoggle{single_column}{
@@
 
-The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
-We adopt the \ac{SCA} method as in Section \ref{sec-3.2} to relax the constraint by a sequence of convex subsets using first order approximations around \me{\tilde{\epsilon}_{l,k,n}} as
+An alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
+We adopt the \ac{SCA} method as in Section \ref{sec-3.2} to relax the constraint by a sequence of convex subsets using first order Taylor series approximation around a fixed \ac{MSE} point  \me{\tilde{\epsilon}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl}
@@
 
-Now, using the above approximation for the rate constraint, the problem defined by \eqref{eqn-mse-1} can be solved optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}} and the users rates over each sub-channel \me{t_{l,n,k}} for the fixed receive beamformers.
+Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,n,k}} given the fixed receive beamformers.
 Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}.
@@
 \subsubsection*{Convergence}
-Following the similar approach in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem.
+Following similar approach as in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem.
 The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution.
@@
 }
-we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are avoided by the real component in the \ac{MSE} expression.
+we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are eliminated by the presence of real component in the \ac{MSE} expression.
 
-At each \ac{SCA} step, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem.
+At each \ac{SCA} iteration, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem.
 Using the transmit precoders, the receive beamformers are obtained using the \ac{MMSE} receivers.
 The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders, leading to the monotonic convergence of the objective function.
-At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, the objective value can either decrease or stays the same after each iteration.
+At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, and the objective value can either decrease or stays the same after each iteration.

### 2014-10-09 Report/primal_approach.tex
modified with markku input

@@
 Once the optimal precoders are designed at each \ac{BS} with the fixed interference constraints \eqref{eqn-decent-3}, the dual variables corresponding to the interference constraints are exchanged between the cooperating \acp{BS} in \me{\mc{B}} to update the interference variables \me{\zeta_{l,k,n,b}} for the next iteration until convergence.
-The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows the same.
+The primal approach is discussed extensively for the min-power problem in \cite{pennanen2011decentralized} and much of the current work follows similar approach.
 %Much of the details are provided in the Appendix \ref{a-2}.
@@
 \subsubsection*{Convergence}
-The convergence of the primal is similar to that of the centralized problem if the interference variables \me{\zeta_{l,k,n,b}} are allowed to converge to a stationary point.
-But in practice, we can limit the number of exchanges to \me{J_{\max}} after which \ac{SCA} update is performed until convergence or for \me{I_{\max}} times.
+The convergence of the primal decomposition is similar to that of the centralized problem if the interference variables \me{\zeta_{l,k,n,b}} are allowed to converge to a stationary point.
+In practice, we can limit the number of exchanges to \me{J_{\max}} after which the \ac{SCA} update is performed until convergence or for \me{I_{\max}} times.
 The update of \me{\tilde{p}_{l,k,n}, \tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} can be made in conjunction with the receiver update \me{\mvec{W}{k,n}}.

### 2014-10-09 Report/problem_formulation.tex
markku_modifications
halfcooked
modified with markku input

@@
-The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by the limiting it to a constant value.
-In fact, Eq.
-\eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
+The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value.
+In fact, \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
 \begin{equation}\label{pf-1}
-\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2
+\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2.
 \end{equation}
+
 It is evident that \eqref{pf-1} is equivalent to \eqref{backpressure-approx} if the second order terms are ignored.
-Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over allocation.
+Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over-allocation.
 In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself.
@@
 In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system.
-The queue deviation objective provides an alternative approach to perform the resource allocation without the additional rate constraints as in \ac{Q-WSRME} approach.
+The queue deviation objective provides an alternative approach to perform the resource allocation without the additional rate constraints as in the \ac{Q-WSRME} formulation.

### 2014-10-09 Report/simulation_distributed.tex
temporary_version
double_ready
modified with markku input

@@
-The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points.
+The performances of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points.
 Fig.
-\ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}.
+\ref{fig-d} compares the performances of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}.
 Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}.
@@
 
-The Fig.
-\ref{fig-d} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} points.
+Fig.
+\ref{fig-d} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using the \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} point.
 In between the \ac{SCA} updates, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables.
@@
 It can be seen from Fig.
-\ref{fig-d} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
+\ref{fig-d} that the distributed algorithms approach the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
 
@@
 \centering
-\includegraphics[width=0.48\textwidth]{fig-3-2}
+\includegraphics[width=\columnwidth]{fig-3-2}
 \label{fig-d-1}
-\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}}
-\label{fig-d}
+\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}.}
+\label{fig-d} \vspace{-0.15in}
 \end{figure}
@@
 Fig.
-\ref{fig-d-3.1} compares the performances of the centralized algorithm based on the \ac{MSE} reformulation with the iterative approach proposed in Section \ref{sec-4.3} based on solving the \ac{KKT} conditions.
-In Fig.
-\ref{fig-d-3.1}, the plots are compared by the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point.
+\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents.
+The plots present the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point.
 Fig.
-\ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over rest of the schemes due to its greedy objective.
+\ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over the rest of the schemes due to its greedy objective.
 The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches.
@@
 	\includegraphics[width=\columnwidth]{fig-9-3}
-	\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
-	\label{fig-d-3.1}
+	\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}.}
+	\label{fig-d-3.1} \vspace{-0.15in}
 \end{figure}
 
-The objective values are mentioned in the legend for all the schemes, since the objective of \me{\ell_2} norm is not the same as \me{\ell_1} norm, which is used for the plot.
+The objective values are mentioned in the legend for all the schemes, since the objective of the \me{\ell_2} norm is not the same as that of the \me{\ell_1} norm, which is used for the plot.
 The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables \me{\alpha_{l,k,n}} and \me{\sigma_{l,k,n}} are not iterated until convergence between each \ac{SCA} steps in the \ac{KKT} approach.

### 2014-10-09 Report/simulation_intro.tex
modified with markku input

@@
-The simulations carried out in this work considered the path loss varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d} samples.
+The simulations carried out in this work consider the path loss varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples.
 The queues are generated based on the Poisson process with the average values specified in each section presented.

### 2014-10-09 Report/simulation_results.tex
temporary_version
double_ready
modified with markku input

@@
+We discuss the performance of the centralized algorithms in Section \ref{sec-3} for some system configurations.
+To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
+The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits, respectively.
 \begin{table*}
 	\centering
+		\caption{Sub-channel-wise channel and rate allocation for a scheduling instant}
 	\renewcommand{\arraystretch}{1.25} \scriptsize
@@
 	\end{tabular}
-	\caption{Sub channel wise allocation for a scheduling instant}
-	\label{tbl-1}
+	\label{tbl-1} \vspace{-0.15in}
 \end{table*}
-%\begin{figure}
-%\centering
-%\includegraphics[width=\columnwidth]{tbl-1}
-%\caption{Allocation for a \ac{SISO} Model comparing different Algorithms}
-%\label{tbl-1}
-%\end{figure}
+\begin{figure*}
+	\centering
+	\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
+		\includegraphics[width=0.485\textwidth]{fig-1-4}
+		\label{fig-1}}
+	\hfill
+	\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
+		\includegraphics[width=0.485\textwidth]{fig-2-5}
+		\label{fig-2}}
+	\caption{Number of backlogged packets at the \ac{SCA} update points.}
+	\label{fig-a} \vspace{-0.15in}
+\end{figure*}
 
-In this section, we discuss the performance of the centralized algorithms from Section \ref{sec-3} for a few system configurations.
-To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
-The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits respectively.
-
-Table.
-\ref{tbl-1} outlines the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} design \cite{wmmse_shi}.
-The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
-Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} got scheduled in the first sub-channel due to the better channel condition.
+Table \ref{tbl-1} tabulates the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using the \ac{WMMSE} design \cite{wmmse_shi}.
+The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted as \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
+Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} is scheduled in the first sub-channel due to the better channel condition.
 In contrast, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets waiting at the transmitter.
@@
 
-For the \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
-The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with lowest path loss component.
+For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
+The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component.
 Fig.
-\ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system.
+\ref{fig-1} shows the performances of the centralized schemes for a single receive antenna system.
 It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
@@
 \ref{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
-\begin{figure*}
-\centering
-\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-1-4}
-\label{fig-1}}
-\hfill
-\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
-\includegraphics[width=0.48\textwidth]{fig-2-5}
-\label{fig-2}}
-\caption{Number of backlogged packets at the \ac{SCA} update points}
-\label{fig-a}
-\end{figure*}
 
-The performance of the centralized algorithms are compared by the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
+The performances of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
 \ref{fig-a}.
-The \ac{Q-WSRM} algorithm is not optimal due to the problem of over allocation when the number of queued packets are small, as in Fig.
+The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets is small, as in Fig.
 \ref{fig-a}.
-In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over allocation problem.
+In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation problem.
 It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}.
-It can be seen that all the algorithms are Pareto-optimal and provides different performance based on the weights used to find a point in the rate region.
+All the algorithms are Pareto-optimal and provide different performances based on the weights used to find a point in the rate region.
 
-In the scenario defined by Fig.
+In the scenario defined for Fig.
 \ref{fig-a}, \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the rate maximization algorithm.
@@
 \ref{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case.
-In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in the Algorithm \ref{algo-1}.
+In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in Algorithm \ref{algo-1}.
 It is also noted that the performance degradation by performing the group update is very minimal.
 Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
+%\begin{figure}
+%\centering
+%\includegraphics[width=\columnwidth]{tbl-2}
+%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
+%\label{tbl-3}
+%\end{figure}
 \begin{table}
-\flushleft
+	\centering
+	\caption{Number of backlogged bits for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}.}
 	\renewcommand{\arraystretch}{1.25} \scriptsize
@@
 		\hline
-\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
+		\multirow{2}{*}{\me{q}} & \multicolumn{8}{c|}{user indices} & \multirow{2}{*}{\me{\chi}} \\
+		\cline{2-9}
+		& 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \\
+		\hline
 		\hline
@@
 	\end{tabular}
-\caption{Queues for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
-\label{tbl-3} \vspace{-0.5cm}
+	\label{tbl-3} \vspace{-0.2in}
 \end{table}
-%\begin{figure}
-%\centering
-%\includegraphics[width=\columnwidth]{tbl-2}
-%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
-%\label{tbl-3}
-%\end{figure}
 
-The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Table.
-\ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas.
-The configuration is mentioned in the caption of Table.
-\ref{tbl-3} along with the number of queued bits for each user.
-It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits.
+The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} is outlined in the Table \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas.
+It is evident that the \ac{JSFRA} algorithm minimizes the total number of queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits.
 The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets to be equal for all users to \me{\chi_k = 3.58} bits.
-The \me{\ell_{\infty}} norm provides the fair allocation by making the queued deviation equal for all the users after the current allocation irrespective of their channel gains.

### 2014-10-09 Report/sub_channel_wsrm.tex
updated document with thanks and punctuations
modified with markku input

@@
 In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size.
-In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
+In order to mitigate the problem, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
 The optimal approach is to decompose the problem over each sub-channel with a fixed transmit power constraint for each sub-channel.
@@
 The proposed \acl{QM} \ac{SRA} formulation enables us to solve for the transmit precoders of all the users associated with the coordinating \ac{BS} in the set \me{\mathcal{B}} over each sub-channel independently by fixing the transmit power on each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}.
-In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization.
-The total number of queued bits for each user are updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
+In contrast to the decomposition based approach for the sub-channel-wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel-wise optimization.
+The total number of queued bits for each user is updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
 \begin{equation}
-Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
+Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U},
 \label{eqn-weight}
@@
 where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}.
-In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}.
+In the expression in \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}.
 However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.

### 2014-10-09 Report/wsrm_formulation.tex
modified with markku input

@@
 }
-where \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} be the vector which needs to be identified for the optimal allocation and \me{\tilde{N}_0 = N_0\|\mvec{w}{l,k,n}\|^2} be the effective noise variance.
+where \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation and \me{\tilde{N}_0 = N_0\|\mvec{w}{l,k,n}\|^2} be the effective noise variance.
 In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-However, this step without loss of optimality leads to the same solution, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}.
-Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by the user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}.
+However, this step leads to the same solution without loss of optimality, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}.
+Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}.
 Similar to the \ac{WSRM} problem in \cite{tran2012fast}, the problem can be shown to be NP-hard even for the single antenna case.
@@
 Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
-Recall the original coordinate descent method assumes that the optimization variables belong to disjoint sets (Cartesian product of sets, to be precise) \cite{xu2013block}.
+Recall that the original coordinate descent method assumes that the optimization variables belong to disjoint sets (Cartesian product of sets, to be precise) \cite{xu2013block}.
 
-By fixing the receivers, the problem now is to find optimal transmit beamformers for a given set of linear receivers which is still a challenging task.
+By fixing the receivers, the problem now is to find the optimal transmit beamformers for a given set of linear receivers which is still a challenging task.
 We note that for fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
 Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}.
-To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by the series of convex constraints.
-Note that the function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}} since it is in fact the ratio between a quadratic form (of \me{\mvec{m}{l,k,n}}) over an affine function (of \me{\beta_{l,k,n}}) \cite{boyd2004convex}.
+To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by a series of convex constraints.
+Note that function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
 According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure.
@@
 \end{subeqnarray}
-and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}.
-Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
-In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.
+and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
+In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier}.
 Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively.
@@
 
-Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} w.r.t \me{\mbf{w}_{l,k,n}} as
+Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} with respect to \me{\mbf{w}_{l,k,n}} as
 \begin{IEEEeqnarray}{CCl}\label{eqn-9--1}
@@
 \end{IEEEeqnarray}
-Solving \eqref{eqn-9--1} using \ac{KKT} conditions, we obtain the following iterative expression for the receive beamformer \me{\mvec{w}{l,k,n}} as
-\begin{IEEEeqnarray}{rCl} \label{opt-rx}
+Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mvec{w}{l,k,n}} as
+\begin{IEEEeqnarray}{rCl}
 \mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}, \IEEEyessubnumber \eqspace
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}, \IEEEyessubnumber \eqspace \label{opt-rx}
 \end{IEEEeqnarray}
@@
 It can be seen that the optimal receiver expression in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
-\begin{IEEEeqnarray}{rCl}\label{eqn-10}
+\begin{IEEEeqnarray}{rCl}
 \mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
-\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber
+\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
 \end{IEEEeqnarray}
 
-The proposed algorithm is referred as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint which is outlined in Algorithm \ref{algo-1}.
+The proposed algorithm is referred to as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint, and it is outlined in Algorithm \ref{algo-1}.
 The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
 Instead of initializing \me{\tilde{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{\tilde{\mbf{u}}_{l,k,n}} in an efficient manner as briefed in Algorithm \ref{algo-1}.
-For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for the predefined iterations, say \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
+For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for the predefined iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
 Next, the receive beamformers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
-This procedure is carried out until convergence of the queue deviation or for fixed number of iterations defined by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
+This procedure is carried out until convergence of the queue deviation or for fixed number of iterations by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
 {\allowdisplaybreaks
@@
 
-In order to prove the convergence of the proposed iterative algorithm, we require the following conditions to be satisfied at each \ac{SCA} iteration \cite{scutari}
+In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}
 \begin{itemize}
@@
 At each \ac{SCA} iteration, the relaxed subproblem is solved for the locally optimal transmit precoders to minimize the objective function.
-Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point,\textit{i.e} \me{\mbf{x}^{\ast(i-1)}}, for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
-Therefore, at each \ac{SCA} steps, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.
+Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point, \textit{i.e},  \me{\mbf{x}^{\ast(i-1)}} for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
+Therefore, at each \ac{SCA} step, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.
 
-Once the problem is converged to a stationary transmit precoders, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}.
-The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, and hence the proposed \ac{JSFRA} scheme guarantees to converge to a stationary point of the original nonconvex problem.
+Once the problem is converged to a stationary transmit precoders, the receive beamformers are updated based on the receivers in \eqref{opt-rx} or \eqref{eqn-10}.
+The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, and hence the proposed \ac{JSFRA} scheme is guaranteed to converge to a stationary point of the original nonconvex problem.

### 2014-10-10 Report/simulation_distributed.tex
Finalized before final review (internal)

@@
 \includegraphics[width=\columnwidth]{fig-3-2}
-\label{fig-d-1}
-\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}.}
-\label{fig-d} \vspace{-0.15in}
+\caption{Convergence behaviour of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}}
+\label{fig-d} \vspace{-0.1in}
 \end{figure}
@@
 	\includegraphics[width=\columnwidth]{fig-9-3}
-	\caption{\me{\chi} at \ac{SCA} points for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}.}
-	\label{fig-d-3.1} \vspace{-0.15in}
+	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
+	\label{fig-d-3.1} \vspace{-0.1in}
 \end{figure}

### 2014-10-10 Report/simulation_results.tex
Finalized before final review (internal)

@@
 	\centering
-		\caption{Sub-channel-wise channel and rate allocation for a scheduling instant}
+		\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
 	\renewcommand{\arraystretch}{1.25} \scriptsize
@@
 	\end{tabular}
-	\label{tbl-1} \vspace{-0.15in}
+	\label{tbl-1} \vspace{-0.1in}
 \end{table*}
@@
 	\centering
-	\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
-		\includegraphics[width=0.485\textwidth]{fig-1-4}
+	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
+		\includegraphics[width=0.5\textwidth]{fig-1-4}
 		\label{fig-1}}
-	\hfill
-	\subfloat[][System \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
-		\includegraphics[width=0.485\textwidth]{fig-2-5}
+	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
+		\includegraphics[width=0.5\textwidth]{fig-2-5}
 		\label{fig-2}}
-	\caption{Number of backlogged packets at the \ac{SCA} update points.}
-	\label{fig-a} \vspace{-0.15in}
+	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates}
+	\label{fig-a} \vspace{-0.1in}
 \end{figure*}
@@
 It is due to the efficient allocation of the total power shared across the sub-channels.
-
-For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
-The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component.
-Fig.
-\ref{fig-1} shows the performances of the centralized schemes for a single receive antenna system.
-It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
-The total number of queued packets for Fig.
-\ref{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig.
-\ref{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
-
-The performances of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
-\ref{fig-a}.
-The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets is small, as in Fig.
-\ref{fig-a}.
-In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation problem.
-It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}.
-All the algorithms are Pareto-optimal and provide different performances based on the weights used to find a point in the rate region.
-
-In the scenario defined for Fig.
-\ref{fig-a}, \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the rate maximization algorithm.
-The performance degradation can be attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
-Fig.
-\ref{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case.
-In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in Algorithm \ref{algo-1}.
-It is also noted that the performance degradation by performing the group update is very minimal.
-Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
-%\begin{figure}
-%\centering
-%\includegraphics[width=\columnwidth]{tbl-2}
-%\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
-%\label{tbl-3}
-%\end{figure}
 \begin{table}
 	\centering
-	\caption{Number of backlogged bits for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}.}
+	\caption{Number of backlogged bits associated with each user for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}.}
 	\renewcommand{\arraystretch}{1.25} \scriptsize
@@
 	\end{tabular}
-	\label{tbl-3} \vspace{-0.2in}
+	\label{tbl-3} \vspace{-0.1in}
 \end{table}
+
+For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
+The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component.
+Fig.
+\subref*{fig-1} shows the performances of the centralized schemes for a single receive antenna system.
+It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
+The total number of queued packets for Fig.
+\subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig.
+\subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
+
+The performances of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
+\ref{fig-a}.
+The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets is small, as in Fig.
+\ref{fig-a}.
+In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation problem.
+It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}.
+All the algorithms are Pareto-optimal and provide different performances based on the weights used to find a point in the rate region.
+
+In both scenarios defined in Fig.
+\ref{fig-a}, \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the rate maximization algorithm.
+The performance degradation can be attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
+Fig.
+\subref*{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case.
+In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in Algorithm \ref{algo-1}.
+It is also noted that the performance degradation by performing the group update is very minimal.
+Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
 

### 2014-10-10 Report/wsrm_formulation.tex
Finalized before final review (internal)

@@
 Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
-Recall that the original coordinate descent method assumes that the optimization variables belong to disjoint sets (Cartesian product of sets, to be precise) \cite{xu2013block}.
+Recall that the original coordinate descent method assumes that the optimization variables belong to disjoint sets, and the domain of the problem is given by the Cartesian product of the independent sets  \cite{xu2013block}.
 

### 2014-10-10 Report/ieee_journal.tex
patched

@@
-\documentclass[10pt,final,twocolumn,a4paper]{./../Styles/IEEEtran}
+\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}
 
-\usepackage{etoolbox}
 \usepackage{amsmath,amssymb}
-\usepackage{graphicx,acronym}
+\usepackage{acronym,etoolbox}
 \usepackage[ruled]{algorithm2e}
-\usepackage{subfig,subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno}
+\usepackage[dvipdfmx]{graphicx}
+\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
+\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno}
 

### 2014-10-10 Report/wsrm_formulation.tex
patched

--- 2014-10-09 Report/wsrm_formulation.tex
@@
 Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
-Recall that the original coordinate descent method assumes that the optimization variables belong to disjoint sets (Cartesian product of sets, to be precise) \cite{xu2013block}.
+Recall that the coordinate descent method assumes that the optimization variables belong to disjoint sets and the problem is convex for a variable while all other variables are fixed \cite{xu2013block}.
 

### 2014-10-14 Report/conclusions.tex
modified with markku input
Updated with rohit comments

@@
-In this paper, we addressed the allocation of space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{OFDM} system.
+In this paper, we addressed the allocation of space-frequency resources to the users in a multi-cell \acl{MIMO} \acl{OFDM} system.
 The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user can be achieved by a non-zero precoding vector.
 We proposed the \ac{JSFRA} scheme by adopting the \ac{SCA} technique to model the nonconvex constraint as a sequence of convex subsets to design the precoders for minimizing the number of queued packets.
-Additionally, an alternative approach using \ac{MSE} relaxation is also proposed with the same objective by fixing the receivers based on \ac{MSE} minimization.
-We also proposed the distributed solutions for the centralized \ac{JSFRA} problem using \ac{ADMM} and primal decomposition methods.
+Additionally, an alternative approach using \acl{MSE} relaxation is also proposed with the same objective by fixing the receivers based on \ac{MSE} minimization.
+We also proposed the distributed solutions for the centralized \ac{JSFRA} problem using primal and \ac{ADMM} decomposition methods.
 Finally, we proposed an iterative algorithm to determine the precoders in a decentralized manner based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme.

### 2014-10-14 Report/simulation_distributed.tex
Updated with rohit comments

@@
 Fig.
-\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents.
-The plots present the surplus number of backlogged packets at the end of each iteration or the \ac{SCA} update point.
-Fig.
-\ref{fig-d-3.1} shows that the \me{\ell_1} norm for \ac{JSFRA} scheme provides better performance over the rest of the schemes due to its greedy objective.
-The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}, thereby performs the worst of all other approaches.
-The heuristic method used in the figure is obtained by forcing the dual variable \me{\sigma_{l,k,n}} in \eqref{kkt-mse-4.2} to \me{0} when the queue deviation is negative \me{Q_k - t_k < 0}, if not, then it will be the same as in \eqref{kkt-mse-4.2}.
-The additional condition can be justified due to the dropping of absolute value operator from the objective.
+\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents by plotting the total number of backlogged packets at each \ac{SCA} update point.
+The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective.
+The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}.
+If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one.
+A heuristic method is proposed in Fig.
+\ref{fig-d-3.1} by assigning zero to the dual variable \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}.
+This additional condition is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function.
 It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
@@
 
-The objective values are mentioned in the legend for all the schemes, since the objective of the \me{\ell_2} norm is not the same as that of the \me{\ell_1} norm, which is used for the plot.
-The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} based approach achieves nearly the same objective value of \me{6.62} but different \me{\chi}, since the dual variables \me{\alpha_{l,k,n}} and \me{\sigma_{l,k,n}} are not iterated until convergence between each \ac{SCA} steps in the \ac{KKT} approach.
-In the simulation, we update all the variables at once at each iteration, \textit{i.e}, \me{J_{\max} = 1}, which is well justified for the practical implementations due to the signaling overheads.
+The objective values are mentioned in the legend for all the schemes and the objective of the \me{\ell_2} norm is not the same as that of the \me{\ell_1} norm used for plotting.
+For simulations, we update all variables in \eqref{kkt-mse-4} at once at each iteration, \textit{i.e}, \me{J_{\max} = 1}, which is well justified for the practical implementations due to the signaling overheads.
+The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} approach achieves nearly the same value of \me{6.62} with different \me{\chi}, due to the limited number of iterations for the dual variable convergence between each \ac{SCA} update.
 Fig.
-\ref{fig-d-3.1} also compares the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRME} scheme compared to the \me{\ell_2} norm which includes it.
-By dropping the squared rate variable, the \ac{Q-WSRME} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues.
+\ref{fig-d-3.1} also shows the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRME} scheme compared to the \me{\ell_2} norm which includes it.
+By dropping it, the \ac{Q-WSRME} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues.
 On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.

### 2014-10-14 Report/ieee_journal.tex
Updated with rohit comments
updated minor changes

@@
-\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 \newtoggle{single_column}
-\toggletrue{single_column}
+\togglefalse{single_column}
 \togglefalse{enable_dist_fig}
@@
 \begin{IEEEkeywords}
-\acs{MIMO}-\acs{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
+\ac{MIMO}-\ac{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
 \end{IEEEkeywords}
@@
 \acresetall
+
 \section{Introduction} \label{sec-1}

### 2014-10-14 Report/kkt_mse_approach.tex
updated minor changes

@@
 
-The problem in \eqref{kkt-mse-1} is solved using the\ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables as shown in the Appendix \ref{a-1}.
+The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables as shown in the Appendix \ref{a-1}.
 Upon solving, we obtain the iterative solution as
@@
 \subsubsection*{Convergence}
-The iterative method presented in Algorithm \ref{algo-4} converges to the stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}.
-The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive precoders \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}.
-Once the dual variables are converged or iterated to a certain accuracy, the receivers are updated using the \ac{MMSE} objective.
-In this algorithm, when \me{t_k > Q_k}, \me{\sigma_{l,k,n}} will be zero (dual feasibility), thereby reducing the priority weights \me{\alpha_{l,k,n}} present in the transmit precoder expression in \eqref{kkt-mse-4.3}.
+The iterative method presented in Algorithm \ref{algo-4} converges to a stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}.
+The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive beamformers \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}.
+Once the dual variables are converged or iterated for certain accuracy, the receivers are updated using the \ac{MMSE} objective.
+Since the \ac{MMSE} receiver is optimal for the fixed transmit precoders, the objective function will improve or stays the same after the receiver update leading to a monotonic convergence of the iterative algorithm provided in \eqref{kkt-mse-4}.

### 2014-10-16 Report/decomposition_solutions.tex
updated final with kkt conditions

@@
 
-Following the similar approach as that in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint in \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in the coordinating set \me{\mathcal{B}} as
+Following similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in \me{\mathcal{B}} as
 \iftoggle{single_column}{
@@
 &\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2,
-\end{IEEEeqnarray}}{
+\end{IEEEeqnarray}}{\allowdisplaybreaks
 \begin{multline}\label{eqn-decent-3}

### 2014-10-16 Report/kkt_mse_approach.tex
updated final with kkt conditions

@@
 \mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}.
+\IEEEyessubnumber \label{kkt-mse-4.6}\\
+\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
 \sigma_{l,k,n}^{(i)} &=& \left [\tfrac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right ]^+  \IEEEyessubnumber \label{kkt-mse-4.2} \\
-\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
-\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}.
-\IEEEyessubnumber \label{kkt-mse-4.6}
+\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1}
 \end{IEEEeqnarray}
@@
 	& \qquad {} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-	\epsilon_{l,k,n}^{(i)} =& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \nonumber \\
-	& \qquad{} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+	\mvec{w}{l,k,n}^{(i)} =& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm \nonumber \\
+	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}. \IEEEyessubnumber \label{kkt-mse-4.6} \\
+	\epsilon_{l,k,n}^{(i)} =& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \nonumber \\
+	& \qquad{} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
 	t_{l,k,n}^{(i)} =&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \tfrac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
 	\sigma_{l,k,n}^{(i)} =& \Big [\tfrac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\Big ]^+  \IEEEyessubnumber \label{kkt-mse-4.2} \\
-	\alpha^{(i)}_{l,k,n} =& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1} \\
-	\mvec{w}{l,k,n}^{(i)} =& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm \nonumber \\
-	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}. \IEEEyessubnumber \label{kkt-mse-4.6}
+	\alpha^{(i)}_{l,k,n} =& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1}
 \end{IEEEeqnarray}}}
@@
 Now, the closed form expressions in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to a certain accuracy.
-In \eqref{kkt-mse-4}, all expressions are in a closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depend on the \ac{BS} specific dual variable \me{\delta_b}.
+In \eqref{kkt-mse-4}, all expressions are in closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depend on the \ac{BS} specific dual variable \me{\delta_b}.
 It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
-After each iteration instant, the transmit and the receive precoders are updated across the coordinating \acp{BS} in \me{\mc{B}} to obtain the next operating point.
+Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}.
 
-In order to find the distributed solution, we can consider the method proposed in \cite{komulainen2013effective}, where the users evaluate the \ac{MSE} and the dual variable \me{\alpha_{l,k,n}} using the transmission made by all \acp{BS} and the updated transmit precoders \me{\mvec{m}{l,k,n}^{(i-1)}}.
-Once the dual variables are evaluated, the users will notify the dual variables and the receive beamformers to the \acp{BS} using the uplink precoded pilots, where the uplink precoder is \me{\mvec{\tilde{w}}{l,k,n}^{(i-1)} = \sqrt{\alpha_{l,k,n}^{(i-1)}}\mvec{w}{l,k,n}^{\ast(i-1)}}.
-Upon receiving the uplink precoded pilots at the \ac{BS} \me{b}, the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i-1)}} can be measured and used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} represents the conjugate of \me{\mbf{x}}.
-The algorithmic representation of the distributed \ac{MSE}-\ac{KKT} scheme is shown in the Algorithm.
-\ref{algo-4}.
+We consider the method proposed in \cite{komulainen2013effective} to design the precoders in a distributed manner across the coordinating \acp{BS} in \me{\mathcal{B}}.
+Upon receiving the transmitted signal from all \acp{BS} using the updated precoders  \me{\mvec{m}{l,k,n}}, each user update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}.
+Once the dual variable \me{\alpha_{l,k,n}} and the receive beamformers are evaluated, the users will notify it to the coordinating \acp{BS} using precoded uplink pilots with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{w}{l,k,n}} as the precoders.
+Upon receiving the precoded uplink pilots, each \ac{BS} will use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the conjugate of \me{\mbf{x}}.
+Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
 \begin{algorithm}
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n},\epsilon_{l,k,n}^{(0)}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}}}
+ \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
  \ForEach{\ac{BS} \me{b \in \mc{B}}}{
@@
  \Repeat{until convergence or \me{i \geq I_{\max}}}{
-	find \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, where \me{\delta_b} is obtained by bisection search satisfying \eqref{kkt-mse-1.4} \;
-	update \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at \ac{BS} \me{b} and perform precoded downlink pilot transmission with \me{\mvec{M}{k,n}^{(i)}}\;
-	update \me{\mvec{W}{k,n}^{(i+1)}} using \eqref{kkt-mse-4.6} and notify to all \acp{BS} using uplink precoded pilot with \me{\mvec{\tilde{w}}{l,k,n}^{(i+1)}} as the precoder\;
+	update \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
+	find \me{\mvec{W}{k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
+	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{W}{k,n}^{(i)}} \;
+	using precoded uplink pilots, \me{\mvec{W}{k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
 	\me{i = i + 1} \;
@@
 \subsubsection*{Convergence}
-The iterative method presented in Algorithm \ref{algo-4} converges to a stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}.
+The iterative method presented in Algorithm \ref{algo-4} converges to a stationary point at each iteration.
+Since the \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}} and the receive beamformers are updated together at each iteration, the convergence proof is not similar to the primal or the \ac{ADMM} methods.
+The convergence proof can be argued based on the monotonic increase of the objective function at each iteration as follows.
+The transmit precoders in \eqref{kkt-mse-4.3} improves the objective function after each update following the \ac{SCA} operating point \me{\tilde{\epsilon}_{l,k,n}} update \cite{marks1978technical}.
+Furthermore, the \ac{MMSE} receivers are globally optimal for the fixed transmit precoders \cite{christensen2008weighted,wmmse_shi}, the alternating beamformer updates improve the objective function monotonically in spite of having a subgradient update in \eqref{kkt-mse-4.1}.
+It is more suitable for the practical implementation due to the reduction in the signaling overhead and the iterations to converge.
+%presented in Algorithm \ref{algo-4} converges to a stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}.
 The convergence of the dual variable is guaranteed, since the problem is convex by fixing the receive beamformers \me{\mvec{w}{l,k,n}} and the operating \ac{MSE} point \me{\epsilon_{l,k,n}} \cite{boyd2011distributed}.

### 2014-10-16 Report/simulation_distributed.tex
updated final with kkt conditions

@@
 If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one.
-A heuristic method is proposed in Fig.
-\ref{fig-d-3.1} by assigning zero to the dual variable \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}.
-This additional condition is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function.
+A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig.
+\ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}.
+It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function.
 It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.

### 2014-10-17 Report/kkt_mse_approach.tex
updated draft with KKT distributed schemes

@@
 Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other.
-In this problem, we fix the dual variable \me{\alpha^{(i)}} to a fixed value as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.
-At each iteration, the dual variable \me{\alpha^{(i)}} is updated linearly from the earlier value \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}.
-It can be seen that, when the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing the dual variable \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}}, which in turn reduces the transmit precoder weights in \eqref{kkt-mse-4.3}.
-This reduction in the precoder weights forces the allocated rate of user \me{k} to reduce from the previous iteration as \me{t_k^{(i)} < t_k^{(i-1)}}.
+So, the variable  \me{\alpha^{(i)}} is fixed as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.
+At each iteration, the dual variables \me{\alpha^{(i)}} are updated linearly from the earlier \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}.
+When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
+Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}}.
 
-The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors.
-The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to provide equal priorities to all streams.
-Now, the closed form expressions in \eqref{kkt-mse-4} are evaluated sequentially until convergence or to a certain accuracy.
-In \eqref{kkt-mse-4}, all expressions are in closed form except the transmit precoders \eqref{kkt-mse-4.3}, which depend on the \ac{BS} specific dual variable \me{\delta_b}.
-It can be solved efficiently by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
+The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors.
+The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to have equal weights.
+The transmit precoders in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
 Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}.
+Following approaches can be performed to decouple the precoder design problem with the limited signaling between the \acp{BS} in \me{\mathcal{B}}.
 
-We consider the method proposed in \cite{komulainen2013effective} to design the precoders in a distributed manner across the coordinating \acp{BS} in \me{\mathcal{B}}.
-Upon receiving the transmitted signal from all \acp{BS} using the updated precoders  \me{\mvec{m}{l,k,n}}, each user update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}.
-Once the dual variable \me{\alpha_{l,k,n}} and the receive beamformers are evaluated, the users will notify it to the coordinating \acp{BS} using precoded uplink pilots with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{w}{l,k,n}} as the precoders.
-Upon receiving the precoded uplink pilots, each \ac{BS} will use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in the expression \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the conjugate of \me{\mbf{x}}.
+As a first approach, in this method, for a fixed the receive beamformers, \me{\alpha_{l,k,n}} and the operating \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}}, each \ac{BS} evaluates the transmit precoder \me{\mvec{m}{l,k,n}^{(i)}} and exchange the total interference contribution by using the updated precoder to the neighboring \ac{BS} users.
+On receiving this information, each \ac{BS} will update \eqref{kkt-mse-4.4}, \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2}, and \eqref{kkt-mse-4.1}.
+For the fixed receive beamformer, the dual variables \me{\alpha_{l,k,n}} and the interference contributions are exchanged until convergence by finding the updated transmit precoders.
+Once the dual variables are converged, the receivers are updated by performing the downlink transmission.
+This procedure is iterated until convergence for a fixed \me{I_{\max}} iterations.
+The convergence is similar to the \ac{JSFRA} scheme with \ac{MSE} reformulation in Section \ref{sec-3.3}.
+
+The following approaches are similar to the decentralization methods proposed in \cite{komulainen2013effective} for the sum rate maximization problem.
+In the this approach, after receiving the transmitted signal with the recent precoders from all \acp{BS} in \me{\mathcal{B}}, the users evaluate the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify it to the \acp{BS} using the precoded uplink pilots.
+Upon receiving, each \ac{BS} estimates the \ac{MSE} using \me{\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}}.
+Using the updated \ac{MSE}, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}.
+The updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.
+
+Finally, in this approach, upon receiving the signal from all \acp{BS}, the users update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}.
+The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified the \acp{BS} using precoded uplink pilots with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{\bar{w}}{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
+On receiving the precoded uplink pilots, the \acp{BS} will use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
 Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
+ \KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}, \tilde{\epsilon}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}
  \ForEach{\ac{BS} \me{b \in \mc{B}}}{
@@
  \label{algo-4}
-\end{algorithm}
-
-\subsubsection*{Convergence}
-The iterative method presented in Algorithm \ref{algo-4} converges to a stationary point at each iteration.
-Since the \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}} and the receive beamformers are updated together at each iteration, the convergence proof is not similar to the primal or the \ac{ADMM} methods.
-The convergence proof can be argued based on the monotonic increase of the objective function at each iteration as follows.
+\end{algorithm}\vspace{-0.1in}
+%\subsubsection*{Convergence}
+%The iterative method presented in Algorithm \ref{algo-4} converges to a stationary point at each iteration.
+Since the \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}} and the receive beamformers are updated together at each iteration, the convergence proof can be argued based on the monotonic increase in the objective function at each iteration.
+In order to illustrate the convergence, we adopt the following argument.
 The transmit precoders in \eqref{kkt-mse-4.3} improves the objective function after each update following the \ac{SCA} operating point \me{\tilde{\epsilon}_{l,k,n}} update \cite{marks1978technical}.
-Furthermore, the \ac{MMSE} receivers are globally optimal for the fixed transmit precoders \cite{christensen2008weighted,wmmse_shi}, the alternating beamformer updates improve the objective function monotonically in spite of having a subgradient update in \eqref{kkt-mse-4.1}.
-It is more suitable for the practical implementation due to the reduction in the signaling overhead and the iterations to converge.
+Furthermore, the \ac{MMSE} receivers are globally optimal for the fixed transmit precoders \cite{christensen2008weighted,wmmse_shi}, the alternating beamformer updates improve the objective function monotonically in spite of having a subgradient like update in \eqref{kkt-mse-4.1}.
 %presented in Algorithm \ref{algo-4} converges to a stationary point if the dual variables \me{\alpha_{l,k,n}} are allowed to converge or for fixed number of iterations \me{J_{\max}}.

### 2014-10-17 Report/mse_formulation.tex
updated draft with KKT distributed schemes

@@
 The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution.
-By reorganizing \eqref{eqn-mse-1.3}
+By reorganizing \eqref{eqn-mse-1.3} as
 \iftoggle{single_column}{
@@
 
-At each \ac{SCA} iteration, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem.
-Using the transmit precoders, the receive beamformers are obtained using the \ac{MMSE} receivers.
-The \ac{MMSE} receiver minimizes the objective value for the fixed transmit precoders, leading to the monotonic convergence of the objective function.
+At each \ac{SCA} update, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem.
+For a fixed transmit precoders, the \ac{MMSE} receiver improves the objective value \cite{christensen2008weighted,wmmse_shi}, leading to the monotonic convergence of the objective function.
 At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, and the objective value can either decrease or stays the same after each iteration.
+Note that the objective function improves at each iteration, whereas the sum rate need not follow the same behavior.

### 2014-10-17 Report/simulation_results.tex
updated draft with KKT distributed schemes

@@
 \subref*{fig-1} shows the performances of the centralized schemes for a single receive antenna system.
-It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRME} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
 The total number of queued packets for Fig.
@@
 \ref{fig-a}.
-The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets is small, as in Fig.
-\ref{fig-a}.
-In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation problem.
+The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets are few in number.
+In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation.
 It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}.
@@
 
-In both scenarios defined in Fig.
-\ref{fig-a}, \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the rate maximization algorithm.
-The performance degradation can be attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
+For both scenarios in Fig.
+\ref{fig-a}, the \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the algorithm.
+The performance loss is  attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
 Fig.

### 2014-10-19 Report/kkt_mse_approach.tex
update final draft

@@
 
-The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors.
-The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to have equal weights.
-The transmit precoders in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}.
+The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive beamformers \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors.
+The dual variable \me{\alpha}'s are initialized with ones to have equal priorities to the corresponding precoders.
+Using this, the transmit and the receive beamformers are evaluated using the expressions in \eqref{kkt-mse-4}.
+The transmit precoder in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by bisection method satisfying the total power constraint \eqref{kkt-mse-1.4}.
 Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}.
-Following approaches can be performed to decouple the precoder design problem with the limited signaling between the \acp{BS} in \me{\mathcal{B}}.
+As discussed in Section \ref{sec-4.1}, the \ac{KKT} expressions can be solved in a distributed manner using primal method with similar convergence behavior.
 
-As a first approach, in this method, for a fixed the receive beamformers, \me{\alpha_{l,k,n}} and the operating \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}}, each \ac{BS} evaluates the transmit precoder \me{\mvec{m}{l,k,n}^{(i)}} and exchange the total interference contribution by using the updated precoder to the neighboring \ac{BS} users.
-On receiving this information, each \ac{BS} will update \eqref{kkt-mse-4.4}, \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2}, and \eqref{kkt-mse-4.1}.
-For the fixed receive beamformer, the dual variables \me{\alpha_{l,k,n}} and the interference contributions are exchanged until convergence by finding the updated transmit precoders.
-Once the dual variables are converged, the receivers are updated by performing the downlink transmission.
-This procedure is iterated until convergence for a fixed \me{I_{\max}} iterations.
-The convergence is similar to the \ac{JSFRA} scheme with \ac{MSE} reformulation in Section \ref{sec-3.3}.
+We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the problem of minimizing the total number of backlogged packets.
+After receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user evaluates the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify them to the \acp{BS} via uplink precoded pilots.
+On receiving pilot signals, \acp{BS} update the \ac{MSE} as
+\begin{equation}
+\epsilon_{l,k,n}^{(i)} = \Re{ \lbrace 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \rbrace }.
+\end{equation}
+Using the current \ac{MSE}, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}.
+The updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.
+The \ac{SCA} operating point is also updated with the current \ac{MSE} value.
 
-The following approaches are similar to the decentralization methods proposed in \cite{komulainen2013effective} for the sum rate maximization problem.
-In the this approach, after receiving the transmitted signal with the recent precoders from all \acp{BS} in \me{\mathcal{B}}, the users evaluate the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify it to the \acp{BS} using the precoded uplink pilots.
-Upon receiving, each \ac{BS} estimates the \ac{MSE} using \me{\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}}.
-Using the updated \ac{MSE}, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}.
-The updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.
-
-Finally, in this approach, upon receiving the signal from all \acp{BS}, the users update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}.
-The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified the \acp{BS} using precoded uplink pilots with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{\bar{w}}{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
-On receiving the precoded uplink pilots, the \acp{BS} will use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
+In order to limit the back-haul exchanges between \acp{BS}, in this approach, users will perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users.
+Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}.
+The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{\bar{w}}{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
+On receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
 Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
+The proposed scheme in Algorithm \ref{algo-4} is of practical importance due to low signaling requirements.
+The convergence proof for the \ac{MSE}-\ac{KKT} schemes are difficult due to the joint update of \me{\mvec{w}{l,k,n}} and the \ac{SCA} update \me{\tilde{\epsilon}_{l,k,n}}.
+It is verified for various exponent values by using numerical simulations.
 \begin{algorithm}

### 2014-10-20 Report/kkt_mse_approach.tex
modified

@@
 Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}.
-As discussed in Section \ref{sec-4.1}, the \ac{KKT} expressions can be solved in a distributed manner using primal method with similar convergence behavior.
+The \ac{KKT} expressions can be solved in a distributed manner using primal decomposition technique with a similar convergence behavior as discussed in Section \ref{sec-4.1}.
 
@@
 The convergence proof for the \ac{MSE}-\ac{KKT} schemes are difficult due to the joint update of \me{\mvec{w}{l,k,n}} and the \ac{SCA} update \me{\tilde{\epsilon}_{l,k,n}}.
-It is verified for various exponent values by using numerical simulations.
+The convergence of the proposed algorithm is verified for different exponent values by using numerical simulations.
 \begin{algorithm}

### 2014-10-21 Report/kkt_mse_approach.tex
updated

--- 2014-10-19 Report/kkt_mse_approach.tex
@@
 Similar work has been considered for the \ac{WSRM} problem with the minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
-When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} includes a nonconvex constraint, which makes the problem difficult to solve due to the additional nonconvex maximum rate constraint \eqref{eqn-3.1.4} for the \ac{WSRM} problem.
+Since the objective of the problem is to minimize the total number of queued packets, the \ac{WSRM} problem requires an additional maximum rate constraint to avoid the over-allocation problem.
+This makes the problem difficult to solve due to the nonconvex maximum rate constraint \eqref{eqn-3.1.4} for the \ac{WSRM} problem.
 
@@
 At each iteration, the dual variables \me{\alpha^{(i)}} are updated linearly from the earlier \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}.
-When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
+When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be zero thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
 Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}}.
@@
 The dual variable \me{\alpha}'s are initialized with ones to have equal priorities to the corresponding precoders.
-Using this, the transmit and the receive beamformers are evaluated using the expressions in \eqref{kkt-mse-4}.
-The transmit precoder in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by bisection method satisfying the total power constraint \eqref{kkt-mse-1.4}.
+Then the transmit and the receive beamformers are evaluated using the expressions in \eqref{kkt-mse-4}.
+The transmit precoder in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by bisection search satisfying the total power constraint \eqref{kkt-mse-1.4}.
 Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}.
-As discussed in Section \ref{sec-4.1}, the \ac{KKT} expressions can be solved in a distributed manner using primal method with similar convergence behavior.
+The \ac{KKT} expressions can be decentralized using primal decomposition technique and it follows similar convergence proof as the centralized scheme in Section \ref{sec-3.3}.
 
-We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the problem of minimizing the total number of backlogged packets.
+To devise an algorithm for a practical implementation, we extend the decentralization methods discussed in \cite{komulainen2013effective}, for our problem of minimizing the total number of backlogged packets as follows.
 After receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user evaluates the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify them to the \acp{BS} via uplink precoded pilots.
-On receiving pilot signals, \acp{BS} update the \ac{MSE} as
+On receiving pilot signals, \acp{BS} update the \ac{MSE} in \eqref{mse-error} as
 \begin{equation}
-\epsilon_{l,k,n}^{(i)} = \Re{ \lbrace 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \rbrace }.
+\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}.
 \end{equation}
-Using the current \ac{MSE}, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}.
-The updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.
+Using the current \ac{MSE} value, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}, and the updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.
 The \ac{SCA} operating point is also updated with the current \ac{MSE} value.
 
-In order to limit the back-haul exchanges between \acp{BS}, in this approach, users will perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users.
+To avoid the back-haul exchanges between \acp{BS}, as an alternative approach, users may perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users.
 Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}.
-The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{\bar{w}}{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
-On receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
-Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
-The proposed scheme in Algorithm \ref{algo-4} is of practical importance due to low signaling requirements.
-The convergence proof for the \ac{MSE}-\ac{KKT} schemes are difficult due to the joint update of \me{\mvec{w}{l,k,n}} and the \ac{SCA} update \me{\tilde{\epsilon}_{l,k,n}}.
-It is verified for various exponent values by using numerical simulations.
+The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
+On receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
+Finally, Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
+The proposed scheme is of practical importance due to low signaling requirements.
+The rigorous convergence proof is similar to the \ac{WMMSE} scheme discussed in  \cite{christensen2008weighted,wmmse_shi} for the \ac{MSE} minimization objective.
+The convergence is verified for different exponent values by numerical simulations.
 \begin{algorithm}

### 2014-10-23 Report/ieee_journal.tex
update final draft
updated

@@
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
-	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
+	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
+Part of this work has been published in ICASSP 2014 conference.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
+	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
 
@@
 
-\subsection{Decomposition based Approaches}
+\subsection{Decomposition based Approaches} \label{sec-4a}
 
@@
 
-\subsection{Decomposition Using \ac{KKT} Equations in \ac{MSE} Formulation} \label{sec-4.3}
+\subsection{Decomposition via \ac{KKT} Conditions for \ac{MSE} Formulation} \label{sec-4.3}
 

### 2014-10-23 Report/kkt_mse_approach.tex
updated

@@
-The distributed solutions via primal and \ac{ADMM} approaches depend on the subgradient update by using a step size parameter for the coupling variables.
-It affects the speed of convergence to the optimal value.
-In this method, we provide an alternative approach to decentralize the \ac{MSE} equivalent problem considered in \cite{christensen2008weighted,wmmse_shi} by directly solving the \ac{KKT} conditions.
-Similar work has been considered for the \ac{WSRM} problem with the minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
-Since the objective of the problem is to minimize the total number of queued packets, the \ac{WSRM} problem requires an additional maximum rate constraint to avoid the over-allocation problem.
-This makes the problem difficult to solve due to the nonconvex maximum rate constraint \eqref{eqn-3.1.4} for the \ac{WSRM} problem.
+In this section, we discuss different ways to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}.
+In contrast to Section \ref{sec-4a}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
+The proposed methods in this section provide algorithms that can be of practical importance due to the limited signaling requirements.
+Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
+Since the formulation in \cite{kaleva2013decentralized,kaleva2013primal} are similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
 
-Even though the rate constraints are implicitly present in the objective function, we cannot formulate the \ac{KKT} conditions readily due to the non-differentiable objective function.
-The non-differentiability is due to the absolute operator present in the norm function.
-In order to make the objective function differentiable, we consider the following case for which the absolute operator can be ignored without affecting the optimal solution, namely,
+In the proposed \ac{JSFRA} formulation, the maximum rate constraints are implicitly handled by the objective function without the need of explicit constraints.
+However, the \ac{KKT} conditions cannot be formulated due to the non-differential objective function.
+The non-differentiability is due to the absolute value operator present in the norm function.
+In order to make the objective function differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the optimal solution, namely,
 \begin{itemize}
@@
 
-The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables as shown in the Appendix \ref{a-1}.
+The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}.
 Upon solving, we obtain the iterative solution as
@@
 At each iteration, the dual variables \me{\alpha^{(i)}} are updated linearly from the earlier \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}.
-When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be zero thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
+When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
 Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}}.
@@
 The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive beamformers \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors.
-The dual variable \me{\alpha}'s are initialized with ones to have equal priorities to the corresponding precoders.
+The dual variable \me{\alpha}'s are initialized with ones to have equal priorities to all the users in the system.
 Then the transmit and the receive beamformers are evaluated using the expressions in \eqref{kkt-mse-4}.
 The transmit precoder in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by bisection search satisfying the total power constraint \eqref{kkt-mse-1.4}.
-Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}.
-The \ac{KKT} expressions can be decentralized using primal decomposition technique and it follows similar convergence proof as the centralized scheme in Section \ref{sec-3.3}.
+Note that the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}, which is considered in the expression \eqref{kkt-mse-4}.
 
@@
 Finally, Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
-The proposed scheme is of practical importance due to low signaling requirements.
-The rigorous convergence proof is similar to the \ac{WMMSE} scheme discussed in  \cite{christensen2008weighted,wmmse_shi} for the \ac{MSE} minimization objective.
-The convergence is verified for different exponent values by numerical simulations.
 \begin{algorithm}

### 2014-10-23 Report/conclusions.tex
final_submission_text

--- 2014-10-01 Report/conclusions.tex
@@
-In this paper, we addressed the allocation of space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{OFDM} system.
-The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user can be achieved by a non-zero precoding vector.
-We proposed the \ac{JSFRA} scheme by adopting the \ac{SCA} technique to model the nonconvex constraint as a sequence of convex subsets to design the precoders for minimizing the number of queued packets.
-Additionally, an alternative approach using \ac{MSE} relaxation is also proposed with the same objective by fixing the receivers based on \ac{MSE} minimization.
-We also proposed the distributed solutions for the centralized \ac{JSFRA} problem using \ac{ADMM} and primal decomposition methods.
-Finally, we proposed an iterative algorithm to determine the precoders in a decentralized manner based on the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme.
-Numerical results shows that the proposed algorithms perform better than the existing approaches.
+In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM} transmission.
+The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector.
+We proposed the \ac{JSFRA} scheme by adopting the \ac{SCA} technique to model the nonconvex constraint by a sequence of convex subsets to design the precoders for minimizing the total number of queued packets in the system.
+In addition to that, an alternative method using \ac{MSE} relaxation is also proposed using the same objective by fixing the receivers based on the \ac{MMSE} criterion.
+Then we proposed distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
+At last, we proposed a practical iterative algorithm to evaluate the precoders in a decentralized manner by solving the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme.
+The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the precoders to minimize the total number of backlogged packets.
+Numerical results are used to compare the performance of the proposed algorithms with the existing solutions.

### 2014-10-23 Report/introduction.tex
final_submission_text

@@
 
-In this paper, we consider the problem of precoder design across the space-frequency resources to minimize the total number of queued packets waiting in all \acp{BS}.
-For this highly nonconvex problem, we first propose two centralized methods.
-In the first method, we relax the nonconvex constraint by the first order Taylor approximation around an operating point, which is updated in an iterative manner until convergence or to a certain accuracy.
-In the second method, we reformulate the \ac{JSFRA} problem using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders.
-For a distributed implementation, we further propose decentralized approaches based on primal and \ac{ADMM} schemes to identify the precoders independently across the \acp{BS} by exchanging limited information via back-haul.
-We also propose an iterative algorithm by solving the \ac{KKT} equations, which can be implemented efficiently in a distributed manner.
+\subsubsection*{Main Contributions}
+In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}.
+Since the problem is nonconvex, we adopt the \ac{SCA} technique to solve by a sequence of convex subproblems using first order approximations.
+Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints.
+First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders.
+Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods.
+Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.
 

### 2014-10-23 Report/kkt_mse_approach.tex
final_submission_text

@@
 
-The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which is obtained by taking the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}.
+The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which are obtained by the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}.
 Upon solving, we obtain the iterative solution as

### 2014-10-24 Report/conclusions.tex
final version

@@
 The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector.
-We proposed the \ac{JSFRA} scheme by adopting the \ac{SCA} technique to model the nonconvex constraint by a sequence of convex subsets to design the precoders for minimizing the total number of queued packets in the system.
-In addition to that, an alternative method using \ac{MSE} relaxation is also proposed using the same objective by fixing the receivers based on the \ac{MMSE} criterion.
-Then we proposed distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
-At last, we proposed a practical iterative algorithm to evaluate the precoders in a decentralized manner by solving the \ac{KKT} conditions for the \ac{MSE} reformulated \ac{JSFRA} scheme.
-The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the precoders to minimize the total number of backlogged packets.
+We proposed the \ac{JSFRA} scheme by employing the \ac{SCA} technique to relax the nonconvex constraint by a sequence of convex subsets for designing the precoders to minimize the total number of user queued packets.
+Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using \ac{SCA} technique to address the nonconvex constraints for a fixed \ac{MMSE} receivers.
+We then introduced distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
+Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method.
+The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations.
 Numerical results are used to compare the performance of the proposed algorithms with the existing solutions.

### 2014-10-24 Report/decomposition_solutions.tex
Submitted version

@@
 This section addresses the distributed precoder designs for the proposed \ac{JSFRA} scheme.
-The formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
-In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are considered.
-In particular, the \acl{PD} and the \ac{ADMM} based \acl{DD} approaches are addressed.
+The formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the \acp{BS} in \me{\mc{B}}.
+In order to design the precoders independently at each \ac{BS} with the minimal information exchange via back-haul, iterative decentralization methods are considered.
+In particular, the \acl{PD} and the \ac{ADMM} which is basically based on \acl{DD} approaches are followed in this paper.
 
 To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-In order to study the decomposition based solutions, we consider the solution proposed in \eqref{eqn-9}, which is based on the Taylor series approximation for the nonconvex constraint.
+To facilitate decomposition based solutions, we consider the solution proposed in \eqref{eqn-9}, which is based on the Taylor series approximation for the nonconvex constraint.
 The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well.

### 2014-10-24 Report/ieee_journal.tex
final_submission_text
final version
Submitted version

@@
-\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[11pt,draftcls,onecolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
-Part of this work has been published in ICASSP 2014 conference.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
-	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
+	\IEEEauthorblockN{Ganesh Venkatraman\IEEEauthorrefmark{1} \thanks{This work is supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
+Part of this work has been published in ICASSP 2014 conference.} \IEEEmembership{Student Member,~IEEE}, Antti T\"{o}lli\IEEEauthorrefmark{1} \IEEEmembership{Member,~IEEE}, Le-Nam Tran\IEEEauthorrefmark{2} \thanks{\IEEEauthorrefmark{2}Dr.
+L.-N.
+Tran is associated with the Department of Electronic Engineering, Maynooth University, Co.
+Kildare, Irealand, e-mail:ltran@eeng.nuim.ie} \IEEEmembership{Member,~IEEE}, and Markku Juntti\IEEEauthorrefmark{1} \IEEEmembership{Senior Member,~IEEE}}\thanks{\IEEEauthorrefmark{1}The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi).}}
 
@@
 \begin{IEEEkeywords}
-\ac{MIMO}-\ac{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
+convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \ac{WSRM}.
 \end{IEEEkeywords}
@@
 
-\acresetall
+%acresetall
 \section{Conclusions} \label{sec-6}

### 2014-10-24 Report/introduction.tex
Submitted version

@@
 
-In a network with multiple \acp{BS} serving \acp{MU}, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
+In a network with multiple \acp{BS} serving \acp{MU}, the main driving factor for downlink transmission is the number of  packets waiting at each \ac{BS} corresponding to the different users present in the network.
 These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints.
 We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets.
-Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.
+Since the space-frequency resources are shared by multiple users in different \acp{BS}, it can be viewed as a resource allocation problem.
 
-In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence in a particular resource \cite{admission_control}.
-In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource.
+In general, the resource allocation problems are formulated by assigning a binary variable for each user to indicate whether the user is allocated to a particular resource \cite{admission_control}.
+In this paper, we follow a different approach in which linear transmit precoders are used as decision variables.
 The purpose is two-fold.
-Firstly, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.
+Firstly, it determines the transmission rate on a particular resource.
+Secondly, in certain resource, if the transmit precoder of a user turns out to be a zero vector after solving the design problem, the corresponding user will not be scheduled.
 
@@
 In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients.
-In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders.
+In this way, the original problem is expressed in terms of the \ac{MSE} weights, precoders, and decoders.
 Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the remaining others are fixed.
@@
 
-The problem of precoder design for the \ac{MIMO} \ac{IBC} system are solved either by using a centralized controller or by using decentralized algorithms where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with the other \acp{BS} via back-haul.
+The problem of precoder design for the \ac{MIMO} \ac{IBC} system is solved either by using a centralized controller or by using decentralized algorithms where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with the other \acp{BS} via back-haul.
 The distributed approaches are based on primal, dual or \ac{ADMM} decomposition, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}.
@@
 
-By adjusting the weights in the \ac{WSRM} objective properly, we can find an arbitrary rate-tuple in the rate region that maximizes the suitable objective measures.
-For example, if the weight of each user is set to be inversely proportional to its average data rate, the corresponding problem guarantees fairness on an average among the users.
-As an approximation, we may assign weights based on the current queue size of the users.
-More specifically, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}.
+By adjusting the weights in the \ac{WSRM} problem properly, we can find a rate-tuple in the rate region that maximizes a performance measure of interest.
+For example, if the weights of each user is set to be inversely proportional to user's average data rate, the problem guarantees fairness on average achieved rate among the users.
+As an approximation to our considered problem, we may assign weights based on the current queue size of the users.
+More specifically, the queue states can be incorporated to the traditional \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a related function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}.
 In backpressure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
@@
 \subsubsection*{Main Contributions}
-In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}.
+In this paper, we design the precoders jointly across space-frequency resources to minimize the total number of backlogged packets waiting at the \acp{BS}.
 Since the problem is nonconvex, we adopt the \ac{SCA} technique to solve by a sequence of convex subproblems using first order approximations.
-Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints.
-First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders.
-Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods.
-Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.
+First, we propose two centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints.
+The first method is based on applying the \ac{SCA} technique to the nonconvex constraints of the problem formulation directly, while the second one applies \ac{SCA} technique to the equivalent formulation obtained by the \ac{MSE} equivalence.
+In the second part, we propose a distributed precoder designs based on the primal and the \ac{ADMM}.
+Finally, we propose an iterative algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.
 

### 2014-10-24 Report/joint_wsrm_formulation.tex
Submitted version

@@
 It determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes.
-Even though the algorithm is primarily designed for the wired infrastructure, it can be extended to the wireless networks by designing the user rate variable \me{t_k} in accordance to the wireless network.
+Even though the algorithm is primarily designed for wired infrastructures, it can be extended to wireless networks by designing the user rate variable \me{t_k} in accordance to wireless networks.
 
@@
 The expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the number of backlogged packets corresponding to the users.
-The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
+The above discussed approach was extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
 Since the expectation can be minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
@@
 where the precoders are associated with \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}.
-By using the number of queued packets as the weights, the resources can be allocated to the user with the more backlogged packets, which essentially does the allocation in a greedy manner.
+By using the number of queued packets as the weights, the resources can be allocated to users with more backlogged packets, which essentially a greedy resource allocation scheme.
 
-As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}.
+As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} to be unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}.
 This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison to the number of queued packets as in \ac{Q-WSRME}.
-Note that in both formulations, the resources allocated to the users are limited by the number of backlogged packets with an explicit maximum rate constraint defined by \eqref{eqn-3.1.4}.
+Note that in both formulations, the resources allocated to the users are limited by the number of backlogged packets with an explicit maximum rate constraint given in \eqref{eqn-3.1.4}.

### 2014-10-24 Report/kkt_mse_approach.tex
Submitted version

@@
 
-The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which are obtained by the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}.
+The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which are obtained by the derivative of the Lagrangian function w.r.t the primal variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}.
 Upon solving, we obtain the iterative solution as
@@
 
-To devise an algorithm for a practical implementation, we extend the decentralization methods discussed in \cite{komulainen2013effective}, for our problem of minimizing the total number of backlogged packets as follows.
+To devise an algorithm for a more practical implementation, we extend the decentralization methods discussed in \cite{komulainen2013effective}, for our problem of minimizing the total number of backlogged packets as follows.
 After receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user evaluates the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify them to the \acp{BS} via uplink precoded pilots.

### 2014-10-24 Report/mse_formulation.tex
Submitted version

@@
-In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{viswanath1999optimal,mse_duality}.
+In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for \ac{MMSE} receivers \cite{viswanath1999optimal,mse_duality}.
 The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by

### 2014-10-24 Report/problem_formulation_intro.tex
Submitted version

@@
 \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with user \me{k} for \me{n^\mathrm{th}} sub-channel, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
 In \eqref{eqn-4.3}, we consider a \ac{BS} specific sum power constraint for each \ac{BS} across all sub-channels.
@@
 
-Before proceeding further, we show that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of norm \me{\ell_q} in the objective of \eqref{eqn-3}.
+Before proceeding further, we show that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of \me{\ell_q} norm in the objective of \eqref{eqn-3}.
 Suppose that \me{t_k>Q_k} for certain \me{k} at the optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
@@
 Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that the optimal solution has been obtained.
-The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as follows
+The choice of the \me{\ell_q} norm used in the objective function \cite{berry2004cross,qps_cioffi} has different effects on the priorities for the queue deviation function as follows
 \begin{itemize}
-\item \me{\ell_{1}} results in greedy allocation \textit{i.e}, emptying the queue of users with good channel conditions before considering the users with worse channel conditions.
-As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
-\item \me{\ell_{2}} prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
+\item the \me{\ell_{1}} norm results in greedy allocation \textit{i.e}, emptying the queue of users with good channel conditions before considering the users with worse channel conditions.
+As a special case, it can be seen that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
+\item the \me{\ell_{2}} norm prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
 For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
-\item \(\ell_{\infty} \) minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
+\item the \(\ell_{\infty} \) norm minimize the maximum queue deviation in each transmission instant by allocating the resources proportional to the number of backlogged packets.
+The queue deviation of all users will be the same after each allocation instant, irrespective of the user channel gains.
 \end{itemize}

### 2014-10-24 Report/queue_minimizing_intro.tex
Submitted version

@@
 
-In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is highly difficult due to the combinatorial and the nonconvex nature of the problem.
-In addition, the objective of minimizing the number of the queued packets over the spatial and the sub-channel dimensions adds further complexity to the existing problem.
-Since the scheduling of users in each sub-channel can be made by allocating zero transmit power over certain sub-channels, our solutions perform joint precoder design and user scheduling.
+In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is difficult due to the combinatorial and the nonconvex nature of the problem.
+In addition, the objective of minimizing the number of the queued packets over space-frequency dimensions adds further complexity to the existing problem.
+Since the scheduling of users in each space-frequency resource can be controlled by the transmit precoders, our solutions perform precoder design and user scheduling jointly.
 Before discussing the proposed solutions, we consider the existing algorithm to minimize the number of backlogged packets with additional constraints required by the problem.

### 2014-10-24 Report/sub_channel_wsrm.tex
Submitted version

@@
 In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size.
-In order to mitigate the problem, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
+In order to address these issues, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
 The optimal approach is to decompose the problem over each sub-channel with a fixed transmit power constraint for each sub-channel.

### 2014-10-24 Report/system_model.tex
Submitted version

@@
 Data for user \me{k} is transmitted from only one \ac{BS} which is denoted by \me{b_k\in \mathcal{B}}.
-We denote by \me{\mathcal{N} = \set{1,2,\dotsc,N}} the set of all sub-channel indices available in the system.
+Let \me{\mathcal{N} = \set{1,2,\dotsc,N}} be the set of all sub-channel indices present in the system.
 
@@
 Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted.
-In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user.
+In order to detect  multiple spatial streams at the user terminal, receive beamformer \me{\mvec{w}{l,k,n}} is employed for each user.
 Consequently, the received data symbol estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
@@
 
-Let \me{Q_k} be the number of backlogged packets destined for the user \me{k} at a given scheduling instant.
-The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for the user \me{k} at the \me{{i}^\mathrm{th}} time instant\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar}.
-The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, denoted as \me{Q_k(i+1)}, is given by
+Let \me{Q_k} be the number of backlogged packets destined for user \me{k} at a given scheduling instant.
+The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{{i}^\mathrm{th}} time instant\footnote{The unit can be either packets or bits as long as the arrival and the transmission units are similar}.
+The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for user \me{k}, denoted as \me{Q_k(i+1)}, is given by
 \begin{equation}
@@
 where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the number of transmitted packets or bits for user \me{k}.
-At the \me{\ith{i}} instant, transmission rate of the user \me{k} is given by
+At the \me{\ith{i}} instant, transmission rate of user \me{k} is given by
 \begin{equation}
@@
 The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} of \me{\gamma_{l,k,n}}\footnote{Upper bound is achieved by using Gaussian signaling}.
-Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.
+Note that the units of \me{t_k} and \me{Q_k} are in bits per channel use.

### 2014-10-24 Report/wsrm_formulation.tex
updated final with kkt conditions
Submitted version

--- 2014-10-09 Report/wsrm_formulation.tex
@@
 However, this step leads to the same solution without loss of optimality, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}.
-Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}.
-Similar to the \ac{WSRM} problem in \cite{tran2012fast}, the problem can be shown to be NP-hard even for the single antenna case.
+Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the optimization variable \me{\beta_{l,k,n}}.
+
+Similar to the \ac{WSRM} problem in \cite{tran2012fast}, the proposed formulation in \eqref{eqn-6} can be shown to be NP-hard even for the single antenna case.
 The reformulation in \eqref{eqn-6} allows a tractable solution as presented below.
@@
 Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
-Recall that the original coordinate descent method assumes that the optimization variables belong to disjoint sets (Cartesian product of sets, to be precise) \cite{xu2013block}.
+Recall that the coordinate descent method assumes that the optimization variables belong to disjoint sets and the problem must be convex for a given set of variables while keeping other variables fixed as discussed in \cite{xu2013block}.
 
@@
 }
+
 \subsubsection*{Convergence}
-
 In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}

### 2015-01-19 Report/convergence_centralized.tex
revision_changes

--- 2014-10-10 Report/wsrm_formulation.tex
@@
-In this approach, we present an algorithm to solve \eqref{eqn-3} to obtain the transmit precoders in a centralized manner by using the idea of alternating optimization and successive convex approximation.
-Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
-\iftoggle{single_column}{
-\begin{IEEEeqnarray}{CCl}\label{eqn-6}
-\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
-\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \label{eqn-6.2} \\
-  & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
-  & \quad & \text{and } \eqref{eqn-4.3}, \IEEEyessubnumber
-\end{IEEEeqnarray}
-}{\allowdisplaybreaks
-\begin{IEEEeqnarray}{CCl}\label{eqn-6}
-	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
-	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
-	&\quad& \beta_{l,k,n} \geq \tilde{N}_0 + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
-	&\quad& \text{and } \eqref{eqn-4.3}, \IEEEyessubnumber
-\end{IEEEeqnarray}
-}
-where \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation and \me{\tilde{N}_0 = N_0\|\mvec{w}{l,k,n}\|^2} be the effective noise variance.
-In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-However, this step leads to the same solution without loss of optimality, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}.
-Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}.
-Similar to the \ac{WSRM} problem in \cite{tran2012fast}, the problem can be shown to be NP-hard even for the single antenna case.
-The reformulation in \eqref{eqn-6} allows a tractable solution as presented below.
-First, we note that the constraints \eqref{eqn-4.3} are convex with involved variables.
-Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
-Recall that the coordinate descent method assumes that the optimization variables belong to disjoint sets and the problem is convex for a variable while all other variables are fixed \cite{xu2013block}.
-
-By fixing the receivers, the problem now is to find the optimal transmit beamformers for a given set of linear receivers which is still a challenging task.
-We note that for fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
-Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}.
-To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by a series of convex constraints.
-Note that function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure.
-Since \me{f(\tilde{\mbf{u}}_{l,k,n})} is convex, a concave approximation of \eqref{eqn-6.2} can be easily found by considering the first order approximation of \me{f(\tilde{\mbf{u}}_{l,k,n})} around the current operation point.
-For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
-\begin{subeqnarray} \label{eqn-wsrm-expr}
-p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \\
-q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}
-\end{subeqnarray}
-and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
-In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier}.
-Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively.
-Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint as
-\iftoggle{single_column}{
-\begin{equation}\label{eqn-8}
-	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
-\end{equation}
-}{
-\begin{multline}\label{eqn-8}
-2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) \\
-+ \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
-\end{multline}
-}
-In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
-\begin{IEEEeqnarray}{CCl}\label{eqn-9}
-\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},,\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
-& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
-& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
-\end{IEEEeqnarray}
-
-Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} with respect to \me{\mbf{w}_{l,k,n}} as
-\begin{IEEEeqnarray}{CCl}\label{eqn-9--1}
-\underset{\substack{\gamma_{l,k,n},\mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
-\text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}.
-\end{IEEEeqnarray}
-Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mvec{w}{l,k,n}} as
-\begin{IEEEeqnarray}{rCl}
-\mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}, \IEEEyessubnumber \eqspace \label{opt-rx}
-\end{IEEEeqnarray}
-where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the earlier iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
-Note that \eqref{opt-rx} is obtained by iterating over the fixed \me{\mvec{w}{l,k,n}^{(i-1)}} at each \ac{SCA} iteration until convergence or for fixed number of iterations.
-It can be seen that the optimal receiver expression in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
-\begin{IEEEeqnarray}{rCl}
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
-\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
-\end{IEEEeqnarray}
-
-The proposed algorithm is referred to as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint, and it is outlined in Algorithm \ref{algo-1}.
-The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
-Instead of initializing \me{\tilde{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{\tilde{\mbf{u}}_{l,k,n}} in an efficient manner as briefed in Algorithm \ref{algo-1}.
-For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for the predefined iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
-Next, the receive beamformers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
-This procedure is carried out until convergence of the queue deviation or for fixed number of iterations by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
-{\allowdisplaybreaks
-\begin{algorithm}
- \SetAlgoLined
- \DontPrintSemicolon
- \BlankLine
- \SetKwInput{KwInit}{Initialize}
- \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
- \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{M}}_{k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
- update \me{\mvec{W}{k,n}} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} using \me{\tilde{\mbf{M}}_{k,n}}\;
- \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
- initialize \me{j = 0}\;
- \Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
- solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
- update the constraint set \eqref{eqn-8} with \me{\tilde{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
- $j = j + 1$\;
- }
- update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
- $i = i + 1$\;
- }
- \caption{Algorithm of \acs{JSFRA} scheme}
- \label{algo-1}
-\end{algorithm}
-}
-\subsubsection*{Convergence}
-
 In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}
@@
 The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, and hence the proposed \ac{JSFRA} scheme is guaranteed to converge to a stationary point of the original nonconvex problem.
+
+Following similar approach as in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem.
+The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution.
+By reorganizing \eqref{eqn-mse-1.3} as
+\iftoggle{single_column}{
+	\begin{equation}
+		\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
+	\end{equation}
+}{
+\begin{multline}
+\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
++ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
+\end{multline}
+}
+we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are eliminated by the presence of real component in the \ac{MSE} expression.
+
+At each \ac{SCA} update, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem.
+For a fixed transmit precoders, the \ac{MMSE} receiver improves the objective value \cite{christensen2008weighted,wmmse_shi}, leading to the monotonic convergence of the objective function.
+At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, and the objective value can either decrease or stays the same after each iteration.
+Note that the objective function improves at each iteration, whereas the sum rate need not follow the same behavior.

### 2015-01-19 Report/ieee_journal.tex
revision_changes

--- 2014-10-23 Report/ieee_journal.tex
@@
-\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,final,onecolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 \usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno}
+\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno,verbatim,todonotes,inputenc}
 
@@
 
+\section{Response to reviewer comments}
+\input{review_comments}
+
 \maketitle
@@
 \begin{IEEEkeywords}
-\ac{MIMO}-\ac{OFDM}, Queue minimizing precoder design, \acs{SCA}, Convex approximation.
+Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, Precoder design, \acs{SCA}, \ac{WSRM}.
 \end{IEEEkeywords}
@@
 \input{sub_channel_wsrm}
+
+\subsection{Convergence Analysis} \label{sec-3.5}
+\input{convergence_centralized}
 

### 2015-01-19 Report/introduction.tex
revision_changes

--- 2014-10-23 Report/introduction.tex
@@
 In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence in a particular resource \cite{admission_control}.
-In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource.
+In contrast to that, we use linear transmit precoders, which are the complex vectors, \review{implicitly} as a decision variable in determining the presence or the absence of a user on a particular resource.
 The purpose is two-fold.

### 2015-01-19 Report/review_comments.tex
revision_changes

\subsection{Reveiwer Comments - \me{1}}

In this paper, the authors proposed a traffic aware resource allocation scheme for multi-cell MIMO-OFDM systems, where the precoders at all BSs are chosen to minimize the total user queue deviations. The problem is nonconvex and the authors proposed two centralized algorithms based on the successive approximation (SCA) technique to find a stationary point. Moreover, several distributed algorithms are also proposed using primal decomposition, alternating directions method of multipliers (ADMM), and decomposition via KKT conditions, respectively.

Most sections of this paper are well written. The results and algorithms also seem valid. However, the motivation of minimizing the total user queue deviations is not well justified. The convergence results of some algorithms are not clearly presented. The presentation of the distributed solutions needs significant improvement. Analysis and comparison of the signaling overhead and computational complexity between the centralized and distributed algorithms are also necessary to justify the advantages of distributed algorithms.

\resp We thank the reviewer for reading the paper and providing the comments. Please consider the responses in line with the comments.

\subsection*{Detailed Comments}  
\cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6). For example, the Queue weighted sum rate maximization (Q-WSRM) is throughput optimal, i.e., if there exists a scheme which can make all queues stable, then the Q-WSRM can also do this. How about the proposed formulation in (6)? Is it also throughput optimal?

\resp We fully agree with the reviewer comment. The Q-WSRM scheme is throughput optimal when the queues associated with the users are significantly large in comparison with the transmission rate (service rate). In order to restrict the over allocation of the available resources to a specific user beyond the total number of queued packets, we have included the additional rate constraint in the Q-WSRME algorithm. It would be ideal to compare with the Q-WSRME algorithm which performs similar to the Q-WSRM when the queued packets are large enough to be emptied by the current transmissions. Fig. \ref{fig-review} compares the centralized algorithms using average number of backlogged packets after \me{100} slots of transmission for different arrival rate. Note that the average arrival rate of all the users are same but the instantaneous arrivals are based on the Poisson distribution. It can be seen from Fig. \ref{fig-review} that the JSFRA scheme with \me{q=2} performs similar to the Q-WSRME scheme for higher arrival rates, which explains the dropping of the squared rate term in the Q-WSRM formulation. When the average arrival rate is smaller, the JSFRA scheme with \me{q=2} performs noticeably better than the Q-WSRME scheme as can be seen from the average number of backlogged packets. In all packet arrival scenarios, JSFRA scheme with \me{q=1} reduces the average number of backlogged packets over the given slots is lesser than the Q-WSRME scheme.
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{Review/reviewer.eps}
\label{fig-review}
\caption{System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
\end{figure}

\cmnt{2} Do the proposed solutions based on (6) achieve better average delay performance than the existing solutions? By the way, in the simulations, you should also add a figure comparing the average delay performance, instead of just comparing the performance metric defined by (6). This will better justify the advantage of the proposed solutions.

\resp We agree with the reviewer comment on the better average delay performance of Q-WSRM(E) approach over JSFRA scheme with \me{q=1} formulation. Note that the average delay can be reduced by including a convex minimum rate constraint in the JSFRA formulation to provide a guaranteed rate to all users or for certain users in the system. More over, the priority can also be incorporated easily in the formulation by the scaling factor \me{a_k} used in the formulation. As mentioned in Section \ref{sec-3.2}, the delay can also be addressed by using \me{q=2} or \me{q=\infty} norm objective in the JSFRA formulation.

\cmnt{3} In Section III.B, the convergence conditions under Algorithm 1 are not clear. First, you should be more specific about what is the SCA subproblem. Do you mean problem (19)? Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?

\resp We understand the reviewer concerns. We have modified the convergence section to include additional information to provide more clarity. \review{Update converge proof}

### 2015-01-19 Report/review_comments.tex
test_2

@@
 \resp We understand the reviewer concerns. We have modified the convergence section to include additional information to provide more clarity. \review{Update converge proof}
+
+\cmnt{4} It is better to clearly summarize the convergence conditions and results (i.e., does it converge to a stationary point or the optimal solution) for all algorithms in a theorem/proposition.
+
+\resp We agree with the reviewers view. We have updated the convergence proof to include the discussions on the stationary point and the optimal point.
+
+\cmnt{5} At the end of Section III, you mentioned that the proposed reduced complexity resource allocation scheme is sensitive to the order in which the subchannels are selected for the optimization problem.
+Please provide a discussion how to choose this order.
+
+\resp We thank the reviewer for the raising the concern on the selection order. We have elaborated the discussion on the sub-channel wise selection scheme. \review{discuss on selection}
+
+\cmnt{6} In the distributed algorithms, it is not clear what exact information is exchanged between the BSs or between the BSs and users.
+Moreover, the signaling overhead should be analyzed and compared with the centralized solution.
+The proposed distributed algorithms require exchanging over-the-air signaling or backhaul signaling for many times within each channel coherent time (e.g., from Fig.
+2, the distributed algorithm requires 20-30 iterations to converge even when there are only 3 subchannels).
+I don’t think this is acceptable in practice.
+Is the signaling overhead of the distributed algorithm really smaller than the centralized algorithm which only requires exchange the CSI between the BSs for once within each channel coherent time?
+
+\resp We thank the reviewer for the insightful comment on the practicality of the distributed algorithm.
+We fully agree with the reviewer comment on the information exchange between the BSs in the distributed approach.
+Please note that the proposed distributed algorithm based on the primal or dual decomposition is provided for the completeness purpose.
+Note that the distributed approach is performed for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution.
+In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which is not the stationary point when the algorithm is allowed to converge.
+In section \ref{sec-4.3}, we have discussed a practical approach based on the KKT conditions, which attains a sub-optimal point with few number of iterations.
+
+\cmnt{7} The convergence analysis of the distributed algorithms is not clear.
+For example, what is the exact condition to ensure the convergence of the distributed algorithms.
+Does the distributed algorithms also converge to a stationary point?
+
+\resp We understand the reviewers concern.
+We have update the text on the convergence of the distributed algorithm (ADMM).
+Please not that the ADMM or the primal decomposition algorithm is used for the convex subproblem only.
+If the distributed algorithm is iterated until convergence, it is guaranteed to attain the same stationary point as that of the centralized algorithm \cite{boyd2011distributed}.
+
+\cmnt{8} I’m totally confused with the ADMM approach in Section IV.A.
+Many notations, such as the local interference vector and consensus interference vector are used without formal definition.
+What is the difference between the local interference vector and consensus interference vector?
+What are their relationships with the actual interference vector.
+It seems that you are using the same notation for all of these interference vectors and I can’t tell when a notation refers to a local interference vector, a consensus interference vector, or the actual interference vector.
+These questions should be clarified and perhaps you should choose the notation system more carefully.
+For example, in (36), there are 3 similar notations and I don’t know which one is local interference vector and which one is the actual interference vector.
+
+\resp We understand the concern of the reviewer. We have updated the distributed section to include all the details pointed by the reviewer.
+
+\cmnt{9} In the distributed algorithms, it is not clear what information is available at each node.
+For example, what are your assumption on CSIT (CSI knowledge at each BS) and CSIR (CSI knowledge at each user)?
+How to 2 obtain the information used to perform the required calculation at each node (such as calculating the actual interference, MMSE receiver and the dual variables)?
+
+\resp We understand the concern of the reviewer. We have updated the distributed section to include all the details pointed by the reviewer.
+
+\cmnt{10} Do you have any convergence result for the proposed distributed solution based on the KKT conditions in Section IV.B?
+It seems that the iterative method to solve the KKT conditions is totally heuristic.
+
+\resp We fully agree with the reviewer.
+It is a heuristic approach since we update the transmit precoder, receive beamformer and the dual variables all at each iteration.
+Please note that the proposed algorithm is of practical significance, since it has few number of iterations before the actual precoder design.
+It is surely not a stationary point of the original nonconvex problem but it is guaranteed to provide better performance in the sum rate compared to the distributed approaches presented in Section \ref{sec-4.1} and Section \ref{sec-4.2} for the same number of iteration.
+Note that, if the dual variables are allowed to iterate until convergence, the proposed KKT based scheme achieves the same stationary point for each fixed receive beamformer (similar to the distributed algorithms).
+
+\cmnt{11} Since queue is a dynamic system evolving according to (3), it doesn’t make sense to compare the queue deviations at a given time.
+You should compare average queue deviations in the simulations.
+Moreover, you should also compare the average delay performance instead of just comparing the performance metric (queue deviations) defined in this paper.
+Using the queue deviations as the performance metric also needs more justification.
+
+\resp We thank the reviewer for the insightful comment.
+We agree that the instantaneous deviation is not the right measure for the comparison.
+In the current work, we planned to discuss on the precoder design only and since the expectation is maximized by maximizing the function inside the expectation at each instant, we used the snapshot a given instant to compare different algorithms.
+Please note that Fig.
+\ref{fig-review} includes the comparison over \me{50} slot duration and plot compares the average number of backlogged packets.
+We thought of presenting the results with the time-correlated fading channel and the precoder design with fixed number of iterations in the future publication.
+If the reviewer still insist this figure needs to be included, we will include.
+
+\cmnt{12} What is “SRA” in the simulation figures?
+
+\resp We have updated the figure.
+
+\cmnt{13} In the discussion for Fig.
+1, you mentioned that JSFRA converge to the optimal point, and all algorithms are Pareto-optimal.
+Since the problem is non-convex, why these algorithm can find optimal solution or Paretooptimal point?
+
+\resp We thank the reviewer for the comment. We have updated the text to include pareto-suboptimal point.

### 2015-01-21 Report/introduction.tex
changes with satya

--- 2014-10-23 Report/introduction.tex
@@
 
-In general, the resource allocation problems are formulated by assigning a binary variable to each user indicating the presence or the absence in a particular resource \cite{admission_control}.
-In contrast to that, we use linear transmit precoders, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource.
-The purpose is two-fold.
-Firstly, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.
+In general, the resource allocation problems are formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}.
+\review{In contrast, the linear transmit precoders, which are complex vectors, are implicitly used as decision variables, thereby avoiding the explicit modeling of binary decision variables.
+It solves two purposes.
+First, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.
+In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence}.
 
@@
 
-The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} can also be used to solve the \ac{WSRM} problem.
+The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{mse_duality,christensen2008weighted} can also be used to solve the \ac{WSRM} problem.
 In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients.

### 2015-01-21 Report/mse_formulation.tex
revision_changes
changes with satya

@@
-In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for \ac{MMSE} receivers \cite{viswanath1999optimal,mse_duality}.
+In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{mse_duality}.
 The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
@@
 \begin{multline} \label{mse-error}
-	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
-	+ \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
+	\epsilon_{l,k,n} = \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise,
 \end{multline}
@@
 \begin{multline} \label{mse-error}
- \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
- + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 = \epsilon_{l,k,n},
+ \epsilon_{l,k,n} = \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
+ + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise,
 \end{multline}
@@
 where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol.
-Now, replacing the receive beamformer in \eqref{mse-error} with the \ac{MMSE} receiver in \eqref{eqn-10}, we obtain the following relation between the \ac{MSE} and the \ac{SINR} as
+By using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression in \eqref{eq:SINR}, we can obtain the following relation between the \ac{MSE} and the \ac{SINR} as
 \begin{equation} \label{eqn-mse-eq}
-\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}},
+\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}}.
 \end{equation}
-where \me{\gamma_{l,k,n}} is the received \ac{SINR} as in \eqref{eq:SINR}.
+The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion.
 Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.
+\review{Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{q} value used in the norm present in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.}
 
@@
 \text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
- & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
+ & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
 & \quad &  \text{and} \; \eqref{eqn-4.3}.  \IEEEyessubnumber \label{eqn-mse-1.4}
@@
 	\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
-	& \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \nonumber \\
+	& \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \enoise \nonumber \\
 	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
@@
 \end{IEEEeqnarray}
+
+\begin{comment}
 \subsubsection*{Convergence}
@@
 Note that the objective function improves at each iteration, whereas the sum rate need not follow the same behavior.
+
+\end{comment}

### 2015-01-21 Report/problem_formulation.tex
Submitted version
changes with satya

@@
 The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value.
-In fact, \eqref{eqn-4.2} provides similar expression when the exponent is set to be \me{\ell_{q=2}} as
+\review{In fact, using \me{\ell_{q=2}} in \eqref{eqn-4.2}, we obtain the following objective
 \begin{equation}\label{pf-1}
-\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2.
+\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2,
 \end{equation}
+which is equivalent to the objective defined in \eqref{q_gen_sum}.
+Note that the equivalence can be seen either by discarding \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly greater than the maximum allowable transmission.}
 

### 2015-01-21 Report/problem_formulation_intro.tex
changes with satya

--- 2014-10-07 Report/problem_formulation_intro.tex
@@
 \begin{equation}
-v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}).
+v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}),
 \label{eqn-4.2}
 \end{equation}
+where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}}.
 
@@
 \begin{IEEEeqnarray}{rCl}\label{eqn-3}
-\underset{\substack{\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
-\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-4.3}
+\underset{\substack{\mvec{m}{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
+\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{eqn-4.3}
 \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}, \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} comprises the beamformers associated with user \me{k} for \me{n^\mathrm{th}} sub-channel transmission, and \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} stacks the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}.
+Let \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} be the matrix formed by stacking the beamformers associated with user \me{k} for \me{n^\mathrm{th}} sub-channel transmission.
+Similarly, let \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} denotes the matrix formed by stacking the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
 In \eqref{eqn-4.3}, we consider a \ac{BS} specific sum power constraint for each \ac{BS} across all sub-channels.

### 2015-01-21 Report/review_comments.tex
changes with satya

@@
 \resp We thank the reviewer for the comment. We have updated the text to include pareto-suboptimal point.
+
+\subsection*{Reveiewer comments - \me{2}}
+
+\cmnt The logic from (6) to (16) is not clear.
+The only difference is the two newly introduced NON-CONVEX constraints (16b) and (16c), while the objective function (16a) and the constraint (16d) is the same as (6).
+The equivalence between (6) and (16) is not straightforward and it is confusing why the reformulation in (16) is beneficial.
+
+\cmnt The authors use the successive convex approximation framework, but the approximate problem proposed by the authors is actually not convex.
+Inspecting (19), its objective function is the same as in (6), and the non-convexity of (6) comes exactly from the objective function, so (19) is not a convex problem.
+The same flaw is repeated several times in the approximate problems proposed by the authors.
+
+\cmnt The authors proposed to use block coordinate descent method to solve (16).
+But as the authors have already pointed out, to apply block coordinate descent method, the constraint sets for different variables should be disjoint (uncoupled), which is however not the case in (16), because receive and transmit precoders (i.e w and m) are coupled in the constraints.
+It is confusing on its own why the authors made a statement that contradicts the proposed methodology, and the convergence followed is in question.
+
+\cmnt Regarding the convergence of the SCA, the authors cited [27] for the convergence conditions, but the reference is wrong, because the conditions after the three bullets on page 6 are not mentioned in [27].
+In case the authors disagree, please make the citation more specific, for example, specify the theorem/statement/proposition in [27] where those conditions are specified.
+
+\cmnt The authors also cited [28] to establish the convergence of SCA.
+But the techniques of [27] and [28] are different, and the convergence conditions are different too.
+It is not clear why the authors need two set of convergence conditions for a single problem, and the resulting convergence analysis itself is not solid enough.
+
+\cmnt Another comment on reference: to the reviewer's knowledge, the term SCA is never explicitly used in [2]. So please either correct the reference or be more specific (section, theorem, etc.).
+
+\cmnt The authors propose primal decomposition method, ADMM approach to the non-convex problem (19), while their convergence analysis is based on literature that proved convergence for convex problems only, e.g., [13].
+So the convergence analysis is not trustworthy.
+
+\cmnt The length of the paper is too extensive.
+Some of the reformulations as mentioned in the previous comment can be skipped.
+Also, Section III.D.
+is not deeply explained and does not bring additional value to the paper.
+The implications of ordering the sub-channels for the iterative approach should be carefully studied and extensively explained in a different publication.
+
+\cmnt Information regarding the value of q used to obtain the simulation results is missing (with exception of Fig. 3).
+
+\cmnt In Fig.
+1 and Fig.
+2, the labels for the system model do not fit with the written description.
+Additionally, the reference scheme Q-WSRM is not optimal, since it over allocates resources if there are few queued packets.
+Therefore, it is not interesting for comparison purposes.
+
+\cmnt Assuming that Fig.
+2 and Fig.
+3 where obtained based on the same simulation setup, i.e.
+user queues, number of transmit and receive antennas and number of base stations, it is not clear why results in Fig.
+3 are worse than Fig.
+2 when comparing JSFRA.
+Even more, since the number of sub-channels is larger in Fig.
+3, the result seems contradictory.
+
+\subsection*{Reveiewer comments - \me{3}}
+
+\cmnt This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods.
+This is an interesting and important topic.
+
+\resp We thank the reviewer for reading the manuscript and providing valuable comments.
+
+\cmnt 1. The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.
+
+\resp Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression.
+It is necessary in case of the MSE formulation, where we have explicitly stated the optimization variable \me{t_k}.
+If the reviewer insist on replacing the rate expression using \me{t_k}, we can make those changes.
+
+\cmnt 2.
+The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5).
+This is not obvious.
+An easy case to check this statement is that assuming the system has two BS and each BS serves one user.
+When \me{Q_1=0} and 2nd BS has sufficiently large power, (16b) and (16c) do not hold equality.
+Rigorous proof is needed if authors stick to this statement.
+
+\resp We thank the reviewer for the insightful comment.
+We modified the statement such that it is an under estimator for the actual SINR expression and will be tight when the system is limited by the transmit power.
+
+\cmnt 3.
+The solution in (21) is obtianed for MMSE, i.e.
+for 2-norm(q=2).
+If \me{q=1} or \me{q=\infty}, it is actually an equivalent linear programming problem.
+Details for this solution should be provided.
+
+\resp We thank the reviewer for the critical comment.
+We have update the manuscript to include the information about the receiver with other q values.
+Please note that the receive beamformer doesn't depend on the q value explicitly.
+It depends inherently through the transmit precoders.
+
+\cmnt 4.
+The convergence proof need to be rigorous.
+The inequality of (23a) is opposite to the reference [28].
+Also the statement on uniqueness of the transmit and the receive beamformers are not correct.
+Although we can choose one antenna to be real value, this does not mean the problem has unique solution!
+
+\cmnt 5.
+(25) is generally wrong.
+(25) only holds when the MSE is minimized(by MMSE receiver) and the snr is the optimized(which is obtained by general eignvalue decompostion).
+This is clearly stated in the reference [5] and [6].
+This can also be easily checked by comparing (25) and (2).
+Consequently the alternative formulation (26) based on this conclusion is questionable.
+
+\resp We thank the reviewer for pointing out the information loss in the statement.
+We have provided more detail in the manuscript.
+The relation is valid if the receiver is based on the MMSE criterion.
+Note that, the receiver does not depend on the \me{q} value used in the objective.
+It depend only on the transmit precoders which in fact change based on the \me{q} value used in the objective function.
+
+\cmnt 6.
+For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed.
+1.
+The numbers of transmitted packets for users  \me{t_k}'s are optimization variables.
+So they should be explicitly stated in the problem formulation (6), (16), (20) and (26) to avoid confusing.
+
+\subsection*{Reveiewer comments - \me{4}}
+
+\cmnt First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method.
+"The SCA method" is often referred to, but never really defined or referenced.
+The three required conditions (as stated on p.
+6, col.
+1, rows 38-40) do not, as far as I can tell, appear in [27].
+Indeed, [27] is concerned with optimization problems where the objective function is non-convex, but the constraint set is convex and separable over the blocks of variables.
+Perhaps you meant to cite [A], wherein non-convex constraints are handled in a similar way?
+Numerically, the algorithms do converge, and the argument put forward makes sense, but the treatment must be improved to be more rigorous.
+
+\cmnt Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates.
+This is due to how the conditional Lyapunov drift is minimized.
+This approach completely removes the queue dynamics from the optimization problem, essentially leading to greedy one-shot optimization in 7
+every time instant.
+The framework would be more interesting if some sort of optimization (or tracking) is performed over several time instants, rather than the one-shot approach that is currently used for the JSFRA algorithms.
+Possibly, some expectation over the queues would be optimized then.
+Even if no analytical treatment of the tracking over several time-steps is added, I would at least highly recommend adding some simulation results where the proposed one-shot algorithms are performed sequentially over several time instants.
+
+\cmnt Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results.
+This reviewer recommends spending more space on the convergence, than on the description of the distributed techniques.
+Still, it would be nice with a direct description of what local CSI is required, and how it is acquired, to perform the local computations for the primal decomposition and ADMM methods.
+For the description of the signaling of the CSI in Sec.
+IV-B, are you envisioning a TDD system?
+
+\cmnt Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier.
+This could easily be clarified.
+
+\cmnt - p. 1, col. 1, row 42: "userss"
+
+\resp Modified.
+
+\cmnt - p.
+1, col.
+2, row 18: the precoders are used \_implicitly\_ as decision variables.
+This is the whole point, to avoid explicitly modeling the hard decisions in the optimization, and instead do soft decisions during the iterations, and then finally hard decisions after convergence.
+
+\resp We thank the reviewer for the insightful comment on the proposed approach. We have modified the text accordingly.
+
+\cmnt - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?
+
+\resp We understand the reviewer's concern. We have provided the valid reference for the SCA scheme.
+
+\cmnt - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead
+
+\resp Changed.
+
+\cmnt - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here
+
+\resp We thank the reviewer for the concern on the grouped variable. We have modified the expressions accordingly.
+
+\cmnt - p.
+3, col.
+2, row 26: Which general MIMO-OFDM problem are you talking about here, and what is combinatorial about it?
+Is it the problem of selecting users to be served on orthogonal subcarriers?
+There is nothing inherently combinatorial over the problem in (6) as far as I can tell, as the beamformers are used as soft decision variables.
+
+\resp We thank the reviewer for the comment. We have removed the word "combinatorial" from the text.
+
+\cmnt - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.
+
+\resp It is restructured to include additional details.
+
+\cmnt - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).
+
+\resp Agreed.
+
+\cmnt - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).
+
+\cmnt - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.
+
+\cmnt - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??
+
+\resp We thank the reviewer for pointing out the mistake. We have modified accordingly to the comment.
+
+\cmnt - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).
+
+\cmnt - p.
+6, col.
+1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs.
+However, does it affect the convergence of the algorithm?
+
+\cmnt - p.
+6, col.
+1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs.
+However, does it affect the convergence of the algorithm?
+
+\resp We thank the reviewer for the comment.
+
+\cmnt - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?
+
+\cmnt - p.
+7, col.
+1, row 35: Just because a problem is convex does not mean that it has a unique solution.
+(Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?
+
+\resp We thank the reviewer for informing the important argument.
+The relaxed sub problem is strongly convex, due to the presence of norm function in the objective.
+Since the relaxation forced \me{q_{l,k,n} = 0}, the precoders are unique.
+
+\cmnt - Table 1: "backpreassure"
+
+\resp Changed in the revised manuscript
+
+\cmnt - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.
+
+\resp Changed in the revised manuscript

### 2015-01-21 Report/simulation_distributed.tex
changes with satya

@@
-The performances of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points.
+The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points.
 Fig.
-\ref{fig-d} compares the performances of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}.
+\ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}.
 Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}.

### 2015-01-21 Report/simulation_results.tex
changes with satya

@@
 		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
-		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \emph{backpreassure})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
+		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
 		\cline{3-14}
@@
 Fig.
-\subref*{fig-1} shows the performances of the centralized schemes for a single receive antenna system.
+\subref*{fig-1} shows the performance of the centralized schemes for a single receive antenna system.
 The total number of queued packets for Fig.
@@
 
-The performances of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
+The performance of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
 \ref{fig-a}.
@@
 It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}.
-All the algorithms are Pareto-optimal and provide different performances based on the weights used to find a point in the rate region.
+All the algorithms are Pareto-optimal and provide different performance based on the weights used to find a point in the rate region.
 

### 2015-01-21 Report/sub_channel_wsrm.tex
changes with satya

--- 2014-10-01 Report/sub_channel_wsrm.tex
@@
 In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size.
-In order to mitigate this, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
-The optimal approach is to decompose the problem over each sub-channel with a fixed transmit power constraint for each sub-channel.
-The power allocated for each sub-channel is controlled by a master problem based on different algorithms as discussed in \cite{palomar2006tutorial,boyd2011distributed}.
+In order to mitigate this, we can adopt the decomposition techniques discussed in \cite{palomar2006tutorial,boyd2011distributed} to distribute the precoder design across each sub-channels independently with some coupling parameters that are exchanged across the sub-channel wise subproblems.
 
-The proposed \acl{QM} \ac{SRA} formulation enables us to solve for the transmit precoders of all the users associated with the coordinating \ac{BS} in the set \me{\mathcal{B}} over each sub-channel independently by fixing the transmit power on each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}.
-In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization.
-The total number of queued bits for each user are updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
+As an alternative sub-optimal solution, we propose \acl{QM} \ac{SRA}, which aims at designing the precoders independently across each sub-channel in a sequential manner by taking the current backlogged packets into account.
+In this approach, the transmit power is fixed across each sub-channel \me{n} as \me{P_{\max,n}} at each \ac{BS}.
+The power split can either follow equal sharing or any predetermined pattern as in partial frequency reuse.
+For the fixed sub-channel power, the \ac{JSFRA} formulation presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} is performed over each sub-channel in a sequential manner.
+The coupling variable across the sub-channel is the total number of backlogged packets associated with each user.
+Let \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}.
+Now, for the first sub-channel, \me{n=1}, the queues are given by \me{Q_{k,n=1} = Q_k}, which corresponds to the actual number of backlogged packets present in the current instant \me{i}.
+Using the updated number of queued packets, the \ac{JSFRA} algorithm is performed over the sub-channel \me{n=1} to obtain the rates associated with each user.
+Now, for \me{n=2}, the number of queued packets for each user is updated as \me{Q_{k,n=2} = Q_k - \sum_{l=0}^L t_{l,k,n=1}}.
+With this updated number of queued packets, the \ac{JSFRA} algorithm is performed for \me{n=1} sub-channel to obtain the optimal precoders.
+In general, the number of queued packets to be used for each user in a given sub-channel \me{n} is given by
 \begin{equation}
-Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
+Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}.
 \label{eqn-weight}
 \end{equation}
-where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}.
-In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}.
+In \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}.
 However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.
+
+The proposed \ac{QM} \ac{SRA} scheme depend on the choice of the sub-channel selection, which is evident from the sequential approach used in the sub-optimal problem formulation.
+However, the proposed approach provides faster convergence in contrast to the \ac{JSFRA} formulation over all sub-channel mainly due to the reduction in the size of the sub-channel wise sub problem.
+The choice of the sub-channel selection is random and it is difficult to determine the order, since the optimization variables \me{\mvec{m}{l,k,n}} are vectors.
 %The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}

### 2015-01-21 Report/system_model.tex
changes with satya

--- 2014-10-08 Report/system_model.tex
@@
 where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
-In \eqref{eqn-1}, \me{L = rank(\mvec{H}{b,k,n}) = min(N_T,N_R)} is the maximum number of spatial streams\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
+In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
 Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
 \begin{equation}\label{eq:SINR}
-\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.
+\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2},
 \end{equation}
+where \me{\enoise = N_0\|\mvec{w}{l,k,n}\|^2} denotes the equivalent noise variance.
 

### 2015-01-21 Report/time_correlated.tex
changes with satya

This section is dedicated to understand the performance of the proposed \ac{JSFRA} scheme with different values of \me{\ell_q} over multiple time slots. The performance is compared with the existing \ac{Q-WSRME} scheme for different arrival rates \me{A_k}. Fig. \ref{fig-review} compares the performance of the centralized algorithms for different \me{\ell_q} values using the average number of backlogged packets present in the system after each time instant. The horizontal axis indicate the average arrivals in bits per user, which is constant for all user. The instantaneous arrival follows Poisson distribution. The model considered for simulation is a \me{4 \times 1} \ac{MIMO} system with \me{N = 4} sub-channels with \me{N_B = 2} \acp{BS}. The path loss is modeled as a uniform random variable \me{[0,-3]} dB with the maximum \ac{SINR} seen by any user is \me{6} dB. The average is performed over \me{100} time slots.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{Review/reviewer.eps}
	\label{fig-review}
	\caption{System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
\end{figure}

It can be seen from Fig. \ref{fig-review} that the performance of the \ac{JSFRA} scheme with \me{\ell_2} norm and the \ac{Q-WSRME} approach are similar in the average residuals after each transmission instant. Note that the performance of the \ac{Q-WSRM} scheme is similar to the \ac{Q-WSRME} approach when the arrival rates are greater than the actual transmissions. It can be seen from Fig. \ref{fig-review} that the average number of backlogged packets are contained until the per user arrival is \me{\leq 4} bits. After that, the average queues become unbounded. The performance of the \ac{JSFRA} scheme with \me{\ell_1} norm has significantly less number of average queued packets in comparison with other schemes. The performance of the \ac{JSFRA} scheme with \me{\ell_{\infty}} performs the worst in terms of the average number of queued packets after each transmission instant by achieving the fair service rate to all users.

### 2015-01-21 Report/wsrm_formulation.tex
revision_changes
changes with satya

@@
-In this approach, we present an algorithm to solve \eqref{eqn-3} to obtain the transmit precoders in a centralized manner by using the idea of alternating optimization and successive convex approximation.
-Using \eqref{eq:SINR}, we can reformulate the problem defined in \eqref{eqn-3} as
+We now present an algorithm to solve problem \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
+To do this, first by using the \ac{SINR} expression in \eqref{eq:SINR}, we equivalently reformulate problem \eqref{eqn-3} as
 \iftoggle{single_column}{
@@
 \underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
-\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \label{eqn-6.2} \\
-  & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
-  & \quad & \text{and } \eqref{eqn-4.3}, \IEEEyessubnumber
+\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-6.2} \\
+  & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
+  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-6.4}
 \end{IEEEeqnarray}
@@
 	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
-	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \triangleq f(\tilde{\mbf{u}}_{l,k,n}) \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
-	&\quad& \beta_{l,k,n} \geq \tilde{N}_0 + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
-	&\quad& \text{and } \eqref{eqn-4.3}, \IEEEyessubnumber
+	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
+	&\quad& \beta_{l,k,n} \geq \enoise + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
+	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
 \end{IEEEeqnarray}
 }
-where \me{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}^\herm, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation and \me{\tilde{N}_0 = N_0\|\mvec{w}{l,k,n}\|^2} be the effective noise variance.
-In this formulation, we relaxed the equality constraint in \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-However, this step leads to the same solution without loss of optimality, since the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3} are active for an optimal solution, following the same arguments as those in \cite{tran2012fast}.
-Intuitively, \eqref{eqn-6.2} denotes the \ac{SINR} constraint for \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} gives an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the optimization variable \me{\beta_{l,k,n}}.
+In this formulation, we relaxed the \ac{SINR} expression \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}.
+\review{Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.
+\review{The constraints are tight when the system is power limited or when the total number of backlogged packets is larger than the transmission rate.}
 
-Similar to the \ac{WSRM} problem in \cite{tran2012fast}, the proposed formulation in \eqref{eqn-6} can be shown to be NP-hard even for the single antenna case.
-The reformulation in \eqref{eqn-6} allows a tractable solution as presented below.
-First, we note that the constraints \eqref{eqn-4.3} are convex with involved variables.
+In order to find a tractable solution for problem \eqref{eqn-6}, we note that the constraints \eqref{eqn-6.4} are convex with involved variables.
 Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}.
 Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
-Recall that the coordinate descent method assumes that the optimization variables belong to disjoint sets and the problem must be convex for a given set of variables while keeping other variables fixed as discussed in \cite{xu2013block}.
+\review{Note that the problem in \eqref{eqn-6} is similar to the \ac{WSRM} formulation, which is known to be NP-hard even for the single antenna case \cite{np_hard}.} % Recall that the coordinate descent method assumes that the optimization variables belong to disjoint sets and the problem is convex for a variable while all other variables are fixed \cite{xu2013block}.
 
-By fixing the receivers, the problem now is to find the optimal transmit beamformers for a given set of linear receivers which is still a challenging task.
+For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task.
 We note that for fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
 Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}.
-To arrive at a tractable formulation, we adopt the \ac{SCA} method to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by a series of convex constraints.
-Note that function \me{f(\tilde{\mbf{u}}_{l,k,n})} in \eqref{eqn-6.2} is convex for fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-According to the \ac{SCA} method, we relax \eqref{eqn-6.2} to a convex constraint in each iteration of the iterative procedure.
-Since \me{f(\tilde{\mbf{u}}_{l,k,n})} is convex, a concave approximation of \eqref{eqn-6.2} can be easily found by considering the first order approximation of \me{f(\tilde{\mbf{u}}_{l,k,n})} around the current operation point.
+\review{To arrive at a tractable formulation, we adopt \ac{SCA} to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by a series of convex constraints \cite{marks1978technical}}.
+Let us define a function,
+\begin{equation*}
+f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}},
+\end{equation*}
+where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation.
+Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
+Eq.
+\eqref{eqn-6.2} can be viewed as a \ac{DC} constraint.
+Now the convex function given by \me{f({\mbf{u}}_{l,k,n})} is approximated by considering the first order approximation around the operating point \me{\tilde{\mbf{u}}_{l,k,n}}.
+
 For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
@@
 \end{subeqnarray}
-and hence \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
+and hence \me{f({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
 In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier}.
@@
 }
-In summary, for the fixed linear receivers, the \ac{JSFRA} problem to find transmit beamformers is shown by
+In summary, for the fixed linear receivers \review{\me{\mvec{w}{l,k,n}}}, the \ac{JSFRA} problem to find transmit beamformers is shown by
 \begin{IEEEeqnarray}{CCl}\label{eqn-9}
-\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},,\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  \tilde{N}_0 + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
-& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
+\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
+\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
+& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
 & \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
@@
 \begin{IEEEeqnarray}{CCl}\label{eqn-9--1}
-\underset{\substack{\gamma_{l,k,n},\mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
-\text{subject to} & \quad & \eqref{eqn-9.1c}, \eqref{eqn-9.1d}, \eqref{eqn-9.1e}, \text{ and } \eqref{eqn-8} \IEEEyessubnumber \label{eqn-9--1.1b}.
+\underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
+\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
+& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9--1.1d} \\
+& \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9--1.1e}
 \end{IEEEeqnarray}
@@
 where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the earlier iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
-Note that \eqref{opt-rx} is obtained by iterating over the fixed \me{\mvec{w}{l,k,n}^{(i-1)}} at each \ac{SCA} iteration until convergence or for fixed number of iterations.
+Eq.
+\eqref{opt-rx} is obtained by iterating over the fixed \me{\mvec{w}{l,k,n}^{(i-1)}} at each \ac{SCA} iteration until convergence or for fixed number of iterations.
+\review{Note that the optimal receiver has no explicit relation with the choice of the \me{q} value used in the objective function.
+The dependency is implied implicitly through the transmit precoders \me{\mvec{m}{l,k,n}}, which in deed depend on the \me{q} value.}
+
 It can be seen that the optimal receiver expression in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
@@
 \end{IEEEeqnarray}
+\review{Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance or the convergence behavior}.
 
@@
 The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
-Instead of initializing \me{\tilde{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{\tilde{\mbf{u}}_{l,k,n}} in an efficient manner as briefed in Algorithm \ref{algo-1}.
+Instead of initializing \me{{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{{\mbf{u}}_{l,k,n}} as briefed in Algorithm \ref{algo-1}.
 For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for the predefined iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
@@
  \KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{M}}_{k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
- update \me{\mvec{W}{k,n}} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} using \me{\tilde{\mbf{M}}_{k,n}}\;
+ update \me{\mvec{W}{k,n}} and \me{{\mbf{u}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} using \me{\tilde{\mbf{M}}_{k,n}}\;
  \Repeat{Queue convergence or \me{i \geq I_{\max}}}{
@@
  solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
- update the constraint set \eqref{eqn-8} with \me{\tilde{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
+ update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
  $j = j + 1$\;
@@
 
+\begin{comment}
 \subsubsection*{Convergence}
@@
 The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, and hence the proposed \ac{JSFRA} scheme is guaranteed to converge to a stationary point of the original nonconvex problem.
+
+\end{comment}

### 2015-01-22 Report/appendix_tightness.tex
satya_2

In order for the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user per \ac{BS} with large enough backlogged packets that cannot be satisfied with the given power budget. To prove this, let us consider a single \ac{BS} \me{N_T \times 1} system with \me{|U|_b} users each with \me{Q_k} backlogged packets. Let us consider the problem for a single \ac{BS} \me{b} as 
\begin{IEEEeqnarray}{rCl}
	\underset{\gamma_{k},\mvec{m}{k},\beta_{k}}{\text{minimize}} &\quad& \sum_{k \in \mc{U}_b} \big | Q_k - \log_2(1 + \gamma_k) \big |^q  \eqsub \\
	\text{subject to} &\quad& \gamma_{k} \leq \frac{ | \mvec{H}{k} \mvec{m}{k}|^2}{\beta_{k}} \IEEEyessubnumber \label{ae-1} \\
	&\quad& \beta_{k} \geq N_0 + \sum_{\mathclap{i \neq k}} |\mvec{H}{k} \mvec{m}{i} |^2 \IEEEyessubnumber \label{ae-2} \\
	&\quad& \sum_{k \in \mc{U}_b} \text{tr} \, (\mvec{m}{k} \mvec{m}{k}^\herm) \leq P_{{\max}}. \IEEEyessubnumber \label{ae-3}
\end{IEEEeqnarray}
Let \me{N_T > |\mc{U}_b|} and the precoders are designed for all users. Let us consider two users, say \me{i} and \me{j}, whose precoders are given by \me{\mvec{m}{i}} and \me{\mvec{m}{j}}. In order to show that the constraint \eqref{ae-1} and \eqref{ae-2} are tight for all users at optimal when the objective has non zero value at the final solution. Let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for user \me{i} only. Let us also consider that \me{\gamma_k} for all users \me{k \in \mc{U}_b \backslash j} are identified to satisfy the backlogged packets.

Now, in order to minimize the objective of the \me{\ith{i}} user, \me{\gamma_i} should be \me{2^{Q_i} - 1} to have the minimum objective. Since the constraints \eqref{ae-1} and \eqref{ae-2} are not tight for the \me{\ith{i}} user, the actual \ac{SINR} on the r.h.s of \eqref{ae-1} is greater than \me{\gamma_i} of the user \me{i}. It is attributed to the excess power in the transmit precoder of user \me{i} as \me{\mvec{m}{i} = \bar{\mbf{m}}_{i} + \mbf{V}_i \mbf{e}}, where \me{\mbf{V}_i = \mc{N}([\mbf{H}^{\mathrm{T}}_0, \dotsc, \mbf{H}^{\mathrm{T}}_{i-1},\mbf{H}^{\mathrm{T}}_{i+1}, \dotsc,\mbf{H}^{\mathrm{T}}_{|\mc{U}_b| - 1}]^{\mathrm{T}})} denotes the null space corresponding to the other user channel vectors and \me{\mbf{e}} is any random vector with power \me{\Delta P}. Note that this extra power has no impact on the interference constraint \eqref{ae-2} of other users.

Since the power is not utilized efficiently, the objective will force the excess \me{\Delta P} to be used for the starving user \me{j} with the non zero objective value with the current precoder \me{\mvec{m}{j}}. In order to minimize the objective, we can find a vector \me{\mvec{m}{j} = \bar{\mbf{m}}_{j} + \mbf{V}_j \mbf{e}}, which has no impact on the interference or the optimal precoders of other users and their objective value, still minimize the objective function. It is in contradiction to our original assumption that the power is utilized for the user \me{i} making the constraints loose. It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.

### 2015-01-22 Report/convergence_centralized.tex
satya_2

@@
+\newcommand{\mx}{\mbf{x}}
+\newcommand{\my}{\mbf{y}}
+\newcommand{\mz}{\mbf{z}}
+
+\newcommand{\mxb}{{\mbf{x}}}
+\newcommand{\myb}{{\mbf{y}}}
+\newcommand{\iterate}[2]{{#1}^{(#2)}}
+
+Let us write the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+\begin{IEEEeqnarray}{RCL} \label{con}
+\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj} \\
+\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
+&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
+&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
+\end{IEEEeqnarray}
+wher \me{g_2,f} are convex functions and \me{h} is a linear function.
+Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both.
+Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}.
+Other convex constraints are addressed by the constraint \eqref{con-cvx}.
+With this, the feasible set of the problem \eqref{con} is given by
+\begin{IEEEeqnarray}{rl}
+\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \eqspace
+\end{IEEEeqnarray}
+
+Before proceeding further, let us define the following notations.
+Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{BCDM} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point.
+Since the problem \eqref{con} is nonconvex, it is not guaranteed to find an optimal solution.
+In order to solve for a suboptimal solution, let us resort to the \ac{BCDM} by fixing a block of variables and optimize for others.
+Since \ac{BCDM} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}.
+Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is now in \ac{DC} form.
+Following the approach presented in \cite{lipp2014variations,lanckriet2009convergence}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around \me{\mxb_0 \in \mc{F}} as
+\begin{equation} \label{con-relax}
+\hat{g}_o(\mx,\iterate{\myb}{0};\mxb_0) = {g}_0(\mxb_0,\iterate{\myb}{0}) + \nabla g_0(\mxb_0,\iterate{\myb}{0})^\mathrm{T} (\mx - \mx_0).
+\end{equation}
+Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{BCDM} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as
+\begin{IEEEeqnarray}{RCL} \label{con-m}
+	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj-m} \\
+	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mx_k) \leq 0 \eqsub \label{con-dc-m} \\
+	&\quad& g_1(\mx,\iterate{\myb}{i}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
+	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
+\end{IEEEeqnarray}
+Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{F}}{i}_k}.
+In order to prove the convergence of the convex subproblems \eqref{con-relax} for a fixed \me{\iterate{\myb}{i}}, let us assume that \eqref{con-relax} yields \me{\mx_{k+1}} as the final solution at the \me{\ith{k}} iteration.
+To show that \me{\mx_{k+1}} minimizes the objective function, let us assume that the previous point \me{\mx_k} is feasible around which the relaxation is made.
+It can be seen that
+\begin{equation*}
+h(\mz) - {g}_0(\mx,\iterate{\myb}{i}) \leq h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k) \leq 0
+\end{equation*}
+
+\begin{comment}
 In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}
@@
 Note that the objective function improves at each iteration, whereas the sum rate need not follow the same behavior.
+\end{comment}

### 2015-01-22 Report/mse_formulation.tex
satya_2

@@
 where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol.
-By using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression in \eqref{eq:SINR}, we can obtain the following relation between the \ac{MSE} and the \ac{SINR} as
+\review{Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as}
 \begin{equation} \label{eqn-mse-eq}
@@
 Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.
-\review{Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{q} value used in the norm present in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.}
+\review{Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.}
 
@@
 	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
-	\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
-	& \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \enoise \nonumber \\
-	& {} + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
-	&  \text{and} \; \eqref{eqn-4.3}. \IEEEyessubnumber \label{eqn-mse-1.4}
+	\text{subject to} & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
+	& \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \nonumber \\	
+	& \qquad + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
+	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
 \end{IEEEeqnarray}}}
 
-An alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
-We adopt the \ac{SCA} method as in Section \ref{sec-3.2} to relax the constraint by a sequence of convex subsets using first order Taylor series approximation around a fixed \ac{MSE} point  \me{\tilde{\epsilon}_{l,k,n}} as
+An alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}, which is in fact a \ac{DC} constraint.
+We resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using first order Taylor series approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl}
@@
 \underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
-\text{subject to} & \quad & \eqref{eqn-4.3},\, \eqref{eqn-mse-1.3},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
+\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
 \end{IEEEeqnarray}

### 2015-01-22 Report/problem_formulation.tex
satya_2

@@
 This makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \acp{BS} independently by exchanging minimal information exchange \cite{boyd2011distributed}.
-In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user in the system.
+In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user.
 The queue deviation objective provides an alternative approach to perform the resource allocation without the additional rate constraints as in the \ac{Q-WSRME} formulation.

### 2015-01-22 Report/wsrm_formulation.tex
satya_2

@@
 \review{Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.
-\review{The constraints are tight when the system is power limited or when the total number of backlogged packets is larger than the transmission rate.}
+\review{The constraints are tight when the per \ac{BS} objective is non zero at the optimal point, as discussed in Appendix \ref{a-3}}.
+\review{Note that the problem in \eqref{eqn-6} is similar to the \ac{WSRM} formulation, which is known to be NP-hard even for the single antenna case \cite{np_hard}.}
 
@@
 Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
-\review{Note that the problem in \eqref{eqn-6} is similar to the \ac{WSRM} formulation, which is known to be NP-hard even for the single antenna case \cite{np_hard}.} % Recall that the coordinate descent method assumes that the optimization variables belong to disjoint sets and the problem is convex for a variable while all other variables are fixed \cite{xu2013block}.
-
 For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task.
@@
 Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-Eq.
-\eqref{eqn-6.2} can be viewed as a \ac{DC} constraint.
-Now the convex function given by \me{f({\mbf{u}}_{l,k,n})} is approximated by considering the first order approximation around the operating point \me{\tilde{\mbf{u}}_{l,k,n}}.
+\review{Eq.
+\eqref{eqn-6.2} can be viewed as a \ac{DC} constraint, in which the convex function given by \me{f({\mbf{u}}_{l,k,n})} is upper bounded by first order approximation around an operating point \me{\tilde{\mbf{u}}_{l,k,n}}}.
 
@@
 \text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
-& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9--1.1d} \\
 & \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9--1.1e}
 \end{IEEEeqnarray}
-Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mvec{w}{l,k,n}} as
+Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mbf{w}^{\ast}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl}
-\mvec{\widetilde{R}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{\widetilde{R}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}, \IEEEyessubnumber \eqspace \label{opt-rx}
+\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}, \IEEEyessubnumber \eqspace \label{opt-rx}
 \end{IEEEeqnarray}
-where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the earlier iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
-Eq.
-\eqref{opt-rx} is obtained by iterating over the fixed \me{\mvec{w}{l,k,n}^{(i-1)}} at each \ac{SCA} iteration until convergence or for fixed number of iterations.
-\review{Note that the optimal receiver has no explicit relation with the choice of the \me{q} value used in the objective function.
-The dependency is implied implicitly through the transmit precoders \me{\mvec{m}{l,k,n}}, which in deed depend on the \me{q} value.}
+where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
+\review{The optimal receiver \me{\mbf{w}^{\ast}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for fixed number of iterations.} \review{Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
+The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which in deed depend on the \me{q} value.}
 
-It can be seen that the optimal receiver expression in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
+It can be seen that the optimal receiver in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
 \begin{IEEEeqnarray}{rCl}

### 2015-01-22 Report/appendix_tightness.tex
convergence_proof

@@
 \end{IEEEeqnarray}
-Let \me{N_T > |\mc{U}_b|} and the precoders are designed for all users.
-Let us consider two users, say \me{i} and \me{j}, whose precoders are given by \me{\mvec{m}{i}} and \me{\mvec{m}{j}}.
-In order to show that the constraint \eqref{ae-1} and \eqref{ae-2} are tight for all users at optimal when the objective has non zero value at the final solution.
-Let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for user \me{i} only.
+Let us assume the system has \me{N_T > |\mc{U}_b|} and the precoders are determined for all users at the optimal point for which the objective is minimum and is nonzero.
+Let us consider two users, say \me{i} and \me{j} with precoders \me{\mvec{m}{i}} and \me{\mvec{m}{j}}.
+In order to show the tightness of the constraints \eqref{ae-1} and \eqref{ae-2}, let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for a user \me{i} only.
 Let us also consider that \me{\gamma_k} for all users \me{k \in \mc{U}_b \backslash j} are identified to satisfy the backlogged packets.
@@
 Now, in order to minimize the objective of the \me{\ith{i}} user, \me{\gamma_i} should be \me{2^{Q_i} - 1} to have the minimum objective.
-Since the constraints \eqref{ae-1} and \eqref{ae-2} are not tight for the \me{\ith{i}} user, the actual \ac{SINR} on the r.h.s of \eqref{ae-1} is greater than \me{\gamma_i} of the user \me{i}.
-It is attributed to the excess power in the transmit precoder of user \me{i} as \me{\mvec{m}{i} = \bar{\mbf{m}}_{i} + \mbf{V}_i \mbf{e}}, where \me{\mbf{V}_i = \mc{N}([\mbf{H}^{\mathrm{T}}_0, \dotsc, \mbf{H}^{\mathrm{T}}_{i-1},\mbf{H}^{\mathrm{T}}_{i+1}, \dotsc,\mbf{H}^{\mathrm{T}}_{|\mc{U}_b| - 1}]^{\mathrm{T}})} denotes the null space corresponding to the other user channel vectors and \me{\mbf{e}} is any random vector with power \me{\Delta P}.
-Note that this extra power has no impact on the interference constraint \eqref{ae-2} of other users.
+Since the constraints \eqref{ae-1} and \eqref{ae-2} are not tight for the \me{\ith{i}} user, the actual \ac{SINR} on the r.h.s of \eqref{ae-1} is greater than \me{\gamma_i}.
+It is attributed to the excess power in the transmit precoder of user \me{i} as \me{\mvec{m}{i} = \bar{\mbf{m}}_{i} + \mbf{V}_i \mbf{e}}, where \me{\mvec{V}{i} = \mc{N}([\mbf{H}^{\mathrm{T}}_0, \dotsc, \mbf{H}^{\mathrm{T}}_{i-1},\mbf{H}^{\mathrm{T}}_{i+1}, \dotsc,\mbf{H}^{\mathrm{T}}_{|\mc{U}_b| - 1}]^{\mathrm{T}})} denotes the null space corresponding to the other user channel vectors and \me{\mbf{e}} be any random vector with power \me{\Delta P}.
+Note that the extra power has no impact on the interference constraint \eqref{ae-2} of other users.
 
-Since the power is not utilized efficiently, the objective will force the excess \me{\Delta P} to be used for the starving user \me{j} with the non zero objective value with the current precoder \me{\mvec{m}{j}}.
-In order to minimize the objective, we can find a vector \me{\mvec{m}{j} = \bar{\mbf{m}}_{j} + \mbf{V}_j \mbf{e}}, which has no impact on the interference or the optimal precoders of other users and their objective value, still minimize the objective function.
+Since the allocated rate of user \me{j} is less than the queued packets, we can find a precoder \me{\mvec{m}{j}} with the additional power of \me{\Delta P} as \me{\mvec{m}{j}^\prime = \bar{\mbf{m}}_{j} + \mvec{V}{j} \mbf{e}^\prime}.
+Note that the new precoder has no impact on the interference constraint of other users.
+The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting other user rates, there by reduces the objective further.
 It is in contradiction to our original assumption that the power is utilized for the user \me{i} making the constraints loose.

### 2015-01-22 Report/convergence_centralized.tex
convergence_proof

@@
+\newcommand{\eqn}[1]{\(#1\)}
 \newcommand{\mx}{\mbf{x}}
@@
 \newcommand{\mz}{\mbf{z}}
-
 \newcommand{\mxb}{{\mbf{x}}}
@@
 Let us write the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
-\begin{IEEEeqnarray}{RCL} \label{con}
+\begin{IEEEeqnarray}{rCl} \label{con}
 \underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj} \\
@@
 \begin{IEEEeqnarray}{rl}
-\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \eqspace
+\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
 \end{IEEEeqnarray}
@@
 Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{BCDM} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point.
-Since the problem \eqref{con} is nonconvex, it is not guaranteed to find an optimal solution.
+Since the problem \eqref{con} is nonconvex, it is not guaranteed to find the optimal solution.
 In order to solve for a suboptimal solution, let us resort to the \ac{BCDM} by fixing a block of variables and optimize for others.
 Since \ac{BCDM} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}.
-Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is now in \ac{DC} form.
-Following the approach presented in \cite{lipp2014variations,lanckriet2009convergence}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around \me{\mxb_0 \in \mc{F}} as
+Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form.
+Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around a feasible point \me{\mxb_0 \in \mc{F}} as
 \begin{equation} \label{con-relax}
@@
 Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{BCDM} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as
-\begin{IEEEeqnarray}{RCL} \label{con-m}
+\begin{subeqnarray} \label{con-m}
 	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj-m} \\
@@
 	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
-\end{IEEEeqnarray}
+\end{subeqnarray}
 Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{F}}{i}_k}.
-In order to prove the convergence of the convex subproblems \eqref{con-relax} for a fixed \me{\iterate{\myb}{i}}, let us assume that \eqref{con-relax} yields \me{\mx_{k+1}} as the final solution at the \me{\ith{k}} iteration.
-To show that \me{\mx_{k+1}} minimizes the objective function, let us assume that the previous point \me{\mx_k} is feasible around which the relaxation is made.
+In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\mx_k}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration.
+To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\mx_k} is feasible for \eqref{con-m}.
+Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\mx_k}, it satisfies
+\begin{equation}
+h(\mz) - {g}_0(\mx,\iterate{\myb}{i}) \leq h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k) \leq 0,
+\end{equation}
+since \me{{g}_0(\mx,\iterate{\myb}{i}) \leq \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k), \forall \mx \in \iterate{\mc{F}}{i}_{k-1}}, where \me{\mc{F}_0 = \mc{F}}.
+Now, \me{\mx_{k+1}} is the solution and feasible for the \me{\ith{k}} subproblem, therefore, it satisfies
+\begin{multline}
+h(\mz_{k+1}) - {g}_0(\mx_{k+1},\iterate{\myb}{i}) \leq h(\mz_{k+1}) - \hat{g}_0(\mx_{k+1},\iterate{\myb}{i};\mxb_k) \\
+\leq h(\mz_{k}) - \hat{g}_0(\mx_{k},\iterate{\myb}{i};\mxb_k) \leq 0. \label{con-sub-set}
+\end{multline}
+Using \eqref{con-sub-set}, we can prove that the solution \me{\mx_{k+1}} and \me{\mz_{k+1}} are feasible, since the initial point \me{\mx_{0}} was chosen to be feasible.
+In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iterate{\mc{F}}{i}_{0} \subseteq \dotsc \subseteq \iterate{\mc{F}}{i}_{k-1} \subseteq \iterate{\mc{F}_k}{i} \subseteq \mc{F}}.
+Since at \me{\ith{k}} iteration, the feasible set of the problem \eqref{con-m} includes the feasible sets of the earlier iteration, we can see that
+\begin{equation} \label{con-convergence}
+f(\mz_0) \geq f(\mz_k) \geq f(\mz_{k+1}) \geq f(\mz_{\ast,y,i}). 
+\end{equation}
+Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point.
+Let \me{\mx_{\ast}} and \me{\mz_{\ast,y,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged.
+The symbol \me{y,i} in \me{\mz_{\ast,y,i}} denotes the optimal \me{\mz} with fixed \me{\my} at the \eqn{\ith{i}} \ac{BCDM} iteration.
+It can be seen from \cite{marks1978technical} that the optimal point of the converged subproblems is in deed the stationary point of the original nonconvex problem \eqref{con}.
+It can be easily verified by the \ac{KKT} expressions and the feasibility of the constraints.
+
+Once the optimal solution is found for the fixed \me{\my}, we fix the variable \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize \me{\my}.
+The problem is still nonconvex due to the \ac{DC} constraint.
+By following similar approach as we discussed for the variable \me{\mx}, we can obtain the optimal solution \me{\my_{k}} for the convex subproblem at the \me{\ith{k}} iteration.
+The convergence and the nonincreasing behavior of the problem follows similar explanations.
+Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,x,i}}.
+Following the arguments presented in \cite{marks1978technical}, the optimal point of the converged convex subproblems is a stationary point of the nonconvex problem in \eqref{con}.
+
+Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{BCDM} update, \textit{i.e}, \me{f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i+1})}.
+Let us assume that for an initial feasible value of \eqn{\my} at \eqn{\iterate{\my}{0}}, we achieve a stationary point of \eqref{con} by solving sequence of convex subproblems.
+The solution is given by \eqn{\mz_{\ast,y,0}} and \eqn{\mx_{\ast}}.
+Now, by fixing \eqn{\iterate{\mx}{0} = \mx_{\ast}}, we find the optimal solution \eqn{\mz_{\ast,x,0}} and \eqn{\my_{\ast}} by solving the convex subproblems.
 It can be seen that
-\begin{equation*}
-h(\mz) - {g}_0(\mx,\iterate{\myb}{i}) \leq h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k) \leq 0
-\end{equation*}
+\begin{equation}
+f_0(\mz_{k,y,0}) \geq f_0(\mz_{\ast,y,0}) \geq f_0(\mz_{0,x,0}) \geq f_0(\mz_{\ast,x,0}),
+\end{equation}
+which follows from the convexity of the objective function \eqn{f_0} and the initial \eqn{\iterate{\my}{0}} is also a feasible point for the variable \eqn{\my} of the \eqn{\ith{k}} subproblem.
+Using the property of induction, we can show that the global problem converges to a stationary point of the nonconvex problem \eqref{con} in a nonincreasing manner.
+
+Note that the uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of the proof.
+We can prove the uniqueness of the convex subproblems defined by \eqref{eqn-9} and \eqref{eqn-mse-2} using the following constraints.
+For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders is guaranteed by the constraint \eqref{eqn-8}, which can be written as
+\begin{equation}
+\gamma_{l,k,n} - \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
+\end{equation}
+where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the convex subproblem \eqref{eqn-mse-2}, uniqueness of the transmit precoder is guaranteed by the constraint
+\begin{multline}
+| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \\ + \enoise \leq \epsilon_{l,k,n}.
+\end{multline}
+Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.
 

### 2015-01-22 Report/ieee_journal.tex
changes with satya
satya_2
convergence_proof

@@
-\documentclass[10pt,final,onecolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 \usepackage[dvipdfmx]{graphicx}
+\usepackage[usenames,dvipsnames]{xcolor}
 \usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno,verbatim,todonotes,inputenc}
+\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,todonotes,inputenc,mathtools}
 
@@
 
-\section{Response to reviewer comments}
-\input{review_comments}
+%\section{Response to reviewer comments}
+%\input{review_comments}
 
@@
 \subsection{Reduced Complexity Resource Allocation} \label{sec-3.4}
-\input{sub_channel_wsrm}
+\review{\input{sub_channel_wsrm}}
 
@@
 
+\subsection{Average Backlogged Packets Over Slots}
+
+\review{\input{time_correlated}}
+
 %acresetall
@@
 
+\section{Tightness of \ac{SINR} relaxation} \label{a-3}
+\review{\input{appendix_tightness}}
+
 \section{\ac{KKT} conditions for \ac{MSE} approach} \label{a-1}

### 2015-01-23 Report/appendix_tightness.tex
manosha

@@
 Note that the new precoder has no impact on the interference constraint of other users.
-The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting other user rates, there by reduces the objective further.
-It is in contradiction to our original assumption that the power is utilized for the user \me{i} making the constraints loose.
+The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting the rates of other user, there by reduces the objective further.
+It is in contradiction to our original assumption that the precoders are optimal and the objective is minimum.
 It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget.

### 2015-01-23 Report/convergence_centralized.tex
manosha

@@
 
-Let us write the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+\subsubsection{Centralized Problem}
+
+Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
 \begin{IEEEeqnarray}{rCl} \label{con}
@@
 Before proceeding further, let us define the following notations.
-Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{BCDM} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point.
+Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{AO} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point.
 Since the problem \eqref{con} is nonconvex, it is not guaranteed to find the optimal solution.
-In order to solve for a suboptimal solution, let us resort to the \ac{BCDM} by fixing a block of variables and optimize for others.
-Since \ac{BCDM} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}.
+In order to solve for a suboptimal solution, let us resort to the \ac{AO} by fixing a block of variables and optimize for others.
+Since \ac{AO} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}.
 Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form.
-Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around a feasible point \me{\mxb_0 \in \mc{F}} as
+Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around a feasible point \me{\mxb_0 \in \mc{F}} by
 \begin{equation} \label{con-relax}
@@
 \end{equation}
-Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{BCDM} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as
+Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as
 \begin{subeqnarray} \label{con-m}
@@
 \end{subeqnarray}
-Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{F}}{i}_k}.
+Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{X}}{i}_{k} \subset \mc{F}}, where \me{\mc{X}} denotes the subset in which \me{\my} is fixed.
 In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\mx_k}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration.
@@
 \end{equation}
-since \me{{g}_0(\mx,\iterate{\myb}{i}) \leq \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k), \forall \mx \in \iterate{\mc{F}}{i}_{k-1}}, where \me{\mc{F}_0 = \mc{F}}.
+since \me{{g}_0(\mx,\iterate{\myb}{i}) \leq \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k), \forall \mx \in \iterate{\mc{X}}{i}_{k-1}}.
 Now, \me{\mx_{k+1}} is the solution and feasible for the \me{\ith{k}} subproblem, therefore, it satisfies
@@
 Using \eqref{con-sub-set}, we can prove that the solution \me{\mx_{k+1}} and \me{\mz_{k+1}} are feasible, since the initial point \me{\mx_{0}} was chosen to be feasible.
-In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iterate{\mc{F}}{i}_{0} \subseteq \dotsc \subseteq \iterate{\mc{F}}{i}_{k-1} \subseteq \iterate{\mc{F}_k}{i} \subseteq \mc{F}}.
+In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iterate{\mc{X}}{i}_{0} \subseteq \dots \subseteq \iterate{\mc{X}}{i}_{k-1} \subseteq \iterate{\mc{X}_k}{i} \subset \mc{F}}.
 Since at \me{\ith{k}} iteration, the feasible set of the problem \eqref{con-m} includes the feasible sets of the earlier iteration, we can see that
 \begin{equation} \label{con-convergence}
-f(\mz_0) \geq f(\mz_k) \geq f(\mz_{k+1}) \geq f(\mz_{\ast,y,i}). 
+f(\mz_0) \geq f(\mz_k) \geq f(\mz_{k+1}) \geq f(\mz_{\ast,x,i}). 
 \end{equation}
 Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point.
-Let \me{\mx_{\ast}} and \me{\mz_{\ast,y,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged.
-The symbol \me{y,i} in \me{\mz_{\ast,y,i}} denotes the optimal \me{\mz} with fixed \me{\my} at the \eqn{\ith{i}} \ac{BCDM} iteration.
-It can be seen from \cite{marks1978technical} that the optimal point of the converged subproblems is in deed the stationary point of the original nonconvex problem \eqref{con}.
-It can be easily verified by the \ac{KKT} expressions and the feasibility of the constraints.
+Let \me{\mx_{\ast}} and \me{\mz_{\ast,x,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged.
+The symbol \me{x,i} in \me{\mz_{\ast,x,i}} denotes the optimal \me{\mz} is found over the variable \me{\mx} at the \eqn{\ith{i}} \ac{AO} iteration.
+Note that this point need not be the stationary point of the original nonconvex problem \eqref{con} since it minimizes over the feasible set \me{\iterate{\mc{X}_{\ast}}{i} \subseteq \iterate{\mc{X}_{\ast}}{i+1} \subset \mc{F}}, which depend on the variable \me{\mx} only.
+The optimal point \me{\mz_{\ast,x,i}} of the convex subproblem \eqref{con-m} is a stationary point of the nonconvex problem \eqref{con} only over the set \me{\iterate{\mc{X}_{\ast}}{i}}.
 
@@
 The problem is still nonconvex due to the \ac{DC} constraint.
-By following similar approach as we discussed for the variable \me{\mx}, we can obtain the optimal solution \me{\my_{k}} for the convex subproblem at the \me{\ith{k}} iteration.
+By following similar approach as earlier, we can obtain an optimal solution \me{\my_{k}} for the convex subproblem at the \me{\ith{k}} iteration.
 The convergence and the nonincreasing behavior of the problem follows similar explanations.
-Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,x,i}}.
-Following the arguments presented in \cite{marks1978technical}, the optimal point of the converged convex subproblems is a stationary point of the nonconvex problem in \eqref{con}.
+Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,y,i}}.
+Note that the solution \me{\mz_{\ast,y,i}} is the minimizer for the subset \me{\iterate{\mc{Y}_{\ast}}{i}}
 
-Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{BCDM} update, \textit{i.e}, \me{f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i+1})}.
-Let us assume that for an initial feasible value of \eqn{\my} at \eqn{\iterate{\my}{0}}, we achieve a stationary point of \eqref{con} by solving sequence of convex subproblems.
-The solution is given by \eqn{\mz_{\ast,y,0}} and \eqn{\mx_{\ast}}.
-Now, by fixing \eqn{\iterate{\mx}{0} = \mx_{\ast}}, we find the optimal solution \eqn{\mz_{\ast,x,0}} and \eqn{\my_{\ast}} by solving the convex subproblems.
+Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, \me{f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i+1})}.
+Let us assume that for an initial feasible value of \eqn{\my} at \eqn{\iterate{\my}{0}}, we achieve a feasible point of \eqref{con} by solving sequence of convex subproblems.
+The solution is given by \eqn{\mz_{\ast,x,0}} and \eqn{\mx_{\ast}}.
+Now, by fixing \eqn{\iterate{\mx}{0} = \mx_{\ast}}, we find next feasible solution \eqn{\mz_{\ast,y,0}} and \eqn{\my_{\ast}} for \eqref{con} by solving the convex subproblems \eqref{con-m}.
 It can be seen that
 \begin{equation}
-f_0(\mz_{k,y,0}) \geq f_0(\mz_{\ast,y,0}) \geq f_0(\mz_{0,x,0}) \geq f_0(\mz_{\ast,x,0}),
+f_0(\mz_{k,x,0}) \geq f_0(\mz_{\ast,x,0}) \geq f_0(\mz_{0,y,0}) \geq f_0(\mz_{\ast,y,0}),
 \end{equation}
-which follows from the convexity of the objective function \eqn{f_0} and the initial \eqn{\iterate{\my}{0}} is also a feasible point for the variable \eqn{\my} of the \eqn{\ith{k}} subproblem.
-Using the property of induction, we can show that the global problem converges to a stationary point of the nonconvex problem \eqref{con} in a nonincreasing manner.
+which follows from the convexity of the objective function \eqn{f_0} and the initial \eqn{\iterate{\my}{0}} is also a feasible point for the variable \eqn{\my} at the \eqn{\ith{k}} subproblem, \textit{i.e},
+\begin{equation}
+\iterate{\mc{X}}{i}_{0} \dots \subseteq \iterate{\mc{X}}{i}_{\ast} \subseteq \iterate{\mc{Y}_{0}}{i} \dots \subseteq \iterate{\mc{Y}}{i}_{\ast} \subseteq \mc{F}.
+\end{equation}
+Using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.
 
-Note that the uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of the proof.
+To show the converged point of the iterative algorithm is in fact the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem.
+Since the converged point is the minimizer for the iterative algorithm such that
+\begin{equation} \label{con-opt}
+f_0(\mz_{\ast,x,i}) = f_0(\mz_{\ast,y,i}) = f_0(\mz_{\ast,x,i+1}),
+\end{equation}
+the solution is inside the feasible set \me{\mc{F}} and \me{\mz_{\ast,x,i+1}} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}, which includes all optimal points of \me{\mz} identified so far.
+Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mz_{\ast,x,i+1}} is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.
+
+Note that the uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO}.
 We can prove the uniqueness of the convex subproblems defined by \eqref{eqn-9} and \eqref{eqn-mse-2} using the following constraints.
 For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders is guaranteed by the constraint \eqref{eqn-8}, which can be written as
-\begin{equation}
-\gamma_{l,k,n} - \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
-\end{equation}
+\begin{multline}
+\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
+- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
+\end{multline}
 where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the convex subproblem \eqref{eqn-mse-2}, uniqueness of the transmit precoder is guaranteed by the constraint
 \begin{multline}
-| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \\ + \enoise \leq \epsilon_{l,k,n}.
+| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
 \end{multline}

### 2015-01-23 Report/kkt_mse_approach.tex
changes with satya
manosha

--- 2014-10-23 Report/kkt_mse_approach.tex
@@
-In this section, we discuss different ways to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}.
+In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}.
 In contrast to Section \ref{sec-4a}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
-The proposed methods in this section provide algorithms that can be of practical importance due to the limited signaling requirements.
+The proposed methods in this section provide algorithms that can be of practical importance \review{in the \ac{TDD} system} due to the limited signaling requirements.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
@@
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
-\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \, \|\mvec{w}{l,k,n}\|^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
+\alpha_{l,k,n} : & \hspace{0.5cm} & \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \eqspace \IEEEyessubnumber \label{kkt-mse-1.2} \\
 \sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
@@
 	\text{subject to} & \nonumber \\
-	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  N_0 \|\mvec{w}{l,k,n}\|^2 \nonumber \\
+	\alpha_{l,k,n} : &  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 +  \enoise \nonumber \\
 	& + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,k,n} \mvec{m}{x,y,n} \right |^2 \leq \epsilon_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.2} \\

### 2015-01-24 Report/appendix_tightness.tex
halfcooked

@@
 It is in contradiction to our original assumption that the precoders are optimal and the objective is minimum.
+
 It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget.
 Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.
+The objective of the \ac{JSFRA} problem can be modified to include the power term to find the minimum power precoders as
+\begin{equation*}
+\| \tilde{\mbf{v}} \|_q + \varphi \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \sum_{n = 1}^{N} \sum_{l=1}^{L} \|\mvec{m}{l,k,n}\|_2,
+\end{equation*}
+for a small \me{\varphi} which doesn't affect the optimal solution.
+Note that the above objective is guaranteed to make the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} tight by relaxing the power constraint \eqref{eqn-6.4}.

### 2015-01-24 Report/convergence_centralized.tex
halfcooked

@@
 \newcommand{\mz}{\mbf{z}}
-\newcommand{\mxb}{{\mbf{x}}}
-\newcommand{\myb}{{\mbf{y}}}
+\newcommand{\mxb}{{{\mbf{x}}}}
+\newcommand{\myb}{{{\mbf{y}}}}
 \newcommand{\iterate}[2]{{#1}^{(#2)}}
+\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
 
@@
 
+In order to solve the problem, we resort to \ac{AO} by fixing a block of varibles and optimize for others.
+In the problem \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint in \eqref{con-dc}.
+In order to solve the problem after fixing the variable \me{\my}, we adopt the \ac{SCA} approach presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets.
+Since the proposed method involves two level of iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
+Let \me{\iter{\mc{X}}{k}{i}} be a feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and for a fixed \me{\mx}, the set is represented as \me{\iter{\mc{Y}}{k}{i}}.
+Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denotes the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
+
+Without affecting the convergence proof, let us consider the variable \me{\my} is fixed in the iteration \me{i} for \ac{AO} and \me{k} for the \ac{SCA} problem to solve for the unique minimizer for \me{\mx \in \iter{\mc{X}}{k}{i}}.
+
+In order to solve for a suboptimal solution, let us resort to the \ac{AO} by fixing a block of variables and optimize for others.
 Before proceeding further, let us define the following notations.
-Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{AO} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point.
-Since the problem \eqref{con} is nonconvex, it is not guaranteed to find the optimal solution.
-In order to solve for a suboptimal solution, let us resort to the \ac{AO} by fixing a block of variables and optimize for others.
-Since \ac{AO} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}.
+Let \me{\iter{\mx}{k}{i}} denote the \me{\ith{i}} \ac{AO} operating point and \me{k} represent the \me{\ith{k}} \ac{SCA} point.
+Let us define a set \eqn{\iter{\mc{X}}{k}{i}} as set of feasible values of the subproblem in the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} optimization point for a fixed variable \me{\my}.
+Since \ac{AO} is an iterative method, let us begin by fixing \me{\my} with the previously found optimal value \me{\iter{\myb}{\ast}{i-1} \in \iter{\mc{Y}}{\ast}{i-1} \subset \mc{F}}, where \me{\ast} in subscript denotes the optimal value over some set \me{\mc{Y}}.
 Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form.
-Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around a feasible point \me{\mxb_0 \in \mc{F}} by
+Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1}, the function \me{g_0(\mx,\iter{\myb}{\ast}{i-1})} is linearized around a fixed feasible point \me{\iter{\mxb}{\ast}{i} \in \iter{\mc{X}}{\ast}{i-1} \subset \mc{F}} by
 \begin{equation} \label{con-relax}
-\hat{g}_o(\mx,\iterate{\myb}{0};\mxb_0) = {g}_0(\mxb_0,\iterate{\myb}{0}) + \nabla g_0(\mxb_0,\iterate{\myb}{0})^\mathrm{T} (\mx - \mx_0).
+\hat{g}_o(\mx,\iter{\myb}{\ast}{i-1});\iter{\mx}{k}{i})) = {g}_0(\iterate{\mxb}{0},\iterate{\myb}{0}) + \nabla g_0(\iterate{\mxb}{0},\iterate{\myb}{0})^\mathrm{T} (\mx - \iterate{\mxb}{0}).
 \end{equation}
@@
 	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj-m} \\
-	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mx_k) \leq 0 \eqsub \label{con-dc-m} \\
+	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\iterate{\mxb}{k}) \leq 0 \eqsub \label{con-dc-m} \\
 	&\quad& g_1(\mx,\iterate{\myb}{i}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
@@
 Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{X}}{i}_{k} \subset \mc{F}}, where \me{\mc{X}} denotes the subset in which \me{\my} is fixed.
-In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\mx_k}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration.
-To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\mx_k} is feasible for \eqref{con-m}.
-Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\mx_k}, it satisfies
+In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\iter{\mxb}{k}{i}}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration.
+To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\iterate{\mxb}{k}} is feasible for \eqref{con-m}.
+Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\iterate{\mxb}{k}}, it satisfies
 \begin{equation}
@@
 The symbol \me{x,i} in \me{\mz_{\ast,x,i}} denotes the optimal \me{\mz} is found over the variable \me{\mx} at the \eqn{\ith{i}} \ac{AO} iteration.
-Note that this point need not be the stationary point of the original nonconvex problem \eqref{con} since it minimizes over the feasible set \me{\iterate{\mc{X}_{\ast}}{i} \subseteq \iterate{\mc{X}_{\ast}}{i+1} \subset \mc{F}}, which depend on the variable \me{\mx} only.
-The optimal point \me{\mz_{\ast,x,i}} of the convex subproblem \eqref{con-m} is a stationary point of the nonconvex problem \eqref{con} only over the set \me{\iterate{\mc{X}_{\ast}}{i}}.
+Note that this point need not be a stationary point of the problem \eqref{con}, since it is the minimizer only in the feasible set \me{\iterate{\mc{X}_{\ast}}{i} \subset \mc{F}}, which depend on \me{\mx} only.
 
-Once the optimal solution is found for the fixed \me{\my}, we fix the variable \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize \me{\my}.
+Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize for \me{\my}.
 The problem is still nonconvex due to the \ac{DC} constraint.
-By following similar approach as earlier, we can obtain an optimal solution \me{\my_{k}} for the convex subproblem at the \me{\ith{k}} iteration.
-The convergence and the nonincreasing behavior of the problem follows similar explanations.
+By following similar approach, we can obtain the minimizer \me{\my_{k}} for the convex subproblem at each iteration \me{{k}}.
+The convergence and the nonincreasing behavior of the problem follows similar arguments as above.
 Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,y,i}}.
-Note that the solution \me{\mz_{\ast,y,i}} is the minimizer for the subset \me{\iterate{\mc{Y}_{\ast}}{i}}
+Note that the solution \me{\mz_{\ast,y,i}} is the minimizer in the subset \me{\iterate{\mc{Y}_{\ast}}{i}}.
 
 Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, \me{f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i+1})}.
-Let us assume that for an initial feasible value of \eqn{\my} at \eqn{\iterate{\my}{0}}, we achieve a feasible point of \eqref{con} by solving sequence of convex subproblems.
-The solution is given by \eqn{\mz_{\ast,x,0}} and \eqn{\mx_{\ast}}.
-Now, by fixing \eqn{\iterate{\mx}{0} = \mx_{\ast}}, we find next feasible solution \eqn{\mz_{\ast,y,0}} and \eqn{\my_{\ast}} for \eqref{con} by solving the convex subproblems \eqref{con-m}.
-It can be seen that
-\begin{equation}
-f_0(\mz_{k,x,0}) \geq f_0(\mz_{\ast,x,0}) \geq f_0(\mz_{0,y,0}) \geq f_0(\mz_{\ast,y,0}),
-\end{equation}
-which follows from the convexity of the objective function \eqn{f_0} and the initial \eqn{\iterate{\my}{0}} is also a feasible point for the variable \eqn{\my} at the \eqn{\ith{k}} subproblem, \textit{i.e},
-\begin{equation}
-\iterate{\mc{X}}{i}_{0} \dots \subseteq \iterate{\mc{X}}{i}_{\ast} \subseteq \iterate{\mc{Y}_{0}}{i} \dots \subseteq \iterate{\mc{Y}}{i}_{\ast} \subseteq \mc{F}.
-\end{equation}
-Using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.
+Let us consider the \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} is obtained as \eqn{\mx^{(i)}_{\ast}} and \eqn{\mz_{\ast,x,i}} using a fixed \eqn{\my} as \eqn{\my_{\ast}^{(i-1)}}.
+In order to find \eqn{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \eqn{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
+Since the problem \eqref{con} is nonconvex even after fixing \me{\mx}, we have to linearize the convex function in the \ac{DC} constraint \eqref{con-dc} around some fixed operating point of \me{\my}.
+Since the linearization is performed with the earlier optimal point \eqn{\iter{\my}{\ast}{i-1}}, the feasible set now includes \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\} \in \mc{Y}^{(i)}_{0}}.
+Now the optimization is performed to find the optimal \me{\my} using the relaxed problem \eqref{con-m}, the optimal solution \me{\mz_{0,y,i}} for the initial iteration after \ac{AO} update follows \me{f_0(\mz_{0,y,i}) \leq f_0(\mz_{\ast,x,i})}, since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}}.
+Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}} since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
+Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.
 

### 2015-01-24 Report/convergence_centralized.tex
modified

@@
 \begin{IEEEeqnarray}{rCl} \label{con}
-\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj} \\
+\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
 \text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
@@
 Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denotes the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
+For the sake of clarity, we define the optimal value of \me{\mz} obtained for the \me{\ith{i}} \ac{AO} iterate for the fixed \me{\my} variable as \me{\iter{\mz}{\ast|y}{i}}.
 
-Without affecting the convergence proof, let us consider the variable \me{\my} is fixed in the iteration \me{i} for \ac{AO} and \me{k} for the \ac{SCA} problem to solve for the unique minimizer for \me{\mx \in \iter{\mc{X}}{k}{i}}.
-
-In order to solve for a suboptimal solution, let us resort to the \ac{AO} by fixing a block of variables and optimize for others.
-Before proceeding further, let us define the following notations.
-Let \me{\iter{\mx}{k}{i}} denote the \me{\ith{i}} \ac{AO} operating point and \me{k} represent the \me{\ith{k}} \ac{SCA} point.
-Let us define a set \eqn{\iter{\mc{X}}{k}{i}} as set of feasible values of the subproblem in the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} optimization point for a fixed variable \me{\my}.
-Since \ac{AO} is an iterative method, let us begin by fixing \me{\my} with the previously found optimal value \me{\iter{\myb}{\ast}{i-1} \in \iter{\mc{Y}}{\ast}{i-1} \subset \mc{F}}, where \me{\ast} in subscript denotes the optimal value over some set \me{\mc{Y}}.
-Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form.
-Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1}, the function \me{g_0(\mx,\iter{\myb}{\ast}{i-1})} is linearized around a fixed feasible point \me{\iter{\mxb}{\ast}{i} \in \iter{\mc{X}}{\ast}{i-1} \subset \mc{F}} by
-\begin{equation} \label{con-relax}
-\hat{g}_o(\mx,\iter{\myb}{\ast}{i-1});\iter{\mx}{k}{i})) = {g}_0(\iterate{\mxb}{0},\iterate{\myb}{0}) + \nabla g_0(\iterate{\mxb}{0},\iterate{\myb}{0})^\mathrm{T} (\mx - \iterate{\mxb}{0}).
-\end{equation}
-Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as
+Let us consider the order for \ac{AO} by optimizing variable \me{\mx} before optimizing the variable \me{\my}.
+Without affecting the convergence proof, let us consider the variable \me{\my} is fixed for the \ac{AO} \me{i} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
+In order to find the optimal value of \me{\mx} for the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate of \me{\mx} as
+\begin{multline} \label{con-relax}
+\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+\end{multline}
+Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
 \begin{subeqnarray} \label{con-m}
-	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj-m} \\
-	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\iterate{\mxb}{k}) \leq 0 \eqsub \label{con-dc-m} \\
-	&\quad& g_1(\mx,\iterate{\myb}{i}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
+	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
+	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
+	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
 	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
 \end{subeqnarray}
-Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{X}}{i}_{k} \subset \mc{F}}, where \me{\mc{X}} denotes the subset in which \me{\my} is fixed.
-In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\iter{\mxb}{k}{i}}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration.
-To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\iterate{\mxb}{k}} is feasible for \eqref{con-m}.
-Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\iterate{\mxb}{k}}, it satisfies
+Let the set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
+In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\my = \iter{\my}{\ast}{i-1}} operating at \me{\iter{\mx}{k}{i}}, let us assume that \eqref{con-m} yields \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution at the \me{\ith{k}} iteration.
+To show \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} minimizes the objective function ans also feasible, let us assume that the point \me{\iter{\mx}{k}{i} \in \iter{\mc{X}}{k}{i}}, which is feasible for \eqref{con-m}.
+Since the function \me{{g}_0(\mx,\iter{\my}{\ast}{i-1}} is linearized at \me{\iter{\mx}{k}{i}}, it satisfies
 \begin{equation}
-h(\mz) - {g}_0(\mx,\iterate{\myb}{i}) \leq h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k) \leq 0,
+h(\mz) - {g}_0(\mx,\iter{\my}{\ast}{i-1}) \leq h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0,
 \end{equation}
-since \me{{g}_0(\mx,\iterate{\myb}{i}) \leq \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k), \forall \mx \in \iterate{\mc{X}}{i}_{k-1}}.
-Now, \me{\mx_{k+1}} is the solution and feasible for the \me{\ith{k}} subproblem, therefore, it satisfies
-\begin{multline}
-h(\mz_{k+1}) - {g}_0(\mx_{k+1},\iterate{\myb}{i}) \leq h(\mz_{k+1}) - \hat{g}_0(\mx_{k+1},\iterate{\myb}{i};\mxb_k) \\
-\leq h(\mz_{k}) - \hat{g}_0(\mx_{k},\iterate{\myb}{i};\mxb_k) \leq 0. \label{con-sub-set}
+since \me{{g}_0(\mx,\iter{\my}{\ast}{i-1}) \leq \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}), \forall \mx \in \iter{\mc{X}}{k}{i}}.
+Now, \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are the optimal and feasible point for the \me{\ith{k}} subproblem \eqref{con-m}, it satisfies
+\begin{multline}\label{con-sub-set}
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\
+\leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 
 \end{multline}
-Using \eqref{con-sub-set}, we can prove that the solution \me{\mx_{k+1}} and \me{\mz_{k+1}} are feasible, since the initial point \me{\mx_{0}} was chosen to be feasible.
-In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iterate{\mc{X}}{i}_{0} \subseteq \dots \subseteq \iterate{\mc{X}}{i}_{k-1} \subseteq \iterate{\mc{X}_k}{i} \subset \mc{F}}.
-Since at \me{\ith{k}} iteration, the feasible set of the problem \eqref{con-m} includes the feasible sets of the earlier iteration, we can see that
-\begin{equation} \label{con-convergence}
-f(\mz_0) \geq f(\mz_k) \geq f(\mz_{k+1}) \geq f(\mz_{\ast,x,i}). 
-\end{equation}
-Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point.
-Let \me{\mx_{\ast}} and \me{\mz_{\ast,x,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged.
-The symbol \me{x,i} in \me{\mz_{\ast,x,i}} denotes the optimal \me{\mz} is found over the variable \me{\mx} at the \eqn{\ith{i}} \ac{AO} iteration.
-Note that this point need not be a stationary point of the problem \eqref{con}, since it is the minimizer only in the feasible set \me{\iterate{\mc{X}_{\ast}}{i} \subset \mc{F}}, which depend on \me{\mx} only.
+Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
+In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iter{\mc{X}}{0}{i} \subseteq \dots \subseteq \iter{\mc{X}}{k-1}{i} \subseteq \iter{\mc{X}}{k}{i} \subset \mc{F}}.
+Since the feasible set of the problem \eqref{con-m} includes the feasible sets from the earlier iteration, we arrive at
+\begin{multline} \label{con-convergence}
+f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
+\end{multline}
+Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and converges to a critical point.
+Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point of the problem \eqref{con}, since it is the minimizer only in the feasible set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, which depends on \me{\mx} and \me{\mz} only.
 
-Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize for \me{\my}.
-The problem is still nonconvex due to the \ac{DC} constraint.
-By following similar approach, we can obtain the minimizer \me{\my_{k}} for the convex subproblem at each iteration \me{{k}}.
+Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
+Even after treating \me{\mx} as a constant, the problem is still nonconvex due to the \ac{DC} constraint.
+Following similar approach, we can find the minimizer \me{\iter{\my}{k}{i}} and \me{\iter{\mz}{k}{i}} for the convex subproblem \eqref{con-m} at each iteration \me{{k}}.
+Note that \me{\iter{\mz}{k}{i}} is reused since the variable \me{\mx} is fixed for the \me{\ith{i}} \ac{AO} iteration.
 The convergence and the nonincreasing behavior of the problem follows similar arguments as above.
-Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,y,i}}.
-Note that the solution \me{\mz_{\ast,y,i}} is the minimizer in the subset \me{\iterate{\mc{Y}_{\ast}}{i}}.
+Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
+Note that the solution point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i})} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
 
-Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, \me{f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i+1})}.
-Let us consider the \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} is obtained as \eqn{\mx^{(i)}_{\ast}} and \eqn{\mz_{\ast,x,i}} using a fixed \eqn{\my} as \eqn{\my_{\ast}^{(i-1)}}.
-In order to find \eqn{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \eqn{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
+Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
+\begin{equation*}
+f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
+\end{equation*}
+Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mx}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
+In order to find \me{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
 Since the problem \eqref{con} is nonconvex even after fixing \me{\mx}, we have to linearize the convex function in the \ac{DC} constraint \eqref{con-dc} around some fixed operating point of \me{\my}.
-Since the linearization is performed with the earlier optimal point \eqn{\iter{\my}{\ast}{i-1}}, the feasible set now includes \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\} \in \mc{Y}^{(i)}_{0}}.
-Now the optimization is performed to find the optimal \me{\my} using the relaxed problem \eqref{con-m}, the optimal solution \me{\mz_{0,y,i}} for the initial iteration after \ac{AO} update follows \me{f_0(\mz_{0,y,i}) \leq f_0(\mz_{\ast,x,i})}, since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}}.
-Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}} since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
+Since we know that \me{\iter{\my}{\ast}{i-1}} is already a feasible point for \me{\my} along with \me{\iter{\mx}{\ast}{i}}, linearization is performed around this feasible point.
+Using the inequality in \eqref{con-sub-set}, we can show that \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}}.
+Now the optimization is performed to find the optimal \me{\my} using the relaxed subproblem \eqref{con-m}, the optimal solution \me{\iter{\mz}{0}{i}} for the initial iteration after \ac{AO} update follows
+\begin{equation*}
+f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}),
+\end{equation*}
+since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}} as the operating point for \ac{AO} and \ac{SCA} iteration.
+Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}}, since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
 Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.
@@
 Since the converged point is the minimizer for the iterative algorithm such that
-\begin{equation} \label{con-opt}
-f_0(\mz_{\ast,x,i}) = f_0(\mz_{\ast,y,i}) = f_0(\mz_{\ast,x,i+1}),
-\end{equation}
-the solution is inside the feasible set \me{\mc{F}} and \me{\mz_{\ast,x,i+1}} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}, which includes all optimal points of \me{\mz} identified so far.
-Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mz_{\ast,x,i+1}} is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+\begin{multline} \label{con-opt}
+f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
+f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
+\end{multline}
+the solution is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
 The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.
 
-Note that the uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO}.
-We can prove the uniqueness of the convex subproblems defined by \eqref{eqn-9} and \eqref{eqn-mse-2} using the following constraints.
-For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders is guaranteed by the constraint \eqref{eqn-8}, which can be written as
+The uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO}.
+For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders are guaranteed by the constraint \eqref{eqn-8}, which can be written as
 \begin{multline}
@@
 \end{multline}
-where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the convex subproblem \eqref{eqn-mse-2}, uniqueness of the transmit precoder is guaranteed by the constraint
+where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the \eqref{eqn-mse-2} by
 \begin{multline}

### 2015-01-24 Report/ieee_journal.tex
manosha
modified

@@
 \usepackage[ruled]{algorithm2e}
-\usepackage[dvipdfmx]{graphicx}
+\usepackage[dvips]{graphicx}
 \usepackage[usenames,dvipsnames]{xcolor}
 \usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,todonotes,inputenc,mathtools}
+\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}
 
@@
 
-\subsection{Convergence Analysis} \label{sec-3.5}
-\input{convergence_centralized}
-
 \section{Distributed Solutions} \label{sec-4}
@@
 
+\subsection{Convergence Analysis} \label{sec-3.5}
+\input{convergence_centralized}
+
 \section{\ac{KKT} conditions for \ac{MSE} approach} \label{a-1}

### 2015-01-27 Report/joint_wsrm_formulation.tex
changes with satya
reductions

--- 2014-10-09 Report/joint_wsrm_formulation.tex
@@
 Since at each time slot, the system is described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state.
-Following similar approach as in \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
+By following \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
 \begin{equation}
@@
 The expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the number of backlogged packets corresponding to the users.
-The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, where the queue weighted sum rate maximization is considered as the objective function to determine the transmit precoders.
-Since the expectation can be minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
+The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, in which the queues are used as weights in the \ac{WSRM} formulation to determine the transmit precoders.
+Since the expectation is minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
 \begin{IEEEeqnarray}{LCl} \label{q_gen_sum}
-	\underset{\substack{\mvec{M}{k,n}, \mvec{W}{k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
-	\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-3.1.3}
+	\underset{\substack{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
+	\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b.
+\IEEEyessubnumber \eqspace \label{eqn-3.1.3}
 \end{IEEEeqnarray}
@@
 where the precoders are associated with \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}.
-By using the number of queued packets as the weights, the resources can be allocated to the user with the more backlogged packets, which essentially does the allocation in a greedy manner.
+By using the number of queued packets as the weights, the resources can be allocated to the user with the more backlogged packets, which essentially does greedy allocation.
 

### 2015-01-27 Report/problem_formulation_intro.tex
reductions

@@
 \end{equation}
-where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}}.
+where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}}\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
 
@@
 where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}.
-Let \me{\mbf{M}_{k,n} \triangleq [ \, \mvec{m}{1,k,n} \, \mvec{m}{2,k,n} \dotsc \mvec{m}{L,k,n} \,]} be the matrix formed by stacking the beamformers associated with user \me{k} for \me{n^\mathrm{th}} sub-channel transmission.
-Similarly, let \me{\mbf{W}_{k,n} \triangleq [ \, \mvec{w}{1,k,n} \, \mvec{w}{2,k,n} \dotsc \mvec{w}{L,k,n} \,]} denotes the matrix formed by stacking the receive beamformers respectively\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
-In \eqref{eqn-4.3}, we consider a \ac{BS} specific sum power constraint for each \ac{BS} across all sub-channels.
+In \eqref{eqn-4.3}, \ac{BS} specific sum power constraint for all sub-channels is considered.
 

### 2015-01-28 Report/dual_approach.tex
updated final with kkt conditions
changes with satya
halfcooked

@@
 \text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
-&& \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-dual-1d} \\
+&& \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \label{eqn-dual-1d} \\
 && \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-	\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) \vspace{-0.25cm} \nonumber \\
-	&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \vspace{-0.25cm} \\
+	\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right )  \nonumber \\
+	&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\
 	\text{subject to} &\quad& \nonumber \\
 	\beta_{l,k,n} \geq \sum_{\mathclap{j = 1,j \neq l}}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
-	+ \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + N_0\|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\
+	+ \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\
 	\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
@@
 			\Repeat{convergence or \me{j \geq J_{\max}}}{
-				solve for \me{\mvec{M}{k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
+				solve for \me{\mvec{m}{l,k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
 				exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
@@
 			}
-			downlink precoded pilot transmission with \me{\mvec{M}{k,n}}\;
-			update \me{\mvec{W}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
-			update \me{\tilde{\mbfa{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
+			downlink precoded pilot transmission with \me{\mvec{m}{k,n}}\;
+			update \me{\mvec{l}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
+			update \me{{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
 			$i = i + 1$ \;
@@
 Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.
+\end{comment}

### 2015-01-28 Report/kkt_mse_approach.tex
halfcooked

@@
 \begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
-\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
+\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
 \text{subject to} & \hspace{0.5cm} & \nonumber \\
@@
 \begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
-	\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \\ \epsilon_{l,k,n}, \mvec{W}{k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
+	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
 	\text{subject to} & \nonumber \\
@@
 
-The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive beamformers \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors.
+The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive beamformers \me{\mvec{m}{l,k,n},\mvec{w}{l,k,n}} with the single user beamforming and the \ac{MMSE} vectors.
 The dual variable \me{\alpha}'s are initialized with ones to have equal priorities to all the users in the system.
@@
  \Repeat{until convergence or \me{i \geq I_{\max}}}{
-	update \me{\mvec{M}{k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
-	find \me{\mvec{W}{k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
-	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{W}{k,n}^{(i)}} \;
-	using precoded uplink pilots, \me{\mvec{W}{k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
+	update \me{\mvec{m}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
+	find \me{\mvec{w}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;
+	evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{w}{l,k,n}^{(i)}} \;
+	using precoded uplink pilots, \me{\mvec{m}{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
 	\me{i = i + 1} \;

### 2015-01-28 Report/sub_channel_wsrm.tex
halfcooked

@@
-The complexity involved in the \ac{JSFRA} scheme scales significantly with the increase in the number of sub-channels considered in the formulation.
-In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size.
-In order to mitigate this, we can adopt the decomposition techniques discussed in \cite{palomar2006tutorial,boyd2011distributed} to distribute the precoder design across each sub-channels independently with some coupling parameters that are exchanged across the sub-channel wise subproblems.
+The complexity of the \ac{JSFRA} algorithm scales with the number of sub-channels considered.
+In addition, the iterations required for the convergence of the algorithm increases with the problem size.
+In order to overcome the complexity, we can perform the distributed approaches presented in \cite{palomar2006tutorial,boyd2011distributed} for sub-channel wise precoder design using primal or dual decomposition.
 
-As an alternative sub-optimal solution, we propose \acl{QM} \ac{SRA}, which aims at designing the precoders independently across each sub-channel in a sequential manner by taking the current backlogged packets into account.
-In this approach, the transmit power is fixed across each sub-channel \me{n} as \me{P_{\max,n}} at each \ac{BS}.
-The power split can either follow equal sharing or any predetermined pattern as in partial frequency reuse.
-For the fixed sub-channel power, the \ac{JSFRA} formulation presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} is performed over each sub-channel in a sequential manner.
+As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which design precoders independently across the sub-channels in a sequential manner using the unserviced number of packets after each sub-channel.
+The transmit power is fixed across each sub-channel \me{n} as \me{P_{\max,n}} for each \ac{BS}.
+The power either be equal sharing or based on predetermined pattern as in partial frequency reuse.
+For a fixed sub-channel power, the \ac{JSFRA} formulation presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} is performed over each sub-channel in a sequential manner.
 The coupling variable across the sub-channel is the total number of backlogged packets associated with each user.

### 2015-01-28 Report/wsrm_formulation.tex
reductions
halfcooked

@@
 This procedure is carried out until convergence of the queue deviation or for fixed number of iterations by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
+The convergence proof is discussed in Appendix \ref{sec-3.5}
 {\allowdisplaybreaks
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{M}}_{k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
- update \me{\mvec{W}{k,n}} and \me{{\mbf{u}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} using \me{\tilde{\mbf{M}}_{k,n}}\;
+ \KwInit{\me{i=0} and transmit precoders \me{\mbf{m}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
+ update \me{\mvec{w}{l,k,n}, \mbf{u}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} with \me{{\mbf{m}}_{l,k,n}}\;
  \Repeat{Queue convergence or \me{i \geq I_{\max}}}{

### 2015-01-28 Report/appendix_tightness.tex
halfcooked

--- 2015-01-23 Report/appendix_tightness.tex
@@
 	&\quad& \beta_{k} \geq N_0 + \sum_{\mathclap{i \neq k}} |\mvec{H}{k} \mvec{m}{i} |^2 \IEEEyessubnumber \label{ae-2} \\
-	&\quad& \sum_{k \in \mc{U}_b} \text{tr} \, (\mvec{m}{k} \mvec{m}{k}^\herm) \leq P_{{\max}}. \IEEEyessubnumber \label{ae-3}
+	&\quad& \sum_{k \in \mc{U}_b} \trace \, (\mvec{m}{k} \mvec{m}{k}^\herm) \leq P_{{\max}}. \IEEEyessubnumber \label{ae-3}
 \end{IEEEeqnarray}
@@
 It is in contradiction to our original assumption that the precoders are optimal and the objective is minimum.
+
 It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget.
-Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.
+Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to empty the current backlogged packets in the system.
+The objective of the \ac{JSFRA} problem can be regularized by including the power term to find the minimum power precoders as
+\begin{equation*}
+\| \tilde{\mbf{v}} \|_q + \varphi \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
+\end{equation*}
+for a small \me{\varphi} without affecting the optimal solution.
+Note that the above objective is guaranteed to make the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} active by relaxing the power constraint \eqref{eqn-6.4}.

### 2015-01-28 Report/convergence_centralized.tex
halfcooked

@@
 \newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
-
-\subsubsection{Centralized Problem}
-
 Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
@@
 Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}}, since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
-Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.
+Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner\footnote{Note that the objective is monotonically decreasing even if the \ac{SCA} subproblem \eqref{con-m} is terminated after predetermined number iterations or for certain accuracy.}.
 

### 2015-01-28 Report/convergence_distributed.tex
halfcooked

--- 2015-01-28 Report/dual_approach.tex
@@
-The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties.
-In contrast to the \acl{PD} problem, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
-In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution.
-Now the sub problems are coupled by the global consensus vector \me{\mbfa{\zeta}} maintaining the complete stacked  interference profile of all users in the system as
-\begin{IEEEeqnarray}{ll}
-\mbfa{\zeta} &= \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1}, \right. \nonumber \\
-& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
-n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
-\end{IEEEeqnarray}
-
-Let \me{\mbfa{\zeta}(b_k)} denote the consensus entries corresponding to \ac{BS} \me{b_k}.
-Let \me{\mbfa{\nu}^{\set{b_k}}} represent the stacked dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} used in the subproblems.
-In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} in \ac{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} in the objective function.
-At optimality, the locally assumed and the consensus interference values will be equal,  providing no contribution to the objective function.
-The optimal step size used to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed,bertsekas1999nonlinear}.
-The equality constraint for the local and the consensus interference vector \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} present in each subproblem is relaxed by the taking the partial Lagrangian.
-Now, the subproblem at \ac{BS} \me{b} for the \me{\ith{i}} iteration is given by
-\iftoggle{single_column}{\allowdisplaybreaks
-\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
-\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
-&& \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \label{eqn-dual-1d} \\
-&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
-&\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3}, \IEEEyessubnumber \label{eqn-dual-1f}
-\end{IEEEeqnarray}
-}{{\allowdisplaybreaks
-\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-	\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right )  \nonumber \\
-	&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\
-	\text{subject to} &\quad& \nonumber \\
-	\beta_{l,k,n} \geq \sum_{\mathclap{j = 1,j \neq l}}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
-	+ \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\
-	\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
-	&& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3}, \IEEEyessubnumber \label{eqn-dual-1f}
-\end{IEEEeqnarray}}}
-where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i-1)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.
-
-Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}.
-Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}.
-Since the entries in \me{\mbfa{\zeta}^{(i)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}.
-For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
-\begin{equation}
-\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
-\label{zeta_update}
-\end{equation}
-The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which includes the stacked dual variables of the interference equality constraint at \ac{BS} \me{b_k}, are updated using the subgradient as
-\begin{equation}\label{dual-sg-update}
-\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ).
-\end{equation}
-The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
-{\allowdisplaybreaks 
-\begin{algorithm}
-	\SetAlgoLined
-	\DontPrintSemicolon
-	\BlankLine
-	\SetKwInput{KwInit}{Initialize}
-	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
-	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
-	\KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
-	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;
-	initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
-	initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
-	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
-		\Repeat{convergence or \me{i \geq I_{\max}}}{
-			initialize \me{j=0} \;
-			\Repeat{convergence or \me{j \geq J_{\max}}}{
-				solve for \me{\mvec{m}{l,k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
-				exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
-				update dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update}\;
-				update the consensus vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update}\;
-				\me{j = j + 1}\;
-			}
-			downlink precoded pilot transmission with \me{\mvec{m}{k,n}}\;
-			update \me{\mvec{l}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
-			update \me{{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
-			$i = i + 1$ \;
-		}
-	}
-	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
-	\label{algo-3}
-\end{algorithm}}
-
-\begin{comment}
-\subsubsection*{Convergence}
 The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point.
@@
 Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.
-\end{comment}

### 2015-01-28 Report/decomposition_solutions.tex
changes with satya
halfcooked

--- 2014-10-16 Report/decomposition_solutions.tex
@@
-This section addresses the distributed precoder designs for the proposed \ac{JSFRA} scheme.
-The formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
-In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are considered.
-In particular, the \acl{PD} and the \ac{ADMM} based \acl{DD} approaches are addressed.
+The distributed precoder designs for the proposed \ac{JSFRA} scheme are discussed in this section.
+The \review{convex} formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
+In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are addressed.
+In particular, the \acl{PD} and the \ac{ADMM} based \acl{DD} approaches are considered.
 
 To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-In order to study the decomposition based solutions, we consider the solution proposed in \eqref{eqn-9}, which is based on the Taylor series approximation for the nonconvex constraint.
+Let us consider the \review{convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented} in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint.
 The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well.
@@
 \begin{IEEEeqnarray}{CCl} \label{eqn-decent-1}
-\underset{\substack{\gamma_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
+\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
 \text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e}, \IEEEyessubnumber
@@
 
-Following similar approach as in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in \me{\mathcal{B}} as
+Following the approaches presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in \me{\mathcal{B}} as
 \iftoggle{single_column}{
@@
 \beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; N_0\|\mvec{w}{l,k,n}\|^2,
+&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; \enoise,
 \end{IEEEeqnarray}}{\allowdisplaybreaks
 \begin{multline}\label{eqn-decent-3}
-	N_0\|\mvec{w}{l,k,n}\|^2 + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
+	\enoise + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
 	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n},
 \end{multline}}
-where \me{\zeta_{l,k,n,b}} is the total interference caused by \ac{BS} \me{b} to the \me{\ith{l}} stream of user \me{k \in \mc{U}_{b_k}} on the \me{\ith{n}} sub-channel, is upper bounded by
+where \me{\zeta_{l,k,n,b}} is the total interference caused by the transmission of \ac{BS} \me{b} to user \me{k \in \mc{U}_{b_k}} in the spatial stream \me{l} and sub-channel \me{n}.
+It is given by the following upper bound as
 \begin{equation}
@@
 
-The coupling variable \me{\beta_{l,k,n}} can be decoupled using the variable \me{\zeta_{l,k,n,b}}, which limits the total interference caused by the transmission from \ac{BS} \me{b} to the \me{\ith{l}} spatial stream of user \me{k} over the sub-channel \me{n}.
-In order the solve for the global optimal precoders, we need to find the coupling variables \me{\zeta_{l,k,n,b}} by either the primal or \acl{DD} method.
-In both approaches, the coupling constraint \eqref{eqn-9.1c} for the \ac{SCA} and \eqref{eqn-mse-1.3} for the \ac{MSE} relaxation schemes are decoupled to perform the distributed precoder design problem.
+The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} by an iterative master-slave model using either primal or \acl{DD} method.
+The coupling variables are controlled by the master problem and the slave problems solve for the optimization variables associated with itself only.
+Now, to decouple the problem in \eqref{eqn-decent-1}, the coupling variable \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3}, which bind all \acp{BS} in \me{\mc{B}}, is replaced by a \ac{BS} specific variable \me{\zeta_{l,k,n,b}^{\{b_k\}}}.
+Using the \ac{BS} specific variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in \eqref{eqn-decent-3}, the subproblem in \eqref{eqn-decent-1} decouples completely for each \ac{BS} to find the precoders only for the users associated with the \ac{BS} \me{b_k}.
+The slave subproblems with the \ac{BS} specific interference variables are controlled by a master subproblem, which determines the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in accordance with the global objective.

### 2015-01-28 Report/dual_approach.tex
halfcooked

@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
 \text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-	\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right )  \nonumber \\
+	\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right )  \nonumber \\
 	&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\
@@
 	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
-	\KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
+	\KwInit{\me{i=0} and the transmit precoders \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
 	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;

### 2015-01-28 Report/kkt_mse_approach.tex
halfcooked

@@
 In contrast to Section \ref{sec-4a}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
-The proposed methods in this section provide algorithms that can be of practical importance \review{in the \ac{TDD} system} due to the limited signaling requirements.
+The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements.
+\review{We consider a \ac{TDD} system due to the unquantized channel state information at the transmitter}.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
@@
 \sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
-\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
+\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
-	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
+	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
 \end{IEEEeqnarray}

### 2015-01-28 Report/mse_formulation.tex
halfcooked

@@
 \begin{multline} \label{mse-error}
-	\epsilon_{l,k,n} = \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise,
+	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n},
 \end{multline}
@@
 \begin{multline} \label{mse-error}
- \epsilon_{l,k,n} = \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
- + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise,
+ \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
+ + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n},
 \end{multline}
@@
 \begin{equation} \label{eqn-mse-eq}
-\epsilon_{l,k,n} = \frac{1}{1 + \gamma_{l,k,n}}.
+\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
 \end{equation}
@@
 	& \qquad + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
-	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
+	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
 \end{IEEEeqnarray}}}

### 2015-01-28 Report/primal_approach.tex
halfcooked

@@
+In \acl{PD}, each slave subproblem are solved the optimal transmit precoders for a fixed \ac{BS} specific interference terms \me{\zeta_{l,k,n,b}^{\{b_k\}}}.
+The coupling variables \me{\zeta_{l,k,n,b}^{\{b_k\}}} associated with all \acp{BS} are updated by a master subproblem in accordance with the global objective of minimizing the backlogged packets.
+The master subproblem updates the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} by exchanging the dual variables corresponding to the interference constraint \eqref{eqn-decent-3} for the next iteration.
+In this manner, the interference variables are updated until the global consensus is achieved.
+The primal approach is similar to the approach presented in \cite{pennanen2011decentralized} for the minimum power precoder design.
+
+\begin{comment}
 The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}.
@@
 The receiver update can be made by using the precoded pilot transmission from each user as in \cite{komulainen2013effective}.
+\end{comment}

### 2015-01-28 Report/problem_formulation.tex
halfcooked

@@
 
-It is evident that \eqref{pf-1} is equivalent to \eqref{backpressure-approx} if the second order terms are ignored.
-Limiting \me{t_k^2} by a constant value, the \ac{Q-WSRM} formulation requires the explicit rate constraint \eqref{eqn-3.1.4} to avoid the resource wastage in the form of over-allocation.
-In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function itself.
-This makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \acp{BS} independently by exchanging minimal information exchange \cite{boyd2011distributed}.
-In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRM} problems include the sub-channels jointly to achieve an efficient allocation by identifying the optimal space-frequency resource for each user.
-The queue deviation objective provides an alternative approach to perform the resource allocation without the additional rate constraints as in the \ac{Q-WSRME} formulation.
+By limiting \me{t_k^2} with a constant value, the \ac{Q-WSRM} formulation requires an explicit rate constraint \eqref{eqn-3.1.4} to avoid over-allocation of the available resources.
+In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function \eqref{eqn-4.2} itself.
+It makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \acp{BS} independently by exchanging minimal information exchange \cite{boyd2011distributed}.
+In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRME} problems include the sub-channels jointly to obtain an efficient allocation by identifying the optimal space-frequency resource for the users.

### 2015-01-28 Report/problem_formulation_intro.tex
halfcooked

@@
 \end{equation}
-where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}}\footnote{It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
+where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}}.
 
@@
 \underset{\substack{\mvec{m}{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
-\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{eqn-4.3}
+\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{eqn-4.3}
 \end{IEEEeqnarray}

### 2015-01-28 Report/sub_channel_wsrm.tex
halfcooked

--- 2014-10-24 Report/sub_channel_wsrm.tex
@@
-The complexity involved in the \ac{JSFRA} scheme scales significantly with the increase in the number of sub-channels considered in the formulation.
-In addition to the increased complexity, the rate of convergence to the optimal precoders also degrades due to its dependency on the problem size.
-In order to address these issues, we provide an alternative sub-optimal solution, in which the precoders are designed over each sub-channel independently in a sequential manner by taking the remaining number of queued bits in the formulation.
-The optimal approach is to decompose the problem over each sub-channel with a fixed transmit power constraint for each sub-channel.
-The power allocated for each sub-channel is controlled by a master problem based on different algorithms as discussed in \cite{palomar2006tutorial,boyd2011distributed}.
+The complexity of the \ac{JSFRA} algorithm scales with the number of sub-channels considered.
+In addition, the iterations required for the algorithm convergence increases with the problem size.
+To overcome the complexity, we can adopt the distributed approaches presented in \cite{palomar2006tutorial,boyd2011distributed} for sub-channel wise precoder design using primal or dual decomposition.
 
-The proposed \acl{QM} \ac{SRA} formulation enables us to solve for the transmit precoders of all the users associated with the coordinating \ac{BS} in the set \me{\mathcal{B}} over each sub-channel independently by fixing the transmit power on each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}.
-In contrast to the decomposition based approach for the sub-channel-wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel-wise optimization.
-The total number of queued bits for each user is updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
-\begin{equation}
-Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{r = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,r} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U},
-\label{eqn-weight}
+As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which designs the precoders independently across the sub-channels in a sequential manner using the unserviced  number of packets after each sub-channel allocation.
+The \ac{BS} transmit power is fixed across the sub-channel \me{n} as \me{P_{\max,n}}.
+The power sharing can be equal or based on predetermined pattern as in partial frequency reuse across the sub-channels.
+After fixing the power and the backlogged packets for a sub-channel \me{i}, precoders are determined using the \ac{JSFRA} algorithm presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} for each sub-channel in a sequential manner.
+Once the precoders and the corresponding rates are identified, the unserviced backlogged packets for the next sub-channel \me{i+1} is updated for user \me{k} as
+\begin{equation}	\label{eqn-weight}
+	Q_{k,i+1} = \max{\left \lbrace Q_k - \sum_{j = 1}^{i} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \right \rbrace }, \; \forall \; k \in \mathcal{U},
 \end{equation}
-where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}.
-In the expression in \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,r}} is the rate or guaranteed bits allocated over the sub-channel \me{r}.
-However, the proposed scheme is sensitive to the order in which the sub-channels are selected for the optimization problem.
+where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream and the initial values are given as \me{Q_{k,1} = Q_k, \forall k}.
+Note that the proposed scheme is sensitive to the order of the sub-channel selection due to the sequential precoder design for each sub-channel.
+However, the \ac{SRA} approach provides faster convergence in contrast to the \ac{JSFRA} formulation due to the substantial reduction in the optimization variables for each sub-channel problem.
+As the number of user increases, the \ac{SRA} formulation will be insusceptible to the sub-channel ordering due to the channel hardening and the availability of users with all possible channel vectors.
 %The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}

### 2015-01-28 Report/system_model.tex
manosha
halfcooked

@@
 where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
-In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
+In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted.
+It can be easily extended for user specific streams \me{L_{k,n}} instead of using the common \me{L} streams for all users}.
 Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
@@
 \end{equation}
-where \me{\enoise = N_0\|\mvec{w}{l,k,n}\|^2} denotes the equivalent noise variance.
+where \me{\enoise = N_0\|\mvec{w}{l,k,n}\|^2} denotes the equivalent noise variance. \review{In order to minimize the feedback overhead on the user channels, we assume \ac{TDD} system.}
 

### 2015-01-28 Report/wsrm_formulation.tex
halfcooked

@@
   & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
-  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-6.4}
+  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-6.4}
 \end{IEEEeqnarray}
@@
 	&\quad& \beta_{l,k,n} \geq \enoise + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
-	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
+	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
 \end{IEEEeqnarray}
@@
 \text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
-& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
+& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
 & \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}

### 2015-01-29 Report/mse_formulation.tex
adhithan

@@
-In this section, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{mse_duality}.
-The \ac{MSE} \me{\epsilon_{l,k,n}}, for the data symbol is given by
+In this, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{mse_duality,christensen2008weighted}.
+The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
 \iftoggle{single_column}{
@@
 }{
+\allowdisplaybreaks{
 \begin{multline} \label{mse-error}
@@
  + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n},
-\end{multline}
+\end{multline}}
 }
@@
  & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
-& \quad &  \text{and} \; \eqref{eqn-4.3}.  \IEEEyessubnumber \label{eqn-mse-1.4}
+& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
 \end{IEEEeqnarray}
@@
 	& \qquad + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
-	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
+	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
 \end{IEEEeqnarray}}}
 
-An alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}, which is in fact a \ac{DC} constraint.
+The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}, which is in fact a \ac{DC} constraint.
 We resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using first order Taylor series approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
@@
 
-Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,n,k}} given the fixed receive beamformers.
-Once the optimal precoders are obtained, the local \ac{MSE} variable  \me{\tilde{\epsilon}_{l,k,n}} is updated with the current update \me{\epsilon_{l,k,n}}.
-The optimization problem for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given as
+Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,n,k}} for a fixed receive beamformers.
+The optimization subproblem to find the transmit precoders for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
@@
 \end{IEEEeqnarray}
+The optimal transmit precoders for a fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
 

### 2015-01-29 Report/system_model.tex
adhithan

--- 2015-01-21 Report/system_model.tex
@@
 where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
-In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams\footnote{\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
+In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users.
+\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
 Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as

### 2015-01-29 Report/wsrm_formulation.tex
adhithan

@@
-We now present an algorithm to solve problem \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
+We now present an iterative algorithm to solve problem \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
 To do this, first by using the \ac{SINR} expression in \eqref{eq:SINR}, we equivalently reformulate problem \eqref{eqn-3} as
@@
 \review{Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.
-\review{The constraints are tight when the per \ac{BS} objective is non zero at the optimal point, as discussed in Appendix \ref{a-3}}.
-\review{Note that the problem in \eqref{eqn-6} is similar to the \ac{WSRM} formulation, which is known to be NP-hard even for the single antenna case \cite{np_hard}.}
+\review{The constraints are tight when each \ac{BS} objective is non zero at the optimal point, as discussed in Appendix \ref{a-3}}.
+\review{Since the \ac{JSFRA} formulation can be modeled as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, it also belongs to the class of NP-hard problems.}
 
-In order to find a tractable solution for problem \eqref{eqn-6}, we note that the constraints \eqref{eqn-6.4} are convex with involved variables.
+In order to find a tractable solution for \eqref{eqn-6}, we note that the constraints \eqref{eqn-6.4} are convex with involved variables.
 Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-Towards this end, we resort to the traditional coordinate descent technique by fixing the linear receivers, and finding the optimal transmit beamformers.
+Towards this end, we resort to the \ac{AO} technique by fixing the linear receivers, and finding the optimal transmit beamformers.
 For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task.
@@
 Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively.
-Using the first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality constraint as
+Using first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality
 \iftoggle{single_column}{
@@
 }
-In summary, for the fixed linear receivers \review{\me{\mvec{w}{l,k,n}}}, the \ac{JSFRA} problem to find transmit beamformers is shown by
+In summary, for the fixed linear receivers \review{\me{\mvec{w}{l,k,n}}} and the operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-9}
@@
 It can be seen that the optimal receiver in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
+\allowdisplaybreaks{
 \begin{IEEEeqnarray}{rCl}
@@
 \mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
-\end{IEEEeqnarray}
+\end{IEEEeqnarray}}
 \review{Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance or the convergence behavior}.
 
-The proposed algorithm is referred to as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint, and it is outlined in Algorithm \ref{algo-1}.
+The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved in an iterative manner by updating the operating point from the previous iteration.
+The iterative algorithm is referred to as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint, and it is outlined in Algorithm \ref{algo-1}.
 The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
-Instead of initializing \me{{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with any feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{{\mbf{u}}_{l,k,n}} as briefed in Algorithm \ref{algo-1}.
+Instead of initializing \me{{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with some feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{{\mbf{u}}_{l,k,n}} as briefed in Algorithm \ref{algo-1}.
 For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for the predefined iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
@@
  \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
- \KwInit{\me{i=0} and transmit precoders \me{\mbf{m}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
+ \KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
  update \me{\mvec{w}{l,k,n}, \mbf{u}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} with \me{{\mbf{m}}_{l,k,n}}\;

### 2015-01-30 Report/decomposition_solutions.tex
cooked half only

@@
 
-To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
 Let us consider the \review{convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented} in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint.
@@
 
+To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
 Following the approaches presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in \me{\mathcal{B}} as
@@
 
-The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} by an iterative master-slave model using either primal or \acl{DD} method.
-The coupling variables are controlled by the master problem and the slave problems solve for the optimization variables associated with itself only.
+The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} by a parallel iterative subproblems using either primal or \acl{DD} method.
+The coupling variables are updated in each iteration by exchanging limited information among the subproblems.
 Now, to decouple the problem in \eqref{eqn-decent-1}, the coupling variable \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3}, which bind all \acp{BS} in \me{\mc{B}}, is replaced by a \ac{BS} specific variable \me{\zeta_{l,k,n,b}^{\{b_k\}}}.
-Using the \ac{BS} specific variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in \eqref{eqn-decent-3}, the subproblem in \eqref{eqn-decent-1} decouples completely for each \ac{BS} to find the precoders only for the users associated with the \ac{BS} \me{b_k}.
-The slave subproblems with the \ac{BS} specific interference variables are controlled by a master subproblem, which determines the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in accordance with the global objective.
+Using the \ac{BS} specific variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in \eqref{eqn-decent-3}, the subproblem in \eqref{eqn-decent-1} decouples completely for each \ac{BS} to find the precoders for the associated users by exchanging limited information to update \me{\zeta_{l,k,n,b}^{\{b_k\}}} in each iteration for the \ac{BS} \me{b_k}.
+
+%The subproblems with the \ac{BS} specific interference variables are controlled by a master subproblem, which determines the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in accordance with the global objective.

### 2015-01-30 Report/primal_approach.tex
cooked half only

--- 2014-10-09 Report/primal_approach.tex
@@
+In \acl{PD}, the convex problem in \eqref{eqn-decent-1} is solved for the optimal transmit precoders in an iterative manner for a fixed \ac{BS} specific interference terms \me{\zeta_{l,k,n,b}^{\{b_k\}}} using master-slave model \cite{pennanen2011decentralized}.
+The slave subproblem is solved in each \ac{BS} for the optimal transmit precoders for the associated users only by assuming a fixed interference \me{\zeta_{l,k,n,b}^{\{b_k\}}} from other \acp{BS} \me{b \in \mc{B} \backslash b_k} in each iteration.
+Upon finding the optimal associated transmit precoders by each slave subproblems, the master problem is used to update the \ac{BS} specific interference terms \me{\zeta_{l,k,n,b}^{\{b_k\}}} to a new value by using dual variables corresponding to the interference constraint \eqref{eqn-decent-3} as discussed in \cite{pennanen2011decentralized}.
+In this manner, the interference variables are updated until the global consensus is obtained.
+The primal approach is similar to the minimum power precoder design presented in \cite{pennanen2011decentralized}.
+Note that the master problem considers \me{\zeta_{l,k,n,b}^{\{b_k\}} \forall \{b,b_k\} \in \mc{B}} as a variable and the slave subproblems assume this to be a constant in each iteration that will be updated by the master problem.
+
+\begin{comment}
 The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}.

### 2015-02-02 Report/decomposition_solutions.tex
half cooked

@@
 \end{IEEEeqnarray}}
-where \me{\tilde{\mbf{v}}_b} denotes the vector of of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.
+where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.
 
 To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-Following the approaches presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in \me{\mathcal{B}} as
+Following similar approaches presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in \me{\mathcal{B}} as
 \iftoggle{single_column}{
@@
 It is given by the following upper bound as
-\begin{equation}
+\begin{equation} \label{inter_exp}
 \zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
@@
 
-The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} by a parallel iterative subproblems using either primal or \acl{DD} method.
+The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} by a parallel iterative subproblems coordinated by either primal or \acl{DD} update.
 The coupling variables are updated in each iteration by exchanging limited information among the subproblems.
-Now, to decouple the problem in \eqref{eqn-decent-1}, the coupling variable \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3}, which bind all \acp{BS} in \me{\mc{B}}, is replaced by a \ac{BS} specific variable \me{\zeta_{l,k,n,b}^{\{b_k\}}}.
-Using the \ac{BS} specific variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in \eqref{eqn-decent-3}, the subproblem in \eqref{eqn-decent-1} decouples completely for each \ac{BS} to find the precoders for the associated users by exchanging limited information to update \me{\zeta_{l,k,n,b}^{\{b_k\}}} in each iteration for the \ac{BS} \me{b_k}.
+Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented as
+\begin{IEEEeqnarray}{rCl}
+	\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b}, \eqsub \\
+	\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran. \eqsub
+\end{IEEEeqnarray}
+Let us define the vector \me{\mbfa{\zeta}_b}, formed by stacking the interference terms corresponding to the \ac{BS} \me{b} as
+\begin{equation}
+	\mbfa{\zeta}_{b} = \left [\hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran.
+	\label{if_vector}
+\end{equation}
+Since the decentralization solution is an iterative procedure, we represent the \me{\ith{i}} iteration index as \me{x^{(i)}}.
+Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to the \ac{BS} \me{b_k} in \ac{BS} \me{b} as
+\begin{equation}
+	\mbfa{\zeta}_{b}(b_k) = \left [ {\zeta}_{l,\mc{U}_b(1),n,b_k},\dotsc, {\zeta}_{l,\mc{U}_b(|\mc{U}_b|),n,b_k} \right].
+\end{equation}
+
+Now, to decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which include all interference terms relevant for the transmission of \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method.
+Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through uplink sounding and the receive beamformers \me{\mvec{w}{l,k,n}}.
 

### 2015-02-02 Report/dual_approach.tex
cooked half only
half cooked

@@
+In this section, we discuss the \ac{ADMM} approach to decouple the precoder design across multiple \acp{BS} to solve the centralized problem \eqref{eqn-decent-1}.
+The \ac{ADMM} is preferred over the \ac{DD} method proposed in \cite{tolli2011decentralized} for its robustness and better convergence behavior \cite{boyd2011distributed}.
+In contrast to the \acl{PD}, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
+Similar decomposition for the precoder design in the minimum power context is considered in \cite{admm_robust}.
+
+Using the definitions presented in the beginning of this section, we can write the \ac{BS} \me{b} specific subproblem at the \me{\ith{i}} iteration as
+{\allowdisplaybreaks
+\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}
+&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
+&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
+&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n}, \eqspace \eqsub \\
+&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b}, \forall \bar{k} \in \bar{\mc{U}}_b, \eqsub \\
+& \text{and } \eqref{eqn-8}, \eqsub
+\end{IEEEeqnarray}}
+where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality assumption at the \me{\ith{i}} iteration as
+\begin{equation}
+\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
+\end{equation}
+
+Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
+\begin{equation}
+\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
+\label{if-sg-update}
+\end{equation}
+The dual variable vector for the next iteration is updated using the subgradient update with the step size parameter \me{\rho} as
+\begin{equation}
+\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} - \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
+\label{dual-sg-update}
+\end{equation}
+where the step size can be chosen as discussed in \cite{boyd2011distributed}.
+The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.
+The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
+{\allowdisplaybreaks 
+\begin{algorithm}
+	\SetAlgoLined
+	\DontPrintSemicolon
+	\BlankLine
+	\SetKwInput{KwInit}{Initialize}
+	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
+	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
+	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
+	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
+	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
+	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
+		\Repeat{convergence or \me{i \geq I_{\max}}}{
+			initialize \me{j=0} \;
+			\Repeat{convergence or \me{j \geq J_{\max}}}{
+				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
+				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
+				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
+				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
+				\me{j = j + 1}\;
+			}
+			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
+			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
+			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
+			$i = i + 1$ \;
+		}
+	}
+	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
+	\label{algo-3}
+\end{algorithm}}
+
+\begin{comment}
 The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties.

### 2015-02-02 Report/kkt_mse_approach.tex
half cooked

@@
 So, the variable  \me{\alpha^{(i)}} is fixed as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.
-At each iteration, the dual variables \me{\alpha^{(i)}} are updated linearly from the earlier \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}.
-When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
+At each iteration, the dual variables \me{\alpha^{(i)}} are updated linearly from the earlier \me{\alpha^{(i-1)}} by a step size of \me{\rho \in (0,1]}.
+\review{Using values between \me{(0,1)}, will update the dual variable \me{\alpha^{(i)}} with history and for \me{\rho = 1}, the \me{\alpha^{(i)}} responds to the change immediately.
+Note that the step size \me{\rho} depend on the problem size and also affect the convergence rate.
+In our simulations, we used \me{\rho = 0.25}.} When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
 Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}}.

### 2015-02-02 Report/primal_approach.tex
half cooked

--- 2014-10-09 Report/primal_approach.tex
@@
+In \acl{PD}, the convex problem in \eqref{eqn-decent-1} is solved for the optimal transmit precoders in an iterative manner for a fixed \ac{BS} specific interference terms \me{\mbfa{\zeta}_{b_k}} using master-slave model \cite{pennanen2011decentralized}.
+The slave subproblem is solved in each \ac{BS} for the optimal transmit precoders only for the associated users by assuming fixed interference terms \me{\mbfa{\zeta}_{b_k}^{(i)}} in each \me{\ith{i}} iteration.
+Upon finding the optimal associated transmit precoders by each slave subproblems, the master problem is used to update the \ac{BS} specific interference terms \me{\mbfa{\zeta}_{b_k}^{(i+1)}} for the next iteration by using dual variables corresponding to the interference constraint \eqref{eqn-decent-3} as discussed in \cite{pennanen2011decentralized}.
+In this manner, the interference variables are updated until the global consensus is obtained.
+The primal approach is similar to the minimum power precoder design presented in \cite{pennanen2011decentralized}.
+Note that the master problem treats \me{\mbfa{\zeta}_{b}} as a variable and the slave subproblems assumes it to be a constant for each iteration to find the transmit precoders.
+
+\begin{comment}
 The \acl{PD} approach decomposes the problem by fixing the interference variables \me{\zeta_{l,k,n,b} \forall k,b} in order to perform the precoder design independently across each \ac{BS}.

### 2015-02-03 Report/conclusions.tex
Submitted version
introduction,  convergence distributed

@@
-In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM} transmission.
+In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM}.
 The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector.
-We proposed the \ac{JSFRA} scheme by employing the \ac{SCA} technique to relax the nonconvex constraint by a sequence of convex subsets for designing the precoders to minimize the total number of user queued packets.
-Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using \ac{SCA} technique to address the nonconvex constraints for a fixed \ac{MMSE} receivers.
-We then introduced distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
-Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method.
+We proposed the \ac{JSFRA} scheme by relaxing the nonconvex \ac{DC} constraint by a sequence of convex subsets using \ac{SCA} for designing the precoders to minimize the total number of user queued packets.
+Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers.
+We also proposed distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method.
 The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations.
 Numerical results are used to compare the performance of the proposed algorithms with the existing solutions.
+The distributed precoder design for the time correlated fading will be considered in future.

### 2015-02-03 Report/convergence_centralized.tex
introduction,  convergence distributed

@@
 The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.
+The monotonic decrease in the objective is still valid if the variables \me{\mx,\my} and \me{\mz} are updated together, since the update in \me{\my} increases the objective function for a fixed point \me{\mx} and \me{\mz}.
 
-The uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO}.
+The uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO} \cite{bezdek2002some}.
 For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders are guaranteed by the constraint \eqref{eqn-8}, which can be written as

### 2015-02-03 Report/convergence_distributed.tex
introduction,  convergence distributed

@@
-The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point.
-Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value.
-The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}.
-Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.
+In order to prove the convergence of the distributed algorithm, we need to prove the convergence of the decentralization approaches presented in Section \ref{sec-4}.
+Since the distributed algorithm outlined in Algorithm \ref{algo-3} is similar to the centralized problem, we only need to show that the distributed algorithms for the subproblem \eqref{eqn-decent-1} achieves the same solution as that of the centralized approach.
+
+Since the subproblem defined by \eqref{eqn-decent-1} is convex, the primal decomposition approach will converge to the centralized solution if the step size diminishes as a function of the iteration index.
+The convergence of \ac{ADMM} scheme follows directly from the Proposition 4.2 in \cite{bertsekas1989parallel}.
+The overall convergence of the \ac{JSFRA} problem in a distributed approach is similar to that of the centralized convergence discussion in Appendix \ref{sec-3.5}.
+
+Note that even if the distributed algorithms in Section \ref{sec-4} are not iterated until convergence, the objective is still monotonically decreasing following the arguments from Appendix \ref{sec-3.5}.
+In this case, the final solution may not reach the stationary point similar to that of the centralized solution.
+In the current approach, \ac{SCA} update is performed after the convergence of the distributed algorithm.
+It is required since the \ac{SCA} subproblems are convex and the \acl{PD} and \ac{ADMM} will converge to the centralized solution.

### 2015-02-03 Report/dual_approach.tex
introduction,  convergence distributed

@@
-In this section, we discuss the \ac{ADMM} approach to decouple the precoder design across multiple \acp{BS} to solve the centralized problem \eqref{eqn-decent-1}.
+In this section, we discuss the \ac{ADMM} approach to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}.
 The \ac{ADMM} is preferred over the \ac{DD} method proposed in \cite{tolli2011decentralized} for its robustness and better convergence behavior \cite{boyd2011distributed}.
@@
 &\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n}, \eqspace \eqsub \\
-&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b}, \forall \bar{k} \in \bar{\mc{U}}_b, \eqsub \\
+&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b}, \forall \bar{k} \in \bar{\mc{U}}_b,  \forall n \eqsub \\
 & \text{and } \eqref{eqn-8}, \eqsub
@@
 \end{equation}
-The dual variable vector for the next iteration is updated using the subgradient update with the step size parameter \me{\rho} as
+The dual vector for the next iteration is updated by using subgradient to maximize the dual objective as
 \begin{equation}
-\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} - \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
+\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
 \label{dual-sg-update}
 \end{equation}
-where the step size can be chosen as discussed in \cite{boyd2011distributed}.
+where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}.
 The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.

### 2015-02-03 Report/introduction.tex
introduction,  convergence distributed

@@
 In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}.
-Since the problem is nonconvex, we adopt the \ac{SCA} technique to solve by a sequence of convex subproblems using first order approximations.
-Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints.
+Since the problem is nonconvex due to the \ac{DC} constraints, we adopt \ac{SCA} to solve by a sequence of convex subproblems using first order approximations.
+Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint.
 First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders.
@@
 Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.
+
+The proposed \ac{JSFRA} formulation provides a way to control the resource allocation across sub-channels by altering the
 

### 2015-02-03 Report/kkt_mse_approach.tex
introduction,  convergence distributed

--- 2015-01-28 Report/kkt_mse_approach.tex
@@
 In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}.
-In contrast to Section \ref{sec-4a}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
+In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
 The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements.
@@
 Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other.
-So, the variable  \me{\alpha^{(i)}} is fixed as in \eqref{kkt-mse-4.1} to obtain the other variables in \eqref{kkt-mse-4}.
-At each iteration, the dual variables \me{\alpha^{(i)}} are updated linearly from the earlier \me{\alpha^{(i-1)}} by a step size of \me{\rho \in [0,1]}.
+So, \me{\alpha^{(i)}} is fixed to evaluate \me{\sigma^{(i)}} using \eqref{kkt-mse-4}.
+\review{At each iteration, the dual variables \me{\alpha^{(i)}} are linearly interpolated with any point between the fixed iterate \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} using a step size \me{\rho \in (0,1)}.
+The choice of \me{\rho} depends on the system model and it affects the convergence behavior of the algorithm.
+It is used to reduce the oscillations in the objective function when \me{\sigma^{(i)}} is negative due to over allocation.}
+
 When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
-Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}}.
+Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}} eventually.
+\review{Since \me{\rho} depend on the system size, we fix the value of \me{\rho = 0.1} in our simulations irrespective of the system, which affects the convergence behavior marginally.}
 
@@
 
-To devise an algorithm for a practical implementation, we extend the decentralization methods discussed in \cite{komulainen2013effective}, for our problem of minimizing the total number of backlogged packets as follows.
+\review{To devise an algorithm for a practical implementation, we assume the cross channels \me{\mvec{H}{b,k,n}, \forall k \in \bar{\mc{U}}_b} and the receive beamformers \me{\mvec{w}{l,k,n}} of all users in the system are known through uplink signaling}.
+We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the current problem as follows.
 After receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user evaluates the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify them to the \acp{BS} via uplink precoded pilots.
@@
 \end{algorithm}\vspace{-0.1in}
+
+The Algorithm \ref{algo-4} outlines a practical approach of implementing the precoder design in a distributed manner using \ac{OTA} signaling of transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed.
+Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha}, it is difficult to prove the convergence of the algorithm to the centralized point.
+If the step size \me{\rho < 1}, the algorithm will converge by following the arguments made for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration.
+Note that the objective is nonincreasing but the queue devation is not.
+
 %\subsubsection*{Convergence}

### 2015-02-04 Report/appendix_tightness.tex
first final report

@@
-In order for the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user per \ac{BS} with large enough backlogged packets that cannot be satisfied with the given power budget.
-To prove this, let us consider a single \ac{BS} \me{N_T \times 1} system with \me{|U|_b} users each with \me{Q_k} backlogged packets.
-Let us consider the problem for a single \ac{BS} \me{b} as
-\begin{IEEEeqnarray}{rCl}
+\begin{comment}
+For the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user in each \ac{BS} with enough backlogged packets that cannot be served with the given power budget.
+To prove this, let us consider a \ac{BS} \me{b} with \me{N_T \times 1} system serving \me{|U|_b} users each with \me{Q_k} backlogged packets.
+The \ac{JSFRA} formulation can be written as
+\begin{IEEEeqnarray}{rCl} \label{tight}
 	\underset{\gamma_{k},\mvec{m}{k},\beta_{k}}{\text{minimize}} &\quad& \sum_{k \in \mc{U}_b} \big | Q_k - \log_2(1 + \gamma_k) \big |^q  \eqsub \\
@@
 \end{IEEEeqnarray}
-Let us assume the system has \me{N_T > |\mc{U}_b|} and the precoders are determined for all users at the optimal point for which the objective is minimum and is nonzero.
+Let \me{N_T > |\mc{U}_b|} and the precoders are found by solving \eqref{tight} with a nonzero objective value at the optimal point.
 Let us consider two users, say \me{i} and \me{j} with precoders \me{\mvec{m}{i}} and \me{\mvec{m}{j}}.
-In order to show the tightness of the constraints \eqref{ae-1} and \eqref{ae-2}, let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for a user \me{i} only.
+In order to show the tightness of \eqref{ae-1} and \eqref{ae-2}, let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for user \me{i} only.
 Let us also consider that \me{\gamma_k} for all users \me{k \in \mc{U}_b \backslash j} are identified to satisfy the backlogged packets.
@@
 It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget.
-Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to empty the current backlogged packets in the system.
+Since the objective is not to minimize power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to empty the current backlogged packets in the system.
 The objective of the \ac{JSFRA} problem can be regularized by including the power term to find the minimum power precoders as
 \begin{equation*}
-\| \tilde{\mbf{v}} \|_q + \varphi \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
+\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
 \end{equation*}
@@
 Note that the above objective is guaranteed to make the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} active by relaxing the power constraint \eqref{eqn-6.4}.
+\end{comment}
+
+For the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user in each \ac{BS} with enough backlogged packets that cannot be served with the given power budget.
+In order to make the constraints active for all scenarios, the objective of the \ac{JSFRA} formulation should be regularized with the transmit power without affecting the solution as
+\begin{equation*}
+\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
+\end{equation*}
+where \me{\varphi \approx 0}. Note that the modified objective will relax the power constraint by making the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} active at the stationary point.

### 2015-02-04 Report/convergence_distributed.tex
first final report

--- 2015-01-28 Report/convergence_distributed.tex
@@
-The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point.
-Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value.
-The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}.
-Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.
+The convergence of the distributed algorithm outlined in Algorithm \ref{algo-3} follows the same discussion in Appendix \ref{sec-3.5} if the subproblem \eqref{eqn-decent-1} converge to the centralized solution.
+Since the subproblem \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}.
+The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \rightarrow \infty} \cite{bertsekas1999nonlinear} for a diminishing step size.
+It can be seen that the subproblem \eqref{eqn-decent-1} satisfies Slater's constraint qualification by having non empty interior and bounded due to the total power constraint for the transmit precoders.
+
+To prove the convergence of the \ac{ADMM} approach, we use the argument presented in \cite{bertsekas1989parallel} Proposition 4.2. 
+If the problem is written as 
+\begin{IEEEeqnarray}{rCl}
+	\underset{\mbf{x},\mbf{z}}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
+	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm} \\
+&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2, \eqsub
+\end{IEEEeqnarray}
+following conditions are required for the convergence if \ac{ADMM} is used.
+\begin{itemize}
+	\item \me{G,H} should be convex
+	\item \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded
+	\item \me{\mbf{A}^\herm \mbf{A}} should be invertible.
+\end{itemize}
+Note that the equality constraint \eqref{const-admm} is identical to \eqref{const-admm1} and therefore \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible.
+The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1}, which are convex.
+The set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has nonempty interior.
+The feasibility of the interior point is verified by having a non zero precoder for only one user.
+Therefore, by following \cite{bertsekas1989parallel} Proposition 4.2, it can be seen that the \ac{ADMM} approach converges to the centralized solution.

### 2015-02-04 Report/dual_approach.tex
first final report

@@
 \end{IEEEeqnarray}}
-where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality assumption at the \me{\ith{i}} iteration as
-\begin{equation}
+where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{i}} iteration as
+\begin{equation} \label{const-admm1}
 \mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.

### 2015-02-04 Report/introduction.tex
first final report

--- 2015-01-21 Report/introduction.tex
@@
 \subsubsection*{Main Contributions}
-In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}.
-Since the problem is nonconvex, we adopt the \ac{SCA} technique to solve by a sequence of convex subproblems using first order approximations.
-Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} technique for the nonconvex constraints.
+\review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}.
+The proposed design provides better control over the resource allocation strategy by the change of a variable.
+Since the transmissions are guided by the backlogged packets, the proposed formulation limits the resource allocation beyond the number of backlogged packets without additional rate constraint.
+Since the problem is nonconvex due to \ac{DC} constraints, we adopt \ac{SCA} to solve by a sequence of convex subproblems using first order approximations.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint.
 First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders.
@@
 Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.
+\review{It is worth noting that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.
 

### 2015-02-04 Report/kkt_mse_approach.tex
first final report

@@
 
-The Algorithm \ref{algo-4} outlines a practical approach of implementing the precoder design in a distributed manner using \ac{OTA} signaling of transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed.
-Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha}, it is difficult to prove the convergence of the algorithm to the centralized point.
-If the step size \me{\rho < 1}, the algorithm will converge by following the arguments made for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration.
-Note that the objective is nonincreasing but the queue devation is not.
+\review{The Algorithm \ref{algo-4} outlines a practical way of implementing the transmit precoders in a distributed manner using \ac{OTA} signaling of transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed.
+Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of centralized solutions.
+It can be viewed as a primal decomposition approach in which the master-slave iterations is performed only once before updating other variables.
+Since each primal subproblem yields a feasible solution, the monotonic behavior is obtained by this algorithm.
+If the step size \me{\rho < 1}, the algorithm will converge by using the arguments made for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration.}
 

### 2015-02-04 Report/problem_formulation.tex
first final report

@@
 which is equivalent to the objective defined in \eqref{q_gen_sum}.
-Note that the equivalence can be seen either by discarding \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly greater than the maximum allowable transmission.}
+Note that the equivalence can be seen either by discarding \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly large for all users such that \me{t_k^2} has no impact on the objective function.}
 

### 2015-02-04 Report/queue_minimizing_intro.tex
changes with satya
first final report

@@
 
-In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is difficult due to the combinatorial and the nonconvex nature of the problem.
-In addition, the objective of minimizing the number of the queued packets over space-frequency dimensions adds further complexity to the existing problem.
-Since the scheduling of users in each space-frequency resource can be controlled by the transmit precoders, our solutions perform precoder design and user scheduling jointly.
+\review{In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is difficult due to its nonconvex nature}.
+In addition, the objective of minimizing the number of the queued packets over space-frequency dimensions adds further complexity.
+Since the scheduling of users in each sub-channel attained by allocating zero transmit power over certain sub-channels, our solutions perform joint precoder design and user scheduling.
 Before discussing the proposed solutions, we consider the existing algorithm to minimize the number of backlogged packets with additional constraints required by the problem.

### 2015-02-04 Report/time_correlated.tex
first final report

@@
-This section is dedicated to understand the performance of the proposed \ac{JSFRA} scheme with different values of \me{\ell_q} over multiple time slots.
-The performance is compared with the existing \ac{Q-WSRME} scheme for different arrival rates \me{A_k}.
+We discuss performance of the \ac{JSFRA} algorithm for different values of \me{\ell_q} over multiple time slots.
+It is compared with the existing \ac{Q-WSRME} scheme by varying the average arrival rate \me{A_k} of all users.
 Fig.
-\ref{fig-review} compares the performance of the centralized algorithms for different \me{\ell_q} values using the average number of backlogged packets present in the system after each time instant.
-The horizontal axis indicate the average arrivals in bits per user, which is constant for all user.
-The instantaneous arrival follows Poisson distribution.
-The model considered for simulation is a \me{4 \times 1} \ac{MIMO} system with \me{N = 4} sub-channels with \me{N_B = 2} \acp{BS}.
+\ref{fig-review} demonstrates the performance of the centralized algorithms for different \me{\ell_q} values.
+The horizontal axis indicates the average number of arrivals \me{A_k} in bits per user and it is constant for all users in the system.
+The vertical axis corresponds to the average of number of backlogged packets left in the system after each time slot.
+Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and is based on Poisson arrival process.
+We considered a \me{4 \times 1} \ac{MIMO} system with \me{N = 4} sub-channels and \me{N_B = 2} \acp{BS}.
 The path loss is modeled as a uniform random variable \me{[0,-3]} dB with the maximum \ac{SINR} seen by any user is \me{6} dB.
@@
 
+The performance of the \ac{JSFRA} scheme using \me{\ell_2} and \ac{Q-WSRME} approach are similar in the average number of residual packets after each transmission slot.
+Note that the additional rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence.
+Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are significantly greater than the actual transmissions.
 It can be seen from Fig.
-\ref{fig-review} that the performance of the \ac{JSFRA} scheme with \me{\ell_2} norm and the \ac{Q-WSRME} approach are similar in the average residuals after each transmission instant.
-Note that the performance of the \ac{Q-WSRM} scheme is similar to the \ac{Q-WSRME} approach when the arrival rates are greater than the actual transmissions.
-It can be seen from Fig.
-\ref{fig-review} that the average number of backlogged packets are contained until the per user arrival is \me{\leq 4} bits.
-After that, the average queues become unbounded.
-The performance of the \ac{JSFRA} scheme with \me{\ell_1} norm has significantly less number of average queued packets in comparison with other schemes.
-The performance of the \ac{JSFRA} scheme with \me{\ell_{\infty}} performs the worst in terms of the average number of queued packets after each transmission instant by achieving the fair service rate to all users.
+\ref{fig-review} that the average number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} formulation due to the greedy resource allocation by serving users with better channel conditions.
+Fig \ref{fig-review} shows that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs worst in terms of the average number of backlogged packets due to the fairness constraints.

### 2015-02-04 Report/wsrm_formulation.tex
first final report

@@
 }
-In this formulation, we relaxed the \ac{SINR} expression \eqref{eq:SINR} by the inequalities in \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-\review{Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.
+\review{Since the equality of the \ac{SINR} in \eqref{eq:SINR} cannot be included as a constraint directly, we relaxed the \ac{SINR} expression by using inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3}.
+Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.
 \review{The constraints are tight when each \ac{BS} objective is non zero at the optimal point, as discussed in Appendix \ref{a-3}}.

### 2015-02-04 Report/simulation_distributed.tex
updated-final darft without optimal word

@@
 It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function.
-It can be seen that the heuristic method oscillates near the optimal point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
+It can be seen that the heuristic method oscillates near the stationary point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
 \begin{figure}

### 2015-02-04 Report/simulation_results.tex
satya_2
updated-final darft without optimal word

@@
 In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation.
-It can be seen that the \ac{JSFRA} algorithms converge to the optimal point for all formulations proposed in Section \ref{sec-3.2.1}.
-All the algorithms are Pareto-optimal and provide different performance based on the weights used to find a point in the rate region.
+It can be seen that the \ac{JSFRA} algorithms converges to a final point for all formulations.
 

### 2015-02-05 Report/appendix_tightness.tex
Updated WSRM

@@
 For the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user in each \ac{BS} with enough backlogged packets that cannot be served with the given power budget.
-In order to make the constraints active for all scenarios, the objective of the \ac{JSFRA} formulation should be regularized with the transmit power without affecting the solution as
+On the other hand, to make the constraints active in all cases, the objective of the \ac{JSFRA} formulation should be regularized with the transmit power without affecting the solution as
 \begin{equation*}
@@
 \end{equation*}
-where \me{\varphi \approx 0}. Note that the modified objective will relax the power constraint by making the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} active at the stationary point.
+where \me{\varphi \approx 0}. Note that the modified objective will relax the power constraint by making the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} active at the final solution.

### 2015-02-05 Report/convergence_distributed.tex
Updated WSRM

@@
 \end{itemize}
-Note that the equality constraint \eqref{const-admm} is identical to \eqref{const-admm1} and therefore \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible.
-The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1}, which are convex.
-The set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has nonempty interior.
+Note that the equality constraint \eqref{const-admm} is identical to \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}.
+It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible.
+The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} are all convex sets and has a nonempty interior.
 The feasibility of the interior point is verified by having a non zero precoder for only one user.
-Therefore, by following \cite{bertsekas1989parallel} Proposition 4.2, it can be seen that the \ac{ADMM} approach converges to the centralized solution.
+Therefore, by following \cite{bertsekas1989parallel} Proposition 4.2, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.

### 2015-02-05 Report/dual_approach.tex
Updated WSRM

@@
 In this section, we discuss the \ac{ADMM} approach to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}.
-The \ac{ADMM} is preferred over the \ac{DD} method proposed in \cite{tolli2011decentralized} for its robustness and better convergence behavior \cite{boyd2011distributed}.
-In contrast to the \acl{PD}, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
+The \ac{ADMM} is preferred over the \ac{DD} approach in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}.
+In contrast to the \acl{PD}, the \ac{ADMM} approach relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
 Similar decomposition for the precoder design in the minimum power context is considered in \cite{admm_robust}.
 
-Using the definitions presented in the beginning of this section, we can write the \ac{BS} \me{b} specific subproblem at the \me{\ith{i}} iteration as
+Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{i}} iteration as
 {\allowdisplaybreaks

### 2015-02-05 Report/system_model.tex
Updated WSRM

@@
 \end{equation}
-where \me{\enoise = N_0\|\mvec{w}{l,k,n}\|^2} denotes the equivalent noise variance. \review{In order to minimize the feedback overhead on the user channels, we assume \ac{TDD} system.}
+where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance.
+\review{To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system, which uses channel reciprocity.}
 

### 2015-02-05 Report/wsrm_formulation.tex
Updated WSRM

@@
 For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task.
-We note that for fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
-Thus, the difficulty is due to the non-convexity in \eqref{eqn-6.2}.
-\review{To arrive at a tractable formulation, we adopt \ac{SCA} to handle \eqref{eqn-6.2} by replacing the original non-convex constraint by a series of convex constraints \cite{marks1978technical}}.
+We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
+Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}.
 Let us define a function,
@@
 where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation.
-Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-\review{Eq.
-\eqref{eqn-6.2} can be viewed as a \ac{DC} constraint, in which the convex function given by \me{f({\mbf{u}}_{l,k,n})} is upper bounded by first order approximation around an operating point \me{\tilde{\mbf{u}}_{l,k,n}}}.
+Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
+The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed by a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}.
+By using the reduced convex subset instead of \eqref{eqn-6.2}, \eqref{eqn-6} can be solved for each operating point iteratively until convergence.
 

### 2015-02-05 Report/wsrm_formulation.tex
final_modified wsrm

@@
 }{\allowdisplaybreaks
-\begin{IEEEeqnarray}{CCl}\label{eqn-6}
+\begin{IEEEeqnarray}{CCl} \label{eqn-6}
 	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
@@
 Let us define a function,
-\begin{equation*}
+\begin{equation}
 f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}},
-\end{equation*}
+\end{equation}
 where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation.
 Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed by a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}.
-By using the reduced convex subset instead of \eqref{eqn-6.2}, \eqref{eqn-6} can be solved for each operating point iteratively until convergence.
+\review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed by a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as \ac{SCA} method in \cite{marks1978technical}.
+By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}
 
 For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
-\begin{subeqnarray} \label{eqn-wsrm-expr}
-p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \\
-q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}
-\end{subeqnarray}
+\begin{IEEEeqnarray}{rCl} \label{eqn-wsrm-expr}
+p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub \\
+q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub
+\end{IEEEeqnarray}
 and hence \me{f({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.

### 2015-02-06 Report/ieee_journal.tex
halfcooked
adhithan
half cooked
introduction,  convergence distributed
first final report
updated-final darft without optimal word
final_modified wsrm
nothing great

@@
-\documentclass[10pt,final,twocolumn,a4paper]{./../Styles/IEEEtran}
+\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 \usepackage[ruled]{algorithm2e}
-\usepackage[dvips]{graphicx}
+\usepackage[dvipdfmx]{graphicx}
 \usepackage[usenames,dvipsnames]{xcolor}
@@
 
-%\section{Response to reviewer comments}
-%\input{review_comments}
+\section{Response to reviewer comments}
+\input{review_comments}
 
@@
 
-\input{decomposition_solutions}
+\review{\input{decomposition_solutions}}
 
-\subsection{Decomposition based Approaches} \label{sec-4a}
+%\subsection{Decomposition based Approaches} \label{sec-4a}
 
-\subsubsection{Primal Decomposition Approach} \label{sec-4.1}
-
+\subsection{Primal Decomposition} \label{sec-4.1}
 \input{primal_approach}
@@
 
-\subsubsection{\ac{ADMM} approach} \label{sec-4.2}
-
+\subsection{Alternating Directions Method of Multipliers (ADMM)} \label{sec-4.2}
 \input{dual_approach}
@@
 
+\subsection{Convergence Analysis for Distributed Algorithms} \label{sec-dist-conv}
+\review{\input{convergence_distributed}}
+
 \subsection{Decomposition via \ac{KKT} Conditions for \ac{MSE} Formulation} \label{sec-4.3}
-
 \input{kkt_mse_approach}
@@
 
-\subsection{Average Backlogged Packets Over Slots}
+\subsection{Average Backlogged Packets Over Slots} \label{time-correlated}
 
@@
 
-\subsection{Convergence Analysis} \label{sec-3.5}
-\input{convergence_centralized}
+\section{Convergence Analysis of Centralized Algorithm} \label{sec-3.5}
+\review{\input{convergence_centralized}}
 

### 2015-02-06 Report/review_comments.tex
nothing great

@@
 
-\resp We thank the reviewer for reading the paper and providing the comments. Please consider the responses in line with the comments.
+\resp We thank the reviewer for reading the paper and providing the comments. The response for the reviewer questions are made in line.
 
@@
 \end{figure}
+The discussions are included in the Section \ref{time-correlated}.
 
@@
 
-\resp We understand the reviewer concerns. We have modified the convergence section to include additional information to provide more clarity. \review{Update converge proof}
+\resp We understand the reviewer concerns.
+We have modified the convergence section to include additional information to provide more clarity.
+Appendix \ref{sec-3.5} discuss the convergence proof of the proposed algorithm in detail.
 
@@
 
-\resp We thank the reviewer for the raising the concern on the selection order. We have elaborated the discussion on the sub-channel wise selection scheme. \review{discuss on selection}
+\resp We thank the reviewer for the raising the concern on the selection order. We have elaborated the discussion on the sub-channel wise selection scheme in Section \ref{sec-3.4}.
 
@@
 In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which is not the stationary point when the algorithm is allowed to converge.
-In section \ref{sec-4.3}, we have discussed a practical approach based on the KKT conditions, which attains a sub-optimal point with few number of iterations.
+In Section \ref{sec-4.3}, we have discussed a practical approach based on the KKT conditions, which attains a sub-optimal point with few number of iterations.
 
@@
 If the distributed algorithm is iterated until convergence, it is guaranteed to attain the same stationary point as that of the centralized algorithm \cite{boyd2011distributed}.
+We have included this discussion in Section \ref{sec-dist-conv}.
 

### 2015-02-06 Report/simulation_results.tex
Updated WSRM
nothing great

@@
 	\end{tabular}
-	\label{tbl-1} \vspace{-0.1in}
+	\label{tbl-1}
 \end{table*}
@@
 	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates}
-	\label{fig-a} \vspace{-0.1in}
+	\label{fig-a}
 \end{figure*}
@@
 	\end{tabular}
-	\label{tbl-3} \vspace{-0.1in}
+	\label{tbl-3}
 \end{table}
@@
 In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in Algorithm \ref{algo-1}.
-It is also noted that the performance degradation by performing the group update is very minimal.
-Since the receiver minimizes the objective for the fixed transmit precoders, the convergence is monotonic as can be seen from the figures.
+It is also noted that the degradation by performing combined update is marginal, since the receiver minimizes the objective for a fixed transmit precoders thereby leading to a monotonic convergence.
 

### 2015-02-10 Report/convergence_centralized.tex
additions

@@
 \newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
+
+In order to prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, we have to show the following conditions are to be satisfied.
+\begin{itemize}
+	\item At each \ac{SCA} update, the objective value decreases monotonically, 
+	\item each \ac{SCA} point is unique, which is required for \ac{AO} to converge,
+	\item and the objective function is monotonically decreasing at each \ac{AO} update.
+\end{itemize}
+In addition, we need to show the converged point is the stationary point for the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+
 Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as

### 2015-02-10 Report/dual_approach.tex
additions

@@
 \end{equation}
-where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}.
+where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}, which depend on the system model under consideration for the convergence rate.
 The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.

### 2015-02-10 Report/kkt_mse_approach.tex
nothing great
additions

--- 2015-02-03 Report/kkt_mse_approach.tex
@@
 The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements.
-\review{We consider a \ac{TDD} system due to the unquantized channel state information at the transmitter}.
+\review{We consider an idealistic assumption of a \ac{TDD} system due to the knowledge of complete channel information at the transmitter}.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
@@
  \label{algo-4}
-\end{algorithm}\vspace{-0.1in}
+\end{algorithm}
 
-The Algorithm \ref{algo-4} outlines a practical approach of implementing the precoder design in a distributed manner using \ac{OTA} signaling of transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed.
-Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha}, it is difficult to prove the convergence of the algorithm to the centralized point.
-If the step size \me{\rho < 1}, the algorithm will converge by following the arguments made for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration.
-Note that the objective is nonincreasing but the queue devation is not.
+\review{The Algorithm \ref{algo-4} outlines a practical way of implementing the transmit precoders in a distributed manner using \ac{OTA} signaling of the transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed with it.
+Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of the centralized problem.
+Since the problem solution in \eqref{kkt-mse-4} is equivalent to the centralized formulation in \eqref{eqn-mse-2} if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}, the problem is guaranteed to converge to the centralized solution.
+Note that it requires four iterations to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders.
+In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations.
+If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration.}
 

### 2015-02-10 Report/review_comments.tex
additions

@@
 
-\cmnt The logic from (6) to (16) is not clear.
+\cmnt{1} The logic from (6) to (16) is not clear.
 The only difference is the two newly introduced NON-CONVEX constraints (16b) and (16c), while the objective function (16a) and the constraint (16d) is the same as (6).
@@
 
-\cmnt The authors use the successive convex approximation framework, but the approximate problem proposed by the authors is actually not convex.
+\resp We thank the reviewer for the critical comment.
+We have updated the discussions on the equivalence in Section \ref{sec-3.1}.
+Please note that the discussion on the \ac{Q-WSRM} formulation is made for the completeness of the problem discussion.
+For more information on this topic, please refer to the Chapter 3 in \cite{neely2010stochastic} book.
+
+\cmnt{2} The authors use the successive convex approximation framework, but the approximate problem proposed by the authors is actually not convex.
 Inspecting (19), its objective function is the same as in (6), and the non-convexity of (6) comes exactly from the objective function, so (19) is not a convex problem.
@@
 
-\cmnt The authors proposed to use block coordinate descent method to solve (16).
+\resp Please note that the objective function is a norm function and is convex.
+Note that the \ac{SCA} is used to decompose the original nonconvex problem due to the nonconvex constraint in \eqref{eqn-6.2} into a series of convex subproblems that are solved in an iterative manner.
+We understand the reviewers concern and we have modified the text to bring out the details clearly.
+
+\cmnt{3} The authors proposed to use block coordinate descent method to solve (16).
 But as the authors have already pointed out, to apply block coordinate descent method, the constraint sets for different variables should be disjoint (uncoupled), which is however not the case in (16), because receive and transmit precoders (i.e w and m) are coupled in the constraints.
@@
 
-\cmnt Regarding the convergence of the SCA, the authors cited [27] for the convergence conditions, but the reference is wrong, because the conditions after the three bullets on page 6 are not mentioned in [27].
+\resp We thank the reviewer for the pointing out the flaw in the text. We have modified the text with more details.
+
+\cmnt{4} Regarding the convergence of the SCA, the authors cited [27] for the convergence conditions, but the reference is wrong, because the conditions after the three bullets on page 6 are not mentioned in [27].
 In case the authors disagree, please make the citation more specific, for example, specify the theorem/statement/proposition in [27] where those conditions are specified.
 
-\cmnt The authors also cited [28] to establish the convergence of SCA.
+\resp We thank the reviewer for the pointing out the citation problem. We have included the text on convergence in Appendix \ref{sec-3.5} to address it in detail.
+
+\cmnt{5} The authors also cited [28] to establish the convergence of SCA.
 But the techniques of [27] and [28] are different, and the convergence conditions are different too.
@@
 
-\cmnt Another comment on reference: to the reviewer's knowledge, the term SCA is never explicitly used in [2]. So please either correct the reference or be more specific (section, theorem, etc.).
+\resp We thank the reviewer for the pointing out the citation problem. We have included the text on convergence in Appendix \ref{sec-3.5} to address it in detail.
 
-\cmnt The authors propose primal decomposition method, ADMM approach to the non-convex problem (19), while their convergence analysis is based on literature that proved convergence for convex problems only, e.g., [13].
+\cmnt{6} Another comment on reference: to the reviewer's knowledge, the term SCA is never explicitly used in [2]. So please either correct the reference or be more specific (section, theorem, etc.).
+
+\resp We thank the reviewer for the pointing out the citation problem. We have removed it in the revised manuscript.
+
+\cmnt{7} The authors propose primal decomposition method, ADMM approach to the non-convex problem (19), while their convergence analysis is based on literature that proved convergence for convex problems only, e.g., [13].
 So the convergence analysis is not trustworthy.
 
-\cmnt The length of the paper is too extensive.
+\resp We apologize for the confusion in the text. We have updated the text accordingly to point out the convex problem for which the decomposition is performed.
+
+\cmnt{8} The length of the paper is too extensive.
 Some of the reformulations as mentioned in the previous comment can be skipped.
@@
 
-\cmnt Information regarding the value of q used to obtain the simulation results is missing (with exception of Fig. 3).
+\resp We understand the reviewers concern.
+We have included the subchannel wise resource allocation or (SRA) in Section \ref{sec-3.4} for the completeness.
+It is a variation to the centralized problem which is included for the completeness.
+If the reviewer still insists on its removal, we will do.
 
-\cmnt In Fig.
+\cmnt{9} Information regarding the value of q used to obtain the simulation results is missing (with exception of Fig. 3).
+
+\resp We thank the reviewer for pointing out the important point. We have included the norm used in Figures in the caption.
+
+\cmnt{10} In Fig.
 1 and Fig.
@@
 
-\cmnt Assuming that Fig.
+\resp We understand the reviewers concern. It is included for the comparison purpose only. If reviewer insists on removing, we will do.
+
+\cmnt{11} Assuming that Fig.
 2 and Fig.
@@
 
+\resp Please note that the number of sub-channels and the number of \acp{BS} are different in addition to the number of backlogged packets.
+If they are same, then both schemes should provide same performance, since the distributed algorithm is performed over the convex subproblem after linearization.
+
 \subsection*{Reveiewer comments - \me{3}}
 
-\cmnt This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods.
+\cmnt{1} This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods.
 This is an interesting and important topic.
@@
 
-\cmnt 1. The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.
+\cmnt{2} The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.
 
@@
 
-\cmnt 2.
-The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5).
+\cmnt{3} The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5).
 This is not obvious.
@@
 
-\cmnt 3.
-The solution in (21) is obtianed for MMSE, i.e.
+\cmnt{4} The solution in (21) is obtianed for MMSE, i.e.
 for 2-norm(q=2).
@@
 
-\cmnt 4.
-The convergence proof need to be rigorous.
+\cmnt{5} The convergence proof need to be rigorous.
 The inequality of (23a) is opposite to the reference [28].
@@
 
-\cmnt 5.
-(25) is generally wrong.
+\cmnt{6} (25) is generally wrong.
 (25) only holds when the MSE is minimized(by MMSE receiver) and the snr is the optimized(which is obtained by general eignvalue decompostion).
@@
 
-\resp We thank the reviewer for pointing out the information loss in the statement.
+\resp We thank the reviewer for pointing out the information missed out in the statement.
 We have provided more detail in the manuscript.
@@
 
-\cmnt 6.
-For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed.
+\cmnt{7} For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed.
 1.
@@
 
-\cmnt First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method.
+\cmnt{1} First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method.
 "The SCA method" is often referred to, but never really defined or referenced.
@@
 
-\cmnt Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates.
+\resp We thank the reviewer for We have updated the proof for convergence in a separate section on Appendix \ref{sec-3.5}.
+
+\cmnt{2} Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates.
 This is due to how the conditional Lyapunov drift is minimized.
@@
 
-\cmnt Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results.
+\resp We thank the reviewer for pointing out the missing information. We have included a figure on the number of backlogged packets over a period of time in Section \ref{time-correlated}.
+
+\cmnt{3} Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results.
 This reviewer recommends spending more space on the convergence, than on the description of the distributed techniques.
@@
 
-\cmnt Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier.
+\resp We agree with the reviewer. We have updated the manuscript with more details.
+
+\cmnt{4} Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier.
 This could easily be clarified.
 
-\cmnt - p. 1, col. 1, row 42: "userss"
+\resp We thank the reviewer for pointing out the misinterpretation of the text. We have included the statement accordingly in the introduction.
+
+\cmnt{5a} - p. 1, col. 1, row 42: "userss"
 
@@
 
-\cmnt - p.
+\cmnt{5b} - p.
 1, col.
@@
 
-\cmnt - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?
+\cmnt{5c} - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?
 
@@
 
-\cmnt - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead
+\cmnt{5d} - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead
 
@@
 
-\cmnt - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here
+\cmnt{5e} - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here
 
@@
 
-\cmnt - p.
+\cmnt{5f} - p.
 3, col.
@@
 
-\cmnt - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.
+\cmnt{5g} - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.
 
@@
 
-\cmnt - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).
+\cmnt{5h} - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).
 
@@
 
-\cmnt - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).
+\cmnt{5i} - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).
 
-\cmnt - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.
+\resp We have updated the NP hardness discussion in the revised version.
 
-\cmnt - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??
+\cmnt{5j} - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.
+
+\resp We thank the reviewer for pointing out the mistake. We have modified the text accordingly.
+
+\cmnt{5k} - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??
 
@@
 
-\cmnt - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).
+\cmnt{5l} - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).
 
-\cmnt - p.
+\resp We have revised the manuscript to make it clear.
+
+\cmnt{5m} - p.
 6, col.
@@
 
-\cmnt - p.
-6, col.
-1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs.
-However, does it affect the convergence of the algorithm?
+\resp We thank the reviewer for the comment. We have revised the manuscript accordingly.
 
-\resp We thank the reviewer for the comment.
+\cmnt{5n} - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?
 
-\cmnt - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?
+\resp We thank the reviewer for raising the concern on the convergence, we have updated the convergence proof in Appendix \ref{sec-3.5} to include much detail for clear understanding.
 
-\cmnt - p.
+\cmnt{5o} - p.
 7, col.
@@
 
-\cmnt - Table 1: "backpreassure"
+\cmnt{5p} - Table 1: "backpreassure"
 
@@
 
-\cmnt - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.
+\cmnt{5q} - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.
 

### 2015-02-10 Report/simulation_distributed.tex
Updated WSRM
nothing great
additions

@@
 \includegraphics[width=\columnwidth]{fig-3-2}
-\caption{Convergence behaviour of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace}}
-\label{fig-d} \vspace{-0.1in}
+\caption{Convergence behaviour of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm}}
+\label{fig-d}
 \end{figure}
@@
 	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
-	\label{fig-d-3.1} \vspace{-0.1in}
+	\label{fig-d-3.1}
 \end{figure}

### 2015-02-10 Report/convergence_centralized.tex
convergence_updated

--- 2015-02-03 Report/convergence_centralized.tex
@@
 \newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
-Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+
+To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, following conditions are necessary to prove the sequence convergence using Bolzano-Weierstrass theorem \cite{rudin1964principles}.
+\begin{itemize}
+	\item At each \ac{SCA} update, the objective value decreases monotonically 
+	\item At each \ac{AO} update, the objective value should decrease monotonically
+	\item Boundedness of the objective value sequence and the uniqueness of the limiting point.
+\end{itemize}
+In addition, we show that the converged point is in fact the stationary point of the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+
+The boundedness of the objective function can be justified by the convexity and the presence of the transmit power constraint.
+Since the objective function is convex, it is bounded from below.
+Due to the total power constraint \eqref{eqn-6.4}, the function is bounded from above as well.
+In addition, the feasible set is a compact set since the boundary points are also included in the feasible set.
+
+To prove the monotonicity of the objective function values, let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} equivalently as
 \begin{IEEEeqnarray}{rCl} \label{con}
@@
 
-In order to solve the problem, we resort to \ac{AO} by fixing a block of varibles and optimize for others.
+To solve the problem, we resort to \ac{AO} by fixing a block of varibles and optimize for others \cite{bezdek2002some}.
 In the problem \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint in \eqref{con-dc}.
@@
 \end{multline}
-Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and converges to a critical point.
+Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and converges to a limiting point.
 Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point of the problem \eqref{con}, since it is the minimizer only in the feasible set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, which depends on \me{\mx} and \me{\mz} only.
@@
 Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
-Note that the solution point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i})} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
+Note that the limiting point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i})} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
 
@@
 
+The uniqueness of the convex subproblems \eqref{con-m} are required for any sequence to convergence \cite{rudin1964principles}.
+For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders are guaranteed by the constraint \eqref{eqn-8}, which can be written as
+\begin{multline}
+\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
+- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
+\end{multline}
+where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the \eqref{eqn-mse-2} by
+\begin{multline}
+| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
+\end{multline}
+Since the limiting point is not unique for different initial point in the feasible set \me{\mc{F}}, the above objective function value sequence is pointwise continuous.
+
 To show the converged point of the iterative algorithm is in fact the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem.
@@
 The monotonic decrease in the objective is still valid if the variables \me{\mx,\my} and \me{\mz} are updated together, since the update in \me{\my} increases the objective function for a fixed point \me{\mx} and \me{\mz}.
-
-The uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of \ac{AO} \cite{bezdek2002some}.
-For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders are guaranteed by the constraint \eqref{eqn-8}, which can be written as
-\begin{multline}
-\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
-- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
-\end{multline}
-where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the \eqref{eqn-mse-2} by
-\begin{multline}
-| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
-\end{multline}
 Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.

### 2015-02-13 Report/decomposition_solutions.tex
halfcooked

@@
 Now, to decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which include all interference terms relevant for the transmission of \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method.
-Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through uplink sounding and the receive beamformers \me{\mvec{w}{l,k,n}}.
+Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through precoded uplink sounding using the receive beamformers \me{\mvec{w}{l,k,n}} \cite{komulainen2013effective}.
 

### 2015-02-13 Report/introduction.tex
halfcooked

@@
 \review{In contrast, the linear transmit precoders, which are complex vectors, are implicitly used as decision variables, thereby avoiding the explicit modeling of binary decision variables.
-It solves two purposes.
-First, the formulation determines the transmission rate on a certain resource, and, secondly, by making the transmit beamformer of a particular user to be a zero vector, the corresponding user will not be scheduled on a certain resource.
+It is used to determine the transmission rate of a user on a space-frequency resource if the precoder vector is non-zero.
+A zero transmit precoder indicates the absence of the user on a given resource.
 In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence}.

### 2015-02-13 Report/kkt_mse_approach.tex
halfcooked

@@
 The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements.
-\review{We consider an idealistic assumption of a \ac{TDD} system due to the knowledge of complete channel information at the transmitter}.
+\review{We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter}.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
@@
 \sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
-\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
+%\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}} eventually.
-\review{Since \me{\rho} depend on the system size, we fix the value of \me{\rho = 0.1} in our simulations irrespective of the system, which affects the convergence behavior marginally.}
+\review{The choice of \me{\rho} is susceptible to the system model under consideration, which affects the convergence speed of the iterative algorithm.
+In our simulations, we fixed \me{\rho = 0.1} irrespective of the model under consideration.}
 
@@
 In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations.
-If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments for controlling overallocation problem and the nonincreasing objective function, since the earlier iterates are in fact the operating point for the current iteration.}
+If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.}
 

### 2015-02-13 Report/problem_formulation.tex
halfcooked

--- 2015-01-28 Report/problem_formulation.tex
@@
 \end{equation}
-which is equivalent to the objective defined in \eqref{q_gen_sum}.
-Note that the equivalence can be seen either by discarding \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly greater than the maximum allowable transmission.}
+which is similar to the objective in \eqref{q_gen_sum}.
+Note that the equivalence can be seen either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly large for all users such that \me{t_k^2} has no impact on the objective function.}
 

### 2015-02-13 Report/sub_channel_wsrm.tex
halfcooked

@@
 In addition, the iterations required for the algorithm convergence increases with the problem size.
-To overcome the complexity, we can adopt the distributed approaches presented in \cite{palomar2006tutorial,boyd2011distributed} for sub-channel wise precoder design using primal or dual decomposition.
+To overcome the complexity, we can decouple the problem to sub-channel specific subproblems by using distributed approaches presented in \cite{palomar2006tutorial,boyd2011distributed} to design the precoders using primal or dual decomposition.
 
-As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which designs the precoders independently across the sub-channels in a sequential manner using the unserviced  number of packets after each sub-channel allocation.
-The \ac{BS} transmit power is fixed across the sub-channel \me{n} as \me{P_{\max,n}}.
-The power sharing can be equal or based on predetermined pattern as in partial frequency reuse across the sub-channels.
-After fixing the power and the backlogged packets for a sub-channel \me{i}, precoders are determined using the \ac{JSFRA} algorithm presented in Section \ref{sec-3.2.1} or \ref{sec-3.3} for each sub-channel in a sequential manner.
-Once the precoders and the corresponding rates are identified, the unserviced backlogged packets for the next sub-channel \me{i+1} is updated for user \me{k} as
+As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation only for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
+The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels by adhering to
+\begin{equation}
+\sum_{i=1}^N P_{\max,i} = P_{\max}.
+\end{equation}
+Even though \me{N} sub-channels are present at any given scheduling instant, precoders are solved for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the backlogged packets.
+Let \me{Q_{k,i}} number of backlogged packets associated with user \me{k} before solving for precoders specific to the sub-channel \me{i}.
+Since the precoder design is sequential, for the initial sub-channel, the number of backlogged packets is given by \me{Q_{k,1} = Q_k} and for the consecutive sub-channels, it is given by
 \begin{equation}	\label{eqn-weight}
@@
 \end{equation}
-where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream and the initial values are given as \me{Q_{k,1} = Q_k, \forall k}.
+where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream.
 Note that the proposed scheme is sensitive to the order of the sub-channel selection due to the sequential precoder design for each sub-channel.
 However, the \ac{SRA} approach provides faster convergence in contrast to the \ac{JSFRA} formulation due to the substantial reduction in the optimization variables for each sub-channel problem.
-As the number of user increases, the \ac{SRA} formulation will be insusceptible to the sub-channel ordering due to the channel hardening and the availability of users with all possible channel vectors.
+As the number of user increases, the \ac{SRA} formulation will be insusceptible to the sub-channel ordering due to the multi-user diversity.
 %The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}

### 2015-02-13 Report/wsrm_formulation.tex
halfcooked

@@
 We now present an iterative algorithm to solve problem \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
-To do this, first by using the \ac{SINR} expression in \eqref{eq:SINR}, we equivalently reformulate problem \eqref{eqn-3} as
+The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system.
+Since the \ac{SINR} expression in \eqref{eq:SINR} cannot be handled directly to formulate the problem, we relax the equality constraint in \eqref{eq:SINR} by the inequality constraints to solve for the transmit and the receive precoders as
 \iftoggle{single_column}{
@@
 }
-\review{Since the equality of the \ac{SINR} in \eqref{eq:SINR} cannot be included as a constraint directly, we relaxed the \ac{SINR} expression by using inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3}.
+\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation.
 Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.

### 2015-02-17 Report/convergence_centralized.tex
final version

@@
 \newcommand{\eqn}[1]{\(#1\)}
-\newcommand{\mx}{\mbf{x}}
-\newcommand{\my}{\mbf{y}}
-\newcommand{\mz}{\mbf{z}}
-\newcommand{\mxb}{{{\mbf{x}}}}
-\newcommand{\myb}{{{\mbf{y}}}}
+\newcommand{\mx}{\mbf{m}}
+\newcommand{\my}{\mbf{w}}
+\newcommand{\mz}{\mbfa{\gamma}}
+\newcommand{\mxb}{{{\mbf{m}}}}
+\newcommand{\myb}{{{\mbf{w}}}}
 \newcommand{\iterate}[2]{{#1}^{(#2)}}
 \newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
+
+To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are to be satisfied by the objective function sequence to prove the convergence of the transmit and the receive beamformers.
+\begin{itemize}
+	\item The objective function should be bounded below
+	\item The feasible set should be a compact set
+	\item The sequence should be monotonically decreasing for each iteration
+	\item Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
+\end{itemize}
+Assuming the above conditions are satisfied by the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point.
+Using the property of one-to-one mapping between the feasible domain and the objective value, the transmit and the receive beamformers also approaches to a limiting point since the inverse mapping is unique in each iteration.
+Let us prove the above conditions are satisfied by the centralized problem.
+Note that the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1} has a solution set with the same objective value due to the invariance of the \ac{SINR} expression to the phase rotations, but the relaxed iterative convex problems lead to a unique solution depending on the initialization point.
+
+\subsection{Boundedness}
+
+The feasible set of the relaxed nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded due to the total power constraint on the transmit precoders \eqref{eqn-6.4}.
+Note that the other variables are also bounded in accordance with this constraint.
+Since the feasible set also includes the boundary value due to the inequality constraint, it is closed and compact.
+
+To prove the boundedness of the objective function, it is enough to show that the objective function is bounded below due to the minimization objective.
+Since the minimum value of the norm operator is zero, \textit{i.e}, the limiting point is \me{< -\infty}, it is bounded below.
+Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
+Note that the objective function is continuous everywhere and not differentiable only at the minimum.
+
+\subsection{Monotonicity}
+
+Let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+\begin{IEEEeqnarray}{rCl} \label{con}
+	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
+	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
+	&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
+	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
+\end{IEEEeqnarray}
+where \me{g_2,f} are convex functions and \me{h} is a linear function.
+Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both.
+Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} correspond to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}.
+Other convex constraints are addressed by the constraint \eqref{con-cvx}.
+With this, the feasible set of the problem \eqref{con} is given by
+\begin{IEEEeqnarray}{rl}
+\mc{F} = \{ \; \mx,\my,\mz \; \big | \; & h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
+								& g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \; \} \nonumber
+\end{IEEEeqnarray}
+
+To solve \eqref{con}, we adopt \ac{AO} by fixing a block of varibles and optimize for others \cite{bezdek2002some}.
+In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}.
+We adopt \ac{SCA} approach presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets.
+Since the proposed method involves two level of iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
+Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\mx}.
+Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denotes the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
+For the sake of clarity, we define the optimal value of \me{\mz} obtained for the \me{\ith{i}} \ac{AO} iterate for the fixed \me{\my} variable as \me{\iter{\mz}{\ast|y}{i}}.
+
+To begin with, let us consider the variable \me{\my} is fixed for the \ac{AO} \me{i} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
+In order to solve for \me{\mx} in the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate of \me{\mx} as
+\begin{multline} \label{con-relax}
+\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+\end{multline}
+Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
+\begin{subeqnarray} \label{con-m}
+	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
+	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
+	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
+	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
+\end{subeqnarray}
+Let the feasible set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
+In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\my = \iter{\my}{\ast}{i-1}} operating at \me{\iter{\mx}{k}{i}}, let us consider that \eqref{con-m} yields \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution for the \me{\ith{k}} iteration.
+Note that the point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality
+\begin{multline}\label{con-sub-set}
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\ + h(\iter{\mz}{k+1}{i}) \leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0.
+\end{multline}
+Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
+At each \ac{SCA} iteration, the feasible set includes the optimal point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, thereby, leading to the monotonic decrease in the objective function \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
+\begin{multline} \label{con-convergence}
+f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
+\end{multline}
+Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches limiting point as \me{k \rightarrow \infty}.
+Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point for \eqref{con}, since it is the minimizer only over the feasible set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
+
+Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
+Even after treating \me{\mx} as a constant, the problem is still nonconvex due to the \ac{DC} constraint.
+Following similar approach, we can find the minimizer \me{\iter{\my}{k}{i}} and \me{\iter{\mz}{k}{i}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}.
+Note that \me{\iter{\mz}{k}{i}} is reused since the variable \me{\mx} is fixed for the \me{\ith{i}} \ac{AO} iteration.
+The convergence and the nonincreasing behavior of the problem follows similar arguments as above.
+Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
+Note that the limiting point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i})} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
+
+Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
+\begin{multline}
+f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
+\leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
+\end{multline}
+Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
+To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
+Since we linearize the convex function in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}} using \eqref{con-sub-set}.
+Using this, we can show the monotonicity of the objective value sequence as
+\begin{equation*}
+f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}).
+\end{equation*}
+Note that the feasible set follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} iteration.
+
+\subsection{Uniqueness}
+
+The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, can be attributed to the linearization performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}.
+The linearized \eqref{eqn-8} can be written as
+\begin{multline}
+\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
+- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
+\end{multline}
+where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and the \ac{MSE} expression as
+\begin{multline}
+| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
+\end{multline}
+Note that the receive beamformer \me{\mvec{w}{l,k,n}} is unique for the given set of transmit precoders.
+
+When the objective function is zero, the uniqueness of the transmit precoders using the above constraints are not valid since the relaxations used in the formulation need not be tight to provide a unique set of transmit precoders.
+To obtain a unique set of transmit precoders even when the objective is zero for a single \ac{BS}, we can regularize the objective with the total transmit power expression without affecting the optimal solution as
+\begin{equation*}
+\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
+\end{equation*}
+for some arbitrarily small value of the scaling factor \me{\varphi \approx 0}.
+
+\subsection{Stationary Point}
+
+To show the limiting point of the iterative algorithm is the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem.
+Since the converged point is the minimizer for the iterative algorithm such that
+\begin{multline} \label{con-opt}
+f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
+f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
+\end{multline}
+the solution is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.
+The monotonic decrease in the objective is still valid if the variables \me{\mx,\my} and \me{\mz} are updated together, since the update in \me{\my} increases the objective function for a fixed point \me{\mx} and \me{\mz}.
+Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.
+
+\begin{comment}
 
@@
 
+\end{comment}
+
 \begin{comment}

### 2015-02-17 Report/ieee_journal.tex
additions
final version

@@
-\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,journal,twocolumn,letterpaper]{./../Styles/IEEEtran}
 
+\usepackage[section]{placeins}
 \usepackage{amsmath,amssymb}
 \usepackage{acronym,etoolbox}
+\usepackage{graphicx,epstopdf}
 \usepackage[ruled]{algorithm2e}
-\usepackage[dvipdfmx]{graphicx}
 \usepackage[usenames,dvipsnames]{xcolor}
-\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
+\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
 \usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}
 
-\graphicspath{{./../Figures/}{./../Figures/Linux/}}
+\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}}
 \DeclareGraphicsExtensions{.eps}
+
+\ifCLASSINFOpdf
+\epstopdfsetup{update,prepend,prefersuffix=false,suffix=}
+\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
+\pdfcompresslevel=9
+\fi
 
@@
 
+\newtoggle{includereview}
 \newtoggle{enable_dist_fig}
@@
 \togglefalse{enable_dist_fig}
+\toggletrue{includereview}
 
@@
 
+\iftoggle{includereview}{
+\newpage
+\onecolumn
+\doublespacing
 \section{Response to reviewer comments}
 \input{review_comments}
+\twocolumn
+\newpage
+\singlespacing
+}
 
@@
 
-\subsection{Reduced Complexity Resource Allocation} \label{sec-3.4}
+\subsection{Reduced Complexity Spatial Resource Allocation (\acs{SRA})} \label{sec-3.4}
 \review{\input{sub_channel_wsrm}}
@@
 \subsection{Average Backlogged Packets Over Slots} \label{time-correlated}
-
 \review{\input{time_correlated}}
@@
 
-\section{Convergence Analysis of Centralized Algorithm} \label{sec-3.5}
+\section{Convergence Proof for Centralized Algorithm} \label{sec-3.5}
 \review{\input{convergence_centralized}}

### 2015-02-17 Report/review_comments.tex
final version

@@
 It would be ideal to compare with the Q-WSRME algorithm which performs similar to the Q-WSRM when the queued packets are large enough to be emptied by the current transmissions.
-Fig.
-\ref{fig-review} compares the centralized algorithms using average number of backlogged packets after \me{100} slots of transmission for different arrival rate.
-Note that the average arrival rate of all the users are same but the instantaneous arrivals are based on the Poisson distribution.
-It can be seen from Fig.
-\ref{fig-review} that the JSFRA scheme with \me{q=2} performs similar to the Q-WSRME scheme for higher arrival rates, which explains the dropping of the squared rate term in the Q-WSRM formulation.
-When the average arrival rate is smaller, the JSFRA scheme with \me{q=2} performs noticeably better than the Q-WSRME scheme as can be seen from the average number of backlogged packets.
-In all packet arrival scenarios, JSFRA scheme with \me{q=1} reduces the average number of backlogged packets over the given slots is lesser than the Q-WSRME scheme.
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{Review/reviewer.eps}
-\label{fig-review}
-\caption{System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
-\end{figure}
-The discussions are included in the Section \ref{time-correlated}.
+In Section \ref{time-correlated}, we have discussed the performance of the proposed schemes with the existing \ac{Q-WSRME} using the average number of backlogged packets at each instant for different arrival rates.
+We have also compared using the instantaneous backlogged packets in the system for a arrival rate of \me{A_k = 5} bits for each user.
 

### 2015-02-17 Report/simulation_intro.tex
final version

@@
 The queues are generated based on the Poisson process with the average values specified in each section presented.
+\begin{table*}
+	\centering
+	\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
+	\renewcommand{\arraystretch}{1.25} \scriptsize
+	\begin{tabular}{|*{14}{c|}}
+		\hline
+		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
+		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
+		\cline{3-14}
+		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
+		\hline
+		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
+		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
+		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
+		\hline
+		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
+		\hline
+	\end{tabular}
+	\label{tbl-1}
+\end{table*}
+\begin{figure*}
+	\centering
+	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
+		\includegraphics[width=0.5\textwidth]{fig-1-4}
+		\label{fig-1}}
+	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
+		\includegraphics[width=0.5\textwidth]{fig-2-5}
+		\label{fig-2}}
+	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm in objective}}
+	\label{fig-a}
+\end{figure*}

### 2015-02-17 Report/simulation_results.tex
additions
final version

@@
 The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits, respectively.
-\begin{table*}
-	\centering
-		\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
-	\renewcommand{\arraystretch}{1.25} \scriptsize
-	\begin{tabular}{|*{14}{c|}}
-		\hline
-		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
-		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
-		\cline{3-14}
-		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
-		\hline
-		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
-		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
-		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
-		\hline
-		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
-		\hline
-	\end{tabular}
-	\label{tbl-1}
-\end{table*}
-\begin{figure*}
-	\centering
-	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
-		\includegraphics[width=0.5\textwidth]{fig-1-4}
-		\label{fig-1}}
-	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
-		\includegraphics[width=0.5\textwidth]{fig-2-5}
-		\label{fig-2}}
-	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates}
-	\label{fig-a}
-\end{figure*}
-
-Table \ref{tbl-1} tabulates the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using the \ac{WMMSE} design \cite{wmmse_shi}.
-The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted as \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
-Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} is scheduled in the first sub-channel due to the better channel condition.
-In contrast, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets waiting at the transmitter.
-The rate allocated for \me{\mc{U}(2)} on the second sub-channel is higher in \ac{JSFRA} scheme compared to the other schemes.
-It is due to the efficient allocation of the total power shared across the sub-channels.
 \begin{table}
@@
 \end{table}
+
+Table \ref{tbl-1} tabulates the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using the \ac{WMMSE} design \cite{wmmse_shi}.
+The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted as \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
+Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} is scheduled in the first sub-channel due to the better channel condition.
+In contrast, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets waiting at the transmitter.
+The rate allocated for \me{\mc{U}(2)} on the second sub-channel is higher in \ac{JSFRA} scheme compared to the other schemes.
+It is due to the efficient allocation of the total power shared across the sub-channels.
 

### 2015-02-17 Report/time_correlated.tex
nothing great
final version

@@
-We discuss performance of the \ac{JSFRA} algorithm for different values of \me{\ell_q} over multiple time slots.
+We discuss performance of the \ac{JSFRA} algorithm for different values of \me{\ell_q} over multiple transmission slots.
 It is compared with the existing \ac{Q-WSRME} scheme by varying the average arrival rate \me{A_k} of all users.
 Fig.
-\ref{fig-review} demonstrates the performance of the centralized algorithms for different \me{\ell_q} values.
-The horizontal axis indicates the average number of arrivals \me{A_k} in bits per user and it is constant for all users in the system.
-The vertical axis corresponds to the average of number of backlogged packets left in the system after each time slot.
+\ref{fig-time-analysis} demonstrates the performance of the centralized algorithms for different \me{\ell_q} values.
 Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and is based on Poisson arrival process.
 We considered a \me{4 \times 1} \ac{MIMO} system with \me{N = 4} sub-channels and \me{N_B = 2} \acp{BS}.
-The path loss is modeled as a uniform random variable \me{[0,-3]} dB with the maximum \ac{SINR} seen by any user is \me{6} dB.
-The average is performed over \me{100} time slots.
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{Review/reviewer.eps}
-\label{fig-review}
-\caption{System \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
-\end{figure}
+The path loss is modeled using a uniform random variable \me{[0,-3]} dB with the maximum \ac{SINR} seen by any user is \me{6} dB.
 
+Fig.
+\ref{fig-review} compares various schemes with the average number of backlogged packets present in the system after each transmission slot.
 The performance of the \ac{JSFRA} scheme using \me{\ell_2} and \ac{Q-WSRME} approach are similar in the average number of residual packets after each transmission slot.
@@
 It can be seen from Fig.
-\ref{fig-review} that the average number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} formulation due to the greedy resource allocation by serving users with better channel conditions.
-Fig \ref{fig-review} shows that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs worst in terms of the average number of backlogged packets due to the fairness constraints.
+\ref{fig-review} and Fig.
+\ref{fig-review-time} that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} formulation due to the greedy allocation by serving users with better channel conditions.
+Fig.
+\ref{fig-time-analysis} shows that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs worst in terms of the average number of backlogged packets due to the instantaneous fairness constraints.

### 2015-02-17 Report/wsrm_formulation.tex
final version

@@
 \review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation.
-Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.
+Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}}.
 \review{The constraints are tight when each \ac{BS} objective is non zero at the optimal point, as discussed in Appendix \ref{a-3}}.
@@
 
-In order to find a tractable solution for \eqref{eqn-6}, we note that the constraints \eqref{eqn-6.4} are convex with involved variables.
+In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables.
 Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-Towards this end, we resort to the \ac{AO} technique by fixing the linear receivers, and finding the optimal transmit beamformers.
+We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers.
 For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task.

### 2015-02-17 Report/convergence_centralized.tex
modified convergence

@@
 \begin{itemize}
-	\item The objective function should be bounded below
-	\item The feasible set should be a compact set
-	\item The sequence should be monotonically decreasing for each iteration
-	\item Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
+	\item[(a)] The function should be coercive and bounded below
+	\item[(b)] The feasible set should be a compact set
+	\item[(c)] The sequence should be monotonically decreasing for each iteration
+	\item[(d)] Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
 \end{itemize}
+Using \cite[Prop.
+A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied.
+Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function, the transmit and the receive precoders.
 Assuming the above conditions are satisfied by the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point.
 Using the property of one-to-one mapping between the feasible domain and the objective value, the transmit and the receive beamformers also approaches to a limiting point since the inverse mapping is unique in each iteration.
-Let us prove the above conditions are satisfied by the centralized problem.
-Note that the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1} has a solution set with the same objective value due to the invariance of the \ac{SINR} expression to the phase rotations, but the relaxed iterative convex problems lead to a unique solution depending on the initialization point.
+Note that the relaxed iterative problem has the unique solution but not the original nonconvex problem.
+Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different unitary rotations.
+The limiting point of the iterative algorithm is susceptible to the initial operating point due to the linearization of the nonconvex \ac{DC} constraint.
 
@@
 
-To prove the boundedness of the objective function, it is enough to show that the objective function is bounded below due to the minimization objective.
+To prove the boundedness, it is enough to show that the objective function is bounded below due to the minimization objective.
 Since the minimum value of the norm operator is zero, \textit{i.e}, the limiting point is \me{< -\infty}, it is bounded below.
 Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
-Note that the objective function is continuous everywhere and not differentiable only at the minimum.
+Note that the norm operator in the objective function is continuous and coercive over the feasible set but not differentiable at its minimum point.
+Using the conditions (a) and (b) we can guarantee the existence of a minimizer to the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 

### 2015-02-17 Report/convergence_distributed.tex
modified convergence

@@
 The feasibility of the interior point is verified by having a non zero precoder for only one user.
-Therefore, by following \cite{bertsekas1989parallel} Proposition 4.2, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.
+Therefore, by following \cite[Prop.
+4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.

### 2015-02-18 Report/convergence_centralized.tex
updated convergence proof

@@
 A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied.
-Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function, the transmit and the receive precoders.
-Assuming the above conditions are satisfied by the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point.
-Using the property of one-to-one mapping between the feasible domain and the objective value, the transmit and the receive beamformers also approaches to a limiting point since the inverse mapping is unique in each iteration.
+Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
+
+Assuming the above conditions are satisfied by the objective function of the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point.
+The one-to-one mapping between the feasible domain and the objective function value is required to prove the convergence of the transmit and the receive beamformers upon convergence of the objective function value iterates.
 Note that the relaxed iterative problem has the unique solution but not the original nonconvex problem.
-Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different unitary rotations.
-The limiting point of the iterative algorithm is susceptible to the initial operating point due to the linearization of the nonconvex \ac{DC} constraint.
+Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary matrix rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different phase rotations.
+The limiting point of the iterative algorithm is susceptible to the initial feasible point, since it is the operating point for linearizing the nonconvex \ac{DC} constraint.
 
@@
 Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
-Note that the norm operator in the objective function is continuous and coercive over the feasible set but not differentiable at its minimum point.
-Using the conditions (a) and (b) we can guarantee the existence of a minimizer to the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive.
+Note that the norm operator is not differentiable at the minimum point for \me{\ell_1} and \me{\ell_infty}.
+Using conditions (a) and (b), we can guarantee the existence of a minimizer to the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 

### 2015-02-18 Report/introduction.tex
updated convergence proof

@@
 
-The connection between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{mse_duality,christensen2008weighted} can also be used to solve the \ac{WSRM} problem.
+The relation between the achievable capacity and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can be used to solve the \ac{WSRM} problem \cite{mse_duality}.
 In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients.

### 2015-02-19 Report/convergence_centralized.tex
updated

@@
 The linearized \eqref{eqn-8} can be written as
-\begin{multline}
+\begin{multline} \label{uniqueness-1}
 \gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
@@
 where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and the \ac{MSE} expression as
-\begin{multline}
+\begin{multline} \label{uniqueness-2}
 | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
@@
 
-When the objective function is zero, the uniqueness of the transmit precoders using the above constraints are not valid since the relaxations used in the formulation need not be tight to provide a unique set of transmit precoders.
-To obtain a unique set of transmit precoders even when the objective is zero for a single \ac{BS}, we can regularize the objective with the total transmit power expression without affecting the optimal solution as
+When the objective function is zero, the uniqueness of the transmit precoders using \eqref{uniqueness-1} and \eqref{uniqueness-2} are not valid due to the inactive constraints \eqref{eqn-6.2} and \eqref{eqn-mse-1.2}.
+To obtain a unique set of transmit precoders when the objective is zero for a single \ac{BS}, we can regularize the objective with the total transmit power expression without affecting the optimal solution as
 \begin{equation*}
@@
 
-To show the limiting point of the iterative algorithm is the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem.
-Since the converged point is the minimizer for the iterative algorithm such that
+To show the limiting point of the iterative algorithm is the stationary point of \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem.
+Since the converged point is a minimizer satisfying
 \begin{multline} \label{con-opt}

### 2015-02-25 Report/decomposition_solutions.tex
updated_lineno

--- 2015-02-02 Report/decomposition_solutions.tex
@@
 
-Now, to decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which include all interference terms relevant for the transmission of \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method.
-Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through uplink sounding and the receive beamformers \me{\mvec{w}{l,k,n}}.
+To decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method.
+\R{who-knows-what}Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through precoded uplink sounding using the receive beamformers \me{\mvec{w}{l,k,n}} \cite{komulainen2013effective}.
+Each receiver is assumed to have the channel and the transmit precoders of all \acp{BS} in \me{\mc{B}} to evaluate \ac{MMSE} receiver.
 

### 2015-02-25 Report/review_comments.tex
updated_lineno

@@
 \resp We understand the reviewer concerns.
-We have modified the convergence section to include additional information to provide more clarity.
-Appendix \ref{sec-3.5} discuss the convergence proof of the proposed algorithm in detail.
+We have updated the convergence section to include additional information to provide more clarity.
+Appendix \ref{sec-3.5} discusses the convergence proof of the proposed algorithm in detail.
 
@@
 
-\resp We agree with the reviewers view. We have updated the convergence proof to include the discussions on the stationary point and the optimal point.
+\resp We agree with the reviewers view.
+We have updated the convergence proof for both centralized and distributed algorithm to include the discussions on the stationary point and the locally optimal point in Appendix \ref{sec-3.5} and Section \ref{sec-dist-conv}.
 
@@
 In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which is not the stationary point when the algorithm is allowed to converge.
-In Section \ref{sec-4.3}, we have discussed a practical approach based on the KKT conditions, which attains a sub-optimal point with few number of iterations.
+In Section \ref{sec-4.3}, we have discussed a practical approach based on the KKT conditions, which attains a local optimal point with few number of iterations.
 
@@
 
-\resp We understand the concern of the reviewer. We have updated the distributed section to include all the details pointed by the reviewer.
+\resp We understand the concern of the reviewer.
+We have updated the distributed section to include all the details pointed by the reviewer.
+Section \ref{sec-4.2} includes the updated discussions on ADMM scheme.
 
@@
 
-\resp We understand the concern of the reviewer. We have updated the distributed section to include all the details pointed by the reviewer.
+\resp We understand the concern of the reviewer.
+We have updated the distributed section to include the details pointed by the reviewer.
+Section \ref{sec-4.2} includes the updated discussions on ADMM scheme.
+In addition, \lr{who-knows-what} includes information about who knows what in the network.
 

### 2015-02-26 Report/convergence_centralized.tex
included antti comments

@@
 
-To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are to be satisfied by the objective function sequence to prove the convergence of the transmit and the receive beamformers.
+To prove the convergence of the transmit precoders, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
 \begin{itemize}
@@
 	\item[(b)] The feasible set should be a compact set
-	\item[(c)] The sequence should be monotonically decreasing for each iteration
+	\item[(c)] The sequence of the objective values should be monotonically decreasing in each iteration
 	\item[(d)] Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
@@
 
-Assuming the above conditions are satisfied by the objective function of the iterative algorithm, using Bolzano-Weierstrass theorem \cite{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a unique limiting point.
+Assuming the above conditions are satisfied by the objective function of the iterative algorithm, using \cite[Th.
+3.14]{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a limiting point.
 The one-to-one mapping between the feasible domain and the objective function value is required to prove the convergence of the transmit and the receive beamformers upon convergence of the objective function value iterates.
-Note that the relaxed iterative problem has the unique solution but not the original nonconvex problem.
+Note that the iterative relaxed convex subproblems has the unique solution but not the original nonconvex problem.
 Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary matrix rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different phase rotations.
@@
 
-\subsection{Boundedness}
+\subsection{Boundedness and Compactness}
 
@@
 Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\mx}.
-Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denotes the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
+Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denote the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
 For the sake of clarity, we define the optimal value of \me{\mz} obtained for the \me{\ith{i}} \ac{AO} iterate for the fixed \me{\my} variable as \me{\iter{\mz}{\ast|y}{i}}.
@@
 Note that the point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality
-\begin{multline}\label{con-sub-set}
+\allowdisplaybreaks{\begin{multline}\label{con-sub-set}
 h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\ + h(\iter{\mz}{k+1}{i}) \leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0.
-\end{multline}
+\end{multline}}
 Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
@@
 Note that \me{\iter{\mz}{k}{i}} is reused since the variable \me{\mx} is fixed for the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the problem follows similar arguments as above.
+The convergence and the nonincreasing behavior of the problem follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver}.
 Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
@@
 Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
-\begin{multline}
+\allowdisplaybreaks{\begin{multline}
 f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
 \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
-\end{multline}
+\end{multline}}
 Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
@@
 Note that the feasible set follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} iteration.
+Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.
 
@@
 
-The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, can be attributed to the linearization performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}.
+Now, to claim the convergence of transmit precoders and receive beamformers, we need to show the uniqueness in the mapping between the transmit and receive beamformers to the objective function.
+The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, can be attributed to the linear relaxation performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}.
 The linearized \eqref{eqn-8} can be written as
@@
 \end{multline}
-Note that the receive beamformer \me{\mvec{w}{l,k,n}} is unique for the given set of transmit precoders.
+Note that the receive beamformer \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} is unique for the given set of transmit precoders.
+It is due to the constraints \eqref{uniqueness-1} and \eqref{uniqueness-2}, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoders phase rotations and thereby having a unique minimizer.
 
 When the objective function is zero, the uniqueness of the transmit precoders using \eqref{uniqueness-1} and \eqref{uniqueness-2} are not valid due to the inactive constraints \eqref{eqn-6.2} and \eqref{eqn-mse-1.2}.
-To obtain a unique set of transmit precoders when the objective is zero for a single \ac{BS}, we can regularize the objective with the total transmit power expression without affecting the optimal solution as
+To obtain a unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the total transmit power expression without affecting the optimal solution as
 \begin{equation*}
@@
 Since the converged point is a minimizer satisfying
-\begin{multline} \label{con-opt}
+\allowdisplaybreaks{\begin{multline} \label{con-opt}
 f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
 f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
-\end{multline}
+\end{multline}}
 the solution is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
@@
 The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.
-The monotonic decrease in the objective is still valid if the variables \me{\mx,\my} and \me{\mz} are updated together, since the update in \me{\my} increases the objective function for a fixed point \me{\mx} and \me{\mz}.
-Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.
+Using the above arguments, we can show that the \ac{JSFRA} schemes attains a stationary point of the original nonconvex problem.
 

### 2015-02-26 Report/decomposition_solutions.tex
included antti comments

--- 2015-02-13 Report/decomposition_solutions.tex
@@
 
-Now, to decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which include all interference terms relevant for the transmission of \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method.
+To decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method.
 Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through precoded uplink sounding using the receive beamformers \me{\mvec{w}{l,k,n}} \cite{komulainen2013effective}.
+Each receiver is assumed to have the channel and the transmit precoders of all \acp{BS} in \me{\mc{B}} to evaluate \ac{MMSE} receiver.
 

### 2015-02-26 Report/ieee_journal.tex
updated_lineno
included antti comments

@@
 \togglefalse{enable_dist_fig}
-\toggletrue{includereview}
+\togglefalse{includereview}
 
@@
 	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
-Part of this work has been published in ICASSP 2014 conference.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
+Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
 	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
@@
 \singlespacing
+\setcounter{page}{1}
 }
@@
 \maketitle
-
-\acused{MU-MIMO}
 

### 2015-02-26 Report/introduction.tex
included antti comments

@@
 \subsubsection*{Main Contributions}
-\review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS}.
-The proposed design provides better control over the resource allocation strategy by the change of a variable.
-Since the transmissions are guided by the backlogged packets, the proposed formulation limits the resource allocation beyond the number of backlogged packets without additional rate constraint.
-Since the problem is nonconvex due to \ac{DC} constraints, we adopt \ac{SCA} to solve by a sequence of convex subproblems using first order approximations.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint.
+\review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS} queues.
+Since the transmissions are guided by the backlogged packets, the proposed formulation limit the allocations beyond the number of backlogged packets without additional rate constraint.
+We adopt \ac{SCA} to solve by a sequence of convex subproblems using first order approximations due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint.
 First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders.

### 2015-02-26 Report/kkt_mse_approach.tex
included antti comments

@@
 Since the problem solution in \eqref{kkt-mse-4} is equivalent to the centralized formulation in \eqref{eqn-mse-2} if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}, the problem is guaranteed to converge to the centralized solution.
-Note that it requires four iterations to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders.
+Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders.
 In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations.

### 2015-02-26 Report/problem_formulation.tex
included antti comments

@@
 which is similar to the objective in \eqref{q_gen_sum}.
-Note that the equivalence can be seen either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly large for all users such that \me{t_k^2} has no impact on the objective function.}
+It is achieved either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly large for all users such that \me{t_k^2} has no impact on the objective function.}
 

### 2015-02-26 Report/problem_formulation_intro.tex
included antti comments

@@
-To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation given by
+To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation objective as given by
 \begin{equation}
@@
 \end{equation}
-where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}}.
+where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receivers \me{\mvec{w}{l,k,n}}.
 
@@
 
-For practical reasons, we may impose a constraint that the maximum number of transmitted bits for the user \me{k} is limited by the total number of backlogged packets available at the transmitter.
+For practical reasons, we impose a constraint on the maximum number of transmitted bits for the user \me{k}, since it is limited by the total number of backlogged packets available at the transmitter.
 As a result, the number of backlogged packets \me{v_k} for user \me{k} remaining in the system is given by

### 2015-02-26 Report/simulation_distributed.tex
final version
included antti comments

@@
 Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{fig-3-2}
+	\caption{Convergence of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
+	\label{fig-d}
+\end{figure}
 
@@
 \ref{fig-d} that the distributed algorithms approach the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{fig-9-3}
+	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
+	\label{fig-d-3.1}
+\end{figure}
 
-\iftoggle{enable_dist_fig}
-{	
+Fig.
+\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents by plotting the total number of backlogged packets at each \ac{SCA} update point.
+The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective.
+The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}.
+If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one.
+A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig.
+\ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}.
+It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function.
+It can be seen that the heuristic method oscillates near the stationary point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
+\begin{figure*}
+	\centering
+	\subfloat[][Average backlogged packets in the system after \me{100} transmission instants]{
+		\includegraphics[width=0.48\textwidth]{average_queue_over_time}
+		\label{fig-review}
+	}
+	\hfill
+	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 5} bits]{
+		\includegraphics[width=0.48\textwidth]{instant_queue_over_time}
+		\label{fig-review-time}
+	}
+	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
+	\label{fig-time-analysis}
+\end{figure*}
+
+The objective values are mentioned in the legend for all the schemes and the objective of the \me{\ell_2} norm is not the same as that of the \me{\ell_1} norm used for plotting.
+For simulations, we update all variables in \eqref{kkt-mse-4} at once at each iteration, \textit{i.e}, \me{J_{\max} = 1}, which is well justified for the practical implementations due to the signaling overheads.
+The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} approach achieves nearly the same value of \me{6.62} with different \me{\chi}, due to the limited number of iterations for the dual variable convergence between each \ac{SCA} update.
+Fig.
+\ref{fig-d-3.1} also shows the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRME} scheme compared to the \me{\ell_2} norm which includes it.
+By dropping it, the \ac{Q-WSRME} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues.
+On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.
+
+\begin{comment}
+
 In Fig.
@@
 It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
-\begin{figure*}
+\begin{figure*}[t]
 	\centering
@@
 \end{figure*}
-% \begin{figure*}
-% \centering
-% \begin{subfigure}{0.49\textwidth}
-% \includegraphics[width=\textwidth]{fig-5}
-% \caption{Queue deviation}
-% \end{subfigure}
-% \hfill
-% \begin{subfigure}{0.49\textwidth}
-% \includegraphics[width=\textwidth]{fig-6}
-% \caption{Sum rate performance}
-% \end{subfigure}
-% \caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
-% \label{fig-d-2}
-% \end{figure*}
-}{
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{fig-3-2}
-\caption{Convergence behaviour of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm}}
-\label{fig-d}
-\end{figure}
-}
-Fig.
-\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents by plotting the total number of backlogged packets at each \ac{SCA} update point.
-The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective.
-The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}.
-If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one.
-A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig.
-\ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}.
-It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function.
-It can be seen that the heuristic method oscillates near the stationary point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{fig-9-3}
-	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
-	\label{fig-d-3.1}
-\end{figure}
 
-The objective values are mentioned in the legend for all the schemes and the objective of the \me{\ell_2} norm is not the same as that of the \me{\ell_1} norm used for plotting.
-For simulations, we update all variables in \eqref{kkt-mse-4} at once at each iteration, \textit{i.e}, \me{J_{\max} = 1}, which is well justified for the practical implementations due to the signaling overheads.
-The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} approach achieves nearly the same value of \me{6.62} with different \me{\chi}, due to the limited number of iterations for the dual variable convergence between each \ac{SCA} update.
-Fig.
-\ref{fig-d-3.1} also shows the effect of dropping the squared rate variable from the objective in the \ac{Q-WSRME} scheme compared to the \me{\ell_2} norm which includes it.
-By dropping it, the \ac{Q-WSRME} scheme minimizes the number of queued packets in a prioritized manner based on the respective queues.
-On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.
+\end{comment}

### 2015-02-26 Report/simulation_intro.tex
included antti comments

@@
 		\label{fig-2}}
-	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm in objective}}
+	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm for \ac{JSFRA} schemes}}
 	\label{fig-a}

### 2015-02-26 Report/sub_channel_wsrm.tex
included antti comments

@@
 In addition, the iterations required for the algorithm convergence increases with the problem size.
-To overcome the complexity, we can decouple the problem to sub-channel specific subproblems by using distributed approaches presented in \cite{palomar2006tutorial,boyd2011distributed} to design the precoders using primal or dual decomposition.
+To overcome the complexity, we can decouple the problem to sub-channel specific subproblems by using decomposition approaches presented in \cite{palomar2006tutorial,boyd2011distributed} to design the precoders using primal or dual decomposition.
 
@@
 Even though \me{N} sub-channels are present at any given scheduling instant, precoders are solved for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the backlogged packets.
-Let \me{Q_{k,i}} number of backlogged packets associated with user \me{k} before solving for precoders specific to the sub-channel \me{i}.
-Since the precoder design is sequential, for the initial sub-channel, the number of backlogged packets is given by \me{Q_{k,1} = Q_k} and for the consecutive sub-channels, it is given by
+Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} before solving for the precoders specific to the sub-channel \me{i}.
+Since the precoder design is sequential, \textit{i.e}, the precoders are designed for sub-channels \me{[0,i-1]} before \me{\ith{i}} sub-channel, the number of backlogged packets for the initial sub-channel is initialized as \me{Q_{k,1} = Q_k}.
+The queues associated with the consecutive sub-channels are given by
 \begin{equation}	\label{eqn-weight}

### 2015-02-26 Report/wsrm_formulation.tex
included antti comments

@@
 The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system.
-Since the \ac{SINR} expression in \eqref{eq:SINR} cannot be handled directly to formulate the problem, we relax the equality constraint in \eqref{eq:SINR} by the inequality constraints to solve for the transmit and the receive precoders as
+Since the \ac{SINR} expression in \eqref{eq:SINR} cannot be handled directly to formulate the problem, we relax the equality constraint of \eqref{eq:SINR} using two inequality constraints by introducing additional variables to solve \eqref{eqn-3} as
 \iftoggle{single_column}{
@@
 
-Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-3} with respect to \me{\mbf{w}_{l,k,n}} as
+Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
 \begin{IEEEeqnarray}{CCl}\label{eqn-9--1}

### 2015-02-27 Report/convergence_centralized.tex
modified in linux

@@
 \end{equation*}
-Note that the feasible set follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} iteration.
+The feasible set follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} iteration.
 Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.
@@
 
-Now, to claim the convergence of transmit precoders and receive beamformers, we need to show the uniqueness in the mapping between the transmit and receive beamformers to the objective function.
-The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, can be attributed to the linear relaxation performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}.
+To prove the convergence of the transmit and the receive beamformers, we use the uniqueness in the mapping between the transmit and receive beamformers with respect to the objective function.
+The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, is achieved due to the linear relaxation performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}.
 The linearized \eqref{eqn-8} can be written as
@@
 \end{multline}
-where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and the \ac{MSE} expression as
+where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for \ac{MSE} expression as
 \begin{multline} \label{uniqueness-2}

### 2015-02-27 Report/ieee_journal.tex
modified in linux

@@
 	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
-Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{
-	The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
+Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
 

### 2015-03-02 Report/convergence_centralized.tex
updated

--- 2015-02-26 Report/convergence_centralized.tex
@@
 When the objective function is zero, the uniqueness of the transmit precoders using \eqref{uniqueness-1} and \eqref{uniqueness-2} are not valid due to the inactive constraints \eqref{eqn-6.2} and \eqref{eqn-mse-1.2}.
-To obtain a unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the total transmit power expression without affecting the optimal solution as
-\begin{equation*}
-\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
-\end{equation*}
-for some arbitrarily small value of the scaling factor \me{\varphi \approx 0}.
+To obtain a unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can follow the regularization approach discussed in Appendix \ref{a-3} without affecting the optimal solution.
+%we can regularize the objective with the total transmit power expression without affecting the optimal solution as 
+%\begin{equation*}
+%\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
+%\end{equation*}
+%for some arbitrarily small value of the scaling factor \me{\varphi \approx 0}.
 
@@
 \begin{comment}
-
 To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, following conditions are necessary to prove the sequence convergence using Bolzano-Weierstrass theorem \cite{rudin1964principles}.

### 2015-03-02 Report/introduction.tex
updated

@@
 The topics on \ac{MIMO} \ac{IBC} precoder design have been studied extensively with different performance criteria in the literature.
-Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, the \ac{SCA} method has become a powerful tool to deal with these problems \cite{bertsekas1999nonlinear}.
+Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, the \ac{SCA} approach has become a powerful tool to deal with these problems.
 For example, in \cite{sin_algorithm}, the nonconvex part of the objective has been linearized around an operating point in order to solve the \ac{WSRM} problem in an iterative manner.
@@
 Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods.
-Finally, we propose a iterative practical algorithm to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation solution.
-\review{It is worth noting that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.
+Finally, an iterative practical algorithm is proposed to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation.
+\review{Note that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.
 

### 2015-03-02 Report/wsrm_formulation.tex
updated

@@
-We now present an iterative algorithm to solve problem \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
+We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
 The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system.
-Since the \ac{SINR} expression in \eqref{eq:SINR} cannot be handled directly to formulate the problem, we relax the equality constraint of \eqref{eq:SINR} using two inequality constraints by introducing additional variables to solve \eqref{eqn-3} as
+The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint of \eqref{eq:SINR}.
+Using additional variables, we relax the expression \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as
 \iftoggle{single_column}{

### 2015-03-02 Report/ieee_journal.tex
Merge remote-tracking branch 'origin/revision_tsp_1' into revision_tsp_1
Conflicts:
	Report/ieee_journal.dvi
	Report/ieee_journal.log
	Report/ieee_journal.pdf
	Report/ieee_journal.synctex.gz
	Report/ieee_journal.tex

@@
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
-Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Member,~IEEE}, Le-Nam Tran \IEEEmembership{Member,~IEEE}, and Markku Juntti \IEEEmembership{Senior Member,~IEEE}}\thanks{The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi).}}
+	\IEEEauthorblockN{Ganesh Venkatraman$^\dagger$ \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
+Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli$^\dagger$ \IEEEmembership{Senior Member,~IEEE}, Le-Nam Tran$^\ddagger$ \IEEEmembership{Member,~IEEE}, and Markku Juntti$^\dagger$ \IEEEmembership{Senior Member,~IEEE}}\thanks{
+	$^\dagger$The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{$^\ddagger$The author is with the Department of Electronic Engineering, Maynooth University, Maynooth, Co.
+Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie}}
 
@@
 
-\subsection{Average Backlogged Packets Over Slots} \label{time-correlated}
+\subsection{Queue Deviations over Multiple Transmission Slots} \label{time-correlated}
 \review{\input{time_correlated}}

### 2015-03-02 Report/review_comments.tex
included antti comments
Merge remote-tracking branch 'origin/revision_tsp_1' into revision_tsp_1
Conflicts:
	Report/ieee_journal.dvi
	Report/ieee_journal.log
	Report/ieee_journal.pdf
	Report/ieee_journal.synctex.gz
	Report/ieee_journal.tex

@@
-\subsection{Reveiwer Comments - \me{1}}
+\section*{Reveiwer Comments - \me{1}}
 
@@
 
-\resp We thank the reviewer for reading the paper and providing the comments. The response for the reviewer questions are made in line.
+\begin{itemize}
 
-\subsection*{Detailed Comments}  
 \cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6).
@@
 
-\subsection*{Reveiewer comments - \me{2}}
+\end{itemize}
+
+\section*{Reveiewer comments - \me{2}}
+
+\begin{itemize}
 
@@
 
-\subsection*{Reveiewer comments - \me{3}}
+\end{itemize}
+
+\section*{Reveiewer comments - \me{3}}
+
+\begin{itemize}
 
@@
 
-\subsection*{Reveiewer comments - \me{4}}
+\end{itemize}
+
+\section*{Reveiewer comments - \me{4}}
+
+\begin{itemize}
 
@@
 
-\resp We thank the reviewer for We have updated the proof for convergence in a separate section on Appendix \ref{sec-3.5}.
+\resp We understand the reviewer concern on the lack of rigorous convergence proof for the proposed JSFRA approach.
+We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on page 14.
+We have included the reference suggested by the reviewer in [34].
 
@@
 
-\resp We thank the reviewer for pointing out the missing information. We have included a figure on the number of backlogged packets over a period of time in Section \ref{time-correlated}.
+\resp We understand the concern raised by the reviewer.
+In the current paper, we are discussing on the precoder design to minimize the number of backlogged packets in the system at a given time.
+Since the greedy approach performed at each instant minimizes the number of backlogged packets on an average, we emphasized on the precoder design based on the current knowledge of the channel state information.
+We have included Section V-C in page 13 to discuss on the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots.
+Plots comparing the average number of backlogged packets for different schemes at each instant and the number of queued packets remained in the system after each transmission instant are provided in Fig.
+4.
 
@@
 
-\resp We agree with the reviewer. We have updated the manuscript with more details.
+\resp We agree with the reviewer comment.
+We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Section IV-C page 8.
+We have included the information on what each network entity knows in page 7, col.
+2 last paragraph.
+We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
 
@@
 
-\resp We thank the reviewer for pointing out the misinterpretation of the text. We have included the statement accordingly in the introduction.
+\resp We agree with the reviewer point. We have included the note on the space-frequency terminology in the introduction section on page 2, col. 2, line 2-4.
 
-\cmnt{5a} - p. 1, col. 1, row 42: "userss"
+\cmnt{5} Please see the itemized questions
 
-\resp Modified.
+\begin{itemize}
 
-\cmnt{5b} - p.
+\cmnts{a} - p. 1, col. 1, row 42: "userss"
+
+\resp Corrected in the revised manuscript in Section I on page 1, col. 1, line 2.
+
+\cmnts{b} - p.
 1, col.
@@
 
-\resp We thank the reviewer for the insightful comment on the proposed approach. We have modified the text accordingly.
+\resp We thank the reviewer for highlighting the important point. We have included the statement in the revised manuscript on Section I, page 1, col. 2, line 5-14.
 
-\cmnt{5c} - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?
+\cmnts{c} - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?
 
-\resp We understand the reviewer's concern. We have provided the valid reference for the SCA scheme.
+\resp We apologize for the wrong reference. We have updated the manuscript to include the proper reference on SCA with [2,3,7,35].
 
-\cmnt{5d} - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead
+\cmnts{d} - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead
 
-\resp Changed.
+\resp We have updated the revised manuscript with the reviewer suggestions on page 2, col. 2, second paragraph in Section II.
 
-\cmnt{5e} - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here
+\cmnts{e} - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here
 
-\resp We thank the reviewer for the concern on the grouped variable. We have modified the expressions accordingly.
+\resp We removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid confusion as suggested by the reviewer.
 
-\cmnt{5f} - p.
+\cmnts{f} - p.
 3, col.
@@
 
-\resp We thank the reviewer for the comment. We have removed the word "combinatorial" from the text.
+\resp We thank the reviewer for pointing out the confusion. We have removed the word "combinatorial" from the text to avoid confusion in page 3, col. 2, initial sentence in Section III.
 
-\cmnt{5g} - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.
+\cmnts{g} - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.
 
-\resp It is restructured to include additional details.
+\resp We have rephrased the sentence to avoid difficulty in the understanding. The manuscript is updated with the revised text on page 4, col. 2, first paragraph in Section III.B.
 
-\cmnt{5h} - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).
+\cmnts{h} - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).
 
-\resp Agreed.
+\resp We have updated the manuscript with the explicit power constraint (16d).
 
-\cmnt{5i} - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).
+\cmnts{i} - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).
 
-\resp We have updated the NP hardness discussion in the revised version.
+\resp We have included the sentence on the NP-hardness
 
-\cmnt{5j} - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.
+\cmnts{j} - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.
 
@@
 
-\cmnt{5k} - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??
+\cmnts{k} - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??
 
@@
 
-\cmnt{5l} - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).
+\cmnts{l} - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).
 
@@
 
-\cmnt{5m} - p.
+\cmnts{m} - p.
 6, col.
@@
 
-\cmnt{5n} - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?
+\cmnts{n} - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?
 
@@
 
-\cmnt{5o} - p.
+\cmnts{o} - p.
 7, col.
@@
 
-\cmnt{5p} - Table 1: "backpreassure"
+\cmnts{p} - Table 1: "backpreassure"
 
@@
 
-\cmnt{5q} - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.
+\cmnts{q} - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.
 
 \resp Changed in the revised manuscript
+
+\end{itemize}
+
+\end{itemize}

### 2015-03-03 Response/response-1.tex
final_version_for Antti, Nam, and Markku

In this paper, the authors proposed a traffic aware resource allocation scheme for multi-cell MIMO-OFDM systems, where the precoders at all BSs are chosen to minimize the total user queue deviations. The problem is nonconvex and the authors proposed two centralized algorithms based on the successive approximation (SCA) technique to find a stationary point. Moreover, several distributed algorithms are also proposed using primal decomposition, alternating directions method of multipliers (ADMM), and decomposition via KKT conditions, respectively.

Most sections of this paper are well written. The results and algorithms also seem valid. However, the motivation of minimizing the total user queue deviations is not well justified. The convergence results of some algorithms are not clearly presented. The presentation of the distributed solutions needs significant improvement. Analysis and comparison of the signaling overhead and computational complexity between the centralized and distributed algorithms are also necessary to justify the advantages of distributed algorithms.

\begin{itemize}

\cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6). For example, the Queue weighted sum rate maximization (Q-WSRM) is throughput optimal, i.e., if there exists a scheme which can make all queues stable, then the Q-WSRM can also do this. How about the proposed formulation in (6)? Is it also throughput optimal?

\resp We thank the reviewer for the valid comment. The Q-WSRM scheme and the proposed schemes are all throughput optimal. It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aims at minimizing the number of backlogged packets in addition to avoid the over allocation of the available resources. The JSFRA formulation with the \me{\ell_1} objective minimizes the number of backlogged packets in a greedy manner at each instant. By increasing the exponent \me{q \rightarrow \infty}, we obtain fair allocation at every transmission instant. We have included the discussions on the average number of backlogged packets at each instant for different arrival rates in Section V-C on page 13, col. 1. We have provided justifications for the problem formulation in (6) and (16) in page 5, col. 1, first paragraph.

\cmnt{2} Do the proposed solutions based on (6) achieve better average delay performance than the existing solutions? By the way, in the simulations, you should also add a figure comparing the average delay performance, instead of just comparing the performance metric defined by (6). This will better justify the advantage of the proposed solutions.

\resp The delay is proportional to the average number of backlogged packets in the queues. Moreover, delay depends on the service type. For example, if we consider a VOIP transmission, the delay requirement is stringent and can be achieved by increasing the priority factor \me{a_k} in (6a) using the current formulation. We can also address the fairness among the users by controlling the norm exponent \me{q} used in the objective function (6a). Since the current work is about the design of precoders to minimize the number of backlogged packets at each instant, we considered the residual number of backlogged packets as a performance measure.

\cmnt{3} In Section III.B, the convergence conditions under Algorithm 1 are not clear. First, you should be more specific about what is the SCA subproblem. Do you mean problem (19)? Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?

\resp We understand the reviewer's point. We have updated the revised manuscript to discuss the convergence of the centralized algorithm in detail in Appendix B on page 14, col. 1. The discussions are provided for the convergence of the iterative algorithm. The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-C on page 15, col. 2.

\cmnt{4} It is better to clearly summarize the convergence conditions and results (i.e., does it converge to a stationary point or the optimal solution) for all algorithms in a theorem/proposition.

\resp The discussions on the convergence of the centralized algorithms are provided in Appendix B on page 14, col. 1 and for the distributed algorithms in Section IV-C on page 8, col. 2.

\cmnt{5} At the end of Section III, you mentioned that the proposed reduced complexity resource allocation scheme is sensitive to the order in which the subchannels are selected for the optimization problem. Please provide a discussion how to choose this order.

\resp We understand the reviewer's concern. Since the algorithm designs the precoders for each sub-channel at a time by using the total number of unserviced packets. For designing the precoders for the sub-channel \me{j+1}, we assume the transmit precoders and the rates of all users are obtained for the sub-channels \me{\{1,2,\dotsc,j\}}. Now, the number of backlogged packets for the \me{\ith{j+1}} sub-channel is given by 
\[Q_k - \sum_{i=1}^j \sum_{l=1}^L t_{l,k,i}\].
Since it depends on the rates of the already completed sub-channels \me{\{1,2,\dotsc,j\}}, it is susceptible to the ordering used to determine the precoders in each sub-channels. It is discussed in detail in Section III-D on page 7, col. 1.

\cmnt{6} In the distributed algorithms, it is not clear what exact information is exchanged between the BSs or between the BSs and users. Moreover, the signaling overhead should be analyzed and compared with the centralized solution. The proposed distributed algorithms require exchanging over-the-air signaling or backhaul signaling for many times within each channel coherent time (e.g., from Fig. 2, the distributed algorithm requires 20-30 iterations to converge even when there are only 3 subchannels). I don’t think this is acceptable in practice. Is the signaling overhead of the distributed algorithm really smaller than the centralized algorithm which only requires exchange the CSI between the BSs for once within each channel coherent time?

\resp Please note that the proposed distributed algorithm based on the primal or dual decomposition are discussed to approach to distribute the precoder design. Note that the distributed approaches are performed for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution. In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which may not be the same stationary point as when the algorithm is allowed to converge. In practice, we can combine the ADMM update, receiver update and the SCA update all at once to minimize the overhead in the backhaul signaling. We have provided a practical scheme in Section IV-D on page 9, col. 1. In a time-correlated channels, we can update the precoders once per coherence time when the number of backlogged packets are significantly large.

\cmnt{7} The convergence analysis of the distributed algorithms is not clear. For example, what is the exact condition to ensure the convergence of the distributed algorithms. Does the distributed algorithms also converge to a stationary point?

\resp We have updated the manuscript to include the discussions on the convergence of the distributed algorithm on page 8, col. 2 last paragraph in Section IV-C.

\cmnt{8} I’m totally confused with the ADMM approach in Section IV.A. Many notations, such as the local interference vector and consensus interference vector are used without formal definition. What is the difference between the local interference vector and consensus interference vector? What are their relationships with the actual interference vector. It seems that you are using the same notation for all of these interference vectors and I can’t tell when a notation refers to a local interference vector, a consensus interference vector, or the actual interference vector. These questions should be clarified and perhaps you should choose the notation system more carefully. For example, in (36), there are 3 similar notations and I don’t know which one is local interference vector and which one is the actual interference vector.

\resp We understand the reviewer's concern. We have shortened the section on ADMM by citing the relevant earlier work on the distributed implementation of the centralized algorithm for the min power problem [29]. We have rewritten the distributed algorithms in Section IV-A and Section IV-B. The variables are discussed in Section IV on page 8, col. 1. It follows the existing literature on the ADMM scheme, which treats the interference as a variable at each BS and the consensus on the interference is achieved upon convergence of the distributed algorithm as discussed in [11].

\cmnt{9} In the distributed algorithms, it is not clear what information is available at each node. For example, what are your assumption on CSIT (CSI knowledge at each BS) and CSIR (CSI knowledge at each user)? How to 2 obtain the information used to perform the required calculation at each node (such as calculating the actual interference, MMSE receiver and the dual variables)?

\resp We understand the reviewer's concern. For the distributed precoder design, we assume that the \ac{BS} \me{b} knows the channel \me{\mbf{H}_{b,k,n}} of all users in the system by the uplink sounding technique. Note that it includes the cross channel of the neighbor BS users as well. In addition, we assume the receivers are informed by the users by using precoded uplink pilots. We have included the information on what each network entity knows in page 7, col. 2 last paragraph. We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.

\cmnt{10} Do you have any convergence result for the proposed distributed solution based on the KKT conditions in Section IV.B? It seems that the iterative method to solve the KKT conditions is totally heuristic.

\resp We agree with the reviewer. Note that, if the dual variables are allowed to iterate until convergence, the proposed KKT based scheme achieves the same stationary point for each fixed receive beamformer (similar to the distributed algorithms). It is heuristic, since we update the transmit precoders, receive beamformers and the dual variables all at once in each iteration. Please note that the proposed algorithm is of practical significance, since it has few number of iterations before the actual transmission of data with the latest precoder update. It may not be a stationary point of the original nonconvex problem but it is guaranteed to provide better performance in the sum rate compared to the distributed approaches presented in Section IV-A and Section IV-B for the same number of iterations. We have provided additional details on the convergence of the KKT based approach in page 10, col 1, last paragraph.

\cmnt{11} Since queue is a dynamic system evolving according to (3), it doesn’t make sense to compare the queue deviations at a given time. You should compare average queue deviations in the simulations. Moreover, you should also compare the average delay performance instead of just comparing the performance metric (queue deviations) defined in this paper. Using the queue deviations as the performance metric also needs more justification.

\resp We thank the reviewer for raising the critical comment. Since the manuscript is about the precoder design to minimize the total number of backlogged packets in the system, we have provided the convergence behavior of the proposed precoder design formulations. The average queue deviation can be minimized by minimizing the deviations at each instant, we have provided the convergence plot for the single slot. In accordance with the reviewer comment, we have included the Section V-C on page 13, col. 1 to discuss the queue deviation over multiple transmission slots. We have presented Fig. 4a by comparing the average number of backlogged packets for different algorithms with various arrival bits and Fig. 4b for the number of backlogged packets at each instant. Please note that the delay is directly proportional to the number of backlogged packets if the arrivals are fixed, we are not addressing this explicitly. Even though, \me{\ell_2} and \me{\ell_{\infty}} norm addresses the delay and the fairness implicitly, we can prioritize the users with the weights \me{a_k} in (6a) for better service rate. We are currently working on the system level study of the proposed formulations.

\cmnt{12} What is “SRA” in the simulation figures?

\resp The \acf{SRA} is updated in the revised manuscript on page 7, col. 1, Section III-D.

\cmnt{13} In the discussion for Fig. 1, you mentioned that JSFRA converge to the optimal point, and all algorithms are Pareto-optimal. Since the problem is non-convex, why these algorithm can find optimal solution or Paretooptimal point?

\resp We thank the reviewer for pointing out the mistake in the text. Since the problem is nonconvex, the JSFRA formulation can find a local optimal point upon convergence. The converged point of the JSFRA problem is in fact the stationary point of the original nonconvex problem, which is discussed in Appendix B-D on page 15, col. 2. We have removed the statement mentioning the pareto-optimal solutions in the discussions on Fig. 1 in the revised manuscript.

\end{itemize}

### 2015-03-03 Response/response-2.tex
final_version_for Antti, Nam, and Markku

\begin{itemize}

\cmnt{1} The logic from (6) to (16) is not clear. The only difference is the two newly introduced NON-CONVEX constraints (16b) and (16c), while the objective function (16a) and the constraint (16d) is the same as (6). The equivalence between (6) and (16) is not straightforward and it is confusing why the reformulation in (16) is beneficial.

\resp We understand the reviewer's concern. The reformulation is required, since the SINR expression in (2) cannot be handled directly in the problem defined in (6). Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), which are the under estimator to the original problem in (6). We have updated the manuscript to include the details for better clarity on page 5, col. 1, first paragraph.

\cmnt{2} The authors use the successive convex approximation framework, but the approximate problem proposed by the authors is actually not convex. Inspecting (19), its objective function is the same as in (6), and the non-convexity of (6) comes exactly from the objective function, so (19) is not a convex problem. The same flaw is repeated several times in the approximate problems proposed by the authors.

\resp Please note that the objective function is convex, which can be verified by writing the difference function inside the norm operator in epigraph form. Since the problem in (16) is jointly nonconvex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable. Even after fixing \me{\mvec{w}{l,k,n}} as constant, the problem in (16) is nonconvex due to the DC constraint (16b), which is handled by the first order relaxation around some fixed operating point. Once the linear relaxation is performed, the problem in (20) is a convex optimization problem with the variables being \me{\mvec{m}{l,k,n},\gamma_{l,k,n},\beta_{l,k,n}}. We have updated the manuscript to illustrate this clearly on page 5, col. 2, first paragraph.

\cmnt{3} The authors proposed to use block coordinate descent method to solve (16). But as the authors have already pointed out, to apply block coordinate descent method, the constraint sets for different variables should be disjoint (uncoupled), which is however not the case in (16), because receive and transmit precoders (i.e w and m) are coupled in the constraints. It is confusing on its own why the authors made a statement that contradicts the proposed methodology, and the convergence followed is in question.

\resp We thank the reviewer for the pointing out the flaw in the text. We have removed the statement on block coordinate descent method with the AO approach. Since the problem is nonconvex, using this approach, we can find a local optima of the original nonconvex problem. The manuscript is modified to include the updated statement on page 5, col. 1, second paragraph.

\cmnt{4} Regarding the convergence of the SCA, the authors cited [27] for the convergence conditions, but the reference is wrong, because the conditions after the three bullets on page 6 are not mentioned in [27]. In case the authors disagree, please make the citation more specific, for example, specify the theorem/statement/proposition in [27] where those conditions are specified.

\resp We understand the reviewer's concern. We have provided the proof on the convergence of the centralized algorithm on Appendix B. We apologize for the inappropriate reference cited in the original manuscript.

\cmnt{5} The authors also cited [28] to establish the convergence of SCA. But the techniques of [27] and [28] are different, and the convergence conditions are different too. It is not clear why the authors need two set of convergence conditions for a single problem, and the resulting convergence analysis itself is not solid enough.

\resp We agree with the reviewer's comment. We have provided the updated proof for the convergence of the centralized algorithm on Appendix B in the revised manuscript.

\cmnt{6} Another comment on reference: to the reviewer's knowledge, the term SCA is never explicitly used in [2]. So please either correct the reference or be more specific (section, theorem, etc.).

\resp We have removed the inappropriate citation of the references.

\cmnt{7} The authors propose primal decomposition method, ADMM approach to the non-convex problem (19), while their convergence analysis is based on literature that proved convergence for convex problems only, e.g., [13]. So the convergence analysis is not trustworthy.

\resp We understand the issue raised by the reviewer. Please note that the distributed algorithm is performed for the convex subproblem presented in (20) and (28). Since the problem is convex, the distributed approach convergence can be guaranteed by satisfying certain conditions. These are discussed in Section IV-C on page 8, col. 2, last paragraph.

\cmnt{8} The length of the paper is too extensive. Some of the reformulations as mentioned in the previous comment can be skipped. Also, Section III.D. is not deeply explained and does not bring additional value to the paper. The implications of ordering the sub-channels for the iterative approach should be carefully studied and extensively explained in a different publication.

\resp We understand the reviewer's concern. We have included the sub-channel wise resource allocation or (SRA) scheme in Section III-D for the completeness. It is presented in the manuscript as an alternative suboptimal approach to perform sub-channel wise distributed precoder design by the centralized controller. We have updated the manuscript with more details for better understanding.

\cmnt{9} Information regarding the value of q used to obtain the simulation results is missing (with exception of Fig. 3).

\resp We have included the information regarding the norm used for the simulation in the figure captions. It is updated for Fig. 1 and Fig. 2.

\cmnt{10} In Fig. 1 and Fig. 2, the labels for the system model do not fit with the written description. Additionally, the reference scheme Q-WSRM is not optimal, since it over allocates resources if there are few queued packets. Therefore, it is not interesting for comparison purposes.

\resp We understand the reviewer's concern. We have updated the manuscript to include the descriptions in the text to refer the legends used in the figures. Table 1 is provided for the purpose of insight, since it deals with the SISO scenario with 3 sub-channels and 3 users.

\cmnt{11} Assuming that Fig. 2 and Fig. 3 where obtained based on the same simulation setup, i.e. user queues, number of transmit and receive antennas and number of base stations, it is not clear why results in Fig. 3 are worse than Fig. 2 when comparing JSFRA. Even more, since the number of sub-channels is larger in Fig. 3, the result seems contradictory.

\resp We thank the reviewer for pointing out the issue in the system description for the figures. Please note that the simulation scenario is different for Fig. 2 and Fig. 3 in terms of path loss distribution and the sub-channel numbers. We have provided different scenario with the centralized algorithm as reference for studying the performance under different system model. The user path loss is distributed uniformly between $[0,-6]$ dB for Fig. 2 and between $[0,-3]$ dB for Fig. 3. We have updated the manuscript to include these details. In addition, the number of backlogged packets in the system for Fig. 3 is \me{[9,16,14,16,9,13,11,12]} bits. These informations are updated in the revised manuscript on page 12, col. 1, lines 3-6 in Section V-B and page 12, col. 2, third paragraph in Section V-B.

\end{itemize}

### 2015-03-03 Response/response-3.tex
final_version_for Antti, Nam, and Markku

\begin{itemize}

\cmnt{1} This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods. This is an interesting and important topic.

\resp We thank the reviewer for reading the manuscript and providing valuable comments.

\cmnt{2} The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.

\resp Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression and thus \me{t_k} is not a variable. However, in the MSE formulation, we have explicitly stated the optimization variable \me{t_k}, since it is present in the DC constraint (27).

\cmnt{3} The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5). This is not obvious. An easy case to check this statement is that assuming the system has two BS and each BS serves one user. When \me{Q_1=0} and 2nd BS has sufficiently large power, (16b) and (16c) do not hold equality. Rigorous proof is needed if authors stick to this statement.

\resp We thank the reviewer for the insightful comment. We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under estimator for the SINR expression in (2). The under estimator is tight when there is at least one user in each BS that cannot be served by the current transmission. It has multiple solutions, when the objective is zero even for a single BS. In this case, we can use a regularization term with the total power in the objective to obtain an unique solution. We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-C.

\cmnt{4} The solution in (21) is obtianed for MMSE, i.e. for 2-norm(q=2). If \me{q=1} or \me{q=\infty}, it is actually an equivalent linear programming problem. Details for this solution should be provided.

\resp We thank the reviewer for the critical comment. Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function. The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which in deed depend on the \me{q} value. We have modified the text to included this information in page 5, col. 2, last paragraph.

\cmnt{5} The convergence proof need to be rigorous. The inequality of (23a) is opposite to the reference [28]. Also the statement on uniqueness of the transmit and the receive beamformers are not correct. Although we can choose one antenna to be real value, this does not mean the problem has unique solution!

\resp We agree with the reviewer. We have updated the manuscript to discuss the convergence proof in a rigorous manner in Appendix B. The uniqueness is also justified implicitly by the linear approximation performed on the DC constraint (16b), which makes the transmit precoders to be susceptible to the phase rotation. The uniqueness discussions are presented in Appendix B-C.

\cmnt{6} (25) is generally wrong. (25) only holds when the MSE is minimized(by MMSE receiver) and the snr is the optimized(which is obtained by general eignvalue decompostion). This is clearly stated in the reference [5] and [6]. This can also be easily checked by comparing (25) and (2). Consequently the alternative formulation (26) based on this conclusion is questionable.

\resp We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on MMSE objective. In our MSE reformulation solution, we have used the MMSE receiver irrespective of the \me{\ell_q} norm used in the objective. Since the receivers are based on the MMSE objective, the equivalence is valid between the MSE and the SINR expression. Since the transmit precoders are updated in accordance with the objective, the MSE reformulation yields the same solution as the SCA approach based JSFRA scheme presented in Section III-B. It can also be verified from Fig. 1 for \me{\ell_1} objective. We have updated the manuscript to include this comments on page 6, col. 2, line 10-13.

\cmnt{7} For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed. 1. The numbers of transmitted packets for users  \me{t_k}'s are optimization variables. So they should be explicitly stated in the problem formulation (6), (16), (20) and (26) to avoid confusing.

\resp We agree with the reviewer's concern. We have included the reference [11] that discusses on the valid choices of the step size parameter for ADMM. We have included the statement that it depends on the system model under consideration. It is updated in the manuscript on page 8, col. 2, line 4-8.

\end{itemize}

### 2015-03-03 Response/response-4.tex
final_version_for Antti, Nam, and Markku

\begin{itemize}

\cmnt{1} First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method. "The SCA method" is often referred to, but never really defined or referenced. The three required conditions (as stated on p. 6, col. 1, rows 38-40) do not, as far as I can tell, appear in [27]. Indeed, [27] is concerned with optimization problems where the objective function is non-convex, but the constraint set is convex and separable over the blocks of variables. Perhaps you meant to cite [A], wherein non-convex constraints are handled in a similar way? Numerically, the algorithms do converge, and the argument put forward makes sense, but the treatment must be improved to be more rigorous.

\resp We understand the reviewer's concern on the lack of rigorous convergence proof for the proposed JSFRA approach. We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on page 14. We have included the reference suggested by the reviewer in [34].

\cmnt{2} Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates. This is due to how the conditional Lyapunov drift is minimized. This approach completely removes the queue dynamics from the optimization problem, essentially leading to greedy one-shot optimization in 7
every time instant. The framework would be more interesting if some sort of optimization (or tracking) is performed over several time instants, rather than the one-shot approach that is currently used for the JSFRA algorithms. Possibly, some expectation over the queues would be optimized then. Even if no analytical treatment of the tracking over several time-steps is added, I would at least highly recommend adding some simulation results where the proposed one-shot algorithms are performed sequentially over several time instants.

\resp We understand the concern raised by the reviewer. In the current paper, we are discussing on the precoder design to minimize the number of backlogged packets in the system at a given time. Since the greedy approach performed at each instant minimizes the number of backlogged packets on an average, we emphasized on the precoder design based on the current knowledge of the channel state information. We have included Section V-C in page 13 to discuss on the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots. Plots comparing the average number of backlogged packets for different schemes at each instant and the number of queued packets remained in the system after each transmission instant are provided in Fig. 4.

\cmnt{3} Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results. This reviewer recommends spending more space on the convergence, than on the description of the distributed techniques. Still, it would be nice with a direct description of what local CSI is required, and how it is acquired, to perform the local computations for the primal decomposition and ADMM methods. For the description of the signaling of the CSI in Sec. IV-B, are you envisioning a TDD system?

\resp We agree with the reviewer's comment. We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Section IV-C page 8. For the distributed precoder design, we assume that the \ac{BS} \me{b} knows the channel \me{\mbf{H}_{b,k,n}} of all users in the system by the uplink sounding technique. Note that it includes the cross channel of the neighbor BS users as well. We have included the information on what each network entity knows in page 7, col. 2 last paragraph. We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.

\cmnt{4} Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier. This could easily be clarified.

\resp We agree with the reviewer's point. We have included the note on the space-frequency terminology in the introduction section on page 2, col. 2, line 2-4.

\cmnt{5} Please see the itemized questions

\begin{itemize}

\cmnts{a} - p. 1, col. 1, row 42: "userss"

\resp Corrected in the revised manuscript in Section I on page 1, col. 1, line 2.

\cmnts{b} - p. 1, col. 2, row 18: the precoders are used \_implicitly\_ as decision variables. This is the whole point, to avoid explicitly modeling the hard decisions in the optimization, and instead do soft decisions during the iterations, and then finally hard decisions after convergence.

\resp We thank the reviewer for highlighting the important point. We have included the statement in the revised manuscript on Section I, page 1, col. 2, line 5-14.

\cmnts{c} - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?

\resp We apologize for the wrong reference. We have updated the manuscript to include the proper reference on SCA with [2,3,7,25,26,35].

\cmnts{d} - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead

\resp We have updated the revised manuscript with the reviewer suggestions on page 2, col. 2, second paragraph in Section II.

\cmnts{e} - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here

\resp We removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid confusion as suggested by the reviewer.

\cmnts{f} - p. 3, col. 2, row 26: Which general MIMO-OFDM problem are you talking about here, and what is combinatorial about it? Is it the problem of selecting users to be served on orthogonal subcarriers? There is nothing inherently combinatorial over the problem in (6) as far as I can tell, as the beamformers are used as soft decision variables.

\resp We thank the reviewer for pointing out the confusion. We have removed the word "combinatorial" from the text to avoid confusion in page 3, col. 2, initial sentence in Section III.

\cmnts{g} - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.

\resp We have rephrased the sentence to avoid difficulty in the understanding. The manuscript is updated with the revised text on page 4, col. 2, first paragraph in Section III.B.

\cmnts{h} - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).

\resp We have updated the manuscript with the explicit power constraint in (16d) as
\[\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b\]
in page 5, col. 1.

\cmnts{i} - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).

\resp We have included the NP-hardness of the proposed solution by modeling the current problem to solve the \ac{WSRM} formulation, which is known to be NP-hard in page 5, col. 1, last sentence in Section III-B third paragraph.

\cmnts{j} - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.

\resp We have removed the sentence mentioning SCA method. We have updated the manuscript to discuss this as SCA approach in pagt 5, col. 1 last paragraph.

\cmnts{k} - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??

\resp We thank the reviewer for pointing out the mistake. We have included all the constraints except the linearization constraint in (20) which is (19) in the original manuscript. Expression (19d) and (18) are same. We have removed this double reference in page 5, col. 2, equation (20).

\cmnts{l} - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).

\resp We have updated the manuscript to avoid the ambiguity in the representation of the optimal and the MMSE receiver. The optimal receiver is denoted by \me{\mvec{w}{l,k,n}^{\ast}} in (22) and the MMSE receiver by \me{\mvec{w}{l,k,n}} in (23).

\cmnts{m} - p. 6, col. 1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs. However, does it affect the convergence of the algorithm?

\resp We thank the reviewer for providing the valid comment. We have updated the manuscript to include this discussion in page 6, col 1, lines 3-6. The performance remains the same and the convergence rate is not affected by this scaling, which can be seen from Fig. 1 comparing the precoder convergence using the optimal and the MMSE receiver for the JSFRA scheme with \me{\ell_1} norm.

\cmnts{n} - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?

\resp To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point. Since the operating point happens to be the optimal solution from the earlier iteration, the optimal point of the previous iterations is also present in the current feasible set. Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective. It is explained in detail in Appendix B on the convergence analysis of the centralized algorithm.

\cmnts{o} - p. 7, col. 1, row 35: Just because a problem is convex does not mean that it has a unique solution. (Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?

\resp We thank the reviewer for the critical comment. It is generally not true that the convex problem has a unique solution. The problem is strictly convex when there is at least one user in each BS that cannot be served by the current transmission. It has multiple solutions, when the objective is zero even for a single BS. In this case, we can use a regularization term with the total power in the objective to obtain an unique solution. We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-C.

\cmnts{p} - Table 1: "backpreassure"

\resp It is updated in the manuscript on page 11, Table 1.

\cmnts{q} - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.

\resp We agree with the reviewer. We have modified the manuscript accordingly by replacing it with the singular form.

\end{itemize}

\end{itemize}

### 2015-03-03 Response/reviewer_response.tex
final_version_for Antti, Nam, and Markku

\documentclass[10pt,letterpaper,onecolumn]{IEEEtran}

\usepackage[left=1in,right=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}

\newcommand{\cmnt}[1]{\item[\textbf{Q}-(#1)]}
\newcommand{\cmnts}[1]{\item[(#1)]}
\newcommand{\resp}{\item[\textbf{Resp} :]}

\renewcommand \thesection{\Roman{section}}
\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}

\input{./../Report/shortcuts}
\input{./../Report/acronyms}

\begin{document}

\doublespacing

\title{Response for Reviewer Comments}

\maketitle

We would like to thank the associate editor and the reviewers for the valuable comments provided for the manuscript. We have written the response for the reviewer comments in line in this report. The changes are addressed in the revised manuscript as well by using blue color italic fonts to discriminate the revision from the actual text in the manuscript.

\newpage
\section*{Response for Reviewer - \me{1}}
\input{response-1}

\newpage
\section*{Response for Reviewer - \me{2}}
\input{response-2}

\newpage
\section*{Response for Reviewer - \me{3}}
\input{response-3}

\newpage
\section*{Response for Reviewer - \me{4}}
\input{response-4}

\end{document}

### 2015-03-03 Report/convergence_centralized.tex
final_version_for Antti, Nam, and Markku

@@
 When the objective function is zero, the uniqueness of the transmit precoders using \eqref{uniqueness-1} and \eqref{uniqueness-2} are not valid due to the inactive constraints \eqref{eqn-6.2} and \eqref{eqn-mse-1.2}.
-To obtain a unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can follow the regularization approach discussed in Appendix \ref{a-3} without affecting the optimal solution.
+To get the unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal solution.
 %we can regularize the objective with the total transmit power expression without affecting the optimal solution as 

### 2015-03-03 Report/dual_approach.tex
final_version_for Antti, Nam, and Markku

--- 2015-02-05 Report/dual_approach.tex
@@
 \end{equation}
-where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}.
+where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}, which depend on the system model under consideration.
+The convergence rate of the distributed algorithm is susceptible to the choice of the step size parameter \me{\rho}.
+For our simulation models, we consider the step size parameter \me{\rho=2}.
 The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.

### 2015-03-03 Report/simulation_distributed.tex
final_version_for Antti, Nam, and Markku

@@
-The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points.
-Fig.
-\ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}.
-Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}.
-The total number of queued packets assumed for both figures is \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
-As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update.
+The distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points.
+\review{Fig.
+\ref{fig-d} compares the performance of the algorithms for the configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS} with the \ac{PL} varies uniformly between \me{[0,-6]} dB}.
+Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets at each \ac{BS}.
+The number of queued packets is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
+As discussed in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update.
 Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
@@
 
-Fig.
-\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents by plotting the total number of backlogged packets at each \ac{SCA} update point.
+\review{Fig.
+\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB}.
 The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective.

### 2015-03-03 Report/simulation_intro.tex
final_version_for Antti, Nam, and Markku

@@
-The simulations carried out in this work consider the path loss varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples.
+The simulations carried out in this work consider the \ac{PL} varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples.
 The queues are generated based on the Poisson process with the average values specified in each section presented.

### 2015-03-03 Report/simulation_results.tex
final_version_for Antti, Nam, and Markku

@@
 For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
-The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component.
+The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest \ac{PL} component.
 Fig.

### 2015-03-03 Report/wsrm_formulation.tex
final_version_for Antti, Nam, and Markku

@@
-We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
+\review{We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
 The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system.
@@
 }
-\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation.
+The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation.
 Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}}.
@@
 Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-\review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed by a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as \ac{SCA} method in \cite{marks1978technical}.
+\review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed by a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as \ac{SCA} approach in \cite{marks1978technical}.
 By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}

### 2015-03-03 Response/response-4.tex
revised

@@
 \resp We thank the reviewer for the critical comment.
-It is generally not true that the convex problem has a unique solution.
-The problem is strictly convex when there is at least one user in each BS that cannot be served by the current transmission.
-It has multiple solutions, when the objective is zero even for a single BS.
+It is true that the convex problem does not need to have a unique solution in general.
+By using Minkowski Inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can show that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
+The uniqueness of the solution is achieved due to the linear constraint (19) for the problem formulation in (20).
+Note that the linear constraint (19) is susceptible to the phase rotations made on the transmit precoders, whereas in (16b), the unitary rotations on the transmit precoders are all valid in the original nonconvex constraint (16b).
+When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero, we obtain unique set of transmit precoders.
+On contrary, it has multiple solutions when the objective is zero even for a single BS.
 In this case, we can use a regularization term with the total power in the objective to obtain an unique solution.

### 2015-03-03 Report/decomposition_solutions.tex
revised

@@
 To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-Following similar approaches presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference contribution from each \ac{BS} in \me{\mathcal{B}} as
+Following similar approach presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference from each \ac{BS} in \me{\mathcal{B}} as
 \iftoggle{single_column}{
@@
 To decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method.
-Since the \ac{BS} specific precoders are solved independently, we assume local channel information and queues are available at each \ac{BS} \me{b_k} together with the cross channel knowledge \me{\mvec{H}{b_k,k,n}, \forall k\in \bar{\mc{U}}_{b_k}} through precoded uplink sounding using the receive beamformers \me{\mvec{w}{l,k,n}} \cite{komulainen2013effective}.
-Each receiver is assumed to have the channel and the transmit precoders of all \acp{BS} in \me{\mc{B}} to evaluate \ac{MMSE} receiver.
+To decouple the precoder design independently, the effective downlink channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are assumed to be known at each \ac{BS} \me{b} through uplink precoded pilot signaling from all the users in the system.
+Similarly to update the \ac{MMSE} receivers at the user \me{k}, the equivalent uplink channels \me{\mvec{m}{l,k^{\prime},n}^\herm \mvec{H}{b,k,n}^\herm, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} are assumed to be known through user specific precoded downlink pilot signaling as detailed in \cite{komulainen2013effective}.
 

### 2015-03-03 Report/wsrm_formulation.tex
revised

@@
 \end{IEEEeqnarray}
-Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mbf{w}^{\ast}_{l,k,n}} as
+Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mbf{w}^{o}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl}
@@
 where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
-\review{The optimal receiver \me{\mbf{w}^{\ast}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for fixed number of iterations.} \review{Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
+\review{The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for fixed number of iterations.} \review{Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
 The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which in deed depend on the \me{q} value.}

### 2015-03-04 Response/response-1.tex
revised

@@
-In this paper, the authors proposed a traffic aware resource allocation scheme for multi-cell MIMO-OFDM systems, where the precoders at all BSs are chosen to minimize the total user queue deviations.
+\textit{In this paper, the authors proposed a traffic aware resource allocation scheme for multi-cell MIMO-OFDM systems, where the precoders at all BSs are chosen to minimize the total user queue deviations.
 The problem is nonconvex and the authors proposed two centralized algorithms based on the successive approximation (SCA) technique to find a stationary point.
-Moreover, several distributed algorithms are also proposed using primal decomposition, alternating directions method of multipliers (ADMM), and decomposition via KKT conditions, respectively.
+Moreover, several distributed algorithms are also proposed using primal decomposition, alternating directions method of multipliers (ADMM), and decomposition via KKT conditions, respectively.}
 
-Most sections of this paper are well written.
+\textit{Most sections of this paper are well written.
 The results and algorithms also seem valid.
@@
 The presentation of the distributed solutions needs significant improvement.
-Analysis and comparison of the signaling overhead and computational complexity between the centralized and distributed algorithms are also necessary to justify the advantages of distributed algorithms.
+Analysis and comparison of the signaling overhead and computational complexity between the centralized and distributed algorithms are also necessary to justify the advantages of distributed algorithms.}
+
+We thank the reviewer for providing valuable and insightful comments. We have address all the comments in the revised manuscript.
 
@@
 
-\cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6).
+\cmnt{1} \textit{In Section II.B, please provides more justifications for the problem formulation in (6).
 For example, the Queue weighted sum rate maximization (Q-WSRM) is throughput optimal, i.e., if there exists a scheme which can make all queues stable, then the Q-WSRM can also do this.
@@
 Is it also throughput optimal?
+}
 
@@
 The Q-WSRM scheme and the proposed schemes are all throughput optimal.
-It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aims at minimizing the number of backlogged packets in addition to avoid the over allocation of the available resources.
+It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aims at minimizing the number of backlogged packets in addition to avoiding the over allocation of the available resources.
 The JSFRA formulation with the \me{\ell_1} objective minimizes the number of backlogged packets in a greedy manner at each instant.
@@
 1, first paragraph.
+The equivalence between the Q-WSRM scheme and the JSFRA problem with \me{\ell_2} can be seen easily when the number queue size increases as outlined in the revised manuscript on page 4, col.
+2, Section III-B starting paragraph.
 
-\cmnt{2} Do the proposed solutions based on (6) achieve better average delay performance than the existing solutions?
+\cmnt{2} \textit{Do the proposed solutions based on (6) achieve better average delay performance than the existing solutions?
 By the way, in the simulations, you should also add a figure comparing the average delay performance, instead of just comparing the performance metric defined by (6).
-This will better justify the advantage of the proposed solutions.
+This will better justify the advantage of the proposed solutions.}
 
-\resp The delay is proportional to the average number of backlogged packets in the queues.
-Moreover, delay depends on the service type.
-For example, if we consider a VOIP transmission, the delay requirement is stringent and can be achieved by increasing the priority factor \me{a_k} in (6a) using the current formulation.
-We can also address the fairness among the users by controlling the norm exponent \me{q} used in the objective function (6a).
-Since the current work is about the design of precoders to minimize the number of backlogged packets at each instant, we considered the residual number of backlogged packets as a performance measure.
+\resp The proposed algorithm is a function of the number of backlogged packets and the channel conditions of all users in the network.
+Since the delay is proportional to the average number of backlogged packets in system, the proposed algorithm performs equally good in comparison with the existing Q-WSRM approach.
+It can be easily verified by the equivalence between the \me{\ell_2} norm JSFRA and the Q-WSRM scheme on page 4, col.
+2, Section III-B starting paragraph.
+We have also provided the performance of different JSFRA algorithm and Q-WSRM scheme based on the average number of backlogged packets in the system over multiple transmission slots by varying the average number arrivals for all users in the system in Fig.
+4 on page 13.
+We can still control the delay behavior by controlling the priority factor \me{a_k} in (6a), which affects the resource allocation.
+For example, if we consider a VOIP transmission, the delay requirements are stringent and it can be achieved by increasing the priority factor \me{a_k} in the current formulation.
+In addition, we can also control the delay by changing the exponent used in the objective \me{\ell_q} of the JSFRA problem.
+We considered the residual number of backlogged packets as a performance measure, since we assume only the instantaneous channel state informations and together with the number of backlogged packets, resources can be allocated only for a given instant.
 
-\cmnt{3} In Section III.B, the convergence conditions under Algorithm 1 are not clear.
+\cmnt{3} \textit{In Section III.B, the convergence conditions under Algorithm 1 are not clear.
 First, you should be more specific about what is the SCA subproblem.
 Do you mean problem (19)?
-Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?
+Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?}
 
@@
 The discussions are provided for the convergence of the iterative algorithm.
+The uniqueness of the convex subproblem (20) can be guaranteed when the objective is non-zero for all coordinating BSs in the precoder design.
+It is due to the linear constraint on the transmit precoders in (19), which is susceptible to the transmit precoder phase rotations.
+On the other hand, the constraint in (16b) is not, since the precoder variable is inside the absolute value operator.
+Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16).
 The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-C on page 15, col.
@@
 
-\cmnt{4} It is better to clearly summarize the convergence conditions and results (i.e., does it converge to a stationary point or the optimal solution) for all algorithms in a theorem/proposition.
+\cmnt{4} \textit{It is better to clearly summarize the convergence conditions and results (i.e., does it converge to a stationary point or the optimal solution) for all algorithms in a theorem/proposition.}
 
@@
 
-\cmnt{5} At the end of Section III, you mentioned that the proposed reduced complexity resource allocation scheme is sensitive to the order in which the subchannels are selected for the optimization problem.
-Please provide a discussion how to choose this order.
+\cmnt{5} \textit{At the end of Section III, you mentioned that the proposed reduced complexity resource allocation scheme is sensitive to the order in which the subchannels are selected for the optimization problem.
+Please provide a discussion how to choose this order.}
 
@@
 
-\cmnt{6} In the distributed algorithms, it is not clear what exact information is exchanged between the BSs or between the BSs and users.
+\cmnt{6} \textit{In the distributed algorithms, it is not clear what exact information is exchanged between the BSs or between the BSs and users.
 Moreover, the signaling overhead should be analyzed and compared with the centralized solution.
@@
 I don’t think this is acceptable in practice.
-Is the signaling overhead of the distributed algorithm really smaller than the centralized algorithm which only requires exchange the CSI between the BSs for once within each channel coherent time?
+Is the signaling overhead of the distributed algorithm really smaller than the centralized algorithm which only requires exchange the CSI between the BSs for once within each channel coherent time?}
 
-\resp Please note that the proposed distributed algorithm based on the primal or dual decomposition are discussed to approach to distribute the precoder design.
-Note that the distributed approaches are performed for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution.
+\resp The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require large number of iterations for the convergence.
 In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which may not be the same stationary point as when the algorithm is allowed to converge.
-In practice, we can combine the ADMM update, receiver update and the SCA update all at once to minimize the overhead in the backhaul signaling.
-We have provided a practical scheme in Section IV-D on page 9, col.
+The number of ADMM or primal updates are controlled by the parameter \me{J_{\max}} in the Algorithm 2.
+In practice, we can combine the ADMM or primal update, receiver update and the SCA update all at once, \textit{i.e}, \me{J_{\max} = 1} to minimize the overhead in the backhaul signaling and to speed up the convergence.
+To this end, we have provided a practical scheme in Section IV-D on page 9, col.
 1.
-In a time-correlated channels, we can update the precoders once per coherence time when the number of backlogged packets are significantly large.
+Note that in the time-correlated case, it is often also enough to update the precoders once per radio frame.
+The decentralized schemes are never allowed to converge until the end, it is only important to follow the fading process when \me{J_{\max} = 1}.
+The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of \cite{tolli2011decentralized}, which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
 
-\cmnt{7} The convergence analysis of the distributed algorithms is not clear.
+\cmnt{7} \textit{The convergence analysis of the distributed algorithms is not clear.
 For example, what is the exact condition to ensure the convergence of the distributed algorithms.
-Does the distributed algorithms also converge to a stationary point?
+Does the distributed algorithms also converge to a stationary point?}
 
-\resp We have updated the manuscript to include the discussions on the convergence of the distributed algorithm on page 8, col. 2 last paragraph in Section IV-C.
+\resp We have updated the manuscript to include the discussions on the convergence of the distributed algorithm on page 8, col.
+2 last paragraph in Section IV-C.
+The condition for the convergence of the distributed algorithm is that when the dual variable updates are not significant or when the decrease in the objective value is below some threshold.
+The distributed algorithm reaches the same stationary point as of the centralized algorithm if we let the inner loop in Algorithm 2 on page 8, col.
+2 to converge.
 
-\cmnt{8} I’m totally confused with the ADMM approach in Section IV.A.
+\cmnt{8} \textit{I’m totally confused with the ADMM approach in Section IV.A.
 Many notations, such as the local interference vector and consensus interference vector are used without formal definition.
@@
 These questions should be clarified and perhaps you should choose the notation system more carefully.
-For example, in (36), there are 3 similar notations and I don’t know which one is local interference vector and which one is the actual interference vector.
+For example, in (36), there are 3 similar notations and I don’t know which one is local interference vector and which one is the actual interference vector.}
 
@@
 
-\cmnt{9} In the distributed algorithms, it is not clear what information is available at each node.
+\cmnt{9} \textit{In the distributed algorithms, it is not clear what information is available at each node.
 For example, what are your assumption on CSIT (CSI knowledge at each BS) and CSIR (CSI knowledge at each user)?
-How to 2 obtain the information used to perform the required calculation at each node (such as calculating the actual interference, MMSE receiver and the dual variables)?
+How to 2 obtain the information used to perform the required calculation at each node (such as calculating the actual interference, MMSE receiver and the dual variables)?}
 
 \resp We understand the reviewer's concern.
-For the distributed precoder design, we assume that the \ac{BS} \me{b} knows the channel \me{\mbf{H}_{b,k,n}} of all users in the system by the uplink sounding technique.
-Note that it includes the cross channel of the neighbor BS users as well.
-In addition, we assume the receivers are informed by the users by using precoded uplink pilots.
+For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
+Note that it includes the cross equivalent downlink channels of the neighbor BS users as well.
+To update the MMSE receiver, the equivalent channel for the \me{\ith{k}} user \me{\mbf{H}_{b,k,n} \mvec{m}{l,k^\prime,n}, \forall k^\prime \in \mc{U}_b, \forall b \in \mc{B}} is obtained from the BSs through user specific downlink precoded pilots.
 We have included the information on what each network entity knows in page 7, col.
@@
 We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
+We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
 
-\cmnt{10} Do you have any convergence result for the proposed distributed solution based on the KKT conditions in Section IV.B?
-It seems that the iterative method to solve the KKT conditions is totally heuristic.
+\cmnt{10} \textit{Do you have any convergence result for the proposed distributed solution based on the KKT conditions in Section IV.B?
+It seems that the iterative method to solve the KKT conditions is totally heuristic.}
 
-\resp We agree with the reviewer.
-Note that, if the dual variables are allowed to iterate until convergence, the proposed KKT based scheme achieves the same stationary point for each fixed receive beamformer (similar to the distributed algorithms).
-It is heuristic, since we update the transmit precoders, receive beamformers and the dual variables all at once in each iteration.
-Please note that the proposed algorithm is of practical significance, since it has few number of iterations before the actual transmission of data with the latest precoder update.
+\resp It is true that the KKT conditions are based on the centralized algorithm in (20).
+It follows the same points as that of the centralized approach if the algorithm is iterated in the same order, \textit{i.e} the dual variables are allowed to converge before the update of the fixed operating point and the receiver.
+Here instead we perform the update of the transmit precoders, receive beamformers and the dual variables all at once in each iteration.
+Thus, we sacrifice the formal convergence for the improved speed of convergence.
 It may not be a stationary point of the original nonconvex problem but it is guaranteed to provide better performance in the sum rate compared to the distributed approaches presented in Section IV-A and Section IV-B for the same number of iterations.
@@
 
-\cmnt{11} Since queue is a dynamic system evolving according to (3), it doesn’t make sense to compare the queue deviations at a given time.
+\cmnt{11} \textit{Since queue is a dynamic system evolving according to (3), it doesn’t make sense to compare the queue deviations at a given time.
 You should compare average queue deviations in the simulations.
 Moreover, you should also compare the average delay performance instead of just comparing the performance metric (queue deviations) defined in this paper.
-Using the queue deviations as the performance metric also needs more justification.
+Using the queue deviations as the performance metric also needs more justification.}
 
 \resp We thank the reviewer for raising the critical comment.
-Since the manuscript is about the precoder design to minimize the total number of backlogged packets in the system, we have provided the convergence behavior of the proposed precoder design formulations.
-The average queue deviation can be minimized by minimizing the deviations at each instant, we have provided the convergence plot for the single slot.
+Since the manuscript is about the precoder design to minimize the total number of backlogged packets in the system, we have provided the convergence behavior of the proposed precoder design formulations for a given time instant.
 In accordance with the reviewer comment, we have included the Section V-C on page 13, col.
@@
 We have presented Fig.
-4a by comparing the average number of backlogged packets for different algorithms with various arrival bits and Fig.
+4a by comparing the average number of backlogged packets for different algorithms with various arrival rates and Fig.
 4b for the number of backlogged packets at each instant.
-Please note that the delay is directly proportional to the number of backlogged packets if the arrivals are fixed, we are not addressing this explicitly.
-Even though, \me{\ell_2} and \me{\ell_{\infty}} norm addresses the delay and the fairness implicitly, we can prioritize the users with the weights \me{a_k} in (6a) for better service rate.
-We are currently working on the system level study of the proposed formulations.
+Note that the question on delay arises when we are considering the resource allocation over certain duration.
+Since the paper is about the precoder design to minimize the number of backlogged packets at each instant, it may not be a valid performance metric for our objective.
+We still agree that delay can be controlled by reducing the number of packets on an average, as we can see from Fig.
+4, on page 13, the proposed algorithms are equally good in minimizing the average number of backlogged packets.
+Note that we can also prioritize the users by controlling the variable \me{a_k} in (6a) to address the QoS constraints for a particular user, in addition to that, we can also change the objective to \me{\ell_2} and \me{\ell_{\infty}} norm to address the delay and the fairness implicitly.
 
-\cmnt{12} What is “SRA” in the simulation figures?
+\cmnt{12} \textit{What is “SRA” in the simulation figures?}
 
@@
 
-\cmnt{13} In the discussion for Fig.
+\cmnt{13} \textit{In the discussion for Fig.
 1, you mentioned that JSFRA converge to the optimal point, and all algorithms are Pareto-optimal.
-Since the problem is non-convex, why these algorithm can find optimal solution or Paretooptimal point?
+Since the problem is non-convex, why these algorithm can find optimal solution or Paretooptimal point?}
 
@@
 \end{itemize}
+
+\bibliographystyle{./../Styles/IEEEtran}
+\bibliography{./../Library/kirja_survey}

### 2015-03-04 Response/response-2.tex
revised

@@
+We would like to thank the reviewer for providing valuable comments. We have modified the manuscript accordingly by addressing it.
+
 \begin{itemize}
 
-\cmnt{1} The logic from (6) to (16) is not clear.
+\cmnt{1} \textit{The logic from (6) to (16) is not clear.
 The only difference is the two newly introduced NON-CONVEX constraints (16b) and (16c), while the objective function (16a) and the constraint (16d) is the same as (6).
-The equivalence between (6) and (16) is not straightforward and it is confusing why the reformulation in (16) is beneficial.
+The equivalence between (6) and (16) is not straightforward and it is confusing why the reformulation in (16) is beneficial.}
 
@@
 Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), which are the under estimator to the original problem in (6).
+Since the inequalities are used to replace the equality constraint, the objective could be improved by the iterative algorithm and the equality will be achieved after the convergence, thereby having one-to-one mapping at the final solution.
 We have updated the manuscript to include the details for better clarity on page 5, col.
@@
 
-\cmnt{2} The authors use the successive convex approximation framework, but the approximate problem proposed by the authors is actually not convex.
+\cmnt{2} \textit{The authors use the successive convex approximation framework, but the approximate problem proposed by the authors is actually not convex.
 Inspecting (19), its objective function is the same as in (6), and the non-convexity of (6) comes exactly from the objective function, so (19) is not a convex problem.
-The same flaw is repeated several times in the approximate problems proposed by the authors.
+The same flaw is repeated several times in the approximate problems proposed by the authors.}
 
 \resp Please note that the objective function is convex, which can be verified by writing the difference function inside the norm operator in epigraph form.
-Since the problem in (16) is jointly nonconvex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
+Since the problem in (16) is not jointly convex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
 Even after fixing \me{\mvec{w}{l,k,n}} as constant, the problem in (16) is nonconvex due to the DC constraint (16b), which is handled by the first order relaxation around some fixed operating point.
@@
 
-\cmnt{3} The authors proposed to use block coordinate descent method to solve (16).
+\cmnt{3} \textit{The authors proposed to use block coordinate descent method to solve (16).
 But as the authors have already pointed out, to apply block coordinate descent method, the constraint sets for different variables should be disjoint (uncoupled), which is however not the case in (16), because receive and transmit precoders (i.e w and m) are coupled in the constraints.
-It is confusing on its own why the authors made a statement that contradicts the proposed methodology, and the convergence followed is in question.
+It is confusing on its own why the authors made a statement that contradicts the proposed methodology, and the convergence followed is in question.}
 
 \resp We thank the reviewer for the pointing out the flaw in the text.
-We have removed the statement on block coordinate descent method with the AO approach.
-Since the problem is nonconvex, using this approach, we can find a local optima of the original nonconvex problem.
-The manuscript is modified to include the updated statement on page 5, col.
+We have removed the incorrect statement on block coordinate descent method with the AO approach on page 5, col.
 1, second paragraph.
+Indeed, due to the coupling of the transmit and the receive precoder variables, we cannot use the standard block coordinate descent method proof for the convergence of the proposed algorithm as pointed out by the reviewer.
+We have provided a completely rewritten convergence proof on Appendix B, page no.
+14, col.
+1.
 
-\cmnt{4} Regarding the convergence of the SCA, the authors cited [27] for the convergence conditions, but the reference is wrong, because the conditions after the three bullets on page 6 are not mentioned in [27].
-In case the authors disagree, please make the citation more specific, for example, specify the theorem/statement/proposition in [27] where those conditions are specified.
+\cmnt{4} \textit{Regarding the convergence of the SCA, the authors cited [27] for the convergence conditions, but the reference is wrong, because the conditions after the three bullets on page 6 are not mentioned in [27].
+In case the authors disagree, please make the citation more specific, for example, specify the theorem/statement/proposition in [27] where those conditions are specified.}
 
-\resp We understand the reviewer's concern.
-We have provided the proof on the convergence of the centralized algorithm on Appendix B.
-We apologize for the inappropriate reference cited in the original manuscript.
+\resp We apologize for the inappropriate reference cited in the original manuscript. We have provided a completely rewritten proof on the convergence of the centralized algorithm on Appendix B.
 
-\cmnt{5} The authors also cited [28] to establish the convergence of SCA.
+\cmnt{5} \textit{The authors also cited [28] to establish the convergence of SCA.
 But the techniques of [27] and [28] are different, and the convergence conditions are different too.
-It is not clear why the authors need two set of convergence conditions for a single problem, and the resulting convergence analysis itself is not solid enough.
+It is not clear why the authors need two set of convergence conditions for a single problem, and the resulting convergence analysis itself is not solid enough.}
 
@@
 
-\cmnt{6} Another comment on reference: to the reviewer's knowledge, the term SCA is never explicitly used in [2]. So please either correct the reference or be more specific (section, theorem, etc.).
+\cmnt{6} \textit{Another comment on reference: to the reviewer's knowledge, the term SCA is never explicitly used in [2].
+So please either correct the reference or be more specific (section, theorem, etc.).}
 
@@
 
-\cmnt{7} The authors propose primal decomposition method, ADMM approach to the non-convex problem (19), while their convergence analysis is based on literature that proved convergence for convex problems only, e.g., [13].
-So the convergence analysis is not trustworthy.
+\cmnt{7} \textit{The authors propose primal decomposition method, ADMM approach to the non-convex problem (19), while their convergence analysis is based on literature that proved convergence for convex problems only, e.g., [13].
+So the convergence analysis is not trustworthy.}
 
@@
 
-\cmnt{8} The length of the paper is too extensive.
+\cmnt{8} \textit{The length of the paper is too extensive.
 Some of the reformulations as mentioned in the previous comment can be skipped.
@@
 is not deeply explained and does not bring additional value to the paper.
-The implications of ordering the sub-channels for the iterative approach should be carefully studied and extensively explained in a different publication.
+The implications of ordering the sub-channels for the iterative approach should be carefully studied and extensively explained in a different publication.}
 
@@
 
-\cmnt{9} Information regarding the value of q used to obtain the simulation results is missing (with exception of Fig. 3).
+\cmnt{9} \textit{Information regarding the value of q used to obtain the simulation results is missing (with exception of Fig. 3).}
 
@@
 
-\cmnt{10} In Fig.
+\cmnt{10} \textit{In Fig.
 1 and Fig.
@@
 Additionally, the reference scheme Q-WSRM is not optimal, since it over allocates resources if there are few queued packets.
-Therefore, it is not interesting for comparison purposes.
+Therefore, it is not interesting for comparison purposes.}
 
@@
 
-\cmnt{11} Assuming that Fig.
+\cmnt{11} \textit{Assuming that Fig.
 2 and Fig.
@@
 Even more, since the number of sub-channels is larger in Fig.
-3, the result seems contradictory.
+3, the result seems contradictory.}
 

### 2015-03-04 Response/response-3.tex
revised

@@
+\textit{This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods.
+This is an interesting and important topic.}
+
+We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helpful in improving the manuscript.
+
 \begin{itemize}
 
-\cmnt{1} This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods.
-This is an interesting and important topic.
-
-\resp We thank the reviewer for reading the manuscript and providing valuable comments.
-
-\cmnt{2} The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.
+\cmnt{1} \textit{The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.}
 
@@
 
-\cmnt{3} The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5).
+\cmnt{2} \textit{The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5).
 This is not obvious.
@@
 When \me{Q_1=0} and 2nd BS has sufficiently large power, (16b) and (16c) do not hold equality.
-Rigorous proof is needed if authors stick to this statement.
+Rigorous proof is needed if authors stick to this statement.}
 
@@
 
-\cmnt{4} The solution in (21) is obtianed for MMSE, i.e.
+\cmnt{3} \textit{The solution in (21) is obtianed for MMSE, i.e.
 for 2-norm(q=2).
 If \me{q=1} or \me{q=\infty}, it is actually an equivalent linear programming problem.
-Details for this solution should be provided.
+Details for this solution should be provided.}
 
@@
 
-\cmnt{5} The convergence proof need to be rigorous.
+\cmnt{4} \textit{The convergence proof need to be rigorous.
 The inequality of (23a) is opposite to the reference [28].
 Also the statement on uniqueness of the transmit and the receive beamformers are not correct.
-Although we can choose one antenna to be real value, this does not mean the problem has unique solution!
+Although we can choose one antenna to be real value, this does not mean the problem has unique solution!}
 
@@
 
-\cmnt{6} (25) is generally wrong.
+\cmnt{5} \textit{(25) is generally wrong.
 (25) only holds when the MSE is minimized(by MMSE receiver) and the snr is the optimized(which is obtained by general eignvalue decompostion).
@@
 This can also be easily checked by comparing (25) and (2).
-Consequently the alternative formulation (26) based on this conclusion is questionable.
+Consequently the alternative formulation (26) based on this conclusion is questionable.}
 
@@
 
-\cmnt{7} For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed.
+\cmnt{6} \textit{For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed.
 1.
 The numbers of transmitted packets for users  \me{t_k}'s are optimization variables.
-So they should be explicitly stated in the problem formulation (6), (16), (20) and (26) to avoid confusing.
+So they should be explicitly stated in the problem formulation (6), (16), (20) and (26) to avoid confusing.}
 

### 2015-03-04 Response/response-4.tex
revised

--- 2015-03-03 Response/response-4.tex
@@
+First, we thank the reviewer for providing valuable and insightful comments. The comments are really helpful in improving the manuscript.
+
 \begin{itemize}
 
-\cmnt{1} First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method.
+\cmnt{1} \textit{First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method.
 "The SCA method" is often referred to, but never really defined or referenced.
@@
 Perhaps you meant to cite [A], wherein non-convex constraints are handled in a similar way?
-Numerically, the algorithms do converge, and the argument put forward makes sense, but the treatment must be improved to be more rigorous.
+Numerically, the algorithms do converge, and the argument put forward makes sense, but the treatment must be improved to be more rigorous.}
 
-\resp We understand the reviewer's concern on the lack of rigorous convergence proof for the proposed JSFRA approach.
+\resp We understand the reviewer's concern on the lack of rigorous convergence proof for the JSFRA approach.
 We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on page 14.
@@
 
-\cmnt{2} Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates.
+\cmnt{2} \textit{Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates.
 This is due to how the conditional Lyapunov drift is minimized.
@@
 Possibly, some expectation over the queues would be optimized then.
-Even if no analytical treatment of the tracking over several time-steps is added, I would at least highly recommend adding some simulation results where the proposed one-shot algorithms are performed sequentially over several time instants.
+Even if no analytical treatment of the tracking over several time-steps is added, I would at least highly recommend adding some simulation results where the proposed one-shot algorithms are performed sequentially over several time instants.}
 
-\resp We understand the concern raised by the reviewer.
-In the current paper, we are discussing on the precoder design to minimize the number of backlogged packets in the system at a given time.
-Since the greedy approach performed at each instant minimizes the number of backlogged packets on an average, we emphasized on the precoder design based on the current knowledge of the channel state information.
-We have included Section V-C in page 13 to discuss on the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots.
+\resp We thank the reviewer for the useful suggestion.
+In this paper, we proposed the precoder design to minimize the number of backlogged packets in the system at a given time.
+Since the greedy approach is performed at each time instant, it minimizes the number of backlogged packets also on an average.
+We focused on the precoder design based on the current knowledge of the channel state information in the simulation results.
+In order to justify the gains over multiple time instants, we have now included Section V-C on page 13 to discuss on the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots.
 Plots comparing the average number of backlogged packets for different schemes at each instant and the number of queued packets remained in the system after each transmission instant are provided in Fig.
@@
 
-\cmnt{3} Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results.
+\cmnt{3} \textit{Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results.
 This reviewer recommends spending more space on the convergence, than on the description of the distributed techniques.
@@
 For the description of the signaling of the CSI in Sec.
-IV-B, are you envisioning a TDD system?
+IV-B, are you envisioning a TDD system?}
 
@@
 We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Section IV-C page 8.
-For the distributed precoder design, we assume that the \ac{BS} \me{b} knows the channel \me{\mbf{H}_{b,k,n}} of all users in the system by the uplink sounding technique.
-Note that it includes the cross channel of the neighbor BS users as well.
+For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
+Note that it includes the cross equivalent downlink channels of the neighbor BS users as well.
+To update the MMSE receiver, the equivalent channel for the \me{\ith{k}} user \me{\mbf{H}_{b,k,n} \mvec{m}{l,k^\prime,n}, \forall k^\prime \in \mc{U}_b, \forall b \in \mc{B}} is obtained from the BSs through user specific downlink precoded pilots.
 We have included the information on what each network entity knows in page 7, col.
@@
 
-\cmnt{4} Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier.
-This could easily be clarified.
+\cmnt{4} \textit{Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier.
+This could easily be clarified.}
 
@@
 
-\cmnt{5} Please see the itemized questions
+\cmnt{5} \textit{Please see the itemized questions}
 
@@
 
-\cmnts{a} - p. 1, col. 1, row 42: "userss"
+\cmnts{a} - \textit{p. 1, col. 1, row 42: "userss"}
 
@@
 
-\cmnts{b} - p.
+\cmnts{b} - \textit{p.
 1, col.
 2, row 18: the precoders are used \_implicitly\_ as decision variables.
-This is the whole point, to avoid explicitly modeling the hard decisions in the optimization, and instead do soft decisions during the iterations, and then finally hard decisions after convergence.
+This is the whole point, to avoid explicitly modeling the hard decisions in the optimization, and instead do soft decisions during the iterations, and then finally hard decisions after convergence.}
 
@@
 
-\cmnts{c} - p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?
+\cmnts{c} - \textit{p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?}
 
@@
 
-\cmnts{d} - p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead
+\cmnts{d} - \textit{p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead}
 
@@
 
-\cmnts{e} - p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here
+\cmnts{e} - \textit{p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here}
 
@@
 
-\cmnts{f} - p.
+\cmnts{f} - \textit{p.
 3, col.
@@
 Is it the problem of selecting users to be served on orthogonal subcarriers?
-There is nothing inherently combinatorial over the problem in (6) as far as I can tell, as the beamformers are used as soft decision variables.
+There is nothing inherently combinatorial over the problem in (6) as far as I can tell, as the beamformers are used as soft decision variables.}
 
@@
 
-\cmnts{g} - p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.
+\cmnts{g} - \textit{p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.}
 
@@
 
-\cmnts{h} - (16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).
+\cmnts{h} - \textit{(16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem.
+There is hardly any spaced saved by referring back to (6b).}
 
@@
 
-\cmnts{i} - p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).
+\cmnts{i} - \textit{p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).}
 
@@
 
-\cmnts{j} - p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.
+\cmnts{j} - \textit{p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.}
 
@@
 
-\cmnts{k} - p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??
+\cmnts{k} - \textit{p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??}
 
@@
 
-\cmnts{l} - p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).
+\cmnts{l} - \textit{p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).}
 
 \resp We have updated the manuscript to avoid the ambiguity in the representation of the optimal and the MMSE receiver.
-The optimal receiver is denoted by \me{\mvec{w}{l,k,n}^{\ast}} in (22) and the MMSE receiver by \me{\mvec{w}{l,k,n}} in (23).
+The optimal receiver is denoted by \me{\mvec{w}{l,k,n}^{o}} in (22) and the MMSE receiver by \me{\mvec{w}{l,k,n}} in (23).
 
-\cmnts{m} - p.
+\cmnts{m} - \textit{p.
 6, col.
 1, row 9: You might want to add somewhere that (22b) can be used instead of the fixed-point of (21b), since the scaling of the receive filters do not matter in the SINRs.
-However, does it affect the convergence of the algorithm?
+However, does it affect the convergence of the algorithm?}
 
@@
 
-\cmnts{n} - p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?
+\cmnts{n} - \textit{p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?}
 
@@
 
-\cmnts{o} - p.
+\cmnts{o} - \textit{p.
 7, col.
 1, row 35: Just because a problem is convex does not mean that it has a unique solution.
-(Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?
+(Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?}
 
 \resp We thank the reviewer for the critical comment.
-It is generally not true that the convex problem has a unique solution.
-The problem is strictly convex when there is at least one user in each BS that cannot be served by the current transmission.
-It has multiple solutions, when the objective is zero even for a single BS.
+It is true that the convex problem does not need to have a unique solution in general.
+By using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can show that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
+The uniqueness of the solution is obtained due to the linear constraint (19) in the problem formulation (20).
+Note that the linear constraint (19) is susceptible to the phase rotations on the transmit precoders, whereas any unitary rotations on the transmit precoders still satisfies the original nonconvex constraint (16b).
+When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain unique set of transmit precoders.
+On contrary, it has multiple solutions when the objective is zero even for a single BS.
 In this case, we can use a regularization term with the total power in the objective to obtain an unique solution.
@@
 
-\cmnts{p} - Table 1: "backpreassure"
+\cmnts{p} - \textit{Table 1: "backpreassure"}
 
@@
 
-\cmnts{q} - p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.
+\cmnts{q} - \textit{p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.}
 

### 2015-03-04 Report/decomposition_solutions.tex
revised

@@
 
-To decouple the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in each iteration in accordance to the decomposition method.
-To decouple the precoder design independently, the effective downlink channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are assumed to be known at each \ac{BS} \me{b} through uplink precoded pilot signaling from all the users in the system.
-Similarly to update the \ac{MMSE} receivers at the user \me{k}, the equivalent uplink channels \me{\mvec{m}{l,k^{\prime},n}^\herm \mvec{H}{b,k,n}^\herm, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} are assumed to be known through user specific precoded downlink pilot signaling as detailed in \cite{komulainen2013effective}.
+To decentralize the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in accordance to the decomposition method.
+To decouple the precoder design across \acp{BS}, the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are to be known at each \ac{BS} \me{b} through the precoded uplink pilots from all the users in the system, where the precoders are the \ac{MMSE} receiver \me{\mvec{w}{l,k,n}} evaluated at the user.
+Similarly to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} are to be known through the user specific precoded downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} by using the equivalent downlink channel that includes the updated \ac{MMSE} receivers of all the users, as in \cite{komulainen2013effective}.
 

### 2015-03-04 Report/kkt_mse_approach.tex
revised

@@
 
-\review{The Algorithm \ref{algo-4} outlines a practical way of implementing the transmit precoders in a distributed manner using \ac{OTA} signaling of the transmit precoders and the receive beamformers for certain iterations before the actual transmission of data is performed with it.
+\review{The Algorithm \ref{algo-4} outlines a practical way of updating the transmit precoders and the receive beamformers by using \ac{OTA} signaling with the precoded pilots.
 Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of the centralized problem.
-Since the problem solution in \eqref{kkt-mse-4} is equivalent to the centralized formulation in \eqref{eqn-mse-2} if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}, the problem is guaranteed to converge to the centralized solution.
+The algorithm in \eqref{kkt-mse-4} is identical to the centralized formulation in \eqref{eqn-mse-2}, if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}.
 Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders.
-In order to avoid this, the proposed method performs the group update of all variables to obtain the transmit and the receive beamformers with the limited number of iterations.
+To avoid this, the proposed method performs the group update of all variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence by sacrificing the formal convergence.
 If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.}

### 2015-03-04 Report/simulation_results.tex
revised

@@
 
-For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
-The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest \ac{PL} component.
+For a \ac{MIMO} scenario, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
+The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the associations are made by selecting the \ac{BS} with the lowest \ac{PL} component.
 Fig.

### 2015-03-04 Report/time_correlated.tex
revised

@@
-We discuss performance of the \ac{JSFRA} algorithm for different values of \me{\ell_q} over multiple transmission slots.
+We discuss the performance of the \ac{JSFRA} algorithm for different \me{\ell_q} over multiple transmission slots.
 It is compared with the existing \ac{Q-WSRME} scheme by varying the average arrival rate \me{A_k} of all users.
 Fig.
-\ref{fig-time-analysis} demonstrates the performance of the centralized algorithms for different \me{\ell_q} values.
-Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and is based on Poisson arrival process.
+\ref{fig-time-analysis} plots the performance of the centralized algorithms for different \me{\ell_q} values.
+Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and it follows Poisson process.
 We considered a \me{4 \times 1} \ac{MIMO} system with \me{N = 4} sub-channels and \me{N_B = 2} \acp{BS}.
-The path loss is modeled using a uniform random variable \me{[0,-3]} dB with the maximum \ac{SINR} seen by any user is \me{6} dB.
+The \ac{PL} is modeled as a uniform random variable \me{[0,-3]} dB.
 
 Fig.
-\ref{fig-review} compares various schemes with the average number of backlogged packets present in the system after each transmission slot.
+\subref*{fig-review} compares various schemes with the average number of backlogged packets present in the system after each transmission slot.
 The performance of the \ac{JSFRA} scheme using \me{\ell_2} and \ac{Q-WSRME} approach are similar in the average number of residual packets after each transmission slot.
 Note that the additional rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence.
-Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are significantly greater than the actual transmissions.
-It can be seen from Fig.
-\ref{fig-review} and Fig.
-\ref{fig-review-time} that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} formulation due to the greedy allocation by serving users with better channel conditions.
+Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are greater than the actual transmissions.
 Fig.
-\ref{fig-time-analysis} shows that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs worst in terms of the average number of backlogged packets due to the instantaneous fairness constraints.
+\subref*{fig-review} and Fig.
+\subref*{fig-review-time} shows that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} scheme due to the greedy allocation of serving users with better channel.
+Fig.
+\ref{fig-time-analysis} highlights the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally good compared to other objectives when the system is in the stable region.
+On contrary, in the unstable region, the performance is inferior, since the fair allocation is not effective when the number of backlogged packets is significantly more for all users.

### 2015-03-07 Response/response-4.tex
halfoocked

@@
 It is true that the convex problem does not need to have a unique solution in general.
-By using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can show that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
+By using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can see that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
 The uniqueness of the solution is obtained due to the linear constraint (19) in the problem formulation (20).
@@
 We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-C.
+It makes the objective strictly convex, therefore, it has a unique minimum.
 

### 2015-03-07 Report/convergence_centralized.tex
halfoocked

--- 2015-03-02 Report/convergence_centralized.tex
@@
 \newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
+\newcommand{\ma}{\mbf{x}}
 
@@
 	\item[(b)] The feasible set should be a compact set
-	\item[(c)] The sequence of the objective values should be monotonically decreasing in each iteration
-	\item[(d)] Uniqueness of the mapping, \textit{i.e}, there should be one-to-one correspondence between the objective value set and the feasible domain.
+	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
+	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
 \end{itemize}
@@
 Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
+Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th.
+3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
 
-Assuming the above conditions are satisfied by the objective function of the iterative algorithm, using \cite[Th.
-3.14]{rudin1964principles}, we can show that any bounded monotonically decreasing sequence has a limiting point.
-The one-to-one mapping between the feasible domain and the objective function value is required to prove the convergence of the transmit and the receive beamformers upon convergence of the objective function value iterates.
-Note that the iterative relaxed convex subproblems has the unique solution but not the original nonconvex problem.
-Since the transmit precoders in problem in \eqref{eqn-6} and \eqref{eqn-mse-1} are invariant to any unitary matrix rotations due to the absolute value operator in the \ac{SINR} expression, the limiting point is a set of precoder vectors with different phase rotations.
-The limiting point of the iterative algorithm is susceptible to the initial feasible point, since it is the operating point for linearizing the nonconvex \ac{DC} constraint.
+\subsection{Boundedness of the Objective and Compactness of the Set}
 
-\subsection{Boundedness and Compactness}
+The feasible set of the problem \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.
 
-The feasible set of the relaxed nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded due to the total power constraint on the transmit precoders \eqref{eqn-6.4}.
-Note that the other variables are also bounded in accordance with this constraint.
-Since the feasible set also includes the boundary value due to the inequality constraint, it is closed and compact.
-
-To prove the boundedness, it is enough to show that the objective function is bounded below due to the minimization objective.
-Since the minimum value of the norm operator is zero, \textit{i.e}, the limiting point is \me{< -\infty}, it is bounded below.
-Note that the objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
+The minimum value of the norm operator in the objective is zero, \textit{i.e}, the limiting point is \me{< -\infty}, therefore it is bounded below.
+The objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
 The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive.
@@
 \end{IEEEeqnarray}
-where \me{g_2,f} are convex functions and \me{h} is a linear function.
-Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both.
-Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} correspond to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}.
-Other convex constraints are addressed by the constraint \eqref{con-cvx}.
-With this, the feasible set of the problem \eqref{con} is given by
+where \me{g_2,f} are convex and \me{h} is a linear function.
+Let \me{g_0,g_1} be convex in either \me{\mx} or \me{\my} but not on both.
+The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
+Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
 \begin{IEEEeqnarray}{rl}
@@
 In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}.
-We adopt \ac{SCA} approach presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets.
-Since the proposed method involves two level of iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
+We adopt \ac{SCA} presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets.
+Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
 Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\mx}.
 Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denote the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
-For the sake of clarity, we define the optimal value of \me{\mz} obtained for the \me{\ith{i}} \ac{AO} iterate for the fixed \me{\my} variable as \me{\iter{\mz}{\ast|y}{i}}.
+Let \me{\iter{\mz}{\ast|y}{i}} be the optimal value of \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iterate for a fixed \me{\my}.
 
@@
 Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
-At each \ac{SCA} iteration, the feasible set includes the optimal point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, thereby, leading to the monotonic decrease in the objective function \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
+At each \ac{SCA} iteration, the feasible set includes the optimal point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, thereby, leading to the monotonic decrease in the objective values \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
 \begin{multline} \label{con-convergence}
@@
 Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches limiting point as \me{k \rightarrow \infty}.
-Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point for \eqref{con}, since it is the minimizer only over the feasible set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
+Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point of \eqref{con}, since it is the minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
 
@@
 \end{equation*}
-The feasible set follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} iteration.
-Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.
+The \ac{AO} update follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
+%Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.
 
@@
 
-To prove the convergence of the transmit and the receive beamformers, we use the uniqueness in the mapping between the transmit and receive beamformers with respect to the objective function.
-The uniqueness of the function mapping, \textit{i.e}, one-to-one correspondence between the feasible solution and the objective value, is achieved due to the linear relaxation performed on the \ac{DC} constraint in problem \eqref{eqn-9} and the \ac{MSE} expression in \eqref{eqn-mse-2}.
-The linearized \eqref{eqn-8} can be written as
-\begin{multline} \label{uniqueness-1}
-\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
-- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
-\end{multline}
-where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for \ac{MSE} expression as
-\begin{multline} \label{uniqueness-2}
-| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
-\end{multline}
-Note that the receive beamformer \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} is unique for the given set of transmit precoders.
-It is due to the constraints \eqref{uniqueness-1} and \eqref{uniqueness-2}, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoders phase rotations and thereby having a unique minimizer.
+The uniqueness of the transmit precoders and the receive beamformers for the convex subproblem can be guaranteed in general by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
+Note that the receive beamformer \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} is also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoders phase rotations and thereby having a unique minimizer.
 
-When the objective function is zero, the uniqueness of the transmit precoders using \eqref{uniqueness-1} and \eqref{uniqueness-2} are not valid due to the inactive constraints \eqref{eqn-6.2} and \eqref{eqn-mse-1.2}.
-To obtain a unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can follow the regularization approach discussed in Appendix \ref{a-3} without affecting the optimal solution.
+When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
+To obtain an unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
 %we can regularize the objective with the total transmit power expression without affecting the optimal solution as 
@@
 
+\subsection{Convergence of the beamformer iterates}
+
+Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and let \me{\mc{A}} be a point-to-set mapping from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}.
+The objective function \me{f} in \eqref{con-cvx} is continuous and the iterative algorithm yields monotonically decreasing objective values \me{f(\ma^{(n)}) \leq f(\ma^{(n-1)})} in each iteration.
+Therefore, the operator \me{\mc{A}} is monotonic with respect to a continuous objective function \me{f} yielding a sequence of beamforming iterates \me{\{\ma^{(n)}\}}.
+The following conditions are satisfied by the iterative algorithm \cite{meyer1976sufficient}.
+\begin{itemize}
+
+\end{itemize}
+
+.
+Let \me{\{\ma^{(n)}\}} be the sequence of beamforming iterates generated by the function \me{f} in \eqref{con-cvx} and the mapping operator \me{\mc{A}}.
+To prove the convergence of the beamformer iterates, following conditions are required \cite{meyer1976sufficient}.
+\begin{itemize}
+\item[(e)] The mapping operator \
+\end{itemize}
+
+approaches a limiting or accumulation point \me{\ma^{\ast} \in \mc{F}^\ast} as \me{n \rightarrow \infty}, where \me{\mc{F}^{\ast}} represents the set of accumulation points for the
+
 \subsection{Stationary Point}
@@
 To show the limiting point of the iterative algorithm is the stationary point of \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem.
-Since the converged point is a minimizer satisfying
+As \me{i \rightarrow \infty} asymptotically, it satisfies
 \allowdisplaybreaks{\begin{multline} \label{con-opt}
@@
 \end{multline}}
-the solution is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+where the solution point is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
 Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
@@
 Using the above arguments, we can show that the \ac{JSFRA} schemes attains a stationary point of the original nonconvex problem.
-
-\begin{comment}
-To prove the convergence of the centralized algorithm in \eqref{eqn-6} and \eqref{eqn-mse-1}, following conditions are necessary to prove the sequence convergence using Bolzano-Weierstrass theorem \cite{rudin1964principles}.
-\begin{itemize}
-	\item At each \ac{SCA} update, the objective value decreases monotonically 
-	\item At each \ac{AO} update, the objective value should decrease monotonically
-	\item Boundedness of the objective value sequence and the uniqueness of the limiting point.
-\end{itemize}
-In addition, we show that the converged point is in fact the stationary point of the original nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
-
-The boundedness of the objective function can be justified by the convexity and the presence of the transmit power constraint.
-Since the objective function is convex, it is bounded from below.
-Due to the total power constraint \eqref{eqn-6.4}, the function is bounded from above as well.
-In addition, the feasible set is a compact set since the boundary points are also included in the feasible set.
-
-To prove the monotonicity of the objective function values, let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} equivalently as
-\begin{IEEEeqnarray}{rCl} \label{con}
-\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
-\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
-&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
-&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
-\end{IEEEeqnarray}
-wher \me{g_2,f} are convex functions and \me{h} is a linear function.
-Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both.
-Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}.
-Other convex constraints are addressed by the constraint \eqref{con-cvx}.
-With this, the feasible set of the problem \eqref{con} is given by
-\begin{IEEEeqnarray}{rl}
-\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
-\end{IEEEeqnarray}
-
-To solve the problem, we resort to \ac{AO} by fixing a block of varibles and optimize for others \cite{bezdek2002some}.
-In the problem \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint in \eqref{con-dc}.
-In order to solve the problem after fixing the variable \me{\my}, we adopt the \ac{SCA} approach presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets.
-Since the proposed method involves two level of iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
-Let \me{\iter{\mc{X}}{k}{i}} be a feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and for a fixed \me{\mx}, the set is represented as \me{\iter{\mc{Y}}{k}{i}}.
-Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denotes the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
-For the sake of clarity, we define the optimal value of \me{\mz} obtained for the \me{\ith{i}} \ac{AO} iterate for the fixed \me{\my} variable as \me{\iter{\mz}{\ast|y}{i}}.
-
-Let us consider the order for \ac{AO} by optimizing variable \me{\mx} before optimizing the variable \me{\my}.
-Without affecting the convergence proof, let us consider the variable \me{\my} is fixed for the \ac{AO} \me{i} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
-In order to find the optimal value of \me{\mx} for the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate of \me{\mx} as
-\begin{multline} \label{con-relax}
-\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
-\end{multline}
-Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
-\begin{subeqnarray} \label{con-m}
-	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
-	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
-	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
-	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
-\end{subeqnarray}
-Let the set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
-In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\my = \iter{\my}{\ast}{i-1}} operating at \me{\iter{\mx}{k}{i}}, let us assume that \eqref{con-m} yields \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution at the \me{\ith{k}} iteration.
-To show \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} minimizes the objective function ans also feasible, let us assume that the point \me{\iter{\mx}{k}{i} \in \iter{\mc{X}}{k}{i}}, which is feasible for \eqref{con-m}.
-Since the function \me{{g}_0(\mx,\iter{\my}{\ast}{i-1}} is linearized at \me{\iter{\mx}{k}{i}}, it satisfies
-\begin{equation}
-h(\mz) - {g}_0(\mx,\iter{\my}{\ast}{i-1}) \leq h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0,
-\end{equation}
-since \me{{g}_0(\mx,\iter{\my}{\ast}{i-1}) \leq \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}), \forall \mx \in \iter{\mc{X}}{k}{i}}.
-Now, \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are the optimal and feasible point for the \me{\ith{k}} subproblem \eqref{con-m}, it satisfies
-\begin{multline}\label{con-sub-set}
-h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\
-\leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 
-\end{multline}
-Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
-In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iter{\mc{X}}{0}{i} \subseteq \dots \subseteq \iter{\mc{X}}{k-1}{i} \subseteq \iter{\mc{X}}{k}{i} \subset \mc{F}}.
-Since the feasible set of the problem \eqref{con-m} includes the feasible sets from the earlier iteration, we arrive at
-\begin{multline} \label{con-convergence}
-f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
-\end{multline}
-Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and converges to a limiting point.
-Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point of the problem \eqref{con}, since it is the minimizer only in the feasible set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, which depends on \me{\mx} and \me{\mz} only.
-
-Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
-Even after treating \me{\mx} as a constant, the problem is still nonconvex due to the \ac{DC} constraint.
-Following similar approach, we can find the minimizer \me{\iter{\my}{k}{i}} and \me{\iter{\mz}{k}{i}} for the convex subproblem \eqref{con-m} at each iteration \me{{k}}.
-Note that \me{\iter{\mz}{k}{i}} is reused since the variable \me{\mx} is fixed for the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the problem follows similar arguments as above.
-Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
-Note that the limiting point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i})} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
-
-Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
-\begin{equation*}
-f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
-\end{equation*}
-Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mx}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
-In order to find \me{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
-Since the problem \eqref{con} is nonconvex even after fixing \me{\mx}, we have to linearize the convex function in the \ac{DC} constraint \eqref{con-dc} around some fixed operating point of \me{\my}.
-Since we know that \me{\iter{\my}{\ast}{i-1}} is already a feasible point for \me{\my} along with \me{\iter{\mx}{\ast}{i}}, linearization is performed around this feasible point.
-Using the inequality in \eqref{con-sub-set}, we can show that \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}}.
-Now the optimization is performed to find the optimal \me{\my} using the relaxed subproblem \eqref{con-m}, the optimal solution \me{\iter{\mz}{0}{i}} for the initial iteration after \ac{AO} update follows
-\begin{equation*}
-f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}),
-\end{equation*}
-since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}} as the operating point for \ac{AO} and \ac{SCA} iteration.
-Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}}, since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
-Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner\footnote{Note that the objective is monotonically decreasing even if the \ac{SCA} subproblem \eqref{con-m} is terminated after predetermined number iterations or for certain accuracy.}.
-
-The uniqueness of the convex subproblems \eqref{con-m} are required for any sequence to convergence \cite{rudin1964principles}.
-For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders are guaranteed by the constraint \eqref{eqn-8}, which can be written as
-\begin{multline}
-\gamma_{l,k,n} + \tilde{\beta}_{l,k,n}^{-2} |\mvec{\tilde{H}}{b_k,k,n} \mvec{\tilde{m}}{l,k,n}|^2 (\beta_{l,k,n} - \tilde{\beta}_{l,k,n}) \\
-- \tilde{\beta}_{l,k,n}^{-1} \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
-\end{multline}
-where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the \eqref{eqn-mse-2} by
-\begin{multline}
-| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 \\ + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 + \enoise \leq \epsilon_{l,k,n}.
-\end{multline}
-Since the limiting point is not unique for different initial point in the feasible set \me{\mc{F}}, the above objective function value sequence is pointwise continuous.
-
-To show the converged point of the iterative algorithm is in fact the stationary point of the nonconvex problem \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem.
-Since the converged point is the minimizer for the iterative algorithm such that
-\begin{multline} \label{con-opt}
-f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
-f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
-\end{multline}
-the solution is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.
-The monotonic decrease in the objective is still valid if the variables \me{\mx,\my} and \me{\mz} are updated together, since the update in \me{\my} increases the objective function for a fixed point \me{\mx} and \me{\mz}.
-Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.
-
-\end{comment}
-
-\begin{comment}
-In order to prove the convergence of the proposed iterative algorithm, following conditions are to be satisfied \cite{scutari}
-\begin{itemize}
-	\item convergence of the \ac{SCA} subproblem	
-	\item uniqueness of the transmit and the receive beamformers
-	\item monotonic convergence of the objective function
-\end{itemize}
-In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}.
-Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
-\begin{subeqnarray} \label{sca-req}
-	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
-	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
-	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}),
-\end{subeqnarray}
-where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}.
-The stationary point of the relaxed convex problem satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}.
-It can be seen that the  \ac{SCA} relaxed formulation converges to a local stationary point at each iteration.
-
-The uniqueness of the transmit and the receive beamformers can be justified by forcing one antenna to be real valued to exclude the phase ambiguity arising from the complex precoders.
-The monotonic convergence of the objective function can be justified by the following arguments.
-At each \ac{SCA} iteration, the relaxed subproblem is solved for the locally optimal transmit precoders to minimize the objective function.
-Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point, \textit{i.e},  \me{\mbf{x}^{\ast(i-1)}} for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
-Therefore, at each \ac{SCA} step, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.
-
-Once the problem is converged to a stationary transmit precoders, the receive beamformers are updated based on the receivers in \eqref{opt-rx} or \eqref{eqn-10}.
-The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, and hence the proposed \ac{JSFRA} scheme is guaranteed to converge to a stationary point of the original nonconvex problem.
-
-Following similar approach as in Section \ref{sec-3.2.1}, at each iteration, the \ac{SCA} subproblems converge to a stationary point of the original nonconvex problem.
-The uniqueness of the precoders are justified if there is no phase ambiguity in the stationary solution.
-By reorganizing \eqref{eqn-mse-1.3} as
-\iftoggle{single_column}{
-	\begin{equation}
-		\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} + \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
-	\end{equation}
-}{
-\begin{multline}
-\epsilon_{l,k,n} \geq  1 - 2 \Re{ \left \lbrace \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right \rbrace} \\ 
-+ \sum_{\mathclap{\forall (j,i)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2,
-\end{multline}
-}
-we can see that the ambiguity in the phase rotations for the transmit and the receive beamformers are eliminated by the presence of real component in the \ac{MSE} expression.
-
-At each \ac{SCA} update, the transmit precoders are obtained uniquely by minimizing \eqref{eqn-mse-1} due to the convex nature of the relaxed problem.
-For a fixed transmit precoders, the \ac{MMSE} receiver improves the objective value \cite{christensen2008weighted,wmmse_shi}, leading to the monotonic convergence of the objective function.
-At each \ac{SCA} step, the optimal value of the previous iteration is also included in the domain of the problem, and the objective value can either decrease or stays the same after each iteration.
-Note that the objective function improves at each iteration, whereas the sum rate need not follow the same behavior.
-\end{comment}

### 2015-03-07 Response/response-1.tex
final_draft

@@
 Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16).
-The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-C on page 15, col.
+The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D on page 15, col.
 2.
@@
 Since the problem is nonconvex, the JSFRA formulation can find a local optimal point upon convergence.
-The converged point of the JSFRA problem is in fact the stationary point of the original nonconvex problem, which is discussed in Appendix B-D on page 15, col.
+The converged point of the JSFRA problem is in fact the stationary point of the original nonconvex problem, which is discussed in Appendix B-E on page 15, col.
 2.

### 2015-03-07 Report/convergence_centralized.tex
final_draft

@@
 
-\subsection{Boundedness of the Objective and Compactness of the Set}
+\subsection{Bounded Objective Function and Compact Feasible Set}
 
@@
 
-\subsection{Monotonicity}
+\subsection{Monotonicity} \label{mcity}
 
@@
 
+\subsection{Convergence of the Beamformer iterates}
+
+Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{k+1} \in \mc{A}(\iterate{\ma}{k})}.
+The set of accumulation points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
+Let \me{\{\iterate{\ma}{k}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
+If the mapping is strictly monotonic and uniformly compact, then the following conditions hold \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}.
+\begin{itemize}
+\item[(i)] all accumulation points will be fixed points,
+\item[(ii)] \eqn{f(\iterate{\ma}{k}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
+\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e} \eqn{\|\iterate{\ma}{k} - \iterate{\ma}{k+1} \| \rightarrow 0}.
+\end{itemize}
+
+The mapping \eqn{\mc{A}} for the iterative algorithm is given by
+\begin{equation}
+\mc{A}(\iterate{\ma}{k}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{k}), \; \text{subject to} \; \ma \in \mc{F},
+\end{equation}
+where \me{\iterate{\ma}{k} \in \mc{A}(\iterate{\ma}{k})}.
+The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{A}(\ma)}, as discussed in Appendix \ref{mcity}.
+The sequence of iterates \me{\{\iterate{\ma}{k}\}} will have at least one accumulation point, which follows from the compactness of the set \cite{zangwill1969nonlinear}.
+The sequence \me{\{\iterate{\ma}{k}\}} converges to the set of fixed point \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
+
+To show the set of fixed points \me{\mc{F}^\ast} are the minimizer for the objective function \me{f}, we can rely on the strict monotonicity of the objective function for each iteration.
+Since \me{f(\mc{A}(\iterate{\ma}{k}) < f({k})}, the objective decreases monotonically for each iteration and the equality achieves when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point.
+Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizer for the objective function \me{f} over the set \me{\mc{F}}.
+
+If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{k+1} = \mc{A}(\iterate{\ma}{k})} and the accumulation point is unique.
+The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{meyer1976sufficient,zangwill1969nonlinear}.
+Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\ast} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.
+
 \subsection{Uniqueness}
@@
 
-\subsection{Convergence of the beamformer iterates}
-
-Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and let \me{\mc{A}} be a point-to-set mapping from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}.
-The objective function \me{f} in \eqref{con-cvx} is continuous and the iterative algorithm yields monotonically decreasing objective values \me{f(\ma^{(n)}) \leq f(\ma^{(n-1)})} in each iteration.
-Therefore, the operator \me{\mc{A}} is monotonic with respect to a continuous objective function \me{f} yielding a sequence of beamforming iterates \me{\{\ma^{(n)}\}}.
-The following conditions are satisfied by the iterative algorithm \cite{meyer1976sufficient}.
-\begin{itemize}
-
-\end{itemize}
-
-.
-Let \me{\{\ma^{(n)}\}} be the sequence of beamforming iterates generated by the function \me{f} in \eqref{con-cvx} and the mapping operator \me{\mc{A}}.
-To prove the convergence of the beamformer iterates, following conditions are required \cite{meyer1976sufficient}.
-\begin{itemize}
-\item[(e)] The mapping operator \
-\end{itemize}
-
-approaches a limiting or accumulation point \me{\ma^{\ast} \in \mc{F}^\ast} as \me{n \rightarrow \infty}, where \me{\mc{F}^{\ast}} represents the set of accumulation points for the
-
 \subsection{Stationary Point}
 
-To show the limiting point of the iterative algorithm is the stationary point of \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem.
-As \me{i \rightarrow \infty} asymptotically, it satisfies
+To show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
 \allowdisplaybreaks{\begin{multline} \label{con-opt}

### 2015-03-09 Report/convergence_centralized.tex
revision_2

@@
 
-Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
+Finally, to prove the global convergence of the iterative algorithm, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
 \allowdisplaybreaks{\begin{multline}
@@
 \end{equation}
-where \me{\iterate{\ma}{k} \in \mc{A}(\iterate{\ma}{k})}.
-The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{A}(\ma)}, as discussed in Appendix \ref{mcity}.
+where \me{\iterate{\ma}{k}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{k})} in the \me{\ith{k}} iteration\footnote{\me{k} refers to the update of all variables in \me{\ma}, \textit{i.e}, both \ac{SCA} and \ac{AO} iterations}.
+The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as discussed in Appendix \ref{mcity}.
 The sequence of iterates \me{\{\iterate{\ma}{k}\}} will have at least one accumulation point, which follows from the compactness of the set \cite{zangwill1969nonlinear}.
@@
 To show the set of fixed points \me{\mc{F}^\ast} are the minimizer for the objective function \me{f}, we can rely on the strict monotonicity of the objective function for each iteration.
-Since \me{f(\mc{A}(\iterate{\ma}{k}) < f({k})}, the objective decreases monotonically for each iteration and the equality achieves when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point.
+Since \me{f(\mc{A}(\iterate{\ma}{k})) < f(\iterate{\ma}{k})}, the objective decreases monotonically for each iteration and the equality achieves when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point.
 Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizer for the objective function \me{f} over the set \me{\mc{F}}.

### 2015-03-09 Report/convergence_centralized.tex
update_finally

@@
 
-Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{k+1} \in \mc{A}(\iterate{\ma}{k})}.
+Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
 The set of accumulation points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
-Let \me{\{\iterate{\ma}{k}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
+Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
 If the mapping is strictly monotonic and uniformly compact, then the following conditions hold \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}.
@@
 \item[(i)] all accumulation points will be fixed points,
-\item[(ii)] \eqn{f(\iterate{\ma}{k}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
-\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e} \eqn{\|\iterate{\ma}{k} - \iterate{\ma}{k+1} \| \rightarrow 0}.
+\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
+\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
 \end{itemize}
@@
 \begin{equation}
-\mc{A}(\iterate{\ma}{k}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{k}), \; \text{subject to} \; \ma \in \mc{F},
+\mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}), \; \text{subject to} \; \ma \in \mc{F},
 \end{equation}
-where \me{\iterate{\ma}{k}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{k})} in the \me{\ith{k}} iteration\footnote{\me{k} refers to the update of all variables in \me{\ma}, \textit{i.e}, both \ac{SCA} and \ac{AO} iterations}.
+where \me{\iterate{\ma}{i}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{i})} in the \me{\ith{i}} iteration\footnote{\me{i} denotes the \ac{AO} to update \me{\mx} and \me{\my} by iterating \ac{SCA} until convergence}.
 The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as discussed in Appendix \ref{mcity}.
-The sequence of iterates \me{\{\iterate{\ma}{k}\}} will have at least one accumulation point, which follows from the compactness of the set \cite{zangwill1969nonlinear}.
-The sequence \me{\{\iterate{\ma}{k}\}} converges to the set of fixed point \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
+The sequence of iterates \me{\{\iterate{\ma}{i}\}} will have at least one accumulation point, which follows from the compactness of the set \cite{zangwill1969nonlinear}.
+The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed point \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
 
 To show the set of fixed points \me{\mc{F}^\ast} are the minimizer for the objective function \me{f}, we can rely on the strict monotonicity of the objective function for each iteration.
-Since \me{f(\mc{A}(\iterate{\ma}{k})) < f(\iterate{\ma}{k})}, the objective decreases monotonically for each iteration and the equality achieves when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point.
+Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality achieves when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point.
 Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizer for the objective function \me{f} over the set \me{\mc{F}}.
 
-If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{k+1} = \mc{A}(\iterate{\ma}{k})} and the accumulation point is unique.
+If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
 The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{meyer1976sufficient,zangwill1969nonlinear}.

### 2015-03-09 Report/convergence_centralized.tex
updated_convergence

@@
 
-The minimum value of the norm operator in the objective is zero, \textit{i.e}, the limiting point is \me{< -\infty}, therefore it is bounded below.
+The minimum value of the norm operator in the objective is zero, \textit{i.e}, \me{\|x\|_q > -\infty}, therefore it is bounded below.
 The objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
 The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive.
-Note that the norm operator is not differentiable at the minimum point for \me{\ell_1} and \me{\ell_infty}.
+Note that the norm operator is not differentiable at the minimum point for \me{\ell_1} and \me{\ell_\infty}.
 Using conditions (a) and (b), we can guarantee the existence of a minimizer to the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
@@
 Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denote the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
-Let \me{\iter{\mz}{\ast|y}{i}} be the optimal value of \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iterate for a fixed \me{\my}.
+Let \me{\iter{\mz}{\ast|\my}{i}} be the optimal value of \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iterate for a fixed \me{\my}.
 
@@
 \begin{multline} \label{con-convergence}
-f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
+f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
 \end{multline}
 Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches limiting point as \me{k \rightarrow \infty}.
-Note that feasible point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i})} need not be a stationary point of \eqref{con}, since it is the minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
+Note that feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not be a stationary point of \eqref{con}, since it is the minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
 
@@
 Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
-Note that the limiting point \me{(\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i})} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
+Note that the limiting point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
 
@@
 \allowdisplaybreaks{\begin{multline}
-f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
-\leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
+f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
+\leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
 \end{multline}}
-Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
+Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|\my}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
 To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
-Since we linearize the convex function in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}} using \eqref{con-sub-set}.
+Since we linearize the convex function in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} using \eqref{con-sub-set}.
 Using this, we can show the monotonicity of the objective value sequence as
 \begin{equation*}
-f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}).
+f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}).
 \end{equation*}
-The \ac{AO} update follows \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
+The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
 %Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.
@@
 \end{equation}
-where \me{\iterate{\ma}{i}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{i})} in the \me{\ith{i}} iteration\footnote{\me{i} denotes the \ac{AO} to update \me{\mx} and \me{\my} by iterating \ac{SCA} until convergence}.
+where \me{\iterate{\ma}{i}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{i})} in the \me{\ith{i}} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations to be performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant}.
 The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as discussed in Appendix \ref{mcity}.
@@
 
-The uniqueness of the transmit precoders and the receive beamformers for the convex subproblem can be guaranteed in general by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
-Note that the receive beamformer \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} is also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoders phase rotations and thereby having a unique minimizer.
+The uniqueness of the transmit precoders and the receive beamformers for each convex subproblem is achieved by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
+The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations.
 
 When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
-To obtain an unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
+To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
 %we can regularize the objective with the total transmit power expression without affecting the optimal solution as 
@@
 \end{multline}}
-where the solution point is inside the feasible set \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})} is the minimizer of the objective function \me{f_0} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using the discussions in \cite{marks1978technical}, we can easily show that the feasible point \me{\mc{F}} and \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in the local neighborhood, is a stationary point of the non convex problem in \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions for the set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires the subdifferential set of the objective function to include \me{0 \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions.
-Using the above arguments, we can show that the \ac{JSFRA} schemes attains a stationary point of the original nonconvex problem.
+where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+Using \cite{marks1978technical}, we can show that the feasible point  \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in its local neighborhood, is a stationary point of \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires \me{\mbf{0}^\tran \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions, where \me{\partial f_0(\mz_{\ast})} denotes the subdifferential set.
+Using these arguments, we can show that the \ac{JSFRA} schemes reaches a stationary point of the original nonconvex problem.

### 2015-03-11 Report/convergence_centralized.tex
updated nam_comments without appendix

@@
 Let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
-\begin{IEEEeqnarray}{rCl} \label{con}
-	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
-	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
-	&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
-	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
-\end{IEEEeqnarray}
+\begin{subeqnarray} \label{con}
+	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \slabel{con-obj} \\
+	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \slabel{con-dc} \\
+	&\quad& g_1(\mx,\my) \leq 0 \eqsub \slabel{con-cvx-blk} \\
+	&\quad& g_2(\mx) \leq 0 \eqsub \slabel{con-cvx}
+\end{subeqnarray}
 where \me{g_2,f} are convex and \me{h} is a linear function.
@@
 Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
-\begin{IEEEeqnarray}{rl}
-\mc{F} = \{ \; \mx,\my,\mz \; \big | \; & h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
-								& g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \; \} \nonumber
-\end{IEEEeqnarray}
+\begin{align}
+\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
+								 & \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
+\end{align}
 
@@
 \begin{subeqnarray} \label{con-m}
-	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
-	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
-	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
-	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
+	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \slabel{con-obj-m} \\
+	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \slabel{con-dc-m} \\
+	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0 \eqsub \slabel{con-cvx-blk-m} \\
+	&\quad& g_2(\mx) \leq 0. \eqsub \slabel{con-cvx-m}
 \end{subeqnarray}
@@
 \begin{equation}
-\mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}), \; \text{subject to} \; \ma \in \mc{F},
+\mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}), \; \text{subject to} \; \ma \in \mc{F}
 \end{equation}
@@
 f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
-f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}),
+f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
 \end{multline}}

### 2015-03-11 Report/dual_approach.tex
updated nam_comments without appendix

@@
 &\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
-&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n}, \eqspace \eqsub \\
-&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b}, \forall \bar{k} \in \bar{\mc{U}}_b,  \forall n \eqsub \\
-& \text{and } \eqref{eqn-8}, \eqsub
+&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
+&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
+& \text{and } \eqsub \eqref{eqn-8}
 \end{IEEEeqnarray}}
@@
 \begin{equation}
-\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
+\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
 \label{dual-sg-update}

### 2015-03-11 Report/kkt_mse_approach.tex
updated nam_comments without appendix

@@
 \sigma_{l,k,n} : & \hspace{0.5cm} & \log(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
-%\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
+\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}\; \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 	\sigma_{l,k,n} : &  \log_2(\tilde{\epsilon}_{l,k,n}) + \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2)\tilde{\epsilon}_{l,k,n}} \leq -t_{l,k,n} \IEEEyessubnumber \label{kkt-mse-1.3} \\
-	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
+	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
 \end{IEEEeqnarray}
@@
 \mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}.
-\IEEEyessubnumber \label{kkt-mse-4.6}\\
+\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}\\
 \epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
@@
 	\mvec{w}{l,k,n}^{(i)} =& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm \nonumber \\
-	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}. \IEEEyessubnumber \label{kkt-mse-4.6} \\
+	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6} \\
 	\epsilon_{l,k,n}^{(i)} =& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \nonumber \\
@@
 \review{The choice of \me{\rho} is susceptible to the system model under consideration, which affects the convergence speed of the iterative algorithm.
-In our simulations, we fixed \me{\rho = 0.1} irrespective of the model under consideration.}
+In all simulations, the step size \me{\rho} is fixed to \me{0.1} irrespectively.}
 
@@
 
-\review{The Algorithm \ref{algo-4} outlines a practical way of updating the transmit precoders and the receive beamformers by using \ac{OTA} signaling with the precoded pilots.
-Unlike \ac{PD} or \ac{ADMM} approach, all variables are updated at once, \textit{i.e}, the \ac{SCA} point of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable \me{\alpha} using subgradient update, it is not guaranteed to obtain the same point as that of the centralized problem.
-The algorithm in \eqref{kkt-mse-4} is identical to the centralized formulation in \eqref{eqn-mse-2}, if the receive beamformers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed and optimized for the transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}.
-Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method for finding the transmit precoders.
-To avoid this, the proposed method performs the group update of all variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence by sacrificing the formal convergence.
+\review{Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling with the precoded pilots.
+Unlike \ac{PD} or \ac{ADMM} schemes, all variables are updated at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient.
+It is not guaranteed to obtain the same point as that of the centralized problem.
+The algorithm in \eqref{kkt-mse-4} is identical to \eqref{eqn-mse-2}, if the receivers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed to find the optimal transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}.
+Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method to find the transmit precoders.
+To avoid this, the proposed method performs group update of all variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
+Even though the convergence is not theoretically guaranteed, it converges in all numerical experiments considered in Section \ref{sec-5.2}.
 If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.}

### 2015-03-11 Report/mse_formulation.tex
included antti comments
updated nam_comments without appendix

@@
 \begin{multline} \label{mse-error}
-	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n},
+	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
 \end{multline}
@@
  \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
- + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n},
+ + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
 \end{multline}}
@@
  & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
-& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
+& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
 \end{IEEEeqnarray}
@@
 	& \qquad + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
-	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
+	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
 \end{IEEEeqnarray}}}
@@
 \begin{IEEEeqnarray}{rCl}
-- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n},
+- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}
 \label{mse-lin}
@@
 The optimal transmit precoders for a fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
+The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.
 

### 2015-03-11 Report/sub_channel_wsrm.tex
revised
updated nam_comments without appendix

@@
-The complexity of the \ac{JSFRA} algorithm scales with the number of sub-channels considered.
-In addition, the iterations required for the algorithm convergence increases with the problem size.
-To overcome the complexity, we can decouple the problem to sub-channel specific subproblems by using decomposition approaches presented in \cite{palomar2006tutorial,boyd2011distributed} to design the precoders using primal or dual decomposition.
+The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of the interior point method, which is used to solve the problem, increases quickly with the problem size.
+Thus, we can use the decomposition methods presented in \cite{palomar2006tutorial,boyd2011distributed} to overcome this complexity by designing precoders for each sub-channels independently with minimal information exchange.
 
 As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation only for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
-The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels by adhering to
+The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels as given by
 \begin{equation}
@@
 \end{equation}
-Even though \me{N} sub-channels are present at any given scheduling instant, precoders are solved for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the backlogged packets.
+Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the backlogged packets.
 Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} before solving for the precoders specific to the sub-channel \me{i}.
@@
 \begin{equation}	\label{eqn-weight}
-	Q_{k,i+1} = \max{\left \lbrace Q_k - \sum_{j = 1}^{i} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \right \rbrace }, \; \forall \; k \in \mathcal{U},
+	Q_{k,i+1} = \max \Big ( Q_k - \sum_{j = 1}^{i} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big ) \; \forall \; k \in \mathcal{U}
 \end{equation}
@@
 However, the \ac{SRA} approach provides faster convergence in contrast to the \ac{JSFRA} formulation due to the substantial reduction in the optimization variables for each sub-channel problem.
-As the number of user increases, the \ac{SRA} formulation will be insusceptible to the sub-channel ordering due to the multi-user diversity.
+As the user count increases, the \ac{SRA} formulation will be insusceptible to the sub-channel ordering due to the multi-user diversity.
 %The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}

### 2015-03-11 Report/wsrm_formulation.tex
updated nam_comments without appendix

@@
   & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
-  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-6.4}
+  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber \label{eqn-6.4}
 \end{IEEEeqnarray}
@@
 	&\quad& \beta_{l,k,n} \geq \enoise + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
-	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
+	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
 \end{IEEEeqnarray}
@@
 \begin{equation}
-f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}},
+f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
 \end{equation}
@@
 \text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
-& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{eqn-9.1d} \\
+& \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
 & \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9.1e}
@@
 \mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n}, \IEEEyessubnumber \eqspace \label{opt-rx}
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
 \end{IEEEeqnarray}

### 2015-03-11 Response/response-1.tex
updated nam comments review should be modified

@@
-\textit{In this paper, the authors proposed a traffic aware resource allocation scheme for multi-cell MIMO-OFDM systems, where the precoders at all BSs are chosen to minimize the total user queue deviations.
+In this paper, the authors proposed a traffic aware resource allocation scheme for multi-cell MIMO-OFDM systems, where the precoders at all BSs are chosen to minimize the total user queue deviations.
 The problem is nonconvex and the authors proposed two centralized algorithms based on the successive approximation (SCA) technique to find a stationary point.
-Moreover, several distributed algorithms are also proposed using primal decomposition, alternating directions method of multipliers (ADMM), and decomposition via KKT conditions, respectively.}
+Moreover, several distributed algorithms are also proposed using primal decomposition, alternating directions method of multipliers (ADMM), and decomposition via KKT conditions, respectively.
 
-\textit{Most sections of this paper are well written.
+Most sections of this paper are well written.
 The results and algorithms also seem valid.
@@
 The presentation of the distributed solutions needs significant improvement.
-Analysis and comparison of the signaling overhead and computational complexity between the centralized and distributed algorithms are also necessary to justify the advantages of distributed algorithms.}
+Analysis and comparison of the signaling overhead and computational complexity between the centralized and distributed algorithms are also necessary to justify the advantages of distributed algorithms.
 
-We thank the reviewer for providing valuable and insightful comments. We have address all the comments in the revised manuscript.
+\review{We thank the reviewer for providing valuable and insightful comments.}
 
@@
 
-\cmnt{1} \textit{In Section II.B, please provides more justifications for the problem formulation in (6).
+\cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6).
 For example, the Queue weighted sum rate maximization (Q-WSRM) is throughput optimal, i.e., if there exists a scheme which can make all queues stable, then the Q-WSRM can also do this.
@@
 Is it also throughput optimal?
-}
 
-\resp We thank the reviewer for the valid comment.
+\resp \review{We thank the reviewer for the comment.
 The Q-WSRM scheme and the proposed schemes are all throughput optimal.
-It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aims at minimizing the number of backlogged packets in addition to avoiding the over allocation of the available resources.
-The JSFRA formulation with the \me{\ell_1} objective minimizes the number of backlogged packets in a greedy manner at each instant.
+It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aim at minimizing the number of backlogged packets in addition to avoiding the over allocation of available resources.
+The JSFRA formulation using \me{\ell_1} norm as the objective minimizes the number of backlogged packets in a greedy manner at each instant.
 By increasing the exponent \me{q \rightarrow \infty}, we obtain fair allocation at every transmission instant.
@@
 1, first paragraph.
-The equivalence between the Q-WSRM scheme and the JSFRA problem with \me{\ell_2} can be seen easily when the number queue size increases as outlined in the revised manuscript on page 4, col.
-2, Section III-B starting paragraph.
+The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen easily when the number queue size increases.
+We have clarified this point in the revised manuscript.
+Please refer to the first paragraph in Section III-B.}
 
-\cmnt{2} \textit{Do the proposed solutions based on (6) achieve better average delay performance than the existing solutions?
+\cmnt{2} Do the proposed solutions based on (6) achieve better average delay performance than the existing solutions?
 By the way, in the simulations, you should also add a figure comparing the average delay performance, instead of just comparing the performance metric defined by (6).
-This will better justify the advantage of the proposed solutions.}
+This will better justify the advantage of the proposed solutions.
 
-\resp The proposed algorithm is a function of the number of backlogged packets and the channel conditions of all users in the network.
+\resp \review{The proposed algorithm is a function of the number of backlogged packets and the channel conditions of all users in the network.
 Since the delay is proportional to the average number of backlogged packets in system, the proposed algorithm performs equally good in comparison with the existing Q-WSRM approach.
@@
 In addition, we can also control the delay by changing the exponent used in the objective \me{\ell_q} of the JSFRA problem.
-We considered the residual number of backlogged packets as a performance measure, since we assume only the instantaneous channel state informations and together with the number of backlogged packets, resources can be allocated only for a given instant.
+We considered the residual number of backlogged packets as a performance measure, since we assume only the instantaneous channel state informations and together with the number of backlogged packets, resources can be allocated only for a given instant.}
 
-\cmnt{3} \textit{In Section III.B, the convergence conditions under Algorithm 1 are not clear.
+\cmnt{3} In Section III.B, the convergence conditions under Algorithm 1 are not clear.
 First, you should be more specific about what is the SCA subproblem.
 Do you mean problem (19)?
-Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?}
+Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?
 
-\resp We understand the reviewer's point.
+\resp \review{We understand the reviewer's point.
 We have updated the revised manuscript to discuss the convergence of the centralized algorithm in detail in Appendix B on page 14, col.
@@
 The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D on page 15, col.
-2.
+2.}
 
-\cmnt{4} \textit{It is better to clearly summarize the convergence conditions and results (i.e., does it converge to a stationary point or the optimal solution) for all algorithms in a theorem/proposition.}
+\cmnt{4} It is better to clearly summarize the convergence conditions and results (i.e., does it converge to a stationary point or the optimal solution) for all algorithms in a theorem/proposition.
 
-\resp The discussions on the convergence of the centralized algorithms are provided in Appendix B on page 14, col. 1 and for the distributed algorithms in Section IV-C on page 8, col. 2.
+\resp \review{The discussions on the convergence of the centralized algorithms are provided in Appendix B on page 14, col. 1 and for the distributed algorithms in Section IV-C on page 8, col. 2.}
 
-\cmnt{5} \textit{At the end of Section III, you mentioned that the proposed reduced complexity resource allocation scheme is sensitive to the order in which the subchannels are selected for the optimization problem.
-Please provide a discussion how to choose this order.}
+\cmnt{5} At the end of Section III, you mentioned that the proposed reduced complexity resource allocation scheme is sensitive to the order in which the subchannels are selected for the optimization problem.
+Please provide a discussion how to choose this order.
 
-\resp We understand the reviewer's concern.
+\resp \review{We understand the reviewer's concern.
 Since the algorithm designs the precoders for each sub-channel at a time by using the total number of unserviced packets.
@@
 It is discussed in detail in Section III-D on page 7, col.
-1.
+1.}
 
-\cmnt{6} \textit{In the distributed algorithms, it is not clear what exact information is exchanged between the BSs or between the BSs and users.
+\cmnt{6} In the distributed algorithms, it is not clear what exact information is exchanged between the BSs or between the BSs and users.
 Moreover, the signaling overhead should be analyzed and compared with the centralized solution.
@@
 I don’t think this is acceptable in practice.
-Is the signaling overhead of the distributed algorithm really smaller than the centralized algorithm which only requires exchange the CSI between the BSs for once within each channel coherent time?}
+Is the signaling overhead of the distributed algorithm really smaller than the centralized algorithm which only requires exchange the CSI between the BSs for once within each channel coherent time?
 
-\resp The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require large number of iterations for the convergence.
+\resp \review{The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require large number of iterations for the convergence.
 In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which may not be the same stationary point as when the algorithm is allowed to converge.
@@
 The decentralized schemes are never allowed to converge until the end, it is only important to follow the fading process when \me{J_{\max} = 1}.
-The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of \cite{tolli2011decentralized}, which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13] in the revised manuscript, which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.}
 
-\cmnt{7} \textit{The convergence analysis of the distributed algorithms is not clear.
+\cmnt{7} The convergence analysis of the distributed algorithms is not clear.
 For example, what is the exact condition to ensure the convergence of the distributed algorithms.
-Does the distributed algorithms also converge to a stationary point?}
+Does the distributed algorithms also converge to a stationary point?
 
-\resp We have updated the manuscript to include the discussions on the convergence of the distributed algorithm on page 8, col.
+\resp \review{We have updated the manuscript to include the discussions on the convergence of the distributed algorithm on page 8, col.
 2 last paragraph in Section IV-C.
@@
 The distributed algorithm reaches the same stationary point as of the centralized algorithm if we let the inner loop in Algorithm 2 on page 8, col.
-2 to converge.
+2 to converge.}
 
-\cmnt{8} \textit{I’m totally confused with the ADMM approach in Section IV.A.
+\cmnt{8} I’m totally confused with the ADMM approach in Section IV.A.
 Many notations, such as the local interference vector and consensus interference vector are used without formal definition.
@@
 These questions should be clarified and perhaps you should choose the notation system more carefully.
-For example, in (36), there are 3 similar notations and I don’t know which one is local interference vector and which one is the actual interference vector.}
+For example, in (36), there are 3 similar notations and I don’t know which one is local interference vector and which one is the actual interference vector.
 
-\resp We understand the reviewer's concern.
+\resp \review{We understand the reviewer's concern.
 We have shortened the section on ADMM by citing the relevant earlier work on the distributed implementation of the centralized algorithm for the min power problem [29].
@@
 1.
-It follows the existing literature on the ADMM scheme, which treats the interference as a variable at each BS and the consensus on the interference is achieved upon convergence of the distributed algorithm as discussed in [11].
+It follows the existing literature on the ADMM scheme, which treats the interference as a variable at each BS and the consensus on the interference is achieved upon convergence of the distributed algorithm as discussed in [11].}
 
-\cmnt{9} \textit{In the distributed algorithms, it is not clear what information is available at each node.
+\cmnt{9} In the distributed algorithms, it is not clear what information is available at each node.
 For example, what are your assumption on CSIT (CSI knowledge at each BS) and CSIR (CSI knowledge at each user)?
-How to 2 obtain the information used to perform the required calculation at each node (such as calculating the actual interference, MMSE receiver and the dual variables)?}
+How to 2 obtain the information used to perform the required calculation at each node (such as calculating the actual interference, MMSE receiver and the dual variables)?
 
-\resp We understand the reviewer's concern.
+\resp \review{We understand the reviewer's concern.
 For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
@@
 We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
-We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
+We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.}
 
-\cmnt{10} \textit{Do you have any convergence result for the proposed distributed solution based on the KKT conditions in Section IV.B?
-It seems that the iterative method to solve the KKT conditions is totally heuristic.}
+\cmnt{10} Do you have any convergence result for the proposed distributed solution based on the KKT conditions in Section IV.B?
+It seems that the iterative method to solve the KKT conditions is totally heuristic.
 
-\resp It is true that the KKT conditions are based on the centralized algorithm in (20).
+\resp \review{It is true that the KKT conditions are based on the centralized algorithm in (20).
 It follows the same points as that of the centralized approach if the algorithm is iterated in the same order, \textit{i.e} the dual variables are allowed to converge before the update of the fixed operating point and the receiver.
@@
 It may not be a stationary point of the original nonconvex problem but it is guaranteed to provide better performance in the sum rate compared to the distributed approaches presented in Section IV-A and Section IV-B for the same number of iterations.
-We have provided additional details on the convergence of the KKT based approach in page 10, col 1, last paragraph.
+We have provided additional details on the convergence of the KKT based approach in page 10, col 1, last paragraph.}
 
-\cmnt{11} \textit{Since queue is a dynamic system evolving according to (3), it doesn’t make sense to compare the queue deviations at a given time.
+\cmnt{11} Since queue is a dynamic system evolving according to (3), it doesn’t make sense to compare the queue deviations at a given time.
 You should compare average queue deviations in the simulations.
 Moreover, you should also compare the average delay performance instead of just comparing the performance metric (queue deviations) defined in this paper.
-Using the queue deviations as the performance metric also needs more justification.}
+Using the queue deviations as the performance metric also needs more justification.
 
-\resp We thank the reviewer for raising the critical comment.
+\resp \review{We thank the reviewer for raising the critical comment.
 Since the manuscript is about the precoder design to minimize the total number of backlogged packets in the system, we have provided the convergence behavior of the proposed precoder design formulations for a given time instant.
@@
 Note that we can also prioritize the users by controlling the variable \me{a_k} in (6a) to address the QoS constraints for a particular user, in addition to that, we can also change the objective to \me{\ell_2} and \me{\ell_{\infty}} norm to address the delay and the fairness implicitly.
+}
 
-\cmnt{12} \textit{What is “SRA” in the simulation figures?}
+\cmnt{12} What is “SRA” in the simulation figures?
 
-\resp The \acf{SRA} is updated in the revised manuscript on page 7, col. 1, Section III-D.
+\resp \review{The \acf{SRA} is updated in the revised manuscript on page 7, col. 1, Section III-D.}
 
-\cmnt{13} \textit{In the discussion for Fig.
+\cmnt{13} In the discussion for Fig.
 1, you mentioned that JSFRA converge to the optimal point, and all algorithms are Pareto-optimal.
-Since the problem is non-convex, why these algorithm can find optimal solution or Paretooptimal point?}
+Since the problem is non-convex, why these algorithm can find optimal solution or Paretooptimal point?
 
-\resp We thank the reviewer for pointing out the mistake in the text.
+\resp \review{We thank the reviewer for pointing out the mistake in the text.
 Since the problem is nonconvex, the JSFRA formulation can find a local optimal point upon convergence.
@@
 We have removed the statement mentioning the pareto-optimal solutions in the discussions on Fig.
-1 in the revised manuscript.
+1 in the revised manuscript.}
 
 \end{itemize}
-
-\bibliographystyle{./../Styles/IEEEtran}
-\bibliography{./../Library/kirja_survey}

### 2015-03-11 Response/response-2.tex
updated nam comments review should be modified

--- 2015-03-03 Response/response-2.tex
@@
+\review{We would like to thank the reviewer for providing valuable comments.}
+
 \begin{itemize}
@@
 
-\resp We understand the reviewer's concern.
+\resp \review{We understand the reviewer's concern.
 The reformulation is required, since the SINR expression in (2) cannot be handled directly in the problem defined in (6).
 Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), which are the under estimator to the original problem in (6).
+Since the inequalities are used to replace the equality constraint, the objective could be improved by the iterative algorithm and the equality will be achieved after the convergence, thereby having one-to-one mapping at the final solution.
 We have updated the manuscript to include the details for better clarity on page 5, col.
-1, first paragraph.
+1, first paragraph.}
 
@@
 
-\resp Please note that the objective function is convex, which can be verified by writing the difference function inside the norm operator in epigraph form.
-Since the problem in (16) is jointly nonconvex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
+\resp \review{Please note that the objective function is convex, which can be verified by writing the difference function inside the norm operator in epigraph form.
+Since the problem in (16) is not jointly convex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
 Even after fixing \me{\mvec{w}{l,k,n}} as constant, the problem in (16) is nonconvex due to the DC constraint (16b), which is handled by the first order relaxation around some fixed operating point.
@@
 We have updated the manuscript to illustrate this clearly on page 5, col.
-2, first paragraph.
+2, first paragraph.}
 
@@
 
-\resp We thank the reviewer for the pointing out the flaw in the text.
-We have removed the statement on block coordinate descent method with the AO approach.
-Since the problem is nonconvex, using this approach, we can find a local optima of the original nonconvex problem.
-The manuscript is modified to include the updated statement on page 5, col.
+\resp \review{We thank the reviewer for the pointing out the flaw in the text.
+We have removed the incorrect statement on block coordinate descent method with the AO approach on page 5, col.
 1, second paragraph.
+Indeed, due to the coupling of the transmit and the receive precoder variables, we cannot use the standard block coordinate descent method proof for the convergence of the proposed algorithm as pointed out by the reviewer.
+We have provided a completely rewritten convergence proof on Appendix B, page no.
+14, col.
+1.
+}
 
@@
 
-\resp We understand the reviewer's concern.
-We have provided the proof on the convergence of the centralized algorithm on Appendix B.
-We apologize for the inappropriate reference cited in the original manuscript.
+\resp \review{We apologize for the inappropriate reference cited in the original manuscript.
+We have provided a completely rewritten proof on the convergence of the centralized algorithm on Appendix B.}
 
@@
 
-\resp We agree with the reviewer's comment. We have provided the updated proof for the convergence of the centralized algorithm on Appendix B in the revised manuscript.
+\resp \review{We agree with the reviewer's comment. We have provided the updated proof for the convergence of the centralized algorithm on Appendix B in the revised manuscript.}
 
@@
 
-\resp We have removed the inappropriate citation of the references.
+\resp \review{We have removed the inappropriate citation of the references.}
 
@@
 
-\resp We understand the issue raised by the reviewer.
+\resp \review{We understand the issue raised by the reviewer.
 Please note that the distributed algorithm is performed for the convex subproblem presented in (20) and (28).
@@
 These are discussed in Section IV-C on page 8, col.
-2, last paragraph.
+2, last paragraph.}
 
@@
 
-\resp We understand the reviewer's concern.
+\resp \review{We understand the reviewer's concern.
 We have included the sub-channel wise resource allocation or (SRA) scheme in Section III-D for the completeness.
 It is presented in the manuscript as an alternative suboptimal approach to perform sub-channel wise distributed precoder design by the centralized controller.
-We have updated the manuscript with more details for better understanding.
+We have updated the manuscript with more details for better understanding.}
 
@@
 
-\resp We have included the information regarding the norm used for the simulation in the figure captions. It is updated for Fig. 1 and Fig. 2.
+\resp \review{We have included the information regarding the norm used for the simulation in the figure captions. It is updated for Fig. 1 and Fig. 2.}
 
@@
 
-\resp We understand the reviewer's concern.
+\resp \review{We understand the reviewer's concern.
 We have updated the manuscript to include the descriptions in the text to refer the legends used in the figures.
 Table 1 is provided for the purpose of insight, since it deals with the SISO scenario with 3 sub-channels and 3 users.
+}
 
@@
 
-\resp We thank the reviewer for pointing out the issue in the system description for the figures.
+\resp \review{We thank the reviewer for pointing out the issue in the system description for the figures.
 Please note that the simulation scenario is different for Fig.
@@
 1, lines 3-6 in Section V-B and page 12, col.
-2, third paragraph in Section V-B.
+2, third paragraph in Section V-B.}
 

### 2015-03-11 Response/response-3.tex
final_draft
updated nam comments review should be modified

--- 2015-03-03 Response/response-3.tex
@@
+This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods.
+This is an interesting and important topic.
+
+\review{We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helpful in improving the manuscript.}
+
 \begin{itemize}
 
-\cmnt{1} This manuscript focuses on the beamforming and scheduling optimization for IBC MIMO-OFDM system, including the centralized and decentralized optimization methods.
-This is an interesting and important topic.
+\cmnt{1} The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.
 
-\resp We thank the reviewer for reading the manuscript and providing valuable comments.
+\resp \review{Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression and thus \me{t_k} is not a variable.
+However, in the MSE formulation, we have explicitly stated the optimization variable \me{t_k}, since it is present in the DC constraint (27).}
 
-\cmnt{2} The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.
-
-\resp Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression and thus \me{t_k} is not a variable.
-However, in the MSE formulation, we have explicitly stated the optimization variable \me{t_k}, since it is present in the DC constraint (27).
-
-\cmnt{3} The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5).
+\cmnt{2} The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5).
 This is not obvious.
@@
 
-\resp We thank the reviewer for the insightful comment.
+\resp \review{We thank the reviewer for the insightful comment.
 We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under estimator for the SINR expression in (2).
@@
 In this case, we can use a regularization term with the total power in the objective to obtain an unique solution.
-We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-C.
+We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-D.}
 
-\cmnt{4} The solution in (21) is obtianed for MMSE, i.e.
+\cmnt{3} The solution in (21) is obtianed for MMSE, i.e.
 for 2-norm(q=2).
@@
 
-\resp We thank the reviewer for the critical comment.
+\resp \review{We thank the reviewer for the critical comment.
 Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
@@
 We have modified the text to included this information in page 5, col.
-2, last paragraph.
+2, last paragraph.}
 
-\cmnt{5} The convergence proof need to be rigorous.
+\cmnt{4} The convergence proof need to be rigorous.
 The inequality of (23a) is opposite to the reference [28].
@@
 
-\resp We agree with the reviewer.
+\resp \review{We agree with the reviewer.
 We have updated the manuscript to discuss the convergence proof in a rigorous manner in Appendix B.
 The uniqueness is also justified implicitly by the linear approximation performed on the DC constraint (16b), which makes the transmit precoders to be susceptible to the phase rotation.
-The uniqueness discussions are presented in Appendix B-C.
+The uniqueness discussions are presented in Appendix B-D.}
 
-\cmnt{6} (25) is generally wrong.
+\cmnt{5} (25) is generally wrong.
 (25) only holds when the MSE is minimized(by MMSE receiver) and the snr is the optimized(which is obtained by general eignvalue decompostion).
@@
 
-\resp We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on MMSE objective.
+\resp \review{We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on MMSE objective.
 In our MSE reformulation solution, we have used the MMSE receiver irrespective of the \me{\ell_q} norm used in the objective.
@@
 We have updated the manuscript to include this comments on page 6, col.
-2, line 10-13.
+2, line 10-13.}
 
-\cmnt{7} For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed.
+\cmnt{6} For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed.
 1.
@@
 
-\resp We agree with the reviewer's concern.
+\resp \review{We agree with the reviewer's concern.
 We have included the reference [11] that discusses on the valid choices of the step size parameter for ADMM.
@@
 It is updated in the manuscript on page 8, col.
-2, line 4-8.
+2, line 4-8.}
 

### 2015-03-11 Response/response-4.tex
final_draft
updated nam comments review should be modified

@@
-First, we thank the reviewer for providing valuable and insightful comments. The comments are really helpful in improving the manuscript.
+\review{ First, we thank the reviewer for providing valuable and insightful comments. The comments are really helpful in improving the manuscript.}
 
@@
 
-\cmnt{1} \textit{First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method.
+\cmnt{1} {First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method.
 "The SCA method" is often referred to, but never really defined or referenced.
@@
 
-\resp We understand the reviewer's concern on the lack of rigorous convergence proof for the JSFRA approach.
+\resp \review{We understand the reviewer's concern on the lack of rigorous convergence proof for the JSFRA approach.
 We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on page 14.
 We have included the reference suggested by the reviewer in [34].
+}
 
-\cmnt{2} \textit{Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates.
+\cmnt{2} {Second, the optimization problems formulated only depend on $Q_k$, the current levels of backlogged packets, and not on the arrival rates.
 This is due to how the conditional Lyapunov drift is minimized.
-This approach completely removes the queue dynamics from the optimization problem, essentially leading to greedy one-shot optimization in 7
-every time instant.
+This approach completely removes the queue dynamics from the optimization problem, essentially leading to greedy one-shot optimization in every time instant.
 The framework would be more interesting if some sort of optimization (or tracking) is performed over several time instants, rather than the one-shot approach that is currently used for the JSFRA algorithms.
@@
 
-\resp We thank the reviewer for the useful suggestion.
+\resp \review{We thank the reviewer for the useful suggestion.
 In this paper, we proposed the precoder design to minimize the number of backlogged packets in the system at a given time.
@@
 Plots comparing the average number of backlogged packets for different schemes at each instant and the number of queued packets remained in the system after each transmission instant are provided in Fig.
-4.
+4.}
 
-\cmnt{3} \textit{Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results.
+\cmnt{3} {Third, the distributed methods (at least the primal decomposition and ADMM) seem to be fairly straight-forward applications of existing results.
 This reviewer recommends spending more space on the convergence, than on the description of the distributed techniques.
@@
 
-\resp We agree with the reviewer's comment.
+\resp \review{We agree with the reviewer's comment.
 We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Section IV-C page 8.
@@
 2 last paragraph.
-We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
+We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.}
 
-\cmnt{4} \textit{Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier.
+\cmnt{4} {Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier.
 This could easily be clarified.}
 
-\resp We agree with the reviewer's point. We have included the note on the space-frequency terminology in the introduction section on page 2, col. 2, line 2-4.
+\resp \review{We agree with the reviewer's point. We have included the note on the space-frequency terminology in the introduction section on page 2, col. 2, line 2-4.}
 
-\cmnt{5} \textit{Please see the itemized questions}
+\cmnt{5} {Please see the itemized questions}
 
@@
 
-\cmnts{a} - \textit{p. 1, col. 1, row 42: "userss"}
+\cmnts{a} - {p. 1, col. 1, row 42: "userss"}
 
-\resp Corrected in the revised manuscript in Section I on page 1, col. 1, line 2.
+\resp \review{Corrected in the revised manuscript in Section I on page 1, col. 1, line 2.}
 
-\cmnts{b} - \textit{p.
+\cmnts{b} - {p.
 1, col.
@@
 
-\resp We thank the reviewer for highlighting the important point. We have included the statement in the revised manuscript on Section I, page 1, col. 2, line 5-14.
+\resp \review{We thank the reviewer for highlighting the important point. We have included the statement in the revised manuscript on Section I, page 1, col. 2, line 5-14.}
 
-\cmnts{c} - \textit{p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?}
+\cmnts{c} - {p. 1, col. 2, row 33: Which chapter in [2] is referred to? With a quick look-through of the table of contents, I can't find and chapter or section treating the SCA method?}
 
-\resp We apologize for the wrong reference. We have updated the manuscript to include the proper reference on SCA with [2,3,7,25,26,35].
+\resp \review{We apologize for the wrong reference. We have updated the manuscript to include the proper reference on SCA with [2,3,7,25,26,35].}
 
-\cmnts{d} - \textit{p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead}
+\cmnts{d} - {p. 2, col. 2, row 36: Write $\text{rank}(.)$ and $\min$ instead}
 
-\resp We have updated the revised manuscript with the reviewer suggestions on page 2, col. 2, second paragraph in Section II.
+\resp \review{We have updated the revised manuscript with the reviewer suggestions on page 2, col. 2, second paragraph in Section II.}
 
-\cmnts{e} - \textit{p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here}
+\cmnts{e} - {p. 3, col. 1, row 26: It would be more clear to explicitly write out the dependence of $\mathbf{M}$ and $\mathbf{W}$ in $\tilde{v}$ here}
 
-\resp We removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid confusion as suggested by the reviewer.
+\resp \review{We removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid confusion as suggested by the reviewer.}
 
-\cmnts{f} - \textit{p.
+\cmnts{f} - {p.
 3, col.
@@
 
-\resp We thank the reviewer for pointing out the confusion. We have removed the word "combinatorial" from the text to avoid confusion in page 3, col. 2, initial sentence in Section III.
+\resp \review{We thank the reviewer for pointing out the confusion. We have removed the word "combinatorial" from the text to avoid confusion in page 3, col. 2, initial sentence in Section III.}
 
-\cmnts{g} - \textit{p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.}
+\cmnts{g} - {p. 4, col. 2, row 40: "In fact, (5) provides similar expression of ..." This sentence is very hard to understand.}
 
-\resp We have rephrased the sentence to avoid difficulty in the understanding. The manuscript is updated with the revised text on page 4, col. 2, first paragraph in Section III.B.
+\resp \review{We have rephrased the sentence to avoid difficulty in the understanding. The manuscript is updated with the revised text on page 4, col. 2, first paragraph in Section III.B.}
 
-\cmnts{h} - \textit{(16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem.
-There is hardly any spaced saved by referring back to (6b).}
+\cmnts{h} - {(16d): suggest your write out the power constraints here, in order to be faster be able to interpret the optimization problem. There is hardly any spaced saved by referring back to (6b).}
 
-\resp We have updated the manuscript with the explicit power constraint in (16d) as
+\resp \review{We have updated the manuscript with the explicit power constraint in (16d) as
 \[\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b\]
-in page 5, col. 1.
+in page 5, col. 1.}
 
-\cmnts{i} - \textit{p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).}
+\cmnts{i} - {p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).}
 
-\resp We have included the NP-hardness of the proposed solution by modeling the current problem to solve the \ac{WSRM} formulation, which is known to be NP-hard in page 5, col.
-1, last sentence in Section III-B third paragraph.
+\resp \review{We have included the NP-hardness of the proposed solution by modeling the current problem to solve the \ac{WSRM} formulation, which is known to be NP-hard in page 5, col.
+1, last sentence in Section III-B third paragraph.}
 
-\cmnts{j} - \textit{p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.}
+\cmnts{j} - {p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.}
 
-\resp We have removed the sentence mentioning SCA method. We have updated the manuscript to discuss this as SCA approach in pagt 5, col. 1 last paragraph.
+\resp \review{We have removed the sentence mentioning SCA method. We have updated the manuscript to discuss this as SCA approach in pagt 5, col. 1 last paragraph.}
 
-\cmnts{k} - \textit{p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??}
+\cmnts{k} - {p. 5, col. 2, row 31: Here is a case where it makes sense to reference earlier optimization constraints. However, are (19d) and (18) not the same??}
 
-\resp We thank the reviewer for pointing out the mistake.
+\resp \review{We thank the reviewer for pointing out the mistake.
 We have included all the constraints except the linearization constraint in (20) which is (19) in the original manuscript.
@@
 We have removed this double reference in page 5, col.
-2, equation (20).
+2, equation (20).}
 
-\cmnts{l} - \textit{p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).}
+\cmnts{l} - {p. 5, col. 2, row 51: Slightly confusing with the notation between the iterates in (21b) and the MMSE filter in (22b).}
 
-\resp We have updated the manuscript to avoid the ambiguity in the representation of the optimal and the MMSE receiver.
-The optimal receiver is denoted by \me{\mvec{w}{l,k,n}^{o}} in (22) and the MMSE receiver by \me{\mvec{w}{l,k,n}} in (23).
+\resp \review{We have updated the manuscript to avoid the ambiguity in the representation of the optimal and the MMSE receiver.
+The optimal receiver is denoted by \me{\mvec{w}{l,k,n}^{o}} in (22) and the MMSE receiver by \me{\mvec{w}{l,k,n}} in (23).}
 
-\cmnts{m} - \textit{p.
+\cmnts{m} - {p.
 6, col.
@@
 
-\resp We thank the reviewer for providing the valid comment.
+\resp \review{We thank the reviewer for providing the valid comment.
 We have updated the manuscript to include this discussion in page 6, col 1, lines 3-6.
 The performance remains the same and the convergence rate is not affected by this scaling, which can be seen from Fig.
-1 comparing the precoder convergence using the optimal and the MMSE receiver for the JSFRA scheme with \me{\ell_1} norm.
+1 comparing the precoder convergence using the optimal and the MMSE receiver for the JSFRA scheme with \me{\ell_1} norm.}
 
-\cmnts{n} - \textit{p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?}
+\cmnts{n} - {p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?}
 
-\resp To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point.
+\resp \review{To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point.
 Since the operating point happens to be the optimal solution from the earlier iteration, the optimal point of the previous iterations is also present in the current feasible set.
 Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective.
-It is explained in detail in Appendix B on the convergence analysis of the centralized algorithm.
+It is explained in detail in Appendix B on the convergence analysis of the centralized algorithm.}
 
-\cmnts{o} - \textit{p.
+\cmnts{o} - {p.
 7, col.
@@
 
-\resp We thank the reviewer for the critical comment.
+\resp \review{We thank the reviewer for the critical comment.
 It is true that the convex problem does not need to have a unique solution in general.
@@
 In this case, we can use a regularization term with the total power in the objective to obtain an unique solution.
-We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-C.
-It makes the objective strictly convex, therefore, it has a unique minimum.
+We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-D.
+It makes the objective strictly convex, therefore, it has a unique minimum.}
 
-\cmnts{p} - \textit{Table 1: "backpreassure"}
+\cmnts{p} - {Table 1: "backpreassure"}
 
-\resp It is updated in the manuscript on page 11, Table 1.
+\resp \review{It is updated in the manuscript on page 11, Table 1.}
 
-\cmnts{q} - \textit{p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.}
+\cmnts{q} - {p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.}
 
-\resp We agree with the reviewer. We have modified the manuscript accordingly by replacing it with the singular form.
+\resp \review{We agree with the reviewer. We have modified the manuscript accordingly by replacing it with the singular form.}
 

### 2015-03-11 Response/reviewer_response.tex
revised
updated nam comments review should be modified

@@
 \usepackage{amsmath,amssymb}
-\usepackage{acronym,etoolbox}
+\usepackage{acronym,etoolbox,color}
 \usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}
 
-\newcommand{\cmnt}[1]{\item[\textbf{Q}-(#1)]}
+\newcommand{\cmnt}[1]{\item[\textbf{Q}#1]}
 \newcommand{\cmnts}[1]{\item[(#1)]}
@@
 
-\title{Response for Reviewer Comments}
+\title{Response for the Reviewer Comments}
 
@@
 
-We would like to thank the associate editor and the reviewers for the valuable comments provided for the manuscript.
-We have written the response for the reviewer comments in line in this report.
-The changes are addressed in the revised manuscript as well by using blue color italic fonts to discriminate the revision from the actual text in the manuscript.
+The authors would like to thank the editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality.
+Based on the comments, we have made several major revisions to the paper, following the suggestions of the reviewers.
+In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors.
+Unless otherwise stated, all the numbered items (figures, equations, references, etc) in this response letter refer to the revised manuscript.
+The revisions in the revised manuscript are highlighted using blue color and the authors responses are also presented in blue color text.
 
 \newpage
-\section*{Response for Reviewer - \me{1}}
+\section*{Response to Reviewer - \me{1}'s Comments}
 \input{response-1}
@@
 \newpage
-\section*{Response for Reviewer - \me{2}}
+\section*{Response to Reviewer - \me{2}'s Comments}
 \input{response-2}
@@
 \newpage
-\section*{Response for Reviewer - \me{3}}
+\section*{Response to Reviewer - \me{3}'s Comments}
 \input{response-3}
@@
 \newpage
-\section*{Response for Reviewer - \me{4}}
+\section*{Response to Reviewer - \me{4}'s Comments}
 \input{response-4}

### 2015-03-11 Report/convergence_centralized.tex
updated nam comments review should be modified

@@
 Using this, we can show the monotonicity of the objective value sequence as
-\begin{equation*}
+\begin{equation}
 f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}).
-\end{equation*}
+\end{equation}
 The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
@@
 where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using \cite{marks1978technical}, we can show that the feasible point  \me{(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})}, which is the minimizer in its local neighborhood, is a stationary point of \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+Using the discussions in \cite{marks1978technical}, we can show that the feasible point  \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\}}, which is the minimizer in its local neighborhood, is a stationary point of \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
 The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires \me{\mbf{0}^\tran \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions, where \me{\partial f_0(\mz_{\ast})} denotes the subdifferential set.
-Using these arguments, we can show that the \ac{JSFRA} schemes reaches a stationary point of the original nonconvex problem.
+Using the above arguments, we can show that the \ac{JSFRA} schemes reaches a stationary point of the original nonconvex problem.

### 2015-03-11 Report/ieee_journal.tex
final_1
final_version_for Antti, Nam, and Markku
updated nam_comments without appendix
updated nam comments review should be modified

@@
 
-\usepackage[section]{placeins}
 \usepackage{amsmath,amssymb}
@@
 \togglefalse{enable_dist_fig}
-\togglefalse{includereview}
 
@@
 	\IEEEauthorblockN{Ganesh Venkatraman$^\dagger$ \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
-Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli$^\dagger$ \IEEEmembership{Senior Member,~IEEE}, Le-Nam Tran$^\ddagger$ \IEEEmembership{Member,~IEEE}, and Markku Juntti$^\dagger$ \IEEEmembership{Senior Member,~IEEE}}\thanks{
+Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli$^\dagger$ \IEEEmembership{Senior Member,~IEEE}, Markku Juntti$^\dagger$ \IEEEmembership{Senior Member,~IEEE}, and Le-Nam Tran$^\ddagger$ \IEEEmembership{Member,~IEEE}}\thanks{
 	$^\dagger$The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{$^\ddagger$The author is with the Department of Electronic Engineering, Maynooth University, Maynooth, Co.
-Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie}}
+Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie)}}
 
 \begin{document}
-
-\iftoggle{includereview}{
-\newpage
-\onecolumn
-\doublespacing
-\section{Response to reviewer comments}
-\input{review_comments}
-\twocolumn
-\newpage
-\singlespacing
-\setcounter{page}{1}
-}
 
@@
 
-\subsection{Convergence Analysis for Distributed Algorithms} \label{sec-dist-conv}
-\review{\input{convergence_distributed}}
-
 \subsection{Decomposition via \ac{KKT} Conditions for \ac{MSE} Formulation} \label{sec-4.3}
@@
 
-\subsection{Distributed Solutions}
+\subsection{Distributed Solutions} \label{sec-5.2}
 \input{simulation_distributed}
 
-\subsection{Queue Deviations over Multiple Transmission Slots} \label{time-correlated}
+\subsection{Queuing Analysis over Multiple Transmission Slots} \label{time-correlated}
 \review{\input{time_correlated}}
@@
 
+\section{Convergence Proof for Distributed Algorithms} \label{sec-dist-conv}
+\review{\input{convergence_distributed}}
+
 \section{\ac{KKT} conditions for \ac{MSE} approach} \label{a-1}

### 2015-03-11 Report/joint_wsrm_formulation.tex
halfcooked
updated nam_comments without appendix
updated nam comments review should be modified

@@
 \begin{equation}
-\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i),
+\mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \, \sum_{k \in \mc{U}} Q_k^2(i)
 \end{equation}
@@
 \begin{equation}
-\leq \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) },
+\leq \sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} + \sum_{k \in \mc{U}} Q_k(i) \set{ \lambda_k(i) - t_k(i) }
 \label{drift-exp}
@@
 \underset{\substack{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
-	\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \text{tr} \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b.
+\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \fall b.
 \IEEEyessubnumber \eqspace \label{eqn-3.1.3}
@@
 
-In order to avoid the excessive  allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}.
-The rate constrained version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system, is given by \label{q_gen_sum-1} with the additional constraint
+To avoid excessive allocation of the resources, we include an additional rate constraint \me{t_k \leq Q_k} to address \me{[x]^+} operation in \eqref{eqn-2a}.
+The rate constrained version of the \ac{Q-WSRM}, denoted by \ac{Q-WSRME} problem for a cellular system, is given by \label{q_gen_sum-1} with the additional constraints as
 \begin{IEEEeqnarray}{rCl} \label{eqn-3.1.4}
-\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k, \fall k \in \mc{U},
+\sum_{n=1}^N \sum_{l = 1}^L \log_2(1 + \gamma_{l,k,n}) \leq Q_k \: \fall k \in \mc{U}
 \end{IEEEeqnarray}

### 2015-03-11 Report/kkt_mse_approach.tex
updated nam comments review should be modified

@@
 \item when the exponent \me{q} is even, or
-\item when the number of backlogged packets of each user is large enough, \textit{i.e}, \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator, which means also ignoring the queues in the first place as well.
+\item when the number of backlogged packets of each user is large enough, \textit{i.e}, \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator and queues in the first place as well.
 \end{itemize}
@@
 
-The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, which are obtained by the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness conditions, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}.
+The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, obtained by the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}.
 Upon solving, we obtain the iterative solution as
@@
 \review{At each iteration, the dual variables \me{\alpha^{(i)}} are linearly interpolated with any point between the fixed iterate \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} using a step size \me{\rho \in (0,1)}.
-The choice of \me{\rho} depends on the system model and it affects the convergence behavior of the algorithm.
-It is used to reduce the oscillations in the objective function when \me{\sigma^{(i)}} is negative due to over allocation.}
+The choice of \me{\rho} depends on the system model and it affects the convergence behavior.
+It reduces the oscillations in the objective function when \me{\sigma^{(i)}} is negative due to over allocation.}
 

### 2015-03-11 Report/time_correlated.tex
updated nam comments review should be modified

@@
 \ref{fig-time-analysis} highlights the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally good compared to other objectives when the system is in the stable region.
-On contrary, in the unstable region, the performance is inferior, since the fair allocation is not effective when the number of backlogged packets is significantly more for all users.
+On contrary, the performance is inferior in the unstable region, since the fair allocation is not effective when the number of backlogged packets is large for all users.

### 2015-03-12 Response/response-1.tex
included nam's comments

@@
 
-\resp \review{The proposed algorithm is a function of the number of backlogged packets and the channel conditions of all users in the network.
-Since the delay is proportional to the average number of backlogged packets in system, the proposed algorithm performs equally good in comparison with the existing Q-WSRM approach.
-It can be easily verified by the equivalence between the \me{\ell_2} norm JSFRA and the Q-WSRM scheme on page 4, col.
-2, Section III-B starting paragraph.
-We have also provided the performance of different JSFRA algorithm and Q-WSRM scheme based on the average number of backlogged packets in the system over multiple transmission slots by varying the average number arrivals for all users in the system in Fig.
-4 on page 13.
-We can still control the delay behavior by controlling the priority factor \me{a_k} in (6a), which affects the resource allocation.
-For example, if we consider a VOIP transmission, the delay requirements are stringent and it can be achieved by increasing the priority factor \me{a_k} in the current formulation.
-In addition, we can also control the delay by changing the exponent used in the objective \me{\ell_q} of the JSFRA problem.
-We considered the residual number of backlogged packets as a performance measure, since we assume only the instantaneous channel state informations and together with the number of backlogged packets, resources can be allocated only for a given instant.}
+\resp \review{
+	\begin{itemize}
+		\item In the previous manuscript, we primarily focused on evaluating the performance of all schemes by comparing the total number of backlogged packets retained in the system after the current transmission.
+Since the delay is proportional to the average number of backlogged packets in the system, this implies that the delay performance was indirectly evaluated in the previous manuscript.
+In addition, the average delay of a particular user can be reduced by controlling the priority factor \me{a_k} in (6a), which affects the resource allocation.
+We can also control the delay by changing the exponent used in the objective \me{\ell_q} of the JSFRA problem as discussed in bullet points before Section III.
+		\item We considered the residual number of backlogged packets as a performance measure, since we assume only the instantaneous channel state informations and together with the number of backlogged packets, resources can be allocated only for a given instant.
+		\item We agree with the reviewer that the delay should be compared directly to justify the advantages of the proposed schemes.
+In this regard, we have included a new figure to clarify this point.
+Please refer to Fig.
+4 and the associated text in Section V-C.
+As can be seen, the proposed methods outperforms the existing schemes.
+	\end{itemize}
+	}
 
@@
 
-\resp \review{We understand the reviewer's point.
-We have updated the revised manuscript to discuss the convergence of the centralized algorithm in detail in Appendix B on page 14, col.
-1.
-The discussions are provided for the convergence of the iterative algorithm.
-The uniqueness of the convex subproblem (20) can be guaranteed when the objective is non-zero for all coordinating BSs in the precoder design.
-It is due to the linear constraint on the transmit precoders in (19), which is susceptible to the transmit precoder phase rotations.
+\resp \review {
+	\begin{itemize}
+	\item We thank the reviewer for the comment.
+The convergence analysis has been clearly written in the revised manuscript in Appendix B.
+The discussions are provided for the convergence of the iterative Algorithm 1, \textit{i.e}, the problem defined in (16).
+	\item The uniqueness of the convex subproblem (20) can be guaranteed by the linear constraint on the transmit precoders in (19), which is susceptible to the transmit precoder phase rotations.
 On the other hand, the constraint in (16b) is not, since the precoder variable is inside the absolute value operator.
 Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16).
-The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D on page 15, col.
-2.}
+The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D.
+	\end{itemize}
+}
 
@@
 
-\resp \review{The discussions on the convergence of the centralized algorithms are provided in Appendix B on page 14, col. 1 and for the distributed algorithms in Section IV-C on page 8, col. 2.}
+\resp \review{The discussions on the convergence of the centralized algorithms are provided in Appendix B and for the distributed algorithms in Appendix C.
+The discussion on the convergence to a stationary point is presented in Appendix B-E.}
 
@@
 Now, the number of backlogged packets for the \me{\ith{j+1}} sub-channel is given by
-\[Q_k - \sum_{i=1}^j \sum_{l=1}^L t_{l,k,i}\].
+\[Q_k - \sum_{i=1}^j \sum_{l=1}^L t_{l,k,i}.\]
 Since it depends on the rates of the already completed sub-channels \me{\{1,2,\dotsc,j\}}, it is susceptible to the ordering used to determine the precoders in each sub-channels.
-It is discussed in detail in Section III-D on page 7, col.
-1.}
+It is discussed in detail in Section III-D.}
 
@@
 
-\resp \review{The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require large number of iterations for the convergence.
-In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which may not be the same stationary point as when the algorithm is allowed to converge.
-The number of ADMM or primal updates are controlled by the parameter \me{J_{\max}} in the Algorithm 2.
-In practice, we can combine the ADMM or primal update, receiver update and the SCA update all at once, \textit{i.e}, \me{J_{\max} = 1} to minimize the overhead in the backhaul signaling and to speed up the convergence.
-To this end, we have provided a practical scheme in Section IV-D on page 9, col.
-1.
+\resp \review{
+	\begin{itemize}
+		\item The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require large number of iterations for the convergence.
+In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which may not be the same as when the algorithm is allowed to converge.
+The number of ADMM or primal updates can be controlled by \me{J_{\max}} in the Algorithm 2.
+		\item Note that the size of the channel state information depends on the number of transmit antennas.
+Thus exchanging channels is not efficient when the number of transmit antennas are large.
+On the other hand, the amount of exchanging interference vector only depends on the number of base stations.
+In practice, we can limit the primal or ADMM update for few iterations, then the distributed algorithms are still be efficient.
+		\item To this end, we have provided a practical scheme in Section IV-D.
 Note that in the time-correlated case, it is often also enough to update the precoders once per radio frame.
 The decentralized schemes are never allowed to converge until the end, it is only important to follow the fading process when \me{J_{\max} = 1}.
-The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13] in the revised manuscript, which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.}
+The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13] in the revised manuscript, which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+	\end{itemize}
+	}
 
@@
 
-\resp \review{We have updated the manuscript to include the discussions on the convergence of the distributed algorithm on page 8, col.
-2 last paragraph in Section IV-C.
-The condition for the convergence of the distributed algorithm is that when the dual variable updates are not significant or when the decrease in the objective value is below some threshold.
-The distributed algorithm reaches the same stationary point as of the centralized algorithm if we let the inner loop in Algorithm 2 on page 8, col.
-2 to converge.}
+\resp \review{We have updated the manuscript to include the discussions on the convergence of the distributed algorithm in Appendix C.
+The distributed algorithm attains the same stationary point as of the centralized algorithm if we let the inner loop in Algorithm 2 to converge.}
 
@@
 
-\resp \review{We understand the reviewer's concern.
-We have shortened the section on ADMM by citing the relevant earlier work on the distributed implementation of the centralized algorithm for the min power problem [29].
-We have rewritten the distributed algorithms in Section IV-A and Section IV-B.
-The variables are discussed in Section IV on page 8, col.
-1.
-It follows the existing literature on the ADMM scheme, which treats the interference as a variable at each BS and the consensus on the interference is achieved upon convergence of the distributed algorithm as discussed in [11].}
+\resp \review{
+	\begin{itemize}
+		\item We have defined those variables in the revised manuscript on Section VI-B
+		\item Since the coupling between the distributed precoder designs are the interference between the BSs and the users, in ADMM approach, the interference is treated as a local variable, which can be included in the precoder design optimization problem for each coordinating BSs.
+This is treated as a local (but not the actual interference) variable for a specific BS.
+Since the actual interference caused is different, the consensus has to be made between the local interference variable maintained at each BS with the global consensus interference variable, which is nothing but the average between the corresponding BSs interference.
+These discussions are made in the revised manuscript in Section IV-B.
+For further details, please refer to the Boyd's paper in [11], which discusses exclusively about the ADMM approach.
+		\item We have revised the manuscript to avoid the subscript confusions in the ADMM approach. 
+	\end{itemize}}
 
@@
 To update the MMSE receiver, the equivalent channel for the \me{\ith{k}} user \me{\mbf{H}_{b,k,n} \mvec{m}{l,k^\prime,n}, \forall k^\prime \in \mc{U}_b, \forall b \in \mc{B}} is obtained from the BSs through user specific downlink precoded pilots.
-We have included the information on what each network entity knows in page 7, col.
-2 last paragraph.
-We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
+We have included the information on what each network entity knows in the paragraph after (36).
 We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.}
@@
 
-\resp \review{It is true that the KKT conditions are based on the centralized algorithm in (20).
-It follows the same points as that of the centralized approach if the algorithm is iterated in the same order, \textit{i.e} the dual variables are allowed to converge before the update of the fixed operating point and the receiver.
+\resp \review{
+	\begin{itemize}
+		\item The heuristic part is that instead of updating the involved variables sequentially, we allow all the variables to be updated at the same time.
+Due to this idea, the convergence is not always guaranteed as in standard methods, but we have observed significantly improved convergence results in all numerical examples.
+		\item It follows the same points as that of the centralized approach if the algorithm is iterated in the same order, \textit{i.e} the dual variables are allowed to converge before the update of the fixed operating point and the receiver.
 Here instead we perform the update of the transmit precoders, receive beamformers and the dual variables all at once in each iteration.
 Thus, we sacrifice the formal convergence for the improved speed of convergence.
-It may not be a stationary point of the original nonconvex problem but it is guaranteed to provide better performance in the sum rate compared to the distributed approaches presented in Section IV-A and Section IV-B for the same number of iterations.
-We have provided additional details on the convergence of the KKT based approach in page 10, col 1, last paragraph.}
+We have provided additional details on the convergence of the KKT based approach in page 10, col 1, last paragraph.
+	\end{itemize}}
 
@@
 
-\resp \review{We thank the reviewer for raising the critical comment.
-Since the manuscript is about the precoder design to minimize the total number of backlogged packets in the system, we have provided the convergence behavior of the proposed precoder design formulations for a given time instant.
-In accordance with the reviewer comment, we have included the Section V-C on page 13, col.
-1 to discuss the queue deviation over multiple transmission slots.
+\resp \review{
+	\begin{itemize}
+		\item We agree with the reviewer comment and is in line with Q.2. Please refer to the response for the comment on delay as the performance metric discusion. 
+		\item In accordance with the reviewer comment, we have included Section V-C to discuss the queue deviation over multiple transmission slots.
 We have presented Fig.
@@
 Since the paper is about the precoder design to minimize the number of backlogged packets at each instant, it may not be a valid performance metric for our objective.
-We still agree that delay can be controlled by reducing the number of packets on an average, as we can see from Fig.
-4, on page 13, the proposed algorithms are equally good in minimizing the average number of backlogged packets.
+		\item We agree that delay can be controlled by reducing the number of packets on an average, as we can see from Fig.
+4, the proposed algorithm performs better in comparison with the existing schemes in minimizing the average number of backlogged packets.
 Note that we can also prioritize the users by controlling the variable \me{a_k} in (6a) to address the QoS constraints for a particular user, in addition to that, we can also change the objective to \me{\ell_2} and \me{\ell_{\infty}} norm to address the delay and the fairness implicitly.
-}
+	\end{itemize}}
 
@@
 
-\resp \review{The \acf{SRA} is updated in the revised manuscript on page 7, col. 1, Section III-D.}
+\resp \review{SRA stands for spatial resource allocation (SRA). It is updated in the revised manuscript in Section III-D.}
 
@@
 \resp \review{We thank the reviewer for pointing out the mistake in the text.
-Since the problem is nonconvex, the JSFRA formulation can find a local optimal point upon convergence.
+Since the problem is nonconvex, the JSFRA formulation can find a stationary point upon convergence.
 The converged point of the JSFRA problem is in fact the stationary point of the original nonconvex problem, which is discussed in Appendix B-E on page 15, col.

### 2015-03-12 Response/response-2.tex
included nam's comments

@@
 Since the inequalities are used to replace the equality constraint, the objective could be improved by the iterative algorithm and the equality will be achieved after the convergence, thereby having one-to-one mapping at the final solution.
-We have updated the manuscript to include the details for better clarity on page 5, col.
-1, first paragraph.}
+We have updated the manuscript to include the details for better clarity on third paragraph in Section III-B.}
 
@@
 
-\resp \review{Please note that the objective function is convex, which can be verified by writing the difference function inside the norm operator in epigraph form.
+\resp \review{
+	\begin{itemize}
+		\item Please note that the objective function is convex, which can be verified by writing the difference function inside the norm operator in epigraph form.
 Since the problem in (16) is not jointly convex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
-Even after fixing \me{\mvec{w}{l,k,n}} as constant, the problem in (16) is nonconvex due to the DC constraint (16b), which is handled by the first order relaxation around some fixed operating point.
+		\item Even after fixing \me{\mvec{w}{l,k,n}} as constant, the problem in (16) is nonconvex due to the DC constraint (16b), which is handled by the first order relaxation around some fixed operating point.
 Once the linear relaxation is performed, the problem in (20) is a convex optimization problem with the variables being \me{\mvec{m}{l,k,n},\gamma_{l,k,n},\beta_{l,k,n}}.
-We have updated the manuscript to illustrate this clearly on page 5, col.
-2, first paragraph.}
+The manuscript is updated to illustrate this clearly on the lines following after (19).
+	\end{itemize}
+}
 
@@
 \resp \review{We thank the reviewer for the pointing out the flaw in the text.
-We have removed the incorrect statement on block coordinate descent method with the AO approach on page 5, col.
-1, second paragraph.
+We have removed the incorrect statement on block coordinate descent method with the AO approach on the fourth paragraph in Section III-B after (16).
 Indeed, due to the coupling of the transmit and the receive precoder variables, we cannot use the standard block coordinate descent method proof for the convergence of the proposed algorithm as pointed out by the reviewer.
-We have provided a completely rewritten convergence proof on Appendix B, page no.
-14, col.
-1.
+We have provided a completely rewritten convergence proof in Appendix B.
 }
@@
 Please note that the distributed algorithm is performed for the convex subproblem presented in (20) and (28).
-Since the problem is convex, the distributed approach convergence can be guaranteed by satisfying certain conditions.
-These are discussed in Section IV-C on page 8, col.
-2, last paragraph.}
+Since the problem is convex, the distributed approach convergence can be guaranteed under certain conditions.
+These are discussed in Appendix C on the convergence analysis for the distributed algorithms.}
 
@@
 
-\resp \review{We thank the reviewer for pointing out the issue in the system description for the figures.
+\resp \review{
+	\begin{itemize}
+		\item We thank the reviewer for pointing out the issue in the system description for the figures.
 Please note that the simulation scenario is different for Fig.
@@
 3 in terms of path loss distribution and the sub-channel numbers.
-We have provided different scenario with the centralized algorithm as reference for studying the performance under different system model.
+		\item We have provided different scenario with the centralized algorithm as reference for studying the performance under different system model.
 The user path loss is distributed uniformly between $[0,-6]$ dB for Fig.
@@
 3.
-We have updated the manuscript to include these details.
+		\item We have updated the manuscript to include these details.
 In addition, the number of backlogged packets in the system for Fig.
 3 is \me{[9,16,14,16,9,13,11,12]} bits.
-These informations are updated in the revised manuscript on page 12, col.
-1, lines 3-6 in Section V-B and page 12, col.
-2, third paragraph in Section V-B.}
+These informations are updated in the revised manuscript on Section V-B third paragraph.
+	\end{itemize}
+  }
 

### 2015-03-12 Response/response-3.tex
included nam's comments

@@
 
-\resp \review{We thank the reviewer for the insightful comment.
-We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under estimator for the SINR expression in (2).
-The under estimator is tight when there is at least one user in each BS that cannot be served by the current transmission.
+\resp \review{
+	\begin{itemize}
+		\item We thank the reviewer for the insightful comment.
+We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under estimator for the SINR expression in (2) on the third paragraph in Section III-B.
+		\item The under estimator is tight when there is at least one user in each BS that cannot be served by the current transmission as discussed in Appendix A.
 It has multiple solutions, when the objective is zero even for a single BS.
 In this case, we can use a regularization term with the total power in the objective to obtain an unique solution.
-We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-D.}
+We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-D.
+	\end{itemize}
+	 }
 
@@
 The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which in deed depend on the \me{q} value.
-We have modified the text to included this information in page 5, col.
-2, last paragraph.}
+We have modified the text to include this information on the sentence following after (22).}
 
@@
 \resp \review{We agree with the reviewer.
-We have updated the manuscript to discuss the convergence proof in a rigorous manner in Appendix B.
+Appendix B in the revised manuscript discuss the convergence proof rigorously..
 The uniqueness is also justified implicitly by the linear approximation performed on the DC constraint (16b), which makes the transmit precoders to be susceptible to the phase rotation.
@@
 
-\resp \review{We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on MMSE objective.
+\resp \review{
+	\begin{itemize}
+		\item We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on MMSE objective.
 In our MSE reformulation solution, we have used the MMSE receiver irrespective of the \me{\ell_q} norm used in the objective.
-Since the receivers are based on the MMSE objective, the equivalence is valid between the MSE and the SINR expression.
+		\item Since the receivers are based on the MMSE objective, the equivalence is valid between the MSE and the SINR expression.
 Since the transmit precoders are updated in accordance with the objective, the MSE reformulation yields the same solution as the SCA approach based JSFRA scheme presented in Section III-B.
@@
 1 for \me{\ell_1} objective.
-We have updated the manuscript to include this comments on page 6, col.
-2, line 10-13.}
+We have updated the manuscript to include this comments in the lines following (25) in Section III-C.
+	\end{itemize}
+	}
 
@@
 We have included the statement that it depends on the system model under consideration.
-It is updated in the manuscript on page 8, col.
-2, line 4-8.}
+This information is updated on the manuscript in the lines following after (40).}
 

### 2015-03-12 Response/response-4.tex
included nam's comments

@@
 
-\resp \review{We understand the reviewer's concern on the lack of rigorous convergence proof for the JSFRA approach.
-We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on page 14.
-We have included the reference suggested by the reviewer in [34].
+\resp \review{We agree that the original manuscript lacks the convergence proof for the JSFRA approach.
+We have presented a rigorous convergence proof for the proposed algorithm in Appendix B after (44).
+We have modified to include the reference suggested by the reviewer in [34] instead of [27] which is for the nonconvex objective function.
 }
@@
 
-\resp \review{We thank the reviewer for the useful suggestion.
+\resp \review{
+	\begin{itemize}
+	\item We thank the reviewer for the suggestion.
 In this paper, we proposed the precoder design to minimize the number of backlogged packets in the system at a given time.
 Since the greedy approach is performed at each time instant, it minimizes the number of backlogged packets also on an average.
-We focused on the precoder design based on the current knowledge of the channel state information in the simulation results.
-In order to justify the gains over multiple time instants, we have now included Section V-C on page 13 to discuss on the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots.
+	\item We focused on the precoder design based on the current knowledge of the channel state information in the simulation results.
+In order to justify the gains over multiple time instants, we have now included Section V-C with Fig.
+4 to discuss on the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots.
 Plots comparing the average number of backlogged packets for different schemes at each instant and the number of queued packets remained in the system after each transmission instant are provided in Fig.
-4.}
+4.
+	\end{itemize}
+}
 
@@
 
-\resp \review{We agree with the reviewer's comment.
-We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Section IV-C page 8.
-For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
+\resp \review{
+	\begin{itemize}
+		\item We agree with the reviewer's comment. We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Appendix C. 
+		\item For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
 Note that it includes the cross equivalent downlink channels of the neighbor BS users as well.
 To update the MMSE receiver, the equivalent channel for the \me{\ith{k}} user \me{\mbf{H}_{b,k,n} \mvec{m}{l,k^\prime,n}, \forall k^\prime \in \mc{U}_b, \forall b \in \mc{B}} is obtained from the BSs through user specific downlink precoded pilots.
-We have included the information on what each network entity knows in page 7, col.
-2 last paragraph.
-We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.}
+We have included the information on what each network entity knows in the paragraph after (36).
+		\item We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
+		\end{itemize}
+	}
 
-\cmnt{4} {Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one subcarrier.
+\cmnt{4} {Finally, some readers might be confused by the "joint space-frequency" terminology, believing that the beamforming is performed over a joint space-frequency channel space, where the space-frequency channels are formed by block-diagonal matrices, each block belonging to one sub-carrier.
 This could easily be clarified.}
 
-\resp \review{We agree with the reviewer's point. We have included the note on the space-frequency terminology in the introduction section on page 2, col. 2, line 2-4.}
+\resp \review{We agree with the reviewer's point. We have included the note on the space-frequency terminology in the lines before the last paragraph in Section I.}
 
@@
 
-\resp \review{Corrected in the revised manuscript in Section I on page 1, col. 1, line 2.}
+\resp \review{Corrected in the revised manuscript in Section I first paragraph.}
 
@@
 
-\resp \review{We thank the reviewer for highlighting the important point. We have included the statement in the revised manuscript on Section I, page 1, col. 2, line 5-14.}
+\resp \review{We thank the reviewer for highlighting the insightful point. We have included the statement in the revised manuscript in Section I, second paragraph.}
 
@@
 
-\resp \review{We have updated the revised manuscript with the reviewer suggestions on page 2, col. 2, second paragraph in Section II.}
+\resp \review{We have updated the revised manuscript with the reviewer suggestions on the second paragraph in Section II.}
 
@@
 
-\resp \review{We thank the reviewer for pointing out the confusion. We have removed the word "combinatorial" from the text to avoid confusion in page 3, col. 2, initial sentence in Section III.}
+\resp \review{We thank the reviewer for pointing out the confusion. We have removed the word "combinatorial" from the text on the initial paragraph in Section III.}
 
@@
 
-\resp \review{We have rephrased the sentence to avoid difficulty in the understanding. The manuscript is updated with the revised text on page 4, col. 2, first paragraph in Section III.B.}
+\resp \review{We have rephrased the sentence to avoid difficulty in the understanding. The manuscript is updated with the revised text on the first paragraph in Section III.B.}
 
@@
 \resp \review{We have updated the manuscript with the explicit power constraint in (16d) as
-\[\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b\]
-in page 5, col. 1.}
+\[\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b\].}
 
@@
 
-\resp \review{We have included the NP-hardness of the proposed solution by modeling the current problem to solve the \ac{WSRM} formulation, which is known to be NP-hard in page 5, col.
-1, last sentence in Section III-B third paragraph.}
+\resp \review{We have included the NP-hardness of the proposed solution by modeling the current problem to solve the \ac{WSRM} formulation, which is known to be NP-hard on the last sentence in Section III-B third paragraph.}
 
@@
 
-\resp \review{We have removed the sentence mentioning SCA method. We have updated the manuscript to discuss this as SCA approach in pagt 5, col. 1 last paragraph.}
+\resp \review{We have removed the sentence mentioning SCA method. We have updated the manuscript to discuss this as SCA approach in the sentences after (17).}
 
@@
 Expression (19d) and (18) are same.
-We have removed this double reference in page 5, col.
-2, equation (20).}
+We have removed this double reference from (20).}
 
@@
 \resp \review{We thank the reviewer for providing the valid comment.
-We have updated the manuscript to include this discussion in page 6, col 1, lines 3-6.
+We have updated the manuscript to include this discussion in the sentences after (23).
 The performance remains the same and the convergence rate is not affected by this scaling, which can be seen from Fig.
@@
 Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective.
-It is explained in detail in Appendix B on the convergence analysis of the centralized algorithm.}
+Please refer to Appendix B for more details on the convergence analysis of the centralized algorithm.}
 
@@
 
-\resp \review{We thank the reviewer for the critical comment.
+\resp \review{
+	\begin{itemize}
+		\item We thank the reviewer for the critical comment.
 It is true that the convex problem does not need to have a unique solution in general.
 By using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can see that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
-The uniqueness of the solution is obtained due to the linear constraint (19) in the problem formulation (20).
+		\item The uniqueness of the solution is obtained due to the linear constraint (19) in the problem formulation (20).
 Note that the linear constraint (19) is susceptible to the phase rotations on the transmit precoders, whereas any unitary rotations on the transmit precoders still satisfies the original nonconvex constraint (16b).
-When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain unique set of transmit precoders.
+		\item When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain unique set of transmit precoders.
 On contrary, it has multiple solutions when the objective is zero even for a single BS.
@@
 We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-D.
-It makes the objective strictly convex, therefore, it has a unique minimum.}
+It makes the objective strictly convex, therefore, it has a unique minimum.
+	\end{itemize}
+		}
 
@@
 
-\resp \review{It is updated in the manuscript on page 11, Table 1.}
+\resp \review{It is updated in the manuscript in Table I.}
 

### 2015-03-12 Report/convergence_centralized.tex
included nam's comments

@@
 
-To prove the convergence of the transmit precoders, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
+To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
 \begin{itemize}
@@
 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
+Finally, we show the limiting point of the iterative algorithm is indeed a stationary point for the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
@@
 The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive.
-Note that the norm operator is not differentiable at the minimum point for \me{\ell_1} and \me{\ell_\infty}.
-Using conditions (a) and (b), we can guarantee the existence of a minimizer to the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
@@
 
-To show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
+Finally, to show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
 \allowdisplaybreaks{\begin{multline} \label{con-opt}

### 2015-03-12 Report/convergence_distributed.tex
updated nam_comments without appendix
updated nam comments review should be modified
included nam's comments

@@
 
-To prove the convergence of the \ac{ADMM} approach, we use the argument presented in \cite{bertsekas1989parallel} Proposition 4.2. 
-If the problem is written as 
-\begin{IEEEeqnarray}{rCl}
+To prove the convergence of the \ac{ADMM} approach, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
+\begin{subeqnarray}
 	\underset{\mbf{x},\mbf{z}}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
-	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm} \\
-&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2, \eqsub
-\end{IEEEeqnarray}
-following conditions are required for the convergence if \ac{ADMM} is used.
+	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \slabel{const-admm} \\
+&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2 \eqsub
+\end{subeqnarray}
+following conditions are required for the \ac{ADMM} convergence.
 \begin{itemize}
@@
 4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.
+The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if the primal or the \ac{ADMM} updates are iterated until convergence.

### 2015-03-16 Report/convergence_centralized.tex
updated Antti Comments

@@
 The sequence of iterates \me{\{\iterate{\ma}{i}\}} will have at least one accumulation point, which follows from the compactness of the set \cite{zangwill1969nonlinear}.
-The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed point \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
+The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed points \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
 
-To show the set of fixed points \me{\mc{F}^\ast} are the minimizer for the objective function \me{f}, we can rely on the strict monotonicity of the objective function for each iteration.
-Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality achieves when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point.
-Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizer for the objective function \me{f} over the set \me{\mc{F}}.
+To show the set of fixed points \me{\mc{F}^\ast} are the minimizers for the objective function \me{f}, we can rely on the strict monotonicity of the objective function for each iteration.
+Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point.
+Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizers for the objective function \me{f} over the set \me{\mc{F}}.
 
@@
 
-\subsection{Stationary Point}
+\subsection{Stationary Points of the Nonconvex Problem}
 

### 2015-03-17 Report/kkt_mse_approach.tex
to include markku's comments

@@
 
-\review{To devise an algorithm for a practical implementation, we assume the cross channels \me{\mvec{H}{b,k,n}, \forall k \in \bar{\mc{U}}_b} and the receive beamformers \me{\mvec{w}{l,k,n}} of all users in the system are known through uplink signaling}.
+\review{To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which includes the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling}.
 We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the current problem as follows.

### 2015-03-17 Report/wsrm_formulation.tex
updated nam comments review should be modified
to include markku's comments

@@
 The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint of \eqref{eq:SINR}.
-Using additional variables, we relax the expression \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as
+Using additional variables, we relax the expression \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as}
 \iftoggle{single_column}{
@@
 }
-The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation.
+\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation.
 Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}}.
@@
 \end{IEEEeqnarray}
-where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex constraint in \eqref{eqn-9--1}.
+where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex \ac{DC} constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}.
 \review{The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for fixed number of iterations.} \review{Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
@@
 This procedure is carried out until convergence of the queue deviation or for fixed number of iterations by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
-The convergence proof is discussed in Appendix \ref{sec-3.5}
+The convergence proof is discussed in Appendix \ref{sec-3.5}.
 {\allowdisplaybreaks

### 2015-03-19 Response/response-1.tex
with_markku_corrections

@@
 In addition, the average delay of a particular user can be reduced by controlling the priority factor \me{a_k} in (6a), which affects the resource allocation.
+We have included this statement in the manuscript in Section II-B after (6).
 We can also control the delay by changing the exponent used in the objective \me{\ell_q} of the JSFRA problem as discussed in bullet points before Section III.
@@
 
-\resp \review{The discussions on the convergence of the centralized algorithms are provided in Appendix B and for the distributed algorithms in Appendix C.
+\resp \review{The discussions on the convergence of the centralized algorithms is provided in Appendix B and for the distributed algorithms in Appendix C.
 The discussion on the convergence to a stationary point is presented in Appendix B-E.}
@@
 
-\resp \review{We understand the reviewer's concern.
-Since the algorithm designs the precoders for each sub-channel at a time by using the total number of unserviced packets.
-For designing the precoders for the sub-channel \me{j+1}, we assume the transmit precoders and the rates of all users are obtained for the sub-channels \me{\{1,2,\dotsc,j\}}.
+\resp \review{Since the sub-channel wise resource allocation considers each sub-channel at a given time for designing the precoders, the performance of this scheme depend on the selection order of the sub-channels.
+For instance, to design the precoders for the sub-channel \me{j+1}, we assume the transmit precoders and the rates of all users are evaluated for the sub-channels \me{\{1,2,\dotsc,j\}}.
+At this point, we have to estimate the number of backlogged packets left over in the system, if the sub-channels \me{\{1,2,\dotsc,j\}} are transmitted with the precoders designed so far.
 Now, the number of backlogged packets for the \me{\ith{j+1}} sub-channel is given by
-\[Q_k - \sum_{i=1}^j \sum_{l=1}^L t_{l,k,i}.\]
-Since it depends on the rates of the already completed sub-channels \me{\{1,2,\dotsc,j\}}, it is susceptible to the ordering used to determine the precoders in each sub-channels.
-It is discussed in detail in Section III-D.}
+\[\max \Big( Q_k - \sum_{i=1}^j \sum_{l=1}^L t_{l,k,i},0 \Big).\]
+Since it depends on the rates of the already evaluated sub-channels \me{\{1,2,\dotsc,j\}}, it is susceptible to the ordering used to determine the precoders in each sub-channels.
+It is discussed in detail in Section III-D.
+Note that the performance will be closer to the JSFRA centralized scheme, if we select the best sub-channel ordering through an exhaustive search.
+In this case, the performance loss is mainly due to the maximum power constraint on each sub-channel.}
 
@@
 	\begin{itemize}
-		\item The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require large number of iterations for the convergence.
+		\item The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require a large number of iterations for the convergence.
 In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which may not be the same as when the algorithm is allowed to converge.
@@
 In practice, we can limit the primal or ADMM update for few iterations, then the distributed algorithms are still be efficient.
-		\item To this end, we have provided a practical scheme in Section IV-D.
+		\item To this end, we have a practical scheme in Section IV-D.
 Note that in the time-correlated case, it is often also enough to update the precoders once per radio frame.
@@
 The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13] in the revised manuscript, which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+The distributed algorithm for the time correlated case is not provided in the current manuscript, since it is not in the scope of the precoder design algorithms considered in this manuscript.
 	\end{itemize}
@@
 4, the proposed algorithm performs better in comparison with the existing schemes in minimizing the average number of backlogged packets.
-Note that we can also prioritize the users by controlling the variable \me{a_k} in (6a) to address the QoS constraints for a particular user, in addition to that, we can also change the objective to \me{\ell_2} and \me{\ell_{\infty}} norm to address the delay and the fairness implicitly.
+Note that we can also prioritize the users by controlling the variable \me{a_k} in (6a) to address the QoS constraints for a particular user.
+In addition to that, we can also change the objective to \me{\ell_2} and \me{\ell_{\infty}} norm to address the delay and the fairness implicitly.
+It is included in Section II-B after (6) and in the itemized listing following (7).
 	\end{itemize}}
@@
 
-\resp \review{We thank the reviewer for pointing out the mistake in the text.
-Since the problem is nonconvex, the JSFRA formulation can find a stationary point upon convergence.
+\resp \review{Since the problem is nonconvex, the JSFRA formulation can find a stationary point upon convergence.
 The converged point of the JSFRA problem is in fact the stationary point of the original nonconvex problem, which is discussed in Appendix B-E on page 15, col.
 2.
-We have removed the statement mentioning the pareto-optimal solutions in the discussions on Fig.
+We have removed the statement mentioning the Pareto-optimal solutions in the discussions on Fig.
 1 in the revised manuscript.}

### 2015-03-19 Response/response-2.tex
with_markku_corrections

@@
 
-\resp \review{We understand the reviewer's concern.
-The reformulation is required, since the SINR expression in (2) cannot be handled directly in the problem defined in (6).
+\resp \review{The reformulation is required, since the SINR expression in (2) cannot be handled directly in the problem defined in (6).
 Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), which are the under estimator to the original problem in (6).
@@
 	\begin{itemize}
-		\item Please note that the objective function is convex, which can be verified by writing the difference function inside the norm operator in epigraph form.
+		\item Please note that the objective function in the problem formulation is convex, which can be verified by writing the difference function inside the norm operator in epigraph form.
 Since the problem in (16) is not jointly convex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
@@
 \resp \review{We thank the reviewer for the pointing out the flaw in the text.
-We have removed the incorrect statement on block coordinate descent method with the AO approach on the fourth paragraph in Section III-B after (16).
+We have removed the incorrect statement on the block coordinate descent method with the AO approach on the fourth paragraph in Section III-B after (16).
 Indeed, due to the coupling of the transmit and the receive precoder variables, we cannot use the standard block coordinate descent method proof for the convergence of the proposed algorithm as pointed out by the reviewer.
@@
 \resp \review{We apologize for the inappropriate reference cited in the original manuscript.
-We have provided a completely rewritten proof on the convergence of the centralized algorithm on Appendix B.}
+We have provided a completely rewritten proof on the convergence of the centralized algorithm in Appendix B.}
 
@@
 
-\resp \review{We understand the issue raised by the reviewer.
-Please note that the distributed algorithm is performed for the convex subproblem presented in (20) and (28).
+\resp \review{Please note that the distributed algorithm is performed for the convex subproblem presented in (20) and (28).
 Since the problem is convex, the distributed approach convergence can be guaranteed under certain conditions.
-These are discussed in Appendix C on the convergence analysis for the distributed algorithms.}
+Those are discussed in Appendix C on the convergence analysis for the distributed algorithms.}
 
@@
 
-\resp \review{We understand the reviewer's concern.
-We have included the sub-channel wise resource allocation or (SRA) scheme in Section III-D for the completeness.
+\resp \review{We have included the sub-channel wise resource allocation or (SRA) scheme in Section III-D for the completeness.
 It is presented in the manuscript as an alternative suboptimal approach to perform sub-channel wise distributed precoder design by the centralized controller.
-We have updated the manuscript with more details for better understanding.}
+We have updated the manuscript with more details for better understanding.
+We have also stream-lined the manuscript so that some redundant discussion has been removed here and there.
+We also improved the grammar and fluency.}
 
@@
 3 is \me{[9,16,14,16,9,13,11,12]} bits.
-These informations are updated in the revised manuscript on Section V-B third paragraph.
+These facts are updated in the revised manuscript on Section V-B third paragraph.
 	\end{itemize}

### 2015-03-19 Response/response-3.tex
with_markku_corrections

@@
 		\item We thank the reviewer for the insightful comment.
-We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under estimator for the SINR expression in (2) on the third paragraph in Section III-B.
-		\item The under estimator is tight when there is at least one user in each BS that cannot be served by the current transmission as discussed in Appendix A.
+We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under-estimator for the SINR expression in (2) on the third paragraph in Section III-B.
+		\item The under-estimator is tight when there is at least one user in each BS that cannot be served by the current transmission as discussed in Appendix A.
 It has multiple solutions, when the objective is zero even for a single BS.
@@
 Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
-The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which in deed depend on the \me{q} value.
+The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which indeed depend on the value of \me{q}.
 We have modified the text to include this information on the sentence following after (22).}
@@
 \resp \review{We agree with the reviewer.
-Appendix B in the revised manuscript discuss the convergence proof rigorously..
+Appendix B in the revised manuscript discuss the convergence proof rigorously.
 The uniqueness is also justified implicitly by the linear approximation performed on the DC constraint (16b), which makes the transmit precoders to be susceptible to the phase rotation.
-The uniqueness discussions are presented in Appendix B-D.}
+The uniqueness discussions are presented in Appendices B-D.}
 
@@
 	\begin{itemize}
-		\item We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on MMSE objective.
-In our MSE reformulation solution, we have used the MMSE receiver irrespective of the \me{\ell_q} norm used in the objective.
+		\item We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on the MMSE objective.
+In our solution based on MSE reformulation, we have used the MMSE receiver irrespective of the \me{\ell_q} norm used in the objective.
 		\item Since the receivers are based on the MMSE objective, the equivalence is valid between the MSE and the SINR expression.
@@
 \resp \review{We agree with the reviewer's concern.
-We have included the reference [11] that discusses on the valid choices of the step size parameter for ADMM.
+We have included reference [11] that discusses on the valid choices of the step size parameter for ADMM.
 We have included the statement that it depends on the system model under consideration.

### 2015-03-19 Response/response-4.tex
with_markku_corrections

@@
 
-\resp \review{We have removed the sentence mentioning SCA method. We have updated the manuscript to discuss this as SCA approach in the sentences after (17).}
+\resp \review{We have removed the sentence mentioning the SCA method. We have updated the manuscript to discuss this as SCA approach in the sentences after (17).}
 
@@
 We have included all the constraints except the linearization constraint in (20) which is (19) in the original manuscript.
-Expression (19d) and (18) are same.
+Expression (19d) and (18) are the same.
 We have removed this double reference from (20).}
@@
 Note that the linear constraint (19) is susceptible to the phase rotations on the transmit precoders, whereas any unitary rotations on the transmit precoders still satisfies the original nonconvex constraint (16b).
-		\item When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain unique set of transmit precoders.
-On contrary, it has multiple solutions when the objective is zero even for a single BS.
+		\item When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain a unique set of transmit precoders.
+On the contrary, it has multiple solutions when the objective is zero even for a single BS.
 In this case, we can use a regularization term with the total power in the objective to obtain an unique solution.
-We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-D.
+We have discussed the uniqueness of the proposed algorithm in detail in Appendices B-D.
 It makes the objective strictly convex, therefore, it has a unique minimum.
@@
 
-\resp \review{We agree with the reviewer. We have modified the manuscript accordingly by replacing it with the singular form.}
+\resp \review{We checked the gramatical validity and kept the plural in some cases.}
 

### 2015-03-19 Report/conclusions.tex
updated nam comments review should be modified
with_markku_corrections

--- 2014-10-24 Report/conclusions.tex
@@
-In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM} transmission.
+In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM}.
 The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector.
-We proposed the \ac{JSFRA} scheme by employing the \ac{SCA} technique to relax the nonconvex constraint by a sequence of convex subsets for designing the precoders to minimize the total number of user queued packets.
-Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using \ac{SCA} technique to address the nonconvex constraints for a fixed \ac{MMSE} receivers.
-We then introduced distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
+We proposed the \ac{JSFRA} scheme by relaxing the nonconvex \ac{DC} constraint by a sequence of convex subsets using the \ac{SCA} for designing the precoders to minimize the total number of user queued packets.
+Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using the \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers.
+We also proposed distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
 Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method.
 The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations.
-Numerical results are used to compare the performance of the proposed algorithms with the existing solutions.
+Numerical results are used to compare the performances of the proposed algorithms with the existing solutions.
+The distributed design for the time correlated fading will be considered in future.

### 2015-03-19 Report/convergence_centralized.tex
with_markku_corrections

@@
 Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
+\iftoggle{single_column}{
+\begin{equation}
+\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
+\end{equation}
+}{
 \begin{align}
@@
 								 & \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
-\end{align}
+\end{align}}
 
@@
 In order to solve for \me{\mx} in the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate of \me{\mx} as
+\iftoggle{single_column}{
+\begin{equation}\label{con-relax}
+\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+\end{equation}}{
 \begin{multline} \label{con-relax}
 \hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
-\end{multline}
+\end{multline}}
 Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
@@
 Note that the point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality
-\allowdisplaybreaks{\begin{multline}\label{con-sub-set}
+\iftoggle{single_column}{
+\begin{equation}\label{con-sub-set}\allowdisplaybreaks
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) + h(\iter{\mz}{k+1}{i}) \leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0.
+\end{equation}}{
+\begin{multline}\label{con-sub-set}\allowdisplaybreaks
 h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\ + h(\iter{\mz}{k+1}{i}) \leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0.
@@
 At each \ac{SCA} iteration, the feasible set includes the optimal point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, thereby, leading to the monotonic decrease in the objective values \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
+\iftoggle{single_column}{
+\begin{equation} \label{con-convergence}
+f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
+\end{equation}}{
 \begin{multline} \label{con-convergence}
 f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
-\end{multline}
+\end{multline}}
 Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches limiting point as \me{k \rightarrow \infty}.
@@
 Note that \me{\iter{\mz}{k}{i}} is reused since the variable \me{\mx} is fixed for the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the problem follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver}.
+The convergence and the nonincreasing behavior of the problem follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.}.
 Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
@@
 Finally, to prove the global convergence of the iterative algorithm, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
-\allowdisplaybreaks{\begin{multline}
+\iftoggle{single_column}{
+\begin{equation}\allowdisplaybreaks
+f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
+\end{equation}}{
+\begin{multline}\allowdisplaybreaks
 f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
@@
 \end{equation}
-where \me{\iterate{\ma}{i}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{i})} in the \me{\ith{i}} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations to be performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant}.
+where \me{\iterate{\ma}{i}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{i})} in the \me{\ith{i}} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations to be performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.}.
 The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as discussed in Appendix \ref{mcity}.
@@
 Finally, to show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
-\allowdisplaybreaks{\begin{multline} \label{con-opt}
+\begin{multline} \label{con-opt}\allowdisplaybreaks
 f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
 f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
-\end{multline}}
+\end{multline}
 where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.

### 2015-03-19 Report/convergence_distributed.tex
with_markku_corrections

@@
-The convergence of the distributed algorithm outlined in Algorithm \ref{algo-3} follows the same discussion in Appendix \ref{sec-3.5} if the subproblem \eqref{eqn-decent-1} converge to the centralized solution.
-Since the subproblem \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}.
+The convergence of the distributed algorithm outlined in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5} if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
+Since the subproblem in \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}.
 The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \rightarrow \infty} \cite{bertsekas1999nonlinear} for a diminishing step size.
-It can be seen that the subproblem \eqref{eqn-decent-1} satisfies Slater's constraint qualification by having non empty interior and bounded due to the total power constraint for the transmit precoders.
+It can be seen that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and bounded due to the total power constraint for the transmit precoders.
 
@@
 \end{subeqnarray}
-following conditions are required for the \ac{ADMM} convergence.
+the following conditions are required for the convergence.
 \begin{itemize}
@@
 \end{itemize}
-Note that the equality constraint \eqref{const-admm} is identical to \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}.
+Note that the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}.
 It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible.
-The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} are all convex sets and has a nonempty interior.
-The feasibility of the interior point is verified by having a non zero precoder for only one user.
+The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has a nonempty interior.
+The feasibility of the interior point is verified by having a non-zero precoder for only one user.
 Therefore, by following \cite[Prop.

### 2015-03-19 Report/decomposition_solutions.tex
updated nam_comments without appendix
updated nam comments review should be modified
with_markku_corrections

@@
 Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
-{\allowdisplaybreaks
-\begin{IEEEeqnarray}{CCl} \label{eqn-decent-1}
-\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}} &\quad & \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
-\text{subject to}&\quad& \eqref{eqn-9.1c} - \eqref{eqn-9.1e}, \IEEEyessubnumber
-\end{IEEEeqnarray}}
+\begin{subeqnarray} \label{eqn-decent-1} \allowdisplaybreaks
+&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \slabel{eqn-decent-1a} \\
+&\text{subject to}& \quad \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber
+\end{subeqnarray}
 where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.
@@
 To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-Following similar approach presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference from each \ac{BS} in \me{\mathcal{B}} as
+Following an approach similar to the one presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference from each \ac{BS} in \me{\bar{\mc{B}}_{b_k}} as
 \iftoggle{single_column}{
-\begin{IEEEeqnarray}{rCl}\label{eqn-decent-3}
+\begin{eqnarray}{rCl}\label{eqn-decent-3}
 \beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; \enoise,
-\end{IEEEeqnarray}}{\allowdisplaybreaks
+&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; \enoise
+\end{eqnarray}}{\allowdisplaybreaks
 \begin{multline}\label{eqn-decent-3}
 \enoise + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
-	+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n},
++ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n}
 \end{multline}}
@@
 \begin{equation} \label{inter_exp}
-\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \forall b \in \bar{\mc{B}}_{b_k}.
+\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{j,i,n} |^2 \; \forall b \in \bar{\mc{B}}_{b_k}.
 \end{equation}
 
-The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} by a parallel iterative subproblems coordinated by either primal or \acl{DD} update.
+The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} to a parallel iterative subproblems coordinated by either primal or \acl{DD} update.
 The coupling variables are updated in each iteration by exchanging limited information among the subproblems.
 Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented as
-\begin{IEEEeqnarray}{rCl}
-	\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b}, \eqsub \\
-	\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran. \eqsub
-\end{IEEEeqnarray}
+\begin{subeqnarray}
+\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b} \\
+\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran.
+\end{subeqnarray}
 Let us define the vector \me{\mbfa{\zeta}_b}, formed by stacking the interference terms corresponding to the \ac{BS} \me{b} as
 \begin{equation}
-	\mbfa{\zeta}_{b} = \left [\hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran.
-	\label{if_vector}
+\mbfa{\zeta}_{b} = \left [\hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran. \label{if_vector}
 \end{equation}
 Since the decentralization solution is an iterative procedure, we represent the \me{\ith{i}} iteration index as \me{x^{(i)}}.
-Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to the \ac{BS} \me{b_k} in \ac{BS} \me{b} as
+Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to \ac{BS} \me{b_k} in \ac{BS} \me{b} as
 \begin{equation}
@@
 To decouple the precoder design across \acp{BS}, the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are to be known at each \ac{BS} \me{b} through the precoded uplink pilots from all the users in the system, where the precoders are the \ac{MMSE} receiver \me{\mvec{w}{l,k,n}} evaluated at the user.
-Similarly to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} are to be known through the user specific precoded downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} by using the equivalent downlink channel that includes the updated \ac{MMSE} receivers of all the users, as in \cite{komulainen2013effective}.
+Similarly, to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} need to be known through the user specific precoded downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} by using the equivalent downlink channel that includes the updated \ac{MMSE} receivers of all the users, as in \cite{komulainen2013effective}.
 

### 2015-03-19 Report/ieee_journal.tex
with_markku_corrections

@@
-\documentclass[10pt,journal,twocolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[11pt,journal,onecolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman$^\dagger$ \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Technology and Innovation (Tekes), Nokia Solutions Networks, Xilinx Ireland, Academy of Finland.
-Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli$^\dagger$ \IEEEmembership{Senior Member,~IEEE}, Markku Juntti$^\dagger$ \IEEEmembership{Senior Member,~IEEE}, and Le-Nam Tran$^\ddagger$ \IEEEmembership{Member,~IEEE}}\thanks{
-	$^\dagger$The authors are with the Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{$^\ddagger$The author is with the Department of Electronic Engineering, Maynooth University, Maynooth, Co.
+	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Innovation (Tekes), Nokia Networks, Xilinx, Elektrobit and the Academy of Finland.
+Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Senior Member,~IEEE}, Markku Juntti \IEEEmembership{Senior Member,~IEEE}, and Le-Nam Tran \IEEEmembership{Member,~IEEE}}\thanks{
+	G.
+Venkatraman, A.
+T\"{o}lli and M.
+Juntti are with Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{L.-N.
+Tran was with Centre for Wireless Communications (CWC), Oulu, FI-90014, is now with the Department of Electronic Engineering, Maynooth University, Maynooth, Co.
 Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie)}}
@@
 \begin{IEEEkeywords}
-Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, Precoder design, \acs{SCA}, \ac{WSRM}.
+Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \ac{WSRM}.
 \end{IEEEkeywords}

### 2015-03-19 Report/introduction.tex
with_markku_corrections

@@
 
-In a network with multiple \acp{BS} serving \acp{MU}, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
-These available packets are transmitted over the shared wireless resources subject to certain system limitations and constraints.
-We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets.
-Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.
+\acused{MU}
 
-In general, the resource allocation problems are formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}.
+In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
+We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets at each \ac{BS}.
+Since the available resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.
+
+In general, the resource allocation problems can be formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}.
 \review{In contrast, the linear transmit precoders, which are complex vectors, are implicitly used as decision variables, thereby avoiding the explicit modeling of binary decision variables.
-It is used to determine the transmission rate of a user on a space-frequency resource if the precoder vector is non-zero.
+They are used to determine the transmission rates of users on a space-frequency resource if the precoder vector is non-zero.
 A zero transmit precoder indicates the absence of the user on a given resource.
-In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence}.
+In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergences}.
 
@@
 
-The relation between the achievable capacity and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can be used to solve the \ac{WSRM} problem \cite{mse_duality}.
+The relation between the achievable sum rate and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can be used to solve the \ac{WSRM} problem \cite{mse_duality}.
 In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients.
 In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders.
-Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the remaining others are fixed.
+Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed.
 The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner.
-Additional rate constraints based on the \ac{QoS} requirements were included in the \ac{WSRM} problem and solved via \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
+Additional the rate constraints based on the \ac{QoS} requirements were included in the \ac{WSRM} problem and solved via the \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
 
-The problem of precoder design for the \ac{MIMO} \ac{IBC} system are solved either by using a centralized controller or by using decentralized algorithms where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with the other \acp{BS} via back-haul.
-The distributed approaches are based on primal, dual or \ac{ADMM} decomposition, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}.
+The problem of precoder design for the \ac{MIMO} \ac{IBC} system can be solved either by using a centralized controller or by using decentralized algorithms, where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with other \acp{BS} via back-haul.
+The distributed approaches are usually based on the primal, or dual decompositions or the \ac{ADMM}, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}.
 In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders.
-The fixed interference are then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}.
-The dual and \ac{ADMM} approaches control the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
+The fixed interference is then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}.
+The dual and the \ac{ADMM} approaches control the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
 
 By adjusting the weights in the \ac{WSRM} objective properly, we can find an arbitrary rate-tuple in the rate region that maximizes the suitable objective measures.
-For example, if the weight of each user is set to be inversely proportional to its average data rate, the corresponding problem guarantees fairness on an average among the users.
+For example, if the weight of each user is set to be inversely proportional to its average data rate, the corresponding problem guarantees fairness on the average among the users.
 As an approximation, we may assign weights based on the current queue size of the users.
-More specifically, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}.
-In backpressure algorithm, the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
+Specifically, the queue states can be incorporated in the \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}, where \me{R_k} denotes the achievable user rate.
+In the backpressure algorithm, the differential queues between the source and the receiver nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
 
-Earlier studies on the queue minimization problem were summarized in the survey paper \cite{berry2004cross,layering_as_opt}.
+Earlier studies on the queue minimization problem were summarized in the survey papers \cite{berry2004cross,layering_as_opt}.
 In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} using geometric programming.
@@
 \review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS} queues.
-Since the transmissions are guided by the backlogged packets, the proposed formulation limit the allocations beyond the number of backlogged packets without additional rate constraint.
-We adopt \ac{SCA} to solve by a sequence of convex subproblems using first order approximations due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint.
-First method is by using the direct formulation and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for an optimal precoders.
+Since the transmissions are guided by the backlogged packets, the proposed formulation limits the allocations beyond the number of backlogged packets without additional rate constraint.
+We adopt the \ac{SCA} to solve a sequence of convex subproblems using the first order Taylor approximation due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} for the nonconvex \ac{DC} constraint.
+The first method is by using the \ac{SINR} expression and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders.
 Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods.
@@
 
-The paper is organized as follows.
+The rest of the paper is organized as follows.
 In Section \ref{sec-2-3.2}, we introduce the system model and the problem formulation for the queue minimizing precoder design.

### 2015-03-19 Report/joint_wsrm_formulation.tex
with_markku_corrections

@@
-The queue minimizing algorithms are discussed extensively in the networking literature to provide congestion-free routing between any two nodes in the network.
+The queue minimizing algorithms have been extensively discussed in the networking literature to provide congestion-free routing between any two nodes in the network.
 One such algorithm  is the \emph{backpressure algorithm} \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
@@
 
-To minimize the total number of backlogged packets for an instant \me{i}, the optimal transmission rate of all users are obtained by minimizing the Lyapunov function drift expressed as  
+To minimize the total number of backlogged packets for time instant \me{i}, the optimal transmission rate of all users are obtained by minimizing the Lyapunov drift expressed as  
 \iftoggle{single_column}{
@@
 
-The expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the number of backlogged packets corresponding to the users.
-The above discussed approach is extended for the wireless networks in \cite{weeraddana2011resource}, in which the queues are used as weights in the \ac{WSRM} formulation to determine the transmit precoders.
+The expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the numbers of backlogged packets of the corresponding users.
+The above approach was extended for the wireless networks in \cite{weeraddana2011resource}, in which the queues were used as weights in the \ac{WSRM} formulation to determine the transmit precoders.
 Since the expectation is minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
@@
 where the precoders are associated with \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}.
-By using the number of queued packets as the weights, the resources can be allocated to the user with the more backlogged packets, which essentially does greedy allocation.
+By using the number of queued packets as the weights, the resources can be allocated to the user with more backlogged packets; this essentially results in greedy allocation.
 

### 2015-03-19 Report/kkt_mse_approach.tex
with_markku_corrections

@@
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
-Since the formulation in \cite{kaleva2013decentralized,kaleva2013primal} are similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
+Since the formulations in \cite{kaleva2013decentralized,kaleva2013primal} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
 
@@
 With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
-\iftoggle{single_column}{\allowdisplaybreaks
+\allowdisplaybreaks\iftoggle{single_column}{
 \begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
@@
 \end{IEEEeqnarray}
-}{
-\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
+}{\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
 	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
@@
 	\delta_b : & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l = 1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \eqspace \label{kkt-mse-1.4}
-\end{IEEEeqnarray}
-}
+\end{IEEEeqnarray}}
 where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}.
@@
 \end{IEEEeqnarray}
-}{{\allowdisplaybreaks
+}{\allowdisplaybreaks
 \begin{IEEEeqnarray}{ll} \label{kkt-mse-4}
@@
 	\alpha^{(i)}_{l,k,n} =& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1}
-\end{IEEEeqnarray}}}
+\end{IEEEeqnarray}}
 Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other.
@@
 The choice of \me{\rho} depends on the system model and it affects the convergence behavior.
-It reduces the oscillations in the objective function when \me{\sigma^{(i)}} is negative due to over allocation.}
+It reduces the oscillations in the objective function when \me{\sigma^{(i)}} is negative due to over-allocation.}
 
 When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
-Once the \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}} eventually.
+Once \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}} eventually.
 \review{The choice of \me{\rho} is susceptible to the system model under consideration, which affects the convergence speed of the iterative algorithm.
@@
 
-To avoid the back-haul exchanges between \acp{BS}, as an alternative approach, users may perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users.
+To avoid the back-haul exchanges between the \acp{BS}, as an alternative approach, users perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users.
 Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}.
@@
 \review{Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling with the precoded pilots.
-Unlike \ac{PD} or \ac{ADMM} schemes, all variables are updated at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient.
+Unlike \ac{PD} or \ac{ADMM} schemes, all variables are updated at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient.
 It is not guaranteed to obtain the same point as that of the centralized problem.
 The algorithm in \eqref{kkt-mse-4} is identical to \eqref{eqn-mse-2}, if the receivers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed to find the optimal transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}.
-Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, dual variable update loop and the bisection method to find the transmit precoders.
+Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, the dual variable update loop and the bisection method to find the transmit precoders.
 To avoid this, the proposed method performs group update of all variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.

### 2015-03-19 Report/primal_approach.tex
with_markku_corrections

@@
-In \acl{PD}, the convex problem in \eqref{eqn-decent-1} is solved for the optimal transmit precoders in an iterative manner for a fixed \ac{BS} specific interference terms \me{\mbfa{\zeta}_{b_k}} using master-slave model \cite{pennanen2011decentralized}.
+In the \acl{PD}, the convex problem in \eqref{eqn-decent-1} is solved for the optimal transmit precoders in an iterative manner for a fixed \ac{BS} specific interference term \me{\mbfa{\zeta}_{b_k}} using the master-slave model \cite{pennanen2011decentralized}.
 The slave subproblem is solved in each \ac{BS} for the optimal transmit precoders only for the associated users by assuming fixed interference terms \me{\mbfa{\zeta}_{b_k}^{(i)}} in each \me{\ith{i}} iteration.

### 2015-03-19 Report/problem_formulation.tex
updated nam_comments without appendix
with_markku_corrections

@@
 \begin{equation}\label{pf-1}
-\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2,
+\underset{t_k}{\text{minimize}} \, \sum_k \, v_k^2 = \underset{t_k}{\text{minimize}} \, \sum_k \, Q_k^2 - 2 \, Q_k t_k + t_k^2
 \end{equation}
 which is similar to the objective in \eqref{q_gen_sum}.
-It is achieved either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is significantly large for all users such that \me{t_k^2} has no impact on the objective function.}
+It is achieved either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is large for all users such that \me{t_k^2} has no impact on the objective function.}
 
@@
 In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function \eqref{eqn-4.2} itself.
-It makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \acp{BS} independently by exchanging minimal information exchange \cite{boyd2011distributed}.
-In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRME} problems include the sub-channels jointly to obtain an efficient allocation by identifying the optimal space-frequency resource for the users.
+It makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \ac{BS} independently with minimal information exchange \cite{boyd2011distributed}.
+In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRME} problems handle the sub-channels jointly to obtain an efficient allocation by identifying the optimal space-frequency resources for the users.

### 2015-03-19 Report/problem_formulation_intro.tex
updated nam_comments without appendix
with_markku_corrections

@@
-To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation objective as given by
+To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation objective as
 \begin{equation}
-v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n}),
+v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})
 \label{eqn-4.2}
@@
 
-Explicitly, the objective of the problem considered is given by \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. With this objective function, the weighted queued packet minimization formulation is given by
+Explicitly, the objective of the problem considered is given as \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. Thus the formulation becomes
 \begin{IEEEeqnarray}{rCl}\label{eqn-3}
-\underset{\substack{\mvec{m}{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \\
-\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \eqspace \label{eqn-4.3}
+\underset{\substack{\mvec{m}{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \label{eqn-3-1.a} \\
+\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \fall b \IEEEyessubnumber \eqspace \label{eqn-4.3}
 \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor which is incorporated to control user priority based on their respective \ac{QoS}.
-In \eqref{eqn-4.3}, \ac{BS} specific sum power constraint for all sub-channels is considered.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor, which is used to alter the user priority based on the \ac{QoS} constraints \review{such as packet delay requirements and packet waiting time, since they are proportional to the corresponding number of backlogged packets.} The \ac{BS} specific power constraint for all sub-channels is considered in \eqref{eqn-4.3}.
 
@@
 Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that the optimal solution has been obtained.
-The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as follows
+The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as follows.
 \begin{itemize}
@@
 As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
-\item \me{\ell_{2}} prioritizes users with higher number of queued packets before considering the users with a smaller number of backlogged packets.
+\item \me{\ell_{2}} prioritizes users with a higher number of queued packets before considering the users with a smaller number of backlogged packets.
 For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.

### 2015-03-19 Report/sub_channel_wsrm.tex
with_markku_corrections

@@
 
-As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation only for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
+As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
 The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels as given by
@@
 \end{equation}
-Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the backlogged packets.
+Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the number of backlogged packets.
 Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} before solving for the precoders specific to the sub-channel \me{i}.
@@
 However, the \ac{SRA} approach provides faster convergence in contrast to the \ac{JSFRA} formulation due to the substantial reduction in the optimization variables for each sub-channel problem.
-As the user count increases, the \ac{SRA} formulation will be insusceptible to the sub-channel ordering due to the multi-user diversity.
+As the number of users in the system increases, the \ac{SRA} formulation will be insensitive to the sub-channel ordering due to the multi-user diversity.
 %The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}

### 2015-03-19 Report/system_model.tex
updated nam_comments without appendix
with_markku_corrections

@@
 \begin{equation}\label{eqn-1}
-\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n},
+\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
 \end{equation}
@@
 \hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n} \\ 
-+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n},
++ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
 \end{multline}
@@
 In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users.
-\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted}.
+\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted.}.
 Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
 \begin{equation}\label{eq:SINR}
-\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2},
+\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}
 \end{equation}
@@
 
-Let \me{Q_k} be the number of backlogged packets destined for the user \me{k} at a given scheduling instant.
-The queue dynamics of the user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for the user \me{k} at the \me{{i}^\mathrm{th}} time instant\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar}.
+Let \me{Q_k} be the number of backlogged packets destined for user \me{k} at a given scheduling instant.
+The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{{i}^\mathrm{th}} time instant\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.}.
 The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, denoted as \me{Q_k(i+1)}, is given by
 \begin{equation}
-Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i),
+Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i)
 \label{eqn-2a}
@@
 where \me{[x]^+ \equiv \max{ \lbrace x,0  \rbrace}} and \me{t_k} denotes the number of transmitted packets or bits for user \me{k}.
-At the \me{\ith{i}} instant, transmission rate of the user \me{k} is given by
+At the \me{\ith{i}} instant, the transmission rate of user \me{k} is given by
 \begin{equation}
-t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i),
+t_k(i) = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}(i)
 \end{equation}
-where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the \me{(l,n)} space-frequency resource is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} of \me{\gamma_{l,k,n}}\footnote{Upper bound is achieved by using Gaussian signaling}.
-Note that the units of \me{t_k} and \me{Q_k} are in bits defined per channel use.
+where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over the \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
+The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}\footnote{The upper bound can be achieved by using Gaussian signaling.}.
+The units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2015-03-19 Report/time_correlated.tex
with_markku_corrections

@@
 We discuss the performance of the \ac{JSFRA} algorithm for different \me{\ell_q} over multiple transmission slots.
-It is compared with the existing \ac{Q-WSRME} scheme by varying the average arrival rate \me{A_k} of all users.
+It is compared to the existing \ac{Q-WSRME} scheme by varying the average arrival rate \me{A_k} of all users.
 Fig.
-\ref{fig-time-analysis} plots the performance of the centralized algorithms for different \me{\ell_q} values.
-Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and it follows Poisson process.
-We considered a \me{4 \times 1} \ac{MIMO} system with \me{N = 4} sub-channels and \me{N_B = 2} \acp{BS}.
+\ref{fig-time-analysis} plots the performances of the centralized algorithms for different \me{\ell_q} values.
+Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and they follow the Poisson process.
+We considered a \me{4 \times 1} \ac{MIMO} with \me{N = 4} sub-channels and \me{N_B = 2} \acp{BS}.
 The \ac{PL} is modeled as a uniform random variable \me{[0,-3]} dB.
@@
 \subref*{fig-review} compares various schemes with the average number of backlogged packets present in the system after each transmission slot.
-The performance of the \ac{JSFRA} scheme using \me{\ell_2} and \ac{Q-WSRME} approach are similar in the average number of residual packets after each transmission slot.
+The performance of the \ac{JSFRA} scheme using \me{\ell_2} is similar to the \ac{Q-WSRME} approach in the average number of residual packets after each transmission slot.
 Note that the additional rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence.
-Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are greater than the actual transmissions.
+Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are larger than those of the actual transmissions.
 Fig.
-\subref*{fig-review} and Fig.
-\subref*{fig-review-time} shows that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} scheme due to the greedy allocation of serving users with better channel.
+\ref{fig-time-analysis} shows that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} scheme due to the greedy allocation of serving users with better channel.
 Fig.
-\ref{fig-time-analysis} highlights the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally good compared to other objectives when the system is in the stable region.
+\ref{fig-time-analysis} highlights that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally well compared to the other objectives when the system is in the stable region.
 On contrary, the performance is inferior in the unstable region, since the fair allocation is not effective when the number of backlogged packets is large for all users.

### 2015-03-19 Report/wsrm_formulation.tex
with_markku_corrections

@@
-\review{We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}.
+\review{We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \ac{SCA} \cite{marks1978technical}.
 The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system.
-The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint of \eqref{eq:SINR}.
-Using additional variables, we relax the expression \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as}
+The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint.
+Using additional variables, we relax the expression in \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as}
 \iftoggle{single_column}{
@@
 }
-\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation.
-Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}}.
-\review{The constraints are tight when each \ac{BS} objective is non zero at the optimal point, as discussed in Appendix \ref{a-3}}.
+\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3}.
+Note that \eqref{eqn-6.2} is an under-estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.
+\review{The constraints are tight when each \ac{BS} objective is non-zero upon convergence at the limiting point, as discussed in Appendix \ref{a-3}}.
 \review{Since the \ac{JSFRA} formulation can be modeled as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, it also belongs to the class of NP-hard problems.}
@@
 Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-\review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed by a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as \ac{SCA} approach in \cite{marks1978technical}.
+\review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as the \ac{SCA} approach in \cite{marks1978technical}.
 By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}
@@
 }
-In summary, for the fixed linear receivers \review{\me{\mvec{w}{l,k,n}}} and the operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
+In summary, for fixed linear receiver \review{\me{\mvec{w}{l,k,n}}} and operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-9}
@@
 
-Now, the optimal linear receivers for the fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
+Now, the optimal linear receivers for fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
 \begin{IEEEeqnarray}{CCl}\label{eqn-9--1}
@@
 where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex \ac{DC} constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}.
-\review{The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for fixed number of iterations.} \review{Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
-The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which in deed depend on the \me{q} value.}
+\review{The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations.} \review{Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
+The dependency is implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which depend on the value of the exponent \me{q}.}
 
@@
 The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
-Instead of initializing \me{{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with some feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{{\mbf{u}}_{l,k,n}} as briefed in Algorithm \ref{algo-1}.
-For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for the predefined iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
+Instead of initializing \me{{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with some feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{{\mbf{u}}_{l,k,n}} as seen in Algorithm \ref{algo-1}.
+For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
 Next, the receive beamformers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
-This procedure is carried out until convergence of the queue deviation or for fixed number of iterations by \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
+This procedure is carried out until convergence of the queue deviation or a fixed number of iterations \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
 The convergence proof is discussed in Appendix \ref{sec-3.5}.
-{\allowdisplaybreaks
+\allowdisplaybreaks
 \begin{algorithm}
@@
 \end{algorithm}
-}
 

### 2015-03-20 Response/response-4.tex
nam_changes

@@
+This paper proposes a practical method for minimizing the number of currently backlogged packets in a wireless multicell MIMO-OFDM network.
+Resource allocation is performed over space (beamformers) and frequency (subcarriers), and a norm of the queue deviations is minimized.
+The problem studied is very relevant, but still most work in the literature has so far focussed on the infinite queue model which clearly does not reflect reality particularly well.
+The proposed methods seem practical, due to their possibility to be implemented as distributed methods coupled with distributed CSI acquisition.
+The paper has a multitude of approaches to the problem, but there are several areas which must be improved before a possible publication.
+
+\vspace{0.25in}
 \review{ First, we thank the reviewer for providing valuable and insightful comments. The comments are really helpful in improving the manuscript.}
 
-\begin{itemize}
+\begin{enumerate}
 
@@
 We have presented a rigorous convergence proof for the proposed algorithm in Appendix B after (44).
-We have modified to include the reference suggested by the reviewer in [34] instead of [27] which is for the nonconvex objective function.
+We have modified to include the reference suggested by the reviewer in [33] instead of [27] which is for the nonconvex objective function.
 }
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 	\item We thank the reviewer for the suggestion.
@@
 4.
-	\end{itemize}
+	\end{enumerate}
 }
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 		\item We agree with the reviewer's comment. We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Appendix C. 
@@
 		\item We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
-		\end{itemize}
+		\end{enumerate}
 	}
@@
 
-\cmnt{5} {Please see the itemized questions}
+\cmnt{5} {Please see the enumerated questions}
 
-\begin{itemize}
+\begin{enumerate}
 
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 		\item We thank the reviewer for the critical comment.
@@
 It makes the objective strictly convex, therefore, it has a unique minimum.
-	\end{itemize}
+	\end{enumerate}
 		}
@@
 
-\end{itemize}
+\end{enumerate}
 
-\end{itemize}
+\end{enumerate}

### 2015-03-20 Response/reviewer_response.tex
nam_changes

@@
-\documentclass[10pt,letterpaper,onecolumn]{IEEEtran}
+\documentclass[11pt,letterpaper,onecolumn]{article}
 
-\usepackage[left=1in,right=1in]{geometry}
+\usepackage[left=1.15in,right=1.15in]{geometry}
 \usepackage{amsmath,amssymb}
@@
 
-\newcommand{\cmnt}[1]{\item[\textbf{Q}#1]}
-\newcommand{\cmnts}[1]{\item[(#1)]}
-\newcommand{\resp}{\item[\textbf{Resp} :]}
+\newcommand{\cmnt}[1]{\vspace{0.25in}\item}
+\newcommand{\cmnts}[1]{\vspace{0.2in}\item[(#1)]}
+\newcommand{\resp}{\vspace{0.25in}\item[\textit{\underline{Reply}}:]}
 
@@
 
-\doublespacing
-
-\title{Response for the Reviewer Comments}
+\title{Reviewer's Comments \& Author's Replies}
 
@@
 
-The authors would like to thank the editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality.
+\begin{enumerate}
+\item[Manuscript No.] Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\
+\item[Title] "Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\
+\item[Authors] Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
+\end{enumerate}
+
+\vspace{2in}
+The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality.
 Based on the comments, we have made several major revisions to the paper, following the suggestions of the reviewers.

### 2015-03-20 Report/convergence_centralized.tex
nam_changes

@@
 	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
-	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
+	%\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
 \end{itemize}
@@
 A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied.
-Since the feasible set is not fixed in each iteration, we require additional conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
+Since the feasible set is not fixed in each iteration, we require additional condition (c) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
 Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th.
 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
-Finally, we show the limiting point of the iterative algorithm is indeed a stationary point for the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence} to show that the limiting point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
@@
 \begin{itemize}
-\item[(i)] all accumulation points will be fixed points,
+\item[(i)] all accumulation points will be a generalized fixed points,
 \item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
@@
 \begin{equation}
-\mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}), \; \text{subject to} \; \ma \in \mc{F}
+\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \mc{F}
 \end{equation}
@@
 To show the set of fixed points \me{\mc{F}^\ast} are the minimizers for the objective function \me{f}, we can rely on the strict monotonicity of the objective function for each iteration.
-Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\mc{A}(\ma^\ast) = \ma^\ast}, which is the fixed point.
+Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\ma^\ast \in \mc{A}(\ma^\ast)}, which is a generalized fixed point.
 Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizers for the objective function \me{f} over the set \me{\mc{F}}.
 
-If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
+%If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
 The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{meyer1976sufficient,zangwill1969nonlinear}.
@@
 
-\subsection{Uniqueness}
+%\subsection{Uniqueness}
 
-The uniqueness of the transmit precoders and the receive beamformers for each convex subproblem is achieved by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
+%The uniqueness of the transmit precoders and the receive beamformers for each convex subproblem is achieved by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
 The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations.
 
-When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
+%When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
 To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
@@
 \end{multline}
-where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using the discussions in \cite{marks1978technical}, we can show that the feasible point  \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\}}, which is the minimizer in its local neighborhood, is a stationary point of \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a generalized fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+Using the discussions in \cite{marks1978technical,lanckriet2009convergence}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
+Using this argument, the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\}}, which is a minimizer in its local neighborhood, is a stationary point of \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
 The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires \me{\mbf{0}^\tran \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions, where \me{\partial f_0(\mz_{\ast})} denotes the subdifferential set.

### 2015-03-21 Response/reviewer_response.tex
revision_on_comments

@@
 \usepackage{amsmath,amssymb}
-\usepackage{acronym,etoolbox,color}
+\usepackage{acronym,etoolbox,color,multicol}
 \usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}
 
-\newcommand{\cmnt}[1]{\vspace{0.25in}\item}
+\newcommand{\cmnt}[1]{\vspace{0.2in}\item}
 \newcommand{\cmnts}[1]{\vspace{0.2in}\item[(#1)]}
-\newcommand{\resp}{\vspace{0.25in}\item[\textit{\underline{Reply}}:]}
+\newcommand{\resp}{\vspace{0.2in}\item[\textit{\underline{Reply}}:]}
 
@@
 
-\begin{enumerate}
-\item[Manuscript No.] Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\
-\item[Title] "Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\
-\item[Authors] Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
-\end{enumerate}
+\begin{tabular}{p{1.5in}p{4in}}
+\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\
+\textbf{Title} & "Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\
+\textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
+\end{tabular}
 
-\vspace{2in}
+\vspace{1in}
 The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality.
@@
 The revisions in the revised manuscript are highlighted using blue color and the authors responses are also presented in blue color text.
+Following are the revisions made in the revised manuscript.
+\input{additions}
 

### 2015-03-21 Response/additions.tex
revision_on_comments

\begin{enumerate}
\item We have provided additional information to improve the continuity in the algorithm formulation from the SINR expression as suggested by the reviewers.
\item We have included the discussion for the MSE based reformulation for different norms in the objective function.
\item We have rewritten the reduced complexity spatial resource allocation (SRA) in Section III-D for better readability.
\item We have shortened the ADMM approach as suggested by the reviewers in Section IV-B.
\item Rigorous convergence analysis is provided for the centralized algorithm in Appendix B.
\item We have included Section V-C on the queue behavior over multiple time instants. We have added Fig. 4 to show the performance of the proposed scheme over the existing precoder design algorithms.
\item We have addressed the issues in the citations and we have provided additional references to prove the convergence of the centralized algorithm as suggested by the reviewers.
\end{enumerate}

### 2015-03-23 Response/response-1.tex
nam_changes
revision_on_comments
updated

@@
 
+\vspace{0.25in}
 \review{We thank the reviewer for providing valuable and insightful comments.}
 
-\begin{itemize}
+\begin{enumerate}
 
@@
 \resp \review{We thank the reviewer for the comment. 
-The Q-WSRM scheme and the proposed schemes are all throughput optimal.
+	\begin{enumerate}
+		\item The reformulation for the problem defined in (6) is required, since the SINR expression in (2) cannot be handled directly in the problem.
+Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), which are the under estimator to the original problem in (6).
+We have provided justifications for the problem formulation in (6) and (16) in the paragraph before (16).
+		\item The Q-WSRM scheme and the proposed schemes are all throughput optimal.
 It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aim at minimizing the number of backlogged packets in addition to avoiding the over allocation of available resources.
@@
 By increasing the exponent \me{q \rightarrow \infty}, we obtain fair allocation at every transmission instant.
-We have included the discussions on the average number of backlogged packets at each instant for different arrival rates in Section V-C on page 13, col.
-1.
-We have provided justifications for the problem formulation in (6) and (16) in page 5, col.
-1, first paragraph.
-The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen easily when the number queue size increases.
+We have included the discussions on the average number of backlogged packets at each instant for different arrival rates in Section V-C.
+		\item The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen easily when the number queue size increases.
 We have clarified this point in the revised manuscript.
-Please refer to the first paragraph in Section III-B.}
+Please refer to the first paragraph in Section III-B.
+	\end{enumerate}
+		}
 
@@
 
-\resp \review{
-	\begin{itemize}
-		\item In the previous manuscript, we primarily focused on evaluating the performance of all schemes by comparing the total number of backlogged packets retained in the system after the current transmission.
+\resp \review{	\begin{enumerate}
+		\item In the previous manuscript, we primarily focused on evaluating the performance of all schemes by comparing the total number of backlogged packets retained in the system after each transmission instant.
 Since the delay is proportional to the average number of backlogged packets in the system, this implies that the delay performance was indirectly evaluated in the previous manuscript.
-In addition, the average delay of a particular user can be reduced by controlling the priority factor \me{a_k} in (6a), which affects the resource allocation.
+In addition, the average delay of a particular user can be reduced by controlling the priority factor \me{a_k} in (6a), which alters the resources allocated to a particular user.
 We have included this statement in the manuscript in Section II-B after (6).
@@
 As can be seen, the proposed methods outperforms the existing schemes.
-	\end{itemize}
+	\end{enumerate}
 	}
@@
 
-\resp \review {
-	\begin{itemize}
+\resp \review {	\begin{enumerate}
 	\item We thank the reviewer for the comment.
@@
 The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D.
-	\end{itemize}
+	\end{enumerate}
 }
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 		\item The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require a large number of iterations for the convergence.
@@
 The distributed algorithm for the time correlated case is not provided in the current manuscript, since it is not in the scope of the precoder design algorithms considered in this manuscript.
-	\end{itemize}
+	\end{enumerate}
 	}
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 		\item We have defined those variables in the revised manuscript on Section VI-B
@@
 		\item We have revised the manuscript to avoid the subscript confusions in the ADMM approach. 
-	\end{itemize}}
+	\end{enumerate}}
 
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 		\item The heuristic part is that instead of updating the involved variables sequentially, we allow all the variables to be updated at the same time.
@@
 We have provided additional details on the convergence of the KKT based approach in page 10, col 1, last paragraph.
-	\end{itemize}}
+	\end{enumerate}}
 
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 		\item We agree with the reviewer comment and is in line with Q.2. Please refer to the response for the comment on delay as the performance metric discusion. 
@@
 In addition to that, we can also change the objective to \me{\ell_2} and \me{\ell_{\infty}} norm to address the delay and the fairness implicitly.
-It is included in Section II-B after (6) and in the itemized listing following (7).
-	\end{itemize}}
+It is included in Section II-B after (6) and in the enumerated listing following (7).
+	\end{enumerate}}
 
@@
 
-\end{itemize}
+\end{enumerate}

### 2015-03-23 Response/reviewer_response.tex
updated

@@
-\documentclass[11pt,letterpaper,onecolumn]{article}
+\documentclass[10pt,letterpaper,onecolumn]{article}
 
-\usepackage[left=1.15in,right=1.15in]{geometry}
+\usepackage[left=1.25in,right=1.25in,top=1in,bottom=1in]{geometry}
 \usepackage{amsmath,amssymb}
@@
 
+\input{./../Report/shortcuts}
+\input{./../Report/acronyms}
+
 \renewcommand \thesection{\Roman{section}}
@@
 
-\input{./../Report/shortcuts}
-\input{./../Report/acronyms}
-
 \begin{document}
 
-\title{Reviewer's Comments \& Author's Replies}
+\title{Reviewers Comments \& Authors Replies}
 
+\date{}
+\author{}
 \maketitle
@@
 \textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\
-\textbf{Title} & "Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\
+\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\
 \textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
@@
 
-\vspace{1in}
+\vspace{0.5in}
 The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality.
@@
 The revisions in the revised manuscript are highlighted using blue color and the authors responses are also presented in blue color text.
-Following are the revisions made in the revised manuscript.
+Following is the summary of the revision made on the manuscript in accordance with the reviewers comments.
 \input{additions}

### 2015-03-23 Report/convergence_centralized.tex
updated

@@
 	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
-	%\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
+	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
 \end{itemize}
@@
 A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied.
-Since the feasible set is not fixed in each iteration, we require additional condition (c) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
+Since the feasible set is not fixed in each iteration, we require the conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
 Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th.
@@
 \begin{itemize}
-\item[(i)] all accumulation points will be a generalized fixed points,
+\item[(i)] all accumulation points will be a fixed point,
 \item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
@@
 
-To show the set of fixed points \me{\mc{F}^\ast} are the minimizers for the objective function \me{f}, we can rely on the strict monotonicity of the objective function for each iteration.
+To show the set of fixed points \me{\mc{F}^\ast} are the minimizers for the objective function \me{f}, we rely on the strict monotonicity of the objective function for each iteration.
 Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\ma^\ast \in \mc{A}(\ma^\ast)}, which is a generalized fixed point.
@@
 
-%If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
+If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
 The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{meyer1976sufficient,zangwill1969nonlinear}.
@@
 
-%\subsection{Uniqueness}
+\subsection{Uniqueness}
 
@@
 
+%Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
+The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations.
+When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
+To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
+
 \subsection{Stationary Points of the Nonconvex Problem}
@@
 where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a generalized fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using the discussions in \cite{marks1978technical,lanckriet2009convergence}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
-Using this argument, the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\}}, which is a minimizer in its local neighborhood, is a stationary point of \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+Using \cite{marks1978technical} and \cite[Theorem 10]{lanckriet2009convergence}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
+Since the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a minimizer in its local neighborhood and the limiting point of the algorithm \me{\mc{A}} under the mapping \me{f}, it is a stationary point of the nonconvex problem in \eqref{con} by satisfying the constraint qualifications over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
 The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires \me{\mbf{0}^\tran \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions, where \me{\partial f_0(\mz_{\ast})} denotes the subdifferential set.
-Using the above arguments, we can show that the \ac{JSFRA} schemes reaches a stationary point of the original nonconvex problem.
+Using the above arguments, we can show that the \ac{JSFRA} schemes reaches a stationary point of the nonconvex problem.

### 2015-03-23 Report/dual_approach.tex
updated nam comments review should be modified
updated

@@
-In this section, we discuss the \ac{ADMM} approach to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}.
+The \ac{ADMM} approach is used to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}.
 The \ac{ADMM} is preferred over the \ac{DD} approach in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}.
 In contrast to the \acl{PD}, the \ac{ADMM} approach relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
-Similar decomposition for the precoder design in the minimum power context is considered in \cite{admm_robust}.
+Similar approach for the precoder design in the minimum power context is considered in \cite{admm_robust}.
 
 Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{i}} iteration as
-{\allowdisplaybreaks
-\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}
+\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks
 &\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
@@
 & \text{and } \eqsub \eqref{eqn-8}
-\end{IEEEeqnarray}}
+\end{IEEEeqnarray}
 where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{i}} iteration as
@@
 \end{equation}
-The dual vector for the next iteration is updated by using subgradient to maximize the dual objective as
+The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
 \begin{equation}
@@
 \end{equation}
-where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}, which depend on the system model under consideration.
-The convergence rate of the distributed algorithm is susceptible to the choice of the step size parameter \me{\rho}.
-For our simulation models, we consider the step size parameter \me{\rho=2}.
+where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration.
+The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}.
+For our simulation models, we consider step size parameter \me{\rho=2}.
 The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.
-The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
-{\allowdisplaybreaks 
+The distributed precoder design using the \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
+The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
 \begin{algorithm}
@@
 	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
-	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
+	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying \eqref{power_update}}
 	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
@@
 				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
-				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
-				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
+				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
 				\me{j = j + 1}\;
 			}
-			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
-			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
+			precoded downlink pilot transmission with \me{\mvec{m}{l,k,n}}\;
+			update \me{\mvec{w}{l,k,n}} to all \acp{BS} in \me{\mc{B}} using precoded uplink pilots \cite{komulainen2013effective}\;
 			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
@@
 	\label{algo-3}
-\end{algorithm}}
+\end{algorithm}
+\vspace{-0.15in}
 

### 2015-03-23 Report/kkt_mse_approach.tex
updated

@@
  \Repeat{until convergence or \me{i \geq I_{\max}}}{
-	update \me{\mvec{m}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform downlink transmission \;
+	update \me{\mvec{m}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.3}, and perform precoded downlink pilot transmission \;
 	find \me{\mvec{w}{l,k,n}^{(i)}} using \eqref{kkt-mse-4.6} at each user \;

### 2015-03-23 Report/simulation_distributed.tex
revised
updated nam comments review should be modified
updated

@@
-The distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points.
+The distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update.
 \review{Fig.
-\ref{fig-d} compares the performance of the algorithms for the configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS} with the \ac{PL} varies uniformly between \me{[0,-6]} dB}.
-Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets at each \ac{BS}.
-The number of queued packets is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
+\ref{fig-d} compares the performances of the algorithms with the \ac{PL} varies uniformly between \me{[0,-6]} dB}.
+Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets, whith the queued packets for each user is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
 As discussed in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update.
 Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{fig-3-2}
-	\caption{Convergence of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
-	\label{fig-d}
-\end{figure}
 
 Fig.
-\ref{fig-d} plots the performance of the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using the \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} point.
+\ref{fig-d} compares the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using the \ac{SCA} and by \ac{MSE} relaxation using the number of backlogged packets.
 In between the \ac{SCA} updates, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables.
-In Fig.
+The number of backlogged packets only at the \ac{SCA} points are marked in the figure.
+The performance of the distributed approaches are similar to the centralized schemes if the primal and dual updates are performed until convergence.
+%In Fig.
 \ref{fig-d}, the total number of backlogged packets at each \ac{SCA} points are plotted without the inner loop iterations of \me{J_{\max}} times for the primal or the dual variables convergence.
-It can be seen from Fig.
-\ref{fig-d} that the distributed algorithms approach the centralized performance by exchanging minimal information between the coordinating \acp{BS}.
+%It can be seen from Fig.
+\ref{fig-d} that the distributed algorithms approach the centralized scheme by exchanging minimal information between the coordinating \acp{BS}.
 \begin{figure}
@@
 	\includegraphics[width=\columnwidth]{fig-9-3}
-	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
+	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace}}
 	\label{fig-d-3.1}
@@
 \review{Fig.
-\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB}.
-The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective.
+\ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB}.
+The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other schemes due to the greedy objective.
 The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}.
-If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one.
+If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}.
 A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig.
-\ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}.
-It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function.
-It can be seen that the heuristic method oscillates near the stationary point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
+\ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when \me{Q_k - t_k < 0}.
+It addresses the over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective.
+It can be seen that the heuristic method oscillates near the converging point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
+The objective values are mentioned in the legend for all the schemes and the objective of the \me{\ell_2} norm is not the same as that of the \me{\ell_1} norm used for plotting.
 \begin{figure*}
 	\centering
-	\subfloat[][Average backlogged packets in the system after \me{100} transmission instants]{
-		\includegraphics[width=0.48\textwidth]{average_queue_over_time}
+	\subfloat[][Average backlogged packets in the system after \me{250} transmission instants]{
+		\includegraphics[width=0.48\textwidth]{average_queue_over_time-2}
 		\label{fig-review}
@@
 	\hfill
-	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 5} bits]{
-		\includegraphics[width=0.48\textwidth]{instant_queue_over_time}
+	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 6} bits]{
+		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-2}
 		\label{fig-review-time}
 	}
-	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
+	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace}}
 	\label{fig-time-analysis}
 \end{figure*}
-
-The objective values are mentioned in the legend for all the schemes and the objective of the \me{\ell_2} norm is not the same as that of the \me{\ell_1} norm used for plotting.
-For simulations, we update all variables in \eqref{kkt-mse-4} at once at each iteration, \textit{i.e}, \me{J_{\max} = 1}, which is well justified for the practical implementations due to the signaling overheads.
-The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} approach achieves nearly the same value of \me{6.62} with different \me{\chi}, due to the limited number of iterations for the dual variable convergence between each \ac{SCA} update.
+%The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} approach achieves nearly the same value of \me{6.62} with different \me{\chi}, due to the limited number of iterations for the dual variable convergence between each \ac{SCA} update.
 Fig.

### 2015-03-23 Report/convergence_centralized.tex
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.

--- 2015-03-20 Report/convergence_centralized.tex
@@
 where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a generalized fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using the discussions in \cite{marks1978technical,lanckriet2009convergence}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
+Using \cite{marks1978technical} and \cite[Theorem 10]{lanckriet2009convergence}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
 Using this argument, the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\}}, which is a minimizer in its local neighborhood, is a stationary point of \eqref{con} satisfying the constraint qualifications and the \ac{KKT} expressions over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
 The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires \me{\mbf{0}^\tran \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions, where \me{\partial f_0(\mz_{\ast})} denotes the subdifferential set.
-Using the above arguments, we can show that the \ac{JSFRA} schemes reaches a stationary point of the original nonconvex problem.
+Using the above arguments, we can show that the \ac{JSFRA} schemes reaches a stationary point of the nonconvex problem.

### 2015-03-23 Report/dual_approach.tex
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.

@@
 The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
-\begin{algorithm}
+\begin{algorithm}\allowdisplaybreaks 
 	\SetAlgoLined
@@
 	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
-	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying \eqref{power_update}}
+	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
 	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
@@
 				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
-				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
+				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
+				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
 				\me{j = j + 1}\;
 			}
-			precoded downlink pilot transmission with \me{\mvec{m}{l,k,n}}\;
-			update \me{\mvec{w}{l,k,n}} to all \acp{BS} in \me{\mc{B}} using precoded uplink pilots \cite{komulainen2013effective}\;
+			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
+			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
 			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
@@
 \end{algorithm}
-\vspace{-0.15in}
 

### 2015-03-23 Report/simulation_distributed.tex
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.

--- 2015-03-03 Report/simulation_distributed.tex
@@
 \review{Fig.
-\ref{fig-d} compares the performance of the algorithms for the configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS} with the \ac{PL} varies uniformly between \me{[0,-6]} dB}.
+\ref{fig-d} compares the performances of the algorithms for the configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS} with the \ac{PL} varies uniformly between \me{[0,-6]} dB}.
 Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets at each \ac{BS}.
@@
 Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{fig-3-2}
-	\caption{Convergence of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
-	\label{fig-d}
-\end{figure}
 
@@
 \review{Fig.
-\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB}.
+\ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB}.
 The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective.
@@
 	\subfloat[][Average backlogged packets in the system after \me{100} transmission instants]{
-		\includegraphics[width=0.48\textwidth]{average_queue_over_time}
+		\includegraphics[width=0.48\textwidth]{average_queue_over_time-1}
 		\label{fig-review}

### 2015-03-23 Response/response-4.tex
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.
Revert "Revert "updated""
This reverts commit 7f4566394f3cbd139d9d5f35e92fa51734a0d5ea.

@@
-This paper proposes a practical method for minimizing the number of currently backlogged packets in a wireless multicell MIMO-OFDM network.
-Resource allocation is performed over space (beamformers) and frequency (subcarriers), and a norm of the queue deviations is minimized.
-The problem studied is very relevant, but still most work in the literature has so far focussed on the infinite queue model which clearly does not reflect reality particularly well.
+This paper proposes a practical method for minimizing the number of currently backlogged packets in a wireless multi-cell MIMO-OFDM network.
+Resource allocation is performed over space (beamformers) and frequency (sub-carriers), and a norm of the queue deviations is minimized.
+The problem studied is very relevant, but still most work in the literature has so far focused on the infinite queue model which clearly does not reflect reality particularly well.
 The proposed methods seem practical, due to their possibility to be implemented as distributed methods coupled with distributed CSI acquisition.

### 2015-03-23 Report/conclusions.tex
Revert "Revert "updated""
This reverts commit 7f4566394f3cbd139d9d5f35e92fa51734a0d5ea.

@@
 We proposed the \ac{JSFRA} scheme by relaxing the nonconvex \ac{DC} constraint by a sequence of convex subsets using the \ac{SCA} for designing the precoders to minimize the total number of user queued packets.
-Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using the \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers.
-We also proposed distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
+Additionally, an alternative \ac{MSE} reformulation approach is also proposed by using the \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers.
+We also proposed various methods to decentralize the precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
 Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method.
 The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations.
-Numerical results are used to compare the performances of the proposed algorithms with the existing solutions.
-The distributed design for the time correlated fading will be considered in future.
+Numerical results are used to compare the performances of the proposed algorithms.

### 2015-03-23 Report/simulation_results.tex
updated nam comments review should be modified
Revert "Revert "updated""
This reverts commit 7f4566394f3cbd139d9d5f35e92fa51734a0d5ea.

@@
 
-Table \ref{tbl-1} tabulates the channel seen by the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the band-wise \ac{Q-WSRM} scheme using the \ac{WMMSE} design \cite{wmmse_shi}.
-The performance metric used for the comparison is the total number of backlogged bits left over at each slot after the allocation, which is denoted as \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
+Table \ref{tbl-1} tabulate the channels of the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the sub-channel wise \ac{Q-WSRM} scheme using the \ac{WMMSE} design \cite{wmmse_shi}.
+The metric used for the comparison is the total number of backlogged bits left over after each transmission, which is denoted as \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
 Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} is scheduled in the first sub-channel due to the better channel condition.
-In contrast, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets waiting at the transmitter.
-The rate allocated for \me{\mc{U}(2)} on the second sub-channel is higher in \ac{JSFRA} scheme compared to the other schemes.
+In contrast, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets.
+The rate allocated for \me{\mc{U}(2)} on the second sub-channel is higher in \ac{JSFRA} scheme compared to the others.
 It is due to the efficient allocation of the total power shared across the sub-channels.
@@
 \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{fig-3-2}
+	\caption{Convergence of the centralized and the distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
+	\label{fig-d}
+\end{figure}
 
-The performance of the centralized algorithms are compared in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
+The comparison is made in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
 \ref{fig-a}.
 The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets are few in number.
-In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation by including the explicit rate constraint to avoid the over-allocation.
-It can be seen that the \ac{JSFRA} algorithms converges to a final point for all formulations.
-
+In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation with the explicit rate constraint to avoid the over-allocation.
 For both scenarios in Fig.
 \ref{fig-a}, the \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the algorithm.
-The performance loss is  attributed to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
+It is due to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
 Fig.
@@
 In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in Algorithm \ref{algo-1}.
-It is also noted that the degradation by performing combined update is marginal, since the receiver minimizes the objective for a fixed transmit precoders thereby leading to a monotonic convergence.
+The degradation by performing combined update is marginal, since the receiver minimizes the objective for a fixed transmit precoders.
 

### 2015-03-23 Report/time_correlated.tex
Revert "Revert "updated""
This reverts commit 7f4566394f3cbd139d9d5f35e92fa51734a0d5ea.

@@
 Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and they follow the Poisson process.
-We considered a \me{4 \times 1} \ac{MIMO} with \me{N = 4} sub-channels and \me{N_B = 2} \acp{BS}.
-The \ac{PL} is modeled as a uniform random variable \me{[0,-3]} dB.
+The \ac{PL} is modeled as a uniform random variable \me{[0,-6]} dB.
 
@@
 The performance of the \ac{JSFRA} scheme using \me{\ell_2} is similar to the \ac{Q-WSRME} approach in the average number of residual packets after each transmission slot.
-Note that the additional rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence.
-Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are larger than those of the actual transmissions.
+The additional rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence in the stable region, \textit{i.e}, when the average number of backlogged packets is bounded.
+Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are larger than the actual transmissions.
 Fig.
 \ref{fig-time-analysis} shows that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} scheme due to the greedy allocation of serving users with better channel.
-Fig.
-\ref{fig-time-analysis} highlights that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally well compared to the other objectives when the system is in the stable region.
-On contrary, the performance is inferior in the unstable region, since the fair allocation is not effective when the number of backlogged packets is large for all users.
+It also highlights that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally well compared to the other objectives when the system is stable.
+On contrary, the performance is inferior in the unstable region, since the fairness is not effective when the number of backlogged packets is large for all users.
+
+%Fig.
+\subref*{fig-review} also includes the performance of the \ac{JSFRA} scheme using \me{\ell_1} norm in the uncoordinated precoder design and in \ac{TDM} mode.
+The total power constraint is fixed at \me{P_{\max}} on each transmission in the \ac{TDM} mode.

### 2015-03-23 Report/convergence_centralized.tex
nam modified (Appendices)

--- 2015-03-23 Report/convergence_centralized.tex
@@
 \end{multline}}
-Using \eqref{con-sub-set}, we can prove that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
-At each \ac{SCA} iteration, the feasible set includes the optimal point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, thereby, leading to the monotonic decrease in the objective values \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
+Using \eqref{con-sub-set}, we can show that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
+At each \ac{SCA} update, the feasible set includes the limiting point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it leads to a monotonic decrease in the objective values \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
 \iftoggle{single_column}{
@@
 \end{multline}}
-Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches limiting point as \me{k \rightarrow \infty}.
-Note that feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not be a stationary point of \eqref{con}, since it is the minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
+Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limiting point as \me{k \rightarrow \infty}.
+The feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not be a stationary point of \eqref{con}, since it is a minimizer in the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
 
@@
 The convergence and the nonincreasing behavior of the problem follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.}.
-Now, the optimal solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
-Note that the limiting point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is the unique minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
+Now, the solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
+Note that the limiting point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
 
-Finally, to prove the global convergence of the iterative algorithm, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
+Finally, to prove the global convergence of the iterative algorithm, we need to show the nonincreasing behavior of the objective function in between the \ac{AO} updates, \textit{i.e}, 
 \iftoggle{single_column}{
@@
 To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
-Since we linearize the convex function in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} using \eqref{con-sub-set}.
+Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by following \eqref{con-sub-set}.
 Using this, we can show the monotonicity of the objective value sequence as
@@
 Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
-The set of accumulation points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
+The set of accumulation points or the limiting points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
 Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
@@
 
+\subsection{Uniqueness}
+
 If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
-The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{meyer1976sufficient,zangwill1969nonlinear}.
+The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}.
 Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\ast} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.
 
-\subsection{Uniqueness}
-
-%The uniqueness of the transmit precoders and the receive beamformers for each convex subproblem is achieved by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
+The uniqueness of the transmit precoders and the receive beamformers for each convex subproblem is achieved by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
 The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations.
 
-%When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
-To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
-%we can regularize the objective with the total transmit power expression without affecting the optimal solution as 
-%\begin{equation*}
-%\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
-%\end{equation*}
-%for some arbitrarily small value of the scaling factor \me{\varphi \approx 0}.
+When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by the constraints \eqref{eqn-8} and \eqref{eqn-mse-1.3}, since they are not active at the minimum of the subproblems.
+To obtain the unique set of transmit precoders and the receive beamformers in all cases, we can regularize the objective of the subproblems as
+\begin{equation}
+\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
+\end{equation}
+where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant to make the objective strongly convex.
+The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
 
@@
 where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a generalized fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using \cite{marks1978technical} and \cite[Theorem 10]{lanckriet2009convergence}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
-Since the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a minimizer in its local neighborhood and the limiting point of the algorithm \me{\mc{A}} under the mapping \me{f}, it is a stationary point of the nonconvex problem in \eqref{con} by satisfying the constraint qualifications over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-The non differentiability of the objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} requires \me{\mbf{0}^\tran \in \partial f_0(\mz_{\ast})} to satisfy the \ac{KKT} conditions, where \me{\partial f_0(\mz_{\ast})} denotes the subdifferential set.
-Using the above arguments, we can show that the \ac{JSFRA} schemes reaches a stationary point of the nonconvex problem.
+Using \cite[Theorem 2]{scutari_1} and \cite[Theorem 10]{lanckriet2009convergence}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
+Since the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} for \me{\mc{A}} under the mapping \me{f}, it is a stationary point of the nonconvex problem in \eqref{con} by satisfying all the constraints over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+Therefore, there exists a Lagrange multipliers that can satisfy the \ac{KKT} conditions of the nonconvex problem in \eqref{con}.
+The local optimality of the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\}} is not guaranteed by the algorithm \me{\mc{A}}.

### 2015-03-23 Report/convergence_distributed.tex
nam modified (Appendices)

@@
 The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if the primal or the \ac{ADMM} updates are iterated until convergence.
+
+Unlike \ac{PD} or \ac{ADMM} schemes, the decomposition via \ac{KKT} conditions for the \ac{MSE} reformulation discussed in Section \ref{sec-4.3}, all variables are update at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient.
+It is not guaranteed to obtain the same point as that of the centralized problem.
+
+The algorithm in \eqref{kkt-mse-4} is identical to \eqref{eqn-mse-2}, if the receivers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed to find the optimal transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}.
+Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, the dual variable update loop and the bisection method to find the transmit precoders.
+To avoid this, the proposed method performs group update of all variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
+Even though the convergence is not theoretically guaranteed, it converges in all numerical experiments considered in Section \ref{sec-5.2}.
+If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.

### 2015-03-23 Report/kkt_mse_approach.tex
nam modified (Appendices)

@@
 On receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
-Finally, Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
+Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling with the precoded pilots for the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
+The convergence of the algorithm is discussed in Appendix \ref{sec-dist-conv}.
 \begin{algorithm}
@@
 
-\review{Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling with the precoded pilots.
-Unlike \ac{PD} or \ac{ADMM} schemes, all variables are updated at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient.
-It is not guaranteed to obtain the same point as that of the centralized problem.
-The algorithm in \eqref{kkt-mse-4} is identical to \eqref{eqn-mse-2}, if the receivers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed to find the optimal transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}.
-Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, the dual variable update loop and the bisection method to find the transmit precoders.
-To avoid this, the proposed method performs group update of all variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
-Even though the convergence is not theoretically guaranteed, it converges in all numerical experiments considered in Section \ref{sec-5.2}.
-If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.}
-
 %\subsubsection*{Convergence}

### 2015-03-24 Response/response-2.tex
nam_changes
update locally
revision_on_comments
updated
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.
updated - final - draft

@@
+\vspace{0.25in}
 \review{We would like to thank the reviewer for providing valuable comments.}
-
-\begin{itemize}
+\begin{enumerate}
 
@@
 \resp \review{
-	\begin{itemize}
-		\item Please note that the objective function in the problem formulation is convex, which can be verified by writing the difference function inside the norm operator in epigraph form.
+	\begin{enumerate}
+		\item Please note that the objective function in the problem formulation (16) is convex, since the \me{\gamma_{l,k,n}} is now treated as an optimization variable and not as an expression.
 Since the problem in (16) is not jointly convex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
@@
 Once the linear relaxation is performed, the problem in (20) is a convex optimization problem with the variables being \me{\mvec{m}{l,k,n},\gamma_{l,k,n},\beta_{l,k,n}}.
-The manuscript is updated to illustrate this clearly on the lines following after (19).
-	\end{itemize}
+The manuscript is updated to illustrate this clearly in the lines following after (19).
+	\end{enumerate}
 }
@@
 
-\resp \review{We thank the reviewer for the pointing out the flaw in the text.
-We have removed the incorrect statement on the block coordinate descent method with the AO approach on the fourth paragraph in Section III-B after (16).
+\resp \review{We thank the reviewer for the pointing out the inappropriate text.
+We have removed the incorrect statement on the block coordinate descent method with the AO approach in the paragraph following after (16) in Section III-B.
 Indeed, due to the coupling of the transmit and the receive precoder variables, we cannot use the standard block coordinate descent method proof for the convergence of the proposed algorithm as pointed out by the reviewer.
@@
 \resp \review{We apologize for the inappropriate reference cited in the original manuscript.
-We have provided a completely rewritten proof on the convergence of the centralized algorithm in Appendix B.}
+We have provided a completely rewritten proof on the convergence of the centralized algorithm in Appendix B on the supplementary document.}
 
@@
 
-\resp \review{We agree with the reviewer's comment. We have provided the updated proof for the convergence of the centralized algorithm on Appendix B in the revised manuscript.}
+\resp \review{We agree with the reviewer's comment. We have provided the updated proof for the convergence of the centralized algorithm on Appendix B on the supplementary document.}
 
@@
 
-\resp \review{We have removed the inappropriate citation of the references.}
+\resp \review{We have removed the inappropriate citation of the references. We have provided appropriate references for SCA in [22,32,34].}
 
@@
 Since the problem is convex, the distributed approach convergence can be guaranteed under certain conditions.
-Those are discussed in Appendix C on the convergence analysis for the distributed algorithms.}
+Those are discussed in Appendix C on the convergence analysis for the distributed algorithms on the supplementary document.}
 
@@
 
-\resp \review{We understand the reviewer's concern.
+\resp \review{We thank the reviewer for providing the critical comment.
 We have updated the manuscript to include the descriptions in the text to refer the legends used in the figures.
@@
 \resp \review{
-	\begin{itemize}
-		\item We thank the reviewer for pointing out the issue in the system description for the figures.
+	\begin{enumerate}
+		\item We thank the reviewer for pointing out the issue in the system model description for the figures.
 Please note that the simulation scenario is different for Fig.
@@
 These facts are updated in the revised manuscript on Section V-B third paragraph.
-	\end{itemize}
+	\end{enumerate}
   }
 
-\end{itemize}
+\end{enumerate}

### 2015-03-24 Response/response-3.tex
nam_changes
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.
updated - final - draft

@@
 
+\vspace{0.25in}
 \review{We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helpful in improving the manuscript.}
 
-\begin{itemize}
+\begin{enumerate}
 
@@
 
-\resp \review{Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression and thus \me{t_k} is not a variable.
+\resp \review{Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression and thus \me{t_k} is not required as a variable.
 However, in the MSE formulation, we have explicitly stated the optimization variable \me{t_k}, since it is present in the DC constraint (27).}
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 		\item We thank the reviewer for the insightful comment.
@@
 		\item The under-estimator is tight when there is at least one user in each BS that cannot be served by the current transmission as discussed in Appendix A.
-It has multiple solutions, when the objective is zero even for a single BS.
-In this case, we can use a regularization term with the total power in the objective to obtain an unique solution.
-We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-D.
-	\end{itemize}
+It is not tight when the objective is zero even for a single BS.
+In this case, we can regularize the objective with the total transmitted power as
+		\begin{equation}
+		\|\tilde{\mbf{v}}\|_q + \varphi \, \|\mbf{m}\|^2
+		\end{equation} 
+		where \me{\mbf{m}} is the stacked vector of all transmit precoders.
+Note that the regularized objective makes the inequalities (16b) and (16c) tight at the optimal solution by making the power constraint in (16d) loose.
+It is discussed in the Appendix A provided on the supplementary document.
+	\end{enumerate}
 	 }
 
-\cmnt{3} The solution in (21) is obtianed for MMSE, i.e.
+\cmnt{3} The solution in (21) is obtained for MMSE, i.e.
 for 2-norm(q=2).
@@
 Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
-The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which indeed depend on the value of \me{q}.
+The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which indeed depend on the value of the exponent \me{q} used in \me{\ell_q} norm.
 We have modified the text to include this information on the sentence following after (22).}
@@
 
-\resp \review{We agree with the reviewer.
-Appendix B in the revised manuscript discuss the convergence proof rigorously.
+\resp \review{We thank the reviewer for the comment.
+Rigorous convergence proof for the proposed algorithm is provided in Appendix B on the supplementary document.
 The uniqueness is also justified implicitly by the linear approximation performed on the DC constraint (16b), which makes the transmit precoders to be susceptible to the phase rotation.
-The uniqueness discussions are presented in Appendices B-D.}
+The discussion on the uniqueness is provided in Appendix B-D.}
 
@@
 \resp \review{
-	\begin{itemize}
+	\begin{enumerate}
 		\item We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on the MMSE objective.
 In our solution based on MSE reformulation, we have used the MMSE receiver irrespective of the \me{\ell_q} norm used in the objective.
-		\item Since the receivers are based on the MMSE objective, the equivalence is valid between the MSE and the SINR expression.
+The formulation assumes the MMSE receiver for all exponents used in the objective, and therefore, the precoders can be designed by with the MSE relation.
+		\item The receivers are based on the MMSE objective, and therefore the equivalence is valid between the MSE and the SINR expression.
 Since the transmit precoders are updated in accordance with the objective, the MSE reformulation yields the same solution as the SCA approach based JSFRA scheme presented in Section III-B.
@@
 We have updated the manuscript to include this comments in the lines following (25) in Section III-C.
-	\end{itemize}
+	\end{enumerate}
 	}
@@
 
-\resp \review{We agree with the reviewer's concern.
+\resp \review{
+	\begin{enumerate}
+		\item We agree with the reviewer's concern.
 We have included reference [11] that discusses on the valid choices of the step size parameter for ADMM.
 We have included the statement that it depends on the system model under consideration.
-This information is updated on the manuscript in the lines following after (40).}
+This information is updated on the manuscript in the lines following after (40).
+		\item We considered the JSFRA scheme without the MSE reformulation as a representative example to discuss the distributed schemes.
+Since the rate variables are not included in the optimization problem, we didn't include it as an optimization variables in (37).
+On the contrary, for the MSE reformulation approach, as suggested by the reviewer, we need to have the rate \me{t_k}'s as the optimization variables.
+	\end{enumerate}
+	}
 
-\end{itemize}
+\end{enumerate}

### 2015-03-24 Response/response-4.tex
updated - final - draft

@@
 \review{ First, we thank the reviewer for providing valuable and insightful comments. The comments are really helpful in improving the manuscript.}
-
 \begin{enumerate}
-
 \cmnt{1} {First, this reviewer is not convinced by the arguments for showing the convergence of the JSFRA method.
@@
 \resp \review{We agree that the original manuscript lacks the convergence proof for the JSFRA approach.
-We have presented a rigorous convergence proof for the proposed algorithm in Appendix B after (44).
-We have modified to include the reference suggested by the reviewer in [33] instead of [27] which is for the nonconvex objective function.
-}
+We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on the supplementary document.
+We have modified to include the reference suggested by the reviewer in [32] instead of [27], which is for the nonconvex objective function with the convex constraints.}
 
@@
 	\begin{enumerate}
-	\item We thank the reviewer for the suggestion.
-In this paper, we proposed the precoder design to minimize the number of backlogged packets in the system at a given time.
-Since the greedy approach is performed at each time instant, it minimizes the number of backlogged packets also on an average.
-	\item We focused on the precoder design based on the current knowledge of the channel state information in the simulation results.
-In order to justify the gains over multiple time instants, we have now included Section V-C with Fig.
-4 to discuss on the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots.
+	\item We thank the reviewer for the suggestion. In this paper, we proposed the precoder design to minimize the number of backlogged packets in the system at a given time. Since 
+	the objective is minimized in each time instant, it minimizes the objective on an average as well.
+	\item We focused on the design of the precoders based on the current knowledge of the channel state information in the system model. 
+	\item As suggested by the reviewer, in order to justify the gains over multiple time instants, we have now included Section V-C with Fig.
+4 to compare the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots.
 Plots comparing the average number of backlogged packets for different schemes at each instant and the number of queued packets remained in the system after each transmission instant are provided in Fig.
@@
 	\begin{enumerate}
-		\item We agree with the reviewer's comment. We have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Appendix C. 
+		\item In accordance with the reviewer, we have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Appendix C. 
 		\item For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
@@
 
-\resp \review{We agree with the reviewer's point. We have included the note on the space-frequency terminology in the lines before the last paragraph in Section I.}
+\resp \review{As per the reviewer's suggestion, we have clarified the space-frequency terminology in the lines before the last paragraph in Section I.}
 
-\cmnt{5} {Please see the enumerated questions}
+\cmnt{5} {Please see the itemized questions}
 
@@
 
-\resp \review{We apologize for the wrong reference. We have updated the manuscript to include the proper reference on SCA with [2,3,7,25,26,35].}
+\resp \review{We apologize for the inappropriate reference. We have updated the manuscript to include the proper reference on SCA with [22,32,34].}
 
@@
 
-\resp \review{We removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid confusion as suggested by the reviewer.}
+\resp \review{We removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid the confusion as suggested by the reviewer.}
 
@@
 \resp \review{We thank the reviewer for pointing out the mistake.
-We have included all the constraints except the linearization constraint in (20) which is (19) in the original manuscript.
+We have included all the constraints except the linearization constraint in (20), which is (19) in the original manuscript.
 Expression (19d) and (18) are the same.
@@
 
-\resp \review{We thank the reviewer for providing the valid comment.
+\resp \review{We thank the reviewer for the comment.
 We have updated the manuscript to include this discussion in the sentences after (23).
@@
 Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective.
-Please refer to Appendix B for more details on the convergence analysis of the centralized algorithm.}
+Please refer to Appendix B in the supplementary document for more details on the convergence analysis of the centralized algorithm.}
 
@@
 		\item We thank the reviewer for the critical comment.
-It is true that the convex problem does not need to have a unique solution in general.
-By using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can see that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
+It is true that the convex problem need not required to have a unique solution in general.
+Using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can see that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
 		\item The uniqueness of the solution is obtained due to the linear constraint (19) in the problem formulation (20).
 Note that the linear constraint (19) is susceptible to the phase rotations on the transmit precoders, whereas any unitary rotations on the transmit precoders still satisfies the original nonconvex constraint (16b).
-		\item When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain a unique set of transmit precoders.
+		\item When all the constraints (20) are active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain a unique set of transmit precoders.
 On the contrary, it has multiple solutions when the objective is zero even for a single BS.
-In this case, we can use a regularization term with the total power in the objective to obtain an unique solution.
-We have discussed the uniqueness of the proposed algorithm in detail in Appendices B-D.
+In this case, we can regularize the objective with a strictly convex term as
+		\begin{equation}
+		\|\tilde{\mbf{v}} \|_q + c \, \|\mbf{x} - \mbf{x}^{(i)}\|^2
+		\end{equation}
+		where \me{\mbf{x}} denotes the stacked vector of optimization variables and \me{\mbf{x}^{(i)}} denotes the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
+It is discussed briefly in the Appendix B-D.
 It makes the objective strictly convex, therefore, it has a unique minimum.
@@
 
-\resp \review{We checked the gramatical validity and kept the plural in some cases.}
+\resp \review{We thank the reviewer for pointing out the gramatical errors. We checked the gramatical validity and kept the plural in some cases.}
 

### 2015-03-24 Report/appendix_tightness.tex
updated nam_comments without appendix
updated nam comments review should be modified
updated - final - draft

@@
 \end{comment}
-
 For the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user in each \ac{BS} with enough backlogged packets that cannot be served with the given power budget.
 On the other hand, to make the constraints active in all cases, the objective of the \ac{JSFRA} formulation should be regularized with the transmit power without affecting the solution as
-\begin{equation*}
-\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
-\end{equation*}
+\begin{equation}
+\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right )
+\end{equation}
 where \me{\varphi \approx 0}. Note that the modified objective will relax the power constraint by making the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} active at the final solution.

### 2015-03-24 Report/convergence_centralized.tex
updated - final - draft

@@
-\newcommand{\eqn}[1]{\(#1\)}
-\newcommand{\mx}{\mbf{m}}
-\newcommand{\my}{\mbf{w}}
-\newcommand{\mz}{\mbfa{\gamma}}
-\newcommand{\mxb}{{{\mbf{m}}}}
-\newcommand{\myb}{{{\mbf{w}}}}
-\newcommand{\iterate}[2]{{#1}^{(#2)}}
-\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
-\newcommand{\ma}{\mbf{x}}
-
 To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
@@
 Since the feasible set is not fixed in each iteration, we require the conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
-Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th.
-3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
-Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence} to show that the limiting point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Theorem 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
+Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limiting point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
 \subsection{Bounded Objective Function and Compact Feasible Set}
-
 The feasible set of the problem \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.
@@
 \subsection{Monotonicity} \label{mcity}
-
 Let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
@@
 Using \eqref{con-sub-set}, we can show that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
-At each \ac{SCA} update, the feasible set includes the limiting point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it leads to a monotonic decrease in the objective values \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
+At each \ac{SCA} update, the feasible set includes the limiting point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it ensures monotonic decrease in the objective values \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
 \iftoggle{single_column}{
@@
 \subsection{Convergence of the Beamformer iterates}
-
 Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
@@
 \subsection{Uniqueness}
-
 If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
@@
 The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
-
 %Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
@@
 \subsection{Stationary Points of the Nonconvex Problem}
-
-Finally, to show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
+To show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
+\iftoggle{single_column}{
+\begin{equation} \label{con-opt}\allowdisplaybreaks
+f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) = 
+f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
+\end{equation}}{
 \begin{multline} \label{con-opt}\allowdisplaybreaks
@@
 f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
-\end{multline}
+\end{multline}}
 where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a generalized fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using \cite[Theorem 2]{scutari_1} and \cite[Theorem 10]{lanckriet2009convergence}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
-Since the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} for \me{\mc{A}} under the mapping \me{f}, it is a stationary point of the nonconvex problem in \eqref{con} by satisfying all the constraints over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Therefore, there exists a Lagrange multipliers that can satisfy the \ac{KKT} conditions of the nonconvex problem in \eqref{con}.
-The local optimality of the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\}} is not guaranteed by the algorithm \me{\mc{A}}.
+Using \cite[Theorem 10]{lanckriet2009convergence} and \cite[Theorems 2,11]{scutari_1}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
+Since the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} for \me{\mc{A}} under the mapping \me{f}, it is a stationary point of \eqref{con} over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+The feasible point need not be a local optimum for the nonconvex problem unless all the constraints are inactive, \textit{i.e}, if it is inside the feasible set \me{\mc{F}} where the Lagrange multipliers are all zero to satisfy the complementary slackness criterion.

### 2015-03-24 Report/convergence_distributed.tex
updated - final - draft

@@
-The convergence of the distributed algorithm outlined in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5} if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
+The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
+The feasible set of the problem in \eqref{eqn-decent-1} satisfies the Slater's constraint by having a non-empty interior and is also compact.
+Since the subproblem in \eqref{eqn-decent-1} is convex, the convergence of the primal and the \ac{ADMM} scheme can be guaranteed by using the discussions in \cite{bertsekas1999nonlinear,boyd2011distributed} and \cite[Prop.
+4.2]{bertsekas1989parallel}.
+
+Unlike the primal or the \ac{ADMM} methods, the decomposition via \ac{KKT} conditions for the \ac{MSE} reformulation discussed in Section \ref{sec-4.3}, all variables are updated at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
+It is not guaranteed to obtain the same point as that of the centralized problem.
+
+The algorithm in \eqref{kkt-mse-4} is identical to \eqref{eqn-mse-2}, if the receivers \me{\mvec{w}{l,k,n}} and the \ac{MSE} operating point \me{\epsilon_{l,k,n}^{(i-1)}} are fixed to find the optimal transmit precoders \me{\mvec{m}{l,k,n}} and the dual variable \me{\alpha_{l,k,n}}.
+Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, the dual variable update loop and the bisection method to find the transmit precoders.
+
+To avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
+Even though the optimization variables are updated together, the monotonicity of the objective still follows from the arguments presented in Appendix \ref{mcity}.
+Using the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}, the convergence to a stationary point of the nonconvex problem in \eqref{eqn-6} can be guaranteed for the proposed distributed algorithm with the \me{\ell_2} norm.
+It is also verified in all the numerical experiments considered in Section \ref{sec-5.2}.
+
+\begin{comment}
+The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5} if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
 Since the subproblem in \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}.
 The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \rightarrow \infty} \cite{bertsekas1999nonlinear} for a diminishing step size.
-It can be seen that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and bounded due to the total power constraint for the transmit precoders.
+It can be seen that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and the set is compact.
 
@@
 the following conditions are required for the convergence.
-\begin{itemize}
+\begin{itemize} \allowdisplaybreaks
 	\item \me{G,H} should be convex
@@
 4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.
-The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if the primal or the \ac{ADMM} updates are iterated until convergence.
+The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if it is iterated until convergence.
 
-Unlike \ac{PD} or \ac{ADMM} schemes, the decomposition via \ac{KKT} conditions for the \ac{MSE} reformulation discussed in Section \ref{sec-4.3}, all variables are update at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient.
+\subsection{KKT based Decomposition} \label{sec-dist-conv-kkt}
+Unlike \ac{PD} or \ac{ADMM} schemes, the decomposition via \ac{KKT} conditions for the \ac{MSE} reformulation discussed in Section \ref{sec-4.3}, all variables are updated at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient.
 It is not guaranteed to obtain the same point as that of the centralized problem.
@@
 Note that it requires four nested loops to obtain the centralized solution, namely, the receive beamformer loop, \ac{MSE} operating point loop, the dual variable update loop and the bisection method to find the transmit precoders.
+
 To avoid this, the proposed method performs group update of all variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
@@
 If the step size \me{\rho < 1}, the algorithm for \me{\ell_2} norm will converge by using the arguments on controlling overallocation and the nonincreasing objective function, since the earlier iterates are the operating point for the current iteration.
+
+\end{comment}

### 2015-03-24 Report/simulation_distributed.tex
updated - final - draft

--- 2015-03-23 Report/simulation_distributed.tex
@@
 Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{fig-9-3}
+	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace}}
+	\label{fig-d-3.1}
+\end{figure}
 
@@
 \ref{fig-d} that the distributed algorithms approach the centralized scheme by exchanging minimal information between the coordinating \acp{BS}.
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{fig-9-3}
-	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace}}
-	\label{fig-d-3.1}
-\end{figure}
 
@@
 The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}.
-If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}.
-A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig.
-\ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when \me{Q_k - t_k < 0}.
-It addresses the over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective.
-It can be seen that the heuristic method oscillates near the converging point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
-The objective values are mentioned in the legend for all the schemes and the objective of the \me{\ell_2} norm is not the same as that of the \me{\ell_1} norm used for plotting.
+If used for \me{\ell_1} norm, the over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}.
+A heuristic method is proposed in Fig.
+\ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when \me{Q_k - t_k < 0} to addresses the over-allocation.
+The heuristic approach oscillates near the converging point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
+The objective values are mentioned in the legend for all the schemes and the \me{\ell_1} norm is used for comparison.
 \begin{figure*}
@@
 \end{figure*}
-%The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} approach achieves nearly the same value of \me{6.62} with different \me{\chi}, due to the limited number of iterations for the dual variable convergence between each \ac{SCA} update.
+
+\begin{comment}
+The \me{\ell_2} norm for the \ac{JSFRA} and the \ac{KKT} approach achieves nearly the same value of \me{6.62} with different \me{\chi}, due to the limited number of iterations for the dual variable convergence between each \ac{SCA} update.
 Fig.
@@
 On contrary, the \me{\ell_2} norm allocate rates to the users with the higher number of queued packets before addressing the users with the smaller number of queued packets.
-
-\begin{comment}
 

### 2015-03-24 Report/time_correlated.tex
updated - final - draft

@@
-We discuss the performance of the \ac{JSFRA} algorithm for different \me{\ell_q} over multiple transmission slots.
+The performance of the \ac{JSFRA} scheme for different \me{\ell_q} over multiple transmission slots are discussed here.
 It is compared to the existing \ac{Q-WSRME} scheme by varying the average arrival rate \me{A_k} of all users.
@@
 \ref{fig-time-analysis} plots the performances of the centralized algorithms for different \me{\ell_q} values.
-Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and they follow the Poisson process.
+Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and it follows the Poisson process.
 The \ac{PL} is modeled as a uniform random variable \me{[0,-6]} dB.
@@
 Fig.
-\subref*{fig-review} compares various schemes with the average number of backlogged packets present in the system after each transmission slot.
-The performance of the \ac{JSFRA} scheme using \me{\ell_2} is similar to the \ac{Q-WSRME} approach in the average number of residual packets after each transmission slot.
-The additional rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence in the stable region, \textit{i.e}, when the average number of backlogged packets is bounded.
-Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are larger than the actual transmissions.
+\subref*{fig-review} compares the average number of backlogged packets present in the system after each transmission slot for various schemes discussed.
+The performance of the \me{\ell_2} \ac{JSFRA} scheme is similar to the \ac{Q-WSRME} approach in terms of the average number of residual packets.
+The explicit rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence in the stable region, \textit{i.e}, when the average number of backlogged packets is bounded.
+Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the system is unstable.
+It also includes the \me{\ell_1} \ac{JSFRA} scheme in both uncoordinated and in \ac{TDM} mode with the total power fixed to \me{P_{\max}} in each transmission.
+The uncoordinated \ac{JSFRA} performs better than \ac{TDM} mode of operation due to the high \ac{SINR} variations among the users.
+Due to the greedy allocation of the \me{\ell_1} \ac{JSFRA} scheme, the total number of backlogged packets is significantly less compared to the other schemes in Fig.
+\ref{fig-time-analysis}.
+Also the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally well compared to the other objectives when the system is stable, whereas it is inferior in the unstable region, since the fairness is not effective when the number of backlogged packets is large.
 Fig.
-\ref{fig-time-analysis} shows that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} scheme due to the greedy allocation of serving users with better channel.
-It also highlights that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally well compared to the other objectives when the system is stable.
-On contrary, the performance is inferior in the unstable region, since the fairness is not effective when the number of backlogged packets is large for all users.
+\subref*{fig-review-time} compares the number of backlogged packets at each instant for the schemes discussed.
 

### 2015-03-24 Response/additions.tex
updated - final - draft

@@
 \end{enumerate}
+
+Due to the page limitation imposed on the resubmitted manuscript, we have included all the Appendices as a supplementary document in the manuscript central.
+In what follows, the comments are listed, each followed by the corresponding reply from the authors.
+Unless stated explicitly, all the numbered items (figures, equations, references, citations, etc.) in the response letter refer to the revised manuscript.

### 2015-03-24 Response/response-1.tex
updated-reviewer-comments

@@
 
-\vspace{0.25in}
+\vspace{0.1in}
 \review{We thank the reviewer for providing valuable and insightful comments.}
@@
 \begin{enumerate}
-
 \cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6).
@@
 	\item We thank the reviewer for the comment.
-The convergence analysis has been clearly written in the revised manuscript in Appendix B.
+The convergence analysis has been clearly rewritten in Appendix B on the supplementary document.
 The discussions are provided for the convergence of the iterative Algorithm 1, \textit{i.e}, the problem defined in (16).
@@
 Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16).
-The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D.
+The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D on the supplementary document.
 	\end{enumerate}
@@
 \resp \review{The discussions on the convergence of the centralized algorithms is provided in Appendix B and for the distributed algorithms in Appendix C.
-The discussion on the convergence to a stationary point is presented in Appendix B-E.}
+The discussion on the convergence to a stationary point is presented in Appendix B-E on the supplementary document.}
 
@@
 Thus, we sacrifice the formal convergence for the improved speed of convergence.
-We have provided additional details on the convergence of the KKT based approach in page 10, col 1, last paragraph.
+		\item Note that for \me{\ell_2} norm in the objective, the objective decreases monotonically, which can be seen by setting \me{J_{\max} = I_{\max} = 1} in the distributed algorithm presented in Algorithm 2.
+Following the monotonicity discussion in Appendix B-B, we can show the convergence of the KKT based algorithm to a stationary point [35],[36].
+		\item We have provided additional details on the convergence of the KKT based approach in the Appendix C on the supplementary document.
 	\end{enumerate}}
@@
 \resp \review{Since the problem is nonconvex, the JSFRA formulation can find a stationary point upon convergence.
-The converged point of the JSFRA problem is in fact the stationary point of the original nonconvex problem, which is discussed in Appendix B-E on page 15, col.
-2.
+The converged point of the JSFRA problem is in fact a stationary point of the original nonconvex problem, which is discussed in Appendix B-E provided on the supplementary document.
 We have removed the statement mentioning the Pareto-optimal solutions in the discussions on Fig.

### 2015-03-24 Response/response-3.tex
updated-reviewer-comments

@@
 
-\vspace{0.25in}
+\vspace{0.1in}
 \review{We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helpful in improving the manuscript.}
@@
 \begin{enumerate}
-
 \cmnt{1} The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.
@@
 It is not tight when the objective is zero even for a single BS.
-In this case, we can regularize the objective with the total transmitted power as
+For this, we can regularize the objective with the total transmitted power as
 		\begin{equation}
@@
 		\end{equation} 
-		where \me{\mbf{m}} is the stacked vector of all transmit precoders.
-Note that the regularized objective makes the inequalities (16b) and (16c) tight at the optimal solution by making the power constraint in (16d) loose.
+		where \me{\mbf{m}} is the stacked vector of all transmit precoders and \me{\varphi} is a constant chosen closer to zero without affecting the optimal solution.
+When the original objective is zero, \textit{i.e}, \me{\|\tilde{\mbf{v}}\| = 0}, the the problem becomes the min power design.
+Therefore, when the backlogged packets can be transmitted with the given power constraint, the regularized objective will find a minimum power precoders to empty the backlogged packets.
+It makes the objective tight at the optimal point.
+		\item Note that the regularized objective makes the inequalities (16b) and (16c) tight at the optimal solution by making the power constraint in (16d) loose.
 It is discussed in the Appendix A provided on the supplementary document.

### 2015-03-24 Response/reviewer_response.tex
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.
updated-reviewer-comments

@@
 
-\usepackage[left=1.25in,right=1.25in,top=1in,bottom=1in]{geometry}
+\usepackage[left=1.0in,right=1.0in,top=1in,bottom=1in]{geometry}
 \usepackage{amsmath,amssymb}
@@
 
-\newcommand{\cmnt}[1]{\vspace{0.2in}\item}
-\newcommand{\cmnts}[1]{\vspace{0.2in}\item[(#1)]}
-\newcommand{\resp}{\vspace{0.2in}\item[\textit{\underline{Reply}}:]}
+\newcommand{\cmnt}[1]{\item}
+\newcommand{\cmnts}[1]{\item[(#1)]}
+\newcommand{\resp}{\item[\textit{\underline{Reply}}:]}
 
@@
 \date{}
-\author{}
 \maketitle
 
-\begin{tabular}{p{1.5in}p{4in}}
-\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\
-\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\
+\begin{tabular}{p{1.25in}p{4.25in}}
+\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\ \\
+\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\ \\
 \textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran

### 2015-03-26 Report/convergence_centralized.tex
need to address nam's final comments

@@
 Since the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} for \me{\mc{A}} under the mapping \me{f}, it is a stationary point of \eqref{con} over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-The feasible point need not be a local optimum for the nonconvex problem unless all the constraints are inactive, \textit{i.e}, if it is inside the feasible set \me{\mc{F}} where the Lagrange multipliers are all zero to satisfy the complementary slackness criterion.
+The feasible point need not be a local optimum for the nonconvex problem unless all the constraints are inactive, \textit{i.e}, if the solution is inside the feasible set \me{\mc{F}}.
+In this scenario, the Lagrange multipliers are all zero to satisfy the complementary slackness criterion, and therefore, the solution point is a local optimum of the non convex problem in \eqref{con}.

### 2015-03-27 Report/convergence_centralized.tex
updated with Nams' comment

@@
 \begin{itemize}
-	\item[(a)] The function should be coercive and bounded below
+	\item[(a)] The function should be bounded below
 	\item[(b)] The feasible set should be a compact set
-	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
+	\item[(c)] The sequence of the objective values should be decreasing in each iteration
 	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
 \end{itemize}
-Using \cite[Prop.
-A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied.
-Since the feasible set is not fixed in each iteration, we require the conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
+The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm.
+Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point.
 Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Theorem 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
@@
 The objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
-The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive.
-Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+%The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, and therefore it is coercive in the feasible set.
+%Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
-\subsection{Monotonicity} \label{mcity}
-Let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+\subsection{Monotonicity of the Objective Function} \label{mcity}
+To show the objective decreases monotonically in each iteration, we need to have a nonincreasing objective values in each \ac{SCA} update and also in each \ac{AO} update.
+To prove this, let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
 \begin{subeqnarray} \label{con}
@@
 Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
-Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\my} and \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\mx}.
-Since the \ac{SCA} iterations are performed until convergence, let \me{\iter{\mx}{\ast}{i}} denote the converged point of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
-Let \me{\iter{\mz}{\ast|\my}{i}} be the optimal value of \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iterate for a fixed \me{\my}.
+As the \ac{SCA} iteration converges, let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
+Let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iterate for a fixed \me{\my}.
 
 To begin with, let us consider the variable \me{\my} is fixed for the \ac{AO} \me{i} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
-In order to solve for \me{\mx} in the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate of \me{\mx} as
+In order to solve for \me{\mx} in the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
 \iftoggle{single_column}{
@@
 \end{multline}}
+Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\ast}{i-1}} and \me{\iter{\mx}{k}{i}}.
+Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\ast}{i}} and \me{\iter{\my}{k}{i}}.
 Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
 \begin{subeqnarray} \label{con-m}
-	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \slabel{con-obj-m} \\
-	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \slabel{con-dc-m} \\
-	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0 \eqsub \slabel{con-cvx-blk-m} \\
-	&\quad& g_2(\mx) \leq 0. \eqsub \slabel{con-cvx-m}
+	\underset{\mx,\mz}{\text{minimize}} && f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \slabel{con-obj-m} \\
+	\text{subject to} && h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \slabel{con-dc-m} \\
+	&& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \slabel{con-cvx-blk-m}
 \end{subeqnarray}
-Let the feasible set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
-In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\my = \iter{\my}{\ast}{i-1}} operating at \me{\iter{\mx}{k}{i}}, let us consider that \eqref{con-m} yields \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution for the \me{\ith{k}} iteration.
-Note that the point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality
+The feasible set defined by the problem in \eqref{con-m} is denoted as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
+To prove the convergence of the \ac{SCA} updates in the \me{\ith{i}} \ac{AO} iteration, let us consider that \eqref{con-m} yields
+\me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution in the \me{\ith{k}} iteration.
+The point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality
 \iftoggle{single_column}{
@@
 \end{multline}}
-Using \eqref{con-sub-set}, we can show that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial point of \me{\mx = \iter{\mx}{\ast}{i-1}} was chosen to be feasible from the earlier \ac{AO} iteration \me{i-1}.
-At each \ac{SCA} update, the feasible set includes the limiting point from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it ensures monotonic decrease in the objective values \cite{lanckriet2009convergence,scutari_1,quoc2011sequential} as
+Using \eqref{con-sub-set}, we can show that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{i-1}} \ac{AO} iteration.
+At each \ac{SCA} update, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,quoc2011sequential}
 \iftoggle{single_column}{
@@
 Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limiting point as \me{k \rightarrow \infty}.
+The equality in \eqref{con-convergence} is achieved when the objective converges.
 The feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not be a stationary point of \eqref{con}, since it is a minimizer in the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
 
-Once the solution is found for a fixed \me{\my}, we fix \me{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
+Once the solution is found for a fixed \me{\my}, \me{\my} is optimized by fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}}.
 Even after treating \me{\mx} as a constant, the problem is still nonconvex due to the \ac{DC} constraint.
-Following similar approach, we can find the minimizer \me{\iter{\my}{k}{i}} and \me{\iter{\mz}{k}{i}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}.
-Note that \me{\iter{\mz}{k}{i}} is reused since the variable \me{\mx} is fixed for the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the problem follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.}.
+Following similar approach, we can find the minimizer \me{\iter{\my}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}.
+Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
+The convergence and the nonincreasing behavior of the objective follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.}.
 Now, the solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
-Note that the limiting point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i}}.
+Note that the limiting point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
 
@@
 \end{multline}}
-Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|\my}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
+Let \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
 To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
 Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by following \eqref{con-sub-set}.
-Using this, we can show the monotonicity of the objective value sequence as
-\begin{equation}
+Using this, we can show the monotonicity of the objective sequence as
+\begin{equation} \label{fixed_point}
 f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}).
@@
 The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
-%Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.
+Using (a),(b) and (c), we can guarantee the convergence of the objective value sequence generated by the iterative algorithm.
 
-\subsection{Convergence of the Beamformer iterates}
-Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
-The set of accumulation points or the limiting points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
-Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
-If the mapping is strictly monotonic and uniformly compact, then the following conditions hold \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}.
-\begin{itemize}
-\item[(i)] all accumulation points will be a fixed point,
-\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
-\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
-\end{itemize}
+\subsection{Uniqueness of the Beamformer Iterates}
+The uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be guaranteed by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
+The \ac{MMSE} receiver in \eqref{eqn-10} and the optimal receiver obtained by solving \eqref{eqn-9--1} are also unique for the given set of transmit precoders.
+%The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations.
 
-The mapping \eqn{\mc{A}} for the iterative algorithm is given by
-\begin{equation}
-\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \mc{F}
-\end{equation}
-where \me{\iterate{\ma}{i}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{i})} in the \me{\ith{i}} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations to be performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.}.
-The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as discussed in Appendix \ref{mcity}.
-The sequence of iterates \me{\{\iterate{\ma}{i}\}} will have at least one accumulation point, which follows from the compactness of the set \cite{zangwill1969nonlinear}.
-The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed points \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
-
-To show the set of fixed points \me{\mc{F}^\ast} are the minimizers for the objective function \me{f}, we rely on the strict monotonicity of the objective function for each iteration.
-Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\ma^\ast \in \mc{A}(\ma^\ast)}, which is a generalized fixed point.
-Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizers for the objective function \me{f} over the set \me{\mc{F}}.
-
-\subsection{Uniqueness}
-If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
-The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}.
-Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\ast} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.
-
-The uniqueness of the transmit precoders and the receive beamformers for each convex subproblem is achieved by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
-The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations.
-
-When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by the constraints \eqref{eqn-8} and \eqref{eqn-mse-1.3}, since they are not active at the minimum of the subproblems.
-To obtain the unique set of transmit precoders and the receive beamformers in all cases, we can regularize the objective of the subproblems as
+When the objective is zero, the uniqueness of the transmit precoders are not guaranteed by the constraints \eqref{eqn-8} and \eqref{eqn-mse-1.3}, since they are the under-estimators and need not be active at the minimum.
+To obtain a unique set of transmit precoders and the receive beamformers in all cases, we can regularize the objective with a strongly convex function as
 \begin{equation}
@@
 To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
+
+\subsection{Convergence of the Beamformer Iterates} \label{c-b}
+So far, we have considered the convergence of the objective sequence.
+In this section, we discuss the convergence of the beamformer iterates generated by the iterative algorithm for \eqref{con} using \cite{zangwill1969nonlinear,meyer1976sufficient}.
+Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point in the \eqn{\ith{i}} \ac{AO} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.}.
+Let \me{\mc{A}} be the point-to-set mapping algorithm defined as
+\begin{equation}
+\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}.
+\end{equation}
+Since the algorithm finds a unique solution in each iteration, the mapping denoted by  \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
+Let \me{\mc{F}^\ast \subset \mc{F}} be the set of fixed points, \textit{i.e}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.
+
+By using \cite[Theorem 3.1]{meyer1976sufficient}, we can show the convergence of beamformer iterates to a fixed point as follows.
+\begin{itemize}
+\item The function \me{f} in \eqref{con-m} should continuous and bounded.
+\item The feasible set \me{\iter{\mc{Y}}{\ast}{i}} for each iteration should be compact.
+\item The sequence \me{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} should be strictly monotonic with respect to the objective function \me{f}, \textit{i.e}, \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
+\end{itemize}
+Note that the above conditions are satisfied by the proposed algorithm and the strict monotonicity can also be verified from \eqref{fixed_point}.
+Using \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}, we can show that (i) all limiting points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
+The algorithm \me{\mc{A}} finds a unique solution in each iteration, \textit{i.e}, \me{\mc{F}^\ast = \{\ma^\ast\}}, which is a limiting point.
+
+\begin{comment}
+and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
+The set of accumulation or the limiting points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
+Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
+If the mapping is strictly monotonic and uniformly compact, then the following conditions hold \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}.
+\begin{itemize}
+\item[(i)] all accumulation points will be a fixed point,
+\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
+\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
+\end{itemize}
+
+To show that the proposed iterative method satisfies the above conditions,  the mapping \eqn{\mc{A}} for the iterative algorithm is given by
+\begin{equation}
+\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iterate{\mc{X}}{i} \subset \mc{F}
+\end{equation}
+where \me{\mc{A}(\iterate{\ma}{i})} denotes the set of iterates in the subset \me{\iterate{\mc{X}}{i}}, which has the same objective value under the mapping \me{f} in the \me{\ith{i}} iteration The monotonicity of the proposed algorithm is guaranteed based on the arguments presented in Appendix \ref{mcity}.
+The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as in \eqref{fixed_point}.
+Using the above discussions, we can show that the sequence \me{\{\iterate{\ma}{i}\}} converges to a fixed point in the set \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}
+
+The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed points \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
+
+To show the set of fixed points \me{\mc{F}^\ast} are the minimizers for the objective function \me{f}, we rely on the strict monotonicity of the objective function for each iteration.
+Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\ma^\ast \in \mc{A}(\ma^\ast)}, which is a generalized fixed point.
+Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizers for the objective function \me{f} over the set \me{\mc{F}}.
+
+If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
+The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}.
+Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\ast} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.
+\end{comment}
 
@@
 \end{multline}}
-where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a generalized fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using \cite[Theorem 10]{lanckriet2009convergence} and \cite[Theorems 2,11]{scutari_1}, we can show that the generalized fixed point is a stationary point of the nonconvex problem \eqref{con}.
-Since the feasible point \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} for \me{\mc{A}} under the mapping \me{f}, it is a stationary point of \eqref{con} over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
+Using \cite[Theorem 10]{lanckriet2009convergence} and \cite[Theorems 2,11]{scutari_1}, we can show that the fixed point is a stationary point of the nonconvex problem \eqref{con}.
+Since the feasible point  \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} for \me{\mc{A}} under the mapping \me{f} \cite{meyer1976sufficient}, it is a stationary point of \eqref{con} over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
 The feasible point need not be a local optimum for the nonconvex problem unless all the constraints are inactive, \textit{i.e}, if the solution is inside the feasible set \me{\mc{F}}.

### 2015-03-27 Report/convergence_centralized.tex
Revert "Revert "half cooked""
This reverts commit 828874af08a4425d26d224eb9b6c5d90b02b8536.

--- 2015-03-26 Report/convergence_centralized.tex
@@
 \begin{itemize}
-	\item[(a)] The function should be coercive and bounded below
+	\item[(a)] The function should bounded below
 	\item[(b)] The feasible set should be a compact set
-	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
+	\item[(c)] The sequence of the objective values should be decreasing in each iteration
 	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
 \end{itemize}
-Using \cite[Prop.
-A.8]{bertsekas1999nonlinear}, the existence of a global minimizer in the feasible set can be guaranteed if the conditions (a) and (b) are satisfied.
-Since the feasible set is not fixed in each iteration, we require the conditions (c) and (d) to prove the global convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders.
+The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm.
+Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point.
 Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Theorem 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
@@
 The objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
-The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive.
+%The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, therefore it is coercive.
 Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
-\subsection{Monotonicity} \label{mcity}
-Let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+\subsection{Monotonicity of the Objective Function} \label{mcity}
+To show the objective decreases monotonically in each iteration, we need to have a nondecreasing objective values in each \ac{SCA} update and also in each \ac{AO} update.
+To prove the monotonicity, let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
 \begin{subeqnarray} \label{con}
@@
 \end{subeqnarray}
-Let the feasible set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
+Let the feasible set defined by the problem in \eqref{con-m} be represented as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}\footnote{Note that the set \me{\iter{\mc{X}}{k}{i}} is defined for the fixed operating point \me{\iter{\my}{\ast}{i-1}} and similarly the set \me{\iter{\mc{Y}}{k}{i}} is defined based on the fixed \me{\iter{\mx}{\ast}{i}} respectively.}.
 In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\my = \iter{\my}{\ast}{i-1}} operating at \me{\iter{\mx}{k}{i}}, let us consider that \eqref{con-m} yields \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution for the \me{\ith{k}} iteration.
@@
 Using this, we can show the monotonicity of the objective value sequence as
-\begin{equation}
+\begin{equation} \label{fixed_point}
 f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}).
@@
 The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
-%Using the conditions (a),(b) and (c), we can show that the objective values of the iterative algorithm converges to a limiting point or a local optimal point of the original nonconvex problem \eqref{con}.
+Using (a),(b) and (c), we can guarantee the convergence of the objective value sequence generated by the iterative algorithm.
 
-\subsection{Convergence of the Beamformer iterates}
+\subsection{Convergence of the Beamformer Iterates}
+To prove the convergence of the beamformer iterates, we use the discussions presented in \cite{zangwill1969nonlinear,meyer1976sufficient}.
 Let \me{\mbf{\ma} \triangleq [\mx,\my,\mz]} be the stacked vector of the optimization variables and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
-The set of accumulation points or the limiting points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
+The set of accumulation or the limiting points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
 Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
@@
 
-The mapping \eqn{\mc{A}} for the iterative algorithm is given by
+To show that the proposed iterative method satisfies the above conditions,  the mapping \eqn{\mc{A}} for the iterative algorithm is given by
 \begin{equation}
-\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \mc{F}
+\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iterate{\mc{X}}{i} \subset \mc{F}
 \end{equation}
-where \me{\iterate{\ma}{i}} belongs to the set of equally valid iterates \me{\mc{A}(\iterate{\ma}{i})} in the \me{\ith{i}} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations to be performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.}.
-The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as discussed in Appendix \ref{mcity}.
-The sequence of iterates \me{\{\iterate{\ma}{i}\}} will have at least one accumulation point, which follows from the compactness of the set \cite{zangwill1969nonlinear}.
+where \me{\mc{A}(\iterate{\ma}{i})} denotes the set of iterates in the subset \me{\iterate{\mc{X}}{i}}, which has the same objective value under the mapping \me{f} in the \me{\ith{i}} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations to be performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.}.
+The monotonicity of the proposed algorithm is guaranteed based on the arguments presented in Appendix \ref{mcity}.
+
+The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as in \eqref{fixed_point}.
+Using the above discussions, we can show that the sequence \me{\{\iterate{\ma}{i}\}} converges to a fixed point in the set \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}
+
 The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed points \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.

### 2015-03-30 Report/convergence_centralized.tex
latest changes

--- 2015-03-27 Report/convergence_centralized.tex
@@
 The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm.
-Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point.
-Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Theorem 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
+Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point \cite{meyer1976sufficient}.
+Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th.
+3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
 Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limiting point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
@@
 \subsection{Bounded Objective Function and Compact Feasible Set}
-The feasible set of the problem \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.
+The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.
 
@@
 
-\subsection{Monotonicity of the Objective Function} \label{mcity}
-To show the objective decreases monotonically in each iteration, we need to have a nonincreasing objective values in each \ac{SCA} update and also in each \ac{AO} update.
-To prove this, let us express the centralized problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+\subsection{Monotonicity of the Objective Sequence} \label{mcity}
+In this section, we show the nonincreasing behavior of the objective values in each \ac{SCA} and \ac{AO} update.
+Let us consider a general formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
 \begin{subeqnarray} \label{con}
@@
 \end{equation}
-}{
-\begin{align}
+}{\begin{align}
 \mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
@@
 Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
-As the \ac{SCA} iteration converges, let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} in the \me{\ith{i}} \ac{AO} iteration.
-Let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iterate for a fixed \me{\my}.
+Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}.
 
@@
 \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution in the \me{\ith{k}} iteration.
-The point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function, is also feasible for \eqref{con-m} using the following inequality
+The point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function satisfies
 \iftoggle{single_column}{
@@
 \end{multline}}
-Using \eqref{con-sub-set}, we can show that the solution \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} are feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{i-1}} \ac{AO} iteration.
+Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{i-1}} \ac{AO} iteration.
 At each \ac{SCA} update, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,quoc2011sequential}
@@
 \end{multline}}
-Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limiting point as \me{k \rightarrow \infty}.
-The equality in \eqref{con-convergence} is achieved when the objective converges.
-The feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not be a stationary point of \eqref{con}, since it is a minimizer in the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}, for a fixed \me{\my}.
+Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limiting point of the \ac{SCA} as \me{k \rightarrow \infty}.
+The equality in \eqref{con-convergence} is achieved upon the \ac{SCA} convergence.
+The feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not to be a stationary point of \eqref{con}, since it is a minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}.
 
-Once the solution is found for a fixed \me{\my}, \me{\my} is optimized by fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}}.
-Even after treating \me{\mx} as a constant, the problem is still nonconvex due to the \ac{DC} constraint.
-Following similar approach, we can find the minimizer \me{\iter{\my}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}.
+Once the solution is found for a fixed \me{\my}, it is then optimized by fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}}.
+Even after treating \me{\mx} as a constant, the problem is nonconvex due to the \ac{DC} constraint.
+Following similar approach as above, we can find a minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}.
 Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
 The convergence and the nonincreasing behavior of the objective follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.}.
-Now, the solution of the converged subproblems with \me{\my} as variable are \me{\iter{\my}{\ast}{i}} and \me{\iter{\mz}{\ast}{i}}.
-Note that the limiting point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
+The limiting point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
 
@@
 \end{equation}
-where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant to make the objective strongly convex.
+where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant.
 The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
@@
 Let \me{\mc{A}} be the point-to-set mapping algorithm defined as
-\begin{equation}
+\begin{equation} \label{algorithm_fixed}
 \iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}.
@@
 
-By using \cite[Theorem 3.1]{meyer1976sufficient}, we can show the convergence of beamformer iterates to a fixed point as follows.
+Using \cite[Th. 3.1]{meyer1976sufficient}, convergence of the iterates to a fixed point can be shown, if the following conditions are satisfied.
 \begin{itemize}
-\item The function \me{f} in \eqref{con-m} should continuous and bounded.
-\item The feasible set \me{\iter{\mc{Y}}{\ast}{i}} for each iteration should be compact.
-\item The sequence \me{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} should be strictly monotonic with respect to the objective function \me{f}, \textit{i.e}, \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
+\item Objective function \me{f} should be bounded and continuous.
+\item The feasible set \me{\iter{\mc{Y}}{\ast}{i}} in each iteration should be compact.
+\item The sequence \me{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} should be strictly monotonic with respect to the objective function \me{f}, \textit{i.e}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
 \end{itemize}
-Note that the above conditions are satisfied by the proposed algorithm and the strict monotonicity can also be verified from \eqref{fixed_point}.
-Using \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}, we can show that (i) all limiting points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
-The algorithm \me{\mc{A}} finds a unique solution in each iteration, \textit{i.e}, \me{\mc{F}^\ast = \{\ma^\ast\}}, which is a limiting point.
+Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{algorithm_fixed} and the strict monotonicity can also be verified from \eqref{fixed_point}.
+Using \cite{zangwill1969nonlinear} and \cite[Th.
+3.1]{meyer1976sufficient}, we can show that (i) all limiting points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
+Even though the fixed points in the set \me{\mc{F}^\ast} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limiting point, \textit{i.e}, \me{\mc{F}^\ast = \{\ma^\ast\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
 
@@
 \subsection{Stationary Points of the Nonconvex Problem}
-To show the stationarity of the fixed points in \me{\mc{F}^\ast}, it must satisfy the \ac{KKT} conditions of \eqref{con}. As \me{i \rightarrow \infty}, it satisfies
+To show the limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}.
+As \me{i \rightarrow \infty}, the objective converges as
 \iftoggle{single_column}{
@@
 \end{multline}}
-where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a fixed point and the minimizer of the objective function \me{f} in the feasible set \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-Using \cite[Theorem 10]{lanckriet2009convergence} and \cite[Theorems 2,11]{scutari_1}, we can show that the fixed point is a stationary point of the nonconvex problem \eqref{con}.
-Since the feasible point  \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast \subset \mc{F}} is a limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} for \me{\mc{A}} under the mapping \me{f} \cite{meyer1976sufficient}, it is a stationary point of \eqref{con} over \me{\iterate{\mc{X}}{i+1}_{\ast} \subset \mc{F}}.
-The feasible point need not be a local optimum for the nonconvex problem unless all the constraints are inactive, \textit{i.e}, if the solution is inside the feasible set \me{\mc{F}}.
-In this scenario, the Lagrange multipliers are all zero to satisfy the complementary slackness criterion, and therefore, the solution point is a local optimum of the non convex problem in \eqref{con}.
+where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the limiting point of \me{\mc{A}} for a given initial point.
+As discussed in Appendix \ref{c-b}, the unique limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a fixed point of \me{\mc{A}}.
+Using \cite[Th.
+10]{lanckriet2009convergence} and \cite[Th.
+2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
+It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limiting point \eqref{con-opt}, by using the linear relaxation \eqref{con-relax} for the nonconvex constraint \cite{marks1978technical}.

### 2015-03-30 Report/convergence_distributed.tex
latest changes

@@
 
-Unlike the primal or the \ac{ADMM} methods, the decomposition via \ac{KKT} conditions for the \ac{MSE} reformulation discussed in Section \ref{sec-4.3}, all variables are updated at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
-It is not guaranteed to obtain the same point as that of the centralized problem.
+Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions for the \ac{MSE} reformulation in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
+Therefore, it is not guaranteed to obtain the same point as that of the centralized problem.
 
@@
 To avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
-Even though the optimization variables are updated together, the monotonicity of the objective still follows from the arguments presented in Appendix \ref{mcity}.
+Since the optimization variables are updated together, it is difficult to prove the monotonicity of the objective in each block update.
+Therefore, it is difficult to prove the convergence of the Algorithm \ref{algo-4} to a stationary point of the original nonconvex problem in \eqref{eqn-mse-1}.
+Even though the convergence is not theoretically guaranteed, it converges in all numerical experiments considered in Section \ref{sec-5.2}.
+
+\begin{comment}
+%Even though the optimization variables are updated together, the monotonicity of the objective still follows from the arguments presented in Appendix \ref{mcity}.
 Using the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}, the convergence to a stationary point of the nonconvex problem in \eqref{eqn-6} can be guaranteed for the proposed distributed algorithm with the \me{\ell_2} norm.
@@
 
-\begin{comment}
 The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5} if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.

### 2015-03-31 Response/response-4.tex
updated-reviewer-comments
antti_changes

@@
 
-\vspace{0.25in}
+\vspace{0.1in}
 \review{ First, we thank the reviewer for providing valuable and insightful comments. The comments are really helpful in improving the manuscript.}
@@
 \resp \review{We have updated the manuscript with the explicit power constraint in (16d) as
-\[\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b\].}
+\begin{equation}
+\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b
+\end{equation}}
 
@@
 	\begin{enumerate}
-		\item We thank the reviewer for the critical comment.
-It is true that the convex problem need not required to have a unique solution in general.
+		\item We thank the reviewer for the critical comment and the suggestion.
+It is true that the convex problem need not have a unique solution in general.
 Using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can see that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
-		\item The uniqueness of the solution is obtained due to the linear constraint (19) in the problem formulation (20).
-Note that the linear constraint (19) is susceptible to the phase rotations on the transmit precoders, whereas any unitary rotations on the transmit precoders still satisfies the original nonconvex constraint (16b).
-		\item When all the constraints (20) are active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain a unique set of transmit precoders.
-On the contrary, it has multiple solutions when the objective is zero even for a single BS.
-In this case, we can regularize the objective with a strictly convex term as
+		\item The uniqueness of the beamformers for the MSE reformulation in (28) is guaranteed due to the MSE constraint (26c), which is susceptible to the transmit beamformer phase rotations.
+		\item On the other hand, the uniqueness of the beamformers for the SCA approach in (20) cannot be guaranteed unless the imaginary part of \me{q_{l,k,n} = \Im \{ \mvec{w}{l,k,n} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} = 0\}.
+It can be achieved by using the MMSE receiver for a randomly chosen initial transmit beamformer.
+		\item The solution is not unique when the objective is zero even for a single BS. In this case, we can regularize the objective with a strictly convex term as
 		\begin{equation}

### 2015-03-31 Report/convergence_centralized.tex
antti_changes

@@
 \subsection{Uniqueness of the Beamformer Iterates}
-The uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be guaranteed by the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
-The \ac{MMSE} receiver in \eqref{eqn-10} and the optimal receiver obtained by solving \eqref{eqn-9--1} are also unique for the given set of transmit precoders.
-%The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations.
+The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed only for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
+However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after certain iteration index, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there can be many solutions satisfying the constraints without changing the objective value.
 
-When the objective is zero, the uniqueness of the transmit precoders are not guaranteed by the constraints \eqref{eqn-8} and \eqref{eqn-mse-1.3}, since they are the under-estimators and need not be active at the minimum.
-To obtain a unique set of transmit precoders and the receive beamformers in all cases, we can regularize the objective with a strongly convex function as
+In general, to ensure the uniqueness of the transmit precoders and the receive beamformers in all iterations, \textit{i.e}, even when the objective value is zero, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized with a strongly convex function.
+Now, the objective function of the \me{\ith{i+1}} iteration is given as
 \begin{equation}
@@
 \end{equation}
-where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant.
+where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant to make the objective strongly convex.
+The uniqueness of the minimizer is guaranteed by the strongly convex objective function \cite{scutari_1}.
+The vector \me{\mbf{x}^{(i)}} is the value of \me{\mbf{x}} obtained from the \me{\ith{i}} iteration.
+
+%The uniqueness of the transmit precoders and the receive beamformers for the \ac{MSE} reformulation in \eqref{eqn-mse-2} can be guaranteed in each iteration by the \ac{MSE} constraint in \eqref{eqn-mse-1.3}.
+The uniqueness of the iterates for the problem in \eqref{eqn-9} can be guaranteed in each convex subproblem if the receivers are matched to the equivalent downlink channel with the initially chosen feasible transmit precoders, \textit{i.e}, \me{q_{l,k,n} = 0 \: \forall \, l,k,n} in \eqref{eqn-wsrm-expr} while beginning the \ac{SCA} iteration.
+%
+%When the objective is zero, the uniqueness of the transmit and the receive beamformers are not guaranteed in both problem formulations, since they are the under-estimators and need not be active at the minimum.
+To obtain a unique set of transmit precoders and the receive beamformers in all scenarios, we can regularize the objective with a strongly convex function as
+%\begin{equation}
+%\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
+%\end{equation}
+%where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant.
 The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
@@
 2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
-It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limiting point \eqref{con-opt}, by using the linear relaxation \eqref{con-relax} for the nonconvex constraint \cite{marks1978technical}.
+It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limiting point \eqref{con-opt}, using the linear relaxation \eqref{con-relax} for the nonconvex constraint \cite{marks1978technical}.

### 2015-03-31 Report/convergence_distributed.tex
antti_changes

@@
 
-Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions for the \ac{MSE} reformulation in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
-Therefore, it is not guaranteed to obtain the same point as that of the centralized problem.
+Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
+Therefore, it is difficult to prove theoretically the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.
 

### 2015-04-02 Response/response-4.tex
Need to update Nam's changes

@@
 		\item The uniqueness of the beamformers for the MSE reformulation in (28) is guaranteed due to the MSE constraint (26c), which is susceptible to the transmit beamformer phase rotations.
-		\item On the other hand, the uniqueness of the beamformers for the SCA approach in (20) cannot be guaranteed unless the imaginary part of \me{q_{l,k,n} = \Im \{ \mvec{w}{l,k,n} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} = 0\}.
+		\item On the other hand, the uniqueness of the beamformers for the SCA approach in (20) cannot be guaranteed unless the imaginary part of \me{q_{l,k,n} = \Im \{ \mvec{w}{l,k,n} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} = 0\}}.
 It can be achieved by using the MMSE receiver for a randomly chosen initial transmit beamformer.

### 2015-04-02 Report/convergence_centralized.tex
Need to update Nam's changes

@@
 3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
-Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limiting point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limit point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
@@
 
-To solve \eqref{con}, we adopt \ac{AO} by fixing a block of varibles and optimize for others \cite{bezdek2002some}.
+To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}.
 In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}.
@@
 \end{multline}}
-Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limiting point of the \ac{SCA} as \me{k \rightarrow \infty}.
+Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limit point of the \ac{SCA} as \me{k \rightarrow \infty}.
 The equality in \eqref{con-convergence} is achieved upon the \ac{SCA} convergence.
@@
 Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the objective follows similar arguments as above\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.}.
-The limiting point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
+The convergence and the nonincreasing behavior of the objective follows similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
 
@@
 \subsection{Uniqueness of the Beamformer Iterates}
-The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed only for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
-However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after certain iteration index, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there can be many solutions satisfying the constraints without changing the objective value.
+The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
+However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} for some iteration, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there are many solutions satisfying the constraints without changing the objective value.
+Similarly, when the objective is non-zero, problem defined in \eqref{eqn-9} has a unique minimizer if the receivers are matched to the respective transmit beamformers, which ensures \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr} while choosing the feasible operating point \me{\iter{\mx}{0}{0}} and \me{\iter{\my}{0}{0}} to begin the iterative procedure.
 
@@
 In this section, we discuss the convergence of the beamformer iterates generated by the iterative algorithm for \eqref{con} using \cite{zangwill1969nonlinear,meyer1976sufficient}.
-Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point in the \eqn{\ith{i}} \ac{AO} iteration\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.}.
-Let \me{\mc{A}} be the point-to-set mapping algorithm defined as
+Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point in the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be the point-to-set mapping algorithm defined as
 \begin{equation} \label{algorithm_fixed}
@@
 \end{equation}
-Since the algorithm finds a unique solution in each iteration, the mapping denoted by  \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
+Since the algorithm finds a unique solution in each iteration,\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.} the mapping denoted by \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
 Let \me{\mc{F}^\ast \subset \mc{F}} be the set of fixed points, \textit{i.e}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.
@@
 Using \cite{zangwill1969nonlinear} and \cite[Th.
-3.1]{meyer1976sufficient}, we can show that (i) all limiting points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
-Even though the fixed points in the set \me{\mc{F}^\ast} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limiting point, \textit{i.e}, \me{\mc{F}^\ast = \{\ma^\ast\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
+3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
+Even though the fixed points in the set \me{\mc{F}^\ast} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e}, \me{\mc{F}^\ast = \{\ma^\ast\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
 
@@
 and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
-The set of accumulation or the limiting points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
+The set of accumulation or the limit points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
 Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
@@
 \subsection{Stationary Points of the Nonconvex Problem}
-To show the limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}.
+To show the limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}.
 As \me{i \rightarrow \infty}, the objective converges as
@@
 \end{multline}}
-where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the limiting point of \me{\mc{A}} for a given initial point.
-As discussed in Appendix \ref{c-b}, the unique limiting point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a fixed point of \me{\mc{A}}.
+where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the limit point of \me{\mc{A}} for a given initial point.
+As discussed in Appendix \ref{c-b}, the unique limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a fixed point of \me{\mc{A}}.
 Using \cite[Th.
@@
 2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
-It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limiting point \eqref{con-opt}, using the linear relaxation \eqref{con-relax} for the nonconvex constraint \cite{marks1978technical}.
+It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limit point \eqref{con-opt}, using the linear relaxation \eqref{con-relax} for the nonconvex constraint \cite{marks1978technical}.

### 2015-04-02 Report/convergence_distributed.tex
Need to update Nam's changes

@@
 
-To avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
-Since the optimization variables are updated together, it is difficult to prove the monotonicity of the objective in each block update.
+In order to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
+Since the optimization variables are updated together, it is difficult to prove the monotonicity of the objective theoretically in each block update.
 Therefore, it is difficult to prove the convergence of the Algorithm \ref{algo-4} to a stationary point of the original nonconvex problem in \eqref{eqn-mse-1}.

### 2015-04-02 Report/system_model.tex
Need to update Nam's changes

@@
 where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
-In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users.
-\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted.}.
-Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
+In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams.\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users.
+\me{L} streams are initialized but after solving the problem, only \me{L_{k,n} \leq L} non-zero data streams are transmitted.} Assuming independent detection of data streams, we can write the signal-to-interference-plus-noise ratio (SINR) as
 \begin{equation}\label{eq:SINR}
@@
 Let \me{Q_k} be the number of backlogged packets destined for user \me{k} at a given scheduling instant.
-The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{{i}^\mathrm{th}} time instant\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.}.
-The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, denoted as \me{Q_k(i+1)}, is given by
+The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{{i}^\mathrm{th}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, denoted as \me{Q_k(i+1)}, is given by
 \begin{equation}
@@
 where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over the \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}\footnote{The upper bound can be achieved by using Gaussian signaling.}.
-The units of \me{t_k} and \me{Q_k} are in bits defined per channel use.
+The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}.\footnote{The upper bound can be achieved by using Gaussian signaling.} The units of \me{t_k} and \me{Q_k} are in bits defined per channel use.

### 2015-04-02 Report/wsrm_formulation.tex
updated - final - draft
ordered algorithm locations
Need to update Nam's changes

@@
 \end{IEEEeqnarray}
-and hence \me{f({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
-In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier}.
-Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively.
+and hence \me{f({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}.\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
+In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.} Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively.
 Using first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality
@@
 \review{Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance or the convergence behavior}.
-
-The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved in an iterative manner by updating the operating point from the previous iteration.
-The iterative algorithm is referred to as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint, and it is outlined in Algorithm \ref{algo-1}.
-The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
-Instead of initializing \me{{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with some feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{{\mbf{u}}_{l,k,n}} as seen in Algorithm \ref{algo-1}.
-For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
-Next, the receive beamformers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
-This procedure is carried out until convergence of the queue deviation or a fixed number of iterations \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
-The convergence proof is discussed in Appendix \ref{sec-3.5}.
-\allowdisplaybreaks
 \begin{algorithm}
@@
 \end{algorithm}
+
+The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved in an iterative manner by updating the operating point from the previous iteration.
+The iterative algorithm is referred to as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint, and it is outlined in Algorithm \ref{algo-1}.
+The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
+Instead of initializing \me{{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with some feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{{\mbf{u}}_{l,k,n}} as seen in Algorithm \ref{algo-1}.
+For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
+Next, the receive beamformers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
+This procedure is carried out until convergence of the queue deviation or a fixed number of iterations \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
+The convergence proof is discussed in Appendix \ref{sec-3.5}.
 

### 2015-04-02 Response/response-1.tex
Updated Nam's response in the reviewer comments

@@
 Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16).
-The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D on the supplementary document.
+The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-C on the supplementary document.
 	\end{enumerate}
@@
 
-\resp \review{The discussions on the convergence of the centralized algorithms is provided in Appendix B and for the distributed algorithms in Appendix C.
+\resp \review{The discussions on the convergence of the centralized algorithms are provided in Appendix B and on the distributed algorithms in Appendix C.
 The discussion on the convergence to a stationary point is presented in Appendix B-E on the supplementary document.}
@@
 \resp \review{Since the sub-channel wise resource allocation considers each sub-channel at a given time for designing the precoders, the performance of this scheme depend on the selection order of the sub-channels.
-For instance, to design the precoders for the sub-channel \me{j+1}, we assume the transmit precoders and the rates of all users are evaluated for the sub-channels \me{\{1,2,\dotsc,j\}}.
+For instance, to design the precoders for the sub-channel \me{j+1}, we assume the transmit precoders and the rates of all users are all evaluated up until previous sub-channels \me{\{1,2,\dotsc,j\}}, considering the normal ordering for selection.
 At this point, we have to estimate the number of backlogged packets left over in the system, if the sub-channels \me{\{1,2,\dotsc,j\}} are transmitted with the precoders designed so far.
 Now, the number of backlogged packets for the \me{\ith{j+1}} sub-channel is given by
-\[\max \Big( Q_k - \sum_{i=1}^j \sum_{l=1}^L t_{l,k,i},0 \Big).\]
-Since it depends on the rates of the already evaluated sub-channels \me{\{1,2,\dotsc,j\}}, it is susceptible to the ordering used to determine the precoders in each sub-channels.
-It is discussed in detail in Section III-D.
+\begin{equation} \label{eqn-1-review}
+\max \Big( Q_k - \sum_{i=1}^j \sum_{l=1}^L t_{l,k,i},0 \Big).
+\end{equation}
+Since \eqref{eqn-1-review} depends on the rates of the already evaluated sub-channels \me{\{1,2,\dotsc,j\}}, the overall achievable throughput is susceptible to the ordering used to determine the precoders in each sub-channels.
+It has been discussed in detail in Section III-D.
 Note that the performance will be closer to the JSFRA centralized scheme, if we select the best sub-channel ordering through an exhaustive search.
-In this case, the performance loss is mainly due to the maximum power constraint on each sub-channel.}
+In this case, the performance loss is mainly due to the maximum power constraint imposed on each sub-channel.}
 
@@
 		\item Note that the size of the channel state information depends on the number of transmit antennas.
-Thus exchanging channels is not efficient when the number of transmit antennas are large.
+Thus exchanging channels is not efficient when the number of transmit antennas is large.
 On the other hand, the amount of exchanging interference vector only depends on the number of base stations.
-In practice, we can limit the primal or ADMM update for few iterations, then the distributed algorithms are still be efficient.
-		\item To this end, we have a practical scheme in Section IV-D.
-Note that in the time-correlated case, it is often also enough to update the precoders once per radio frame.
-The decentralized schemes are never allowed to converge until the end, it is only important to follow the fading process when \me{J_{\max} = 1}.
-The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13] in the revised manuscript, which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+In practice, we can limit the primal or ADMM update for a few iterations, then the distributed algorithms are still be efficient.
+		\item To address this concern, we propose a practical scheme in Section IV-D.
+Note that in the time-correlated case, it is often enough to update the precoders once per radio frame.
+The decentralized schemes are not necessary to converge until the end, it is only important to follow the fading process when \me{J_{\max} = 1}.
+The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13], which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
 The distributed algorithm for the time correlated case is not provided in the current manuscript, since it is not in the scope of the precoder design algorithms considered in this manuscript.
@@
 	\begin{enumerate}
-		\item We have defined those variables in the revised manuscript on Section VI-B
-		\item Since the coupling between the distributed precoder designs are the interference between the BSs and the users, in ADMM approach, the interference is treated as a local variable, which can be included in the precoder design optimization problem for each coordinating BSs.
+		\item We have defined all the variables mentioned by the reviewer in the revised manuscript on Section VI-B
+		\item Since the coupling between the distributed precoder designs are the interference between the BSs and the users, in ADMM approach, the interference is treated as a local variable, which can be included in the precoder design optimization problem for each coordinating BS.
 This is treated as a local (but not the actual interference) variable for a specific BS.
 Since the actual interference caused is different, the consensus has to be made between the local interference variable maintained at each BS with the global consensus interference variable, which is nothing but the average between the corresponding BSs interference.
-These discussions are made in the revised manuscript in Section IV-B.
-For further details, please refer to the Boyd's paper in [11], which discusses exclusively about the ADMM approach.
+These discussions have been made in the revised manuscript in Section IV-B.
+For further details we have also referred the interested reader to [11], which discusses exclusively about the ADMM approach.
 		\item We have revised the manuscript to avoid the subscript confusions in the ADMM approach. 
@@
 
-\resp \review{We understand the reviewer's concern.
-For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
-Note that it includes the cross equivalent downlink channels of the neighbor BS users as well.
+\resp \review{We thank the reveiwer for the valuable comment.
+For the distributed precoder designs, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
+Note that it includes the equivalent downlink channels of all the users in the system.
 To update the MMSE receiver, the equivalent channel for the \me{\ith{k}} user \me{\mbf{H}_{b,k,n} \mvec{m}{l,k^\prime,n}, \forall k^\prime \in \mc{U}_b, \forall b \in \mc{B}} is obtained from the BSs through user specific downlink precoded pilots.
 We have included the information on what each network entity knows in the paragraph after (36).
-We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.}
+We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in the last paragraph of Section II.}
 
@@
 Thus, we sacrifice the formal convergence for the improved speed of convergence.
-		\item Note that for \me{\ell_2} norm in the objective, the objective decreases monotonically, which can be seen by setting \me{J_{\max} = I_{\max} = 1} in the distributed algorithm presented in Algorithm 2.
-Following the monotonicity discussion in Appendix B-B, we can show the convergence of the KKT based algorithm to a stationary point [35],[36].
-		\item We have provided additional details on the convergence of the KKT based approach in the Appendix C on the supplementary document.
+		\item Since the update of the optimization variables are grouped together, it is difficult to prove the monotonicity of the objective function theoretically to prove the convergence of the algorithm.
+However, in all the numerical experiments in Section V-B, the proposed KKT conditions based algorithm converges, which can be seen from Fig.
+3.
+		\item We have provided the discussions on the convergence of the KKT based approach in the Appendix C on the supplementary document.
 	\end{enumerate}}

### 2015-04-02 Response/response-2.tex
updated-reviewer-comments
Updated Nam's response in the reviewer comments

@@
-\vspace{0.25in}
+\vspace{0.1in}
 \review{We would like to thank the reviewer for providing valuable comments.}
 \begin{enumerate}
-
 \cmnt{1} The logic from (6) to (16) is not clear.
@@
 
-\resp \review{We have removed the inappropriate citation of the references. We have provided appropriate references for SCA in [22,32,34].}
+\resp \review{We have removed the inappropriate citation of the references, and provided appropriate references for SCA in [22,32,34].}
 
@@
 
-\resp \review{Please note that the distributed algorithm is performed for the convex subproblem presented in (20) and (28).
+\resp \review{Please note that the distributed algorithm is performed for the \textbf{convex subproblem} presented in (20) and (28).
 Since the problem is convex, the distributed approach convergence can be guaranteed under certain conditions.
@@
 It is presented in the manuscript as an alternative suboptimal approach to perform sub-channel wise distributed precoder design by the centralized controller.
-We have updated the manuscript with more details for better understanding.
+We have updated the manuscript with more details.
 We have also stream-lined the manuscript so that some redundant discussion has been removed here and there.
-We also improved the grammar and fluency.}
+We also improved the grammar and continuity of the paper.}
 
@@
 
-\resp \review{We have included the information regarding the norm used for the simulation in the figure captions. It is updated for Fig. 1 and Fig. 2.}
+\resp \review{We have included the information regarding the norm used for the simulations in the figure captions of Fig. 1 and Fig. 2.}
 
@@
 
-\resp \review{We thank the reviewer for providing the critical comment.
+\resp \review{We thank the reviewer for pointing out the issue.
 We have updated the manuscript to include the descriptions in the text to refer the legends used in the figures.
@@
 		\item We thank the reviewer for pointing out the issue in the system model description for the figures.
-Please note that the simulation scenario is different for Fig.
+Please note that the simulation scenarios are different for Fig.
 2 and Fig.
 3 in terms of path loss distribution and the sub-channel numbers.
-		\item We have provided different scenario with the centralized algorithm as reference for studying the performance under different system model.
+		\item We have provided different scenario with the centralized algorithm as reference for studying the performance under different system models.
 The user path loss is distributed uniformly between $[0,-6]$ dB for Fig.
@@
 3 is \me{[9,16,14,16,9,13,11,12]} bits.
-These facts are updated in the revised manuscript on Section V-B third paragraph.
+These numbers have been updated in the revised manuscript on the third paragraph of Section V-B.
 	\end{enumerate}

### 2015-04-02 Response/response-3.tex
Updated Nam's response in the reviewer comments

@@
 \vspace{0.1in}
-\review{We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helpful in improving the manuscript.}
+\review{We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helps to improve the manuscript.}
 
@@
 \resp \review{Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression and thus \me{t_k} is not required as a variable.
-However, in the MSE formulation, we have explicitly stated the optimization variable \me{t_k}, since it is present in the DC constraint (27).}
+However, in the MSE formulation, we have explicitly stated the optimization variable \me{t_k}, since it is present in the DC constraint (27).
+	\begin{enumerate}
+		\item (6), (16), (20) and (21) does not depend upon the variable \me{t_k}
+		\item (26) and (28) depend on the variable \me{t_k} and it is defined as an optimization variable.
+	\end{enumerate}	
+	}
 
@@
 		\end{equation} 
-		where \me{\mbf{m}} is the stacked vector of all transmit precoders and \me{\varphi} is a constant chosen closer to zero without affecting the optimal solution.
+		where \me{\mbf{m}} is the stacked vector of all transmit precoders and \me{\varphi} is a constant chosen closer to zero such that it has no effect on the optimal solution.
 When the original objective is zero, \textit{i.e}, \me{\|\tilde{\mbf{v}}\| = 0}, the the problem becomes the min power design.
@@
 		\item Note that the regularized objective makes the inequalities (16b) and (16c) tight at the optimal solution by making the power constraint in (16d) loose.
-It is discussed in the Appendix A provided on the supplementary document.
+It is discussed in Appendix A provided on the supplementary document.
 	\end{enumerate}
@@
 The uniqueness is also justified implicitly by the linear approximation performed on the DC constraint (16b), which makes the transmit precoders to be susceptible to the phase rotation.
-The discussion on the uniqueness is provided in Appendix B-D.}
+The discussion on the uniqueness is provided in Appendix B-C.}
 
 \cmnt{5} (25) is generally wrong.
-(25) only holds when the MSE is minimized(by MMSE receiver) and the snr is the optimized(which is obtained by general eignvalue decompostion).
+(25) only holds when the MSE is minimized(by MMSE receiver) and the SNR is the optimized(which is obtained by general Eignvalue decomposition).
 This is clearly stated in the reference [5] and [6].
@@
 	\begin{enumerate}
-		\item We agree with the reviewer's concern.
+		\item We agree with the reviewer's comment.
 We have included reference [11] that discusses on the valid choices of the step size parameter for ADMM.
-We have included the statement that it depends on the system model under consideration.
-This information is updated on the manuscript in the lines following after (40).
+We have included the statement that the parameter \me{\rho} depends on the system model under consideration.
+This information has been updated on the manuscript in the lines following after (40).
 		\item We considered the JSFRA scheme without the MSE reformulation as a representative example to discuss the distributed schemes.
-Since the rate variables are not included in the optimization problem, we didn't include it as an optimization variables in (37).
+Since the rate variables are not included in the optimization problem, we do not include the rate variables \me{t_k} as an optimization variables in (37).
 On the contrary, for the MSE reformulation approach, as suggested by the reviewer, we need to have the rate \me{t_k}'s as the optimization variables.

### 2015-04-02 Response/response-4.tex
Updated Nam's response in the reviewer comments

@@
 We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on the supplementary document.
-We have modified to include the reference suggested by the reviewer in [32] instead of [27], which is for the nonconvex objective function with the convex constraints.}
+We are grateful to the reviewer for bringing our attention to reference [A] which has been cited as [32] in the revised manuscript.
+Some of the arguments in [32] are indeed useful to prove the convergence of the proposed algorithms in our paper.}
 
@@
 	\item We thank the reviewer for the suggestion. In this paper, we proposed the precoder design to minimize the number of backlogged packets in the system at a given time. Since 
-	the objective is minimized in each time instant, it minimizes the objective on an average as well.
+	the objective is minimized in each time instant, it somehow minimizes the objective on an average as well.
 	\item We focused on the design of the precoders based on the current knowledge of the channel state information in the system model. 
@@
 4 to compare the performance of the JSFRA scheme for different \me{\ell_q} norm over multiple time slots.
-Plots comparing the average number of backlogged packets for different schemes at each instant and the number of queued packets remained in the system after each transmission instant are provided in Fig.
-4.
+	\item Fig.
+4(a) demonstrates the performance of the proposed schemes and the existing algorithms using the average number of backlogged packets after each transmission instant for different arrival rates.
+The y-axis denotes the expected number of queued packets in the system after each transmission slot.
+	\item Fig.
+4(b) shows the instantaneous number of backlogged packets of various schemes at each transmission instant.
+In Fig.
+4(b), y-axis shows the total number of backlogged packets in the system after each transmission instant for an average arrival rate of \me{6} bits for all users.
+The x-axis represents the transmission slot at which the backlogged packets are evaluated.
 	\end{enumerate}
@@
 
-\resp \review{As per the reviewer's suggestion, we have clarified the space-frequency terminology in the lines before the last paragraph in Section I.}
+\resp \review{We thank the reviewer for the comment. We have clarified the space-frequency terminology in the lines before the last paragraph in Section I.}
 
@@
 
-\resp \review{We removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid the confusion as suggested by the reviewer.}
+\resp \review{We have removed the matrix representation of the transmit precoders and the receive beamformers from the manuscript to avoid the confusion as pointed out by the reviewer.}
 
@@
 
-\resp \review{We have rephrased the sentence to avoid difficulty in the understanding. The manuscript is updated with the revised text on the first paragraph in Section III.B.}
+\resp \review{We have rephrased the sentence to clarify the meaning. The manuscript has been updated with the revised text on the first paragraph in Section III.B.}
 
@@
 \resp \review{We thank the reviewer for pointing out the mistake.
-We have included all the constraints except the linearization constraint in (20), which is (19) in the original manuscript.
+We have included all the constraints except the linearization constraint in (20), which was (19) in the original manuscript.
 Expression (19d) and (18) are the same.
@@
 \resp \review{To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point.
-Since the operating point happens to be the optimal solution from the earlier iteration, the optimal point of the previous iterations is also present in the current feasible set.
+Since the operating point is the optimal solution from the earlier iteration, the optimal point of the previous iterations is also present in the current feasible set.
 Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective.
@@
 	\begin{enumerate}
-		\item We thank the reviewer for the critical comment and the suggestion.
-It is true that the convex problem need not have a unique solution in general.
-Using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can see that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function.
+		\item We thank the reviewer for the important comment and the suggestion. It is true that the convex problem need not require a unique solution in general. 
 		\item The uniqueness of the beamformers for the MSE reformulation in (28) is guaranteed due to the MSE constraint (26c), which is susceptible to the transmit beamformer phase rotations.
@@
 		where \me{\mbf{x}} denotes the stacked vector of optimization variables and \me{\mbf{x}^{(i)}} denotes the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
-It is discussed briefly in the Appendix B-D.
-It makes the objective strictly convex, therefore, it has a unique minimum.
+It has been discussed in the Appendix B-C.
+It makes the objective strictly convex, therefore, the resulting subproblem has a unique minimizer.
 	\end{enumerate}
@@
 
-\resp \review{We thank the reviewer for pointing out the gramatical errors. We checked the gramatical validity and kept the plural in some cases.}
+\resp \review{We thank the reviewer for pointing out the gramatical errors. We have checked the gramatical validity and kept the plural form in some cases.}
 

### 2015-04-02 Report/convergence_centralized.tex
Updated Nam's response in the reviewer comments

@@
 The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
-However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} for some iteration, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there are many solutions satisfying the constraints without changing the objective value.
-Similarly, when the objective is non-zero, problem defined in \eqref{eqn-9} has a unique minimizer if the receivers are matched to the respective transmit beamformers, which ensures \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr} while choosing the feasible operating point \me{\iter{\mx}{0}{0}} and \me{\iter{\my}{0}{0}} to begin the iterative procedure.
+However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there are many solutions satisfying the constraints without affecting the objective value.
+Similarly, when the objective is non-zero, problem defined in \eqref{eqn-9} has a unique minimizer if the receivers are matched to the corresponding transmit beamformers, \textit{i.e}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr},  while choosing the feasible operating point \me{\iter{\mx}{0}{0}} and \me{\iter{\my}{0}{0}} to begin the iterative procedure.
 

### 2015-04-02 Response/additions.tex
Updated Nam's response in the reviewer comments

@@
 \item We have included Section V-C on the queue behavior over multiple time instants. We have added Fig. 4 to show the performance of the proposed scheme over the existing precoder design algorithms.
-\item We have addressed the issues in the citations and we have provided additional references to prove the convergence of the centralized algorithm as suggested by the reviewers.
+\item We have addressed the issues in the citations and also provided additional references to prove the convergence of the centralized algorithm as suggested by the reviewers.
 \end{enumerate}

### 2015-04-02 Report/convergence_centralized.tex
# WARNING: head commit changed in the meantime
updated Nam's response in the reviewer comments

@@
 However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there are many solutions satisfying the constraints without affecting the objective value.
-Similarly, when the objective is non-zero, problem defined in \eqref{eqn-9} has a unique minimizer if the receivers are matched to the corresponding transmit beamformers, \textit{i.e}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr},  while choosing the feasible operating point \me{\iter{\mx}{0}{0}} and \me{\iter{\my}{0}{0}} to begin the iterative procedure.
+Similarly, when the objective is non-zero, problem defined in \eqref{eqn-9} has a unique minimizer if the receivers are matched to the corresponding transmit beamformers, \textit{i.e}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr},  while choosing a feasible operating point \me{\iter{\mx}{0}{0}} and \me{\iter{\my}{0}{0}} to initialize the iterative procedure.
 

### 2015-04-03 Report/time_correlated.tex
antti changes

--- 2015-03-19 Report/time_correlated.tex
@@
-We discuss the performance of the \ac{JSFRA} algorithm for different \me{\ell_q} over multiple transmission slots.
-It is compared to the existing \ac{Q-WSRME} scheme by varying the average arrival rate \me{A_k} of all users.
-Fig.
-\ref{fig-time-analysis} plots the performances of the centralized algorithms for different \me{\ell_q} values.
-Even though \me{A_k}'s are constant for all users, the instantaneous arrivals are random and they follow the Poisson process.
-We considered a \me{4 \times 1} \ac{MIMO} with \me{N = 4} sub-channels and \me{N_B = 2} \acp{BS}.
-The \ac{PL} is modeled as a uniform random variable \me{[0,-3]} dB.
+In this section, we numerically study the performance of the centralized algorithms with different \me{\ell_q} values over multiple transmission slots.
+The system model examined for the illustrations is provided in Fig.
+\ref{fig-time-analysis}.
+For all users in the system, the average arrivals \me{A_k}'s are fixed and varied equally for the model considered in Fig.
+\subref*{fig-review}, and for Fig.
+\subref*{fig-review-time}, the average arrival is fixed to be \me{A_k = 6} bits.
+Note that the instantaneous arrivals \me{\lambda_k(i)} are all different and it follows the Poisson process.
+The \ac{PL} is modeled as a uniform random variable \me{[0,-6]} dB.
 
 Fig.
-\subref*{fig-review} compares various schemes with the average number of backlogged packets present in the system after each transmission slot.
-The performance of the \ac{JSFRA} scheme using \me{\ell_2} is similar to the \ac{Q-WSRME} approach in the average number of residual packets after each transmission slot.
-Note that the additional rate constraints in the \ac{Q-WSRME} scheme is the reason for the equivalence.
-Both \ac{Q-WSRM} and \ac{Q-WSRME} performs similar to \me{\ell_2} \ac{JSFRA} scheme when the arrival rates are larger than those of the actual transmissions.
+\subref*{fig-review} plots the average of the total number of backlogged packets left out in the system after each transmission instant, \textit{i.e}, \me{\mathbf{\mathrm{E}}_i \, [ \Sigma_k \left [ Q_k(i) - t_k(i) \right ]^+ ]}.
+Unlike the \ac{Q-WSRM} scheme, the average backlogged packets of the \me{\ell_2} \ac{JSFRA} scheme is comparable to the \ac{Q-WSRME} approach for all average arrival rates due to the explicit rate constraints \eqref{eqn-3.1.4}.
+However, when \me{A_k \geq 7} bits in Fig.
+\subref*{fig-review}, both \ac{Q-WSRM} and \ac{Q-WSRME} schemes perform the same since the problem of over-allocation is negligible.
+The performance of the \me{\ell_1} \ac{JSFRA} scheme outperforms all other schemes in terms of the average number of residual packets due to the greedy allocation at each instant.
+
 Fig.
-\ref{fig-time-analysis} shows that the number of backlogged packets are noticeably less for the \me{\ell_1} \ac{JSFRA} scheme due to the greedy allocation of serving users with better channel.
+\subref*{fig-review} also includes the uncoordinated \me{\ell_1} \ac{JSFRA} scheme and the \ac{TDM} mode without considering the inter-cell interference terms in the \ac{SINR} expressions while designing the precoders.
+The \ac{TDM} scheme with the fixed total power constraint performs inferior to the uncoordinated transmission due to the diverse user \ac{PL} variations considered.
 Fig.
-\ref{fig-time-analysis} highlights that the \me{\ell_{\infty}} \ac{JSFRA} scheme performs equally well compared to the other objectives when the system is in the stable region.
-On contrary, the performance is inferior in the unstable region, since the fair allocation is not effective when the number of backlogged packets is large for all users.
+\subref*{fig-review-time} compares the total number of backlogged packets left in the system after each transmission slot by different centralized algorithms.
+The total number of residual packets for the \ac{Q-WSRM} scheme is noticeably large in comparison with the other schemes in Fig.
+\subref*{fig-review-time} due to the inability in controlling the over-allocations at each instant.
+The instantaneous fairness constraint imposed by the \me{\ell_\infty} \ac{JSFRA} scheme is effective in reducing the number of backlogged packets for the average arrival rate considered in Fig.
+\subref*{fig-review-time}.
+However, in Fig.
+\subref*{fig-review}, the \me{\ell_\infty} \ac{JSFRA} performs inferior to the \ac{Q-WSRM} scheme, since the fairness is not effective when the system is unstable, \textit{i.e}, when \me{A_k \geq 7} in the current model.

### 2015-04-06 Response/response-1.tex
removed-tightness-discussion

@@
 		\item The reformulation for the problem defined in (6) is required, since the SINR expression in (2) cannot be handled directly in the problem.
-Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), which are the under estimator to the original problem in (6).
+Note that the equality constraint imposed by the SINR expression in (2) is handled by two explicit inequality constraints (16b) and (16c), leading to an approximation for the original problem in (6).
 We have provided justifications for the problem formulation in (6) and (16) in the paragraph before (16).
@@
 We have included the discussions on the average number of backlogged packets at each instant for different arrival rates in Section V-C.
-		\item The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen easily when the number queue size increases.
+		\item The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen easily when the queue size increases.
 We have clarified this point in the revised manuscript.
@@
 	\item We thank the reviewer for the comment.
-The convergence analysis has been clearly rewritten in Appendix B on the supplementary document.
+The convergence analysis has been clearly rewritten in Appendix A on the supplementary document.
 The discussions are provided for the convergence of the iterative Algorithm 1, \textit{i.e}, the problem defined in (16).
@@
 Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16).
-The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-C on the supplementary document.
+The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix A-C on the supplementary document.
 	\end{enumerate}
@@
 
-\resp \review{The discussions on the convergence of the centralized algorithms are provided in Appendix B and on the distributed algorithms in Appendix C.
-The discussion on the convergence to a stationary point is presented in Appendix B-E on the supplementary document.}
+\resp \review{The discussions on the convergence of the centralized algorithms are provided in Appendix A and on the distributed algorithms in Appendix B.
+The discussion on the convergence to a stationary point is presented in Appendix A-E on the supplementary document.}
 
@@
 
-\resp \review{We have updated the manuscript to include the discussions on the convergence of the distributed algorithm in Appendix C.
+\resp \review{We have updated the manuscript to include the discussions on the convergence of the distributed algorithm in Appendix B.
 The distributed algorithm attains the same stationary point as of the centralized algorithm if we let the inner loop in Algorithm 2 to converge.}
@@
 3.
-		\item We have provided the discussions on the convergence of the KKT based approach in the Appendix C on the supplementary document.
+		\item We have provided the discussions on the convergence of the KKT based approach in the Appendix B on the supplementary document.
 	\end{enumerate}}
@@
 \resp \review{Since the problem is nonconvex, the JSFRA formulation can find a stationary point upon convergence.
-The converged point of the JSFRA problem is in fact a stationary point of the original nonconvex problem, which is discussed in Appendix B-E provided on the supplementary document.
+The converged point of the JSFRA problem is in fact a stationary point of the original nonconvex problem, which is discussed in Appendix A-E provided on the supplementary document.
 We have removed the statement mentioning the Pareto-optimal solutions in the discussions on Fig.

### 2015-04-06 Response/response-2.tex
removed-tightness-discussion

@@
 \resp \review{The reformulation is required, since the SINR expression in (2) cannot be handled directly in the problem defined in (6).
-Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), which are the under estimator to the original problem in (6).
-Since the inequalities are used to replace the equality constraint, the objective could be improved by the iterative algorithm and the equality will be achieved after the convergence, thereby having one-to-one mapping at the final solution.
-We have updated the manuscript to include the details for better clarity on third paragraph in Section III-B.}
+Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), therefore leading to an approximation for the original problem in (6).
+We have updated the manuscript to include these details for better clarity in the third paragraph in Section III-B.}
 
@@
 Since the problem in (16) is not jointly convex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
-		\item Even after fixing \me{\mvec{w}{l,k,n}} as constant, the problem in (16) is nonconvex due to the DC constraint (16b), which is handled by the first order relaxation around some fixed operating point.
+		\item Even after fixing \me{\mvec{w}{l,k,n}} as a constant, the problem in (16) is nonconvex due to the DC constraint (16b), which is handled by the first order relaxation around some fixed operating point.
 Once the linear relaxation is performed, the problem in (20) is a convex optimization problem with the variables being \me{\mvec{m}{l,k,n},\gamma_{l,k,n},\beta_{l,k,n}}.
-The manuscript is updated to illustrate this clearly in the lines following after (19).
+The manuscript is updated to illustrate this clearly in the lines following (19).
 	\end{enumerate}
@@
 
-\resp \review{We thank the reviewer for the pointing out the inappropriate text.
-We have removed the incorrect statement on the block coordinate descent method with the AO approach in the paragraph following after (16) in Section III-B.
-Indeed, due to the coupling of the transmit and the receive precoder variables, we cannot use the standard block coordinate descent method proof for the convergence of the proposed algorithm as pointed out by the reviewer.
-We have provided a completely rewritten convergence proof in Appendix B.
+\resp \review{We thank the reviewer for pointing out the inappropriate text.
+We have removed the incorrect statement on the block coordinate descent method with the AO approach in the paragraph following (16) in Section III-B.
+Indeed, due to the coupling of the transmit and the receive precoder variables, we cannot use the proof of the standard block coordinate descent method for the convergence of the proposed algorithm as pointed out by the reviewer.
+We have provided a completely rewritten convergence proof in Appendix A.
 }
@@
 \resp \review{We apologize for the inappropriate reference cited in the original manuscript.
-We have provided a completely rewritten proof on the convergence of the centralized algorithm in Appendix B on the supplementary document.}
+We have provided a completely rewritten proof on the convergence of the centralized algorithm in Appendix A on the supplementary document.}
 
@@
 
-\resp \review{We agree with the reviewer's comment. We have provided the updated proof for the convergence of the centralized algorithm on Appendix B on the supplementary document.}
+\resp \review{We agree with the reviewer's comment. We have provided the updated proof for the convergence of the centralized algorithm on Appendix A on the supplementary document.}
 
@@
 Since the problem is convex, the distributed approach convergence can be guaranteed under certain conditions.
-Those are discussed in Appendix C on the convergence analysis for the distributed algorithms on the supplementary document.}
+Those are discussed in Appendix B on the convergence analysis for the distributed algorithms on the supplementary document.}
 

### 2015-04-06 Response/response-3.tex
removed-tightness-discussion

@@
 
-\resp \review{
+\resp \review{We thank the reviewer for the insightful comment.
+We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under-estimator for the SINR expression in (2) on the third paragraph in Section III-B.}
+\begin{comment}
 	\begin{enumerate}
@@
 	 }
+\end{comment}
 
@@
 \resp \review{We thank the reviewer for the comment.
-Rigorous convergence proof for the proposed algorithm is provided in Appendix B on the supplementary document.
-The uniqueness is also justified implicitly by the linear approximation performed on the DC constraint (16b), which makes the transmit precoders to be susceptible to the phase rotation.
-The discussion on the uniqueness is provided in Appendix B-C.}
+Rigorous convergence proof for the proposed algorithm is provided in Appendix A on the supplementary document.
+The uniqueness is justified implicitly by the MSE relation in (26c) for the MSE reformulation in (28), which makes the transmit precoders to be susceptible to the phase rotation.
+The uniqueness of the beamformer can be guaranteed by adding a strongly convex term in the objective as discussed in Appendix A-C.}
 
@@
 In our solution based on MSE reformulation, we have used the MMSE receiver irrespective of the \me{\ell_q} norm used in the objective.
-The formulation assumes the MMSE receiver for all exponents used in the objective, and therefore, the precoders can be designed by with the MSE relation.
+The formulation assumes the MMSE receiver for all exponents used in the objective, and therefore, the precoders can be designed by using the MSE relation.
 		\item The receivers are based on the MMSE objective, and therefore the equivalence is valid between the MSE and the SINR expression.
@@
 It can also be verified from Fig.
-1 for \me{\ell_1} objective.
-We have updated the manuscript to include this comments in the lines following (25) in Section III-C.
+1 with the \me{\ell_1} objective.
+We have updated the manuscript to include these comments in the lines following (25) in Section III-C.
 	\end{enumerate}

### 2015-04-06 Response/response-4.tex
removed-tightness-discussion

@@
 \resp \review{We agree that the original manuscript lacks the convergence proof for the JSFRA approach.
-We have presented a rigorous convergence proof for the proposed algorithm in Appendix B on the supplementary document.
+We have presented a rigorous convergence proof for the proposed algorithm in Appendix A on the supplementary document.
 We are grateful to the reviewer for bringing our attention to reference [A] which has been cited as [32] in the revised manuscript.
@@
 	\begin{enumerate}
-		\item In accordance with the reviewer, we have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Appendix C. 
-		\item For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver of all the users.
-Note that it includes the cross equivalent downlink channels of the neighbor BS users as well.
+		\item In accordance with the reviewer, we have shortened the discussions on the distributed approaches and discussed the convergence proof of the decentralized algorithm in Appendix B. 
+		\item For the distributed precoder design, we assume that each \ac{BS} \me{b} knows the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mbf{H}_{b,k,n}} of all users in the system by using precoded uplink pilots, where the precoders are the MMSE receiver evaluated at each user terminal.
+Note that it includes the equivalent downlink cross channels of the neighbor BS users as well.
 To update the MMSE receiver, the equivalent channel for the \me{\ith{k}} user \me{\mbf{H}_{b,k,n} \mvec{m}{l,k^\prime,n}, \forall k^\prime \in \mc{U}_b, \forall b \in \mc{B}} is obtained from the BSs through user specific downlink precoded pilots.
-We have included the information on what each network entity knows in the paragraph after (36).
+We have included this discussion in the paragraph after (36).
 		\item We have included the type of duplexing scheme adopted in the model, \textit{i.e}, TDD system, in the system description in Section II, last paragraph.
@@
 
-\resp \review{We have updated the manuscript to avoid the ambiguity in the representation of the optimal and the MMSE receiver.
+\resp \review{We have updated the manuscript to avoid the ambiguity in representing the optimal and the MMSE receiver.
 The optimal receiver is denoted by \me{\mvec{w}{l,k,n}^{o}} in (22) and the MMSE receiver by \me{\mvec{w}{l,k,n}} in (23).}
@@
 \resp \review{We thank the reviewer for the comment.
-We have updated the manuscript to include this discussion in the sentences after (23).
-The performance remains the same and the convergence rate is not affected by this scaling, which can be seen from Fig.
-1 comparing the precoder convergence using the optimal and the MMSE receiver for the JSFRA scheme with \me{\ell_1} norm.}
+We have updated the manuscript to include this discussion in the sentences following (23).
+The performance remains the same and the convergence behavior is not affected by this scaling, which can be seen from Fig.
+1, which compares the queue deviation objective convergence using the optimal and the MMSE receiver for the JSFRA scheme with \me{\ell_1} norm.}
 
@@
 \resp \review{To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point.
-Since the operating point is the optimal solution from the earlier iteration, the optimal point of the previous iterations is also present in the current feasible set.
+Since the operating point is the optimal solution from the earlier iteration, the optimal point of the previous iteration is also present in the current feasible set.
 Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective.
-Please refer to Appendix B in the supplementary document for more details on the convergence analysis of the centralized algorithm.}
+Please refer to Appendix A in the supplementary document for more details on the convergence analysis of the centralized algorithm.}
 
@@
 		where \me{\mbf{x}} denotes the stacked vector of optimization variables and \me{\mbf{x}^{(i)}} denotes the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
-It has been discussed in the Appendix B-C.
+It has been discussed in the Appendix A-C.
 It makes the objective strictly convex, therefore, the resulting subproblem has a unique minimizer.

### 2015-04-06 Report/wsrm_formulation.tex
removed-tightness-discussion

@@
 \review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-Note that \eqref{eqn-6.2} is an under-estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}}.
-\review{The constraints are tight when each \ac{BS} objective is non-zero upon convergence at the limiting point, as discussed in Appendix \ref{a-3}}.
-\review{Since the \ac{JSFRA} formulation can be modeled as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, it also belongs to the class of NP-hard problems.}
+Note that \eqref{eqn-6.2} is an under-estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}.
+Using the relaxation for the \ac{SINR} constraint, \eqref{eqn-6} provides an equivalent formulation for the problem in \eqref{eqn-3}.	Note that the \ac{JSFRA} formulation in \eqref{eqn-6} can be modeled as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, and therefore, it also belongs to the class of NP-hard problem.}
 

### 2015-04-06 Report/time_correlated.tex
adhi

@@
 Fig.
-\subref*{fig-review} plots the average of the total number of backlogged packets left out in the system after each transmission instant, \textit{i.e}, \me{\mathbf{\mathrm{E}}_i \, [ \Sigma_k \left [ Q_k(i) - t_k(i) \right ]^+ ]}.
+\subref*{fig-review} plots the average of the total number of backlogged packets left out in the system after each transmission instant, \textit{i.e}, \me{\mathbf{\mathrm{E}}_i \, [ \sum_k \left [ Q_k(i) - t_k(i) \right ]^+ ]}.
 Unlike the \ac{Q-WSRM} scheme, the average backlogged packets of the \me{\ell_2} \ac{JSFRA} scheme is comparable to the \ac{Q-WSRME} approach for all average arrival rates due to the explicit rate constraints \eqref{eqn-3.1.4}.

### 2015-04-07 Response/response-3.tex
adhi-alarm

@@
 \resp \review{We thank the reviewer for the insightful comment.
-We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under-estimator for the SINR expression in (2) on the third paragraph in Section III-B.}
+We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) together provides an under-estimator for the SINR expression in (2).
+This information is highlighted in the third paragraph in Section III-B.}
+
+\review{For the constraints (16b) and (16c) to be tight, there should be at least one user in each \ac{BS} with enough backlogged packets that cannot be served with the given power budget.
+On the other hand, to make the constraints active in all cases, the objective of the \ac{JSFRA} formulation should be regularized with the transmit power without affecting the solution as
+\begin{equation}
+\| \tilde{\mbf{v}} \|_q + \varphi \sum_{k \in \mc{U}} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right )
+\end{equation}
+where \me{\varphi \approx 0}.
+Note that the modified objective will relax the power constraint by making the constraints (16b) and (16c) tight in the final solution.
+Note that the tightness discussion is valid only for the active spatial streams, \textit{i.e}, \me{\mvec{m}{l,k,n} \neq \mbf{0}^\tran}.
+}
 \begin{comment}

### 2015-04-07 Report/convergence_centralized.tex
adhi-alarm

@@
 \subsection{Bounded Objective Function and Compact Feasible Set}
-The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which can be verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, and therefore, a compact set.
+The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
 

### 2015-04-07 Report/wsrm_formulation.tex
adhi
adhi-alarm

@@
 Note that \eqref{eqn-6.2} is an under-estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}.
-Using the relaxation for the \ac{SINR} constraint, \eqref{eqn-6} provides an equivalent formulation for the problem in \eqref{eqn-3}.	Note that the \ac{JSFRA} formulation in \eqref{eqn-6} can be modeled as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, and therefore, it also belongs to the class of NP-hard problem.}
+Therefore, the formulation in \eqref{eqn-6} is an equivalent approximation for the problem presented in \eqref{eqn-3}.
+Note that the \ac{JSFRA} formulation in \eqref{eqn-6} can be reformulated as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, and therefore it belongs to the class of NP-hard problems.}
 

### 2015-04-07 Response/response-1.tex
adhithya-sleeping

@@
 It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aim at minimizing the number of backlogged packets in addition to avoiding the over allocation of available resources.
-The JSFRA formulation using \me{\ell_1} norm as the objective minimizes the number of backlogged packets in a greedy manner at each instant.
+The JSFRA formulation using \me{\ell_1} norm as the objective minimizes the number of backlogged packets in a greedy manner at each time instant.
 By increasing the exponent \me{q \rightarrow \infty}, we obtain fair allocation at every transmission instant.
-We have included the discussions on the average number of backlogged packets at each instant for different arrival rates in Section V-C.
-		\item The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen easily when the queue size increases.
+We have included the discussions on the average of number of backlogged packets after each transmission instant for different arrival rates in Section V-C.
+		\item The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen when the queue size increases.
 We have clarified this point in the revised manuscript.
@@
 The discussions are provided for the convergence of the iterative Algorithm 1, \textit{i.e}, the  problem defined in (16).
-	\item The uniqueness of the convex subproblem (20) can be guaranteed by the linear constraint on the transmit precoders in (19), which is susceptible to the transmit precoder phase rotations.
-On the other hand, the constraint in (16b) is not, since the precoder variable is inside the absolute value operator.
+	\item The uniqueness of the convex subproblem (20) can be guaranteed by the linear constraint (19), if the initial feasible operating point is matched, \textit{i.e}, \me{q_{l,k,n} = \Im \{ \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}\} = 0} while starting the iterative solution.
+On the other hand, the constraint in (16b) is not unique, since the precoder is inside the absolute value operator.
 Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16).
 The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix A-C on the supplementary document.
+	\item The solution for the problem (16) is not unique, since all unitary transformations on the precoders identified by the iterative algorithm (20) are indeed the solutions for (16). 
+	\item The uniqueness of the transmit precoders can be guaranteed by adding a strongly convex function in the objective as discussed in Appendix A-C on the supplementary document.
 	\end{enumerate}
@@
 \resp \review{We have updated the manuscript to include the discussions on the convergence of the distributed algorithm in Appendix B.
-The distributed algorithm attains the same stationary point as of the centralized algorithm if we let the inner loop in Algorithm 2 to converge.}
+The distributed algorithm attains the same stationary point as that of the centralized algorithm if we let the inner loop in Algorithm 2 to converge, \textit{i.e}, the dual or the coupling variables are updated until convergence.}
 
@@
 		\item We have defined all the variables mentioned by the reviewer in the revised manuscript on Section VI-B
-		\item Since the coupling between the distributed precoder designs are the interference between the BSs and the users, in ADMM approach, the interference is treated as a local variable, which can be included in the precoder design optimization problem for each coordinating BS.
-This is treated as a local (but not the actual interference) variable for a specific BS.
+		\item Since the coupling between the distributed precoder designs are the interference between the BSs and the users, in the ADMM approach, the interference is treated as a local variable, which is then included in the precoder design problem for each coordinating BS.
+This is treated as a local variable for a specific BS.
+Note that the local variable is an assumption made by the BS on the actual interference caused by the neighboring BSs.
 Since the actual interference caused is different, the consensus has to be made between the local interference variable maintained at each BS with the global consensus interference variable, which is nothing but the average between the corresponding BSs interference.

### 2015-04-07 Response/response-3.tex
adhithya-sleeping

@@
 
-\resp \review{We thank the reviewer for the comment.
-Rigorous convergence proof for the proposed algorithm is provided in Appendix A on the supplementary document.
-The uniqueness is justified implicitly by the MSE relation in (26c) for the MSE reformulation in (28), which makes the transmit precoders to be susceptible to the phase rotation.
-The uniqueness of the beamformer can be guaranteed by adding a strongly convex term in the objective as discussed in Appendix A-C.}
+\resp \review{\begin{enumerate}
+	\item We thank the reviewer for the comment. Rigorous convergence proof for the proposed algorithm is provided in Appendix A on the supplementary document. 	
+	\item The uniqueness is justified implicitly by the MSE relation in (26c) for the MSE reformulation in (28), which makes the transmit precoders to be susceptible to the phase rotation.
+In general, the uniqueness of the beamformer can be guaranteed by adding a strongly convex term in the objective as discussed in Appendix A-C.
+\end{enumerate}}
 

### 2015-04-07 Response/response-4.tex
adhithya-sleeping

@@
 	\item Fig.
-4(a) demonstrates the performance of the proposed schemes and the existing algorithms using the average number of backlogged packets after each transmission instant for different arrival rates.
-The y-axis denotes the expected number of queued packets in the system after each transmission slot.
+4(a) demonstrate the performance of the proposed schemes and the existing algorithms using the average of the number of backlogged packets after each transmission instant for different arrival rates.
+The y-axis denotes the expectation taken over the number of queued packets in the system after each transmission slot.
 	\item Fig.
@@
 
-\resp \review{We have included the NP-hardness of the proposed solution by modeling the current problem to solve the \ac{WSRM} formulation, which is known to be NP-hard on the last sentence in Section III-B third paragraph.}
+\resp \review{We thank the reviewer for the comment.
+We have included the text on proving the NP-hardness of the problem (16).
+Since the formulation in (16) can be reformulated as a \ac{WSRM} problem, which is known to be NP-hard [23], therefore, it also belongs to the class of NP-hard problems.
+This information is included in the third paragraph in Section III-B.}
 
@@
 \resp \review{To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point.
-Since the operating point is the optimal solution from the earlier iteration, the optimal point of the previous iteration is also present in the current feasible set.
-Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective.
-Please refer to Appendix A in the supplementary document for more details on the convergence analysis of the centralized algorithm.}
+Since the operating point is a solution from the earlier iteration, it is also included in the current feasible set.
+Therefore, at each iteration, the algorithm finds a better solution or the same as compared to the previous solution, which leads to a monotonically decreasing objective.
+Please refer to Appendix A on the supplementary document for more details on the convergence analysis of the centralized algorithm.}
 
@@
 		\item The uniqueness of the beamformers for the MSE reformulation in (28) is guaranteed due to the MSE constraint (26c), which is susceptible to the transmit beamformer phase rotations.
-		\item On the other hand, the uniqueness of the beamformers for the SCA approach in (20) cannot be guaranteed unless the imaginary part of \me{q_{l,k,n} = \Im \{ \mvec{w}{l,k,n} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} = 0\}}.
+		\item On the other hand, the uniqueness of the beamformers for the SCA approach in (20) cannot be guaranteed unless the imaginary part of \me{q_{l,k,n} = \Im \{ \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}\} = 0}.
 It can be achieved by using the MMSE receiver for a randomly chosen initial transmit beamformer.

### 2015-04-07 Response/additions.tex
adhithya-sleeping

@@
 \item We have shortened the ADMM approach as suggested by the reviewers in Section IV-B.
-\item Rigorous convergence analysis is provided for the centralized algorithm in Appendix B.
+\item Rigorous convergence analysis is provided for the centralized algorithm in Appendix A.
 \item We have included Section V-C on the queue behavior over multiple time instants. We have added Fig. 4 to show the performance of the proposed scheme over the existing precoder design algorithms.
@@
 In what follows, the comments are listed, each followed by the corresponding reply from the authors.
-Unless stated explicitly, all the numbered items (figures, equations, references, citations, etc.) in the response letter refer to the revised manuscript.
+Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript.

### 2015-04-07 Report/mse_formulation.tex
with_markku_corrections
updated - final - draft
antti-inputs

@@
-In this, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{mse_duality,christensen2008weighted}.
+In this, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable \ac{SINR} by using the receivers designed with the \ac{MMSE} criterion \cite{mse_duality,christensen2008weighted}.
 The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
@@
 	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
-\end{multline}
-}{
-\allowdisplaybreaks{
+\end{multline}}{\allowdisplaybreaks
 \begin{multline} \label{mse-error}
@@
 \end{multline}}
-}
 where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol.
@@
 \end{IEEEeqnarray}
-}{{\allowdisplaybreaks
+}{\allowdisplaybreaks
 \begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
@@
 	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
-\end{IEEEeqnarray}}}
+\end{IEEEeqnarray}}
 

### 2015-04-07 Report/ieee_journal.tex
updated
Revert "updated"
This reverts commit 3664d68b10b962e2267a6fe47e1ec19a87ab526c.
nam modified (Appendices)
updated - final - draft
ordered algorithm locations
need to address nam's final comments
latest changes
antti changes
removed-tightness-discussion
Updated color for the revisions
adhi
adhi-calling

@@
-\documentclass[11pt,journal,onecolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,journal,twocolumn,letterpaper]{./../Styles/IEEEtran}
 
@@
 \begin{IEEEkeywords}
-Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \ac{WSRM}.
+Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \acs{WSRM}.
 \end{IEEEkeywords}
@@
 \acresetall 
+\acused{MU}
 
@@
 
-\subsection{\acs{JSFRA} Scheme via \ac{SCA} approach} \label{sec-3.2.1}
+\subsection{\acs{JSFRA} Scheme via \ac{SINR} Relaxation} \label{sec-3.2.1}
 \input{problem_formulation}
+
 \input{wsrm_formulation}
@@
 
+\bibliographystyle{./../Styles/IEEEtran}
+\bibliography{./../Library/kirja_survey}
+
+\clearpage
+
 \appendices
@@
 
-\section{Tightness of \ac{SINR} relaxation} \label{a-3}
-\review{\input{appendix_tightness}}
+%\section{Tightness of \ac{SINR} relaxation} \label{a-3}
+%\input{appendix_tightness}
 
 \section{Convergence Proof for Centralized Algorithm} \label{sec-3.5}
-\review{\input{convergence_centralized}}
+\input{convergence_centralized}
 
 \section{Convergence Proof for Distributed Algorithms} \label{sec-dist-conv}
-\review{\input{convergence_distributed}}
+\input{convergence_distributed}
 
@@
 
-\bibliographystyle{./../Styles/IEEEtran}
-\bibliography{./../Library/kirja_survey}
-
 \end{document}

### 2015-04-07 Report/introduction.tex
updated - final - draft
adhi-calling

@@
 The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
-
-\acused{MU}
-
 In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
@@
 Since the transmissions are guided by the backlogged packets, the proposed formulation limits the allocations beyond the number of backlogged packets without additional rate constraint.
-We adopt the \ac{SCA} to solve a sequence of convex subproblems using the first order Taylor approximation due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs the \ac{SCA} for the nonconvex \ac{DC} constraint.
-The first method is by using the \ac{SINR} expression and the second one is by using the \ac{MSE} equivalence with the rate expression to solve for the optimal precoders.
+We adopt \ac{SCA} to solve a sequence of convex subproblems using the first order Taylor approximation due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint.
+The first method is obtained by relaxing the \ac{SINR} expression and the second one is by utilizing the \ac{MSE} equivalence with the \ac{SINR} expression to solve for the precoders.
 Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods.

### 2015-04-10 Report/mse_formulation.tex
halfcooked

@@
-In this, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable \ac{SINR} by using the receivers designed with the \ac{MMSE} criterion \cite{mse_duality,christensen2008weighted}.
+In this, we solve the \ac{JSFRA} problem by exploiting the relation between the \ac{MSE} and the achievable \ac{SINR} when the \ac{MMSE} receivers are used at the user terminals as shown in \cite{mse_duality,christensen2008weighted}.
 The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by

### 2015-04-10 Report/wsrm_formulation.tex
halfcooked

@@
 Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-\review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as the \ac{SCA} approach in \cite{marks1978technical}.
+\review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}.
 By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}

### 2015-04-13 Report/convergence_distributed.tex
final

--- 2015-03-31 Report/convergence_distributed.tex
@@
 
-To avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
-Since the optimization variables are updated together, it is difficult to prove the monotonicity of the objective in each block update.
+However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
+Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
 Therefore, it is difficult to prove the convergence of the Algorithm \ref{algo-4} to a stationary point of the original nonconvex problem in \eqref{eqn-mse-1}.

### 2015-04-13 Report/ieee_journal.tex
final

@@
 Juntti are with Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{L.-N.
-Tran was with Centre for Wireless Communications (CWC), Oulu, FI-90014, is now with the Department of Electronic Engineering, Maynooth University, Maynooth, Co.
+Tran was with Centre for Wireless Communications (CWC), Oulu, FI-90014.
+He is now with the Department of Electronic Engineering, Maynooth University, Maynooth, Co.
 Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie)}}
@@
 
-\subsection{Queue Weighted Sum Rate Maximization (\acs{Q-WSRM}) Formulation} \label{sec-3.1}
+\subsection{Queue Weighted Sum Rate Maximization (\acs{Q-WSRM}) Formulation} \label{sec-3.1} %\acused{Q-WSRM}
 \input{joint_wsrm_formulation}
@@
 \bibliographystyle{./../Styles/IEEEtran}
-\bibliography{./../Library/kirja_survey}
+\bibliography{./../Library/IEEEabrv,./../Library/kirja_survey}
 

### 2015-04-13 Report/introduction.tex
final

@@
 The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
-In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network.
+In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users present in the network.
 We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets at each \ac{BS}.
@@
 
-In general, the resource allocation problems can be formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}.
-\review{In contrast, the linear transmit precoders, which are complex vectors, are implicitly used as decision variables, thereby avoiding the explicit modeling of binary decision variables.
-They are used to determine the transmission rates of users on a space-frequency resource if the precoder vector is non-zero.
+In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}.
+\review{Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables.
+After the decision stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource.
 A zero transmit precoder indicates the absence of the user on a given resource.
@@
 The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner.
-Additional the rate constraints based on the \ac{QoS} requirements were included in the \ac{WSRM} problem and solved via the \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
+Additionally the rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem and solved via the \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
 
@@
 
-By adjusting the weights in the \ac{WSRM} objective properly, we can find an arbitrary rate-tuple in the rate region that maximizes the suitable objective measures.
+By adjusting the weights in the \ac{WSRM} objective, we can find an arbitrary rate-tuple in the rate region that maximizes suitable objective measures.
 For example, if the weight of each user is set to be inversely proportional to its average data rate, the corresponding problem guarantees fairness on the average among the users.
-As an approximation, we may assign weights based on the current queue size of the users.
-Specifically, the queue states can be incorporated in the \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}, where \me{R_k} denotes the achievable user rate.
-In the backpressure algorithm, the differential queues between the source and the receiver nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.
+To reduce the number of backlogged packets, we can assign weights based on the current queue size of the users.
+Specifically, the queue states can be incorporated in the \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}, where \me{R_k} denotes the achievable data rate of user \me{k}.
+In the backpressure algorithm, the differential queues between the source and the receiver nodes are used to scale the transmission rate \cite{georgiadis2006resource}.
 
@@
 \subsubsection*{Main Contributions}
-\review{In this paper, we design the precoders jointly across space-frequency resources by minimizing the total number of backlogged packets waiting at the \acp{BS} queues.
-Since the transmissions are guided by the backlogged packets, the proposed formulation limits the allocations beyond the number of backlogged packets without additional rate constraint.
-We adopt \ac{SCA} to solve a sequence of convex subproblems using the first order Taylor approximation due to the nonconvexity imposed by the \ac{DC} constraints.} Initially, we propose centralized \ac{JSFRA} algorithms, which employs \ac{SCA} for the nonconvex \ac{DC} constraint.
-The first method is obtained by relaxing the \ac{SINR} expression and the second one is by utilizing the \ac{MSE} equivalence with the \ac{SINR} expression to solve for the precoders.
-Then we propose distributed precoder designs based on the primal and the \ac{ADMM} methods.
-Finally, an iterative practical algorithm is proposed to decouple the precoder design across the coordinating \acp{BS} with limited information exchange by solving the \ac{KKT} conditions for the \ac{MSE} reformulation.
+\review{In this paper, we design precoders jointly over space-frequency resources to reduce the number of backlogged packets waiting at each \acp{BS}.
+The proposed formulation also limits the allocations beyond the number of backlogged packets without explicit rate constraints.
+Initially, we propose centralized \ac{JSFRA} formulation, which is solved by two iterative algorithms based on the combination of \ac{SCA} and \ac{AO} due to the nonconvex nature of the problem.
+The proposed algorithms solve a sequence of convex problems obtained by fixing a subset of optimization variables or by approximating the nonconvex constraints by the convex ones.
+The first approach is performed by directly relaxing the \ac{SINR} expression, while in the second technique the equivalence between the \ac{MSE} and the \ac{SINR} is exploited.} We then discuss the distributed implementation of the \ac{JSFRA} methods using primal decomposition and the \ac{ADMM}.
+Finally, we also propose a more practical iterative precoder design by directly solving the \ac{KKT} system of equations for the \ac{MSE} reformulation that is numerically shown to require minimal information exchange for each update.
 \review{Note that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.

### 2015-04-13 Report/joint_wsrm_formulation.tex
updated - final - draft
final

@@
 
-To minimize the total number of backlogged packets for time instant \me{i}, the optimal transmission rate of all users are obtained by minimizing the Lyapunov drift expressed as  
+To minimize the total number of backlogged packets for time instant \me{i}, the optimal transmission rate of all users is obtained by minimizing the Lyapunov drift expressed as  
 \iftoggle{single_column}{

### 2015-04-13 Report/mse_formulation.tex
final

--- 2015-04-07 Report/mse_formulation.tex
@@
-In this, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable \ac{SINR} by using the receivers designed with the \ac{MMSE} criterion \cite{mse_duality,christensen2008weighted}.
+In the second method, we solve the \ac{JSFRA} problem by exploiting the relation between the \ac{MSE} and the achievable \ac{SINR} when the \ac{MMSE} receivers are used at the user terminals \cite{mse_duality,christensen2008weighted}.
 The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by

### 2015-04-13 Report/problem_formulation.tex
final

@@
 By limiting \me{t_k^2} with a constant value, the \ac{Q-WSRM} formulation requires an explicit rate constraint \eqref{eqn-3.1.4} to avoid over-allocation of the available resources.
-In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function \eqref{eqn-4.2} itself.
+In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function \eqref{eqn-4.2} as discussed earlier.
 It makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \ac{BS} independently with minimal information exchange \cite{boyd2011distributed}.
-In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRME} problems handle the sub-channels jointly to obtain an efficient allocation by identifying the optimal space-frequency resources for the users.
+In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRME} problems handle the sub-channels jointly to obtain an efficient allocation by identifying the optimal space-frequency resources for the contending users.

### 2015-04-13 Report/system_model.tex
final

@@
 Data for user \me{k} is transmitted from only one \ac{BS} which is denoted by \me{b_k\in \mathcal{B}}.
-We denote by \me{\mathcal{N} = \set{1,2,\dotsc,N}} the set of all sub-channel indices available in the system.
+Let \me{\mathcal{N} = \set{1,2,\dotsc,N}} be the set of all sub-channel indices available in the system.
 
 We adopt linear transmit beamforming technique at \acp{BS}.
-Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over the sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted.
+Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted.
 In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user.
-Consequently, the received data symbol estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
+Consequently, the received data estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
 \iftoggle{single_column}{
@@
 }
-where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for the user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
+where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
 In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams.\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users.
@@
 where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance.
-\review{To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system, which uses channel reciprocity.}
+\review{To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system in which \acp{BS} can estimate the downlink channels from the uplink ones using the so-called channel reciprocity.}
 
 Let \me{Q_k} be the number of backlogged packets destined for user \me{k} at a given scheduling instant.
-The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{{i}^\mathrm{th}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for the user \me{k}, denoted as \me{Q_k(i+1)}, is given by
+The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{{i}^\mathrm{th}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for user \me{k}, denoted as \me{Q_k(i+1)}, is given by
 \begin{equation}

### 2015-04-13 Report/wsrm_formulation.tex
final

@@
-\review{We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \ac{SCA} \cite{marks1978technical}.
+\review{We present iterative algorithms to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with the \ac{SCA} presented \cite{marks1978technical}.
 The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system.
 The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint.
-Using additional variables, we relax the expression in \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as}
+However, by using additional variables, we can relax the \ac{SINR} expression in \eqref{eq:SINR} by inequality constraints to solve the problem \eqref{eqn-3} as}
 \iftoggle{single_column}{
@@
 Note that \eqref{eqn-6.2} is an under-estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}.
-Therefore, the formulation in \eqref{eqn-6} is an equivalent approximation for the problem presented in \eqref{eqn-3}.
+Therefore, the problem formulation in \eqref{eqn-6} is an equivalent approximation for the problem presented in \eqref{eqn-3}.
 Note that the \ac{JSFRA} formulation in \eqref{eqn-6} can be reformulated as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, and therefore it belongs to the class of NP-hard problems.}

### 2015-04-13 Response/additions.tex
final

@@
 \item We have shortened the ADMM approach as suggested by the reviewers in Section IV-B.
-\item Rigorous convergence analysis is provided for the centralized algorithm in Appendix A.
+\item Rigorous convergence analysis is provided for the centralized algorithm in Appendix A on the supplementary document. 
 \item We have included Section V-C on the queue behavior over multiple time instants. We have added Fig. 4 to show the performance of the proposed scheme over the existing precoder design algorithms.
@@
 
-Due to the page limitation imposed on the resubmitted manuscript, we have included all the Appendices as a supplementary document in the manuscript central.
+Due to the strict page limitation imposed on the resubmitted manuscript, we have included all Appendices on the supplementary document in the manuscript central.
 In what follows, the comments are listed, each followed by the corresponding reply from the authors.

### 2015-04-13 Report/convergence_centralized.tex
final_antti_show_adhithya_all

@@
 In general, to ensure the uniqueness of the transmit precoders and the receive beamformers in all iterations, \textit{i.e}, even when the objective value is zero, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized with a strongly convex function.
-Now, the objective function of the \me{\ith{i+1}} iteration is given as
+The objective function for the \me{\ith{i+1}} iteration can be regularized as
 \begin{equation}
@@
 2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
-It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limit point \eqref{con-opt}, using the linear relaxation \eqref{con-relax} for the nonconvex constraint \cite{marks1978technical}.
+It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limit point \eqref{con-opt}, using the relation in \eqref{con-relax} between the nonconvex constraint and the corresponding convex approximation \cite{marks1978technical}.

### 2015-04-13 Report/introduction.tex
final_antti_show_adhithya_all

@@
 Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed.
-The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using the \ac{SCA} to solve the problem in an iterative manner.
-Additionally the rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} problem and solved via the \ac{MSE} reformulation in \cite{kaleva2013primal,kaleva2013decentralized}.
+The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using \ac{SCA} to solve the problem in an iterative manner.
+Moreover, distributed precoder design with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013primal,kaleva2013decentralized}.
 
@@
 Specifically, the queue states can be incorporated in the \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}, where \me{R_k} denotes the achievable data rate of user \me{k}.
-In the backpressure algorithm, the differential queues between the source and the receiver nodes are used to scale the transmission rate \cite{georgiadis2006resource}.
+In the \textit{backpressure algorithm}, the differential queues between the source and the receiver nodes are used to scale the transmission rate \cite{georgiadis2006resource}.
 
-Earlier studies on the queue minimization problem were summarized in the survey papers \cite{berry2004cross,layering_as_opt}.
-In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} using geometric programming.
+Earlier studies on the queue minimization problem are summarized in the survey papers \cite{berry2004cross,layering_as_opt}.
+In particular, the problem of power allocation to minimize the number of backlogged packets is considered in \cite{qps_cioffi} using geometric programming.
 Since the problem addressed in \cite{qps_cioffi} assumed single antenna transmitters and receivers, the queue minimizing problem reduces to the optimal power allocation problem.
-In the context of wireless networks, the backpressure algorithm mentioned above was extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.
+In the context of wireless networks, the \textit{backpressure algorithm} mentioned above is extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.
 Recently, the precoder design for the video transmission over \ac{MIMO} system is considered in \cite{video_queues}.
@@
 \subsubsection*{Main Contributions}
-\review{In this paper, we design precoders jointly over space-frequency resources to reduce the number of backlogged packets waiting at each \acp{BS}.
+In this paper, we design precoders jointly over space-frequency resources to reduce the number of backlogged packets waiting at each \acp{BS}.
 The proposed formulation also limits the allocations beyond the number of backlogged packets without explicit rate constraints.
-Initially, we propose centralized \ac{JSFRA} formulation, which is solved by two iterative algorithms based on the combination of \ac{SCA} and \ac{AO} due to the nonconvex nature of the problem.
+\review{Initially, we propose a centralized \ac{JSFRA} formulation, which is solved by two iterative algorithms based on the combination of \ac{SCA} and \ac{AO} due to the nonconvex nature of the problem.
 The proposed algorithms solve a sequence of convex problems obtained by fixing a subset of optimization variables or by approximating the nonconvex constraints by the convex ones.
-The first approach is performed by directly relaxing the \ac{SINR} expression, while in the second technique the equivalence between the \ac{MSE} and the \ac{SINR} is exploited.} We then discuss the distributed implementation of the \ac{JSFRA} methods using primal decomposition and the \ac{ADMM}.
+The first approach is performed by directly relaxing the \ac{SINR} expression, while in the second method, the equivalence between the \ac{MSE} and the \ac{SINR} is exploited.} We then discuss the distributed implementation of the \ac{JSFRA} methods using primal decomposition and the \ac{ADMM}.
 Finally, we also propose a more practical iterative precoder design by directly solving the \ac{KKT} system of equations for the \ac{MSE} reformulation that is numerically shown to require minimal information exchange for each update.

### 2015-04-13 Report/system_model.tex
final_antti_show_adhithya_all

@@
 where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance.
-\review{To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system in which \acp{BS} can estimate the downlink channels from the uplink ones using the so-called channel reciprocity.}
+\review{To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system in which \acp{BS} can estimate the downlink channels from the uplink pilots using channel reciprocity.}
 

### 2015-04-28 Report/convergence_centralized.tex
submitted_version

@@
 
-To begin with, let us consider the variable \me{\my} is fixed for the \ac{AO} \me{i} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
+To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
 In order to solve for \me{\mx} in the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
@@
 Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\ast}{i}} and \me{\iter{\my}{k}{i}}.
-Using \eqref{con-relax}, the convex subproblem for \me{\ith{i}} \ac{AO} iteration and \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
+Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
 \begin{subeqnarray} \label{con-m}
@@
 \begin{equation}
-\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
+\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2_2
 \end{equation}

### 2015-04-28 Report/dual_approach.tex
nam modified (Appendices)
updated - final - draft
ordered algorithm locations
submitted_version

--- 2015-03-23 Report/dual_approach.tex
@@
 Similar approach for the precoder design in the minimum power context is considered in \cite{admm_robust}.
-
-Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{i}} iteration as
-\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks
-&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
-&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
-&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
-&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
-& \text{and } \eqsub \eqref{eqn-8}
-\end{IEEEeqnarray}
-where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{i}} iteration as
-\begin{equation} \label{const-admm1}
-\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
-\end{equation}
-
-Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
-\begin{equation}
-\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
-\label{if-sg-update}
-\end{equation}
-The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
-\begin{equation}
-\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
-\label{dual-sg-update}
-\end{equation}
-where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration.
-The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}.
-For our simulation models, we consider step size parameter \me{\rho=2}.
-The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.
-The distributed precoder design using the \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
-The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
 \begin{algorithm}
@@
 \end{algorithm}
-\vspace{-0.15in}
+
+Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{i}} iteration as
+\iftoggle{single_column}{\allowdisplaybreaks
+\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks
+\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
+\text{subject to} &\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
+&\quad&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
+&\quad& \sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
+&\quad& \text{and } \eqsub \eqref{eqn-8}
+\end{IEEEeqnarray}
+}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks
+&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
+&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
+&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
+&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
+& \text{and } \eqsub \eqref{eqn-8}
+\end{IEEEeqnarray}}
+where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{i}} iteration as
+\begin{equation} \label{const-admm1}
+\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
+\end{equation}
+
+Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
+\begin{equation}
+\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
+\label{if-sg-update}
+\end{equation}
+The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
+\begin{equation}
+\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
+\label{dual-sg-update}
+\end{equation}
+where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration.
+The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}.
+For our simulation models, we consider step size parameter \me{\rho=2}.
+The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.
+The distributed precoder design using the \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
+The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
 

### 2015-04-28 Report/mse_formulation.tex
submitted_version

@@
 \iftoggle{single_column}{
-\begin{multline} \label{mse-error}
+\begin{equation} \label{mse-error}
 	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
-\end{multline}}{\allowdisplaybreaks
+\end{equation}}{\allowdisplaybreaks
 \begin{multline} \label{mse-error}
@@
  & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
-& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
+& \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
 \end{IEEEeqnarray}

### 2015-06-22 Response/Response 2/response-1.tex
updated

Comments:
The response to the reviewer's concerns are generally satisfying, except the convergence proof.

\vspace{0.1in}
\review{We thank the reviewer for providing valuable and insightful comments.}

For the resubmitted manuscript, the reviewer still has the following concerns

\begin{enumerate}
\cmnt{1} Considering the length of the manuscript, it would be better to shorten some parts that are not new in this manuscript, e.g. III.A. More space can be left for convergence proof, which is very important.

\resp \review{We thank the reviewer for the comment. 
		}

\cmnt{2} In convergence proof (48), why does the 2nd inequality hold? In fact, to prove the feasibility of  \eqn{{m_{k+1}^{(i)}, w_{*}^{(i-1)};m_k^{(i)} }}, the part between 2nd and 3rd inequality is not necessary, ''<=0'' directly follows the 2nd inequality since the solution \eqn{m_{k+1}^{(i)}, \gamma_{k+1}^{(i)} } is the optimal solution, and therefore  feasible.

\resp \review{
	}

\cmnt{3} The solutions SCA iterations \eqn{m^{(i)}_k} does not necessarily converge. In fact \eqn{m} has compact feasible region, and thus \eqn{m^{(i)}_k} has limit points for any specific \eqn{i}.  However \eqn{m_{*}^{(i)}} does not necessarily exist( the whole sequence \eqn{m^{(i)}_k} may be not convergent). Similar problem happens to \eqn{w^{(i)}_k}.

\resp \review {	
}

\cmnt{4} Strict monotonicity with respect to the objective function \eqn{f} should be rigorously proved. Note that to guarantee the uniqueness of the beamformer iterates, (52) instead of the objective function is used.

\resp \review{}

\cmnt{5} Note that the conclusions [32, Thm 2] and [26, Thm 10] have lots of assumptions. To invoke these reference, explicit exposition should be provided to show that these conclusions can be applied to our problem. The same questions occur to the proof in Appendix B, where conclusions in [11] [36] and [37] are used. Too many details are omitted to make the proof convincing and clear.

\resp \review{}

\end{enumerate}

### 2015-06-22 Response/Response 2/response-2.tex
updated

The authors have addressed many of my previous comments. However, there are still several major issues that need further clarification.

\vspace{0.1in}
\review{We would like to thank the reviewer for providing valuable comments.}

\begin{enumerate}
\cmnt{1} The revised paper did not address my previous comment about how to select the sub-channel ordering. I understand that finding the best sub-channel ordering requires exhaustive search which has extremely high complexity. But it is important to provide a guidance on what would be a good choice of sub-channel ordering. For example, can we achieve a good performance by using a low complexity ordering algorithm such as a greedy sub-channel ordering algorithm?

\resp \review{}

\cmnt{2} The authors mentioned that the signaling overhead of the distributed algorithm can be reduced by using a smaller number of iterations \eqn{J_{\max}}. But still, you didn't answer my question about whether the signaling overhead of the distributed algorithm is smaller than the centralized algorithm. You should first analyze the signaling overhead of the distributed algorithm for fixed \eqn{J_{\max}} and the signaling overhead of the centralized algorithm. Then you should point out under what \eqn{J_{\max}} the distributed algorithm will have less signaling overhead than the centralized algorithm. Is it possible that the distributed algorithm always has more signaling overhead than the centralized algorithm even when \eqn{J_{\max} = 1}? Finally, there is a tradeoff between performance and signaling overhead (\eqn{J_{\max}}) for the distributed algorithm. For the same signaling overhead (we can control \eqn{J_{\max}} to make the signaling overhead of the distributed algorithm approximately equal to that of the centralized algorithm), does the distributed algorithm achieve better performance than the centralized algorithm?

\resp \review{
}

\cmnt{3} If the authors can't prove the convergence of the ADMM algorithm (or the decomposition approach via KKT conditions) in Section IV.B, then at least, you should discuss the property of the fixed point of the algorithm. For example, does there exist a fixed point of the algorithm? If so, is the fixed point of the algorithm unique? Is any fixed point of the algorithm also the optimal solution of the original problem in (20)? Assuming that the ADMM algorithm converges to a fixed point, will the interference vector in (39) converges to the actual interference in the network? These questions must be clarified in the paper. Otherwise, it is not clear how the ADMM algorithm is related to the original problem in (20). Similar questions should also be answered for the decomposition approach via KKT conditions.

\resp \review{}

\end{enumerate}

### 2015-06-22 Response/Response 2/response-3.tex
updated

The authors have introduced changes in the manuscript that improved the paper's quality. Additionally, the authors have taken into account the reviewers' comments giving clarifications and modifying the content when required. More specifically, the following aspects have been treated:

\vspace{0.1in}
\review{We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helps to improve the manuscript.}

\begin{enumerate}
\cmnt{1} Convexity of problem (16). The paragraphs surrounding (16) allow a better understanding of the usage of the additional variables, i.e. gamma and beta, to remove the equality constraint in (2). For the reviewer remains however unclear, the procedure/criterion to determine the operating point for the parameter \eqn{\tilde{\beta}} required in (19) and used in the convex subproblems (20) and (21).

\resp \review{
	}

\cmnt{2} Proof of convergence. The proof of convergence introduced by the authors in the Appendix seems correct and enhances the content of the manuscript.

\resp \review{}

Additional Comments -

\begin{enumerate}

	\cmnts{a} - {The reviewer considers that closing statements regarding the applicability of the proposed schemes are missing. Since the results are quite similar (when not identical), which formulation is preferable between the centralized schemes? Which one for the distributed solutions?}

	\resp \review{}

	\cmnts{b} - {The last discussion in section IV-C could benefit from restructuring. The information on how to obtain a practical distributed precoder design and to avoid backhaul exchange is too condensed and difficult to understand.}

	\resp \review{}

	\cmnts{c} - {For the simulation results, why not to unify configurations when possible? Having to read a different configuration for each graph is cumbersome and no additional comparisons are possible between figures. E.g. PL uniformly distributed between [0,-6] dB in Fig. 2 and [0,-3] dB in Fig. 3.}

	\resp \review{}

	\cmnts{d} - {In Fig. 1, the description of the system model does not agree with the statement of N = 3 subchannels.}

	\resp \review{}

	\cmnts{e} - {In Fig. 4(b), the performance of Q-WSRME seems to be (in average) worse than Q-WSRM. However, that should not be the case, since Q-WSRME is taking into account the over allocation. Any reason for this?}

	\resp \review{}

	\cmnts{f} - {p 6, col 2, row 49: it should be \eqn{t_{l,k,n}} instead of \eqn{t_{l,n,k}}}

	\resp \review{}

	\cmnts{g} - {p 10, col 1, row 28: is it \eqn{\lambda} a dual variable?}

	\resp \review{}

	\cmnts{h} - {p 10, col 2, row 59: typo wHith}

	\resp \review{}

	\cmnts{i} - {In general, a grammar check is recommended, several mistakes with respect to singular and plural nouns have been observed, e.g. -p 6, col 2, row 56 "... for A fixed receiverS" is not correct.}

	\resp \review{}

\end{enumerate}

\end{enumerate}

### 2015-06-22 Report/convergence_distributed.tex
updated

@@
 The feasible set of the problem in \eqref{eqn-decent-1} satisfies the Slater's constraint by having a non-empty interior and is also compact.
-Since the subproblem in \eqref{eqn-decent-1} is convex, the convergence of the primal and the \ac{ADMM} scheme can be guaranteed by using the discussions in \cite{bertsekas1999nonlinear,boyd2011distributed} and \cite[Prop.
+Since the subproblem in \eqref{eqn-decent-1} is convex, the convergence of the primal and the \ac{ADMM} scheme can be justified by using the discussions in \cite{bertsekas1999nonlinear,boyd2011distributed} and \cite[Prop.
 4.2]{bertsekas1989parallel}.
 
+\review{However, if the distributed algorithm is terminated well before the convergence or iterated only for limited iteration, it is difficult to prove the convergence of the algorithm.
+Since at each \ac{AO} update for \eqn{\mbf{x}^{(i)}}, which involves two \ac{SCA} updates until convergence with limited distributed iterations at each \ac{SCA} step, the objective is not guaranteed to be monotonically decreasing after the distributed iterations, and therefore the convergence is not guaranteed unless the number of iterations is large enough to achieve monotonically decreasing objective.
+In this case, it converges to a fixed point which is indeed a stationary point for the original nonconvex problem \cite{zangwill1969nonlinear,meyer1976sufficient}}.
+
 Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
-Therefore, it is difficult to prove theoretically the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.
+Therefore, it is difficult to theoretically prove the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.
 

### 2015-06-22 Report/decomposition_solutions.tex
ordered algorithm locations
submitted_version
updated

@@
 The distributed precoder designs for the proposed \ac{JSFRA} scheme are discussed in this section.
-The \review{convex} formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
+The convex formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
 In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are addressed.
@@
 
-Let us consider the \review{convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented} in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint.
+Let us consider the convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint.
 The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well.
@@
 \iftoggle{single_column}{
-\begin{eqnarray}{rCl}\label{eqn-decent-3}
-\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
-&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; \enoise
-\end{eqnarray}}{\allowdisplaybreaks
+\begin{equation}\label{eqn-decent-3}
+\beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; \enoise
+\end{equation}}{\allowdisplaybreaks
 \begin{multline}\label{eqn-decent-3}
@@
 Similarly, to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} need to be known through the user specific precoded downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} by using the equivalent downlink channel that includes the updated \ac{MMSE} receivers of all the users, as in \cite{komulainen2013effective}.
-
 %The subproblems with the \ac{BS} specific interference variables are controlled by a master subproblem, which determines the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in accordance with the global objective.

### 2015-06-22 Report/ieee_journal.tex
final_antti_show_adhithya_all
updated

@@
-\documentclass[10pt,journal,twocolumn,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,journal,final,letterpaper]{./../Styles/IEEEtran}
 
@@
 \usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}
+\usepackage{multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools,url,subeqnarray}
 
@@
 \subsection{Reduced Complexity Spatial Resource Allocation (\acs{SRA})} \label{sec-3.4}
-\review{\input{sub_channel_wsrm}}
+{\input{sub_channel_wsrm}
 
 \section{Distributed Solutions} \label{sec-4}
-
-\review{\input{decomposition_solutions}}
+\input{decomposition_solutions}
 
@@
 \subsection{Queuing Analysis over Multiple Transmission Slots} \label{time-correlated}
-\review{\input{time_correlated}}
+\input{time_correlated}
 
@@
 \input{conclusions}
-
-\bibliographystyle{./../Styles/IEEEtran}
-\bibliography{./../Library/IEEEabrv,./../Library/kirja_survey}
-
-\clearpage
 
@@
 
+\bibliographystyle{./../Styles/IEEEtran}
+\bibliography{./../Library/IEEEabrv,./../Library/kirja_survey}
+
 \end{document}

### 2015-06-22 Report/introduction.tex
updated

@@
 In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}.
-\review{Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables.
+Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables.
 After the decision stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource.
 A zero transmit precoder indicates the absence of the user on a given resource.
-In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergences}.
+In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergences.
 
@@
 The proposed formulation also limits the allocations beyond the number of backlogged packets without explicit rate constraints.
-\review{Initially, we propose a centralized \ac{JSFRA} formulation, which is solved by two iterative algorithms based on the combination of \ac{SCA} and \ac{AO} due to the nonconvex nature of the problem.
+Initially, we propose a centralized \ac{JSFRA} formulation, which is solved by two iterative algorithms based on the combination of \ac{SCA} and \ac{AO} due to the nonconvex nature of the problem.
 The proposed algorithms solve a sequence of convex problems obtained by fixing a subset of optimization variables or by approximating the nonconvex constraints by the convex ones.
-The first approach is performed by directly relaxing the \ac{SINR} expression, while in the second method, the equivalence between the \ac{MSE} and the \ac{SINR} is exploited.} We then discuss the distributed implementation of the \ac{JSFRA} methods using primal decomposition and the \ac{ADMM}.
+The first approach is performed by directly relaxing the \ac{SINR} expression, while in the second method, the equivalence between the \ac{MSE} and the \ac{SINR} is exploited.
+We then discuss the distributed implementation of the \ac{JSFRA} methods using primal decomposition and the \ac{ADMM}.
 Finally, we also propose a more practical iterative precoder design by directly solving the \ac{KKT} system of equations for the \ac{MSE} reformulation that is numerically shown to require minimal information exchange for each update.
-\review{Note that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.
+Note that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users.
 

### 2015-06-22 Report/kkt_mse_approach.tex
updated - final - draft
ordered algorithm locations
updated

@@
 The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements.
-\review{We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter}.
+We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
@@
 So, \me{\alpha^{(i)}} is fixed to evaluate \me{\sigma^{(i)}} using \eqref{kkt-mse-4}.
-\review{At each iteration, the dual variables \me{\alpha^{(i)}} are linearly interpolated with any point between the fixed iterate \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} using a step size \me{\rho \in (0,1)}.
+At each iteration, the dual variables \me{\alpha^{(i)}} are linearly interpolated with any point between the fixed iterate \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} using a step size \me{\rho \in (0,1)}.
 The choice of \me{\rho} depends on the system model and it affects the convergence behavior.
-It reduces the oscillations in the objective function when \me{\sigma^{(i)}} is negative due to over-allocation.}
+It reduces the oscillations in the objective function when \me{\sigma^{(i)}} is negative due to over-allocation.
 
@@
 Once \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}} eventually.
-\review{The choice of \me{\rho} is susceptible to the system model under consideration, which affects the convergence speed of the iterative algorithm.
-In all simulations, the step size \me{\rho} is fixed to \me{0.1} irrespectively.}
+The choice of \me{\rho} is susceptible to the system model under consideration, which affects the convergence speed of the iterative algorithm.
+In all simulations, the step size \me{\rho} is fixed to \me{0.1} irrespectively.
 
@@
 
-\review{To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which includes the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling}.
+To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which includes the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling.
 We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the current problem as follows.
@@
 The \ac{SCA} operating point is also updated with the current \ac{MSE} value.
-
-To avoid the back-haul exchanges between the \acp{BS}, as an alternative approach, users perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users.
-Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}.
-The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
-On receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
-Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling with the precoded pilots for the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
-The convergence of the algorithm is discussed in Appendix \ref{sec-dist-conv}.
 \begin{algorithm}
@@
 
+To avoid the back-haul exchanges between the \acp{BS}, as an alternative approach, users perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users.
+Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}}.
+The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
+After receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
+Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling with the precoded pilots for the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
+The convergence of the algorithm is discussed in Appendix \ref{sec-dist-conv}.
+
 %\subsubsection*{Convergence}

### 2015-06-22 Report/mse_formulation.tex
updated

@@
 where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol.
-\review{Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as}
+Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as
 \begin{equation} \label{eqn-mse-eq}
@@
 Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.
-\review{Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.}
+Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
 
@@
 
-Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,n,k}} for a fixed receive beamformers.
-The optimization subproblem to find the transmit precoders for a fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by
+Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \review{\me{t_{l,k,n}}} for a fixed receive beamformer.
+The optimization subproblem to find the transmit precoders for a fixed receive beamformer \me{\mvec{w}{l,k,n}} is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
@@
 \end{IEEEeqnarray}
-The optimal transmit precoders for a fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
+The optimal transmit precoders for a fixed receiver are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
 The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.

### 2015-06-22 Report/problem_formulation.tex
updated

@@
 The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value.
-\review{In fact, using \me{\ell_{q=2}} in \eqref{eqn-4.2}, we obtain the following objective
+In fact, using \me{\ell_{q=2}} in \eqref{eqn-4.2}, we obtain the following objective
 \begin{equation}\label{pf-1}
@@
 which is similar to the objective in \eqref{q_gen_sum}.
-It is achieved either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is large for all users such that \me{t_k^2} has no impact on the objective function.}
+It is achieved either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is large for all users such that \me{t_k^2} has no impact on the objective function.
 

### 2015-06-22 Report/problem_formulation_intro.tex
updated

@@
 \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor, which is used to alter the user priority based on the \ac{QoS} constraints \review{such as packet delay requirements and packet waiting time, since they are proportional to the corresponding number of backlogged packets.} The \ac{BS} specific power constraint for all sub-channels is considered in \eqref{eqn-4.3}.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor, which is used to alter the user priority based on the \ac{QoS} constraints such as packet delay requirements and packet waiting time, since they are proportional to the corresponding number of backlogged packets.
+The \ac{BS} specific power constraint for all sub-channels is considered in \eqref{eqn-4.3}.
 

### 2015-06-22 Report/simulation_distributed.tex
antti changes
updated

@@
 The distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update.
-\review{Fig.
-\ref{fig-d} compares the performances of the algorithms with the \ac{PL} varies uniformly between \me{[0,-6]} dB}.
-Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets, whith the queued packets for each user is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
+Fig.
+\ref{fig-d} compares the performances of the algorithms with the \ac{PL} varies uniformly between \me{[0,-6]} dB.
+Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets, \review{with} the queued packets for each user is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
 As discussed in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update.
@@
 
-\review{Fig.
-\ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB}.
+Fig.
+\ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB.
 The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other schemes due to the greedy objective.
@@
 	\subfloat[][Average backlogged packets in the system after \me{250} transmission instants]{
-		\includegraphics[width=0.48\textwidth]{average_queue_over_time-2}
+		\includegraphics[width=0.48\textwidth]{average_queue_over_time-3}
 		\label{fig-review}
@@
 	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 6} bits]{
-		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-2}
+		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-3}
 		\label{fig-review-time}

### 2015-06-22 Report/simulation_intro.tex
updated nam comments review should be modified
updated

@@
 		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
-		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
+		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \emph{backpressure})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
 		\cline{3-14}
@@
 		\label{fig-2}}
-	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm for \ac{JSFRA} schemes}}
+	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates using \me{\ell_1 (q = 1)} norm for \ac{JSFRA} schemes}
 	\label{fig-a}

### 2015-06-22 Report/simulation_results.tex
updated

@@
 
-For a \ac{MIMO} scenario, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
+For a \ac{MIMO} scenario, we consider a system with \review{\me{N=4,2}} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
 The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the associations are made by selecting the \ac{BS} with the lowest \ac{PL} component.
@@
 	\includegraphics[width=\columnwidth]{fig-3-2}
-	\caption{Convergence of the centralized and the distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
+	\caption{Convergence of the centralized and the distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace} using \me{\ell_1} norm for \ac{JSFRA} schemes}
 	\label{fig-d}

### 2015-06-22 Report/sub_channel_wsrm.tex
updated - final - draft
updated

@@
-The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of the interior point method, which is used to solve the problem, increases quickly with the problem size.
+The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of the interior point method, which is used to solve the problem, increases with the problem size.
 Thus, we can use the decomposition methods presented in \cite{palomar2006tutorial,boyd2011distributed} to overcome this complexity by designing precoders for each sub-channels independently with minimal information exchange.
 
-As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
+As an alternative sub-optimal solution, we present a \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
 The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels as given by
@@
 where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream.
-Note that the proposed scheme is sensitive to the order of the sub-channel selection due to the sequential precoder design for each sub-channel.
-However, the \ac{SRA} approach provides faster convergence in contrast to the \ac{JSFRA} formulation due to the substantial reduction in the optimization variables for each sub-channel problem.
-As the number of users in the system increases, the \ac{SRA} formulation will be insensitive to the sub-channel ordering due to the multi-user diversity.
+\review{Inspite of the improved covergence speed over the \ac{JSFRA} approach, the \ac{SRA} scheme is sensitive to the order in which the sub-channels are selected.
+Heuristically, we can adopt \ac{MU}-\ac{MIMO} scheduling scheme in \cite{sus2006zfbf} to find an efficient subset of users and the corresponding sum rate using zero-forcing precoders in each sub-channel, which can be used to determine the selection order.
+Since the scheduling is based on the infinite buffer model, it is used only in the sub-channel ordering.
+However, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the multi-user diversity.}
+
 %The algorithmic representation of the \ac{SRA} scheme is shown in Algorithm \ref{algo-5}

### 2015-06-22 Report/system_model.tex
updated

@@
 where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance.
-\review{To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system in which \acp{BS} can estimate the downlink channels from the uplink pilots using channel reciprocity.}
+To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system in which \acp{BS} can estimate the downlink channels from the uplink pilots using channel reciprocity.
 

### 2015-06-22 Report/wsrm_formulation.tex
updated

@@
-\review{We present iterative algorithms to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with the \ac{SCA} presented \cite{marks1978technical}.
+We present iterative algorithms to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with the \ac{SCA} presented \cite{marks1978technical}.
 The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system.
 The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint.
-However, by using additional variables, we can relax the \ac{SINR} expression in \eqref{eq:SINR} by inequality constraints to solve the problem \eqref{eqn-3} as}
+However, by using additional variables, we can relax the \ac{SINR} expression in \eqref{eq:SINR} by inequality constraints to solve the problem \eqref{eqn-3} as
 \iftoggle{single_column}{
@@
 }
-\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3}.
+The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3}.
 Note that \eqref{eqn-6.2} is an under-estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by variable \me{\beta_{l,k,n}}.
 Therefore, the problem formulation in \eqref{eqn-6} is an equivalent approximation for the problem presented in \eqref{eqn-3}.
-Note that the \ac{JSFRA} formulation in \eqref{eqn-6} can be reformulated as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, and therefore it belongs to the class of NP-hard problems.}
+Note that the \ac{JSFRA} formulation in \eqref{eqn-6} can be reformulated as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, and therefore it belongs to the class of NP-hard problems.
 
@@
 Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-\review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}.
-By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}
+The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}.
+By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.
 
@@
 }
-In summary, for fixed linear receiver \review{\me{\mvec{w}{l,k,n}}} and operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
+In summary, for fixed linear receiver \me{\mvec{w}{l,k,n}} and operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-9}
@@
 where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex \ac{DC} constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}.
-\review{The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations.} \review{Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
-The dependency is implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which depend on the value of the exponent \me{q}.}
+The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations.
+Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
+The dependency is implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which depend on the value of the exponent \me{q}.
 
@@
 \end{IEEEeqnarray}}
-\review{Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance or the convergence behavior}.
+Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance or the convergence behavior.
 \begin{algorithm}
@@
 	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
-	\KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
-	update \me{\mvec{w}{l,k,n}, \mbf{u}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-8} with \me{{\mbf{m}}_{l,k,n}}\;
+	\KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-9.1d}}
+	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
 	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
@@
 The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved in an iterative manner by updating the operating point from the previous iteration.
-The iterative algorithm is referred to as \acl{QM} \ac{JSFRA} scheme with a per \ac{BS} power constraint, and it is outlined in Algorithm \ref{algo-1}.
-The iterative procedure repeats until the improvement on the objective is less than a predetermined tolerance parameter or the maximum number of iterations is reached.
-Instead of initializing \me{{\mbf{u}}_{l,k,n}} arbitrarily to a feasible point, transmit precoders can also be initialized with some feasible point \me{\tilde{\mbf{m}}_{l,k,n}}, which is then used to find \me{{\mbf{u}}_{l,k,n}} as seen in Algorithm \ref{algo-1}.
-For a fixed receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} for the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
-Next, the receive beamformers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
-This procedure is carried out until convergence of the queue deviation or a fixed number of iterations \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
+The iterative algorithm is referred as \acl{QM} \ac{JSFRA} scheme, and it is outlined in Algorithm \ref{algo-1}.
+\review{The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10} and \me{\tilde{\mbf{\beta}}_{l,k,n}} is updated using \eqref{eqn-9.1c} with the corresponding precoders and receivers.} For a fixed receiver \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} to find the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
+Next, the receivers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
+This procedure is carried out until convergence or for fixed number of iterations \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
 The convergence proof is discussed in Appendix \ref{sec-3.5}.

### 2015-06-23 Report/convergence_centralized.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
 Let us consider a general formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
-\begin{subeqnarray} \label{con}
-	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \slabel{con-obj} \\
-	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \slabel{con-dc} \\
-	&\quad& g_1(\mx,\my) \leq 0 \eqsub \slabel{con-cvx-blk} \\
-	&\quad& g_2(\mx) \leq 0 \eqsub \slabel{con-cvx}
-\end{subeqnarray}
-where \me{g_2,f} are convex and \me{h} is a linear function.
+\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
+	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
+	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
+	&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
+	&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
+\end{IEEEeqnarray}
+where \me{g_2} is convex and \me{h} is a linear function.
 Let \me{g_0,g_1} be convex in either \me{\mx} or \me{\my} but not on both.
-The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
+\review{Let \eqn{f} be a strongly convex function.
+Even though the objective function in \eqref{eqn-6.1} is not strongly convex, it can be regularized with an additional quadratic term as discussed in the next section to transform it to a strongly convex function.} The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
 Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
@@
 Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
-\begin{subeqnarray} \label{con-m}
-	\underset{\mx,\mz}{\text{minimize}} && f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \slabel{con-obj-m} \\
-	\text{subject to} && h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \slabel{con-dc-m} \\
-	&& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \slabel{con-cvx-blk-m}
-\end{subeqnarray}
+\begin{IEEEeqnarray}{rCl} \label{con-m} \neqsub
+	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
+	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
+	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \label{con-cvx-blk-m}
+\end{IEEEeqnarray}
 The feasible set defined by the problem in \eqref{con-m} is denoted as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
@@
 \begin{multline}\label{con-sub-set}\allowdisplaybreaks
-h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \\ + h(\iter{\mz}{k+1}{i}) \leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0.
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq \\
+h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 
 \end{multline}}
@@
 The feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not to be a stationary point of \eqref{con}, since it is a minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}.
+\review{Since the function \eqn{f} is strongly convex, the minimizer \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} obtained by the iterative \ac{SCA} algorithm is unique.}
 
@@
 The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
-Using (a),(b) and (c), we can guarantee the convergence of the objective value sequence generated by the iterative algorithm.
 
-\subsection{Uniqueness of the Beamformer Iterates}
+\subsection{Uniqueness of the Iterates and Strong Convexity}
 The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
@@
 
-In general, to ensure the uniqueness of the transmit precoders and the receive beamformers in all iterations, \textit{i.e}, even when the objective value is zero, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized with a strongly convex function.
-The objective function for the \me{\ith{i+1}} iteration can be regularized as
-\begin{equation}
-\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2_2
+To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, \textit{i.e}, even when the objective value is zero, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized with a strongly convex function.
+Now, the objective function for the iteration \me{\{k+1,i\}} is given as
+\begin{equation} \label{mod_obj}
+\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2
 \end{equation}
-where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant to make the objective strongly convex.
+where the vector \eqn{\mbf{z}} is either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the optimization variables and \me{c} is a positive constant to make the objective strongly convex.
 The uniqueness of the minimizer is guaranteed by the strongly convex objective function \cite{scutari_1}.
-The vector \me{\mbf{x}^{(i)}} is the value of \me{\mbf{x}} obtained from the \me{\ith{i}} iteration.
+The vector \me{\mbf{z}^{(i)}_{k}} is the value of \me{\mbf{z}} obtained from the earlier iteration \me{\{k,i\}}.
+\review{Note that the modified objective in \eqref{mod_obj} is strongly convex, and therefore has an unique minimizer, which is obtained by the \ac{SCA} algorithm.}
 
@@
 To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
+\subsection{Strict Monotonicity of the Objective Sequence} \label{c-e}
+\review{So far we have discussed the uniqueness of the iterates at each \ac{SCA} update points and the monotonicity requirement for the \ac{SCA} convergence.
+In this, we discuss the strict monotonicity requirement of the objective function, which is required for the global convergence proof as in \cite{zangwill1969nonlinear,meyer1976sufficient}.
+In order to prove that, let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point in the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be the point-to-set mapping algorithm defined as
+\begin{equation} \label{g-algo}
+\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) =
+\begin{cases}
+\underset{\mx,\mz}{\mathrm{argmin}} \; f(\mx,\mz;\iter{\my}{\ast}{i-1})& \forall \mx,\mz \in \iter{\mc{X}}{\ast}{i} \\
+\underset{\my,\mz}{\mathrm{argmin}} \; f(\my,\mz;\iter{\mx}{\ast}{i})& \forall \my,\mz \in \iter{\mc{Y}}{\ast}{i} 
+\end{cases}
+\end{equation}
+Note that each iteration \me{i} of the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for \me{\my} by fixing \me{\mx} as constant.
+At each \ac{SCA} convergence points, the objective holds with equality, and therefore it is not strictly monotonic.
+However, since the algorithm is defined to include two \ac{SCA} updates until convergence, the objective decreases monotonically at every update points \me{i}.
+Using the strong convexity of the objective function, it can be ensured that the decrement is strictly monotonic and it also has a unique minimizer.
+Using (a),(b) and (c), we can guarantee the convergence of the objective value sequence generated by the iterative algorithm.}
 
 \subsection{Convergence of the Beamformer Iterates} \label{c-b}
-So far, we have considered the convergence of the objective sequence.
-In this section, we discuss the convergence of the beamformer iterates generated by the iterative algorithm for \eqref{con} using \cite{zangwill1969nonlinear,meyer1976sufficient}.
-Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point in the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be the point-to-set mapping algorithm defined as
-\begin{equation} \label{algorithm_fixed}
-\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}.
-\end{equation}
-Since the algorithm finds a unique solution in each iteration,\footnote{Index \me{i} denotes the \ac{AO} iteration to update the vector \me{\ma}, which involves two \ac{SCA} iterations performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for the variable \me{\my} by fixing \me{\mx} as constant.} the mapping denoted by \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
-Let \me{\mc{F}^\ast \subset \mc{F}} be the set of fixed points, \textit{i.e}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.
+Since the algorithm \eqn{\mc{A}} finds an unique minimizer after two inner \ac{SCA} convergence, the algorithm mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
+In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\ast \subset \mc{F}} as the set of fixed points, \textit{i.e}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.
 
-Using \cite[Th. 3.1]{meyer1976sufficient}, convergence of the iterates to a fixed point can be shown, if the following conditions are satisfied.
+Now by using \cite[Th. 3.1]{meyer1976sufficient}, convergence of the iterates to a fixed point can be shown, if the following conditions are satisfied.
 \begin{itemize}
@@
 \end{itemize}
-Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{algorithm_fixed} and the strict monotonicity can also be verified from \eqref{fixed_point}.
+\review{Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity is guaranteed from Section \ref{c-e} with modified objective in \eqref{mod_obj}}.
 Using \cite{zangwill1969nonlinear} and \cite[Th.

### 2015-06-23 Report/convergence_distributed.tex
updated revision 2 with ADMM proof and strict monotonicity

--- 2015-04-13 Report/convergence_distributed.tex
@@
 The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
-The feasible set of the problem in \eqref{eqn-decent-1} satisfies the Slater's constraint by having a non-empty interior and is also compact.
-Since the subproblem in \eqref{eqn-decent-1} is convex, the convergence of the primal and the \ac{ADMM} scheme can be guaranteed by using the discussions in \cite{bertsekas1999nonlinear,boyd2011distributed} and \cite[Prop.
-4.2]{bertsekas1989parallel}.
+Note that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and the set is compact, which is required for the distributed approach to converge.
+Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem can be guaranteed as the iteration index \me{i \rightarrow \infty} for a diminishing step size \cite{bertsekas1999nonlinear}.
+
+To prove the convergence of the \ac{ADMM} approach, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
+\begin{IEEEeqnarray}{rCl} \neqsub
+	\underset{\mbf{x},\mbf{z}}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
+	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm} \\
+	&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2 \eqsub
+\end{IEEEeqnarray}
+the following conditions are required for the convergence.
+\begin{itemize} \allowdisplaybreaks
+	\item \me{G,H} should be convex
+	\item \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded
+	\item \me{\mbf{A}^\herm \mbf{A}} should be invertible.
+\end{itemize}
+Note that the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}.
+It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible.
+The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has a nonempty interior.
+The feasibility of the interior point is verified by having a non-zero precoder for only one user.
+Therefore, by following \cite[Prop.
+4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.
+The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if it is iterated until convergence.
+
+However, if the distributed algorithm is terminated well before the convergence or performed for limited iterations, convergence of the algorithm is not guaranteed.
+Since at each update of \eqn{\mbf{x}^{(i)}}, which involves two \ac{SCA} updates until convergence with limited distributed iterations at each \ac{SCA} step, the monotonicity of the objective is not guaranteed, and therefore the convergence, unless the number of iterations is large enough to have strictly decreasing objective.
+In this case, the limit point is a stationary point of the original nonconvex problem following \cite{zangwill1969nonlinear,meyer1976sufficient}.
 
 Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
-Therefore, it is difficult to prove theoretically the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.
+Therefore, it is difficult to theoretically prove the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.
 

### 2015-06-23 Report/decomposition_solutions.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
 Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
-\begin{subeqnarray} \label{eqn-decent-1} \allowdisplaybreaks
-&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \slabel{eqn-decent-1a} \\
+\begin{IEEEeqnarray}{rCl} \label{eqn-decent-1} \allowdisplaybreaks  \neqsub
+&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \label{eqn-decent-1a} \\
 &\text{subject to}& \quad \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber
-\end{subeqnarray}
+\end{IEEEeqnarray}
 where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.
@@
 Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented as
-\begin{subeqnarray}
-\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b} \\
-\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran.
-\end{subeqnarray}
+\begin{IEEEeqnarray}{rCl} \neqsub
+\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b} \eqsub \\
+\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran. \eqsub
+\end{IEEEeqnarray}
 Let us define the vector \me{\mbfa{\zeta}_b}, formed by stacking the interference terms corresponding to the \ac{BS} \me{b} as

### 2015-06-23 Report/dual_approach.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
 Similar approach for the precoder design in the minimum power context is considered in \cite{admm_robust}.
-\begin{algorithm}
-	\SetAlgoLined
-	\DontPrintSemicolon
-	\BlankLine
-	\SetKwInput{KwInit}{Initialize}
-	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
-	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
-	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying \eqref{power_update}}
-	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
-	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
-	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
-	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
-		\Repeat{convergence or \me{i \geq I_{\max}}}{
-			initialize \me{j=0} \;
-			\Repeat{convergence or \me{j \geq J_{\max}}}{
-				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
-				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
-				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
-				\me{j = j + 1}\;
-			}
-			precoded downlink pilot transmission with \me{\mvec{m}{l,k,n}}\;
-			update \me{\mvec{w}{l,k,n}} to all \acp{BS} in \me{\mc{B}} using precoded uplink pilots \cite{komulainen2013effective}\;
-			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
-			$i = i + 1$ \;
-		}
-	}
-	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
-	\label{algo-3}
-\end{algorithm}
 
@@
 \iftoggle{single_column}{\allowdisplaybreaks
-\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks
+\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
 \underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
@@
 \end{IEEEeqnarray}
-}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks
+}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
 &\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
@@
 The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
+\begin{algorithm}
+	\SetAlgoLined
+	\DontPrintSemicolon
+	\BlankLine
+	\SetKwInput{KwInit}{Initialize}
+	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
+	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
+	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
+	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
+	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
+	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
+		\Repeat{convergence or \me{i \geq I_{\max}}}{
+			\Repeat{convergence or \me{j \geq J_{\max}}}{
+				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
+				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
+				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
+				\me{j = j + 1}\;
+			}
+			precoded downlink pilot transmission with \me{\mvec{m}{l,k,n}}\;
+			update \me{\mvec{w}{l,k,n}} to all \acp{BS} in \me{\mc{B}} using precoded uplink pilots \cite{komulainen2013effective}\;
+			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
+			$i = i + 1$, \me{j=0} \;
+		}
+	}
+	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
+	\label{algo-3}
+\end{algorithm}
 

### 2015-06-23 Report/ieee_journal.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
 \usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
-\usepackage{multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools,url,subeqnarray}
+\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases}
 
@@
 
-\subsection{Queue Weighted Sum Rate Maximization (\acs{Q-WSRM}) Formulation} \label{sec-3.1} %\acused{Q-WSRM}
+\subsection{Queue Weighted Sum Rate Maximization (\acs{Q-WSRM})} \label{sec-3.1} %\acused{Q-WSRM}
 \input{joint_wsrm_formulation}

### 2015-06-23 Report/introduction.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
 In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders.
-The fixed interference is then updated by using the subgradient method as discussed in \cite{pennanen2011decentralized}.
+The fixed interference is then updated using the subgradients as discussed in \cite{pennanen2011decentralized}.
 The dual and the \ac{ADMM} approaches control the distributed subproblems by fixing the \emph{`interference price'} for each \ac{BS} as detailed in \cite{tolli2011decentralized}.
@@
 The rest of the paper is organized as follows.
-In Section \ref{sec-2-3.2}, we introduce the system model and the problem formulation for the queue minimizing precoder design.
-The existing and the proposed centralized precoder designs are presented in Section \ref{sec-3}.
+Section \ref{sec-2-3.2} introduces the system model and the problem formulation for the proposed design.
+The existing and the proposed centralized designs are presented in Section \ref{sec-3}.
 The distributed solutions are provided in Section \ref{sec-4} followed by the simulation results in Section \ref{sec-5}.

### 2015-06-23 Report/joint_wsrm_formulation.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
-The queue minimizing algorithms have been extensively discussed in the networking literature to provide congestion-free routing between any two nodes in the network.
+The queue minimizing algorithms have been studied extensively in the networking literature to provide congestion-free routing between any two nodes in the network.
 One such algorithm is the \emph{backpressure algorithm} \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
-It determines an optimal control policy in the form of rate or resource allocation for the nodes in the network by considering the differential backlogged packets between the source and the destination nodes.
-Even though the algorithm is primarily designed for the wired infrastructure, it can be extended to the wireless networks by designing the user rate variable \me{t_k} in accordance to the wireless network.
+It finds an optimal control policy in the form of rate or resource allocation by considering the differential backlogged packets between the source and the destination nodes for the networking entities.
+%Even though the algorithm is primarily designed for the wired infrastructure, it can be extended to the wireless networks by designing the user rate variable \me{t_k} in accordance to the wireless network.
 
@@
 \iftoggle{single_column}{
-\begin{equation}\label{eqn-3.1}
+\begin{equation} \label{eqn-3.1}
 \mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} = \frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ].
 \end{equation}}{
-\begin{multline}\label{eqn-3.1}
+\begin{multline} \label{eqn-3.1}
 \mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} = \\ \frac{1}{2} \Big [ \sum_{k \in \mc{U}} \, \Big ( \left [ Q_k(i) - t_k(i) \right ]^+ + \lambda_k(i) \Big )^2 - Q^2_k(i) \Big ].
@@
 \iftoggle{single_column}{
-\begin{IEEEeqnarray}{rCl} \label{backpressure-approx}
+\begin{IEEEeqnarray}{rCl} \label{backpressure-approx} \neqsub
 	\underset{\mbf{t}}{\text{inf}} &\quad& \Delta(\mbf{Q}(i)) \triangleq \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
@@
 \end{IEEEeqnarray}}{
-\begin{IEEEeqnarray}{CL} \label{backpressure-approx}
-	\underset{\mbf{t}}{\text{inf}} \quad & \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \IEEEyessubnumber \\
+\begin{IEEEeqnarray}{CL} \label{backpressure-approx} \neqsub
+	\underset{\mbf{t}}{\text{inf}} \quad & \mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set{\mathrm{L}\sset{\mbf{Q}(i+1)} - \mathrm{L}\sset{\mbf{Q}(i)} \vert \mbf{Q}(i)} \eqsub \\
 	\leq & \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \Big \lbrace \sum_{k \in \mc{U}} \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i) \Big \rbrace }_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) \nonumber \\
@@
 Since the expectation is minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
-\begin{IEEEeqnarray}{LCl} \label{q_gen_sum}
+\begin{IEEEeqnarray}{LCl} \label{q_gen_sum} \neqsub
 \underset{\substack{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
@@
 
-As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}.
+%As a special case of the problem defined in \eqref{q_gen_sum}, we can formulate the sum rate maximization problem by setting the weights in \eqref{eqn-3.1.1} as unity, leading to the problem as in \eqref{q_gen_sum} with \me{Q_k = 1, \forall k \in \mc{U}}.
 This approach provides a greedy queue minimizing allocation as compared to \ac{Q-WSRME}, since the resource allocation is driven by the channel conditions in comparison to the number of queued packets as in \ac{Q-WSRME}.

### 2015-06-23 Report/primal_approach.tex
updated - final - draft
ordered algorithm locations
updated revision 2 with ADMM proof and strict monotonicity

@@
 The primal approach is similar to the minimum power precoder design presented in \cite{pennanen2011decentralized}.
-Note that the master problem treats \me{\mbfa{\zeta}_{b}} as a variable and the slave subproblems assumes it to be a constant for each iteration to find the transmit precoders.
-
+Note that the master problem treats \me{\mbfa{\zeta}_{b}} as a variable and the slave subproblems assumes it to be a constant in each iteration.
 \begin{comment}

### 2015-06-23 Report/problem_formulation_intro.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
 To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation objective as
-\begin{equation}
+\begin{equation} \label{eqn-4.2}
 v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})
-\label{eqn-4.2}
 \end{equation}
@@
 Explicitly, the objective of the problem considered is given as \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. Thus the formulation becomes
-\begin{IEEEeqnarray}{rCl}\label{eqn-3}
-\underset{\substack{\mvec{m}{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q\IEEEyessubnumber \label{eqn-3-1.a} \\
-\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \fall b \IEEEyessubnumber \eqspace \label{eqn-4.3}
-\end{IEEEeqnarray}
+\begin{IEEEeqnarray}{rCl} \label{eqn-3} \eqsubn
+\underset{\substack{\mvec{m}{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-3-1.a} \\
+\text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \fall b \eqspace \label{eqn-4.3} \end{IEEEeqnarray}
 where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor, which is used to alter the user priority based on the \ac{QoS} constraints such as packet delay requirements and packet waiting time, since they are proportional to the corresponding number of backlogged packets.

### 2015-06-23 Report/simulation_results.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
 The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets are few in number.
-In contrast, the \ac{Q-WSRME} algorithm provides more favorable allocation with the explicit rate constraint to avoid the over-allocation.
+In contrast, the \ac{Q-WSRME} algorithm provides better allocation with the explicit rate constraint to avoid the over-allocation.
 For both scenarios in Fig.
-\ref{fig-a}, the \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the algorithm.
-It is due to the fact that the \ac{Q-WSRME} algorithm favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
+\ref{fig-a}, the \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the algorithm, since the \ac{Q-WSRME} scheme favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
 Fig.
 \subref*{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case.
-In all figures, the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} in Algorithm \ref{algo-1}.
-The degradation by performing combined update is marginal, since the receiver minimizes the objective for a fixed transmit precoders.
+The receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} on all figures.
+However, degradation in the performance is marginal, since the receiver minimizes the objective for fixed precoders.
 

### 2015-06-23 Report/wsrm_formulation.tex
updated revision 2 with ADMM proof and strict monotonicity

@@
 \iftoggle{single_column}{
-\begin{IEEEeqnarray}{CCl}\label{eqn-6}
-\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
+\begin{IEEEeqnarray}{CCl}\label{eqn-6}  \neqsub
+\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \label{eqn-6.1} \\
 \text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-6.2} \\
@@
 }{\allowdisplaybreaks
-\begin{IEEEeqnarray}{CCl} \label{eqn-6}
-	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
+\begin{IEEEeqnarray}{CCl} \label{eqn-6}  \neqsub
+	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm} \label{eqn-6.1} \\
 	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
@@
 Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}.
-Let us define a function,
-\begin{equation}
+Let
+\begin{IEEEeqnarray}{l}
 f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
-\end{equation}
-where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation.
+\end{IEEEeqnarray}
+be a function, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector to be identified for the optimal allocation.
 Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
@@
 For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
-\begin{IEEEeqnarray}{rCl} \label{eqn-wsrm-expr}
+\begin{IEEEeqnarray}{rCl} \label{eqn-wsrm-expr}  \neqsub
 p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}} \eqsub \\
@@
 \iftoggle{single_column}{
-\begin{equation}\label{eqn-8}
+\begin{IEEEeqnarray}{l} \label{eqn-8} \IEEEyesnumber
 	2 \frac{\tilde{p}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( p_{l,k,n} - \tilde{p}_{l,k,n} \right ) + 2 \frac{\tilde{q}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left ( q_{l,k,n} - \tilde{q}_{l,k,n} \right ) + \frac{\tilde{p}_{l,k,n}^2 + \tilde{q}^2_{l,k,n}}{\tilde{\beta}_{l,k,n}} \left (1 - \frac{\beta_{l,k,n} - \tilde{\beta}_{l,k,n}}{\tilde{\beta}_{l,k,n}} \right ) \geq \gamma_{l,k,n}.
-\end{equation}
+\end{IEEEeqnarray}
 }{
@@
 In summary, for fixed linear receiver \me{\mvec{w}{l,k,n}} and operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
-\begin{IEEEeqnarray}{CCl}\label{eqn-9}
+\begin{IEEEeqnarray}{CCl}\label{eqn-9} \neqsub
 \underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
@@
 Now, the optimal linear receivers for fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
-\begin{IEEEeqnarray}{CCl}\label{eqn-9--1}
+\begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub
 \underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
@@
 Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mbf{w}^{o}_{l,k,n}} as
-\begin{IEEEeqnarray}{rCl}
+\begin{IEEEeqnarray}{rCl} \neqsub
 \mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
@@
 \allowdisplaybreaks{
-\begin{IEEEeqnarray}{rCl}
+\begin{IEEEeqnarray}{rCl} \neqsub
 \mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
@@
 \end{IEEEeqnarray}}
-Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance or the convergence behavior.
+Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance.
+
+The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved iteratively by updating the operating point from the previous iteration.
+The iterative algorithm is referred as \acl{QM} \ac{JSFRA} scheme, and it is outlined in Algorithm \ref{algo-1}.
+\review{The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is updated using \eqref{eqn-9.1c} with the chosen transmit precoders and the receivers.} For a fixed receiver \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} to find an optimal transmit precoders \me{\mvec{m}{l,k,n}}.
+Next, the receivers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
+The iterative procedure is performed until convergence or for fixed number of iterations \me{I_{\max}} as shown in Algorithm \ref{algo-1}.
+The convergence analysis is given in Appendix \ref{sec-3.5}.
 \begin{algorithm}
@@
 	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
-	\KwInit{\me{i=0} and transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-9.1d}}
+	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
 	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
 	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
-		initialize \me{j = 0}\;
 		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
@@
 		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
-		$i = i + 1$\;
+		$i = i + 1$, \me{j = 0}\;
 	}
@@
 \end{algorithm}
-
-The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved in an iterative manner by updating the operating point from the previous iteration.
-The iterative algorithm is referred as \acl{QM} \ac{JSFRA} scheme, and it is outlined in Algorithm \ref{algo-1}.
-\review{The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10} and \me{\tilde{\mbf{\beta}}_{l,k,n}} is updated using \eqref{eqn-9.1c} with the corresponding precoders and receivers.} For a fixed receiver \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} to find the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
-Next, the receivers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
-This procedure is carried out until convergence or for fixed number of iterations \me{I_{\max}} as outlined in Algorithm \ref{algo-1}.
-The convergence proof is discussed in Appendix \ref{sec-3.5}.
 

### 2015-06-27 Response/Response 2/response-1.tex
before sending to nam and antti

@@
 Comments:
-The response to the reviewer's concerns are generally satisfying, except the convergence proof.
+\review{The response to the reviewer's concerns are generally satisfying, except the convergence proof.}
 
 \vspace{0.1in}
-\review{We thank the reviewer for providing valuable and insightful comments.}
+We thank the reviewer for providing valuable and insightful comments.
 
@@
 \begin{enumerate}
-\cmnt{1} Considering the length of the manuscript, it would be better to shorten some parts that are not new in this manuscript, e.g.
+\cmnt{1} \review{Considering the length of the manuscript, it would be better to shorten some parts that are not new in this manuscript, e.g.
 III.A.
 More space can be left for convergence proof, which is very important.
-
-\resp \review{We thank the reviewer for the comment. 
 }
 
-\cmnt{2} In convergence proof (48), why does the 2nd inequality hold?
-In fact, to prove the feasibility of  \eqn{{m_{k+1}^{(i)}, w_{*}^{(i-1)};m_k^{(i)} }}, the part between 2nd and 3rd inequality is not necessary, ''<=0'' directly follows the 2nd inequality since the solution \eqn{m_{k+1}^{(i)}, \gamma_{k+1}^{(i)} } is the optimal solution, and therefore  feasible.
+\resp We understand the reviewer concern.
+Based on the suggestion, we have removed couple of paragraphs from Section III.A and shortened the discussions on the simulation section to provide additional details for the convergence proof.
 
-\resp \review{
+\cmnt{2} \review{In convergence proof (48), why does the 2nd inequality hold?
+In fact, to prove the feasibility of  \eqn{{m_{k+1}^{(i)}, w_{*}^{(i-1)};m_k^{(i)} }}, the part between 2nd and 3rd inequality is not necessary, \eqn{\leq 0} directly follows the 2nd inequality since the solution \eqn{m_{k+1}^{(i)}, \gamma_{k+1}^{(i)} } is the optimal solution, and therefore feasible.
 }
 
-\cmnt{3} The solutions SCA iterations \eqn{m^{(i)}_k} does not necessarily converge.
-In fact \eqn{m} has compact feasible region, and thus \eqn{m^{(i)}_k} has limit points for any specific \eqn{i}.
-However \eqn{m_{*}^{(i)}} does not necessarily exist( the whole sequence \eqn{m^{(i)}_k} may be not convergent).
-Similar problem happens to \eqn{w^{(i)}_k}.
+\resp We thank the reviewer for the critical comment.
+It is not possible to define the inequality with the previous optimal point.
+Since it is not possible to comment on the inclusion of the previous constraint set in the current update (except the earlier optimal point), the inequality is not guaranteed.
+Based on the comment from the reviewer, we have removed the inequality specifying the previous operating point from (48), since the newly found optimal point is inside the feasible set.
 
-\resp \review {	
+\cmnt{3} \review{The solutions SCA iterations \eqn{\mbf{m}^{(i)}_k} does not necessarily converge.
+In fact \eqn{\mbf{m}} has compact feasible region, and thus \eqn{\mbf{m}^{(i)}_k} has limit points for any specific \eqn{i}.
+However \eqn{m_{*}^{(i)}} does not necessarily exist( the whole sequence \eqn{\mbf{m}^{(i)}_k} may be not convergent).
+Similar problem happens to \eqn{\mbf{w}^{(i)}_k}.
 }
 
-\cmnt{4} Strict monotonicity with respect to the objective function \eqn{f} should be rigorously proved.
-Note that to guarantee the uniqueness of the beamformer iterates, (52) instead of the objective function is used.
+\resp We understand the reviewer concern.
+Even though the \ac{SCA} algorithm converges, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge.
+It is true that the iterates need not converge when the objective function is convex.
+We have modified the discussion on the strong convexity of the objective function to impose the uniqueness of the iterates in each \ac{SCA} update as well.
+By regularizing the objective function with a strongly convex term like \eqn{\|\mbf{m} - \mbf{m}^{(i)}_k\|^2}, we can guarantee the uniqueness of the iterates upon the \ac{SCA} convergence.
+We thank the reviewer for citing this issue on the sequence convergence and the uniqueness of the minimizer.
+We have included this information in the centralized convergence proof on Appendix A-B after (44), after (49) and on Appendix A-C to describe the strong convexity.
 
-\resp \review{}
+\cmnt{4} \review{Strict monotonicity with respect to the objective function \eqn{f} should be rigorously proved.
+Note that to guarantee the uniqueness of the beamformer iterates, (52) instead of the objective function is used.}
 
-\cmnt{5} Note that the conclusions [32, Thm 2] and [26, Thm 10] have lots of assumptions.
+\resp We thank the reviewer for the pointing out the issue involving the strict monotonicity.
+As suggested by the reviewer, we have included Appendix A-D to discuss the strict monotonicity of the objective function in each update point of the algorithm.
+Due to the strong convexity of the objective function, strict monotonicity is ensured after each update and also upon convergence.
+In order to ensure the strict monotonicity in the objective until convergence, \textit{i.e}, \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k} and equal only when \eqn{\mbf{z}^{(i)}_k = \mbf{z}^{(i)}_{k+1}}, which is a limit point.
+Since each of the earlier update in the \ac{SCA} are strictly monotonic, we consider the point where the original convex function, say, \eqn{\hat{f}} has multiple limit points with the same objective value \eqn{\hat{f}(\mbf{z})}, where \eqn{f(\mbf{z}) = \hat{f}(z) + \|\mbf{z} - \mbf{z}_k^{(i)}\|^2} is the modified objective function from the \eqn{\ith{k+1}} iteration.
+Since \eqn{\hat{f}(\mbf{z})} is convex, it can have multiple limit points, therefore, it is monotonic.
+However, due to the strong convexity of \eqn{f(\mbf{z})} in (52), the limit point of the \ac{SCA} updates is also unique, and therefore has strict monotonicity in \eqn{f(\mbf{z}^{(i)}_k)} in each update.
+It can be justified, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even by including other limit points in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}} with the same original objective value as \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
+This information and the proof is also included in the revised manuscript in Appendix A-D.
+
+\cmnt{5} \review{Note that the conclusions [32, Thm 2] and [26, Thm 10] have lots of assumptions.
 To invoke these reference, explicit exposition should be provided to show that these conclusions can be applied to our problem.
@@
 Too many details are omitted to make the proof convincing and clear.
+}
 
-\resp \review{}
+\resp We thank the reviewer for raising the concern.
+We have updated the manuscript to include the details regarding the stationary point discussion in Appendix A-F and the convergence proof analysis for the primal and the \ac{ADMM} algorithms in Appendix B.
+Additional detail includes the conditions required for showing the stationarity of the limit point and we have included more details to utilize the conclusions from [37] to show the convergence of the ADMM scheme.
 

### 2015-06-27 Response/Response 2/response-2.tex
before sending to nam and antti

@@
-The authors have addressed many of my previous comments. However, there are still several major issues that need further clarification.
+\review{The authors have addressed many of my previous comments. However, there are still several major issues that need further clarification.}
 
 \vspace{0.1in}
-\review{We would like to thank the reviewer for providing valuable comments.}
+We thank the reviewer for providing useful comments. The comments are constructive and helped us to improve the manuscript better.
 
 \begin{enumerate}
-\cmnt{1} The revised paper did not address my previous comment about how to select the sub-channel ordering.
+
+\cmnt{1} \review{The revised paper did not address my previous comment about how to select the sub-channel ordering.
 I understand that finding the best sub-channel ordering requires exhaustive search which has extremely high complexity.
 But it is important to provide a guidance on what would be a good choice of sub-channel ordering.
-For example, can we achieve a good performance by using a low complexity ordering algorithm such as a greedy sub-channel ordering algorithm?
+For example, can we achieve a good performance by using a low complexity ordering algorithm such as a greedy sub-channel ordering algorithm?}
 
-\resp \review{}
+\resp We apologize for not discussing the sub-channel ordering guidelines in a detailed manner.
+As suggested by the reviewer, we have included the guidelines on selecting the sub-channel ordering based on the greedy selection, which could be an educated guess over the random sub-channel ordering.
+Even though the number of backlogged packets must also be involved in the sub-channel ordering, greedy selection provides an effective ordering when the queues are fairly equal among the serving users or when the number of backlogged packets are significantly large.
+This information is now included in the revised manuscript under Section III-D final paragraph.
+We have included a plot comparing different ordering schemes to justify the above statement.
+Even though we are not including it in the paper, we have included in the response letter to justify the reviewers claim.
+We considered a system model with \eqn{N = 6} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users.
+The \ac{PL} is distributed uniformly over \eqn{[0,-3]} dB.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{reviewer_2_Q1.eps}
+	\caption{Convergence of the algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 6,2,12,4,1 \rbrace} using \me{\ell_1} norm}
+	\label{fig-review-1}
+\end{figure}
 
-\cmnt{2} The authors mentioned that the signaling overhead of the distributed algorithm can be reduced by using a smaller number of iterations \eqn{J_{\max}}.
+Fig.
+\ref{fig-review-1} compares different ordering of sub-channels with the total number of backlogged packets remaining in the system as the metric.
+The random ordering are based on permutation of the sub-channel indices and sequential ordering is the natural way of selection.
+The greedy sub-channel ordering is based on sorting the best channel from each sub-channel, which is obtained by finding the highest channel norm between the users from the respective serving \ac{BS}.
+As pointed out by the reviewer, greedy scheduling performed much better when compared to the other random ordering schemes.
+
+\cmnt{2} \review{The authors mentioned that the signaling overhead of the distributed algorithm can be reduced by using a smaller number of iterations \eqn{J_{\max}}.
 But still, you didn't answer my question about whether the signaling overhead of the distributed algorithm is smaller than the centralized algorithm.
@@
 Is it possible that the distributed algorithm always has more signaling overhead than the centralized algorithm even when \eqn{J_{\max} = 1}?
-Finally, there is a tradeoff between performance and signaling overhead (\eqn{J_{\max}}) for the distributed algorithm.
-For the same signaling overhead (we can control \eqn{J_{\max}} to make the signaling overhead of the distributed algorithm approximately equal to that of the centralized algorithm), does the distributed algorithm achieve better performance than the centralized algorithm?
+Finally, there is a trade-off between performance and signaling overhead (\eqn{J_{\max}}) for the distributed algorithm.
+For the same signaling overhead (we can control \eqn{J_{\max}} to make the signaling overhead of the distributed algorithm approximately equal to that of the centralized algorithm), does the distributed algorithm achieve better performance than the centralized algorithm?}
 
-\resp \review{
-}
+\resp
+	We thank the reviewer for the insightful comment and we apologize for the lack of clarity in explaining this information in our earlier manuscript.
+	\begin{enumerate}
+		\item Quantifying the signaling overhead of the distributed algorithm over the centralized one depends on the system model under consideration.
+For example, let us consider a model with \eqn{N = 1,N_B = 2,K = 4,N_T = 4,N_R = 1}, where each \ac{BS} has two users.
+In this scenario, the amount of information exchange to perform a centralized algorithm by a common controller requires the knowledge of complete channel matrices interlinked in the system, \textit{i.e}, the number of users times the \acp{BS}.
+In order to quantify the total number of bits required to be exchanged, let us assume that each complex channel for a single-input single-output requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is important).
+Using this assumption, the total number of channel information in bits to be exchanged via backhaul requires \eqn{10 \times K \times N_B \times N_R \times N_T \approx 320} bits.
+On the other hand, for the distributed case, let us consider \eqn{6} bits are required to quantize the scalar interference in the consensus vector.
+Therefore, it requires \eqn{6 \times 2 \times 2} bits of information to be exchanged for each iteration.
+With this overhead, we can perform only \eqn{6} \ac{SCA} updates with \eqn{J_{\max} = 2} internal iterations in each to reach the centralized overhead.
+Note that the number iteration includes the \ac{SCA} update as well.
+However, by knowing the complete channel of the users in the system, the centralized controller can perform the precoder design until convergence.
+However, as the number of sub-channels, users or the antenna element increases, it may not be a viable option to feedback the user channels across the coordinating \acp{BS} to the centralized controller.
+The quantizing the channel information degrades the achievable performance of the centralized solution that also needs to be considered while comparing the signaling overhead.
+		\item Using the above discussion, we can say that when the system size is huge, it would be favorable to consider the distributed algorithm over the centralized approach due to the huge signaling overhead involved in exchanging the channels.
+		\item In particular, \ac{ADMM} and primal approach requires significant overhead compared to the centralized algorithm when \eqn{J_{\max} = 1} for a small system, since by exchanging the quantized channels, each \ac{BS} can perform the centralized algorithm independently until convergence.
+However, it depends on the channel quantizer, which is likely to be based on the channel density function (eg.
+Lloyd quantizer).
+For a system involving more number of coordinating \acp{BS}, users and number of antenna elements, it would be beneficial to use distributed algorithm with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
+		\item Even with the same signaling overhead, it is not possible to prove the benefits of the distributed algorithm like \ac{ADMM} and primal approach over the independent centralized scheme performed by exchanging the channel state information across the \acp{BS}.
+It is dependent on the system model under consideration.
+As explained earlier, for the considered system model, the independent centralized algorithm performs better in terms of the over head involved.
+	\end{enumerate}
 
-\cmnt{3} If the authors can't prove the convergence of the ADMM algorithm (or the decomposition approach via KKT conditions) in Section IV.B, then at least, you should discuss the property of the fixed point of the algorithm.
+	We have included the above information briefly in Section IV-C first paragraph and in the last paragraph.
+We have also included this information in the paragraph before the Conclusions section.
+Having said that, note that in reality, the channel is time-correlated, and it is often enough to update the precoders once per radio frame or certain number of symbols later.
+It is not necessary for the decentralized algorithm to converge until the end, it is only important to follow the fading process when \eqn{J_{\max} > 1}.
+The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13], which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+The distributed algorithm for the time correlated case is not provided in the current manuscript, since it is not in the scope of the precoder design algorithms considered in this manuscript.
+However, for the clarity purpose, we have provided a plot demonstrating this behavior for the \ac{KKT} based algorithm in Section IV-C presented in the manuscript.
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[width=0.8\columnwidth]{reviewer_2_Q2.eps}
+		\caption{Average number backlogged packets after each transmission for system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,16,4,2 \rbrace} evaluated for \eqn{500} slots}
+		\label{fig-review-2}
+	\end{figure}
+
+	Fig.
+\ref{fig-review-2} compares the performance of the distributed \ac{KKT} approach presented in Section IV-C for different iteration.
+The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.
+We considered that the channel is coherent over \eqn{N_S = 100} symbols or frames and the precoder update is performed by exchanging the equivalent channel for \eqn{J_{\max} = 3,5,10} number of iterations.
+The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{J_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{J_{\max}}{N_S})} is considered as a penalty involved due to the precoder exchange.
+The average number of backlogged packets after each transmission slot is evaluated as
+	\begin{equation}
+	\chi = \sum_{k = 1}^K \; [ Q_k - \tilde{t}_k ]^+
+	\end{equation}
+	Unlike the distributed algorithm, the centralized scheme presented in Fig.
+\ref{fig-review-2} has no penalty term and it is used as a benchmark for the other figures.
+In order to improve the performance of the distributed scheme, the operating point involved in the \ac{SCA} algorithm is considered from the earlier frame instead of starting initializing randomly.
+Since we use \ac{KKT} approach, we can either use all users in the system for the precoder design or we can utilize single-cell MU-MIMO user selection presented in the literature to limit the number of users for which the precoders are designed, which leads to the faster convergence.
+As we can see from Fig.
+\ref{fig-review-2}, as the arrival rate per user increases, the performance of \ac{KKT} schemes with \eqn{J_{\max} = 3,5,10} converges since the number of backlogged packets are significantly large, therefore, the same set of users will be served by the algorithm with better precoders by utilizing the memory.
+
+	In spite of using memory and prior scheduling in the \ac{KKT} approach, isolated single \ac{BS} processing performs much better than the distributed scheme due to the limited number of iterations allowed in the algorithm.
+Note that the precoders are not updated for the desired users until convergence, after the limited number of iterations.
+However, if we perform the single cell precoder design by considering the neighboring precoders as fixed after the recent exchange as discussed in [28], we can improve the performance significantly for Algorithm 3 as shown by red curves in Fig.
+\ref{fig-review-2}.
+In this approach, in between each exchange across the coordinating \acp{BS}, each \ac{BS} will perform \eqn{J_{\max} = 20} with the neighboring precoders as fixed.
+Once the iterations are performed to update the precoders, it is then exchanged across the coordinating \acp{BS} to perform the same procedure as mentioned earlier.
+
+\cmnt{3} \review{If the authors can't prove the convergence of the ADMM algorithm (or the decomposition approach via KKT conditions) in Section IV.B, then at least, you should discuss the property of the fixed point of the algorithm.
 For example, does there exist a fixed point of the algorithm?
@@
 Similar questions should also be answered for the decomposition approach via KKT conditions.
+}
 
-\resp \review{}
+\resp We thank the reviewer for raising the important concern regarding the convergence issue of the distributed algorithm with limited number of iterations.
+In view of this, we have updated the manuscript to include the discussion on the convergence of the distributed algorithms with limited number of iterations in Appendix B third paragraph after (55).
+Since the distributed algorithm cannot be guaranteed to be monotonic in each iteration, it is not possible to prove the convergence of the algorithm.
+However, if the algorithm is allowed to converge or iterated to guarantee the monotonicity of the objective, it is possible to prove the convergence based on the discussions provided in the manuscript.
+\begin{itemize}
+\item The fixed points for each convex subproblem exist, but may not be unique unless the objective function is regularized with a strongly convex term as discussed in Appendix A-C.
+\item If the distributed algorithm is iterated for limited number of iterations, it is not guaranteed to achieve the fixed point even if the outer \ac{SCA} update is performed for large number of iterations.
+In this scenario, it is not guaranteed to converge.
+In all our simulations on the primal and the \ac{ADMM} approach, we have iterated \eqn{J_{\max} = 20} in order to guarantee the monotonicity of the objective.
+\item Unless the objective function is regularized with a strongly convex term as in Appendix A-C, the uniqueness of the iterates is not guaranteed. 
+\item In each \ac{SCA} update, if the distributed algorithm converges to a fixed point, then the overall convergence will be a stationary point of the original nonconvex problem.
+It may not be an optimal solution to the original nonconvex problem.
+It can be proved based on the strict monotonicity of the objective, since the distributed algorithm converges to a centralized solution.
+\item Since the coupling between the distributed precoder designs are the interference between the BSs and the users, in the \ac{ADMM} approach, the interference is treated as a local variable, which is then included in the precoder design problem for each coordinating BS.
+This is treated as a local variable for a specific BS.
+Note that the local variable is an assumption made by the BS on the actual interference caused by the neighboring BSs.
+Since the actual interference caused is different, the consensus has to be made between the local interference variable maintained at each BS with the global consensus interference variable, which is nothing but the average between the corresponding BSs interference.
+These discussions have been made in the revised manuscript in Section IV-B.
+For further details we have also referred the interested reader to [11], which discusses exclusively about the ADMM approach.
+Upon convergence of the \ac{ADMM} approach, the interference vector can be considered as an upper bound of the actual interference seen in the network.
+It can be equal to the actual interference but not less.
+\end{itemize}
 

### 2015-06-27 Response/Response 2/response-3.tex
before sending to nam and antti

@@
-The authors have introduced changes in the manuscript that improved the paper's quality.
+\review{The authors have introduced changes in the manuscript that improved the paper's quality.
 Additionally, the authors have taken into account the reviewers' comments giving clarifications and modifying the content when required.
-More specifically, the following aspects have been treated:
+More specifically, the following aspects have been treated:}
 
 \vspace{0.1in}
-\review{We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helps to improve the manuscript.}
+\review{We thank the reviewer for recognizing the changes made on our earlier manuscript. We also thank the reviewer for providing constructive comments to help us to improve our manuscript.}
 
 \begin{enumerate}
-\cmnt{1} Convexity of problem (16).
+\cmnt{1} \review{Convexity of problem (16).
 The paragraphs surrounding (16) allow a better understanding of the usage of the additional variables, i.e.
 gamma and beta, to remove the equality constraint in (2).
-For the reviewer remains however unclear, the procedure/criterion to determine the operating point for the parameter \eqn{\tilde{\beta}} required in (19) and used in the convex subproblems (20) and (21).
+For the reviewer remains however unclear, the procedure/criterion to determine the operating point for the parameter \eqn{\tilde{\beta}} required in (19) and used in the convex subproblems (20) and (21).}
 
-\resp \review{
-	}
+\resp We understand the reviewer concern.
+The initial operating point for the \ac{SCA} approach can be identified by initializing the transmit precoders \eqn{\mvec{m}{l,k,n}} with the single user transmit beamformers satisfying the total power constraint at each \ac{BS}.
+Once the transmit precoders are initialized, the receive beamformers \eqn{\mvec{w}{l,k,n}} can be initialized with the \ac{MMSE} receiver based on (23).
+Upon initializing both transmit and the receive beamformers, the interference term \eqn{\beta_{l,k,n}} can be initialized from (20b).
+This information is included in the revised manuscript in the paragraph on Section III-B following after (23).
 
-\cmnt{2} Proof of convergence. The proof of convergence introduced by the authors in the Appendix seems correct and enhances the content of the manuscript.
+\cmnt{2} \review{Proof of convergence. The proof of convergence introduced by the authors in the Appendix seems correct and enhances the content of the manuscript.}
 
-\resp \review{}
+\resp We thank the reviewer for the comment. We have updated the manuscript further for better clarity and understanding based on the other reviewers.
 
@@
 
-	\cmnts{a} - {The reviewer considers that closing statements regarding the applicability of the proposed schemes are missing.
+	\cmnts{a} - \review{The reviewer considers that closing statements regarding the applicability of the proposed schemes are missing.
 Since the results are quite similar (when not identical), which formulation is preferable between the centralized schemes?
@@
 
-	\resp \review{}
+	\resp We understand the reviewer concern.
+We have updated the manuscript to include a discussion on the choice of selecting an algorithm for the practical purposes.
+The choice of selecting a centralized algorithm is equally fair when \eqn{N_R > 1}.
+For a single antenna receiver, the \ac{JSFRA} formulation in Section III-B is efficient, as there is no receiver update, and therefore has less complexity.
+The distributed algorithms based on primal and \ac{ADMM} schemes are favorable when \eqn{N_R = 1} due to the limited signaling between the coordinating \acp{BS}, involving the scalar interference values.
+However, when \eqn{N_R > 1}, the \ac{KKT} based distributed approach is much more efficient, since it has less signaling overhead for a given throughput.
+The choice of the \eqn{\ell_q} norm is as discussed in Section II-B.
+These lines are included in the paragraph before the Conclusions section.
+If the reviewer is interested on the practical usage of the algorithms, please refer to the response for the reviewer 2's question 2 in this response document for more details involving the performance of the KKT based distributed algorithm.
 
-	\cmnts{b} - {The last discussion in section IV-C could benefit from restructuring.
+	\cmnts{b} - \review{The last discussion in section IV-C could benefit from restructuring.
 The information on how to obtain a practical distributed precoder design and to avoid backhaul exchange is too condensed and difficult to understand.}
 
-	\resp \review{}
+	\resp It is rewritten to provide additional clarity as suggested by the reviewer. We have included the reference [28] for more illustrative discussions on the backhaul signaling.
 
-	\cmnts{c} - {For the simulation results, why not to unify configurations when possible?
+	\cmnts{c} - \review{For the simulation results, why not to unify configurations when possible?
 Having to read a different configuration for each graph is cumbersome and no additional comparisons are possible between figures.
@@
 
-	\resp \review{}
+	\resp We understand the reviewer concern.
+We used different path loss models for improved clarity and to show that the proposed algorithms works reasonably well on all scenarios.
+To provide a fair comparison, we have also included the centralized algorithm to draw the difference between the other schemes.
+We will consider the reviewer comment in our future work.
+However, if the reviewer insists on the unanimous configuration across the figures, we will revise the manuscript accordingly.
 
-	\cmnts{d} - {In Fig. 1, the description of the system model does not agree with the statement of N = 3 subchannels.}
+	\cmnts{d} - \review{In Fig. 1, the description of the system model does not agree with the statement of N = 3 subchannels.}
 
-	\resp \review{}
+	\resp We apologize for the error. We have modified the text to agree with the simulation Fig. 1.
 
-	\cmnts{e} - {In Fig.
+	\cmnts{e} - \review{In Fig.
 4(b), the performance of Q-WSRME seems to be (in average) worse than Q-WSRM.
@@
 
-	\resp \review{}
+	\resp The performance of the Q-WSRME is better than Q-WSRM in Fig.
+4(b).
+Since we have plotted the instantaneous arrival rates also in the same figure, it is difficult to discriminate between the colors.
+We have updated the manuscript to provide better clarity in the figure.
 
-	\cmnts{f} - {p 6, col 2, row 49: it should be \eqn{t_{l,k,n}} instead of \eqn{t_{l,n,k}}}
+	\cmnts{f} - \review{p 6, col 2, row 49: it should be \eqn{t_{l,k,n}} instead of \eqn{t_{l,n,k}}}
 
-	\resp \review{}
+	\resp We have update the manuscript with the proper subscript.
 
-	\cmnts{g} - {p 10, col 1, row 28: is it \eqn{\lambda} a dual variable?}
+	\cmnts{g} - \review{p 10, col 1, row 28: is it \eqn{\lambda} a dual variable?}
 
-	\resp \review{}
+	\resp We thank the reviewer for pointing out the mistake. It is the dual variable \eqn{\sigma_{l,k,n}} and not \eqn{\lambda_{l,k,n}}. We have updated the manuscript accordingly.
 
-	\cmnts{h} - {p 10, col 2, row 59: typo wHith}
+	\cmnts{h} - \review{p 10, col 2, row 59: typo wHith}
 
-	\resp \review{}
+	\resp We have updated the manuscript with the proper word.
 
@@
 
-	\resp \review{}
+	\resp We have updated the manuscript with the singular tense and we have also verified the grammatical validity of the manuscript as per the reviewer suggestion.
 

### 2015-06-27 Report/convergence_centralized.tex
before sending to nam and antti

@@
 	\item[(b)] The feasible set should be a compact set
-	\item[(c)] The sequence of the objective values should be decreasing in each iteration
+	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
 	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
@@
 \review{Let \eqn{f} be a strongly convex function.
-Even though the objective function in \eqref{eqn-6.1} is not strongly convex, it can be regularized with an additional quadratic term as discussed in the next section to transform it to a strongly convex function.} The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
+Even though the objective function in \eqref{eqn-6.1} is not strongly convex, it can be regularized with an additional quadratic term, which will be discussed in the Appendix \ref{c-a} to transform it to a strongly convex function.} The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
 Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
@@
 \begin{equation}\label{con-sub-set}\allowdisplaybreaks
-h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) + h(\iter{\mz}{k+1}{i}) \leq h(\iter{\mz}{k}{i}) - \hat{g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0.
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 
 \end{equation}}{
@@
 Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{i-1}} \ac{AO} iteration.
-At each \ac{SCA} update, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,quoc2011sequential}
+In each \ac{SCA} step, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,amir}
 \iftoggle{single_column}{
@@
 \end{equation}}{
-\begin{multline} \label{con-convergence}
+\begin{multline} \label{con-convergence} \allowdisplaybreaks
 f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
@@
 
-\subsection{Uniqueness of the Iterates and Strong Convexity}
+\subsection{Uniqueness of the Iterates and the Strong Convexity} \label{c-a}
 The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
@@
 Now, the objective function for the iteration \me{\{k+1,i\}} is given as
-\begin{equation} \label{mod_obj}
-\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2
-\end{equation}
-where the vector \eqn{\mbf{z}} is either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the optimization variables and \me{c} is a positive constant to make the objective strongly convex.
-The uniqueness of the minimizer is guaranteed by the strongly convex objective function \cite{scutari_1}.
-The vector \me{\mbf{z}^{(i)}_{k}} is the value of \me{\mbf{z}} obtained from the earlier iteration \me{\{k,i\}}.
-\review{Note that the modified objective in \eqref{mod_obj} is strongly convex, and therefore has an unique minimizer, which is obtained by the \ac{SCA} algorithm.}
+\begin{IEEEeqnarray}{rCl} \label{mod_obj} \neqsub
+\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \\ 
+f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub
+\end{IEEEeqnarray}
+where \eqn{\mbf{z}} is the stacked vector of optimization variables, which can either be \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c} is a small positive constant to transform the original convex function \eqn{\hat{f}(\mbf{z})} into a strongly convex \eqn{f(\mbf{z})} without affecting the solution.
+\review{The uniqueness of the minimizer in \ac{SCA} steps are ensured by the strong convexity of \eqn{f(\mbf{z})} \cite{scutari_1}, where \me{\mbf{z}^{(i)}_{k}} is the solution from previous iteration.}
 
@@
 \subsection{Strict Monotonicity of the Objective Sequence} \label{c-e}
-\review{So far we have discussed the uniqueness of the iterates at each \ac{SCA} update points and the monotonicity requirement for the \ac{SCA} convergence.
-In this, we discuss the strict monotonicity requirement of the objective function, which is required for the global convergence proof as in \cite{zangwill1969nonlinear,meyer1976sufficient}.
-In order to prove that, let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point in the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be the point-to-set mapping algorithm defined as
+In Section, we ensure the strict monotonicity in the objective until convergence, \textit{i.e}, \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k} and equal only when \eqn{\mbf{z}^{(i)}_k = \mbf{z}^{(i)}_{k+1}}, which is a limit point.
+Since \eqn{\hat{f}(\mbf{z})} is convex, it can have multiple limit points, therefore, it is monotonic.
+However, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point of the \ac{SCA} updates is also unique, and therefore has strict monotonicity in \eqn{f(\mbf{z}^{(i)}_k)} in each update.
+It can be justified, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even by including other limit points in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}} with the same original objective value as \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
+
+Let \eqn{\mbf{z}^{i}_{k}} be an unique minimizer and also a limit point of the \eqn{\ith{k}} \ac{SCA} step.
+Let \eqn{\mbf{z}^{i}_{k+1}} be another limit point with the same objective \eqn{\hat{f}(\mbf{z}^{i}_{k}) = \hat{f}(\mbf{z}^{i}_{k+1})} in the \eqn{\ith{k+1}} feasible set \eqn{\iter{\mc{X}}{k+1}{i}}.
+Due to the convexity of \eqn{\hat{f}(\mbf{z})}, strict monotonicity is not ensured since the selection of \eqn{\mbf{z}^{i}_{k}} and \eqn{\mbf{z}^{i}_{k+1}} are equally likely.
+However, due to the additional quadratic term \eqn{c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} in \eqn{f(\mbf{z})} for the \eqn{\ith{k+1}} iteration, the update cannot choose \eqn{\mbf{z}^{i}_{k+1}} due to the positive quadratic residual, therefore, it selects \eqn{\mbf{z}^{i}_{k}} in the \eqn{\ith{k+1}} iteration.
+In spite of choosing \eqn{\mbf{z}_{k}^{(i)}} in both \eqn{k} and \eqn{k+1} iteration, \eqn{f(\mbf{z})} decreases strictly due to the vanishing quadratic term in the \eqn{\ith{k+1}} step, therefore, it is a fixed point.
+%In spite of the additional quadratic term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} to ensure unique minimizer, strict monotonicity of the objective in each \ac{SCA} update cannot be ensured.
+However, strict monotonicity can be guaranteed in each update \eqn{i} of the algorithm \me{\mc{A}} in \eqref{g-algo} for the objective.
+Using (a),(b),(c) along with the above discussion, we can ensure strict monotonicity and the convergence of the objective.}
+%Due to the additional quadratic term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} from the earlier iteration and the unique minimizer from the previous step is also included, the objective decreases strictly in each \ac{SCA} update for an arbitrary value of \eqn{c} in \eqref{mod_obj}.
+Therefore, in each update \eqn{i} of the algorithm \me{\mc{A}} in \ref{g-algo}, the objective decreases monotonically in strict sense.
+Using (a),(b),(c) along with the above discussion, we can ensure strict monotonicity and the convergence of the objective.}
+
+\subsection{Convergence of the Beamformer Iterates} \label{c-b}
+Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
 \begin{equation} \label{g-algo}
-\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) =
+\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) \triangleq
 \begin{cases}
@@
 \end{equation}
-Note that each iteration \me{i} of the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e}, one for the variable \me{\mx} by keeping \me{\my} fixed and another for \me{\my} by fixing \me{\mx} as constant.
-At each \ac{SCA} convergence points, the objective holds with equality, and therefore it is not strictly monotonic.
-However, since the algorithm is defined to include two \ac{SCA} updates until convergence, the objective decreases monotonically at every update points \me{i}.
-Using the strong convexity of the objective function, it can be ensured that the decrement is strictly monotonic and it also has a unique minimizer.
-Using (a),(b) and (c), we can guarantee the convergence of the objective value sequence generated by the iterative algorithm.}
-
-\subsection{Convergence of the Beamformer Iterates} \label{c-b}
-Since the algorithm \eqn{\mc{A}} finds an unique minimizer after two inner \ac{SCA} convergence, the algorithm mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
+Note that each iteration \me{i} of the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant.
+Since the minimizer is unique, the mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
 In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\ast \subset \mc{F}} as the set of fixed points, \textit{i.e}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.
 
-Now by using \cite[Th. 3.1]{meyer1976sufficient}, convergence of the iterates to a fixed point can be shown, if the following conditions are satisfied.
+Using \cite[Th. 3.1]{meyer1976sufficient}, convergence of the iterates to a fixed point can be shown, if the following conditions are satisfied.
 \begin{itemize}
 \item Objective function \me{f} should be bounded and continuous.
-\item The feasible set \me{\iter{\mc{Y}}{\ast}{i}} in each iteration should be compact.
-\item The sequence \me{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} should be strictly monotonic with respect to the objective function \me{f}, \textit{i.e}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
+\item Feasible set \me{\iter{\mc{X}}{\ast}{i},\iter{\mc{Y}}{\ast}{i}} in each step should be compact.
+\item The sequence \me{\{\iterate{\ma}{i}\}} generated by \me{\mc{A}} should be strictly monotonic with respect to the objective \me{f}, \textit{i.e}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
 \end{itemize}
@@
 \subsection{Stationary Points of the Nonconvex Problem}
+Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by iterative algorithm \eqn{\mc{A}}.
+We need to show that the limit point \eqn{\ma^{\ast}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem \eqref{con}.
+In order for \eqn{\ma^{\ast}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}.
+In each iteration, the algorithm \eqn{\mc{A}} in \eqref{g-algo} finds a point \eqn{\iterate{\ma}{i} \in \mc{F}} with \eqn{f(\iterate{\ma}{i}) < f(\iterate{\ma}{i-1})}, therefore, it satisfies all the constraints of \eqref{con}.
+Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \rightarrow \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\ast}) = \ma^{\ast}} finds a unique \eqn{\ma^{\ast} \in \mc{F}^{\ast}} due to the strong convexity of \eqn{f}.
+
+To show the equivalence in the gradients of \eqref{con} and \eqref{con-m} at \eqn{\ma^{\ast}}, let us consider the limit point of the \ac{SCA} update in \eqn{\mc{A}} as it converges to a fixed point \eqn{\ma^{\ast} \in \mc{F}^{\ast}}.
+The \ac{KKT} expression for the convex subproblem \eqref{con-cvx} is given by
+\begin{equation} \label{kkt_expr}
+\nabla f(\ma^{\ast}) + \mu_1 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0
+\end{equation}
+for some Lagrange multipliers \eqn{\mu_i \geq 0}.
+Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}.
+Moreover, \eqn{\ma^{\ast}} is a regular point \textit{i.e} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}.
+Now, with the above conditions and by using \cite[Th.
+2 and 11]{scutari_1} and \cite[Prop.
+3.2]{amir}, we can show that the fixed points obtained by \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
+
+\begin{comment}
 To show the limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}.
@@
 \end{multline}}
-where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is the limit point of \me{\mc{A}} for a given initial point.
+where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a limit point of \me{\mc{A}} for a given initial point.
+Since the function \eqn{f} is strongly convex, the limit point is unique.
 As discussed in Appendix \ref{c-b}, the unique limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a fixed point of \me{\mc{A}}.
+
 Using \cite[Th.
@@
 2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
-It can be verified by writing the \ac{KKT} expressions for the original problem in \eqref{con} and the relaxed one in \eqref{con-m} at the limit point \eqref{con-opt}, using the relation in \eqref{con-relax} between the nonconvex constraint and the corresponding convex approximation \cite{marks1978technical}.
+\end{comment}

### 2015-06-27 Report/convergence_distributed.tex
before sending to nam and antti

@@
 The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
-Note that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and the set is compact, which is required for the distributed approach to converge.
+Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence.
 Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem can be guaranteed as the iteration index \me{i \rightarrow \infty} for a diminishing step size \cite{bertsekas1999nonlinear}.
 
-To prove the convergence of the \ac{ADMM} approach, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
+\review{To show the convergence of \ac{ADMM} approach, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
 \begin{IEEEeqnarray}{rCl} \neqsub
-	\underset{\mbf{x},\mbf{z}}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
-	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm} \\
-	&\quad&	\mbf{x} \in \mc{C}_1, \mbf{z} \in \mc{C}_2 \eqsub
+	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
+	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
 \end{IEEEeqnarray}
@@
 It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible.
-The objective function \me{G,H} are \me{\ell_q} norm in \eqref{eqn-decent-1} are convex and the set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has a nonempty interior.
-The feasibility of the interior point is verified by having a non-zero precoder for only one user.
+The objective function \me{G,H} includes \me{\ell_q} norm with an additional quadratic term as in \eqref{mod_obj}, and therefore exhibits strong convexity.
+The set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has a nonempty interior.
+The feasibility of the interior point can be verified by having a non-zero precoder for only one user.
 Therefore, by following \cite[Prop.
 4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.
-The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if it is iterated until convergence.
+The distributed algorithms also converges to a stationary point of the original nonconvex problem by following Appendix \ref{sec-3.5}, if the \ac{ADMM} is iterated until convergence in each \ac{SCA} step.}
 
-However, if the distributed algorithm is terminated well before the convergence or performed for limited iterations, convergence of the algorithm is not guaranteed.
-Since at each update of \eqn{\mbf{x}^{(i)}}, which involves two \ac{SCA} updates until convergence with limited distributed iterations at each \ac{SCA} step, the monotonicity of the objective is not guaranteed, and therefore the convergence, unless the number of iterations is large enough to have strictly decreasing objective.
-In this case, the limit point is a stationary point of the original nonconvex problem following \cite{zangwill1969nonlinear,meyer1976sufficient}.
+\review{However, if the distributed algorithms are terminated well before the convergence or performed for limited number of iterations, convergence of the algorithm is not guaranteed.
+Since each update of \eqn{\mbf{x}^{(i)}} involves two \ac{SCA} updates until convergence with limited distributed iterations, the monotonicity and the convergence of the objective is not guaranteed unless the number of iterations is large enough to have strictly decreasing objective.
+Moreover, monotonicity of the overall objective in each primal or \ac{ADMM} update is not ensured, despite reaching the centralized solution upon convergence.}
 

### 2015-06-27 Report/dual_approach.tex
before sending to nam and antti

@@
 \end{algorithm}
-
 \begin{comment}

### 2015-06-27 Report/kkt_mse_approach.tex
updated revision 2 with ADMM proof and strict monotonicity
before sending to nam and antti

@@
 In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
-The proposed methods in this section provide algorithms that can be of practical importance owing to the limited signaling requirements.
-We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter.
+\review{Note that the distributed approaches discussed so far may not be viable for multi antenna receivers in practice due to the signaling overhead involved in exchanging the coupling variables if the number iterations required to converge is large, which depends on the system size.
+In this section, we provide an algorithm that can be of practical importance owing to the limited signaling requirements.} We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
@@
 \allowdisplaybreaks\iftoggle{single_column}{
-\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
+\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1} \neqsub
 \underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
@@
 \end{IEEEeqnarray}
-}{\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1}
+}{\begin{IEEEeqnarray}{Rl}\label{kkt-mse-1} \neqsub
 	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n}, \\ \epsilon_{l,k,n}, \mvec{w}{l,k,n}}}{\text{minimize}} & \quad \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \Big ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \Big )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
@@
 \iftoggle{single_column}{
-\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
+\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4} \neqsub
 \mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
@@
 }{\allowdisplaybreaks
-\begin{IEEEeqnarray}{ll} \label{kkt-mse-4}
+\begin{IEEEeqnarray}{ll} \label{kkt-mse-4} \neqsub
 	\mvec{m}{l,k,n}^{(i)} =& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} \nonumber \\
@@
 	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
-		initialize \me{i = 0} \;
 		\Repeat{until convergence or \me{i \geq I_{\max}}}{

### 2015-06-27 Report/mse_formulation.tex
updated revision 2 with ADMM proof and strict monotonicity
before sending to nam and antti

@@
 \iftoggle{single_column}{
-\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
+\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1} \neqsub \allowdisplaybreaks
 \underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
@@
 }{\allowdisplaybreaks
-\begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
+\begin{IEEEeqnarray}{CL}\label{eqn-mse-1} \neqsub \allowdisplaybreaks
 	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
@@
 \end{IEEEeqnarray}}
+\begin{algorithm}
+	\SetAlgoLined
+	\DontPrintSemicolon
+	\BlankLine
+	\SetKwInput{KwInit}{Initialize}
+	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
+	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
+	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
+	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
+		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
+			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
+			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
+			$j = j + 1$\;
+		}
+		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
+		$i = i + 1$, \me{j = 0}\;
+	}
+	\caption{Algorithm of \acs{JSFRA} scheme}
+	\label{algo-1} 
+\end{algorithm}
 
@@
 The optimization subproblem to find the transmit precoders for a fixed receive beamformer \me{\mvec{w}{l,k,n}} is given by
-\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2}
+\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
 \underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\

### 2015-06-27 Report/sub_channel_wsrm.tex
before sending to nam and antti

@@
 where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream.
-\review{Inspite of the improved covergence speed over the \ac{JSFRA} approach, the \ac{SRA} scheme is sensitive to the order in which the sub-channels are selected.
-Heuristically, we can adopt \ac{MU}-\ac{MIMO} scheduling scheme in \cite{sus2006zfbf} to find an efficient subset of users and the corresponding sum rate using zero-forcing precoders in each sub-channel, which can be used to determine the selection order.
-Since the scheduling is based on the infinite buffer model, it is used only in the sub-channel ordering.
+\review{In spite of the improved covergence speed over the \ac{JSFRA} approach, the \ac{SRA} scheme is sensitive to the order in which the sub-channels are selected.
+Heuristically, we can choose the order by sorting the available best channel norm from each sub-channel, obtained by sorting the norm of the channel between the users and the corresponding serving \ac{BS} for each sub-channel.
+In spite of not considering the number of backlogged packets in the sub-channel ordering, it can be preferred over random ordering.
 However, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the multi-user diversity.}

### 2015-06-27 Report/time_correlated.tex
before sending to nam and antti

@@
 \subref*{fig-review}, the \me{\ell_\infty} \ac{JSFRA} performs inferior to the \ac{Q-WSRM} scheme, since the fairness is not effective when the system is unstable, \textit{i.e}, when \me{A_k \geq 7} in the current model.
+
+\review{Since we have presented different formulations for the \ac{JSFRA} problem, the choice of selecting a centralized algorithm is equal fair for \eqn{N_R > 1}.
+However, for \eqn{N_R = 1} scenario, the \ac{JSFRA} formulation in Section \ref{sec-3.2.1} is efficient, as there is no receiver update, and therefore has less complexity.
+Similarly, when \eqn{N_R = 1}, the distributed approaches based on primal and \ac{ADMM} are efficient due to the limited signaling between the coordinating \acp{BS}, involving the scalar interference values.
+However, when \eqn{N_R > 1}, the \ac{KKT} approach in Section \ref{sec-4.3} has less signaling overhead for a given throughput.
+The selection of \eqn{\ell_q} norm is presented in Section \ref{sec-3.2}.}

### 2015-06-27 Report/wsrm_formulation.tex
before sending to nam and antti

@@
 The convergence analysis is given in Appendix \ref{sec-3.5}.
-\begin{algorithm}
-	\SetAlgoLined
-	\DontPrintSemicolon
-	\BlankLine
-	\SetKwInput{KwInit}{Initialize}
-	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
-	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
-	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
-	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
-	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
-		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
-			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
-			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
-			$j = j + 1$\;
-		}
-		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
-		$i = i + 1$, \me{j = 0}\;
-	}
-	\caption{Algorithm of \acs{JSFRA} scheme}
-	\label{algo-1}
-\end{algorithm}
-
 \begin{comment}

### 2015-06-27 Response/Response 2/additions.tex
before sending to nam and antti

\begin{enumerate}
\item We have shortened the discussions on the existing \textit{backpressure algorithm} in Section III-A.
\item Strong convexity of the objective function is emphasized in Appendix A-C.
\item Strict Monotonicity of the algorithm is discussed separately in Appendix A-D with more clarity.
\item We have provided additional details on the distributed algorithm convergence as suggested by the reviewers
\item Section III-D is updated to include the guidelines involved in selecting the sub-channel order.
\item Short discussion on the choice of algorithm selection is provided 
\item Initialization of the \ac{SCA} operating point is also included in the revised manuscript
\end{enumerate}

In what follows, the comments are listed, each followed by the corresponding reply from the authors. Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript.

### 2015-06-27 Response/Response 2/document.tex
before sending to nam and antti

\documentclass[10pt,letterpaper,onecolumn]{article}

\usepackage[left=1.0in,right=1.0in,top=1in,bottom=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[dvipdfmx]{graphicx}
\usepackage{acronym,etoolbox,color,multicol,xcolor}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}

\newcommand{\cmnt}[1]{\item}
\newcommand{\cmnts}[1]{\item[(#1)]}
\newcommand{\resp}{\item[\textit{\underline{Reply}}:]}

\input{./../../Report/shortcuts}
\input{./../../Report/acronyms}

\DeclareGraphicsExtensions{{eps}}
\graphicspath{{Figures/}}
\renewcommand \thesection{\Roman{section}}
\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}

\begin{document}

\title{Reviewers Comments \& Authors Replies}

\date{}
\maketitle

\begin{tabular}{p{1.25in}p{4.25in}}
\textbf{Manuscript No.} & Paper T-SP-18051-2014, submitted to \emph{``IEEE Transactions on Signal Processing"} \\ \\
\textbf{Title} & ``Traffic Aware Resource Allocation Schemes for Multi-Cell MIMO-OFDM Systems" \\ \\
\textbf{Authors} & Ganesh Venkatraman, Antti T\"{o}lli, Markku Juntti, and Le-Nam Tran
\end{tabular}

\vspace{0.5in}
The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality. Based on the comments, we have made several major revisions to the paper, following the suggestions of the reviewers. In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors. The revisions in the revised manuscript are highlighted using blue color and the authors responses are also presented in blue color text. Following is the summary of the revision made on the manuscript in accordance with the reviewers comments.
\input{additions}

\newpage
\section*{Response to Reviewer - \me{1}'s Comments}
\input{response-1}

\newpage
\section*{Response to Reviewer - \me{2}'s Comments}
\input{response-2}

\newpage
\section*{Response to Reviewer - \me{3}'s Comments}
\input{response-3}

\newpage
\section*{Response to Reviewer - \me{4}'s Comments}
\input{response-4}

\end{document}

### 2015-06-27 Report/convergence_centralized.tex
updated

@@
 However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there are many solutions satisfying the constraints without affecting the objective value.
-Similarly, when the objective is non-zero, problem defined in \eqref{eqn-9} has a unique minimizer if the receivers are matched to the corresponding transmit beamformers, \textit{i.e}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while choosing a feasible operating point \me{\iter{\mx}{0}{0}} and \me{\iter{\my}{0}{0}} to initialize the iterative procedure.
+Similarly, when the objective is non-zero for  \eqref{eqn-9}, the minimizer is unique, if the receivers are matched to the corresponding transmit beamformers, \textit{i.e}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.
 
-To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, \textit{i.e}, even when the objective value is zero, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized with a strongly convex function.
-Now, the objective function for the iteration \me{\{k+1,i\}} is given as
+To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations under all conditions, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized with a strongly convex function in each iteration \me{\{k+1,i\}} as
 \begin{IEEEeqnarray}{rCl} \label{mod_obj} \neqsub
@@
 where \eqn{\mbf{z}} is the stacked vector of optimization variables, which can either be \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c} is a small positive constant to transform the original convex function \eqn{\hat{f}(\mbf{z})} into a strongly convex \eqn{f(\mbf{z})} without affecting the solution.
-\review{The uniqueness of the minimizer in \ac{SCA} steps are ensured by the strong convexity of \eqn{f(\mbf{z})} \cite{scutari_1}, where \me{\mbf{z}^{(i)}_{k}} is the solution from previous iteration.}
+\review{Therefore, the uniqueness of the minimizer in each \ac{SCA} step is ensured by the strong convexity in \eqn{f(\mbf{z})} by including the quadratic penalty term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2}, where \me{\mbf{z}^{(i)}_{k}} is the solution from the previous iteration.}
 
@@
 \subsection{Strict Monotonicity of the Objective Sequence} \label{c-e}
-In Section, we ensure the strict monotonicity in the objective until convergence, \textit{i.e}, \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k} and equal only when \eqn{\mbf{z}^{(i)}_k = \mbf{z}^{(i)}_{k+1}}, which is a limit point.
+In this section, we ensure strict monotonicity in the objective until convergence, \textit{i.e}, \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k} and equal only if \eqn{\mbf{z}^{(i)}_k = \mbf{z}^{(i)}_{k+1}}, which is a limit point.
 Since \eqn{\hat{f}(\mbf{z})} is convex, it can have multiple limit points, therefore, it is monotonic.
-However, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point of the \ac{SCA} updates is also unique, and therefore has strict monotonicity in \eqn{f(\mbf{z}^{(i)}_k)} in each update.
+However, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point of the \ac{SCA} updates is also unique, and therefore has strict monotonicity in \eqn{f(\mbf{z}^{(i)}_k)} after each update.
 It can be justified, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even by including other limit points in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}} with the same original objective value as \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
@@
 Let \eqn{\mbf{z}^{i}_{k+1}} be another limit point with the same objective \eqn{\hat{f}(\mbf{z}^{i}_{k}) = \hat{f}(\mbf{z}^{i}_{k+1})} in the \eqn{\ith{k+1}} feasible set \eqn{\iter{\mc{X}}{k+1}{i}}.
-Due to the convexity of \eqn{\hat{f}(\mbf{z})}, strict monotonicity is not ensured since the selection of \eqn{\mbf{z}^{i}_{k}} and \eqn{\mbf{z}^{i}_{k+1}} are equally likely.
+Due to the convexity of \eqn{\hat{f}(\mbf{z})}, strict monotonicity cannot be ensured since the selection of \eqn{\mbf{z}^{i}_{k}} and \eqn{\mbf{z}^{i}_{k+1}} are equally likely.
 However, due to the additional quadratic term \eqn{c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} in \eqn{f(\mbf{z})} for the \eqn{\ith{k+1}} iteration, the update cannot choose \eqn{\mbf{z}^{i}_{k+1}} due to the positive quadratic residual, therefore, it selects \eqn{\mbf{z}^{i}_{k}} in the \eqn{\ith{k+1}} iteration.
@@
 \end{equation}
-Note that each iteration \me{i} of the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant.
+Note that in each iteration \me{i}, the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant.
 Since the minimizer is unique, the mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.

### 2015-06-27 Report/kkt_mse_approach.tex
updated

@@
 In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
-\review{Note that the distributed approaches discussed so far may not be viable for multi antenna receivers in practice due to the signaling overhead involved in exchanging the coupling variables if the number iterations required to converge is large, which depends on the system size.
-In this section, we provide an algorithm that can be of practical importance owing to the limited signaling requirements.} We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter.
+\review{Note that the distributed approaches discussed so far may not be viable for multi-antenna receivers due to the signaling overhead involved in exchanging the coupling variables if the number iterations required to converge is large, which depends on the system size.}
+
+In this section, we provide an algorithm that can be of practical importance owing to the limited signaling requirements.
+We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.

### 2015-06-29 Response/Response 2/response-1.tex
updated with ADMM convergence

@@
 As suggested by the reviewer, we have included Appendix A-D to discuss the strict monotonicity of the objective function in each update point of the algorithm.
+
+Let \eqn{\mbf{z}} be the stacked vector of optimization variables that can either be \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the optimization problem that we are trying to solve, \textit{i.e}, either solving for \eqn{\mx} and \eqn{\mz} by fixing \eqn{\iter{\my}{\ast}{i-1}} or solving for \eqn{\my} and \eqn{\mz} by keeping \eqn{\iter{\mx}{\ast}{i}} fixed.
 Due to the strong convexity of the objective function, strict monotonicity is ensured after each update and also upon convergence.

### 2015-06-29 Response/Response 2/response-2.tex
updated with ADMM convergence

@@
 However, by knowing the complete channel of the users in the system, the centralized controller can perform the precoder design until convergence.
-However, as the number of sub-channels, users or the antenna element increases, it may not be a viable option to feedback the user channels across the coordinating \acp{BS} to the centralized controller.
+However, as the number of sub-channels, users or the antenna element increases, it may not be a feasible option to feedback the user channels across the coordinating \acp{BS} to the centralized controller.
 The quantizing the channel information degrades the achievable performance of the centralized solution that also needs to be considered while comparing the signaling overhead.
+Moreover, in the centralized algorithm, resulting transmit precoders need to be exchanged with the corresponding \acp{BS} before the actual transmission, involving huge overhead in the backhaul.
 		\item Using the above discussion, we can say that when the system size is huge, it would be favorable to consider the distributed algorithm over the centralized approach due to the huge signaling overhead involved in exchanging the channels.

### 2015-06-29 Report/convergence_distributed.tex
updated with ADMM convergence

@@
 \review{However, if the distributed algorithms are terminated well before the convergence or performed for limited number of iterations, convergence of the algorithm is not guaranteed.
-Since each update of \eqn{\mbf{x}^{(i)}} involves two \ac{SCA} updates until convergence with limited distributed iterations, the monotonicity and the convergence of the objective is not guaranteed unless the number of iterations is large enough to have strictly decreasing objective.
-Moreover, monotonicity of the overall objective in each primal or \ac{ADMM} update is not ensured, despite reaching the centralized solution upon convergence.}
+Since each update of \eqn{\mbf{x}^{(i)}} involves two \ac{SCA} updates until convergence with limited distributed iterations, the monotonicity of the objective and hence the convergence of the iterates is not guaranteed, unless the number of iterations is large enough to ensure strictly decreasing objective.
+It follows from the fact that in each primal or \ac{ADMM} update, the global objective is not guaranteed to be monotonically decreasing, despite reaching the centralized solution upon convergence.}
+
+	%Since each update of \eqn{\mbf{x}^{(i)}} involves two \ac{SCA} updates until convergence with limited distributed iterations, the monotonicity and the convergence of the objective is not guaranteed unless the number of iterations is large enough to have strictly decreasing objective.
+Moreover, monotonicity of the global objective in each primal or \ac{ADMM} update is not ensured, despite reaching the centralized solution upon convergence.}
 

### 2015-06-29 Report/decomposition_solutions.tex
updated with ADMM convergence

@@
 To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-Following an approach similar to the one presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference from each \ac{BS} in \me{\bar{\mc{B}}_{b_k}} as
+Following an approach similar to the one presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference from all \acp{BS} in \me{\bar{\mc{B}}_{b_k}} as
 \iftoggle{single_column}{

### 2015-06-29 Report/kkt_mse_approach.tex
updated with ADMM convergence

@@
 In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
-\review{Note that the distributed approaches discussed so far may not be viable for multi-antenna receivers due to the signaling overhead involved in exchanging the coupling variables if the number iterations required to converge is large, which depends on the system size.}
+\review{Note that the distributed approaches discussed so far may not be efficient for multi-antenna receivers due to the signaling involved in exchanging the coupling variables and the receive beamformers if the number iterations required to converge is large.
+It also depends on system size under consideration, which governs the number of the coupling interference variables to be exchanged.}
 

### 2015-06-29 Report/primal_approach.tex
updated with ADMM convergence

@@
-In the \acl{PD}, the convex problem in \eqref{eqn-decent-1} is solved for the optimal transmit precoders in an iterative manner for a fixed \ac{BS} specific interference term \me{\mbfa{\zeta}_{b_k}} using the master-slave model \cite{pennanen2011decentralized}.
+In the \acl{PD}, the convex problem in \eqref{eqn-decent-1} is solved for the transmit precoders in an iterative manner by fixing the \ac{BS} specific interference terms \me{\mbfa{\zeta}_{b_k}} using master-slave model \cite{pennanen2011decentralized}.
 The slave subproblem is solved in each \ac{BS} for the optimal transmit precoders only for the associated users by assuming fixed interference terms \me{\mbfa{\zeta}_{b_k}^{(i)}} in each \me{\ith{i}} iteration.
@@
 In this manner, the interference variables are updated until the global consensus is obtained.
-The primal approach is similar to the minimum power precoder design presented in \cite{pennanen2011decentralized}.
-Note that the master problem treats \me{\mbfa{\zeta}_{b}} as a variable and the slave subproblems assumes it to be a constant in each iteration.
+It is similar to the minimum power design presented in \cite{pennanen2011decentralized}.
+The master problem treats \me{\mbfa{\zeta}_{b}} as a variable and the slave subproblems assumes it to be a constant in each iteration.
+\review{Since the interference levels are fixed in each subproblem, the feasibility of the subproblems depend on the step size used to update the interference variables by the master problem.}
+
 \begin{comment}

### 2015-06-29 Report/wsrm_formulation.tex
updated with ADMM convergence

@@
 The iterative algorithm is referred as \acl{QM} \ac{JSFRA} scheme, and it is outlined in Algorithm \ref{algo-1}.
-\review{The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is updated using \eqref{eqn-9.1c} with the chosen transmit precoders and the receivers.} For a fixed receiver \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} to find an optimal transmit precoders \me{\mvec{m}{l,k,n}}.
+\review{To begin the iterative procedure, the initial feasible points \me{\tilde{\mbf{u}}_{l,k,n}} are obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is obtained by evaluating \eqref{eqn-9.1c} with the initialized transmit precoders and the receive beamformers of all the users in the system.} For a fixed receiver \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} to find an optimal transmit precoders \me{\mvec{m}{l,k,n}}.
 Next, the receivers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.

### 2015-07-04 Response/Response 2/response-1.tex
given to nam and antti

@@
 Let \eqn{\mbf{z}} be the stacked vector of optimization variables that can either be \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the optimization problem that we are trying to solve, \textit{i.e}, either solving for \eqn{\mx} and \eqn{\mz} by fixing \eqn{\iter{\my}{\ast}{i-1}} or solving for \eqn{\my} and \eqn{\mz} by keeping \eqn{\iter{\mx}{\ast}{i}} fixed.
-Due to the strong convexity of the objective function, strict monotonicity is ensured after each update and also upon convergence.
-In order to ensure the strict monotonicity in the objective until convergence, \textit{i.e}, \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k} and equal only when \eqn{\mbf{z}^{(i)}_k = \mbf{z}^{(i)}_{k+1}}, which is a limit point.
-Since each of the earlier update in the \ac{SCA} are strictly monotonic, we consider the point where the original convex function, say, \eqn{\hat{f}} has multiple limit points with the same objective value \eqn{\hat{f}(\mbf{z})}, where \eqn{f(\mbf{z}) = \hat{f}(z) + \|\mbf{z} - \mbf{z}_k^{(i)}\|^2} is the modified objective function from the \eqn{\ith{k+1}} iteration.
-Since \eqn{\hat{f}(\mbf{z})} is convex, it can have multiple limit points, therefore, it is monotonic.
-However, due to the strong convexity of \eqn{f(\mbf{z})} in (52), the limit point of the \ac{SCA} updates is also unique, and therefore has strict monotonicity in \eqn{f(\mbf{z}^{(i)}_k)} in each update.
-It can be justified, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even by including other limit points in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}} with the same original objective value as \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
-This information and the proof is also included in the revised manuscript in Appendix A-D.
+
+Due to the strong convexity of the modified objective \eqn{f(\mbf{z})}, there exist an unique minimizer in each \ac{SCA} step \eqn{k}.
+Moreover, in each \ac{SCA} step \eqn{k}, the feasible set \eqn{\mc{X}_{k}^{(i)}} includes the earlier optimal point \eqn{\mbf{z}^{(i)}_k}, therefore, the objective decreases strictly unless \eqn{\mbf{z}^{(i)}_k} is a fixed point or a limit point of the \ac{SCA} iterations [22].
+Following the strong convexity of \eqn{f(\mbf{z})}, we have
+\begin{equation} \label{strict_monotonicity}
+f(\mbf{z}) \geq f(\mbf{z}_{\ast}^{(i)}) + \nabla f(\mbf{z}_{\ast}^{(i)}) (\mbf{z} - \mbf{z}_{\ast}^{(i)}) + c \|\mbf{z} - \mbf{z}_{\ast}^{(i)}\|^2, \forall \mbf{z}\in \mc{X}^{(i)}_\ast
+\end{equation}
+where \eqn{\mbf{z}_{\ast}^{(i)}} is a limit point as \eqn{k \rightarrow \infty} for the \eqn{\ith{i}} \ac{AO} iteration.
+The equality in \eqref{strict_monotonicity} is valid iff \eqn{\mbf{z} = \mbf{z}_{\ast}^{(i)}}.
+Strict monotonicity of \eqn{f(\mbf{z}_k^{(i)})} is ensured in the \ac{SCA} steps by the additional quadratic term, which holds with equality at the limit point \eqn{\mbf{z}_{\ast}^{(i)} \in \mc{X}_{\ast}^{(i)}}.
+
+To ensure strict monotonicity of the objective while swapping the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration, we rely on the discussions to show the inequality (51).
+Note that the modified objective \eqn{f} is strongly convex, and therefore has a unique minimizer in each \ac{SCA} step.
+Additionally, the feasible set \eqn{\mc{Y}_0^{(i)}} for \eqn{k=0} \ac{SCA} step with the variables \eqn{\my,\mz} includes the previous minimizer \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}}, thereby having strictly decreasing objective in (51).
+The equality in (51) holds for the limit point \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}.
+Using the above arguments, we can ensure the strict monotonicity of the overall objective sequence.
 

### 2015-07-04 Response/Response 2/response-2.tex
given to nam and antti

@@
 \resp We thank the reviewer for raising the important concern regarding the convergence issue of the distributed algorithm with limited number of iterations.
-In view of this, we have updated the manuscript to include the discussion on the convergence of the distributed algorithms with limited number of iterations in Appendix B third paragraph after (55).
+In view of this, we have updated the manuscript to include the discussion on the convergence of the distributed algorithms with limited number of iterations in Appendix B third paragraph after (57).
 Since the distributed algorithm cannot be guaranteed to be monotonic in each iteration, it is not possible to prove the convergence of the algorithm.

### 2015-07-04 Report/convergence_centralized.tex
given to nam and antti

@@
 \iftoggle{single_column}{
-\begin{equation}\allowdisplaybreaks
-f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
+\begin{equation}
+f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
 \end{equation}}{
-\begin{multline}\allowdisplaybreaks
-f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \\
-\leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
-\end{multline}}
+\begin{equation}
+f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
+\end{equation}}
 Let \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
@@
 \subsection{Strict Monotonicity of the Objective Sequence} \label{c-e}
-In this section, we ensure strict monotonicity in the objective until convergence, \textit{i.e}, \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k} and equal only if \eqn{\mbf{z}^{(i)}_k = \mbf{z}^{(i)}_{k+1}}, which is a limit point.
-Since \eqn{\hat{f}(\mbf{z})} is convex, it can have multiple limit points, therefore, it is monotonic.
+Due to the strong convexity of the modified objective \eqn{f(\mbf{z})}, there exist an unique minimizer in each \ac{SCA} step \eqn{k}.
+Moreover, in each \ac{SCA} step \eqn{k}, the feasible set \eqn{\mc{X}_{k}^{(i)}} includes the earlier optimal point \eqn{\mbf{z}^{(i)}_k}, therefore, the objective decreases strictly unless \eqn{\mbf{z}^{(i)}_k} is a fixed point or a limit point of the \ac{SCA} iterations \cite{marks1978technical}.
+Following the strong convexity of \eqn{f(\mbf{z})}, we have
+\begin{equation} \label{strict_monotonicity}
+f(\mbf{z}) \geq f(\mbf{z}_{\ast}^{(i)}) + \nabla f(\mbf{z}_{\ast}^{(i)}) (\mbf{z} - \mbf{z}_{\ast}^{(i)}) + c \|\mbf{z} - \mbf{z}_{\ast}^{(i)}\|^2, \forall \mbf{z}\in \mc{X}^{(i)}_\ast
+\end{equation}
+where \eqn{\mbf{z}_{\ast}^{(i)}} is a limit point as \eqn{k \rightarrow \infty} for the \eqn{\ith{i}} \ac{AO} iteration.
+The equality in \eqref{strict_monotonicity} is valid iff \eqn{\mbf{z} = \mbf{z}_{\ast}^{(i)}}.
+Strict monotonicity of \eqn{f(\mbf{z}_k^{(i)})} is ensured in the \ac{SCA} steps by the additional quadratic term, which holds with equality at the limit point \eqn{\mbf{z}_{\ast}^{(i)} \in \mc{X}_{\ast}^{(i)}}.
+
+To ensure strict monotonicity of the objective while swapping the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration, we rely on the discussions to show the inequality \eqref{fixed_point}.
+Note that the modified objective \eqn{f} is strongly convex, and therefore has a unique minimizer in each \ac{SCA} step.
+Additionally, the feasible set \eqn{\mc{Y}_0^{(i)}} for \eqn{k=0} \ac{SCA} step with the variables \eqn{\my,\mz} includes the previous minimizer \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}}, thereby having strictly decreasing objective in \eqref{fixed_point}.
+The equality in \eqref{fixed_point} holds for the limit point \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}.
+Using the above arguments, we can ensure the strict monotonicity of the overall objective sequence.
+%Even though the original convex function \eqn{\hat{f}(\mbf{z})} can have multiple limit points upon the \ac{SCA} convergence, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point is unique, and therefore the objective decreases monotonically in a strict sense.
+It can be proved, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even if the other limit points are included in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}}, with the same \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
+%Let \eqn{\mbf{z}^{i}_{k}} be an unique minimizer and also a limit point of the \eqn{\ith{k}} \ac{SCA} step.
+Let \eqn{\mbf{z}^{i}_{k+1}} be another limit point with the same objective \eqn{\hat{f}(\mbf{z}^{i}_{k}) = \hat{f}(\mbf{z}^{i}_{k+1})} in the \eqn{\ith{k+1}} feasible set \eqn{\iter{\mc{X}}{k+1}{i}}.
+Due to the convexity of \eqn{\hat{f}(\mbf{z})}, strict monotonicity cannot be ensured since the selection of \eqn{\mbf{z}^{i}_{k}} and \eqn{\mbf{z}^{i}_{k+1}} are equally likely.
+However, due to the additional quadratic term \eqn{c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} in \eqn{f(\mbf{z})} for the \eqn{\ith{k+1}} iteration, the update cannot choose \eqn{\mbf{z}^{i}_{k+1}} due to the positive quadratic residual, therefore, it selects the fixed point \eqn{\mbf{z}^{i}_{k}} in the \eqn{\ith{k+1}} iteration.
+Similarly, using the above argument, we can also prove the strict monotonicity of the objective in each \ac{AO} update \eqn{i}, and thereby proving strict monotonicity of the overall objective sequence.
+
+%Due to the convexity in the original objective \eqn{\hat{f}(\mbf{z})}, it can have multiple limit points for the \ac{SCA} update, and therefore it follows \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k}.
 However, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point of the \ac{SCA} updates is also unique, and therefore has strict monotonicity in \eqn{f(\mbf{z}^{(i)}_k)} after each update.
 It can be justified, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even by including other limit points in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}} with the same original objective value as \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
-
-Let \eqn{\mbf{z}^{i}_{k}} be an unique minimizer and also a limit point of the \eqn{\ith{k}} \ac{SCA} step.
-Let \eqn{\mbf{z}^{i}_{k+1}} be another limit point with the same objective \eqn{\hat{f}(\mbf{z}^{i}_{k}) = \hat{f}(\mbf{z}^{i}_{k+1})} in the \eqn{\ith{k+1}} feasible set \eqn{\iter{\mc{X}}{k+1}{i}}.
-Due to the convexity of \eqn{\hat{f}(\mbf{z})}, strict monotonicity cannot be ensured since the selection of \eqn{\mbf{z}^{i}_{k}} and \eqn{\mbf{z}^{i}_{k+1}} are equally likely.
-However, due to the additional quadratic term \eqn{c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} in \eqn{f(\mbf{z})} for the \eqn{\ith{k+1}} iteration, the update cannot choose \eqn{\mbf{z}^{i}_{k+1}} due to the positive quadratic residual, therefore, it selects \eqn{\mbf{z}^{i}_{k}} in the \eqn{\ith{k+1}} iteration.
-In spite of choosing \eqn{\mbf{z}_{k}^{(i)}} in both \eqn{k} and \eqn{k+1} iteration, \eqn{f(\mbf{z})} decreases strictly due to the vanishing quadratic term in the \eqn{\ith{k+1}} step, therefore, it is a fixed point.
+%In spite of choosing \eqn{\mbf{z}_{k}^{(i)}} in both \eqn{k} and \eqn{k+1} iteration, \eqn{f(\mbf{z})} decreases strictly due to the vanishing quadratic term in the \eqn{\ith{k+1}} step, therefore, it is a fixed point.
+Similarly, by using the above argument, we can also prove the strict monotonicity of the objective in each \ac{AO} update, and thereby proving strict monotonicity of the overall sequence.
 %In spite of the additional quadratic term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} to ensure unique minimizer, strict monotonicity of the objective in each \ac{SCA} update cannot be ensured.
@@
 \subsection{Stationary Points of the Nonconvex Problem}
-Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by iterative algorithm \eqn{\mc{A}}.
-We need to show that the limit point \eqn{\ma^{\ast}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem \eqref{con}.
-In order for \eqn{\ma^{\ast}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}.
+Let \eqn{\ma^{\ast}} be the limit point of the sequence \eqn{\{\iterate{\ma}{i}\}} of iterates generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}.
+The limit point \eqn{\ma^\ast} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions of \eqn{con}.
+Let us consider the approximate problem in \eqref{con-m}.
+The feasible set \eqn{\mc{X}_{k}^{i}} and  \eqn{\mc{Y}_{k}^{i}} in each iteration \eqn{\{k,i\}} has a nonempty interior and by using \eqref{con-relax}, the feasible set in each iteration obeys \eqn{\mc{X}_{k}^{i} \subset \mc{F}}.
+Therefore, all the iterates \eqn{\{\iterate{\ma}{i}\}} found by \eqn{\mc{A}} are feasible.
+By the strong convexity of \eqn{f(\ma)}, we have
+\begin{IEEEeqnarray}{rl}  \neqsub \label{strong_cvxty}
+&(\ma^{(i)} - \ma^{(i+1)}) \nabla {f}(\ma^{(i+1)}) \geq 0 \eqsub \\
+&f(\ma^{(i)}) - f(\ma^{(i+1)}) \geq c \: \|\ma^{(i)} - \ma^{(i+1)}\|^2. \eqsub
+\end{IEEEeqnarray}
+Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \ma^{(i+1)}\| \rightarrow 0} as the objective converges and \eqn{\ma^{(i+1)} \rightarrow \ma^{\ast}} as \eqn{i \rightarrow \infty}.
+
+To show that \eqn{\ma^{\ast}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem \eqref{con}.
+Let us consider \eqn{\mc{Y}_{\ast}^{\ast}} as the feasible set of \eqref{con-m} upon convergence, containing \eqn{\ma^{\ast}}.
+The \ac{KKT} conditions at \eqn{\ma^{\ast}} is given by
+\begin{equation} \label{kkt_expr}
+\textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0
+\end{equation}
+for some Lagrange multipliers \eqn{\mu_i \geq 0}.
+Using \eqn{\hat{f}(\ma^{\ast}) = f(\ma^{\ast})} and \eqref{con-relax} in \eqref{kkt_expr}, we can see that \eqref{kkt_expr} is indeed the \ac{KKT} condition for the nonconvex problem \eqref{con}.
+Since the gradient is zero in \eqref{kkt_expr}, the objective cannot be decreased any further.
+Now, by using \cite[Th.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that the limit points \eqn{\ma^\ast} of \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
+
+%In order for \eqn{\ma^{\ast}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}.
 In each iteration, the algorithm \eqn{\mc{A}} in \eqref{g-algo} finds a point \eqn{\iterate{\ma}{i} \in \mc{F}} with \eqn{f(\iterate{\ma}{i}) < f(\iterate{\ma}{i-1})}, therefore, it satisfies all the constraints of \eqref{con}.
@@
 
-To show the equivalence in the gradients of \eqref{con} and \eqref{con-m} at \eqn{\ma^{\ast}}, let us consider the limit point of the \ac{SCA} update in \eqn{\mc{A}} as it converges to a fixed point \eqn{\ma^{\ast} \in \mc{F}^{\ast}}.
+%To show the equivalence in the gradients of \eqref{con} and \eqref{con-m} at \eqn{\ma^{\ast}}, let us consider the limit point of the \ac{SCA} update in \eqn{\mc{A}} as it converges to a fixed point \eqn{\ma^{\ast} \in \mc{F}^{\ast}}.
 The \ac{KKT} expression for the convex subproblem \eqref{con-cvx} is given by
-\begin{equation} \label{kkt_expr}
-\nabla f(\ma^{\ast}) + \mu_1 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0
-\end{equation}
-for some Lagrange multipliers \eqn{\mu_i \geq 0}.
+%\begin{equation} \label{kkt_expr}
+%\nabla f(\ma^{\ast}) + \mu_1 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0
+%\end{equation}
+%for some Lagrange multipliers \eqn{\mu_i \geq 0}.
 Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}.

### 2015-07-06 Response/Response 2/response-1.tex
half cooked

@@
 
-\vspace{0.1in}
-We thank the reviewer for providing valuable and insightful comments.
+\vspace{1eM}
+\underline{\textit{Reply:}} We thank the reviewer for providing valuable and insightful comments.
 
+\vspace{1eM}
 For the resubmitted manuscript, the reviewer still has the following concerns
@@
 
-\resp We understand the reviewer concern.
-Based on the suggestion, we have removed couple of paragraphs from Section III.A and shortened the discussions on the simulation section to provide additional details for the convergence proof.
+\resp After a careful check of the manuscript, we have removed couple of paragraphs from Section III.A and shortened the discussions on the simulation section to provide additional details for the convergence proof.
+We believe the removed parts don't affect the readability of the paper and the added text regarding convergence proof certainly improves the quality.
 
@@
 
-Let \eqn{\mbf{z}} be the stacked vector of optimization variables that can either be \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the optimization problem that we are trying to solve, \textit{i.e}, either solving for \eqn{\mx} and \eqn{\mz} by fixing \eqn{\iter{\my}{\ast}{i-1}} or solving for \eqn{\my} and \eqn{\mz} by keeping \eqn{\iter{\mx}{\ast}{i}} fixed.
+Let \eqn{\mbf{z}} be the stacked vector of optimization variables that can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the optimization problem that we are trying to solve, \textit{i.e}, either solving for \eqn{\mx} and \eqn{\mz} by fixing \eqn{\iter{\my}{\ast}{i-1}} or solving for \eqn{\my} and \eqn{\mz} by keeping \eqn{\iter{\mx}{\ast}{i}} fixed.
 

### 2015-07-06 Response/Response 2/response-2.tex
half cooked

@@
 
-\vspace{0.1in}
-We thank the reviewer for providing useful comments. The comments are constructive and helped us to improve the manuscript better.
+\vspace{1eM}
+\underline{\textit{Reply:}} We thank the reviewer for providing useful comments. The comments are constructive and helped us to improve the manuscript better.
 
@@
 
-\resp We apologize for not discussing the sub-channel ordering guidelines in a detailed manner.
-As suggested by the reviewer, we have included the guidelines on selecting the sub-channel ordering based on the greedy selection, which could be an educated guess over the random sub-channel ordering.
-Even though the number of backlogged packets must also be involved in the sub-channel ordering, greedy selection provides an effective ordering when the queues are fairly equal among the serving users or when the number of backlogged packets are significantly large.
-This information is now included in the revised manuscript under Section III-D final paragraph.
-We have included a plot comparing different ordering schemes to justify the above statement.
-Even though we are not including it in the paper, we have included in the response letter to justify the reviewers claim.
-We considered a system model with \eqn{N = 6} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users.
+\resp We apologize for not discussing the sub-channel ordering in a detailed manner.
+We have included the guidelines for selecting the sub-channel ordering based on channel gains, \textit{i.e}, greedy selection.
+In random ordering scheme, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
+As suggested by the reviewer, the greedy sub-channel ordering is based on sorting the best channel from each sub-channel, which is obtained by finding the highest channel norm between the users from the respective serving \ac{BS}.
+Note that the users channel used in the ordering procedure is the channel seen by the users with the corresponding serving \acp{BS} only.
+
+However, it may not be optimal for all system configurations, since the ordering scheme should also consider the number of backlogged packets associated with each user. We have 
+emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user.
+Even though we are not including it in the paper, we have included in the response letter to answer the reviewer's question.
+We considered a system with \eqn{N = 4} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users.
 The \ac{PL} is distributed uniformly over \eqn{[0,-3]} dB.
-\begin{figure}[h!]
+The number of backlogged packets assumed for each user is provided in the corresponding captions in Fig.
+\ref{fig-review-1}.
+\begin{figure*}[h!]
 	\centering
-	\includegraphics[width=0.8\columnwidth]{reviewer_2_Q1.eps}
-	\caption{Convergence of the algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 6,2,12,4,1 \rbrace} using \me{\ell_1} norm}
+	\subfloat[][Number of backlogged packets for each user in bits \eqn{Q_k = [11,8,14,6,6,2,10,10,5,6,9,5]}]{
+		\includegraphics[width=0.8\textwidth]{reviewer_2_Q1B.eps}
+		\label{fig-review-1a}
+	}
+	\hfill
+	\subfloat[][Number of backlogged packets for each user in bits \eqn{Q_k = [8,9,12,8,12,5,4,10,8,5,7,9]}]{
+		\includegraphics[width=0.8\textwidth]{reviewer_2_Q1A.eps}
+		\label{fig-review-1b}
+	}
+	\caption{Convergence of the algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace} using \me{\ell_1} norm}
 	\label{fig-review-1}
-\end{figure}
+\end{figure*}
 
@@
 \ref{fig-review-1} compares different ordering of sub-channels with the total number of backlogged packets remaining in the system as the metric.
-The random ordering are based on permutation of the sub-channel indices and sequential ordering is the natural way of selection.
-The greedy sub-channel ordering is based on sorting the best channel from each sub-channel, which is obtained by finding the highest channel norm between the users from the respective serving \ac{BS}.
-As pointed out by the reviewer, greedy scheduling performed much better when compared to the other random ordering schemes.
+As can be seen from Fig.
+\ref{fig-review-1a}, the greedy sub-channel ordering provides a favorable way of choosing the sub-channels to minimize the total number of backlogged packets.
+However in Fig.
+\ref{fig-review-1b}, the greedy sub-channel ordering is not an efficient strategy in determining the order in which the sub-channels are to be chosen.
+We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic method under Section III-D final paragraph.
+Note that as the number of users in the system increases, all channel ordering provides favorable order to minimize the total number of backlogged packets in the system.
 
@@
 	\begin{enumerate}
-		\item Quantifying the signaling overhead of the distributed algorithm over the centralized one depends on the system model under consideration.
-For example, let us consider a model with \eqn{N = 1,N_B = 2,K = 4,N_T = 4,N_R = 1}, where each \ac{BS} has two users.
+		\item The amount of signaling overhead of the distributed algorithm and the centralized one depends on the system model of consideration.
+For example, let us consider a model with \eqn{N = 1} sub-channels ,\eqn{N_B = 2} \acp{BS}, and \eqn{K = 4} users in total, each \ac{BS} serving \eqn{2} users.
+Let \eqn{N_T = 4} be the number of transmit antennas and \eqn{N_R = 1} be the number of receive antenna at each user.
 In this scenario, the amount of information exchange to perform a centralized algorithm by a common controller requires the knowledge of complete channel matrices interlinked in the system, \textit{i.e}, the number of users times the \acp{BS}.
-In order to quantify the total number of bits required to be exchanged, let us assume that each complex channel for a single-input single-output requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is important).
-Using this assumption, the total number of channel information in bits to be exchanged via backhaul requires \eqn{10 \times K \times N_B \times N_R \times N_T \approx 320} bits.
-On the other hand, for the distributed case, let us consider \eqn{6} bits are required to quantize the scalar interference in the consensus vector.
-Therefore, it requires \eqn{6 \times 2 \times 2} bits of information to be exchanged for each iteration.
-With this overhead, we can perform only \eqn{6} \ac{SCA} updates with \eqn{J_{\max} = 2} internal iterations in each to reach the centralized overhead.
-Note that the number iteration includes the \ac{SCA} update as well.
-However, by knowing the complete channel of the users in the system, the centralized controller can perform the precoder design until convergence.
-However, as the number of sub-channels, users or the antenna element increases, it may not be a feasible option to feedback the user channels across the coordinating \acp{BS} to the centralized controller.
-The quantizing the channel information degrades the achievable performance of the centralized solution that also needs to be considered while comparing the signaling overhead.
+
+		In order to quantify the total number of bits required to be exchanged, let us assume that each complex channel for a single-input single-output requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is important) or it can be a equal share of \eqn{5} bits for both amplitude and phase.
+Using this assumption, the total number of channel information in bits to be exchanged via backhaul requires \eqn{10 \times K \times N_B \times N_R \times N_T = 320} bits.
+On the other hand, for the distributed case, let us consider \eqn{6} bits are required to quantize the scalar interference in the consensus vectors.
+Consequently, the proposed distributed solutions require \eqn{6 \times 2 \times 2} bits to be exchanged in each iteration.
+
+		In this example, for the same amount of signaling overhead as in centralized method, we can performance only up to 6 SCA updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for ADMM part).
+This may not be sufficient for the distributed algorithms to attain the same performance as the centralized method.
+However, as the number of sub-channels, users and/or the antenna element increases, it may not be a feasible option to feedback the \ac{CSI} across the coordinating \acp{BS} to the centralized controller.
+In addition to comparing the signaling overhead, we also need to consider the effects of the quantization of the \ac{CSI} on the performance of a centralized algorithm, which is beyond the scope of our paper.
+Generally, the performance is significantly degraded if the \ac{CSI} is quantized \cite{nam_robust}.
 Moreover, in the centralized algorithm, resulting transmit precoders need to be exchanged with the corresponding \acp{BS} before the actual transmission, involving huge overhead in the backhaul.
+
 		\item Using the above discussion, we can say that when the system size is huge, it would be favorable to consider the distributed algorithm over the centralized approach due to the huge signaling overhead involved in exchanging the channels.
-		\item In particular, \ac{ADMM} and primal approach requires significant overhead compared to the centralized algorithm when \eqn{J_{\max} = 1} for a small system, since by exchanging the quantized channels, each \ac{BS} can perform the centralized algorithm independently until convergence.
+
+		\item In particular, \ac{ADMM} and primal approach requires significant overhead compared to the centralized algorithm for a small system, since by exchanging the quantized channels, each \ac{BS} can perform the centralized algorithm independently until convergence.
 However, it depends on the channel quantizer, which is likely to be based on the channel density function (eg.
 Lloyd quantizer).
-For a system involving more number of coordinating \acp{BS}, users and number of antenna elements, it would be beneficial to use distributed algorithm with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
-		\item Even with the same signaling overhead, it is not possible to prove the benefits of the distributed algorithm like \ac{ADMM} and primal approach over the independent centralized scheme performed by exchanging the channel state information across the \acp{BS}.
-It is dependent on the system model under consideration.
-As explained earlier, for the considered system model, the independent centralized algorithm performs better in terms of the over head involved.
+For a system involving more coordinating \acp{BS}, users and antenna elements, it would be beneficial to use distributed algorithm with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
+If we set \eqn{J_{\max} = 1}, the proposed algorithms still converge (but monotonicity of SCA is not guaranteed).
+
 	\end{enumerate}
 
-	We have included the above information briefly in Section IV-C first paragraph and in the last paragraph.
-We have also included this information in the paragraph before the Conclusions section.
-Having said that, note that in reality, the channel is time-correlated, and it is often enough to update the precoders once per radio frame or certain number of symbols later.
-It is not necessary for the decentralized algorithm to converge until the end, it is only important to follow the fading process when \eqn{J_{\max} > 1}.
-The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13], which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
-The distributed algorithm for the time correlated case is not provided in the current manuscript, since it is not in the scope of the precoder design algorithms considered in this manuscript.
-However, for the clarity purpose, we have provided a plot demonstrating this behavior for the \ac{KKT} based algorithm in Section IV-C presented in the manuscript.
+	We have included the above discussions in the first and last paragraphs of Section IV-C, and the paragraph before Section VI (i.e., the conclusion section).
+In reality, since the channel is time-correlated, it is enough to update the precoders once per radio frame.
+Thus, it is not necessary for the distributed algorithm to converge until the end.
+Instead, the decentralized parts only need to follow the fading process when \eqn{J_{\max} > 1}.
+
+	The performance of the distributed algorithm based on dual decomposition scheme was discussed for the time-correlated fading in Section C of [13], which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+The distributed algorithm for the time correlated case is beyond the scope of our paper and thus is not considered in the current manuscript.
+However, we take this opportunity to show a plot demonstrating this behavior for the \ac{KKT} based algorithm presented in Section IV-C of the manuscript.
 	\begin{figure}[h!]
@@
 The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.
-We considered that the channel is coherent over \eqn{N_S = 100} symbols or frames and the precoder update is performed by exchanging the equivalent channel for \eqn{J_{\max} = 3,5,10} number of iterations.
+We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the equivalent channel for \eqn{J_{\max} = 3,5,10} number of iterations.
 The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{J_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{J_{\max}}{N_S})} is considered as a penalty involved due to the precoder exchange.
@@
 	\end{equation}
+
 	Unlike the distributed algorithm, the centralized scheme presented in Fig.
@@
 \resp We thank the reviewer for raising the important concern regarding the convergence issue of the distributed algorithm with limited number of iterations.
-In view of this, we have updated the manuscript to include the discussion on the convergence of the distributed algorithms with limited number of iterations in Appendix B third paragraph after (57).
+In view of this, we have updated the manuscript to include the discussion on the convergence of the distributed algorithms with a limited number of iterations in the third paragraph of Appendix B after (57).
 Since the distributed algorithm cannot be guaranteed to be monotonic in each iteration, it is not possible to prove the convergence of the algorithm.
@@
 \begin{itemize}
-\item The fixed points for each convex subproblem exist, but may not be unique unless the objective function is regularized with a strongly convex term as discussed in Appendix A-C.
-\item If the distributed algorithm is iterated for limited number of iterations, it is not guaranteed to achieve the fixed point even if the outer \ac{SCA} update is performed for large number of iterations.
-In this scenario, it is not guaranteed to converge.
-In all our simulations on the primal and the \ac{ADMM} approach, we have iterated \eqn{J_{\max} = 20} in order to guarantee the monotonicity of the objective.
+\item If there exists a fixed point or a set of fixed points for the original nonconvex problem in (16), then the proposed centralized algorithm in Section III-B and III-C finds at least one such point if iterated until convergence, which is provided in Appendix A.
+In order to find a unique fixed point, we regularize the objective function in (16) with a quadratic penalty term as discussed in Appendix A to transform the objective as a strongly convex function.
+\item If the distributed algorithm is carried out for a limited number of iterations, it is not guaranteed to achieve a fixed point even if the outer \ac{SCA} update is performed for a large number of iterations.
+By this approach, the distributed approaches are not guaranteed to converge to a stationary point.
+In all our simulations on the primal and the \ac{ADMM} approach, we have set \eqn{J_{\max} = 20} in order to guarantee the monotonicity of the objective.
 \item Unless the objective function is regularized with a strongly convex term as in Appendix A-C, the uniqueness of the iterates is not guaranteed. 
-\item In each \ac{SCA} update, if the distributed algorithm converges to a fixed point, then the overall convergence will be a stationary point of the original nonconvex problem.
-It may not be an optimal solution to the original nonconvex problem.
-It can be proved based on the strict monotonicity of the objective, since the distributed algorithm converges to a centralized solution.
-\item Since the coupling between the distributed precoder designs are the interference between the BSs and the users, in the \ac{ADMM} approach, the interference is treated as a local variable, which is then included in the precoder design problem for each coordinating BS.
-This is treated as a local variable for a specific BS.
+\item In each \ac{SCA} update, if the distributed algorithms are allowed to converge to the centralized solution, then the overall convergence will be a stationary point of the original nonconvex problem by following the same argument as that of the centralized algorithm.
+\item Since the coupling between the distributed precoder designs is the interference between the BSs and the users, in the \ac{ADMM} approach, the interference is treated as a local variable, which is then included in the precoder design problem for each coordinating BS.
+This is treated as a local variable for individual \acp{BS}.
 Note that the local variable is an assumption made by the BS on the actual interference caused by the neighboring BSs.
@@
 These discussions have been made in the revised manuscript in Section IV-B.
-For further details we have also referred the interested reader to [11], which discusses exclusively about the ADMM approach.
-Upon convergence of the \ac{ADMM} approach, the interference vector can be considered as an upper bound of the actual interference seen in the network.
-It can be equal to the actual interference but not less.
+For reference purpose, we have also referred the interested reader to [11], which discusses exclusively about the ADMM approach.
+Upon convergence of the \ac{ADMM} approach, the interference vector is equal to the actual interference seen in the network.
 \end{itemize}
@@
 \end{enumerate}
+
+\bibliographystyle{./../../Styles/IEEEtran}
+\bibliography{./../../Library/IEEEabrv,./../../Library/kirja_survey}

### 2015-07-06 Response/Response 2/response-3.tex
half cooked

@@
 
-\vspace{0.1in}
-\review{We thank the reviewer for recognizing the changes made on our earlier manuscript. We also thank the reviewer for providing constructive comments to help us to improve our manuscript.}
+\vspace{1eM}
+\underline{\textit{Reply:}} We thank the reviewer for recognizing the changes made on our earlier manuscript.
+We also thank the reviewer for providing constructive comments to help us to improve our manuscript.
 
@@
 
-\resp We understand the reviewer concern.
+\resp We thank the reviewer for the comment.
 The initial operating point for the \ac{SCA} approach can be identified by initializing the transmit precoders \eqn{\mvec{m}{l,k,n}} with the single user transmit beamformers satisfying the total power constraint at each \ac{BS}.
@@
 Upon initializing both transmit and the receive beamformers, the interference term \eqn{\beta_{l,k,n}} can be initialized from (20b).
+The operating point for \eqn{\tilde{\mbf{m}}_{l,k,n}^{(i+1)}} is updated using as
+\begin{equation}
+\tilde{\mbf{m}}_{l,k,n}^{(i+1)} = \mvec{m}{l,k,n}^{(i)} + \varphi^{(i)} \: (\mbf{m}_{l,k,n} - \mbf{m}_{l,k,n}^{(i+1)})
+\end{equation}
+where \eqn{\varphi^{(i)} \in (0,1]} is the step size used to update the operating variables.
+The choice of the variable \eqn{\varphi^{(i)}} can be selected such that \eqn{\sum_{i} \varphi^{(i)} = \infty} as discussed in [32].
 This information is included in the revised manuscript in the paragraph on Section III-B following after (23).
@@
 
-\resp We thank the reviewer for the comment. We have updated the manuscript further for better clarity and understanding based on the other reviewers.
+\resp We thank the reviewer for the comment. We have included several materials to make the proof of convergence more rigorous.
 
@@
 
-	\resp We understand the reviewer concern.
-We have updated the manuscript to include a discussion on the choice of selecting an algorithm for the practical purposes.
+	\resp We have updated the manuscript to include a discussion on the choice of selecting an algorithm for the practical purposes.
 The choice of selecting a centralized algorithm is equally fair when \eqn{N_R > 1}.
@@
 However, when \eqn{N_R > 1}, the \ac{KKT} based distributed approach is much more efficient, since it has less signaling overhead for a given throughput.
-The choice of the \eqn{\ell_q} norm is as discussed in Section II-B.
-These lines are included in the paragraph before the Conclusions section.
-If the reviewer is interested on the practical usage of the algorithms, please refer to the response for the reviewer 2's question 2 in this response document for more details involving the performance of the KKT based distributed algorithm.
+The choice of the \eqn{\ell_q} norm is discussed in Section II-B.
+These lines have been included in the paragraph before the Conclusions section.
+For the practical usage of the algorithms, please refer to the response for the reviewer 2's question 2 in this response document for more details involving the performance of the KKT based distributed algorithm.
 
@@
 
-	\resp It is rewritten to provide additional clarity as suggested by the reviewer. We have included the reference [28] for more illustrative discussions on the backhaul signaling.
+	\resp The part mentioned above has been rewritten to improve its readability as suggested by the reviewer.
+We have included the reference [28] for more illustrative discussions on the backhaul signaling.
 
@@
 
-	\resp We understand the reviewer concern.
-We used different path loss models for improved clarity and to show that the proposed algorithms works reasonably well on all scenarios.
-To provide a fair comparison, we have also included the centralized algorithm to draw the difference between the other schemes.
-We will consider the reviewer comment in our future work.
-However, if the reviewer insists on the unanimous configuration across the figures, we will revise the manuscript accordingly.
+	\resp We thank the reviewer for the comment.
+The main purpose of considering several path loss models is simply to show that the proposed algorithms works reasonably well on various scenarios.
+For benchmarking, we have also included the centralized algorithm to draw the difference between the other schemes.
+We are conducting more numerical experiments to have a more complete comparison of the schemes.
+Unfortunately those results cannot be included in the current manuscript due to space limitation.
+We aim to make them available online as a companion technical report whey they are ready.
 
@@
 
-	\resp We apologize for the error. We have modified the text to agree with the simulation Fig. 1.
+	\resp We apologize for the error which has been fixed in the revised manuscript.
 
@@
 
-	\resp The performance of the Q-WSRME is better than Q-WSRM in Fig.
+	\resp Indeed the performance of the Q-WSRME is better than Q-WSRM in Fig.
 4(b).
-Since we have plotted the instantaneous arrival rates also in the same figure, it is difficult to discriminate between the colors.
-We have updated the manuscript to provide better clarity in the figure.
+The misleading observation was probably due to the visualization effect where the colors representing the performance of sum arrivals and Q-WSRME are quite similar.
+We have updated Fig.
+4 (and all other figures) in the revised manuscript to avoid such visualization problems.
 
@@
 
-	\resp We have update the manuscript with the proper subscript.
+	\resp This issue is corrected in the revised manuscript.
 
@@
 
-	\resp We thank the reviewer for pointing out the mistake. It is the dual variable \eqn{\sigma_{l,k,n}} and not \eqn{\lambda_{l,k,n}}. We have updated the manuscript accordingly.
+	\resp We thank the reviewer for pointing out the mistake.
+In fact, it should be the dual variable \eqn{\sigma_{l,k,n}} and not \eqn{\lambda_{l,k,n}}.
+We have fixed this problem in the revised manuscript.
 
@@
 
-	\resp We have updated the manuscript with the proper word.
+	\resp We have fixed this error.
 
@@
 
-	\resp We have updated the manuscript with the singular tense and we have also verified the grammatical validity of the manuscript as per the reviewer suggestion.
+	\resp We thank the reviewer for the comment and we have proofread the manuscript carefully to eliminate all grammar errors.
 

### 2015-07-06 Report/introduction.tex
half cooked

@@
 To reduce the number of backlogged packets, we can assign weights based on the current queue size of the users.
-Specifically, the queue states can be incorporated in the \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{tassiulas,neely2010stochastic}, where \me{R_k} denotes the achievable data rate of user \me{k}.
+Specifically, the queue states can be incorporated in the \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{neely2010stochastic}, where \me{R_k} denotes the achievable data rate of user \me{k}.
 In the \textit{backpressure algorithm}, the differential queues between the source and the receiver nodes are used to scale the transmission rate \cite{georgiadis2006resource}.

### 2015-07-06 Report/joint_wsrm_formulation.tex
half cooked

@@
-The queue minimizing algorithms have been studied extensively in the networking literature to provide congestion-free routing between any two nodes in the network.
-One such algorithm is the \emph{backpressure algorithm} \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
-It finds an optimal control policy in the form of rate or resource allocation by considering the differential backlogged packets between the source and the destination nodes for the networking entities.
+The queue minimizing algorithms have been studied extensively in the networking context for providing congestion-free routing between any two nodes in the network.
+One such algorithm is the \emph{backpressure algorithm} \cite{georgiadis2006resource,neely2010stochastic}.
+It finds an optimal control policy in the form of resource allocation by utilizing differential packets between any two nodes.
 %Even though the algorithm is primarily designed for the wired infrastructure, it can be extended to the wireless networks by designing the user rate variable \me{t_k} in accordance to the wireless network.
@@
 \end{equation}
-by using the following inequality 
-\begin{equation}
-\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
-\end{equation}
+%by using the following inequality 
+%\begin{equation}
+%\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
+%\end{equation}
 The total number of backlogged packets at any given instant \me{i} is reduced by minimizing the conditional expectation of the Lyapunov drift expression \eqref{drift-exp} given the current number of queued packets \me{\mbfa{Q}(i)} waiting in the system.
@@
 Now, the conditional Lyapunov drift, denoted by \me{\Delta{(\mbfa{Q}(i))}}, is given by the infimum over the transmission rate as
-\iftoggle{single_column}{
+\iftoggle{single_column}{ \allowdisplaybreaks
 \begin{IEEEeqnarray}{rCl} \label{backpressure-approx} \neqsub
@@
 	&\leq& \underbrace{\mathbb{E}_{\mbfa{\lambda},\mbf{t}} \set {\sum_{k \in \mc{U}} \, \frac{\lambda^2_k(i) + t_k^2(i)}{2} \vert \mbf{Q}(i)}}_{\le B} + \sum_{k \in \mc{U}} Q_k(i) A_k(i) - \mathbb{E}_{\mbfa{\lambda},\mbf{t}}\set{\sum_{k \in \mc{U}} Q_k(i) t_k(i)  \vert \mbf{Q}(i)}, \eqsub \label{backpressure-approx-1b}
-\end{IEEEeqnarray}}{
+\end{IEEEeqnarray}}{ \allowdisplaybreaks
 \begin{IEEEeqnarray}{CL} \label{backpressure-approx} \neqsub
@@
 \end{IEEEeqnarray}}
-where the subscripts \me{\mbf{t}} and \me{\mbfa{\lambda}} represents the vector formed by stacking the transmission and the arrival rate of all users in the system.
+where \me{\mbf{t}} and \me{\mbfa{\lambda}} are the vectors formed by stacking the transmission and the arrival rate of all users in the system.
+Since the second order moments of \me{\mbf{t}} and \me{\mbfa{\lambda}} are bounded, it can be replaced by a constant \me{B} in \eqref{backpressure-approx-1b} as discussed in \cite{neely2010stochastic}.
+The second term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.
+
+%where the subscripts \me{\mbf{t}} and \me{\mbfa{\lambda}} represents the vector formed by stacking the transmission and the arrival rate of all users.
 Since the transmission and the arrival rates are bounded, the second order moments in the first term of \eqref{backpressure-approx-1b} can be bounded by a constant \me{B} without affecting the optimal solution of the problem \cite{neely2010stochastic}.
@@
 where the precoders are associated with \me{\gamma_{l,k,n}} defined in \eqref{eq:SINR}.
-By using the number of queued packets as the weights, the resources can be allocated to the user with more backlogged packets; this essentially results in greedy allocation.
+%By using the number of queued packets as the weights, the resources can be allocated to the user with more backlogged packets; this essentially results in greedy allocation.
 

### 2015-07-06 Report/kkt_mse_approach.tex
half cooked

--- 2015-06-27 Report/kkt_mse_approach.tex
@@
 In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
-\review{Note that the distributed approaches discussed so far may not be viable for multi-antenna receivers due to the signaling overhead involved in exchanging the coupling variables if the number iterations required to converge is large, which depends on the system size.}
+\review{Note that the distributed approaches discussed so far may not be efficient for multi-antenna receivers in terms of signaling overhead involved in exchanging the coupling variables and the receivers as the system size and the required number of iterations increases.}
 
@@
 
-In the proposed \ac{JSFRA} formulation, the maximum rate constraints are implicitly handled by the objective function without the need of explicit constraints.
-However, the \ac{KKT} conditions cannot be formulated due to the non-differential objective function.
-The non-differentiability is due to the absolute value operator present in the norm function.
-In order to make the objective function differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the optimal solution, namely,
+In the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without additional rate constraints.
+However, due to the non-differential objective, the \ac{KKT} conditions cannot be formulated.
+The non-differentiability is due to the absolute operator present in the norm function.
+To make the objective differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the solution, namely,
 \begin{itemize}
@@
 
+\review{To conclude this section, we provide some remarks regarding the choices of centralized and distributed algorithms under some scenarios.
+We can choose the \ac{JSFRA} formulation via either \ac{SINR} relaxation (Sect.
+\ref{sec-3.2.1}) or \ac{MSE} equivalence (Sect.
+\ref{sec-3.3}) equally when \eqn{N_R > 1}.
+However, for \eqn{N_R = 1} scenario, the \ac{JSFRA} formulation in Section \ref{sec-3.2.1} is more efficient, as there is no receiver update, and therefore has less complexity.
+Similarly, when \eqn{N_R = 1}, the distributed approaches based on the \ac{JSFRA} method via \ac{SINR} relaxation is preferred over other schemes due to the limited signaling between the coordinating \acp{BS}, involving the scalar interference values.
+However, when \eqn{N_R > 1}, the \ac{KKT} scheme presented in Section \ref{sec-4.3} has less signaling requirements for a given throughput improvement.}
+
 %\subsubsection*{Convergence}

### 2015-07-06 Report/mse_formulation.tex
half cooked

--- 2015-06-22 Report/mse_formulation.tex
@@
 \end{IEEEeqnarray}}
+\begin{algorithm}
+	\SetAlgoLined
+	\DontPrintSemicolon
+	\BlankLine
+	\SetKwInput{KwInit}{Initialize}
+	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
+	\KwOut{\me{\mbf{m}} and \me{\mbf{w} \: \fall l \in \set{1,2,\dotsc,L}} and \me{i=0,j=0}}
+	\KwInit{\me{\tilde{\mbf{m}}} by satisfying total power constraint \eqref{eqn-9.1d}}
+	update \me{\tilde{\mbf{w}}, \tilde{\mbf{\beta}}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}} \;
+	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
+		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
+			solve for transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
+			update the operating point \eqn{\tilde{\mbf{u}}_{l,k,n}^{(j+1)}} using \eqref{operating_point_update}\;
+			update $j = j + 1$\;
+		}
+		solve for \me{\mbf{w}} using \eqref{eqn-9--1} or \eqref{eqn-10} and update \eqn{\tilde{\mbf{u}}_{l,k,n}^{(0)}}\;
+		update $i = i + 1$ and set \me{j = 0}\;
+	}
+	\caption{Algorithm of \acs{JSFRA} scheme}
+	\label{algo-1}  
+\end{algorithm}
 
@@
 \end{IEEEeqnarray}
-The optimal transmit precoders for a fixed receiver are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
-The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.
-
+The optimal transmit precoders for a fixed receiver are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as outlined in Algorithm \ref{algo-1}.
+The convergence proof follows the discussions in Appendix \ref{sec-3.5}.
 \begin{comment}

### 2015-07-06 Report/primal_approach.tex
half cooked

@@
 The master problem treats \me{\mbfa{\zeta}_{b}} as a variable and the slave subproblems assumes it to be a constant in each iteration.
-\review{Since the interference levels are fixed in each subproblem, the feasibility of the subproblems depend on the step size used to update the interference variables by the master problem.}
+\review{Since the interference levels are fixed in each subproblem, the feasibility of the subproblems depends on the step size used to update the interference variables by the master problem.}
 

### 2015-07-06 Report/sub_channel_wsrm.tex
half cooked

@@
 As an alternative sub-optimal solution, we present a \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
-The sharing of power can be equal or based on a predetermined pattern as in partial frequency reuse for the sub-channels as given by
-\begin{equation}
-\sum_{i=1}^N P_{\max,i} = P_{\max}.
-\end{equation}
+The sharing of power can be either equal or based on predetermined pattern as in partial frequency reuse with \eqn{\sum_{i=1}^N P_{\max,i} = P_{\max}}.
 Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the number of backlogged packets.
@@
 \end{equation}
-where \me{t_{l,k,j}} denotes the rate corresponding to the user \me{k} on the \me{\ith{j}} sub-channel and \me{\ith{l}} spatial stream.
-\review{In spite of the improved covergence speed over the \ac{JSFRA} approach, the \ac{SRA} scheme is sensitive to the order in which the sub-channels are selected.
-Heuristically, we can choose the order by sorting the available best channel norm from each sub-channel, obtained by sorting the norm of the channel between the users and the corresponding serving \ac{BS} for each sub-channel.
-In spite of not considering the number of backlogged packets in the sub-channel ordering, it can be preferred over random ordering.
-However, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the multi-user diversity.}
+where \me{t_{l,k,j}} is the \me{\ith{k}} user rate on the sub-channel \me{j}.
+
+\review{Since the performance of the \ac{SRA} scheme is sensitive to sub-channel ordering, for simplicity we use random selection in all our simulations.
+We can also use greedy ordering by considering the channel norm associated with the user and the corresponding serving \ac{BS}, but this comes at the cost of increased complexity.
+However, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the available multi-user diversity.}
 

### 2015-07-06 Report/wsrm_formulation.tex
half cooked

--- 2015-06-23 Report/wsrm_formulation.tex
@@
 Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}.
+The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}.
 By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.
@@
 }
-In summary, for fixed linear receiver \me{\mvec{w}{l,k,n}} and operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
+For a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n} = \{ \tilde{\mbf{m}}_{l,k,n},\tilde{\mbf{w}}_{l,k,n},\tilde{\mbf{\beta}}_{l,k,n} \}}, the relaxed convex subproblem is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-9} \neqsub
-\underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
+\underset{\substack{\mbf{m}, \mbfa{\gamma},\mbfa{\beta}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
+\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\tilde{\mbf{w}}_{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
 & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
@@
 
-Now, the optimal linear receivers for fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
+Now, the optimal linear receivers for fixed transmit precoders \me{\tilde{\mbf{m}}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
 \begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub
 \underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
+\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \tilde{\mbf{m}}_{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
 & \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9--1.1e}
@@
 \begin{IEEEeqnarray}{rCl} \neqsub
-\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
+\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} \tilde{\mbf{m}}_{j,i,n} \tilde{\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} \tilde{\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} \tilde{\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} \tilde{\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
 \end{IEEEeqnarray}
@@
 \begin{IEEEeqnarray}{rCl} \neqsub
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
-\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \tilde{\mbf{m}}_{j,i,n} \tilde{\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
+\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \tilde{\mbf{m}}_{l,k,n}. \IEEEyessubnumber \label{eqn-10}
 \end{IEEEeqnarray}}
@@
 
-The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved iteratively by updating the operating point from the previous iteration.
-The iterative algorithm is referred as \acl{QM} \ac{JSFRA} scheme, and it is outlined in Algorithm \ref{algo-1}.
-\review{The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is updated using \eqref{eqn-9.1c} with the chosen transmit precoders and the receivers.} For a fixed receiver \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} to find an optimal transmit precoders \me{\mvec{m}{l,k,n}}.
-Next, the receivers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
-The iterative procedure is performed until convergence or for fixed number of iterations \me{I_{\max}} as shown in Algorithm \ref{algo-1}.
+The subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved by updating the operating point with the solution from the previous update as
+\begin{equation} \label{operating_point_update}
+\tilde{\mbf{u}}_{l,k,n}^{(j+1)} = \tilde{\mbf{u}}_{l,k,n}^{(j)} +  \varphi^{(j)} \, (\mbf{u}_{l,k,n}^{(j+1)} - \tilde{\mbf{u}}_{l,k,n}^{(j)})
+\end{equation}
+where \eqn{\tilde{\mbf{u}}_{l,k,n}^{(j+1)}} is the operating point for the \eqn{\ith{j+1}} iteration, \eqn{\mbf{u}_{l,k,n}^{(j+1)}} is the optimal solution obtained in the \eqn{\ith{j}} \ac{SCA} step and \eqn{\varphi^{(j)} \in (0,1]} is the step size used to update the operating point \cite{scutari_1}.
+The iterative algorithm, referred as \acl{QM} \ac{JSFRA} scheme, is outlined in Algorithm \ref{algo-1}.
+To find a solution, we first generate transmit beamformers \eqn{\tilde{\mbf{m}}} satisfying the total power constraints \eqref{eqn-9.1d}.
+Then the initial values for receivers \eqn{\tilde{\mbf{w}}} are computed using \eqref{eqn-10}.
+Finally the initial values for \me{\tilde{\mbf{\beta}}} are obtained by \eqref{eqn-9.1c}.
+Note that the initial values for \eqn{p} and \eqn{q} are defined based on \eqref{eqn-wsrm-expr}.
+For fixed receivers \me{\tilde{\mbf{w}}}, the \ac{SCA} updates are carried out until convergence or for fixed number of iterations, say, \me{J_{\max}} to find a minimizer \me{\mbf{m}}.
+Next, the receivers are updated by either \eqref{opt-rx} or \eqref{eqn-10} using fixed \me{\tilde{\mbf{m}}}.
+It is carried out until convergence or for fixed number of iterations \me{I_{\max}}.
 The convergence analysis is given in Appendix \ref{sec-3.5}.
+Even though the objective sequence in Algorithm \ref{algo-1} converges in all our numerical simulations, in order to ensure the convergence of the iterates to a \ac{KKT} point theoretically, we consider a modified objective in \eqref{mod_obj} instead of \eqref{eqn-6.1}.
+\begin{comment}
 \begin{algorithm}
@@
 
-\begin{comment}
 \subsubsection*{Convergence}

### 2015-07-06 Response/Response 2/additions.tex
half cooked

@@
 \item Strong convexity of the objective function is emphasized in Appendix A-C.
-\item Strict Monotonicity of the algorithm is discussed separately in Appendix A-D with more clarity.
+\item Strict monotonicity of the algorithm is discussed separately in Appendix A-D with more clarity.
 \item We have provided additional details on the distributed algorithm convergence as suggested by the reviewers
 \item Section III-D is updated to include the guidelines involved in selecting the sub-channel order.
-\item Short discussion on the choice of algorithm selection is provided 
+\item Discussions on the choice of algorithm selection have been provided 
 \item Initialization of the \ac{SCA} operating point is also included in the revised manuscript

### 2015-07-06 Response/Response 2/document.tex
half cooked

@@
 \usepackage{acronym,etoolbox,color,multicol,xcolor}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}
+%\usetikzlibrary{plotmarks}
+\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools,pgfplots,subfig}
+
+\pgfplotsset{compat=newest}
+\pgfplotsset{plot coordinates/math parser=false}
+\newlength\figureheight
+\newlength\figurewidth
 
@@
 
+\usetikzlibrary{plotmarks}
 \title{Reviewers Comments \& Authors Replies}
@@
 In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors.
-The revisions in the revised manuscript are highlighted using blue color and the authors responses are also presented in blue color text.
+The reviewers questions in the revised manuscript are highlighted in blue color and the authors responses are presented in black.
 Following is the summary of the revision made on the manuscript in accordance with the reviewers comments.

### 2015-07-16 Response/Response 2/response-1.tex
updated with nam response

@@
 Since it is not possible to comment on the inclusion of the previous constraint set in the current update (except the earlier optimal point), the inequality is not guaranteed.
-Based on the comment from the reviewer, we have removed the inequality specifying the previous operating point from (48), since the newly found optimal point is inside the feasible set.
+Based on the comment from the reviewer, we have removed the inequality specifying the previous operating point from (49) in the revised manuscript, since it cannot be guaranteed.
 
@@
 \resp We understand the reviewer concern.
-Even though the \ac{SCA} algorithm converges, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge.
+Even though the objective of the \ac{SCA} iteration converges, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge.
 It is true that the iterates need not converge when the objective function is convex.
-We have modified the discussion on the strong convexity of the objective function to impose the uniqueness of the iterates in each \ac{SCA} update as well.
-By regularizing the objective function with a strongly convex term like \eqn{\|\mbf{m} - \mbf{m}^{(i)}_k\|^2}, we can guarantee the uniqueness of the iterates upon the \ac{SCA} convergence.
+We have modified the discussion by using the strong convexity of the objective function to impose the uniqueness of the iterates in each \ac{SCA} update as well.
+By regularizing the objective function with a strongly convex term like \eqn{\|\mbf{m} - \mbf{m}^{(i)}_k\|^2}, we can guarantee the uniqueness of the iterates upon the \ac{SCA} convergence, \textit{i.e.}, the limit point of the \ac{SCA} update is unique.
 We thank the reviewer for citing this issue on the sequence convergence and the uniqueness of the minimizer.
-We have included this information in the centralized convergence proof on Appendix A-B after (44), after (49) and on Appendix A-C to describe the strong convexity.
+We have updated the manuscript to include this information in the convergence proof in Appendix A-B around (46) and in Appendix A-C.
 
@@
 \resp We thank the reviewer for the pointing out the issue involving the strict monotonicity.
-As suggested by the reviewer, we have included Appendix A-D to discuss the strict monotonicity of the objective function in each update point of the algorithm.
+As suggested by the reviewer, we have included the strict monotonicity of the objective sequence in Appendix A-C following (52).
 
-Let \eqn{\mbf{z}} be the stacked vector of optimization variables that can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the optimization problem that we are trying to solve, \textit{i.e}, either solving for \eqn{\mx} and \eqn{\mz} by fixing \eqn{\iter{\my}{\ast}{i-1}} or solving for \eqn{\my} and \eqn{\mz} by keeping \eqn{\iter{\mx}{\ast}{i}} fixed.
-
-Due to the strong convexity of the modified objective \eqn{f(\mbf{z})}, there exist an unique minimizer in each \ac{SCA} step \eqn{k}.
-Moreover, in each \ac{SCA} step \eqn{k}, the feasible set \eqn{\mc{X}_{k}^{(i)}} includes the earlier optimal point \eqn{\mbf{z}^{(i)}_k}, therefore, the objective decreases strictly unless \eqn{\mbf{z}^{(i)}_k} is a fixed point or a limit point of the \ac{SCA} iterations [22].
-Following the strong convexity of \eqn{f(\mbf{z})}, we have
-\begin{equation} \label{strict_monotonicity}
-f(\mbf{z}) \geq f(\mbf{z}_{\ast}^{(i)}) + \nabla f(\mbf{z}_{\ast}^{(i)}) (\mbf{z} - \mbf{z}_{\ast}^{(i)}) + c \|\mbf{z} - \mbf{z}_{\ast}^{(i)}\|^2, \forall \mbf{z}\in \mc{X}^{(i)}_\ast
+Note that the objective sequence \eqn{\{f(\mbf{x}_k)\}} generated by an iterative \ac{SCA} algorithm is monotonic, \textit{i.e}, \eqn{f(\mbf{x}_k) \leq f(\mbf{x}_{k-1})} and holds with equality at the limit point of the iterative procedure.
+However, upon convergence, due to the convexity of the objective, we may have multiple limit points, say, \eqn{\mbf{y}_{\ast}} with the same objective as \eqn{f(\mbf{y}_{\ast}) = f(\mbf{x}_{\ast})}.
+Therefore, strict monotonicity cannot be guaranteed for the objective sequence.
+However, when the objective function is strongly convex, as discussed in Appendix A-B, the minimizer for the subproblem in each \ac{SCA} iteration \eqn{k} is unique as
+\begin{equation} \label{eqn-aa}
+f(\ma_{k}) - f(\ma_{k+1}) \geq  \nabla f(\ma_{k+1})^\tran (\ma_{k} - \ma_{k+1}) + c \|\ma_{k} - \ma_{k+1}\|^2
 \end{equation}
-where \eqn{\mbf{z}_{\ast}^{(i)}} is a limit point as \eqn{k \rightarrow \infty} for the \eqn{\ith{i}} \ac{AO} iteration.
-The equality in \eqref{strict_monotonicity} is valid iff \eqn{\mbf{z} = \mbf{z}_{\ast}^{(i)}}.
-Strict monotonicity of \eqn{f(\mbf{z}_k^{(i)})} is ensured in the \ac{SCA} steps by the additional quadratic term, which holds with equality at the limit point \eqn{\mbf{z}_{\ast}^{(i)} \in \mc{X}_{\ast}^{(i)}}.
-
-To ensure strict monotonicity of the objective while swapping the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration, we rely on the discussions to show the inequality (51).
-Note that the modified objective \eqn{f} is strongly convex, and therefore has a unique minimizer in each \ac{SCA} step.
-Additionally, the feasible set \eqn{\mc{Y}_0^{(i)}} for \eqn{k=0} \ac{SCA} step with the variables \eqn{\my,\mz} includes the previous minimizer \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}}, thereby having strictly decreasing objective in (51).
-The equality in (51) holds for the limit point \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}.
-Using the above arguments, we can ensure the strict monotonicity of the overall objective sequence.
+where \eqn{\ma_{k+1}} is the optimal solution for the \eqn{\ith{k}} \ac{SCA} subproblem and \eqn{\ma_{k}} is the unique minimizer obtained in the previous \eqn{\ith{k-1}} \ac{SCA} step, which is a feasible point for the current problem.
+Since \eqn{\ma_{k+1}} is the solution in the \eqn{\ith{k}} \ac{SCA} problem, following conditions hold
+\begin{subeqnarray}
+\nabla f(\ma_{k+1})^\tran (\ma_{k} - \ma_{k+1}) &\geq& 0 \slabel{eqn-a} \\
+f(\ma_{k}) - f(\ma_{k+1}) &\geq& c \|\ma_{k} - \ma_{k+1}\|^2 \slabel{eqn-b}
+\end{subeqnarray}
+where \eqref{eqn-a} is due to the lack of any descent direction in the feasible set and \eqref{eqn-b} follows from \eqref{eqn-aa} using \eqref{eqn-a}.
+As \eqn{k \rightarrow \infty, \|\ma_{k+1} - \ma_{k}\| \rightarrow 0}, and therefore the iterative algorithm converges to a unique minimizer, say, \eqn{\ma_{\ast}}, which is the limit point of the algorithm.
+Now by using the monotonicity of the \ac{SCA} updates and the uniqueness of the minimizer in each step, we can guarantee the strict monotonicity of the objective sequence generated by the iterative problem.
 
@@
 \resp We thank the reviewer for raising the concern.
-We have updated the manuscript to include the details regarding the stationary point discussion in Appendix A-F and the convergence proof analysis for the primal and the \ac{ADMM} algorithms in Appendix B.
-Additional detail includes the conditions required for showing the stationarity of the limit point and we have included more details to utilize the conclusions from [37] to show the convergence of the ADMM scheme.
+We have updated the manuscript to include the details regarding the stationary point discussion in Appendix A-E and the convergence proof analysis for the primal and the \ac{ADMM} algorithms in Appendix B.
+Additional detail includes the conditions required for showing the stationarity of the limit point and we have included additional details to show the distributed approaches convergence convincing.
 

### 2015-07-16 Response/Response 2/response-3.tex
updated with nam response

@@
 \resp We thank the reviewer for the comment.
-The initial operating point for the \ac{SCA} approach can be identified by initializing the transmit precoders \eqn{\mvec{m}{l,k,n}} with the single user transmit beamformers satisfying the total power constraint at each \ac{BS}.
-Once the transmit precoders are initialized, the receive beamformers \eqn{\mvec{w}{l,k,n}} can be initialized with the \ac{MMSE} receiver based on (23).
-Upon initializing both transmit and the receive beamformers, the interference term \eqn{\beta_{l,k,n}} can be initialized from (20b).
-The operating point for \eqn{\tilde{\mbf{m}}_{l,k,n}^{(i+1)}} is updated using as
+We have included additional information on how to choose the operating point while initializing the iterative algorithm.
+It is included in the fourth paragraph following (23).
+We have also provided a detailed discussion on how to update the operating point after each iteration in the paragraph following (23).
+Note that the objective function is convex, and therefore we can update operating point for the current step with the solution obtained in the previous iteration as
 \begin{equation}
-\tilde{\mbf{m}}_{l,k,n}^{(i+1)} = \mvec{m}{l,k,n}^{(i)} + \varphi^{(i)} \: (\mbf{m}_{l,k,n} - \mbf{m}_{l,k,n}^{(i+1)})
+\tilde{\mbf{m}}_{j}^{(i)} = \mvec{m}{j}^{(i)}
 \end{equation}
-where \eqn{\varphi^{(i)} \in (0,1]} is the step size used to update the operating variables.
-The choice of the variable \eqn{\varphi^{(i)}} can be selected such that \eqn{\sum_{i} \varphi^{(i)} = \infty} as discussed in [32].
-This information is included in the revised manuscript in the paragraph on Section III-B following after (23).
+where \eqn{\tilde{\mbf{m}}_{j}^{(i)}} denotes the operating point for the \eqn{\ith{j+1}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step and \eqn{\mbf{m}_{j}^{(i)}} is the solution obtained by solving (20) in the \eqn{\ith{j}} \ac{SCA} iteration.
 
@@
 
-	\resp We have updated the manuscript to include a discussion on the choice of selecting an algorithm for the practical purposes.
-The choice of selecting a centralized algorithm is equally fair when \eqn{N_R > 1}.
-For a single antenna receiver, the \ac{JSFRA} formulation in Section III-B is efficient, as there is no receiver update, and therefore has less complexity.
-The distributed algorithms based on primal and \ac{ADMM} schemes are favorable when \eqn{N_R = 1} due to the limited signaling between the coordinating \acp{BS}, involving the scalar interference values.
-However, when \eqn{N_R > 1}, the \ac{KKT} based distributed approach is much more efficient, since it has less signaling overhead for a given throughput.
-The choice of the \eqn{\ell_q} norm is discussed in Section II-B.
-These lines have been included in the paragraph before the Conclusions section.
-For the practical usage of the algorithms, please refer to the response for the reviewer 2's question 2 in this response document for more details involving the performance of the KKT based distributed algorithm.
+	\resp We have updated the manuscript to include a discussion on the possible conditions for selecting an algorithm for a specific implementation.
+The choice of considering a centralized approach is equally good when the number of receive antenna is greater than one, \textit{i.e.}, \eqn{N_R > 1}.
+However, in case of a single antenna receiver, the \ac{JSFRA} formulation outlined in Section III-B is more efficient than the \ac{MSE} reformulation, as there is no need for the receiver update, thereby reducing the complexity significantly.
+
+	As far as the distributed approaches are concerned, the primal and the \ac{ADMM} schemes are equally favorable when \eqn{N_R = 1} since the signaling required to be exchanged between the coordinating \acp{BS} involves only the scalar interference values.
+However, when \eqn{N_R > 1}, then the \ac{KKT} based distributed approach is more efficient than the primal or the \ac{ADMM} schemes, since it has less signaling overhead for a throughput improvement.
+The choice of selecting \eqn{\ell_q} norm is discussed in Section II-B last paragraph.
+The above information is included in the paragraph before the simulations section in Section IV.
+
+	However, if the reviewer is interested to understand the performance of the \ac{KKT} based scheme in a fading environment, please refer to the response provided for the reviewer 2, question 2 in this document for more details.
 
@@
 
-	\resp The part mentioned above has been rewritten to improve its readability as suggested by the reviewer.
-We have included the reference [28] for more illustrative discussions on the backhaul signaling.
+	\resp It has been rewritten to improve the readability as suggested by the reviewer. We have included the reference [28] for more illustrative discussions on the backhaul signaling.
 

### 2015-07-16 Report/convergence_centralized.tex
updated with nam response

@@
 	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
-	\item[(d)] Uniqueness of the minimizer, \textit{i.e}, the transmit and the receive beamformers should be unique in each iteration.
+	\item[(d)] Uniqueness of the minimizer, \textit{i.e.}, the transmit and the receive beamformers should be unique in each iteration.
 \end{itemize}
@@
 
-\subsection{Bounded Objective Function and Compact Feasible Set}
-The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
-
-The minimum value of the norm operator in the objective is zero, \textit{i.e}, \me{\|x\|_q > -\infty}, therefore it is bounded below.
-The objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
-%The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, and therefore it is coercive in the feasible set.
-%Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
-
-\subsection{Monotonicity of the Objective Sequence} \label{mcity}
-In this section, we show the nonincreasing behavior of the objective values in each \ac{SCA} and \ac{AO} update.
-Let us consider a general formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+Before proceeding further, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
 \begin{IEEEeqnarray}{RcL} \label{con} \neqsub
-	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
+	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
 	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
@@
 \end{IEEEeqnarray}
-where \me{g_2} is convex and \me{h} is a linear function.
+where \me{g_2}, \me{\hat{f}} are convex and \me{h} is a linear function.
 Let \me{g_0,g_1} be convex in either \me{\mx} or \me{\my} but not on both.
-\review{Let \eqn{f} be a strongly convex function.
-Even though the objective function in \eqref{eqn-6.1} is not strongly convex, it can be regularized with an additional quadratic term, which will be discussed in the Appendix \ref{c-a} to transform it to a strongly convex function.} The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
+The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
 Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
@@
 In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}.
-We adopt \ac{SCA} presented in \cite{lipp2014variations,lanckriet2009convergence,scutari_1} by relaxing the nonconvex set by a sequence of convex subsets.
+We adopt \ac{SCA} presented in \cite{lanckriet2009convergence,scutari_1,yang_yang} by relaxing the nonconvex set by a sequence of convex subsets.
 Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
 Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}.
+Let \eqn{\mx_k^{(i)}} denotes the stacked transmit precoders of all users at the \eqn{\ith{k}} \ac{SCA} step in the \eqn{\ith{i}} \ac{AO} iteration.
+
+\subsection{Bounded Objective Function and Compact Feasible Set}
+The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
+
+The minimum of the norm in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below.
+The objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
+%The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, and therefore it is coercive in the feasible set.
+%Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+
+\subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
+The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
+However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness is not guaranteed since there can be many solutions satisfying the constraints with the same objective value.
+Similarly, when the objective is non-zero for  \eqref{eqn-9}, the minimizer is unique, if the receivers are matched to the corresponding transmit beamformers.
+%, \textit{i.e.}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.
+
+\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as
+\begin{IEEEeqnarray}{rCl} \neqsub
+	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \\ 
+	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+\end{IEEEeqnarray}
+where \eqn{\mbf{z}} is the stacked vector of optimization variables, which can either be \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c > 0} is a positive constant to ensure strong convexity in the objective, and therefore guarantees a unique minimizer \cite{yang_yang}.
+Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}
+
+%The uniqueness of the transmit precoders and the receive beamformers for the \ac{MSE} reformulation in \eqref{eqn-mse-2} can be guaranteed in each iteration by the \ac{MSE} constraint in \eqref{eqn-mse-1.3}.
+The uniqueness of the iterates for the problem in \eqref{eqn-9} can be guaranteed in each convex subproblem if the receivers are matched to the equivalent downlink channel with the initially chosen feasible transmit precoders, \textit{i.e.}, \me{q_{l,k,n} = 0 \: \forall \, l,k,n} in \eqref{eqn-wsrm-expr} while beginning the \ac{SCA} iteration.
+%
+%When the objective is zero, the uniqueness of the transmit and the receive beamformers are not guaranteed in both problem formulations, since they are the under-estimators and need not be active at the minimum.
+To obtain a unique set of transmit precoders and the receive beamformers in all scenarios, we can regularize the objective with a strongly convex function as
+%\begin{equation}
+%\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
+%\end{equation}
+%where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant.
+The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
+%Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
+The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e.}, unitary transformations.
+When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
+To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
+
+\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
+\review{In the forthcoming discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness property.
+Note that the modified objective \eqn{f} is equivalent to \eqn{\hat{f}} upon convergence, \textit{i.e.}, when the solution is a limit point.
+Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the original objective \eqref{eqn-6.1} as \eqref{mod_obj}.}
 
@@
 \end{multline}}
-Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{i-1}} \ac{AO} iteration.
+Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{(i-1)}} \ac{AO} iteration.
 In each \ac{SCA} step, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,amir}
@@
 \end{multline}}
-Thus the sequence \me{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})} is nonincreasing and approaches a limit point of the \ac{SCA} as \me{k \rightarrow \infty}.
-The equality in \eqref{con-convergence} is achieved upon the \ac{SCA} convergence.
-The feasible point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not to be a stationary point of \eqref{con}, since it is a minimizer over the set \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}}.
-\review{Since the function \eqn{f} is strongly convex, the minimizer \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} obtained by the iterative \ac{SCA} algorithm is unique.}
+Thus the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing and approaches limit point of the \ac{SCA} as \me{k \rightarrow \infty}.
+The equality in \eqref{con-convergence} is attained upon the \ac{SCA} convergence.
+The limit point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not to be a stationary point of \eqref{con}, since it is the minimizer in \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}} only.
+\review{Since the objective is strongly convex, due to the quadratic term in \eqref{mod_obj}, the minimizer \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} in each \ac{SCA} step is unique.}
 
@@
 Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the objective follows similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is a minimizer in the set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
+The convergence and the nonincreasing behavior of the objective follows similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is the minimizer in the feasible set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
 
-Finally, to prove the global convergence of the iterative algorithm, we need to show the nonincreasing behavior of the objective function in between the \ac{AO} updates, \textit{i.e}, 
+Finally, to prove the global convergence of the iterative algorithm, we need to show the nonincreasing behavior of the objective function in between the \ac{AO} updates, \textit{i.e.}, 
 \iftoggle{single_column}{
@@
 Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by following \eqref{con-sub-set}.
-Using this, we can show the monotonicity of the objective sequence as
+Using this, we can show the monotonicity of the objective as
 \begin{equation} \label{fixed_point}
@@
 
-\subsection{Uniqueness of the Iterates and the Strong Convexity} \label{c-a}
-The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
-However when \eqn{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness of the iterates are not guaranteed since there are many solutions satisfying the constraints without affecting the objective value.
-Similarly, when the objective is non-zero for  \eqref{eqn-9}, the minimizer is unique, if the receivers are matched to the corresponding transmit beamformers, \textit{i.e}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.
+\review{Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step.
+In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj}.
+We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} iteration \cite{marks1978technical}.
+By using the strong convexity of \eqref{mod_obj}, it follows that in the \eqn{\ith{k}} update
+\begin{equation} \label{strict_monotonicity}
+f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + c \, \|\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}\|^2  \eqspace
+\end{equation}
+since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}.
+Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}.
+Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
+However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.
 
-To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations under all conditions, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized with a strongly convex function in each iteration \me{\{k+1,i\}} as
-\begin{IEEEeqnarray}{rCl} \label{mod_obj} \neqsub
-\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \\ 
-f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub
-\end{IEEEeqnarray}
-where \eqn{\mbf{z}} is the stacked vector of optimization variables, which can either be \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c} is a small positive constant to transform the original convex function \eqn{\hat{f}(\mbf{z})} into a strongly convex \eqn{f(\mbf{z})} without affecting the solution.
-\review{Therefore, the uniqueness of the minimizer in each \ac{SCA} step is ensured by the strong convexity in \eqn{f(\mbf{z})} by including the quadratic penalty term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2}, where \me{\mbf{z}^{(i)}_{k}} is the solution from the previous iteration.}
+Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update.
+Since \eqn{\iter{\mbf{z}}{\ast}{i}} is also included in the set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} strictly unless the overall sequence \eqn{\{\mbf{z}_{\ast}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}
 
-%The uniqueness of the transmit precoders and the receive beamformers for the \ac{MSE} reformulation in \eqref{eqn-mse-2} can be guaranteed in each iteration by the \ac{MSE} constraint in \eqref{eqn-mse-1.3}.
-The uniqueness of the iterates for the problem in \eqref{eqn-9} can be guaranteed in each convex subproblem if the receivers are matched to the equivalent downlink channel with the initially chosen feasible transmit precoders, \textit{i.e}, \me{q_{l,k,n} = 0 \: \forall \, l,k,n} in \eqref{eqn-wsrm-expr} while beginning the \ac{SCA} iteration.
-%
-%When the objective is zero, the uniqueness of the transmit and the receive beamformers are not guaranteed in both problem formulations, since they are the under-estimators and need not be active at the minimum.
-To obtain a unique set of transmit precoders and the receive beamformers in all scenarios, we can regularize the objective with a strongly convex function as
-%\begin{equation}
-%\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
-%\end{equation}
-%where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant.
-The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
-%Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
-The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e}, unitary transformations.
-When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
-To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
-\subsection{Strict Monotonicity of the Objective Sequence} \label{c-e}
-Due to the strong convexity of the modified objective \eqn{f(\mbf{z})}, there exist an unique minimizer in each \ac{SCA} step \eqn{k}.
-Moreover, in each \ac{SCA} step \eqn{k}, the feasible set \eqn{\mc{X}_{k}^{(i)}} includes the earlier optimal point \eqn{\mbf{z}^{(i)}_k}, therefore, the objective decreases strictly unless \eqn{\mbf{z}^{(i)}_k} is a fixed point or a limit point of the \ac{SCA} iterations \cite{marks1978technical}.
-Following the strong convexity of \eqn{f(\mbf{z})}, we have
-\begin{equation} \label{strict_monotonicity}
-f(\mbf{z}) \geq f(\mbf{z}_{\ast}^{(i)}) + \nabla f(\mbf{z}_{\ast}^{(i)}) (\mbf{z} - \mbf{z}_{\ast}^{(i)}) + c \|\mbf{z} - \mbf{z}_{\ast}^{(i)}\|^2, \forall \mbf{z}\in \mc{X}^{(i)}_\ast
-\end{equation}
-where \eqn{\mbf{z}_{\ast}^{(i)}} is a limit point as \eqn{k \rightarrow \infty} for the \eqn{\ith{i}} \ac{AO} iteration.
-The equality in \eqref{strict_monotonicity} is valid iff \eqn{\mbf{z} = \mbf{z}_{\ast}^{(i)}}.
-Strict monotonicity of \eqn{f(\mbf{z}_k^{(i)})} is ensured in the \ac{SCA} steps by the additional quadratic term, which holds with equality at the limit point \eqn{\mbf{z}_{\ast}^{(i)} \in \mc{X}_{\ast}^{(i)}}.
+\begin{comment}
 
-To ensure strict monotonicity of the objective while swapping the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration, we rely on the discussions to show the inequality \eqref{fixed_point}.
-Note that the modified objective \eqn{f} is strongly convex, and therefore has a unique minimizer in each \ac{SCA} step.
-Additionally, the feasible set \eqn{\mc{Y}_0^{(i)}} for \eqn{k=0} \ac{SCA} step with the variables \eqn{\my,\mz} includes the previous minimizer \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}}, thereby having strictly decreasing objective in \eqref{fixed_point}.
-The equality in \eqref{fixed_point} holds for the limit point \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}.
-Using the above arguments, we can ensure the strict monotonicity of the overall objective sequence.
 %Even though the original convex function \eqn{\hat{f}(\mbf{z})} can have multiple limit points upon the \ac{SCA} convergence, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point is unique, and therefore the objective decreases monotonically in a strict sense.
@@
 Similarly, using the above argument, we can also prove the strict monotonicity of the objective in each \ac{AO} update \eqn{i}, and thereby proving strict monotonicity of the overall objective sequence.
+
+{Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{k-1}} \ac{SCA} step.
+In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj}.
+We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{k}} solution \eqn{\mbf{z}^{(i)}_k} is a feasible point in \eqn{\mc{X}_{k+1}^{(i)}} of the \eqn{\ith{k+1}} iteration \cite{marks1978technical}.
+However, due to the strong convexity of \eqref{mod_obj}, it follows that \eqn{\forall \mbf{z} \in \mc{X}^{(i)}_{k}}
+	\begin{equation} \label{strict_monotonicity}
+	f(\mbf{z}) \geq f(\mbf{z}_{k}^{(i)}) + \nabla f(\mbf{z}_{k}^{(i)})^\tran (\mbf{z} - \mbf{z}_{k}^{(i)}) + c \, \|\mbf{z} - \mbf{z}_{k}^{(i)}\|^2
+	\end{equation}
+	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\rightarrow\infty}, \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}}.
+Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
+However, if \eqn{\hat{f}} is used in the objective of \eqref{con-m}, then the limit point is not unique, \textit{i.e.}, \eqn{\{\exists \mbf{z} \in \mc{X}_{\ast}^{(i)} \vert \hat{f}(\mbf{z}) = \hat{f}(\mbf{z}_{\ast}^{(i)})\}}, and therefore the sequence generated by \eqref{con-m} with \eqn{\hat{f}} is not strictly monotonic.
+
+	Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration.
+Since the limit point \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\ast}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}
+
+\end{comment}
 
@@
 \end{equation}
-Note that in each iteration \me{i}, the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant.
+Note that in each iteration \me{i}, the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e.}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant.
 Since the minimizer is unique, the mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
-In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\ast \subset \mc{F}} as the set of fixed points, \textit{i.e}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.
+In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\ast \subset \mc{F}} as the set of fixed points, \textit{i.e.}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.
 
@@
 \item Feasible set \me{\iter{\mc{X}}{\ast}{i},\iter{\mc{Y}}{\ast}{i}} in each step should be compact.
-\item The sequence \me{\{\iterate{\ma}{i}\}} generated by \me{\mc{A}} should be strictly monotonic with respect to the objective \me{f}, \textit{i.e}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
+\item The sequence \me{\{\iterate{\ma}{i}\}} generated by \me{\mc{A}} should be strictly monotonic with respect to the objective \me{f}, \textit{i.e.}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
 \end{itemize}
-\review{Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity is guaranteed from Section \ref{c-e} with modified objective in \eqref{mod_obj}}.
+\review{Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity is guaranteed from Section \ref{mcity} with modified objective \eqref{mod_obj}}.
 Using \cite{zangwill1969nonlinear} and \cite[Th.
-3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
-Even though the fixed points in the set \me{\mc{F}^\ast} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e}, \me{\mc{F}^\ast = \{\ma^\ast\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
+3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
+Even though the fixed points in the set \me{\mc{F}^\ast} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e.}, \me{\mc{F}^\ast = \{\ma^\ast\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
 
 \begin{comment}
-and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
+and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e.}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
 The set of accumulation or the limit points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
@@
 \item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
-\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
+\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
 \end{itemize}
@@
 where \me{\mc{A}(\iterate{\ma}{i})} denotes the set of iterates in the subset \me{\iterate{\mc{X}}{i}}, which has the same objective value under the mapping \me{f} in the \me{\ith{i}} iteration The monotonicity of the proposed algorithm is guaranteed based on the arguments presented in Appendix \ref{mcity}.
-The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e}, \me{\ma \notin \mc{F}^\ast}, as in \eqref{fixed_point}.
+The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e.}, \me{\ma \notin \mc{F}^\ast}, as in \eqref{fixed_point}.
 Using the above discussions, we can show that the sequence \me{\{\iterate{\ma}{i}\}} converges to a fixed point in the set \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}
@@
 \subsection{Stationary Points of the Nonconvex Problem}
-Let \eqn{\ma^{\ast}} be the limit point of the sequence \eqn{\{\iterate{\ma}{i}\}} of iterates generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}.
-The limit point \eqn{\ma^\ast} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions of \eqn{con}.
-Let us consider the approximate problem in \eqref{con-m}.
-The feasible set \eqn{\mc{X}_{k}^{i}} and  \eqn{\mc{Y}_{k}^{i}} in each iteration \eqn{\{k,i\}} has a nonempty interior and by using \eqref{con-relax}, the feasible set in each iteration obeys \eqn{\mc{X}_{k}^{i} \subset \mc{F}}.
-Therefore, all the iterates \eqn{\{\iterate{\ma}{i}\}} found by \eqn{\mc{A}} are feasible.
-By the strong convexity of \eqn{f(\ma)}, we have
-\begin{IEEEeqnarray}{rl}  \neqsub \label{strong_cvxty}
-&(\ma^{(i)} - \ma^{(i+1)}) \nabla {f}(\ma^{(i+1)}) \geq 0 \eqsub \\
-&f(\ma^{(i)}) - f(\ma^{(i+1)}) \geq c \: \|\ma^{(i)} - \ma^{(i+1)}\|^2. \eqsub
+\review{So far, we have shown that the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point as \eqn{i \rightarrow \infty}.
+To show that \eqn{\ma^{\ast}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem \eqref{con}, \textit{i.e.},
+\begin{equation} \label{kkt_expr}
+\textstyle	\nabla \hat{f}(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla {g}_0(\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0
+\end{equation}
+for some multipliers \eqn{\mu_i \geq 0} and lies in the feasible set \eqn{\ma^{\ast} \in \mc{F}}.
+
+Now, to prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
+Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications.
+Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}, therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
+\begin{equation} \label{kkt_mod_expr}
+\textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
+\end{equation}
+The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}.
+Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfies \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}.
+(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the \ac{DC} constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
+\begin{equation} \label{rhs_equiv}
+\nabla h(\ma^{\ast}) - \nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla h(\ma^{\ast}) - \nabla g_o(\mbf{\ma}^{\ast}).
+\end{equation}
+Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}.
+By using \cite[Th.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that the limit point of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of \eqref{con}.}
+
+\begin{comment}
+In this section, we show that the limit point \eqn{\ma^{\ast}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
+In order for \eqn{\ma^{\ast}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
+Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\ast^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\ast}} satisfies the constraint qualifications of the problem \eqref{con}.
+
+To show that the limit point \eqn{\mbf{\ma}^{\ast}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\ast}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
+Therefore, it satisfies the \ac{KKT} conditions of the convex subproblem for some Lagrange multipliers \eqn{\mu_i \geq 0} as
+\begin{equation} \label{kkt_expr}
+\textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
+\end{equation}
+It is evident that the modified objective \eqn{f} and the convex function \eqn{\hat{f}} in \eqref{mod_obj} are equal at the limit point due to the vanishing quadratic penalty term.
+Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla g_o(\mbf{\ma}^{\ast})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\ast}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
+Now, by using \cite[Th.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that all the limit points of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
+
+\review{Let \eqn{\ma^{\ast}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}.
+The limit point \eqn{\ma^\ast} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions.
+%and there exists no descent direction in the feasible set as
+%\begin{equation}
+%\nabla {f}(\ma^{\ast})^\tran \, (\ma - \ma^{\ast}) \geq 0, \: \forall \, \ma \in \mc{Y}^{\ast}
+%\end{equation}
+%where \eqn{\mc{Y}^{\ast}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\ast}^{i}} as \eqn{i \rightarrow \infty}. 
+Let us consider the problem in \eqref{con-m}.
+Using \eqref{con-relax}, we can show that the feasible set \eqn{\mc{Y}_{\ast}^{i}} in each \ac{AO} iteration \eqn{i} is a subset of \eqn{\mc{F}}.
+Therefore, all iterates \eqn{\{\iterate{\ma}{i}\}} of the algorithm \eqn{\mc{A}} are feasible.
+Additionally, by the strong convexity of \eqn{f(\ma)}, following conditions are satisfied.
+\begin{IEEEeqnarray}{rCl}  \neqsub \label{strong_cvxty}
+\nabla {f}(\ma^{(i)})^\tran \, (\ma^{(i-1)} - \ma^{(i)}) &\geq& 0 \eqsub \\
+f(\ma^{(i-1)}) - f(\ma^{(i)}) &\geq& c \: \|\ma^{(i-1)} - \ma^{(i)}\|^2. \eqsub
 \end{IEEEeqnarray}
-Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \ma^{(i+1)}\| \rightarrow 0} as the objective converges and \eqn{\ma^{(i+1)} \rightarrow \ma^{\ast}} as \eqn{i \rightarrow \infty}.
+Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \mc{A}(\ma^{(i)})\| \rightarrow 0} as \eqn{i \rightarrow \infty}, which is the limit point of the algorithm \eqn{\mc{A}}.
 
-To show that \eqn{\ma^{\ast}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem \eqref{con}.
-Let us consider \eqn{\mc{Y}_{\ast}^{\ast}} as the feasible set of \eqref{con-m} upon convergence, containing \eqn{\ma^{\ast}}.
-The \ac{KKT} conditions at \eqn{\ma^{\ast}} is given by
+Now, it remains to show that the \eqn{\ma^{\ast}} is a stationary point of the nonconvex problem \eqref{con}.
+To see this, we note that \eqn{\ma^{\ast}} must satisfy the \ac{KKT} conditions of \eqref{con}.
+Since \eqn{\ma^{\ast}} is the fixed point of the algorithm \eqn{\mc{A}}, it satisfies the \ac{KKT} conditions of the convex subproblem \eqref{con-m} given by
 \begin{equation} \label{kkt_expr}
@@
 for some Lagrange multipliers \eqn{\mu_i \geq 0}.
-Using \eqn{\hat{f}(\ma^{\ast}) = f(\ma^{\ast})} and \eqref{con-relax} in \eqref{kkt_expr}, we can see that \eqref{kkt_expr} is indeed the \ac{KKT} condition for the nonconvex problem \eqref{con}.
+Using the equivalence between \eqn{\hat{f}(\ma^{\ast}) = f(\ma^{\ast})} and the relation in \eqref{con-relax} in \eqref{kkt_expr}, we can see that \eqref{kkt_expr} is indeed the \ac{KKT} condition for the nonconvex problem \eqref{con}.
 Since the gradient is zero in \eqref{kkt_expr}, the objective cannot be decreased any further.
@@
 2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that the limit points \eqn{\ma^\ast} of \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
+3.2]{amir}, we can show that the limit points \eqn{\ma^\ast} of \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.}
 
@@
 Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}.
-Moreover, \eqn{\ma^{\ast}} is a regular point \textit{i.e} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}.
+Moreover, \eqn{\ma^{\ast}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}.
 Now, with the above conditions and by using \cite[Th.
@@
 2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
+
+ In this section, we show that the limit point \eqn{\ma^{\ast}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
+In order for \eqn{\ma^{\ast}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
+Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\ast^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\ast}} satisfies the constraint qualifications of the problem \eqref{con}.
+
+ To show that the limit point \eqn{\mbf{\ma}^{\ast}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\ast}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
+Therefore, it satisfies the \ac{KKT} conditions of the convex subproblem for some Lagrange multipliers \eqn{\mu_i \geq 0} as
+ \begin{equation} \label{kkt_expr}
+ \textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
+ \end{equation}
+ It is evident that the modified objective \eqn{f} and the convex function \eqn{\hat{f}} in \eqref{mod_obj} are equal at the limit point due to the vanishing quadratic penalty term.
+Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\ast};\iterate{\ma}{\ast}) = \nabla g_o(\mbf{\ma}^{\ast})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\ast}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
+Now, by using \cite[Th.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that all the limit points of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
+
 \end{comment}

### 2015-07-16 Report/convergence_distributed.tex
half cooked
updated with nam response

@@
 Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence.
-Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem can be guaranteed as the iteration index \me{i \rightarrow \infty} for a diminishing step size \cite{bertsekas1999nonlinear}.
+Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem is guaranteed as \me{i \rightarrow \infty} for a diminishing step size as shown in \cite{scutari_1},\cite[Prop 8.2.6]{bertsekas2003convex}.
 
@@
 \begin{IEEEeqnarray}{rCl} \neqsub
-	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{y}) \eqsub \\
+	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
 	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
@@
 Therefore, by following \cite[Prop.
-4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.
+4.2]{bertsekas1989parallel}, it can be shown that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size as discussed in \cite{boyd2011distributed}.
 The distributed algorithms also converges to a stationary point of the original nonconvex problem by following Appendix \ref{sec-3.5}, if the \ac{ADMM} is iterated until convergence in each \ac{SCA} step.}
@@
 However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
-Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
-Therefore, it is difficult to prove the convergence of the Algorithm \ref{algo-4} to a stationary point of the original nonconvex problem in \eqref{eqn-mse-1}.
-Even though the convergence is not theoretically guaranteed, it converges in all numerical experiments considered in Section \ref{sec-5.2}.
+\review{Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
+Therefore, the convergence of the Algorithm \ref{algo-4} to a stationary point of \eqref{eqn-mse-1} is not guaranteed.
+In addition, due to the convexity of the objective in \eqref{eqn-mse-1}, the sequence of iterates generated by Algorithm \ref{algo-4} need not be a convergent one.} However, the objective converges in all numerical experiments considered in Section \ref{sec-5.2}.
 

### 2015-07-16 Report/decomposition_solutions.tex
updated with nam response

@@
 
-To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
-Following an approach similar to the one presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference from all \acp{BS} in \me{\bar{\mc{B}}_{b_k}} as
+To begin with, let \me{\bar{\mc{B}}_b} be the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
+Following an approach similar to the one presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be
+expressed by stacking the interference from all \acp{BS} in \me{\bar{\mc{B}}_{b_k}} as
 \iftoggle{single_column}{

### 2015-07-16 Report/joint_wsrm_formulation.tex
updated with nam response

--- 2015-06-23 Report/joint_wsrm_formulation.tex
@@
-The queue minimizing algorithms have been studied extensively in the networking literature to provide congestion-free routing between any two nodes in the network.
-One such algorithm is the \emph{backpressure algorithm} \cite{tassiulas,georgiadis2006resource,neely2010stochastic}.
-It finds an optimal control policy in the form of rate or resource allocation by considering the differential backlogged packets between the source and the destination nodes for the networking entities.
+The queue minimizing algorithms have been studied extensively in the networking context to provide congestion-free routing between any two nodes in the network.
+One such is the \emph{backpressure algorithm} \cite{georgiadis2006resource,neely2010stochastic}.
+It finds an optimal control policy in the form of rate or resource allocation by considering differential backlogged packets between any two entities.
 %Even though the algorithm is primarily designed for the wired infrastructure, it can be extended to the wireless networks by designing the user rate variable \me{t_k} in accordance to the wireless network.
 
-The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the downlink \ac{MIMO}-\ac{OFDM} framework, in which the multiple \acp{BS} act as the source nodes and the user terminals as the receiver nodes.
+The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the downlink \ac{MIMO}-\ac{OFDM} framework, in which the \acp{BS} acts as the source nodes and the users as the receivers.
 The control policy in the form of transmit precoders aims at minimizing the number of queued packets waiting in the \acp{BS}.
-In order to find the optimal strategy, we resort to the Lyapunov theory, which is predominantly used in the control theory to achieve system stability.
-Since at each time slot, the system is described by the channel conditions and the number of backlogged packets of each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves toward the undesirable state.
-By following \cite{neely2010stochastic}, the scalar measure for the queue stability is given by
+To find an optimal strategy, we resort to the Lyapunov theory, which is predominantly used in control theory to achieve system stability.
+Since at each time slot, the system is described by the channel conditions and the number of backlogged packets for each user, the Lyapunov function is used to provide a scalar measure, which grows large when the system moves towards an undesirable state \cite{neely2010stochastic}.
+The scalar measure for queue stability is given by
 \begin{equation}
@@
 \end{equation}
-where \me{\mbf{Q}(i) = \sset{Q_1(i),Q_2(i),\dotsc,Q_K(i)}^\mathrm{T}} and \me{\tfrac{1}{2}} is used for the convenience.
-It provides a scalar measure of congestion present in the system \cite[Ch.
-3]{neely2010stochastic}.
+where \me{\mbf{Q}(i) = \sset{Q_1(i),Q_2(i),\dotsc,Q_K(i)}^\mathrm{T}}. It provides a scalar measure of congestion in the system \cite[Ch. 3]{neely2010stochastic}.
 
@@
 \end{multline}}
-In order to eliminate the nonlinear operator \me{[x]^+}, we bound the expression in \eqref{eqn-3.1} as
+To eliminate the nonlinear operator \me{[x]^+}, we bound \eqref{eqn-3.1} as
 \begin{equation}
@@
 \end{IEEEeqnarray}}
-where the subscripts \me{\mbf{t}} and \me{\mbfa{\lambda}} represents the vector formed by stacking the transmission and the arrival rate of all users in the system.
-Since the transmission and the arrival rates are bounded, the second order moments in the first term of \eqref{backpressure-approx-1b} can be bounded by a constant \me{B} without affecting the optimal solution of the problem \cite{neely2010stochastic}.
-The second term in \eqref{backpressure-approx-1b} follows from the Poisson arrival process.
+where \me{\mbf{t}} and \me{\mbfa{\lambda}} are the vectors formed by stacking the transmission and the arrival rate of all users.
+Since they are bounded, the second order moments on the first term in \eqref{backpressure-approx-1b} can be bounded by a constant \me{B} without affecting the optimal solution \cite{neely2010stochastic}.
+The second term in \eqref{backpressure-approx-1b} follows the Poisson arrivals.
 
 The expression in \eqref{backpressure-approx} looks similar to the \ac{WSRM} formulation if the weights in the \ac{WSRM} problem are replaced by the numbers of backlogged packets of the corresponding users.
-The above approach was extended for the wireless networks in \cite{weeraddana2011resource}, in which the queues were used as weights in the \ac{WSRM} formulation to determine the transmit precoders.
+The above approach was extended to the wireless networks in \cite{weeraddana2011resource}, in which the queues were used as weights in the \ac{WSRM} formulation to determine the transmit precoders.
 Since the expectation is minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
 \begin{IEEEeqnarray}{LCl} \label{q_gen_sum} \neqsub
-\underset{\substack{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \left ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \right ) \IEEEyessubnumber \label{eqn-3.1.1} \\
+\underset{\substack{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \Big ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \Big ) \IEEEyessubnumber \label{eqn-3.1.1} \\
 \text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \fall b.

### 2015-07-16 Report/kkt_mse_approach.tex
updated with nam response

@@
 
-In the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without additional rate constraints.
-However, due to the non-differential objective, the \ac{KKT} conditions cannot be formulated.
-The non-differentiability is due to the absolute operator present in the norm function.
-To make the objective differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the solution, namely,
+In the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints.
+However, the \ac{KKT} conditions cannot be formulated due to the non-differentiability of the absolute value operator present in the objective function.
+In order to make the objective function differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the optimal solution, namely,
 \begin{itemize}
@@
 \sigma_{l,k,n}^{(i)} &=& \left [\tfrac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right ]^+  \IEEEyessubnumber \label{kkt-mse-4.2} \\
-\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1}
+\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho^{(i)} \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1}
 \end{IEEEeqnarray}
@@
 	\sigma_{l,k,n}^{(i)} =& \Big [\tfrac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\Big ]^+  \IEEEyessubnumber \label{kkt-mse-4.2} \\
-	\alpha^{(i)}_{l,k,n} =& \alpha^{(i-1)}_{l,k,n} + \rho \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1}
+	\alpha^{(i)}_{l,k,n} =& \alpha^{(i-1)}_{l,k,n} + \rho^{(i)} \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \IEEEyessubnumber \label{kkt-mse-4.1}
 \end{IEEEeqnarray}}
@@
 So, \me{\alpha^{(i)}} is fixed to evaluate \me{\sigma^{(i)}} using \eqref{kkt-mse-4}.
-At each iteration, the dual variables \me{\alpha^{(i)}} are linearly interpolated with any point between the fixed iterate \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} using a step size \me{\rho \in (0,1)}.
-The choice of \me{\rho} depends on the system model and it affects the convergence behavior.
-It reduces the oscillations in the objective function when \me{\sigma^{(i)}} is negative due to over-allocation.
+At each iteration, the dual variables \me{\alpha^{(i)}} are linearly interpolated with any point between the fixed iterate \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} using a diminishing or a fixed step size \me{\rho^{(i)} \in (0,1)}.
+The choice of \eqn{\rho^{(i)}} affects the convergence behavior and also controls the oscillations in the users rate when \me{\sigma^{(i)}} is negative due to over-allocation.
 
@@
 
-To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which includes the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling.
+To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channels \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which includes the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling.
 We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the current problem as follows.
-After receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user evaluates the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify them to the \acp{BS} via uplink precoded pilots.
-On receiving pilot signals, \acp{BS} update the \ac{MSE} in \eqref{mse-error} as
+Upon receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user will evaluate the \ac{MMSE} receiver \eqref{kkt-mse-4.6} and notify to all \acp{BS} by using precoded uplink pilots.
+On receiving the pilots, each \ac{BS} update the \ac{MSE} in \eqref{mse-error} as
 \begin{equation}
@@
 
-To avoid the back-haul exchanges between the \acp{BS}, as an alternative approach, users perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users.
-Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}}.
-The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
-After receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
+To avoid the back-haul exchanges between the \acp{BS}, as an alternative approach, users can perform all the processing required and \acp{BS} will update the precoders based on the feedback from all the users.
+Upon receiving the transmit precoders from the \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}}.
+Then, the updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilots with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
+Upon receiving the precoded uplink pilots, each \ac{BS} evaluate the effective channels \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} to update the transmit precoders using \eqref{kkt-mse-4.3}, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
 Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling with the precoded pilots for the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.

### 2015-07-16 Report/mse_formulation.tex
updated with nam response

--- 2015-06-27 Report/mse_formulation.tex
@@
 			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
-			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
+			update \me{\tilde{\mbf{u}}_{l,k,n}} and the constraint set \eqref{eqn-8} with the newly found \me{\mvec{m}{l,k,n}} and \me{\mvec{\beta}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
 			$j = j + 1$\;

### 2015-07-16 Report/problem_formulation.tex
updated with nam response

--- 2015-03-19 Report/problem_formulation.tex
@@
 The problem defined in \eqref{q_gen_sum} ignores the second order term arising from the Lyapunov drift minimization objective by limiting it to a constant value.
-\review{In fact, using \me{\ell_{q=2}} in \eqref{eqn-4.2}, we obtain the following objective
+In fact, by using \me{\ell_{q=2}} norm in \eqref{eqn-4.2}, we obtain the objective function, similar to \eqref{q_gen_sum} as
 \begin{equation}\label{pf-1}
@@
 \end{equation}
-which is similar to the objective in \eqref{q_gen_sum}.
-It is achieved either by removing \me{t_k^2} from \eqref{pf-1} or when the total number of queued packets is large for all users such that \me{t_k^2} has no impact on the objective function.}
+The equivalence is achieved by either removing \me{t_k^2} from \eqref{pf-1} or when the number of queued packets is large enough.
 
-By limiting \me{t_k^2} with a constant value, the \ac{Q-WSRM} formulation requires an explicit rate constraint \eqref{eqn-3.1.4} to avoid over-allocation of the available resources.
-In the proposed queue deviation formulation, the explicit rate constraint is not needed, since it is handled by the objective function \eqref{eqn-4.2} itself.
-It makes the problem simpler and allows us to employ efficient algorithms to distribute the precoder design problem across each \ac{BS} independently with minimal information exchange \cite{boyd2011distributed}.
+By ignoring \me{t_k^2} from \eqref{pf-1}, the \ac{Q-WSRM} scheme requires an explicit rate constraint \eqref{eqn-3.1.4} to avoid over-allocation of the resources.
+In the proposed queue deviation approach, explicit rate constraints are not needed, since they are handled by the objective function \eqref{eqn-4.2} itself.
 In contrast to the \ac{WSRM} formulation, the \ac{JSFRA} and the \ac{Q-WSRME} problems handle the sub-channels jointly to obtain an efficient allocation by identifying the optimal space-frequency resources for the users.

### 2015-07-16 Report/queue_minimizing_intro.tex
updated - final - draft
updated
updated with nam response

@@
 At the end, we discuss a low complex solution for the \ac{JSFRA} problem by limiting the precoder design over each sub-channel at a given instant.
-
-\review{In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is difficult due to its nonconvex nature}.
+In general, the precoder design for the \ac{MIMO} \ac{OFDM} problem is difficult due to its nonconvex nature.
 In addition, the objective of minimizing the number of the queued packets over space-frequency dimensions adds further complexity.
-Since the scheduling of users in each sub-channel attained by allocating zero transmit power over certain sub-channels, our solutions perform joint precoder design and user scheduling.
+Since the scheduling of users in each sub-channel is achieved by allocating zero transmit power over certain sub-channels, our solutions perform joint precoder design and user scheduling.
 Before discussing the proposed solutions, we consider the existing algorithm to minimize the number of backlogged packets with additional constraints required by the problem.

### 2015-07-16 Report/sub_channel_wsrm.tex
updated with nam response

@@
 As an alternative sub-optimal solution, we present a \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
-The sharing of power can be either equal or based on predetermined pattern as in partial frequency reuse with \eqn{\sum_{i=1}^N P_{\max,i} = P_{\max}}.
-Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel in a sequential manner with the sub-channel specific total power constraint \me{P_{\max,i}} and the number of backlogged packets.
-Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} before solving for the precoders specific to the sub-channel \me{i}.
+The power sharing can either be equal or based on some predetermined limits on each sub-channel as in partial frequency reuse as
+\begin{equation}
+\sum_{i=1}^N P_{\max,i} = P_{\max}.
+\end{equation}
+Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel sequentially with \me{P_{\max,i}} and the residual number of backlogged packets.
+Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} while determining the precoders for the \eqn{\ith{i}} sub-channel.
 Since the precoder design is sequential, \textit{i.e}, the precoders are designed for sub-channels \me{[0,i-1]} before \me{\ith{i}} sub-channel, the number of backlogged packets for the initial sub-channel is initialized as \me{Q_{k,1} = Q_k}.

### 2015-07-16 Report/system_model.tex
updated with nam response

@@
 We adopt linear transmit beamforming technique at \acp{BS}.
-Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted.
+Specifically, the data symbols \me{d_{l,k,n}} for  user \me{k} on the \me{\ith{l}} spatial stream over sub-channel \me{n} is multiplied with beamformer \me{\mvec{m}{l,k,n} \in \mathbb{C}^{N_T \times 1}} before being transmitted.
 In order to detect  multiple spatial streams at the user terminal, receive beamforming vector \me{\mvec{w}{l,k,n}} is employed for each user.
-Consequently, the received data estimate corresponding to the \me{l^\mathrm{th}} spatial stream over sub-channel \me{n} at user $k$ is given by
+Consequently, the received data estimate corresponding to the \me{\ith{l}} spatial stream over sub-channel \me{n} at user $k$ is given by
 \iftoggle{single_column}{
@@
 }
-where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{n^\mathrm{th}} sub-channel and \me{l^\mathrm{th}} spatial stream.
+where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{\ith{n}} sub-channel and \me{\ith{l}} spatial stream.
 In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams.\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users.
@@
 Let \me{Q_k} be the number of backlogged packets destined for user \me{k} at a given scheduling instant.
-The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{{i}^\mathrm{th}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{{(i+1)}^\mathrm{th}} instant for user \me{k}, denoted as \me{Q_k(i+1)}, is given by
+The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{\ith{i}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{\ith{(i+1)}} instant for user \me{k}, denoted as \me{Q_k(i+1)}, is given by
 \begin{equation}

### 2015-07-16 Report/wsrm_formulation.tex
updated with nam response

--- 2015-06-27 Report/wsrm_formulation.tex
@@
 \begin{IEEEeqnarray}{l}
-f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
+g({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}}
 \end{IEEEeqnarray}
-be a function, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector to be identified for the optimal allocation.
-Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}.
-By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.
+be a function, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{m}{l,k,n}, \mvec{w}{l,k,n},\beta_{l,k,n}\}} denotes the variables to be identified for an efficient allocation.
+Note that the function \me{g({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
+The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{g({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}.
+By using the reduced convex subset for \eqref{eqn-6.2}, the problem in \eqref{eqn-6} is solved iteratively by updating the operating point in each iteration.
 
@@
 \end{IEEEeqnarray}
-and hence \me{f({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}.\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notation and not the newly introduced optimization variables.
-In CVX \cite{grant2008cvx}, for example,  we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.} Suppose that the current value of \me{p_{l,k,n}} and \me{q_{l,k,n}} at a specific iteration are \me{\tilde{p}_{l,k,n}} and \me{\tilde{q}_{l,k,n}}, respectively.
-Using first order Taylor approximation around the local point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, we can approximate \eqref{eqn-6.2} by the following linear inequality
+and hence \me{g({\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}.\footnote{Note that \me{p_{l,k,n}} and \me{q_{l,k,n}} are just symbolic notations.
+In CVX \cite{grant2008cvx}, for example, we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.} Let \eqn{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\tilde{\mbf{m}}_{l,k,n}, \tilde{\mbf{w}}_{l,k,n},\tilde{\beta}_{l,k,n} \}} be a minimizer from the previous \ac{SCA} iteration.
+Using the first order Taylor approximation around the operating point \eqn{\tilde{\mbf{u}}_{l,k,n}}, we can approximate \eqref{eqn-6.2} as
 \iftoggle{single_column}{
@@
 }
-In summary, for fixed linear receiver \me{\mvec{w}{l,k,n}} and operating point \me{ [ \, \tilde{p}_{l,k,n},\tilde{q}_{l,k,n},\tilde{\beta}_{l,k,n} \, ]^T}, the relaxed convex subproblem to find transmit beamformers is given by
+In summary, for fixed receivers \me{\tilde{\mbf{w}}_{l,k,n}} and \me{\tilde{\mbf{u}}_{l,k,n}}, the relaxed convex subproblem for finding transmit precoders is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-9} \neqsub
 \underset{\substack{\mvec{m}{l,k,n},\\ \gamma_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9.1a} \vspace{-0.15cm} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
+\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\tmvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9.1c} \\
 & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b \IEEEyessubnumber \label{eqn-9.1d} \\
@@
 
-Now, the optimal linear receivers for fixed transmit precoders \me{\mbf{m}_{j,i,n} \, \forall i \in \mc{U}, \, \forall n \in \mc{C}} are obtained by minimizing \eqref{eqn-6} with respect to \me{\mbf{w}_{l,k,n}} as
+Now, the optimal receivers for fixed transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} are obtained by minimizing \eqref{eqn-6} w.r.t. \me{\mbf{w}_{l,k,n}} as
 \begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub
 \underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
-\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
+\text{subject to} & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \tmvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-9--1.1c} \\
 & \quad & \text{and } \eqref{eqn-8}. \IEEEyessubnumber \label{eqn-9--1.1e}
 \end{IEEEeqnarray}
-Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for the receiver \me{\mbf{w}^{o}_{l,k,n}} as
+Solving \eqref{eqn-9--1} using the \ac{KKT} conditions, we obtain the following iterative expression for an optimal receiver \me{\mbf{w}^{o}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl} \neqsub
-\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\mbf{m}}_{j,i,n} {\mbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
-\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\mbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
+\mvec{{A}}{l,k,n} &=& \displaystyle \sum_{\mathclap{(j,i)\neq (l,k)}} \mvec{H}{b_i,k,n} {\tmbf{m}}_{j,i,n} {\tmbf{m}}_{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \\
+\mvec{w}{l,k,n}^{(i)} &=& \left ( \tfrac{\tilde{\beta}_{l,k,n} {\tmbf{m}}_{l,k,n}^\herm \mvec{H}{b_k,k,n}^\herm \mbf{w}_{l,k,n}^{(i-1)} }{\|\mvec{w}{l,k,n}^{(i-1)} \mvec{H}{b_k,k,n} {\mbf{m}}_{l,k,n} \|^2} \right )\mvec{{A}}{l,k,n}^{-1}\mvec{H}{b_k,k,n} {\tmbf{m}}_{l,k,n} \IEEEyessubnumber \eqspace \label{opt-rx}
 \end{IEEEeqnarray}
@@
 The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations.
-Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function.
-The dependency is implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which depend on the value of the exponent \me{q}.
+Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective.
+The dependency is implied by the precoders \me{\mvec{m}{l,k,n}}, which depends on the exponent \me{q}.
 
 It can be seen that the optimal receiver in \eqref{opt-rx} is in fact a scaled version of the \ac{MMSE} receiver, which is given by
-\allowdisplaybreaks{
 \begin{IEEEeqnarray}{rCl} \neqsub
-\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \mvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
-\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
-\end{IEEEeqnarray}}
+\mvec{R}{l,k,n} &=& \displaystyle \sum_{i\in \mc{U}} \sum_{j=1}^L \mvec{H}{b_i,k,n} \tmvec{m}{j,i,n} \tmvec{m}{j,i,n}^\herm \mvec{H}{b_i,k,n}^\herm + N_0 \, \mathbf{I}_{N_R} \IEEEyessubnumber \eqspace \\
+\mvec{w}{l,k,n} &=& \mathbf{R}^{-1}_{l,k,n} \; \mvec{H}{b_k,k,n} \; \tmvec{m}{l,k,n}. \IEEEyessubnumber \label{eqn-10}
+\end{IEEEeqnarray}
 Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance.
 
-The proposed subproblems in \eqref{eqn-9} and \eqref{eqn-9--1} are solved iteratively by updating the operating point from the previous iteration.
-The iterative algorithm is referred as \acl{QM} \ac{JSFRA} scheme, and it is outlined in Algorithm \ref{algo-1}.
-\review{The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is updated using \eqref{eqn-9.1c} with the chosen transmit precoders and the receivers.} For a fixed receiver \me{\mvec{w}{l,k,n}}, the \ac{SCA} iteration is carried out until convergence or for predefined number of iterations, say, \me{J_{\max}} to find an optimal transmit precoders \me{\mvec{m}{l,k,n}}.
-Next, the receivers are updated based on either \eqref{opt-rx} or \eqref{eqn-10} using the fixed transmit precoders \me{\mvec{m}{l,k,n}}.
-The iterative procedure is performed until convergence or for fixed number of iterations \me{I_{\max}} as shown in Algorithm \ref{algo-1}.
+\review{The proposed solution involves two nested iterations, \textit{i.e.}, one for the outer \ac{AO} loop denoted by \eqn{i} and the second for the inner \ac{SCA} loop represented by \eqn{j}.
+Each \ac{AO} loop involves two \ac{SCA} approaches performed until convergence, \textit{i.e.}, at first, the transmit precoders are identified by solving \eqref{eqn-9} iteratively for fixed receivers.
+In the second step, the receivers are updated with the previously found fixed transmit precoders by either solving \eqref{opt-rx} recursively or using the \ac{MMSE} receiver in \eqref{eqn-10}.
+
+Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}.
+Let \eqn{\{\mbf{m}^{(i)}_j, \mbf{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{j-1}} \ac{SCA} step.
+In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{j+1}} \ac{SCA} step is given by \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the optimal receiver obtained by solving \eqref{opt-rx} recursively or by using \eqref{eqn-10} from the \eqn{\ith{i-1}} \ac{AO} step.
+The \ac{SCA} updates are performed until \eqn{j \rightarrow \infty} or for \eqn{J_{\max}} number of iterations.
+
+Upon convergence of the transmit precoders, the receivers are updated in a similar manner by solving \eqref{eqn-9--1} recursively until \eqn{j \rightarrow \infty} or by using the \ac{MMSE} receiver in \eqref{eqn-10} with the fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\ast}} obtained from the previous \ac{SCA} step.
+Once the receivers are obtained, the transmit precoders are again updated by solving \eqref{eqn-9} recursively with the newly found receivers fixed for an operating point.
+The above procedure is repeated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations.
+The overall iterative approach is outlined in Algorithm \ref{algo-1}.
+
+The initial feasible points \me{\tilde{\mbf{u}}_{l,k,n}} are obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is obtained by evaluating \eqref{eqn-9.1c} with the preinitialized transmit precoders and the receive beamformers of all the users in the system.
+
+Even though the iterative approach in Algorithm \ref{algo-1} converges in all our numerical simulations, in order to ensure the theoretical convergence of the iterates to a stationary point, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of \eqref{eqn-6.1} due to better convergence properties.
+The convergence analysis is given in Appendix \ref{sec-3.5}.}
+\begin{comment}
+
+Let \eqn{i} be the \ac{AO} iteration count and let \eqn{j} denotes the \ac{SCA} index.
+To find the transmit precoders, \eqref{eqn-9} is solved recursively by updating the \eqn{\ith{j}} \ac{SCA} operating point \eqn{\tmbf{x}_{j}^{(i)} \triangleq \{ \tmbf{m}_{j}^{(i)},\tmbf{\beta}_{j}^{(i)} \}} in the \eqn{\ith{i}} \ac{AO} iteration for fixed receivers \eqn{\tmbf{w}} as \eqn{\tmbf{x}_{j}^{(i)} = \mbf{x}_{j}^{(i)}}, where \eqn{\mbf{x}_{j}^{(i)} \triangleq \{ \mbf{m}_{j}^{(i)},\mbf{\beta}_{j}^{(i)} \}} is the solution for the problem \eqref{eqn-9} in the \eqn{\ith{j-1}} \ac{SCA} step.\footnote{We can also update the operating point as \eqn{\tmbf{x}_{j}^{(i)} = \tmbf{x}_{j-1}^{(i)} + \rho_{j} (\mbf{x}_{j}^{(i)} - \tmbf{x}_{j-1}^{(i)})}, where \eqn{\rho_j \in (0,1]} is the step size as discussed in \cite{scutari_1,yang_yang}.} The iterative update is performed until \eqn{j \rightarrow \infty} or for \eqn{J_{\max}} number of iterations.
+Let \eqn{\tmbf{m}^{(i)}} be the transmit precoders obtained by \eqref{eqn-9} upon convergence in the \eqn{\ith{i}} \ac{AO} step with fixed receivers \eqn{\tmbf{w}^{(i-1)}}.
+Now, for the fixed transmit precoders, the receivers are determined either by solving \eqref{opt-rx} iteratively or by using \eqref{eqn-10}.
+The above procedure is iterated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations.
+Algorithm \ref{algo-1} outlines this procedure.
+
+To begin the iterative procedure, the initial feasible points \me{\tilde{\mbf{u}}_{l,k,n}} are obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is obtained by evaluating \eqref{eqn-9.1c} with the initialized transmit precoders and the receive beamformers of all the users in the system.
 The convergence analysis is given in Appendix \ref{sec-3.5}.
-\begin{comment}
+Even though the objective sequence in Algorithm \ref{algo-1} converges in all our simulations, in order to theoretically ensure the convergence of the iterates to a \ac{KKT} point, we consider a modified objective in \eqref{mod_obj} instead of \eqref{eqn-6.1}.
+
 \subsubsection*{Convergence}

### 2015-07-16 Response/Response 2/additions.tex
updated with nam response

--- 2015-06-27 Response/Response 2/additions.tex
@@
 \item We have shortened the discussions on the existing \textit{backpressure algorithm} in Section III-A.
-\item Strong convexity of the objective function is emphasized in Appendix A-C.
-\item Strict Monotonicity of the algorithm is discussed separately in Appendix A-D with more clarity.
+\item Initialization of the \ac{SCA} operating point is included in the revised manuscript
+\item Section III-D is updated to include the guidelines involved in selecting the sub-channel order.
+\item Strong convexity of the objective function is emphasized in Appendix A-B.
+\item Strict monotonicity of the algorithm is discussed in a detailed manner in Appendix A-C.
 \item We have provided additional details on the distributed algorithm convergence as suggested by the reviewers
-\item Section III-D is updated to include the guidelines involved in selecting the sub-channel order.
-\item Short discussion on the choice of algorithm selection is provided 
-\item Initialization of the \ac{SCA} operating point is also included in the revised manuscript
 \end{enumerate}

### 2015-07-20 Response/Response 2/response-1.tex
updated with Nam changes (half cooked)

@@
 
-\resp After a careful check of the manuscript, we have removed couple of paragraphs from Section III.A and shortened the discussions on the simulation section to provide additional details for the convergence proof.
-We believe the removed parts don't affect the readability of the paper and the added text regarding convergence proof certainly improves the quality.
+\resp After a careful check of the manuscript, we have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results section) to provide additional details for the convergence proof.
+We believe the removed parts do not affect the readability of the paper and the added text regarding convergence proof certainly improves the quality.
 
@@
 \resp We thank the reviewer for the critical comment.
-It is not possible to define the inequality with the previous optimal point.
-Since it is not possible to comment on the inclusion of the previous constraint set in the current update (except the earlier optimal point), the inequality is not guaranteed.
+It is not possible to comment on the inclusion of the previous constraint set in the current update (except the earlier optimal point), the inequality is not guaranteed.
 Based on the comment from the reviewer, we have removed the inequality specifying the previous operating point from (49) in the revised manuscript, since it cannot be guaranteed.
@@
 
-\resp We understand the reviewer concern.
+\resp  We thank the reviewer for citing this issue on the sequence convergence.
 Even though the objective of the \ac{SCA} iteration converges, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge.
 It is true that the iterates need not converge when the objective function is convex.
-We have modified the discussion by using the strong convexity of the objective function to impose the uniqueness of the iterates in each \ac{SCA} update as well.
-By regularizing the objective function with a strongly convex term like \eqn{\|\mbf{m} - \mbf{m}^{(i)}_k\|^2}, we can guarantee the uniqueness of the iterates upon the \ac{SCA} convergence, \textit{i.e.}, the limit point of the \ac{SCA} update is unique.
-We thank the reviewer for citing this issue on the sequence convergence and the uniqueness of the minimizer.
+However, we have modified the discussion by using the strong convexity of the objective function to impose the uniqueness of the iterates in each \ac{SCA} update.
+
+Since our problem is (highly) nonconvex and there are possibly many stationary points.
+If we start from different initial points, we may end up at different stationary points.
+That is to say, the limit point of \ac{SCA} approach is not unique.
+However, by regularizing the objective with a small quadratic term, the iterate in each step of \ac{SCA} algorithm is unique.
+This and the fact that the set is compact ensure the \ac{SCA} converges to a limit point.
 We have updated the manuscript to include this information in the convergence proof in Appendix A-B around (46) and in Appendix A-C.
@@
 As suggested by the reviewer, we have included the strict monotonicity of the objective sequence in Appendix A-C following (52).
+In addition, we also have noted the reader that we in fact use the regularized objective in (52) to analytically prove the convergence of iterates, although we have numerically observed that the iterates of Algorithm 1 (with the original objective) always converge.
+Please refer to the paragraph before Section III-C.
 
+\begin{comment}
 Note that the objective sequence \eqn{\{f(\mbf{x}_k)\}} generated by an iterative \ac{SCA} algorithm is monotonic, \textit{i.e}, \eqn{f(\mbf{x}_k) \leq f(\mbf{x}_{k-1})} and holds with equality at the limit point of the iterative procedure.
@@
 Therefore, strict monotonicity cannot be guaranteed for the objective sequence.
-However, when the objective function is strongly convex, as discussed in Appendix A-B, the minimizer for the subproblem in each \ac{SCA} iteration \eqn{k} is unique as
+However, when the objective function is strongly convex with a parameter \eqn{m > 0}, as discussed in Appendix A-B, the minimizer for the subproblem in each \ac{SCA} iteration \eqn{k} is unique as
 \begin{equation} \label{eqn-aa}
-f(\ma_{k}) - f(\ma_{k+1}) \geq  \nabla f(\ma_{k+1})^\tran (\ma_{k} - \ma_{k+1}) + c \|\ma_{k} - \ma_{k+1}\|^2
+f(\ma_{k}) - f(\ma_{k+1}) \geq  \nabla f(\ma_{k+1})^\tran (\ma_{k} - \ma_{k+1}) + m \|\ma_{k} - \ma_{k+1}\|^2
 \end{equation}
@@
 \nabla f(\ma_{k+1})^\tran (\ma_{k} - \ma_{k+1}) &\geq& 0 \slabel{eqn-a} \\
-f(\ma_{k}) - f(\ma_{k+1}) &\geq& c \|\ma_{k} - \ma_{k+1}\|^2 \slabel{eqn-b}
+f(\ma_{k}) - f(\ma_{k+1}) &\geq& m \|\ma_{k} - \ma_{k+1}\|^2 \slabel{eqn-b}
 \end{subeqnarray}
@@
 Now by using the monotonicity of the \ac{SCA} updates and the uniqueness of the minimizer in each step, we can guarantee the strict monotonicity of the objective sequence generated by the iterative problem.
+\end{comment}
 
@@
 We have updated the manuscript to include the details regarding the stationary point discussion in Appendix A-E and the convergence proof analysis for the primal and the \ac{ADMM} algorithms in Appendix B.
-Additional detail includes the conditions required for showing the stationarity of the limit point and we have included additional details to show the distributed approaches convergence convincing.
+We have also mentioned the conditions required for showing the stationarity property of the limit point and included more mathematical materials to make the convergence proof of distributed approaches rigorous.
 

### 2015-07-20 Response/Response 2/response-2.tex
updated with nam response
updated with Nam changes (half cooked)

@@
 \vspace{1eM}
-\underline{\textit{Reply:}} We thank the reviewer for providing useful comments. The comments are constructive and helped us to improve the manuscript better.
+\underline{\textit{Reply:}} We thank the reviewer for providing further useful comments which help us to greatly improve the manuscript.
 
@@
 
-\resp We apologize for not discussing the sub-channel ordering in a detailed manner.
-We have included the guidelines for selecting the sub-channel ordering based on channel gains, \textit{i.e}, greedy selection.
-In random ordering scheme, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
-As suggested by the reviewer, the greedy sub-channel ordering is based on sorting the best channel from each sub-channel, which is obtained by finding the highest channel norm between the users from the respective serving \ac{BS}.
-Note that the users channel used in the ordering procedure is the channel seen by the users with the corresponding serving \acp{BS} only.
+\resp We apologize for not clarifying the sub-channel ordering in a detailed manner in the previous manuscript.
+For simplicity we use random sub-channel ordering in our paper.
+That is, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
 
-However, it may not be optimal for all system configurations, since the ordering scheme should also consider the number of backlogged packets associated with each user. We have 
-emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user.
+As suggested by the reviewer, the greedy sub-channel ordering is based on sorting the best channel gain from each sub-channel, which is obtained by finding the highest channel norm between the users from the respective serving base station (BS).
+
+We remark that the choice of a sub-channel ordering scheme should also consider the number of backlogged packets associated with each user.
+We have emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user.
 Even though we are not including it in the paper, we have included in the response letter to answer the reviewer's question.
@@
 Fig.
-\ref{fig-review-1} compares different ordering of sub-channels with the total number of backlogged packets remaining in the system as the metric.
+\ref{fig-review-1} compares different sub-channel ordering schemes in terms of the total number of backlogged packets remaining in the system.
 As can be seen from Fig.
@@
 However in Fig.
-\ref{fig-review-1b}, the greedy sub-channel ordering is not an efficient strategy in determining the order in which the sub-channels are to be chosen.
+\ref{fig-review-1b}, the greedy sub-channel ordering is no longer efficient.
 We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic method under Section III-D final paragraph.
@@
 		\item The amount of signaling overhead of the distributed algorithm and the centralized one depends on the system model of consideration.
-For example, let us consider a model with \eqn{N = 1} sub-channels ,\eqn{N_B = 2} \acp{BS}, and \eqn{K = 4} users in total, each \ac{BS} serving \eqn{2} users.
-Let \eqn{N_T = 4} be the number of transmit antennas and \eqn{N_R = 1} be the number of receive antenna at each user.
-In this scenario, the amount of information exchange to perform a centralized algorithm by a common controller requires the knowledge of complete channel matrices interlinked in the system, \textit{i.e}, the number of users times the \acp{BS}.
+For example, let us consider a model with \eqn{N = 1} sub-channel, \eqn{K = 4} users and \eqn{N_B = 2} \acp{BS}, each serving 2 users.
+Let \eqn{N_T = 4} be the number of transmit antennas and \eqn{N_R = 1} be the number of receive antennas at each user.
+We note that a centralized algorithm requires the knowledge of all channels matrices in the system and thus the resulting amount of information exchange is proportional to the product of the numbers of users (\eqn{K}), \acp{BS} (\eqn{N_B}), and transmit and receive antennas (\textit{i.e.}, \eqn{N_T} and \eqn{N_R}).
 
-		In order to quantify the total number of bits required to be exchanged, let us assume that each complex channel for a single-input single-output requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is important) or it can be a equal share of \eqn{5} bits for both amplitude and phase.
-Using this assumption, the total number of channel information in bits to be exchanged via backhaul requires \eqn{10 \times K \times N_B \times N_R \times N_T = 320} bits.
-On the other hand, for the distributed case, let us consider \eqn{6} bits are required to quantize the scalar interference in the consensus vectors.
+		In order to quantify the total number of bits required in a centralized solution, let us assume that each complex channel for a single-input single-output requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is more important) or it can be a equal share of \eqn{5} bits for both amplitude and phase.
+Using this assumption, the total amount of channel information in bits to be exchanged via backhaul is \eqn{10 \times K \times N_B \times N_R \times N_T = 320} bits.
+On the other hand, for the distributed algorithms, let us consider \eqn{6} bits for quantizing each element of the consensus vectors.
 Consequently, the proposed distributed solutions require \eqn{6 \times 2 \times 2} bits to be exchanged in each iteration.
 
-		In this example, for the same amount of signaling overhead as in centralized method, we can performance only up to 6 SCA updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for ADMM part).
+		In the above example, for the same amount of signaling overhead as in centralized method, we can performance only up to 6 SCA updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for ADMM part).
 This may not be sufficient for the distributed algorithms to attain the same performance as the centralized method.
-However, as the number of sub-channels, users and/or the antenna element increases, it may not be a feasible option to feedback the \ac{CSI} across the coordinating \acp{BS} to the centralized controller.
+However, as the number of sub-channels, users and/or the antenna element increases, it may not be a feasible option to feedback the \ac{CSI} across the coordinating \acp{BS} to the centralized controller in the current cellular systems.
 In addition to comparing the signaling overhead, we also need to consider the effects of the quantization of the \ac{CSI} on the performance of a centralized algorithm, which is beyond the scope of our paper.
-Generally, the performance is significantly degraded if the \ac{CSI} is quantized \cite{nam_robust}.
+Generally, the performance is significantly degraded if the \ac{CSI} is quantized [R1].
 Moreover, in the centralized algorithm, resulting transmit precoders need to be exchanged with the corresponding \acp{BS} before the actual transmission, involving huge overhead in the backhaul.
+
+		\vspace{1eM}
+		[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti Tölli, Markku Juntti,  and Savo Glisic, "\emph{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}," \textit{IEEE Trans.
+Signal Process}., vol 61, no.
+22, pp.
+5659-5674, Nov.
+2013.
+		\vspace{1eM}
 
@@
 
-		\item In particular, \ac{ADMM} and primal approach requires significant overhead compared to the centralized algorithm for a small system, since by exchanging the quantized channels, each \ac{BS} can perform the centralized algorithm independently until convergence.
-However, it depends on the channel quantizer, which is likely to be based on the channel density function (eg.
-Lloyd quantizer).
-For a system involving more coordinating \acp{BS}, users and antenna elements, it would be beneficial to use distributed algorithm with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
-If we set \eqn{J_{\max} = 1}, the proposed algorithms still converge (but monotonicity of SCA is not guaranteed).
+		\item From the above discussions we can see that \ac{ADMM} and primal approach require significant overhead compared to a centralized algorithm for a small system.
+For a system involving more coordinating \acp{BS}, users and antenna elements, it would be beneficial to use the proposed distributed algorithms with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
+If we set \eqn{J_{\max} = 1}, the convergence of the proposed algorithms is not guaranteed as shown in Fig.
+\ref{fig-review-2-a}, which has same system model as that of Fig.
+\ref{fig-review-1a}.
+		\begin{figure}[h!]
+			\centering
+			\includegraphics[width=0.8\columnwidth]{reviewer_2_Q1C.eps}
+			\caption{Convergence of the centralized and distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace} using \me{\ell_1} norm}
+			\label{fig-review-2-a}
+		\end{figure}
+		Note that Fig. \ref{fig-review-2-a} plots the queue deviation at the \ac{SCA} update points only. The number of backlogged packets in each \ac{ADMM} iteration is not shown for clarity reason.
 
@@
 
-	The performance of the distributed algorithm based on dual decomposition scheme was discussed for the time-correlated fading in Section C of [13], which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
-The distributed algorithm for the time correlated case is beyond the scope of our paper and thus is not considered in the current manuscript.
+	The performance of the distributed algorithm based on dual decomposition scheme was discussed for the time-correlated fading in Section C of [13], which showed that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+Studying the performance of distributed algorithms for the time correlated case is beyond the scope of our paper and thus is not considered in the current manuscript.
 However, we take this opportunity to show a plot demonstrating this behavior for the \ac{KKT} based algorithm presented in Section IV-C of the manuscript.
@@
 		\includegraphics[width=0.8\columnwidth]{reviewer_2_Q2.eps}
-		\caption{Average number backlogged packets after each transmission for system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,16,4,2 \rbrace} evaluated for \eqn{500} slots}
+		\caption{Expected number backlogged packets after each transmission instant for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,16,4,2 \rbrace} evaluated for \eqn{500} slots}
 		\label{fig-review-2}
@@
 	Fig.
-\ref{fig-review-2} compares the performance of the distributed \ac{KKT} approach presented in Section IV-C for different iteration.
-The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.
-We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the equivalent channel for \eqn{J_{\max} = 3,5,10} number of iterations.
+\ref{fig-review-2} compares the performance of the distributed \ac{KKT} approach, \textit{i.e.}, Algorithm 3 for different values of \eqn{I_{\max}}.
+The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.\footnote{Please refer to [27] for further details.} We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the required information for \eqn{J_{\max} = 3,5,10}.
 The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{J_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{J_{\max}}{N_S})} is considered as a penalty involved due to the precoder exchange.
@@
 
-	Unlike the distributed algorithm, the centralized scheme presented in Fig.
-\ref{fig-review-2} has no penalty term and it is used as a benchmark for the other figures.
-In order to improve the performance of the distributed scheme, the operating point involved in the \ac{SCA} algorithm is considered from the earlier frame instead of starting initializing randomly.
+	Unlike Algorithm 3, the centralized scheme presented in Fig.
+\ref{fig-review-2} has no penalty term and it is used as a benchmark.
+In order to improve the performance of the distributed scheme, the operating point involved in the \ac{SCA} algorithm is considered from the earlier frame instead of begin generated randomly.
+
+	\begin{comment}
 	Since we use \ac{KKT} approach, we can either use all users in the system for the precoder design or we can utilize single-cell MU-MIMO user selection presented in the literature to limit the number of users for which the precoders are designed, which leads to the faster convergence.
@@
 Once the iterations are performed to update the precoders, it is then exchanged across the coordinating \acp{BS} to perform the same procedure as mentioned earlier.
+	\end{comment}
 
@@
 
-\resp We thank the reviewer for raising the important concern regarding the convergence issue of the distributed algorithm with limited number of iterations.
-In view of this, we have updated the manuscript to include the discussion on the convergence of the distributed algorithms with a limited number of iterations in the third paragraph of Appendix B after (57).
-Since the distributed algorithm cannot be guaranteed to be monotonic in each iteration, it is not possible to prove the convergence of the algorithm.
-However, if the algorithm is allowed to converge or iterated to guarantee the monotonicity of the objective, it is possible to prove the convergence based on the discussions provided in the manuscript.
+\resp We thank the reviewer for raising the important concern regarding the convergence issue of the distributed algorithms.
+We want to clarify that we are able to prove the convergence of Algorithm 2 which is based on \ac{ADMM}.
+In our paper the number of updates for the \ac{ADMM} part is denoted by \eqn{J_{\max}}.
+There is a trade-off between signaling overhead and achieved performance by varying \eqn{J_{\max}}.
+In reality we may set \eqn{J_{\max}} to a finite value to reduce the signaling overhead.
+In such a case, the convergence is not guaranteed.
+In our simulation, the \ac{ADMM} part can find an optimal solution to the (convex) subproblem in each \ac{SCA} step when \eqn{J_{\max} = 20}.
+
+\begin{itemize}
+\item We also want to remark that  the proposed distributed algorithms are not based on fixed-point theory.
+The \ac{ADMM} part is to find a (unique) optimal solution to the strongly convex subproblem in each \ac{SCA} step.
+More explicitly, the \ac{ADMM} approach is used to solve the problem given in (20) based on augmented Lagrangian function which is different from fixed-point theory.
+However, the optimal solution of (20) is not necessarily a fixed-point of the problem.
+
+\item When the ADMM approach converges, the interference vector is guaranteed to be equal to the actual interference in the next work.
+This is the main principle of \ac{ADMM} where the local variables (the vectors in (39)) converge to the global variables (the actual inference vectors).
+
+\item Another point we want to make is that Algorithm 2 yields a stationary point of the original noncovex problem at convergence and this stationary point may not be a fixed-point of the original noncovex problem.
+
+\item Since Algorithm 3 is based on a heuristic iterative approach to find a solution of \ac{KKT} equations, we cannot prove its convergence.
+When Algorithm 3 terminates, we will use the transmit and receive beamforming vectors to calculate the original objective.
+
+\end{itemize}
+
+We have updated the manuscript to clarify the points mentioned above.
+Please refer to Section IV-B in the revised manuscript.
+For reference purpose, we have also referred the interested reader to [11], which discusses exclusively about the ADMM approach.
+
+\begin{comment}
+\resp We thank the reviewer for raising the concern regarding the convergence of the distributed algorithms with limited number of iterations.
+In view of this, we have updated the manuscript to include discussions on the convergence of the distributed algorithms with a limited number of iterations in the third paragraph of Appendix B after (57).
+Since the monotonicity of the algorithm with limited number of updates in each subproblem is not guaranteed in each iteration, it is hard to prove the convergence of the overall algorithm.
+However, if the algorithm is allowed to converge or iterated enough to guarantee the strict monotonicity of the objective in between the \ac{SCA} updates, the global convergence of the algorithm to a limit point of the original nonconvex problem is guaranteed based on the discussions provided in Appendix A.
 \begin{itemize}
@@
 
+\end{comment}
+
 \end{enumerate}
-
-\bibliographystyle{./../../Styles/IEEEtran}
-\bibliography{./../../Library/IEEEabrv,./../../Library/kirja_survey}

### 2015-07-20 Response/Response 2/response-3.tex
updated with Nam changes (half cooked)

@@
 We have included additional information on how to choose the operating point while initializing the iterative algorithm.
-It is included in the fourth paragraph following (23).
+It is written in the fourth paragraph following (23).
 We have also provided a detailed discussion on how to update the operating point after each iteration in the paragraph following (23).
@@
 
-	\resp We have updated the manuscript to include a discussion on the possible conditions for selecting an algorithm for a specific implementation.
+	\resp We have updated the manuscript to discuss possible options for selecting an algorithm for a specific implementation.
 The choice of considering a centralized approach is equally good when the number of receive antenna is greater than one, \textit{i.e.}, \eqn{N_R > 1}.
@@
 	As far as the distributed approaches are concerned, the primal and the \ac{ADMM} schemes are equally favorable when \eqn{N_R = 1} since the signaling required to be exchanged between the coordinating \acp{BS} involves only the scalar interference values.
-However, when \eqn{N_R > 1}, then the \ac{KKT} based distributed approach is more efficient than the primal or the \ac{ADMM} schemes, since it has less signaling overhead for a throughput improvement.
+However, when \eqn{N_R > 1}, then the \ac{KKT} based distributed approach is more efficient than the primal and the \ac{ADMM} schemes, since it has less signaling overhead.
 The choice of selecting \eqn{\ell_q} norm is discussed in Section II-B last paragraph.
 The above information is included in the paragraph before the simulations section in Section IV.
-
-	However, if the reviewer is interested to understand the performance of the \ac{KKT} based scheme in a fading environment, please refer to the response provided for the reviewer 2, question 2 in this document for more details.
 
@@
 For benchmarking, we have also included the centralized algorithm to draw the difference between the other schemes.
-We are conducting more numerical experiments to have a more complete comparison of the schemes.
+We are conducting more numerical experiments to have a more complete comparison of all the schemes.
 Unfortunately those results cannot be included in the current manuscript due to space limitation.

### 2015-07-20 Report/conclusions.tex
updated with Nam changes (half cooked)

@@
-In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM}.
+In this paper, we have addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM}.
 The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector.
-We proposed the \ac{JSFRA} scheme by relaxing the nonconvex \ac{DC} constraint by a sequence of convex subsets using the \ac{SCA} for designing the precoders to minimize the total number of user queued packets.
-Additionally, an alternative \ac{MSE} reformulation approach is also proposed by using the \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers.
+We have proposed the \ac{JSFRA} scheme by relaxing the nonconvex constraint by a sequence of convex subsets using the \ac{SCA} for designing the precoders to minimize the total number of user queued packets.
+Additionally, an alternative \ac{MSE} reformulation approach has been proposed by using the \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers.
 We also proposed various methods to decentralize the precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.
-Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method.
+Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} expressions of the \ac{MSE} reformulated problem.
 The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations.
-Numerical results are used to compare the performances of the proposed algorithms.
+Numerical results are used to compare the performances of the proposed schemes.

### 2015-07-20 Report/convergence_centralized.tex
updated with Nam changes (half cooked)

@@
-To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we need to show that the following conditions are satisfied by the centralized formulations.
+To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we will show that the following conditions are satisfied by the centralized formulations.
 \begin{itemize}
@@
 where \me{g_2}, \me{\hat{f}} are convex and \me{h} is a linear function.
-Let \me{g_0,g_1} be convex in either \me{\mx} or \me{\my} but not on both.
-The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} correspond to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
+Let \me{g_0,g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not on both.
+The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
 Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
@@
 To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}.
-In \eqref{con}, even after fixing the variable \me{\my}, the problem is nonconvex due to the \ac{DC} constraint \eqref{con-dc}.
-We adopt \ac{SCA} presented in \cite{lanckriet2009convergence,scutari_1,yang_yang} by relaxing the nonconvex set by a sequence of convex subsets.
-Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{DC} constraint relaxations by a subscript \me{k}.
+In \eqref{con}, even after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}.
+To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,yang_yang} by relaxing the nonconvex set by a sequence of convex subsets.
+Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{SCA} step by a subscript \me{k}.
 Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}.
@@
 \begin{IEEEeqnarray}{rCl} \neqsub
-	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \\ 
-	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
+	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + \frac{c}{2} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
 \end{IEEEeqnarray}
-where \eqn{\mbf{z}} is the stacked vector of optimization variables, which can either be \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c > 0} is a positive constant to ensure strong convexity in the objective, and therefore guarantees a unique minimizer \cite{yang_yang}.
+where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c > 0} is a positive constant to ensure strong convexity in the objective, and therefore guarantees the unique minimizer \cite{yang_yang}.
 Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}
@@
 To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
-In order to solve for \me{\mx} in the \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
+In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
 \iftoggle{single_column}{
@@
 \end{multline}}
-Thus the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing and approaches limit point of the \ac{SCA} as \me{k \rightarrow \infty}.
-The equality in \eqref{con-convergence} is attained upon the \ac{SCA} convergence.
-The limit point \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} need not to be a stationary point of \eqref{con}, since it is the minimizer in \me{\iter{\mc{X}}{\ast}{i} \subset \mc{F}} only.
-\review{Since the objective is strongly convex, due to the quadratic term in \eqref{mod_obj}, the minimizer \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} in each \ac{SCA} step is unique.}
+Thus the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing.
+\review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique.
+Using this and the fact that the sequence of objectives is nondecreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.
+However, note that the limit point need not be a stationary point of \eqref{con} since the receive beamformers \eqn{\my} have been fixed.}
+
+% and approaches limit point of the \ac{SCA} as \me{k \rightarrow \infty}.
+The equality in \eqref{con-convergence} is achieved upon the \ac{SCA} convergence.
+The limit point obtained in the \eqn{\ith{i}} \ac{AO} step need not to be a stationary point of \eqref{con}, since it is the minimizer in \me{\iter{\mc{X}}{\ast}{i}} only.
+\review{Note that for a fixed initial operating point of the iterative \ac{SCA} procedure, the minimizer in each \ac{SCA} step is unique and so the limit point due to the strong convexity of the modified objective \eqref{mod_obj}.}
+
+%\review{Since the objective is strongly convex, due to the quadratic term in \eqref{mod_obj}, the minimizer \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} in each \ac{SCA} step is unique.}
 
@@
 Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the objective follows similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is the minimizer in the feasible set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
+The convergence and the nonincreasing behavior of the objective follow similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is the minimizer in the feasible set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
 
-Finally, to prove the global convergence of the iterative algorithm, we need to show the nonincreasing behavior of the objective function in between the \ac{AO} updates, \textit{i.e.}, 
+Finally, to prove the global convergence of the iterative algorithm, we need to show the \ac{AO} updates also produce a nondecreasing sequence of objectives, \textit{i.e.}, 
 \iftoggle{single_column}{
@@
 To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
-Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by following \eqref{con-sub-set}.
+Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by the equality in \eqref{con-sub-set}.
 Using this, we can show the monotonicity of the objective as
@@
 
-\review{Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step.
+\review{Note that the \ac{AO} and \ac{SCA} iterative procedures generates a nonincreasing sequence of objectives for the original function in \eqref{orig_obj} using the above discussions.
+However, by using the regularized objective in \eqref{mod_obj}, we can show that the sequence of objectives provided by \ac{AO} and \ac{SCA} steps is strictly increasing.
+Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step.
 In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj}.
-We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} iteration \cite{marks1978technical}.
-By using the strong convexity of \eqref{mod_obj}, it follows that in the \eqn{\ith{k}} update
+%We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} \ac{SCA} step \cite{marks1978technical}.
+It follows by the strong convexity of \eqref{mod_obj} with \eqn{m > 0} in the \eqn{\ith{k}} update
 \begin{equation} \label{strict_monotonicity}
-f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + c \, \|\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}\|^2  \eqspace
+f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + m \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
 \end{equation}
@@
 
-Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update.
+Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update.
 Since \eqn{\iter{\mbf{z}}{\ast}{i}} is also included in the set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} strictly unless the overall sequence \eqn{\{\mbf{z}_{\ast}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}

### 2015-07-20 Report/decomposition_solutions.tex
updated with Nam changes (half cooked)

@@
 The convex formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
-In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are addressed.
-In particular, the \acl{PD} and the \ac{ADMM} based \acl{DD} approaches are considered.
+In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are based on the \acl{PD} and the \ac{ADMM} are considered herein.
 
@@
 \end{IEEEeqnarray}
-where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.
+where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviations corresponding to users \me{k \in \mc{U}_b}.
 
-To begin with, let \me{\bar{\mc{B}}_b} be the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}.
+To begin with, let \me{\bar{\mc{B}}_b} be the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represent the set \me{\mc{U} \backslash \mc{U}_b}.
 Following an approach similar to the one presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be
@@
 \end{multline}}
-where \me{\zeta_{l,k,n,b}} is the total interference caused by the transmission of \ac{BS} \me{b} to user \me{k \in \mc{U}_{b_k}} in the spatial stream \me{l} and sub-channel \me{n}.
-It is given by the following upper bound as
+where \me{\zeta_{l,k,n,b}} is the total interference caused by the transmission of \ac{BS} \me{b} to user \me{k \in \mc{U}_{b_k}} in spatial stream \me{l} and sub-channel \me{n}.
+To ensure \eqref{eqn-9.1c}, we impose
 \begin{equation} \label{inter_exp}
@@
 
-The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} to a parallel iterative subproblems coordinated by either primal or \acl{DD} update.
-The coupling variables are updated in each iteration by exchanging limited information among the subproblems.
+The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} to a parallel subproblems coordinated by either primal or \acl{DD} update.
+The coupling variables are updated in each iteration by exchanging limited information among the \acp{BS}.
 Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented as
@@
 To decentralize the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in accordance to the decomposition method.
-To decouple the precoder design across \acp{BS}, the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are to be known at each \ac{BS} \me{b} through the precoded uplink pilots from all the users in the system, where the precoders are the \ac{MMSE} receiver \me{\mvec{w}{l,k,n}} evaluated at the user.
-Similarly, to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} need to be known through the user specific precoded downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} by using the equivalent downlink channel that includes the updated \ac{MMSE} receivers of all the users, as in \cite{komulainen2013effective}.
+To decouple the precoder design across \acp{BS}, the equivalent downlink channels \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are to be known at each \ac{BS} \me{b} through the precoded uplink pilots from all the users in the system, where the linear precoders are evaluated at the user using \ac{MMSE} formulation in \eqref{eqn-mse-2}.
+Similarly, to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} need to be known.
+It is obtained through the user specific downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} using the equivalent downlink channels as in \cite{komulainen2013effective}.
 %The subproblems with the \ac{BS} specific interference variables are controlled by a master subproblem, which determines the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in accordance with the global objective.

### 2015-07-20 Report/dual_approach.tex
half cooked
updated with nam response
updated with Nam changes (half cooked)

@@
-The \ac{ADMM} approach is used to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}.
-The \ac{ADMM} is preferred over the \ac{DD} approach in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}.
-In contrast to the \acl{PD}, the \ac{ADMM} approach relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
-Similar approach for the precoder design in the minimum power context is considered in \cite{admm_robust}.
+The \ac{ADMM} approach can also be used to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}.
+Generally, the \ac{ADMM} is preferred over the \ac{DD} approach in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}.
+In contrast to the \acl{PD}, the \ac{ADMM} relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
+Similar approach for the precoder design in the minimum power context was considered in \cite{admm_robust}.
 
@@
 For our simulation models, we consider step size parameter \me{\rho=2}.
-The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.
+The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of iterations.
 The distributed precoder design using the \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
 The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
+\begin{algorithm}
+	\SetAlgoLined
+	\DontPrintSemicolon
+	\BlankLine
+	\SetKwInput{KwInit}{Initialize}
+	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
+	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
+	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
+	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
+	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
+	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
+		\Repeat{convergence or \me{i \geq I_{\max}}}{
+			\Repeat{convergence or \me{j \geq J_{\max}}}{
+				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
+				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
+				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
+				update \me{j = j + 1}\;
+			}
+			send precoded downlink pilot with \me{\mbf{m}}\;
+			evaluate \me{\mvec{w}{l,k,n}} at each user and inform to all \acp{BS} in \eqn{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective} \;
+			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
+			$i = i + 1$, \me{j=0} \;
+		}
+	}
+	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
+	\label{algo-3}
+\end{algorithm}
+\begin{comment}
 \begin{algorithm}
@@
 \end{algorithm}
-\begin{comment}
 The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties.

### 2015-07-20 Report/introduction.tex
updated with Nam changes (half cooked)

@@
 In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users present in the network.
-We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets at each \ac{BS}.
-Since the available resources are shared by multiple users associated with different \acp{BS}, it can be viewed as a resource allocation problem.
+We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}.
+Since the resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation one.
 
-In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}.
+In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or absence of a particular resource \cite{admission_control}.
 Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables.
-After the decision stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource.
+After the design stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource.
 A zero transmit precoder indicates the absence of the user on a given resource.
 In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergences.
-
 %The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
@@
 
-The queue minimizing precoder designs are closely related to the \ac{WSRM} problem with additional rate constraints determined by the number of backlogged packets for each user in the system.
+The queue minimizing precoder designs are closely related to the \ac{WSRM} problem with additional rate constraints to limit the throughput beyond the number of backlogged packets associated with the users.
 The topics on \ac{MIMO} \ac{IBC} precoder design have been studied extensively with different performance criteria in the literature.
-Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, the \ac{SCA} approach has become a powerful tool to deal with these problems.
-For example, in \cite{sin_algorithm}, the nonconvex part of the objective has been linearized around an operating point in order to solve the \ac{WSRM} problem in an iterative manner.
-Similar approach of solving the \ac{WSRM} problem by using arithmetic-geometric inequality has been proposed in \cite{tran2012fast}.
+Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, \ac{SCA} approach has become a powerful tool to deal with these problems.
+For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around an operating point to solve the \ac{WSRM} problem in a iterative manner.
+A similar approach using arithmetic-geometric inequality was proposed in \cite{tran2012fast}.
 
@@
 Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed.
-The \ac{MSE} reformulation for the \ac{WSRM} problem has also been studied in \cite{hong2012decomposition} by using \ac{SCA} to solve the problem in an iterative manner.
-Moreover, distributed precoder design with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013primal,kaleva2013decentralized}.
+The \ac{MSE} reformulation for the \ac{WSRM} problem was also studied in \cite{hong2012decomposition} by using \ac{SCA} to solve the problem in an iterative manner.
+Moreover, distributed precoder designs with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013primal,kaleva2013decentralized}.
 
 The problem of precoder design for the \ac{MIMO} \ac{IBC} system can be solved either by using a centralized controller or by using decentralized algorithms, where each \ac{BS} handles the corresponding subproblem independently with the limited information exchange with other \acp{BS} via back-haul.
-The distributed approaches are usually based on the primal, or dual decompositions or the \ac{ADMM}, which has been discussed in \cite{palomar2006tutorial,boyd2011distributed}.
+The distributed approaches are usually based on the primal, or dual decompositions or the \ac{ADMM}, as discussed in \cite{palomar2006tutorial,boyd2011distributed}.
 In the  primal decomposition, the so-called coupling interference variables are fixed for the subproblem at each \ac{BS} to find the optimal precoders.
@@
 Earlier studies on the queue minimization problem are summarized in the survey papers \cite{berry2004cross,layering_as_opt}.
-In particular, the problem of power allocation to minimize the number of backlogged packets is considered in \cite{qps_cioffi} using geometric programming.
+In particular, the problem of power allocation to minimize the number of backlogged packets was considered in \cite{qps_cioffi} using geometric programming.
 Since the problem addressed in \cite{qps_cioffi} assumed single antenna transmitters and receivers, the queue minimizing problem reduces to the optimal power allocation problem.
-In the context of wireless networks, the \textit{backpressure algorithm} mentioned above is extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.
-Recently, the precoder design for the video transmission over \ac{MIMO} system is considered in \cite{video_queues}.
-In this design, the \ac{MU}-\ac{MIMO} precoders are designed by the \ac{MSE} reformulation as in \cite{christensen2008weighted} with the higher layer performance objective such as playback interruptions and buffer overflow probabilities.
+In the context of wireless networks, the \textit{backpressure algorithm} mentioned above was extended in \cite{weeraddana2011resource} by formulating the corresponding user queues as the weights in the \ac{WSRM} problem.
+Recently, the precoder design for the video transmission over \ac{MIMO} system was considered in \cite{video_queues}.
+In this design, the \ac{MU}-\ac{MIMO} precoders are designed by the \ac{MSE} reformulation as in \cite{christensen2008weighted} with the higher layer performance objectives such as playback interruptions and buffer overflow probabilities.
 
@@
 The rest of the paper is organized as follows.
-Section \ref{sec-2-3.2} introduces the system model and the problem formulation for the proposed design.
+Section \ref{sec-2-3.2} introduces the system model and the problem formulation.
 The existing and the proposed centralized designs are presented in Section \ref{sec-3}.

### 2015-07-20 Report/joint_wsrm_formulation.tex
updated with Nam changes (half cooked)

@@
 
-The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the downlink \ac{MIMO}-\ac{OFDM} framework, in which the \acp{BS} acts as the source nodes and the users as the receivers.
+The \ac{Q-WSRM} formulation extends the \emph{backpressure algorithm} to the downlink \ac{MIMO}-\ac{OFDM} framework, in which the \acp{BS} act as the source nodes and the users as the receivers.
 The control policy in the form of transmit precoders aims at minimizing the number of queued packets waiting in the \acp{BS}.
@@
 \begin{equation}
-\sset{\max(Q-t,0) + \lambda)}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
+\sset{\max(Q-t,0) + \lambda}^2 \leq Q^2 + t^2 + \lambda^2 + 2 Q (\lambda - t).
 \end{equation}

### 2015-07-20 Report/kkt_mse_approach.tex
updated with Nam changes (half cooked)

@@
 In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}.
-In contrast to Section \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same instant to minimize the global queue deviation objective with few number of iterations.
-\review{Note that the distributed approaches discussed so far may not be efficient for multi-antenna receivers in terms of signaling overhead involved in exchanging the coupling variables and the receivers as the system size and the required number of iterations increases.}
+In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the global queue deviation objective with few number of iterations.
+\review{The alterantive way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}
 
-In this section, we provide an algorithm that can be of practical importance owing to the limited signaling requirements.
+In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements.
 We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
-Since the formulations in \cite{kaleva2013decentralized,kaleva2013primal} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, it requires explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
+Since the work in \cite{kaleva2013decentralized,kaleva2013primal} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, the formulations require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
 
 In the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints.
-However, the \ac{KKT} conditions cannot be formulated due to the non-differentiability of the absolute value operator present in the objective function.
+However, due to the non-differentiability of the objective, the \ac{KKT} conditions are not computationally useful to find the optimization variables.
 In order to make the objective function differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the optimal solution, namely,
@@
 
-With the assumption of either one of the above conditions to be true, the problem in \eqref{eqn-mse-2} can be written as
+With the assumption of either one of the above conditions, the problem in \eqref{eqn-mse-2} can be written as
 \allowdisplaybreaks\iftoggle{single_column}{
@@
 
-The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} expressions, obtained by the derivative of the Lagrangian function w.r.t the primal and the dual variables, complementary slackness, and the primal, dual feasibility requirements as shown in Appendix \ref{a-1}.
-Upon solving, we obtain the iterative solution as
+The problem in \eqref{kkt-mse-1} is solved using the \ac{KKT} conditions which include stationarity, complementary slackness, and primal and dual feasibility requirement as shown in Appendix \ref{a-1}.
+In particular, we propose an iterative algorithm to compute a solution to the system of equations \eqref{kkt-mse-2} in Appendix \ref{a-1} as
 \iftoggle{single_column}{
@@
 So, \me{\alpha^{(i)}} is fixed to evaluate \me{\sigma^{(i)}} using \eqref{kkt-mse-4}.
-At each iteration, the dual variables \me{\alpha^{(i)}} are linearly interpolated with any point between the fixed iterate \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} using a diminishing or a fixed step size \me{\rho^{(i)} \in (0,1)}.
-The choice of \eqn{\rho^{(i)}} affects the convergence behavior and also controls the oscillations in the users rate when \me{\sigma^{(i)}} is negative due to over-allocation.
+At iteration \eqn{i}, the dual variables \me{\alpha^{(i)}} is a point in the line segment between \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} determined by using a diminishing or a fixed step size \me{\rho^{(i)} \in (0,1)}.
+The choice of \eqn{\rho^{(i)}} affects the convergence behavior and also controls the oscillations in the users' rate when \me{\sigma^{(i)}} is negative (before projection) due to over-allocation.
+In all numerical simulations, the step size \me{\rho^{(i)}} is fixed to \me{0.1} irrespectively.
+However, the choice of \me{\rho^{(i)}} depends on the system model and it affects the rate of convergence of the iterative algorithm.
 
-When the allocated rate \me{t_k^{(i-1)}} is greater than the number of queued packets \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
+For a physical interpretation, when the allocated rate \me{t_k^{(i-1)}} is greater than \me{Q_k} for a user \me{k}, the corresponding dual variable \me{\sigma^{(i)}} will be negative and due to the projection operator \me{[x]^+} in \eqref{kkt-mse-4.2}, it will be zero, thereby forcing \me{\alpha_k^{(i)} < \alpha_k^{(i-1)}} as in \eqref{kkt-mse-4.1}.
 Once \me{\alpha_k^{(i)}} is reduced, the precoder weight in \eqref{kkt-mse-4.3} is lowered to make the rate \me{t_k^{(i)} < t_k^{(i-1)}} eventually.
-The choice of \me{\rho} is susceptible to the system model under consideration, which affects the convergence speed of the iterative algorithm.
-In all simulations, the step size \me{\rho} is fixed to \me{0.1} irrespectively.
 
@@
 
-To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channels \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which includes the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling.
+To obtain a practical distributed precoder design, we assume that each \ac{BS} \me{b} knows the corresponding equivalent channels \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}}, which embeds the receivers \me{\mvec{w}{l,k,n}}, through precoded uplink pilot signaling.
 We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the current problem as follows.
 Upon receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user will evaluate the \ac{MMSE} receiver \eqref{kkt-mse-4.6} and notify to all \acp{BS} by using precoded uplink pilots.
-On receiving the pilots, each \ac{BS} update the \ac{MSE} in \eqref{mse-error} as
+On receiving the pilots, each \ac{BS} updates the \ac{MSE} in \eqref{mse-error} as
 \begin{equation}
@@
 \end{equation}
-Using the current \ac{MSE} value, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}, and the updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.
+Using \eqn{\epsilon_{l,k,n}^{(i)}}, the variables \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are updated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} respectively, and the obtained dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.
 The \ac{SCA} operating point is also updated with the current \ac{MSE} value.
@@
 
-To avoid the back-haul exchanges between the \acp{BS}, as an alternative approach, users can perform all the processing required and \acp{BS} will update the precoders based on the feedback from all the users.
+To avoid the back-haul exchanges between the \acp{BS}, as an alternative approach, users can perform all the required processing and \acp{BS} will update the precoders based on the feedback from all the users.
 Upon receiving the transmit precoders from the \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}}.
-Then, the updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilots with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders.
-Upon receiving the precoded uplink pilots, each \ac{BS} evaluate the effective channels \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} to update the transmit precoders using \eqref{kkt-mse-4.3}, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
-Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling with the precoded pilots for the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.
-The convergence of the algorithm is discussed in Appendix \ref{sec-dist-conv}.
+Then, the updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilots with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
+Upon receiving the precoded uplink pilots, each \ac{BS} evaluates the equivalent channels \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} to update the transmit precoders using \eqref{kkt-mse-4.3}.
+Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling as in \cite{komulainen2013effective}.
 
@@
 However, for \eqn{N_R = 1} scenario, the \ac{JSFRA} formulation in Section \ref{sec-3.2.1} is more efficient, as there is no receiver update, and therefore has less complexity.
-Similarly, when \eqn{N_R = 1}, the distributed approaches based on the \ac{JSFRA} method via \ac{SINR} relaxation is preferred over other schemes due to the limited signaling between the coordinating \acp{BS}, involving the scalar interference values.
+Similarly, when \eqn{N_R = 1}, the distributed approaches based on the \ac{JSFRA} method via \ac{SINR} relaxation are preferred over other schemes due to the limited signaling between the coordinating \acp{BS} involving the exchange of the scalar interference values.
 However, when \eqn{N_R > 1}, the \ac{KKT} scheme presented in Section \ref{sec-4.3} has less signaling requirements for a given throughput improvement.}

### 2015-07-20 Report/mse_formulation.tex
updated with Nam changes (half cooked)

--- 2015-06-27 Report/mse_formulation.tex
@@
 where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol.
-Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as
+Plugging the \ac{MMSE} receivers in \eqref{eqn-10} into the \ac{MSE} expression in \eqref{mse-error} and into the \ac{SINR} expression in \eqref{eq:SINR}, we arrive at the following relation between the \ac{MSE} and the \ac{SINR} as
 \begin{equation} \label{eqn-mse-eq}
@@
 The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion.
-Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.
-Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
+Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.
+Note that the receive beamformers based on the \ac{MMSE} criterion are independent of the choice of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
 
-Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent.
-By using the relaxed \ac{MSE} expression in \eqref{mse-error}, the problem in \eqref{eqn-3} can be expressed as
+Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represent the weighted formulation.
+By using the relaxed \ac{MSE} expression in \eqref{mse-error}, we can reformulate \eqref{eqn-3} as
 \iftoggle{single_column}{
@@
 \end{IEEEeqnarray}}
-\begin{algorithm}
-	\SetAlgoLined
-	\DontPrintSemicolon
-	\BlankLine
-	\SetKwInput{KwInit}{Initialize}
-	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
-	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
-	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
-	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
-	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
-		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
-			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
-			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
-			$j = j + 1$\;
-		}
-		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
-		$i = i + 1$, \me{j = 0}\;
-	}
-	\caption{Algorithm of \acs{JSFRA} scheme}
-	\label{algo-1} 
-\end{algorithm}
 
-The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}, which is in fact a \ac{DC} constraint.
-We resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using first order Taylor series approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
+The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
+Again we resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using the first order Taylor approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
 \begin{IEEEeqnarray}{rCl}
@@
 
-Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \review{\me{t_{l,k,n}}} for a fixed receive beamformer.
-The optimization subproblem to find the transmit precoders for a fixed receive beamformer \me{\mvec{w}{l,k,n}} is given by
+Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \review{\me{t_{l,k,n}}} for fixed receive beamformers.
+The optimization subproblem to find the transmit precoders for fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
@@
 \end{IEEEeqnarray}
-The optimal transmit precoders for a fixed receiver are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
+The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
 The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.

### 2015-07-20 Report/problem_formulation_intro.tex
updated with Nam changes (half cooked)

@@
 \end{equation}
-The above positivity constraint need to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.
+The above positivity constraint needs to be satisfied by \me{v_k} to avoid the excessive allocation of the resources.
 
-Before proceeding further, we show that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of norm \me{\ell_q} in the objective of \eqref{eqn-3}.
-Suppose that \me{t_k>Q_k} for certain \me{k} at the optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
+Before proceeding further, we show that the constraint in \eqref{rate_constraint_a} is handled implicitly by the definition of \me{\ell_q} norm in the objective of \eqref{eqn-3}.
+Suppose that \me{t_k>Q_k} for a certain \me{k} at the optimum, i.e., \me{-{v}_k=t_k-Q_k>0}.
 Then there exists \me{\delta_k>0} such that \me{-{v}^{\prime}_k=t^{\prime}_k-Q_k<-{v}_k} where \me{t^{\prime}_k=t_k-\delta_k}.
-Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a smaller objective which contradicts with the fact that the optimal solution has been obtained.
-The choice of the norm \me{\ell_q} used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as follows.
+Since \me{\|\tilde{\mbf{v}}\|_q=\| |\tilde{\mbf{v}}| \|_q=\||-\tilde{\mbf{v}}|\|_q}, this means that the newly created vector \me{\mbf{t}^{\prime}} achieves a strictly smaller objective which contradicts with the fact that the optimal solution has been obtained.
+The choice of \me{\ell_q} norm used in the objective function \cite{berry2004cross,qps_cioffi} alters the priorities for the queue deviation function as follows.
 \begin{itemize}
-\item \me{\ell_{1}} results in greedy allocation \textit{i.e}, emptying the queue of users with good channel conditions before considering the users with worse channel conditions.
+\item \me{\ell_{1}} norm results in greedy allocation \textit{i.e}, emptying the queue of users with good channel states before considering the users with worse channel conditions.
 As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
-\item \me{\ell_{2}} prioritizes users with a higher number of queued packets before considering the users with a smaller number of backlogged packets.
+\item \me{\ell_{2}} norm prioritizes users with a higher number of queued packets before considering the users with a smaller number of backlogged packets.
 For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
-\item \(\ell_{\infty} \) minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating the resources proportional to the number of backlogged packets.
+\item \(\ell_{\infty} \) norm minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating resources proportional to the number of backlogged packets.
 \end{itemize}

### 2015-07-20 Report/simulation_distributed.tex
before sending to nam and antti
updated with Nam changes (half cooked)

@@
 Fig.
-\ref{fig-d} compares the performances of the algorithms with the \ac{PL} varies uniformly between \me{[0,-6]} dB.
-Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets, \review{with} the queued packets for each user is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits.
-As discussed in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update.
+\ref{fig-d} compares the performances of the algorithms with the \ac{PL} varies uniformly between \me{[0,-6]} dB and each \ac{BS} serves \me{|\mc{U}_b| = 4} users.
+As discussed in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size \eqn{\rho^{(i)}}.
 Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
@@
 	\includegraphics[width=\columnwidth]{fig-9-3}
-	\caption{Impact of varying \me{q} in the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace}}
+	\caption{Impact of varying \me{q} on the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace} and \me{Q_k = [9,16,14,16,9,13,11,12]} bits}
 	\label{fig-d-3.1}
@@
 Fig.
-\ref{fig-d} compares the primal and the \ac{ADMM} solutions for the \ac{JSFRA} scheme using the \ac{SCA} and by \ac{MSE} relaxation using the number of backlogged packets.
-In between the \ac{SCA} updates, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables.
+\ref{fig-d} compares the performance of the \ac{JSFRA} schemes discussed in Sections \ref{sec-3.2.1} and \ref{sec-3.3} using primal and \ac{ADMM} approaches.
+For each \ac{SCA} update, the primal or the \ac{ADMM} scheme is performed for \me{J_{\max} = 20} iterations to exchange the respective coupling variables.
 The number of backlogged packets only at the \ac{SCA} points are marked in the figure.
-The performance of the distributed approaches are similar to the centralized schemes if the primal and dual updates are performed until convergence.
+The performance of the distributed approaches is similar to that of the centralized schemes if the distributed algorithms are allowed converge.
+However, in our simulations, we observe that \eqn{J_{\max} = 20} is sufficient for the \ac{ADMM} to converge.
 %In Fig.
@@
 Fig.
-\ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB.
-The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other schemes due to the greedy objective.
-The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}.
+\ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \ac{PL} chosen uniformly between \me{[0,-3]} dB.
+The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other schemes due to the greedy nature of the objective.
+The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in Section \ref{sec-4.3}.
 If used for \me{\ell_1} norm, the over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}.
@@
 	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 6} bits]{
-		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-3}
+		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-4}
 		\label{fig-review-time}

### 2015-07-20 Report/simulation_intro.tex
updated with Nam changes (half cooked)

@@
-The simulations carried out in this work consider the \ac{PL} varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples.
-The queues are generated based on the Poisson process with the average values specified in each section presented.
+The simulations carried out in this work consider the \ac{PL} varying uniformly across all users in the system with the small-scale fading drawn from the \textit{i.i.d.} samples.
+The queues are generated based on the Poisson process with the average values specified for each numerical experiments.
 \begin{table*}
@@
 	\centering
-	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
+	\subfloat[][System model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}, number of backlogged bits for each user \eqn{Q_k = [14,15,14,8,12,9,12,11,11]} bits]{
 		\includegraphics[width=0.5\textwidth]{fig-1-4}
 		\label{fig-1}}
-	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
+	\subfloat[][System model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}, number of backlogged bits for each user \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits]{
 		\includegraphics[width=0.5\textwidth]{fig-2-5}

### 2015-07-20 Report/simulation_results.tex
updated with Nam changes (half cooked)

@@
 To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
-The number of packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits, respectively.
+The total number of backlogged packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits, respectively.
 \begin{table}
@@
 
-Table \ref{tbl-1} tabulate the channels of the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the sub-channel wise \ac{Q-WSRM} scheme using the \ac{WMMSE} design \cite{wmmse_shi}.
+Table \ref{tbl-1} tabulates the channels of the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the sub-channel wise \ac{Q-WSRM} scheme using the \ac{WMMSE} design \cite{wmmse_shi}.
 The metric used for the comparison is the total number of backlogged bits left over after each transmission, which is denoted as \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
-Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} has equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} is scheduled in the first sub-channel due to the better channel condition.
+Even though \me{\mc{U}(1)} and \me{\mc{U}(3)} have equal number of backlogged packets of \me{Q_{1} = Q_{3} = 4} bits, user \me{\mc{U}(3)} is scheduled in the first sub-channel due to the better channel condition.
 In contrast, the \ac{JSFRA} approach assigns the first user on the first sub-channel, which reduces the total number of backlogged packets.
@@
 
-For a \ac{MIMO} scenario, we consider a system with \review{\me{N=4,2}} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
-The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the associations are made by selecting the \ac{BS} with the lowest \ac{PL} component.
+For a \ac{MIMO} setup, we consider a system with \review{\me{N=4} and \eqn{N=2}} sub-channels with \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
+The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the \ac{BS}-user associations are made by selecting the \ac{BS} with the lowest \ac{PL} component.
 Fig.
-\subref*{fig-1} shows the performance of the centralized schemes for a single receive antenna system.
-The total number of queued packets for Fig.
-\subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig.
-\subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
+\subref*{fig-1} and Fig.
+\subref*{fig-2} compares the performance of the centralized schemes for \eqn{N_R = 1} and \me{N_R = 2} receive antenna cases respectively.
+%The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.
 \begin{figure}
@@
 	\includegraphics[width=\columnwidth]{fig-3-2}
-	\caption{Convergence of the centralized and the distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace} using \me{\ell_1} norm for \ac{JSFRA} schemes}
+	\caption{Convergence of the centralized and the distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace} using \me{\ell_1} norm for \ac{JSFRA} schemes with \me{Q_k = [5,7,9,11,8,12,5,4]} bits}
 	\label{fig-d}
@@
 
-The comparison is made in terms of the total number of residual bits remaining in the system after each \ac{SCA} update in Fig.
-\ref{fig-a}.
-The \ac{Q-WSRM} algorithm is not optimal due to the problem of over-allocation when the number of queued packets are few in number.
+The comparison in Fig.
+\ref{fig-a} is made in terms of the total number of residual bits remaining in the system after each \ac{SCA} update.
+The \ac{Q-WSRM} scheme is not optimal due to the problem of over-allocation when the number of queued packets is small.
 In contrast, the \ac{Q-WSRME} algorithm provides better allocation with the explicit rate constraint to avoid the over-allocation.
@@
 \ref{fig-a}, the \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the algorithm, since the \ac{Q-WSRME} scheme favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
-Fig.
-\subref*{fig-2} compares the algorithms for \me{N_R = 2} receive antenna case.
-The receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} on all figures.
-However, degradation in the performance is marginal, since the receiver minimizes the objective for fixed precoders.
+Note that the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} for both Fig.
+\subref*{fig-1} and Fig.
+\subref*{fig-2}.
+However, the performance loss incurred by the combined update of the \ac{SCA} operating point and the receiver is marginal.
 

### 2015-07-20 Report/sub_channel_wsrm.tex
updated with Nam changes (half cooked)

@@
-The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of the interior point method, which is used to solve the problem, increases with the problem size.
+The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of an interior point method, which is used to solve the problem, increases with the problem size.
 Thus, we can use the decomposition methods presented in \cite{palomar2006tutorial,boyd2011distributed} to overcome this complexity by designing precoders for each sub-channels independently with minimal information exchange.
@@
 Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} while determining the precoders for the \eqn{\ith{i}} sub-channel.
-Since the precoder design is sequential, \textit{i.e}, the precoders are designed for sub-channels \me{[0,i-1]} before \me{\ith{i}} sub-channel, the number of backlogged packets for the initial sub-channel is initialized as \me{Q_{k,1} = Q_k}.
+Since the precoder design is sequential, \textit{i.e}, the precoders are designed for sub-channels \me{[0,i-1]} before the \me{\ith{i}} sub-channel, the number of backlogged packets for the initial sub-channel is initialized as \me{Q_{k,1} = Q_k}.
 The queues associated with the consecutive sub-channels are given by
@@
 \end{equation}
-where \me{t_{l,k,j}} is the \me{\ith{k}} user rate on the sub-channel \me{j}.
+where \me{t_{l,k,j}} is the \me{\ith{k}} user rate on sub-channel \me{j}.
 
-\review{Since the performance of the \ac{SRA} scheme is sensitive to sub-channel ordering, for simplicity we use random selection in all our simulations.
-We can also use greedy ordering by considering the channel norm associated with the user and the corresponding serving \ac{BS}, but this comes at the cost of increased complexity.
+\review{For simplicity we use random sub-channel ordering in our paper, \textit{i.e.}, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
+We can also use greedy ordering by considering the norm of the channel between a user and the corresponding serving \ac{BS}, but this comes at the cost of increased complexity.
 However, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the available multi-user diversity.}

### 2015-07-20 Report/system_model.tex
updated with Nam changes (half cooked)

@@
 Let \me{Q_k} be the number of backlogged packets destined for user \me{k} at a given scheduling instant.
-The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets/bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{\ith{i}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{\ith{(i+1)}} instant for user \me{k}, denoted as \me{Q_k(i+1)}, is given by
+The queue dynamics of user \me{k} are modeled using the Poisson arrival process with the average number of packet arrivals of \me{A_k = \mathbf{E}_i\{\lambda_k\}} packets or bits, where \me{\lambda_k(i) \sim \mathrm{Pois}(A_k)} represents the instantaneous number of packets arriving for user \me{k} at the \me{\ith{i}} time instant.\footnote{The unit can either be packets or bits as long as the arrival and the transmission units are similar.} The total number of queued packets at the \me{\ith{(i+1)}} instant for user \me{k}, denoted as \me{Q_k(i+1)}, is given by
 \begin{equation}

### 2015-07-20 Report/time_correlated.tex
updated with Nam changes (half cooked)

--- 2015-04-06 Report/time_correlated.tex
@@
 Fig.
-\subref*{fig-review} also includes the uncoordinated \me{\ell_1} \ac{JSFRA} scheme and the \ac{TDM} mode without considering the inter-cell interference terms in the \ac{SINR} expressions while designing the precoders.
-The \ac{TDM} scheme with the fixed total power constraint performs inferior to the uncoordinated transmission due to the diverse user \ac{PL} variations considered.
+\subref*{fig-review} also includes the uncoordinated \me{\ell_1} \ac{JSFRA} scheme and the \ac{TDM} mode, which ignores the inter-cell interference terms in the \ac{SINR} expressions while designing the precoders.
+The performance of the \ac{TDM} scheme with the total power constraint is inferior to the uncoordinated transmission due to the diverse user \ac{PL} variations in the system model.
 Fig.
-\subref*{fig-review-time} compares the total number of backlogged packets left in the system after each transmission slot by different centralized algorithms.
+\subref*{fig-review-time} compares the number of backlogged packets left in the system after each transmission slot by different centralized algorithms.
 The total number of residual packets for the \ac{Q-WSRM} scheme is noticeably large in comparison with the other schemes in Fig.
-\subref*{fig-review-time} due to the inability in controlling the over-allocations at each instant.
+\subref*{fig-review-time}.
+This performance loss is due to the inability in controlling the over-allocations at each instant.
 The instantaneous fairness constraint imposed by the \me{\ell_\infty} \ac{JSFRA} scheme is effective in reducing the number of backlogged packets for the average arrival rate considered in Fig.
@@
 However, in Fig.
-\subref*{fig-review}, the \me{\ell_\infty} \ac{JSFRA} performs inferior to the \ac{Q-WSRM} scheme, since the fairness is not effective when the system is unstable, \textit{i.e}, when \me{A_k \geq 7} in the current model.
+\subref*{fig-review}, the performance of the \me{\ell_\infty} \ac{JSFRA} is inferior to the \ac{Q-WSRM} scheme, since the fairness is not effective when the system is unstable, \textit{i.e}, when \me{A_k \geq 7} in the current model.

### 2015-07-20 Report/wsrm_formulation.tex
updated with Nam changes (half cooked)

@@
 In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables.
-Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}.
-We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers.
-For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task.
-We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
+Thus, we need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}.
+To this end, we resort to the \ac{AO} technique by fixing the linear receivers to solve for the transmit beamformers.
+For fixed receivers \me{\{\mvec{w}{l,k,n}\}}, \textit{i.e.}, we fix all receivers and not only the one related to \eqn{l,k,n}, the problem now is to find optimal transmit precoders \me{\{\mvec{m}{l,k,n}\}} which is still challenging.
+By using fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
 Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}.
@@
 \end{IEEEeqnarray}
-be a function, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{m}{l,k,n}, \mvec{w}{l,k,n},\beta_{l,k,n}\}} denotes the variables to be identified for an efficient allocation.
+be the r.h.s of \eqref{eqn-6.2}, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{m}{l,k,n}, \mvec{w}{l,k,n},\beta_{l,k,n}\}}.
 Note that the function \me{g({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{g({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred as \ac{SCA} in \cite{marks1978technical}.
+The nonconvex set defined by \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{g({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred to as \ac{SCA} in \cite{marks1978technical}.
 By using the reduced convex subset for \eqref{eqn-6.2}, the problem in \eqref{eqn-6} is solved iteratively by updating the operating point in each iteration.
 
-For this purpose, let the real and imaginary component of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
+For this purpose, let the real and imaginary components of the complex number \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}} be represented by
 \begin{IEEEeqnarray}{rCl} \label{eqn-wsrm-expr}  \neqsub
@@
 Now, the optimal receivers for fixed transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} are obtained by minimizing \eqref{eqn-6} w.r.t. \me{\mbf{w}_{l,k,n}} as
-\begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub
+\begin{IEEEeqnarray}{CCl}\label{eqn-9--1} \neqsub \allowdisplaybreaks
 \underset{\substack{\gamma_{l,k,n},\\ \mvec{w}{l,k,n},\beta_{l,k,n}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}} \|_q \IEEEyessubnumber\label{eqn-9--1.1a} \\
@@
 \end{IEEEeqnarray}
-where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex \ac{DC} constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}.
+where \me{\mvec{w}{l,k,n}^{(i-1)}} is the receive beamformer from the previous iteration, upon which the linear relaxation is performed for the nonconvex constraint  in \eqref{eqn-6.2}, as used in the formulation \eqref{eqn-9--1}.
 The optimal receiver \me{\mbf{w}^{o}_{l,k,n}} is obtained by either iterating \eqref{opt-rx} until convergence or for a fixed number of iterations.
@@
 \end{IEEEeqnarray}
-Since the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, the \ac{MMSE} receiver in \eqref{eqn-10} can also be used without compromising the performance.
+Note that the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, and therefore the \ac{MMSE} receiver in \eqref{eqn-10} can also be used.
+However, the rate of convergence might be different with the two receivers.
 
-\review{The proposed solution involves two nested iterations, \textit{i.e.}, one for the outer \ac{AO} loop denoted by \eqn{i} and the second for the inner \ac{SCA} loop represented by \eqn{j}.
-Each \ac{AO} loop involves two \ac{SCA} approaches performed until convergence, \textit{i.e.}, at first, the transmit precoders are identified by solving \eqref{eqn-9} iteratively for fixed receivers.
-In the second step, the receivers are updated with the previously found fixed transmit precoders by either solving \eqref{opt-rx} recursively or using the \ac{MMSE} receiver in \eqref{eqn-10}.
+\review{The proposed solution involves two nested iterations, \textit{i.e.}, one for the outer \ac{AO} loop and the second for the inner \ac{SCA} loop.
+Each \ac{AO} iteration involves two steps, one for finding transmit precoders by solving \eqref{eqn-9} iteratively until convergence for fixed receivers, and the other for updating the receive beamformers with the previously found fixed transmit precoders by either solving \eqref{opt-rx} recursively or by using \eqref{eqn-10}.
 
 Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}.
-Let \eqn{\{\mbf{m}^{(i)}_j, \mbf{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{j-1}} \ac{SCA} step.
-In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{j+1}} \ac{SCA} step is given by \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the optimal receiver obtained by solving \eqref{opt-rx} recursively or by using \eqref{eqn-10} from the \eqn{\ith{i-1}} \ac{AO} step.
-The \ac{SCA} updates are performed until \eqn{j \rightarrow \infty} or for \eqn{J_{\max}} number of iterations.
+Let \eqn{\{\mbf{m}^{(i)}_j, \mbf{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step.
+In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is given by \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained from the \eqn{\ith{(i-1)}} \ac{AO} step by either solving \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver in \eqref{eqn-10}.
+\begin{algorithm}
+	\SetAlgoLined
+	\DontPrintSemicolon
+	\BlankLine
+	\SetKwInput{KwInit}{Initialize}
+	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
+	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
+	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
+	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
+		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
+			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
+			update \me{\tilde{\mbf{u}}_{l,k,n}} and the constraint set \eqref{eqn-8} with the newly found \me{\mvec{m}{l,k,n}} and \me{\mvec{\beta}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
+			$j = j + 1$\;
+		}
+		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
+		$i = i + 1$, \me{j = 0}\;
+	}
+	\caption{Algorithm of \acs{JSFRA} scheme}
+	\label{algo-1} 
+\end{algorithm}
 
-Upon convergence of the transmit precoders, the receivers are updated in a similar manner by solving \eqref{eqn-9--1} recursively until \eqn{j \rightarrow \infty} or by using the \ac{MMSE} receiver in \eqref{eqn-10} with the fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\ast}} obtained from the previous \ac{SCA} step.
-Once the receivers are obtained, the transmit precoders are again updated by solving \eqref{eqn-9} recursively with the newly found receivers fixed for an operating point.
+Upon convergence of the transmit precoders, the receivers are updated using the fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\ast}} obtained from the previous \ac{SCA} step.
+Once the receive beamformers are obtained, the transmit precoders are again updated by solving \eqref{eqn-9} recursively with the newly found receivers.
 The above procedure is repeated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations.
-The overall iterative approach is outlined in Algorithm \ref{algo-1}.
+The iterative approach is outlined in Algorithm \ref{algo-1}.
 
@@
 
-Even though the iterative approach in Algorithm \ref{algo-1} converges in all our numerical simulations, in order to ensure the theoretical convergence of the iterates to a stationary point, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of \eqref{eqn-6.1} due to better convergence properties.
-The convergence analysis is given in Appendix \ref{sec-3.5}.}
+Even though the iterative approach in Algorithm \ref{algo-1} converges in all our numerical simulations, in order to provide an analytical convergence proof of the iterates to a stationary point, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of \eqref{eqn-6.1}.
+The convergence proof for the centralized solutions is provided in Appendix \ref{sec-3.5}.}
 \begin{comment}

### 2015-07-20 Response/Response 2/additions.tex
updated with Nam changes (half cooked)

@@
 
-In what follows, the comments are listed, each followed by the corresponding reply from the authors.
+In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors.
+The reviewers questions in the revised manuscript are highlighted in blue color and the authors responses are presented in black.
 Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript.

### 2015-07-20 Response/Response 2/document.tex
updated with Nam changes (half cooked)

@@
 
+\renewcommand{\thefigure}{\Roman{figure}}
+%\renewcommand{\thesubfigure}{\Roman{figure}}
+\renewcommand{\theequation}{\roman{equation}}
+
 \begin{document}
@@
 The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality.
-Based on the comments, we have made several major revisions to the paper, following the suggestions of the reviewers.
-In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors.
-The reviewers questions in the revised manuscript are highlighted in blue color and the authors responses are presented in black.
-Following is the summary of the revision made on the manuscript in accordance with the reviewers comments.
+Based on the comments, we have made several major revisions to the paper, which is summarized below.
 \input{additions}

### 2015-07-21 Report/conclusions.tex
finalized

@@
 We have proposed the \ac{JSFRA} scheme by relaxing the nonconvex constraint by a sequence of convex subsets using the \ac{SCA} for designing the precoders to minimize the total number of user queued packets.
-Additionally, an alternative \ac{MSE} reformulation approach has been proposed by using the \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers.
+Additionally, an alternative \ac{MSE} reformulation approach has been proposed by using the \ac{SCA} to address the nonconvex constraints for a fixed \ac{MMSE} receivers.
 We also proposed various methods to decentralize the precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods.

### 2015-07-21 Report/convergence_centralized.tex
finalized

@@
 To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,yang_yang} by relaxing the nonconvex set by a sequence of convex subsets.
-Since it involves two nested iterations, we denote the \ac{AO} iteration index by a superscript \me{(i)} and the \ac{SCA} step by a subscript \me{k}.
+Since it involves two nested iterations, we denote the \ac{AO} step index by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}.
 Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}.
@@
 	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
-	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + \frac{c}{2} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + \tfrac{c}{2} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
 \end{IEEEeqnarray}
@@
 \review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique.
-Using this and the fact that the sequence of objectives is nondecreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.
+Using this and the fact that the sequence of objectives is nonincreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.
 However, note that the limit point need not be a stationary point of \eqref{con} since the receive beamformers \eqn{\my} have been fixed.}
@@
 
-Once the solution is found for a fixed \me{\my}, it is then optimized by fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}}.
-Even after treating \me{\mx} as a constant, the problem is nonconvex due to the \ac{DC} constraint.
-Following similar approach as above, we can find a minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} for a similar convex subproblem \eqref{con-m} at each iteration \me{{k}}.
+Once \me{\iter{\mx}{\ast}{i}} is found for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}.
+However, after fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}.
+Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively.
 Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the objective follow similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the converged \ac{SCA} subproblems with \me{\my} as a variable is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}}, which is the minimizer in the feasible set \me{\iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
+The sequence convergence and the nonincreasing behavior of the objective follow similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the sequence of iterates generated by iteratively solving \eqref{con-m} is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\} \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
 
-Finally, to prove the global convergence of the iterative algorithm, we need to show the \ac{AO} updates also produce a nondecreasing sequence of objectives, \textit{i.e.}, 
+Finally, to prove the global convergence of the iterative algorithm, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
 \iftoggle{single_column}{
@@
 
-\review{Note that the \ac{AO} and \ac{SCA} iterative procedures generates a nonincreasing sequence of objectives for the original function in \eqref{orig_obj} using the above discussions.
-However, by using the regularized objective in \eqref{mod_obj}, we can show that the sequence of objectives provided by \ac{AO} and \ac{SCA} steps is strictly increasing.
-Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step.
-In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj}.
-%We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} \ac{SCA} step \cite{marks1978technical}.
-It follows by the strong convexity of \eqref{mod_obj} with \eqn{m > 0} in the \eqn{\ith{k}} update
+\review{Using the above discussions, the monotonicity of the objective seqeunce is guaranteed in each \ac{AO} and \ac{SCA} updates.
+However, to ensure strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{m > 0}.
+Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step.
+At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
+\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
+\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
+f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
+\end{IEEEeqnarray}
+since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
+Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds at each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}.
+Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured.
+However, if \eqn{\hat{f}} is used instead of \eqn{f} in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to multiple solutions.
+
+Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update.
+It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.}
+
+\begin{comment}
+
 \begin{equation} \label{strict_monotonicity}
-f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + m \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
+f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
+\end{equation}
+
+Note that the \ac{AO} and \ac{SCA} procedures generate a nonincreasing sequence of objectives for the original objective in \eqref{orig_obj} using the above discussions.
+However, by using the regularized objective in \eqref{mod_obj}, we can show that the sequence of objectives provided by \ac{AO} and \ac{SCA} steps is strictly decreasing.
+Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} \ac{SCA} step.
+Note that the objective \eqref{con-obj-m} is strongly convex with some parameter \eqn{m > 0}, and therefore \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}
+\begin{IEEEeqnarray}{l}
+f(\mbf{z}) \geq f(\iter{\mbf{z}}{k+1}{i}) + \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) + \tfrac{m}{2} \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2. \eqspace 
+\end{IEEEeqnarray}
+Since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer for \eqref{con-m} in the \eqn{\ith{k}} \ac{SCA} step, 
+\begin{IEEEeqnarray}{rCl} \neqsub \label{s_ineq_g}
+\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0, \quad \iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i} \eqsub \\
+f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}\|^2. \eqsub \label{s_ineq}
+\end{IEEEeqnarray}
+Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}.
+Using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{s_ineq_g}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured.
+However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.
+
+	In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj} with parameter \eqn{m > 0} as %We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} \ac{SCA} step \cite{marks1978technical}.
+	%It follows by the strong convexity of \eqref{mod_obj} with \eqn{m > 0} in the \eqn{\ith{k}} update
+	\begin{equation} \label{strict_monotonicity}
+	f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \underbrace{\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i})}_{= 0} + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
 	\end{equation}
@@
 However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.
-
-Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update.
-Since \eqn{\iter{\mbf{z}}{\ast}{i}} is also included in the set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} strictly unless the overall sequence \eqn{\{\mbf{z}_{\ast}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}
-
-\begin{comment}
 
@@
 \subsection{Convergence of the Beamformer Iterates} \label{c-b}
-Let \me{\ma \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
+Let \me{\ma^{(i)} \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
 \begin{equation} \label{g-algo}
@@
 2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that the limit point of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of \eqref{con}.}
+3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the original nonconvex problem in \eqref{con}.}
 

### 2015-07-21 Report/convergence_distributed.tex
finalized

@@
 
-\review{To show the convergence of \ac{ADMM} approach, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
+\review{To show the convergence of \ac{ADMM}, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 \end{IEEEeqnarray}
-the following conditions are required for the convergence.
-\begin{itemize} \allowdisplaybreaks
-	\item \me{G,H} should be convex
-	\item \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded
-	\item \me{\mbf{A}^\herm \mbf{A}} should be invertible.
-\end{itemize}
-Note that the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}.
-It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is an identity matrix and is invertible.
-The objective function \me{G,H} includes \me{\ell_q} norm with an additional quadratic term as in \eqref{mod_obj}, and therefore exhibits strong convexity.
-The set defined by the constraints of the problem \eqref{eqn-decent-1} is convex and has a nonempty interior.
-The feasibility of the interior point can be verified by having a non-zero precoder for only one user.
+where the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
+To show the convergence, we rely on the following conditions.
+(i) \me{G,H} should be convex.
+(ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded.
+(iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible.
+It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is invertible.
+The objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, and therefore exhibits strong convexity.
+The feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior.
 Therefore, by following \cite[Prop.
-4.2]{bertsekas1989parallel}, it can be shown that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size as discussed in \cite{boyd2011distributed}.
-The distributed algorithms also converges to a stationary point of the original nonconvex problem by following Appendix \ref{sec-3.5}, if the \ac{ADMM} is iterated until convergence in each \ac{SCA} step.}
+4.2]{bertsekas1989parallel} and \cite{boyd2011distributed}, it can be shown that \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size.
 
-\review{However, if the distributed algorithms are terminated well before the convergence or performed for limited number of iterations, convergence of the algorithm is not guaranteed.
-Since each update of \eqn{\mbf{x}^{(i)}} involves two \ac{SCA} updates until convergence with limited distributed iterations, the monotonicity of the objective and hence the convergence of the iterates is not guaranteed, unless the number of iterations is large enough to ensure strictly decreasing objective.
-It follows from the fact that in each primal or \ac{ADMM} update, the global objective is not guaranteed to be monotonically decreasing, despite reaching the centralized solution upon convergence.}
+If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence is a stationary point of \eqref{con}, using Appendix \ref{sec-3.5}.
+However, if the distributed algorithms are terminated well before the convergence or performed for few number of iterations, say, \eqn{J_{\max}}, then the convergence of the iterates \me{\{\ma^{(i)}\}} is not guaranteed.
+It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
+However, if the distributed schemes for \eqref{con-m} are updated for sufficient number iterations to ensure strict monotonicity in each \ac{SCA} step, then the limit point of \me{\{\ma^{(i)}\}} is a stationary point of \eqref{con}, which can be different from the one obtained by solving \eqref{con-m} with \eqn{J_{\max} = \infty}.}
+
+%\review{However, if the distributed algorithms are terminated well before the convergence or performed for limited number of iterations, say, \eqn{J_{\max}}, the convergence of the sequence \me{\{\ma^{(i)}\} \triangleq \{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is not guaranteed.
+It follows from the fact that in each primal or \ac{ADMM} update, the global objective is not guaranteed to be monotonically decreasing, despite reaching the centralized solution upon convergence.
+If the distributed algorithm is iterated sufficient number of times to ensure strict monotonicity of the objective in each \ac{SCA} step with the modified function \eqref{mod_obj}, then the limit point of the convergent sequence is a stationary point of \eqref{con}, which can be different from the limit point obtained by solving the centralized solution.}
 
@@
 Therefore, the convergence of the Algorithm \ref{algo-4} to a stationary point of \eqref{eqn-mse-1} is not guaranteed.
-In addition, due to the convexity of the objective in \eqref{eqn-mse-1}, the sequence of iterates generated by Algorithm \ref{algo-4} need not be a convergent one.} However, the objective converges in all numerical experiments considered in Section \ref{sec-5.2}.
+In addition, due to the convexity of the objective in \eqref{eqn-mse-1}, the sequence of iterates generated by Algorithm \ref{algo-4} need not be convergent.} However, the objective converges in all numerical experiments considered in Section \ref{sec-5.2}.
 

### 2015-07-21 Report/wsrm_formulation.tex
finalized

@@
 To this end, we resort to the \ac{AO} technique by fixing the linear receivers to solve for the transmit beamformers.
-For fixed receivers \me{\{\mvec{w}{l,k,n}\}}, \textit{i.e.}, we fix all receivers and not only the one related to \eqn{l,k,n}, the problem now is to find optimal transmit precoders \me{\{\mvec{m}{l,k,n}\}} which is still challenging.
-By using fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
-Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}.
+For fixed receivers \me{\mvec{w}{l,k,n}}, \textit{i.e.}, by fixing the receive beamformers of all users in the system, the problem now is to find optimal transmit precoders \me{\mvec{m}{l,k,n}} which is still a challenging task.
+Now, by fixing \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint.
+Thus, the difficulty is due to the non-convexity of the constraint in \eqref{eqn-6.2}.
 Let
@@
 }
-In summary, for fixed receivers \me{\tilde{\mbf{w}}_{l,k,n}} and \me{\tilde{\mbf{u}}_{l,k,n}}, the relaxed convex subproblem for finding transmit precoders is given by
+In summary, for fixed receivers \me{\tilde{\mbf{w}}_{l,k,n}} and operating point \me{\tilde{\mbf{u}}_{l,k,n}} as in \eqref{eqn-8}, obtained by using \eqref{eqn-wsrm-expr}, the relaxed convex subproblem for finding transmit precoders is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-9} \neqsub

### 2015-07-25 Response/Response 2/response-1.tex
to read

@@
 
-\resp After a careful check of the manuscript, we have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results section) to provide additional details for the convergence proof.
+\resp After a careful check of the manuscript, we have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results) to provide additional details for the convergence proof.
 We believe the removed parts do not affect the readability of the paper and the added text regarding convergence proof certainly improves the quality.
@@
 \resp We thank the reviewer for the critical comment.
-It is not possible to comment on the inclusion of the previous constraint set in the current update (except the earlier optimal point), the inequality is not guaranteed.
-Based on the comment from the reviewer, we have removed the inequality specifying the previous operating point from (49) in the revised manuscript, since it cannot be guaranteed.
+Based on the comment by the reviewer, we have removed the additional inequality relating the previous operating point from (49) in the revised manuscript.
 
@@
 
-\resp  We thank the reviewer for citing this issue on the sequence convergence.
-Even though the objective of the \ac{SCA} iteration converges, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge.
-It is true that the iterates need not converge when the objective function is convex.
-However, we have modified the discussion by using the strong convexity of the objective function to impose the uniqueness of the iterates in each \ac{SCA} update.
+\resp  We thank the reviewer for citing the issue regarding the sequence convergence.
+Even though the objective converges in each \ac{SCA} update, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge.
+It follows from the convexity of the original function, which can have multiple solutions.
+However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [31] and [32], which ensures the uniqueness of the solution in each \ac{SCA} update.
 
 Since our problem is (highly) nonconvex and there are possibly many stationary points.
-If we start from different initial points, we may end up at different stationary points.
+If we start from different initial points, we may end up with different stationary points.
 That is to say, the limit point of \ac{SCA} approach is not unique.
@@
 This and the fact that the set is compact ensure the \ac{SCA} converges to a limit point.
-We have updated the manuscript to include this information in the convergence proof in Appendix A-B around (46) and in Appendix A-C.
+We have updated the manuscript to include this information in the convergence proof for the centralized algorithm in Appendix A.
+The modifications are included in Appendix A-B around (46) and in Appendix A-C after (50).
 
@@
 As suggested by the reviewer, we have included the strict monotonicity of the objective sequence in Appendix A-C following (52).
-In addition, we also have noted the reader that we in fact use the regularized objective in (52) to analytically prove the convergence of iterates, although we have numerically observed that the iterates of Algorithm 1 (with the original objective) always converge.
+Moreover, we have also noted the reader that we in fact use the regularized objective in (46b) to analytically prove the convergence of iterates, although we have numerically observed that the objective sequence of Algorithm 1 (with the original objective) always converge.
 Please refer to the paragraph before Section III-C.

### 2015-07-25 Response/Response 2/response-2.tex
to read

@@
 
-\resp We apologize for not clarifying the sub-channel ordering in a detailed manner in the previous manuscript.
+\resp We apologize for not clarifying the sub-channel ordering in detail in our previous manuscript.
 For simplicity we use random sub-channel ordering in our paper.
 That is, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
-
-As suggested by the reviewer, the greedy sub-channel ordering is based on sorting the best channel gain from each sub-channel, which is obtained by finding the highest channel norm between the users from the respective serving base station (BS).
+As suggested by the reviewer, the greedy sub-channel ordering can also be considered while selecting the order.
+The greedy ordering can be based on sorting the best channel gain from each sub-channel, which is obtained by finding the highest channel norm seen between any user and the corresponding serving \ac{BS}.
 
@@
 We have emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user.
-Even though we are not including it in the paper, we have included in the response letter to answer the reviewer's question.
+Even though we are not including it in the paper, we have included in the response letter to answer the reviewers' question.
 We considered a system with \eqn{N = 4} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users.
@@
 As can be seen from Fig.
-\ref{fig-review-1a}, the greedy sub-channel ordering provides a favorable way of choosing the sub-channels to minimize the total number of backlogged packets.
+\ref{fig-review-1a}, the greedy sub-channel ordering provides a favorable way of choosing sub-channels to minimize the total number of backlogged packets.
 However in Fig.
-\ref{fig-review-1b}, the greedy sub-channel ordering is no longer efficient.
+\ref{fig-review-1b}, it is evident that the greedy sub-channel ordering is no longer better in comparison with the few other random ordering schemes.
 We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic method under Section III-D final paragraph.
-Note that as the number of users in the system increases, all channel ordering provides favorable order to minimize the total number of backlogged packets in the system.
+However, as the number of users in the system increases, all sub-channel ordering are similar in minimizing the total number of backlogged packets in the system without any noticeable gain.
 
@@
 
-		In order to quantify the total number of bits required in a centralized solution, let us assume that each complex channel for a single-input single-output requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is more important) or it can be a equal share of \eqn{5} bits for both amplitude and phase.
+		In order to quantify the total number of bits required in a centralized solution, let us assume that each complex channel for a \ac{SISO} model requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is more important) or it can be a equal share of \eqn{5} bits for both amplitude and phase.
 Using this assumption, the total amount of channel information in bits to be exchanged via backhaul is \eqn{10 \times K \times N_B \times N_R \times N_T = 320} bits.
@@
 
-		In the above example, for the same amount of signaling overhead as in centralized method, we can performance only up to 6 SCA updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for ADMM part).
+		In the above example, for the same amount of signaling overhead as in centralized method, we can perform only up to 6 \ac{SCA} updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for \ac{ADMM} part).
 This may not be sufficient for the distributed algorithms to attain the same performance as the centralized method.
-However, as the number of sub-channels, users and/or the antenna element increases, it may not be a feasible option to feedback the \ac{CSI} across the coordinating \acp{BS} to the centralized controller in the current cellular systems.
-In addition to comparing the signaling overhead, we also need to consider the effects of the quantization of the \ac{CSI} on the performance of a centralized algorithm, which is beyond the scope of our paper.
-Generally, the performance is significantly degraded if the \ac{CSI} is quantized [R1].
-Moreover, in the centralized algorithm, resulting transmit precoders need to be exchanged with the corresponding \acp{BS} before the actual transmission, involving huge overhead in the backhaul.
+However, as the number of sub-channels, users and/or the antenna element increases, it may not be a feasible option to feedback all \acp{CSI} across the coordinating \acp{BS} to the centralized controller in the current cellular systems.
+In addition to comparing the signaling overhead, we also need to consider the performance loss due to \ac{CSI} quantization in the centralized approaches, which is beyond the scope of our paper.
+Generally, the performance is significantly degraded if precoders are designed with the quantized \ac{CSI} as discussed in [R1].
+Moreover, in the centralized algorithm, resulting transmit precoders need to be exchanged with the corresponding \acp{BS} before the actual transmission, which involves significant overhead in the backhaul usage.
 
 		\vspace{1eM}
-		[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti Tölli, Markku Juntti,  and Savo Glisic, "\emph{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}," \textit{IEEE Trans.
+		[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti Tölli, Markku Juntti,  and Savo Glisic, "\emph{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}'', \textit{IEEE Trans.
 Signal Process}., vol 61, no.
@@
 
-		\item From the above discussions we can see that \ac{ADMM} and primal approach require significant overhead compared to a centralized algorithm for a small system.
-For a system involving more coordinating \acp{BS}, users and antenna elements, it would be beneficial to use the proposed distributed algorithms with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
+		\item From the above discussions, we can see that \ac{ADMM} and primal schemes require significant overhead compared to the centralized algorithms for a small system.
+However, for a system involving more coordinating \acp{BS}, users and antenna elements, it would be beneficial to use the proposed distributed algorithms with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
 If we set \eqn{J_{\max} = 1}, the convergence of the proposed algorithms is not guaranteed as shown in Fig.
-\ref{fig-review-2-a}, which has same system model as that of Fig.
+\ref{fig-review-2-a}.
+The system model considered is the same as used for Fig.
 \ref{fig-review-1a}.
@@
 
-	We have included the above discussions in the first and last paragraphs of Section IV-C, and the paragraph before Section VI (i.e., the conclusion section).
+	The above discussions are included in the first and the last paragraph of Section IV-C.
+
 	In reality, since the channel is time-correlated, it is enough to update the precoders once per radio frame.
@@
 Instead, the decentralized parts only need to follow the fading process when \eqn{J_{\max} > 1}.
-
-	The performance of the distributed algorithm based on dual decomposition scheme was discussed for the time-correlated fading in Section C of [13], which showed that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+The performance of the distributed algorithm based on dual decomposition scheme was discussed for the time-correlated fading in Section C of [12], which showed that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
 Studying the performance of distributed algorithms for the time correlated case is beyond the scope of our paper and thus is not considered in the current manuscript.
@@
 The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.\footnote{Please refer to [27] for further details.} We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the required information for \eqn{J_{\max} = 3,5,10}.
-The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{J_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{J_{\max}}{N_S})} is considered as a penalty involved due to the precoder exchange.
+The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{J_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{J_{\max}}{N_S})} is considered as a penalty involved due to the precoder exchange as discussed in [R2] and [R3].
 The average number of backlogged packets after each transmission slot is evaluated as
@@
 
+	\vspace{1eM}
+	[R2] Muhammad-Fainan Hanif, Le-Nam Tran, Antti T\"{o}lli, Markku Juntti,  and Savo Glisic, "\emph{Bi-directional Training for Adaptive Beamforming and Power Control in Interference Networks},'' \textit{IEEE Trans.
+Signal Process}., vol 62, no.
+3, pp.
+607--618, Feb.
+2014.
+
+	[R3] P.
+Jayasinghe, A.
+T\"{o}lli, J.
+Kaleva,  M.
+Latva-aho, "\emph{Bi-directional Signaling for Dynamic TDD with Decentralized Beamforming}'', in \textit{Proceedings of IEEE ICC SmallNets Workshop}, London, UK, June, 2015
+	\vspace{1eM}
+
 \cmnt{3} \review{If the authors can't prove the convergence of the ADMM algorithm (or the decomposition approach via KKT conditions) in Section IV.B, then at least, you should discuss the property of the fixed point of the algorithm.
@@
 In our paper the number of updates for the \ac{ADMM} part is denoted by \eqn{J_{\max}}.
-There is a trade-off between signaling overhead and achieved performance by varying \eqn{J_{\max}}.
+There is a trade-off between signaling overhead and achievable performance by varying \eqn{J_{\max}}.
 In reality we may set \eqn{J_{\max}} to a finite value to reduce the signaling overhead.
@@
 
-We have updated the manuscript to clarify the points mentioned above.
-Please refer to Section IV-B in the revised manuscript.
-For reference purpose, we have also referred the interested reader to [11], which discusses exclusively about the ADMM approach.
+We have updated the manuscript to clarify all the points mentioned above.
+Please refer to Section IV-B last paragraph after (40) in the revised manuscript.
+Additional information regarding the convergence of the distributed algorithms is provided in Appendix B second paragraph.
+The discussion on the convergence of the KKT based approach for MSE reformulation scheme is also presented in Appendix B last paragraph.
+For reference purpose, we have also referred the interested reader to [10], which discusses exclusively about the ADMM approach.
 

### 2015-07-25 Response/Response 2/response-3.tex
to read

@@
 \resp We thank the reviewer for the comment.
-We have included additional information on how to choose the operating point while initializing the iterative algorithm.
-It is written in the fourth paragraph following (23).
+We have included additional material on how to choose the operating point while initializing the iterative algorithm.
+It is described briefly in the fourth paragraph following (23).
 We have also provided a detailed discussion on how to update the operating point after each iteration in the paragraph following (23).
-Note that the objective function is convex, and therefore we can update operating point for the current step with the solution obtained in the previous iteration as
+Since the objective function is convex, we can update the current operating point with the solution obtained from the previous iteration as
 \begin{equation}
-\tilde{\mbf{m}}_{j}^{(i)} = \mvec{m}{j}^{(i)}
+\tilde{\mbf{m}}_{j}^{(i)} = \mvec{m}{j}^{(i)}.
 \end{equation}
-where \eqn{\tilde{\mbf{m}}_{j}^{(i)}} denotes the operating point for the \eqn{\ith{j+1}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step and \eqn{\mbf{m}_{j}^{(i)}} is the solution obtained by solving (20) in the \eqn{\ith{j}} \ac{SCA} iteration.
+Note that \eqn{\tilde{\mbf{m}}_{j}^{(i)}} is the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step and \eqn{\mbf{m}_{j}^{(i)}} is the solution obtained by solving (20) in the \eqn{\ith{j}} \ac{SCA} iteration.
 
@@
 The choice of selecting \eqn{\ell_q} norm is discussed in Section II-B last paragraph.
-The above information is included in the paragraph before the simulations section in Section IV.
+The above information is included in Section IV last paragraph, \textit{i.e.}, before the simulations section.
 
@@
 
-	\resp It has been rewritten to improve the readability as suggested by the reviewer. We have included the reference [28] for more illustrative discussions on the backhaul signaling.
+	\resp It has been rewritten to improve the readability as suggested by the reviewer.
 

### 2015-07-25 Report/convergence_centralized.tex
to read

@@
 Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th.
-3.14]{rudin1964principles}, we can show that the bounded monotonically decreasing objective value sequence has a unique minimum.
+3.14]{rudin1964principles}, we can show that the bounded and strictly decreasing objective sequence has a unique minimum in the feasible set.
 Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limit point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
@@
 To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}.
-In \eqref{con}, even after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}.
-To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,yang_yang} by relaxing the nonconvex set by a sequence of convex subsets.
-Since it involves two nested iterations, we denote the \ac{AO} step index by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}.
-Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when the \ac{SCA} iteration converges in the \me{\ith{i}} \ac{AO} iteration and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} obtained in the \me{\ith{i}} \ac{AO} iteration for a fixed \me{\my}.
-Let \eqn{\mx_k^{(i)}} denotes the stacked transmit precoders of all users at the \eqn{\ith{k}} \ac{SCA} step in the \eqn{\ith{i}} \ac{AO} iteration.
+However, after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}.
+To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,scutari-1} by relaxing \eqref{con-dc} by a sequence of convex subsets.
+Since it involves two nested iterations, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}.
+Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when \ac{SCA} converges in the \me{\ith{i}} \ac{AO} step and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} in the \me{\ith{i}} \ac{AO} step for fixed \me{\my}.
+The stacked transmit precoders of all users in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} is given by \eqn{\mx_k^{(i)}}.
 
@@
 \subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
-The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} are guaranteed for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
-However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness is not guaranteed since there can be many solutions satisfying the constraints with the same objective value.
-Similarly, when the objective is non-zero for  \eqref{eqn-9}, the minimizer is unique, if the receivers are matched to the corresponding transmit beamformers.
+The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
+However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set.
+Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers.
 %, \textit{i.e.}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.
@@
 	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
-	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + \tfrac{c}{2} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
 \end{IEEEeqnarray}
-where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c > 0} is a positive constant to ensure strong convexity in the objective, and therefore guarantees the unique minimizer \cite{yang_yang}.
+where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c_{k}^{(i)} > 0} is a positive constant to ensure strong convexity of the objective with some parameter \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} and \eqn{m > 0} as discussed in \cite{scutari-1}.
+Now by using the strong convexity of the modified objective in \eqref{mod_obj}, we can guarantee the uniqueness of the minimizer in each \ac{SCA} step \eqn{k} \cite{yang_yang,scutari-1}.
 Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}
@@
 The uniqueness of the iterates for the problem in \eqref{eqn-9} can be guaranteed in each convex subproblem if the receivers are matched to the equivalent downlink channel with the initially chosen feasible transmit precoders, \textit{i.e.}, \me{q_{l,k,n} = 0 \: \forall \, l,k,n} in \eqref{eqn-wsrm-expr} while beginning the \ac{SCA} iteration.
-%
+%of the objective
 %When the objective is zero, the uniqueness of  the transmit and the receive beamformers are not guaranteed in both problem formulations, since they are the under-estimators and need not be active at the minimum.
@@
 
-To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value achieved from the previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
+To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
 In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
@@
 Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfies \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}.
-(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the \ac{DC} constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
+(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
 \begin{equation} \label{rhs_equiv}

### 2015-07-25 Report/convergence_distributed.tex
to read

@@
 
-\review{To show the convergence of \ac{ADMM}, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} by writing the problem as
+\review{To show the convergence of \ac{ADMM}, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing the problem as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is invertible.
-The objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, and therefore exhibits strong convexity.
-The feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior.
-Therefore, by following \cite[Prop.
-4.2]{bertsekas1989parallel} and \cite{boyd2011distributed}, it can be shown that \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size.
+The objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity.
+Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior.
+Now, by using \cite[Prop.
+4.2]{bertsekas1989parallel}, we can show that \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size.
+If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence generated by the distributed methods is a stationary point of \eqref{con}, using similar arguments in Appendix \ref{sec-3.5}.
+}
 
-If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence is a stationary point of \eqref{con}, using Appendix \ref{sec-3.5}.
+%However, if the distributed algorithms are terminated well before the convergence or performed for few number of iterations, say, \eqn{J_{\max}}, then the convergence of the iterates \me{\{\ma^{(i)}\}} is not guaranteed.
+It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
+However, if the distributed schemes for \eqref{con-m} are updated for sufficient number iterations to ensure strict monotonicity in each \ac{SCA} step, then the limit point of \me{\{\ma^{(i)}\}} is a stationary point of \eqref{con}, which can be different from the one obtained by solving \eqref{con-m} with \eqn{J_{\max} = \infty}.}
+%\review{However, if the distributed algorithms are terminated well before the convergence or performed for limited number of iterations, say, \eqn{J_{\max}}, the convergence of the sequence \me{\{\ma^{(i)}\} \triangleq \{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is not guaranteed.
+It follows from the fact that in each primal or \ac{ADMM} update, the global objective is not guaranteed to be monotonically decreasing, despite reaching the centralized solution upon convergence.
+If the distributed algorithm is iterated sufficient number of times to ensure strict monotonicity of the objective in each \ac{SCA} step with the modified function \eqref{mod_obj}, then the limit point of the convergent sequence is a stationary point of \eqref{con}, which can be different from the limit point obtained by solving the centralized solution.}
+%If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence is a stationary point of \eqref{con}, using Appendix \ref{sec-3.5}.
 However, if the distributed algorithms are terminated well before the convergence or performed for few number of iterations, say, \eqn{J_{\max}}, then the convergence of the iterates \me{\{\ma^{(i)}\}} is not guaranteed.
@@
 However, if the distributed schemes for \eqref{con-m} are updated for sufficient number iterations to ensure strict monotonicity in each \ac{SCA} step, then the limit point of \me{\{\ma^{(i)}\}} is a stationary point of \eqref{con}, which can be different from the one obtained by solving \eqref{con-m} with \eqn{J_{\max} = \infty}.}
-
-%\review{However, if the distributed algorithms are terminated well before the convergence or performed for limited number of iterations, say, \eqn{J_{\max}}, the convergence of the sequence \me{\{\ma^{(i)}\} \triangleq \{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\}} is not guaranteed.
-It follows from the fact that in each primal or \ac{ADMM} update, the global objective is not guaranteed to be monotonically decreasing, despite reaching the centralized solution upon convergence.
-If the distributed algorithm is iterated sufficient number of times to ensure strict monotonicity of the objective in each \ac{SCA} step with the modified function \eqref{mod_obj}, then the limit point of the convergent sequence is a stationary point of \eqref{con}, which can be different from the limit point obtained by solving the centralized solution.}
-
 %Since each update of \eqn{\mbf{x}^{(i)}} involves two \ac{SCA} updates until convergence with limited distributed iterations, the monotonicity and the convergence of the objective is not guaranteed unless the number of iterations is large enough to have strictly decreasing objective.
@@
 \review{Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
-Therefore, the convergence of the Algorithm \ref{algo-4} to a stationary point of \eqref{eqn-mse-1} is not guaranteed.
-In addition, due to the convexity of the objective in \eqref{eqn-mse-1}, the sequence of iterates generated by Algorithm \ref{algo-4} need not be convergent.} However, the objective converges in all numerical experiments considered in Section \ref{sec-5.2}.
+Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed.
+Moreover, note that the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the iterates are not unique in each update.
+Due to this reason, the algorithm cannot find a fixed point to ensure the convergence of the beamformer iterates.}
 

### 2015-07-25 Report/decomposition_solutions.tex
to read

@@
-The distributed precoder designs for the proposed \ac{JSFRA} scheme are discussed in this section.
-The convex formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
-In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are based on the \acl{PD} and the \ac{ADMM} are considered herein.
+In this section, we discuss the distributed precoder designs for the solutions in Sections \ref{sec-3.2.1} and \ref{sec-3.3} for \eqref{eqn-6}.
+Note that the convex formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the \acp{BS} in \eqn{\mc{B}}.
+In order to design the precoders independently at each \ac{BS} with a minimal information exchange via backhaul, iterative decentralization methods based on the \acl{PD} and the \ac{ADMM} are considered herein.
 
-Let us consider the convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint.
+Let us consider the convex subproblem with fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the \ac{SINR} relaxation for the nonconvex constraint in \eqref{eqn-6.2}.
 The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well.

### 2015-07-25 Report/dual_approach.tex
to read

--- 2015-06-23 Report/dual_approach.tex
@@
 The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}.
-For our simulation models, we consider step size parameter \me{\rho=2}.
-The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates.
-The distributed precoder design using the \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
-The convergence analysis of the distributed algorithms are discussed in Appendix \ref{sec-dist-conv}.
+In numerical simulations, we consider step size \me{\rho=2}.
+The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of iterations, say, \eqn{J_{\max}}.
+The \ac{ADMM} based precoder design is outlined in Algorithm \ref{algo-3}.
+\begin{algorithm}
+	\SetAlgoLined
+	\DontPrintSemicolon
+	\BlankLine
+	\SetKwInput{KwInit}{Initialize}
+	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
+	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
+	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
+	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
+	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
+	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
+		\Repeat{convergence or \me{i \geq I_{\max}}}{
+			\Repeat{convergence or \me{j \geq J_{\max}}}{
+				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
+				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
+				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
+				update \me{j = j + 1}\;
+			}
+			send precoded downlink pilot with \me{\mbf{m}}\;
+			evaluate \me{\mvec{w}{l,k,n}} at each user and inform to all \acp{BS} in \eqn{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective} \;
+			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
+			$i = i + 1$, \me{j=0} \;
+		}
+	}
+	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
+	\label{algo-3}
+\end{algorithm}
+
+The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}.
+\review{In practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of steps, say, \eqn{J_{\max}}.
+If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
+It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
+However, if the distributed algorithms are performed for adequate number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step, then the limit point of the sequence of iterates is a stationary point of \eqref{eqn-6}.}
+
+\begin{comment}
 \begin{algorithm}
@@
 \end{algorithm}
-
-\begin{comment}
 The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties.

### 2015-07-25 Report/introduction.tex
to read

@@
 The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
-In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users present in the network.
+In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users existing in the network.
 We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}.
@@
 Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables.
-After the design stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource.
-A zero transmit precoder indicates the absence of the user on a given resource.
-In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergences.
+After the design stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource, and the zero transmit precoder indicates the absence of the user on a given resource.
+In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence.
 %The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets.
@@
 The topics on \ac{MIMO} \ac{IBC} precoder design have been studied extensively with different performance criteria in the literature.
-Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, \ac{SCA} approach has become a powerful tool to deal with these problems.
-For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around an operating point to solve the \ac{WSRM} problem in a iterative manner.
+Due to the nonconvex nature of the \ac{MIMO} \ac{IBC} precoder design problems, \ac{SCA} approach has become a powerful tool to solve these problems.
+For example, in \cite{sin_algorithm}, the nonconvex part of the objective is linearized around a fixed operating point to solve the \ac{WSRM} problem in a iterative manner.
 A similar approach using arithmetic-geometric inequality was proposed in \cite{tran2012fast}.
 
-The relation between the achievable sum rate and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can be used to solve the \ac{WSRM} problem \cite{mse_duality}.
+The relation between the achievable sum rate and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can also be used to solve the \ac{WSRM} problem \cite{mse_duality}.
 In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients.
-In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders.
+In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and receivers.
 Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed.
 The \ac{MSE} reformulation for the \ac{WSRM} problem was also studied in \cite{hong2012decomposition} by using \ac{SCA} to solve the problem in an iterative manner.
-Moreover, distributed precoder designs with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013primal,kaleva2013decentralized}.
+Moreover, distributed precoder designs with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013decentralized}.
 

### 2015-07-25 Report/kkt_mse_approach.tex
updated noise information in KKT solutions
to read

@@
 In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the global queue deviation objective with few number of iterations.
-\review{The alterantive way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}
+\review{The alternative way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}
 
@@
 We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter.
-Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized,kaleva2013primal}.
-Since the work in \cite{kaleva2013decentralized,kaleva2013primal} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, the formulations require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
+Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized}.
+Since the work in \cite{kaleva2013decentralized} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, the formulations require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
 
@@
 \mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
-\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}\\
+\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}\\
 \epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
@@
 	\mvec{w}{l,k,n}^{(i)} =& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm \nonumber \\
-	& \qquad {} + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6} \\
+	& \qquad {} + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6} \\
 	\epsilon_{l,k,n}^{(i)} =& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \nonumber \\

### 2015-07-25 Report/mse_formulation.tex
to read

@@
 
-Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represent the weighted formulation.
-By using the relaxed \ac{MSE} expression in \eqref{mse-error}, we can reformulate \eqref{eqn-3} as
+Before proceeding futher, let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} be the corresponding weighted objective.By using the relaxed \ac{MSE} expression in \eqref{mse-error}, we can reformulate \eqref{eqn-3} as
 \iftoggle{single_column}{

### 2015-07-25 Report/sub_channel_wsrm.tex
to read

@@
 \review{For simplicity we use random sub-channel ordering in our paper, \textit{i.e.}, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
-We can also use greedy ordering by considering the norm of the channel between a user and the corresponding serving \ac{BS}, but this comes at the cost of increased complexity.
-However, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the available multi-user diversity.}
+Additionally, we can also use greedy ordering by considering the channel norm between all users in the system and the corresponding serving \acp{BS}, but this comes at the cost of increased complexity.
+However, it is worth noting that, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the available multi-user diversity present in the system.}
 

### 2015-07-25 Report/system_model.tex
to read

@@
 where \me{\enoise = N_0 \, \trace (\mvec{w}{l,k,n} \mbf{w}_{l,k,n}^\herm)} denotes the equivalent noise variance.
-To reduce the overhead involved in feeding back the user channels, we consider a \ac{TDD} system in which \acp{BS} can estimate the downlink channels from the uplink pilots using channel reciprocity.
+In order to avoid the overhead involved in feeding back the user channels, we consider \ac{TDD} system in which \acp{BS} can estimate the downlink channels from uplink pilots by using channel reciprocity property.
 

### 2015-07-25 Report/wsrm_formulation.tex
to read

@@
-We present iterative algorithms to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with the \ac{SCA} presented \cite{marks1978technical}.
+We present iterative algorithms to solve \eqref{eqn-3} using \acl{AO} technique in conjunction with \ac{SCA} approach presented \cite{marks1978technical}.
 The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system.
-The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint.
+Note that the \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint.
 However, by using additional variables, we can relax the \ac{SINR} expression in \eqref{eq:SINR} by inequality constraints to solve the problem \eqref{eqn-3} as
@@
 be the r.h.s of \eqref{eqn-6.2}, where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{m}{l,k,n}, \mvec{w}{l,k,n},\beta_{l,k,n}\}}.
-Note that the function \me{g({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}.
-The nonconvex set defined by \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{g({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred to as \ac{SCA} in \cite{marks1978technical}.
+Note that the function \me{g({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} as in \cite{boyd2004convex}.
+The nonconvex set defined by \eqref{eqn-6.2} can be decomposed as a series of convex subsets by linearizing the convex function \me{g({\mbf{u}}_{l,k,n})} with the first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{scutari_1,lanckriet2009convergence}, also referred to as \ac{SCA} in \cite{marks1978technical}.
 By using the reduced convex subset for \eqref{eqn-6.2}, the problem in \eqref{eqn-6} is solved iteratively by updating the operating point in each iteration.
@@
 In CVX \cite{grant2008cvx}, for example, we declare \me{p_{l,k,n}} and \me{q_{l,k,n}} with the `\emph{expression}' qualifier.} Let \eqn{\tilde{\mbf{u}}_{l,k,n} \triangleq \{\tilde{\mbf{m}}_{l,k,n}, \tilde{\mbf{w}}_{l,k,n},\tilde{\beta}_{l,k,n} \}} be a minimizer from the previous \ac{SCA} iteration.
-Using the first order Taylor approximation around the operating point \eqn{\tilde{\mbf{u}}_{l,k,n}}, we can approximate \eqref{eqn-6.2} as
+Now, by using the first order Taylor approximation around the operating point \eqn{\tilde{\mbf{u}}_{l,k,n}}, we can approximate \eqref{eqn-6.2} as
 \iftoggle{single_column}{
@@
 Note that the scaling present in the optimal receiver \eqref{opt-rx} has no impact on the received \acp{SINR}, and therefore the \ac{MMSE} receiver in \eqref{eqn-10} can also be used.
-However, the rate of convergence might be different with the two receivers.
+However, the convergence speed is different between the two receiver implementations.
 
@@
 Let \eqn{\{\mbf{m}^{(i)}_j, \mbf{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step.
-In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is given by \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained from the \eqn{\ith{(i-1)}} \ac{AO} step by either solving \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver in \eqref{eqn-10}.
+In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is updated as \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
 \begin{algorithm}
@@
 
-Upon convergence of the transmit precoders, the receivers are updated using the fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\ast}} obtained from the previous \ac{SCA} step.
-Once the receive beamformers are obtained, the transmit precoders are again updated by solving \eqref{eqn-9} recursively with the newly found receivers.
-The above procedure is repeated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations.
-The iterative approach is outlined in Algorithm \ref{algo-1}.
+Upon convergence of the transmit precoders, the receivers are then updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\ast}} obtained from the previous \ac{SCA} step.
+Once the receive beamformers are updated, the transmit precoders are again evaluated with the newly found receivers by solving \eqref{eqn-9} recursively or by using \eqref{eqn-10}.
+The above procedure is repeated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations as outlined in Algorithm \ref{algo-1}.
 
-The initial feasible points \me{\tilde{\mbf{u}}_{l,k,n}} are obtained by initializing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single user beamformers satisfying the total power constraint \eqref{eqn-9.1d}, \me{\tilde{\mbf{w}}_{l,k,n}} with the corresponding \ac{MMSE} receivers \eqref{eqn-10}, and \me{\tilde{\mbf{\beta}}_{l,k,n}} is obtained by evaluating \eqref{eqn-9.1c} with the preinitialized transmit precoders and the receive beamformers of all the users in the system.
+The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained with the corresponding \ac{MMSE} receivers in \eqref{eqn-10}.
+Now, by using the fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c} for all the users in the system.
 
-Even though the iterative approach in Algorithm \ref{algo-1} converges in all our numerical simulations, in order to provide an analytical convergence proof of the iterates to a stationary point, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of \eqref{eqn-6.1}.
-The convergence proof for the centralized solutions is provided in Appendix \ref{sec-3.5}.}
+Note that in all our numerical simulations, the objective sequence of Algorithm \ref{algo-1} converges.
+However, to show the convergence of the sequence of beamformer iterates, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of the one defined in \eqref{eqn-6.1}.
+Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.}
 \begin{comment}

### 2015-07-25 Response/Response 2/document.tex
to read

@@
 \vspace{0.5in}
-The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality.
-Based on the comments, we have made several major revisions to the paper, which is summarized below.
+The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript, which have been greatly helpful to improve the paper quality.
+Based on the comments, we have made several revisions to the paper, which are summarized below.
 \input{additions}

### 2015-07-26 Report/convergence_centralized.tex
updated with perusu

@@
 \end{IEEEeqnarray}
-where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c_{k}^{(i)} > 0} is a positive constant to ensure strong convexity of the objective with some parameter \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} and \eqn{m > 0} as discussed in \cite{scutari-1}.
-Now by using the strong convexity of the modified objective in \eqref{mod_obj}, we can guarantee the uniqueness of the minimizer in each \ac{SCA} step \eqn{k} \cite{yang_yang,scutari-1}.
+where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c_{k}^{(i)} > 0} is a positive constant to ensure strong convexity of \eqn{f} in each step as discussed in \cite{scutari-1}.
+Let \eqn{m > 0} be the constant of strong convexity of \eqn{f}, where \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}}.
+Using the strong convexity of the modified objective in \eqref{mod_obj}, we can guarantee the uniqueness of the minimizer in each \ac{SCA} step \eqn{k} \cite{yang_yang,scutari-1}.
 Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}

### 2015-07-30 Response/Response 2/response-1.tex
updated before Algorithm 2 Changes

@@
 
-\resp After a careful check of the manuscript, we have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results) to provide additional details for the convergence proof.
+\resp We have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results) to provide additional details for the convergence proof.
 We believe the removed parts do not affect the readability of the paper and the added text regarding convergence proof certainly improves the quality.
@@
 
-\resp We thank the reviewer for the critical comment.
-Based on the comment by the reviewer, we have removed the additional inequality relating the previous operating point from (49) in the revised manuscript.
+\resp We have removed the additional inequality relating the previous operating point from (49) in the revised manuscript.
 
@@
 In fact \eqn{\mbf{m}} has compact feasible region, and thus \eqn{\mbf{m}^{(i)}_k} has limit points for any specific \eqn{i}.
-However \eqn{m_{*}^{(i)}} does not necessarily exist( the whole sequence \eqn{\mbf{m}^{(i)}_k} may be not convergent).
+However \eqn{m_{*}^{(i)}} does not necessarily exist (the whole sequence \eqn{\mbf{m}^{(i)}_k} may be not convergent).
 Similar problem happens to \eqn{\mbf{w}^{(i)}_k}.
@@
 
-\resp  We thank the reviewer for citing the issue regarding the sequence convergence.
-Even though the objective converges in each \ac{SCA} update, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge.
-It follows from the convexity of the original function, which can have multiple solutions.
-However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [31] and [32], which ensures the uniqueness of the solution in each \ac{SCA} update.
+\resp  Even though the objective converges in each \ac{SCA} update, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} converge.
+The multiple solution follows from the convex objective of the original problem, which can have multiple solutions.
+However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [31] and [32].
+This approach ensures the uniqueness of the solution in each \ac{SCA} update.
 
-Since our problem is (highly) nonconvex and there are possibly many stationary points.
-If we start from different initial points, we may end up with different stationary points.
-That is to say, the limit point of \ac{SCA} approach is not unique.
-However, by regularizing the objective with a small quadratic term, the iterate in each step of \ac{SCA} algorithm is unique.
-This and the fact that the set is compact ensure the \ac{SCA} converges to a limit point.
+Since our problem is (highly) nonconvex, there are possibly many stationary points.
+If we start from different initial points, we may end up in different stationary points.
+That is to say, the limit point of the \ac{SCA} approach is not unique.
+However, by regularizing the objective with a small quadratic term, the iterate in each step of the \ac{SCA} algorithm is unique.
+This and the fact that the set is compact ensure that the \ac{SCA} converges to a limit point.
 We have updated the manuscript to include this information in the convergence proof for the centralized algorithm in Appendix A.
@@
 
-\resp We thank the reviewer for the pointing out the issue involving the strict monotonicity.
-As suggested by the reviewer, we have included the strict monotonicity of the objective sequence in Appendix A-C following (52).
-Moreover, we have also noted the reader that we in fact use the regularized objective in (46b) to analytically prove the convergence of iterates, although we have numerically observed that the objective sequence of Algorithm 1 (with the original objective) always converge.
+\resp As suggested by the reviewer, we have included the strict monotonicity of the objective sequence in Appendix A-C following (52).
+Moreover, we have also mentioned that we in fact use the regularized objective in (46b) to analytically prove the convergence of the iterates, although we have numerically observed that the objective sequence of Algorithm 1 (with the original objective) always converges.
 Please refer to the paragraph before Section III-C.
@@
 
-\resp We thank the reviewer for raising the concern.
-We have updated the manuscript to include the details regarding the stationary point discussion in Appendix A-E and the convergence proof analysis for the primal and the \ac{ADMM} algorithms in Appendix B.
-We have also mentioned the conditions required for showing the stationarity property of the limit point and included more mathematical materials to make the convergence proof of distributed approaches rigorous.
+\resp We have updated the manuscript to include the details regarding the stationary point discussion in Appendix A-E.
+The convergence analysis for the primal and the \ac{ADMM} algorithms are presented in Appendix B.
+We have also mentioned the conditions required for showing the stationarity property of the limit point and included more mathematical steps to make the convergence proof of distributed approaches rigorous.
 

### 2015-07-30 Response/Response 2/response-2.tex
updated before Algorithm 2 Changes

@@
 We have emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user.
-Even though we are not including it in the paper, we have included in the response letter to answer the reviewers' question.
+We do not include in the manuscript due to space limitations, we have included in the response letter to answer the reviewers' question.
 We considered a system with \eqn{N = 4} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users.
 The \ac{PL} is distributed uniformly over \eqn{[0,-3]} dB.
-The number of backlogged packets assumed for each user is provided in the corresponding captions in Fig.
-\ref{fig-review-1}.
+The number of backlogged packets assumed for each user is provided in the corresponding captions in Figure \ref{fig-review-1}.
 	\begin{figure*}[h!]
@@
 
-Fig.
-\ref{fig-review-1} compares different sub-channel ordering schemes in terms of the total number of backlogged packets remaining in the system.
-As can be seen from Fig.
-\ref{fig-review-1a}, the greedy sub-channel ordering provides a favorable way of choosing sub-channels to minimize the total number of backlogged packets.
-However in Fig.
-\ref{fig-review-1b}, it is evident that the greedy sub-channel ordering is no longer better in comparison with the few other random ordering schemes.
+	Figure \ref{fig-review-1} compares different sub-channel ordering schemes in terms of the total number of backlogged packets remaining in the system.
+As can be seen from Figure \ref{fig-review-1}\subref{fig-review-1a}, the greedy sub-channel ordering provides a favorable way of choosing sub-channels to minimize the total number of backlogged packets.
+However in Figure \ref{fig-review-1}\subref{fig-review-1b}, it is evident that the greedy sub-channel ordering is no longer better in comparison to the few other random ordering schemes.
 We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic method under Section III-D final paragraph.
-However, as the number of users in the system increases, all sub-channel ordering are similar in minimizing the total number of backlogged packets in the system without any noticeable gain.
+However, as the number of users in the system increases, all sub-channel ordering schemes are similar in minimizing the total number of backlogged packets in the system without any noticeable gain.
 
@@
 		In order to quantify the total number of bits required in a centralized solution, let us assume that each complex channel for a \ac{SISO} model requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is more important) or it can be a equal share of \eqn{5} bits for both amplitude and phase.
-Using this assumption, the total amount of channel information in bits to be exchanged via backhaul is \eqn{10 \times K \times N_B \times N_R \times N_T = 320} bits.
+Using this assumption, the total number of bits for channel information to be exchanged via backhaul is \eqn{10 \times K \times N_B \times N_R \times N_T = 320} bits.
 On the other hand, for the distributed algorithms, let us consider \eqn{6} bits for quantizing each element of the consensus vectors.
@@
 
-		In the above example, for the same amount of signaling overhead as in centralized method, we can perform only up to 6 \ac{SCA} updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for \ac{ADMM} part).
+		In the above example, for the same signaling overhead as in centralized method, we can perform only up to 6 \ac{SCA} updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for \ac{ADMM} part).
 This may not be sufficient for the distributed algorithms to attain the same performance as the centralized method.
-However, as the number of sub-channels, users and/or the antenna element increases, it may not be a feasible option to feedback all \acp{CSI} across the coordinating \acp{BS} to the centralized controller in the current cellular systems.
-In addition to comparing the signaling overhead, we also need to consider the performance loss due to \ac{CSI} quantization in the centralized approaches, which is beyond the scope of our paper.
+However, as the number of sub-channels, users and/or the antenna elements increases, it may not be a feasible option to send complete \acp{CSI} across the coordinating \acp{BS} to the centralized controller in the current cellular systems.
+In addition to comparing the signaling overhead, we also need to consider the performance loss due to the \ac{CSI} quantization in the centralized approaches, which is beyond the scope of our paper.
 Generally, the performance is significantly degraded if precoders are designed with the quantized \ac{CSI} as discussed in [R1].
@@
 		\vspace{1eM}
-		[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti Tölli, Markku Juntti,  and Savo Glisic, "\emph{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}'', \textit{IEEE Trans.
+		[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti Tölli, Markku Juntti,  and Savo Glisic, "{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}'', \textit{IEEE Trans.
 Signal Process}., vol 61, no.
@@
 
-		\item From the above discussions, we can see that \ac{ADMM} and primal schemes require significant overhead compared to the centralized algorithms for a small system.
+		\item From the above discussions, we can see that the \ac{ADMM} and primal schemes require significant overhead compared to the centralized algorithms for a small system.
 However, for a system involving more coordinating \acp{BS}, users and antenna elements, it would be beneficial to use the proposed distributed algorithms with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
-If we set \eqn{J_{\max} = 1}, the convergence of the proposed algorithms is not guaranteed as shown in Fig.
-\ref{fig-review-2-a}.
-The system model considered is the same as used for Fig.
-\ref{fig-review-1a}.
+If we set \eqn{J_{\max} = 1}, the convergence of the proposed algorithms is not guaranteed as shown in Figure \ref{fig-review-2-a}.
+The system model considered is the same as the one used for Figure \ref{fig-review-1}\subref{fig-review-1a}.
 		\begin{figure}[h!]
@@
 		\end{figure}
-		Note that Fig. \ref{fig-review-2-a} plots the queue deviation at the \ac{SCA} update points only. The number of backlogged packets in each \ac{ADMM} iteration is not shown for clarity reason.
+		Note that Figure \ref{fig-review-2-a} plots the queue deviation at the \ac{SCA} update points only. The number of backlogged packets in each \ac{ADMM} iteration is not shown for clarity reason.
 
@@
 
-	The above discussions are included in the first and the last paragraph of Section IV-C.
+	The above discussion is included in a condensed form in the first and the last paragraph of Section IV-C.
 
@@
 Instead, the decentralized parts only need to follow the fading process when \eqn{J_{\max} > 1}.
-The performance of the distributed algorithm based on dual decomposition scheme was discussed for the time-correlated fading in Section C of [12], which showed that it is enough for the distributed precoder design to follow the fading process to provide desired performance.
+The performance of the distributed algorithm based on the dual decomposition scheme was discussed for the time-correlated fading in Section C of [12], which showed that it is enough for the distributed precoder design to follow the fading process to provide the desired performance.
 Studying the performance of distributed algorithms for the time correlated case is beyond the scope of our paper and thus is not considered in the current manuscript.
@@
 
-	Fig.
-\ref{fig-review-2} compares the performance of the distributed \ac{KKT} approach, \textit{i.e.}, Algorithm 3 for different values of \eqn{I_{\max}}.
+	Figure \ref{fig-review-2} compares the performance of the distributed \ac{KKT} approach, \textit{i.e.}, Algorithm 3 for different values of \eqn{I_{\max}}.
 The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.\footnote{Please refer to [27] for further details.} We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the required information for \eqn{J_{\max} = 3,5,10}.
@@
 
-	Unlike Algorithm 3, the centralized scheme presented in Fig.
-\ref{fig-review-2} has no penalty term and it is used as a benchmark.
+	Unlike Algorithm 3, the centralized scheme presented in Figure \ref{fig-review-2} has no penalty term and it is used as a benchmark.
 In order to improve the performance of the distributed scheme, the operating point involved in the \ac{SCA} algorithm is considered from the earlier frame instead of begin generated randomly.
@@
 	Since we use \ac{KKT} approach, we can either use all users in the system for the precoder design or we can utilize single-cell MU-MIMO user selection presented in the literature to limit the number of users for which the precoders are designed, which leads to the faster convergence.
-As we can see from Fig.
-\ref{fig-review-2}, as the arrival rate per user increases, the performance of \ac{KKT} schemes with \eqn{J_{\max} = 3,5,10} converges since the number of backlogged packets are significantly large, therefore, the same set of users will be served by the algorithm with better precoders by utilizing the memory.
+As we can see from Figure \ref{fig-review-2}, as the arrival rate per user increases, the performance of \ac{KKT} schemes with \eqn{J_{\max} = 3,5,10} converges since the number of backlogged packets are significantly large, therefore, the same set of users will be served by the algorithm with better precoders by utilizing the memory.
 
@@
 Note that the precoders are not updated for the desired users until convergence, after the limited number of iterations.
-However, if we perform the single cell precoder design by considering the neighboring precoders as fixed after the recent exchange as discussed in [28], we can improve the performance significantly for Algorithm 3 as shown by red curves in Fig.
-\ref{fig-review-2}.
+However, if we perform the single cell precoder design by considering the neighboring precoders as fixed after the recent exchange as discussed in [28], we can improve the performance significantly for Algorithm 3 as shown by red curves in Figure \ref{fig-review-2}.
 In this approach, in between each exchange across the coordinating \acp{BS}, each \ac{BS} will perform \eqn{J_{\max} = 20} with the neighboring precoders as fixed.
@@
 	\vspace{1eM}
-	[R2] Muhammad-Fainan Hanif, Le-Nam Tran, Antti T\"{o}lli, Markku Juntti,  and Savo Glisic, "\emph{Bi-directional Training for Adaptive Beamforming and Power Control in Interference Networks},'' \textit{IEEE Trans.
-Signal Process}., vol 62, no.
-3, pp.
-607--618, Feb.
-2014.
+	[R2] Changxin Shi, Berry R.A., Honig M.L., ``{Bi-Directional Training for Adaptive Beamforming and Power Control in Interference Networks}," \textit{IEEE Transactions on Signal Processing}, vol.62, no.3, pp.607,618, Feb.1, 2014
 
@@
 Kaleva,  M.
-Latva-aho, "\emph{Bi-directional Signaling for Dynamic TDD with Decentralized Beamforming}'', in \textit{Proceedings of IEEE ICC SmallNets Workshop}, London, UK, June, 2015
+Latva-aho, "{Bi-directional Signaling for Dynamic TDD with Decentralized Beamforming}'', in \textit{Proceedings of IEEE ICC SmallNets Workshop}, London, UK, June, 2015
 	\vspace{1eM}
@@
 In such a case, the convergence is not guaranteed.
-In our simulation, the \ac{ADMM} part can find an optimal solution to the (convex) subproblem in each \ac{SCA} step when \eqn{J_{\max} = 20}.
+In our simulations, the \ac{ADMM} part can find an optimal solution to the (convex) subproblem in each \ac{SCA} step when \eqn{J_{\max} = 20}.
 
 \begin{itemize}
+\item The fixed point for the algorithm exists if the distributed approaches are performed until convergence or iterated for significant number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step.
+In such scenarios, the iterative method in Algorithm 2 finds a fixed point such that \eqn{\mc{A}(\mbf{x}^{\ast}) = \mbf{x^{\ast}}}, \eqn{\forall \mbf{x}^{\ast} \in \mc{F}^{\ast}}, where \eqn{\mc{F}^{\ast}} is the set of all fixed points of the algorithm and \eqn{\mc{A}} denotes the Algorithm 2 at each \ac{AO} update point as in (54).
+
+\item Note that in each \ac{SCA} step, the iterative procedure in Algorithm 2 finds a (unique) solution by solving (20) or (28) with the previous solution as the operating point.
+Therefore, the fixed point of Algorithm 2 depends on the initial operating point chosen for the iterative procedure.
+Upon convergence, the fixed point of Algorithm 2 can be distinct for different starting points chosen to initialize the iterative procedure.
+
+\item Since the original problem is nonconvex, there exists multiple stationary point.
+Therefore, if the Algorithm 2 is initialized with a feasible operating point, then the limit point of the iterative algorithm is a fixed point of Algorithm 2, provided strict monotonicity of the objective and the uniqueness of the iterates are ensured in each \ac{SCA} step.
+Due to the fact that the limit point depends on the chosen initial operating point, there exists a set of limit points, which are also a fixed point of Algorithm 2.
+Therefore, all fixed points found by Algorithm 2, satisfying strict monotonicity and the uniqueness of the iterates in each \ac{SCA} step, are stationary points of the original nonconvex problem (16).
+
 \item We also want to remark that  the proposed distributed algorithms are not based on fixed-point theory.
@@
 
-\item When the ADMM approach converges, the interference vector is guaranteed to be equal to the actual interference in the next work.
-This is the main principle of \ac{ADMM} where the local variables (the vectors in (39)) converge to the global variables (the actual inference vectors).
+\item When the ADMM approach converges, the interference vector is guaranteed to be equal to the actual interference seen in the network.
+This is the main principle of \ac{ADMM} where the local variables (the vectors in (38)) converge to the global variables (the actual inference vectors).
 
-\item Another point we want to make is that Algorithm 2 yields a stationary point of the original noncovex problem at convergence and this stationary point may not be a fixed-point of the original noncovex problem.
+\item Another point we want to make is that Algorithm 2 yields a stationary point of the original noncovex problem upon convergence and this stationary point may not be a fixed-point of the original noncovex problem, \textit{i.e.}, \eqn{f(\mbf{x}) = \mbf{x}}.
 

### 2015-07-30 Response/Response 2/response-3.tex
updated before Algorithm 2 Changes

@@
 	\resp We have updated the manuscript to discuss possible options for selecting an algorithm for a specific implementation.
-The choice of considering a centralized approach is equally good when the number of receive antenna is greater than one, \textit{i.e.}, \eqn{N_R > 1}.
+The choice of considering a centralized approach is equally good when the number of receive antennas is larger than one, \textit{i.e.}, \eqn{N_R > 1}.
 However, in case of a single antenna receiver, the \ac{JSFRA} formulation outlined in Section III-B is more efficient than the \ac{MSE} reformulation, as there is no need for the receiver update, thereby reducing the complexity significantly.
@@
 
-	\resp It has been rewritten to improve the readability as suggested by the reviewer.
+	\resp It has been rewritten to improve the readability as suggested by the reviewer. For additional information, the reviewer is requested to refer [R1].
+
+	[R1] Changxin Shi, Berry R.A., Honig M.L., ``{Bi-Directional Training for Adaptive Beamforming and Power Control in Interference Networks}," \textit{IEEE Transactions on Signal Processing}, vol.62, no.3, pp.607,618, Feb.1, 2014
 
@@
 
-	\resp We thank the reviewer for the comment.
-The main purpose of considering several path loss models is simply to show that the proposed algorithms works reasonably well on various scenarios.
+	\resp The main purpose of considering several path loss models is simply to show that the proposed algorithms works reasonably well on various scenarios mentioned in Section V (Simulation Section).
 For benchmarking, we have also included the centralized algorithm to draw the difference between the other schemes.
@@
 Unfortunately those results cannot be included in the current manuscript due to space limitation.
-We aim to make them available online as a companion technical report whey they are ready.
+We aim at making them available online as a companion technical report whey they are ready.
 
@@
 
-	\resp We apologize for the error which has been fixed in the revised manuscript.
+	\resp The error has been fixed in the revised manuscript.
 
 	\cmnts{e} - \review{In Fig.
-4(b), the performance of Q-WSRME seems to be (in average) worse than Q-WSRM.
+4(b), the performance of Q-WSRME seems to be (in average) worse than that of Q-WSRM.
 However, that should not be the case, since Q-WSRME is taking into account the over allocation.
@@
 
-	\resp We thank the reviewer for pointing out the mistake.
-In fact, it should be the dual variable \eqn{\sigma_{l,k,n}} and not \eqn{\lambda_{l,k,n}}.
-We have fixed this problem in the revised manuscript.
+	\resp In fact, it should be the dual variable \eqn{\sigma_{l,k,n}} and not \eqn{\lambda_{l,k,n}}. We have fixed this problem in the revised manuscript.
 

### 2015-07-30 Report/convergence_centralized.tex
updated before Algorithm 2 Changes

--- 2015-07-25 Report/convergence_centralized.tex
@@
 
-\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update \eqn{i} as
+\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 \end{IEEEeqnarray}
-where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem and \me{c_{k}^{(i)} > 0} is a positive constant to ensure strong convexity of the objective with some parameter \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} and \eqn{m > 0} as discussed in \cite{scutari-1}.
-Now by using the strong convexity of the modified objective in \eqref{mod_obj}, we can guarantee the uniqueness of the minimizer in each \ac{SCA} step \eqn{k} \cite{yang_yang,scutari-1}.
-Note that the quadratic term in \eqref{mod_obj} includes the previous solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, which is solved in the \eqn{\ith{k}} \ac{SCA} iteration.}
+where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem.
+The positive constant \me{c_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{m > 0} be the constant of strong convexity of \eqn{f} with \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} as in \cite{scutari-1}.
+Therefore, by using the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step \cite{yang_yang,scutari-1}.
+The quadratic term in \eqref{mod_obj} includes the earlier solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, obtained by solving \eqref{eqn-9} or \eqref{eqn-mse-2} in the \eqn{\ith{(k-1)}} \ac{SCA} step.}
 
@@
 \review{Using the above discussions, the monotonicity of the objective seqeunce is guaranteed in each \ac{AO} and \ac{SCA} updates.
-However, to ensure strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{m > 0}.
+However, to ensure strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some constant \eqn{m > 0}.
 Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step.
@@
 since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
-Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds at each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}.
-Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured.
+Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}.
+Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
 However, if \eqn{\hat{f}} is used instead of \eqn{f} in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to multiple solutions.
@@
 Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update.
-It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.}
+It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.
+}
 

### 2015-07-30 Report/convergence_distributed.tex
updated before Algorithm 2 Changes

@@
 \end{IEEEeqnarray}
-where the equality constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
+where the constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
 To show the convergence, we rely on the following conditions.
@@
 It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is invertible.
-The objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity.
+Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity.
 Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior.
@@
 Moreover, note that the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the iterates are not unique in each update.
-Due to this reason, the algorithm cannot find a fixed point to ensure the convergence of the beamformer iterates.}
+Due to the above said reasons, the iterative scheme outlined in Algorithm \ref{algo-4} cannot find a fixed point to ensure the convergence of the beamformer iterates.}
 

### 2015-07-30 Report/dual_approach.tex
updated before Algorithm 2 Changes

@@
-The \ac{ADMM} approach can also be used to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}.
-Generally, the \ac{ADMM} is preferred over the \ac{DD} approach in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}.
+The \ac{ADMM} approach can also be used to decouple the precoder design across multiple \acp{BS} to solve the convex subproblem in \eqref{eqn-decent-1}.
+Generally, the \ac{ADMM} is preferred over the \acl{DD} in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}.
 In contrast to the \acl{PD}, the \ac{ADMM} relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}.
@@
 	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
-	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
-	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
+	initialize the vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
 	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
@@
 The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}.
-\review{In practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of steps, say, \eqn{J_{\max}}.
+\review{In practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
 If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
 It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
-However, if the distributed algorithms are performed for adequate number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step, then the limit point of the sequence of iterates is a stationary point of \eqref{eqn-6}.}
+However, if the distributed methods are performed for an adequate number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step, then the limit point of the sequence of iterates is a stationary point of \eqref{eqn-6}.
+Additionally, if the receiver is updated together with the transmit precoder in each \ac{SCA} step as in Algorithm \ref{algo-3}, then the convergence of the iterates is still guaranteed.
+It follows from the feasibility of the solution and the strict monotonicity of the objective after the combined update.}
 

### 2015-07-30 Report/introduction.tex
updated before Algorithm 2 Changes

@@
 Specifically, the queue states can be incorporated in the \ac{WSRM} objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or its function, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states \cite{neely2010stochastic}, where \me{R_k} denotes the achievable data rate of user \me{k}.
-In the \textit{backpressure algorithm}, the differential queues between the source and the receiver nodes are used to scale the transmission rate \cite{georgiadis2006resource}.
+In the \textit{backpressure algorithm}, the differential queues between the source and the receiver nodes are used to scale the transmission rate \cite{neely2010stochastic}.
 

### 2015-07-30 Report/kkt_mse_approach.tex
updated before Algorithm 2 Changes

@@
 \ref{sec-3.3}) equally when \eqn{N_R > 1}.
-However, for \eqn{N_R = 1} scenario, the \ac{JSFRA} formulation in Section \ref{sec-3.2.1} is more efficient, as there is no receiver update, and therefore has less complexity.
+However, for \eqn{N_R = 1}, the \ac{JSFRA} formulation in Section \ref{sec-3.2.1} is more efficient, as there is no receiver update, and therefore has less complexity.
 Similarly, when \eqn{N_R = 1}, the distributed approaches based on the \ac{JSFRA} method via \ac{SINR} relaxation are preferred over other schemes due to the limited signaling between the coordinating \acp{BS} involving the exchange of the scalar interference values.

### 2015-07-30 Report/wsrm_formulation.tex
updated before Algorithm 2 Changes

@@
 \review{The proposed solution involves two nested iterations, \textit{i.e.}, one for the outer \ac{AO} loop and the second for the inner \ac{SCA} loop.
-Each \ac{AO} iteration involves two steps, one for finding transmit precoders by solving \eqref{eqn-9} iteratively until convergence for fixed receivers, and the other for updating the receive beamformers with the previously found fixed transmit precoders by either solving \eqref{opt-rx} recursively or by using \eqref{eqn-10}.
+Each \ac{AO} iteration involves two steps, one for finding the transmit precoders by solving \eqref{eqn-9} iteratively until convergence for fixed receivers, and the other for updating the receive beamformers with the previously found fixed transmit precoders by either solving \eqref{opt-rx} recursively or by using \eqref{eqn-10}.
 
@@
 
-The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained with the corresponding \ac{MMSE} receivers in \eqref{eqn-10}.
+The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying the total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained with the corresponding \ac{MMSE} receivers in \eqref{eqn-10}.
 Now, by using the fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c} for all the users in the system.
@@
 Note that in all our numerical simulations, the objective sequence of Algorithm \ref{algo-1} converges.
-However, to show the convergence of the sequence of beamformer iterates, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of the one defined in \eqref{eqn-6.1}.
+However, to show the convergence of the sequence of the beamformer iterates, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of the one in \eqref{eqn-6.1}.
 Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.}

### 2015-07-30 Report/convergence_centralized.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response

@@
 	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
-	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + c_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
 \end{IEEEeqnarray}
 where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem.
-The positive constant \me{c_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{m > 0} be the constant of strong convexity of \eqn{f} with \eqn{m \triangleq \min_{k} \{c_{k}^{(i)}\}} as in \cite{scutari-1}.
+The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity of \eqn{f} with \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} as in \cite{scutari-1}.
 Therefore, by using the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step \cite{yang_yang,scutari-1}.
@@
 \end{multline}}
-Thus the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing.
+Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing.
 \review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique.
 Using this and the fact that the sequence of objectives is nonincreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.
-However, note that the limit point need not be a stationary point of \eqref{con} since the receive beamformers \eqn{\my} have been fixed.}
+However, note that the limit point need not be a stationary point of \eqref{con}, since the receive equalizers \eqn{\my} have been fixed.}
 
@@
 Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
-The sequence convergence and the nonincreasing behavior of the objective follow similar arguments as above.\footnote{Note that we can also use the \ac{MMSE} receiver in \eqref{eqn-10} instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the sequence of iterates generated by iteratively solving \eqref{con-m} is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\} \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
+The sequence convergence and the nonincreasing behavior of the objective follow similar arguments as above.
+\footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the sequence of iterates generated by iteratively solving \eqref{con-m} is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\} \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
 
@@
 
-\review{Using the above discussions, the monotonicity of the objective seqeunce is guaranteed in each \ac{AO} and \ac{SCA} updates.
-However, to ensure strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some constant \eqn{m > 0}.
+\review{Using the above discussions, the monotonicity of the objective sequence is guaranteed in each \ac{AO} and \ac{SCA} updates.
+However, to ensure the strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}.
 Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step.
@@
 \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
-f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
+f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{c}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
 \end{IEEEeqnarray}
@@
 
-Now, to prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
+To prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
 Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications.
-Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}, therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
+Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}.
+Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
 \begin{equation} \label{kkt_mod_expr}
@@
 The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}.
-Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfies \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}.
-(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given by
+Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfy \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}.
+(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given as
 \begin{equation} \label{rhs_equiv}
@@
 Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}.
-By using \cite[Th.
+By using \cite[Thms.
 2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the original nonconvex problem in \eqref{con}.}
+3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the problem in \eqref{con}.}
 

### 2015-07-30 Report/convergence_distributed.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response

@@
 
-\review{To show the convergence of \ac{ADMM}, we use the discussions in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing the problem as
+\review{To show the convergence of the \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 Now, by using \cite[Prop.
-4.2]{bertsekas1989parallel}, we can show that \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size.
-If both primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence generated by the distributed methods is a stationary point of \eqref{con}, using similar arguments in Appendix \ref{sec-3.5}.
+4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size.
+If both the primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence generated by the distributed methods is a stationary point of \eqref{con}, using similar arguments as in Appendix \ref{sec-3.5}.
 }
@@
 
-However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus it achieves improved speed of convergence.
+However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus, achieving improved speed of convergence.
 \review{Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
 Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed.
-Moreover, note that the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the iterates are not unique in each update.
-Due to the above said reasons, the iterative scheme outlined in Algorithm \ref{algo-4} cannot find a fixed point to ensure the convergence of the beamformer iterates.}
+Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the iterates are not unique in each update.
+Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot find a fixed point to ensure the convergence of the beamformer iterates.}
 

### 2015-07-30 Report/dual_approach.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response

--- 2015-07-25 Report/dual_approach.tex
@@
 
-Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{i}} iteration as
+Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{j}} iteration as
 \iftoggle{single_column}{\allowdisplaybreaks
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
-\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right \|^2 \eqsub \eqspace \\
 \text{subject to} &\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
@@
 }{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
-&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
+&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right \|^2 \eqsub \eqspace \\
 &\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
@@
 \end{IEEEeqnarray}}
-where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{i}} iteration as
+where \me{\mbfa{\zeta}^{(j)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(j)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{j}} iteration as
 \begin{equation} \label{const-admm1}
-\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
+\mbfa{\zeta}_b = \mbfa{\zeta}^{(j)}_b.
 \end{equation}
 
-Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
+Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{j}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
 \begin{equation}
-\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
+\mbfa{\zeta}_{b_k}(b)^{(j+1)} = \mbfa{\zeta}_{b}(b_k)^{(j+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
 \label{if-sg-update}
@@
 \begin{equation}
-\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
+\mbfa{\nu}_b^{(j+1)} = \mbfa{\nu}_b^{(j)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(j+1)} \right )
 \label{dual-sg-update}
@@
 	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
-	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall users}}
 	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
 	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
-	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
-	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
+	initialize the vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
 	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
 		\Repeat{convergence or \me{i \geq I_{\max}}}{
-			\Repeat{convergence or \me{j \geq J_{\max}}}{
+			\Repeat{convergence or \me{j \geq J_{\max}}, \me{\forall b \in \mc{B}}}{
 				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
@@
 \end{algorithm}
+%\begin{algorithm}
+%	\SetAlgoLined
+%	\DontPrintSemicolon
+%	\BlankLine
+%	\SetKwInput{KwInit}{Initialize}
+%	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
+%	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall users}}
+%	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
+%	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
+%	initialize the vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
+%	\Repeat{convergence or \me{i \geq I_{\max}}}{ 
+%		\Repeat{convergence or \me{k \geq K_{\max}}}{
+%			\Repeat{convergence or \me{j \geq J_{\max}}, \me{\forall b \in \mc{B}}}{
+%				solve for \me{\{\mbf{m}\}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
+%				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
+%				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
+%				update \me{j = j + 1}\;
+%			}
+%			update \me{\{\tilde{\mbf{u}}\}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\{\tilde{\epsilon}\}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
+%			$k = k + 1$, \me{j=0} \;
+%		}
+%		using \me{\{\mbf{m}\}}, update the receivers \me{\{\mbf{w}\}} of all users \;		
+%		update \me{\{\tilde{\mbf{u}}\}} or \me{\{\tilde{\epsilon}\}} respectively with \me{\{\mbf{m}\}} and \me{\{\mbf{w}\}} \;
+%		$i = i + i$, \me{k=0} \;
+%	}
+%	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
+%	\label{algo-3}
+%\end{algorithm}
 
 The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}.
-\review{In practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of steps, say, \eqn{J_{\max}}.
+\review{To reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
 If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
-It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
-However, if the distributed algorithms are performed for adequate number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step, then the limit point of the sequence of iterates is a stationary point of \eqref{eqn-6}.}
+The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
+However, if the distributed methods are performed for an adequate number of iterations to ensure the strict monotonicity of the objective sequence in each \ac{SCA} update, then the limit point of the sequence of iterates is a stationary point of the nonconvex problem \eqref{eqn-6}.} %Note that the receivers can also be updated together with the transmit precoders in each \ac{SCA} step, \textit{i.e.}, \eqn{K_{\max} = 1}, since the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained in each \ac{SCA} step.}
 
@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
-\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(j)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(j-1)}T} \left ( \mbfa{\zeta}^{\set{b}(j)} - \mbfa{\zeta}^{(j-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(j)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(j-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
+\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(j-1)}_{l,k,n,{\hat{b}}} \nonumber \\
 && \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \label{eqn-dual-1d} \\
-&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
+&& \zeta^{\set{b}(j)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
 &\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3}, \IEEEyessubnumber \label{eqn-dual-1f}
@@
 \begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
-\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right )  \nonumber \\
-&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\
+\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(j)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(j-1)}T} \left ( \mbfa{\zeta}^{\set{b}(j)} - \mbfa{\zeta}^{(j-1)}(b) \right )  \nonumber \\
+&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(j)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(j-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\
 \text{subject to} &\quad& \nonumber \\
-\beta_{l,k,n} \geq \sum_{\mathclap{j = 1,j \neq l}}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
+\beta_{l,k,n} \geq \sum_{\mathclap{j = 1,j \neq l}}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(j-1)}_{l,k,n,{\hat{b}}} \nonumber \\
 + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\
-\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
+\zeta^{\set{b}(j)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
 && \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3}, \IEEEyessubnumber \label{eqn-dual-1f}
 \end{IEEEeqnarray}}}
-where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i-1)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.
+where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(j-1)}} denotes the updated global interference level from the \me{\ith{(j-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(j-1)}, \forall b \in \mc{B}}.
 
 Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}.
-Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}.
-Since the entries in \me{\mbfa{\zeta}^{(i)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}.
-For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
+Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(j)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(j)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(j)}, \forall b \in \mc{B}}.
+Since the entries in \me{\mbfa{\zeta}^{(j)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(j)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}.
+For instance, the entry \me{\zeta^{(j)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(j)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(j)}_{l,\mc{U}_{b_k}(1),n,b}} as
 \begin{equation}
-\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
+\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(j)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(j)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(j)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
 \label{zeta_update}
@@
 \begin{equation}\label{dual-sg-update}
-\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ).
+\nu^{\set{b_k}(j)}_{l,k,n,b} = \nu^{\set{b_k}(j-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(j)}_{l,k,n,b} - \zeta^{(j)}_{l,k,n,b} \right ).
 \end{equation}

### 2015-07-30 Report/wsrm_formulation.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response

@@
 Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}.
-Let \eqn{\{\mbf{m}^{(i)}_j, \mbf{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step.
-In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is updated as \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_j, \mbf{w}^{(i-1)}_{\ast}, \mbf{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
+Let \eqn{\mbf{m},\mbf{w}}, and \eqn{\mbfa{\beta}} denote the corresponding sets obtained by grouping all transmit precoders, receive beamformers and interference values respectively in the system.
+Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step.
+In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is updated as \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\ast}, \mbfa{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
 \begin{algorithm}
@@
 	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
-		\Repeat{\ac{SCA} convergence or \me{j \geq J_{\max}}}{
+		\Repeat{\ac{SCA} convergence or \me{j \geq K_{\max}}}{
 			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
-			update \me{\tilde{\mbf{u}}_{l,k,n}} and the constraint set \eqref{eqn-8} with the newly found \me{\mvec{m}{l,k,n}} and \me{\mvec{\beta}{l,k,n}} using \eqref{eqn-wsrm-expr}\;
-			$j = j + 1$\;
+			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr} and increment $j = j + 1$\;
 		}

### 2015-07-30 Response/Response 2/response-1.tex
Updated with proper response

@@
 
-\resp  Even though the objective converges in each \ac{SCA} update, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} converge.
-The multiple solution follows from the convex objective of the original problem, which can have multiple solutions.
-However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [31] and [32].
+\resp  Even though the objective converges in each \ac{SCA} update, it is not guaranteed for the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} to converge.
+It follows from the convexity of the objective in problem (16), which can have multiple solutions in the feasible set.
+However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [30] and [31].
 This approach ensures the uniqueness of the solution in each \ac{SCA} update.
@@
 This and the fact that the set is compact ensure that the \ac{SCA} converges to a limit point.
-We have updated the manuscript to include this information in the convergence proof for the centralized algorithm in Appendix A.
-The modifications are included in Appendix A-B around (46) and in Appendix A-C after (50).
+We have updated the manuscript to include this information in the convergence proof of the centralized algorithm in Appendix A.
+The above modifications are included in Appendix A-B around (46) and in Appendix A-C after (50).
 

### 2015-07-30 Response/Response 2/response-2.tex
Updated with proper response

@@
 We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic method under Section III-D final paragraph.
-However, as the number of users in the system increases, all sub-channel ordering schemes are similar in minimizing the total number of backlogged packets in the system without any noticeable gain.
+However, it is worth noting that as the number of users in the system increases, all sub-channel ordering schemes are similar in minimizing the total number of backlogged packets in the system without any noticeable gain.
 
@@
 
-\resp We thank the reviewer for raising the important concern regarding the convergence issue of the distributed algorithms.
-We want to clarify that we are able to prove the convergence of Algorithm 2 which is based on \ac{ADMM}.
-In our paper the number of updates for the \ac{ADMM} part is denoted by \eqn{J_{\max}}.
-There is a trade-off between signaling overhead and achievable performance by varying \eqn{J_{\max}}.
-In reality we may set \eqn{J_{\max}} to a finite value to reduce the signaling overhead.
-In such a case, the convergence is not guaranteed.
-In our simulations, the \ac{ADMM} part can find an optimal solution to the (convex) subproblem in each \ac{SCA} step when \eqn{J_{\max} = 20}.
+\resp We thank the reviewer for raising the concern regarding the convergence of the distributed algorithms.
+We have substantially improved the clarity of both primal and the \ac{ADMM} based approach in the revised manuscript (see Appendix B).
+There, we have utilized the strong convexity of the objective function to ensure the uniqueness of the minimizer in each \ac{SCA} step.
+Additionally, since each subproblem in (20) or (28) has a convex feasible set, the convergence of the \ac{ADMM} scheme is guaranteed by using [10] and [36, Prop.
+4.2] as discussed in Appendix B.
+
+In our paper, the number of \ac{ADMM} iterations is denoted by \eqn{J_{\max}} in Algorithm 2.
+In order to obtain the centralized solution, we need to perform the distributed approaches until convergence or for very large value of \eqn{J_{\max}}.
+In practice, it may not be possible to perform the distributed methods until convergence.
+In such cases, the overall convergence of the objective sequence and beamformer iterates of Algorithm 2 is not guaranteed.
+The reason is that the strict monotonicity of the objective is not ensured in each \ac{SCA} update.
+
+However, if we perform the distributed algorithms for significantly enough to ensure strict monotonicity of the objective, then the overall of convergence of Algorithm 2 is guaranteed by following the arguments in [27].
+Note that in addition, uniqueness of the limit point is also necessary for the sequence convergence.
+It can be assured by regularizing the original convex objective with a quadratic term as in (46b) in each \ac{SCA} step to guarantee strong convexity, and thereby ensuring a unique minimizer and limit point.
+
+Additionally, to reduce the signaling overhead involved with the information exchange due to multiple loops, we can also combine the \ac{MMSE} receiver update in (23b) after each \ac{SCA} step for the transmit precoders.
+If in addition \eqn{J_{\max}} is sufficiently large, then the strict monotonicity of the objective sequence is still ensured by the combined update.
+It follows from the fact that the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained after each \ac{SCA} update.
+The newly found solution is also feasible and the objective improves monotonically in strict sense.
+Therefore, if the above conditions are satisfied, then the convergence of the sequence of iterates is guaranteed.
+
+For our simulation scenario, we have fixed the maximum number of \ac{ADMM} iterations in each \ac{SCA} step as \eqn{J_{\max} = 20}.
+Note that it is sufficient to ensure strict monotonic decrease of the objective value in each \ac{SCA} step.
+However, the number of iterations to ensure strict monotonicity of the objective depends on the problem under consideration.
+The practical significance of limited number of \ac{ADMM} iterations is discussed briefly in [10, Section 3.2.2].
+
+Response for the reviewer questions related to the \ac{ADMM} convergence for subproblem (20).
 
 \begin{itemize}
-\item The fixed point for the algorithm exists if the distributed approaches are performed until convergence or iterated for significant number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step.
-In such scenarios, the iterative method in Algorithm 2 finds a fixed point such that \eqn{\mc{A}(\mbf{x}^{\ast}) = \mbf{x^{\ast}}}, \eqn{\forall \mbf{x}^{\ast} \in \mc{F}^{\ast}}, where \eqn{\mc{F}^{\ast}} is the set of all fixed points of the algorithm and \eqn{\mc{A}} denotes the Algorithm 2 at each \ac{AO} update point as in (54).
+\item Note that the objective is regularized with a quadratic term to ensure strong convexity as discussed in [30], [31].
+Since the primal objective and the augmented Lagrangian are strongly convex, the optimal solution is unique due to the convexity of the feasible domain.
+Therefore, the limit point of the \ac{ADMM} algorithm is unique, which guarantees the existence of fixed point.
 
-\item Note that in each \ac{SCA} step, the iterative procedure in Algorithm 2 finds a (unique) solution by solving (20) or (28) with the previous solution as the operating point.
-Therefore, the fixed point of Algorithm 2 depends on the initial operating point chosen for the iterative procedure.
-Upon convergence, the fixed point of Algorithm 2 can be distinct for different starting points chosen to initialize the iterative procedure.
+\item Note that if the objective function is convex, then it can have multiple optimal solutions.
+However, due to the additional quadratic term in the objective of (20) in each \ac{SCA} step, uniqueness of the minimizer is ensured.
+Therefore, even though the original problem (20) with the convex objective has a set of fixed points, due to the strong convexity of the modified objective, the \ac{ADMM} will find a fixed point upon convergence.
+However, note that the choice of fixed point depends on the \ac{SCA} operating point, since it is also used to regularize the objective as in (46b).
 
-\item Since the original problem is nonconvex, there exists multiple stationary point.
-Therefore, if the Algorithm 2 is initialized with a feasible operating point, then the limit point of the iterative algorithm is a fixed point of Algorithm 2, provided strict monotonicity of the objective and the uniqueness of the iterates are ensured in each \ac{SCA} step.
-Due to the fact that the limit point depends on the chosen initial operating point, there exists a set of limit points, which are also a fixed point of Algorithm 2.
-Therefore, all fixed points found by Algorithm 2, satisfying strict monotonicity and the uniqueness of the iterates in each \ac{SCA} step, are stationary points of the original nonconvex problem (16).
+\item Using the earlier argument, any fixed point is a solution for the problem (20), since the original convex objective can have multiple solutions.
+The particular choice of the fixed point of the \ac{ADMM} approach depends on the operating point used in the regularization term in the objective.
 
-\item We also want to remark that  the proposed distributed algorithms are not based on fixed-point theory.
-The \ac{ADMM} part is to find a (unique) optimal solution to the strongly convex subproblem in each \ac{SCA} step.
-More explicitly, the \ac{ADMM} approach is used to solve the problem given in (20) based on augmented Lagrangian function which is different from fixed-point theory.
-However, the optimal solution of (20) is not necessarily a fixed-point of the problem.
-
-\item When the ADMM approach converges, the interference vector is guaranteed to be equal to the actual interference seen in the network.
-This is the main principle of \ac{ADMM} where the local variables (the vectors in (38)) converge to the global variables (the actual inference vectors).
-
-\item Another point we want to make is that Algorithm 2 yields a stationary point of the original noncovex problem upon convergence and this stationary point may not be a fixed-point of the original noncovex problem, \textit{i.e.}, \eqn{f(\mbf{x}) = \mbf{x}}.
-
-\item Since Algorithm 3 is based on a heuristic iterative approach to find a solution of \ac{KKT} equations, we cannot prove its convergence.
-When Algorithm 3 terminates, we will use the transmit and receive beamforming vectors to calculate the original objective.
+\item Upon convergence of the \ac{ADMM} approach, the interference vector is guaranteed to be equal to the actual interference seen in the network.
+This is the main principle of \ac{ADMM} where the local variables (the vectors in (38)) converge to the global variables, which are the actual inference vectors.
 
 \end{itemize}
+
+On the other hand, the iterative method described in Algorithm 3 is based on a heuristic iterative approach to find a solution of \ac{KKT} equations, we cannot prove its convergence.
+When Algorithm 3 terminates, we will use the transmit and receive beamforming vectors to calculate the original objective.
+Based on the reviewer comments, we have mentioned that the convergence of the Algorithm 3 cannot be proved theoretically (see Appendix B last paragraph).
 
@@
 The discussion on the convergence of the KKT based approach for MSE reformulation scheme is also presented in Appendix B last paragraph.
-For reference purpose, we have also referred the interested reader to [10], which discusses exclusively about the ADMM approach.
+For reference purpose, we have also referred the interested reader to [10], which discusses exclusively about the \ac{ADMM} approach.
 

### 2015-07-30 Response/Response 2/response-3.tex
Updated with proper response

@@
 It is described briefly in the fourth paragraph following (23).
-We have also provided a detailed discussion on how to update the operating point after each iteration in the paragraph following (23).
+We have also provided a detailed discussion on how to update the operating point after each iteration in the paragraphs following (23).
 Since the objective function is convex, we can update the current operating point with the solution obtained from the previous iteration as
 \begin{equation}
-\tilde{\mbf{m}}_{j}^{(i)} = \mvec{m}{j}^{(i)}.
+\tilde{\mbf{m}}_{j}^{(i)} = \mvec{m}{j}^{(i)}
 \end{equation}
+where \eqn{\mbf{m} = \{\mbf{m}_{l,k,n} \}_{\forall l, \forall k \in \mc{U}, \forall n}} corresponds to the collection of all transmit precoders in the system.
 Note that \eqn{\tilde{\mbf{m}}_{j}^{(i)}} is the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step and \eqn{\mbf{m}_{j}^{(i)}} is the solution obtained by solving (20) in the \eqn{\ith{j}} \ac{SCA} iteration.

### 2015-07-30 Report/wsrm_formulation.tex
Updated with proper response

@@
 Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}.
-Let \eqn{\mbf{m},\mbf{w}}, and \eqn{\mbfa{\beta}} denote the corresponding sets obtained by grouping all transmit precoders, receive beamformers and interference values respectively in the system.
-Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution obtained by solving \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step.
-In order to proceed with the iterative procedure, the operating point for the \eqn{\ith{(j+1)}} \ac{SCA} step is updated as \eqn{\tilde{\mbf{u}} = \mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\ast}, \mbfa{\beta}^{(i)}_{j} \}}, where \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
+For brevity, let us consider \eqn{\mbf{m}} as the collection of all transmit precoders in the system as \eqn{\mbf{m} = \{\mvec{m}{l,k,n}\}_{\forall l,\forall k, \forall n}}.
+Similarly, we denote \eqn{\mbf{w}} and \eqn{\mbfa{\beta}} as \eqn{\{\mvec{w}{l,k,n}\}_{\forall l,\forall k, \forall n}} and \eqn{\{\mvec{\beta}{l,k,n}\}_{\forall l,\forall k, \forall n}} respectively.
+Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution of \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step.
+Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\ast}, \mbfa{\beta}^{(i)}_{j} \}}.
+Note that \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver, which is obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
 \begin{algorithm}

### 2015-07-31 Response/Response 2/response-2.tex
updated

@@
 
-Response for the reviewer questions related to the \ac{ADMM} convergence for subproblem (20).
+Regarding the specific comments related to the \ac{ADMM} convergence for subproblem (20), we provide the following remarks by considering that the objective is regularized by a quadratic term as discussed in Appendix A-B to ensure strongly convexity.
 
-\begin{itemize}
-\item Note that the objective is regularized with a quadratic term to ensure strong convexity as discussed in [30], [31].
-Since the primal objective and the augmented Lagrangian are strongly convex, the optimal solution is unique due to the convexity of the feasible domain.
-Therefore, the limit point of the \ac{ADMM} algorithm is unique, which guarantees the existence of fixed point.
+\begin{enumerate}
+\item The primal objective and the augmented Lagrangian are strongly convex, therefore, the optimal solution exists and is unique in the feasible convex set of subproblem (20).
+It follows from that the \ac{ADMM} algorithm converges to a unique limit point, which is a fixed point of the iterative \ac{ADMM} algorithm.
 
-\item Note that if the objective function is convex, then it can have multiple optimal solutions.
-However, due to the additional quadratic term in the objective of (20) in each \ac{SCA} step, uniqueness of the minimizer is ensured.
-Therefore, even though the original problem (20) with the convex objective has a set of fixed points, due to the strong convexity of the modified objective, the \ac{ADMM} will find a fixed point upon convergence.
-However, note that the choice of fixed point depends on the \ac{SCA} operating point, since it is also used to regularize the objective as in (46b).
+\item In general, the fixed point of the subproblem (20) is not unique.
+It is due to the fact that the original objective is convex, and therefore it can have multiple solutions in the feasible convex set.
+Therefore, the \ac{ADMM} algorithm can have a set of fixed points in the feasible set.
+However, if we regularize the objective with a strongly convex quadratic term as discussed in Appendix A-B, then the distributed approach finds a fixed point of the original convex subproblem.
 
-\item Using the earlier argument, any fixed point is a solution for the problem (20), since the original convex objective can have multiple solutions.
+\item By using previous argument, any fixed point of the algorithm is a solution for the problem (20), since the original convex objective can have multiple solutions.
 The particular choice of the fixed point of the \ac{ADMM} approach depends on the operating point used in the regularization term in the objective.
@@
 
+\end{enumerate}
+
+However, to answer the reviewer questions in relation to the overall convergence of the distributed method presented in Algorithm 2, we consider the following conditions are satisfied in each \ac{SCA} update step.
+\begin{itemize}
+	\item The objective function is regularized by a quadratic term as discussed in Appendix A-B to ensure strict convexity of the objective function, which leads to the uniqueness of the solution.
+	\item The distributed algorithms are performed until convergence or for sufficient number of iterations to ensure strict monotonic decrease of the objective sequence.
 \end{itemize}
+Upon satisfying the above conditions, even if we update the receive beamformers using the \ac{MMSE} receiver in (23b) after each \ac{SCA} step for solving the transmit precoders, strict monotonicity is still ensured.
+It follows from the fact that the \ac{MMSE} receivers are optimal for the fixed transmit precoders, and therefore the objective sequence decreases monotonically after each update in strict sense.
+
+\begin{enumerate}
+	\item Since the above conditions are satisfied by Algorithm 2, then the existence of a fixed point for Algorithm 2 is guaranteed by following the arguments in [27].
+
+	\item In general, fixed point of Algorithm 2 is not unique.
+Note that the iterative nature of the \ac{SCA} approach is based on approximating the nonconvex constraint by a convex one around some fixed operating point.
+While initializing the iterative Algorithm 2, we need to find a fixed operating point upon which the convex function is approximated.
+Therefore, depending on the choice of initial feasible point, the algorithm terminates at different fixed point upon convergence.
+Hence, there exist a set of fixed points for Algorithm 2.
+
+	\item The nonconvex problem (16) can have multiple stationary points and the iterative method proposed in Algorithm 2 finds a stationary point of the nonconvex problem.
+Therefore, all fixed points found by Algorithm 2 upon convergence are indeed the stationary points of the original nonconvex problem.
+
+	\item Upon convergence of the \ac{ADMM} approach, the interference vector is guaranteed to be equal to the actual interference seen in the network.
+This is the main principle of \ac{ADMM} where the local variables (the vectors in (38)) converge to the global variables, which are the actual inference vectors.
+
+\end{enumerate}
 

### 2015-07-31 Report/dual_approach.tex
updated

@@
 }{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
-&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right \|^2 \eqsub \eqspace \\
+	&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b   ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b  ) +  \tfrac{\rho}{2}  \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b  \|^2 \eqsub \eqspace \\
 	&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
@@
 	& \text{and } \eqsub \eqref{eqn-8}
-\end{IEEEeqnarray}}
+\end{IEEEeqnarray}
+}
 where \me{\mbfa{\zeta}^{(j)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(j)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{j}} iteration as
@@
 \begin{equation}
-\mbfa{\nu}_b^{(j+1)} = \mbfa{\nu}_b^{(j)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(j+1)} \right )
+\mbfa{\nu}_b^{(j+1)} = \mbfa{\nu}_b^{(j)} + \rho \: (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(j+1)}  )
 \label{dual-sg-update}
 \end{equation}
-where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration.
-The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}.
+where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model.
+The convergence rate is susceptible to the choice of step size parameter \me{\rho}.
 In numerical simulations, we consider step size \me{\rho=2}.
-The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of iterations, say, \eqn{J_{\max}}.
-The \ac{ADMM} based precoder design is outlined in Algorithm \ref{algo-3}.
+The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of steps, say, \eqn{J_{\max}}.
+Algorithm \ref{algo-3} outlines a practical way of implementing the \ac{ADMM} based precoder design with minimal signaling overhead.
 \begin{algorithm}
@@
 			}
-			send precoded downlink pilot with \me{\mbf{m}}\;
-			evaluate \me{\mvec{w}{l,k,n}} at each user and inform to all \acp{BS} in \eqn{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective} \;
+			send precoded downlink pilot with \me{\mbf{m}_{l,k,n}}\;
+			evaluate \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} at each user \;
 			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
@@
 The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
-However, if the distributed methods are performed for an adequate number of iterations to ensure the strict monotonicity of the objective sequence in each \ac{SCA} update, then the limit point of the sequence of iterates is a stationary point of the nonconvex problem \eqref{eqn-6}.} %Note that the receivers can also be updated together with the transmit precoders in each \ac{SCA} step, \textit{i.e.}, \eqn{K_{\max} = 1}, since the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained in each \ac{SCA} step.}
+However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large to ensure strict monotonicity of the objective, then the convergence can be guaranteed (see Appendices \ref{sec-3.5} and \ref{sec-dist-conv}).
+Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured.
+The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.}
+
+%	Additionally, if the receivers are updated together with the transmit precoders using \eqref{eqn-10} in each \ac{SCA} step, strict monotonicity is still ensured, since the \ac{MMSE} receivers are optimal for the fixed transmit precoders.}
+%However, if the distributed methods are performed for an adequate number of iterations to ensure the strict monotonicity in each \ac{SCA} update, then the limit point of the sequence of iterates is a stationary point of the nonconvex problem \eqref{eqn-6}.
+Note that the receivers can also be updated together with the transmit precoders in each \ac{SCA} step, \textit{i.e.}, \eqn{K_{\max} = 1}, since the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained in each \ac{SCA} step.}
 

### 2015-07-31 Report/kkt_mse_approach.tex
updated

@@
 In this section, we discuss an alternative way to decentralize the precoder design across the coordinating \acp{BS} in \me{\mc{B}} based on the \ac{MSE} reformulation method discussed in Section \ref{sec-3.3}.
-In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the global queue deviation objective with few number of iterations.
+In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the queue deviation with few number of iterations.
 \review{The alternative way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}

### 2015-08-03 Response/Response 2/reviewer_response.tex
Before Antti Corrections

--- 2015-03-24 Response/reviewer_response.tex
@@
 \usepackage{amsmath,amssymb}
-\usepackage{acronym,etoolbox,color,multicol}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}
+\usepackage[dvipdfmx]{graphicx}
+\usepackage{acronym,etoolbox,color,multicol,xcolor}
+%\usetikzlibrary{plotmarks}
+\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools,pgfplots,subfig}
+
+\pgfplotsset{compat=newest}
+\pgfplotsset{plot coordinates/math parser=false}
+\newlength\figureheight
+\newlength\figurewidth
 
@@
 
-\input{./../Report/shortcuts}
-\input{./../Report/acronyms}
+\input{./../../Report/shortcuts}
+\input{./../../Report/acronyms}
 
+\DeclareGraphicsExtensions{{eps}}
+\graphicspath{{Figures/}}
 \renewcommand \thesection{\Roman{section}}
@@
 
+\renewcommand{\thefigure}{\Alph{figure}}
+\renewcommand{\thesubfigure}{\roman{subfigure}}
+%\renewcommand{\thesubfigure}{\Roman{figure}}
+\renewcommand{\theequation}{\roman{equation}}
+
 \begin{document}
 
+\usetikzlibrary{plotmarks}
 \title{Reviewers Comments \& Authors Replies}
@@
 \vspace{0.5in}
-The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript of the paper, which have been greatly helpful to improve the paper quality.
-Based on the comments, we have made several major revisions to the paper, following the suggestions of the reviewers.
-In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors.
-Unless otherwise stated, all the numbered items (figures, equations, references, etc) in this response letter refer to the revised manuscript.
-The revisions in the revised manuscript are highlighted using blue color and the authors responses are also presented in blue color text.
-Following is the summary of the revision made on the manuscript in accordance with the reviewers comments.
+The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript, which have been greatly helpful to improve the paper quality.
+Based on the comments, we have made several revisions to the paper, which are summarized below.
 \input{additions}

### 2015-08-03 Report/convergence_centralized.tex
Before Antti Corrections

@@
 \end{itemize}
-\review{Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity is guaranteed from Section \ref{mcity} with modified objective \eqref{mod_obj}}.
+\review{Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity is guaranteed from Section \ref{mcity} by using the modified objective \eqref{mod_obj}}.
 Using \cite{zangwill1969nonlinear} and \cite[Th.

### 2015-08-03 Report/convergence_distributed.tex
Before Antti Corrections

@@
 Now, by using \cite[Prop.
-4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} with a diminishing step size.
+4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as presented in \cite{boyd2011distributed}.
 If both the primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence generated by the distributed methods is a stationary point of \eqref{con}, using similar arguments as in Appendix \ref{sec-3.5}.

### 2015-08-03 Report/kkt_mse_approach.tex
Before Antti Corrections

@@
 \mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6}\\
-\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
+\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + \enoise \IEEEyessubnumber \label{kkt-mse-4.4} \\
 t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.5} \\
@@
 	& \qquad {} + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \IEEEyessubnumber \label{kkt-mse-4.6} \\
-	\epsilon_{l,k,n}^{(i)} =& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i)}\|^2 \nonumber \\
+	\epsilon_{l,k,n}^{(i)} =& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \enoise \nonumber \\
 	& \qquad{} + \sum_{\mathclap{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
@@
 Upon receiving the transmit precoders from the \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}}.
-Then, the updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilots with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
+Then, the updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilots with \me{\tilde{\mbf{w}}_{l,k,n}^{(i)} = (\alpha_{l,k,n}^{(i)})^{\rfrac{1}{2}} \, \mvec{w}{l,k,n}^{\ast(i)}} and \me{\bar{\mbf{w}}_{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}.
 Upon receiving the precoded uplink pilots, each \ac{BS} evaluates the equivalent channels \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} to update the transmit precoders using \eqref{kkt-mse-4.3}.

### 2015-08-03 Report/simulation_distributed.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response
Before Antti Corrections

@@
 Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{fig-9-3}
-	\caption{Impact of varying \me{q} on the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace} and \me{Q_k = [9,16,14,16,9,13,11,12]} bits}
-	\label{fig-d-3.1}
-\end{figure}
 
@@
 The objective values are mentioned in the legend for all the schemes and the \me{\ell_1} norm is used for comparison.
-\begin{figure*}
+\begin{figure}
 	\centering
-	\subfloat[][Average backlogged packets in the system after \me{250} transmission instants]{
-		\includegraphics[width=0.48\textwidth]{average_queue_over_time-3}
-		\label{fig-review}
-	}
-	\hfill
-	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 6} bits]{
-		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-4}
-		\label{fig-review-time}
-	}
-	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace}}
-	\label{fig-time-analysis}
-\end{figure*}
+	\includegraphics[width=\columnwidth]{fig-9-3}
+	\vspace{-0.2in}
+	\caption{Impact of varying \me{q} on the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace} and \me{Q_k = [9,16,14,16,9,13,11,12]} bits}
+	\label{fig-d-3.1}
+\end{figure}
 

### 2015-08-03 Report/time_correlated.tex
Before Antti Corrections

@@
 The \ac{PL} is modeled as a uniform random variable \me{[0,-6]} dB.
+\begin{figure*}
+	\centering
+	\subfloat[][Average backlogged packets in the system after \me{250} transmission instants]{
+		\includegraphics[width=0.48\textwidth]{average_queue_over_time-3}
+		\label{fig-review}
+	}
+	\hfill
+	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 6} bits]{
+		\includegraphics[width=0.48\textwidth]{instant_queue_over_time-4}
+		\label{fig-review-time}
+	}
+	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace}}
+	\label{fig-time-analysis}
+\end{figure*}
 
 Fig.
-\subref*{fig-review} plots the average of the total number of backlogged packets left out in the system after each transmission instant, \textit{i.e}, \me{\mathbf{\mathrm{E}}_i \, [ \sum_k \left [ Q_k(i) - t_k(i) \right ]^+ ]}.
+\subref*{fig-review} plots the average of the total number of backlogged packets left out in the system after each transmission instant, \textit{i.e}, \me{\mathbf{\mathbb{E}}_i \, [ \sum_k \left [ Q_k(i) - t_k(i) \right ]^+ ]}.
 Unlike the \ac{Q-WSRM} scheme, the average backlogged packets of the \me{\ell_2} \ac{JSFRA} scheme is comparable to the \ac{Q-WSRME} approach for all average arrival rates due to the explicit rate constraints \eqref{eqn-3.1.4}.

### 2015-08-06 Response/Response 2/response-1.tex
finalized for final submission

--- 2015-07-30 Response/Response 2/response-1.tex
@@
 \vspace{1eM}
-For the resubmitted manuscript, the reviewer still has the following concerns
+\review{For the resubmitted manuscript, the reviewer still has the following concerns}
 
@@
 
-\resp We have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results) to provide additional details for the convergence proof.
-We believe the removed parts do not affect the readability of the paper and the added text regarding convergence proof certainly improves the quality.
+\resp We have removed a couple of paragraphs from Section III-A and shortened the discussions on Section V (\textit{i.e.}, the simulation results) to provide additional details on the convergence proof.
+We believe the removed parts do not affect the readability of the paper and the added text regarding the convergence analysis certainly improves the quality.
 
@@
 
-\resp  Even though the objective converges in each \ac{SCA} update, it is not guaranteed that the iterates involved in the iterative algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} converge.
-The multiple solution follows from the convex objective of the original problem, which can have multiple solutions.
-However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective function with a quadratic term as discussed in [31] and [32].
-This approach ensures the uniqueness of the solution in each \ac{SCA} update.
-
-Since our problem is (highly) nonconvex, there are possibly many stationary points.
-If we start from different initial points, we may end up in different stationary points.
-That is to say, the limit point of the \ac{SCA} approach is not unique.
-However, by regularizing the objective with a small quadratic term, the iterate in each step of the \ac{SCA} algorithm is unique.
-This and the fact that the set is compact ensure that the \ac{SCA} converges to a limit point.
-We have updated the manuscript to include this information in the convergence proof for the centralized algorithm in Appendix A.
-The modifications are included in Appendix A-B around (46) and in Appendix A-C after (50).
+\resp We thank the reviewer for the comment.
+It is true that the sequence of iterates generated by the iterative \ac{SCA} algorithm, namely, \eqn{\mbf{m}^{(i)}_k} and \eqn{\mbf{w}^{(i)}_k} need not converge even if the objective sequence converges.
+It follows from the fact that there can be multiple minimizers (solutions) for the convex subproblem in each \ac{SCA} step.
+However, we have modified the convergence discussion using the strong convexity argument by regularizing the objective of each \ac{SCA} subproblem with a quadratic term as discussed in [30] and [31].
+The additional quadratic term ensures the uniqueness of the minimizer in each of the \ac{SCA} subproblem.
+Due to the uniqueness of the minimizer and the strict monotonicity of the objective sequence in each \ac{SCA} step, the convergence of the iterates is guaranteed.
+The above discussion is included in Appendix A-B around (46) and in Appendix A-C after (50).
 
@@
 
-\resp As suggested by the reviewer, we have included the strict monotonicity of the objective sequence in Appendix A-C following (52).
+\resp As suggested by the reviewer, we have included the argument to show the strict monotonicity of the objective sequence in Appendix A-C following (52).
 Moreover, we have also mentioned that we in fact use the regularized objective in (46b) to analytically prove the convergence of the iterates, although we have numerically observed that the objective sequence of Algorithm 1 (with the original objective) always converges.

### 2015-08-06 Response/Response 2/response-2.tex
finalized for final submission

@@
 The greedy ordering can be based on sorting the best channel gain from each sub-channel, which is obtained by finding the highest channel norm seen between any user and the corresponding serving \ac{BS}.
-
-	We remark that the choice of a sub-channel ordering scheme should also consider the number of backlogged packets associated with each user.
-We have emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user.
-We do not include in the manuscript due to space limitations, we have included in the response letter to answer the reviewers' question.
-We considered a system with \eqn{N = 4} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users.
-The \ac{PL} is distributed uniformly over \eqn{[0,-3]} dB.
-The number of backlogged packets assumed for each user is provided in the corresponding captions in Figure \ref{fig-review-1}.
+However, note that the interference among the neighboring users are not included in this procedure, since the precoders that are required to evaluate the interference are designed after the sub-channel selection step only.
 \begin{figure*}[h!]
@@
 
+We remark that the choice of a sub-channel ordering scheme should also consider the number of backlogged packets associated with each user.
+We have emphasized this issue by comparing various ordering schemes for the same system model with two different set of backlogged packets associated with each user.
+We do not include the following figures in the manuscript due to space limitations, nevertheless, we have included in the response letter to answer the reviewers' question.
+We considered a system with \eqn{N = 4} sub-channels, \eqn{N_B = 2} \acp{BS} with \eqn{N_T = 4} transmit antennas and \eqn{K = 12} single antenna users.
+The \ac{PL} is distributed uniformly over \eqn{[0,-3]} dB.
+The number of backlogged packets assumed for each user is provided in the corresponding captions in Figure \ref{fig-review-1}.
+
 Figure \ref{fig-review-1} compares different sub-channel ordering schemes in terms of the total number of backlogged packets remaining in the system.
 As can be seen from Figure \ref{fig-review-1}\subref{fig-review-1a}, the greedy sub-channel ordering provides a favorable way of choosing sub-channels to minimize the total number of backlogged packets.
-However in Figure \ref{fig-review-1}\subref{fig-review-1b}, it is evident that the greedy sub-channel ordering is no longer better in comparison to the few other random ordering schemes.
-We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic method under Section III-D final paragraph.
+However for another scenario in Figure \ref{fig-review-1}\subref{fig-review-1b}, it is evident that the greedy sub-channel ordering is no longer better in comparison to the few other random ordering schemes.
+Note that the difference between the two scenarios is only the queue distribution, which are listed out in the corresponding figure caption.
+We have included the discussions regarding the greedy sub-channel ordering in the revised manuscript as a heuristic approach under Section III-D final paragraph.
 However, it is worth noting that as the number of users in the system increases, all sub-channel ordering schemes are similar in minimizing the total number of backlogged packets in the system without any noticeable gain.
 
+\pagebreak
 \cmnt{2} \review{The authors mentioned that the signaling overhead of the distributed algorithm can be reduced by using a smaller number of iterations \eqn{J_{\max}}.
@@
 
+\resp We apologize for the lack of clarity in explaining this information in our earlier submission.
+To answer this question in detail, we consider the following scenarios based on the channel correlation between the adjacent transmission instants.
+
+\begin{itemize}
+\item At first we consider a semi-static scenario, where the channel remains constant for multiple transmission instants.
+Therefore, the \ac{CSI} information available at the transmitter or the centralized controller are valid for multiple transmission instants.
+In order to discuss the performance of the centralized and the distributed schemes, let us consider a system model with \eqn{N=4} sub-channels, \eqn{N_B = 3} \acp{BS}, each equipped with \eqn{N_T = 8} transmit antennas.
+Let \eqn{K = 12} be the number of users in the system equipped with \eqn{N_R = 1} receive antenna.
+Let the \ac{PL} between the \acp{BS} and the users are drawn uniformly between \eqn{[0,-3]} dB.
+Figure \ref{fig-review-2-a} plots the number of backlogged packets present in the system after each \ac{SCA} update point.
+Note that for \eqn{J_{\max} > 1}, each \ac{SCA} points includes \eqn{J_{\max}} number of \ac{ADMM} iterations performed.
+Therefore, it needs to be considered while analyzing the signaling overhead.
+Note that we consider only \ac{ADMM} based distributed approach outlined in Algorithm 2.
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.8\columnwidth]{reviewer_2_Q1C-B.eps}
+\caption{Convergence of the centralized and distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,12,8,1 \rbrace} using \me{\ell_1} norm with the backlogged packets as \eqn{Q_k = [17,7,14,14,12,14,8,13,8,11,9,12]} bits}
+\label{fig-review-2-a}
+\end{figure}
+
+Let us consider the centralized configuration, in which the \ac{CSI} required to be exchanged between \acp{BS} and the centralized controller.
+In order to quantify the amount of signaling overhead, let us consider that each real entity of the complex channel is represented by \eqn{N_C = 10} bits.\footnote{Note that \eqn{N_C = 10} bits can be justified for the \ac{CSI} quantization, since the precoders are designed based on the quantized \ac{CSI} fed back from the \acp{BS} to the centralized controller.} Using this information, the amount of signaling required to be exchanged between \acp{BS} and the centralized controller is given by \eqn{N \times N_B \times N_T \times K \times 2} real entities, which is equal to \eqn{23,040} bits.
+In addition, we also need the precoder signaling from the centralized controller to all \acp{BS}.
+It accounts to \eqn{N \times K \times N_T \times 2} real entities, which is equal to \eqn{7,680} bits.
+On the whole, it requires \eqn{30,720} bits that needs to be exchanged via backhaul over \eqn{T} transmission slots, where \eqn{T} denotes the number of slots for which the channel remains constant.
+Additionally, we also need to update the queue information to the controller in each transmission instant and the updated precoders are required to be transmitted back.
+Therefore, even though the \ac{CSI} is not required to be signaled to the controller, the precoders are fed back to all \acp{BS} in each transmission slot based on the current backlogged packets, which are updated by all \acp{BS} to the controller.
+Even though, we are not using quantized \ac{CSI} in our performance evaluation, it is worth noting that the achievable gains deteriorates significantly if the precoders are designed using the quantized \acp{CSI} [R1].
+
+On contrary, the distributed approach based on \ac{ADMM} requires only the exchange of coupling interference variables that are scalar values.
+For a fully connected network, each consensus variable binds only two \acp{BS} only, therefore, the overall number of entities that needs to be exchanged is \eqn{N \times (N_B - 1) \times K \times 2} real entries, which is equal to \eqn{960} bits by considering \eqn{N_D = 5} bits to represent the scalar coupling variables.
+Note that \eqn{5} bits are more than sufficient for representing the interference variables since they are bounded by the transmit power.
+Therefore, in each transmission instant, the overall signaling required to design the precoders jointly requires \eqn{J_{\max} \times I_{\max} \times 960} bits.
+Note that there is no need to exchange the backlogged packets to the coordinating \acp{BS} in the distributed scheme.
+Note that \eqn{I_{\max}} denotes the number of \ac{SCA} iterations and \eqn{J_{\max}} represents the inner \ac{ADMM} update steps.
+
+Now, let us consider the performance of \ac{ADMM} based distributed precoder design for different \eqn{J_{\max}} values as in Figure \ref{fig-review-2-a} for analyzing the signaling overhead required and the performance improvement from the exchange of information.
+The centralized scheme is given as a lower bound in Figure \ref{fig-review-2-a}, since the \acp{CSI} available at the controller can be used to design the precoder until convergence.
+Figure \ref{fig-review-2-a} shows noticeable improvement in the reduction of number of backlogged packets in the system as we increase the number of \ac{ADMM} iterations.
+However, note that as we increase the number of iterations, the signaling requirement also grows with the factor of \eqn{J_{\max}}.
+
+From Figure \ref{fig-review-2-a}, it is evident that the \ac{ADMM} with \eqn{J_{\max} = 1} requires \eqn{I_{\max} = 15} iterations to perform close enough to the centralized scheme.
+In order to reach the performance close enough to that of centralized scheme, using above assumptions, it requires \eqn{960 \times 15 = 14,400} bits to be exchanged among the coordinating \acp{BS}.
+Note that it is \eqn{\approx 0.62} times the overhead involved in the centralized scheme to feedback only the \acp{CSI} to the controller, assuming single transmission instant.
+However, since the channel remains constant for certain duration, say \eqn{T}, the centralized approach may be favorable for this type of scenario.
+It is worth noting that the precoder exchange, which is required at each instant due to the changing traffic, involves significant overhead that also needs to be accounted while considering the selection.
+
+However, if the channel changes once in every three transmission instants, \textit{i.e.}, the fed back \ac{CSI} is valid only for \eqn{T = 3}, then the distributed methods with \eqn{J_{\max} = 1} is preferred to the centralized approaches.
+The duration of the \ac{CSI} validity is evaluated using \eqn{B_{CSI} + B_{P} \times T = B_D \times T}, where \eqn{B_{CSI} = 23,040} denotes the number of bits required for the \ac{CSI} feedback, \eqn{N_C \times B_P = 7,680} corresponds to the number of bits required for the precoder feedback from the controller, and \eqn{B_D = 14,400} refers to the number of bits required to exchange the coupling interference variables in the distributed scheme.
+
+In general, the choice of selecting the centralized scheme over the decentralized approach depends on the factor \eqn{\Gamma} defined as
+\begin{equation}
+\Gamma \triangleq \left (\frac{N_C}{N_D} \right ) \times \frac{N_T \, (N_B + T)}{T \, (N_B - 1)}
+\end{equation}
+where \eqn{T} represents the duration over which the \ac{CSI} is valid for designing the precoders by the centralized controller.
+Note that we considered different quantization scales for the centralized and the distributed exchanges.
+If the fraction is \eqn{\Gamma > 1}, then the distributed scheme is preferred and if \eqn{\Gamma < 1}, then the centralized overhead is smaller and therefore, it is preferred.
+Note that we considered the distributed algorithms are iterated for the same count in each transmission slot.
+It is worth noting that since the channel is semi-static, the distributed schemes are not required to iterate for the same number of iterations in each transmission instant.
+Since the operating point can be chosen to be the solution obtained from the previous transmission instant, the convergence speed of the distributed algorithm can be accelerated significantly by doing so.
+
+Note that the above discussions does not include the overhead involved in the queue transfers to the controller and the loss in performance due to the distributed approach.
+The loss involved in the centralized performance due to the quantized \ac{CSI} is also not considered.
+Therefore, by using the above arguments, if the system size grows, \textit{i.e.}, as the number of transmit antennas increase, then the distributed approach is preferred to the centralized scheme even if the channel remains constant for longer duration such that \eqn{\Gamma > 1}.
+The reason is that the overhead involved in feeding back the precoders from the centralized controller will be significantly large.
+
+In practice, it is not required to perform the distributed approaches for higher number of iterations [Chapter 3.2.2, 10].
+According to the results in Figure \ref{fig-review-2-a}, it is sufficient to iterate for \eqn{I_{\max} = 10, J_{\max} = 1} iterations to achieve acceptable performance improvement from the coordinated precoder design.
+The reason is that the performance gained by exchanging additional coupling variables is marginal compared to the overhead involved in doing so.
+
+\item Secondly, we consider a time-correlated fading scenario, where the channel changes slowly over each transmission instant based on the user mobility or the surrounding environment.
+In such cases, the pilots are periodically sent from each user to measure the \ac{CSI} by each \acp{BS} to design the precoders efficiently.
+In such scenarios, where the channel cannot be assumed constant over multiple transmission instants, the distributed schemes are much preferred to the centralized approaches.
+One such analysis was studied in Section C of [12] using dual decomposition based distributed precoder design, where they have showed that it is enough to follow the fading process to obtain desired performance instead iterating until convergence.
+Using this argument, it is beneficial to just follow the fading process by using the precoders designed in the previous transmission as the operating point for the current instant for \ac{SCA} rather starting at some random feasible point.
+
+Studying the performance of distributed algorithms for the time correlated case is beyond the scope of our paper and thus is not considered in the current manuscript.
+However, we take this opportunity to show a plot demonstrating this behavior for the \ac{KKT} based algorithm presented in Section IV-C of the manuscript.
+Note that there is no need for the backhaul exchange to design the precoders in the \ac{KKT} scheme proposed in Algorithm 3.
+However, it requires the exchange of information via \ac{OTA} transmissions using precoded pilots as discussed in Section IV-C.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.8\columnwidth]{reviewer_2_Q2A.eps}
+	\caption{Expected number backlogged packets after each transmission instant for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,16,4,2 \rbrace} evaluated for \eqn{500} slots and \ac{PL} is distributed \eqn{\mathbb{U}(0,-3)}}
+	\label{fig-review-2}
+\end{figure}
+
+Figure \ref{fig-review-2} compares the performance of the distributed \ac{KKT} approach, \textit{i.e.}, Algorithm 3 for different values of \eqn{I_{\max}}.
+The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.\footnote{Please refer to [25] for further details.} We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the required information for \eqn{I_{\max} = 3,5,10}.
+The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{I_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{I_{\max}}{N_S})} is considered as a penalty involved due to the precoded pilot exchange.
+More details can be found in [R2] and [R3].
+The average number of backlogged packets after each transmission slot is evaluated as
+\begin{equation}
+\chi = \sum_{k = 1}^K \; [ Q_k - \tilde{t}_k ]^+
+\end{equation}
+and the \ac{PL} is distributed uniformly between \eqn{[0,-3]} dB.
+
+Unlike Algorithm 3, the centralized precoder design presented in Figure \ref{fig-review-2} does not include any penalty term and it is used as a benchmark.
+In order to improve the performance of the distributed scheme, the operating point involved in the \ac{SCA} algorithm is considered from the earlier frame instead of being generated randomly.
+Note that the performance of the distributed scheme is significantly improved by performing the internal iterations as discussed in [25] as strategy B.
+By doing so, we can achieve the performance close enough to the centralized approach (which does not included any penalty term in the rate).
+Therefore, for the time-correlated scenarios, it would be beneficial to do distributed approaches as discussed above to avail the channel correlation rather than feeding back the \acp{CSI} to the centralized controller.
+
+\end{itemize}
+
+\vspace{1eM}
+[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti T\"{o}lli, Markku Juntti,  and Savo Glisic, "{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}'', \textit{IEEE Trans.
+Signal Process}., vol 61, no.
+22, pp.
+5659-5674, Nov.
+2013.
+
+[R2] Changxin Shi, Berry R.A., Honig M.L., ``{Bi-Directional Training for Adaptive Beamforming and Power Control in Interference Networks}," \textit{IEEE Transactions on Signal Processing}, vol.62, no.3, pp.607,618, Feb.1, 2014
+
+[R3] P.
+Jayasinghe, A.
+T\"{o}lli, J.
+Kaleva,  M.
+Latva-aho, "{Bi-directional Signaling for Dynamic TDD with Decentralized Beamforming}'', in \textit{Proceedings of IEEE ICC SmallNets Workshop}, London, UK, June, 2015
+
+\vspace{1eM}
+
+The discussions are described in a condensed form in the first paragraph of Section IV and in the first and the last paragraph of Section IV-C.
+
+\begin{comment}
+
 	\resp
 	We thank the reviewer for the insightful comment and we apologize for the lack of clarity in explaining this information in our earlier manuscript.
+The answer to this question, we need to consider the following scenarios.
 	\begin{enumerate}
-		\item The amount of signaling overhead of the distributed algorithm and the centralized one depends on the system model of consideration.
+	\item[(i)] How big is the system configuration and
+	\item[(ii)] How fast the channel varies in relation to the transmit frame duration, \textit{i.e.}, whether the channel is semi-static (where the \ac{CSI} remains almost constant for multiple transmission slots) or time-correlated (where the channel changes over each transmission slot with some memory).
+	\end{enumerate}
+
+	\begin{itemize}
+
+	\item Based on the condition (i), we can discuss the possibilities of the centralized schemes over the distributed methods using the amount of signaling overhead involved in the precoder design.
+
+	\begin{enumerate}
+	\item The amount of signaling required for the distributed algorithms and the centralized ones depend on the system configuration under consideration.
 For example, let us consider a model with \eqn{N = 1} sub-channel, \eqn{K = 4} users and \eqn{N_B = 2} \acp{BS}, each serving 2 users.
@@
 
-		In order to quantify the total number of bits required in a centralized solution, let us assume that each complex channel for a \ac{SISO} model requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is more important) or it can be a equal share of \eqn{5} bits for both amplitude and phase.
+	In order to quantify the total number of bits required for a centralized solution, let us assume that each scalar complex channel component requires \eqn{10} bits, \textit{i.e}, \eqn{4} bits for amplitude and \eqn{6} bits for phase (assuming phase is more important) or it can be a equal share of \eqn{5} bits for both amplitude and phase.
 Using this assumption, the total number of bits for channel information to be exchanged via backhaul is \eqn{10 \times K \times N_B \times N_R \times N_T = 320} bits.
-On the other hand, for the distributed algorithms, let us consider \eqn{6} bits for quantizing each element of the consensus vectors.
+On the other hand, for the distributed algorithms, let us consider \eqn{6} bits for quantizing each element of the real-valued coupling variables.
 Consequently, the proposed distributed solutions require \eqn{6 \times 2 \times 2} bits to be exchanged in each iteration.
+Note that here we consider the distributed approaches discussed in Sections IV-A and IV-B only, since the \ac{KKT} based approach involves the precoded pilot transmissions to update the corresponding precoders and receivers.
 
-		In the above example, for the same signaling overhead as in centralized method, we can perform only up to 6 \ac{SCA} updates for \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for \ac{ADMM} part).
-This may not be sufficient for the distributed algorithms to attain the same performance as the centralized method.
+	In the above scenario, for the same amount of signaling overhead as that of the centralized schemes, we can perform only 6 \ac{SCA} updates with \eqn{J_{\max} = 2} (\textit{i.e.}, two updates for \ac{ADMM} part).
+This may not be sufficient for the distributed algorithms to attain the same performance as that of the centralized methods.
 However, as the number of sub-channels, users and/or the antenna elements increases, it may not be a feasible option to send complete \acp{CSI} across the coordinating \acp{BS} to the centralized controller in the current cellular systems.
+
 	In addition to comparing the signaling overhead, we also need to consider the performance loss due to the \ac{CSI} quantization in the centralized approaches, which is beyond the scope of our paper.
@@
 Moreover, in the centralized algorithm, resulting transmit precoders need to be exchanged with the corresponding \acp{BS} before the actual transmission, which involves significant overhead in the backhaul usage.
+Using the above discussion, we can say that for a small sized systems, centralized algorithm would be preferable as compared with the distributed schemes.
 
 	\vspace{1eM}
-		[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti Tölli, Markku Juntti,  and Savo Glisic, "{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}'', \textit{IEEE Trans.
+	[R1] Muhammad-Fainan Hanif, Le-Nam Tran, Antti T\"{o}lli, Markku Juntti,  and Savo Glisic, "{Efficient Solutions for Weighted Sum Rate Maximization in Multicellular Networks With Channel Uncertainties}'', \textit{IEEE Trans.
 Signal Process}., vol 61, no.
@@
 
-		\item Using the above discussion, we can say that when the system size is huge, it would be favorable to consider the distributed algorithm over the centralized approach due to the huge signaling overhead involved in exchanging the channels.
+	\item However, for a system involving more coordinating \acp{BS}, users and antenna elements, it would be preferable to use the distributed algorithms for designing the precoders independently across the coordinating \acp{BS}.
+It can be justified by using Figure.
+\ref{fig-review-2-a}, which compares the total number of backlogged packets present in the system after each \ac{SCA} update.
+Note that for the sake of clarity, we have plotted only the number of backlogged packets at each \ac{SCA} points.
 
-		\item From the above discussions, we can see that the \ac{ADMM} and primal schemes require significant overhead compared to the centralized algorithms for a small system.
-However, for a system involving more coordinating \acp{BS}, users and antenna elements, it would be beneficial to use the proposed distributed algorithms with \eqn{J_{\max} > 1} to have a strictly monotonic decrease in the objective.
-If we set \eqn{J_{\max} = 1}, the convergence of the proposed algorithms is not guaranteed as shown in Figure \ref{fig-review-2-a}.
-The system model considered is the same as the one used for Figure \ref{fig-review-1}\subref{fig-review-1a}.
+	Let us consider the system in Figure \ref{fig-review-2-a} for the overhead analysis.
+It requires \eqn{N=4 \times N_B=2 \times K=12 \times N_T=4 \times N_R=1 = 384} complex channel components to be exchanged between \acp{BS} to the controller for the centralized approach to design the precoders.
+Additionally, it also requires to transmit the precoders back to the \acp{BS} upon convergence of the algorithm, which requires \eqn{N = 4 \times K=12\times N_T = 4 \times = 192} complex precoder components.
+Now, assuming \eqn{10} bits are used to quantize each real entity, it requires \eqn{11520} bits to be exchanged overall to obtain the performance shown in Figure \ref{fig-review-2-a}.
 	\begin{figure}[h!]
 		\centering
-			\includegraphics[width=0.8\columnwidth]{reviewer_2_Q1C.eps}
-			\caption{Convergence of the centralized and distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace} using \me{\ell_1} norm}
+		\includegraphics[width=0.8\columnwidth]{reviewer_2_Q1C-A.eps}
+		\caption{Convergence of the centralized and distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,2,12,4,1 \rbrace} using \me{\ell_1} norm with the backlogged packets as \eqn{Q_k = [10,9,6,11,7,9,9,10,7,8,6]} bits}
 		\label{fig-review-2-a}
 	\end{figure}
-		Note that Figure \ref{fig-review-2-a} plots the queue deviation at the \ac{SCA} update points only. The number of backlogged packets in each \ac{ADMM} iteration is not shown for clarity reason.
+	On contrary, for the distributed \ac{ADMM} case, real valued coupling interference variables are required to be exchanged among the coordinating \acp{BS} in the network.
+For the system scenario used in Figure \ref{fig-review-2-a}, the scalar interference values that needs to be exchanged across the coupling \acp{BS} is \eqn{N=4 \times K = 12 \times N_B = 2 = 96} real values.
+Assuming \eqn{10} bits are required to quantize the scalar interference values, on the whole, in each exchange it requires \eqn{960} bits among the coordinating \acp{BS}.
+However, note that in practice we do not need \eqn{10} bits to quantize the scalar interference values, since they are bounded by the total transmit power, unlike the channel coefficients that has a large dynamic range due to \ac{PL}.
 
+	Now, assuming \eqn{J_{\max} = 1}, we require \eqn{1920} bits, \textit{i.e.}, roughly \eqn{\ith{\tfrac{1}{6}}} of the overhead involved in the centralized approach to reach the backlogged packets of \eqn{42} bits.
+Note that the loss in the performance is only \eqn{2} bits over the centralized approach, whereas the gain in reducing the overhead is \eqn{9600} bits over the centralized scheme.
+Similarly, for \eqn{J_{\max} = 5} case, it requires \eqn{15} iterations to achieve \eqn{42} bits of backlogged packets, and therefore the overhead is roughly around \eqn{7200} bits (it includes 5 inner \ac{ADMM} iterations as well) which is roughly \eqn{1.6} times less than the centralized scheme.
+Therefore, as the system size increases, the performance improved from the centralized scheme by exchanging \ac{CSI} information becomes marginal compared to the reduction in the backlogged packets.
+
+	However, it is worth noting that \ac{ADMM} with \eqn{J_{\max} = 1} is not monotonic, and therefore it is difficult to prove the convergence theoretically, despite being the preferable approach for practical implementation.
 	\end{enumerate}
 
-	The above discussion is included in a condensed form in the first and the last paragraph of Section IV-C.
+	\item Now, based on condition (ii), the selection between the centralized and the distributed approaches are argued as follows.
 
-	In reality, since the channel is time-correlated, it is enough to update the precoders once per radio frame.
+	\begin{enumerate}
+
+	\item If the channel is semi-static, \textit{i.e.}, the \acp{CSI} exchanged by the coordinating \acp{BS} to the centralized controller are valid for multiple transmission frames, then it would be beneficial to choose centralized schemes.
+It follows from the fact that the controller can update the beamformers based on the instantaneous backlogged packets, and the \acp{CSI} are available from the earlier feedback.
+Note that the \acp{CSI} are still valid due to the static nature of the channel seen between any two entities in the network.
+
+	\item However, in reality, since the channel is time-correlated, it is enough to update the precoders once per radio frame.
 Thus, it is not necessary for the distributed algorithm to converge until the end.
@@
 	Figure \ref{fig-review-2} compares the performance of the distributed \ac{KKT} approach, \textit{i.e.}, Algorithm 3 for different values of \eqn{I_{\max}}.
-The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.\footnote{Please refer to [27] for further details.} We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the required information for \eqn{J_{\max} = 3,5,10}.
-The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{J_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{J_{\max}}{N_S})} is considered as a penalty involved due to the precoder exchange as discussed in [R2] and [R3].
+The signaling requirements are outlined in Algorithm 3 and the overhead involved in the signaling is penalized in the achievable rate of the users.\footnote{Please refer to [27] for further details.} We considered that the channel is coherent over \eqn{N_S = 100} symbols and the precoder update is performed by exchanging the required information for \eqn{I_{\max} = 3,5,10}.
+The overhead is considered as \eqn{\tilde{t}_{l,k,n} = (1 - \frac{I_{\max}}{N_S}) \times t_{l,k,n}}, where \eqn{\tilde{t}_{l,k,n}} is the rate seen by the user and the factor \eqn{(1 - \frac{I_{\max}}{N_S})} is considered as a penalty involved due to the precoded pilot exchange.
+More details can be found in [R2] and [R3].
 The average number of backlogged packets after each transmission slot is evaluated as
@@
 	\end{equation}
+	and the \ac{PL} is distributed uniformly between \eqn{[0,-3]} dB.
 
-	Unlike Algorithm 3, the centralized scheme presented in Figure \ref{fig-review-2} has no penalty term and it is used as a benchmark.
-In order to improve the performance of the distributed scheme, the operating point involved in the \ac{SCA} algorithm is considered from the earlier frame instead of begin generated randomly.
+	Unlike Algorithm 3, the centralized and the isolated precoder designs presented in Figure \ref{fig-review-2} does not include any penalty term and it is used as a benchmark.
+In order to improve the performance of the distributed scheme, the operating point involved in the \ac{SCA} algorithm is considered from the earlier frame instead of being generated randomly.
+Note that the performance of the distributed scheme is significantly improved by performing the internal iterations as discussed in [25] as strategy B.
+By doing so, we can achieve the performance close enough to the centralized approach (which does not included any penalty term in the rate).
+Therefore, for the time-correlated scenarios, it would be beneficial to do distributed approaches as discussed above to avail the channel correlation rather than feeding back the \acp{CSI} to the centralized controller.
 
-	\begin{comment}
 	Since we use \ac{KKT} approach, we can either use all users in the system for the precoder design or we can utilize single-cell MU-MIMO user selection presented in the literature to limit the number of users for which the precoders are designed, which leads to the faster convergence.
@@
 Once the iterations are performed to update the precoders, it is then exchanged across the coordinating \acp{BS} to perform the same procedure as mentioned earlier.
-	\end{comment}
 
@@
 
+	\end{enumerate}
+
+	\end{itemize}
+
+\end{comment}
+
+\pagebreak
 \cmnt{3} \review{If the authors can't prove the convergence of the ADMM algorithm (or the decomposition approach via KKT conditions) in Section IV.B, then at least, you should discuss the property of the fixed point of the algorithm.
@@
 In our paper, the number of \ac{ADMM} iterations is denoted by \eqn{J_{\max}} in Algorithm 2.
-In order to obtain the centralized solution, we need to perform the distributed approaches until convergence or for very large value of \eqn{J_{\max}}.
+In order to obtain the centralized solution, we need to perform the distributed approaches until convergence or for some finite number, say, \eqn{J_{\max}}.
 In practice, it may not be possible to perform the distributed methods until convergence.
-In such cases, the overall convergence of the objective sequence and beamformer iterates of Algorithm 2 is not guaranteed.
-The reason is that the strict monotonicity of the objective is not ensured in each \ac{SCA} update.
+In such cases, the overall convergence of the objective sequence and beamformer iterates of Algorithm 2 cannot be guaranteed.
+It follows from the fact that in each distributed step, the global objective need not decrease strictly to ensure the convergence of the beamformer iterates.
 
-However, if we perform the distributed algorithms for significantly enough to ensure strict monotonicity of the objective, then the overall of convergence of Algorithm 2 is guaranteed by following the arguments in [27].
+However, if we perform the distributed algorithms for significant number of iterations to ensure strict monotonicity of the objective, then the overall of convergence of Algorithm 2 is guaranteed by following the arguments in [27].
 Note that in addition, uniqueness of the limit point is also necessary for the sequence convergence.
-It can be assured by regularizing the original convex objective with a quadratic term as in (46b) in each \ac{SCA} step to guarantee strong convexity, and thereby ensuring a unique minimizer and limit point.
+It is achieved by regularizing the original convex objective with a quadratic term as in (46b) in each \ac{SCA} step to guarantee strong convexity, and thereby ensuring unique minimizer and limit point.
 
-Additionally, to reduce the signaling overhead involved with the information exchange due to multiple loops, we can also combine the \ac{MMSE} receiver update in (23b) after each \ac{SCA} step for the transmit precoders.
-If in addition \eqn{J_{\max}} is sufficiently large, then the strict monotonicity of the objective sequence is still ensured by the combined update.
+Upon satisfying the strict monotonicity of the objective sequence in each \ac{SCA} update with some \eqn{J_{\max}}, we can also combine the \ac{MMSE} receiver update in (23b) after each \ac{SCA} step for the transmit precoders.
+It reduces the signaling overhead involved with the information exchange due to multiple loops that are required for \ac{AO} and \ac{SCA} as mentioned for the centralized scheme.
+Even though the receivers are updated together with the transmit precoders in each \ac{SCA} step, strict monotonicity of the objective sequence is still ensured.
 It follows from the fact that the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained after each \ac{SCA} update.
-The newly found solution is also feasible and the objective improves monotonically in strict sense.
+Moreover, the newly found solution is also feasible and the objective improves monotonically in strict sense.
 Therefore, if the above conditions are satisfied, then the convergence of the sequence of iterates is guaranteed.
@@
 \item In general, the fixed point of the subproblem (20) is not unique.
-It is due to the fact that the original objective is convex, and therefore it can have multiple solutions in the feasible convex set.
-Therefore, the \ac{ADMM} algorithm can have a set of fixed points in the feasible set.
-However, if we regularize the objective with a strongly convex quadratic term as discussed in Appendix A-B, then the distributed approach finds a fixed point of the original convex subproblem.
+It is due to the fact that the original objective is not strongly convex, thereby having multiple solutions in the feasible convex set.
+Due to the existence of multiple solutions, the \ac{ADMM} algorithm can have a set of fixed points in the feasible set.
+However, if we regularize the objective with a strongly convex quadratic term as discussed in Appendix A-B, then the distributed approaches find a unique fixed point of the original convex subproblem.
 
-\item By using previous argument, any fixed point of the algorithm is a solution for the problem (20), since the original convex objective can have multiple solutions.
-The particular choice of the fixed point of the \ac{ADMM} approach depends on the operating point used in the regularization term in the objective.
+\item By using previous argument, any fixed point of the algorithm is a solution for the problem (20), since all fixed points are in fact the solution for the convex subproblem in (20).
+The particular choice of the fixed point of the \ac{ADMM} approach depends on the initial operating point used in the regularization term in the objective.
 
@@
 
-However, to answer the reviewer questions in relation to the overall convergence of the distributed method presented in Algorithm 2, we consider the following conditions are satisfied in each \ac{SCA} update step.
+However, if the reviewer comments are for the Algorithm 2, then the following response will answer the questions.
+For that, we consider the following conditions are satisfied in each \ac{SCA} update step.
 \begin{itemize}

### 2015-08-06 Report/convergence_centralized.tex
finalized for final submission

@@
 	\item[(b)] The feasible set should be a compact set
-	\item[(c)] The sequence of the objective values should be strictly decreasing in each iteration
+	\item[(c)] The sequence of the objective values should be \review{strictly} decreasing in each iteration
 	\item[(d)] Uniqueness of the minimizer, \textit{i.e.}, the transmit and the receive beamformers should be unique in each iteration.
@@
 \review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique.
-Using this and the fact that the sequence of objectives is nonincreasing ensure that the iterates of the \ac{SCA} update converges to a limit point in the \eqn{\ith{i}} \ac{AO} step.
-However, note that the limit point need not be a stationary point of \eqref{con}, since the receive equalizers \eqn{\my} have been fixed.}
+Now, by using the fact that the objective sequence is nonincreasing and the uniqueness of the minimizer in each convex subproblem \eqref{con-m}, we can ensure that the sequence of iterates generated by the iterative \ac{SCA} approach converges to a unique limit point in each \ac{AO} step \eqn{{i}}}.
+	%However, note that the limit point need not be a stationary point of \eqref{con}, since the receive equalizers \eqn{\my} have been fixed.}
 
@@
 Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
-However, if \eqn{\hat{f}} is used instead of \eqn{f} in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to multiple solutions.
+However, if \eqn{\hat{f}} is used instead of \eqn{f} as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple minimizers in each convex subproblem.
 
 Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update.
-It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.
-}
-
+It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.}
 \begin{comment}
-
 \begin{equation} \label{strict_monotonicity}
@@
 
-\end{comment}
-
 %Due to the convexity in the original objective \eqn{\hat{f}(\mbf{z})}, it can have multiple limit points for the \ac{SCA} update, and therefore it follows \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k}.
@@
 Using (a),(b),(c) along with the above discussion, we can ensure strict monotonicity and the convergence of the objective.}
-
+\end{comment}
 \subsection{Convergence of the Beamformer Iterates} \label{c-b}
@@
 \subsection{Stationary Points of the Nonconvex Problem}
-\review{So far, we have shown that the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point as \eqn{i \rightarrow \infty}.
-To show that \eqn{\ma^{\ast}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} conditions of the nonconvex problem \eqref{con}, \textit{i.e.},
+\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\ast}} as \eqn{i \rightarrow \infty}.
+Now, to show that \eqn{\ma^{\ast}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} gradient condition of \eqref{con}, \textit{i.e.},
 \begin{equation} \label{kkt_expr}

### 2015-08-06 Report/convergence_distributed.tex
finalized for final submission

@@
 (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible.
-It is evident from the equality constraint \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, which is invertible.
+It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible.
 Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity.
@@
 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as presented in \cite{boyd2011distributed}.
-If both the primal and \ac{ADMM} approaches are allowed to converge in each \ac{SCA} step to the centralized solution, then the limit point of the sequence generated by the distributed methods is a stationary point of \eqref{con}, using similar arguments as in Appendix \ref{sec-3.5}.
-}
+Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, then the limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}
 

### 2015-08-06 Report/decomposition_solutions.tex
updated
finalized for final submission

--- 2015-07-20 Report/decomposition_solutions.tex
@@
-The distributed precoder designs for the proposed \ac{JSFRA} scheme are discussed in this section.
-The convex formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}.
-In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are based on the \acl{PD} and the \ac{ADMM} are considered herein.
+In this section, we discuss the distributed designs for the formulations proposed in Sections \ref{sec-3.2.1} and \ref{sec-3.3} for problem \eqref{eqn-6}.
+Note that the convex subproblems in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to design the precoders for all users in the system.
+\review{However, the amount of \ac{CSI} that needs to be exchanged between the \acp{BS} and the controller grows significantly as the network size increases (e.g., the number of \acp{BS} and users, and the number of associated antennas).
+The overhead involved in the \ac{CSI} exchanges can be avoided, if we design the respective precoders independently at each \ac{BS} with the minimal information exchange, which is determined by the distributed schemes discussed herein.}
 
-Let us consider the convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint.
+Let us consider the convex subproblem with fixed receivers \me{\mvec{w}{l,k,n}} as presented in \eqref{eqn-9} based on the \ac{SINR} relaxation for the nonconvex constraint \eqref{eqn-6.2}.
 The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well.
@@
 \end{IEEEeqnarray}
-where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviations corresponding to users \me{k \in \mc{U}_b}.
+where \me{\tilde{\mbf{v}}_b} denotes the stacked vector of weighted queue deviations corresponding to all users in \ac{BS} \eqn{b} as \me{\forall k \in \mc{U}_b}.
 
@@
 \end{equation}
-Since the decentralization solution is an iterative procedure, we represent the \me{\ith{i}} iteration index as \me{x^{(i)}}.
+Since the decentralization solution is an iterative procedure, we represent the \me{\ith{j}} iteration index as \me{x^{(j)}}.
 Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to \ac{BS} \me{b_k} in \ac{BS} \me{b} as
@@
 It is obtained through the user specific downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} using the equivalent downlink channels as in \cite{komulainen2013effective}.
+
 %The subproblems with the \ac{BS} specific interference variables are controlled by a master subproblem, which determines the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in accordance with the global objective.

### 2015-08-06 Report/kkt_mse_approach.tex
finalized for final submission

@@
 In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements.
-We consider an idealized \ac{TDD} system due to the knowledge of complete channel information at the transmitter.
+We consider an idealized \ac{TDD} system due to the knowledge of complete \ac{CSI} at the transmitter.
 Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized}.
@@
 \item when the exponent \me{q} is even, or
-\item when the number of backlogged packets of each user is large enough, \textit{i.e}, \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator and queues in the first place as well.
+\item when the number of backlogged packets waiting to be transmitted for each user is large enough, \textit{i.e}, \me{\textstyle Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}} to ignore the absolute operator in the objective and queues in the first place as well.
 \end{itemize}
@@
 At iteration \eqn{i}, the dual variables \me{\alpha^{(i)}} is a point in the line segment between \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} determined by using a diminishing or a fixed step size \me{\rho^{(i)} \in (0,1)}.
-The choice of \eqn{\rho^{(i)}} affects the convergence behavior and also controls the oscillations in the users' rate when \me{\sigma^{(i)}} is negative (before projection) due to over-allocation.
-In all numerical simulations, the step size \me{\rho^{(i)}} is fixed to \me{0.1} irrespectively.
-However, the choice of \me{\rho^{(i)}} depends on the system model and it affects the rate of convergence of the iterative algorithm.
+The choice of \eqn{\rho^{(i)}}, which depends on the system, affects the convergence behavior and also controls the oscillations in the users' rate when \me{\sigma^{(i)}} is negative (before projection) due to over-allocation.
+However, in all numerical simulations, the step size \me{\rho^{(i)}} is fixed to \me{0.1} irrespectively.
 
@@
 
-To avoid the back-haul exchanges between the \acp{BS}, as an alternative approach, users can perform all the required processing and \acp{BS} will update the precoders based on the feedback from all the users.
+To avoid the backhaul exchanges between the \acp{BS}, as an alternative approach, users can perform all the required processing and \acp{BS} will update the precoders based on the feedback from all the users.
 Upon receiving the transmit precoders from the \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}}.
@@
 Upon receiving the precoded uplink pilots, each \ac{BS} evaluates the equivalent channels \me{\mvec{H}{b,k,n}^{\mathrm{T}} \tilde{\mbf{w}}_{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \bar{\mbf{w}}_{l,k,n}^{(i)}} to update the transmit precoders using \eqref{kkt-mse-4.3}.
-Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling as in \cite{komulainen2013effective}.
+The algorithmic description of the above scheme is presented in Algorithm \ref{algo-4}.
 
-\review{To conclude this section, we provide some remarks regarding the choices of centralized and distributed algorithms under some scenarios.
+%It is outlined in Algorithm \ref{algo-4} outlines a practical way of updating the transmit and the receive beamformers by using \ac{OTA} signaling as in \cite{komulainen2013effective}.
+
+\review{We conclude this section by providing some remarks on selecting an algorithm within centralized and distributed approaches for certain scenarios.
+Among the centralized algorithms proposed in Section \ref{sec-3}, both the \ac{SINR} relaxation and the \ac{MSE} reformulation schemes are equally attractive when \eqn{N_R > 1}.
+However, when \eqn{N_R = 1} the \ac{SINR} relaxation is preferable, since the receiver update is not needed, unlike the \ac{MSE} reformulation which requires the scalar \ac{MMSE} receiver update.
+Similarly, for the distributed approaches with \eqn{N_R = 1}, the \ac{SINR} relaxation is preferred to the \ac{MSE} reformulation schemes, since the variables to be exchanged among \acp{BS} are only the scalar interference values.
+However, when \eqn{N_R > 1} the \ac{KKT} scheme in Section \ref{sec-4.3} is favorable, since the overhead required to achieve a certain throughput improvement is less, as compared to the primal decomposition or \ac{ADMM}.}
+
+%since we do not need to update the receivers,
+%the choice of selecting algorithms within each centralized and distributed approaches.
+\review{To conclude, we provide some remarks on the choice of selection between centralized and distributed approaches under some scenarios.
+Among the centralized \ac{JSFRA} formulations, we can choose either \ac{SINR} relaxation in Section \ref{sec-3.2.1} or \ac{MSE} equivalence in Section \ref{sec-3.3} equally for all scenarios with \eqn{N_R > 1}.
+However, when \eqn{N_R = 1}, the \ac{SINR} relaxation is more efficient, as there is no need for receiver updates, thereby leading to low complex designs.
+Similarly, for the distributed schemes with \eqn{N_R = 1}, the \ac{JSFRA} method via \ac{SINR} relaxation is preferred over other schemes due to the limited signaling requirements among the \acp{BS} in \eqn{\mc{B}}, involving only the exchange of the scalar interference values.
+However, when \eqn{N_R > 1}, the \ac{KKT} scheme presented in Section \ref{sec-4.3} has less signaling overhead for a given throughput improvement.
+The choice of either centralized or distributed schemes depend on the system size and the overhead required in exchanging either complete \acp{CSI} to a common controller or only the coupling variables among the \acp{BS} in \eqn{\mc{B}} respectively.
+The centralized schemes are preferable when the channel is semi-static and the system is small, since the available \acp{CSI} are valid for multiple frames.}
+
+%	We can choose the \ac{JSFRA} formulation via either \ac{SINR} relaxation (Sect.
+\ref{sec-3.2.1}) or \ac{MSE} equivalence (Sect.
+\ref{sec-3.3}) equally when \eqn{N_R > 1}.
+However, for \eqn{N_R = 1}, the \ac{JSFRA} formulation in Section \ref{sec-3.2.1} is more efficient, as there is no receiver update, and therefore has less complexity.
+Similarly, when \eqn{N_R = 1}, the distributed approaches based on the \ac{JSFRA} method via \ac{SINR} relaxation are preferred over other schemes due to the limited signaling between the coordinating \acp{BS} involving the exchange of the scalar interference values.
+However, when \eqn{N_R > 1}, the \ac{KKT} scheme presented in Section \ref{sec-4.3} has less signaling requirements for a given throughput improvement.
+The choice of the centralized schemes over the distributed methods depend on the trade-off between performance and the overhead involved in exchanging either the \ac{CSI} of all users or the coupling interference values.}
+
+%\review{To conclude this section, we provide some remarks on the selection between centralized and distributed algorithms under some scenarios.
 We can choose the \ac{JSFRA} formulation via either \ac{SINR} relaxation (Sect.
@@
 Similarly, when \eqn{N_R = 1}, the distributed approaches based on the \ac{JSFRA} method via \ac{SINR} relaxation are preferred over other schemes due to the limited signaling between the coordinating \acp{BS} involving the exchange of the scalar interference values.
-However, when \eqn{N_R > 1}, the \ac{KKT} scheme presented in Section \ref{sec-4.3} has less signaling requirements for a given throughput improvement.}
+However, when \eqn{N_R > 1}, the \ac{KKT} scheme presented in Section \ref{sec-4.3} has less signaling requirements for a given throughput improvement.
+The choice of the centralized schemes over the distributed methods depend on the trade-off between performance and the overhead involved in exchanging either the \ac{CSI} of all users or the coupling interference values.
+}
 

### 2015-08-06 Report/primal_approach.tex
updated with Nam changes (half cooked)
updated
finalized for final submission

--- 2015-06-29 Report/primal_approach.tex
@@
 The slave subproblem is solved in each \ac{BS} for the optimal transmit precoders only for the associated users by assuming fixed interference terms \me{\mbfa{\zeta}_{b_k}^{(i)}} in each \me{\ith{i}} iteration.
-Upon finding the optimal associated transmit precoders by each slave subproblems, the master problem is used to update the \ac{BS} specific interference terms \me{\mbfa{\zeta}_{b_k}^{(i+1)}} for the next iteration by using dual variables corresponding to the interference constraint \eqref{eqn-decent-3} as discussed in \cite{pennanen2011decentralized}.
-In this manner, the interference variables are updated until the global consensus is obtained.
-It is similar to the minimum power design presented in \cite{pennanen2011decentralized}.
+Upon finding the associated transmit precoders by each slave subproblems, the master problem is used to update the \ac{BS} specific interference terms \me{\mbfa{\zeta}_{b_k}^{(i+1)}} for the next iteration by using dual variables corresponding to the interference constraint \eqref{eqn-decent-3} as discussed in \cite{pennanen2011decentralized}.
+In this manner, the interference variables are updated until the global consensus is reached.
 The master problem treats \me{\mbfa{\zeta}_{b}} as a variable and the slave subproblems assumes it to be a constant in each iteration.
-\review{Since the interference levels are fixed in each subproblem, the feasibility of the subproblems depend on the step size used to update the interference variables by the master problem.}
-
 \begin{comment}
@@
 %Much of the details are provided in the Appendix \ref{a-2}.
-
 \subsubsection*{Convergence}

### 2015-08-06 Report/simulation_distributed.tex
finalized for final submission

@@
 However, in our simulations, we observe that \eqn{J_{\max} = 20} is sufficient for the \ac{ADMM} to converge.
+
 %In Fig.

### 2015-08-06 Report/sub_channel_wsrm.tex
updated before Algorithm 2 Changes
finalized for final submission

--- 2015-07-20 Report/sub_channel_wsrm.tex
@@
 As an alternative sub-optimal solution, we present a \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
-The power sharing can either be equal or based on some predetermined limits on each sub-channel as in partial frequency reuse as
+For each sub-channel, the power sharing can either be equal or based on some predetermined limits as in partial frequency reuse satisfying
 \begin{equation}
@@
 Even though \me{N} sub-channels are present at any given scheduling instant, precoders are computed for each sub-channel sequentially with \me{P_{\max,i}} and the residual number of backlogged packets.
-Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} while determining the precoders for the \eqn{\ith{i}} sub-channel.
-Since the precoder design is sequential, \textit{i.e}, the precoders are designed for sub-channels \me{[0,i-1]} before the \me{\ith{i}} sub-channel, the number of backlogged packets for the initial sub-channel is initialized as \me{Q_{k,1} = Q_k}.
-The queues associated with the consecutive sub-channels are given by
+Let \me{Q_{k,i}} be the number of backlogged packets associated with user \me{k} while designing the precoders for the \eqn{\ith{i}} sub-channel.
+Since the precoder design is sequential, \textit{i.e}, the precoders are designed for sub-channels \me{[0,i-1]} before the \me{\ith{i}} sub-channel, the number of queued packets for the first chosen sub-channel is given by \me{Q_{k,1} = Q_k}.
+The queues associated with the consecutive sub-channels are updated as
 \begin{equation}	\label{eqn-weight}
@@
 \review{For simplicity we use random sub-channel ordering in our paper, \textit{i.e.}, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
-We can also use greedy ordering by considering the norm of the channel between a user and the corresponding serving \ac{BS}, but this comes at the cost of increased complexity.
-However, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the available multi-user diversity.}
+As an alternative approach, we can also use greedy ordering, which selects the sub-channels by sorting the channel norm between all users and the respective serving \acp{BS} in the system, but this comes at the cost of increased complexity.
+It is worth noting that, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the available multi-user diversity present in the system.}
+
+%	the sub-channel selection can also be performed deterministically by using greedy ordering, in which the norm of the channel between the users and the corresponding serving \acp{BS} in the system.
+However, it comes with the cost of increased complexity.
+%Note that the interference cannot be considered in this selection process, since the precoders are designed only after the sub-channel selection.
+%It is worth noting that, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the available multi-user diversity present in the system.}
 

### 2015-08-07 Response/Response 2/response-2.tex
about to submit version

@@
 \item In general, the fixed point of the subproblem (20) is not unique.
-It is due to the fact that the original objective is not strongly convex, thereby having multiple solutions in the feasible convex set.
-Due to the existence of multiple solutions, the \ac{ADMM} algorithm can have a set of fixed points in the feasible set.
+It is due to the fact that the original objective is not strongly convex, thereby having possibly multiple solutions in the feasible convex set.
+It is due to the existence of multiple solutions, the \ac{ADMM} algorithm can have a set of fixed points in the feasible set.
 However, if we regularize the objective with a strongly convex quadratic term as discussed in Appendix A-B, then the distributed approaches find a unique fixed point of the original convex subproblem.

### 2015-08-07 Report/convergence_centralized.tex
about to submit version

@@
 
-\review{To ensure the uniqueness of the transmit precoders and the receive beamformers on all iterations, the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} can be regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
+\review{To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 \end{IEEEeqnarray}
-where \eqn{\mbf{z}} is vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem.
-The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity of \eqn{f} with \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} as in \cite{scutari-1}.
-Therefore, by using the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step \cite{yang_yang,scutari-1}.
+where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem.
+The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, as shown in \cite{scutari-1}.
+Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}.
 The quadratic term in \eqref{mod_obj} includes the earlier solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, obtained by solving \eqref{eqn-9} or \eqref{eqn-mse-2} in the \eqn{\ith{(k-1)}} \ac{SCA} step.}
 
+%in each step and let \eqn{c > 0} be the constant of strong convexity of \eqn{f} with \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} as in \cite{scutari-1}.
 %The uniqueness of the transmit precoders and the receive beamformers for the \ac{MSE} reformulation in \eqref{eqn-mse-2} can be guaranteed in each iteration by the \ac{MSE} constraint in \eqref{eqn-mse-1.3}.
@@
 \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
-f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{c}{2} \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
+f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& c \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
 \end{IEEEeqnarray}
@@
 \end{itemize}
-\review{Note that the above conditions are satisfied by the proposed algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity is guaranteed from Section \ref{mcity} by using the modified objective \eqref{mod_obj}}.
+\review{Note that the strict monotonicity of the objective is guaranteed using the strong convexity of \eqn{f} in Section \ref{mcity}.
+Therefore, all the above requirements are satisfied by algorithm \eqref{g-algo}}.
 Using \cite{zangwill1969nonlinear} and \cite[Th.
@@
 \begin{comment}
+	Note that the above conditions are satisfied by the algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity of the objective sequence is guaranteed in Section \ref{mcity} using strong convexity of \eqn{f}}.
 and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e.}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
@@
 \end{equation}
-for some multipliers \eqn{\mu_i \geq 0} and lies in the feasible set \eqn{\ma^{\ast} \in \mc{F}}.
+for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\ma^{\ast} \in \mc{F}}.
 
@@
 The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}.
-Therefore, the gradients evaluated at \eqn{\ma^{\ast}} satisfy \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}.
+Therefore, the gradient evaluated at \eqn{\ma^{\ast}} satisfy \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}.
 (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given as

### 2015-08-07 Report/convergence_distributed.tex
about to submit version

@@
-The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
+\review{The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
 Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence.
@@
 
-\review{To show the convergence of the \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
+To show the convergence of the \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 Now, by using \cite[Prop.
-4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as presented in \cite{boyd2011distributed}.
+4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}.
 Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, then the limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}
@@
 Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed.
-Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the iterates are not unique in each update.
-Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot find a fixed point to ensure the convergence of the beamformer iterates.}
+Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is not guaranteed in each update.
+Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the beamformer iterates.}
 

### 2015-08-07 Report/decomposition_solutions.tex
about to submit version

@@
 Similarly, to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} need to be known.
-It is obtained through the user specific downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} using the equivalent downlink channels as in \cite{komulainen2013effective}.
+It is obtained through the user specific downlink pilots precoded with the newly obtained transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} using the equivalent downlink channels as discussed in \cite{komulainen2013effective}.
 

### 2015-08-07 Report/dual_approach.tex
about to submit version

@@
 The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
-However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large to ensure strict monotonicity of the objective, then the convergence can be guaranteed (see Appendices \ref{sec-3.5} and \ref{sec-dist-conv}).
+However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, then the convergence can be guaranteed (see Appendices \ref{sec-3.5} and \ref{sec-dist-conv}).
 Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured.

### 2015-08-07 Report/introduction.tex
about to submit version

@@
 The existing and the proposed centralized designs are presented in Section \ref{sec-3}.
-The distributed solutions are provided in Section \ref{sec-4} followed by the simulation results in Section \ref{sec-5}.
-Conclusions are drawn in Section \ref{sec-6}.
+The distributed solutions for the proposed problem are provided in Section \ref{sec-4} followed by the simulation results in Section \ref{sec-5}.
+Finally, conclusions are drawn in Section \ref{sec-6}.

### 2015-08-07 Report/sub_channel_wsrm.tex
about to submit version

@@
 \review{For simplicity we use random sub-channel ordering in our paper, \textit{i.e.}, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
-As an alternative approach, we can also use greedy ordering, which selects the sub-channels by sorting the channel norm between all users and the respective serving \acp{BS} in the system, but this comes at the cost of increased complexity.
-It is worth noting that, as the number of users in the system increases, the \ac{SRA} scheme will be insensitive to the sub-channel ordering due to the available multi-user diversity present in the system.}
+Alternatively, we can also use greedy ordering to select the sub-channels by sorting the norm of the channel seen between the users and the respective serving \acp{BS}.
+However, it comes at the cost of increased complexity.
+Nevertheless, the \ac{SRA} scheme will be insensitive to the sub-channel ordering as the number of users in the system increases, due to the available multi-user diversity in the system.}
 

### 2015-08-07 Report/system_model.tex
about to submit version

@@
 where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over the \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}.\footnote{The upper bound can be achieved by using Gaussian signaling.} The units of \me{t_k} and \me{Q_k} are in bits defined per channel use.
+The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}.\footnote{The upper bound can be achieved by using Gaussian signaling.} Note that \me{t_k} and \me{Q_k} are represented by the same units, \textit{i.e.}, in bits defined per channel use.

### 2015-08-11 Report/manuscript.tex
Before Antti Corrections
about to submit version
submitted version

--- 2015-06-23 Report/ieee_journal.tex
@@
-\documentclass[10pt,journal,final,letterpaper]{./../Styles/IEEEtran}
+\documentclass[10pt,journal,final,letterpaper,onecolumn]{./../Styles/IEEEtran}
 
@@
 \usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
-\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases}
+\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases,algorithmic}
 
@@
 \DeclareGraphicsExtensions{.eps}
+
+\setlength{\floatsep}{0.5\baselineskip}
+\setlength{\textfloatsep}{0.5\baselineskip}
+
+\captionsetup{width=0.48\textwidth}
 
@@
 \subsection{Primal Decomposition} \label{sec-4.1}
-\input{primal_approach}
+\input{primal_approach} %\vspace{-0.25em}
 %\input{primal_algorithm}

### 2015-08-22 Presentation/icassp_presentation.tex
updated presentation and draft

\documentclass[10pt]{beamer} 
\usetheme{cwc}

\usepackage{amsmath,amssymb}
\usepackage{graphicx,acronym,setspace}
\usepackage[ruled]{algorithm2e}
\usepackage{subeqnarray,multirow,cite,array,color}

\acrodef{MSE}{mean squared error}
\acrodef{BC}{broadcast channel}
\acrodef{MC}{multi-cell}
\acrodef{BS}{base station}
\acrodef{MIMO}{multiple-input multiple-output}
\acrodef{SISO}{single-input single-output}
\acrodef{MU}{multi-user}
\acrodef{MU-MIMO}{\acl{MU} \acl{MIMO}}
\acrodef{OFDM}{orthogonal frequency division multiplexing}
\acrodef{WSRM}{weighted sum rate maximization}
\acrodef{QoS}{quality of service}
\acrodef{SCA}{successive convex approximation}
\acrodef{SNR}{signal-to-noise ratio}
\acrodef{MMSE}{minimum \acl{MSE}}
\acrodef{SIR}{signal-to-interference ratio}
\acrodef{SINR}{signal-to-interference-plus-noise ratio}
\acrodef{Q-WSRM}{queue \acl{WSRM}}
\acrodef{QM}{queue minimizing}
\acrodef{SRA}{spatial resource allocation}
\acrodef{JSFRA}{joint space-frequency resource allocation}
\acrodef{WMMSE}{weighted \acl{MMSE}}
\acrodef{KKT}{Karush-Kuhn-Tucker}
\acrodef{GP}{geometric programming}
\acrodef{SOC}{second-order cone}
\acrodef{BCDM}{block coordinate descent method}

\include{..\Report\shortcuts}
\include{..\Report\acronyms}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\me}[1]{\( #1 \)}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\fall}{\; \forall \;}
\newcommand{\set}[1]{\left \lbrace #1 \right \rbrace }
\newcommand{\mvec}[2]{\mathbf{#1}_{#2}}
\newcommand{\ith}[1]{{#1}^{\mathrm{th}}}

\graphicspath{{./../../ICASSP-2014/Figures/}}
\DeclareGraphicsExtensions{.eps}

\title{Queue Aware Precoder Design for Space Frequency Resource Allocation}
\author{{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}

\begin{document}

\setstretch{1.3}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Outline}
    \tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}{Introduction and Motivation}
\begin{itemize}
\item Complex algorithms are adopted to maximize the throughput to satisfy the data requirements of the higher layers
\item Available wireless resources are to be utilized efficiently to minimize the backlogged packets 
\item Spatial and Frequency resources are exploited to empty the packets waiting at the \acsp{BS}
\item In this work, we discuss the precoder design for the \acl{MU} \acs{MIMO}-\acs{OFDM} setup to minimize the number of queued packets 
\end{itemize}
\end{frame}

\section{System Model}

\begin{frame}{Symbols used}
\begin{itemize}
\item \acs{OFDM} system with \me{N} sub-channels and \me{N_B} \acsp{BS}, each equipped with \me{N_T} transmit antennas.
\item Let \me{K} users with \me{N_R} antennas each be present in the system
\item Users belonging to the \acs{BS} \me{b} is denoted by the set \me{\mc{U}_b \in \mc{U}}
\item Let \me{\mathcal{C} = \set{1,2,\dotsc,N}} be the set corresponding to the available sub-channels
\item The set of coordinating \acsp{BS} is represented by the set \me{\mc{B}}
\item Let \me{b_k \in \mathcal{B}} denotes the \ac{BS} serving the user \me{k}
\item Let \me{L} be the total available spatial streams for a user \me{k}, given by \me{\min (N_T,N_R)}
\end{itemize}
\end{frame}

\begin{frame}{System Model}
\begin{itemize}
\item The \me{\ith{l}} spatial signal received over the sub-channel \me{n} of the user \me{k} user is given by
\begin{multline*}\label{eqn-1}
y_{l,k,n} = \mvec{w}{l,k,n}^H \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} \\
 + \quad{} \mvec{w}{l,k,n}^H \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \tilde{n}_{l,k,n},
\end{multline*}
\item where \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}} are the transmit and receive beamformer corresponding to the \me{\ith{l}} spatial stream over \me{\ith{n}} sub-channel for the user \me{k}
\end{itemize}
\end{frame}

\begin{frame}{System Model}
\begin{itemize}
\item \me{\mvec{H}{b_k,k,n} \in \mathbb{C}^{N_R \times N_T}} denotes the channel between the \acs{BS} \me{b_k} and the user \me{k}
\item \me{d_{l,k,n}} and \me{\tilde{n}_{l,k,n}} are the data and the equalized noise corresponding to the \me{\ith{l}} spatial stream of the user \me{k}
\item Now, the \acs{SINR} seen by the \me{\ith{l}} spatial stream over \me{\ith{n}} sub-channel for the user \me{k} is given by
\end{itemize}
\[ \gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{N_0 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^H \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}.\]
\end{frame}

\begin{frame}{Queueing Model}
\begin{itemize}
\item Each user is associated with the backlogged packets of size \me{Q_k} packets.
\item Queued packets \me{Q_k} of each user follows the dynamic equation at the \me{\ith{i}} instant as
\begin{equation}
Q_k(i) = \Big [ Q_k(i-1) - t_k(i-1) \Big ]^+ + \lambda_k(i),
\label{queue_dynamics}
\end{equation}
\item where \me{t_k = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}} corresponds to the total transmitted packets of the user \me{k} in the previous \me{\ith{(i-1)}} instant
\item \me{\lambda_k} represents the arriving fresh packets for the user \me{k} at the \ac{BS} \me{b_k}
\end{itemize}
\end{frame}

\section{Problem Formulation}

\begin{frame}{Problem Formulation}
\begin{itemize}
\item Objective is to transmit the queued packets waiting at the \acsp{BS} to the corresponding users.
\item The available spatial and the frequency resources are to be utilized in an effective manner
\item In order to achieve this, precoders are to be designed with the similar objective
\item Precoders can perform scheduling of users by providing zero powers so as to eliminate from the resource elements
\end{itemize}
\end{frame}

\section{Proposed Solutions}

\subsection{\acs{Q-WSRM} Formulation}

\begin{frame}{Queue-Weighted Sum Rate Maximization (\acs{Q-WSRM})}
\begin{itemize}
\item \acs{Q-WSRM} formulation is the result of minimizing the conditional Lyapunov drift \footnote{Neely, Michael J. "Stochastic network optimization with application to communication and queueing systems." Synthesis Lectures on Communication Networks 3.1 (2010): 1-211.}
\item \acs{Q-WSRM} formulation is also called as back pressure algorithm, since it acts greedily in minimizing the backlogged packets at each instant
\[ \underset{t_{l,k,n}}{\text{minimize}} \quad \sum_{k \in \mc{U}} \left \lbrace Q_k(i)^2 - Q_k(i-1)^2 \right \rbrace, \]
\item where \me{Q_k} follows the dynamic Queue expression in \eqref{queue_dynamics} and \me{t_k = \sum_{n = 1}^N \, \sum_{l=1}^L \, t_{l,k,n}}
\end{itemize}
\end{frame}

\begin{frame}{Queue-Weighted Sum Rate Maximization (\acs{Q-WSRM})}
\begin{itemize}
\item Upon solving the Lyapunov drift expression, we obtain the \acs{Q-WSRM} formulation as
\end{itemize}
\begin{subequations}
\begin{align}
 \underset{t_{l,k,n}}{\text{maximize}} & \qquad \sum_{k \in \mc{U}} \; Q_k \left ( \alert{\sum_{n=1}^N} \, \sum_{l = 1}^L  t_{l,k,n} \right ) \\
& \qquad {\color{blue} \alert{\sum_{n=1}^N} \, \sum_{l = 1}^L  t_{l,k,n}  \leq \alert{Q_k} \; / \; Q_{k,n}}
\end{align}
\end{subequations}
\begin{itemize}
\item Performs better in the cell-edge scenario
\item Since each sub-channels are interference free, the queues are updated after designing the precoders at each sub-channels as
\end{itemize}
\begin{equation*}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\end{equation*}
\end{frame}

\subsection{\acs{JSFRA} Formulation}

\begin{frame}{\acs{JSFRA} Formulation}
\begin{itemize}
\item Precoders are designed by a centralized controller, which is then used for the transmission by the \acsp{BS} in \me{\mc{B}}
\item The objective used to design the precoders is 
\[ {\color{blue} v_k = \left | Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right |^q } \]
\item To generalize the objective, we use \me{\tilde{v}_k \triangleq a_k \, v_k}, where \me{a_k} is arbitrary weights used control the priorities
\item Exponent \me{q} plays different role based on the value it assumes
	\begin{itemize}
	\item \me{\ell_{q=1}} results in greedy allocation
	\item \me{\ell_{q=2}} ideal for the delay or buffer size limited scenarios
	\item \me{\ell_{q=\infty}} provides fair resource allocation
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{\acs{JSFRA} Formulation}
\begin{itemize}
\item Now, the precoder design problem is given as
\end{itemize}
\begin{subequations} \label{eqn-6}
\begin{align}
\underset{{t_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} & \hspace{0.25em} && \| \tilde{\mbf{v}} \|_q \label{eqn-obj} \\
\text{subject to} & \hspace{0.25em} && t_{l,k,n}\leq \log_2(1 + \gamma_{l,k,n}) \\
& \hspace{0.25em} && \alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2\triangleq f(\tilde{\mbf{u}}_{l,k,n})},\label{eqn-6.2}\\
& \hspace{0.25em} && \beta_{l,k,n}  \geq  N_0 + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^H \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \label{eqn-6.3} \\
& \hspace{0.25em} && \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^H) \leq P_{{\max}}, \fall b
\end{align}
\end{subequations}
\begin{itemize}
\item where \me{\tilde{\mbf{u}}_{l,k,n}  \triangleq \{\mvec{w}{l,k,n}^H, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}}
\end{itemize}
\end{frame}

\begin{frame}{\acs{JSFRA} Formulation}
\begin{itemize}
\item To maximize the received \acs{SINR}, \me{\mvec{W}{k,n}} are modeled with the \acs{MMSE} receivers
\item The \acs{JSFRA} formulation in \eqref{eqn-6} is nonconvex due to the constraint defined by \eqref{eqn-6.2} as
\me{\alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2}}
\item In order to solve the problem in \eqref{eqn-6}, we use \ac{SCA} approach for the constraint defined by \eqref{eqn-6.2}
\item Let, \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}, where
\end{itemize}
\begin{subeqnarray}
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^H \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^H \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}
\end{subeqnarray}
\end{frame}

\begin{frame}{\acs{JSFRA} Formulation}
\begin{itemize}
\item Now, the first order Taylor approximation is used for the function \me{f(\tilde{\mbf{u}}_{l,k,n})} around an arbitrary point \me{\tilde{\mbf{u}}_{l,k,n}^{(i-1)}}
\item With this approximation, the problem in \eqref{eqn-6} can be solved using the well known solvers for the optimal precoders and \me{\tilde{\mbf{u}}_{l,k,n}}
\item Once the optimal precoders \me{\mvec{M}{k,n}} are evaluated, \me{\mvec{W}{k,n}} are updated using the \acs{MMSE} receivers
\item The local point \me{\tilde{\mbf{u}}_{l,k,n}^{(i-1)}} is updated with the current optimal point \me{\tilde{\mbf{u}}_{l,k,n}^{(i)}}
\item With the updated precoders and \me{\tilde{\mbf{u}}_{l,k,n}^{(i)}}, optimization is carried out in an iterative manner until convergence
\end{itemize}
\end{frame}

\section{Simulation Results}

\subsection{SISO Example}

\begin{frame}{\acs{SISO} Example}
\begin{itemize}
\item Let us consider a simple example with \me{N_T = N_R = 1}, \me{N=3} sub-channels, and \me{K = 3} users, each having \me{Q_k = 6}
\item Rates allocated to each user by the two schemes are outlined as 
\end{itemize}
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\( \begin{array}{|*{10}{c|}}
\hline
\multirow{2}{*}{{k}} & \multicolumn{3}{c|}{{n = 1}} & \multicolumn{3}{c|}{{n = 2}} & \multicolumn{3}{c|}{{n = 3}} \\
\cline{2-10}
 & h_{k,1} & {a} & {b} & h_{k,2} & {a} & {b} & h_{k,3} & {a} & {b} \\
\hline
1 &  1.70 & 0 & 4.91 & 0.52 & 0 & 0 & 0.55 & 2.04 & 0 \\
2 &  0.39 & 0 & 0 & 1.41 & 4.39 & 4.39 & 1.02 & 0 & 0 \\
3 &  2.34 & 5.81 & 0 & 1.25 & 0 & 0 & 2.31 & 0 & 5.77 \\
\hline
\end{array} \)
\caption{Sub channel wise allocation for a scheduling instant}
\label{tbl-1}
\vspace{-0.35cm}
\end{table}
\begin{itemize}
\item \me{\zeta = 5.76} bits for \acs{Q-WSRM} and \me{\zeta = 2.93} bits for \acs{JSFRA} scheme, where \me{\zeta = \sum_{k = 1}^K \left [ \, Q_k - t_k \,\right ]^+}
\item \acs{Q-WSRM} scheme depends on the sub-channel permutation pattern
\end{itemize}
\end{frame}

\subsection{MIMO Example}

\begin{frame}{System Model - \me{\lbrace \, N_B,N_T,N,K,N_R \, \rbrace = \lbrace \, 2,4,5,8,1 \, \rbrace}}
\begin{figure}
\includegraphics[width=0.8\textwidth]{qdeviation_4x1}
\end{figure}
\end{frame}

\begin{frame}{System Model - \me{\lbrace \, N_B,N_T,N,K,N_R \, \rbrace = \lbrace \, 2,4,5,8,2 \, \rbrace}}
\begin{figure}
\includegraphics[width=0.8\textwidth]{qdeviation_4x2}
\end{figure}
\end{frame}

\begin{frame}{System Model - \me{\lbrace \, N_B,N_T,N,K,N_R \, \rbrace = \lbrace \, 2,4,3,6,1 \, \rbrace}}
\begin{figure}
\includegraphics[width=0.8\textwidth]{qdeviation_4x1_2}
\end{figure}
\end{frame}

\begin{frame}{System Model - \me{\lbrace \, N_B,N_T,N,K,N_R \, \rbrace = \lbrace \, 2,4,5,8,1 \, \rbrace}}
\begin{itemize}
\item Let the backlogged packets (bits) for each user be \me{Q_k = 12} bits
\item The resource allocation for different exponent \me{q}'s are given as
\end{itemize}
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\(\begin{array}{|c|*{8}{c}|c|}
\hline
{q} & \multicolumn{8}{c|}{\text{user indices}} & {\zeta} \\
\hline
{\ell_{1}} & 12.0 &  6.15 &  5.32 & 12.0 &  6.95 & 11.1 & 11.9 & 10.8 & 19.71 \\
{\ell_2} & 11.9 & 7.3 & 5.9 & 10.1 & 9.19 & 10.1 & 10.8 & 10.3 & 20.48 \\
{\ell_{\infty}} & 9.15 & 9.15 & 9.15 & 9.15 & 9.16 & 9.15 & 9.15 & 9.15 & 22.75 \\
\hline
\end{array}\)
\caption{Queue information for \me{N=5} sub-channels}
\label{tbl-3}
\vspace{-0.35cm}
\end{table}
\begin{itemize}
\item As seen from the table, for \me{q=1}, the resource are allocated in a greedy manner as compared to the \me{q=\infty}, which provides fair allocation of \me{\approx 9.15} bits each
\end{itemize}
\end{frame}

\section{Conclusions}

\begin{frame}{Conclusions}
\begin{itemize}
\item We discussed the problem of wireless resource allocation to minimize backlogged packets in an efficient way
\item The proposed approach uses \ac{SCA} method by using linear approximation for the nonconvex constraint
\item In future, we address the distributed approaches for the precoder design across each \acsp{BS} with minimal information exchange
\item An iterative algorithm for the \acs{JSFRA} scheme using \acs{MSE} reformulation will be addressed for the implementation purpose
\end{itemize}
\end{frame}

\begin{frame}
\begin{center}
{\color{blue}\Huge{Questions !}}
\end{center}
\end{frame}

\end{document}

### 2015-08-22 Presentation/latex_presentation.tex
updated presentation and draft

\documentclass[10pt]{beamer} 
\usetheme{cwc}

\usepackage{amsmath,amssymb}
\usepackage{graphicx,acronym,setspace,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage{subeqnarray,multirow,cite,array,color,mathtools}

\acrodef{MSE}{mean squared error}
\acrodef{BC}{broadcast channel}
\acrodef{MC}{multi-cell}
\acrodef{BS}{base station}
\acrodef{MIMO}{multiple-input multiple-output}
\acrodef{SISO}{single-input single-output}
\acrodef{MU}{multi-user}
\acrodef{MU-MIMO}{\acl{MU} \acl{MIMO}}
\acrodef{OFDM}{orthogonal frequency division multiplexing}
\acrodef{WSRM}{weighted sum rate maximization}
\acrodef{QoS}{quality of service}
\acrodef{SCA}{successive convex approximation}
\acrodef{SNR}{signal-to-noise ratio}
\acrodef{MMSE}{minimum \acl{MSE}}
\acrodef{SIR}{signal-to-interference ratio}
\acrodef{SINR}{signal-to-interference-plus-noise ratio}
\acrodef{Q-WSRM}{queue \acl{WSRM}}
\acrodef{QM}{queue minimizing}
\acrodef{SRA}{spatial resource allocation}
\acrodef{JSFRA}{joint space-frequency resource allocation}
\acrodef{WMMSE}{weighted \acl{MMSE}}
\acrodef{KKT}{Karush-Kuhn-Tucker}
\acrodef{GP}{geometric programming}
\acrodef{SOC}{second-order cone}
\acrodef{BCDM}{block coordinate descent method}

\input{./../Report/shortcuts}
\input{./../Report/acronyms}

\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}}
\DeclareGraphicsExtensions{.eps}

\epstopdfsetup{update,prepend,prefersuffix=false,suffix=}
\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
\pdfcompresslevel=9

\title{Traffic Aware Precoder Design for Space Frequency Resource Allocation}
\author{{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}

\begin{document}

\AtBeginSection{\frame{\sectionpage}}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Outline}
    \tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}{Introduction and Motivation}
\begin{itemize}
\item Complex algorithms are adopted to maximize the throughput to satisfy the data requirements of the higher layers
\item Available wireless resources are to be utilized efficiently to minimize the backlogged packets 
\item Spatial and Frequency resources are exploited to empty the packets waiting at the \acsp{BS}
\item In this work, we discuss the precoder design for the \acl{MU} \acs{MIMO}-\acs{OFDM} setup to minimize the number of queued packets 
\end{itemize}
\end{frame}

\section{System Model \& Problem Formulation}

\begin{frame}{Symbols used}
\begin{itemize}
\item \acs{OFDM} system with \me{N} sub-channels and \me{N_B} \acp{BS}, each equipped with \me{N_T} transmit antennas
\item Let \me{K} be the total number of users with \me{N_R} antennas
\item Let \me{\mc{B}} and \me{\mc{U}} denote the set of coordinating \acp{BS} and users in the system
\item The set of users belonging to \acs{BS} \me{b} is denoted by \me{\mc{U}_b \in \mc{U}}
\item Let \me{b_k \in \mathcal{B}} denotes the \ac{BS} serving the user \me{k}
\item Let \me{L} be the total available spatial streams for a user \me{k}, given by \me{\min (N_T,N_R)}
\end{itemize}
\end{frame}

\begin{frame}{System Model}
\begin{itemize}
\item The \me{\ith{l}} spatial signal received on sub-channel \me{n} of user \me{k} is given by
\begin{multline}\label{eqn-1}
\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n} \\ 
+ \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
\end{multline}
\item where \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}} are transmit and receive beamformers corresponding to the \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel of user \me{k}
\end{itemize}
\end{frame}

\begin{frame}{System Model}
\begin{itemize}
\item \me{\mvec{H}{b_k,k,n} \in \mathbb{C}^{N_R \times N_T}} denotes the channel between \ac{BS} \me{b_k} and user \me{k}
\item \me{d_{l,k,n}} and \me{{n}_{l,k,n}} correspond to data symbol and equivalent noise on \me{\ith{l}} spatial stream of user \me{k}
\item Using the above notations, the \acs{SINR} seen by the \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel for user \me{k} is given by
\end{itemize}
\begin{equation}\label{eq:SINR}
\gamma_{l,k,n} = \dfrac{\left |\mvec{w}{l,k,n}^\herm \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |^2}{\enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2}
\end{equation}
\begin{itemize}
\item where \eqn{\enoise = \|\mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n} \|^2 }
\end{itemize}
\end{frame}

\begin{frame}{Queueing Model}
\begin{itemize}
\item Each user is associated with backlogged packets of size \me{Q_k} packets.
\item Queued packets \me{Q_k} of each user follows dynamic equation at the \me{\ith{i}} instant as
\begin{equation}
Q_k(i+1) = \Big [ Q_k(i) - t_k(i) \Big ]^+ + \lambda_k(i)
\label{eqn-2a}
\end{equation}
\item where \me{t_k = \sum_{n = 1}^N \, \sum_{l = 1}^L \, t_{l,k,n}} denotes the total number of transmitted packets corresponding to user \me{k} in the previous \me{\ith{i}} instant
\item \me{\lambda_k} represents the fresh arrivals of user \me{k} at \ac{BS} \me{b_k}
\end{itemize}
\end{frame}

\begin{frame}{Problem Formulation}
\begin{itemize}
\item Objective is to transmit the queued packets waiting at \acsp{BS} to corresponding users in the system.
\item The available spatial and frequency resources are to be efficiently utilized to minimize the queued packets
\item In order to achieve this, precoders are to be designed with certain objective that involves the backlogged packets as well
\item Precoders can perform scheduling of users by providing zero powers to exclude from the resource elements
\end{itemize}
\end{frame}

\section{Centralized Solutions}

\subsection{Existing \acs{Q-WSRM} Formulation}

\begin{frame}{Queue-Weighted Sum Rate Maximization (\acs{Q-WSRM})}
\begin{itemize}
\item \acs{Q-WSRM} formulation is the result of minimizing the conditional Lyapunov drift \footnote{Neely, Michael J. "Stochastic network optimization with application to communication and queueing systems." Synthesis Lectures on Communication Networks 3.1 (2010): 1-211.}
\item \acs{Q-WSRM} formulation is also called as back pressure algorithm, since it acts greedily in minimizing the backlogged packets at each instant
\[ \underset{t_{l,k,n}}{\text{minimize}} \quad \sum_{k \in \mc{U}} \left \lbrace Q_k(i)^2 - Q_k(i-1)^2 \right \rbrace, \]
\item where \me{Q_k} follows the dynamic Queue expression in \eqref{eqn-2a} and \me{t_k = \sum_{n = 1}^N \, \sum_{l=1}^L \, t_{l,k,n}}
\end{itemize}
\end{frame}

\begin{frame}{Queue-Weighted Sum Rate Maximization (\acs{Q-WSRM})}
\begin{itemize}
\item Upon solving the Lyapunov drift expression, we obtain the \acs{Q-WSRM} formulation as
\end{itemize}
\begin{subequations}
\begin{align}
 \underset{t_{l,k,n}}{\text{maximize}} & \qquad \sum_{k \in \mc{U}} \; Q_k \left ( \alert{\sum_{n=1}^N} \, \sum_{l = 1}^L  t_{l,k,n} \right ) \\
& \qquad {\color{blue} \alert{\sum_{n=1}^N} \, \sum_{l = 1}^L  t_{l,k,n}  \leq \alert{Q_k} \; / \; Q_{k,n}}
\end{align}
\end{subequations}
\begin{itemize}
\item Performs better in cell-edge scenarios
\item Complexity can be reduced if precoders are designed for each sub-channel independently
\end{itemize}
\end{frame}

\begin{frame}{Queue-Weighted Sum Rate Maximization (\acs{Q-WSRM})}
	\begin{itemize}
		\item Complexity can be reduced if precoders are designed for each sub-channel independently
		\item Coupling across sub-channels is obtained by the queues, which are updated after evaluating the rate from previously chosen sub-channels as
	\end{itemize}
	\begin{equation*}
	Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
	\end{equation*}
\end{frame}

\subsection{\acs{JSFRA} Formulation (\acs{SINR} Relaxation)}

\begin{frame}{\acs{JSFRA} Formulation (\acs{SINR} Relaxation)}
\begin{itemize}
\item Precoders are designed by a centralized controller, which are then used by all \acp{BS} in \me{\mc{B}}
\item The objective used to design transmit precoders is 
\[ {\color{blue} v_k = \left | Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right |^q } \]
\item To generalize the objective, we use \me{\tilde{v}_k \triangleq a_k \, v_k}, where \me{a_k} is arbitrary weights used control the priorities
\item Exponent \me{q} plays different role based on the value it assumes
	\begin{itemize}
	\item \me{\ell_{q=1}} results in greedy allocation
	\item \me{\ell_{q=2}} ideal for the delay or buffer size limited scenarios
	\item \me{\ell_{q=\infty}} provides fair resource allocation in each transmission instant
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{\acs{JSFRA} Formulation (\acs{SINR} Relaxation)}
\begin{itemize}
\item Now, the precoder design problem is given as
\end{itemize}
\begin{subequations} \label{eqn-6}
\begin{align}
\underset{{t_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} & \hspace{0.25em} && \| \tilde{\mbf{v}} \|_q \label{eqn-obj} \\
\text{subject to} & \hspace{0.25em} && t_{l,k,n}\leq \log_2(1 + \gamma_{l,k,n}) \\
& \hspace{0.25em} && \alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2\triangleq f(\tilde{\mbf{u}}_{l,k,n})},\label{eqn-6.2}\\
& \hspace{0.25em} && \beta_{l,k,n}  \geq  \enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^H \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \label{eqn-6.3} \\
& \hspace{0.25em} && \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^H) \leq P_{{\max}}, \fall b
\end{align}
\end{subequations}
\begin{itemize}
\item where \me{\tilde{\mbf{u}}_{l,k,n}  \triangleq \{\mvec{w}{l,k,n}^H, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}}
\end{itemize}
\end{frame}

\begin{frame}{\acs{JSFRA} Formulation (\acs{SINR} Relaxation)}
\begin{itemize}
\item To maximize the received \acs{SINR}, \me{\mvec{w}{l,k,n}} are modeled with the \acs{MMSE} receivers
\item The \acs{JSFRA} formulation in \eqref{eqn-6} is nonconvex due to the constraint defined by \eqref{eqn-6.2} as
\me{\alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2}}
\item In order to solve the problem in \eqref{eqn-6}, we use \ac{SCA} approach for the constraint defined by \eqref{eqn-6.2}
\item Let, \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}, where
\end{itemize}
\begin{subeqnarray}
p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^H \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^H \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}
\end{subeqnarray}
\end{frame}

\begin{frame}{\acs{JSFRA} Formulation (\acs{SINR} Relaxation)}
\begin{itemize}
\item Now, the first order Taylor approximation is used for the function \me{f(\tilde{\mbf{u}}_{l,k,n})} around an arbitrary point \me{\tilde{\mbf{u}}_{l,k,n}^{(i-1)}}
\item With this approximation, the problem in \eqref{eqn-6} can be solved using the well known solvers for the optimal precoders and \me{\tilde{\mbf{u}}_{l,k,n}}
\item Once the precoders \me{\mvec{m}{l,k,n}} are evaluated, \me{\mvec{w}{l,k,n}} are updated using the \acs{MMSE} receivers
\item The local point \me{\tilde{\mbf{u}}_{l,k,n}^{(i-1)}} is updated with the current optimal point \me{\tilde{\mbf{u}}_{l,k,n}^{(i)}}
\item With the updated precoders and \me{\tilde{\mbf{u}}_{l,k,n}^{(i)}}, optimization is carried out in an iterative manner until convergence
\end{itemize}
\end{frame}

\subsection{\acs{JSFRA} Formulation (\acs{MSE} Reformulation)}

\begin{frame}{\acs{JSFRA} Formulation (\acs{MSE} Reformulation)}
	\begin{itemize}
		\item In this approach, we utilize the relation between the \acs{MSE} and the \acs{SINR} as \me{\color{blue} \epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}}
		\item Equivalence is valid only when the receivers are designed with the \ac{MSE} objective, \textit{i.e.}, using \acs{MMSE} receivers
	\end{itemize}
	\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
		+ \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
	\end{multline}
\end{frame}

\begin{frame}{\acs{JSFRA} Formulation (\acs{MSE} Reformulation)}
	\begin{itemize}
		\item Using the above reformulation, we can formulate the \acs{JSFRA} problem as
	\end{itemize}
	\begin{subeqnarray} \label{eqn-mse-1}
		\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \label{eqn-mse-1.1} \\
		\text{subject to} &\quad & \alert{t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n})}  \slabel{eqn-mse-1.2} \\
		& \quad & {\color{blue} \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise} \nonumber \\	
		&\quad & {\color{blue} \qquad {} + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}} \slabel{eqn-mse-1.3} \\
		&\quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b.  \slabel{eqn-mse-1.4}
	\end{subeqnarray}
\end{frame}

\begin{frame}{\acs{JSFRA} Formulation (\acs{MSE} Reformulation)}
	\begin{itemize}
		\item The nonconvex constraint in \eqref{eqn-mse-1.2} is approximated by a sequence of convex constraints
		\item It is achieved by using \ac{SCA} technique as earlier
		\item The iterative procedure is performed until convergence or for suitable number of iterations
		\item \alert{The above reformulation works only with the \acs{MMSE} receiver}
	\end{itemize}
\end{frame}

\section{Distributed Solutions}

\subsection{Primal \& \acs{ADMM} based decompositions}

\begin{frame}{Distributed Methods}
	\begin{itemize}
		\item When the system size is small, centralized approach is viable if the channel remains constant for multiple transmission slots
		\item However, the overhead involved in the centralized design scales up significantly as the network size grows
		\item Distributed schemes based on primal decomposition or \acs{ADMM} can be used to reduce the signaling requirements
		\item The overhead involved in the design of precoders are only scalar interference variables
		\item Only the convex approximated subproblem in each \acs{SCA} step is performed via distributed approaches
	\end{itemize}
\end{frame}

\begin{frame}{Primal Decomposition Method}
	\begin{itemize}
		\item Precoder design is performed by a master-slave approach
		\item Interference created to the neighboring \ac{BS} users are bounded by a scalar variable
		\item The interference thresholds are determined by the master problem, which is performed at each \ac{BS} with the signaling exchange
	\end{itemize}
	\begin{equation} \label{inter_exp}
	\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{j,i,n} |^2 \; \forall b \in \bar{\mc{B}}_{b_k}.
	\end{equation}
	\begin{itemize}
		\item Each \ac{BS} subproblem includes \eqref{inter_exp} as an additional interference constraint in the respective optimization problem
	\end{itemize}
\end{frame}

\begin{frame}{ADMM based Decomposition Method}
	\begin{itemize}
		\item The \ac{ADMM} is superior to other distributed schemes in terms of the convergence speed
		\item The \ac{ADMM} includes an additional quadratic term in the objective as \me{\color{blue} \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \|^2}, where \eqn{\mbfa{\zeta}^{(j)}_b} is global consensus variable
		\item Unlike primal decomposition method, \eqn{\zeta_{l,k,n,b}} in \eqref{inter_exp} is treated as an optimization variable in \ac{ADMM}
		\item The consensus variables are updated as
	\end{itemize}
	\begin{equation}
	\mbfa{\zeta}_{b_k}(b)^{(j+1)} = \mbfa{\zeta}_{b}(b_k)^{(j+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
	\label{if-sg-update}
	\end{equation}
	\begin{itemize}
		\item where \eqn{\mbfa{\zeta}_{b_k}(b)} denotes the entries corresponding to \ac{BS} \eqn{b} in \ac{BS} \eqn{b_k}
	\end{itemize}
\end{frame}

\subsection{KKT based Distributed Solution}

\begin{frame}{KKT based Distributed Solution}
	\begin{itemize}
		\item The decentralization methods considered so far involve considerable signaling exchanges via backhaul
		\item However, when the users are equipped with multiple receive antennas, the overhead requirement is significantly large
		\item Since the signaling requirements are large, the iterative algorithm should design efficient precoders in few number of iterations to reduce the backlogged packets
		\item In order to achieve that, we design an iterative procedure based on solving the \ac{KKT} equations for the \acs{JSFRA} problem via \acs{MSE} reformulation
		\item Unlike the earlier schemes, we perform the group update of all the involved optimization variables to speed up the convergence of precoder design
	\end{itemize}
\end{frame}

\begin{frame}{KKT based Distributed Solution}
	\renewcommand{\arraystretch}{0.8} \scriptsize
\begin{subeqnarray} \label{kkt-mse-4}
	\mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \nonumber \\
	\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \label{kkt-mse-4.6}\\
	\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + \enoise \label{kkt-mse-4.4} \\
	t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \label{kkt-mse-4.5} \\
	\sigma_{l,k,n}^{(i)} &=& \left [\tfrac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right ]^+  \label{kkt-mse-4.2} \\
	\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho^{(i)} \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \label{kkt-mse-4.1}
\end{subeqnarray}
\end{frame}

\section{Simulation Results}

\subsection{SISO Example}

\begin{frame}{\acs{SISO} Example}
\begin{itemize}
\item Let us consider a simple example with \me{N_T = N_R = 1}, \me{N=3} sub-channels, and \me{K = 3} users
\end{itemize}
\begin{table} \scriptsize
	\caption{Sub-channel-wise listing of channel gains and rate allocations}
	\begin{tabular}{|*{13}{c|}}
		\hline
		$Q_k$ & \multicolumn{3}{c|}{\eqn{\mvec{H}{b_k,k}}} & \multicolumn{3}{c|}{(A)} & \multicolumn{3}{c|}{(B)} & \multicolumn{3}{c|}{(C)} \\
		\cline{2-13}
		& \me{1} & \me{2} & \me{3} & \me{1} & \me{2} & \me{3} & \me{1} & \me{2} & \me{3} & \me{1} & \me{2} & \me{3} \\
		\hline
		\me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{4}{|c|}{Remaining packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1}
\end{table}
\begin{itemize}
\item \me{\zeta = \sum_{k = 1}^K \left [ \, Q_k - t_k \,\right ]^+}
\item \me{\zeta = 5.89} bits for \acs{Q-WSRM} (C), \me{\zeta = 3.92} bits for \acs{Q-WSRME} scheme (A) and, \me{\zeta = 2.51} bits for \acs{JSFRA} scheme (B)
\end{itemize}
\end{frame}

\subsection{MIMO Examples}

\subsubsection{Centralized Solutions}

\begin{frame}{Performance Comparison with Number of Residual Packets}
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{fig-2-5}
	\caption{System Model - \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}}
\end{figure}
\end{frame}

\subsubsection{Distributed Solutions}

\begin{frame}{Performance Comparison with Number of Residual Packets}
	\begin{figure}
		\centering
		\includegraphics[width=0.75\textwidth]{fig-3-2}
		\caption{System Model - \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace}}
	\end{figure}
\end{frame}

\subsubsection{Effect of varying \eqn{\ell_q} norms}

\begin{frame}{Effect on Residual Packets with different \eqn{\ell_q} norms}
	\begin{table}
		\centering
		\caption{Number of backlogged bits associated with each user for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}.}
		\renewcommand{\arraystretch}{1.25} \scriptsize
		\begin{tabular}{|c|*{8}{c}|c|}
			\hline
			\multirow{2}{*}{\me{q}} & \multicolumn{8}{c|}{user indices} & \multirow{2}{*}{\me{\chi}} \\
			\cline{2-9}
			& 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \\
			\hline
			\hline
			\me{1} & 15.0 & 3.95 & 5.26 & 8.95 & 7.0 & 11.9 & 12.0 & 9.7 & 25.15 \\
			\me{2} & 11.2 & 3.9 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.9 & 27.77 \\
			\me{\infty} & 11.4 & 4.4 & 10.4 & 10.4 & 10.4 & 8.4 &  8.4 &  6.4 & 28.68 \\
			\hline
			\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
			\cline{1-9}
		\end{tabular}
		\label{tbl-3}
	\end{table}	
\end{frame}

\subsubsection{KKT Based Approach}

\begin{frame}{Performance Comparison with Number of Residual Packets}
	\begin{figure}
		\centering
		\includegraphics[width=0.75\textwidth]{fig-9-3}
		\caption{System Model - \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace}}
	\end{figure}
\end{frame}

\subsection{Time Correlated Fading Performance}

\begin{frame}{Average Residual Packets after each Transmission Slot}
	\begin{figure}
		\centering
		\includegraphics[width=0.75\textwidth]{average_queue_over_time-3}
		\caption{System Model - \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} after \eqn{250} transmissions}
	\end{figure}
\end{frame}

\section{Conclusions}

\begin{frame}{Conclusions}
\begin{itemize}
\item We discussed the problem of wireless resource allocation to minimize backlogged packets in an efficient way
\item The proposed approach uses \ac{SCA} method by using linear approximation for the nonconvex constraint
\item We also addressed different distributed methods for the precoder design across each \acsp{BS} with minimal information exchange
\item An iterative algorithm for the \acs{JSFRA} scheme using \acs{MSE} reformulation is also studied
\end{itemize}
\end{frame}

\begin{frame}
\begin{center}
{\color{blue}\Huge{Questions !}}
\end{center}
\end{frame}

\end{document}

### 2015-08-22 Report/system_model.tex
updated presentation and draft

@@
 \begin{equation}\label{eqn-1}
-\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n}
+\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n}
 \end{equation}
@@
 \begin{multline}\label{eqn-1}
-\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{k,n} \\ 
+\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n} \\ 
 + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
@@
 }
-where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{\ith{n}} sub-channel and \me{\ith{l}} spatial stream.
+where \me{\mvec{H}{b,k,n} \in \mathbb{C}^{N_R \times N_T}} is the channel between \ac{BS} \me{b} and  user \me{k} on sub-channel \me{n}, and \me{\mvec{n}{l,k,n}} \me{\sim \mc{CN}(0,N_0)} is the additive noise vector for user \me{k} on the \me{\ith{n}} sub-channel and \me{\ith{l}} spatial stream.
 In \eqref{eqn-1}, \me{L = \text{rank}(\mvec{H}{b,k,n}) = \min(N_T,N_R)} is the maximum number of spatial streams.\footnote{It can be easily extended for user specific streams \me{L_k} instead of using common \me{L} streams for all users.

### 2015-09-01 Presentation/markku_reduced.tex
updated with presentation

--- 2015-08-22 Presentation/latex_presentation.tex
@@
-\documentclass[10pt]{beamer} 
+\documentclass[9pt]{beamer} 
 \usetheme{cwc}
@@
 \usepackage[ruled]{algorithm2e}
-\usepackage{subeqnarray,multirow,cite,array,color,mathtools}
+\usepackage{subeqnarray,multirow,cite,array,color,mathtools,setspace,geometry}
 
@@
 
+\linespread{1.4}
+
 \title{Traffic Aware Precoder Design for Space Frequency Resource Allocation}
-\author{{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}
+\author{{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti\eqn{^\dagger}} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}
 
@@
 
-\begin{frame}{Outline}
+\begin{frame}{Outline} \scriptsize
     \tableofcontents
 \end{frame}
+
+\acused{BS} \acused{MIMO} \acused{OFDM}
 
@@
 \begin{itemize}
-\item Complex algorithms are adopted to maximize the throughput to satisfy the data requirements of the higher layers
+\item Complex algorithms are adopted to maximize throughput to satisfy the data requirements from higher layers
 \item Available wireless resources are to be utilized efficiently to minimize the backlogged packets 
-\item Spatial and Frequency resources are exploited to empty the packets waiting at the \acsp{BS}
-\item In this work, we discuss the precoder design for the \acl{MU} \acs{MIMO}-\acs{OFDM} setup to minimize the number of queued packets 
+\item Spatial and Frequency resources are exploited to empty the packets waiting at the \acp{BS}
+\item In this work, we discuss precoder designs for \acl{MU} \acs{MIMO}-\acs{OFDM} setup to minimize the number of queued packets 
 \end{itemize}
@@
 \begin{itemize}
-\item Objective is to transmit the queued packets waiting at \acsp{BS} to corresponding users in the system.
-\item The available spatial and frequency resources are to be efficiently utilized to minimize the queued packets
-\item In order to achieve this, precoders are to be designed with certain objective that involves the backlogged packets as well
-\item Precoders can perform scheduling of users by providing zero powers to exclude from the resource elements
+\item Available spatial and frequency resources are to be efficiently utilized to minimize the queued packets
+\item {\color{red}Objective} - to minimize the number of backlogged packets waiting at \acp{BS}
+\item {\color{red}Optimization variables} - transmit precoders and receive beamformers
+\item {\color{red}\ac{MIMO}-\ac{OFDM}} - scheduling of users across sub-channels is inherently performed by precoders
 \end{itemize}
@@
 \begin{itemize}
-\item \acs{Q-WSRM} formulation is the result of minimizing the conditional Lyapunov drift \footnote{Neely, Michael J.
-"Stochastic network optimization with application to communication and queueing systems." Synthesis Lectures on Communication Networks 3.1 (2010): 1-211.}
+\item \acs{Q-WSRM} formulation is the result of minimizing the conditional Lyapunov drift\eqn{^\dagger}
 \item \acs{Q-WSRM} formulation is also called as back pressure algorithm, since it acts greedily in minimizing the backlogged packets at each instant
@@
 \end{itemize}
+
+\vspace{2eM}
+\eqn{^\dagger}\footnotesize{Neely, Michael J. "Stochastic network optimization with application to communication and queueing systems." Synthesis Lectures on Communication Networks 3.1 (2010): 1-211.}
 \end{frame}
@@
 \begin{itemize}
-\item Upon solving the Lyapunov drift expression, we obtain the \acs{Q-WSRM} formulation as
+\item \acs{Q-WSRM} formulation, which is obtained by solving Lyapunov drift, is given by
 \end{itemize}
@@
 \begin{itemize}
-\item Performs better in cell-edge scenarios
-\item Complexity can be reduced if precoders are designed for each sub-channel independently
+\item Queue-Rate product is maximized
+\item Users with more number of backlogged packets are favored over good channel users
 \end{itemize}
@@
 \item The objective used to design transmit precoders is 
-\[ {\color{blue} v_k = \left | Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right |^q } \]
-\item To generalize the objective, we use \me{\tilde{v}_k \triangleq a_k \, v_k}, where \me{a_k} is arbitrary weights used control the priorities
+\begin{equation}
+\scriptsize {\color{blue} v_k = \left | Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right |^q }
+\end{equation}
+\item To generalize the objective, we use \me{\tilde{v}_k \triangleq a_k^{\frac{1}{q}} \, v_k}, where \me{a_k} is arbitrary weights used control the priorities
 \item Exponent \me{q} plays different role based on the value it assumes
@@
 \begin{itemize}
-\item Now, the precoder design problem is given as
-\end{itemize}
-\begin{subequations} \label{eqn-6}
-\begin{align}
-\underset{{t_{l,k,n},\mvec{M}{k,n},\mvec{W}{k,n}}}{\text{minimize}} & \hspace{0.25em} && \| \tilde{\mbf{v}} \|_q \label{eqn-obj} \\
-\text{subject to} & \hspace{0.25em} && t_{l,k,n}\leq \log_2(1 + \gamma_{l,k,n}) \\
-& \hspace{0.25em} && \alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2\triangleq f(\tilde{\mbf{u}}_{l,k,n})},\label{eqn-6.2}\\
-& \hspace{0.25em} && \beta_{l,k,n}  \geq  \enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^H \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2, \label{eqn-6.3} \\
-& \hspace{0.25em} && \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^H) \leq P_{{\max}}, \fall b
-\end{align}
-\end{subequations}
-\begin{itemize}
-\item where \me{\tilde{\mbf{u}}_{l,k,n}  \triangleq \{\mvec{w}{l,k,n}^H, \mvec{H}{b_k,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{\acs{JSFRA} Formulation (\acs{SINR} Relaxation)}
-\begin{itemize}
-\item To maximize the received \acs{SINR}, \me{\mvec{w}{l,k,n}} are modeled with the \acs{MMSE} receivers
-\item The \acs{JSFRA} formulation in \eqref{eqn-6} is nonconvex due to the constraint defined by \eqref{eqn-6.2} as
-\me{\alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2}}
-\item In order to solve the problem in \eqref{eqn-6}, we use \ac{SCA} approach for the constraint defined by \eqref{eqn-6.2}
-\item Let, \me{f(\tilde{\mbf{u}}_{l,k,n})=(p_{l,k,n}^2 + q_{l,k,n}^2)/\beta_{l,k,n}}, where
-\end{itemize}
-\begin{subeqnarray}
-p_{l,k,n} &\triangleq& \Re \set{{\mvec{w}{l,k,n}^H \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}, \\
-q_{l,k,n} &\triangleq& \Im \set{{\mvec{w}{l,k,n}^H \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}}}
-\end{subeqnarray}
-\end{frame}
-
-\begin{frame}{\acs{JSFRA} Formulation (\acs{SINR} Relaxation)}
-\begin{itemize}
-\item Now, the first order Taylor approximation is used for the function \me{f(\tilde{\mbf{u}}_{l,k,n})} around an arbitrary point \me{\tilde{\mbf{u}}_{l,k,n}^{(i-1)}}
-\item With this approximation, the problem in \eqref{eqn-6} can be solved using the well known solvers for the optimal precoders and \me{\tilde{\mbf{u}}_{l,k,n}}
-\item Once the precoders \me{\mvec{m}{l,k,n}} are evaluated, \me{\mvec{w}{l,k,n}} are updated using the \acs{MMSE} receivers
-\item The local point \me{\tilde{\mbf{u}}_{l,k,n}^{(i-1)}} is updated with the current optimal point \me{\tilde{\mbf{u}}_{l,k,n}^{(i)}}
-\item With the updated precoders and \me{\tilde{\mbf{u}}_{l,k,n}^{(i)}}, optimization is carried out in an iterative manner until convergence
+\item Optimization problem with queue difference objective is nonconvex due to the constraint
+\begin{equation}  \scriptsize
+\alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2 }
+\end{equation}
+\item The nonconvex constraints are approximated by sequence of convex subsets and solved iteratively
+\item Convergence of the iterative algorithm is guaranteed
+\item Receive beamformers are designed by the \acs{MMSE} receivers using the converged transmit precoders
 \end{itemize}
@@
 	\begin{itemize}
-		\item In this approach, we utilize the relation between the \acs{MSE} and the \acs{SINR} as \me{\color{blue} \epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}}
+	\item Alternatively, we solve the queue minimization problem by utilizing the relation between the \acs{MSE} and the \acs{SINR} as \me{\color{blue} \epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}}
 	\item Equivalence is valid only when the receivers are designed with the \ac{MSE} objective, \textit{i.e.}, using \acs{MMSE} receivers
+	\begin{eqnarray} \label{mse-error} \scriptsize
+	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \big | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \big |^2 \nonumber \\
+	+ \sum_{{(j,i) \neq (l,k)}} \big | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \big |^2 + \enoise = \epsilon_{l,k,n}
+	\end{eqnarray}
+	\item Problem involves nonconvex constraint 
+	\begin{equation}
+	\alert{t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n})}
+	\end{equation}
 	\end{itemize}
-	\begin{multline} \label{mse-error}
-	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
-		+ \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
-	\end{multline}
 \end{frame}
@@
 	\begin{itemize}
-		\item Using the above reformulation, we can formulate the \acs{JSFRA} problem as
-	\end{itemize}
-	\begin{subeqnarray} \label{eqn-mse-1}
-		\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \label{eqn-mse-1.1} \\
-		\text{subject to} &\quad & \alert{t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n})}  \slabel{eqn-mse-1.2} \\
-		& \quad & {\color{blue} \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise} \nonumber \\	
-		&\quad & {\color{blue} \qquad {} + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}} \slabel{eqn-mse-1.3} \\
-		&\quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b.  \slabel{eqn-mse-1.4}
-	\end{subeqnarray}
-\end{frame}
-
-\begin{frame}{\acs{JSFRA} Formulation (\acs{MSE} Reformulation)}
-	\begin{itemize}
-		\item The nonconvex constraint in \eqref{eqn-mse-1.2} is approximated by a sequence of convex constraints
-		\item It is achieved by using \ac{SCA} technique as earlier
+		\item The nonconvex constraint is approximated by a sequence of convex constraints
+		\item It is achieved by using \ac{SCA} technique
 		\item The iterative procedure is performed until convergence or for suitable number of iterations
@@
 	\begin{itemize}
-		\item When the system size is small, centralized approach is viable if the channel remains constant for multiple transmission slots
-		\item However, the overhead involved in the centralized design scales up significantly as the network size grows
-		\item Distributed schemes based on primal decomposition or \acs{ADMM} can be used to reduce the signaling requirements
-		\item The overhead involved in the design of precoders are only scalar interference variables
-		\item Only the convex approximated subproblem in each \acs{SCA} step is performed via distributed approaches
+		\item Small System - centralized approach is viable, provided channel remains constant for multiple transmission slots
+		\item However, overhead involved in the centralized design scales up significantly as the network size grows
+		\item Distributed approaches based on primal decomposition or \acs{ADMM} can be used to reduce the signaling requirements
+		\item Overhead involved in the design of precoders are only scalar interference variables
+		\item Only convex approximated subproblem in each \acs{SCA} step is performed via distributed approaches
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Precoder design is performed by a master-slave approach
-		\item Interference created to the neighboring \ac{BS} users are bounded by a scalar variable
-		\item The interference thresholds are determined by the master problem, which is performed at each \ac{BS} with the signaling exchange
-	\end{itemize}
-	\begin{equation} \label{inter_exp}
+		\item Precoder design is based on master-slave approach
+		\item Interference to the neighboring \ac{BS} users are bounded by a scalar variable
+		\item The interference thresholds are determined by the master problem and used in each slave subproblem constraint as
+		\begin{equation} \label{inter_exp} \scriptsize
 		\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{j,i,n} |^2 \; \forall b \in \bar{\mc{B}}_{b_k}.
 		\end{equation}
-	\begin{itemize}
-		\item Each \ac{BS} subproblem includes \eqref{inter_exp} as an additional interference constraint in the respective optimization problem
 	\end{itemize}
@@
 
+\acused{ADMM}
 \begin{frame}{ADMM based Decomposition Method}
@@
 		\item The \ac{ADMM} is superior to other distributed schemes in terms of the convergence speed
-		\item The \ac{ADMM} includes an additional quadratic term in the objective as \me{\color{blue} \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \|^2}, where \eqn{\mbfa{\zeta}^{(j)}_b} is global consensus variable
-		\item Unlike primal decomposition method, \eqn{\zeta_{l,k,n,b}} in \eqref{inter_exp} is treated as an optimization variable in \ac{ADMM}
+		\item \ac{ADMM} includes an additional quadratic term 
+		\begin{equation}
+		\color{blue} \|v_k\|_q + \sum_{l,k,n} \nu_{l,k,n}^{(j)} \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) + \frac{\rho}{2}  \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \|^2
+		\end{equation}
+		in objective, where \eqn{\mbfa{\zeta}^{(j)}_b} is global consensus variable
+		\item \eqn{\zeta_{l,k,n,b}} in \eqref{inter_exp} is treated as an optimization variable in \ac{ADMM}
 		\item The consensus variables are updated as
-	\end{itemize}
-	\begin{equation}
-	\mbfa{\zeta}_{b_k}(b)^{(j+1)} = \mbfa{\zeta}_{b}(b_k)^{(j+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
-	\label{if-sg-update}
+		\begin{equation} \scriptsize
+		\mbfa{\zeta}_{b_k}(b)^{(j+1)} = \mbfa{\zeta}_{b}(b_k)^{(j+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}
 		\end{equation}
-	\begin{itemize}
 		\item where \eqn{\mbfa{\zeta}_{b_k}(b)} denotes the entries corresponding to \ac{BS} \eqn{b} in \ac{BS} \eqn{b_k}
@@
 	\begin{itemize}
-		\item The decentralization methods considered so far involve considerable signaling exchanges via backhaul
-		\item However, when the users are equipped with multiple receive antennas, the overhead requirement is significantly large
-		\item Since the signaling requirements are large, the iterative algorithm should design efficient precoders in few number of iterations to reduce the backlogged packets
-		\item In order to achieve that, we design an iterative procedure based on solving the \ac{KKT} equations for the \acs{JSFRA} problem via \acs{MSE} reformulation
-		\item Unlike the earlier schemes, we perform the group update of all the involved optimization variables to speed up the convergence of precoder design
+		\item Decentralization methods considered so far involve considerable signaling exchanges via backhaul
+		\item Since the overhead involved is large for multi-antenna receivers, the iterative design should reduce the backlogged packets significantly in first few iterations
+		\item To achieve that, we design an iterative procedure by solving the \ac{KKT} equations of the \acs{JSFRA} problem via \acs{MSE} reformulation
+		\item Group update of all the involved optimization variables is carried out to speed up the convergence of precoder design
 	\end{itemize}
-\end{frame}
-
-\begin{frame}{KKT based Distributed Solution}
-	\renewcommand{\arraystretch}{0.8} \scriptsize
-\begin{subeqnarray} \label{kkt-mse-4}
-	\mvec{m}{l,k,n}^{(i)} &=& \Big ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \nonumber \\
-	\mvec{w}{l,k,n}^{(i)} &=& \Big ( \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)} \label{kkt-mse-4.6}\\
-	\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{{(x,y) \neq (l,k)}} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + \enoise \label{kkt-mse-4.4} \\
-	t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}} \label{kkt-mse-4.5} \\
-	\sigma_{l,k,n}^{(i)} &=& \left [\tfrac{a_k \, q}{\log(2)}  \, \Big (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i)} \Big )^{(q-1)}\right ]^+  \label{kkt-mse-4.2} \\
-	\alpha^{(i)}_{l,k,n} &=& \alpha^{(i-1)}_{l,k,n} + \rho^{(i)} \left ( \tfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i)}} - \alpha^{(i-1)}_{l,k,n} \right ) \label{kkt-mse-4.1}
-\end{subeqnarray}
 \end{frame}
@@
 
-\subsection{SISO Example}
+\subsection{Centralized Solutions}
 
-\begin{frame}{\acs{SISO} Example}
-\begin{itemize}
-\item Let us consider a simple example with \me{N_T = N_R = 1}, \me{N=3} sub-channels, and \me{K = 3} users
-\end{itemize}
-\begin{table} \scriptsize
-	\caption{Sub-channel-wise listing of channel gains and rate allocations}
-	\begin{tabular}{|*{13}{c|}}
-		\hline
-		$Q_k$ & \multicolumn{3}{c|}{\eqn{\mvec{H}{b_k,k}}} & \multicolumn{3}{c|}{(A)} & \multicolumn{3}{c|}{(B)} & \multicolumn{3}{c|}{(C)} \\
-		\cline{2-13}
-		& \me{1} & \me{2} & \me{3} & \me{1} & \me{2} & \me{3} & \me{1} & \me{2} & \me{3} & \me{1} & \me{2} & \me{3} \\
-		\hline
-		\me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
-		\me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
-		\me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
-		\hline
-		\multicolumn{4}{|c|}{Remaining packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
-		\hline
-	\end{tabular}
-	\label{tbl-1}
-\end{table}
-\begin{itemize}
-\item \me{\zeta = \sum_{k = 1}^K \left [ \, Q_k - t_k \,\right ]^+}
-\item \me{\zeta = 5.89} bits for \acs{Q-WSRM} (C), \me{\zeta = 3.92} bits for \acs{Q-WSRME} scheme (A) and, \me{\zeta = 2.51} bits for \acs{JSFRA} scheme (B)
-\end{itemize}
-\end{frame}
-
-\subsection{MIMO Examples}
-
-\subsubsection{Centralized Solutions}
-
-\begin{frame}{Performance Comparison with Number of Residual Packets}
+\begin{frame}{Centralized Solutions}
 \begin{figure}
@@
 
-\subsubsection{Distributed Solutions}
+\subsection{Distributed Solutions}
 
-\begin{frame}{Performance Comparison with Number of Residual Packets}
+\begin{frame}{Distributed Solutions}
 	\begin{figure}
@@
 
-\subsubsection{Effect of varying \eqn{\ell_q} norms}
+\subsection{KKT based Approach}
 
-\begin{frame}{Effect on Residual Packets with different \eqn{\ell_q} norms}
-	\begin{table}
-		\centering
-		\caption{Number of backlogged bits associated with each user for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}.}
-		\renewcommand{\arraystretch}{1.25} \scriptsize
-		\begin{tabular}{|c|*{8}{c}|c|}
-			\hline
-			\multirow{2}{*}{\me{q}} & \multicolumn{8}{c|}{user indices} & \multirow{2}{*}{\me{\chi}} \\
-			\cline{2-9}
-			& 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & \\
-			\hline
-			\hline
-			\me{1} & 15.0 & 3.95 & 5.26 & 8.95 & 7.0 & 11.9 & 12.0 & 9.7 & 25.15 \\
-			\me{2} & 11.2 & 3.9 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.9 & 27.77 \\
-			\me{\infty} & 11.4 & 4.4 & 10.4 & 10.4 & 10.4 & 8.4 &  8.4 &  6.4 & 28.68 \\
-			\hline
-			\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\
-			\cline{1-9}
-		\end{tabular}
-		\label{tbl-3}
-	\end{table}	
-\end{frame}
-
-\subsubsection{KKT Based Approach}
-
-\begin{frame}{Performance Comparison with Number of Residual Packets}
+\begin{frame}{Performance of KKT based Approach}
 	\begin{figure}
@@
 
-\begin{frame}{Average Residual Packets after each Transmission Slot}
+\begin{frame}{Time Correlated Fading Performance}
 	\begin{figure}

### 2015-09-02 Presentation/markku_reduced.tex
presentation

@@
 \title{Traffic Aware Precoder Design for Space Frequency Resource Allocation}
-\author{{Ganesh Venkatraman, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti\eqn{^\dagger}} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}
+\author{{Ganesh Venkatraman\eqn{^\dagger}, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}
 
@@
 \item Spatial and Frequency resources are exploited to empty the packets waiting at the \acp{BS}
-\item In this work, we discuss precoder designs for \acl{MU} \acs{MIMO}-\acs{OFDM} setup to minimize the number of queued packets 
+\item We discuss precoder designs for \acl{MU} \acs{MIMO}-\acs{OFDM} setup to minimize the number of queued packets 
 \end{itemize}
@@
 \item Let \me{\mc{B}} and \me{\mc{U}} denote the set of coordinating \acp{BS} and users in the system
-\item The set of users belonging to \acs{BS} \me{b} is denoted by \me{\mc{U}_b \in \mc{U}}
-\item Let \me{b_k \in \mathcal{B}} denotes the \ac{BS} serving the user \me{k}
 \item Let \me{L} be the total available spatial streams for a user \me{k}, given by \me{\min (N_T,N_R)}
@@
 \begin{itemize}
-\item Available spatial and frequency resources are to be efficiently utilized to minimize the queued packets
 \item {\color{red}Objective} - to minimize the number of backlogged packets waiting at \acp{BS}
@@
 \begin{itemize}
-\item \acs{Q-WSRM} formulation is the result of minimizing the conditional Lyapunov drift\eqn{^\dagger}
-\item \acs{Q-WSRM} formulation is also called as back pressure algorithm, since it acts greedily in minimizing the backlogged packets at each instant
+\item \acs{Q-WSRM} formulation is the result of \textcolor{blue}{minimizing the conditional Lyapunov drift}\eqn{^\dagger}
+\item \acs{Q-WSRM} formulation is also called as \alert{back pressure algorithm}, since it acts greedily in minimizing the backlogged packets at each instant
 \[ \underset{t_{l,k,n}}{\text{minimize}} \quad \sum_{k \in \mc{U}} \left \lbrace Q_k(i)^2 - Q_k(i-1)^2 \right \rbrace, \]
-\item where \me{Q_k} follows the dynamic Queue expression in \eqref{eqn-2a} and \me{t_k = \sum_{n = 1}^N \, \sum_{l=1}^L \, t_{l,k,n}}
+\item where \me{Q_k} follows the dynamic Queue expression in \eqref{eqn-2a}
 \end{itemize}
@@
 
-\begin{frame}{Queue-Weighted Sum Rate Maximization (\acs{Q-WSRM})}
-	\begin{itemize}
-		\item Complexity can be reduced if precoders are designed for each sub-channel independently
-		\item Coupling across sub-channels is obtained by the queues, which are updated after evaluating the rate from previously chosen sub-channels as
-	\end{itemize}
-	\begin{equation*}
-	Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
-	\end{equation*}
-\end{frame}
-
 \subsection{\acs{JSFRA} Formulation (\acs{SINR} Relaxation)}
@@
 \begin{itemize}
-\item Precoders are designed by a centralized controller, which are then used by all \acp{BS} in \me{\mc{B}}
+\item Centralized Design - precoders are designed by a controller, which are then used by all \acp{BS} in \me{\mc{B}}
 \item The objective used to design transmit precoders is 
@@
 	\begin{itemize}
-	\item \me{\ell_{q=1}} results in greedy allocation
-	\item \me{\ell_{q=2}} ideal for the delay or buffer size limited scenarios
-	\item \me{\ell_{q=\infty}} provides fair resource allocation in each transmission instant
+	\item \me{\ell_{q=1}} \alert{results in greedy allocation}
+	\item \me{\ell_{q=2}} \alert{ideal for the delay or buffer size limited scenarios}
+	\item \me{\ell_{q=\infty}} \alert{provides fair resource allocation in each transmission instant}
 	\end{itemize}
@@
 \item Optimization problem with queue difference objective is nonconvex due to the constraint
-\begin{equation}  \scriptsize
-\alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2 }
-\end{equation}
-\item The nonconvex constraints are approximated by sequence of convex subsets and solved iteratively
-\item Convergence of the iterative algorithm is guaranteed
+\begin{subequations}  \scriptsize
+\begin{align}
+\underset{\mvec{m}{l,k,n}}{\text{minimize}} & \qquad \left | Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log \left (1 + \gamma_{l,k,n} \right) \right |^q \\
+\text{subject to} & \qquad \alert{\gamma_{l,k,n} \leq \dfrac{\left |\mvec{w}{l,k,n}^H \, \mvec{H}{b_k,k,n} \, \mvec{m}{l,k,n} \right |}{\beta_{l,k,n}}^2 } \\
+& \qquad \enoise + \sum_{(j,i) \neq (l,k)} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n}
+\end{align}
+\end{subequations}
+\item The nonconvex constraints are approximated by sequence of convex subsets and solved iteratively by \alert{\ac{SCA} method}
 \item Receive beamformers are designed by the \acs{MMSE} receivers using the converged transmit precoders
@@
 	\begin{itemize}
-	\item Alternatively, we solve the queue minimization problem by utilizing the relation between the \acs{MSE} and the \acs{SINR} as \me{\color{blue} \epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}}
-	\item Equivalence is valid only when the receivers are designed with the \ac{MSE} objective, \textit{i.e.}, using \acs{MMSE} receivers
-	\begin{eqnarray} \label{mse-error} \scriptsize
-	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \big | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \big |^2 \nonumber \\
-	+ \sum_{{(j,i) \neq (l,k)}} \big | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \big |^2 + \enoise = \epsilon_{l,k,n}
+	\item Alternatively, we solve the queue minimization problem by utilizing the relation between the \acs{MSE} and the \acs{SINR} as 
+	\begin{eqnarray}
+	\color{blue} \epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}
 	\end{eqnarray}
+	\item Equivalence is valid only when the receivers are designed with the \ac{MSE} objective, \textit{i.e.}, \textcolor{blue}{using \acs{MMSE} receivers}
 	\item Problem involves nonconvex constraint 
-	\begin{equation}
-	\alert{t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n})}
-	\end{equation}
+	\begin{subeqnarray}
+	\color{red}{t_{l,k,n}} &\alert{\leq}& \alert{-\log_2(\epsilon_{l,k,n})} \\
+	\epsilon_{l,k,n} &=& \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \big | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \big |^2 \nonumber \\
+	&\quad& + \sum_{{(j,i) \neq (l,k)}} \big | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \big |^2 + \enoise
+	\end{subeqnarray}
 	\end{itemize}
@@
 	\begin{itemize}
-		\item The nonconvex constraint is approximated by a sequence of convex constraints
-		\item It is achieved by using \ac{SCA} technique
-		\item The iterative procedure is performed until convergence or for suitable number of iterations
+		\item The nonconvex constraint is approximated by a sequence of convex constraints, which is performed using \ac{SCA} technique
+		\item The iterative procedure is carried out until convergence or for suitable number of iterations
 		\item \alert{The above reformulation works only with the \acs{MMSE} receiver}
@@
 	\begin{itemize}
-		\item Small System - centralized approach is viable, provided channel remains constant for multiple transmission slots
+		\item \alert{Small System - centralized approach is viable}, provided channel remains constant for multiple transmission slots
 		\item However, overhead involved in the centralized design scales up significantly as the network size grows
 		\item Distributed approaches based on primal decomposition or \acs{ADMM} can be used to reduce the signaling requirements
-		\item Overhead involved in the design of precoders are only scalar interference variables
-		\item Only convex approximated subproblem in each \acs{SCA} step is performed via distributed approaches
+		\item Signaling involved in the design of precoders are only \alert{scalar interference variables}
+		\item Approximated convex subproblem in each \acs{SCA} step is performed via distributed methods
 	\end{itemize}
@@
 		\item Precoder design is based on master-slave approach
-		\item Interference to the neighboring \ac{BS} users are bounded by a scalar variable
+		\item Interference to the neighboring \ac{BS} users are \alert{bounded by a scalar variable, treated as a constant in subproblems}
 		\item The interference thresholds are determined by the master problem and used in each slave subproblem constraint as
@@
 		in objective, where \eqn{\mbfa{\zeta}^{(j)}_b} is global consensus variable
-		\item \eqn{\zeta_{l,k,n,b}} in \eqref{inter_exp} is treated as an optimization variable in \ac{ADMM}
-		\item The consensus variables are updated as
-		\begin{equation} \scriptsize
-		\mbfa{\zeta}_{b_k}(b)^{(j+1)} = \mbfa{\zeta}_{b}(b_k)^{(j+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}
-		\end{equation}
-		\item where \eqn{\mbfa{\zeta}_{b_k}(b)} denotes the entries corresponding to \ac{BS} \eqn{b} in \ac{BS} \eqn{b_k}
+		\item \eqn{\zeta_{l,k,n,b}} in \eqref{inter_exp} is \alert{treated as an optimization variable in \ac{ADMM}}
+		\item Consensus variables are updated upon exchanging corresponding local \eqn{\zeta_{l,k,n,b}}'s among coordinating \acp{BS}
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Decentralization methods considered so far involve considerable signaling exchanges via backhaul
-		\item Since the overhead involved is large for multi-antenna receivers, the iterative design should reduce the backlogged packets significantly in first few iterations
-		\item To achieve that, we design an iterative procedure by solving the \ac{KKT} equations of the \acs{JSFRA} problem via \acs{MSE} reformulation
-		\item Group update of all the involved optimization variables is carried out to speed up the convergence of precoder design
+		\item Decentralization methods involve significant signaling exchanges via backhaul
+		\item \alert{Overhead is large for multi-antenna receivers} - iterative design should reduce the backlogged packets significantly in first few iterations
+		\item To achieve that, we design precoders by solving the \ac{KKT} equations of the \acs{JSFRA} problem via \acs{MSE} reformulation
+		\item \alert{Group update of all involved optimization variables} - to speed up the convergence of precoder design
 	\end{itemize}
@@
 \begin{itemize}
-\item We discussed the problem of wireless resource allocation to minimize backlogged packets in an efficient way
-\item The proposed approach uses \ac{SCA} method by using linear approximation for the nonconvex constraint
-\item We also addressed different distributed methods for the precoder design across each \acsp{BS} with minimal information exchange
-\item An iterative algorithm for the \acs{JSFRA} scheme using \acs{MSE} reformulation is also studied
+\item We studied cross layer problem of designing transmit and receive beamformers based on the number of residual packets
+\item Since the problem is nonconvex, we solve the problem iteratively by solving convex subproblems in each iteration
+\item We also proposed a practical way of implementing the precoder design in a distributed manner by solving the \ac{KKT} expressions
+\item Extensions of the proposed work in time-correlated fading scenario with limited number of information exchange cycle is in progress
 \end{itemize}

### 2015-10-20 Report/convergence_centralized.tex
updated convergence proof

@@
 The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm.
-Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function and the corresponding arguments namely, the transmit and the receive precoders to a stationary point \cite{meyer1976sufficient}.
-Assuming the conditions (a), (b) and (c) are satisfied, using \cite[Th.
+Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function by enforcing unique transmit precoders and receive beamformer in each step of the iterative algorithm.
+Assuming conditions (a), (b) and (c) are satisfied, using \cite[Th.
 3.14]{rudin1964principles}, we can show that the bounded and strictly decreasing objective sequence has a unique minimum in the feasible set.
-Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that the limit point of the iterative algorithm is indeed a stationary point of the nonconvex problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that \reviewF{every limit point of a convergent subsequence is a stationary point of the nonconvex problem} in \eqref{eqn-6} and \eqref{eqn-mse-1}, since the compact feasible set can have multiple limit points \cite{bertsekas1999nonlinear}.
 
@@
 Since it involves two nested iterations, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}.
-Let \me{\iter{\mx}{\ast}{i}} be the value of \me{\mx} when \ac{SCA} converges in the \me{\ith{i}} \ac{AO} step and let \me{\iter{\mz}{\ast|\my}{i}} be the solution for \me{\mz} in the \me{\ith{i}} \ac{AO} step for fixed \me{\my}.
-The stacked transmit precoders of all users in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} is given by \eqn{\mx_k^{(i)}}.
+Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k|\my}{i}} be a solution for stacked \me{\mx} and \me{\gamma} obtained in the \eqn{\ith{k}} \ac{SCA} step and in the \eqn{\ith{i}} \ac{AO} step for fixed \me{\my}.
+Let \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} be a solution obtained for \me{\mx} and \me{\gamma} when the objective sequence converges in \eqn{\ith{i}} \ac{AO} step.
 
-\subsection{Bounded Objective Function and Compact Feasible Set}
+\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
 The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
@@
 \subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
-The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
-However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set.
+%The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
+However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set.
 Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers.
@@
 \begin{IEEEeqnarray}{rCl} \neqsub
-	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
-	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+	\hat{f}(\mbf{x}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
+	f(\mbf{x}) &=& \hat{f}(\mbf{x}) + {\tau}_k^{(i)} \, \| \mbf{x} - \mbf{x}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
 \end{IEEEeqnarray}
-where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\ast}{i-1},\mz]} or \eqn{[\iter{\mx}{\ast}{i},\my,\mz]} depending on the problem.
+where \eqn{\mbf{x}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{x}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step.
 The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, as shown in \cite{scutari-1}.
-Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, the uniqueness of the minimizer can be guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}.
-The quadratic term in \eqref{mod_obj} includes the earlier solution \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} in the objective of \eqref{con-m}, obtained by solving \eqref{eqn-9} or \eqref{eqn-mse-2} in the \eqn{\ith{(k-1)}} \ac{SCA} step.}
+Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, uniqueness of the minimizer is guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}}.
 
@@
 \subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
-\review{In the forthcoming discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness property.
-Note that the modified objective \eqn{f} is equivalent to \eqn{\hat{f}} upon convergence, \textit{i.e.}, when the solution is a limit point.
-Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the original objective \eqref{eqn-6.1} as \eqref{mod_obj}.}
+\review{In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness of the minimizer and upon convergence of the objective, \eqn{f} is equal to \eqn{\hat{f}}.
+Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.}
 
-To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\ast}{i-1}}.
+To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\lpoint}{i-1}}.
 In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
@@
 \begin{equation}\label{con-relax}
-\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
 \end{equation}}{
 \begin{multline} \label{con-relax}
-\hat{g}_o(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
 \end{multline}}
-Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\ast}{i-1}} and \me{\iter{\mx}{k}{i}}.
-Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\ast}{i}} and \me{\iter{\my}{k}{i}}.
+Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\lpoint}{i-1}} and \me{\iter{\mx}{k}{i}}.
+Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\my}{k}{i}}.
 Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
 \begin{IEEEeqnarray}{rCl} \label{con-m} \neqsub
-	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\ast}{i-1},\mz) \eqsub \label{con-obj-m} \\
-	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
-	&\quad& g_1(\mx,\iter{\my}{\ast}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \label{con-cvx-blk-m}
+	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\lpoint}{i-1},\mz) \eqsub \label{con-obj-m} \\
+	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
+	&\quad& g_1(\mx,\iter{\my}{\lpoint}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \label{con-cvx-blk-m}
 \end{IEEEeqnarray}
@@
 \begin{equation}\label{con-sub-set}\allowdisplaybreaks
-h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0. 
 \end{equation}}{
 \begin{multline}\label{con-sub-set}\allowdisplaybreaks
-h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}) \leq \\
-h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1};\iter{\mx}{k}{i}) \leq 0. 
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}) \leq \\
+h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0. 
 \end{multline}}
-Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\ast}{i-1}} was chosen to be feasible from the \me{\ith{(i-1)}} \ac{AO} iteration.
-In each \ac{SCA} step, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,amir}
+Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\lpoint}{i-1}} was chosen to be feasible from the \me{\ith{(i-1)}} \ac{AO} iteration.
+In each \ac{SCA} step, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,amir}
 \iftoggle{single_column}{
 \begin{equation} \label{con-convergence}
-f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
+f(\iter{\mx}{0}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}) \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
 \end{equation}}{
 \begin{multline} \label{con-convergence} \allowdisplaybreaks
-f(\iter{\mx}{0}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
+f(\iter{\mx}{0}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
 \end{multline}}
-Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing.
-\review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique.
+Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing.
+%\review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique.
 Now, by using the fact that the objective sequence is nonincreasing and the uniqueness of the minimizer in each convex subproblem \eqref{con-m}, we can ensure that the sequence of iterates generated by the iterative \ac{SCA} approach converges to a unique limit point in each \ac{AO} step \eqn{{i}}}.
-	%However, note that the limit point need not be a stationary point of \eqref{con}, since the receive equalizers \eqn{\my} have been fixed.}
-
-% and approaches limit point of the \ac{SCA} as \me{k \rightarrow \infty}.
-The equality in \eqref{con-convergence} is achieved upon the \ac{SCA} convergence.
-The limit point obtained in the \eqn{\ith{i}} \ac{AO} step need not to be a stationary point of \eqref{con}, since it is the minimizer in \me{\iter{\mc{X}}{\ast}{i}} only.
-\review{Note that for a fixed initial operating point of the iterative \ac{SCA} procedure, the minimizer in each \ac{SCA} step is unique and so the limit point due to the strong convexity of the modified objective \eqref{mod_obj}.}
-
-%\review{Since the objective is strongly convex, due to the quadratic term in \eqref{mod_obj}, the minimizer \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\}} in each \ac{SCA} step is unique.}
-
-Once \me{\iter{\mx}{\ast}{i}} is found for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}.
-However, after fixing \me{\mx} as \me{\iter{\mx}{\ast}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}.
-Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\ast}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively.
-Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
-The sequence convergence and the nonincreasing behavior of the objective follow similar arguments as above.
-\footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The limit point of the sequence of iterates generated by iteratively solving \eqref{con-m} is given by \me{\{\iter{\mx}{\ast}{i}, \iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}\} \in \iter{\mc{Y}}{\ast}{i} \subset \mc{F}}.
-
-Finally, to prove the global convergence of the iterative algorithm, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
-\iftoggle{single_column}{
-\begin{equation}
-f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
-\end{equation}}{
-\begin{equation}
-f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}).
-\end{equation}}
-Let \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mz}{\ast|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\ast}{i-1}}.
-To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}.
-Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by the equality in \eqref{con-sub-set}.
-Using this, we can show the monotonicity of the objective as
-\begin{equation} \label{fixed_point}
-f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}).
-\end{equation}
-The \ac{AO} update follows \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\my}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
-
-\review{Using the above discussions, the monotonicity of the objective sequence is guaranteed in each \ac{AO} and \ac{SCA} updates.
-However, to ensure the strict monotonicity, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}.
-Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step.
+\review{However, to ensure strict monotonicity of the objective sequence, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}.
+Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step.
 At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
@@
 since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
-Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}.
+Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
 Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
-However, if \eqn{\hat{f}} is used instead of \eqn{f} as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple minimizers in each convex subproblem.
+Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of the objective sequence in each \ac{AO} step \eqn{{i}}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the unique solution obtained upon the convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}
 
-Similarly, we can also guarantee strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update.
-It follows from that fact that \eqn{\iter{\mbf{z}}{\ast}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} iteration unless the sequence \eqn{\{\mbf{z}_{\ast}^{i}\}} converges to a limit point as \eqn{i \rightarrow \infty}.}
+Once \me{\iter{\mx}{\lpoint}{i}} is obtained for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}.
+However, after fixing \me{\mx} as \me{\iter{\mx}{\lpoint}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}.
+Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\lpoint}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively.
+Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
+The convergence and the nonincreasing behavior of the objective follow similar arguments as above.
+\footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The solution obtained by solving \eqref{con-m} iteratively until convergence of the objective value is given as \me{\{\iter{\mx}{\lpoint}{i}, \iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}\} \in \iter{\mc{Y}}{\lpoint}{i} \subset \mc{F}}.
+
+Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
+\iftoggle{single_column}{
+\begin{equation}
+f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+\end{equation}}{
+\begin{equation}
+f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+\end{equation}}
+Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}.
+To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}.
+Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by the equality in \eqref{con-sub-set}.
+Using this, we can show the monotonicity of the objective as
+\begin{equation} \label{fixed_point}
+f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}).
+\end{equation}
+The \ac{AO} update follows \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
+
+\review{Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured.
+It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.}
 \begin{comment}
@@
 However, by using the regularized objective in \eqref{mod_obj}, we can show that the sequence of objectives provided by \ac{AO} and \ac{SCA} steps is strictly decreasing.
-Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} \ac{SCA} step.
+Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} \ac{SCA} step.
 Note that the objective \eqref{con-obj-m} is strongly convex with some parameter \eqn{m > 0}, and therefore \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}
@@
 \end{IEEEeqnarray}
-Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}.
+Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
 Using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{s_ineq_g}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured.
@@
 	since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}.
-Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}} as \eqn{k \rightarrow \infty}.
+Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
 Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
@@
 
-{Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\ast}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{k-1}} \ac{SCA} step.
+{Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{k-1}} \ac{SCA} step.
 In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj}.
@@
 	\end{equation}
-	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\rightarrow\infty}, \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\ast}^{(i)}}.
+	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\rightarrow\infty}, \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}}.
 Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
-However, if \eqn{\hat{f}} is used in the objective of \eqref{con-m}, then the limit point is not unique, \textit{i.e.}, \eqn{\{\exists \mbf{z} \in \mc{X}_{\ast}^{(i)} \vert \hat{f}(\mbf{z}) = \hat{f}(\mbf{z}_{\ast}^{(i)})\}}, and therefore the sequence generated by \eqref{con-m} with \eqn{\hat{f}} is not strictly monotonic.
+However, if \eqn{\hat{f}} is used in the objective of \eqref{con-m}, then the limit point is not unique, \textit{i.e.}, \eqn{\{\exists \mbf{z} \in \mc{X}_{\lpoint}^{(i)} \vert \hat{f}(\mbf{z}) = \hat{f}(\mbf{z}_{\lpoint}^{(i)})\}}, and therefore the sequence generated by \eqref{con-m} with \eqn{\hat{f}} is not strictly monotonic.
 
 	Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration.
-Since the limit point \eqn{\{\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\ast}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}
+Since the limit point \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\lpoint}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}
 
@@
 \end{comment}
-\subsection{Convergence of the Beamformer Iterates} \label{c-b}
-Let \me{\ma^{(i)} \triangleq [\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
+
+\subsection{Stationarity of Limit Points} \label{c-b}
+
+In order to discuss the convergence of the sequence of iterates, let us define a global index \eqn{t}, which includes \ac{SCA} indexing \eqn{k} and \ac{AO} iteration count \eqn{i} corresponding to both transmit and receive beamformer updates.
+Using this global indexing, let us define \eqn{\ma^{t}} as a vector formed by stacking the solution obtained at the \eqn{\ith{k}} \ac{SCA} update of the \eqn{\ith{i}} \ac{AO} step as \eqn{[\iter{\mx}{k}{i},\iter{\my}{}{i-1},\iter{\mz}{k|\my}{i}]}.
+Note that for some other \eqn{t}, say, \eqn{t^\prime > t}, such that \eqn{\ma^{t^\prime} \triangleq [\iter{\mx}{}{i},\iter{\my}{k}{i},\iter{\mz}{k|\mx}{i}]}.
+Therefore, \eqn{\ma^t} corresponds to all solutions obtained by the algorithm in each iteration.
+
+Now, using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the whole sequence \eqn{\{{f}(\ma^t)\}} converges and \eqn{\forall t, \; \hat{f}(\ma^t) \leq f(\ma^t)}, and therefore \eqn{\hat{f}(\ma^t)} also converges.
+However, it is not the case with the sequence of iterates \eqn{\{\ma^t\}} generated by the algorithm, since there can be two different convergent subsequences, say, \eqn{\{\ma^{t_i} | i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} | k = 0,1,\dotsc\}}, such that
+\begin{equation}
+\lim_{t \rightarrow \infty} {f}(\ma^t) = \lim_{i \rightarrow \infty} {f}(\ma^{t_i}) = \lim_{k \rightarrow \infty} {f}(\ma^{t_k}).
+\end{equation}
+
+Due to the existence of multiple limit points, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
+Note that since the objective sequence \eqn{\{f(\ma^t)\}} converges to, say, \eqn{f(\bar{\ma})}, for some \eqn{\bar{\ma}}, then we show that \eqn{\bar{\ma}} is a stationary point.
+To show that, let us consider a subsequence \eqn{\{\ma^{t_j} | j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
+It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
+\begin{equation}
+f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}).
+\end{equation}
+Now, by taking the limit as \eqn{j \rightarrow \infty}, we obtain
+\begin{equation}
+f(\bar{\ma}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}})
+\end{equation}
+therefore, \eqn{\bar{\ma}} is a stationary point.
+The above discussion also includes the \ac{AO} step, since in between each \ac{AO} update, the objective sequence is strictly monotonic \eqref{fixed_point} \cite[Prop.
+2.7.1]{bertsekas1999nonlinear}.
+
+Now to show that \eqn{\bar{\ma}} is a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between the gradient of the subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}.
+In order to show that \eqn{\bar{\ma}} is a \ac{KKT} point for \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
+\begin{equation} \label{kkt_expr}
+	\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
+\end{equation}
+for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.
+
+To prove the feasibility of the limit point \me{\bar{\ma}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
+Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}} is regular as it satisfies the Slater's constraint qualifications.
+Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
+\begin{equation} \label{kkt_mod_expr}
+	\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
+\end{equation}
+The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since \eqn{\bar{\ma}} is a limit point of a convergent subsequence .
+Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfy \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
+(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\lpoint}} is given as
+\begin{equation} \label{rhs_equiv}
+	\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
+\end{equation}
+Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+By using \cite[Thms.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of problem \eqref{con}.}
+
+\begin{comment}
+However, it is not the case with the sequence of iterates \eqn{\{\iter{\ma}{k}{i}\}}, since there can be two different convergent subsequences that has the, say, \eqn{\{\iter{\ma}{k}{i}\}_{k,i \in \mc{Q}_1}} and \eqn{\{\iter{\ma}{k}{i}\}_{k,i \in \mc{Q}_2}} such that
+
+Let \me{\ma^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
 \begin{equation} \label{g-algo}
@@
 \begin{cases}
-\underset{\mx,\mz}{\mathrm{argmin}} \; f(\mx,\mz;\iter{\my}{\ast}{i-1})& \forall \mx,\mz \in \iter{\mc{X}}{\ast}{i} \\
-\underset{\my,\mz}{\mathrm{argmin}} \; f(\my,\mz;\iter{\mx}{\ast}{i})& \forall \my,\mz \in \iter{\mc{Y}}{\ast}{i} 
+\underset{\mx,\mz}{\mathrm{argmin}} \; f(\mx,\mz;\iter{\my}{\lpoint}{i-1})& \forall \mx,\mz \in \iter{\mc{X}}{\lpoint}{i} \\
+\underset{\my,\mz}{\mathrm{argmin}} \; f(\my,\mz;\iter{\mx}{\lpoint}{i})& \forall \my,\mz \in \iter{\mc{Y}}{\lpoint}{i} 
 \end{cases} 
@@
 Since the minimizer is unique, the mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
-In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\ast \subset \mc{F}} as the set of fixed points, \textit{i.e.}, \me{\forall {\ma}^{\ast} \in \mc{F}^\ast, \, {\ma}^{\ast} = \mc{A}({\ma}^{\ast})}, identified by the algorithm \me{\mc{A}} for different initialization points.
+In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\lpoint \subset \mc{F}} as the set of fixed points, \textit{i.e.}, \me{\forall {\ma}^{\lpoint} \in \mc{F}^\lpoint, \, {\ma}^{\lpoint} = \mc{A}({\ma}^{\lpoint})}, identified by the algorithm \me{\mc{A}} for different initialization points.
 
@@
 \item Objective function \me{f} should be bounded and continuous.
-\item Feasible set \me{\iter{\mc{X}}{\ast}{i},\iter{\mc{Y}}{\ast}{i}} in each step should be compact.
+\item Feasible set \me{\iter{\mc{X}}{\lpoint}{i},\iter{\mc{Y}}{\lpoint}{i}} in each step should be compact.
 \item The sequence \me{\{\iterate{\ma}{i}\}} generated by \me{\mc{A}} should be strictly monotonic with respect to the objective \me{f}, \textit{i.e.}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
@@
 Using \cite{zangwill1969nonlinear} and \cite[Th.
-3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point, and (iii) \eqn{\ma^\ast} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
-Even though the fixed points in the set \me{\mc{F}^\ast} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e.}, \me{\mc{F}^\ast = \{\ma^\ast\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
+3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point, and (iii) \eqn{\ma^\lpoint} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
+Even though the fixed points in the set \me{\mc{F}^\lpoint} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e.}, \me{\mc{F}^\lpoint = \{\ma^\lpoint\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
 
@@
 and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e.}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
-The set of accumulation or the limit points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\ast} and the objective function be \me{f} is closed and continuous.
+The set of accumulation or the limit points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\lpoint} and the objective function be \me{f} is closed and continuous.
 Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
@@
 \item[(i)] all accumulation points will be a fixed point,
-\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\ast)}, where \eqn{\ma^\ast} is a fixed point,
-\item[(iii)] \eqn{\ma^\ast} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
+\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point,
+\item[(iii)] \eqn{\ma^\lpoint} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
 \end{itemize}
@@
 where \me{\mc{A}(\iterate{\ma}{i})} denotes the set of iterates in the subset \me{\iterate{\mc{X}}{i}}, which has the same objective value under the mapping \me{f} in the \me{\ith{i}} iteration The monotonicity of the proposed algorithm is guaranteed based on the arguments presented in Appendix \ref{mcity}.
-The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e.}, \me{\ma \notin \mc{F}^\ast}, as in \eqref{fixed_point}.
-Using the above discussions, we can show that the sequence \me{\{\iterate{\ma}{i}\}} converges to a fixed point in the set \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}
+The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e.}, \me{\ma \notin \mc{F}^\lpoint}, as in \eqref{fixed_point}.
+Using the above discussions, we can show that the sequence \me{\{\iterate{\ma}{i}\}} converges to a fixed point in the set \me{\mc{F}^\lpoint} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}
 
-The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed points \me{\mc{F}^\ast} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
+The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed points \me{\mc{F}^\lpoint} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
 
-To show the set of fixed points \me{\mc{F}^\ast} are the minimizers for the objective function \me{f}, we rely on the strict monotonicity of the objective function for each iteration.
-Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\ma^\ast \in \mc{A}(\ma^\ast)}, which is a generalized fixed point.
-Therefore, the fixed points in \me{\mc{F}^\ast} are the minimizers for the objective function \me{f} over the set \me{\mc{F}}.
+To show the set of fixed points \me{\mc{F}^\lpoint} are the minimizers for the objective function \me{f}, we rely on the strict monotonicity of the objective function for each iteration.
+Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\ma^\lpoint \in \mc{A}(\ma^\lpoint)}, which is a generalized fixed point.
+Therefore, the fixed points in \me{\mc{F}^\lpoint} are the minimizers for the objective function \me{f} over the set \me{\mc{F}}.
 
@@
 The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}.
-Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\ast} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.
+Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\lpoint} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.
 \end{comment}
 
-\subsection{Stationary Points of the Nonconvex Problem}
-\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\ast}} as \eqn{i \rightarrow \infty}.
-Now, to show that \eqn{\ma^{\ast}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} gradient condition of \eqref{con}, \textit{i.e.},
+\begin{comment}
+%\subsection{Stationary Points of the Nonconvex Problem}
+\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\lpoint}} as \eqn{i \rightarrow \infty}.
+Now, to show that \eqn{\ma^{\lpoint}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} gradient condition of \eqref{con}, \textit{i.e.},
 \begin{equation} \label{kkt_expr}
-\textstyle	\nabla \hat{f}(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla {g}_0(\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0
+\textstyle	\nabla \hat{f}(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla {g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
 \end{equation}
-for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\ma^{\ast} \in \mc{F}}.
+for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\ma^{\lpoint} \in \mc{F}}.
 
-To prove the feasibility of the limit point \me{\ma^{\ast}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
-Therefore, the limit point \eqn{\ma^{\ast} \in \mc{F}} and it satisfies the Slater's constraint qualifications.
-Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\ast}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}.
+To prove the feasibility of the limit point \me{\ma^{\lpoint}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
+Therefore, the limit point \eqn{\ma^{\lpoint} \in \mc{F}} and it satisfies the Slater's constraint qualifications.
+Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\lpoint}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}.
 Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
 \begin{equation} \label{kkt_mod_expr}
-\textstyle \nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
+\textstyle \nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
 \end{equation}
-The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\ast}}, since \eqn{\ma^{\ast}} is the fixed point of \eqn{\mc{A}}.
-Therefore, the gradient evaluated at \eqn{\ma^{\ast}} satisfy \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})}.
-(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\ast}} is given as
+The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\lpoint}}, since \eqn{\ma^{\lpoint}} is the fixed point of \eqn{\mc{A}}.
+Therefore, the gradient evaluated at \eqn{\ma^{\lpoint}} satisfy \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})}.
+(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\lpoint}} is given as
 \begin{equation} \label{rhs_equiv}
-\nabla h(\ma^{\ast}) - \nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla h(\ma^{\ast}) - \nabla g_o(\mbf{\ma}^{\ast}).
+\nabla h(\ma^{\lpoint}) - \nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\mbf{\ma}^{\lpoint}) = \nabla h(\ma^{\lpoint}) - \nabla g_o(\mbf{\ma}^{\lpoint}).
 \end{equation}
-Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\ast}) = \nabla \hat{f}(\ma^{\ast})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\ast}} satisfies \eqref{kkt_expr}.
+Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\lpoint}} satisfies \eqref{kkt_expr}.
 By using \cite[Thms.
@@
 3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the problem in \eqref{con}.}
+\end{comment}
+\begin{comment}
+In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
+In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
+Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\lpoint^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\lpoint}} satisfies the constraint qualifications of the problem \eqref{con}.
 
-\begin{comment}
-In this section, we show that the limit point \eqn{\ma^{\ast}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
-In order for \eqn{\ma^{\ast}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
-Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\ast^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\ast}} satisfies the constraint qualifications of the problem \eqref{con}.
-
-To show that the limit point \eqn{\mbf{\ma}^{\ast}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\ast}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
+To show that the limit point \eqn{\mbf{\ma}^{\lpoint}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\lpoint}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
 Therefore, it satisfies the \ac{KKT} conditions of the convex subproblem for some Lagrange multipliers \eqn{\mu_i \geq 0} as
 \begin{equation} \label{kkt_expr}
-\textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
+\textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
 \end{equation}
 It is evident that the modified objective \eqn{f} and the convex function \eqn{\hat{f}} in \eqref{mod_obj} are equal at the limit point due to the vanishing quadratic penalty term.
-Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\ast};\mbf{\ma}^{\ast}) = \nabla g_o(\mbf{\ma}^{\ast})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\ast}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
+Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\mbf{\ma}^{\lpoint}) = \nabla g_o(\mbf{\ma}^{\lpoint})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\lpoint}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
 Now, by using \cite[Th.
@@
 
-\review{Let \eqn{\ma^{\ast}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}.
-The limit point \eqn{\ma^\ast} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions.
+\review{Let \eqn{\ma^{\lpoint}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}.
+The limit point \eqn{\ma^\lpoint} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions.
 %and there exists no descent direction in the feasible set as
 %\begin{equation}
-%\nabla {f}(\ma^{\ast})^\tran \, (\ma - \ma^{\ast}) \geq 0, \: \forall \, \ma \in \mc{Y}^{\ast}
+%\nabla {f}(\ma^{\lpoint})^\tran \, (\ma - \ma^{\lpoint}) \geq 0, \: \forall \, \ma \in \mc{Y}^{\lpoint}
 %\end{equation}
-%where \eqn{\mc{Y}^{\ast}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\ast}^{i}} as \eqn{i \rightarrow \infty}. 
+%where \eqn{\mc{Y}^{\lpoint}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\lpoint}^{i}} as \eqn{i \rightarrow \infty}. 
 Let us consider the problem in \eqref{con-m}.
-Using \eqref{con-relax}, we can show that the feasible set \eqn{\mc{Y}_{\ast}^{i}} in each \ac{AO} iteration \eqn{i} is a subset of \eqn{\mc{F}}.
+Using \eqref{con-relax}, we can show that the feasible set \eqn{\mc{Y}_{\lpoint}^{i}} in each \ac{AO} iteration \eqn{i} is a subset of \eqn{\mc{F}}.
 Therefore, all iterates \eqn{\{\iterate{\ma}{i}\}} of the algorithm \eqn{\mc{A}} are feasible.
@@
 
-Now, it remains to show that the \eqn{\ma^{\ast}} is a stationary point of the nonconvex problem \eqref{con}.
-To see this, we note that \eqn{\ma^{\ast}} must satisfy the \ac{KKT} conditions of \eqref{con}.
-Since \eqn{\ma^{\ast}} is the fixed point of the algorithm \eqn{\mc{A}}, it satisfies the \ac{KKT} conditions of the convex subproblem \eqref{con-m} given by
+Now, it remains to show that the \eqn{\ma^{\lpoint}} is a stationary point of the nonconvex problem \eqref{con}.
+To see this, we note that \eqn{\ma^{\lpoint}} must satisfy the \ac{KKT} conditions of \eqref{con}.
+Since \eqn{\ma^{\lpoint}} is the fixed point of the algorithm \eqn{\mc{A}}, it satisfies the \ac{KKT} conditions of the convex subproblem \eqref{con-m} given by
 \begin{equation} \label{kkt_expr}
-\textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0
+\textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
 \end{equation}
 for some Lagrange multipliers \eqn{\mu_i \geq 0}.
-Using the equivalence between \eqn{\hat{f}(\ma^{\ast}) = f(\ma^{\ast})} and the relation in \eqref{con-relax} in \eqref{kkt_expr}, we can see that \eqref{kkt_expr} is indeed the \ac{KKT} condition for the nonconvex problem \eqref{con}.
+Using the equivalence between \eqn{\hat{f}(\ma^{\lpoint}) = f(\ma^{\lpoint})} and the relation in \eqref{con-relax} in \eqref{kkt_expr}, we can see that \eqref{kkt_expr} is indeed the \ac{KKT} condition for the nonconvex problem \eqref{con}.
 Since the gradient is zero in \eqref{kkt_expr}, the objective cannot be decreased any further.
@@
 2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that the limit points \eqn{\ma^\ast} of \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.}
+3.2]{amir}, we can show that the limit points \eqn{\ma^\lpoint} of \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.}
 
-%In order for \eqn{\ma^{\ast}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}.
+%In order for \eqn{\ma^{\lpoint}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}.
 In each iteration, the algorithm \eqn{\mc{A}} in \eqref{g-algo} finds a point \eqn{\iterate{\ma}{i} \in \mc{F}} with \eqn{f(\iterate{\ma}{i}) < f(\iterate{\ma}{i-1})}, therefore, it satisfies all the constraints of \eqref{con}.
-Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \rightarrow \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\ast}) = \ma^{\ast}} finds a unique \eqn{\ma^{\ast} \in \mc{F}^{\ast}} due to the strong convexity of \eqn{f}.
+Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \rightarrow \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\lpoint}) = \ma^{\lpoint}} finds a unique \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}} due to the strong convexity of \eqn{f}.
 
-%To show the equivalence in the gradients of \eqref{con} and \eqref{con-m} at \eqn{\ma^{\ast}}, let us consider the limit point of the \ac{SCA} update in \eqn{\mc{A}} as it converges to a fixed point \eqn{\ma^{\ast} \in \mc{F}^{\ast}}.
+%To show the equivalence in the gradients of \eqref{con} and \eqref{con-m} at \eqn{\ma^{\lpoint}}, let us consider the limit point of the \ac{SCA} update in \eqn{\mc{A}} as it converges to a fixed point \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}}.
 The \ac{KKT} expression for the convex subproblem \eqref{con-cvx} is given by
 %\begin{equation} \label{kkt_expr}
-%\nabla f(\ma^{\ast}) + \mu_1 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0
+%\nabla f(\ma^{\lpoint}) + \mu_1 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
 %\end{equation}
@@
 Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}.
-Moreover, \eqn{\ma^{\ast}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}.
+Moreover, \eqn{\ma^{\lpoint}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}.
 Now, with the above conditions and by using \cite[Th.
@@
 \begin{equation} \label{con-opt}\allowdisplaybreaks
-f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) = 
-f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
+f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|x}{i}) = f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|y}{i+1}) = 
+f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1})
 \end{equation}}{
 \begin{multline} \label{con-opt}\allowdisplaybreaks
-f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) = f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i},\iter{\mz}{\ast|y}{i+1}) \\ = 
-f(\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1})
+f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|x}{i}) = f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|y}{i+1}) \\ = 
+f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1})
 \end{multline}}
-where \me{\{\iter{\mx}{\ast}{i+1},\iter{\my}{\ast}{i+1},\iter{\mz}{\ast|x}{i+1}\} \in \mc{F}^\ast} is a limit point of \me{\mc{A}} for a given initial point.
+where \me{\{\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1}\} \in \mc{F}^\lpoint} is a limit point of \me{\mc{A}} for a given initial point.
 Since the function \eqn{f} is strongly convex, the limit point is unique.
@@
 
- In this section, we show that the limit point \eqn{\ma^{\ast}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
-In order for \eqn{\ma^{\ast}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
-Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\ast^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\ast}} satisfies the constraint qualifications of the problem \eqref{con}.
+ In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
+In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
+Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\lpoint^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\lpoint}} satisfies the constraint qualifications of the problem \eqref{con}.
 
- To show that the limit point \eqn{\mbf{\ma}^{\ast}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\ast}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
+ To show that the limit point \eqn{\mbf{\ma}^{\lpoint}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\lpoint}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
 Therefore, it satisfies the \ac{KKT} conditions of the convex subproblem for some Lagrange multipliers \eqn{\mu_i \geq 0} as
  \begin{equation} \label{kkt_expr}
- \textstyle	\nabla f(\ma^{\ast}) + \mu_0 \big [ \nabla h(\ma^{\ast}) - \nabla\hat{g}_0(\ma^{\ast};\ma^{\ast}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\ast}) = 0.
+ \textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
  \end{equation}
  It is evident that the modified objective \eqn{f} and the convex function \eqn{\hat{f}} in \eqref{mod_obj} are equal at the limit point due to the vanishing quadratic penalty term.
-Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\ast};\iterate{\ma}{\ast}) = \nabla g_o(\mbf{\ma}^{\ast})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\ast}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
+Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\iterate{\ma}{\lpoint}) = \nabla g_o(\mbf{\ma}^{\lpoint})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\lpoint}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
 Now, by using \cite[Th.

### 2015-10-20 Report/convergence_distributed.tex
updated convergence proof

@@
 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}.
-Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, then the limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}
+Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}}
 

### 2015-10-20 Report/dual_approach.tex
updated convergence proof

--- 2015-07-31 Report/dual_approach.tex
@@
 The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
-However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large to ensure strict monotonicity of the objective, then the convergence can be guaranteed (see Appendices \ref{sec-3.5} and \ref{sec-dist-conv}).
+However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, \reviewF{then the convergence discussions follows Appendices \ref{sec-3.5} and \ref{sec-dist-conv}}.
 Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured.

### 2015-10-20 Report/wsrm_formulation.tex
updated convergence proof

@@
 	&\quad& \beta_{l,k,n} \geq \enoise + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
-	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
+	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}. \IEEEyessubnumber \eqspace \label{eqn-6.4}
 \end{IEEEeqnarray}
@@
 Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution of \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step.
-Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\ast}, \mbfa{\beta}^{(i)}_{j} \}}.
-Note that \eqn{\mbf{w}^{(i-1)}_{\ast}} is the receiver, which is obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
+Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\lpointx}, \mbfa{\beta}^{(i)}_{j} \}}.
+Note that \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is the receiver, which is obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
 \begin{algorithm}
@@
 
-Upon convergence of the transmit precoders, the receivers are then updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\ast}} obtained from the previous \ac{SCA} step.
+Upon convergence of the objective sequence, the receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from the previous \ac{SCA} step.
 Once the receive beamformers are updated, the transmit precoders are again evaluated with the newly found receivers by solving \eqref{eqn-9} recursively or by using \eqref{eqn-10}.
@@
 Note that in all our numerical simulations, the objective sequence of Algorithm \ref{algo-1} converges.
-However, to show the convergence of the sequence of the beamformer iterates, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of the one in \eqref{eqn-6.1}.
+\reviewF{However, to discuss on the convergence of the beamformer iterates}, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of the one in \eqref{eqn-6.1}.
 Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.}
@@
 \end{subeqnarray}
-where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\ast(i)}}.
+where \me{\bar{f}(\mbf{x},\mbf{x}^{(i)})} is the approximate function of \me{f(\mbf{x})} around the point \me{\mbf{x}^{\lpointx(i)}}.
 The stationary point of the relaxed convex problem satisfies the \ac{KKT} conditions of the original nonconvex problem, which can be obtained by using conditions in \eqref{sca-req}.
@@
 At each \ac{SCA} iteration, the relaxed subproblem is solved for the locally optimal transmit precoders to minimize the objective function.
-Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point, \textit{i.e},  \me{\mbf{x}^{\ast(i-1)}} for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
+Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point, \textit{i.e},  \me{\mbf{x}^{\lpointx(i-1)}} for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well.
 Therefore, at each \ac{SCA} step, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.

### 2015-10-21 Report/convergence_centralized.tex
conv modified

@@
-To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we will show that the following conditions are satisfied by the centralized formulations.
-\begin{itemize}
-	\item[(a)] The function should be bounded below
-	\item[(b)] The feasible set should be a compact set
-	\item[(c)] The sequence of the objective values should be \review{strictly} decreasing in each iteration
-	\item[(d)] Uniqueness of the minimizer, \textit{i.e.}, the transmit and the receive beamformers should be unique in each iteration.
-\end{itemize}
-The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm.
-Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function by enforcing unique transmit precoders and receive beamformer in each step of the iterative algorithm.
-Assuming conditions (a), (b) and (c) are satisfied, using \cite[Th.
-3.14]{rudin1964principles}, we can show that the bounded and strictly decreasing objective sequence has a unique minimum in the feasible set.
-Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that \reviewF{every limit point of a convergent subsequence is a stationary point of the nonconvex problem} in \eqref{eqn-6} and \eqref{eqn-mse-1}, since the compact feasible set can have multiple limit points \cite{bertsekas1999nonlinear}.
-
-Before proceeding further, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
 \begin{IEEEeqnarray}{RcL} \label{con} \neqsub
@@
 \end{IEEEeqnarray}
-where \me{g_2}, \me{\hat{f}} are convex and \me{h} is a linear function.
-Let \me{g_0,g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not on both.
-The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}.
+where the functions \me{g_2} and \me{\hat{f}} are convex, and the function \me{h} is linear.
+Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly.
+The constraint \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} respectively.
 Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
@@
 
-To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}.
-However, after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}.
-To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,scutari-1} by relaxing \eqref{con-dc} by a sequence of convex subsets.
-Since it involves two nested iterations, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}.
-Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k|\my}{i}} be a solution for stacked \me{\mx} and \me{\gamma} obtained in the \eqn{\ith{k}} \ac{SCA} step and in the \eqn{\ith{i}} \ac{AO} step for fixed \me{\my}.
-Let \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} be a solution obtained for \me{\mx} and \me{\gamma} when the objective sequence converges in \eqn{\ith{i}} \ac{AO} step.
+Now, to show the convergence of the sequence of objective values generated by the centralized algorithm Algorithm \ref{algo-1} for the formulations \eqref{eqn-6} and \eqref{eqn-mse-1}, we require the following.
+\begin{itemize}
+	\item[(a)] Objective function should be bounded below
+	\item[(b)] Feasible set should be a compact
+	\item[(c)] Sequence of objective values should be strictly decreasing
+	\item[(d)] Uniqueness of the minimizer in each step.
+\end{itemize}
+The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}.
+However, to ensure strict monotonicity of the objective sequence, we need condition (d).
+Assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, we can ensure the convergence of objective sequence \cite[Th.
+3.14]{rudin1964principles}.
+Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates is a stationary point of the nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}, where iterates correspond to stacked vector of all optimization variables.
+
+Before proceeding further, we denote the representations used in the following proof with respect to Algorithm \ref{algo-1}.
+Since it involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
+Let \me{\mx}, \me{\my}, and \me{\mz} correspond to the stacked vector all transmit precoders, receive beamformers, and other optimization variables, such as \me{\beta_{l,k,n},\gamma_{l,k,n}} or \eqn{t_{l,k,n},\epsilon_{l,k,n}} respectively.
+Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k}{i}} be the solution obtained in \eqn{\ith{i}} \ac{AO} step of \eqn{\ith{k}} \ac{SCA} iteration for the optimization variables \me{\mx} and \me{\gamma} with fixed \me{\my}.
+%We denote \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} as the solution obtained for \me{\mx} and \me{\mz} when the sequence of objective values converges in \eqn{\ith{i}} \ac{AO} step for fixed \eqn{\my}.
+Similarly, \me{\iter{\my}{\lpointx}{i}} and \me{\iter{\mz}{|\mx}{i}} correspond to the solutions of \eqn{\my} and \eqn{\mz} in \eqn{\ith{i}} \ac{AO} update for fixed \eqn{\mx}.
 
@@
 Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
-Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of the objective sequence in each \ac{AO} step \eqn{{i}}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the unique solution obtained upon the convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}
+Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of the objective sequence in each \ac{AO} step \eqn{{i}}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon the convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}
 
@@
 It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.}
+
 \begin{comment}
@@
 
-In order to discuss the convergence of the sequence of iterates, let us define a global index \eqn{t}, which includes \ac{SCA} indexing \eqn{k} and \ac{AO} iteration count \eqn{i} corresponding to both transmit and receive beamformer updates.
-Using this global indexing, let us define \eqn{\ma^{t}} as a vector formed by stacking the solution obtained at the \eqn{\ith{k}} \ac{SCA} update of the \eqn{\ith{i}} \ac{AO} step as \eqn{[\iter{\mx}{k}{i},\iter{\my}{}{i-1},\iter{\mz}{k|\my}{i}]}.
-Note that for some other \eqn{t}, say, \eqn{t^\prime > t}, such that \eqn{\ma^{t^\prime} \triangleq [\iter{\mx}{}{i},\iter{\my}{k}{i},\iter{\mz}{k|\mx}{i}]}.
-Therefore, \eqn{\ma^t} corresponds to all solutions obtained by the algorithm in each iteration.
+In this section, we discuss the convergence of the sequence of iterates generated by the iterative algorithm.
+In order to do so, let us use single global index \eqn{t} to represent both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}.
+Using this, we can represent \eqn{\ma^{t} \triangleq [\iter{\mx}{k}{i},\iter{\my}{}{i-1},\iter{\mz}{k|\my}{i}]} as a stacked vector of solution obtained in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} update with fixed \eqn{\my}.
+The index \eqn{t} is used to represent both \ac{SCA} updates involving transmit and receive beamformers within each \ac{AO} step.
 
-Now, using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the whole sequence \eqn{\{{f}(\ma^t)\}} converges and \eqn{\forall t, \; \hat{f}(\ma^t) \leq f(\ma^t)}, and therefore \eqn{\hat{f}(\ma^t)} also converges.
-However, it is not the case with the sequence of iterates \eqn{\{\ma^t\}} generated by the algorithm, since there can be two different convergent subsequences, say, \eqn{\{\ma^{t_i} | i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} | k = 0,1,\dotsc\}}, such that
+Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
+Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.
+However, similar claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}, since there can be two different convergent subsequences of \eqn{\{\ma^t\}}, say, \eqn{\{\ma^{t_i} \, | \, i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} \, | \, k = 0,1,\dotsc\}}, such that
 \begin{equation}
-\lim_{t \rightarrow \infty} {f}(\ma^t) = \lim_{i \rightarrow \infty} {f}(\ma^{t_i}) = \lim_{k \rightarrow \infty} {f}(\ma^{t_k}).
+\lim_{t \rightarrow \infty} {f}(\ma^t) = \lim_{i \rightarrow \infty} {f}(\ma^{t_i}) = \lim_{k \rightarrow \infty} {f}(\ma^{t_k})
 \end{equation}
+therefore, \eqn{\{\ma^t\}} is not convergent.
+The existence of a convergent subsequence is guaranteed by \cite[Th.
+3.6]{rudin1964principles}, since \eqn{\{\ma^t\}} is a sequence in the compact set \eqn{\mc{F}}, and therefore bounded.
 
-Due to the existence of multiple limit points, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
-Note that since the objective sequence \eqn{\{f(\ma^t)\}} converges to, say, \eqn{f(\bar{\ma})}, for some \eqn{\bar{\ma}}, then we show that \eqn{\bar{\ma}} is a stationary point.
-To show that, let us consider a subsequence \eqn{\{\ma^{t_j} | j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
+Since the sequence of iterates \eqn{\{\ma^t\}} may not be convergent, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
+To prove the stationarity of a limit point \eqn{\bar{\ma}}, let us consider that \eqn{\{f(\ma^t)\}} converges to \eqn{f(\bar{\ma})}, then we show that \eqn{\bar{\ma}} is a stationary point.
+To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to the limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
 It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
-\begin{equation}
+\begin{equation} \label{seq_mon}
 f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}).
 \end{equation}
-Now, by taking the limit as \eqn{j \rightarrow \infty}, we obtain
+Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of the objective function \eqn{f}, we obtain
 \begin{equation}
-f(\bar{\ma}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}})
+\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma})
 \end{equation}
-therefore, \eqn{\bar{\ma}} is a stationary point.
-The above discussion also includes the \ac{AO} step, since in between each \ac{AO} update, the objective sequence is strictly monotonic \eqref{fixed_point} \cite[Prop.
+and moreover, it follows
+\begin{equation} \label{seq_mon1}
+\nabla f (\bar{\ma}) (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub
+\end{equation}
+where \eqn{\mc{Q}} is the feasible set defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
+Eq.
+\eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
+Hence, the limit point of a convergent subsequence \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.
+
+%The above discussion also considers \ac{AO} step, since in between each \ac{AO} update, the objective sequence is strictly monotonic \eqref{fixed_point} and it follows \cite[Prop.
 2.7.1]{bertsekas1999nonlinear}.

### 2015-10-21 Report/convergence_centralized.tex
updated convergence proof at home

@@
 where the functions \me{g_2} and \me{\hat{f}} are convex, and the function \me{h} is linear.
-Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly.
+Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both.
 The constraint \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} respectively.
-Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
+Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
 \iftoggle{single_column}{
@@
 
-Now, to show the convergence of the sequence of objective values generated by the centralized algorithm Algorithm \ref{algo-1} for the formulations \eqref{eqn-6} and \eqref{eqn-mse-1}, we require the following.
+The following conditions are required to prove the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative approach.
 \begin{itemize}
@@
 However, to ensure strict monotonicity of the objective sequence, we need condition (d).
-Assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, we can ensure the convergence of objective sequence \cite[Th.
+Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of objective sequence can be shown by using \cite[Th.
 3.14]{rudin1964principles}.
-Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates is a stationary point of the nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}, where iterates correspond to stacked vector of all optimization variables.
+Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that \reviewF{every limit point of the sequence of iterates is a stationary point of the nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+The term iterates correspond to the stacked vector of solution obtained in each iteration.
 
-Before proceeding further, we denote the representations used in the following proof with respect to Algorithm \ref{algo-1}.
-Since it involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
-Let \me{\mx}, \me{\my}, and \me{\mz} correspond to the stacked vector all transmit precoders, receive beamformers, and other optimization variables, such as \me{\beta_{l,k,n},\gamma_{l,k,n}} or \eqn{t_{l,k,n},\epsilon_{l,k,n}} respectively.
+Before proceeding further, we denote the representations used in the following proof.
+Since Algorithm \ref{algo-1} involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
+Let \me{\mx}, \me{\my}, and \me{\mz} correspond to the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1}, such as \me{\beta_{l,k,n},\gamma_{l,k,n}} or \eqn{t_{l,k,n},\epsilon_{l,k,n}} respectively.
 Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k}{i}} be the solution obtained in \eqn{\ith{i}} \ac{AO} step of \eqn{\ith{k}} \ac{SCA} iteration for the optimization variables \me{\mx} and \me{\gamma} with fixed \me{\my}.
+Let \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} be the solution obtained for \me{\mx} and \me{\mz} when \ac{SCA} iteration converges as \eqn{k \rightarrow \infty} in the \eqn{\ith{i}} \ac{AO} step for fixed \eqn{\my}.
+Similarly, \me{\iter{\my}{\lpointx}{i}} and \me{\iter{\mz}{|\mx}{i}} correspond to the solutions of \eqn{\my} and \eqn{\mz} in \eqn{\ith{i}} \ac{AO} update for fixed \eqn{\mx}, \textit{i.e.}, upon convergence of the \ac{SCA} loop as \eqn{k \rightarrow \infty}.
+
 %We denote \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} as the solution obtained for \me{\mx} and \me{\mz} when the sequence of objective values converges in \eqn{\ith{i}} \ac{AO} step for fixed \eqn{\my}.
@@
 \subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
-The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is verified by the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
+The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is due to the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
 
 The minimum of the norm in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below.
-The objective function is Lipschitz continuous over the feasible set, and therefore, it is bounded from above as well, since the feasible set is bounded.
+The objective function is Lipschitz continuous over the feasible set.
+The objective function is bounded from above as well, since the feasible set is bounded.
 %The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, and therefore it is coercive in the feasible set.
@@
 
+%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.
 Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
-Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.
-However, similar claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}, since there can be two different convergent subsequences of \eqn{\{\ma^t\}}, say, \eqn{\{\ma^{t_i} \, | \, i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} \, | \, k = 0,1,\dotsc\}}, such that
+Note that similar claim cannot be made for the convergence of \eqn{\{\ma^t\}}, since the sequence is not monotonic.
+However, due to the compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded.
+Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th.
+3.6]{rudin1964principles}.
+By considering two different convergent subsequences of \eqn{\{\ma^t\}}, say, \eqn{\{\ma^{t_i} \, | \, i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} \, | \, k = 0,1,\dotsc\}} that converges to two different limit points, such that
 \begin{equation}
@@
 \end{equation}
-therefore, \eqn{\{\ma^t\}} is not convergent.
-The existence of a convergent subsequence is guaranteed by \cite[Th.
-3.6]{rudin1964principles}, since \eqn{\{\ma^t\}} is a sequence in the compact set \eqn{\mc{F}}, and therefore bounded.
+we can show that \eqn{\{\ma^t\}} is not a convergent sequence.
 
-Since the sequence of iterates \eqn{\{\ma^t\}} may not be convergent, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
-To prove the stationarity of a limit point \eqn{\bar{\ma}}, let us consider that \eqn{\{f(\ma^t)\}} converges to \eqn{f(\bar{\ma})}, then we show that \eqn{\bar{\ma}} is a stationary point.
-To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to the limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
+Since \eqn{\{\ma^t\}} is not a convergent sequence, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
+To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
 It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
@@
 \end{equation}
-Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of the objective function \eqn{f}, we obtain
+Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain
 \begin{equation}
@@
 \end{equation}
-and moreover, it follows
+moreover, note that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0} and
 \begin{equation} \label{seq_mon1}
@@
 \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
-Hence, the limit point of a convergent subsequence \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.
+Hence, the limit point of any convergent subsequence \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.
 
@@
 To prove the feasibility of the limit point \me{\bar{\ma}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
-Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}} is regular as it satisfies the Slater's constraint qualifications.
+Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}}, and is regular as it satisfies the Slater's constraint qualifications.
 Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
@@
 \end{equation}
-The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since \eqn{\bar{\ma}} is a limit point of a convergent subsequence .
-Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfy \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
-(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\lpoint}} is given as
+The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}.
+Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
+(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\bar{\ma}} is given as
 \begin{equation} \label{rhs_equiv}
@@
 \end{equation}
-Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
 By using \cite[Thms.
-2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of problem \eqref{con}.}
+2 and 11]{scutari_1} and \cite[Prop.
+3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of \eqref{con}.}
 

### 2015-10-21 Report/wsrm_formulation.tex
updated convergence proof at home

@@
 
-Note that in all our numerical simulations, the objective sequence of Algorithm \ref{algo-1} converges.
-\reviewF{However, to discuss on the convergence of the beamformer iterates}, we consider a modified objective by augmenting a quadratic term as in \eqref{mod_obj} instead of the one in \eqref{eqn-6.1}.
+Note that in all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges.
+\reviewF{However, to analyze the convergence of the sequence of beamformer iterates}, we consider a modified objective \eqref{mod_obj} with a quadratic term instead of \eqref{eqn-6.1}.
 Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.}

### 2015-10-22 Report/convergence_centralized.tex
reverted most of the changes

@@
+The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
+\begin{itemize}
+	\item[(a)] Objective function should be bounded below
+	\item[(b)] Feasible set should be compact
+	\item[(c)] Sequence of objective values should be strictly decreasing
+	\item[(d)] Uniqueness of the minimizer in each step.
+\end{itemize}
+\review{The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}.
+However, to ensure strict monotonicity of the objective sequence, we require condition (d).
+Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of the objective sequence can be shown by using \cite[Th.
+3.14]{rudin1964principles}.
+Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+The term iterates denotes the stacked vector of solution variables obtained in each iteration.}
+
 Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
@@
 where the functions \me{g_2} and \me{\hat{f}} are convex, and the function \me{h} is linear.
-Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both.
+Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables.
 The constraint \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} respectively.
@@
 
-The following conditions are required to prove the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative approach.
-\begin{itemize}
-	\item[(a)] Objective function should be bounded below
-	\item[(b)] Feasible set should be a compact
-	\item[(c)] Sequence of objective values should be strictly decreasing
-	\item[(d)] Uniqueness of the minimizer in each step.
-\end{itemize}
-The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}.
-However, to ensure strict monotonicity of the objective sequence, we need condition (d).
-Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of objective sequence can be shown by using \cite[Th.
-3.14]{rudin1964principles}.
-Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that \reviewF{every limit point of the sequence of iterates is a stationary point of the nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}.
-The term iterates correspond to the stacked vector of solution obtained in each iteration.
-
-Before proceeding further, we denote the representations used in the following proof.
+\review{We use the following notations to discuss the convergence proof.
 Since Algorithm \ref{algo-1} involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
-Let \me{\mx}, \me{\my}, and \me{\mz} correspond to the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1}, such as \me{\beta_{l,k,n},\gamma_{l,k,n}} or \eqn{t_{l,k,n},\epsilon_{l,k,n}} respectively.
-Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k}{i}} be the solution obtained in \eqn{\ith{i}} \ac{AO} step of \eqn{\ith{k}} \ac{SCA} iteration for the optimization variables \me{\mx} and \me{\gamma} with fixed \me{\my}.
-Let \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} be the solution obtained for \me{\mx} and \me{\mz} when \ac{SCA} iteration converges as \eqn{k \rightarrow \infty} in the \eqn{\ith{i}} \ac{AO} step for fixed \eqn{\my}.
-Similarly, \me{\iter{\my}{\lpointx}{i}} and \me{\iter{\mz}{|\mx}{i}} correspond to the solutions of \eqn{\my} and \eqn{\mz} in \eqn{\ith{i}} \ac{AO} update for fixed \eqn{\mx}, \textit{i.e.}, upon convergence of the \ac{SCA} loop as \eqn{k \rightarrow \infty}.
+Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1} respectively.
+Since Algorithm \ref{algo-1} includes two \ac{SCA} iterations performed until convergence in each \ac{AO} iteration, let us now consider \ac{AO} step \eqn{i} for fixed \eqn{\my}.
+The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented as \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
+As \eqn{k \rightarrow \infty}, the objective sequence converges, and the corresponding solution obtained is denoted as \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
+Similarly, for fixed \eqn{\mx} and as \eqn{k \rightarrow \infty}, the corresponding solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}} respectively.}
 
@@
 
-\review{To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
+To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
 \begin{IEEEeqnarray}{rCl} \neqsub
-	\hat{f}(\mbf{x}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
-	f(\mbf{x}) &=& \hat{f}(\mbf{x}) + {\tau}_k^{(i)} \, \| \mbf{x} - \mbf{x}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
+	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
 \end{IEEEeqnarray}
-where \eqn{\mbf{x}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{x}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step.
+where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step.
 The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, as shown in \cite{scutari-1}.
-Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, uniqueness of the minimizer is guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}}.
+Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, uniqueness of the minimizer is guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}.
 
@@
 \subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
-\review{In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness of the minimizer and upon convergence of the objective, \eqn{f} is equal to \eqn{\hat{f}}.
-Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.}
+In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness of the minimizer and upon convergence of the objective, \eqn{f} is equal to \eqn{\hat{f}}.
+Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.
 
@@
 Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\my}{k}{i}}.
-Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by
+Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for variables \me{\mx} and \me{\mz} is given by
 \begin{IEEEeqnarray}{rCl} \label{con-m} \neqsub
@@
 \end{IEEEeqnarray}
-The feasible set defined by the problem in \eqref{con-m} is denoted as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
+The feasible set defined by the problem \eqref{con-m} is denoted by \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
 To prove the convergence of the \ac{SCA} updates in the \me{\ith{i}} \ac{AO} iteration, let us consider that \eqref{con-m} yields
@@
 Now, by using the fact that the objective sequence is nonincreasing and the uniqueness of the minimizer in each convex subproblem \eqref{con-m}, we can ensure that the sequence of iterates generated by the iterative \ac{SCA} approach converges to a unique limit point in each \ac{AO} step \eqn{{i}}}.
-\review{However, to ensure strict monotonicity of the objective sequence, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}.
+However, to ensure strict monotonicity of the objective sequence, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}.
 Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step.
@@
 Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
-Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of the objective sequence in each \ac{AO} step \eqn{{i}}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon the convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}
+Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of objective sequence in each \ac{AO} step \eqn{{i}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}
 
@@
 
-\review{Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured.
-It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.}
+Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured.
+It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.
 
@@
 In order to do so, let us use single global index \eqn{t} to represent both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}.
-Using this, we can represent \eqn{\ma^{t} \triangleq [\iter{\mx}{k}{i},\iter{\my}{}{i-1},\iter{\mz}{k|\my}{i}]} as a stacked vector of solution obtained in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} update with fixed \eqn{\my}.
+Using this, we can represent \eqn{\ma^{t} \triangleq [\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k|\my}{i}]} as a stacked vector of solution obtained in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} update with fixed \eqn{\my}.
 The index \eqn{t} is used to represent both \ac{SCA} updates involving transmit and receive beamformers within each \ac{AO} step.
@@
 Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
-Note that similar claim cannot be made for the convergence of \eqn{\{\ma^t\}}, since the sequence is not monotonic.
+Note that similar claim cannot be made on the convergence of \eqn{\{\ma^t\}}, since the sequence need not be monotonic.
 However, due to the compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded.
@@
 3.6]{rudin1964principles}.
-By considering two different convergent subsequences of \eqn{\{\ma^t\}}, say, \eqn{\{\ma^{t_i} \, | \, i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} \, | \, k = 0,1,\dotsc\}} that converges to two different limit points, such that
-\begin{equation}
-\lim_{t \rightarrow \infty} {f}(\ma^t) = \lim_{i \rightarrow \infty} {f}(\ma^{t_i}) = \lim_{k \rightarrow \infty} {f}(\ma^{t_k})
-\end{equation}
-we can show that \eqn{\{\ma^t\}} is not a convergent sequence.
+Since there can be possibly two subsequences of \eqn{\{\ma^t\}} that converges to two different limit points, the sequence of iterates \eqn{\{\ma^t\}} need not be convergent sequence.
 
-Since \eqn{\{\ma^t\}} is not a convergent sequence, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
+Therefore, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
 To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
@@
 \end{equation}
+Eq.
+\eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
 Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain
-\begin{equation}
-\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma})
+\begin{equation} \label{limpoint}
+\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma}).
 \end{equation}
-moreover, note that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0} and
+Using strict monotonicity in \eqn{\{f(\ma^{t_j})\}} and the fact that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0}, we can show that limit point \eqn{\bar{\ma}} satisfies the optimality condition \cite[Prop.
+2.1.2]{bertsekas1999nonlinear} as
 \begin{equation} \label{seq_mon1}
@@
 \end{equation}
-where \eqn{\mc{Q}} is the feasible set defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
-Eq.
-\eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
-Hence, the limit point of any convergent subsequence \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.
+where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
+Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
 
@@
 To prove the feasibility of the limit point \me{\bar{\ma}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
-Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}}, and is regular as it satisfies the Slater's constraint qualifications.
-Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
+Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}}.
+Since \eqn{\bar{\ma}} satisfies Slater's constraint qualifications, there exist Lagrange multipliers \eqn{\mu_i} such that
 \begin{equation} \label{kkt_mod_expr}
@@
 2 and 11]{scutari_1} and \cite[Prop.
-3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of \eqref{con}.}
+3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the algorithm is a stationary point of problem \eqref{con}.}
 
@@
 3.2]{amir}, we can show that all the limit points of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
-
 \end{comment}

### 2015-10-22 Report/convergence_distributed.tex
reverted most of the changes

--- 2015-08-07 Report/convergence_distributed.tex
@@
-\review{The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
+The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
 Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence.
@@
 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}.
-Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, then the limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}
+Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}
 
@@
 However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus, achieving improved speed of convergence.
-\review{Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
+Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
 Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed.
 Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is not guaranteed in each update.
-Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the beamformer iterates.}
+Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the beamformer iterates.
 

### 2015-10-22 Report/decomposition_solutions.tex
reverted most of the changes

@@
 Note that the convex subproblems in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to design the precoders for all users in the system.
-\review{However, the amount of \ac{CSI} that needs to be exchanged between the \acp{BS} and the controller grows significantly as the network size increases (e.g., the number of \acp{BS} and users, and the number of associated antennas).
-The overhead involved in the \ac{CSI} exchanges can be avoided, if we design the respective precoders independently at each \ac{BS} with the minimal information exchange, which is determined by the distributed schemes discussed herein.}
+However, the amount of \ac{CSI} that needs to be exchanged between the \acp{BS} and the controller grows significantly as the network size increases (e.g., the number of \acp{BS} and users, and the number of associated antennas).
+The overhead involved in the \ac{CSI} exchanges can be avoided, if we design the respective precoders independently at each \ac{BS} with the minimal information exchange, which is determined by the distributed schemes discussed herein.
 

### 2015-10-22 Report/dual_approach.tex
reverted most of the changes

@@
 The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}.
-\review{To reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
+To reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
 If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
@@
 Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured.
-The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.}
+The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.
 

### 2015-10-22 Report/kkt_mse_approach.tex
reverted most of the changes

@@
 In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the queue deviation with few number of iterations.
-\review{The alternative way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.}
+The alternative way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.
 
@@
 
-\review{We conclude this section by providing some remarks on selecting an algorithm within centralized and distributed approaches for certain scenarios.
+We conclude this section by providing some remarks on selecting an algorithm within centralized and distributed approaches for certain scenarios.
 Among the centralized algorithms proposed in Section \ref{sec-3}, both the \ac{SINR} relaxation and the \ac{MSE} reformulation schemes are equally attractive when \eqn{N_R > 1}.
@@
 Similarly, for the distributed approaches with \eqn{N_R = 1}, the \ac{SINR} relaxation is preferred to the \ac{MSE} reformulation schemes, since the variables to be exchanged among \acp{BS} are only the scalar interference values.
-However, when \eqn{N_R > 1} the \ac{KKT} scheme in Section \ref{sec-4.3} is favorable, since the overhead required to achieve a certain throughput improvement is less, as compared to the primal decomposition or \ac{ADMM}.}
+However, when \eqn{N_R > 1} the \ac{KKT} scheme in Section \ref{sec-4.3} is favorable, since the overhead required to achieve a certain throughput improvement is less, as compared to the primal decomposition or \ac{ADMM}.
 

### 2015-10-22 Report/mse_formulation.tex
reverted most of the changes

@@
 
-Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \review{\me{t_{l,k,n}}} for fixed receive beamformers.
+Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receive beamformers.
 The optimization subproblem to find the transmit precoders for fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by

### 2015-10-22 Report/simulation_results.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response
reverted most of the changes

@@
 
-For a \ac{MIMO} setup, we consider a system with \review{\me{N=4} and \eqn{N=2}} sub-channels with \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
+For a \ac{MIMO} setup, we consider a system with \me{N=4} and \eqn{N=2} sub-channels with \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
 The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the \ac{BS}-user associations are made by selecting the \ac{BS} with the lowest \ac{PL} component.
@@
 	\includegraphics[width=\columnwidth]{fig-3-2}
+	\vspace{-0.3in}
 	\caption{Convergence of the centralized and the distributed algorithms for \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace} using \me{\ell_1} norm for \ac{JSFRA} schemes with \me{Q_k = [5,7,9,11,8,12,5,4]} bits}
@@
 \ref{fig-a}, the \ac{Q-WSRME} performs marginally inferior to the \ac{JSFRA} algorithms due to the weights used in the algorithm, since the \ac{Q-WSRME} scheme favors the users with the large number of backlogged packets as compared to the users with better channel conditions.
-Note that the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{J_{\max} = 1} for both Fig.
+Note that the receivers are updated along with the \ac{SCA} update instants \textit{i.e}, \me{K_{\max} = 1} for both Fig.
 \subref*{fig-1} and Fig.

### 2015-10-22 Report/sub_channel_wsrm.tex
reverted most of the changes

@@
 
-\review{For simplicity we use random sub-channel ordering in our paper, \textit{i.e.}, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
+For simplicity we use random sub-channel ordering in our paper, \textit{i.e.}, after finding the precoders for a current sub-channel, we can choose any previously unselected sub-channels as the next candidate sub-channel for which the precoders are identified using the updated backlogged packets.
 Alternatively, we can also use greedy ordering to select the sub-channels by sorting the norm of the channel seen between the users and the respective serving \acp{BS}.
 However, it comes at the cost of increased complexity.
-Nevertheless, the \ac{SRA} scheme will be insensitive to the sub-channel ordering as the number of users in the system increases, due to the available multi-user diversity in the system.}
+Nevertheless, the \ac{SRA} scheme will be insensitive to the sub-channel ordering as the number of users in the system increases, due to the available multi-user diversity in the system.
 

### 2015-10-22 Report/wsrm_formulation.tex
reverted most of the changes

@@
 
-\review{The proposed solution involves two nested iterations, \textit{i.e.}, one for the outer \ac{AO} loop and the second for the inner \ac{SCA} loop.
+The proposed solution involves two nested iterations, \textit{i.e.}, one for the outer \ac{AO} loop and the second for the inner \ac{SCA} loop.
 Each \ac{AO} iteration involves two steps, one for finding the transmit precoders by solving \eqref{eqn-9} iteratively until convergence for fixed receivers, and the other for updating the receive beamformers with the previously found fixed transmit precoders by either solving \eqref{opt-rx} recursively or by using \eqref{eqn-10}.
@@
 \reviewF{However, to analyze the convergence of the sequence of beamformer iterates}, we consider a modified objective \eqref{mod_obj} with a quadratic term instead of \eqref{eqn-6.1}.
-Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.}
+Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.
 \begin{comment}

### 2015-10-22 Report/convergence_centralized.tex
added

@@
+%\begin{comment}
+%
+%The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
+%\begin{itemize}
+%	\item[(a)] Objective function should be bounded below
+%	\item[(b)] Feasible set should be compact
+%	\item[(c)] Sequence of objective values should be strictly decreasing
+%	\item[(d)] Uniqueness of the minimizer in each step.
+%\end{itemize}
+%\review{The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}.
+However, to ensure strict monotonicity of the objective sequence, we require condition (d).
+Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of the objective sequence can be shown by using \cite[Th.
+3.14]{rudin1964principles}.
+Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+The term iterates denotes the stacked vector of solution variables obtained in each iteration.}
+%
+%Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+%\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
+%	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
+%	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
+%	&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
+%	&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
+%\end{IEEEeqnarray}
+%where the functions \me{g_2} and \me{\hat{f}} are convex, and the function \me{h} is linear.
+Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables.
+The constraint \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} respectively.
+Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
+%\iftoggle{single_column}{
+%	\begin{equation}
+%		\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
+%	\end{equation}
+%}{\begin{align}
+%\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
+%& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
+%\end{align}}
+%
+%\review{We use the following notations to discuss the convergence proof.
+Since Algorithm \ref{algo-1} involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
+Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1} respectively.
+Since Algorithm \ref{algo-1} includes two \ac{SCA} iterations performed until convergence in each \ac{AO} iteration, let us now consider \ac{AO} step \eqn{i} for fixed \eqn{\my}.
+The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented as \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
+As \eqn{k \rightarrow \infty}, the objective sequence converges, and the corresponding solution obtained is denoted as \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
+Similarly, for fixed \eqn{\mx} and as \eqn{k \rightarrow \infty}, the corresponding solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}} respectively.}
+%
+%%We denote \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} as the solution obtained for \me{\mx} and \me{\mz} when the sequence of objective values converges in \eqn{\ith{i}} \ac{AO} step for fixed \eqn{\my}.
+Similarly, \me{\iter{\my}{\lpointx}{i}} and \me{\iter{\mz}{|\mx}{i}} correspond to the solutions of \eqn{\my} and \eqn{\mz} in \eqn{\ith{i}} \ac{AO} update for fixed \eqn{\mx}.
+%
+%\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
+%The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is due to the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
+%
+%The minimum of the norm in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below.
+The objective function is Lipschitz continuous over the feasible set.
+The objective function is bounded from above as well, since the feasible set is bounded.
+%The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, and therefore it is coercive in the feasible set.
+%Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
+%
+%\subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
+%%The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
+However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set.
+Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers.
+%, \textit{i.e.}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.
+%
+%To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
+%\begin{IEEEeqnarray}{rCl} \neqsub
+%	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
+%	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+%\end{IEEEeqnarray}
+%where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step.
+The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, as shown in \cite{scutari-1}.
+Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, uniqueness of the minimizer is guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}.
+%
+%%in each step and let \eqn{c > 0} be the constant of strong convexity of \eqn{f} with \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} as in \cite{scutari-1}.
+%%The uniqueness of the transmit precoders and the receive beamformers for the \ac{MSE} reformulation in \eqref{eqn-mse-2} can be guaranteed in each iteration by the \ac{MSE} constraint in \eqref{eqn-mse-1.3}.
+The uniqueness of the iterates for the problem in \eqref{eqn-9} can be guaranteed in each convex subproblem if the receivers are matched to the equivalent downlink channel with the initially chosen feasible transmit precoders, \textit{i.e.}, \me{q_{l,k,n} = 0 \: \forall \, l,k,n} in \eqref{eqn-wsrm-expr} while beginning the \ac{SCA} iteration.
+%%of the objective
+%%When the objective is zero, the uniqueness of  the transmit and the receive beamformers are not guaranteed in both problem formulations, since they are the under-estimators and need not be active at the minimum.
+To obtain a unique set of transmit precoders and the receive beamformers in all scenarios, we can regularize the objective with a strongly convex function as
+%%\begin{equation}
+%%\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
+%%\end{equation}
+%%where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant.
+The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
+%Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
+The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e.}, unitary transformations.
+When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
+To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
+%
+%\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
+%In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness of the minimizer and upon convergence of the objective, \eqn{f} is equal to \eqn{\hat{f}}.
+Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.
+%
+%To begin with, let us consider the variable \me{\my} is fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\lpoint}{i-1}}.
+In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
+%\iftoggle{single_column}{
+%\begin{equation}\label{con-relax}
+%\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+%\end{equation}}{
+%\begin{multline} \label{con-relax}
+%\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) = {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+%\end{multline}}
+%Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\lpoint}{i-1}} and \me{\iter{\mx}{k}{i}}.
+Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\my}{k}{i}}.
+Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for variables \me{\mx} and \me{\mz} is given by
+%\begin{IEEEeqnarray}{rCl} \label{con-m} \neqsub
+%	\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\lpoint}{i-1},\mz) \eqsub \label{con-obj-m} \\
+%	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
+%	&\quad& g_1(\mx,\iter{\my}{\lpoint}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \label{con-cvx-blk-m}
+%\end{IEEEeqnarray}
+%The feasible set defined by the problem \eqref{con-m} is denoted by \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
+To prove the convergence of the \ac{SCA} updates in the \me{\ith{i}} \ac{AO} iteration, let us consider that \eqref{con-m} yields
+%\me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution in the \me{\ith{k}} iteration.
+The point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimizes the objective function satisfies
+%\iftoggle{single_column}{
+%\begin{equation}\label{con-sub-set}\allowdisplaybreaks
+%h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0. 
+%\end{equation}}{
+%\begin{multline}\label{con-sub-set}\allowdisplaybreaks
+%h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}) \leq \\
+%h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0. 
+%\end{multline}}
+%Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\lpoint}{i-1}} was chosen to be feasible from the \me{\ith{(i-1)}} \ac{AO} iteration.
+In each \ac{SCA} step, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,amir}
+%\iftoggle{single_column}{
+%\begin{equation} \label{con-convergence}
+%f(\iter{\mx}{0}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}) \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+%\end{equation}}{
+%\begin{multline} \label{con-convergence} \allowdisplaybreaks
+%f(\iter{\mx}{0}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+%\end{multline}}
+%Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing.
+%\review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique.
+Now, by using the fact that the objective sequence is nonincreasing and the uniqueness of the minimizer in each convex subproblem \eqref{con-m}, we can ensure that the sequence of iterates generated by the iterative \ac{SCA} approach converges to a unique limit point in each \ac{AO} step \eqn{{i}}}.
+%However, to ensure strict monotonicity of the objective sequence, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}.
+Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step.
+At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
+%\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
+%\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
+%f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& c \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
+%\end{IEEEeqnarray}
+%since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
+Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
+Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
+Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of objective sequence in each \ac{AO} step \eqn{{i}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}
+%
+%Once \me{\iter{\mx}{\lpoint}{i}} is obtained for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}.
+However, after fixing \me{\mx} as \me{\iter{\mx}{\lpoint}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}.
+Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\lpoint}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively.
+Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
+The convergence and the nonincreasing behavior of the objective follow similar arguments as above.
+\footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The solution obtained by solving \eqref{con-m} iteratively until convergence of the objective value is given as \me{\{\iter{\mx}{\lpoint}{i}, \iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}\} \in \iter{\mc{Y}}{\lpoint}{i} \subset \mc{F}}.
+%
+%Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
+%\iftoggle{single_column}{
+%\begin{equation}
+%f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+%\end{equation}}{
+%\begin{equation}
+%f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+%\end{equation}}
+%Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}.
+To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}.
+Since the convex function is linearized in \eqref{con-dc}, the fixed operating point is also included in the feasible set \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}} by the equality in \eqref{con-sub-set}.
+Using this, we can show the monotonicity of the objective as
+%\begin{equation} \label{fixed_point}
+%f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}).
+%\end{equation}
+%The \ac{AO} update follows \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
+%
+%Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured.
+It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.
+%
+%
+%\begin{comment}
+%\begin{equation} \label{strict_monotonicity}
+%f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
+%\end{equation}
+%
+%Note that the \ac{AO} and \ac{SCA} procedures generate a nonincreasing sequence of objectives for the original objective in \eqref{orig_obj} using the above discussions.
+However, by using the regularized objective in \eqref{mod_obj}, we can show that the sequence of objectives provided by \ac{AO} and \ac{SCA} steps is strictly decreasing.
+Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} \ac{SCA} step.
+Note that the objective \eqref{con-obj-m} is strongly convex with some parameter \eqn{m > 0}, and therefore \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}
+%\begin{IEEEeqnarray}{l}
+%f(\mbf{z}) \geq f(\iter{\mbf{z}}{k+1}{i}) + \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) + \tfrac{m}{2} \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2. \eqspace 
+%\end{IEEEeqnarray}
+%Since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer for \eqref{con-m} in the \eqn{\ith{k}} \ac{SCA} step, 
+%\begin{IEEEeqnarray}{rCl} \neqsub \label{s_ineq_g}
+%\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0, \quad \iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i} \eqsub \\
+%f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}\|^2. \eqsub \label{s_ineq}
+%\end{IEEEeqnarray}
+%Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
+Using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{s_ineq_g}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured.
+However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.
+%
+%	In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj} with parameter \eqn{m > 0} as %We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} \ac{SCA} step \cite{marks1978technical}.
+%	%It follows by the strong convexity of \eqref{mod_obj} with \eqn{m > 0} in the \eqn{\ith{k}} update
+%	\begin{equation} \label{strict_monotonicity}
+%	f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \underbrace{\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i})}_{= 0} + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
+%	\end{equation}
+%	since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}.
+Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
+Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
+However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.
+%
+%
+%%Even though the original convex function \eqn{\hat{f}(\mbf{z})} can have multiple limit points upon the \ac{SCA} convergence, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point is unique, and therefore the objective decreases monotonically in a strict sense.
+It can be proved, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even if the other limit points are included in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}}, with the same \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
+%%Let \eqn{\mbf{z}^{i}_{k}} be an unique minimizer and also a limit point of the \eqn{\ith{k}} \ac{SCA} step.
+Let \eqn{\mbf{z}^{i}_{k+1}} be another limit point with the same objective \eqn{\hat{f}(\mbf{z}^{i}_{k}) = \hat{f}(\mbf{z}^{i}_{k+1})} in the \eqn{\ith{k+1}} feasible set \eqn{\iter{\mc{X}}{k+1}{i}}.
+Due to the convexity of \eqn{\hat{f}(\mbf{z})}, strict monotonicity cannot be ensured since the selection of \eqn{\mbf{z}^{i}_{k}} and \eqn{\mbf{z}^{i}_{k+1}} are equally likely.
+However, due to the additional quadratic term \eqn{c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} in \eqn{f(\mbf{z})} for the \eqn{\ith{k+1}} iteration, the update cannot choose \eqn{\mbf{z}^{i}_{k+1}} due to the positive quadratic residual, therefore, it selects the fixed point \eqn{\mbf{z}^{i}_{k}} in the \eqn{\ith{k+1}} iteration.
+Similarly, using the above argument, we can also prove the strict monotonicity of the objective in each \ac{AO} update \eqn{i}, and thereby proving strict monotonicity of the overall objective sequence.
+%
+%
+%{Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{k-1}} \ac{SCA} step.
+In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj}.
+We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{k}} solution \eqn{\mbf{z}^{(i)}_k} is a feasible point in \eqn{\mc{X}_{k+1}^{(i)}} of the \eqn{\ith{k+1}} iteration \cite{marks1978technical}.
+However, due to the strong convexity of \eqref{mod_obj}, it follows that \eqn{\forall \mbf{z} \in \mc{X}^{(i)}_{k}}
+%	\begin{equation} \label{strict_monotonicity}
+%	f(\mbf{z}) \geq f(\mbf{z}_{k}^{(i)}) + \nabla f(\mbf{z}_{k}^{(i)})^\tran (\mbf{z} - \mbf{z}_{k}^{(i)}) + c \, \|\mbf{z} - \mbf{z}_{k}^{(i)}\|^2
+%	\end{equation}
+%	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\rightarrow\infty}, \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}}.
+Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
+However, if \eqn{\hat{f}} is used in the objective of \eqref{con-m}, then the limit point is not unique, \textit{i.e.}, \eqn{\{\exists \mbf{z} \in \mc{X}_{\lpoint}^{(i)} \vert \hat{f}(\mbf{z}) = \hat{f}(\mbf{z}_{\lpoint}^{(i)})\}}, and therefore the sequence generated by \eqref{con-m} with \eqn{\hat{f}} is not strictly monotonic.
+%	
+%	Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration.
+Since the limit point \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\lpoint}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}
+%
+%
+%%Due to the convexity in the original objective \eqn{\hat{f}(\mbf{z})}, it can have multiple limit points for the \ac{SCA} update, and therefore it follows \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k}.
+However, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point of the \ac{SCA} updates is also unique, and therefore has strict monotonicity in \eqn{f(\mbf{z}^{(i)}_k)} after each update.
+It can be justified, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even by including other limit points in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}} with the same original objective value as \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
+%%In spite of choosing \eqn{\mbf{z}_{k}^{(i)}} in both \eqn{k} and \eqn{k+1} iteration, \eqn{f(\mbf{z})} decreases strictly due to the vanishing quadratic term in the \eqn{\ith{k+1}} step, therefore, it is a fixed point.
+Similarly, by using the above argument, we can also prove the strict monotonicity of the objective in each \ac{AO} update, and thereby proving strict monotonicity of the overall sequence.
+%%In spite of the additional quadratic term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} to ensure unique minimizer, strict monotonicity of the objective in each \ac{SCA} update cannot be ensured.
+However, strict monotonicity can be guaranteed in each update \eqn{i} of the algorithm \me{\mc{A}} in \eqref{g-algo} for the objective.
+Using (a),(b),(c) along with the above discussion, we can ensure strict monotonicity and the convergence of the objective.}
+%%Due to the additional quadratic term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} from the earlier iteration and the unique minimizer from the previous step is also included, the objective decreases strictly in each \ac{SCA} update for an arbitrary value of \eqn{c} in \eqref{mod_obj}.
+Therefore, in each update \eqn{i} of the algorithm \me{\mc{A}} in \ref{g-algo}, the objective decreases monotonically in strict sense.
+Using (a),(b),(c) along with the above discussion, we can ensure strict monotonicity and the convergence of the objective.}
+%\end{comment}
+%
+%\subsection{Stationarity of Limit Points} \label{c-b}
+%
+%In this section, we discuss the convergence of the sequence of iterates generated by the iterative algorithm.
+In order to do so, let us use single global index \eqn{t} to represent both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}.
+Using this, we can represent \eqn{\ma^{t} \triangleq [\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k|\my}{i}]} as a stacked vector of solution obtained in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} update with fixed \eqn{\my}.
+The index \eqn{t} is used to represent both \ac{SCA} updates involving transmit and receive beamformers within each \ac{AO} step.
+%
+%%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.
+%Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
+Note that similar claim cannot be made on the convergence of \eqn{\{\ma^t\}}, since the sequence need not be monotonic.
+However, due to the compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded.
+Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th.
+3.6]{rudin1964principles}.
+Since there can be possibly two subsequences of \eqn{\{\ma^t\}} that converges to two different limit points, the sequence of iterates \eqn{\{\ma^t\}} need not be convergent sequence.
+%
+%Therefore, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
+To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
+It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
+%\begin{equation} \label{seq_mon}
+%f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}).
+%\end{equation}
+%Eq.
+\eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
+Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain
+%\begin{equation} \label{limpoint}
+%\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma}).
+%\end{equation}
+%Using strict monotonicity in \eqn{\{f(\ma^{t_j})\}} and the fact that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0}, we can show that limit point \eqn{\bar{\ma}} satisfies the optimality condition \cite[Prop.
+2.1.2]{bertsekas1999nonlinear} as
+%\begin{equation} \label{seq_mon1}
+%\nabla f (\bar{\ma}) (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub
+%\end{equation}
+%where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
+Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
+%
+%%The above discussion also considers \ac{AO} step, since in between each \ac{AO} update, the objective sequence is strictly monotonic \eqref{fixed_point} and it follows \cite[Prop.
+2.7.1]{bertsekas1999nonlinear}.
+%
+%Now to show that \eqn{\bar{\ma}} is a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between the gradient of the subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}.
+In order to show that \eqn{\bar{\ma}} is a \ac{KKT} point for \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
+%\begin{equation} \label{kkt_expr}
+%	\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
+%\end{equation}
+%for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.
+%
+%To prove the feasibility of the limit point \me{\bar{\ma}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
+Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}}.
+Since \eqn{\bar{\ma}} satisfies Slater's constraint qualifications, there exist Lagrange multipliers \eqn{\mu_i} such that
+%\begin{equation} \label{kkt_mod_expr}
+%	\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
+%\end{equation}
+%The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}.
+Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
+(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\bar{\ma}} is given as
+%\begin{equation} \label{rhs_equiv}
+%	\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
+%\end{equation}
+%Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+By using \cite[Thms.
+2 and 11]{scutari_1} and \cite[Prop.
+3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the algorithm is a stationary point of problem \eqref{con}.}
+%
+%\begin{comment}
+%However, it is not the case with the sequence of iterates \eqn{\{\iter{\ma}{k}{i}\}}, since there can be two different convergent subsequences that has the, say, \eqn{\{\iter{\ma}{k}{i}\}_{k,i \in \mc{Q}_1}} and \eqn{\{\iter{\ma}{k}{i}\}_{k,i \in \mc{Q}_2}} such that
+%
+%Let \me{\ma^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
+%\begin{equation} \label{g-algo}
+%\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) \triangleq
+%\begin{cases}
+%\underset{\mx,\mz}{\mathrm{argmin}} \; f(\mx,\mz;\iter{\my}{\lpoint}{i-1})& \forall \mx,\mz \in \iter{\mc{X}}{\lpoint}{i} \\
+%\underset{\my,\mz}{\mathrm{argmin}} \; f(\my,\mz;\iter{\mx}{\lpoint}{i})& \forall \my,\mz \in \iter{\mc{Y}}{\lpoint}{i} 
+%\end{cases} 
+%\end{equation}
+%Note that in each iteration \me{i}, the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e.}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant.
+Since the minimizer is unique, the mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
+In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\lpoint \subset \mc{F}} as the set of fixed points, \textit{i.e.}, \me{\forall {\ma}^{\lpoint} \in \mc{F}^\lpoint, \, {\ma}^{\lpoint} = \mc{A}({\ma}^{\lpoint})}, identified by the algorithm \me{\mc{A}} for different initialization points.
+%
+%Using \cite[Th. 3.1]{meyer1976sufficient}, convergence of the iterates to a fixed point can be shown, if the following conditions are satisfied.
+%\begin{itemize}
+%\item Objective function \me{f} should be bounded and continuous.
+%\item Feasible set \me{\iter{\mc{X}}{\lpoint}{i},\iter{\mc{Y}}{\lpoint}{i}} in each step should be compact.
+%\item The sequence \me{\{\iterate{\ma}{i}\}} generated by \me{\mc{A}} should be strictly monotonic with respect to the objective \me{f}, \textit{i.e.}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
+%\end{itemize}
+%\review{Note that the strict monotonicity of the objective is guaranteed using the strong convexity of \eqn{f} in Section \ref{mcity}.
+Therefore, all the above requirements are satisfied by algorithm \eqref{g-algo}}.
+Using \cite{zangwill1969nonlinear} and \cite[Th.
+3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point, and (iii) \eqn{\ma^\lpoint} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
+Even though the fixed points in the set \me{\mc{F}^\lpoint} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e.}, \me{\mc{F}^\lpoint = \{\ma^\lpoint\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
+%
+%\begin{comment}
+%	Note that the above conditions are satisfied by the algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity of the objective sequence is guaranteed in Section \ref{mcity} using strong convexity of \eqn{f}}.
+%and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e.}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
+The set of accumulation or the limit points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\lpoint} and the objective function be \me{f} is closed and continuous.
+Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
+If the mapping is strictly monotonic and uniformly compact, then the following conditions hold \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}.
+%\begin{itemize}
+%\item[(i)] all accumulation points will be a fixed point,
+%\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point,
+%\item[(iii)] \eqn{\ma^\lpoint} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
+%\end{itemize}
+%
+%To show that the proposed iterative method satisfies the above conditions,  the mapping \eqn{\mc{A}} for the iterative algorithm is given by
+%\begin{equation}
+%\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iterate{\mc{X}}{i} \subset \mc{F}
+%\end{equation}
+%where \me{\mc{A}(\iterate{\ma}{i})} denotes the set of iterates in the subset \me{\iterate{\mc{X}}{i}}, which has the same objective value under the mapping \me{f} in the \me{\ith{i}} iteration The monotonicity of the proposed algorithm is guaranteed based on the arguments presented in Appendix \ref{mcity}.
+The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e.}, \me{\ma \notin \mc{F}^\lpoint}, as in \eqref{fixed_point}.
+Using the above discussions, we can show that the sequence \me{\{\iterate{\ma}{i}\}} converges to a fixed point in the set \me{\mc{F}^\lpoint} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}
+%
+%The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed points \me{\mc{F}^\lpoint} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
+%
+%To show the set of fixed points \me{\mc{F}^\lpoint} are the minimizers for the objective function \me{f}, we rely on the strict monotonicity of the objective function for each iteration.
+Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\ma^\lpoint \in \mc{A}(\ma^\lpoint)}, which is a generalized fixed point.
+Therefore, the fixed points in \me{\mc{F}^\lpoint} are the minimizers for the objective function \me{f} over the set \me{\mc{F}}.
+%
+%If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
+The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}.
+Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\lpoint} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.
+%\end{comment}
+%
+%\begin{comment}
+%%\subsection{Stationary Points of the Nonconvex Problem}
+%\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\lpoint}} as \eqn{i \rightarrow \infty}.
+Now, to show that \eqn{\ma^{\lpoint}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} gradient condition of \eqref{con}, \textit{i.e.},
+%\begin{equation} \label{kkt_expr}
+%\textstyle	\nabla \hat{f}(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla {g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
+%\end{equation}
+%for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\ma^{\lpoint} \in \mc{F}}.
+%
+%To prove the feasibility of the limit point \me{\ma^{\lpoint}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
+Therefore, the limit point \eqn{\ma^{\lpoint} \in \mc{F}} and it satisfies the Slater's constraint qualifications.
+Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\lpoint}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}.
+Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
+%\begin{equation} \label{kkt_mod_expr}
+%\textstyle \nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
+%\end{equation}
+%The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\lpoint}}, since \eqn{\ma^{\lpoint}} is the fixed point of \eqn{\mc{A}}.
+Therefore, the gradient evaluated at \eqn{\ma^{\lpoint}} satisfy \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})}.
+(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\lpoint}} is given as
+%\begin{equation} \label{rhs_equiv}
+%\nabla h(\ma^{\lpoint}) - \nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\mbf{\ma}^{\lpoint}) = \nabla h(\ma^{\lpoint}) - \nabla g_o(\mbf{\ma}^{\lpoint}).
+%\end{equation}
+%Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\lpoint}} satisfies \eqref{kkt_expr}.
+By using \cite[Thms.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the problem in \eqref{con}.}
+%\end{comment}
+%\begin{comment}
+%In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
+In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
+Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\lpoint^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\lpoint}} satisfies the constraint qualifications of the problem \eqref{con}.
+%
+%To show that the limit point \eqn{\mbf{\ma}^{\lpoint}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\lpoint}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
+Therefore, it satisfies the \ac{KKT} conditions of the convex subproblem for some Lagrange multipliers \eqn{\mu_i \geq 0} as
+%\begin{equation} \label{kkt_expr}
+%\textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
+%\end{equation}
+%It is evident that the modified objective \eqn{f} and the convex function \eqn{\hat{f}} in \eqref{mod_obj} are equal at the limit point due to the vanishing quadratic penalty term.
+Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\mbf{\ma}^{\lpoint}) = \nabla g_o(\mbf{\ma}^{\lpoint})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\lpoint}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
+Now, by using \cite[Th.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that all the limit points of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
+%
+%\review{Let \eqn{\ma^{\lpoint}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}.
+The limit point \eqn{\ma^\lpoint} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions.
+%%and there exists no descent direction in the feasible set as
+%%\begin{equation}
+%%\nabla {f}(\ma^{\lpoint})^\tran \, (\ma - \ma^{\lpoint}) \geq 0, \: \forall \, \ma \in \mc{Y}^{\lpoint}
+%%\end{equation}
+%%where \eqn{\mc{Y}^{\lpoint}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\lpoint}^{i}} as \eqn{i \rightarrow \infty}. 
+%Let us consider the problem in \eqref{con-m}.
+Using \eqref{con-relax}, we can show that the feasible set \eqn{\mc{Y}_{\lpoint}^{i}} in each \ac{AO} iteration \eqn{i} is a subset of \eqn{\mc{F}}.
+Therefore, all iterates \eqn{\{\iterate{\ma}{i}\}} of the algorithm \eqn{\mc{A}} are feasible.
+Additionally, by the strong convexity of \eqn{f(\ma)}, following conditions are satisfied.
+%\begin{IEEEeqnarray}{rCl}  \neqsub \label{strong_cvxty}
+%\nabla {f}(\ma^{(i)})^\tran \, (\ma^{(i-1)} - \ma^{(i)}) &\geq& 0 \eqsub \\
+%f(\ma^{(i-1)}) - f(\ma^{(i)}) &\geq& c \: \|\ma^{(i-1)} - \ma^{(i)}\|^2. \eqsub
+%\end{IEEEeqnarray}
+%Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \mc{A}(\ma^{(i)})\| \rightarrow 0} as \eqn{i \rightarrow \infty}, which is the limit point of the algorithm \eqn{\mc{A}}.
+%
+%Now, it remains to show that the \eqn{\ma^{\lpoint}} is a stationary point of the nonconvex problem \eqref{con}.
+To see this, we note that \eqn{\ma^{\lpoint}} must satisfy the \ac{KKT} conditions of \eqref{con}.
+Since \eqn{\ma^{\lpoint}} is the fixed point of the algorithm \eqn{\mc{A}}, it satisfies the \ac{KKT} conditions of the convex subproblem \eqref{con-m} given by
+%\begin{equation} \label{kkt_expr}
+%\textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
+%\end{equation}
+%for some Lagrange multipliers \eqn{\mu_i \geq 0}.
+Using the equivalence between \eqn{\hat{f}(\ma^{\lpoint}) = f(\ma^{\lpoint})} and the relation in \eqref{con-relax} in \eqref{kkt_expr}, we can see that \eqref{kkt_expr} is indeed the \ac{KKT} condition for the nonconvex problem \eqref{con}.
+Since the gradient is zero in \eqref{kkt_expr}, the objective cannot be decreased any further.
+Now, by using \cite[Th.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that the limit points \eqn{\ma^\lpoint} of \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.}
+%
+%%In order for \eqn{\ma^{\lpoint}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}.
+In each iteration, the algorithm \eqn{\mc{A}} in \eqref{g-algo} finds a point \eqn{\iterate{\ma}{i} \in \mc{F}} with \eqn{f(\iterate{\ma}{i}) < f(\iterate{\ma}{i-1})}, therefore, it satisfies all the constraints of \eqref{con}.
+Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \rightarrow \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\lpoint}) = \ma^{\lpoint}} finds a unique \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}} due to the strong convexity of \eqn{f}.
+%
+%%To show the equivalence in the gradients of \eqref{con} and \eqref{con-m} at \eqn{\ma^{\lpoint}}, let us consider the limit point of the \ac{SCA} update in \eqn{\mc{A}} as it converges to a fixed point \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}}.
+The \ac{KKT} expression for the convex subproblem \eqref{con-cvx} is given by
+%%\begin{equation} \label{kkt_expr}
+%%\nabla f(\ma^{\lpoint}) + \mu_1 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
+%%\end{equation}
+%%for some Lagrange multipliers \eqn{\mu_i \geq 0}.
+Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}.
+Moreover, \eqn{\ma^{\lpoint}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}.
+Now, with the above conditions and by using \cite[Th.
+2 and 11]{scutari_1} and \cite[Prop.
+3.2]{amir}, we can show that the fixed points obtained by \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
+%
+%\begin{comment}
+%To show the limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}.
+As \me{i \rightarrow \infty}, the objective converges as
+%\iftoggle{single_column}{
+%\begin{equation} \label{con-opt}\allowdisplaybreaks
+%f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|x}{i}) = f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|y}{i+1}) = 
+%f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1})
+%\end{equation}}{
+%\begin{multline} \label{con-opt}\allowdisplaybreaks
+%f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|x}{i}) = f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|y}{i+1}) \\ = 
+%f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1})
+%\end{multline}}
+%where \me{\{\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1}\} \in \mc{F}^\lpoint} is a limit point of \me{\mc{A}} for a given initial point.
+Since the function \eqn{f} is strongly convex, the limit point is unique.
+As discussed in Appendix \ref{c-b}, the unique limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a fixed point of \me{\mc{A}}.
+%
+%Using \cite[Th.
+10]{lanckriet2009convergence} and \cite[Th.
+2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
+%
+%In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
+In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
+Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\lpoint^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\lpoint}} satisfies the constraint qualifications of the problem \eqref{con}.
+% 
+%To show that the limit point \eqn{\mbf{\ma}^{\lpoint}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\lpoint}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
+Therefore, it satisfies the \ac{KKT} conditions of the convex subproblem for some Lagrange multipliers \eqn{\mu_i \geq 0} as
+% \begin{equation} \label{kkt_expr}
+% \textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
+% \end{equation}
+% It is evident that the modified objective \eqn{f} and the convex function \eqn{\hat{f}} in \eqref{mod_obj} are equal at the limit point due to the vanishing quadratic penalty term.
+Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\iterate{\ma}{\lpoint}) = \nabla g_o(\mbf{\ma}^{\lpoint})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\lpoint}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
+Now, by using \cite[Th.
+2 and 11]{scutari_1} or \cite[Prop.
+3.2]{amir}, we can show that all the limit points of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
+%\end{comment}
+
 The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
@@
 
-%We denote \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} as the solution obtained for \me{\mx} and \me{\mz} when the sequence of objective values converges in \eqn{\ith{i}} \ac{AO} step for fixed \eqn{\my}.
-Similarly, \me{\iter{\my}{\lpointx}{i}} and \me{\iter{\mz}{|\mx}{i}} correspond to the solutions of \eqn{\my} and \eqn{\mz} in \eqn{\ith{i}} \ac{AO} update for fixed \eqn{\mx}.
-
 \subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
@@
 The objective function is bounded from above as well, since the feasible set is bounded.
-%The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, and therefore it is coercive in the feasible set.
-%Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
 \subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
-%The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
+The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
 However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set.
 Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers.
-%, \textit{i.e.}, \me{q_{l,k,n} = 0} in \eqref{eqn-wsrm-expr}, while initializing the feasible point \eqn{\iter{\mx}{0}{0}} and \eqn{\iter{\my}{0}{0}}.
 
@@
 Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, uniqueness of the minimizer is guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}.
-
-%in each step and let \eqn{c > 0} be the constant of strong convexity of \eqn{f} with \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} as in \cite{scutari-1}.
-%The uniqueness of the transmit precoders and the receive beamformers for the \ac{MSE} reformulation in \eqref{eqn-mse-2} can be guaranteed in each iteration by the \ac{MSE} constraint in \eqref{eqn-mse-1.3}.
-The uniqueness of the iterates for the problem in \eqref{eqn-9} can be guaranteed in each convex subproblem if the receivers are matched to the equivalent downlink channel with the initially chosen feasible transmit precoders, \textit{i.e.}, \me{q_{l,k,n} = 0 \: \forall \, l,k,n} in \eqref{eqn-wsrm-expr} while beginning the \ac{SCA} iteration.
-%of the objective
-%When the objective is zero, the uniqueness of  the transmit and the receive beamformers are not guaranteed in both problem formulations, since they are the under-estimators and need not be active at the minimum.
-To obtain a unique set of transmit precoders and the receive beamformers in all scenarios, we can regularize the objective with a strongly convex function as
-%\begin{equation}
-%\| \tilde{\mbf{v}} \|_q + c \, \| \mbf{x} - \mbf{x}^{(i)} \|^2
-%\end{equation}
-%where \me{\mbf{x}} is the vector containing all the optimization variables and \me{c} is a positive constant.
-The vector \me{ \mbf{x}^{(i)}} is the value of \me{\mbf{x}} in the \me{\ith{i}} iteration.
-%Note that the uniqueness of the transmit precoders and the receive beamformers for each convex subproblem can be shown by using the constraint \eqref{eqn-8} for the problem \eqref{eqn-9} and \eqref{eqn-mse-1.3} for the \ac{MSE} reformulation in \eqref{eqn-mse-2}.
-The receive beamformers \me{\mvec{w}{l,k,n}} in \eqref{eqn-10} are also unique for the given set of transmit precoders, since the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are susceptible to the transmit precoder phase rotations, \textit{i.e.}, unitary transformations.
-When the objective function is zero, the uniqueness of the transmit precoders are not guaranteed by using \eqref{eqn-8} and \eqref{eqn-mse-1.3} constraints, since they are not active at the optimal solution of the subproblems.
-To obtain unique set of transmit precoders when the objective is zero even for a single \ac{BS}, we can regularize the objective with the transmit power as discussed in Appendix \ref{a-3} without affecting the optimal value.
 
@@
 Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing.
-%\review{Since the objective is strongly convex due to the introduced quadratic term in \eqref{mod_obj}, the minimizer \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}\}} in each \ac{SCA} step is unique.
-Now, by using the fact that the objective sequence is nonincreasing and the uniqueness of the minimizer in each convex subproblem \eqref{con-m}, we can ensure that the sequence of iterates generated by the iterative \ac{SCA} approach converges to a unique limit point in each \ac{AO} step \eqn{{i}}}.
 However, to ensure strict monotonicity of the objective sequence, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}.
@@
 The \ac{AO} update follows \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}}.
-
 Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured.
 It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.
-
-\begin{comment}
-\begin{equation} \label{strict_monotonicity}
-f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
-\end{equation}
-
-Note that the \ac{AO} and \ac{SCA} procedures generate a nonincreasing sequence of objectives for the original objective in \eqref{orig_obj} using the above discussions.
-However, by using the regularized objective in \eqref{mod_obj}, we can show that the sequence of objectives provided by \ac{AO} and \ac{SCA} steps is strictly decreasing.
-Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} \ac{SCA} step.
-Note that the objective \eqref{con-obj-m} is strongly convex with some parameter \eqn{m > 0}, and therefore \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}
-\begin{IEEEeqnarray}{l}
-f(\mbf{z}) \geq f(\iter{\mbf{z}}{k+1}{i}) + \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) + \tfrac{m}{2} \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2. \eqspace 
-\end{IEEEeqnarray}
-Since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer for \eqref{con-m} in the \eqn{\ith{k}} \ac{SCA} step, 
-\begin{IEEEeqnarray}{rCl} \neqsub \label{s_ineq_g}
-\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0, \quad \iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i} \eqsub \\
-f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& \tfrac{m}{2} \, \|\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}\|^2. \eqsub \label{s_ineq}
-\end{IEEEeqnarray}
-Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
-Using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{s_ineq_g}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured.
-However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.
-
-	In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj} with parameter \eqn{m > 0} as %We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{(k-1)}} solution \eqn{\mbf{z}^{(i)}_{k}} is a feasible point of \eqn{\mc{X}_{k}^{(i)}} in the \eqn{\ith{k}} \ac{SCA} step \cite{marks1978technical}.
-	%It follows by the strong convexity of \eqref{mod_obj} with \eqn{m > 0} in the \eqn{\ith{k}} update
-	\begin{equation} \label{strict_monotonicity}
-	f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \underbrace{\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i})}_{= 0} + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
-	\end{equation}
-	since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}.
-Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
-Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
-However, if \eqn{\hat{f}} is used as the objective in \eqref{con-m}, then strict monotonicity of \eqn{\{\hat{f}(\mbf{z}^{(i)}_k)\}} cannot be guaranteed due to the existence of multiple solutions.
-
-%Even though the original convex function \eqn{\hat{f}(\mbf{z})} can have multiple limit points upon the \ac{SCA} convergence, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point is unique, and therefore the objective decreases monotonically in a strict sense.
-It can be proved, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even if the other limit points are included in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}}, with the same \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
-%Let \eqn{\mbf{z}^{i}_{k}} be an unique minimizer and also a limit point of the \eqn{\ith{k}} \ac{SCA} step.
-Let \eqn{\mbf{z}^{i}_{k+1}} be another limit point with the same objective \eqn{\hat{f}(\mbf{z}^{i}_{k}) = \hat{f}(\mbf{z}^{i}_{k+1})} in the \eqn{\ith{k+1}} feasible set \eqn{\iter{\mc{X}}{k+1}{i}}.
-Due to the convexity of \eqn{\hat{f}(\mbf{z})}, strict monotonicity cannot be ensured since the selection of \eqn{\mbf{z}^{i}_{k}} and \eqn{\mbf{z}^{i}_{k+1}} are equally likely.
-However, due to the additional quadratic term \eqn{c \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} in \eqn{f(\mbf{z})} for the \eqn{\ith{k+1}} iteration, the update cannot choose \eqn{\mbf{z}^{i}_{k+1}} due to the positive quadratic residual, therefore, it selects the fixed point \eqn{\mbf{z}^{i}_{k}} in the \eqn{\ith{k+1}} iteration.
-Similarly, using the above argument, we can also prove the strict monotonicity of the objective in each \ac{AO} update \eqn{i}, and thereby proving strict monotonicity of the overall objective sequence.
-
-{Let \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be the solution of \eqref{con-m} in the \eqn{\ith{k-1}} \ac{SCA} step.
-In order to show the strict monotonicity of the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} method, we rely on the strong convexity of \eqref{mod_obj}.
-We know that the objective decreases in each \ac{SCA} step, since the \eqn{\ith{k}} solution \eqn{\mbf{z}^{(i)}_k} is a feasible point in \eqn{\mc{X}_{k+1}^{(i)}} of the \eqn{\ith{k+1}} iteration \cite{marks1978technical}.
-However, due to the strong convexity of \eqref{mod_obj}, it follows that \eqn{\forall \mbf{z} \in \mc{X}^{(i)}_{k}}
-	\begin{equation} \label{strict_monotonicity}
-	f(\mbf{z}) \geq f(\mbf{z}_{k}^{(i)}) + \nabla f(\mbf{z}_{k}^{(i)})^\tran (\mbf{z} - \mbf{z}_{k}^{(i)}) + c \, \|\mbf{z} - \mbf{z}_{k}^{(i)}\|^2
-	\end{equation}
-	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\rightarrow\infty}, \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}}.
-Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
-However, if \eqn{\hat{f}} is used in the objective of \eqref{con-m}, then the limit point is not unique, \textit{i.e.}, \eqn{\{\exists \mbf{z} \in \mc{X}_{\lpoint}^{(i)} \vert \hat{f}(\mbf{z}) = \hat{f}(\mbf{z}_{\lpoint}^{(i)})\}}, and therefore the sequence generated by \eqref{con-m} with \eqn{\hat{f}} is not strictly monotonic.
-
-	Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration.
-Since the limit point \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\lpoint}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}
-
-%Due to the convexity in the original objective \eqn{\hat{f}(\mbf{z})}, it can have multiple limit points for the \ac{SCA} update, and therefore it follows \eqn{f(\mbf{z}^{(i)}_{k+1}) \leq f(\mbf{z}^{(i)}_k), \forall k}.
-However, due to the strong convexity of \eqn{f(\mbf{z})} in \eqref{mod_obj}, the limit point of the \ac{SCA} updates is also unique, and therefore has strict monotonicity in \eqn{f(\mbf{z}^{(i)}_k)} after each update.
-It can be justified, if \eqn{f(\mbf{z}^{(i)}_k)} is the unique minimizer in two consecutive steps even by including other limit points in the feasible set \eqn{\iter{\mc{X}}{k+1}{i}} with the same original objective value as \eqn{\hat{f}(\mbf{z}^{(i)}_{k})}.
-%In spite of choosing \eqn{\mbf{z}_{k}^{(i)}} in both \eqn{k} and \eqn{k+1} iteration, \eqn{f(\mbf{z})} decreases strictly due to the vanishing quadratic term in the \eqn{\ith{k+1}} step, therefore, it is a fixed point.
-Similarly, by using the above argument, we can also prove the strict monotonicity of the objective in each \ac{AO} update, and thereby proving strict monotonicity of the overall sequence.
-%In spite of the additional quadratic term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} to ensure unique minimizer, strict monotonicity of the objective in each \ac{SCA} update cannot be ensured.
-However, strict monotonicity can be guaranteed in each update \eqn{i} of the algorithm \me{\mc{A}} in \eqref{g-algo} for the objective.
-Using (a),(b),(c) along with the above discussion, we can ensure strict monotonicity and the convergence of the objective.}
-%Due to the additional quadratic term \eqn{\| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2} from the earlier iteration and the unique minimizer from the previous step is also included, the objective decreases strictly in each \ac{SCA} update for an arbitrary value of \eqn{c} in \eqref{mod_obj}.
-Therefore, in each update \eqn{i} of the algorithm \me{\mc{A}} in \ref{g-algo}, the objective decreases monotonically in strict sense.
-Using (a),(b),(c) along with the above discussion, we can ensure strict monotonicity and the convergence of the objective.}
-\end{comment}
 
@@
 
-%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.
 Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
@@
 3.6]{rudin1964principles}.
-Since there can be possibly two subsequences of \eqn{\{\ma^t\}} that converges to two different limit points, the sequence of iterates \eqn{\{\ma^t\}} need not be convergent sequence.
+Note that the sequence of iterates \eqn{\{\ma^t\}} need not be a convergent sequence, as there can possibly be two subsequences of \eqn{\{\ma^t\}} that converges to different limit points.
 
@@
 Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
-
-%The above discussion also considers \ac{AO} step, since in between each \ac{AO} update, the objective sequence is strictly monotonic \eqref{fixed_point} and it follows \cite[Prop.
-2.7.1]{bertsekas1999nonlinear}.
 
@@
 2 and 11]{scutari_1} and \cite[Prop.
-3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the algorithm is a stationary point of problem \eqref{con}.}
-
-\begin{comment}
-However, it is not the case with the sequence of iterates \eqn{\{\iter{\ma}{k}{i}\}}, since there can be two different convergent subsequences that has the, say, \eqn{\{\iter{\ma}{k}{i}\}_{k,i \in \mc{Q}_1}} and \eqn{\{\iter{\ma}{k}{i}\}_{k,i \in \mc{Q}_2}} such that
-
-Let \me{\ma^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}]} be the stacked vector of the solution point from the \eqn{\ith{i}} \ac{AO} iteration and let \me{\mc{A}} be a point-to-set mapping algorithm defined as
-\begin{equation} \label{g-algo}
-\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) \triangleq
-\begin{cases}
-\underset{\mx,\mz}{\mathrm{argmin}} \; f(\mx,\mz;\iter{\my}{\lpoint}{i-1})& \forall \mx,\mz \in \iter{\mc{X}}{\lpoint}{i} \\
-\underset{\my,\mz}{\mathrm{argmin}} \; f(\my,\mz;\iter{\mx}{\lpoint}{i})& \forall \my,\mz \in \iter{\mc{Y}}{\lpoint}{i} 
-\end{cases} 
-\end{equation}
-Note that in each iteration \me{i}, the algorithm \eqn{\mc{A}} in \eqref{g-algo} includes two \ac{SCA} updates performed until convergence, \textit{i.e.}, one for variable \me{\mx} and \me{\mz} by keeping \me{\my} fixed and another for \me{\my} and \me{\mz} by fixing \me{\mx} as constant.
-Since the minimizer is unique, the mapping can be defined as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})}.
-In order to prove the convergence of the beamformer iterates, we define \me{\mc{F}^\lpoint \subset \mc{F}} as the set of fixed points, \textit{i.e.}, \me{\forall {\ma}^{\lpoint} \in \mc{F}^\lpoint, \, {\ma}^{\lpoint} = \mc{A}({\ma}^{\lpoint})}, identified by the algorithm \me{\mc{A}} for different initialization points.
-
-Using \cite[Th. 3.1]{meyer1976sufficient}, convergence of the iterates to a fixed point can be shown, if the following conditions are satisfied.
-\begin{itemize}
-\item Objective function \me{f} should be bounded and continuous.
-\item Feasible set \me{\iter{\mc{X}}{\lpoint}{i},\iter{\mc{Y}}{\lpoint}{i}} in each step should be compact.
-\item The sequence \me{\{\iterate{\ma}{i}\}} generated by \me{\mc{A}} should be strictly monotonic with respect to the objective \me{f}, \textit{i.e.}, \me{\ma^\prime = \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point.
-\end{itemize}
-\review{Note that the strict monotonicity of the objective is guaranteed using the strong convexity of \eqn{f} in Section \ref{mcity}.
-Therefore, all the above requirements are satisfied by algorithm \eqref{g-algo}}.
-Using \cite{zangwill1969nonlinear} and \cite[Th.
-3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point, and (iii) \eqn{\ma^\lpoint} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
-Even though the fixed points in the set \me{\mc{F}^\lpoint} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e.}, \me{\mc{F}^\lpoint = \{\ma^\lpoint\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
-
-\begin{comment}
-	Note that the above conditions are satisfied by the algorithm \me{\mc{A}} in \eqref{g-algo} and the strict monotonicity of the objective sequence is guaranteed in Section \ref{mcity} using strong convexity of \eqn{f}}.
-and \me{\mc{A}} be a point-to-set mapping algorithm from \me{\mc{F}} into the nonempty subsets of \me{\mc{F}}, \textit{i.e.}, \eqn{\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i})}.
-The set of accumulation or the limit points in the compact set \me{\mc{F}} be denoted by \me{\mc{F}^\lpoint} and the objective function be \me{f} is closed and continuous.
-Let \me{\{\iterate{\ma}{i}\}} be the sequence of iterates generated by the algorithm \me{\mc{A}} and the objective function \me{f}.
-If the mapping is strictly monotonic and uniformly compact, then the following conditions hold \cite{zangwill1969nonlinear} and \cite[Theorem 3.1]{meyer1976sufficient}.
-\begin{itemize}
-\item[(i)] all accumulation points will be a fixed point,
-\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point,
-\item[(iii)] \eqn{\ma^\lpoint} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
-\end{itemize}
-
-To show that the proposed iterative method satisfies the above conditions,  the mapping \eqn{\mc{A}} for the iterative algorithm is given by
-\begin{equation}
-\iterate{\ma}{i+1} \in \mc{A}(\iterate{\ma}{i}) : \underset{\ma}{\mathrm{argmin}} \; f(\ma;\iterate{\ma}{i}) \; \forall \ma \in \iterate{\mc{X}}{i} \subset \mc{F}
-\end{equation}
-where \me{\mc{A}(\iterate{\ma}{i})} denotes the set of iterates in the subset \me{\iterate{\mc{X}}{i}}, which has the same objective value under the mapping \me{f} in the \me{\ith{i}} iteration The monotonicity of the proposed algorithm is guaranteed based on the arguments presented in Appendix \ref{mcity}.
-The mapping is strictly monotonic on \me{\mc{F}} with respect to the objective function as \me{\ma^\prime \in \mc{A}(\ma)} implies \me{f(\ma^\prime) < f(\ma)} whenever \me{\ma} is not a fixed point, \textit{i.e.}, \me{\ma \notin \mc{F}^\lpoint}, as in \eqref{fixed_point}.
-Using the above discussions, we can show that the sequence \me{\{\iterate{\ma}{i}\}} converges to a fixed point in the set \me{\mc{F}^\lpoint} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}
-
-The sequence \me{\{\iterate{\ma}{i}\}} converges to the set of fixed points \me{\mc{F}^\lpoint} for any feasible starting point \me{\iterate{\ma}{0} \in \mc{F}}, therefore the mapping is uniformly compact.
-
-To show the set of fixed points \me{\mc{F}^\lpoint} are the minimizers for the objective function \me{f}, we rely on the strict monotonicity of the objective function for each iteration.
-Since \me{f(\mc{A}(\iterate{\ma}{i})) < f(\iterate{\ma}{i})}, the objective decreases monotonically for each iteration and the equality is achieved when \me{\ma^\lpoint \in \mc{A}(\ma^\lpoint)}, which is a generalized fixed point.
-Therefore, the fixed points in \me{\mc{F}^\lpoint} are the minimizers for the objective function \me{f} over the set \me{\mc{F}}.
-
-If the uniqueness of the iterates are guaranteed, then the algorithm will find a unique solution at each iteration as \me{\iterate{\ma}{i+1} = \mc{A}(\iterate{\ma}{i})} and the accumulation point is unique.
-The convergence of the iterates to a single fixed point is guaranteed by the discussions in \cite{zangwill1969nonlinear,meyer1976sufficient}.
-Even though the algorithm finds a single fixed point, all fixed points in \me{\mc{F}^\lpoint} are equally valid as a minimizer for the function \me{f} in \eqref{con}, since the \ac{SINR} in \eqref{eq:SINR} is invariant to the unitary rotations on the beamformers.
-\end{comment}
-
-\begin{comment}
-%\subsection{Stationary Points of the Nonconvex Problem}
-\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\lpoint}} as \eqn{i \rightarrow \infty}.
-Now, to show that \eqn{\ma^{\lpoint}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} gradient condition of \eqref{con}, \textit{i.e.},
-\begin{equation} \label{kkt_expr}
-\textstyle	\nabla \hat{f}(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla {g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
-\end{equation}
-for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\ma^{\lpoint} \in \mc{F}}.
-
-To prove the feasibility of the limit point \me{\ma^{\lpoint}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
-Therefore, the limit point \eqn{\ma^{\lpoint} \in \mc{F}} and it satisfies the Slater's constraint qualifications.
-Moreover, as discussed in Appendix \ref{c-b}, \eqn{\ma^{\lpoint}} is a regular point of the algorithm \eqn{\mc{A}} and also the solution for \eqref{con-m}.
-Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
-\begin{equation} \label{kkt_mod_expr}
-\textstyle \nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
-\end{equation}
-The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\lpoint}}, since \eqn{\ma^{\lpoint}} is the fixed point of \eqn{\mc{A}}.
-Therefore, the gradient evaluated at \eqn{\ma^{\lpoint}} satisfy \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})}.
-(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\ma^{\lpoint}} is given as
-\begin{equation} \label{rhs_equiv}
-\nabla h(\ma^{\lpoint}) - \nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\mbf{\ma}^{\lpoint}) = \nabla h(\ma^{\lpoint}) - \nabla g_o(\mbf{\ma}^{\lpoint}).
-\end{equation}
-Now, by applying the relation in \eqref{rhs_equiv} and \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\ma^{\lpoint}} satisfies \eqref{kkt_expr}.
-By using \cite[Thms.
-2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} is a stationary point of the problem in \eqref{con}.}
-\end{comment}
-\begin{comment}
-In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
-In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
-Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\lpoint^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\lpoint}} satisfies the constraint qualifications of the problem \eqref{con}.
-
-To show that the limit point \eqn{\mbf{\ma}^{\lpoint}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\lpoint}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
-Therefore, it satisfies the \ac{KKT} conditions of the convex subproblem for some Lagrange multipliers \eqn{\mu_i \geq 0} as
-\begin{equation} \label{kkt_expr}
-\textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
-\end{equation}
-It is evident that the modified objective \eqn{f} and the convex function \eqn{\hat{f}} in \eqref{mod_obj} are equal at the limit point due to the vanishing quadratic penalty term.
-Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\mbf{\ma}^{\lpoint}) = \nabla g_o(\mbf{\ma}^{\lpoint})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\lpoint}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
-Now, by using \cite[Th.
-2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that all the limit points of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
-
-\review{Let \eqn{\ma^{\lpoint}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}.
-The limit point \eqn{\ma^\lpoint} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions.
-%and there exists no descent direction in the feasible set as
-%\begin{equation}
-%\nabla {f}(\ma^{\lpoint})^\tran \, (\ma - \ma^{\lpoint}) \geq 0, \: \forall \, \ma \in \mc{Y}^{\lpoint}
-%\end{equation}
-%where \eqn{\mc{Y}^{\lpoint}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\lpoint}^{i}} as \eqn{i \rightarrow \infty}. 
-Let us consider the problem in \eqref{con-m}.
-Using \eqref{con-relax}, we can show that the feasible set \eqn{\mc{Y}_{\lpoint}^{i}} in each \ac{AO} iteration \eqn{i} is a subset of \eqn{\mc{F}}.
-Therefore, all iterates \eqn{\{\iterate{\ma}{i}\}} of the algorithm \eqn{\mc{A}} are feasible.
-Additionally, by the strong convexity of \eqn{f(\ma)}, following conditions are satisfied.
-\begin{IEEEeqnarray}{rCl}  \neqsub \label{strong_cvxty}
-\nabla {f}(\ma^{(i)})^\tran \, (\ma^{(i-1)} - \ma^{(i)}) &\geq& 0 \eqsub \\
-f(\ma^{(i-1)}) - f(\ma^{(i)}) &\geq& c \: \|\ma^{(i-1)} - \ma^{(i)}\|^2. \eqsub
-\end{IEEEeqnarray}
-Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \mc{A}(\ma^{(i)})\| \rightarrow 0} as \eqn{i \rightarrow \infty}, which is the limit point of the algorithm \eqn{\mc{A}}.
-
-Now, it remains to show that the \eqn{\ma^{\lpoint}} is a stationary point of the nonconvex problem \eqref{con}.
-To see this, we note that \eqn{\ma^{\lpoint}} must satisfy the \ac{KKT} conditions of \eqref{con}.
-Since \eqn{\ma^{\lpoint}} is the fixed point of the algorithm \eqn{\mc{A}}, it satisfies the \ac{KKT} conditions of the convex subproblem \eqref{con-m} given by
-\begin{equation} \label{kkt_expr}
-\textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
-\end{equation}
-for some Lagrange multipliers \eqn{\mu_i \geq 0}.
-Using the equivalence between \eqn{\hat{f}(\ma^{\lpoint}) = f(\ma^{\lpoint})} and the relation in \eqref{con-relax} in \eqref{kkt_expr}, we can see that \eqref{kkt_expr} is indeed the \ac{KKT} condition for the nonconvex problem \eqref{con}.
-Since the gradient is zero in \eqref{kkt_expr}, the objective cannot be decreased any further.
-Now, by using \cite[Th.
-2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that the limit points \eqn{\ma^\lpoint} of \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.}
-
-%In order for \eqn{\ma^{\lpoint}} to be stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con}.
-In each iteration, the algorithm \eqn{\mc{A}} in \eqref{g-algo} finds a point \eqn{\iterate{\ma}{i} \in \mc{F}} with \eqn{f(\iterate{\ma}{i}) < f(\iterate{\ma}{i-1})}, therefore, it satisfies all the constraints of \eqref{con}.
-Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \rightarrow \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\lpoint}) = \ma^{\lpoint}} finds a unique \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}} due to the strong convexity of \eqn{f}.
-
-%To show the equivalence in the gradients of \eqref{con} and \eqref{con-m} at \eqn{\ma^{\lpoint}}, let us consider the limit point of the \ac{SCA} update in \eqn{\mc{A}} as it converges to a fixed point \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}}.
-The \ac{KKT} expression for the convex subproblem \eqref{con-cvx} is given by
-%\begin{equation} \label{kkt_expr}
-%\nabla f(\ma^{\lpoint}) + \mu_1 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0
-%\end{equation}
-%for some Lagrange multipliers \eqn{\mu_i \geq 0}.
-Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}.
-Moreover, \eqn{\ma^{\lpoint}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}.
-Now, with the above conditions and by using \cite[Th.
-2 and 11]{scutari_1} and \cite[Prop.
-3.2]{amir}, we can show that the fixed points obtained by \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
-
-\begin{comment}
-To show the limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}.
-As \me{i \rightarrow \infty}, the objective converges as
-\iftoggle{single_column}{
-\begin{equation} \label{con-opt}\allowdisplaybreaks
-f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|x}{i}) = f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|y}{i+1}) = 
-f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1})
-\end{equation}}{
-\begin{multline} \label{con-opt}\allowdisplaybreaks
-f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|x}{i}) = f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|y}{i+1}) \\ = 
-f(\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1})
-\end{multline}}
-where \me{\{\iter{\mx}{\lpoint}{i+1},\iter{\my}{\lpoint}{i+1},\iter{\mz}{\lpoint|x}{i+1}\} \in \mc{F}^\lpoint} is a limit point of \me{\mc{A}} for a given initial point.
-Since the function \eqn{f} is strongly convex, the limit point is unique.
-As discussed in Appendix \ref{c-b}, the unique limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a fixed point of \me{\mc{A}}.
-
-Using \cite[Th.
-10]{lanckriet2009convergence} and \cite[Th.
-2 and 11]{scutari_1}, we can show that the fixed points obtained by the algorithm \me{\mc{A}} under the mapping \me{f} is a stationary point of the nonconvex problem \eqref{con}.
-
- In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
-In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
-Note that all points satisfies \eqn{\iterate{\ma}{i} \in \mc{Y}_\lpoint^{(i)} \subset \mc{F}}, and therefore the limit point \eqn{\ma^{\lpoint}} satisfies the constraint qualifications of the problem \eqref{con}.
-
- To show that the limit point \eqn{\mbf{\ma}^{\lpoint}} satisfies the \ac{KKT} expression of the nonconvex problem, we utilize the fact that the limit point \eqn{\mbf{\ma}^{\lpoint}} is the solution of the convex subproblem \eqref{con-m} upon convergence.
-Therefore, it satisfies the \ac{KKT} conditions of the convex subproblem for some Lagrange multipliers \eqn{\mu_i \geq 0} as
- \begin{equation} \label{kkt_expr}
- \textstyle	\nabla f(\ma^{\lpoint}) + \mu_0 \big [ \nabla h(\ma^{\lpoint}) - \nabla\hat{g}_0(\ma^{\lpoint};\ma^{\lpoint}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\ma^{\lpoint}) = 0.
- \end{equation}
- It is evident that the modified objective \eqn{f} and the convex function \eqn{\hat{f}} in \eqref{mod_obj} are equal at the limit point due to the vanishing quadratic penalty term.
-Now, by utilizing the relation \eqn{\nabla \hat{g}_o(\mbf{\ma}^{\lpoint};\iterate{\ma}{\lpoint}) = \nabla g_o(\mbf{\ma}^{\lpoint})} between the \ac{DC} constraint \eqref{con-dc} and the corresponding convex approximation in \eqref{con-relax}, we can ensure that the limit point \eqn{\mbf{\ma}^{\lpoint}} indeed satisfies the \ac{KKT} condition of the nonconvex problem \eqref{con}.
-Now, by using \cite[Th.
-2 and 11]{scutari_1} or \cite[Prop.
-3.2]{amir}, we can show that all the limit points of the sequence \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \me{\mc{A}} are the \ac{KKT} points of \eqref{con}.
-\end{comment}
+3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iteration method is a stationary point of problem \eqref{con}.

### 2015-10-22 Report/convergence_centralized.tex
updated proof

@@
 Therefore, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
-To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
-It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
+To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
+It follows from Appendices \ref{c-a} and \ref{mcity} that
 \begin{equation} \label{seq_mon}
@@
 \end{equation}
-Eq.
-\eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
+Note that \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
 Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain
 \begin{equation} \label{limpoint}
-\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma}).
+\lim_{t \rightarrow \infty} f(\ma^{t}) = \lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma})
 \end{equation}
-Using strict monotonicity in \eqn{\{f(\ma^{t_j})\}} and the fact that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0}, we can show that limit point \eqn{\bar{\ma}} satisfies the optimality condition \cite[Prop.
-2.1.2]{bertsekas1999nonlinear} as
+and therefore \eqn{\bar{\ma}} is a limit point of the sequence \eqn{\{\ma^t\}}.
+
+In order to show that \eqn{\bar{\ma}} is a stationary point, let us assume by contradiction that \eqn{\nabla f(\bar{\ma}) \neq 0}.
+Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \rightarrow \infty}, \eqn{\ma^{t_j} \rightarrow \bar{\ma}} and
+\eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \rightarrow 0}, which contradicts the initial assumption.
+Therefore, by using \eqref{seq_mon}, we can show that the limit point \eqn{\bar{\ma}} satisfies the optimality condition as
 \begin{equation} \label{seq_mon1}
@@
 where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
-Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
+Hence, \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.
 

### 2015-10-26 Report/convergence_centralized.tex
updated manuscript

@@
 \review{The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}.
-However, to ensure strict monotonicity of the objective sequence, we require condition (d).
-Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of the objective sequence can be shown by using \cite[Th.
+However, to ensure strict monotonicity of the objective sequence, we require the additional condition (d).
+Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of the objective sequence can be shown using \cite[Th.
 3.14]{rudin1964principles}.
 Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}.
-The term iterates denotes the stacked vector of solution variables obtained in each iteration.}
+The term iterates correspond to the stacked vector of solution variables obtained in each iteration.}
 
@@
 
-\review{We use the following notations to discuss the convergence proof.
-Since Algorithm \ref{algo-1} involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
-Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1} respectively.
-Since Algorithm \ref{algo-1} includes two \ac{SCA} iterations performed until convergence in each \ac{AO} iteration, let us now consider \ac{AO} step \eqn{i} for fixed \eqn{\my}.
-The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented as \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
-As \eqn{k \rightarrow \infty}, the objective sequence converges, and the corresponding solution obtained is denoted as \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
-Similarly, for fixed \eqn{\mx} and as \eqn{k \rightarrow \infty}, the corresponding solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}} respectively.}
+\review{We use following notations to analyze the convergence behavior of the algorithm presented in Algorithm \ref{algo-1}.
+Since it involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
+Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1}.
+Let us consider \ac{AO} step \eqn{i} with fixed \eqn{\my}.
+The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented by \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
+As \eqn{k \rightarrow \infty}, the objective sequence converges, and the corresponding solution obtained is denoted by \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
+Similarly, while alternating the optimization variables with fixed \eqn{\mx}, as \eqn{k \rightarrow \infty}, the solution is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}.
+In the following, we show that the conditions listed in (a)-(d) are satisfied by Algorithm \ref{algo-1}.}
 
@@
 \subsection{Stationarity of Limit Points} \label{c-b}
-
-In this section, we discuss the convergence of the sequence of iterates generated by the iterative algorithm.
-In order to do so, let us use single global index \eqn{t} to represent both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}.
-Using this, we can represent \eqn{\ma^{t} \triangleq [\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k|\my}{i}]} as a stacked vector of solution obtained in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} update with fixed \eqn{\my}.
-The index \eqn{t} is used to represent both \ac{SCA} updates involving transmit and receive beamformers within each \ac{AO} step.
+\reviewF{In this section, we discuss the convergence of sequence of iterates generated by the iterative algorithm.
+In order to do so, let us use single global index \eqn{t} that represents both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}.
+Using this, we represent \eqn{\ma^{t}} as a stacked vector of solution variables obtained in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
+Note that it includes both \ac{SCA} steps involving transmit and receive beamformers in each \ac{AO} step.
 
@@
 3.6]{rudin1964principles}.
-Note that the sequence of iterates \eqn{\{\ma^t\}} need not be a convergent sequence, as there can possibly be two subsequences of \eqn{\{\ma^t\}} that converges to different limit points.
+Note that the sequence of iterates \eqn{\{\ma^t\}} need not be convergent, as there can possibly be two subsequences of \eqn{\{\ma^t\}} that converges to different limit points.
 
@@
 
-In order to show that \eqn{\bar{\ma}} is a stationary point, let us assume by contradiction that \eqn{\nabla f(\bar{\ma}) \neq 0}.
-Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \rightarrow \infty}, \eqn{\ma^{t_j} \rightarrow \bar{\ma}} and
-\eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \rightarrow 0}, which contradicts the initial assumption.
-Therefore, by using \eqref{seq_mon}, we can show that the limit point \eqn{\bar{\ma}} satisfies the optimality condition as
+In order to show that \eqn{\bar{\ma}} is a stationary point, \eqn{\bar{\ma}} should satisfy the optimality condition in \cite[Prop.
+2.1.2]{bertsekas1999nonlinear}.
+Again, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \rightarrow \infty}, \eqn{\ma^{t_j} \rightarrow \bar{\ma}} and
+\eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \rightarrow 0}.
+Moreover, since \eqn{\bar{\ma}} is a solution for subproblem \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which is defined as \eqn{\iter{\mc{X}}{k}{i}} and \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
+Therefore, \eqn{\bar{\ma}} satisfies the optimality condition
 \begin{equation} \label{seq_mon1}
-\nabla f (\bar{\ma}) (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub
+\nabla f (\bar{\ma}) (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \in \mc{F} \eqsub
 \end{equation}
-where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
-Hence, \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.
+and hence limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.
 
-Now to show that \eqn{\bar{\ma}} is a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between the gradient of the subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}.
+Now to show that \eqn{\bar{\ma}} is a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between gradients of subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}.
 In order to show that \eqn{\bar{\ma}} is a \ac{KKT} point for \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
@@
 
-To prove the feasibility of the limit point \me{\bar{\ma}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}.
-Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}}.
-Since \eqn{\bar{\ma}} satisfies Slater's constraint qualifications, there exist Lagrange multipliers \eqn{\mu_i} such that
+Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}.
+Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}.
+Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \rightarrow \infty,i \rightarrow \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
 \begin{equation} \label{kkt_mod_expr}
@@
 Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
-(ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\bar{\ma}} is given as
+(ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \rightarrow \bar{\ma}}
 \begin{equation} \label{rhs_equiv}
@@
 \end{equation}
-Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
-By using \cite[Thms.
-2 and 11]{scutari_1} and \cite[Prop.
-3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iteration method is a stationary point of problem \eqref{con}.
+Now, by using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+Using \cite[Thms.
+2 and 11]{scutari_1},\cite[Prop.
+3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}

### 2015-10-26 Report/convergence_distributed.tex
updated manuscript

@@
 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}.
-Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}
+Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as discussed in Appendix \ref{sec-3.5}.}
 

### 2015-10-26 Report/dual_approach.tex
updated manuscript

@@
 The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
-However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, \reviewF{then the convergence discussions follows Appendices \ref{sec-3.5} and \ref{sec-dist-conv}}.
+However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, \reviewF{then the convergence follows the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}}.
 Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured.

### 2015-10-26 Report/kkt_mse_approach.tex
updated manuscript

@@
 In contrast to Sections \ref{sec-4.1} and \ref{sec-4.2}, the problem is solved using the \ac{KKT} conditions in which the transmit precoders, receive beamformers and the subgradient updates are performed at the same time to minimize the queue deviation with few number of iterations.
-The alternative way is motivated by the fact that the distributed approaches presented in the preceeding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.
+The alternative way is motivated by the fact that distributed approaches presented in the preceding sections may not be efficient for large systems in terms of signaling overhead involved in exchanging the coupling variables and the receivers.
 
@@
 In the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints.
-However, due to the non-differentiability of the objective, the \ac{KKT} conditions are not computationally useful to find the optimization variables.
-In order to make the objective function differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the optimal solution, namely,
+However, due to the non-differentiability of objective, the \ac{KKT} conditions are not computationally useful to find the optimization variables.
+In order to make the objective function differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the problem, namely,
 \begin{itemize}
@@
 
-With the assumption of either one of the above conditions, the problem in \eqref{eqn-mse-2} can be written as
+With the assumption that either one of the above conditions, the problem in \eqref{eqn-mse-2} can be written as
 \allowdisplaybreaks\iftoggle{single_column}{

### 2015-10-26 Report/wsrm_formulation.tex
updated manuscript

@@
 Note that in all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges.
-\reviewF{However, to analyze the convergence of the sequence of beamformer iterates}, we consider a modified objective \eqref{mod_obj} with a quadratic term instead of \eqref{eqn-6.1}.
+\reviewF{However, to analyze the convergence of the sequence of beamformer iterates}, we consider modified objective \eqref{mod_obj} with a quadratic term instead of \eqref{eqn-6.1}.
 Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.

### 2015-10-28 Report/convergence_centralized.tex
updated stationarity

@@
 The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented as \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
-As \eqn{k \rightarrow \infty}, the objective sequence converges, and the corresponding solution obtained is denoted as \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
-Similarly, for fixed \eqn{\mx} and as \eqn{k \rightarrow \infty}, the corresponding solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}} respectively.}
+As \eqn{k \to \infty}, the objective sequence converges, and the corresponding solution obtained is denoted as \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
+Similarly, for fixed \eqn{\mx} and as \eqn{k \to \infty}, the corresponding solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}} respectively.}
 %
@@
 The objective function is bounded from above as well, since the feasible set is bounded.
-%The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \rightarrow \infty}, and therefore it is coercive in the feasible set.
+%The objective function in \eqref{eqn-6} and \eqref{eqn-mse-1} is continuous and approaches \me{\infty} as \me{\mbf{t}_k \to \infty}, and therefore it is coercive in the feasible set.
 %Using conditions (a) and (b), we can guarantee the existence of a minimizer to the problem in \eqref{eqn-6} and \eqref{eqn-mse-1}.
@@
 %since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
-Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
+Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}.
 Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
@@
 %\end{IEEEeqnarray}
-%Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
+%Note that \eqref{s_ineq} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}.
 Using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic \cite{marks1978technical}, and (ii) the uniqueness of the minimizer (see \eqref{s_ineq_g}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured.
@@
 %	since \eqn{\iter{\mbf{z}}{k+1}{i}} is the minimizer of \eqref{con-m}.
-Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
+Note that \eqref{strict_monotonicity} holds with strict inequality in each update as \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})}, unless \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, which occurs at \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}.
 Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
@@
 %	\end{equation}
-%	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\rightarrow\infty}, \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}}.
+%	where the equality is valid when \eqn{\mbf{z}_{k}^{(i)} = \mbf{z}_{k+1}^{(i)}}, \textit{i.e.}, as \eqn{k\to\infty}, \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}}.
 Using the facts that (i) the sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} generated by the \ac{SCA} approach is monotonic \cite{marks1978technical}, and  (ii) the uniqueness of the minimizer in each \ac{SCA} step (see \eqref{strict_monotonicity}), we can ensure the strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}}.
@@
 %	Similarly, we can ensure strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} iteration.
-Since the limit point \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\lpoint}^{i} \}} converges to a limit point as \eqn{i \rightarrow \infty}.}
+Since the limit point \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\mx}{i}\}} is also included in the feasible set \eqn{\mc{Y}_{0}^{i}}, the objective function follows \eqref{fixed_point} in strict sense unless the overall sequence \eqn{\{\mbf{z}_{\lpoint}^{i} \}} converges to a limit point as \eqn{i \to \infty}.}
 %
@@
 %
-%%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.
+%%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \to \infty}, \eqn{\|\ma - \ma^t\|^2 \to 0}.
 %Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
@@
 %Therefore, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
-To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
+To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}}.
 It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
@@
 \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
-Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain
+Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
 %\begin{equation} \label{limpoint}
-%\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma}).
+%\lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).
 %\end{equation}
-%Using strict monotonicity in \eqn{\{f(\ma^{t_j})\}} and the fact that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0}, we can show that limit point \eqn{\bar{\ma}} satisfies the optimality condition \cite[Prop.
+%Using strict monotonicity in \eqn{\{f(\ma^{t_j})\}} and the fact that as \eqn{j \to \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \to 0}, we can show that limit point \eqn{\bar{\ma}} satisfies the optimality condition \cite[Prop.
 2.1.2]{bertsekas1999nonlinear} as
@@
 %\end{equation}
-%where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
-Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
+%where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \to \infty, i \to \infty}.
+Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \to \infty, i \to \infty}.
 %
@@
 %\end{equation}
-%The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}.
+%The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}.
 Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
@@
 Using \cite{zangwill1969nonlinear} and \cite[Th.
-3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point, and (iii) \eqn{\ma^\lpoint} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \rightarrow 0}.
+3.1]{meyer1976sufficient}, we can show that (i) all limit points will be a fixed point, (ii) \eqn{f(\iterate{\ma}{i}) \to f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point, and (iii) \eqn{\ma^\lpoint} is a regular point, \textit{i.e.}, \eqn{\|\iterate{\ma}{i} - \mc{A}(\iterate{\ma}{i}) \| \to 0}.
 Even though the fixed points in the set \me{\mc{F}^\lpoint} can be achieved by the algorithm \me{\mc{A}} for different initial points, the algorithm \me{\mc{A}} achieves a unique limit point, \textit{i.e.}, \me{\mc{F}^\lpoint = \{\ma^\lpoint\}}, once a feasible point is chosen to be the operating point while initializing \me{\mc{A}}.
@@
 %\item[(i)] all accumulation points will be a fixed point,
-%\item[(ii)] \eqn{f(\iterate{\ma}{i}) \rightarrow f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point,
-%\item[(iii)] \eqn{\ma^\lpoint} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0}.
+%\item[(ii)] \eqn{f(\iterate{\ma}{i}) \to f(\ma^\lpoint)}, where \eqn{\ma^\lpoint} is a fixed point,
+%\item[(iii)] \eqn{\ma^\lpoint} is a regular point, \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \to 0}.
 %\end{itemize}
@@
 %%\subsection{Stationary Points of the Nonconvex Problem}
-%\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\lpoint}} as \eqn{i \rightarrow \infty}.
+%\review{Upon satisfying the conditions (a)-(d), we have shown that the sequence \eqn{\{\iterate{\ma}{i}\}} generated by \eqn{\mc{A}} converges to a limit point \eqn{\ma^{\lpoint}} as \eqn{i \to \infty}.
 Now, to show that \eqn{\ma^{\lpoint}} is a stationary point of \eqref{con}, it must satisfy the \ac{KKT} gradient condition of \eqref{con}, \textit{i.e.},
@@
 %\end{equation}
-%The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \rightarrow \infty, \ma^{(i)} \rightarrow \ma^{\lpoint}}, since \eqn{\ma^{\lpoint}} is the fixed point of \eqn{\mc{A}}.
+%The relation between \eqref{kkt_mod_expr} and \eqref{kkt_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{(i)}\|^2} in \eqref{mod_obj} vanishes as \eqn{i \to \infty, \ma^{(i)} \to \ma^{\lpoint}}, since \eqn{\ma^{\lpoint}} is the fixed point of \eqn{\mc{A}}.
 Therefore, the gradient evaluated at \eqn{\ma^{\lpoint}} satisfy \eqn{\nabla {f}(\ma^{\lpoint}) = \nabla \hat{f}(\ma^{\lpoint})}.
@@
 %\begin{comment}
-%In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
+%In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \to \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
 In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
@@
 %
-%\review{Let \eqn{\ma^{\lpoint}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \rightarrow \infty}.
+%\review{Let \eqn{\ma^{\lpoint}} be the limit point of the sequence of iterates \eqn{\{\iterate{\ma}{i}\}} generated by the algorithm \eqn{\mc{A}} as \eqn{i \to \infty}.
 The limit point \eqn{\ma^\lpoint} is a stationary point of \eqref{con} if it satisfies the \ac{KKT} conditions.
@@
 %%\end{equation}
-%%where \eqn{\mc{Y}^{\lpoint}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\lpoint}^{i}} as \eqn{i \rightarrow \infty}. 
+%%where \eqn{\mc{Y}^{\lpoint}} is the feasible set of \eqref{con-m} upon convergence, \textit{i.e.}, \eqn{\mc{Y}_{\lpoint}^{i}} as \eqn{i \to \infty}. 
 %Let us consider the problem in \eqref{con-m}.
@@
 %\end{IEEEeqnarray}
-%Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \mc{A}(\ma^{(i)})\| \rightarrow 0} as \eqn{i \rightarrow \infty}, which is the limit point of the algorithm \eqn{\mc{A}}.
+%Using (a),(b),(c) and (d), we can show that \eqn{\|\ma^{(i)} - \mc{A}(\ma^{(i)})\| \to 0} as \eqn{i \to \infty}, which is the limit point of the algorithm \eqn{\mc{A}}.
 %
@@
 In each iteration, the algorithm \eqn{\mc{A}} in \eqref{g-algo} finds a point \eqn{\iterate{\ma}{i} \in \mc{F}} with \eqn{f(\iterate{\ma}{i}) < f(\iterate{\ma}{i-1})}, therefore, it satisfies all the constraints of \eqref{con}.
-Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \rightarrow \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\lpoint}) = \ma^{\lpoint}} finds a unique \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}} due to the strong convexity of \eqn{f}.
+Since the feasible set is compact and strict monotonicity is ensured, as \eqn{i \to \infty}, the objective no longer decreases as the algorithm \eqn{\mc{A}(\ma^{\lpoint}) = \ma^{\lpoint}} finds a unique \eqn{\ma^{\lpoint} \in \mc{F}^{\lpoint}} due to the strong convexity of \eqn{f}.
 %
@@
 Using \eqref{con-relax} in \eqref{kkt_expr}, we can ensure the equivalence of the gradient between \eqref{con} and \eqref{con-m}.
-Moreover, \eqn{\ma^{\lpoint}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \rightarrow 0} as \eqn{i \rightarrow 0}.
+Moreover, \eqn{\ma^{\lpoint}} is a regular point \textit{i.e.} \eqn{\|\iterate{\ma}{i} - \iterate{\ma}{i+1} \| \to 0} as \eqn{i \to 0}.
 Now, with the above conditions and by using \cite[Th.
@@
 %To show the limit point of the sequence of iterates \me{\{\iterate{\ma}{i}\}} is a stationary point, it must satisfy the \ac{KKT} conditions of the problem in \eqref{con}.
-As \me{i \rightarrow \infty}, the objective converges as
+As \me{i \to \infty}, the objective converges as
 %\iftoggle{single_column}{
@@
 %
-%In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \rightarrow \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
+%In this section, we show that the limit point \eqn{\ma^{\lpoint}} of the sequence \eqn{\{\iterate{\ma}{i}\}}, obtained from \eqn{\mc{A}} as \eqn{i \to \infty} is a stationary point of the original nonconvex problem in \eqref{con}.
 In order for \eqn{\ma^{\lpoint}} to be a stationary point, it must satisfy the \ac{KKT} conditions of \eqref{con} and the Slater's constraint qualifications.
@@
 \end{itemize}
-\review{The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}.
-However, to ensure strict monotonicity of the objective sequence, we require the additional condition (d).
-Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of the objective sequence can be shown using \cite[Th.
-3.14]{rudin1964principles}.
-Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+\review{Note that condition (d) is required to ensure strict monotonicity of the objective sequence.
+Therefore, by using above conditions (a)-(c) along with \cite[Th.
+3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}.
+Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}.
 The term iterates correspond to the stacked vector of solution variables obtained in each iteration.}
@@
 \end{IEEEeqnarray}
-where the functions \me{g_2} and \me{\hat{f}} are convex, and the function \me{h} is linear.
-Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables.
-The constraint \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} respectively.
+where functions \me{g_2} and \me{\hat{f}} are convex, and function \me{h} is linear.
+Let \me{g_0} and \me{g_1} be a convex functions w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables.
+The constraint \eqref{con-dc} corresponds to either \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} represents to either  \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} correspondingly.
 Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
@@
 
-\review{We use following notations to analyze the convergence behavior of the algorithm presented in Algorithm \ref{algo-1}.
-Since it involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
-Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1}.
+\review{We use following notations to discuss the convergence of algorithm in Algorithm \ref{algo-1}.
+Since it involves two nested loops, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}.
+Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables used in \eqref{eqn-6} and \eqref{eqn-mse-1} respectively.
 Let us consider \ac{AO} step \eqn{i} with fixed \eqn{\my}.
-The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented by \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
-As \eqn{k \rightarrow \infty}, the objective sequence converges, and the corresponding solution obtained is denoted by \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
-Similarly, while alternating the optimization variables with fixed \eqn{\mx}, as \eqn{k \rightarrow \infty}, the solution is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}.
+The solution obtained in the \eqn{\ith{k}} \ac{SCA} step is given by \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
+As \eqn{k \to \infty}, objective sequence converges, and the respective solution is denoted by \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
+Similarly, while alternating the optimization variables for fixed \eqn{\mx}, as \eqn{k \to \infty}, the solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}.
 In the following, we show that the conditions listed in (a)-(d) are satisfied by Algorithm \ref{algo-1}.}
@@
 since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
-Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}.
+Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}.
 Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
@@
 \subsection{Stationarity of Limit Points} \label{c-b}
-\reviewF{In this section, we discuss the convergence of sequence of iterates generated by the iterative algorithm.
-In order to do so, let us use single global index \eqn{t} that represents both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}.
-Using this, we represent \eqn{\ma^{t}} as a stacked vector of solution variables obtained in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
-Note that it includes both \ac{SCA} steps involving transmit and receive beamformers in each \ac{AO} step.
+\reviewF{We discuss the convergence of whole sequence of iterates generated by the iterative algorithm.
+In order to do that, let us use single index \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}.
+It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
+Using global index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a stacked vector of solution variables obtained in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
 
-Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
-Note that similar claim cannot be made on the convergence of \eqn{\{\ma^t\}}, since the sequence need not be monotonic.
-However, due to the compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded.
+Using the arguments in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
+Similar claim cannot be made on the convergence of \eqn{\{\ma^t\}}.
+However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded.
 Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th.
@@
 Therefore, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
-To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}.
-It follows from Appendices \ref{c-a} and \ref{mcity} that
+To show that, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}.
+Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity} that
 \begin{equation} \label{seq_mon}
@@
 Note that \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}.
-Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain
+Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
 \begin{equation} \label{limpoint}
-\lim_{t \rightarrow \infty} f(\ma^{t}) = \lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma})
+\lim_{t \to \infty} f(\ma^{t}) = \lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).
 \end{equation}
-and therefore \eqn{\bar{\ma}} is a limit point of the sequence \eqn{\{\ma^t\}}.
+Similarly, we can show that for every limit point of \eqn{\{\ma^t\}}, there exists a convergent subsequence \eqn{\{\ma^{t_k}|k=0,1,\dotsc\}}, such that 
+\begin{equation} \label{limpoint1}
+\lim_{t \to \infty} f(\ma^{t}) = \lim_{k \to \infty} f(\ma^{t_k}) = f(\lim_{k \to \infty} \ma^{t_{k}}) = f(\hat{\ma}) = f(\bar{\ma})
+\end{equation}
+where \eqn{\lim_{k\to\infty}\ma^{t_k} \to \hat{\ma}} is another limit point of \eqn{\{\ma^t\}}.
 
-In order to show that \eqn{\bar{\ma}} is a stationary point, \eqn{\bar{\ma}} should satisfy the optimality condition in \cite[Prop.
-2.1.2]{bertsekas1999nonlinear}.
-Again, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \rightarrow \infty}, \eqn{\ma^{t_j} \rightarrow \bar{\ma}} and
-\eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \rightarrow 0}.
-Moreover, since \eqn{\bar{\ma}} is a solution for subproblem \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which is defined as \eqn{\iter{\mc{X}}{k}{i}} and \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.
-Therefore, \eqn{\bar{\ma}} satisfies the optimality condition
+Let us prove the stationarity of \eqn{\bar{\ma}} by contradiction.
+Assume that \eqn{\bar{\ma}} is not a stationary point, then there exist some other point \eqn{\ma^\prime}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}.
+Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point.
+However, by \eqref{limpoint} and \eqref{limpoint1}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of any convergent subsequence of \eqn{\{\ma^t\}}, which is a contradiction.
+
+Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}.
+Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}.
+Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop.
+2.1.2]{bertsekas1999nonlinear} as
 \begin{equation} \label{seq_mon1}
-\nabla f (\bar{\ma}) (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \in \mc{F} \eqsub
+\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
 \end{equation}
-and hence limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.
+Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint} and \eqref{limpoint1}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point.
 
-Now to show that \eqn{\bar{\ma}} is a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between gradients of subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}.
+Now to show that \eqn{\bar{\ma}} is also a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between gradients of subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}.
 In order to show that \eqn{\bar{\ma}} is a \ac{KKT} point for \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
@@
 Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}.
-Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \rightarrow \infty,i \rightarrow \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
+Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
 \begin{equation} \label{kkt_mod_expr}
@@
 \end{equation}
-The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}.
+The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}.
 Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
-(ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \rightarrow \bar{\ma}}
+(ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
 \begin{equation} \label{rhs_equiv}
@@
 \end{equation}
-Now, by using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
-Using \cite[Thms.
-2 and 11]{scutari_1},\cite[Prop.
+Now, by using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+Finally, using \cite[Thms.
+2 and 11]{scutari_1} and \cite[Prop.
 3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}

### 2015-10-28 Report/problem_formulation_intro.tex
updated stationarity

@@
-To minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation objective as
+In order to minimize the total number of backlogged packets, we consider minimizing the weighted \me{\ell_{q}}-norm of the queue deviation metric as
 \begin{equation} \label{eqn-4.2}
@@
 \end{equation}
-where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are the transmit precoders \me{\mvec{m}{l,k,n}} and the receivers \me{\mvec{w}{l,k,n}}.
+where \me{\gamma_{l,k,n}} is given by \eqref{eq:SINR} and the optimization variables are transmit precoders \me{\mvec{m}{l,k,n}} and receive beamformers \me{\mvec{w}{l,k,n}}.
 

### 2015-10-29 Report/mse_formulation.tex
final modifications
Updated draft with boundedness argument

@@
 The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
-The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.
+
+In all simulations, the objective of Algorithm \ref{algo-1} converges.
+\reviewF{However, to discuss the theoretical convergence of subproblems \eqref{eqn-9}, \eqref{eqn-9--1} and \eqref{eqn-mse-2}, following modifications are considered.
+(i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective with quadratic term as in \eqref{mod_obj} to ensure strong convexity in objective function.
+(ii) To guarantee the boundedness of feasible sets, we trivially bound \eqn{\beta_{l,k,n}}'s and \eqn{\mvec{w}{l,k,n}}'s as \eqn{\beta_{l,k,n} \leq P_{\max}} and \eqn{\|\mvec{w}{l,k,n}\|^2 \leq 1} in subproblems \eqref{eqn-9} and \eqref{eqn-9--1}.
+However, these additional constraints on optimization variables has no impact on final solution or objective.
+Using this, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
 

### 2015-10-29 Report/wsrm_formulation.tex
final modifications
Updated draft with boundedness argument

@@
 
-Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find the transmit precoders by solving the subproblem \eqref{eqn-9}.
-For brevity, let us consider \eqn{\mbf{m}} as the collection of all transmit precoders in the system as \eqn{\mbf{m} = \{\mvec{m}{l,k,n}\}_{\forall l,\forall k, \forall n}}.
+Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find transmit precoders by solving \eqref{eqn-9}.
+For brevity, let us consider \eqn{\mbf{m}} as the collection of all transmit precoders as \eqn{\mbf{m} = \{\mvec{m}{l,k,n}\}_{\forall l,\forall k, \forall n}}.
 Similarly, we denote \eqn{\mbf{w}} and \eqn{\mbfa{\beta}} as \eqn{\{\mvec{w}{l,k,n}\}_{\forall l,\forall k, \forall n}} and \eqn{\{\mvec{\beta}{l,k,n}\}_{\forall l,\forall k, \forall n}} respectively.
@@
 Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\lpointx}, \mbfa{\beta}^{(i)}_{j} \}}.
-Note that \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is the receiver, which is obtained by solving either \eqref{opt-rx} recursively or by using the \ac{MMSE} receiver \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
+Note that \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is obtained by solving either \eqref{opt-rx} or by using \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
 \begin{algorithm}
@@
 
-Upon convergence of the objective sequence, the receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from the previous \ac{SCA} step.
-Once the receive beamformers are updated, the transmit precoders are again evaluated with the newly found receivers by solving \eqref{eqn-9} recursively or by using \eqref{eqn-10}.
-The above procedure is repeated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations as outlined in Algorithm \ref{algo-1}.
+Upon convergence of objective sequence, receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from previous \ac{SCA} step.
+Once the receivers are updated, transmit precoders are again evaluated with the newly found receivers by solving \eqref{eqn-9} or \eqref{eqn-10}.
+The above procedure is repeated until \eqn{i \to \infty} or for some fixed \eqn{I_{\max}} as outlined in Algorithm \ref{algo-1}.
 
-The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying the total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained with the corresponding \ac{MMSE} receivers in \eqref{eqn-10}.
-Now, by using the fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c} for all the users in the system.
+The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying the total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained using \ac{MMSE} receivers in \eqref{eqn-10}.
+Now, by using fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c} for all users.
 
-Note that in all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges.
-\reviewF{However, to analyze the convergence of the sequence of beamformer iterates}, we consider modified objective \eqref{mod_obj} with a quadratic term instead of \eqref{eqn-6.1}.
-Using the regularized objective in \eqref{mod_obj}, the convergence of the sequence of iterates is discussed for the centralized solutions in Appendix \ref{sec-3.5}.
+%	consider modified objective \eqref{mod_obj} with a quadratic term instead of \eqref{eqn-6.1}.
+Moreover, we also bound \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq \beta_{\max}} for some large \eqn{\beta_{\max} \gg P_{\max}} without affecting the solution to ensure compactness of the feasible set, since \eqn{\beta_{l,k,n}} need not be bounded when \eqn{\gamma_{l,k,n} = 0}, \textit{i.e.}, when \eqn{\ith{l}} stream is inactive.
+Using these modifications, convergence of the sequence of iterates is discussed in Appendix \ref{sec-3.5}.}
 \begin{comment}

### 2015-10-29 Report/mse_formulation.tex
second update without W

@@
 (i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective with quadratic term as in \eqref{mod_obj} to ensure strong convexity in objective function.
-(ii) To guarantee the boundedness of feasible sets, we trivially bound \eqn{\beta_{l,k,n}}'s and \eqn{\mvec{w}{l,k,n}}'s as \eqn{\beta_{l,k,n} \leq P_{\max}} and \eqn{\|\mvec{w}{l,k,n}\|^2 \leq 1} in subproblems \eqref{eqn-9} and \eqref{eqn-9--1}.
-However, these additional constraints on optimization variables has no impact on final solution or objective.
-Using this, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
+(ii) To guarantee the boundedness of feasible sets in \eqref{eqn-9} and \eqref{eqn-9--1}, we include an additional constraint on  \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq P_{\max}} without affecting the solution.
+It restricts \eqn{\beta_{l,k,n}} from taking \eqn{\infty} when \eqn{\gamma_{l,k,n} = 0} for inactive users, since \eqref{eqn-6.3} need not be active.
+Using these, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
 

### 2015-11-05 Response/Response 3/response-3.tex
updated discussion

\reviewF{The authors have modified the manuscript taken into account the reviewers' comments. However, the proof of convergence still lacks of convincing argumentation to make this paper suitable for publication. Two main aspects are arguable as follows: }

\vspace{1eM}
\underline{\textit{Reply:}} We thank the reviewer for all constructive comments. We agree with the reviewer's concern on the claim that convergence proof still lacks the convincing arguments. We have completely rewritten Appendix A-D with similar kind of arguments used to discuss the convergence of projected gradient algorithms in Nonlinear Programming book as suggested by the reviewer. We hope that the proposed changes would make the convergence proof complete.

\begin{itemize}

	\item \reviewF{When discussing the convergence of the SCA algorithm (Appendix A-C), the authors claim that the SCA algorithm converges because the objective function is strictly decreasing and the minimizer in each iteration is unique. However, this is in general not enough to guarantee the convergence of the whole sequence. Instead, one can only claim that every limit point of the whole sequence is a stationary point, or globally optimal solution if the problem is convex. As an example, simply consider the gradient projection algorithm, where each subproblem is strongly convex and the objective function  is strictly decreasing but the whole sequence may not converge. The authors are referred to Bertsekas'  book: Nonlinear Programming.}

	\vspace{1eM}	
	\underline{\textit{Reply:}} We agree with the reviewer comment on the convergence of the sequence of beamformer iterates generated by the SCA algorithm. It is true that since the objective sequence is strictly monotonic and the minimizer is unique in each iteration, it does not guarantee the convergence of the sequence of iterates. We have removed our earlier claim on the convergence of beamformer iterates generated by the SCA algorithm. We now refer the minimizer obtained upon objective convergence is \eqn{\mbf{z}_\ast^{(i)}}, as presented in the paragraph following (51). Now, considering the whole sequence of beamformer iterates generated by repeatedly performing SCA and AO until the objective convergence, we can only show that the limit point of every convergent subsequence of iterates is a stationary point.

	We have revised our convergence of beamformer iterates in Appendix A-D using subsequence convergence proof. In order to do so, the feasible set should be compact. Even though the original set \eqn{\mc{F}} of nonconvex problem is compact, the feasible sets \eqn{\mc{X}^{(i)}_k} and \eqn{\mc{Y}^{(i)}_k} of relaxed subproblems need not be compact on all scenarios due to the newly introduced optimization variable \eqn{\beta_{l,k,n}} to bound the interference. It happens when \eqn{\gamma_{l,k,n} \to 0}, \textit{i.e.}, when the \eqn{\ith{k}} user stream \eqn{l} is not active on sub-channel \eqn{n}. In such a case, \eqn{\beta_{l,k,n}} can take any value, since \eqn{\gamma_{l,k,n} \to 0} as  \eqn{\mvec{m}{l,k,n} \to 0} and \eqn{\mvec{w}{l,k,n} \to 0}. It has no impact on the solution of each convex subproblem even if \eqn{\beta_{l,k,n} \to \infty}. However to discuss the convergence of proposed iterative algorithms, the feasible set needs to be compact.

	Therefore, we include an additional constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq P_{\max}} without altering the problem or solution for the sake of convergence analysis. Note that \eqn{\beta_{l,k,n}} can be bounded above with \eqn{P_{\max}}, since the total interference power on each stream cannot exceed the total transmit power, which follows from the passive behavior of wireless channels. Using this additional constraint, the feasible set of each subproblem is guaranteed to be compact, and therefore the sequence of iterates generated by the iterative algorithm is bounded. This information is included in the paragraph after (28) on page 6.

	Furthermore, the convergence discussions on the sequence of iterates generated by the iterative algorithm is presented in Appendix A-D.

	\vspace{1eM}	
	\item \reviewF{Even under the assumption that the inner loop SCA converges, there are doubts with respect to the convergence of the alternating optimization algorithm described by (54). The authors cite [27] to justify convergence, but it is not straightforward to claim that the algorithmic model considered in this manuscript is the same as in [27]. More specifically, let us consider the variable \eqn{x} (so it is consistent with the authors' notation in Appendix A-D). In the algorithmic model of [27], at iteration \eqn{t+1}, all elements of \eqn{x} are updated simultaneously, based on \eqn{x^t}. But in the authors' model, the update of \eqn{x} is performed in two phases: in the first phase, only the elements of \eqn{m} and \eqn{\gamma} in \eqn{x} are updated based on \eqn{x^t}. In the second phase, the remaining elements of \eqn{x} are updated, i.e. \eqn{w} and \eqn{\gamma}, based on both \eqn{x^t} and the elements that have been updated in the first phase. This is not a trivial difference and thus the direct application of the conclusion from [27] in the current context cannot be taken for granted. Due to the open concerns after several revision rounds, it is recommended to reject the paper.}

	\vspace{1eM}
	\underline{\textit{Reply:}} We agree with the reviewer's concern on lack of relevant references to show that the proposed method of alternating optimization variables can be applicable to the Zangwill's model. In [R1, Appendix I], the convergence of the sequence of iterates generated by the alternating projections algorithm was discussed with Zangwill's model using composition of two subalgorithms. However, based on reviewer's suggestion, we have modified the convergence proof similar to the one provided for gradient projection method in Nonlinear programming book by Bertsekas.

	In our earlier manuscript, the convergence of the sequence of beamformer iterates claim based on the Meyer's paper was incomplete. We apologize for the incomplete usage of the theorem presented in Meyer's paper [R2]. In [R2, Theorem. 3.1], it has been shown that if strict monotonicity of the objective sequence is guaranteed and the sequence of iterates is bounded, then either the sequence of beamformer iterates converges or the accumulation points of \eqn{\{x^t\}} is a continuum. Therefore, our earlier claim on the guaranteed convergence of the sequence of iterates is not correct as pointed out by the reviewer. The current approach of ensuring strict monotonic decrease in the objective sequence by using a quadratic regularization term in the objective as in projected gradient is discussed in [R2, Section 4] and in [R2, Lemma 4.1].

	\begin{itemize}
		\item[R1]  J. Tropp, I. Dhillon, R. Heath, and T. Strohmer, ``Designing structured tight frames via an alternating projection method," \emph{IEEE Trans. Inform. Theory}, vol. 51, no. 1, pp. 188–209, Jan. 2005.
		\item[R2] R.R. Meyer, ``Sufficient Conditions for the Convergence of Monotonic Mathematical Programming Algorithms," \emph{Journal of Computer and System Sciences}, vol. 12, no. 1, pp. 108-121, 1976
	\end{itemize}

\end{itemize}

### 2015-11-05 Report/convergence_centralized.tex
updated discussion

@@
 \end{equation}
-Now, by using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
-Finally, using \cite[Thms.
+Now, using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+Finally, by following \cite[Thms.
 2 and 11]{scutari_1} and \cite[Prop.

### 2015-11-05 Report/convergence_distributed.tex
updated discussion

--- 2015-10-22 Report/convergence_distributed.tex
@@
 Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence.
-Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem is guaranteed as \me{i \rightarrow \infty} for a diminishing step size as shown in \cite{scutari_1},\cite[Prop 8.2.6]{bertsekas2003convex}.
+Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem is guaranteed as \me{i \to \infty} for a diminishing step size as shown in \cite{scutari_1},\cite[Prop 8.2.6]{bertsekas2003convex}.
 
@@
 Now, by using \cite[Prop.
-4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \rightarrow \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}.
-Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following similar arguments as in Appendix \ref{sec-3.5}.}
+4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \to \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}.
+Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following the discussions presented in Appendix \ref{sec-3.5}.}
 
@@
 Since the subproblem in \eqref{eqn-decent-1} is convex, each \ac{BS} specific slave subproblem is also convex for a fixed interference vector \me{\mbfa{\zeta}_{b_k}^{(i)}} \cite{palomar2006tutorial}.
-The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \rightarrow \infty} \cite{bertsekas1999nonlinear} for a diminishing step size.
+The master subproblem in the \acl{PD} uses subgradient to update the coupling interference vectors in consensus with the objective function, it is guaranteed to converge to the centralized solution as the iteration \me{i \to \infty} \cite{bertsekas1999nonlinear} for a diminishing step size.
 It can be seen that the subproblem \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and the set is compact.
@@
 Therefore, by following \cite[Prop.
-4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \rightarrow \infty}.
+4.2]{bertsekas1989parallel}, it can be seen that the \ac{ADMM} approach converges to the centralized solution as \me{i \to \infty}.
 The distributed algorithms also converges to a stationary point of the original nonconvex problem as that of the centralized algorithms by following the discussions on Appendix \ref{sec-3.5}, if it is iterated until convergence.

### 2015-11-05 Report/kkt_mse_approach.tex
updated stationarity
updated discussion

@@
 In this section, we provide an algorithm that can be of practical importance owing to lower signaling requirements.
-We consider an idealized \ac{TDD} system due to the knowledge of complete \ac{CSI} at the transmitter.
-Similar work has been considered for the \ac{WSRM} problem with minimum rate constraints in \cite{kaleva2013decentralized}.
-Since the work in \cite{kaleva2013decentralized} are similar to that of the \ac{Q-WSRME} scheme with an additional maximum rate constraint \eqref{eqn-3.1.4}, the formulations require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
+We consider an idealized \ac{TDD} system due to the knowledge of local \ac{CSI} at the transmitter that includes channel between \ac{BS} \eqn{b} and all interfering users in the system.
+Similar work has been considered for the \ac{WSRM} problem with minimum guaranteed rate constraints in \cite{kaleva2013decentralized}.
+Since the work in \cite{kaleva2013decentralized} is similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint as in \eqref{eqn-3.1.4}, the formulation in \cite{kaleva2013decentralized} require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
 
-In the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints.
+However, in the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints.
 However, due to the non-differentiability of objective, the \ac{KKT} conditions are not computationally useful to find the optimization variables.
-In order to make the objective function differentiable, we consider the following two cases for which the absolute operator can be ignored without affecting the problem, namely,
+In order to make the objective function differentiable, we consider the following two conditions in which the absolute operator can be ignored without affecting the problem, namely,
 \begin{itemize}
@@
 
-With the assumption that either one of the above conditions, the problem in \eqref{eqn-mse-2} can be written as
+Assuming that either one of the above conditions is satisfied, the problem in \eqref{eqn-mse-2} can be written as
 \allowdisplaybreaks\iftoggle{single_column}{

### 2015-11-05 Report/mse_formulation.tex
updated discussion

--- 2015-10-22 Report/mse_formulation.tex
@@
 The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
-The convergence analysis follows the discussions in Appendix \ref{sec-3.5}.
+
+In all simulations, the objective of Algorithm \ref{algo-1} converges.
+\reviewF{However, to discuss formal convergence of relaxed problems \eqref{eqn-9}, \eqref{eqn-9--1} and \eqref{eqn-mse-2}, following modifications are considered.
+(i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective with quadratic term as in \eqref{mod_obj} to ensure strong convexity in objective function.
+(ii) To guarantee the boundedness of feasible sets in \eqref{eqn-9} and \eqref{eqn-9--1}, we limit \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq P_{\max}} to make the convergence analysis easier without affecting the solution.
+It restricts \eqn{\beta_{l,k,n}} from taking \eqn{\infty} as  \eqn{\gamma_{l,k,n} \to 0} for inactive users, since \eqref{eqn-6.3} need not be active.
+Using these, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
 

### 2015-11-05 Report/wsrm_formulation.tex
updated discussion

@@
 Let \eqn{i} be the \ac{AO} iteration count and let \eqn{j} denotes the \ac{SCA} index.
-To find the transmit precoders, \eqref{eqn-9} is solved recursively by updating the \eqn{\ith{j}} \ac{SCA} operating point \eqn{\tmbf{x}_{j}^{(i)} \triangleq \{ \tmbf{m}_{j}^{(i)},\tmbf{\beta}_{j}^{(i)} \}} in the \eqn{\ith{i}} \ac{AO} iteration for fixed receivers \eqn{\tmbf{w}} as \eqn{\tmbf{x}_{j}^{(i)} = \mbf{x}_{j}^{(i)}}, where \eqn{\mbf{x}_{j}^{(i)} \triangleq \{ \mbf{m}_{j}^{(i)},\mbf{\beta}_{j}^{(i)} \}} is the solution for the problem \eqref{eqn-9} in the \eqn{\ith{j-1}} \ac{SCA} step.\footnote{We can also update the operating point as \eqn{\tmbf{x}_{j}^{(i)} = \tmbf{x}_{j-1}^{(i)} + \rho_{j} (\mbf{x}_{j}^{(i)} - \tmbf{x}_{j-1}^{(i)})}, where \eqn{\rho_j \in (0,1]} is the step size as discussed in \cite{scutari_1,yang_yang}.} The iterative update is performed until \eqn{j \rightarrow \infty} or for \eqn{J_{\max}} number of iterations.
+To find the transmit precoders, \eqref{eqn-9} is solved recursively by updating the \eqn{\ith{j}} \ac{SCA} operating point \eqn{\tmbf{x}_{j}^{(i)} \triangleq \{ \tmbf{m}_{j}^{(i)},\tmbf{\beta}_{j}^{(i)} \}} in the \eqn{\ith{i}} \ac{AO} iteration for fixed receivers \eqn{\tmbf{w}} as \eqn{\tmbf{x}_{j}^{(i)} = \mbf{x}_{j}^{(i)}}, where \eqn{\mbf{x}_{j}^{(i)} \triangleq \{ \mbf{m}_{j}^{(i)},\mbf{\beta}_{j}^{(i)} \}} is the solution for the problem \eqref{eqn-9} in the \eqn{\ith{j-1}} \ac{SCA} step.\footnote{We can also update the operating point as \eqn{\tmbf{x}_{j}^{(i)} = \tmbf{x}_{j-1}^{(i)} + \rho_{j} (\mbf{x}_{j}^{(i)} - \tmbf{x}_{j-1}^{(i)})}, where \eqn{\rho_j \in (0,1]} is the step size as discussed in \cite{scutari_1,yang_yang}.} The iterative update is performed until \eqn{j \to \infty} or for \eqn{J_{\max}} number of iterations.
 Let \eqn{\tmbf{m}^{(i)}} be the transmit precoders obtained by \eqref{eqn-9} upon convergence in the \eqn{\ith{i}} \ac{AO} step with fixed receivers \eqn{\tmbf{w}^{(i-1)}}.
 Now, for the fixed transmit precoders, the receivers are determined either by solving \eqref{opt-rx} iteratively or by using \eqref{eqn-10}.
-The above procedure is iterated until \eqn{i \rightarrow \infty} or for \eqn{I_{\max}} number of iterations.
+The above procedure is iterated until \eqn{i \to \infty} or for \eqn{I_{\max}} number of iterations.
 Algorithm \ref{algo-1} outlines this procedure.

### 2015-11-05 Response/Response 3/additions.tex
updated discussion

--- 2015-07-20 Response/Response 2/additions.tex
@@
 \begin{enumerate}
-\item We have shortened the discussions on the existing \textit{backpressure algorithm} in Section III-A.
-\item Initialization of the \ac{SCA} operating point is included in the revised manuscript
-\item Section III-D is updated to include the guidelines involved in selecting the sub-channel order.
-\item Strong convexity of the objective function is emphasized in Appendix A-B.
-\item Strict monotonicity of the algorithm is discussed in a detailed manner in Appendix A-C.
-\item We have provided additional details on the distributed algorithm convergence as suggested by the reviewers
+	\item We have rewritten Appendix A-D to discuss the stationarity of limit points of the sequence of beamformer iterates generated by the proposed algorithm.
+	\item We have updated the convergence of distributed algorithm to reflect the same.
+	\item We included additional constraints on optimization variables to ensure compactness of feasible set in each subproblem
 \end{enumerate}
@@
 Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript.
+All revisions in the manuscript are highlighted in blue color.

### 2015-11-06 Report/convergence_centralized.tex
updated after Nam's correction

@@
 
+\begin{comment}
 The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
@@
 3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}
+\end{comment}
+
+The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
+\begin{itemize}
+\item[(a)] Objective function should be bounded below
+\item[(b)] Feasible set should be compact
+\item[(c)] Sequence of objective values should be strictly decreasing
+\item[(d)] Uniqueness of the minimizer in each step.
+\end{itemize}
+Note that condition (d) is required to ensure strict monotonicity of the objective sequence.
+Therefore, by using above conditions (a)-(c) along with \cite[Th.
+3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}.
+Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by the Algorithm \ref{algo-1} is a stationary point of original nonconvex problem formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+
+Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
+\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
+\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
+&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
+&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
+\end{IEEEeqnarray}
+where \me{g_2} and \me{\hat{f}} are convex, \me{h} is linear, and \me{g_0} and \me{g_1} are convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables.
+The constraint \eqref{con-dc} corresponds to either \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} represents to either  \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} correspondingly.
+Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by
+\iftoggle{single_column}{
+\begin{equation}
+\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
+\end{equation}
+}{\begin{align}
+\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
+& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
+\end{align}}
+
+We use the following notations to discuss the convergence of Algorithm \ref{algo-1}.
+Since it involves two nested loops, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}.
+Let \me{\mx}, \me{\my}, and \me{\mz} be the vector stacking all transmit precoders, receive beamformers, and other optimization variables used in \eqref{eqn-6} and \eqref{eqn-mse-1} respectively.
+Let us consider \ac{AO} step \eqn{i} with fixed \eqn{\my}.
+The solution obtained in the \eqn{\ith{k}} \ac{SCA} step is given by \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
+As \eqn{k \to \infty}, objective sequence converges, and the respective solution is denoted by \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}.
+Similarly, while alternating the optimization variables for fixed \eqn{\mx}, as \eqn{k \to \infty}, the solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}.
+In the following, we show that the conditions listed in (a)-(d) are satisfied by Algorithm \ref{algo-1}.
+
+\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
+The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is due to the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
+
+The minimum of the norm in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below.
+The objective function is Lipschitz continuous over the feasible set.
+The objective function is bounded from above as well, since the feasible set is bounded.
+
+\subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
+The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
+However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set.
+Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers.
+
+To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
+\begin{IEEEeqnarray}{rCl} \neqsub
+\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
+f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
+\end{IEEEeqnarray}
+where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step.
+The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite{scutari-1}.
+Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.
+
+\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
+In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} to exploit the uniqueness of the minimizer at each iteration.
+However, we note that upon convergence \eqn{f} is equal to \eqn{\hat{f}}.
+Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.
+
+To begin with, let us consider the variable \me{\my} begin fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\lpoint}{i-1}}.
+In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
+\iftoggle{single_column}{
+\begin{equation}\label{con-relax}
+\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \triangleq {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+\end{equation}}{
+\begin{multline} \label{con-relax}
+\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \triangleq {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
+\end{multline}}
+Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\lpoint}{i-1}} and \me{\iter{\mx}{k}{i}}.
+Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\my}{k}{i}}.
+Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for variables \me{\mx} and \me{\mz} is given by
+\begin{IEEEeqnarray}{rCl} \label{con-m} \neqsub
+\underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\lpoint}{i-1},\mz) \eqsub \label{con-obj-m} \\
+\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0 \eqsub \label{con-dc-m} \\
+&\quad& g_1(\mx,\iter{\my}{\lpoint}{i-1}) \leq 0, \quad g_2(\mx) \leq 0 \eqsub \label{con-cvx-blk-m}
+\end{IEEEeqnarray}
+The feasible set defined by the problem \eqref{con-m} is denoted by \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}.
+To prove the convergence of the \ac{SCA} updates in the \me{\ith{i}} \ac{AO} iteration, let us consider that \eqref{con-m} yields
+\me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution in the \me{\ith{k}} iteration.
+The point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimize the objective function satisfy
+\iftoggle{single_column}{
+\begin{equation}\label{con-sub-set}\allowdisplaybreaks
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}) \leq h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0. 
+\end{equation}}{
+\begin{multline}\label{con-sub-set}\allowdisplaybreaks
+h(\iter{\mz}{k+1}{i}) - {g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}) \leq \\
+h(\iter{\mz}{k+1}{i}) - \hat{g}_0(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \leq 0. 
+\end{multline}}
+Using \eqref{con-sub-set}, we can show that \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1}, \iter{\mz}{k+1}{i}\}} is feasible, since the initial \ac{SCA} operating point \me{\iter{\mx}{\lpoint}{i-1}} was chosen to be feasible from the \me{\ith{(i-1)}} \ac{AO} iteration.
+In each \ac{SCA} step, the feasible set includes the solution from the previous iteration as \me{\{\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}\} \in \iter{\mc{X}}{k+1}{i} \subset \mc{F}}, therefore, it decreases the objective as \cite{lanckriet2009convergence,scutari_1,amir}
+\iftoggle{single_column}{
+\begin{equation} \label{con-convergence}
+f(\iter{\mx}{0}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}) \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+\end{equation}}{
+\begin{multline} \label{con-convergence} \allowdisplaybreaks
+f(\iter{\mx}{0}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{0}{i}) \geq f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i}) \\ \geq f(\iter{\mx}{k+1}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k+1}{i}) \geq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+\end{multline}}
+Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing.
+Using strong convexity of the objective, we can show that the inequalities in \eqref{con-convergence} are strict, \textit{i.e.}, the sequence of objectives returned by Algorithm \ref{algo-1} is strictly decreasing.
+To this end, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step.
+At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
+\begin{IEEEeqnarray}{rCl} \neqsub \label{strict_monotonicity}
+\nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z} - \iter{\mbf{z}}{k+1}{i}) &\geq& 0 \eqsub \\
+f(\mbf{z}) - f(\iter{\mbf{z}}{k+1}{i}) &\geq& c \, \|\mbf{z} - \iter{\mbf{z}}{k+1}{i}\|^2 \eqsub
+\end{IEEEeqnarray}
+where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
+Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}.
+Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
+Since the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of objective sequence in each \ac{AO} step \eqn{{i}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon convergence of the sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}
+
+Once \me{\iter{\mx}{\lpoint}{i}} is obtained for fixed \me{\my}, then \eqref{con} is solved for \me{\my} with fixed \me{\mx}.
+However, after fixing \me{\mx} as \me{\iter{\mx}{\lpoint}{i}} in \eqref{con}, the problem is still nonconvex due to \eqref{con-dc}.
+Following similar approach as above, the minimizer \me{ \{\iter{\mx}{\lpoint}{i},\iter{\my}{k+1}{i},\iter{\mz}{k+1}{i}\}} can be found in each \ac{SCA} step \me{k} by solving \eqref{con-m} iteratively.
+Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
+The convergence and the nonincreasing behavior of the objective follow similar arguments as above.
+\footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The solution obtained by solving \eqref{con-m} iteratively until convergence of the objective value is given as \me{\{\iter{\mx}{\lpoint}{i}, \iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}\} \in \iter{\mc{Y}}{\lpoint}{i} \subset \mc{F}}.
+
+Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
+\iftoggle{single_column}{
+\begin{equation}
+f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+\end{equation}}{
+\begin{equation}
+f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+\end{equation}}
+Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}.
+To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}.
+Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
+\begin{equation} \label{fixed_point}
+f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
+\end{equation}
+\reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}.
+Moreover, note that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is also present in objective function \eqref{mod_obj}, therefore, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges.
+}
+
+\subsection{Stationarity of Limit Points} \label{c-b}
+\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm.
+In order to do that, let us use single index \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}.
+It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
+Using global index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
+
+Using the arguments in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
+Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}.
+However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded.
+Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th.
+3.6]{rudin1964principles}.
+
+We now show that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point.
+To do this, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}.
+Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity} that
+\begin{equation} \label{seq_mon}
+\dotsc < f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}) < \dotsc.
+\end{equation}
+Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}.
+Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
+\begin{equation} \label{limpoint}
+\lim_{t \to \infty} f(\ma^{t}) = \lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).
+\end{equation}
+
+Let us prove the stationarity of \eqn{\bar{\ma}} by contradiction.
+Assume that \eqn{\bar{\ma}} is not a stationary point, then there exist some other point \eqn{\ma^\prime \in \{\ma^t\}}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}.
+Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point.
+However, from \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of any convergent subsequence of \eqn{\{\ma^t\}}, which is a contradiction.
+
+Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}.
+Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}.
+Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop.
+2.1.2]{bertsekas1999nonlinear} as
+\begin{equation} \label{seq_mon1}
+\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
+\end{equation}
+Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point.
+
+Now to prove that \eqn{\bar{\ma}} is also a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between gradients of subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}.
+In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point for \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
+\begin{equation} \label{kkt_expr}
+\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
+\end{equation}
+for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.
+
+Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}.
+Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}.
+Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
+\begin{equation} \label{kkt_mod_expr}
+\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
+\end{equation}
+The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}.
+Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
+(ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
+\begin{equation} \label{rhs_equiv}
+\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
+\end{equation}
+If follows immediately from \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr} that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+Finally, by following \cite[Thms.
+2 and 11]{scutari_1} and \cite[Prop.
+3.2]{amir}, we can prove that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}

### 2015-11-06 Report/convergence_distributed.tex
updated after Nam's correction

@@
 Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed.
-Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is not guaranteed in each update.
+Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update.
 Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the beamformer iterates.

### 2015-11-06 Report/mse_formulation.tex
updated after Nam's correction

--- 2015-10-29 Report/mse_formulation.tex
@@
 
-Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receive beamformers.
-The optimization subproblem to find the transmit precoders for fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by
+Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receivers.
+The optimization subproblem to find transmit precoders for fixed \me{\mvec{w}{l,k,n}} is given by
 \begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
@@
 
-In all simulations, the objective of Algorithm \ref{algo-1} converges.
-\reviewF{However, to discuss the theoretical convergence of subproblems \eqref{eqn-9}, \eqref{eqn-9--1} and \eqref{eqn-mse-2}, following modifications are considered.
-(i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective with quadratic term as in \eqref{mod_obj} to ensure strong convexity in objective function.
-(ii) To guarantee the boundedness of feasible sets, we trivially bound \eqn{\beta_{l,k,n}}'s and \eqn{\mvec{w}{l,k,n}}'s as \eqn{\beta_{l,k,n} \leq P_{\max}} and \eqn{\|\mvec{w}{l,k,n}\|^2 \leq 1} in subproblems \eqref{eqn-9} and \eqref{eqn-9--1}.
-However, these additional constraints on optimization variables has no impact on final solution or objective.
-Using this, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
+In all simulations, objective sequence generated by Algorithm \ref{algo-1} converges.
+\reviewF{However, for formal convergence analysis, following modifications are assumed.
+(i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective in \eqref{mod_obj}, which exhibits strong convexity.
+(ii) Moreover, for some large \eqn{B_{\max} \gg P_{\max}}, we limit \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}} without altering the solution, to ensure the feasible sets of \eqref{eqn-9} and \eqref{eqn-9--1} bounded.
+The additional constraint on \eqn{\beta_{l,k,n}} is necessary, since \eqref{eqn-6.3} need not be tight when \eqn{\gamma_{l,k,n} \to 0}.
+Due to this, \eqn{\beta_{l,k,n}} becomes unbounded, since any value of \eqn{\beta_{l,k,n}} satisfying \eqref{eqn-6.3} with inequality, satisfies \eqref{eqn-6.3} with equality.
+Finally, with these changes, convergence of Algorithm \ref{algo-1} is dealt in Appendix \ref{sec-3.5}.}
 

### 2015-11-06 Report/sub_channel_wsrm.tex
updated after Nam's correction

@@
 
-As an alternative sub-optimal solution, we present a \acl{QM} \ac{SRA}, which solves for the precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with a fixed transmit power \me{P_{\max,i}}.
-For each sub-channel, the power sharing can either be equal or based on some predetermined limits as in partial frequency reuse satisfying
+As an alternative sub-optimal solution, we present \acl{QM} \ac{SRA}, which solves for precoders using \ac{JSFRA} formulation for a specific sub-channel \me{i} with fixed transmit power \me{P_{\max,i}}.
+For each sub-channel, power sharing can either be equal or based on some predetermined limits as in partial frequency reuse satisfying
 \begin{equation}

### 2015-11-13 Response/Response 3/response-3.tex
updated response document and manuscript

@@
 \vspace{1eM}
-\underline{\textit{Reply:}} We thank the reviewer for all constructive comments.
-We agree with the reviewer's concern on the claim that convergence proof still lacks the convincing arguments.
-We have completely rewritten Appendix A-D with similar kind of arguments used to discuss the convergence of projected gradient algorithms in Nonlinear Programming book as suggested by the reviewer.
-We hope that the proposed changes would make the convergence proof complete.
+\underline{\textit{Reply:}} We thank the reviewer for pointing the flaw in our earlier convergence proof.
+Based on the reviewer's suggestion, we have rewritten Appendix A-D with similar arguments used to discuss the convergence of projected gradient algorithms in [R3].
+We hope that our current changes will be convincing enough to make the convergence proof complete.
 
@@
 
-	\item \reviewF{When discussing the convergence of the SCA algorithm (Appendix A-C), the authors claim that the SCA algorithm converges because the objective function is strictly decreasing and the minimizer in each iteration is unique.
+	\item \reviewF{When discussing the convergence of the \ac{SCA} algorithm (Appendix A-C), the authors claim that the \ac{SCA} algorithm converges because the objective function is strictly decreasing and the minimizer in each iteration is unique.
 However, this is in general not enough to guarantee the convergence of the whole sequence.
@@
 	\vspace{1eM}	
-	\underline{\textit{Reply:}} We agree with the reviewer comment on the convergence of the sequence of beamformer iterates generated by the SCA algorithm.
-It is true that since the objective sequence is strictly monotonic and the minimizer is unique in each iteration, it does not guarantee the convergence of the sequence of iterates.
-We have removed our earlier claim on the convergence of beamformer iterates generated by the SCA algorithm.
-We now refer the minimizer obtained upon objective convergence is \eqn{\mbf{z}_\ast^{(i)}}, as presented in the paragraph following (51).
-Now, considering the whole sequence of beamformer iterates generated by repeatedly performing SCA and AO until the objective convergence, we can only show that the limit point of every convergent subsequence of iterates is a stationary point.
+	\underline{\textit{Reply:}} We agree with the reviewer's comment.
+The convergence of iterates cannot be guaranteed based on the strict monotonicity of the objective sequence and the uniqueness of minimizer in each step.
+We apologize for our emphasis on the convergence of sequence of iterates.
+In view of reviewer's suggestion, we have revised our claim based on subsequence convergence theory.
 
-	We have revised our convergence of beamformer iterates in Appendix A-D using subsequence convergence proof.
-In order to do so, the feasible set should be compact.
-Even though the original set \eqn{\mc{F}} of nonconvex problem is compact, the feasible sets \eqn{\mc{X}^{(i)}_k} and \eqn{\mc{Y}^{(i)}_k} of relaxed subproblems need not be compact on all scenarios due to the newly introduced optimization variable \eqn{\beta_{l,k,n}} to bound the interference.
-It happens when \eqn{\gamma_{l,k,n} \to 0}, \textit{i.e.}, when the \eqn{\ith{k}} user stream \eqn{l} is not active on sub-channel \eqn{n}.
-In such a case, \eqn{\beta_{l,k,n}} can take any value, since \eqn{\gamma_{l,k,n} \to 0} as  \eqn{\mvec{m}{l,k,n} \to 0} and \eqn{\mvec{w}{l,k,n} \to 0}.
-It has no impact on the solution of each convex subproblem even if \eqn{\beta_{l,k,n} \to \infty}.
-However to discuss the convergence of proposed iterative algorithms, the feasible set needs to be compact.
+	Since the feasible set is bounded, the iterates generated by the iterative algorithm are bounded.
+Therefore, there exists at least one subsequence that converges to a limit point.
+Now, by using a convergent subsequence of original sequence of iterates, we argued that every limit point is a stationary point of the original nonconvex problem.
+In order to do so, we used a unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}.
+Now, by using this unified index \eqn{t}, we represent iterate \eqn{\mbf{x}^{t}} as the solution variable produced by the iterative algorithm in every \ac{SCA} \eqn{k} and \ac{AO} step {i}.
+By using this notation and the subsequence argument, we have revised our convergence discussions in Appendices A-C and A-D.
 
-	Therefore, we include an additional constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq P_{\max}} without altering the problem or solution for the sake of convergence analysis.
-Note that \eqn{\beta_{l,k,n}} can be bounded above with \eqn{P_{\max}}, since the total interference power on each stream cannot exceed the total transmit power, which follows from the passive behavior of wireless channels.
-Using this additional constraint, the feasible set of each subproblem is guaranteed to be compact, and therefore the sequence of iterates generated by the iterative algorithm is bounded.
-This information is included in the paragraph after (28) on page 6.
-
-	Furthermore, the convergence discussions on the sequence of iterates generated by the iterative algorithm is presented in Appendix A-D.
+	Even though the feasible sets of the original nonconvex problem in (6) and the relaxed \ac{MSE} reformulated problem in (26) are bounded due to the total power constraint, we noted that the solution space of the relaxed nonconvex problem (16) need not be bounded.
+It is because of the newly introduced variables in (16b) and (16c) to relax the \ac{SINR} expression, since \eqn{\beta_{l,k,n}} can assume any value satisfying (16c) without violating any other constraints in (16) when \eqn{\gamma_{l,k,n} = 0}.
+In order to ensure boundedness of the feasible set, we can include an additional bounding constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}}, where \eqn{B_{\max}} can be a maximum interference threshold seen by any user in the network with the maximum transmit power constraint of \eqn{P_{\max}}.
+Note that the additional bounding constraint on \eqn{\beta_{l,k,n}} will not alter the solution space of other optimization variables.
+However, as a consequence of considering the regularized objective in (46b), the additional constraint on \eqn{\beta_{l,k,n}} is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in (46b).
+We have highlighted this information on page 6, after (28).
 
@@
 More specifically, let us consider the variable \eqn{x} (so it is consistent with the authors' notation in Appendix A-D).
-In the algorithmic model of [27], at iteration \eqn{t+1}, all elements of \eqn{x} are updated simultaneously, based on \eqn{x^t}.
-But in the authors' model, the update of \eqn{x} is performed in two phases: in the first phase, only the elements of \eqn{m} and \eqn{\gamma} in \eqn{x} are updated based on \eqn{x^t}.
-In the second phase, the remaining elements of \eqn{x} are updated, i.e.
-\eqn{w} and \eqn{\gamma}, based on both \eqn{x^t} and the elements that have been updated in the first phase.
+In the algorithmic model of [27], at iteration \eqn{t+1}, all elements of \eqn{\mbf{x}} are updated simultaneously, based on \eqn{\sol{t}}.
+But in the authors' model, the update of \eqn{\mbf{x}} is performed in two phases: in the first phase, only the elements of \eqn{\mbf{m}} and \eqn{\mbf{\gamma}} in \eqn{\mbf{x}} are updated based on \eqn{\sol{t}}.
+In the second phase, the remaining elements of \eqn{\mbf{x}} are updated, i.e.
+\eqn{\mbf{w}} and \eqn{\mbf{\gamma}}, based on both \eqn{\sol{t}} and the elements that have been updated in the first phase.
 This is not a trivial difference and thus the direct application of the conclusion from [27] in the current context cannot be taken for granted.
@@
 	\vspace{1eM}
-	\underline{\textit{Reply:}} We agree with the reviewer's concern on lack of relevant references to show that the proposed method of alternating optimization variables can be applicable to the Zangwill's model.
-In [R1, Appendix I], the convergence of the sequence of iterates generated by the alternating projections algorithm was discussed with Zangwill's model using composition of two subalgorithms.
-However, based on reviewer's suggestion, we have modified the convergence proof similar to the one provided for gradient projection method in Nonlinear programming book by Bertsekas.
+	\underline{\textit{Reply:}} We understand the reviewer's concern on using [R1] to our problem involving \ac{SCA} and \ac{AO} updates, which involves partial update of optimization variables.
+Even though our revised convergence proof is not based on [R1], we clarify our usage of [R1] for \ac{AO} update.
+Therefore, we refer to [R2], where the problem considered was to design tight frames based on solving matrix nearness problem using \ac{AO} approach.
+In order to prove the convergence of the sequence of iterates generated by the \ac{AO} iterations, [R1] is used with the composition of two sub-algorithms as discussed briefly in [Appendix I and II, R2].
 
-	In our earlier manuscript, the convergence of the sequence of beamformer iterates claim based on the Meyer's paper was incomplete.
-We apologize for the incomplete usage of the theorem presented in Meyer's paper [R2].
-In [R2, Theorem.
-3.1], it has been shown that if strict monotonicity of the objective sequence is guaranteed and the sequence of iterates is bounded, then either the sequence of beamformer iterates converges or the accumulation points of \eqn{\{x^t\}} is a continuum.
+	We note that in our previous manuscript, the convergence of the sequence of beamformer iterates claim based on [R1] was incomplete.
+We apologize for the incomplete usage of the theorem presented in [R1].
+In [Theorem.
+3.1, R1], it has been shown that if the strict monotonicity of the objective sequence is ensured and the iterates are bounded, then \textit{either the sequence of iterates converges or the accumulation points of \eqn{\{\sol{t}\}} is a continuum}.
 Therefore, our earlier claim on the guaranteed convergence of the sequence of iterates is not correct as pointed out by the reviewer.
-The current approach of ensuring strict monotonic decrease in the objective sequence by using a quadratic regularization term in the objective as in projected gradient is discussed in [R2, Section 4] and in [R2, Lemma 4.1].
+Ensuring strict monotonic decrease in the objective sequence by restricting the solution set is discussed briefly in [Section 4, R1].
+By using [R1], we can only claim the convergence of subsequence of \eqn{\{\sol{t}\}} and not the sequence itself.
 
+	We revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss briefly on the convergence of iterates.
+We show that every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
+
+	\vspace{1eM}
 	\begin{itemize}
-		\item[R1]  J.
+
+		\item[R1.] R.R.
+Meyer, ``Sufficient Conditions for the Convergence of Monotonic Mathematical Programming Algorithms," \emph{Journal of Computer and System Sciences}, vol.
+12, no.
+1, pp.
+108-121, 1976
+		\item[R2.] J.
 Tropp, I.
@@
 2005.
-		\item[R2] R.R. Meyer, ``Sufficient Conditions for the Convergence of Monotonic Mathematical Programming Algorithms," \emph{Journal of Computer and System Sciences}, vol. 12, no. 1, pp. 108-121, 1976
+		\item[R3.] D. P. Bertsekas, ``Nonlinear Programming," 2nd ed., \emph{Athena Scientific}, 1999.
 	\end{itemize}

### 2015-11-13 Response/Response 3/reviewer_response.tex
updated discussion
updated response document and manuscript

--- 2015-08-03 Response/Response 2/reviewer_response.tex
@@
 \usepackage{acronym,etoolbox,color,multicol,xcolor}
-%\usetikzlibrary{plotmarks}
 \usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools,pgfplots,subfig}
-
-\pgfplotsset{compat=newest}
-\pgfplotsset{plot coordinates/math parser=false}
-\newlength\figureheight
-\newlength\figurewidth
-
-\newcommand{\cmnt}[1]{\item}
-\newcommand{\cmnts}[1]{\item[(#1)]}
-\newcommand{\resp}{\item[\textit{\underline{Reply}}:]}
 
@@
 
-\renewcommand{\thefigure}{\Alph{figure}}
-\renewcommand{\thesubfigure}{\roman{subfigure}}
-%\renewcommand{\thesubfigure}{\Roman{figure}}
+\renewcommand{\thefigure}{\Roman{figure}}
+\renewcommand{\thesubfigure}{\alph{subfigure}}
 \renewcommand{\theequation}{\roman{equation}}
@@
 
-\usetikzlibrary{plotmarks}
 \title{Reviewers Comments \& Authors Replies}
@@
 \vspace{0.5in}
-The authors would like to thank the associate editor and the reviewers for their valuable comments on the manuscript, which have been greatly helpful to improve the paper quality.
-Based on the comments, we have made several revisions to the paper, which are summarized below.
+The authors are grateful to the associate editor for being considerate enough to provide us with this additional opportunity to revise and correct our convergence proof.
+We thank all the reviewers for their valuable comments on the manuscript, which have been greatly helpful to improve the paper quality.
+Based on the comments, we have revised our manuscript to ensure that all the reviewers comments are addressed properly and the technical correctness of the convergence proof is also verified.
 \input{additions}
@@
 \newpage
-\section*{Response to Reviewer - \me{1}'s Comments}
+\section*{Response to first reviewer comments}
 \input{response-1}
@@
 \newpage
-\section*{Response to Reviewer - \me{2}'s Comments}
+\section*{Response to second reviewer comments}
 \input{response-2}
@@
 \newpage
-\section*{Response to Reviewer - \me{3}'s Comments}
+\section*{Response to third reviewer comments}
 \input{response-3}
@@
 \newpage
-\section*{Response to Reviewer - \me{4}'s Comments}
+\section*{Response to fourth reviewer comments}
 \input{response-4}

### 2015-11-13 Report/convergence_centralized.tex
updated response document and manuscript

@@
 \subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
-The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, which is due to the total power constraint on the transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
+The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, due to the total power constraint on transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
 
-The minimum of the norm in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below.
-The objective function is Lipschitz continuous over the feasible set.
-The objective function is bounded from above as well, since the feasible set is bounded.
+The minimum value of the norm function in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below.
+Additionally, the objective function is Lipschitz continuous and due to the fact that the feasible set is compact, objective function is bounded from above as well.
 
@@
 \end{IEEEeqnarray}
-where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
+where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution.
 Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}.
-Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}.
-Since the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of objective sequence in each \ac{AO} step \eqn{{i}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon convergence of the sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}
+Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in every \ac{SCA} update \cite{scutari2010convex}.
+\reviewF{Since the sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} is strictly decreasing and bounded, the convergence in each \ac{AO} step \eqn{{i}} is guaranteed.
+Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} iteration.}
 
@@
 Note that \me{\iter{\mz}{k+1}{i}} is reused since the variable \me{\mx} is fixed in the \me{\ith{i}} \ac{AO} iteration.
-The convergence and the nonincreasing behavior of the objective follow similar arguments as above.
-\footnote{Note that the \ac{MMSE} receiver in \eqref{eqn-10} can also be used instead of performing the \ac{SCA} updates until convergence for the optimal receiver.} The solution obtained by solving \eqref{con-m} iteratively until convergence of the objective value is given as \me{\{\iter{\mx}{\lpoint}{i}, \iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}\} \in \iter{\mc{Y}}{\lpoint}{i} \subset \mc{F}}.
+The convergence and the nonincreasing behavior of the objective follow similar arguments as above.\footnote{Note that the receive beamformers can also be designed by the \ac{MMSE} receiver using closed-form \eqref{eqn-10} instead designing recursively by updating the \ac{SCA} operating point as in optimal receiver \eqref{opt-rx}.} The solution obtained by solving \eqref{con-m} iteratively until convergence of the objective value is given as \me{\{\iter{\mx}{\lpoint}{i}, \iter{\my}{\lpoint}{i},\iter{\mz}{\lpoint|\mx}{i}\} \in \iter{\mc{Y}}{\lpoint}{i} \subset \mc{F}}.
 
@@
 \reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}.
-Moreover, note that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is also present in objective function \eqref{mod_obj}, therefore, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges.
-}
+Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges.
+Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in every \ac{SCA} and \ac{AO} step.}
 
@@
 \reviewF{We discuss the convergence of the iterates generated by the iterative algorithm.
-In order to do that, let us use single index \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}.
+In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}.
 It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
-Using global index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
+Using unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
 
-Using the arguments in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.
+Using the arguments in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges \cite[Prop.
+A.3]{bertsekas1999nonlinear}.
 Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}.
@@
 \end{equation}
-Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}.
+%Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}. 
 Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
@@
 Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point.
-However, from \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of any convergent subsequence of \eqn{\{\ma^t\}}, which is a contradiction.
+However, from \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of \eqn{\{\ma^t\}}, which is a contradiction to our initial assumption.
 
@@
 Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
-(ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
+(ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
 \begin{equation} \label{rhs_equiv}
@@
 2 and 11]{scutari_1} and \cite[Prop.
-3.2]{amir}, we can prove that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}
+3.2]{amir}, we can prove that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of the problem \eqref{con}.}

### 2015-11-13 Report/convergence_distributed.tex
updated response document and manuscript

@@
 
-However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus, achieving improved speed of convergence.
+However, to avoid the nested iterations, the proposed method performs block update of all variables at once to obtain transmit and receive beamformers for limited number of iterations, thus, achieving improved speed of convergence.
 Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
@@
 Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update.
-Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the beamformer iterates.
+Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the sequence of beamformer iterates.
 

### 2015-11-13 Report/mse_formulation.tex
updated response document and manuscript

@@
 where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol.
-Plugging the \ac{MMSE} receivers in \eqref{eqn-10} into the \ac{MSE} expression in \eqref{mse-error} and into the \ac{SINR} expression in \eqref{eq:SINR}, we arrive at the following relation between the \ac{MSE} and the \ac{SINR} as
+Plugging the \ac{MMSE} receivers in \eqref{eqn-10} into the \ac{MSE} expression in \eqref{mse-error} and into the \ac{SINR} expression in \eqref{eq:SINR}, we arrive at
 \begin{equation} \label{eqn-mse-eq}
@@
 
-The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
+The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is nonconvex even for a fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}.
 Again we resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using the first order Taylor approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
@@
 \end{IEEEeqnarray}
-The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
+For fixed receivers, transmit precoders are obtained by solving \eqref{eqn-mse-2} iteratively by updating \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} found in previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
 
-In all simulations, objective sequence generated by Algorithm \ref{algo-1} converges.
-\reviewF{However, for formal convergence analysis, following modifications are assumed.
-(i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective in \eqref{mod_obj}, which exhibits strong convexity.
-(ii) Moreover, for some large \eqn{B_{\max} \gg P_{\max}}, we limit \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}} without altering the solution, to ensure the feasible sets of \eqref{eqn-9} and \eqref{eqn-9--1} bounded.
-The additional constraint on \eqn{\beta_{l,k,n}} is necessary, since \eqref{eqn-6.3} need not be tight when \eqn{\gamma_{l,k,n} \to 0}.
-Due to this, \eqn{\beta_{l,k,n}} becomes unbounded, since any value of \eqn{\beta_{l,k,n}} satisfying \eqref{eqn-6.3} with inequality, satisfies \eqref{eqn-6.3} with equality.
-Finally, with these changes, convergence of Algorithm \ref{algo-1} is dealt in Appendix \ref{sec-3.5}.}
+In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
+\reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} for \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
+The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step.
+Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} are bounded.
+However, the feasible set of \eqref{eqn-6} need not be bounded due to the introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
+Therefore, by restricting \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}}, the feasible set can be bounded without altering the solution space of other variables.
+However, as a consequence of considering the regularized objective in \eqref{mod_obj}, the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}.
+With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}
+
+%In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
+\reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}.
+The quadratic term in the objective ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step.
+Even though the feasible set of \eqref{eqn-3} and \eqref{eqn-mse-2} are bounded, the feasible set of \eqref{eqn-6} need not be bounded due to the newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}.
+Since, \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
+However, it can be avoided by bounding \eqn{\beta_{l,k,n}}'s with a maximum interference value depending on \eqn{P_{\max}}.
+By doing so, the domain of other variables are not affected by restricting \eqn{\beta_{l,k,n}}.
+Alternatively, if \eqref{mod_obj} is used instead of \eqref{eqn-6.1}, then the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}.
+With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}
+
+%In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
+\reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} for \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
+The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step.
+Even though the feasible set of \eqref{eqn-3} and the relaxed problem in \eqref{eqn-mse-1} are bounded, the feasible set of \eqref{eqn-6} need not be bounded due to the newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}.
+Since, \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
+Note that it can be avoided by bounding \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}} without altering the solution space of other variables.
+However, as a consequence of considering a regularized objective as in \eqref{mod_obj}, the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}.
+With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}
+
+%In all simulations, objective sequence generated by Algorithm \ref{algo-1} converges.
+\reviewF{However, for formal convergence analysis, following alterations are assumed.
+(i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective as in \eqref{mod_obj} to ensure uniqueness of the minimizer in each step.
+(ii) Even though the feasible set of \eqref{eqn-3} is compact, it is due to the newly introduced variables in \eqref{eqn-6}, the feasible set in \eqref{eqn-9} and \eqref{eqn-9--1} can become unbounded.
+Since when \eqn{\gamma_{l,k,n} = 0}, \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating other constraints.
+Therefore, to bound \eqn{\beta_{l,k,n}}, we introduce an additional constraint to limit \eqn{\beta_{l,k,n}} for some large \eqn{B_{\max} \gg P_{\max}} as \eqn{\beta_{l,k,n} \leq B_{\max}} without altering the problem.
+Now, with these assumptions, convergence proof is dealt in Appendix \ref{sec-3.5}.}
+
+%Note that due to the newly introduced variables in \eqref{eqn-6}, the feasible set of \eqref{eqn-9} and \eqref{eqn-9--1} can become unbounded even if the feasible set of \eqref{eqn-3} is bounded.
+It happens only when \eqn{\gamma_{l,k,n} = 0}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating other constraints in \eqref{eqn-6}.
+However, as a result of using \eqref{mod_obj}, the feasible set of \eqref{eqn-9} and \eqref{eqn-9--1} are always bounded.
+Now, by using the modified objective in \eqref{mod_obj}, convergence of Algorithm \ref{algo-1} is dealt in Appendix \ref{sec-3.5}.}
+
+%In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
+However, for a theoretical convergence analysis, we consider a regularized objective function as in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}.
+The proximal term in \eqref{mod_obj} is introduced to guarantee strict monotonicity of the objective function, thereby ensuring unique minimizer in every \ac{SCA} and \ac{AO} step.
+By using the modified objective function in \eqref{mod_obj}, the convergence analysis of the proposed iterative algorithms is discussed in Appendix \ref{sec-3.5}.
 

### 2015-11-13 Report/sub_channel_wsrm.tex
updated response document and manuscript

@@
-The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of an interior point method, which is used to solve the problem, increases with the problem size.
-Thus, we can use the decomposition methods presented in \cite{palomar2006tutorial,boyd2011distributed} to overcome this complexity by designing precoders for each sub-channels independently with minimal information exchange.
+The \ac{JSFRA} algorithm complexity scales with the number of sub-channels, since the complexity of interior point method, used to solve the problem, increases with the problem size.
+Thus, we can use the decomposition methods in \cite{palomar2006tutorial,boyd2011distributed} for designing precoders of each sub-channel with less complexity by using additional coupling variables among the subproblems.
 

### 2015-11-13 Report/wsrm_formulation.tex
updated response document and manuscript

@@
 Similarly, we denote \eqn{\mbf{w}} and \eqn{\mbfa{\beta}} as \eqn{\{\mvec{w}{l,k,n}\}_{\forall l,\forall k, \forall n}} and \eqn{\{\mvec{\beta}{l,k,n}\}_{\forall l,\forall k, \forall n}} respectively.
-Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution of \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step.
-Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\lpointx}, \mbfa{\beta}^{(i)}_{j} \}}.
-Note that \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is obtained by solving either \eqref{opt-rx} or by using \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
+Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be a minimizer obtained in the \eqn{\ith{(j-1)}} \ac{SCA} step.
+Since \ac{SCA} is an iterative scheme, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is given as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\lpointx}, \mbfa{\beta}^{(i)}_{j} \}}.
+Note that  \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is obtained by solving either \eqref{opt-rx} or by using \eqref{eqn-10} in the \eqn{\ith{(i-1)}} \ac{AO} step.
 \begin{algorithm}
@@
 
-Upon convergence of objective sequence, receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from previous \ac{SCA} step.
-Once the receivers are updated, transmit precoders are again evaluated with the newly found receivers by solving \eqref{eqn-9} or \eqref{eqn-10}.
+Upon convergence of the objective sequence, receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from the previous \ac{SCA} step.
+Once the receivers are updated, transmit precoders are again evaluated using the newly found receivers by solving \eqref{eqn-9} or \eqref{eqn-10}.
 The above procedure is repeated until \eqn{i \to \infty} or for some fixed \eqn{I_{\max}} as outlined in Algorithm \ref{algo-1}.
 
-The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying the total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained using \ac{MMSE} receivers in \eqref{eqn-10}.
-Now, by using fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c} for all users.
+A feasible initial point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user precoders satisfying total power constraint in \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are updated by using the \ac{MMSE} receiver in \eqref{eqn-10}.
+Now, for fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c}.
 

### 2015-11-13 Response/Response 3/additions.tex
updated response document and manuscript

@@
 \begin{enumerate}
-	\item We have rewritten Appendix A-D to discuss the stationarity of limit points of the sequence of beamformer iterates generated by the proposed algorithm.
+	\item We have rewritten Appendix A-D to discuss the stationarity of limit points of the sequence of beamformer iterates generated by the centralized algorithms.
 	\item We have updated the convergence of distributed algorithm to reflect the same.
-	\item We included additional constraints on optimization variables to ensure compactness of feasible set in each subproblem
 \end{enumerate}
@@
 All revisions in the manuscript are highlighted in blue color.
+
+\subsection*{List of Changes:}
+\vspace*{1eM}
+\begin{itemize}
+	\item Page 6, paragraph after (28)
+	\item Page 8, \eqn{\ith{13}} line on last paragraph in Section IV-B
+	\item Page 12, paragraph following itemized requirements in Appendix A
+	\item Last sentence after (51) on page 14
+	\item Last paragraph in Appendix A-C
+	\item Appendix A-D is rewritten using subsequence convergence
+	\item Last sentence after (60) on page 15
+\end{itemize}

### 2015-11-17 Report/convergence_centralized.tex
ccc

@@
 where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step.
-The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite{scutari-1}.
+The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite[Sec.
+3.4.3]{bertsekas1989parallel}.
 Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.
@@
 Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in every \ac{SCA} update \cite{scutari2010convex}.
-\reviewF{Since the sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} is strictly decreasing and bounded, the convergence in each \ac{AO} step \eqn{{i}} is guaranteed.
-Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} iteration.}
+\reviewF{Since the objective is strictly decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in every \ac{AO} step \eqn{i}.
+Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} update.}
 
@@
 It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
-Using unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
+Using the unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
 

### 2015-11-17 Report/convergence_distributed.tex
ccc

@@
-The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution.
-Note that \eqref{eqn-decent-1} satisfies the Slater's constraint qualification by having a non-empty interior and a compact set, which are required for the convergence.
-Since in primal decomposition, the master subproblem uses subgradient to update the coupling interference vectors in consensus with the objective function, the convergence of the subproblem is guaranteed as \me{i \to \infty} for a diminishing step size as shown in \cite{scutari_1},\cite[Prop 8.2.6]{bertsekas2003convex}.
+\reviewF{Assuming a regularized objective function as in \eqref{mod_obj} for each subproblem \eqref{eqn-decent-1}, convergence of Algorithm \ref{algo-3} follows the discussions in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the primal decomposition converges to the centralized solution.
+It can be ensured by the following properties.
+(i) The feasible set has a non-empty interior and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications.
+(ii) Due to the strongly convex objective \eqref{mod_obj} in each subproblem, uniqueness of the minimizer is guaranteed.
+Therefore, by using the above facts, convergence of the primal decomposition algorithm can be ensured as \eqn{j \to \infty} using \cite[Prop.
+8.2.6]{bertsekas2003convex} by considering diminishing step size in each subgradient update.}
 
-To show the convergence of the \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
+Now, to show the convergence of \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 \end{IEEEeqnarray}
-where the constraint in \eqref{const-admm} is identical to that in \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
+where the constraint in \eqref{const-admm} is identical to that of \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
 To show the convergence, we rely on the following conditions.
@@
 Now, by using \cite[Prop.
-4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} converges to the centralized solution as \me{i \to \infty} by using diminishing step size in each \ac{ADMM} iteration as discussed in \cite{boyd2011distributed}.
-Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following the discussions presented in Appendix \ref{sec-3.5}.}
+4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}.
+Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}
 
@@
 
-Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
+Unlike the primal or the \ac{ADMM} approaches, the decomposition method via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
 Therefore, it is difficult to theoretically prove the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.
@@
 Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update.
-Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the sequence of beamformer iterates.
+Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure convergence.
 

### 2015-11-17 Report/dual_approach.tex
ccc

--- 2015-10-22 Report/dual_approach.tex
@@
 
-The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}.
-To reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
-If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
-The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence.
-However, if the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, \reviewF{then the convergence discussions follows Appendices \ref{sec-3.5} and \ref{sec-dist-conv}}.
+Assuming that the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, \reviewF{then the convergence follows the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}}.
 Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured.
 The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.
+However, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
+If so, convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
+The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.
 

### 2015-11-17 Report/mse_formulation.tex
ccc

@@
 The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step.
-Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} are bounded.
-However, the feasible set of \eqref{eqn-6} need not be bounded due to the introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
+Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded.
+However, for \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
 Therefore, by restricting \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}}, the feasible set can be bounded without altering the solution space of other variables.

### 2015-11-18 Response/Response 3/response-3.tex
finalized

@@
 \vspace{1eM}
-\underline{\textit{Reply:}} We thank the reviewer for pointing the flaw in our earlier convergence proof.
-Based on the reviewer's suggestion, we have rewritten Appendix A-D with similar arguments used to discuss the convergence of projected gradient algorithms in [R3].
+\underline{\textit{Reply:}} We thank the reviewer for pointing out the flaw in our previous convergence proof.
+Based on the reviewer's suggestion, we have rewritten Appendix A-D with the subsequence convergence instead of claiming the sequence convergence.
 We hope that our current changes will be convincing enough to make the convergence proof complete.
+
+In order to discuss the convergence of the sequence of iterates generated by the centralized method in Algorithm 1, we use a unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}.
+By doing so, we represent iterate \eqn{\mbf{x}^{t}} as the solution variable produced by the iterative algorithm in every \ac{SCA} \eqn{k} and \ac{AO} step {i}.
+Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.
+
+As an observation, we have noted that the feasible set of nonconvex problem (16) need not be bounded, even if the feasible set of the original nonconvex problem in (6) and the relaxed \ac{MSE} reformulated problem in (26) is bounded.
+It happens in problem (16) because of the newly introduced optimization variables in (16b) and (16c) to relax the \ac{SINR} expression, since \eqn{\beta_{l,k,n}} can assume any value satisfying (16c) without violating any other constraints in (16) when \eqn{\gamma_{l,k,n} = 0}.
+Therefore, to ensure boundedness of the feasible set of problem (16), we can include an additional bounding constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}}, where \eqn{B_{\max}} can be a maximum interference threshold seen by any user in the network for a given maximum transmit power budget \eqn{P_{\max}}.
+Note that the additional constraint on \eqn{\beta_{l,k,n}} will not alter the solution space of other optimization variables.
+However, as a consequence of considering the regularized objective in (46b), the additional constraint on \eqn{\beta_{l,k,n}} is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in (46b).
+We have highlighted this discussion on page 6, after (28).
 
@@
 	\underline{\textit{Reply:}} We agree with the reviewer's comment.
-The convergence of iterates cannot be guaranteed based on the strict monotonicity of the objective sequence and the uniqueness of minimizer in each step.
+Convergence of iterates cannot be guaranteed based on the strict monotonicity of the objective sequence and the uniqueness of minimizer in each step.
 We apologize for our emphasis on the convergence of sequence of iterates.
-In view of reviewer's suggestion, we have revised our claim based on subsequence convergence theory.
-
+Based on the reviewer's suggestion, we have modified the convergence analysis for the sequence of iterates generated by the centralized method in Appendices A-C and A-D.
+The revised discussion on the convergence of iterates is presented briefly here for reference.
 Since the feasible set is bounded, the iterates generated by the iterative algorithm are bounded.
 Therefore, there exists at least one subsequence that converges to a limit point.
-Now, by using a convergent subsequence of original sequence of iterates, we argued that every limit point is a stationary point of the original nonconvex problem.
-In order to do so, we used a unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}.
-Now, by using this unified index \eqn{t}, we represent iterate \eqn{\mbf{x}^{t}} as the solution variable produced by the iterative algorithm in every \ac{SCA} \eqn{k} and \ac{AO} step {i}.
-By using this notation and the subsequence argument, we have revised our convergence discussions in Appendices A-C and A-D.
-
-	Even though the feasible sets of the original nonconvex problem in (6) and the relaxed \ac{MSE} reformulated problem in (26) are bounded due to the total power constraint, we noted that the solution space of the relaxed nonconvex problem (16) need not be bounded.
-It is because of the newly introduced variables in (16b) and (16c) to relax the \ac{SINR} expression, since \eqn{\beta_{l,k,n}} can assume any value satisfying (16c) without violating any other constraints in (16) when \eqn{\gamma_{l,k,n} = 0}.
-In order to ensure boundedness of the feasible set, we can include an additional bounding constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}}, where \eqn{B_{\max}} can be a maximum interference threshold seen by any user in the network with the maximum transmit power constraint of \eqn{P_{\max}}.
-Note that the additional bounding constraint on \eqn{\beta_{l,k,n}} will not alter the solution space of other optimization variables.
-However, as a consequence of considering the regularized objective in (46b), the additional constraint on \eqn{\beta_{l,k,n}} is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in (46b).
-We have highlighted this information on page 6, after (28).
+Now, by using a convergent subsequence of the sequence of iterates, we argue that every limit point is a stationary point of the original nonconvex problem.
 
@@
 	\vspace{1eM}
-	\underline{\textit{Reply:}} We understand the reviewer's concern on using [R1] to our problem involving \ac{SCA} and \ac{AO} updates, which involves partial update of optimization variables.
-Even though our revised convergence proof is not based on [R1], we clarify our usage of [R1] for \ac{AO} update.
-Therefore, we refer to [R2], where the problem considered was to design tight frames based on solving matrix nearness problem using \ac{AO} approach.
-In order to prove the convergence of the sequence of iterates generated by the \ac{AO} iterations, [R1] is used with the composition of two sub-algorithms as discussed briefly in [Appendix I and II, R2].
+	\underline{\textit{Reply:}} We understand the reviewer's concern on using [R1] to our problem involving both \ac{SCA} and \ac{AO} updates, which solves only for a subset of optimization variables by keeping others fixed.
+Even though we have revised our convergence proof based on a convergent subsequence of the original sequence without referring [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates.
+We refer to [R2] for a similar usage of [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem.
+The usage of [R1] to address the convergence of \ac{AO} method in [R2] is based on the composition of two sub-algorithms and the compactness of the feasible set, where each sub-algorithm updates only a subset of optimization variables.
+It is discussed briefly in [Appendix I and II, R2] and in particular for \ac{AO} algorithm in [Appendix I-F, R2].
 
-	We note that in our previous manuscript, the convergence of the sequence of beamformer iterates claim based on [R1] was incomplete.
-We apologize for the incomplete usage of the theorem presented in [R1].
+	However, we note that in our previous manuscript, convergence of the sequence of beamformer iterates claim based on [R1] was incomplete and we apologize for that.
 In [Theorem.
@@
 Therefore, our earlier claim on the guaranteed convergence of the sequence of iterates is not correct as pointed out by the reviewer.
-Ensuring strict monotonic decrease in the objective sequence by restricting the solution set is discussed briefly in [Section 4, R1].
-By using [R1], we can only claim the convergence of subsequence of \eqn{\{\sol{t}\}} and not the sequence itself.
+Similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is highlighted in [Section 4, R1] under restrictive mapping.
+Therefore, by using the discussions in [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
 
-	We revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss briefly on the convergence of iterates.
-We show that every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
+	We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss the convergence of the sequence of iterates.
+We have shown that every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
 
@@
 	\begin{itemize}		
-
 		\item[R1.] R.R.
@@
 2005.
-		\item[R3.] D. P. Bertsekas, ``Nonlinear Programming," 2nd ed., \emph{Athena Scientific}, 1999.
 	\end{itemize}

### 2015-11-18 Response/Response 3/reviewer_response.tex
finalized

@@
 \vspace{0.5in}
-The authors are grateful to the associate editor for being considerate enough to provide us with this additional opportunity to revise and correct our convergence proof.
+The authors are grateful to the associate editor for being considerate enough to provide us with this additional opportunity to revise and correct our convergence analysis.
 We thank all the reviewers for their valuable comments on the manuscript, which have been greatly helpful to improve the paper quality.
-Based on the comments, we have revised our manuscript to ensure that all the reviewers comments are addressed properly and the technical correctness of the convergence proof is also verified.
+Based on the comments, we have revised our manuscript to ensure that all the reviewers comments are addressed properly and also verified the technical correctness of the convergence proof.
+We have also modified some parts of text to improve the readability.
 \input{additions}

### 2015-11-18 Report/convergence_distributed.tex
finalized

@@
-\reviewF{Assuming a regularized objective function as in \eqref{mod_obj} for each subproblem \eqref{eqn-decent-1}, convergence of Algorithm \ref{algo-3} follows the discussions in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the primal decomposition converges to the centralized solution.
-It can be ensured by the following properties.
-(i) The feasible set has a non-empty interior and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications.
-(ii) Due to the strongly convex objective \eqref{mod_obj} in each subproblem, uniqueness of the minimizer is guaranteed.
+\reviewF{Convergence of primal decomposition and \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution.
+To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved in a decentralized manner, by considering a regularized objective as in \eqref{mod_obj}.
+At first, the convergence of primal decomposition is discussed by using following properties.
+(i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications.
+(ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique.
 Therefore, by using the above facts, convergence of the primal decomposition algorithm can be ensured as \eqn{j \to \infty} using \cite[Prop.
@@
 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}.
-Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed schemes is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}
+Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed algorithms is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}
 
@@
 
-Unlike the primal or the \ac{ADMM} approaches, the decomposition method via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
+Unlike the primal or the \ac{ADMM} approaches, decomposition via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method.
 Therefore, it is difficult to theoretically prove the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.

### 2015-11-18 Report/dual_approach.tex
finalized

@@
 
-Assuming that the following conditions are satisfied in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large in order to ensure strict monotonicity of the objective, \reviewF{then the convergence follows the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}}.
-Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, then strict monotonic decrease of the objective sequence is still ensured.
+\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
+Moreover, even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence is still ensured.
 The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.
-However, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
-If so, convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
-The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.
+However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
+If so, then the convergence of the sequence of iterates generated by the distributed algorithm is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
+The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.}
 

### 2015-11-18 Report/kkt_mse_approach.tex
finalized

@@
 			evaluate \me{\epsilon_{l,k,n}^{(i)}}, \me{t_{l,k,n}^{(i)}}, \me{\sigma_{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1} at each user with the updated \me{\mvec{w}{l,k,n}^{(i)}} \;
-			using precoded uplink pilots, \me{\mvec{m}{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
+			using precoded uplink pilots, \me{\mvec{w}{l,k,n}^{(i)}} and \me{\alpha_{l,k,n}^{(i)}} are notified to all \acp{BS} in \me{\mathcal{B}} \;
 			\me{i = i + 1} \;

### 2015-11-18 Report/mse_formulation.tex
finalized

@@
 \reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} for \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
-The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step.
+The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each step.
 Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded.
@@
 Therefore, by restricting \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}}, the feasible set can be bounded without altering the solution space of other variables.
-However, as a consequence of considering the regularized objective in \eqref{mod_obj}, the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}.
+However, as a consequence of considering the regularized objective in \eqref{mod_obj}, the additional constraint on \eqn{\beta_{l,k,n}} is not required, since it is bounded due to the proximal term in \eqref{mod_obj}.
 With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}

### 2015-11-19 Report/convergence_centralized.tex
updated

@@
 
-Using the arguments in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges \cite[Prop.
+Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop.
 A.3]{bertsekas1999nonlinear}.
@@
 \begin{equation} \label{seq_mon}
-\dotsc < f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}) < \dotsc.
+f(\ma^{t_{j+1}}) \leq f(\ma^{t_{j}}).
 \end{equation}
@@
 \end{equation}
-Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point.
+\review{Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point.
+Now, we show that \eqn{\{\hat{f}(\ma^t)\}} is also convergent.
+Since \eqn{\{f(\mat{t}) \}} is monotonically decreasing, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}, therefore, we have
+\begin{equation} \label{mcity_origfunc}
+\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|.
+\end{equation}
+Moreover, we know that \eqn{\{\hat{f}(\mat{t})\}} is bounded, therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be ensured.}
 
-Now to prove that \eqn{\bar{\ma}} is also a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between gradients of subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}.
-In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point for \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
+Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between gradients of subproblems \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}.
+In order to ensure \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
 \begin{equation} \label{kkt_expr}

### 2015-11-19 Report/convergence_distributed.tex
updated

@@
-\reviewF{Convergence of primal decomposition and \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution.
-To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved in a decentralized manner, by considering a regularized objective as in \eqref{mod_obj}.
-At first, the convergence of primal decomposition is discussed by using following properties.
+\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution.
+To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}.
+At first, the convergence of the primal decomposition method is discussed by using following properties.
 (i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications.
 (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique.
-Therefore, by using the above facts, convergence of the primal decomposition algorithm can be ensured as \eqn{j \to \infty} using \cite[Prop.
-8.2.6]{bertsekas2003convex} by considering diminishing step size in each subgradient update.}
+\review{Therefore, by using the above facts, as \eqn{j \to \infty}, the convergence of the primal decomposition can be shown using \cite[Prop.
+8.2.6]{bertsekas2003convex} for a diminishing step size in each subgradient update.}}
 
@@
 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}.
-Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed algorithms is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}
+Therefore, if both the primal and the \ac{ADMM} methods are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the whole sequence of iterates generated by the distributed algorithms is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}
 
@@
 Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update.
-Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed.
 Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update.
-Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure convergence.
+Thus, the convergence of iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed.
 

### 2015-11-19 Report/decomposition_solutions.tex
updated

@@
 The coupling variables are updated in each iteration by exchanging limited information among the \acp{BS}.
-Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented as
+Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented for each \eqn{b \in \mc{B}} as
 \begin{IEEEeqnarray}{rCl} \neqsub
-\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b} \eqsub \\
-\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran. \eqsub
+\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{1,\mc{U}_b(1),1,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{L,\mc{U}_b(|\mc{U}_b|),N,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran \eqsub \\
+\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{1,\bar{\mc{U}}_b(1),1,b}, \dotsc, {\zeta}_{L,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),N,b} \right]^\tran. \eqsub
 \end{IEEEeqnarray}
@@
 \begin{equation}
-\mbfa{\zeta}_{b}(b_k) = \left [ {\zeta}_{l,\mc{U}_b(1),n,b_k},\dotsc, {\zeta}_{l,\mc{U}_b(|\mc{U}_b|),n,b_k} \right].
+\mbfa{\zeta}_{b}(b_k) = \left [ {\zeta}_{1,\mc{U}_b(1),1,b_k},\dotsc, {\zeta}_{L,\mc{U}_b(|\mc{U}_b|),N,b_k} \right].
 \end{equation}

### 2015-11-19 Report/dual_approach.tex
updated

@@
 	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
-	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall users}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \forall l,k,n}}
 	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
@@
 			}
-			send precoded downlink pilot with \me{\mbf{m}_{l,k,n}}\;
 			evaluate \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} at each user \;
@@
 
-\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
-Moreover, even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence is still ensured.
+\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large enough to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
+Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence can still be ensured.
 The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.
-However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}.
-If so, then the convergence of the sequence of iterates generated by the distributed algorithm is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
+However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of iterations, say, for \eqn{J_{\max}} only.
+In such a case, the convergence of the sequence of iterates generated by the distributed algorithm cannot not be guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
 The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.}

### 2015-11-19 Report/introduction.tex
updated

@@
 In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users existing in the network.
-We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}.
-Since the resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation one.
+We consider the problem of transmit precoder design and resource allocation over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}.
+Thus, the problem of interest inherently includes resource allocation of users associated with different \acp{BS}.
 
-In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or absence of a particular resource \cite{admission_control}.
+In general, the resource allocation problems such as admission control can be formulated by assigning a binary variable for each user to indicate the presence or absence of a particular resource \cite{admission_control}.
 Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables.
@@
 Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed.
-The \ac{MSE} reformulation for the \ac{WSRM} problem was also studied in \cite{hong2012decomposition} by using \ac{SCA} to solve the problem in an iterative manner.
+The \ac{MSE} reformulation for the \ac{WSRM} problem was also studied in \cite{kaleva2012weighted} by using \ac{SCA} to solve the problem in an iterative manner.
 Moreover, distributed precoder designs with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013decentralized}.

### 2015-11-19 Report/mse_formulation.tex
updated

@@
 The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion.
-Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}.
+Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,kaleva2012weighted}.
 Note that the receive beamformers based on the \ac{MMSE} criterion are independent of the choice of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.
@@
 In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
-\reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} for \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
+\reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
 The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each step.

### 2015-11-19 Report/problem_formulation_intro.tex
updated

@@
 
-Explicitly, the objective of the problem considered is given as \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. Thus the formulation becomes
+Explicitly, the objective of the problem considered is given as \me{\sum_{k \in \mc{U}} \, a_k | v_k |^q}. Thus, the formulation becomes
 \begin{IEEEeqnarray}{rCl} \label{eqn-3} \eqsubn
@@
 \text{subject to} & \quad&\sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \fall b \eqspace \label{eqn-4.3} \end{IEEEeqnarray}
-where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}, and \me{a_k} is the weighting factor, which is used to alter the user priority based on the \ac{QoS} constraints such as packet delay requirements and packet waiting time, since they are proportional to the corresponding number of backlogged packets.
+where \me{\tilde{v}_k \triangleq a_k^{1/{q}}v_k} is the element of vector \me{\tilde{\mbf{v}}}.
+Weighing factors \me{a_k} are used to alter the user priority based on the \ac{QoS} constraints such as packet delay requirements and packet waiting time, since they are proportional to the corresponding number of backlogged packets.
 The \ac{BS} specific power constraint for all sub-channels is considered in \eqref{eqn-4.3}.
@@
 \begin{itemize}
-\item \me{\ell_{1}} norm results in greedy allocation \textit{i.e}, emptying the queue of users with good channel states before considering the users with worse channel conditions.
+\item \me{\ell_{1}} norm results in greedy allocation, \textit{i.e}, emptying the queue of users with good channel states before considering the users with worse channel conditions.
 As a special case, it is easy to see that \eqref{eqn-3} reduces to the \ac{WSRM} problem when the queue size is large enough for all users.
 \item \me{\ell_{2}} norm prioritizes users with a higher number of queued packets before considering the users with a smaller number of backlogged packets.
-For example, it could be more ideal for the delay limited scenario when the packet arrival rates of the users are similar, since the number of backlogged packets is proportional to the delay in the transmission following the Little's law \cite{neely2010stochastic}.
+For example, it would be more ideal for the delay limited scenario when the packet arrival rate of users are almost similar, since the number of queued packets waiting in the buffer is proportional to the transmission delay, by following Little's law \cite{neely2010stochastic}.
 \item \(\ell_{\infty} \) norm minimizes the maximum number of queued packets among users with the current transmission, thereby providing queue fairness by allocating resources proportional to the number of backlogged packets.

### 2015-11-19 Report/wsrm_formulation.tex
updated

@@
 
-Upon convergence of the objective sequence, receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from the previous \ac{SCA} step.
+Upon convergence of the objective sequence or for some fixed \eqn{K_{\max}}, receivers are then updated using fixed \eqn{\mbf{m}^{(i)}_{\lpointx}} found in previous \ac{SCA} step.
 Once the receivers are updated, transmit precoders are again evaluated using the newly found receivers by solving \eqref{eqn-9} or \eqref{eqn-10}.

### 2015-11-19 Report/convergence_centralized.tex
updated

@@
 To do this, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}.
-Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity} that
+Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity}, we have
 \begin{equation} \label{seq_mon}
@@
 \review{Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point.
-Now, we show that \eqn{\{\hat{f}(\ma^t)\}} is also convergent.
-Since \eqn{\{f(\mat{t}) \}} is monotonically decreasing, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}, therefore, we have
+In order to ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}.
+Then, by using \eqref{mod_obj} and \eqref{strict_monotonicity}, monotonicity of \eqn{\{\hat{f}(\ma^t)\}} is shown by using \eqref{mod_obj} as
 \begin{equation} \label{mcity_origfunc}
-\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|.
+\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|
 \end{equation}
-Moreover, we know that \eqn{\{\hat{f}(\mat{t})\}} is bounded, therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be ensured.}
+where \eqn{\tau^t} is as in \eqref{mod_obj}. Additionally, by using Appendix \ref{c-a}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by \cite[Prop. A.3]{bertsekas1999nonlinear}.}
 

### 2015-11-20 Report/convergence_centralized.tex
different position for {\hat{f}(x^t)}

--- 2015-11-19 Report/convergence_centralized.tex
@@
 To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}.
-Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
+Since \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore,
 \begin{equation} \label{fixed_point}
@@
 
-Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop.
+\review{Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop.
+A.3]{bertsekas1999nonlinear}.
+Similarly, in order to ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, let us prove the monotonicity of \eqn{\{\hat{f}(\ma^t)\}} by considering an instant \eqn{t}.
+Let \eqn{\mat{t}} and \eqn{\mat{t+1}} be the minimizers of \eqref{con-m} for the iterations \eqn{{t-1}} and \eqn{{t}}, respectively.
+Then, by using \eqref{mod_obj} with the proximal term \eqn{\|\mat{} - \mat{t}\|^2} at \eqn{t}, we have
+\begin{equation} \label{mcity_origfunc}
+\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t})
+\end{equation}
+where \eqn{\tau^t} is defined as \eqn{\tau_k^{(i)}} in \eqref{mod_obj}.
+Additionally, by using Appendix \ref{c-a}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by using \cite[Prop.
 A.3]{bertsekas1999nonlinear}.
@@
 Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th.
-3.6]{rudin1964principles}.
+3.6]{rudin1964principles}.}
 
@@
 To do this, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}.
-Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity} that
-\begin{equation} \label{seq_mon}
-f(\ma^{t_{j+1}}) \leq f(\ma^{t_{j}}).
-\end{equation}
-%Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}. 
+Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, we have from Appendix \ref{mcity} that \eqn{f(\ma^{t_{j+1}}) \leq f(\ma^{t_{j}})}.
 Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
@@
 \review{Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point. 
-Now, we show that \eqn{\{\hat{f}(\ma^t)\}} is also convergent.
-Since \eqn{\{f(\mat{t}) \}} is monotonically decreasing, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}, therefore, we have
-\begin{equation} \label{mcity_origfunc}
-\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|.
-\end{equation}
-Moreover, we know that \eqn{\{\hat{f}(\mat{t})\}} is bounded, therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be ensured.}
+%In order to ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}.
+Then, by using \eqref{mod_obj} and \eqref{strict_monotonicity}, monotonicity of \eqn{\{\hat{f}(\ma^t)\}} is shown by using \eqref{mod_obj} as
+%\begin{equation} \label{mcity_origfunc}
+%\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|
+%\end{equation}
+%where \eqn{\tau^t} is as in \eqref{mod_obj}. Additionally, by using Appendix \ref{c-a}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by \cite[Prop. A.3]{bertsekas1999nonlinear}.
+}
 

### 2015-11-20 Response/Response 3/response-3.tex
with Antti reviews

--- 2015-11-13 Response/Response 3/response-3.tex
@@
 \vspace{1eM}
-\underline{\textit{Reply:}} We thank the reviewer for pointing the flaw in our earlier convergence proof.
-Based on the reviewer's suggestion, we have rewritten Appendix A-D with similar arguments used to discuss the convergence of projected gradient algorithms in [R3].
+\underline{\textbf{Response:}} We thank the reviewer for pointing out the mistake in our previous convergence proof.
+Based on the reviewer's comments and suggestions, we have rewritten Appendix A-D using subsequence convergence instead of claiming the sequence convergence.
 We hope that our current changes will be convincing enough to make the convergence proof complete.
 
-\begin{itemize}
+%As an observation, we have noted that the feasible set of nonconvex problem (16) need not be bounded, even if the feasible set of the original nonconvex problem in (6) and the relaxed \ac{MSE} reformulated problem in (26) is bounded.
+It happens in problem (16) because of the newly introduced optimization variables in (16b) and (16c) to relax the \ac{SINR} expression, since \eqn{\beta_{l,k,n}} can assume any value satisfying (16c) without violating any other constraints in (16) when \eqn{\gamma_{l,k,n} = 0}.
+Therefore, to ensure boundedness of the feasible set of problem (16), we can include an additional bounding constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}}, where \eqn{B_{\max}} can be a maximum interference threshold seen by any user in the network for a given maximum transmit power budget \eqn{P_{\max}}.
+Note that the additional constraint on \eqn{\beta_{l,k,n}} will not alter the solution space of other optimization variables.
+However, as a consequence of considering the regularized objective in (46b), the additional constraint on \eqn{\beta_{l,k,n}} is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in (46b).
+We have highlighted this discussion on page 6, after (28).
+
+\begin{enumerate}
 
@@
 	\vspace{1eM}
-	\underline{\textit{Reply:}} We agree with the reviewer's comment.
-The convergence of iterates cannot be guaranteed based on the strict monotonicity of the objective sequence and the uniqueness of minimizer in each step.
-We apologize for our emphasis on the convergence of sequence of iterates.
-In view of reviewer's suggestion, we have revised our claim based on subsequence convergence theory.
+	\underline{\textbf{Response:}} We thank the reviewer for pointing out that the sequence of iterates generated by the \ac{SCA} algorithm in each \ac{AO} step need not be convergent in Appendix A-C.
+Based on the reviewer's reference to Nonlinear Programming textbook, we have realized that our earlier convergence proof is not mathematically rigorous.
+We apologize for our emphasis on the convergence of iterates in our previous manuscript.
+As suggested by the reviewer, stationarity of limit points of the whole sequence of iterates is now addressed in Appendix A-D by using the following statements.
+	\begin{itemize}
+		\item The sequence of iterates generated by the algorithm is bounded, therefore, we can only claim that there exist at least one subsequence that converges to a limit point of the original sequence.
+		\item Using a convergent subsequence, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
+	\end{itemize}
 
-	Since the feasible set is bounded, the iterates generated by the iterative algorithm are bounded.
-Therefore, there exists at least one subsequence that converges to a limit point.
-Now, by using a convergent subsequence of original sequence of iterates, we argued that every limit point is a stationary point of the original nonconvex problem.
-In order to do so, we used a unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}.
-Now, by using this unified index \eqn{t}, we represent iterate \eqn{\mbf{x}^{t}} as the solution variable produced by the iterative algorithm in every \ac{SCA} \eqn{k} and \ac{AO} step {i}.
-By using this notation and the subsequence argument, we have revised our convergence discussions in Appendices A-C and A-D.
-
-	Even though the feasible sets of the original nonconvex problem in (6) and the relaxed \ac{MSE} reformulated problem in (26) are bounded due to the total power constraint, we noted that the solution space of the relaxed nonconvex problem (16) need not be bounded.
-It is because of the newly introduced variables in (16b) and (16c) to relax the \ac{SINR} expression, since \eqn{\beta_{l,k,n}} can assume any value satisfying (16c) without violating any other constraints in (16) when \eqn{\gamma_{l,k,n} = 0}.
-In order to ensure boundedness of the feasible set, we can include an additional bounding constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}}, where \eqn{B_{\max}} can be a maximum interference threshold seen by any user in the network with the maximum transmit power constraint of \eqn{P_{\max}}.
-Note that the additional bounding constraint on \eqn{\beta_{l,k,n}} will not alter the solution space of other optimization variables.
-However, as a consequence of considering the regularized objective in (46b), the additional constraint on \eqn{\beta_{l,k,n}} is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in (46b).
-We have highlighted this information on page 6, after (28).
+	We have made changes in Appendices A-C and A-D to address the concerns raised by the reviewer.
 
@@
 	\vspace{1eM}
-	\underline{\textit{Reply:}} We understand the reviewer's concern on using [R1] to our problem involving \ac{SCA} and \ac{AO} updates, which involves partial update of optimization variables.
-Even though our revised convergence proof is not based on [R1], we clarify our usage of [R1] for \ac{AO} update.
-Therefore, we refer to [R2], where the problem considered was to design tight frames based on solving matrix nearness problem using \ac{AO} approach.
-In order to prove the convergence of the sequence of iterates generated by the \ac{AO} iterations, [R1] is used with the composition of two sub-algorithms as discussed briefly in [Appendix I and II, R2].
+	\underline{\textbf{Response:}} We understand the reviewer's concern on using [R1] to our problem involving both \ac{SCA} and \ac{AO} updates.
+In each iteration, the proposed method solves only a subset of optimization variables by keeping others fixed, therefore, we cannot use [R1] directly as suggested by the reviewer.
+Even though we have revised our convergence proof based on a convergent subsequence without referring to [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates.
 
-	We note that in our previous manuscript, the convergence of the sequence of beamformer iterates claim based on [R1] was incomplete.
-We apologize for the incomplete usage of the theorem presented in [R1].
-In [Theorem.
-3.1, R1], it has been shown that if the strict monotonicity of the objective sequence is ensured and the iterates are bounded, then \textit{either the sequence of iterates converges or the accumulation points of \eqn{\{\sol{t}\}} is a continuum}.
-Therefore, our earlier claim on the guaranteed convergence of the sequence of iterates is not correct as pointed out by the reviewer.
-Ensuring strict monotonic decrease in the objective sequence by restricting the solution set is discussed briefly in [Section 4, R1].
-By using [R1], we can only claim the convergence of subsequence of \eqn{\{\sol{t}\}} and not the sequence itself.
+	\begin{itemize}
+		\item We refer to [R2] for a similar usage of [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem.
+In order to discuss the convergence of iterates generated by the \ac{AO} method, [R1] is used by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables.
+It has been discussed briefly in [R2, Appendices I and II], and in particular for \ac{AO} algorithm in [R2, Appendix I-F].
+		\item However, we apologize for the incomplete usage of [R1, Theorem 3.1] in our previous manuscript to claim the convergence of beamformer iterates.
+In [R1, Theorem.
+3.1], it has been shown that if the strict monotonicity of the objective sequence is ensured and the iterates are bounded, then \textit{either the sequence of iterates converges or the accumulation points of \eqn{\{\sol{t}\}} is a continuum}.
+		\item Therefore, our previous claim on the guaranteed convergence of iterates is not correct, as pointed out by the reviewer. 
+		\item Similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is discussed in [R1, Section 4] under restrictive mapping.
+Therefore, if we use the discussions in [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
+	\end{itemize}
 
-	We revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss briefly on the convergence of iterates.
-We show that every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
+	We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss the convergence of the sequence of iterates.
+We have shown that every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
 
@@
 2005.
-		\item[R3.] D. P. Bertsekas, ``Nonlinear Programming," 2nd ed., \emph{Athena Scientific}, 1999.
 	\end{itemize}
 
-\end{itemize}
+\end{enumerate}

### 2015-11-20 Report/convergence_centralized.tex
with Antti reviews

@@
 \begin{itemize}
-\item[(a)] Objective function should be bounded below
-\item[(b)] Feasible set should be compact
-\item[(c)] Sequence of objective values should be strictly decreasing
-\item[(d)] Uniqueness of the minimizer in each step.
+\item[(a)] Uniqueness of the minimizer in each step
+\item[(b)] Objective function should be bounded below
+\item[(c)] Feasible set should be compact
+\item[(d)] Sequence of objective values should be strictly decreasing
 \end{itemize}
-Note that condition (d) is required to ensure strict monotonicity of the objective sequence.
-Therefore, by using above conditions (a)-(c) along with \cite[Th.
+Note that condition (a) is required to ensure strict monotonicity of the objective sequence.
+Therefore, by using above conditions (a)-(d) along with \cite[Th.
 3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}.
@@
 
-\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
-The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, due to the total power constraint on transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.
-
-The minimum value of the norm function in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below.
-Additionally, the objective function is Lipschitz continuous and due to the fact that the feasible set is compact, objective function is bounded from above as well.
-
 \subsection{Uniqueness of the Iterates and Strong Convexity} \label{c-a}
@@
 
+\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
+The feasible set of problems \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on transmit precoders by \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.
+
+The minimum value of the norm function present in the objective is \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all exponents used in \eqn{\ell_q} norm, therefore, it is bounded from below.
+Moreover, by the fact that the feasible set is compact, the objective function is Lipschitz continuous, and therefore bounded from above as well.
+
 \subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
@@
 However, we note that upon convergence \eqn{f} is equal to \eqn{\hat{f}}.
-Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.
+Therefore, the discussions are valid for the \ac{JSFRA} problems in \eqref{eqn-6} and \eqref{eqn-mse-1} by regularizing the objective functions \eqref{eqn-6.1} and \eqref{eqn-mse-1.1} as \eqref{mod_obj}.
 
@@
 To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}.
-Since \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore,
+Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
 \begin{equation} \label{fixed_point}
@@
 It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
-Using the unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
+Using the unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
 
 \review{Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop.
-A.3]{bertsekas1999nonlinear}.
-Similarly, in order to ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, let us prove the monotonicity of \eqn{\{\hat{f}(\ma^t)\}} by considering an instant \eqn{t}.
-Let \eqn{\mat{t}} and \eqn{\mat{t+1}} be the minimizers of \eqref{con-m} for the iterations \eqn{{t-1}} and \eqn{{t}}, respectively.
-Then, by using \eqref{mod_obj} with the proximal term \eqn{\|\mat{} - \mat{t}\|^2} at \eqn{t}, we have
-\begin{equation} \label{mcity_origfunc}
-\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t})
-\end{equation}
-where \eqn{\tau^t} is defined as \eqn{\tau_k^{(i)}} in \eqref{mod_obj}.
-Additionally, by using Appendix \ref{c-a}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by using \cite[Prop.
 A.3]{bertsekas1999nonlinear}.
@@
 
+\review{Before proceeding further, we ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that \eqn{\{\hat{f}(\ma^t)\}} is monotonically decreasing in each step \eqn{t}.
+To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively.
+Then, by using \eqn{\mat{t}} in the proximal term of \eqref{mod_obj} as \eqn{\|\mat{} - \mat{t}\|^2}, the following inequality holds at every update step \eqn{{t}} as
+\begin{equation} \label{mcity_origfunc}
+\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t})
+\end{equation}
+where \eqn{\tau^t} is defined as \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}.
+Therefore, by using \eqref{mcity_origfunc} and Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by using \cite[Prop.
+A.3]{bertsekas1999nonlinear}.}
+
 Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between gradients of subproblems \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}.
@@
 
-Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}.
+Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)} \subset \mc{F}} and \eqn{\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}.
 Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}.
@@
 \end{equation}
-The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}.
+The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}.
 Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.

### 2015-11-20 Report/dual_approach.tex
with Antti reviews

@@
 However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of iterations, say, for \eqn{J_{\max}} only.
-In such a case, the convergence of the sequence of iterates generated by the distributed algorithm cannot not be guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
-The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.}
+In such a case, the convergence of the sequence of iterates generated by the distributed algorithm cannot not be ensured, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
+It follows from the fact that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}
 

### 2015-11-20 Report/simulation_distributed.tex
with Antti reviews

@@
 Fig.
-\ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \ac{PL} chosen uniformly between \me{[0,-3]} dB.
-The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other schemes due to the greedy nature of the objective.
+\ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \ac{PL} chosen uniformly between \me{[0,-3]} dB.
+The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other \eqn{\ell_q} norms due to the greedy nature of the objective.
 The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in Section \ref{sec-4.3}.

### 2015-11-20 Report/simulation_results.tex
with Antti reviews

@@
 To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources.
-The total number of backlogged packets waiting at the transmitter for each user is given by \me{Q_k = 4,8} and \me{4} bits, respectively.
+The total number of backlogged packets waiting at the transmitter for each user is given by \me{Q_1 = 4}, \eqn{Q_2 = 8} and \me{Q_3 = 4} bits, respectively.
 \begin{table}
@@
 
-Table \ref{tbl-1} tabulates the channels of the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the sub-channel wise \ac{Q-WSRM} scheme using the \ac{WMMSE} design \cite{wmmse_shi}.
+Table \ref{tbl-1} tabulates the channels of the users over each sub-channel followed by the rates assigned by three different algorithms, \ac{Q-WSRME} allocation, \ac{JSFRA} approach and the sub-channel wise \ac{Q-WSRM} scheme using the \ac{MSE} reformulation for all cases \cite{christensen2008weighted}.
 The metric used for the comparison is the total number of backlogged bits left over after each transmission, which is denoted as \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}.
@@
 For a \ac{MIMO} setup, we consider a system with \me{N=4} and \eqn{N=2} sub-channels with \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each.
-The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the \ac{BS}-user associations are made by selecting the \ac{BS} with the lowest \ac{PL} component.
+The \ac{PL} difference between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the \ac{BS}-user associations are made by selecting the \ac{BS} with the lowest \ac{PL} component.
 Fig.
@@
 It is evident that the \ac{JSFRA} algorithm minimizes the total number of queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits.
-The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets to be equal for all users to \me{\chi_k = 3.58} bits.
+The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the leftover packets to be equal for all users to \me{\chi_k = 3.58} bits.

### 2015-11-20 Response/Response 3/additions.tex
finalized
with Antti reviews

@@
 	\item Page 6, paragraph after (28)
-	\item Page 8, \eqn{\ith{13}} line on last paragraph in Section IV-B
+	\item Page 8, last paragraph in Section IV-B
 	\item Page 12, paragraph following itemized requirements in Appendix A
@@
 \end{itemize}
+
+Finally, to discuss the convergence of the sequence of iterates generated by the centralized scheme in Algorithm 1, we use an unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}.
+By doing so, we represent iterate \eqn{\mbf{x}^{t}} as the solution variable produced by the iterative algorithm in every \ac{SCA} \eqn{k} and \ac{AO} step {i}.
+Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.

### 2015-11-22 Response/Response 3/response-3.tex
updated

@@
 	\vspace{1eM}
-	\underline{\textbf{Response:}} We thank the reviewer for pointing out that the sequence of iterates generated by the \ac{SCA} algorithm in each \ac{AO} step need not be convergent in Appendix A-C.
-Based on the reviewer's reference to Nonlinear Programming textbook, we have realized that our earlier convergence proof is not mathematically rigorous.
+	\underline{\textbf{Response:}} We thank the reviewer for pointing out that the sequence of iterates generated by the \ac{SCA} algorithm in each \ac{AO} step need not be convergent.
+Based on the reviewer's reference to the gradient projection algorithm in Nonlinear Programming textbook, we have realized that our earlier convergence proof is not mathematically rigorous.
 We apologize for our emphasis on the convergence of iterates in our previous manuscript.
@@
 		\item The sequence of iterates generated by the algorithm is bounded, therefore, we can only claim that there exist at least one subsequence that converges to a limit point of the original sequence.
-		\item Using a convergent subsequence, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
+		\item Using a convergent subsequence of the original sequence of iterates, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
 	\end{itemize}
@@
 		\item We refer to [R2] for a similar usage of [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem.
-In order to discuss the convergence of iterates generated by the \ac{AO} method, [R1] is used by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables.
-It has been discussed briefly in [R2, Appendices I and II], and in particular for \ac{AO} algorithm in [R2, Appendix I-F].
+The reference [R1] used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables.
+It has been discussed comprehensively in [R2, Appendices I and II].
+In particular, the discussion on referring \ac{AO} as two sub-algorithms is presented in [R2, Appendix I-F].
 		\item However, we apologize for the incomplete usage of [R1, Theorem 3.1] in our previous manuscript to claim the convergence of beamformer iterates.
@@
 		\item Therefore, our previous claim on the guaranteed convergence of iterates is not correct, as pointed out by the reviewer. 
-		\item Similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is discussed in [R1, Section 4] under restrictive mapping.
-Therefore, if we use the discussions in [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
+		\item Similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is presented in [R1, Section 4] under restrictive mapping section.
+Therefore, even if we use the discussions in [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
 	\end{itemize}
@@
 	We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss the convergence of the sequence of iterates.
-We have shown that every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
+We have revised our claim as every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
 

### 2015-11-22 Response/Response 3/reviewer_response.tex
updated

@@
 
-\vspace{0.5in}
+\vspace{0.35in}
 The authors are grateful to the associate editor for being considerate enough to provide us with this additional opportunity to revise and correct our convergence analysis.

### 2015-11-22 Report/convergence_centralized.tex
updated

@@
 \end{itemize}
-Note that condition (a) is required to ensure strict monotonicity of the objective sequence.
-Therefore, by using above conditions (a)-(d) along with \cite[Th.
-3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}.
-Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by the Algorithm \ref{algo-1} is a stationary point of original nonconvex problem formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the Algorithm \ref{algo-1}, using \cite[Th.
+3.14]{rudin1964principles}.
+However, it is not  sufficient enough to ensure the convergence of the corresponding sequence of iterates.
+Therefore, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can only claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.
 
-Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
+Before discussing further on the analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
 \begin{IEEEeqnarray}{RcL} \label{con} \neqsub
@@
 It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
-Using the unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
+Using this unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
 
-\review{Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop.
-A.3]{bertsekas1999nonlinear}.
+\review{By following the discussions in Appendices \ref{b_obj} and \ref{mcity}, the sequence \eqn{\{f(\ma^t)\}} generated by the algorithm is bounded and monotonically decreasing, therefore, by using \cite[Prop.
+A.3]{bertsekas1999nonlinear}, convergence of the sequence \eqn{\{f(\ma^t)\}} can be ensured.
 Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}.
 However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded.
-Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th.
+Therefore, we can only claim that there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th.
 3.6]{rudin1964principles}.}
@@
 Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point.
-However, from \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of \eqn{\{\ma^t\}}, which is a contradiction to our initial assumption.
+However, by using \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of \eqn{\{\ma^t\}}, which is a contradiction to our initial assumption.
 
@@
 
-\review{Before proceeding further, we ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that \eqn{\{\hat{f}(\ma^t)\}} is monotonically decreasing in each step \eqn{t}.
+\review{Before proceeding further, we ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that \eqn{\{\hat{f}(\ma^t)\}} is decreasing in every update and it is bounded.
 To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively.
-Then, by using \eqn{\mat{t}} in the proximal term of \eqref{mod_obj} as \eqn{\|\mat{} - \mat{t}\|^2}, the following inequality holds at every update step \eqn{{t}} as
+Since the proximal term in \eqref{mod_obj} is given as \eqn{\|\mat{} - \mat{t}\|^2} for iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
 \begin{equation} \label{mcity_origfunc}
-\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t})
+\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|^2
 \end{equation}
-where \eqn{\tau^t} is defined as \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}.
-Therefore, by using \eqref{mcity_origfunc} and Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by using \cite[Prop.
+where \eqn{\tau^t} denotes \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}.
+Thus, by extending \eqref{mcity_origfunc} to every update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop.
 A.3]{bertsekas1999nonlinear}.}
@@
 \end{equation}
-The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}.
+
+The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by using following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}.
 Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
@@
 \end{equation}
-If follows immediately from \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr} that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
-Finally, by following \cite[Thms.
+Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+Finally, by using \cite[Thms.
 2 and 11]{scutari_1} and \cite[Prop.
-3.2]{amir}, we can prove that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of the problem \eqref{con}.}
+3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of problem \eqref{con}.}

### 2015-11-22 Report/convergence_distributed.tex
different position for {\hat{f}(x^t)}
updated

@@
 (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique.
-\review{Therefore, by using the above facts, as \eqn{j \to \infty}, the convergence of the primal decomposition can be shown using \cite[Prop.
-8.2.6]{bertsekas2003convex} for a diminishing step size in each subgradient update.}}
+\review{Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop.
+8.2.6]{bertsekas2003convex} by using diminishing step size in each subgradient update.}}
 

### 2015-11-22 Report/dual_approach.tex
updated

@@
 
-\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large enough to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
-Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence can still be ensured.
+\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, convergence analysis follow the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
+Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since strict monotonic decrease of the objective sequence can still be ensured.
 The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.
-However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of iterations, say, for \eqn{J_{\max}} only.
-In such a case, the convergence of the sequence of iterates generated by the distributed algorithm cannot not be ensured, since it is difficult to show the monotonicity of objective in each \ac{SCA} step.
+However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only.
+In such a case, convergence of the distributed algorithms cannot not be ensured, since it is difficult to show that the objective value is monotonically decreasing at every \ac{SCA} step.
 It follows from the fact that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}

### 2015-11-22 Response/Response 3/additions.tex
updated

@@
+In summary, the revised manuscript includes the following changes.
 \begin{enumerate}
@@
 
-Finally, to discuss the convergence of the sequence of iterates generated by the centralized scheme in Algorithm 1, we use an unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}.
+\vspace{1eM}
+In order to discuss the convergence of the sequence of iterates generated by the centralized scheme in Algorithm 1, we use an unified superscript index \eqn{t} to represent both \ac{AO} index \eqn{i} and \ac{SCA} indexing \eqn{k}.
 By doing so, we represent iterate \eqn{\mbf{x}^{t}} as the solution variable produced by the iterative algorithm in every \ac{SCA} \eqn{k} and \ac{AO} step {i}.

### 2015-11-24 Report/convergence_centralized.tex
before Nam's correction

@@
 \reviewF{We discuss the convergence of the iterates generated by the iterative algorithm.
-In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}.
-It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
+In order to do that, let us consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}.
+It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each \ac{AO} step.
 Using this unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

### 2015-11-24 Report/mse_formulation.tex
before Nam's correction

@@
 \end{IEEEeqnarray}
-For fixed receivers, transmit precoders are obtained by solving \eqref{eqn-mse-2} iteratively by updating \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} found in previous iteration until termination as discussed in Section \ref{sec-3.2.1}.
+For fixed receivers, transmit precoders are obtained by solving \eqref{eqn-mse-2} iteratively by updating \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} found in previous step until termination as in Section \ref{sec-3.2.1} and Algorithm \ref{algo-1}.
 

### 2015-11-24 Response/Response 3/reviewer_response.tex
updated and finalized

--- 2015-11-13 Response/Response 3/reviewer_response.tex
@@
 
-\vspace{0.5in}
-The authors are grateful to the associate editor for being considerate enough to provide us with this additional opportunity to revise and correct our convergence proof.
-We thank all the reviewers for their valuable comments on the manuscript, which have been greatly helpful to improve the paper quality.
-Based on the comments, we have revised our manuscript to ensure that all the reviewers comments are addressed properly and the technical correctness of the convergence proof is also verified.
-\input{additions}
+	\vspace{0.35in}
+	The authors are grateful to the associate editor for giving us an additional opportunity to revise and correct our convergence analysis.
+In this regard, we would like to give a special thank to Review 3 who pointed out the issues with our convergence analysis of the proposed solutions.
+In this revision, we have mainly focused on providing a more mathematically rigorous  proof of the convergence analysis of the proposed iterative algorithms.
+	%\input{additions}
+	Towards this end the following changes have been made to the revised manuscript.
+	\begin{enumerate}
+		\item We have restated the convergence results of the centralized algorithms in this revision, claiming that any accumulated point (i.e., a limit point) is a stationary point.
+The proof is essentially based on the convergence of a subsequence of iterates.
+We have rewritten Appendix A-D according to these changes.
+In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})).
+Using this index \eqn{t}, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving convex subproblem \eqref{con-m} at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration.
+Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.
+		\item We have updated the convergence of distributed algorithms in a similar way.
+	\end{enumerate}
 
+	We have  also revised some parts of text to support the changes mentioned above and to further improve the readability. Specifically, the following parts of the revision have been rewritten.
+	\begin{itemize}
+		\item Page 6, paragraph after (28): We have elaborated the discussions on showing that the feasible set is bounded.
+		\item Page 8, last paragraph in Section IV-B: We discussed the conditions under which the overall algorithm converges upon using the distributed schemes in each \ac{SCA} step.
+		\item Last sentence after (51) on page 14: We emphasized the convergence of objective sequence only in each \ac{AO} step. 
+		\item Last sentence after (60) on page 15: We have rewritten the convergence claim on the sequence of iterates generated by the Algorithm 2 similar to that of centralized method.
+	\end{itemize}
+
+	\vspace{1eM}
+	In what follows, the comments are listed, each followed immediately by the corresponding reply from the authors.
+The reviewers questions in the revised manuscript are highlighted in blue color and the authors responses are presented in black.
+Unless otherwise stated, all the numbered items (figures, equations, references, citations, etc) in this response letter refer to the revised manuscript.
+All revisions in the manuscript are highlighted in blue color.
 	\newpage

### 2015-11-24 Report/convergence_centralized.tex
updated and finalized

--- 2015-11-22 Report/convergence_centralized.tex
@@
 \end{itemize}
+Note that the uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence.
 Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the Algorithm \ref{algo-1}, using \cite[Th.
 3.14]{rudin1964principles}.
-However, it is not  sufficient enough to ensure the convergence of the corresponding sequence of iterates.
-Therefore, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can only claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.
 
@@
 The uniqueness of the iterates \eqn{\{\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}\}} can be ensured for the \ac{MSE} reformulated problem in \eqref{eqn-mse-2} when all the constraints are active.
-However when \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, the uniqueness cannot be guaranteed as there can be multiple solutions with the same objective value in the feasible set.
-Similarly, when the objective is non-zero for \eqref{eqn-9}, the minimizer is unique only if the receivers are matched to the transmit beamformers.
+However, if \eqn{\hat{f}(\iter{\mx}{k}{i},\iter{\my}{\lpointx}{i-1},\iter{\mz}{k|\my}{i}) = 0} after some iteration, say \me{k} and \me{i}, then the uniqueness is not ensured as there can be multiple solutions in the feasible set.
 
-To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
+To ensure the uniqueness of transmit and receive beamformers in each iteration, the objective function of subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 \end{IEEEeqnarray}
-where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step.
+where \eqn{\mbf{z}} is a vector formed by stacking all optimization variables that can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the variables that are fixed.
+Moreover, \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained on the \eqn{\ith{(k-1)}} \ac{SCA} step of \ac{AO} update instant \eqn{i}.
 The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite[Sec.
@@
 \subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
-The feasible set of problems \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on transmit precoders by \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.
+The feasible set of problems \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on the transmit precoders by the constraints \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.
 
@@
 \subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
-In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} to exploit the uniqueness of the minimizer at each iteration.
-However, we note that upon convergence \eqn{f} is equal to \eqn{\hat{f}}.
+In the following discussions, we consider the modified objective \eqn{f(\mbf{z})} in \eqref{mod_obj} instead of \eqn{\hat{f}(\mbf{z})} to exploit the uniqueness of the minimizer at each iteration.
+However, note that upon convergence \eqn{f(\mbf{z})} is equal to \eqn{\hat{f}(\mbf{z})}.
 Therefore, the discussions are valid for the \ac{JSFRA} problems in \eqref{eqn-6} and \eqref{eqn-mse-1} by regularizing the objective functions \eqref{eqn-6.1} and \eqref{eqn-mse-1.1} as \eqref{mod_obj}.
@@
 Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}.
-Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in every \ac{SCA} update \cite{scutari2010convex}.
-\reviewF{Since the objective is strictly decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in every \ac{AO} step \eqn{i}.
+Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} update \cite{scutari2010convex}.
+\reviewF{Since the objective is strictly decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in each \ac{AO} step \eqn{i}.
 Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} update.}
@@
 \end{equation}}
-Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}.
-To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}.
+Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} with respect to \eqn{\mx} and \eqn{\mz} by performing \ac{SCA} update as \eqn{k \to \infty} in the \me{\ith{i}} \ac{AO} step with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}.
+In order to find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and solve problem \eqref{con-m} for \me{\my} and \eqn{\mz}.
 Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
@@
 Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges.
-Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in every \ac{SCA} and \ac{AO} step.}
+Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in each \ac{SCA} and \ac{AO} step.}
 
 \subsection{Stationarity of Limit Points} \label{c-b}
-\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm.
-In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}.
-It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
-Using this unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.
+\reviewF{We now discuss the convergence properties of the sequence of iterates generated by the proposed algorithm.
+For convenience, let us consider a unified superscript index \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})).
+Using this, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving \eqref{con-m} at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration.
+%Furthermore, we introduce variable \eqn{\ma^{t}} to denote a vector formed by stacking solution obtained at \eqn{\ith{t}} iteration, \textit{i.e.}, \eqn{\mat{t} = \mbf{z}^{(i)}_k}, the respective iterate.
 
-\review{By following the discussions in Appendices \ref{b_obj} and \ref{mcity}, the sequence \eqn{\{f(\ma^t)\}} generated by the algorithm is bounded and monotonically decreasing, therefore, by using \cite[Prop.
-A.3]{bertsekas1999nonlinear}, convergence of the sequence \eqn{\{f(\ma^t)\}} can be ensured.
-Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}.
-However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded.
-Therefore, we can only claim that there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th.
-3.6]{rudin1964principles}.}
+The objective sequence \eqn{\{f(\ma^t)\}} generated by the algorithm is bounded and monotonically decreasing (see Appendices \ref{b_obj} and \ref{mcity}).
+Therefore, by using \cite[Prop.
+A.3]{bertsekas1999nonlinear}, the convergence of the sequence \eqn{\{f(\ma^t)\}} can be ensured.
+Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}.
+However, since the feasible set is compact, the sequence \eqn{\{\ma^t\}} is bounded.
+Therefore, the sequence \eqn{\{\ma^t\}} has at least one limit point, say \eqn{\bar{\mbf{x}}}, such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\mbf{x}}} \cite[Prop.
+A.5]{bertsekas1999nonlinear}.
 
@@
 \end{equation}
-\review{Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point. 
-%In order to ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}.
-Then, by using \eqref{mod_obj} and \eqref{strict_monotonicity}, monotonicity of \eqn{\{\hat{f}(\ma^t)\}} is shown by using \eqref{mod_obj} as
-%\begin{equation} \label{mcity_origfunc}
-%\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|
-%\end{equation}
-%where \eqn{\tau^t} is as in \eqref{mod_obj}. Additionally, by using Appendix \ref{c-a}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by \cite[Prop. A.3]{bertsekas1999nonlinear}.
-}
+Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.
 
-\review{Before proceeding further, we ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that \eqn{\{\hat{f}(\ma^t)\}} is decreasing in every update and it is bounded.
+Before proceeding further, we also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that the original objective function in \eqref{orig_obj} also decreases at each iteration.
 To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively.
-Since the proximal term in \eqref{mod_obj} is given as \eqn{\|\mat{} - \mat{t}\|^2} for iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
+Since \eqn{\|\mat{} - \mat{t}\|^2} is the proximal term in \eqref{mod_obj} for iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
 \begin{equation} \label{mcity_origfunc}
@@
 Thus, by extending \eqref{mcity_origfunc} to every update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop.
-A.3]{bertsekas1999nonlinear}.}
+A.3]{bertsekas1999nonlinear}.
 

### 2015-11-24 Report/convergence_distributed.tex
updated and finalized

--- 2015-11-19 Report/convergence_distributed.tex
@@
 (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique.
-\review{Therefore, by using the above facts, as \eqn{j \to \infty}, the convergence of the primal decomposition can be shown using \cite[Prop.
-8.2.6]{bertsekas2003convex} for a diminishing step size in each subgradient update.}}
+Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop.
+8.2.6]{bertsekas2003convex} by using diminishing step size in each subgradient update.}
 

### 2015-11-24 Report/dual_approach.tex
updated and finalized

@@
 
-\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, convergence analysis follow the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
+\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, convergence analysis follows the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
 Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since strict monotonic decrease of the objective sequence can still be ensured.
@@
 However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only.
-In such a case, convergence of the distributed algorithms cannot not be ensured, since it is difficult to show that the objective value is monotonically decreasing at every \ac{SCA} step.
-It follows from the fact that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}
+In such a case, convergence of the distributed algorithms cannot not be ensured, since it is impossible to show that the objective value is monotonically decreasing at every \ac{SCA} step.
+We recall that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}
 

### 2015-11-24 Report/mse_formulation.tex
updated and finalized

@@
 
-In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
-\reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
-The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each step.
+In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
+\reviewF{However, to provide a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
+The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration.
 Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded.
-However, for \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
-Therefore, by restricting \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}}, the feasible set can be bounded without altering the solution space of other variables.
-However, as a consequence of considering the regularized objective in \eqref{mod_obj}, the additional constraint on \eqn{\beta_{l,k,n}} is not required, since it is bounded due to the proximal term in \eqref{mod_obj}.
-With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}
+However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
+Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem.
+By using the above assumptions, convergence analysis for the centralized problem is discussed in Appendix \ref{sec-3.5}.}
 

### 2015-11-24 Response/Response 3/reviewer_response.tex
updated

@@
 In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})).
-Using this index \eqn{t}, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving convex subproblem \eqref{con-m} at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration.
+Using this index \eqn{t}, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving convex subproblem (48) at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration.
 Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.

### 2015-11-25 Response/Response 3/response-3.tex
finalized so far

@@
 	\begin{itemize}
-		\item The sequence of iterates generated by the algorithm is bounded, therefore, we can only claim that there exist at least one subsequence that converges to a limit point of the original sequence.
-		\item Using a convergent subsequence of the original sequence of iterates, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
+		\item The sequence of iterates generated by the algorithm is bounded, therefore, we can claim that there exist at least one subsequence of original sequence that converges to a limit point of original sequence.
+		\item Using a convergent subsequence of original sequence of iterates, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
 	\end{itemize}
@@
 	\vspace{1eM}
-	\underline{\textbf{Response:}} We understand the reviewer's concern on using [R1] to our problem involving both \ac{SCA} and \ac{AO} updates.
-In each iteration, the proposed method solves only a subset of optimization variables by keeping others fixed, therefore, we cannot use [R1] directly as suggested by the reviewer.
+	\underline{\textbf{Response:}} We understand the reviewer's concern on using reference [R1] to our problem involving both \ac{SCA} and \ac{AO} updates.
+In each iteration, the proposed method solves only a subset of optimization variables by keeping others fixed, therefore, we cannot use reference [R1] directly as suggested by the reviewer.
 Even though we have revised our convergence proof based on a convergent subsequence without referring to [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates.
@@
 	\begin{itemize}
-		\item We refer to [R2] for a similar usage of [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem.
+		\item We refer to [R2] for a similar usage of reference [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem.
 The reference [R1] used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables.
@@
 3.1], it has been shown that if the strict monotonicity of the objective sequence is ensured and the iterates are bounded, then \textit{either the sequence of iterates converges or the accumulation points of \eqn{\{\sol{t}\}} is a continuum}.
-		\item Therefore, our previous claim on the guaranteed convergence of iterates is not correct, as pointed out by the reviewer. 
-		\item Similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is presented in [R1, Section 4] under restrictive mapping section.
-Therefore, even if we use the discussions in [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
+		\item Therefore, our previous statement claiming guaranteed convergence of iterates is not correct, as pointed out by the reviewer. 
+		\item A similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is presented in [R1, Section 4] under restrictive mapping title.
+Therefore, even if we use the discussions from reference [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
 	\end{itemize}
@@
 	We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss the convergence of the sequence of iterates.
-We have revised our claim as every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
+We have revised our statement as every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.
 

### 2015-11-25 Response/Response 3/reviewer_response.tex
finalized so far

@@
 	\begin{enumerate}
-		\item We have restated the convergence results of the centralized algorithms in this revision, claiming that any accumulated point (i.e., a limit point) is a stationary point.
+		\item We have restated the convergence results of the centralized algorithms in this revision, claiming that any accumulation point (i.e., limit point) is a stationary point.
 The proof is essentially based on the convergence of a subsequence of iterates.
@@
 In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})).
-Using this index \eqn{t}, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving convex subproblem (48) at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration.
-Using this notation, we have revised our convergence discussions in Appendices A-C and A-D.
+Then, by using index \eqn{t}, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer obtained by solving (48) at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence of minimizers obtained at each iteration.
+With these notations, we have revised our convergence discussions in Appendices A-C and A-D.
 		\item We have updated the convergence of distributed algorithms in a similar way.
@@
 		\item Page 6, paragraph after (28): We have elaborated the discussions on showing that the feasible set is bounded.
-		\item Page 8, last paragraph in Section IV-B: We discussed the conditions under which the overall algorithm converges upon using the distributed schemes in each \ac{SCA} step.
-		\item Last sentence after (51) on page 14: We emphasized the convergence of objective sequence only in each \ac{AO} step. 
+		\item Page 8, last paragraph in Section IV-B: We have highlighted the conditions under which the overall objective sequence generated by the distributed methods will converge.
+		\item Last sentence after (51) on page 14: We have emphasized the convergence of objective sequence only in each \ac{AO} step and not the iterates. 
 		\item Last sentence after (60) on page 15: We have rewritten the convergence claim on the sequence of iterates generated by the Algorithm 2 similar to that of centralized method.

### 2015-11-25 Report/convergence_centralized.tex
finalized so far

@@
 Note that the uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence.
-Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the Algorithm \ref{algo-1}, using \cite[Th.
+Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the centralized method in Algorithm \ref{algo-1} by using \cite[Th.
 3.14]{rudin1964principles}.
@@
 
-To ensure the uniqueness of transmit and receive beamformers in each iteration, the objective function of subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
+To ensure the uniqueness of transmit and receive beamformers in each iteration, the objective function of subproblems \eqref{eqn-9} and \eqref{eqn-mse-2} is regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as
 \begin{IEEEeqnarray}{rCl} \neqsub
@@
 \end{IEEEeqnarray}
-where \eqn{\mbf{z}} is a vector formed by stacking all optimization variables that can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the variables that are fixed.
-Moreover, \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained on the \eqn{\ith{(k-1)}} \ac{SCA} step of \ac{AO} update instant \eqn{i}.
-The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite[Sec.
+where vector \eqn{\mbf{z}} is formed by stacking all optimization variables that can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the fixed variables.
+Moreover, \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be a stacked vector of solution obtained at the \eqn{\ith{(k-1)}} \ac{SCA} step in \ac{AO} iteration \eqn{i}.
+The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f(\mbf{z})} in each step \cite[Sec.
 3.4.3]{bertsekas1989parallel}.
-Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.
+Thus, due to strong convexity in \eqn{f(\mbf{z})}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.
 
 \subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
-The feasible set of problems \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on the transmit precoders by the constraints \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.
+The feasible set of \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on transmit precoders, given by \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.%\footnote{The feasible set in each iteration is bounded due to the proximal operator in \eqref{mod_obj} as \eqn{\{\mbf{z} | f(\mbf{z}) \leq f(\mbf{z}_k^{(i)})\}}, therefore, the sequence \eqn{\{\mbf{z}_k^{(i)}\}} is bounded.}
 
-The minimum value of the norm function present in the objective is \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all exponents used in \eqn{\ell_q} norm, therefore, it is bounded from below.
-Moreover, by the fact that the feasible set is compact, the objective function is Lipschitz continuous, and therefore bounded from above as well.
+Since the norm function present in the objective satisfies \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all \eqn{q} used in \eqn{\ell_q} norm, it is bounded from below.
+Moreover, due to the compactness of the feasible set, it is bounded from above as well.
+In addition, the objective function satisfies Lipschitz continuity, since the feasible set is compact.
 
@@
 Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for variables \me{\mx} and \me{\mz} is given by
-\begin{IEEEeqnarray}{rCl} \label{con-m} \neqsub
+\begin{IEEEeqnarray}{rCl} \label{con-m} \neqsub \allowdisplaybreaks
 \underset{\mx,\mz}{\text{minimize}} &\quad& f(\mx,\iter{\my}{\lpoint}{i-1},\mz) \eqsub \label{con-obj-m} \\
@@
 Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} update \cite{scutari2010convex}.
-\reviewF{Since the objective is strictly decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in each \ac{AO} step \eqn{i}.
-Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be the solution obtained upon convergence of the objective sequence in the \eqn{\ith{i}} \ac{AO} update.}
+\reviewF{Since the objective is decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in each \ac{AO} step \eqn{i}.
+Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be a stacked vector of the solution obtained upon objective convergence in the \eqn{\ith{i}} \ac{AO} update.}
 
@@
 \subsection{Stationarity of Limit Points} \label{c-b}
-\reviewF{We now discuss the convergence properties of the sequence of iterates generated by the proposed algorithm.
-For convenience, let us consider a unified superscript index \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})).
-Using this, we denote iterate \eqn{\ma^t} as a stacked vector of the minimizer obtained by solving \eqref{con-m} at each step \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k} for some \ac{SCA} and \ac{AO} iteration.
-%Furthermore, we introduce variable \eqn{\ma^{t}} to denote a vector formed by stacking solution obtained at \eqn{\ith{t}} iteration, \textit{i.e.}, \eqn{\mat{t} = \mbf{z}^{(i)}_k}, the respective iterate.
+\reviewF{We now discuss the convergence properties of the sequence of iterates.
+For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step \eqn{(k,i)}).
+Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer obtained by solving \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence of minimizers obtained at each iteration.
 
-The objective sequence \eqn{\{f(\ma^t)\}} generated by the algorithm is bounded and monotonically decreasing (see Appendices \ref{b_obj} and \ref{mcity}).
+Note that the objective sequence \eqn{\{f(\ma^t)\}} is bounded and nonincreasing (see Appendices \ref{b_obj} and \ref{mcity}).
 Therefore, by using \cite[Prop.
-A.3]{bertsekas1999nonlinear}, the convergence of the sequence \eqn{\{f(\ma^t)\}} can be ensured.
+A.3]{bertsekas1999nonlinear}, we can ensure the convergence of \eqn{\{f(\ma^t)\}}.
 Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}.
-However, since the feasible set is compact, the sequence \eqn{\{\ma^t\}} is bounded.
-Therefore, the sequence \eqn{\{\ma^t\}} has at least one limit point, say \eqn{\bar{\mbf{x}}}, such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\mbf{x}}} \cite[Prop.
+However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded, and therefore the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it, by following \cite[Prop.
 A.5]{bertsekas1999nonlinear}.
@@
 \end{equation}
-Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.
+Thus, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.
 
@@
 To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively.
-Since \eqn{\|\mat{} - \mat{t}\|^2} is the proximal term in \eqref{mod_obj} for iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
+Since \eqn{\|\mat{} - \mat{t}\|^2} is the proximal term in \eqref{mod_obj} at iteration \eqn{t}, the relation between \eqn{\mat{t}} and \eqn{\mat{t+1}} satisfies
 \begin{equation} \label{mcity_origfunc}
@@
 where \eqn{\tau^t} denotes \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}.
-Thus, by extending \eqref{mcity_origfunc} to every update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop.
+Thus, by extending \eqref{mcity_origfunc} for each update and by using Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be shown using \cite[Prop.
 A.3]{bertsekas1999nonlinear}.
 
-Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between gradients of subproblems \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}.
-In order to ensure \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
+Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between the gradients of \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}.
+In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
 \begin{equation} \label{kkt_expr}

### 2015-11-25 Report/dual_approach.tex
finalized so far

@@
 
-\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, convergence analysis follows the discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
-Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since strict monotonic decrease of the objective sequence can still be ensured.
+\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
+Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured.
 The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.

### 2015-11-25 Report/mse_formulation.tex
finalized so far

@@
 In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
-\reviewF{However, to provide a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
+\reviewF{However, to provide a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
 The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration.

### 2015-11-25 Report/decomposition_solutions.tex
dual change

@@
 \begin{IEEEeqnarray}{rCl} \neqsub
-\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{1,\mc{U}_b(1),1,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{L,\mc{U}_b(|\mc{U}_b|),N,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran \eqsub \\
-\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{1,\bar{\mc{U}}_b(1),1,b}, \dotsc, {\zeta}_{L,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),N,b} \right]^\tran. \eqsub
+\bar{\mbfa{\zeta}}_{b} &=&  \left[ {\zeta}_{1,\mc{U}_b(1),1,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{L,\mc{U}_b(|\mc{U}_b|),N,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right ]^\tran \eqsub \\
+\hat{\mbfa{\zeta}}_{b} &=&  \left [ {\zeta}_{1,\bar{\mc{U}}_b(1),1,b}, \dotsc, {\zeta}_{L,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),N,b} \right ]^\tran. \eqsub
 \end{IEEEeqnarray}
@@
 \begin{equation}
-\mbfa{\zeta}_{b} = \left [\hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran. \label{if_vector}
+\mbfa{\zeta}_{b} = \left [ \hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran. \label{if_vector}
 \end{equation}
@@
 Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to \ac{BS} \me{b_k} in \ac{BS} \me{b} as
-\begin{equation}
-\mbfa{\zeta}_{b}(b_k) = \left [ {\zeta}_{1,\mc{U}_b(1),1,b_k},\dotsc, {\zeta}_{L,\mc{U}_b(|\mc{U}_b|),N,b_k} \right].
-\end{equation}
+\begin{multline}
+\mbfa{\zeta}_{b}(b_k) = [ {\zeta}_{1,\mc{U}_b(1),1,b_k},\dotsc, {\zeta}_{L,\mc{U}_b(|\mc{U}_b|),N,b_k} \\
+{\zeta}_{1,\mc{U}_{b_k}(1),1,b},\dotsc, {\zeta}_{L,\mc{U}_{b_k}(|\mc{U}_{b_k}|),N,b_k} ].
+\end{multline}
 
-To decentralize the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in accordance to the decomposition method.
+To decentralize \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in accordance to the decomposition method.
 To decouple the precoder design across \acp{BS}, the equivalent downlink channels \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are to be known at each \ac{BS} \me{b} through the precoded uplink pilots from all the users in the system, where the linear precoders are evaluated at the user using \ac{MMSE} formulation in \eqref{eqn-mse-2}.
 Similarly, to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} need to be known.
-It is obtained through the user specific downlink pilots precoded with the newly obtained transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} using the equivalent downlink channels as discussed in \cite{komulainen2013effective}.
+It is obtained through the user specific downlink pilots precoded with the newly obtained transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} using equivalent downlink channels \cite{komulainen2013effective}.
 

### 2015-11-25 Response/Response 3/response-3.tex
updated and corrected verify tomorrow !!

@@
 	\item We refer to [R2] for a similar usage of reference [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem.
-The reference [R1] used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables.
+The reference [R1] is used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables.
 It has been discussed comprehensively in [R2, Appendices I and II].
@@
 \begin{itemize}		
-		\item[R1.] R.R.
-Meyer, ``Sufficient Conditions for the Convergence of Monotonic Mathematical Programming Algorithms," \emph{Journal of Computer and System Sciences}, vol.
-12, no.
-1, pp.
-108-121, 1976
+	\item[R1.] R.R. Meyer, ``Sufficient Conditions for the Convergence of Monotonic Mathematical Programming Algorithms," \emph{Journal of Computer and System Sciences}, vol. 12, no. 1, pp. 108-121, 1976
 	\item[R2.] J.

### 2015-11-25 Response/Response 3/reviewer_response.tex
updated and corrected verify tomorrow !!

@@
 \usepackage[dvipdfmx]{graphicx}
-\usepackage{acronym,etoolbox,color,multicol,xcolor}
-\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools,pgfplots,subfig}
+\usepackage{acronym,etoolbox,color,multicol,xcolor,subfig}
 
@@
 The authors are grateful to the associate editor for giving us an additional opportunity to revise and correct our convergence analysis.
-In this regard, we would like to give a special thank to Review 3 who pointed out the issues with our convergence analysis of the proposed solutions.
+In this regard, we would like to give a special thank to Reviewer 3 who pointed out the issues with our convergence analysis of the proposed solutions.
 In this revision, we have mainly focused on providing a more mathematically rigorous  proof of the convergence analysis of the proposed iterative algorithms.
@@
 In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})).
-Then, by using index \eqn{t}, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer obtained by solving (48) at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence of minimizers obtained at each iteration.
+Then, by using index \eqn{t}, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer obtained by solving problem (48) at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence formed by collecting the minimizers of problem (48) from each iteration.
 With these notations, we have revised our convergence discussions in Appendices A-C and A-D.

### 2015-11-25 Report/convergence_centralized.tex
updated and corrected verify tomorrow !!

@@
 Note that the uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence.
-Upon satisfying (a)-(d), we can show the convergence of the objective sequence generated by the centralized method in Algorithm \ref{algo-1} by using \cite[Th.
+Upon satisfying conditions (a)-(d), we can show that the objective sequence generated by the centralized approach in Algorithm \ref{algo-1} converges, by using \cite[Th.
 3.14]{rudin1964principles}.
@@
 Since it involves two nested loops, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}.
-Let \me{\mx}, \me{\my}, and \me{\mz} be the vector stacking all transmit precoders, receive beamformers, and other optimization variables used in \eqref{eqn-6} and \eqref{eqn-mse-1} respectively.
-Let us consider \ac{AO} step \eqn{i} with fixed \eqn{\my}.
+Let \me{\mx}, \me{\my}, and \me{\mz} be the vector stacking all transmit precoders, receive beamformers, and other optimization variables used in \eqref{eqn-6} and \eqref{eqn-mse-1}, respectively.
+Now, let us consider \ac{AO} step \eqn{i} with fixed \eqn{\my}.
 The solution obtained in the \eqn{\ith{k}} \ac{SCA} step is given by \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}.
@@
 Similarly, while alternating the optimization variables for fixed \eqn{\mx}, as \eqn{k \to \infty}, the solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}.
-In the following, we show that the conditions listed in (a)-(d) are satisfied by Algorithm \ref{algo-1}.
+In the following, we will show that the conditions in (a)-(d) are satisfied by Algorithm \ref{algo-1}.
 
@@
 \subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
-The feasible set of \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on transmit precoders, given by \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.%\footnote{The feasible set in each iteration is bounded due to the proximal operator in \eqref{mod_obj} as \eqn{\{\mbf{z} | f(\mbf{z}) \leq f(\mbf{z}_k^{(i)})\}}, therefore, the sequence \eqn{\{\mbf{z}_k^{(i)}\}} is bounded.}
+The feasible set of \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total transmit power constraint given by \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, respectively.
+Therefore, the feasible region is compact.%\footnote{The feasible set in each iteration is bounded due to the proximal operator in \eqref{mod_obj} as \eqn{\{\mbf{z} | f(\mbf{z}) \leq f(\mbf{z}_k^{(i)})\}}, therefore, the sequence \eqn{\{\mbf{z}_k^{(i)}\}} is bounded.}
 
@@
 Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}.
-Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} update \cite{scutari2010convex}.
-\reviewF{Since the objective is decreasing and bounded, convergence of \eqn{\{f(\mbf{z}_k^{(i)})\}} is guaranteed in each \ac{AO} step \eqn{i}.
-Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} be a stacked vector of the solution obtained upon objective convergence in the \eqn{\ith{i}} \ac{AO} update.}
+Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} step \cite{scutari2010convex}.
+\reviewF{Additionally, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is bounded, we can ensure that \eqn{\{f(\mbf{z}_k^{(i)})\}} converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}.
+Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} denote a stacked vector of the minimizer obtained upon the objective convergence in \ac{AO} iteration \eqn{{i}}.}
 
@@
 \subsection{Stationarity of Limit Points} \label{c-b}
-\reviewF{We now discuss the convergence properties of the sequence of iterates.
-For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step \eqn{(k,i)}).
-Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer obtained by solving \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence of minimizers obtained at each iteration.
+\reviewF{We now discuss the convergence properties of sequence of iterates.
+For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} step \eqn{k} and \ac{AO} step \eqn{i}).
+Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking minimizer obtained by solving \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and \eqn{\{\mat{t}\}} be the sequence formed by collecting minimizers from each iteration.
 
@@
 \end{equation}
-Thus, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.
+Thus, \eqn{\bar{\ma}} is a stationary point, and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.
 
@@
 Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between the gradients of \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}.
-In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
+In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con} as
 \begin{equation} \label{kkt_expr}
@@
 \end{equation}
-Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
-Finally, by using \cite[Thms.
+Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
+Finally, by using above discussions for every limit point, and by using \cite[Thm.
+2]{scutari_1} and \cite[Prop.
+3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} is a stationary point of \eqref{con}.}
+%using \cite[Thms.
 2 and 11]{scutari_1} and \cite[Prop.

### 2015-11-25 Report/dual_approach.tex
updated and corrected verify tomorrow !!

@@
 However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only.
-In such a case, convergence of the distributed algorithms cannot not be ensured, since it is impossible to show that the objective value is monotonically decreasing at every \ac{SCA} step.
-We recall that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}
+In such a case, convergence of the distributed algorithms cannot not be ensured, since it is impossible to show that the objective value is monotonically decreasing in each \ac{SCA} update step.
+We recall that in each primal or \ac{ADMM} iteration, the global objective cannot be guaranteed to decrease monotonically.}
 

### 2015-11-25 Report/mse_formulation.tex
updated and corrected verify tomorrow !!

--- 2015-11-24 Report/mse_formulation.tex
@@
 In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
-\reviewF{However, to provide a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
+\reviewF{However, to provide a formal convergence analysis, we consider using a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
 The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration.

### 2015-11-27 Response/Response 3/response-3.tex
submitted

--- 2015-11-25 Response/Response 3/response-3.tex
@@
 We apologize for our emphasis on the convergence of iterates in our previous manuscript.
-As suggested by the reviewer, stationarity of limit points of the whole sequence of iterates is now addressed in Appendix A-D by using the following statements.
+As suggested by the reviewer, stationarity of limit points of the whole sequence of iterates is now addressed in Appendix A-D by using the following statements:
 \begin{itemize}
@@
 \underline{\textbf{Response:}} We understand the reviewer's concern on using reference [R1] to our problem involving both \ac{SCA} and \ac{AO} updates.
-In each iteration, the proposed method solves only a subset of optimization variables by keeping others fixed, therefore, we cannot use reference [R1] directly as suggested by the reviewer.
-Even though we have revised our convergence proof based on a convergent subsequence without referring to [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates.
+In each iteration, the proposed method solves only a subset of optimization variables by keeping the others fixed.
+Therefore, we cannot use reference [R1] directly as suggested by the reviewer, and we have now completely revised the argumentation as detailed above.
+Even though we have revised our convergence proof based on a convergent subsequence without referring to [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates:
 
@@
 	\item We refer to [R2] for a similar usage of reference [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem.
-The reference [R1] used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables.
+Reference [R1] is used to discuss the convergence of iterates generated by the \ac{AO} method in [R2] by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables.
 It has been discussed comprehensively in [R2, Appendices I and II].
@@
 
-	We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss the convergence of the sequence of iterates.
+We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to address the convergence of the sequence of iterates.
 We have revised our statement as every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.

### 2015-11-27 Response/Response 3/reviewer_response.tex
submitted

@@
 In particular, to discuss the convergence of the sequence of iterates generated by the centralized method, we use a unified superscript index \eqn{t} to refer to the step index of both \ac{AO} and \ac{SCA} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} and \ac{AO} update step (\eqn{k,i})).
-Then, by using index \eqn{t}, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer obtained by solving problem (48) at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence formed by collecting the minimizers of problem (48) from each iteration.
+Then, by using index \eqn{t}, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer of problem (48) at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence formed by collecting the minimizers of problem (48) from each iteration.
 With these notations, we have revised our convergence discussions in Appendices A-C and A-D.

### 2015-11-27 Report/convergence_centralized.tex
submitted

@@
 \end{itemize}
-Note that the uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence.
-Upon satisfying conditions (a)-(d), we can show that the objective sequence generated by the centralized approach in Algorithm \ref{algo-1} converges, by using \cite[Th.
+The uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence.
+Therefore, upon satisfying the conditions (a)-(d), we can show that the objective sequence generated by Algorithm \ref{algo-1} converges, by using \cite[Th.
 3.14]{rudin1964principles}.
-Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can claim that \reviewF{every limit point of the sequence of iterates generated by the iterative method is a stationary point of original nonconvex formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that \reviewF{every limit point of sequence of iterates is a stationary point of nonconvex problems in \eqref{eqn-6} and \eqref{eqn-mse-1}}.
 
@@
 Similarly, while alternating the optimization variables for fixed \eqn{\mx}, as \eqn{k \to \infty}, the solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}.
-In the following, we will show that the conditions in (a)-(d) are satisfied by Algorithm \ref{algo-1}.
+In the following discussion we will show that the conditions listed in (a)-(d) are satisfied by Algorithm \ref{algo-1} using the above notations.
 
@@
 \end{IEEEeqnarray}
-where vector \eqn{\mbf{z}} is formed by stacking all optimization variables that can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the fixed variables.
-Moreover, \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} be a stacked vector of solution obtained at the \eqn{\ith{(k-1)}} \ac{SCA} step in \ac{AO} iteration \eqn{i}.
+where \eqn{\mbf{z}} is a vector formed by stacking all the optimization variables, \textit{i.e.}, \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the variables being optimized, and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is a vector formed by stacking the solution obtained from \ac{SCA} step \eqn{k-1} and \ac{AO} iteration \eqn{i}, respectively.
 The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f(\mbf{z})} in each step \cite[Sec.
 3.4.3]{bertsekas1989parallel}.
-Thus, due to strong convexity in \eqn{f(\mbf{z})}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.
+Thus, due to strong convexity in \eqn{f(\mbf{z})}, uniqueness of the minimizer is ensured in each iteration \cite{yang_yang,scutari-1}.
 
@@
 
-Since the norm function present in the objective satisfies \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all \eqn{q} used in \eqn{\ell_q} norm, it is bounded from below.
+Note that the norm function present in the objective satisfies \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all exponents \eqn{q} used in \eqn{\ell_q} norm, therefore, it is bounded from below.
 Moreover, due to the compactness of the feasible set, it is bounded from above as well.
-In addition, the objective function satisfies Lipschitz continuity, since the feasible set is compact.
 
@@
 Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} step \cite{scutari2010convex}.
-\reviewF{Additionally, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is bounded, we can ensure that \eqn{\{f(\mbf{z}_k^{(i)})\}} converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}.
-Let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} denote a stacked vector of the minimizer obtained upon the objective convergence in \ac{AO} iteration \eqn{{i}}.}
+\reviewF{Furthermore, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is also bounded, we can show that the objective sequence converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}, and let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}]} be a stacked vector of the corresponding minimizer of \eqref{con-m} when \eqn{k \to \infty} in \ac{AO} step \eqn{i}.}
 
@@
 For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} step \eqn{k} and \ac{AO} step \eqn{i}).
-Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking minimizer obtained by solving \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and \eqn{\{\mat{t}\}} be the sequence formed by collecting minimizers from each iteration.
+Then, we denote iterate \eqn{\ma^t} as a vector formed by stacking the minimizer of \eqref{con-m} at iteration \eqn{t} as \eqn{\mat{t} = \mbf{z}^{(i)}_k}, and let \eqn{\{\mat{t}\}} be the sequence formed by collecting the minimizers of \eqref{con-m} from each iteration.
 
@@
 Unfortunately, such a claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}.
-However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded, and therefore the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it, by following \cite[Prop.
+However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded.
+Therefore, the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it, by following \cite[Prop.
 A.5]{bertsekas1999nonlinear}.
@@
 Let us prove the stationarity of \eqn{\bar{\ma}} by contradiction.
-Assume that \eqn{\bar{\ma}} is not a stationary point, then there exist some other point \eqn{\ma^\prime \in \{\ma^t\}}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}.
-Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point.
+Assume that \eqn{\bar{\ma}} is not a stationary point.
+Then there exists some other point \eqn{\ma^\prime \in \{\ma^t\}}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}.
+Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exists a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point.
 However, by using \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of \eqn{\{\ma^t\}}, which is a contradiction to our initial assumption.
 
-Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}.
+Now, by using the strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}.
 Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}.
@@
 
-Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between the gradients of \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}.
+Now to prove that \eqn{\bar{\ma}} is also a stationary point of the original problem \eqref{con}, we show the equivalence between the gradients of \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}.
 In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con} as
@@
 Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)} \subset \mc{F}} and \eqn{\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}.
-Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}.
-Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
+Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty.
+Thus, the Slater's constraint qualification holds for \eqref{con-m}.
+Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} which satisfy
 \begin{equation} \label{kkt_mod_expr}
@@
 
-The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by using following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}.
+The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}.
 Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}.
@@
 Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}.
-Finally, by using above discussions for every limit point, and by using \cite[Thm.
+Finally, by following \cite[Thm.
 2]{scutari_1} and \cite[Prop.
-3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} is a stationary point of \eqref{con}.}
+3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}
 %using \cite[Thms.

### 2015-11-27 Report/convergence_distributed.tex
submitted

@@
 To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}.
-At first, the convergence of the primal decomposition method is discussed by using following properties.
-(i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications.
-(ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique.
+At first, the convergence of the primal decomposition method is discussed by using the following properties.
+(i) The feasible set is non-empty and bounded.
+Therefore, each subproblem satisfies the Slater's constraint qualifications.
+(ii) Due to the strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique.
 Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop.
-8.2.6]{bertsekas2003convex} by using diminishing step size in each subgradient update.}
+8.2.6]{bertsekas2003convex} by using a diminishing step size in each subgradient update.}
 

### 2015-11-27 Report/dual_approach.tex
submitted

@@
 
-\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are performed for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
-Moreover, the convergence discussions in Appendices \ref{sec-3.5} and \ref{sec-dist-conv} are still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured.
+\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are carried out until convergence or for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
+Moreover, it is still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured.
 The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update.
-However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for limited number of iterations, say, for \eqn{J_{\max}} only.
-In such a case, convergence of the distributed algorithms cannot not be ensured, since it is impossible to show that the objective value is monotonically decreasing in each \ac{SCA} update step.
+However, in practice, to reduce the amount of information exchange between the coupling \acp{BS}, the distributed schemes are often iterated for a limited number of iterations, say, for \eqn{J_{\max}} only.
+In such a case, convergence of the distributed algorithms cannot be ensured, since it is impossible to show that the objective value is monotonically decreasing in each \ac{SCA} update step.
 We recall that in each primal or \ac{ADMM} iteration, the global objective cannot be guaranteed to decrease monotonically.}

### 2015-11-27 Report/mse_formulation.tex
submitted

@@
 
-In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges.
+In all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges.
 \reviewF{However, to provide a formal convergence analysis, we consider using a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
@@
 Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} is bounded.
-However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
+However, for problem \eqref{eqn-6}, the feasible set need not be bounded due to newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax the \ac{SINR} expression in \eqref{eq:SINR}.
+This follows from the fact that  \eqn{\beta_{l,k,n}} can take any value by satisfying \eqref{eqn-6.3} without violating the constraints of problem \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}.
 Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem.
-By using the above assumptions, convergence analysis for the centralized problem is discussed in Appendix \ref{sec-3.5}.}
+With the above assumptions, convergence analysis of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
 

### 2016-01-12 Presentation/antti_eurocomm.tex
antti_presentation
update

--- 2015-09-02 Presentation/markku_reduced.tex
@@
 \usepackage{amsmath,amssymb}
-\usepackage{graphicx,acronym,setspace,epstopdf}
+\usepackage{graphicx,acronym,setspace,epstopdf,IEEEtrantools}
 \usepackage[ruled]{algorithm2e}
 \usepackage{subeqnarray,multirow,cite,array,color,mathtools,setspace,geometry}
+
+\let\oldfootnote\footnote
+\renewcommand\footnote[1][]{\oldfootnote[frame,#1]}
 
@@
 \acrodef{BCDM}{block coordinate descent method}
+\acrodef{BiT}{Bi-directional training}
 
@@
 
-\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}}
+\graphicspath{{./}{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}{./../../flaming-octo-dangerzone/TeX3/Figures/}}
 \DeclareGraphicsExtensions{.eps}
@@
 \title{Traffic Aware Precoder Design for Space Frequency Resource Allocation}
+
 \author{{Ganesh Venkatraman\eqn{^\dagger}, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}
@@
 
+\begin{frame}{System Model with User Queues}
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.9\columnwidth]{system-scenario.pdf}
+	\end{figure}
+\end{frame}
+
 \begin{frame}{Queueing Model}
@@
 \begin{itemize}
-\item \acs{Q-WSRM} formulation is the result of \textcolor{blue}{minimizing the conditional Lyapunov drift}\eqn{^\dagger}
+\item \acs{Q-WSRM} formulation is the result of \textcolor{blue}{minimizing the conditional Lyapunov drift}\footnote{Neely, Michael J.
+"Stochastic network optimization with application to communication and queueing systems." Synthesis Lectures on Communication Networks 3.1 (2010): 1-211.}
 \item \acs{Q-WSRM} formulation is also called as \alert{back pressure algorithm}, since it acts greedily in minimizing the backlogged packets at each instant
@@
 \end{itemize}
-
-\vspace{2eM}
-\eqn{^\dagger}\footnotesize{Neely, Michael J. "Stochastic network optimization with application to communication and queueing systems." Synthesis Lectures on Communication Networks 3.1 (2010): 1-211.}
 \end{frame}
@@
 
+\subsection{Simulation Results}
+
+\begin{frame}{Centralized Solutions}
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.75\textwidth]{fig-2-5}
+		\caption{System Model - \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Time Correlated Fading - Centralized Performance}
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.75\textwidth]{average_queue_over_time-3}
+		\caption{System Model - \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} after \eqn{250} transmissions}
+	\end{figure}
+\end{frame}
+
 \section{Distributed Solutions}
@@
 
-\section{Simulation Results}
+\subsection{Simulation Results}
 
-\subsection{Centralized Solutions}
-
-\begin{frame}{Centralized Solutions}
-\begin{figure}
-	\centering
-	\includegraphics[width=0.75\textwidth]{fig-2-5}
-	\caption{System Model - \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}}
-\end{figure}
-\end{frame}
-
-\subsection{Distributed Solutions}
-
-\begin{frame}{Distributed Solutions}
+\begin{frame}{Performance of Distributed Solutions}
 	\begin{figure}
@@
 \end{frame}
-
-\subsection{KKT based Approach}
 
@@
 
-\subsection{Time Correlated Fading Performance}
+\section{Time Correlated Fading Performance}
 
-\begin{frame}{Time Correlated Fading Performance}
+\subsection{Methods to Update Precoders via \acs{OTA}}
+
+\begin{frame}{Time Correlated Precoder Design - Introduction}
+	\begin{itemize}
+		\item So far, we have discussed few methods to design precoders in a distributed manner
+		\item Now, we discuss a \textcolor{red}{practical approach to design precoders with minimal backhaul usage}
+		\item To discuss further, we consider \ac{KKT} based design for following reasons
+		\begin{itemize}
+			\item Due to closed form solution, \textcolor[rgb]{0,0.6,0}{each \ac{SCA} update requires only single exchange of coupling variables}
+			\item Moreover, transmit and receive precoders expressions can be formed by using precoded pilot transmissions
+		\end{itemize}
+		\item We \textcolor[rgb]{0,0,0.6}{adopt \ac{BiT}} to update transmit and receive beamformers \footnote{P.
+Komulainen, A.
+T\"olli \& M.
+Juntti, “Effective CSI Signaling and Decentralized Beam Coordination in TDD Multi-Cell MIMO Systems”, IEEE Transactions on Signal Processing, vol.
+61, no.
+9, pp.
+2204 -- 2218, May 2013}
+	\end{itemize}	
+\end{frame}
+
+\begin{frame}{Time Correlated Precoder Design - Strategy A}
+	\begin{itemize}
+		\item To devise \ac{OTA} based iterative algorithm - let us consider transmit and receive beamformer expressions
+		\begin{IEEEeqnarray*}{ll}
+		\mvec{m}{l,k,n}^{(i)} &= \Big (\displaystyle \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i-1)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(i-1)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)}  \\
+		\mvec{w}{l,k,n}^{(i)} &= \Big (\displaystyle \sum_{x\in\mc{U}}\sum_{y=1}^L \mvec{H}{b_x,k,n} \mvec{m}{y,x,n}^{(i)} \mvec{m}{y,x,n}^{\herm \, (i)} \mvec{H}{b_{x},k,n}^\herm + N_0 \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i)}
+		\end{IEEEeqnarray*}
+		\item Note that transmit precoders \eqn{\mvec{m}{l,k,n}} depend on \eqn{\mvec{H}{b_k,i,n}^\tran \mvec{u}{l,i,n}}, \textit{i.e.}, \textcolor{blue}{effective uplink channel}
+		\item Similarly, receive beamformers \eqn{\mvec{w}{l,k,n}} depend on \eqn{\mvec{H}{b_k,i,n} \mvec{m}{l,k,n}}, \textit{i.e.}, \textcolor[rgb]{0,0.6,0}{effective downlink channel}
+	\end{itemize}	
+\end{frame}
+
+\begin{frame}{Time Correlated Precoder Design - Strategy A}
+	\begin{itemize}
+		\item To update receive beamformers at the user terminals, \textcolor{blue}{each \ac{BS} transmits precoded downlink pilots orthogonally} by using \eqn{\mvec{m}{l,k,n}^{(i)}}
+		\item Upon receiving effective channel, each user update the respective receive beamformer
+		\item Similarly, to update transmit beamformers at \acp{BS}, \textcolor[rgb]{0,0.6,0}{each user transmits two precoded pilot transmission}, namely, \eqn{\sqrt{\alpha_{l,k,n}^{(i-1)}} \mvec{w}{l,k,n}^\ast} and \eqn{\alpha_{l,k,n} \mvec{w}{l,k,n}^{\ast}}
+		\item Upon receiving two uplink precoded pilots, each \ac{BS} then evaluates the respective transmit beamformers of all users
+		\item The above iterative procedure is performed until convergence or for predetermined number of updates - \alert{Strategy A}
+	\end{itemize}	
+\end{frame}
+
+\begin{frame}{Bi-directional Frame Structure}
+	\begin{itemize}
+		\item To perform iterative \ac{OTA} based update, we \textcolor[rgb]{0.7,0,0}{consider \ac{TDD} frame format}
+		\item Using \ac{OTA} transmissions, \textcolor[rgb]{0,0.6,0}{effective channel can be conveyed to \acp{BS} and users by precoded pilots}
+	\end{itemize}
 	\begin{figure}
 		\centering
-		\includegraphics[width=0.75\textwidth]{average_queue_over_time-3}
-		\caption{System Model - \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} after \eqn{250} transmissions}
+		\includegraphics[trim=4mm 40mm 10mm 10mm,clip, width=\columnwidth ]{bit_model.pdf}
+		\label{fig-a}
 	\end{figure}
 \end{frame}
+
+\begin{frame}{Time Correlated Precoder Design - Strategy B}
+	\begin{itemize}
+		\item To \alert{speed up the convergence} of iterative algorithm, we update the precoders of desired users \textcolor[rgb]{0,0.6,0}{locally by fixing neighboring \acp{BS} transmit beamformers}
+		\item To do so, in addition to the signaling requirements in strategy A, \textcolor[rgb]{0,0,0.6}{inter-cell interference covariance seen by desired users} is also fed back to serving \ac{BS}, \textit{i.e.},
+		\begin{equation}
+		\mvec{Z}{l,k,n} = \sum_{i \in \mc{U} \backslash \mc{U}_b} \mvec{H}{b_i,i,n} \mvec{m}{l,i,n} \mvec{m}{l,i,n}^\herm \mvec{H}{b_i,i,n}^\herm + N_0 \mbf{I}_{N_R}.
+		\end{equation}
+		\item Since inter-cell interference covariance is not required explicitly, \textcolor[rgb]{0.6,0,0}{effective whitened channel is enough to evaluate precoders}
+		\item The whitening filter \eqn{\mvec{Q}{l,k,n}} is given by \eqn{\mvec{Z}{l,k,n}^{-1} = \mvec{Q}{l,k,n}^\herm \mvec{Q}{l,k,n}}
+		\item Whitened channel is constructed at \ac{BS} by \textcolor[rgb]{0,0.6,0}{transmitting columns of \eqn{\mvec{Q}{l,k,n}} orthogonally from each user}
+	\end{itemize}	
+\end{frame}
+
+\begin{frame}{Time Correlated Precoder Design - Strategy B}
+	\begin{itemize}
+		\item Upon receiving \eqn{\mvec{Q}{l,k,n}}, \textcolor[rgb]{0,0.6,0}{each \ac{BS} can construct whitened channel} as \eqn{\mvec{\bar{H}}{b_k,k} = \mvec{Q}{l,k,n} \mvec{H}{b_k,k}}
+		\item The \ac{BS} specific local iteration \eqn{j} to update transmit and receive beamformer is given as
+	\end{itemize}	
+\begin{IEEEeqnarray*}{ll} \label{kkt-mse-x} \neqsub
+	\mvec{m}{l,k,n}^{(j)} =& \Big ( \sum_{x \in \mc{U}_b} \sum_{y=1}^L \alpha_{y,x,n}^{(j-1)} \mvec{\bar{H}}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(j-1)} \mvec{w}{y,x,n}^{\herm \, {(j-1)}} \mvec{\bar{H}}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \Big )^{-1} \alpha^{(j-1)}_{l,k,n} \mvec{\bar{H}}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(j-1)} \\
+	\mvec{w}{l,k,n}^{(j)} =& \Big ( \sum_{x\in\mc{U}_b}\sum_{y=1}^L \mvec{\bar{H}}{b_x,k,n} \mvec{m}{y,x,n}^{(j)} \mvec{m}{y,x,n}^{\herm \, (j)} \mvec{\bar{H}}{b_{x},k,n}^\herm + \mathbf{I}_{N_R} \Big ) ^{-1} \; \mvec{\bar{H}}{b_k,k,n} \; \mvec{m}{l,k,n}^{(j)}
+\end{IEEEeqnarray*}
+\begin{itemize}
+	\item The above iterative procedure is performed until convergence or for predetermined number of updates - \alert{Strategy B}
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Summary - Signaling Requirement for OTA based Updates}
+\begin{figure}
+	\centering
+	\includegraphics[trim=0mm 10mm 0mm 10mm, width=\columnwidth ]{Doc2.pdf}
+	\caption{\ac{TDD} frame structure with \ac{BiT} signaling}
+	\label{fig-a}
+\end{figure}
+\end{frame}
+
+\subsection{Simulation Results}
+
+\begin{frame}{Assumptions and Evaluation Model}
+	\begin{itemize}
+		\item Every \ac{BS} and user terminal uses \textcolor[rgb]{0,0.6,0}{orthogonal pilots in UL and DL \ac{OTA} signaling}
+		\item For simplicity, pilot transmissions used to convey the equivalent channel information in one \ac{BiT} iteration - \textcolor[rgb]{0,0,0.6}{consume \eqn{\eta} resource share}.\footnote{In practice, the performance depends on the amount of available pilots and the size of coherence block.}
+		\item Under this assumption, the effective rate by considering the signaling overhead is given as
+		\begin{equation} \label{penalty}
+		\tilde{t}_{l,k,n} = \left ( 1 - I_{\max} \, \eta \right ) \times t_{l,k,n}
+		\end{equation}
+		\item Total number of backlogged packets is evaluated as - \eqn{\textstyle \chi = \sum_{k = 1}^K \; [ Q_k - \tilde{t}_k ]^+}
+		\item In all simulations, \textcolor[rgb]{0.6,0,0}{we consider \eqn{\eta = 1 \%}}
+	\end{itemize}	
+\end{frame}
+
+\begin{frame}{Average Backlogged Packets - Distributed Design}
+	\begin{figure}
+		\centering
+		\includegraphics[trim=5mm 90mm 5mm 90mm,clip, width=\columnwidth]{ICC-A-B-1}
+		\caption{Average backlogged packets for \eqn{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,12,4,2 \rbrace} evaluated over \eqn{250} slots with \eqn{f_dT_s\approx 0.1}}
+		\label{fig-1}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Average Backlogged Packets - Distributed Design}
+	\begin{figure}
+		\centering
+		\includegraphics[trim=5mm 90mm 5mm 90mm,clip, width=\columnwidth]{ICC-A-B1}
+		\caption{Average backlogged packets for \eqn{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,12,4,2 \rbrace} evaluated over \eqn{250} slots with \eqn{f_dT_s\approx 0.01}}
+		\label{fig-2}
+	\end{figure}
+\end{frame}
+
+%\begin{frame}{Time Correlated Fading Performance}
+%	\begin{figure}
+%		\centering
+%		\includegraphics[width=0.75\textwidth]{Doc2}
+%		\caption{System Model - \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} after \eqn{250} transmissions}
+%	\end{figure}
+%\end{frame}
+%
+%\begin{frame}{Time Correlated Fading Performance}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\columnwidth]{ICC-A-B-1}
+%	\caption{Average backlogged packets for \eqn{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,12,4,2 \rbrace} evaluated over \eqn{250} slots with \eqn{f_dT_s\approx 0.1}}
+%	\label{fig-1}
+%\end{figure}
+%\end{frame}
 
@@
 \item We also proposed a practical way of implementing the precoder design in a distributed manner by solving the \ac{KKT} expressions
-\item Extensions of the proposed work in time-correlated fading scenario with limited number of information exchange cycle is in progress
+\item Extensions of the proposed work in time-correlated fading scenario with limited number of information exchange cycle is also presented
 \end{itemize}

### 2016-02-01 Eurocomm/antti_eurocomm.tex
updated

--- 2016-01-12 Presentation/antti_eurocomm.tex
@@
 
-\acrodef{MSE}{mean squared error}
-\acrodef{BC}{broadcast channel}
-\acrodef{MC}{multi-cell}
-\acrodef{BS}{base station}
-\acrodef{MIMO}{multiple-input multiple-output}
-\acrodef{SISO}{single-input single-output}
-\acrodef{MU}{multi-user}
-\acrodef{MU-MIMO}{\acl{MU} \acl{MIMO}}
-\acrodef{OFDM}{orthogonal frequency division multiplexing}
-\acrodef{WSRM}{weighted sum rate maximization}
-\acrodef{QoS}{quality of service}
-\acrodef{SCA}{successive convex approximation}
-\acrodef{SNR}{signal-to-noise ratio}
-\acrodef{MMSE}{minimum \acl{MSE}}
-\acrodef{SIR}{signal-to-interference ratio}
-\acrodef{SINR}{signal-to-interference-plus-noise ratio}
-\acrodef{Q-WSRM}{queue \acl{WSRM}}
-\acrodef{QM}{queue minimizing}
-\acrodef{SRA}{spatial resource allocation}
-\acrodef{JSFRA}{joint space-frequency resource allocation}
-\acrodef{WMMSE}{weighted \acl{MMSE}}
-\acrodef{KKT}{Karush-Kuhn-Tucker}
-\acrodef{GP}{geometric programming}
-\acrodef{SOC}{second-order cone}
-\acrodef{BCDM}{block coordinate descent method}
-\acrodef{BiT}{Bi-directional training}
+\input{acronyms}
+\input{shortcuts}
 
-\input{./../Report/shortcuts}
-\input{./../Report/acronyms}
+\graphicspath{{./Figures/}}
+\DeclareGraphicsExtensions{{.pdf}}
 
-\graphicspath{{./}{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}{./../../flaming-octo-dangerzone/TeX3/Figures/}}
-\DeclareGraphicsExtensions{.eps}
-
-\epstopdfsetup{update,prepend,prefersuffix=false,suffix=}
-\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
-\pdfcompresslevel=9
+%\epstopdfsetup{update,prepend,prefersuffix=false,suffix=}
+%\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
+%\pdfcompresslevel=9
 
@@
 
-\author{{Ganesh Venkatraman\eqn{^\dagger}, Antti T\"{o}lli, Le-Nam Tran and Markku Juntti} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}
+\author{{Ganesh Venkatraman, Antti T\"{o}lli\eqn{^\dagger}, Le-Nam Tran and Markku Juntti} \\ \scriptsize{Email: \{gvenkatr, antti.tolli, le.nam.tran, markku.juntti\}@ee.oulu.fi}}
 
@@
 		\centering
-		\includegraphics[width=0.75\textwidth]{fig-2-5}
+		\includegraphics[width=0.7\columnwidth]{fig-2-5}
 		\caption{System Model - \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth]{average_queue_over_time-3}
+		\includegraphics[width=0.7\textwidth]{average_queue_over_time-3}
 		\caption{System Model - \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} after \eqn{250} transmissions}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth]{fig-3-2}
+		\includegraphics[width=0.7\textwidth]{fig-3-2}
 		\caption{System Model - \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 3,2,8,4,1 \rbrace}}
@@
 		\centering
-		\includegraphics[width=0.75\textwidth]{fig-9-3}
+		\includegraphics[width=0.7\textwidth]{fig-9-3}
 		\caption{System Model - \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace}}

### 2016-02-08 IEEE TSP - Incl Bios/Report/biography.tex
updated TSP submission

\begin{IEEEbiography}{Ganesh Venkatraman}
	(S'14) received the B.E. degree in electronics and communications engineering from the Madras University, Chennai, India in 2003, and the M.S. degree in electrical engineering from the Indian Institute of Technology (IIT) Madras, Chennai, India in 2006. He is currently pursuing the Dr. Sc. (Tech.) degree in the Department of Communication Engineering (DCE), Centre for Wireless Communications (CWC), University of Oulu, Oulu, Finland. %Prior to this, he worked as a Design Engineer in the Freescale Semiconductor India Pvt. Ltd., Noida, India during the year (2010-2011) and as a Research Engineer at the Center of Excellence in Wireless Technology (CEWiT), Chennai, India during the year (2008-2010). 
	His research interests include radio resource management, transceiver algorithms for wireless communications, and signal processing techniques in baseband implementation.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[trim=0cm 1.2cm 0.2cm 0.3cm,clip,scale=0.52]{TolliAntti_0.jpg}}]{Antti T\"olli}
(M'08, SM'14) received the Dr.Sc. (Tech.) degree in electrical engineering from the University of Oulu, Oulu, Finland, in 2008. Before joining the Department of Communication Engineering (DCE) and Centre for Wireless Communications (CWC) at the University of Oulu, he worked for 5 years with Nokia Networks, IP Mobility Networks Division, as a Research Engineer and Project Manager both in Finland and Spain. In May 2014, he was granted a five year (2014--2019) Academy Research Fellow post by the Research Council for Natural Sciences and Engineering of the Academy of Finland. He also holds an Adjunct Professor position with the DCE, University of Oulu. During the academic year 2015-2016, he holds a visiting position at EURECOM, Sophia Antipolis, France. He has authored more than 120 papers in peer-reviewed international journals and conferences and several patents all in the area
of signal processing and wireless communications. His research interests include radio resource management and transceiver design for broadband wireless communications with a special emphasis on distributed interference management in heterogeneous wireless networks. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[trim=2cm 1cm 3cm 1cm,clip,scale=0.18]{Markku_Juntti_200x200mm.jpg}}]{Markku Juntti}
(S'93-M'98-SM'04) received his M.Sc.\ (EE) and Dr.Sc.\ (EE) degrees from University of Oulu, Oulu, Finland in 1993 and 1997, respectively.

Dr.\ Juntti was with University of Oulu in 1992--98. In academic year 1994--95, he was a Visiting Scholar at Rice University, Houston, Texas. In 1999--2000, he was a Senior Specialist with Nokia Networks. Dr.\ Juntti has been a a professor of communications engineering since 2000 at University of Oulu, Department of Communication Engineering (DCE) and Centre for Wireless Communications (CWC), where he leads the Communications Signal Processing (CSP) Research Group. In 2014--2017, he also serves as Dean of University of Oulu Graduate School. His research interests include signal processing for wireless networks as well as communication and information theory. He is an author or co-author in some 350 papers published in international journals and conference records as well as in books {\it WCDMA for UMTS} and {\it Signal Processing Handbook}. Dr.\ Juntti is also an Adjunct Professor at Department of Electrical and Computer Engineering, Rice University, Houston, Texas, USA.

Dr.\ Juntti is an Editor of \textsc{IEEE Transactions on Communications} and was an Associate Editor for \textsc{IEEE Transactions on Vehicular Technology} in 2002--2008. He was Secretary of IEEE Communication Society Finland Chapter in 1996--97 and the Chairman for years 2000--01. He has been Secretary of the Technical Program Committee (TPC) of the 2001 IEEE International Conference on Communications (ICC'01), and the Co-Chair of the Technical Program Committee of 2004 Nordic Radio Symposium and 2006 IEEE International Symposium on Personal, Indoor and Mobile Radio Communications (PIMRC 2006), and the General Chair of 2011 IEEE Communication Theory Workshop (CTW 2011). He has served as Co-Chair of the Signal Processing for Communications Symposium of GLOBECOM 2014.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[trim=0cm 0cm 0.5cm 0cm,clip,scale=0.094]{Nam_Tran.jpg}}]{Le-Nam Tran}
	(M'10) received the B.S. degree in electrical engineering from Ho Chi Minh City University of Technology, Ho Chi Minh City, Vietnam, in 2003 and the M.S. and Ph.D. degrees in radio engineering from Kyung Hee University, Seoul, Korea, in 2006 and 2009, respectively. In 2009, he joined the Department of Electrical Engineering, Kyung Hee University, as a Lecturer. From 2010 to 2014, he had held postdoctoral positions at the Signal Processing Laboratory, ACCESS Linnaeus Centre, KTH Royal Institute of Technology, Sweden and the Centre for Wireless Communications and the Department of Communications Engineering, University of Oulu, Finland. Since Sep. 2014, he has been a lecturer at the Department of Electronic Engineering, Maynooth University, Co. Kildare, Ireland. His current research interests include multiuser MIMO systems, energy-efficient communications, full-duplex transmission, and applications of optimization techniques.
\end{IEEEbiography}

### 2016-02-08 IEEE TSP - Incl Bios/Report/convergence_distributed.tex
updated TSP submission

--- 2015-11-27 Report/convergence_distributed.tex
@@
-\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution.
+Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution.
 To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}.
@@
 Therefore, by using the above facts and as \eqn{j \to \infty}, the convergence of the primal decomposition method follows \cite[Prop.
-8.2.6]{bertsekas2003convex} by using a diminishing step size in each subgradient update.}
+8.2.6]{bertsekas2003convex} by using a diminishing step size in each subgradient update.
 
@@
 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}.
-Therefore, if both the primal and the \ac{ADMM} methods are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the whole sequence of iterates generated by the distributed algorithms is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}
+Therefore, if both the primal and the \ac{ADMM} methods are allowed to converge to the centralized solution in each \ac{SCA} step, then every limit point of the whole sequence of iterates generated by the distributed algorithms is a stationary point of \eqref{con} by following the discussions in Appendix \ref{sec-3.5}.
 

### 2016-02-08 IEEE TSP - Incl Bios/Report/dual_approach.tex
updated TSP submission

--- 2015-11-27 Report/dual_approach.tex
@@
 
-\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are carried out until convergence or for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
+Assuming that the following conditions are satisfied by the distributed schemes in each \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) the distributed methods are carried out until convergence or for \eqn{j \to \infty}, then the convergence analysis follows the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}.
 Moreover, it is still valid even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, since the strict monotonic decrease in the objective sequence can still be ensured.
@@
 In such a case, convergence of the distributed algorithms cannot be ensured, since it is impossible to show that the objective value is monotonically decreasing in each \ac{SCA} update step.
-We recall that in each primal or \ac{ADMM} iteration, the global objective cannot be guaranteed to decrease monotonically.}
+We recall that in each primal or \ac{ADMM} iteration, the global objective cannot be guaranteed to decrease monotonically.
 

### 2016-02-08 IEEE TSP - Incl Bios/Report/kkt_mse_approach.tex
updated TSP submission

--- 2015-11-18 Report/kkt_mse_approach.tex
@@
 Similar work has been considered for the \ac{WSRM} problem with minimum guaranteed rate constraints in \cite{kaleva2013decentralized}.
-Since the work in \cite{kaleva2013decentralized} is similar to the \ac{Q-WSRME} scheme with an additional maximum rate constraint as in \eqref{eqn-3.1.4}, the formulation in \cite{kaleva2013decentralized} require explicit dual variables to handle the maximum rate constraint, thereby making the problem difficult to solve in an iterative manner.
-
 However, in the proposed scheme, the maximum rate constraints are implicitly handled by the objective function without any need for explicit constraints.
@@
 Since the dual variables \me{\alpha^{(i)}} and \me{\sigma^{(i)}} are interdependent in \eqref{kkt-mse-4}, one has to be fixed to optimize for the other.
-So, \me{\alpha^{(i)}} is fixed to evaluate \me{\sigma^{(i)}} using \eqref{kkt-mse-4}.
-At iteration \eqn{i}, the dual variables \me{\alpha^{(i)}} is a point in the line segment between \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} determined by using a diminishing or a fixed step size \me{\rho^{(i)} \in (0,1)}.
+So, \me{\alpha^{(i)}} is fixed to evaluate \me{\sigma^{(i)}} using \eqref{kkt-mse-4.2}.
+At iteration \eqn{i}, the dual variable \me{\alpha^{(i)}} is a point in the line segment between \me{\alpha^{(i-1)}} and \me{\tfrac{\sigma^{(i)}}{\epsilon^{(i)}}} determined by using a diminishing or a fixed step size \me{\rho^{(i)} \in (0,1)}.
 The choice of \eqn{\rho^{(i)}}, which depends on the system, affects the convergence behavior and also controls the oscillations in the users' rate when \me{\sigma^{(i)}} is negative (before projection) due to over-allocation.
@@
 	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
-	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
+	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l,k,n}}
 	\KwInit{\me{i=1}, \me{\mbf{w}^{(0)}_{l,k,n}, \tilde{\epsilon}_{l,k,n}} randomly, dual variables \me{{\alpha}_{l,k,n}^{(0)} = 1}, and \me{I_{\max}} for certain value}

### 2016-02-08 IEEE TSP - Incl Bios/Report/manuscript.tex
updated TSP submission

--- 2015-08-11 Report/manuscript.tex
@@
-\documentclass[10pt,journal,final,letterpaper,onecolumn]{./../Styles/IEEEtran}
+\documentclass[10pt,journal,final,letterpaper,twocolumn]{./../IEEE/IEEEtran/IEEEtran}
 
@@
 \usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
-\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases,algorithmic}
+\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases,algorithmic,placeins}
 
-\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}}
-\DeclareGraphicsExtensions{.eps}
+\graphicspath{{./../Figures/}{./../Bios/}}
+\DeclareGraphicsExtensions{.pdf}
 
@@
 
-\ifCLASSINFOpdf
-\epstopdfsetup{update,prepend,prefersuffix=false,suffix=}
-\DeclareGraphicsRule{.eps}{pdf}{.pdf}{`epstopdf #1}
-\pdfcompresslevel=9
-\fi
-
 \input{shortcuts}
 \input{acronyms}
-
-\newtoggle{includereview}
-\newtoggle{enable_dist_fig}
 \newtoggle{single_column}
-\toggletrue{single_column}
-\togglefalse{enable_dist_fig}
-
-\iftoggle{single_column}{
-	\doublespacing
-}
+\togglefalse{single_column}
 
@@
 \author{
-	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Innovation (Tekes), Nokia Networks, Xilinx, Elektrobit and the Academy of Finland.
+	\IEEEauthorblockN{Ganesh Venkatraman \IEEEmembership{Student Member,~IEEE}\thanks{This work has been supported by the Finnish Funding Agency for Innovation (Tekes), Nokia Networks, Xilinx, Elektrobit, the Riitta ja Jorma Takanen Foundation, and the Academy of Finland.
+This work was supported by a research grant from Science Foundation Ireland and is co-funded by the European Regional Development Fund under Grant 13/RC/2077.
 Part of this work is presented in ICASSP 2014.}, Antti T\"{o}lli \IEEEmembership{Senior Member,~IEEE}, Markku Juntti \IEEEmembership{Senior Member,~IEEE}, and Le-Nam Tran \IEEEmembership{Member,~IEEE}}\thanks{
@@
 T\"{o}lli and M.
-Juntti are with Centre for Wireless Communications (CWC), Department of Communications Engineering (DCE), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{L.-N.
-Tran was with Centre for Wireless Communications (CWC), Oulu, FI-90014.
-He is now with the Department of Electronic Engineering, Maynooth University, Maynooth, Co.
-Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie)}}
+Juntti are with Department of Communications Engineering (DCE), Centre for Wireless Communications (CWC), University of Oulu, Oulu, FI-90014, (e-mail: \{ganesh.venkatraman, antti.tolli, markku.juntti\}@ee.oulu.fi)}\thanks{L.-N.
+Tran is with the Department of Electronic Engineering, Maynooth University, Maynooth, Co.
+Kildare, Ireland, (e-mail:ltran@eeng.nuim.ie).}}
 
@@
 \begin{IEEEkeywords}
-Convex approximations, \ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \acs{WSRM}.
+\ac{MIMO}-\acs{IBC}, \ac{MIMO}-\ac{OFDM}, precoder design, \acs{SCA}, \acs{WSRM}, nonconvex problem, convergence analysis.
 \end{IEEEkeywords}
@@
 
-\bibliographystyle{./../Styles/IEEEtran}
+\bibliographystyle{./../IEEE/IEEEtranBST/IEEEtran}
 \bibliography{./../Library/IEEEabrv,./../Library/kirja_survey}
 
+%\input{biography}
+
 \end{document}

### 2016-02-08 IEEE TSP - Incl Bios/Report/queue_minimizing_intro.tex
updated TSP submission

--- 2015-07-16 Report/queue_minimizing_intro.tex
@@
 Since the scheduling of users in each sub-channel is achieved by allocating zero transmit power over certain sub-channels, our solutions perform joint precoder design and user scheduling.
-Before discussing the proposed solutions, we consider the existing algorithm to minimize the number of backlogged packets with additional constraints required by the problem.
+Before discussing the proposed solutions, we consider an existing algorithm to minimize the number of backlogged packets with additional constraints required by the problem.

### 2016-02-08 IEEE TSP/TeX/convergence_centralized.tex
updated TSP submission

--- 2015-11-27 Report/convergence_centralized.tex
@@
 The uniqueness condition in (a) is required to ensure strict monotonicity in the objective sequence.
-Therefore, upon satisfying the conditions (a)-(d), we can show that the objective sequence generated by Algorithm \ref{algo-1} converges, by using \cite[Th.
+Therefore, upon satisfying the conditions (a)-(d), we can show that the objective sequence generated by Algorithm \ref{algo-1} converges by using \cite[Th.
 3.14]{rudin1964principles}.
-Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that \reviewF{every limit point of sequence of iterates is a stationary point of nonconvex problems in \eqref{eqn-6} and \eqref{eqn-mse-1}}.
+Then, by following the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that every limit point of sequence of iterates is a stationary point of nonconvex problems in \eqref{eqn-6} and \eqref{eqn-mse-1}.
 
@@
 Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured in each \ac{SCA} step \cite{scutari2010convex}.
-\reviewF{Furthermore, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is also bounded, we can show that the objective sequence converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}, and let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}]} be a stacked vector of the corresponding minimizer of \eqref{con-m} when \eqn{k \to \infty} in \ac{AO} step \eqn{i}.}
+Furthermore, by using the fact that \eqn{\{f(\mbf{z}^{(i)}_k)\}} is also bounded, we can show that the objective sequence converges as \eqn{k \to \infty} in \ac{AO} step \eqn{i}, and let \eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq [\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}]} be a stacked vector of the corresponding minimizer of \eqref{con-m} when \eqn{k \to \infty} in \ac{AO} step \eqn{i}.
 
@@
 
-Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
+Finally, to prove the global convergence of the objective sequence, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
 \iftoggle{single_column}{
@@
 \end{equation}
-\reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}.
+Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}.
 Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges.
-Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in each \ac{SCA} and \ac{AO} step.}
+Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in each \ac{SCA} and \ac{AO} step.
 
 \subsection{Stationarity of Limit Points} \label{c-b}
-\reviewF{We now discuss the convergence properties of sequence of iterates.
+We now discuss the convergence properties of sequence of iterates.
 For convenience, let us consider a unified superscript \eqn{t} to refer to the index of both \ac{SCA} and \ac{AO} procedures (\textit{i.e.}, index \eqn{t} denotes \ac{SCA} step \eqn{k} and \ac{AO} step \eqn{i}).
@@
 However, due to compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\} \subset \mc{F}} is bounded.
-Therefore, the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it, by following \cite[Prop.
+Therefore, the sequence \eqn{\{\mat{t}\}} has at least one limit such that there exists a subsequence of \eqn{\{\ma^t\}} that converges to it by following \cite[Prop.
 A.5]{bertsekas1999nonlinear}.
@@
 Now, by using the strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}.
-Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}.
+Furthermore, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}.
 Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop.
@@
 \begin{equation} \label{seq_mon1}
-\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
+\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub
 \end{equation}
-Thus, \eqn{\bar{\ma}} is a stationary point, and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of \eqref{con-m}.
+thus, \eqn{\bar{\ma}} is a stationary point. Moreover, by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point of~\eqref{con-m}.
 
@@
 2]{scutari_1} and \cite[Prop.
-3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}
+3.2]{amir}, we can show that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.
 %using \cite[Thms.

### 2016-02-08 IEEE TSP/TeX/introduction.tex
updated TSP submission

--- 2015-11-19 Report/introduction.tex
@@
 The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
-In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users existing in the network.
-We consider the problem of transmit precoder design and resource allocation over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}.
-Thus, the problem of interest inherently includes resource allocation of users associated with different \acp{BS}.
+In a network with multiple \acp{BS} serving multiple users, the driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the users in the network.
+We consider the problem of transmit precoder design and resource allocation over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to reduce the number of queued packets in the \acp{BS}.
+%Thus, the problem of interest inherently includes resource allocation of users associated with different \acp{BS}.
 

### 2016-02-08 IEEE TSP/TeX/joint_wsrm_formulation.tex
updated TSP submission

--- 2015-07-20 Report/joint_wsrm_formulation.tex
@@
 The queue minimizing algorithms have been studied extensively in the networking context to provide congestion-free routing between any two nodes in the network.
-One such is the \emph{backpressure algorithm} \cite{georgiadis2006resource,neely2010stochastic}.
+One such is the \emph{backpressure algorithm} \cite{neely2010stochastic}.
 It finds an optimal control policy in the form of rate or resource allocation by considering differential backlogged packets between any two entities.
@@
 The above approach was extended to the wireless networks in \cite{weeraddana2011resource}, in which the queues were used as weights in the \ac{WSRM} formulation to determine the transmit precoders.
-Since the expectation is minimized by minimizing the function inside, the \ac{Q-WSRM} formulation is given by
+Since \eqref{backpressure-approx} is minimized by maximizing the function inside expectation, the \ac{Q-WSRM} formulation is given by
 \begin{IEEEeqnarray}{LCl} \label{q_gen_sum} \neqsub
-\underset{\substack{\mvec{m}{l,k,n}, \mvec{w}{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \Big ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \Big ) \IEEEyessubnumber \label{eqn-3.1.1} \\
-\text{subject to.} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \fall b.
+\underset{\substack{\mvec{m}{l,k,n},\\ \mvec{w}{l,k,n}}}{\text{maximize}} &\quad& \sum_{k \in \mc{U}} \, Q_k \Big ( \sum_{n = 1}^N \sum_{l=1}^L \log_2(1 + \gamma_{l,k,n}) \Big ) \IEEEyessubnumber \label{eqn-3.1.1} \\
+\text{subject to} & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \fall b.
 \IEEEyessubnumber \eqspace \label{eqn-3.1.3}

### 2016-02-08 IEEE TSP/TeX/mse_formulation.tex
updated TSP submission

--- 2015-11-27 Report/mse_formulation.tex
@@
 In all our numerical simulations, the objective sequence generated by Algorithm \ref{algo-1} converges.
-\reviewF{However, to provide a formal convergence analysis, we consider using a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
+However, to provide a formal convergence analysis, we consider using a regularized objective in \eqref{mod_obj} instead of using \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}.
 The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of the minimizer in each iteration.
@@
 Nevertheless, we can limit \eqn{\beta_{l,k,n}}'s by using a maximum interference threshold depending on \eqn{P_{\max}} and the channel gains, and thus the feasible set can be bounded without affecting the optimality of the considered problem.
-With the above assumptions, convergence analysis of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}
+With the above assumptions, convergence analysis of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.
 

### 2016-02-08 IEEE TSP/TeX/system_model.tex
updated TSP submission

--- 2015-08-22 Report/system_model.tex
@@
 \begin{equation}\label{eqn-1}
-\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n}
+\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \sum_{j = 1}^L \mvec{m}{j,k,n} d_{j,k,n} + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n}
 \end{equation}
@@
 \begin{multline}\label{eqn-1}
-\hat{d}_{l,k,n} = \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \,\mvec{m}{l,k,n} d_{l,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n} \\ 
+\hat{d}_{l,k,n} = \textstyle \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \sum_{j = 1}^L \mvec{m}{j,k,n} d_{j,k,n} + \mvec{w}{l,k,n}^\herm \mvec{n}{l,k,n} \\ 
 + \mvec{w}{l,k,n}^\herm \sum_{i \in \mc{U} \backslash \set{k}} \mvec{H}{b_i,k,n} \sum_{j = 1}^L \mvec{m}{j,i,n}d_{j,i,n}
@@
 where \me{t_{l,k,n}} denotes the number of transmitted packets or bits over the \me{\ith{l}} spatial stream on the \me{\ith{n}} sub-channel.
-The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}.\footnote{The upper bound can be achieved by using Gaussian signaling.} Note that \me{t_k} and \me{Q_k} are represented by the same units, \textit{i.e.}, in bits defined per channel use.
+The maximum rate achieved over the space-frequency resource \me{(l,n)} is given by \me{t_{l,k,n} \leq \log_2(1 + \gamma_{l,k,n})} for the \ac{SINR} \me{\gamma_{l,k,n}}.\footnote{The upper bound can be achieved by using Gaussian signaling.} The variables \me{t_k} and \me{Q_k} are represented by the same units, \textit{i.e.}, in bits defined per channel use.

### 2016-02-08 Report/biography.tex
updated TSP submission

--- 2016-02-08 IEEE TSP - Incl Bios/Report/biography.tex
@@
-\begin{IEEEbiography}{Ganesh Venkatraman}
+\begin{IEEEbiography}[{\includegraphics[trim=0cm 1.2cm 0.2cm 0.3cm,clip,scale=0.52]{TolliAntti_0.jpg}}]{Ganesh Venkatraman}
 	(S'14) received the B.E.
@@
 (Tech.) degree in the Department of Communication Engineering (DCE), Centre for Wireless Communications (CWC), University of Oulu, Oulu, Finland.
-%Prior to this, he worked as a Design Engineer in the Freescale Semiconductor India Pvt.
+Prior to this, he worked as a Design Engineer in the Freescale Semiconductor India Pvt.
 Ltd., Noida, India during the year (2010-2011) and as a Research Engineer at the Center of Excellence in Wireless Technology (CEWiT), Chennai, India during the year (2008-2010).
@@
 
-\begin{IEEEbiography}[{\includegraphics[trim=0cm 0cm 0.5cm 0cm,clip,scale=0.094]{Nam_Tran.jpg}}]{Le-Nam Tran}
+\begin{IEEEbiography}[{\includegraphics[scale=0.094]{Nam_Tran.jpg}}]{Le-Nam Tran}
 	(M'10) received the B.S.

### 2016-02-08 Report/manuscript.tex
after 3A + 1R
submitted
updated
updated TSP submission

@@
 \usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
-\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases,algorithmic}
+\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases,algorithmic,placeins}
 
-\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}}
+\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}{./../Figures/Bio/}}
 \DeclareGraphicsExtensions{.eps}
@@
 
-\bibliographystyle{./../Styles/IEEEtran}
+\bibliographystyle{./../IEEE/IEEEtranBST/IEEEtran}
 \bibliography{./../Library/IEEEabrv,./../Library/kirja_survey}
 
+\input{biography}
+
 \end{document}
